### 2023-02-08 2023-1-19/efficient_way_for_counting.tex
version with complement

%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}
%% NOTE that a single column version is required for 
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to 
%% \documentclass[manuscript,screen]{acmart}
%% 
%% To ensure 100% compatibility, please check the white list of
%% approved LaTeX packages to be used with the Master Article Template at
%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
%% before creating your document. The white list page provides 
%% information on how to submit additional LaTeX packages for 
%% review and adoption.
%% Fonts used in the template cannot be substituted; margin 
%% adjustments are not allowed.

\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary {arrows.meta, automata, positioning, fit}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%
%  Uncomment \acmBooktitle if th title of the proceedings is different
%  from ``Proceedings of ...''!
%
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%  June 03--05, 2018, Woodstock, NY} 
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/22/12}
% set algorithmicx

\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

\newcommand*{\red}[1]{\textcolor{red}{#1}}

\newcommand*{\myvec}[1]{\bar{#1}}
\newcommand*{\regex}{\mathcal{R}}
\newcommand*{\strsort}{\verb|Str|}
\newcommand*{\intsort}{\verb|Int|}
\newcommand*{\lan}{\mathcal{L}}
\newcommand*{\highlight}[1]{\textbf{\textit{#1}}}
\newcommand*{\aut}{\mathcal{A}}
\newcommand*{\algfun}[1]{\texttt{#1}}
\newcommand*{\strlen}[1]{\texttt{len}(#1)}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Efficient Methods for Solving String Constraints with Large Repetition Bound}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{DengHang Hu}
% \authornote{Both authors contributed equally to this research.}
\affiliation{%
  \institution{State Key Laboratory of Computer Science,
    Institute of Software, Chinese Academy of Sciences}
  \city{}
  \country{}
}
\email{hudh@ios.ac.cn}

\author{Zhilin Wu}
% \authornote{Both authors contributed equally to this research.}
\affiliation{%
  \institution{State Key Laboratory of Computer Science,
    Institute of Software, Chinese Academy of Sciences}
  \city{}
  \country{}
}
\email{wuzl@ios.ac.cn}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Regular expression with large repetition bounds frequently appears in the real world. However, state-of-art string solvers can not efficiently solve string constraints with large
  repetition bounds, which slows down string constraint
  applications like formal verification and symbolic execution. In this paper, we
  propose a new systematic algorithm based on the decision procedure in our previous work to solve the problem efficiently. We use
  heuristic ways like over-approximation and under-approximation to accelerate the search. Further, we extract amounts of regex expressions with repetition
  times from real-world programs and generate a significant benchmark. We evaluate the algorithm's performance on our generated
  and developed benchmarks. The result shows that our solver outperforms the state-of-art string solvers.

\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
% \begin{CCSXML}
% <ccs2012>
%    <concept>
%        <concept_id>10003752.10003766.10003776</concept_id>
%        <concept_desc>Theory of computation~Regular languages</concept_desc>
%        <ignificance>500</concept_significance>
%        </concept>
%  </ccs2012>
% \end{CCSXML}

\ccsdesc[500]{Theory of computation~Regular languages}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{string constraints, cost-enriched automata, regex expression, bounded repetition}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
% \begin{teaserfigure}
%   \includegraphics[width=\textwidth]{sampleteaser}
%   \caption{Seattle Mariners at Spring Training, 2010.}
%   \Description{Enjoying the baseball game from the third-base
%   seats. Ichiro Suzuki preparing to bat.}
%   \label{fig:teaser}
% \end{teaserfigure}

% \received{20 February 2007}
% \received[revised]{12 March 2009}
% \received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
Regular expressions are widely used in programming languages such as Javascript and Python. About 30–40 \% of Java, JavaScript, and Python software uses regex
matching\cite{redos_fse2019}. To find
potential software bugs automatically, many researchers prefer to use one of the
formal verification technology - symbolic execution \cite{symbolic_pldi2021}. Symbolic execution views symbolic paths as multi-theories
constraints and uses a constraints solver to solve these constraints. Thus the
efficiency and the ability of the constraints solver are vitally important.
However, the string theory is one of the most challenging theories in multi-theory constraints because it is easy to be undecidable\cite{undecidable_2016}. So the string constraints solver with the higher
ability (support more operators) usually performs slower. Most solvers try very hard to improve efficiency. For example, Z3 and cvc5 append many heuristic
derivation rules to speed up their search in the DPLL framework. Trau+ proposes
a new model called flat automaton and uses the CEGAR framework to under-approximate
and over-approximate the string constraints again and again.
Unfortunately, the string solvers above perform poorly when the string constraints contain large repetition bound. The DPLL-framework string solvers prefer to
search model strings with smaller lengths, but large repetition bound most often stands
for considerable model string lengths. The automaton-based solvers
unwind the automaton naively, so the search space of the unwound automaton is
exponential of the repetition bound. To address this issue, we extend
cost-enriched finite automaton\cite{atva2020} whose search space is linear to the
repetition bound. Our main contributions are:
\begin{enumerate}
  \item We extend cost-enriched finite automaton to model the extended regular expression with large repetition bound.
  \item We devise an efficient algorithm to solve string constraints with large repetition bound with the new automaton model.
  \item We generate many instances with large repetition bound from real-word regular expressions.
  \item We implemented our efficient algorithm on ostrich and compared it with state-of-art string solvers. The result shows the superiority of our automaton model and algorithm.
\end{enumerate}
%TODO: list the main contributions
The structure of this paper is as follows: We introduce some abbreviations and concepts in section \ref{sec:pre} and introduce the syntax and semantics of the string theory logic in section \ref{sec:str_t}. Then we develop cost-enriched finite automaton model and its operations at section \ref{sec:cefa}. The efficient algorithm is discussed in section \ref{sec:solve}, and the implementation of the algorithm is mentioned in section \ref{sec:imp}. Finally, we conclude our work and look into future work in section \ref{sec:conclu}.

\section{Preliminaries} \label{sec:pre}
%TODO: preliminaries
\highlight{Tokens.} We consider a finite \emph{alphabet} $\Sigma$, the set of all \emph{letters}. A
\emph{string} is a finite sequence of letters from $\Sigma$. We use $\Sigma^*$ to
denote the set of strings over $\Sigma$, $\epsilon$ to denote the empty string, and $a,
  b,\cdots$ to denote constant letters in $\Sigma$. We use $u, v,\cdots$ to denote constant
string and $x, y,\cdots$ to denote variable string. Moreover, we also consider a set of natural integer numbers $\mathbb{N} = \{0,1,2,3,\cdots\}$ and a set of integer numbers $\mathbb{Z}= \{\cdots, -1, 0, 1, \cdots\}$. We use $m,n,\cdots$ to
denote constant integer, and $i,j\cdots$ to denote variable integer. For vector, we use $\bar{v}$ to denote the vector of constant integer, $0_n$ to denote the zero vector with length $n$, $|\bar{v}|$ to denote the length of $|\bar{v}|$, and $v(i)$ to denote the integer value of $\bar{v}$
at position $i$, and $\cdot$ to denote the concatenation of two vectors.\newline
\highlight{CNF, DNF, clause, cube.} We assume that the reader is familiar with first-order logic. A \emph{literal} is an atomic proposition or its negation. Briefly, A \emph{clause} is a disjunction of literals. The empty clause is $false$. A formula is in \emph{conjunctive normal norm} (CNF) if it is a conjunction of clauses. A \emph{cube} is a conjunction of a consistent set of literals; The empty cube is $true$. A formula is in \emph{disjunctive normal form} (DNF) if it is a disjunction of cubes.\newline
\highlight{Basic Regular Language.} A nondeterministic finite state automaton (NFA) is a tuple $\aut=(Q, \Sigma, \delta, I, F)$ where $Q$ is a finite set of states; $\Sigma$ is a finite alphabet; $\delta\in Q\times\Sigma\times Q$ is the transition relation; $I, F\subseteq Q$ are the set of initial states and finite states respectively. We write a transition $(q, a, q') \in \delta$ as $q\xrightarrow{a} q'$ for readability. A \emph{run} of an NFA $\aut$ on a string $w = a_1\cdots a_n$ is a sequence of transitions $q_0\xrightarrow{a_1}q_1\cdots q_{n-1}\xrightarrow{a_n}q_n$ with $q_0\in I$. The run is \emph{accepting} if $q_{n}\in F$. A word $w$ is \emph{accepted} by an NFA $\aut$ if there is an accepting run on $w$. The \emph{language} of $\aut$ is the set of all words accepted by $\aut$, denoted by $\lan(\aut)$. From automata theory\cite{aut_hopcraft}, we know that the languages generated by basic regular expression are also in the class of $\lan(\aut)$. We call them \emph{Basic Regular Language}.
\section{String Theory with Extended Regex} \label{sec:str_t}
% TODO: Syntax and semantic
\subsection{Syntax}
In this paper, we extend string theory in our previous work \cite{atva2020} with extended regex. We call
the new theory as \textit{Extended String Logic (ESL)}. ESL contains the following
sorts: string sort \verb|Str|, integer sort \verb|Int|, the enumerable set of string
sort $\verb|Str|^m$, and the enumerable set of integer sort $\verb|Int|^m$ for each $m\in
  \mathbb{N}$. Furthermore, ESL includes the following predicate and function constants:
string concatenation $\verb|con|:\verb|Str|\times\verb|Str|\rightarrow \verb|Str|$;
string length $\verb|len|: \verb|Str|\rightarrow \verb|Int|$; regular membership $\in:
\verb|Str|\times \verb|Str|^m$; the basic regex operators such as Kleene, concatenation,  conjunction, and disjunction; the extended regex operator repetition and complement; and the usual constants of linear arithmetic.

The syntax of ESL is presented in Table\ref{tab:syntax}. $\varphi$ is a first-order logic formula that can be a regular membership $x\in\regex$,
a word equation $e$, a linear arithmetic (in)equality $\beta$, a negation of a formula, or a
disjunction of two formulas. A word equation $e$ is an equality of two string terms. The
(in)equality operator $\odot$ contains $=, \geq$. $\beta$ is an (in)equality
of two integer terms. A string term $s$ is an empty string $\epsilon$, letters
$a\in\Sigma$, string variable $x$, or a concatenation of two string terms. An integer
term $\alpha$ is an integer constant 0, integer constant 1, integer variable $i$, the
length of the string term $s$, minus an integer term, or plus of two integer terms. The
regular expression $\regex$ is built on empty string $\epsilon$, constant letter $a\in \Sigma$. The supported regex operations involve concatenation $\cdot$, disjunction $+$,
intersection $\times$, Kleene $*$, complement $C$, and repetition $\{m, n\}$.

We use function $FV(\varphi)$ to return all free variables of $\varphi$. We consider \emph{straight-line} fragment\cite{atva2020}\cite{quadratic_aplas2018} of this string theory logic. A word equation \emph{cube} $\bigwedge_{i=1}^n e_i$ is said to be straight-line if it can be rewritten as the form $\bigwedge_{j=1}^m x_j = s_j$ such that: (i) $x_1, \cdots, x_m$ are different variables; and (ii) $FV(s_j)\cap \{x_1, x_2,
  \cdots, x_{j-1}\} = \emptyset$. A formula $\varphi = (\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$
is said to be straight-line if $\bigwedge_{i=1}^n e_i$ is straight-line, $\Re$ is a
\emph{tube} of regular membership $x\in \regex$ or its negation $x\not\in \regex$, and $P$ is a Presburger arithmetic formula.

Note that we can convert an ESL formula to a DNF formula such that each term in the DNF
formula is the form $(\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$ where $P$ is a
Presburger formula. We call the form $(\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$ as \emph{normal form}. The straight-line fragment is similar to the SSA form of the
program.  Sometimes we use $s_1s_2$ to stand for $\verb|concat|(s_1,s_2)$ and $|x|$ to
stand for $\verb|len|(x)$.
\begin{table}
  \begin{tabular}{l}
    $\regex$ ::= $\epsilon\mid a\mid \regex\cdot\regex\mid \regex+\regex\mid \regex\times \regex\mid \regex^*\mid\regex^C \mid \regex\{m,n\}$ \\
    $\varphi$ ::= $x\in \regex\mid e\mid\beta\mid \neg\varphi\mid \varphi\vee\varphi$                                                      \\
    $e$ ::= $s_1=s_2 $                                                                                                                     \\
    $\beta$ ::= $\alpha_1\odot \alpha_2$                                                                                                   \\
    $s$ ::= $\emptyset \mid \epsilon \mid a\mid x\mid \verb|concat|(s_1, s_2)$                                                             \\
    $\alpha$ ::= $0\mid 1\mid i \mid  \verb|len|(s)\mid -\alpha\mid \alpha_1+\alpha_2$
  \end{tabular}
  \caption{Syntax of ESL}
  \label{tab:syntax}
\end{table}

\begin{example}[Straight-line Formula]
  \begin{equation} \label{eq:1}
    \varphi_1 ::= x = \verb|concat|(y,z) \wedge y = z \wedge x\in a\{1,100\}
  \end{equation}
  The word equation cube
  $c ::= (x = \verb|concat|(y,z) \wedge y = z)$ is straight-line because it santisfy : (i) $FV(z) = \{z\}$, (ii)$\{z\}\cap\{x\} = \emptyset$. So the formula $\varphi_1 = c\wedge  x\in a\{1,100\}$ is also straight-line.
\end{example}

\begin{example}[Non Straight-line Formula]
  \begin{equation} \label{eq:1}
    \varphi_2 ::=  x = \verb|concat|(y,z) \wedge y = \verb|concat|(x,z) \wedge x\in a\{1,100\}
  \end{equation}
  $\varphi_2$ is not straight-line because the word equation cube\newline
  $(x = \verb|concat|(y,z) \wedge y = z)$ is not straight-line.
\end{example}

\subsection{Semantics}
\highlight{Extended Regular Language} We have introduced basic regular language at
section \ref{sec:preliminaries}. In our paper, we add a new operator \emph{repetition} $\regex\{m,n\}$, which means repeating regex $\regex$ at least $m$ times and at most $n$ times. Repetition can be syntactically rewritten by concatenation and disjunction:
$\regex\{m,n\} \equiv \regex^m\mid\cdots\mid\regex^n$ where $\regex^k$ defines concatenate $k$ times($m\leq k\leq n$) to $\regex$. However, if we naively rewrite the repetition operation, the automaton size will be huge (linear to repetition times), causing the search space to be exponential. To address the issue, we proposed a new automaton model called \emph{Cost-Enriched Finite Automaton (CEFA)}, whose size is constant to repetition times. CEFA can not handle nested repetition ($\regex\{m,n\}$ or $\regex *$, where $\regex$ contains the repetition operator). So we have to rewrite it syntactically when the regex contains nested repetition (e.g., $a\{1,100\}\{2,2\}$ is rewritten to $a\{1,100\}a\{1,100\}$). Our regular expression is semantically equal to basic regular language but syntactically extended. We call the language of our regex \emph{Extended Regular Language} and denote it to $\lan^e(\regex)$.\newline
\highlight{Semantics} We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables. $\eta: S\times\Sigma\rightarrow\Sigma^*$ is the interpretation on string where $\eta(c)=c$ for every letter $c\in \Sigma$ and $\eta(s_1s_2)=\eta(s_1)\eta(s_2)$. $\theta: I\rightarrow\mathbb{Z}$ is the interpretation of arithmetic that is the same as that of Presburger arithmetic. Then the semantics is given by a satisfaction relation: $\eta, \theta\models \varphi$ defined in Table \ref{tab:semantics}. We say a formula $\varphi$ is \emph{satisfiable} if a solution exists $(\eta, \theta)$ such as $\eta, \theta\models \varphi$. A formula $\varphi$ is \emph{unsatisfiable} if no solution exists.

\begin{table}[h]
  \begin{tabular}{lcl}
     $\eta,\theta \models \varphi_1\vee \varphi_2$ & $\mathsf{iff}$ & $\eta,\theta \models \varphi_1 \text{ or } \eta,\theta \models \varphi_2$\\
     $\eta,\theta \models \neg\varphi $          & $\mathsf{iff}$ & $\eta,\theta \not\models \varphi$\\
     $\eta, \theta \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan^e(\regex),\eta,\theta \models x = w$\\
     $\eta, \theta \models s_1 = s_2$              & $\mathsf{iff}$ & $\eta(s_1) = \eta(s_2)$\\
     $\eta, \theta \models \alpha_1\odot\alpha_2$  & $\mathsf{iff}$ & $\theta(\alpha_1) \odot \theta(\alpha_2) \text{ where } \odot = \{=, \geq \}$
  \end{tabular}
  \caption{Semantics}
  \label{tab:semantics}
\end{table}
\subsection{Problem}
In this paper, we consider the following problem:
\begin{table}[h]
  \begin{tabular}{l l}
    \hline
    \textbf{Problem:} & Is a ESL formula $\varphi$ satisfiable?                   \\
    \textbf{Input:}   & A straight-line ESL formula $\varphi$ in the normal form. \\
    \textbf{Output:}  & \emph{sat} or \emph{unsat}.                               \\
    \hline
  \end{tabular}
\end{table}

\section{Cost-Enriched Finite Automaton and Basic Operation} \label{sec:cefa}
%TODO: The definition of cost-enriched automata
%      The operation on the cost-enriched automata (union, intersection, complement, concatenate)
In this section, we will define the cost-enriched finite automaton and operations on it. The operations are intersection, union, complement, concatenation, and repetition.
\subsection{Cost-Enriched Finite Automaton}
\begin{definition}[Cost-Enriched Finite Automaton]
  A cost-enriched finite automaton(CEFA) $\aut$ is a tuple $(Q, \Sigma, \delta, I, F, R, \theta)$ where
  \begin{itemize}
    \item $Q,\Sigma,I,F$ is defined as NFA,
    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers. We use $\mathcal{V}(r_i)$ to denote the value of $r_1$. Note that the initial value of each register is 0,
    \item $\delta$ is the transition set whose elements are tuple $(q, a, q', \bar{v})$ where $q, q'$ are states in $Q$, $a$ is a letter in alphabet $\Sigma$ and $\bar{v}$ is vector of natural number. We write the transition $(q, a, q', \bar{v})$ as $q\xrightarrow[\bar{v}]{a} q'$ for readability.
    \item $\theta$ is the linear integer arithmetic on registers.
  \end{itemize}
  A \emph{run} of $\aut$ on string $a_1\cdots a_m$ is a transition sequence $q_0\xrightarrow[\bar{v_1}]{a_1}q_1\cdots q_{m-1}\xrightarrow[\bar{v_m}]{a_m}q_m$ such that $q_0\in I$ and $r_i = \displaystyle\sum_{j=1}^m v_j(i)$ for $r_i \in R$. The run is \emph{accepting} if $q_m\in F$ and $\theta[r_i/\mathcal{V}(r_i)]$ is satisfiable. Note that $\theta[r_i/\mathcal{V}(r_i)]$ means a substitution of all occurrences of $r_i$ in $\theta$ to its current value. A string word $w$ is accepted by $\aut$ if there is an accepting run of $\aut$ on $w$. The language of $\aut$ is the set of string words accepted by $\aut$, denoted by $\lan(\aut)$.
\end{definition}
\begin{example}[The CEFA  $\aut_{ab\{1,100\}}$ ] \label{eg:1}
  We build a CEFA $\aut_{ab\{1,100\}}$ (table \ref{fig:cefa1}) whose language is the language of the extended regular expression $ab\{1,100\}$. The transition set of $\aut_{ab\{1,100\}}$ are $\{q_0\xrightarrow[1]{a} q_1, q_1 \xrightarrow[0]{b} q_2, q_2 \xrightarrow[0]{\epsilon} q_0\}$. The register is $r_1$. And the linear arithmetic is $1\leq r_1\leq 100$. Intuitively, the accepted run of $\aut_{ab\{1,100\}}$ will repeatedly run word $ab$. The transition $q_0\xrightarrow[1]{a} q_1$ should appear at least once and at most 100 times because of the linear constraint $1\leq r_1 \leq 100$.
  \begin{figure}[h]
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every state/.style={draw=blue!50,very thick,fill=blue!20}, initial text=]

      \node[state,initial]            (q_0)                      {$q_0$};
      \node[state]                    (q_1) [right=of q_0]       {$q_1$};
      \node[state,accepting]          (q_2) [right=of q_1]       {$q_2$};

      \path[->] (q_0) edge              node      [above]           {a/1} (q_1)
      (q_1) edge              node      [above]           {b/0} (q_2)
      (q_2) edge [bend left]  node      [below]           {$\epsilon$/0} (q_0);
    \end{tikzpicture}
    \caption{$\aut_{ab\{1,100\}}$ where $R=(r_1)$ and $\theta = 1\leq r_1 \leq 100$}
    \label{fig:cefa1}
  \end{figure}
\end{example}
The example \ref{eg:1} gives a general picture of constructing a CEFA for a specific extended regex. Firstly, we build an NFA from the extended regex $\regex$
(e.g, To construct CEFA in example \ref{eg:1}, we firstly construct an NFA with
transition to be $q_0\xrightarrow{a} q_1\xrightarrow{b}q_2\xrightarrow{\epsilon}
  q_0$ and $I={q_0}, F={q_2}$). Secondly, we extend NFA to CEFA by adding
registers to $R$ and vectors $\bar{v}$ to each transition (e.g., we secondly add a
register $r_1$ to store repetition times and add vector $(1)$ to transition
$q_0\xrightarrow{a}q_1$ to update the repetition time). Finally, we set the
linear arithmetic $\theta$ carefully to restrict the accepted word to be
included in $\lan(\regex)$ (e.g., we finally set $\theta = 1\leq r_1\geq 100$ to
restrict the repetition times to $[1,100]$). Besides the special
operation repetition, other basic automaton operations are non-trivial. We individually discuss operations repetition, concatenation,
union, intersection, complement, and Kleene.

\subsection{Repetition}\label{subsec:rep}
Given a CEFA $\aut = (Q,\Sigma,\delta,I,F,R,\theta)$, its repetition with lower bound $l$ and upper bound $k$  is defined as $\aut_{rep} = (Q, \Sigma, \delta', I, F, R\cup\{r'\}, \theta\wedge l\leq r'\leq k )$ where
\begin{itemize}
  \item $r'$ is the new register,
  \item and $\delta'$ is composed by transitions $q\xrightarrow[(v_1, \cdots, v_n, 0)]{a} q'$ for all transitions $q\xrightarrow[(v_1, \cdots, v_n)]{a} q' \in \delta$, and transitions $q_m\xrightarrow[0_{n}\cdot 1]{\epsilon} q_0$  for all $q_m\in F$ and $q_0\in I$,
\end{itemize}
\begin{figure}[h]
  \begin{subfigure}{0.20\textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut$}
  \end{subfigure}
  \begin{subfigure}{0.20\textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a/\bar{v}\cdot \red{0}$} (q_1)
      (q_1) edge [bend right] node [above] {$\epsilon /0_n\cdot \red{1}$} (q_0);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The repetition of $\aut$}
  \end{subfigure}
  \caption{Repetition}
  \label{fig:rep}
\end{figure}
Figure \ref{fig:rep} illustrates the transition relation between $\aut$ and $\aut_{rep}$. Informally, $\aut_{rep}$ add a register $r_{n+1}$ to store the repetition time and update the repetition time on the transitions starting from the initial state. $\aut_{rep}$ add formula $l\leq r_{n+1}\leq k$ to ensure the repetition time is greater or equal to $l$ and less or equal to $k$.

\subsection{Concatenation}\label{subsec:con}
Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ where $R_1\cap R_2= \emptyset$ and $|R_1|=m,|R_2|=n$, the concatenation is defined as $\aut_{con}=(Q_1\cup Q_2, \Sigma, \delta', I_1, F_2, R_1\cup R_2, \theta_1\wedge\theta_2)$ where $\delta'$ is composed by
\begin{itemize}
  \item $q_1\xrightarrow[\bar{v_1}\cdot 0_n]{a} q_1'$ for each transition $q_1\xrightarrow[\bar{v_1}]{a} q_1' \in \delta_1$,
  \item $q_2\xrightarrow[0_m\cdot\bar{v_2}]{a} q_2'$ for each transition $q_2\xrightarrow[\bar{v_2}]{a} q_2' \in \delta_2$,
  \item and $q_1\xrightarrow[0_{m+n}]{\epsilon} q_2$ for each $q_1\in F_1$ and $q_2 \in I_2$.
\end{itemize}
\begin{figure}[h]
  \centering
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v_1}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_1$}
  \end{subfigure}
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v_2}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_2$}
  \end{subfigure}
  \begin{subfigure}{0.4\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state]    (q_1) [right=of q_0] {};
      \node[state]    (q_2) [right=of q_1] {};
      \node[state, accepting]    (q_3) [right=of q_2] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a/\bar{v_1}\cdot \red{0_n}$} (q_1)
      (q_1) edge node [below] {$\red{0_{m+n}}$} (q_2)
      (q_2) edge [bend right] node [below] {$a/\red{0_m}\cdot \bar{v_2}$} (q_3);
      \node [fit=(q_0) (q_1)] {$\cdots$};
      \node [fit=(q_2) (q_3)] {$\cdots$};
    \end{tikzpicture}
    \caption{The concatenation of $\aut_1$ and $\aut_2$}
  \end{subfigure}
  \caption{Concatenation}
  \label{fig:con}
\end{figure}
Figure \ref{fig:con} outlines the vector change on transitions when concatenating two CEFA. Without losing information, $\aut_{con}$ contains all registers in $\aut_1$ and $\aut_2$. Furthermore, $\aut_{con}$ update registers' value of $\aut_1$ and $\aut_2$ separately: $\aut_{con}$ only update registers of $R_1$ on the transitions of $\aut_1$ and update registers of $R_2$ on the transition of $\aut_2$. $\theta'$ is the conjunction of $\theta_1$ and $\theta_2$ to make sure all linear constraints in $\aut_1$ and $\aut_2$ are satisfiable.
\subsection{Intersection}\label{subsec:inter}
Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the intersection is defined as $\aut_{inter} = (Q_1\times Q_2, \Sigma, \delta', I_1\times I_2, F_1\times F_2, R_1\cup R_2, \theta_1\wedge \theta_2)$ where $\delta'$ is composed by
\begin{itemize}
  \item transitions $(q_1,q_2)\xrightarrow[\bar{v_1}\cdot\bar{v_2}]{a} (q_1',q_2')$ when both transition $q_1\xrightarrow[\bar{v_1}]{a}q_1'$ and transition $q_2\xrightarrow[\bar{v_2}]{a}q_2'$ exist in $\delta$.
\end{itemize}
\begin{figure}[h]
  \centering
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a$/$\bar{v_1}$} (q_1)
      (q_0) edge [bend left] node [above] {$b$/$\bar{v_1}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_1$}
  \end{subfigure}
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a$/$\bar{v_2}$} (q_1)
      (q_0) edge [bend left] node [above] {$c$/$\bar{v_2}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_2$}
  \end{subfigure}
  \begin{subfigure}{0.4\textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_3) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a$/\red{$\bar{v_1}\cdot \bar{v_2}$}} (q_3);
      \node [fit=(q_0) (q_3)] {$\cdots$};
    \end{tikzpicture}
    \caption{The intersection of $\aut_1$ and $\aut_2$}
  \end{subfigure}
  \caption{Intersection}
  \label{fig:inter}
\end{figure}
The transition relation of $\aut_1,\aut_2$ and their intersection is displayed by Figure \ref{fig:inter}. The intersection of CEFA is similar to the intersection of NFA, except that the intersection of CEFA intersects registers updates and linear arithmetic.
\subsection{Union}\label{subsec:union}
Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$ and $|R_1|=m,|R_2|=n$, the union is defined as $\aut_{union} = (Q_1\cup Q_2, \Sigma, \delta', \{q_0\}, F_1\cup F_2, R_1\cup R_2\cup (r', r''), \theta')$ where $\delta'$ is composed by
\begin{itemize}
  \item transitions $q_0\xrightarrow[0_{m+n}\cdot(1,0)]{\epsilon}q_1$ for all $q_1\in I_1$,
  \item transitions $q_0\xrightarrow[0_{m+n}\cdot(0,1)]{\epsilon}q_2$ for all $q_2\in I_2$,
  \item transitions $q_1\xrightarrow[\bar{v_1}0_{n+2}]{a} q_1'$ for all $q_1\xrightarrow[\bar{v_1}]{a} q_1'\in \delta_1$,
  \item transitions $q_2\xrightarrow[0_m\bar{v_2}0_2]{a} q_2'$ for all $q_2\xrightarrow[\bar{v_2}]{a} q_2'\in \delta_2$,
\end{itemize}
and 
\begin{itemize}
  \item $r'$ and $r''$ are new registers,
  \item $q_0$ is a new state where $q_0\not\in Q_1$ and $q_0\not\in Q_2$,
  \item $\theta_{tmp} = (r'>0\wedge\theta_1)\vee(r''>0\wedge\theta_2)$, $\theta'$ is constructed differently in four cases:
  \begin{itemize}
    \item [-]$I_1\cap F_1=\emptyset$ and $I_2\cap F_2=\emptyset$: $\theta'$ = $\theta_{tmp}$;
    \item [-]$I_1\cap F_1\not=\emptyset$ and $I_2\cap F_2=\emptyset$: $\theta'$ = $\theta_{tmp}\vee (r'==0\wedge r''==0\wedge\theta_1)$;
    \item [-]$I_1\cap F_1=\emptyset$ and $I_2\cap F_2\not=\emptyset$: $\theta'$ = $\theta_{tmp}\vee (r'==0\wedge r''==0\wedge\theta_2)$;
    \item [-]$I_1\cap F_1\not=\emptyset$ and $I_2\cap F_2\not=\emptyset$: $\theta'$ = $\theta_{tmp}\vee (r'==0\wedge r''==0\wedge(\theta_1\vee\theta_2))$;
  \end{itemize}
\end{itemize}
\begin{figure}[h]
  \centering
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend left] node [above] {$a$/$\bar{v_1}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_1$}
  \end{subfigure}
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a$/$\bar{v_2}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_2$}
  \end{subfigure}
  \begin{subfigure}{0.4\textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state]   (q_1) [above right=of q_0] {};
      \node[state, accepting]   (q_1') [right=of q_1] {};
      \node[state]   (q_2) [below right=of q_0] {};
      \node[state, accepting]   (q_2') [right=of q_2] {};
      \path[->]
      (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(1,0)}$} (q_1)
      (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(0,1)}$} (q_2)
      (q_1) edge [bend left] node [above] {$a$/\red{$\bar{v_1}\cdot 0_{n+2}$}} (q_1')
      (q_2) edge [bend right] node [below] {$a$/\red{$0_m\cdot \bar{v_2}\cdot 0_2$}} (q_2');
      \node [fit=(q_1) (q_1')] {$\cdots$};
      \node [fit=(q_2) (q_2')] {$\cdots$};
    \end{tikzpicture}
    \caption{The union of $\aut_1$ and $\aut_2$}
  \end{subfigure}
  \caption{Union}
  \label{fig:union}

\end{figure}
The Union of two CEFA is shown in Figure \ref{fig:union}. To simulate the semantics of the union, we add an initial state $q_0$ and transitions from $q_0$ to initial states of $\aut_1$ and $\aut_2$ to randomly choose one automaton. The values of $r'$ and $r''$ distinguish which automaton we run. In the construction above, $r'>0$ means that we choose $\aut_1$ to run a word, $r''>0$ implies that we select $r''$ to run a word, and $r'==0\wedge r''=0$ means that we decide to run word $\epsilon$.

\subsection{Complement}\label{subsec:comp}
We use the function $nfa$ to return the NFA form of a CEFA. More precisely, given a CEFA $\aut = (Q, \Sigma, I, F, \delta, R, \theta)$, $nfa(\aut)$ is an NFA tuple $(Q, \Sigma, \delta', I, F)$  where $\delta'$ comprises transition $(q, a, q')$ for $(q, a, q', \bar{v})\in \delta$ . Similarly, the function $cefa(\aut)$ is used to return the CEFA form of an NFA: $cefa(\aut_{nfa}) = (Q, \Sigma, I, F, \delta, \emptyset, true)$ for $\aut_{nfa} = (Q, \Sigma, I, F, \delta')$ where $\delta$ comprises transition $(q, a, q', \emptyset)$ for $(q, a, q')\in \delta'$. \verb|uion| denotes the CEFA operation union.

Given a CEFA $\aut = (Q,\Sigma, \delta, I, F, R, \theta)$, the complement of $\aut$ is defined as $\aut_{comp} = \verb|union|(\aut_{NFA}^C, \aut_{negf})$ where $\aut_{negf} = \\(Q,\Sigma, \delta, I, F, R, \neg\theta)$ and $\aut_{NFA}^C$ is obtained by three steps:
\begin{itemize}
  \item compute the NFA form $\aut_n = nfa(\aut) = (Q,\sigma, \delta', I, F)$,
  \item the complement of $\aut_n$ is $\aut_n^C = (Q, \sigma, \delta', F, I)$,
  \item extend $\aut_n^C$ to CEFA form $\aut_{NFA}^C = cefa(\aut_n^C)$.
\end{itemize}
\begin{figure}[h]
  \begin{subfigure}{0.40\textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v}$} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut$}
  \end{subfigure}
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=
      ]
      \node[state, initial, accepting]   (q_0) {};
      \node[state]    (q_1) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a$/\red{$\emptyset$}} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_{NFA}^C$}
  \end{subfigure}
  \begin{subfigure}{0.20\textwidth}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->]
      (q_0) edge [bend right] node [below] {$a$/\red{$\bar{v}$}} (q_1);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA $\aut_{negf}$}
  \end{subfigure}
  \caption{Complement}
  \label{fig:comp}
\end{figure}
As Figure \ref{fig:comp} shows, the complement of CEFA is the union of $\aut_{NFA}^C$ and $\aut_{negf}$. $\aut_{NFA}^C$ accepts words that $nfa(\aut)$ does not accept and $\aut_{negf}$ accepted words might be accepted by the $nfa(\aut)$ but not satisfy linear constraints $\theta$.
\subsection{Kleene}\label{subsec:klee}
The construction of Kleene is trivial. Given a CEFA $\aut = (Q,\Sigma,\delta,I,F,R,\theta)$ with $|R|=n$, the Kleene of $\aut_{Kleene}$ is defined as $(Q,\Sigma,\delta',I,F,R,\theta)$ where $\delta'$ comprises all transitions in $\delta$ and new transitions $q_f\xrightarrow[0_n]{\epsilon} q_0$ for each $q_0\in I$ and $q_f\in F$.

\subsection{From Extended Regex to CEFA} \label{subsec:regex2cefa}
\highlight{Basis}: The basis has three parts with empty registers and valid linear arithmetic, shown in Fig. \ref{fig:basis}. In part \ref{fig:basis:a}, we see how to handle the expression $\epsilon$. The language of the automaton is easily seen to be $\{\epsilon\}$ since the only path from the start state to an accepting state
is labeled $\epsilon$. Part \ref{fig:basis:b} gives the CEFA for a regular expression $\mathbf{a}$. The language of this CEFA consists of the single string $a$, which is also $\lan(\mathbf{a})$. Finally, part \ref{fig:basis:c} shows the construction for $\emptyset$. There are no paths from the initial state to the accepting state.
\begin{figure}[h]
  \centering
  \begin{subfigure}{0.13\textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=1.2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=1.0cm,minimum width=2.2cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->] (q_0) edge node [below] {$\epsilon/\emptyset$} (q_1);
      \node [fit=(q_0) (q_1)] {};
    \end{tikzpicture}
    \caption{}
    \label{fig:basis:a}
  \end{subfigure}
  \begin{subfigure}{0.13\textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=1.2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=1.0cm,minimum width=2.2cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \path[->] (q_0) edge node [below] {$a/\emptyset$} (q_1);
      \node [fit=(q_0) (q_1)] {};
    \end{tikzpicture}
    \caption{}
    \label{fig:basis:b}
  \end{subfigure}
  \begin{subfigure}{0.13 \textwidth}
    \centering
    \begin{tikzpicture}[shorten >=1pt,node distance=1.2cm,on grid,>={Stealth[round]},
      every fit/.style={draw,minimum height=1.0cm,minimum width=2.2cm,dashed},
      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
      \node[state, initial]   (q_0) {};
      \node[state, accepting]    (q_1) [right=of q_0] {};
      \node [fit=(q_0) (q_1)] {};
    \end{tikzpicture}
    \caption{}
    \label{fig:basis:c}
  \end{subfigure}
  \caption{The basis of the construction of a CEFA from extended regex}
  \label{fig:basis}
\end{figure}\\
\highlight{Induction}: Given the CEFA of the subexpression, we construct the CEFA in five cases:
\begin{enumerate}
  \item The expression is $\regex\{m,n\}$ for some smaller expression $\regex$. We can repeat the CEFA of $\regex$ with lower bound $m$ and upper bound $n$ as shown in section \ref{subsec:rep}.
  \item The expression is $\regex_1\cdot\regex_2$ for some smaller expression $\regex_1$ and $\regex_2$. We can concatenate the CEFA of $\regex_1$ and the CEFA of $\regex_2$ as shown in section \ref{subsec:con}.
  \item The expression is $\regex_1\times \regex_2$ for some smaller expression $\regex_1$ and $\regex_2$. We can intersect the CEFA of $\regex_1$ and the CEFA of $\regex_2$ as shown in section \ref{subsec:inter}.
  \item The expression is $\regex_1 + \regex_2$ for some smaller expression $\regex_1$ and $\regex_2$. We can union the CEFA of $\regex_1$ and the CEFA of $\regex_2$ as shown in section \ref{subsec:union}.
  \item The expression is $\regex*$ for some smaller expression $\regex$. We can construct the Kleene Star of the CEFA of $\regex$  as shown in section \ref{subsec:klee}.
  \item The expression is $\regex^C$ for some smaller expression $\regex$. We can construct the complement of the CEFA of $\regex$  as shown in section \ref{subsec:comp}
\end{enumerate}
\highlight{Special Case}: When the expression $\regex$ contains nested repetition, we firstly write $\regex$ to a new regex $\regex'$ without nested repetition. Then we build the CEFA of the new expression $\regex'$ by basis and induction steps.

\section{Solve String Constraints with Large Repetition Bound} \label{sec:solve}
Following the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve string constraints by CEFA. Firstly, we replace all length operations $i=\strlen{x}$ to pre-images, and intersect these pre-images to $lenAut_x$. Then for each term $x$, we genearte CEFAs from all regular expressiones $\regex$ in all terms $x\in \regex$, and intersect the CEFAs with $lenAut_x$ to get the final CEFAs. Finally, we check whether the final CEFAs is empty under the linear integer arithmetic $P$. If one of the final CEFAs is empty, the string constraints are unsatisfiable. Otherwise, the string constraints are satisfiable. The high-level algorithm is shown in the Algorithm \ref{alg:high}.\newline
The emptiness checking problem of CEFAs under linear integer arithmetic $P$ is theoretically pspace-complete\cite{atva2020}. To solve it efficiently for practical example, we add some heuristics. The details of the heuristics are shown in Algorithm \ref{alg:emptiness}.
% \pagebreak
\subsection{High-level algorithm}
\begin{algorithm}
  \caption{High-level algorithm}
  \label{alg:high}
  \begin{algorithmic}[1]
    \Require  Conjunction $\varphi$ of the form $x\in \regex$, and conjunction of linear integer arithmetic $P$ over string lengths
    \Ensure \emph{sat} or \emph{unsat}
    \Statex
    \ForAll{length operation $i = \strlen{x}$} \label{alg:high:line1}
      \State $lenAut_{x} \leftarrow \aut_{allstring}$ \label{alg:high:line2}
      \State Let $\aut_{i}$ be the pre-image of length operation with length $i$ \label{alg:high:line3}
      \State $lenAut_{x} \leftarrow lenAut_{x} \times \aut_{i}$ \label{alg:high:line4}
    \EndFor \label{alg:high:line5}
    \State $atomAuts \leftarrow \emptyset$ \label{alg:high:line6}
    \ForAll{string variables $x$ occurring in $\varphi$} 
    \State Let $S$ be the set of all regexes $\regex$ in all terms $x \in \regex$ 
    \State CEFA $\aut_x \leftarrow$ intersection of $lenAut_x$ and all CEFAs corresponding to regexes in $S$
    \If{$nfa(\aut_x)$ is empty} \label{alg:high:line5}
      \State \textbf{return} \emph{unsat}
    \EndIf
    \State $atomAuts \leftarrow atomAuts \cup \{\aut_x\}$ 
    \EndFor
    \If{$\algfun{isEmpty}(atomAuts, P)$ }
      \State \textbf{return} \emph{unsat}
    \Else 
      \State \textbf{return} \emph{sat}
    \EndIf
  \end{algorithmic}
\end{algorithm}
The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process. The implemented details are eliminated for clarity. From line \ref{alg:high:line1} to line \ref{alg:high:line5}, we construct the CEFAs of all length operations $i = \strlen{x}$ occurring in $\varphi$. The CEFA $lenAut_x$ is the automaton reserving all length information on $x$. $lenAut_x$ is initiated to accept all strings at line \ref{alg:high:line2}. And for each length operation $i = \strlen{x}$, we construct the pre-image of the length operation at line \ref{alg:high:line3}. Then we intersect $lenAut_x$ with the pre-image at line \ref{alg:high:line4}. Note that the final $lenAut_x$ is the intersection of many pre-images.\newline
In the following steps, we call a CEFA to be \emph{atomic} if we will not operate it anymore. The set $atomAuts$ is the set of all atomic CEFAs for all terms $x$ occurring in $\varphi$, and it is initiated to empty set at line \ref{alg:high:line6}. From line \ref{alg:high:line6} to line 14, we construct the atomic CEFAs of all string variables $x$ occurring in $\varphi$. For each string variable $x$, we construct the CEFA $\aut_x$ by intersecting $lenAut_x$ and all CEFAs corresponding to regexes in $S$. If the NFA form of $\aut_x$ is empty (i.e., the NFA accepts no word), we return $unsat$ directly because the NFA form is an over-approximation of CEFA. Otherwise, we add $\aut_x$ to $atomAuts$ at line 9.\newline
After obtaining the atomic CEFAs of all string terms, we check whether the atomic CEFAs are empty under the linear integer arithmetic $P$ at line 15. If the atomic CEFAs are empty, we return $unsat$. Otherwise, we return $sat$. The emptiness checking is complex, and we will discuss its details in the following subsection.\newline

\subsection{Emptyness Checking}
As mentioned, the emptiness checking problem of CEFA under linear integer arithmetic $P$ is theoretically pspace-complete \cite{atva2020}. In our previous research, we rewrote CEFA to an infinite system and used a model-checking tool \emph{NuSMV} to solve it. In this paper, we use a more efficient method to solve the emptiness checking problem. The details are shown in Algorithm \ref{alg:emptiness}.\newline
The input CEFAs may have many transitions and registers, so the emptiness checking problem is hard to solve. We simplify the CEFAs at line 1. The simplification is to remove all duplicated transitions and registers in the CEFAs. The simplification is implemented by Algorithm \ref{alg:simplify}. Then we try to find a solution by under-approximation at line 3. The under-approximation is implemented by Algorithm \ref{alg:underApprox}. If we find a solution, the CEFAs under linear integer arithmetic $P$ are not empty. So we return $false$ at line 5. We will try many times until we find a solution or reach $MaxBound$. Otherwise, we try to find an unsat core by over-approximation at line 8. The over-approximation is implemented by Algorithm \ref{alg:overApprox}. If we discover an unsat core, we know that the CEFAs under $P$ are empty, and we return $true$ at line 10. Suppose both under- and over-approximation do not make sense. In that case, we compute the Parikh images\cite{parikh_2005} of the simplified CEFAs and check if the Parikh images in conjunction with $P$ are satisfiable at line 12. The unsatisfiability implies emptiness directly.
\begin{algorithm}
  \caption{ $\algfun{isEmpty}(auts, P)$}
  \label{alg:emptiness}
  \begin{algorithmic}[1]
    \Require CEFAs $auts$ and linear integer arithmetic $P$
    \Ensure $true$ or $false$
    \Statex
    \State $simpliAuts \leftarrow \algfun{simplify}(auts)$
    \For{$bound \gets 1, MaxBound$ }
      \State $\varphi_{under}\gets \algfun{underApprox}(simpliAuts, bound)$
      \If{$\varphi_{under}\wedge P$ is sat}
        \State \textbf{return} $false$
      \EndIf
    \EndFor
    \State $\varphi_{over}\gets \algfun{overApprox}(simpliAuts)$
    \If{$\varphi_{over}\wedge P$ is unsat}
      \State \textbf{return} $true$
    \EndIf
    \State $\varphi \gets \algfun{parikhImage}(simpliAuts)$
    \If{$\varphi\wedge P$ is unsat}
      \State \textbf{return} $true$
    \Else
      \State \textbf{return} $false$
    \EndIf
  \end{algorithmic}
\end{algorithm}
\subsection{Simplification of CEFA}
The main idea of simplification is to remove duplicated transitions and registers. In emptiness checking Algorithm \ref{alg:emptiness}, the vectors on the transitions are meaningful, but the letters on the transitions are not. So we see the alphabet of the CEFA as unary (i.e., the alphabet is $\{a\}$). Compared with NFA, the vectors in the CEFA are the letters in the NFA, and the vector $\myvec{0}_n$ is seen as $\epsilon$. Based on the similarity between NFA and CEFA, firstly, determinization and minimization \cite{aut_hopcraft} are applied to simplify the CEFA. Then we merge the registers having the same updating at all transitions and get the final CEFA. The main simplification framework is shown in Algorithm \ref{alg:simplify}, and some details are eliminated for simplicity.
\begin{algorithm}
  \caption{$\algfun{simplify}(auts)$}
  \label{alg:simplify}
  \begin{algorithmic}[1]
    \Require CEFAs $auts$
    \Ensure Simplified CEFAs $simpliAuts$
    \Statex
    \State $simpliAuts \gets \emptyset$
    \For{$aut \in auts$}
      \State $aut \gets \algfun{determinizeByVec}(aut)$
      \State $aut \gets \algfun{minimizeByVec}(aut)$
      \State $aut \gets \algfun{mergeRegisters}(aut)$
      \State $simpliAuts \gets simpliAuts \cup \{aut\}$
    \EndFor
    \State \textbf{return} $simpliAuts$
  \end{algorithmic}
\end{algorithm}

\subsection{Under-Approximation}
To solve the emptiness checking problem, we translate the CEFAs to linear integer arithmetic and check if the linear integer arithmetic in conjunction with $P$ is satisfiable. The main idea of under-approximation is to translate the CEFAs step by step. A string length bound controls the translation, and linear integer arithmetic is generated from low to high length bound. This section only discusses the situation where the bound is fixed. The details are shown in the Algorithm \ref{alg:underApprox}. Firstly, the linear integer arithmetic $\varphi_{under}$ is assigned to be false at line 1. Then for each CEFA, we enumerate all the accepted paths with lengths less than the bound and translate the paths to linear integer arithmetic. The linear integer arithmetic is in conjunction with $\varphi_{under}$ at line 4.
\begin{algorithm}
  \caption{$\algfun{underApprox}(auts, bound)$}
  \label{alg:underApprox}
  \begin{algorithmic}[1]
    \Require CEFAs $auts$ and length bound $bound$
    \Ensure Linear integer arithmetic $\varphi_{under}$
    \Statex
    \State $\varphi_{under} \gets false$
    \For{$aut \in auts$}
      \State Let $\varphi_{aut}$ to be the linear integer arithmetic generated by  enumerating all the paths with length less than $bound$ in $aut$
      \State $\varphi_{under} \gets \varphi_{under} \wedge \varphi_{aut}$
    \EndFor
    \State \textbf{return} $\varphi_{under}$
  \end{algorithmic}
\end{algorithm}
\subsection{Over-Approximation}
Sometimes when the bound reaches the maximum, the linear integer arithmetic $\varphi_{under}$ is still unsatisfiable. We must use over-approximation to solve the emptiness checking problem in this case. The main idea of over-approximation is to split each CEFA into sub-CEFAs, translate each sub-CEFA respectively, and finally in conjunction with the LIA of all sub-CEFAs. The details are shown in the Algorithm \ref{alg:overApprox}. Firstly, each CEFA is split into $n$ sub-CEFAs, where $n$ is the number of registers in the CEFA. The sub-CEFA has only one register. After simplifying each sub-CEFA by Algorithm \ref{alg:simplify}, the vector of each transition must be $\myvec{1}$. So the register value of each sub-CEFA equals the length of the accepted path. We apply the efficient construction of semilinear representations\cite{unary_nfa_2010} to get the linear integer arithmetic $\varphi_{over}$.
\begin{algorithm}
  \caption{$\algfun{overApprox}(auts)$}
  \label{alg:overApprox}
  \begin{algorithmic}[1]
    \Require CEFAs $auts$
    \Ensure Linear integer arithmetic $\varphi_{over}$
    \Statex
    \State $\varphi_{over} \gets true$
    \For{$aut \in auts$}
      \State Let $subAut$ be the sub-CEFA of $aut$ with only one register
      \State Let $subAut \gets \algfun{simplify}(subAut)$
      \State Let $\varphi_{subAut}$ be the linear integer arithmetic generated by efficient construction of semilinear representations
      \State $\varphi_{over} \gets \varphi_{over} \wedge \varphi_{subAut}$
    \EndFor
    \State \textbf{return} $\varphi_{over}$
  \end{algorithmic}
\end{algorithm}
\section{Implementation and Experiment} \label{sec:imp}
% % TODO: Implementation and experiment result
TODO
% We implement Algorithm \ref{alg:high} on our string solver ostrich \cite{ostrich2023}. And compare our solver with z3 on benchmark \emph{LoopBench}. The result shows that our algorithm performs better than z3.\\
% \highlight{LoopBench}: The benchmark consists of three parts:
% \begin{enumerate}
%   \item \textbf{Z3strRE}: We extract instances with repetition operator from (paper z3str3Re). z3strRE support string operation \verb|num2str| which is not supported by ostrich. So we remove these instances with \verb|num2str|.
%   \item \textbf{StackOverflow}: We extract real-world regexes from StackOverflow\cite{stackoverflow} using the tool zaligvinder\cite{zaligvinder_2021} and translate these regexes to smtlib2 format. For each regex, we generate an instance with one regular membership and a length operation.
%   \item \textbf{RegexLib}: We also extract real-world regexes from regexlib\cite{regexlib} using zaligvinder and generate instances in the same way as StackOverflow.
% \end{enumerate}
% The experimental result is shown in Table \ref{tab:res}. ostrich performs very closely on satisfiable instances and outperforms z3 on unsatisfiable instances. Furthermore, ostrich use a little more time to find the result rather than z3.
% \begin{table}[h]
%   \begin{tabular}{|l|l|l|l|l|l|}
%     \hline
%             & sat  & unsat & error & sat time & unsat time \\ \hline
%     z3      & 6995 & 5491  & 382   & 1.09s    & 0.42s      \\ \hline
%     ostrich & 6966 & 5751  & 150   & 2.82s    & 1.81s      \\ \hline
%   \end{tabular}
%   \caption{Detailed results for the LoopBench benchmark. Ostrich can solve more instances.}
%   \label{tab:res}
% \end{table}

\section{Conclusion and Future Work} \label{sec:conclu}
In this paper, we aim to solve the string constraints with large repetition time efficiently. A new automaton model CEFA is proposed to reduce the search space. Many basic operations on CEFA are non-trivial and we should formal them carefully. Moreover, we extend the algorithm in the paper \cite{atva2020} with heuristics such as under- and over-approximation. The implementation of the algorithm is done on string solver ostrich. The extensive empirical comparison against z3 over a large and diverse benchmark shows the power of our model and algorithm. In the future, we plan to explore the way to solve nested repetition and use CEFA to solve more string operations.

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{ref}

\end{document}

%%
%% End of file `sample-sigconf.tex'.

### 2023-03-13 2023-1-19/efficient_way_for_counting.tex
draft with concat

@@
-%% This is file `sample-sigconf.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigconf')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-sigconf.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% Commands for TeXCount
-%TC:macro \cite [option:text,text]
-%TC:macro \citep [option:text,text]
-%TC:macro \citet [option:text,text]
-%TC:envir table 0 1
-%TC:envir table* 0 1
-%TC:envir tabular [ignore] word
-%TC:envir displaymath 0 word
-%TC:envir math 0 word
-%TC:envir comment 0 0
-%%
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf]{acmart}
-%% NOTE that a single column version is required for 
-%% submission and peer review. This can be done by changing
-%% the \doucmentclass[...]{acmart} in this template to 
-%% \documentclass[manuscript,screen]{acmart}
-%% 
-%% To ensure 100% compatibility, please check the white list of
-%% approved LaTeX packages to be used with the Master Article Template at
-%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
-%% before creating your document. The white list page provides 
-%% information on how to submit additional LaTeX packages for 
-%% review and adoption.
-%% Fonts used in the template cannot be substituted; margin 
-%% adjustments are not allowed.
+\documentclass[runningheads]{llncs}
 
@@
 \usepackage{algpseudocode}
-
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2022}
-\acmYear{2022}
-\acmDOI{XXXXXXX.XXXXXXX}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation emai}{June 03--05,
-  2018}{Woodstock, NY}
-%
-%  Uncomment \acmBooktitle if th title of the proceedings is different
-%  from ``Proceedings of ...''!
-%
-%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-%  June 03--05, 2018, Woodstock, NY} 
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/22/12}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage[]{float}
 % set algorithmicx
-
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
@@
 
-\newcommand*{\myvec}[1]{\bar{#1}}
+\newcommand*{\myvec}[1]{\vec{#1}}
 \newcommand*{\regex}{\mathcal{R}}
@@
 \newcommand*{\strlen}[1]{\texttt{len}(#1)}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% For managing citations, it is recommended to use bibliography
-%% files in BibTeX format.
-%%
-%% You can then either use BibTeX with the ACM-Reference-Format style,
-%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
-%% support for advanced citation of software artefact from the
-%% biblatex-software package, also separately available on CTAN.
-%%
-%% Look at the sample-*-biblatex.tex files for templates showcasing
-%% the biblatex styles.
-%%
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
 
@@
 %%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{DengHang Hu}
+\author{Denghang Hu\inst{1} \and
+Zhilin Wu\inst{1}}
+\authorrunning{D.Hu et al.}
 % \authornote{Both authors contributed equally to this research.}
-\affiliation{%
-  \institution{State Key Laboratory of Computer Science,
-    Institute of Software, Chinese Academy of Sciences}
-  \city{}
-  \country{}
-}
-\email{hudh@ios.ac.cn}
 
-\author{Zhilin Wu}
-% \authornote{Both authors contributed equally to this research.}
-\affiliation{%
-  \institution{State Key Laboratory of Computer Science,
-    Institute of Software, Chinese Academy of Sciences}
-  \city{}
-  \country{}
-}
-\email{wuzl@ios.ac.cn}
+\institute{State Key Laboratory of Computer Science,
+Institute of Software, Chinese Academy of Sciences, China\\
+\email{\{hudh,wuzl\}@ios.ac.cn}}
+
+\maketitle
 
@@
 \begin{abstract}
-  Regular expression with large repetition bounds frequently appears in the real world. However, state-of-art string solvers can not efficiently solve string constraints with large
-  repetition bounds, which slows down string constraint
-  applications like formal verification and symbolic execution. In this paper, we
-  propose a new systematic algorithm based on the decision procedure in our previous work to solve the problem efficiently. We use
-  heuristic ways like over-approximation and under-approximation to accelerate the search. Further, we extract amounts of regex expressions with repetition
-  times from real-world programs and generate a significant benchmark. We evaluate the algorithm's performance on our generated
-  and developed benchmarks. The result shows that our solver outperforms the state-of-art string solvers.
+  Regular expression with large repetition bounds frequently appears in the real world.
+However, state-of-art string solvers can not efficiently solve string constraints with such regular expression, which slows down string solver applications like formal verification and symbolic execution.
+In this paper, we
+  propose a new systematic algorithm based on cost-enriched automaton. We use
+  heuristic ways like over-approximation and under-approximation to accelerate the search. Further, we extract amounts of regex expressions with large repetition
+  bounds from real-world programs and generate a significant benchmark.
+We evaluate the algorithm's performance on our developed benchmarks and other typical benchmarks.
+The result shows that our solver outperforms the state-of-art string solvers.
 
+\keywords{string constraints, cost-enriched automata, regex expression, bounded repetition}
 \end{abstract}
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-% \begin{CCSXML}
-% <ccs2012>
-%    <concept>
-%        <concept_id>10003752.10003766.10003776</concept_id>
-%        <concept_desc>Theory of computation~Regular languages</concept_desc>
-%        <ignificance>500</concept_significance>
-%        </concept>
-%  </ccs2012>
-% \end{CCSXML}
-
-\ccsdesc[500]{Theory of computation~Regular languages}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{string constraints, cost-enriched automata, regex expression, bounded repetition}
-
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-% \begin{teaserfigure}
-%   \includegraphics[width=\textwidth]{sampleteaser}
-%   \caption{Seattle Mariners at Spring Training, 2010.}
-%   \Description{Enjoying the baseball game from the third-base
-%   seats. Ichiro Suzuki preparing to bat.}
-%   \label{fig:teaser}
-% \end{teaserfigure}
-
-% \received{20 February 2007}
-% \received[revised]{12 March 2009}
-% \received[accepted]{5 June 2009}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-
 \section{Introduction}
-Regular expressions are widely used in programming languages such as Javascript and Python. About 30–40 \% of Java, JavaScript, and Python software uses regex
-matching\cite{redos_fse2019}. To find
-potential software bugs automatically, many researchers prefer to use one of the
-formal verification technology - symbolic execution \cite{symbolic_pldi2021}. Symbolic execution views symbolic paths as multi-theories
-constraints and uses a constraints solver to solve these constraints. Thus the
-efficiency and the ability of the constraints solver are vitally important.
-However, the string theory is one of the most challenging theories in multi-theory constraints because it is easy to be undecidable\cite{undecidable_2016}.
-So the string constraints solver with the higher
-ability (support more operators) usually performs slower. Most solvers try very hard to improve efficiency. For example, Z3 and cvc5 append many heuristic
-derivation rules to speed up their search in the DPLL framework. Trau+ proposes
-a new model called flat automaton and uses the CEGAR framework to under-approximate
+Regular expressions are widely used in programming languages.
+About 30–40 \% of Java, JavaScript, and Python software uses regex matching \cite{redos_fse2019}.
+To handle the problems in software verification reasoning about string, the string theory is introduced and amounts of string solvers are developed.
+However, the string theory is one of the most challenging theories because it is easy to be undecidable \cite{undecidable_2016}.
+String solvers try very hard to improve efficiency:  DPLL(T)-based string solver Z3 \cite{z3} and Cvc5 \cite{cvc5} apply many heuristic derivation rules.
+Automaton-based string solver Trau+\cite{trau} proposed flat automaton and uses the CEGAR framework to under-approximate
 and over-approximate the string constraints again and again.
-Unfortunately, the string solvers above perform poorly when the string constraints contain large repetition bound. The DPLL-framework string solvers prefer to
-search model strings with smaller lengths, but large repetition bound most often stands
-for considerable model string lengths. The automaton-based solvers
-unwind the automaton naively, so the search space of the unwound automaton is
-exponential of the repetition bound. To address this issue, we extend
-cost-enriched finite automaton\cite{atva2020} whose search space is linear to the
-repetition bound. Our main contributions are:
+Unfortunately, the string solvers above perform poorly when the string constraints contain large repetition bounds.
+[add a example].
+To address this issue, we extend cost-enriched finite automaton(CEFA)\cite{atva2020} with linear arithmetical constraint.
+Use backward-propagating algorithm to search a solution.
+Our main contributions are as follows:
 \begin{enumerate}
-  \item We extend cost-enriched finite automaton to model the extended regular expression with large repetition bound.
-  \item We devise an efficient algorithm to solve string constraints with large repetition bound with the new automaton model.
-  \item We generate many instances with large repetition bound from real-word regular expressions.
-  \item We implemented our efficient algorithm on ostrich and compared it with state-of-art string solvers. The result shows the superiority of our automaton model and algorithm.
+  \item  Extend cost-enriched finite automaton to model the regular expression with large repetition bound.
+  \item  Devise an efficient algorithm based on CEFA to solve string constraints with large repetition bound.
+  \item  Generate many instances with large repetition bound from real-word regular expressions.
+  \item  Implemented our efficient algorithm on Ostrich\ref{Ostrich} and compared it with state-of-art string solvers. The result shows the superiority of our automaton model and algorithm.
 \end{enumerate}
 %TODO: list the main contributions
-The structure of this paper is as follows: We introduce some abbreviations and concepts in section \ref{sec:pre} and introduce the syntax and semantics of the string theory logic in section \ref{sec:str_t}.
+% The structure of this paper is as follows: We introduce some abbreviations and concepts in section \ref{sec:pre} and introduce the syntax and semantics of the string theory logic in section \ref{sec:str_t}.
 Then we develop cost-enriched finite automaton model and its operations at section \ref{sec:cefa}.
@@
 %TODO: preliminaries
-\highlight{Tokens.} We consider a finite \emph{alphabet} $\Sigma$, the set of all \emph{letters}. A
+\highlight{Tokens.} A finite \emph{alphabet} $\Sigma$ is the set of all \emph{letters}. A
 \emph{string} is a finite sequence of letters from $\Sigma$. We use $\Sigma^*$ to
@@
 We use $m,n,\cdots$ to
-denote constant integer, and $i,j\cdots$ to denote variable integer.
-For vector, we use $\bar{v}$ to denote the vector of constant integer, $0_n$ to denote the zero vector with length $n$, $|\bar{v}|$ to denote the length of $|\bar{v}|$, and $v(i)$ to denote the integer value of $\bar{v}$
-at position $i$, and $\cdot$ to denote the concatenation of two vectors.\newline
+denote integer constant, and $i,j\cdots$ to denote integer variable.
+For vector, we use $\myvec{v}$ to denote the vector of integer constant, $0_n$ to denote the zero vector with length $n$, $v(i)$ to denote the integer value of $\myvec{v}$ at position $i$, $\myvec{v_1}\cdot\myvec{v_2}$ to denote the concatenation of $\myvec{v_1}$ and $\myvec{v_2}$, $R$ to denote the vector of integer variable, $R_1 \cap R_2$ to denote the same variables of $R_1$ and $R_2$, and $|\myvec{v}|$ or $|R|$ to denote the length of vector.\newline
 \highlight{CNF, DNF, clause, cube.} We assume that the reader is familiar with first-order logic.
 A \emph{literal} is an atomic proposition or its negation.
-Briefly, A \emph{clause} is a disjunction of literals.
-The empty clause is $false$.
+A \emph{clause} is a disjunction of literals.
+The empty clause is $true$.
 A formula is in \emph{conjunctive normal norm} (CNF) if it is a conjunction of clauses.
-A \emph{cube} is a conjunction of a consistent set of literals; The empty cube is $true$.
+A \emph{cube} is a conjunction of a consistent set of literals; The empty cube is $false$.
 A formula is in \emph{disjunctive normal form} (DNF) if it is a disjunction of cubes.\newline
@@
 The \emph{language} of $\aut$ is the set of all words accepted by $\aut$, denoted by $\lan(\aut)$.
-From automata theory\cite{aut_hopcraft}, we know that the languages generated by basic regular expression are also in the class of $\lan(\aut)$.
-We call them \emph{Basic Regular Language}.
-\section{String Theory with Extended Regex} \label{sec:str_t}
+From automata theory\cite{aut_hopcraft}, basic regular expression only contains union, concatenation, and closure operations.
+We know that the language of basic regular expression are also in the class of $\lan(\aut)$.
+We call it \emph{Basic Regular Language}.
+\section{String Theory with Regex} \label{sec:str_t}
 % TODO: Syntax and semantic
+In this section, the syntax and semantic of string theory is defined.
 \subsection{Syntax}
-In this paper, we extend string theory in our previous work \cite{atva2020} with extended regex. We call
-the new theory as \textit{Extended String Logic (ESL)}. ESL contains the following
+In this paper, we propose a new logic called \textit{Extended String Logic (ESL)}. ESL contains the following
 sorts: string sort \verb|Str|, integer sort \verb|Int|, the enumerable set of string
@@
 string length $\verb|len|: \verb|Str|\rightarrow \verb|Int|$; regular membership $\in:
-\verb|Str|\times \verb|Str|^m$; the basic regex operators such as Kleene, concatenation,  conjunction, and disjunction; the extended regex operator repetition and complement; and the usual constants of linear arithmetic.
+\verb|Str|\times \verb|Str|^m$; the regex operators such as closure, concatenation,  conjunction, disjunction, intersection, repetition and complement; and the usual constants of linear arithmetic.
 
-The syntax of ESL is presented in Table\ref{tab:syntax}. $\varphi$ is a first-order logic formula that can be a regular membership $x\in\regex$,
-a word equation $e$, a linear arithmetic (in)equality $\beta$, a negation of a formula, or a
-disjunction of two formulas. A word equation $e$ is an equality of two string terms. The
-(in)equality operator $\odot$ contains $=, \geq$. $\beta$ is an (in)equality
-of two integer terms. A string term $s$ is an empty string $\epsilon$, letters
+The syntax of ESL is presented in Table \ref{tab:syntax}. $\varphi$ is a first-order logic formula that can be a regular membership $x\in\regex$,
+a word equation $e$, a quantifier-free Presburger arithmetic formula $\beta$, a negation of a formula, or a
+disjunction of two formulas.
+A word equation $e$ is an equality of two string terms.$\beta$ is an (in)equality of two integer terms and the (in)equality operator $\odot$ contains $=, \geq$.
+A string term $s$ is an empty string $\epsilon$, letters
 $a\in\Sigma$, string variable $x$, or a concatenation of two string terms. An integer
@@
 regular expression $\regex$ is built on empty string $\epsilon$, constant letter $a\in \Sigma$. The supported regex operations involve concatenation $\cdot$, disjunction $+$,
-intersection $\times$, Kleene $*$, complement $C$, and repetition $\{m, n\}$.
+intersection $\times$, closure $*$, complement $C$, and repetition $\{m, n\}$.
 
-We use function $FV(\varphi)$ to return all free variables of $\varphi$.
-We consider \emph{straight-line} fragment\cite{atva2020}\cite{quadratic_aplas2018} of this string theory logic.
-A word equation \emph{cube} $\bigwedge_{i=1}^n e_i$ is said to be straight-line if it can be rewritten as the form $\bigwedge_{j=1}^m x_j = s_j$ such that: (i) $x_1, \cdots, x_m$ are different variables; and (ii) $FV(s_j)\cap \{x_1, x_2,
-  \cdots, x_{j-1}\} = \emptyset$. A formula $\varphi = (\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$
-is said to be straight-line if $\bigwedge_{i=1}^n e_i$ is straight-line, $\Re$ is a
-\emph{tube} of regular membership $x\in \regex$ or its negation $x\not\in \regex$, and $P$ is a Presburger arithmetic formula.
-
-Note that we can convert an ESL formula to a DNF formula such that each term in the DNF
-formula is the form $(\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$ where $P$ is a
-Presburger formula. We call the form $(\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$ as \emph{normal form}. The straight-line fragment is similar to the SSA form of the
-program.  Sometimes we use $s_1s_2$ to stand for $\verb|concat|(s_1,s_2)$ and $|x|$ to
+We consider \emph{straight-line} fragment\cite{atva2020}\cite{quadratic_aplas2018} $ESL_{s}$ of the string theory logic. 
+A formula $\varphi$ is said to be straight-line if it can be converted to a DNF formula $\bigvee_{i} \phi_i$ and $\phi_i= (\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$
+where $\bigwedge_{i=1}^n e_i$ is straight-line, $\Re$ is a
+\emph{cube} of regular membership $x\in \regex$ or its negation $x\not\in \regex$, and $P$ is a Presburger arithmetic formula.
+A word equation \emph{cube} $\bigwedge_{i=1}^n e_i$ is said to be straight-line if it can be rewritten as the form $\bigwedge_{j=1}^m x_j = s_j$ such that:
+\begin{enumerate}
+  \item $x_1, \cdots, x_m$ are different variables,
+  \item $FV(s_j)\cap \{x_1, x_2, \cdots, x_{j-1}\} = \emptyset$ where $FV(\varphi)$ are all free variables of $\varphi$. \label{straigth_line_condition_2}
+\end{enumerate} 
+We call straight-line formula $(\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$ \emph{normal form}.We use $s_1s_2$ to stand for $\verb|concat|(s_1,s_2)$, $|x|$ to
 stand for $\verb|len|(x)$.
-\begin{table}
+\begin{table}[H]
+  \centering
   \begin{tabular}{l}
@@
   \begin{equation} \label{eq:1}
-    \varphi_1 ::= x = \verb|concat|(y,z) \wedge y = z \wedge x\in a\{1,100\}
+    \varphi_s ::= x =yz \wedge y = z \wedge x\in a\{1,100\} \wedge |x| = 1
   \end{equation}
-  The word equation cube
-  $c ::= (x = \verb|concat|(y,z) \wedge y = z)$ is straight-line because it santisfy : (i) $FV(z) = \{z\}$, (ii)$\{z\}\cap\{x\} = \emptyset$.
-So the formula $\varphi_1 = c\wedge  x\in a\{1,100\}$ is also straight-line.
+  $\varphi_s$ is straight-line because we can split it to three parts: (i) a straight-line word equation cube $x =yz \wedge y = z$,
+  (ii) a regular membership cube $x\in a\{1,100\}$, and (iii) a Presburger arithmetic formula $|x| = 1$.
 \end{example}
@@
   \begin{equation} \label{eq:1}
-    \varphi_2 ::=  x = \verb|concat|(y,z) \wedge y = \verb|concat|(x,z) \wedge x\in a\{1,100\}
+    \varphi_{ns} ::=  x =yz \wedge y = xz \wedge x\in a\{1,100\} \wedge |x| = 1
   \end{equation}
-  $\varphi_2$ is not straight-line because the word equation cube\newline
-  $(x = \verb|concat|(y,z) \wedge y = z)$ is not straight-line.
+  $\varphi_{ns}$ is not straight-line because the word equation cube\newline
+  $x = yz \wedge y = xz$ does not satisfy condition \ref{straigth_line_condition_2}: $FV(yz) \cap \{y\} \not = \emptyset$ and $FV(xz) \cap \{x\} \not = \emptyset$.
 \end{example}
@@
 \subsection{Semantics}
-\highlight{Extended Regular Language} We have introduced basic regular language at
-section \ref{sec:preliminaries}.
-In our paper, we add a new operator \emph{repetition} $\regex\{m,n\}$, which means repeating regex $\regex$ at least $m$ times and at most $n$ times.
-Repetition can be syntactically rewritten by concatenation and disjunction:
+\highlight{Regular Language} We have introduced basic regular language at
+section \ref{sec:pre}.
+In addition to basic regular operations, we syntactically support intersection, complement and repetition.
+As we all know, basic regular language is closed under intersection and complement.
+Furthermore, the operation \emph{repetition} $\regex\{m,n\}$ means repeating regex $\regex$ at least $m$ times and at most $n$ times.
+It can be syntactically rewritten by concatenation and union:
 $\regex\{m,n\} \equiv \regex^m\mid\cdots\mid\regex^n$ where $\regex^k$ defines concatenate $k$ times($m\leq k\leq n$) to $\regex$.
-However, if we naively rewrite the repetition operation, the automaton size will be huge (linear to repetition times), causing the search space to be exponential.
-To address the issue, we proposed a new automaton model called \emph{Cost-Enriched Finite Automaton (CEFA)}, whose size is constant to repetition times.
-CEFA can not handle nested repetition ($\regex\{m,n\}$ or $\regex *$, where $\regex$ contains the repetition operator).
-So we have to rewrite it syntactically when the regex contains nested repetition (e.g., $a\{1,100\}\{2,2\}$ is rewritten to $a\{1,100\}a\{1,100\}$).
-Our regular expression is semantically equal to basic regular language but syntactically extended.
-We call the language of our regex \emph{Extended Regular Language} and denote it to $\lan^e(\regex)$.\newline
+So the regular language defined in Table \ref{tab:syntax} is semantically equal to basic regular language.
+However, if we naively rewrite the repetition operation, the automaton size will linear to the repetition times, causing the search space to be exponential.
+To address the issue, we proposed a new automaton model called \emph{Cost-Enriched Finite Automaton (CEFA)}, whose size is not relevant to the repetition times.
+CEFA can not handle nested repetition (e.g., $\regex\{m_1,n_1\} \regex\{m_2,n_2\}$ or $(\regex\{m, n\}) *$) and complementation of repetition (e.g, $(\regex\{m,n\})^C$).
+So we have to rewrite these regexes syntactically (e.g., $a\{1,100\}\{2,2\}$ is rewritten to $a\{1,100\}a\{1,100\}$).\newline
 \highlight{Semantics} We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables.
 $\eta: S\times\Sigma\rightarrow\Sigma^*$ is the interpretation on string where $\eta(c)=c$ for every letter $c\in \Sigma$ and $\eta(s_1s_2)=\eta(s_1)\eta(s_2)$.
-$\theta: I\rightarrow\mathbb{Z}$ is the interpretation of arithmetic that is the same as that of Presburger arithmetic.
+$\theta: I\rightarrow\mathbb{Z}$ is the interpretation of arithmetic that is the same as Presburger arithmetic.
 Then the semantics is given by a satisfaction relation: $\eta, \theta\models \varphi$ defined in Table \ref{tab:semantics}.
-We say a formula $\varphi$ is \emph{satisfiable} if a solution exists $(\eta, \theta)$ such as $\eta, \theta\models \varphi$.
+We say a formula $\varphi$ is \emph{satisfiable} if a solution $(\eta, \theta)$ exists such as $\eta, \theta\models \varphi$.
 A formula $\varphi$ is \emph{unsatisfiable} if no solution exists.
 
-\begin{table}[h]
+\begin{table}[H]
+  \centering
   \begin{tabular}{lcl}
@@
      $\eta,\theta \models \neg\varphi $          & $\mathsf{iff}$ & $\eta,\theta \not\models \varphi$\\
-     $\eta, \theta \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan^e(\regex),\eta,\theta \models x = w$\\
+     $\eta, \theta \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan(\regex),\eta,\theta \models x = w$\\
      $\eta, \theta \models s_1 = s_2$              & $\mathsf{iff}$ & $\eta(s_1) = \eta(s_2)$\\
@@
 In this paper, we consider the following problem:
-\begin{table}[h]
+\begin{table}[H]
+  \centering
   \begin{tabular}{l l}
     \hline
-    \textbf{Problem:} & Is a ESL formula $\varphi$ satisfiable?                   \\
-    \textbf{Input:}   & A straight-line ESL formula $\varphi$ in the normal form. \\
+    \textbf{Problem:} & Is an $ESL_s$ formula $\varphi$ satisfiable?                   \\
+    \textbf{Input:}   & A straight-line $ESL_s$ formula $\varphi$ in the normal form. \\
     \textbf{Output:}  & \emph{sat} or \emph{unsat}.                               \\
@@
 %      The operation on the cost-enriched automata (union, intersection, complement, concatenate)
-In this section, we will define the cost-enriched finite automaton and operations on it. The operations are intersection, union, complement, concatenation, and repetition.
+In this section, the cost-enriched finite automaton and operations on it is defined. The operations contains intersection, union, complement, concatenation, and repetition.
 \subsection{Cost-Enriched Finite Automaton}
 \begin{definition}[Cost-Enriched Finite Automaton]
-  A cost-enriched finite automaton(CEFA) $\aut$ is a tuple $(Q, \Sigma, \delta, I, F, R, \theta)$ where
+  A cost-enriched finite automaton $\aut$ is a tuple $(Q, \Sigma, \delta, I, F, R, \theta)$ where
   \begin{itemize}
     \item $Q,\Sigma,I,F$ is defined as NFA,
-    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers. We use $\mathcal{V}(r_i)$ to denote the value of $r_1$. Note that the initial value of each register is 0,
-    \item $\delta$ is the transition set whose elements are tuple $(q, a, q', \bar{v})$ where $q, q'$ are states in $Q$, $a$ is a letter in alphabet $\Sigma$ and $\bar{v}$ is vector of natural number.
-We write the transition $(q, a, q', \bar{v})$ as $q\xrightarrow[\bar{v}]{a} q'$ for readability.
-    \item $\theta$ is the linear integer arithmetic on registers.
+    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
+    \item $\delta$ is the transitions set whose elements are transition tuple $(q, a, q', \myvec{v})$ where $q, q'$ are states in $Q$, $a$ is a letter in alphabet $\Sigma$ and $\myvec{v}$ is vector of natural number.
+The transition $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
+    \item $\theta$ is the linear integer arithmetic constraint of registers.
   \end{itemize}
-  A \emph{run} of $\aut$ on string $a_1\cdots a_m$ is a transition sequence $q_0\xrightarrow[\bar{v_1}]{a_1}q_1\cdots q_{m-1}\xrightarrow[\bar{v_m}]{a_m}q_m$ such that $q_0\in I$ and $r_i = \displaystyle\sum_{j=1}^m v_j(i)$ for $r_i \in R$.
+  A \emph{run} of $\aut$ on string $a_1\cdots a_m$ is a transition sequence $q_0\xrightarrow[\myvec{v_1}]{a_1}q_1\cdots q_{m-1}\xrightarrow[\myvec{v_m}]{a_m}q_m$ such that $q_0\in I$ and $\mathcal{V}(r_i) = \displaystyle\sum_{j=1}^m v_j(i)$ is the \emph{value} of register $r_i$ after the run.
+Note that $\mathcal{V}(r_i)$ is initiated to 0 at state $q_0$.
 The run is \emph{accepting} if $q_m\in F$ and $\theta[r_i/\mathcal{V}(r_i)]$ is satisfiable.
@@
 \end{definition}
-\begin{example}[The CEFA  $\aut_{ab\{1,100\}}$ ] \label{eg:1}
-  We build a CEFA $\aut_{ab\{1,100\}}$ (table \ref{fig:cefa1}) whose language is the language of the extended regular expression $ab\{1,100\}$.
-The transition set of $\aut_{ab\{1,100\}}$ are $\{q_0\xrightarrow[1]{a} q_1, q_1 \xrightarrow[0]{b} q_2, q_2 \xrightarrow[0]{\epsilon} q_0\}$.
+\begin{example}[The CEFA  $\aut_{(ab)\{1,100\}}$] \label{eg:1}
+   Table \ref{fig:repetition} is the CEFA of the regular expression $(ab)\{1,100\}$.
+The transition set are $\{q_0\xrightarrow[1]{a} q_1, q_1 \xrightarrow[0]{b} q_2, q_2 \xrightarrow[0]{\epsilon} q_0\}$.
 The register is $r_1$.
 And the linear arithmetic is $1\leq r_1\leq 100$.
-Intuitively, the accepted run of $\aut_{ab\{1,100\}}$ will repeatedly run word $ab$.
-The transition $q_0\xrightarrow[1]{a} q_1$ should appear at least once and at most 100 times because of the linear constraint $1\leq r_1 \leq 100$.
+Intuitively, each accepted run of $\aut_{(ab)\{1,100\}}$ repeatedly run word $ab$ from one time to 100 times because $1\leq r_1 \leq 100$ restrict the value of $r_1$ to the range $[1,100]$.
+More precisely, the repeat time of the transition $q_0\xrightarrow[1]{a}q_1$ is restricted to $[1,100]$.
   \begin{figure}[h]
+    \centering
     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
@@
     \end{tikzpicture}
-    \caption{$\aut_{ab\{1,100\}}$ where $R=(r_1)$ and $\theta = 1\leq r_1 \leq 100$}
-    \label{fig:cefa1}
+    \caption{$\aut_{(ab)\{1,100\}}$ with one register $r_1$ and $\theta = 1\leq r_1 \leq 100$}
+    \label{fig:repetition}
   \end{figure}
 \end{example}
-The example \ref{eg:1} gives a general picture of constructing a CEFA for a specific extended regex. Firstly, we build an NFA from the extended regex $\regex$
-(e.g, To construct CEFA in example \ref{eg:1}, we firstly construct an NFA with
-transition to be $q_0\xrightarrow{a} q_1\xrightarrow{b}q_2\xrightarrow{\epsilon}
-  q_0$ and $I={q_0}, F={q_2}$). Secondly, we extend NFA to CEFA by adding
-registers to $R$ and vectors $\bar{v}$ to each transition (e.g., we secondly add a
-register $r_1$ to store repetition times and add vector $(1)$ to transition
-$q_0\xrightarrow{a}q_1$ to update the repetition time). Finally, we set the
+The example \ref{eg:1} gives a general picture of constructing a CEFA for a regular expression: firstly, we build an NFA from the regex $\regex$
+(e.g, To construct CEFA in example \ref{eg:1}, an NFA is construted with
+transitions \{$q_0\xrightarrow{a} q_1\xrightarrow{b}q_2\xrightarrow{\epsilon}
+  q_0\}$ initial state $q_0$, and accepting state $q_2$). Secondly, we extend NFA to CEFA by adding registers to $R$ and vector to each transition (e.g., the
+register $r_1$ is added to store repetition times and add vector $\myvec{1}$ is set to transition $q_0\xrightarrow{a}q_1$ to update the repetition time). Finally, we set the
 linear arithmetic $\theta$ carefully to restrict the accepted word to be
-included in $\lan(\regex)$ (e.g., we finally set $\theta = 1\leq r_1\geq 100$ to
-restrict the repetition times to $[1,100]$). Besides the special
-operation repetition, other basic automaton operations are non-trivial. We individually discuss operations repetition, concatenation,
-union, intersection, complement, and Kleene.
+included in $\lan(\regex)$ (e.g., $\theta = 1\leq r_1\geq 100$ is set to
+restrict the repetition times to $[1,100]$). Besides the repetition operation, other operations are non-trivial on CEFA. We individually discuss them in the following subsections.
 
-\subsection{Repetition}\label{subsec:rep}
-Given a CEFA $\aut = (Q,\Sigma,\delta,I,F,R,\theta)$, its repetition with lower bound $l$ and upper bound $k$  is defined as $\aut_{rep} = (Q, \Sigma, \delta', I, F, R\cup\{r'\}, \theta\wedge l\leq r'\leq k )$ where
+\subsection{Non-nested Repetition}\label{subsec:rep}
+Given a CEFA $\aut = (Q,\Sigma,\delta,I,F,\emptyset,true)$, the repetition operation $\{m,n\}$ on it is defined as a CEFA $\aut_{rep} = (Q, \Sigma, \delta', I, F, r_1, \theta')$ where: 
 \begin{itemize}
-  \item $r'$ is the new register,
-  \item and $\delta'$ is composed by transitions $q\xrightarrow[(v_1, \cdots, v_n, 0)]{a} q'$ for all transitions $q\xrightarrow[(v_1, \cdots, v_n)]{a} q' \in \delta$, and transitions $q_m\xrightarrow[0_{n}\cdot 1]{\epsilon} q_0$  for all $q_m\in F$ and $q_0\in I$,
+  \item $r_1$ is the new register,
+  \item $\delta'$ is composed by transitions $q\xrightarrow[\myvec{v}\cdot 0]{a} q'$ for all transitions $q\xrightarrow[\myvec{v}]{a} q' \in \delta$, and transitions $q_m\xrightarrow[0_{n}\cdot 1]{\epsilon} q_0$  for all $q_m\in F$ and $q_0\in I$,
+  \item $\theta'$ is the linear arithmetic $m\leq r_1\leq n$ if all initial states are not accepting. Otherwise, $\theta'$ is the linear arithmetic $r_1\leq n$. 
 \end{itemize} 
-\begin{figure}[h]
-  \begin{subfigure}{0.20\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut$}
-  \end{subfigure}
-  \begin{subfigure}{0.20\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a/\bar{v}\cdot \red{0}$} (q_1)
-      (q_1) edge [bend right] node [above] {$\epsilon /0_n\cdot \red{1}$} (q_0);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The repetition of $\aut$}
-  \end{subfigure}
-  \caption{Repetition}
-  \label{fig:rep}
-\end{figure}
-Figure \ref{fig:rep} illustrates the transition relation between $\aut$ and $\aut_{rep}$.
-Informally, $\aut_{rep}$ add a register $r_{n+1}$ to store the repetition time and update the repetition time on the transitions starting from the initial state.
-$\aut_{rep}$ add formula $l\leq r_{n+1}\leq k$ to ensure the repetition time is greater or equal to $l$ and less or equal to $k$.
+In the construction of $\aut_{rep}$, a new register $r_1$ is added to store the repetition times.
+The transition $q_m\xrightarrow[0_{n}\cdot 1]{\epsilon} q_0$ is added to update the repetition times.
+The linear arithmetic $\theta'$ is set to restrict the repetition times to $[m,n]$.
+Because arbitrary repetition times of empty string is still empty string, the value of $r_i$ need not be greater than $m$ when some initial states are accepting.\newline
+Note that the given CEFA $\aut$ does not contain register. So the repetition operation on $\aut$ is non-nested.
 
 \subsection{Concatenation}\label{subsec:con}
-Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ where $R_1\cap R_2= \emptyset$ and $|R_1|=m,|R_2|=n$, the concatenation is defined as $\aut_{con}=(Q_1\cup Q_2, \Sigma, \delta', I_1, F_2, R_1\cup R_2, \theta_1\wedge\theta_2)$ where $\delta'$ is composed by
+Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2= \emptyset$ and $|R_1|=m,|R_2|=n$, the concatenation is defined as $\aut_{con}=(Q_1\cup Q_2, \Sigma, \delta', I_1, F_2, R_1\cdot R_2, \theta_1\wedge\theta_2)$ where $\delta'$ is composed by
 \begin{itemize}
-  \item $q_1\xrightarrow[\bar{v_1}\cdot 0_n]{a} q_1'$ for each transition $q_1\xrightarrow[\bar{v_1}]{a} q_1' \in \delta_1$,
-  \item $q_2\xrightarrow[0_m\cdot\bar{v_2}]{a} q_2'$ for each transition $q_2\xrightarrow[\bar{v_2}]{a} q_2' \in \delta_2$,
+  \item $q_1\xrightarrow[\myvec{v_1}\cdot 0_n]{a} q_1'$ for each transition $q_1\xrightarrow[\myvec{v_1}]{a} q_1' \in \delta_1$,
+  \item $q_2\xrightarrow[0_m\cdot\myvec{v_2}]{a} q_2'$ for each transition $q_2\xrightarrow[\myvec{v_2}]{a} q_2' \in \delta_2$,
   \item and $q_1\xrightarrow[0_{m+n}]{\epsilon} q_2$ for each $q_1\in F_1$ and $q_2 \in I_2$.
 \end{itemize}
-\begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v_1}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_1$}
-  \end{subfigure}
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v_2}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_2$}
-  \end{subfigure}
-  \begin{subfigure}{0.4\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state]    (q_1) [right=of q_0] {};
-      \node[state]    (q_2) [right=of q_1] {};
-      \node[state, accepting]    (q_3) [right=of q_2] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a/\bar{v_1}\cdot \red{0_n}$} (q_1)
-      (q_1) edge node [below] {$\red{0_{m+n}}$} (q_2)
-      (q_2) edge [bend right] node [below] {$a/\red{0_m}\cdot \bar{v_2}$} (q_3);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-      \node [fit=(q_2) (q_3)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The concatenation of $\aut_1$ and $\aut_2$}
-  \end{subfigure}
-  \caption{Concatenation}
-  \label{fig:con}
-\end{figure}
-Figure \ref{fig:con} outlines the vector change on transitions when concatenating two CEFA.
+% \begin{figure}[h]
+%   \centering
+%   \begin{subfigure}{0.20\textwidth}
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state, accepting]    (q_1) [right=of q_0] {};
+%       \path[->] (q_0) edge [bend right] node [below] {$a/\myvec{v_1}$} (q_1);
+%       \node [fit=(q_0) (q_1)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The CEFA $\aut_1$}
+%   \end{subfigure}
+%   \begin{subfigure}{0.20\textwidth}
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state, accepting]    (q_1) [right=of q_0] {};
+%       \path[->] (q_0) edge [bend right] node [below] {$a/\myvec{v_2}$} (q_1);
+%       \node [fit=(q_0) (q_1)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The CEFA $\aut_2$}
+%   \end{subfigure}
+%   \begin{subfigure}{0.4\textwidth}
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state]    (q_1) [right=of q_0] {};
+%       \node[state]    (q_2) [right=of q_1] {};
+%       \node[state, accepting]    (q_3) [right=of q_2] {};
+%       \path[->]
+%       (q_0) edge [bend right] node [below] {$a/\myvec{v_1}\cdot \red{0_n}$} (q_1)
+%       (q_1) edge node [below] {$\red{0_{m+n}}$} (q_2)
+%       (q_2) edge [bend right] node [below] {$a/\red{0_m}\cdot \myvec{v_2}$} (q_3);
+%       \node [fit=(q_0) (q_1)] {$\cdots$};
+%       \node [fit=(q_2) (q_3)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The concatenation of $\aut_1$ and $\aut_2$}
+%   \end{subfigure}
+%   \caption{Concatenation}
+%   \label{fig:con}
+% \end{figure}
+The concatenation of two CEFAs is similar to the concatenation of two NFAs, except that the registers and its updates are also concatenated.
+
+% Figure \ref{fig:con} outlines the vector change on transitions when concatenating two CEFA.
 Without losing information, $\aut_{con}$ contains all registers in $\aut_1$ and $\aut_2$.
@@
 \subsection{Intersection}\label{subsec:inter}
-Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the intersection is defined as $\aut_{inter} = (Q_1\times Q_2, \Sigma, \delta', I_1\times I_2, F_1\times F_2, R_1\cup R_2, \theta_1\wedge \theta_2)$ where $\delta'$ is composed by
+Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the intersection is defined as $\aut_{inter} = (Q_1\times Q_2, \Sigma, \delta', I_1\times I_2, F_1\times F_2, R_1\cdot R_2, \theta_1\wedge \theta_2)$ where $\delta'$ is composed by
 \begin{itemize}
-  \item transitions $(q_1,q_2)\xrightarrow[\bar{v_1}\cdot\bar{v_2}]{a} (q_1',q_2')$ when both transition $q_1\xrightarrow[\bar{v_1}]{a}q_1'$ and transition $q_2\xrightarrow[\bar{v_2}]{a}q_2'$ exist in $\delta$.
+  \item transitions $(q_1,q_2)\xrightarrow[\myvec{v_1}\cdot\myvec{v_2}]{a} (q_1',q_2')$ for  transition $q_1\xrightarrow[\myvec{v_1}]{a}q_1'$ and transition $q_2\xrightarrow[\myvec{v_2}]{a}q_2'$ exist individually in  $\delta_1$ and $\delta_2$.
 \end{itemize}
-\begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a$/$\bar{v_1}$} (q_1)
-      (q_0) edge [bend left] node [above] {$b$/$\bar{v_1}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_1$}
-  \end{subfigure}
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a$/$\bar{v_2}$} (q_1)
-      (q_0) edge [bend left] node [above] {$c$/$\bar{v_2}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_2$}
-  \end{subfigure}
-  \begin{subfigure}{0.4\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_3) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a$/\red{$\bar{v_1}\cdot \bar{v_2}$}} (q_3);
-      \node [fit=(q_0) (q_3)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The intersection of $\aut_1$ and $\aut_2$}
-  \end{subfigure}
-  \caption{Intersection}
-  \label{fig:inter}
-\end{figure}
-The transition relation of $\aut_1,\aut_2$ and their intersection is displayed by Figure \ref{fig:inter}.
-The intersection of CEFA is similar to the intersection of NFA, except that the intersection of CEFA intersects registers updates and linear arithmetic.
+% \begin{figure}[h]
+%   \centering
+%   \begin{subfigure}{0.20\textwidth}
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state, accepting]    (q_1) [right=of q_0] {};
+%       \path[->]
+%       (q_0) edge [bend right] node [below] {$a$/$\myvec{v_1}$} (q_1)
+%       (q_0) edge [bend left] node [above] {$b$/$\myvec{v_1}$} (q_1);
+%       \node [fit=(q_0) (q_1)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The CEFA $\aut_1$}
+%   \end{subfigure}
+%   \begin{subfigure}{0.20\textwidth}
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state, accepting]    (q_1) [right=of q_0] {};
+%       \path[->]
+%       (q_0) edge [bend right] node [below] {$a$/$\myvec{v_2}$} (q_1)
+%       (q_0) edge [bend left] node [above] {$c$/$\myvec{v_2}$} (q_1);
+%       \node [fit=(q_0) (q_1)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The CEFA $\aut_2$}
+%   \end{subfigure}
+%   \begin{subfigure}{0.4\textwidth}
+%     \centering
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state, accepting]    (q_3) [right=of q_0] {};
+%       \path[->]
+%       (q_0) edge [bend right] node [below] {$a$/\red{$\myvec{v_1}\cdot \myvec{v_2}$}} (q_3);
+%       \node [fit=(q_0) (q_3)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The intersection of $\aut_1$ and $\aut_2$}
+%   \end{subfigure}
+%   \caption{Intersection}
+%   \label{fig:inter}
+% \end{figure}
+The intersection of two CEFAs is similar to the intersection of NFA, except that the registers updates and linear arithmetic are also intersected.
+
 \subsection{Union}\label{subsec:union}
-Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$ and $|R_1|=m,|R_2|=n$, the union is defined as $\aut_{union} = (Q_1\cup Q_2, \Sigma, \delta', \{q_0\}, F_1\cup F_2, R_1\cup R_2\cup (r', r''), \theta')$ where $\delta'$ is composed by
+Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$ and $|R_1|=m,|R_2|=n$, the union is defined as $\aut_{union} = (Q_1\cup Q_2\cup\{q_0\}, \Sigma, \delta', \{q_0\}, F_1\cup F_2, R_1\cdot R_2\cdot (r_1, r_2), \theta')$ where $\delta'$ is composed by
 \begin{itemize}
@@
   \item transitions $q_0\xrightarrow[0_{m+n}\cdot(0,1)]{\epsilon}q_2$ for all $q_2\in I_2$,
-  \item transitions $q_1\xrightarrow[\bar{v_1}0_{n+2}]{a} q_1'$ for all $q_1\xrightarrow[\bar{v_1}]{a} q_1'\in \delta_1$,
-  \item transitions $q_2\xrightarrow[0_m\bar{v_2}0_2]{a} q_2'$ for all $q_2\xrightarrow[\bar{v_2}]{a} q_2'\in \delta_2$,
+  \item transitions $q_1\xrightarrow[\myvec{v_1}0_{n+2}]{a} q_1'$ for all $q_1\xrightarrow[\myvec{v_1}]{a} q_1'\in \delta_1$,
+  \item transitions $q_2\xrightarrow[0_m\myvec{v_2}0_2]{a} q_2'$ for all $q_2\xrightarrow[\myvec{v_2}]{a} q_2'\in \delta_2$.
 \end{itemize}
-and 
+$r_1$ and $r_2$ are new registers.
+$q_0$ is a new state where $q_0\not\in Q_1$ and $q_0\not\in Q_2$.
+Assume that $\theta  = (r_1>0\wedge\theta_1)\vee(r_2>0\wedge\theta_2)$, $\theta'$ is constructed differently in four cases:
 \begin{itemize}
-  \item $r'$ and $r''$ are new registers,
-  \item $q_0$ is a new state where $q_0\not\in Q_1$ and $q_0\not\in Q_2$,
-  \item $\theta_{tmp} = (r'>0\wedge\theta_1)\vee(r''>0\wedge\theta_2)$, $\theta'$ is constructed differently in four cases:
-  \begin{itemize}
-    \item [-]$I_1\cap F_1=\emptyset$ and $I_2\cap F_2=\emptyset$: $\theta'$ = $\theta_{tmp}$;
-    \item [-]$I_1\cap F_1\not=\emptyset$ and $I_2\cap F_2=\emptyset$: $\theta'$ = $\theta_{tmp}\vee (r'==0\wedge r''==0\wedge\theta_1)$;
-    \item [-]$I_1\cap F_1=\emptyset$ and $I_2\cap F_2\not=\emptyset$: $\theta'$ = $\theta_{tmp}\vee (r'==0\wedge r''==0\wedge\theta_2)$;
-    \item [-]$I_1\cap F_1\not=\emptyset$ and $I_2\cap F_2\not=\emptyset$: $\theta'$ = $\theta_{tmp}\vee (r'==0\wedge r''==0\wedge(\theta_1\vee\theta_2))$;
+  \item both $I_1$ and $I_2$ do not contain accepting states: $\theta'$ = $\theta $;
+  \item $I_1$ contains accepting states while $I_2$ does not: $\theta'$ = $\theta \vee (r_1==0\wedge r_2==0\wedge\theta_1)$;
+  \item $I_2$ contains accepting states while $I_1$ does not: $\theta'$ = $\theta \vee (r_1==0\wedge r_2==0\wedge\theta_2)$;
+  \item both $I_1$ and $I_2$ contain accepting states: $\theta'$ = $\theta \vee (r_1==0\wedge r_2==0\wedge(\theta_1\vee\theta_2))$;
 \end{itemize}
-\end{itemize}
-\begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend left] node [above] {$a$/$\bar{v_1}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_1$}
-  \end{subfigure}
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a$/$\bar{v_2}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_2$}
-  \end{subfigure}
-  \begin{subfigure}{0.4\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state]   (q_1) [above right=of q_0] {};
-      \node[state, accepting]   (q_1') [right=of q_1] {};
-      \node[state]   (q_2) [below right=of q_0] {};
-      \node[state, accepting]   (q_2') [right=of q_2] {};
-      \path[->]
-      (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(1,0)}$} (q_1)
-      (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(0,1)}$} (q_2)
-      (q_1) edge [bend left] node [above] {$a$/\red{$\bar{v_1}\cdot 0_{n+2}$}} (q_1')
-      (q_2) edge [bend right] node [below] {$a$/\red{$0_m\cdot \bar{v_2}\cdot 0_2$}} (q_2');
-      \node [fit=(q_1) (q_1')] {$\cdots$};
-      \node [fit=(q_2) (q_2')] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The union of $\aut_1$ and $\aut_2$}
-  \end{subfigure}
-  \caption{Union}
-  \label{fig:union}
 
-\end{figure}
-The Union of two CEFA is shown in Figure \ref{fig:union}.
-To simulate the semantics of the union, we add an initial state $q_0$ and transitions from $q_0$ to initial states of $\aut_1$ and $\aut_2$ to randomly choose one automaton.
-The values of $r'$ and $r''$ distinguish which automaton we run.
-In the construction above, $r'>0$ means that we choose $\aut_1$ to run a word, $r''>0$ implies that we select $r''$ to run a word, and $r'==0\wedge r''=0$ means that we decide to run word $\epsilon$.
+% \begin{figure}[h]
+%   \centering
+%   \begin{subfigure}{0.20\textwidth}
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state, accepting]    (q_1) [right=of q_0] {};
+%       \path[->]
+%       (q_0) edge [bend left] node [above] {$a$/$\myvec{v_1}$} (q_1);
+%       \node [fit=(q_0) (q_1)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The CEFA $\aut_1$}
+%   \end{subfigure}
+%   \begin{subfigure}{0.20\textwidth}
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state, accepting]    (q_1) [right=of q_0] {};
+%       \path[->]
+%       (q_0) edge [bend right] node [below] {$a$/$\myvec{v_2}$} (q_1);
+%       \node [fit=(q_0) (q_1)] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The CEFA $\aut_2$}
+%   \end{subfigure}
+%   \begin{subfigure}{0.4\textwidth}
+%     \centering
+%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
+%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
+%       \node[state, initial]   (q_0) {};
+%       \node[state]   (q_1) [above right=of q_0] {};
+%       \node[state, accepting]   (q_1') [right=of q_1] {};
+%       \node[state]   (q_2) [below right=of q_0] {};
+%       \node[state, accepting]   (q_2') [right=of q_2] {};
+%       \path[->]
+%       (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(1,0)}$} (q_1)
+%       (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(0,1)}$} (q_2)
+%       (q_1) edge [bend left] node [above] {$a$/\red{$\myvec{v_1}\cdot 0_{n+2}$}} (q_1')
+%       (q_2) edge [bend right] node [below] {$a$/\red{$0_m\cdot \myvec{v_2}\cdot 0_2$}} (q_2');
+%       \node [fit=(q_1) (q_1')] {$\cdots$};
+%       \node [fit=(q_2) (q_2')] {$\cdots$};
+%     \end{tikzpicture}
+%     \caption{The union of $\aut_1$ and $\aut_2$}
+%   \end{subfigure}
+%   \caption{Union}
+%   \label{fig:union}
 
-\subsection{Complement}\label{subsec:comp}
-We use the function $nfa$ to return the NFA form of a CEFA.
-More precisely, given a CEFA $\aut = (Q, \Sigma, I, F, \delta, R, \theta)$, $nfa(\aut)$ is an NFA tuple $(Q, \Sigma, \delta', I, F)$  where $\delta'$ comprises transition $(q, a, q')$ for $(q, a, q', \bar{v})\in \delta$ .
-Similarly, the function $cefa(\aut)$ is used to return the CEFA form of an NFA: $cefa(\aut_{nfa}) = (Q, \Sigma, I, F, \delta, \emptyset, true)$ for $\aut_{nfa} = (Q, \Sigma, I, F, \delta')$ where $\delta$ comprises transition $(q, a, q', \emptyset)$ for $(q, a, q')\in \delta'$.
-\verb|uion| denotes the CEFA operation union.
+% \end{figure}
+To simulate the semantics of the union, we add transitions from $q_0$ to initial states of $\aut_1$ and $\aut_2$ to randomly choose one automaton.
+$r_1 > 0$ indicates we choose $\aut_1$ to run while $r_2 > 0$ indicates we choose $\aut_2$ to run.
+We should make sure the accepting condition is consistent.
+Therefore, the accepting condition $(r_1>0\wedge\theta_1)\vee(r_2>0\wedge\theta_2)$ is generated.
+Furthermore, the accepting run may stop at the new initial state $q_0$ with $\mathcal{V}(r_1) = 0, \mathcal{V}(r_2)=0$.
+It can only happen when some initial states of two given CEFAs are accepting.
+If some initial states of $\aut_1$ are accepting, the accepting condition $r_1=0\wedge r_2=0\wedge \theta_1$ is generated.
+Similarly, if some initial states of $\aut_2$ are accepting, the accepting condition $r_1=0\wedge r_2=0\wedge \theta_2$ is generated.
+Finally, the disjunction of all generated accepting conditions $\theta'$ is obtained to express the non-nondeterministic.
+\subsection{Complement}
+Given a CEFA $\aut = (Q, \Sigma, I, F, \delta, \emptyset, true)$, the complement $\aut^c$ is defined as the CEFA $\aut^c = (Q, \Sigma, I, F^c, \delta, R, \theta^c)$ where $F^c = Q\setminus F$ and $\theta^c = \neg \theta$.
+\subsection{Closure}
+\subsection{Complement of Repetition and Nested Repetition}\label{subsec:comp}
+As we mentioned,  CEFA
 
-Given a CEFA $\aut = (Q,\Sigma, \delta, I, F, R, \theta)$, the complement of $\aut$ is defined as $\aut_{comp} = \verb|union|(\aut_{NFA}^C, \aut_{negf})$ where $\aut_{negf} = \\(Q,\Sigma, \delta, I, F, R, \neg\theta)$ and $\aut_{NFA}^C$ is obtained by three steps:
-\begin{itemize}
-  \item compute the NFA form $\aut_n = nfa(\aut) = (Q,\sigma, \delta', I, F)$,
-  \item the complement of $\aut_n$ is $\aut_n^C = (Q, \sigma, \delta', F, I)$,
-  \item extend $\aut_n^C$ to CEFA form $\aut_{NFA}^C = cefa(\aut_n^C)$.
-\end{itemize}
-\begin{figure}[h]
-  \begin{subfigure}{0.40\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->] (q_0) edge [bend right] node [below] {$a/\bar{v}$} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut$}
-  \end{subfigure}
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=
-      ]
-      \node[state, initial, accepting]   (q_0) {};
-      \node[state]    (q_1) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a$/\red{$\emptyset$}} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_{NFA}^C$}
-  \end{subfigure}
-  \begin{subfigure}{0.20\textwidth}
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->]
-      (q_0) edge [bend right] node [below] {$a$/\red{$\bar{v}$}} (q_1);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA $\aut_{negf}$}
-  \end{subfigure}
-  \caption{Complement}
-  \label{fig:comp}
-\end{figure}
-As Figure \ref{fig:comp} shows, the complement of CEFA is the union of $\aut_{NFA}^C$ and $\aut_{negf}$.
-$\aut_{NFA}^C$ accepts words that $nfa(\aut)$ does not accept and $\aut_{negf}$ accepted words might be accepted by the $nfa(\aut)$ but not satisfy linear constraints $\theta$.
-\subsection{Kleene}\label{subsec:klee}
-The construction of Kleene is trivial.
-Given a CEFA $\aut = (Q,\Sigma,\delta,I,F,R,\theta)$ with $|R|=n$, the Kleene of $\aut_{Kleene}$ is defined as $(Q,\Sigma,\delta',I,F,R,\theta)$ where $\delta'$ comprises all transitions in $\delta$ and new transitions $q_f\xrightarrow[0_n]{\epsilon} q_0$ for each $q_0\in I$ and $q_f\in F$.
-
-\subsection{From Extended Regex to CEFA} \label{subsec:regex2cefa}
+\subsection{From Regex to CEFA} \label{subsec:regex2cefa}
 \highlight{Basis}: The basis has three parts with empty registers and valid linear arithmetic, shown in Fig.
@@
   \centering
-  \begin{subfigure}{0.13\textwidth}
+  \begin{subfigure}{0.3\textwidth}
     \centering
@@
   \end{subfigure}
-  \begin{subfigure}{0.13\textwidth}
+  \begin{subfigure}{0.3\textwidth}
     \centering
@@
   \end{subfigure}
-  \begin{subfigure}{0.13 \textwidth}
+  \begin{subfigure}{0.3\textwidth}
     \centering
@@
 We can union the CEFA of $\regex_1$ and the CEFA of $\regex_2$ as shown in section \ref{subsec:union}.
-  \item The expression is $\regex*$ for some smaller expression $\regex$. We can construct the Kleene Star of the CEFA of $\regex$  as shown in section \ref{subsec:klee}.
+  \item The expression is $\regex*$ for some smaller expression $\regex$. We can construct the closure Star of the CEFA of $\regex$  as shown in section \ref{subsec:klee}.
   \item The expression is $\regex^C$ for some smaller expression $\regex$. We can construct the complement of the CEFA of $\regex$  as shown in section \ref{subsec:comp}
@@
 \section{Solve String Constraints with Large Repetition Bound} \label{sec:solve}
-Following the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve string constraints by CEFA.
-Firstly, we replace all length operations $i=\strlen{x}$ to pre-images, and intersect these pre-images to $lenAut_x$.
-Then for each term $x$, we genearte CEFAs from all regular expressiones $\regex$ in all terms $x\in \regex$, and intersect the CEFAs with $lenAut_x$ to get the final CEFAs.
-Finally, we check whether the final CEFAs is empty under the linear integer arithmetic $P$.
+Following the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve string constraints with help of CEFA.
+Firstly, we replace all length operations $i=\strlen{x}$ to pre-images which are represented by CEFAs, and intersect these CEFAs to $lenAut_x$.
+Then for each term $x$, we generate CEFAs of all regular expressions $\regex$ in all terms $x\in \regex$, and intersect these CEFAs with $lenAut_x$ to get the final CEFA.
+Finally, we check whether each final CEFA is empty under the linear integer arithmetic $P$.
 If one of the final CEFAs is empty, the string constraints are unsatisfiable.
@@
 The implemented details are eliminated for clarity.
-From line \ref{alg:high:line1} to line \ref{alg:high:line5}, we construct the CEFAs of all length operations $i = \strlen{x}$ occurring in $\varphi$.
-The CEFA $lenAut_x$ is the automaton reserving all length information on $x$.
+From line \ref{alg:high:line1} to line \ref{alg:high:line5}, we construct the CEFAs of all length operations occurring in the string constraints.
+The CEFA $lenAut_x$ is the automaton used to store length information on $x$.
 $lenAut_x$ is initiated to accept all strings at line \ref{alg:high:line2}.
-And for each length operation $i = \strlen{x}$, we construct the pre-image of the length operation at line \ref{alg:high:line3}.
-Then we intersect $lenAut_x$ with the pre-image at line \ref{alg:high:line4}.
-Note that the final $lenAut_x$ is the intersection of many pre-images.\newline
+For each length operation $i = \strlen{x}$, we construct the pre-image of it at line \ref{alg:high:line3}, and intersect the pre-image to $lenAut_x$ at line \ref{alg:high:line4} to store length information.
+Note that the final $lenAut_x$ is the intersection of all pre-images so that it can store all length information on $x$.\newline
 In the following steps, we call a CEFA to be \emph{atomic} if we will not operate it anymore.
-The set $atomAuts$ is the set of all atomic CEFAs for all terms $x$ occurring in $\varphi$, and it is initiated to empty set at line \ref{alg:high:line6}.
-From line \ref{alg:high:line6} to line 14, we construct the atomic CEFAs of all string variables $x$ occurring in $\varphi$.
-For each string variable $x$, we construct the CEFA $\aut_x$ by intersecting $lenAut_x$ and all CEFAs corresponding to regexes in $S$.
-If the NFA form of $\aut_x$ is empty (i.e., the NFA accepts no word), we return $unsat$ directly because the NFA form is an over-approximation of CEFA.
-Otherwise, we add $\aut_x$ to $atomAuts$ at line 9.\newline
+The set $atomAuts$ is the set of all atomic CEFAs for all terms $x$ occurring in the string constraints, and is initially empty at line \ref{alg:high:line6}.
+From line 7 to line 14, each atomic automaton in the set is constructed by intersecting the length automaton $lenAut_x$ to all CEFAs corresponding to the regex expressions with regard to string term $x$.
+If the NFA form of the atomic automaton is empty (i.e., the NFA accepts no word), we return $unsat$ directly because the NFA form is an over-approximation of CEFA.
+\newline
 After obtaining the atomic CEFAs of all string terms, we check whether the atomic CEFAs are empty under the linear integer arithmetic $P$ at line 15.
-If the atomic CEFAs are empty, we return $unsat$.
+If the atomic CEFAs are empty under $P$, we return $unsat$.
 Otherwise, we return $sat$.
-The emptiness checking is complex, and we will discuss its details in the following subsection.\newline
+The emptiness checking at line 15 is complex, and we discuss it detailly in the following subsection.\newline
 
@@
 In our previous research, we rewrote CEFA to an infinite system and used a model-checking tool \emph{NuSMV} to solve it.
-In this paper, we use a more efficient method to solve the emptiness checking problem.
-The details are shown in Algorithm \ref{alg:emptiness}.\newline
-The input CEFAs may have many transitions and registers, so the emptiness checking problem is hard to solve.
-We simplify the CEFAs at line 1.
-The simplification is to remove all duplicated transitions and registers in the CEFAs.
-The simplification is implemented by Algorithm \ref{alg:simplify}.
-Then we try to find a solution by under-approximation at line 3.
-The under-approximation is implemented by Algorithm \ref{alg:underApprox}.
-If we find a solution, the CEFAs under linear integer arithmetic $P$ are not empty.
-So we return $false$ at line 5.
-We will try many times until we find a solution or reach $MaxBound$.
+However, the previous method was not effictive enough.
+So we put forward a new method to solve it.\newline
+As shown in Algorithm \ref{alg:emptiness}, We simplify the CEFAs at line 1 because the input CEFAs may have many transitions and registers.
+The purpose of the simplification is removing duplicated transitions and registers in the CEFA.
+After simplifying the input CEFAs, we try to find a solution by under-approximation at line 3.
+If we find a solution, we return $false$ at line 5 because the CEFAs under linear integer arithmetic $P$ are not empty.
 Otherwise, we try to find an unsat core by over-approximation at line 8.
-The over-approximation is implemented by Algorithm \ref{alg:overApprox}.
-If we discover an unsat core, we know that the CEFAs under $P$ are empty, and we return $true$ at line 10.
-Suppose both under- and over-approximation do not make sense.
-In that case, we compute the Parikh images\cite{parikh_2005} of the simplified CEFAs and check if the Parikh images in conjunction with $P$ are satisfiable at line 12.
-The unsatisfiability implies emptiness directly.
+If we discover an unsat core,
+we return $true$ at line 10 because we know that the CEFAs under $P$ are empty.
+Suppose that both under- and over-approximation do not make sense, we compute the Parikh images of the simplified CEFAs by algorithm in the paper \cite{parikh_2005}, and check if the Parikh images are satisfiable in conjunction with $P$ at line 12.
+The satisfiability implies non-emptiness directly.
+\newline
+Note that the under-approximation program is executed many times until $MaxBound$ is reached.
+The details of simplification is shown in Algorithm \ref{alg:simplify}.
+The details of under- and over-approximation are shown in Algorithm \ref{alg:underApprox} and Algorithm \ref{alg:overApprox} respectively.
+The details of Parikh image computation are omitted for clarity.\newline
 \begin{algorithm}
@@
 \end{algorithm}
-\subsection{Simplification of CEFA}
-The main idea of simplification is to remove duplicated transitions and registers.
-In emptiness checking Algorithm \ref{alg:emptiness}, the vectors on the transitions are meaningful, but the letters on the transitions are not.
-So we see the alphabet of the CEFA as unary (i.e., the alphabet is $\{a\}$).
-Compared with NFA, the vectors in the CEFA are the letters in the NFA, and the vector $\myvec{0}_n$ is seen as $\epsilon$.
-Based on the similarity between NFA and CEFA, firstly, determinization and minimization \cite{aut_hopcraft} are applied to simplify the CEFA.
-Then we merge the registers having the same updating at all transitions and get the final CEFA.
-The main simplification framework is shown in Algorithm \ref{alg:simplify}, and some details are eliminated for simplicity.
-\begin{algorithm}
-  \caption{$\algfun{simplify}(auts)$}
-  \label{alg:simplify}
-  \begin{algorithmic}[1]
-    \Require CEFAs $auts$
-    \Ensure Simplified CEFAs $simpliAuts$
-    \Statex
-    \State $simpliAuts \gets \emptyset$
-    \For{$aut \in auts$}
-      \State $aut \gets \algfun{determinizeByVec}(aut)$
-      \State $aut \gets \algfun{minimizeByVec}(aut)$
-      \State $aut \gets \algfun{mergeRegisters}(aut)$
-      \State $simpliAuts \gets simpliAuts \cup \{aut\}$
-    \EndFor
-    \State \textbf{return} $simpliAuts$
-  \end{algorithmic}
-\end{algorithm}
 
 \subsection{Under-Approximation}
-To solve the emptiness checking problem, we translate the CEFAs to linear integer arithmetic and check if the linear integer arithmetic in conjunction with $P$ is satisfiable.
-The main idea of under-approximation is to translate the CEFAs step by step.
-A string length bound controls the translation, and linear integer arithmetic is generated from low to high length bound.
-This section only discusses the situation where the bound is fixed.
+To solve the satisfiable instances of the emptiness checking problem, under-approximation procedure is come up.
+The main idea is exploring the CEFA deep-firstly.
+The string length bound the deep, and linear integer arithmetic is generated from low to high string length.
+This section only discusses the situation in where the string length bound is fixed.
 The details are shown in the Algorithm \ref{alg:underApprox}.
@@
   \begin{algorithmic}[1]
-    \Require CEFAs $auts$ and length bound $bound$
-    \Ensure Linear integer arithmetic $\varphi_{under}$
+    \Require The CEFAs $auts$ and string length $bound$
+    \Ensure The linear integer arithmetic $\varphi_{under}$ representing under-approximation of the register values of $auts$
     \Statex
@@
     \For{$aut \in auts$}
-      \State Let $\varphi_{aut}$ to be the linear integer arithmetic generated by  enumerating all the paths with length less than $bound$ in $aut$
-      \State $\varphi_{under} \gets \varphi_{under} \wedge \varphi_{aut}$
+      \State Suppose $aut = (Q, \Sigma, \delta, q_0, F, (r_1, \cdots, r_m), \theta)$
+      \State $S_0 \gets \{(q_0, \myvec{0}_m)\}$
+      \ForAll{path $q_0q_1\cdots q_{n}$ whose length is $bound$ and $\myvec{R}$ is the sum of the vectors on the path}
+        \If{$q_{n}\in F$}
+          \State $\varphi_{under} \gets \varphi_{under} \bigwedge_{i\in[1,m]} r_i = \myvec{R}(i)$
+        \EndIf
+      \EndFor
     \EndFor
@@
 \end{algorithm}
+
+\subsection{Simplification of CEFA}
+The main purpose of simplification is to remove duplicated transitions and registers.
+In the emptiness checking Algorithm \ref{alg:emptiness}, the vectors on the transitions are meaningful while the letters on the transitions are not.
+So we see the alphabet of the CEFA as unary (i.e., the alphabet is $\{a\}$).
+Then the vector in the CEFA is seen as the letter in the NFA, and the vector $\myvec{0}_n$ is seen as $\epsilon$.
+Based on the homomorphism between NFA and CEFA, we determinate and minimize \cite{aut_hopcraft} the CEFA by vector firstly.
+Then we merge the registers having the same updating at all transitions.
+The main simplification framework is shown in Algorithm \ref{alg:simplify}.
+\begin{algorithm}
+  \caption{$\algfun{simplify}(auts)$}
+  \label{alg:simplify}
+  \begin{algorithmic}[1]
+    \Require CEFAs $auts$
+    \Ensure Simplified CEFAs $simpliAuts$
+    \Statex
+    \State $simpliAuts \gets \emptyset$
+    \For{$aut \in auts$}
+      \State $aut \gets \algfun{determinizeByVec}(aut)$
+      \State $aut \gets \algfun{minimizeByVec}(aut)$
+      \State $aut \gets \algfun{mergeRegisters}(aut)$
+      \State $simpliAuts \gets simpliAuts \cup \{aut\}$
+    \EndFor
+    \State \textbf{return} $simpliAuts$
+  \end{algorithmic}
+\end{algorithm}
+
 \section{Implementation and Experiment} \label{sec:imp}
@@
 TODO
-% We implement Algorithm \ref{alg:high} on our string solver ostrich \cite{ostrich2023}.
-And compare our solver with z3 on benchmark \emph{LoopBench}.
-The result shows that our algorithm performs better than z3.\\
-% \highlight{LoopBench}: The benchmark consists of three parts:
-% \begin{enumerate}
-%   \item \textbf{Z3strRE}: We extract instances with repetition operator from (paper z3str3Re).
-z3strRE support string operation \verb|num2str| which is not supported by ostrich.
-So we remove these instances with \verb|num2str|.
-%   \item \textbf{StackOverflow}: We extract real-world regexes from StackOverflow\cite{stackoverflow} using the tool zaligvinder\cite{zaligvinder_2021} and translate these regexes to smtlib2 format.
-For each regex, we generate an instance with one regular membership and a length operation.
-%   \item \textbf{RegexLib}: We also extract real-world regexes from regexlib\cite{regexlib} using zaligvinder and generate instances in the same way as StackOverflow.
-% \end{enumerate}
-% The experimental result is shown in Table \ref{tab:res}.
-ostrich performs very closely on satisfiable instances and outperforms z3 on unsatisfiable instances.
-Furthermore, ostrich use a little more time to find the result rather than z3.
-% \begin{table}[h]
-%   \begin{tabular}{|l|l|l|l|l|l|}
-%     \hline
-%             & sat  & unsat & error & sat time & unsat time \\ \hline
-%     z3      & 6995 & 5491  & 382   & 1.09s    & 0.42s      \\ \hline
-%     ostrich & 6966 & 5751  & 150   & 2.82s    & 1.81s      \\ \hline
-%   \end{tabular}
-%   \caption{Detailed results for the LoopBench benchmark. Ostrich can solve more instances.}
-%   \label{tab:res}
-% \end{table}
+\subsection{Overall Evaluation of Experiment}
+tools: cvc5, z3str3, z3str3re, z3-trau, ostrich
+benchmark: total benchmark
+
+\subsection{Experimental Details}
+tools: cvc5, z3str3, z3str3re, z3-trau, ostrich
+benchmmark:
+\begin{itemize}
+  \item Small Count: the sum of upper bounds on the repetition operator is less than 50
+  \begin{itemize}
+    \item z3str3re-bench
+    \item regexlib
+    \item stackoverflow
+    \item ReDos-bench
+  \end{itemize}
+  \item Large Count: the sum of upper bounds on the repetition operator is greater than 50
+  \begin{itemize}
+    \item z3str3re-bench
+    \item regexlib
+    \item stackoverflow
+    \item ReDos-bench
+  \end{itemize}
+\end{itemize}
+
+\subsection{Analysis of All Algorithms}
+tools:
+\begin{itemize}
+  \item ostrich-baseline: the origin ostrich syntactically unwind all repetition operators.
+  \item ostrich-new: the most efficient ostrich which using CEFA and all heuristics
+  \item ostrich-without-under: without under-approxiamtion
+  \item ostrich-without-over: without over-approximation
+  \item ostrich-without-simplification: without simplification of CEFA
+  \item ostrich-without-rapidly-finding-string: without context-aware finding string
+\end{itemize}
 

### 2023-04-10 2023-1-19/efficient_way_for_counting.tex
atva2023 first version

@@
 
+\usepackage{standalone}
+\usepackage{import}
 \usepackage{subcaption}
+\usepackage{pgfplots}
+\usepackage{color}
 \usepackage{tikz}
+\usepackage{pgfplots}
+\usepgfplotslibrary{fillbetween}
+\pgfplotsset{compat=1.16}
 \usetikzlibrary {arrows.meta, automata, positioning, fit}
@@
 \newcommand*{\strlen}[1]{\texttt{len}(#1)}
-
+\newcommand*{\myemph}[1]{\textcolor{red}{#1}}
+\newcommand*{\mult}[1]{$\times$}
 %%
@@
 \begin{document}
-
 %%
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Efficient Methods for Solving String Constraints with Large Repetition Bound}
+\title{Efficient Methods for Solving String Constraints with Bounded Repetition}
 
@@
 
-%%
-%% The abstract is a short summary of the work to be presented in the
+%% The abstract is a summary of the work to be presented in the
 %% article.
 \begin{abstract}
-  Regular expression with large repetition bounds frequently appears in the real world.
-However, state-of-art string solvers can not efficiently solve string constraints with such regular expression, which slows down string solver applications like formal verification and symbolic execution.
-In this paper, we
-  propose a new systematic algorithm based on cost-enriched automaton. We use
-  heuristic ways like over-approximation and under-approximation to accelerate the search. Further, we extract amounts of regex expressions with large repetition
-  bounds from real-world programs and generate a significant benchmark.
-We evaluate the algorithm's performance on our developed benchmarks and other typical benchmarks.
-The result shows that our solver outperforms the state-of-art string solvers.
-
-\keywords{string constraints, cost-enriched automata, regex expression, bounded repetition}
+\subimport{sections/}{abstract.tex}
 \end{abstract}
 
-\section{Introduction}
-Regular expressions are widely used in programming languages.
-About 30–40 \% of Java, JavaScript, and Python software uses regex matching \cite{redos_fse2019}.
-To handle the problems in software verification reasoning about string, the string theory is introduced and amounts of string solvers are developed.
-However, the string theory is one of the most challenging theories because it is easy to be undecidable \cite{undecidable_2016}.
-String solvers try very hard to improve efficiency:  DPLL(T)-based string solver Z3 \cite{z3} and Cvc5 \cite{cvc5} apply many heuristic derivation rules.
-Automaton-based string solver Trau+\cite{trau} proposed flat automaton and uses the CEGAR framework to under-approximate
-and over-approximate the string constraints again and again.
-Unfortunately, the string solvers above perform poorly when the string constraints contain large repetition bounds.
-[add a example].
-To address this issue, we extend cost-enriched finite automaton(CEFA)\cite{atva2020} with linear arithmetical constraint.
-Use backward-propagating algorithm to search a solution.
-Our main contributions are as follows:
-\begin{enumerate}
-  \item  Extend cost-enriched finite automaton to model the regular expression with large repetition bound.
-  \item  Devise an efficient algorithm based on CEFA to solve string constraints with large repetition bound.
-  \item  Generate many instances with large repetition bound from real-word regular expressions.
-  \item  Implemented our efficient algorithm on Ostrich\ref{Ostrich} and compared it with state-of-art string solvers. The result shows the superiority of our automaton model and algorithm.
-\end{enumerate}
-%TODO: list the main contributions
-% The structure of this paper is as follows: We introduce some abbreviations and concepts in section \ref{sec:pre} and introduce the syntax and semantics of the string theory logic in section \ref{sec:str_t}.
-Then we develop cost-enriched finite automaton model and its operations at section \ref{sec:cefa}.
-The efficient algorithm is discussed in section \ref{sec:solve}, and the implementation of the algorithm is mentioned in section \ref{sec:imp}.
-Finally, we conclude our work and look into future work in section \ref{sec:conclu}.
+\section{Introduction} \label{sec:intro}
+\subimport{sections/}{introduction.tex}
 
 \section{Preliminaries} \label{sec:pre}
-%TODO: preliminaries
-\highlight{Tokens.} A finite \emph{alphabet} $\Sigma$ is the set of all \emph{letters}. A
-\emph{string} is a finite sequence of letters from $\Sigma$. We use $\Sigma^*$ to
-denote the set of strings over $\Sigma$, $\epsilon$ to denote the empty string, and $a,
-  b,\cdots$ to denote constant letters in $\Sigma$. We use $u, v,\cdots$ to denote constant
-string and $x, y,\cdots$ to denote variable string.
-Moreover, we also consider a set of natural integer numbers $\mathbb{N} = \{0,1,2,3,\cdots\}$ and a set of integer numbers $\mathbb{Z}= \{\cdots, -1, 0, 1, \cdots\}$.
-We use $m,n,\cdots$ to
-denote integer constant, and $i,j\cdots$ to denote integer variable.
-For vector, we use $\myvec{v}$ to denote the vector of integer constant, $0_n$ to denote the zero vector with length $n$, $v(i)$ to denote the integer value of $\myvec{v}$ at position $i$, $\myvec{v_1}\cdot\myvec{v_2}$ to denote the concatenation of $\myvec{v_1}$ and $\myvec{v_2}$, $R$ to denote the vector of integer variable, $R_1 \cap R_2$ to denote the same variables of $R_1$ and $R_2$, and $|\myvec{v}|$ or $|R|$ to denote the length of vector.\newline
-\highlight{CNF, DNF, clause, cube.} We assume that the reader is familiar with first-order logic.
-A \emph{literal} is an atomic proposition or its negation.
-A \emph{clause} is a disjunction of literals.
-The empty clause is $true$.
-A formula is in \emph{conjunctive normal norm} (CNF) if it is a conjunction of clauses.
-A \emph{cube} is a conjunction of a consistent set of literals; The empty cube is $false$.
-A formula is in \emph{disjunctive normal form} (DNF) if it is a disjunction of cubes.\newline
-\highlight{Basic Regular Language.} A nondeterministic finite state automaton (NFA) is a tuple $\aut=(Q, \Sigma, \delta, I, F)$ where $Q$ is a finite set of states; $\Sigma$ is a finite alphabet; $\delta\in Q\times\Sigma\times Q$ is the transition relation; $I, F\subseteq Q$ are the set of initial states and finite states respectively.
-We write a transition $(q, a, q') \in \delta$ as $q\xrightarrow{a} q'$ for readability.
-A \emph{run} of an NFA $\aut$ on a string $w = a_1\cdots a_n$ is a sequence of transitions $q_0\xrightarrow{a_1}q_1\cdots q_{n-1}\xrightarrow{a_n}q_n$ with $q_0\in I$.
-The run is \emph{accepting} if $q_{n}\in F$.
-A word $w$ is \emph{accepted} by an NFA $\aut$ if there is an accepting run on $w$.
-The \emph{language} of $\aut$ is the set of all words accepted by $\aut$, denoted by $\lan(\aut)$.
-From automata theory\cite{aut_hopcraft}, basic regular expression only contains union, concatenation, and closure operations.
-We know that the language of basic regular expression are also in the class of $\lan(\aut)$.
-We call it \emph{Basic Regular Language}.
-\section{String Theory with Regex} \label{sec:str_t}
-% TODO: Syntax and semantic
-In this section, the syntax and semantic of string theory is defined.
-\subsection{Syntax}
-In this paper, we propose a new logic called \textit{Extended String Logic (ESL)}. ESL contains the following
-sorts: string sort \verb|Str|, integer sort \verb|Int|, the enumerable set of string
-sort $\verb|Str|^m$, and the enumerable set of integer sort $\verb|Int|^m$ for each $m\in
-  \mathbb{N}$. Furthermore, ESL includes the following predicate and function constants:
-string concatenation $\verb|con|:\verb|Str|\times\verb|Str|\rightarrow \verb|Str|$;
-string length $\verb|len|: \verb|Str|\rightarrow \verb|Int|$; regular membership $\in:
-\verb|Str|\times \verb|Str|^m$; the regex operators such as closure, concatenation,  conjunction, disjunction, intersection, repetition and complement; and the usual constants of linear arithmetic.
+\subimport{sections/}{preliminaries.tex}
 
-The syntax of ESL is presented in Table \ref{tab:syntax}. $\varphi$ is a first-order logic formula that can be a regular membership $x\in\regex$,
-a word equation $e$, a quantifier-free Presburger arithmetic formula $\beta$, a negation of a formula, or a
-disjunction of two formulas.
-A word equation $e$ is an equality of two string terms.$\beta$ is an (in)equality of two integer terms and the (in)equality operator $\odot$ contains $=, \geq$.
-A string term $s$ is an empty string $\epsilon$, letters
-$a\in\Sigma$, string variable $x$, or a concatenation of two string terms. An integer
-term $\alpha$ is an integer constant 0, integer constant 1, integer variable $i$, the
-length of the string term $s$, minus an integer term, or plus of two integer terms. The
-regular expression $\regex$ is built on empty string $\epsilon$, constant letter $a\in \Sigma$. The supported regex operations involve concatenation $\cdot$, disjunction $+$,
-intersection $\times$, closure $*$, complement $C$, and repetition $\{m, n\}$.
+\section{Overview} \label{sec:overall}
+\subimport{sections/}{overview.tex}
 
-We consider \emph{straight-line} fragment\cite{atva2020}\cite{quadratic_aplas2018} $ESL_{s}$ of the string theory logic. 
-A formula $\varphi$ is said to be straight-line if it can be converted to a DNF formula $\bigvee_{i} \phi_i$ and $\phi_i= (\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$
-where $\bigwedge_{i=1}^n e_i$ is straight-line, $\Re$ is a
-\emph{cube} of regular membership $x\in \regex$ or its negation $x\not\in \regex$, and $P$ is a Presburger arithmetic formula.
-A word equation \emph{cube} $\bigwedge_{i=1}^n e_i$ is said to be straight-line if it can be rewritten as the form $\bigwedge_{j=1}^m x_j = s_j$ such that:
-\begin{enumerate}
-  \item $x_1, \cdots, x_m$ are different variables,
-  \item $FV(s_j)\cap \{x_1, x_2, \cdots, x_{j-1}\} = \emptyset$ where $FV(\varphi)$ are all free variables of $\varphi$. \label{straigth_line_condition_2}
-\end{enumerate} 
-We call straight-line formula $(\bigwedge_{i=1}^n e_i) \wedge \Re \wedge P$ \emph{normal form}.We use $s_1s_2$ to stand for $\verb|concat|(s_1,s_2)$, $|x|$ to
-stand for $\verb|len|(x)$.
-\begin{table}[H]
-  \centering
-  \begin{tabular}{l}
-    $\regex$ ::= $\epsilon\mid a\mid \regex\cdot\regex\mid \regex+\regex\mid \regex\times \regex\mid \regex^*\mid\regex^C \mid \regex\{m,n\}$ \\
-    $\varphi$ ::= $x\in \regex\mid e\mid\beta\mid \neg\varphi\mid \varphi\vee\varphi$                                                      \\
-    $e$ ::= $s_1=s_2 $                                                                                                                     \\
-    $\beta$ ::= $\alpha_1\odot \alpha_2$                                                                                                   \\
-    $s$ ::= $\emptyset \mid \epsilon \mid a\mid x\mid \verb|concat|(s_1, s_2)$                                                             \\
-    $\alpha$ ::= $0\mid 1\mid i \mid  \verb|len|(s)\mid -\alpha\mid \alpha_1+\alpha_2$ 
-  \end{tabular}
-  \caption{Syntax of ESL}
-  \label{tab:syntax}
-\end{table}
+\section{Automaton Model} \label{sec:overview}
+\subimport{sections/}{automaton_model.tex}
 
-\begin{example}[Straight-line Formula]
-  \begin{equation} \label{eq:1}
-    \varphi_s ::= x =yz \wedge y = z \wedge x\in a\{1,100\} \wedge |x| = 1
-  \end{equation}
-  $\varphi_s$ is straight-line because we can split it to three parts: (i) a straight-line word equation cube $x =yz \wedge y = z$,
-  (ii) a regular membership cube $x\in a\{1,100\}$, and (iii) a Presburger arithmetic formula $|x| = 1$.
-\end{example}
+\section{Solve ESL Formula with Large Repetition Bound} \label{sec:algorithm}
+\subimport{sections/}{algorithms.tex}
 
-\begin{example}[Non Straight-line Formula]
-  \begin{equation} \label{eq:1}
-    \varphi_{ns} ::=  x =yz \wedge y = xz \wedge x\in a\{1,100\} \wedge |x| = 1
-  \end{equation}
-  $\varphi_{ns}$ is not straight-line because the word equation cube\newline
-  $x = yz \wedge y = xz$ does not satisfy condition \ref{straigth_line_condition_2}: $FV(yz) \cap \{y\} \not = \emptyset$ and $FV(xz) \cap \{x\} \not = \emptyset$.
-\end{example}
-
-\subsection{Semantics}
-\highlight{Regular Language} We have introduced basic regular language at
-section \ref{sec:pre}.
-In addition to basic regular operations, we syntactically support intersection, complement and repetition.
-As we all know, basic regular language is closed under intersection and complement.
-Furthermore, the operation \emph{repetition} $\regex\{m,n\}$ means repeating regex $\regex$ at least $m$ times and at most $n$ times.
-It can be syntactically rewritten by concatenation and union:
-$\regex\{m,n\} \equiv \regex^m\mid\cdots\mid\regex^n$ where $\regex^k$ defines concatenate $k$ times($m\leq k\leq n$) to $\regex$.
-So the regular language defined in Table \ref{tab:syntax} is semantically equal to basic regular language.
-However, if we naively rewrite the repetition operation, the automaton size will linear to the repetition times, causing the search space to be exponential.
-To address the issue, we proposed a new automaton model called \emph{Cost-Enriched Finite Automaton (CEFA)}, whose size is not relevant to the repetition times.
-CEFA can not handle nested repetition (e.g., $\regex\{m_1,n_1\} \regex\{m_2,n_2\}$ or $(\regex\{m, n\}) *$) and complementation of repetition (e.g, $(\regex\{m,n\})^C$).
-So we have to rewrite these regexes syntactically (e.g., $a\{1,100\}\{2,2\}$ is rewritten to $a\{1,100\}a\{1,100\}$).\newline
-\highlight{Semantics} We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables.
-$\eta: S\times\Sigma\rightarrow\Sigma^*$ is the interpretation on string where $\eta(c)=c$ for every letter $c\in \Sigma$ and $\eta(s_1s_2)=\eta(s_1)\eta(s_2)$.
-$\theta: I\rightarrow\mathbb{Z}$ is the interpretation of arithmetic that is the same as Presburger arithmetic.
-Then the semantics is given by a satisfaction relation: $\eta, \theta\models \varphi$ defined in Table \ref{tab:semantics}.
-We say a formula $\varphi$ is \emph{satisfiable} if a solution $(\eta, \theta)$ exists such as $\eta, \theta\models \varphi$.
-A formula $\varphi$ is \emph{unsatisfiable} if no solution exists.
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{lcl}
-     $\eta,\theta \models \varphi_1\vee \varphi_2$ & $\mathsf{iff}$ & $\eta,\theta \models \varphi_1 \text{ or } \eta,\theta \models \varphi_2$\\
-     $\eta,\theta \models \neg\varphi $          & $\mathsf{iff}$ & $\eta,\theta \not\models \varphi$\\
-     $\eta, \theta \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan(\regex),\eta,\theta \models x = w$\\
-     $\eta, \theta \models s_1 = s_2$              & $\mathsf{iff}$ & $\eta(s_1) = \eta(s_2)$\\
-     $\eta, \theta \models \alpha_1\odot\alpha_2$  & $\mathsf{iff}$ & $\theta(\alpha_1) \odot \theta(\alpha_2) \text{ where } \odot = \{=, \geq \}$
-  \end{tabular}
-  \caption{Semantics}
-  \label{tab:semantics}
-\end{table}
-\subsection{Problem}
-In this paper, we consider the following problem:
-\begin{table}[H]
-  \centering
-  \begin{tabular}{l l}
-    \hline
-    \textbf{Problem:} & Is an $ESL_s$ formula $\varphi$ satisfiable?                   \\
-    \textbf{Input:}   & A straight-line $ESL_s$ formula $\varphi$ in the normal form. \\
-    \textbf{Output:}  & \emph{sat} or \emph{unsat}.                               \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\section{Cost-Enriched Finite Automaton and Basic Operation} \label{sec:cefa}
-%TODO: The definition of cost-enriched automata
-%      The operation on the cost-enriched automata (union, intersection, complement, concatenate)
-In this section, the cost-enriched finite automaton and operations on it is defined. The operations contains intersection, union, complement, concatenation, and repetition.
-\subsection{Cost-Enriched Finite Automaton}
-\begin{definition}[Cost-Enriched Finite Automaton]
-  A cost-enriched finite automaton $\aut$ is a tuple $(Q, \Sigma, \delta, I, F, R, \theta)$ where
-  \begin{itemize}
-    \item $Q,\Sigma,I,F$ is defined as NFA,
-    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
-    \item $\delta$ is the transitions set whose elements are transition tuple $(q, a, q', \myvec{v})$ where $q, q'$ are states in $Q$, $a$ is a letter in alphabet $\Sigma$ and $\myvec{v}$ is vector of natural number.
-The transition $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
-    \item $\theta$ is the linear integer arithmetic constraint of registers.
-  \end{itemize}
-  A \emph{run} of $\aut$ on string $a_1\cdots a_m$ is a transition sequence $q_0\xrightarrow[\myvec{v_1}]{a_1}q_1\cdots q_{m-1}\xrightarrow[\myvec{v_m}]{a_m}q_m$ such that $q_0\in I$ and $\mathcal{V}(r_i) = \displaystyle\sum_{j=1}^m v_j(i)$ is the \emph{value} of register $r_i$ after the run.
-Note that $\mathcal{V}(r_i)$ is initiated to 0 at state $q_0$.
-The run is \emph{accepting} if $q_m\in F$ and $\theta[r_i/\mathcal{V}(r_i)]$ is satisfiable.
-Note that $\theta[r_i/\mathcal{V}(r_i)]$ means a substitution of all occurrences of $r_i$ in $\theta$ to its current value.
-A string word $w$ is accepted by $\aut$ if there is an accepting run of $\aut$ on $w$.
-The language of $\aut$ is the set of string words accepted by $\aut$, denoted by $\lan(\aut)$.
-\end{definition}
-\begin{example}[The CEFA  $\aut_{(ab)\{1,100\}}$] \label{eg:1}
-   Table \ref{fig:repetition} is the CEFA of the regular expression $(ab)\{1,100\}$.
-The transition set are $\{q_0\xrightarrow[1]{a} q_1, q_1 \xrightarrow[0]{b} q_2, q_2 \xrightarrow[0]{\epsilon} q_0\}$.
-The register is $r_1$.
-And the linear arithmetic is $1\leq r_1\leq 100$.
-Intuitively, each accepted run of $\aut_{(ab)\{1,100\}}$ repeatedly run word $ab$ from one time to 100 times because $1\leq r_1 \leq 100$ restrict the value of $r_1$ to the range $[1,100]$.
-More precisely, the repeat time of the transition $q_0\xrightarrow[1]{a}q_1$ is restricted to $[1,100]$.
-  \begin{figure}[h]
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      every state/.style={draw=blue!50,very thick,fill=blue!20}, initial text=]
-
-      \node[state,initial]            (q_0)                      {$q_0$};
-      \node[state]                    (q_1) [right=of q_0]       {$q_1$};
-      \node[state,accepting]          (q_2) [right=of q_1]       {$q_2$};
-
-      \path[->] (q_0) edge              node      [above]           {a/1} (q_1)
-      (q_1) edge              node      [above]           {b/0} (q_2)
-      (q_2) edge [bend left]  node      [below]           {$\epsilon$/0} (q_0);
-    \end{tikzpicture}
-    \caption{$\aut_{(ab)\{1,100\}}$ with one register $r_1$ and $\theta = 1\leq r_1 \leq 100$}
-    \label{fig:repetition}
-  \end{figure}
-\end{example}
-The example \ref{eg:1} gives a general picture of constructing a CEFA for a regular expression: firstly, we build an NFA from the regex $\regex$
-(e.g, To construct CEFA in example \ref{eg:1}, an NFA is construted with
-transitions \{$q_0\xrightarrow{a} q_1\xrightarrow{b}q_2\xrightarrow{\epsilon}
-  q_0\}$ initial state $q_0$, and accepting state $q_2$). Secondly, we extend NFA to CEFA by adding registers to $R$ and vector to each transition (e.g., the
-register $r_1$ is added to store repetition times and add vector $\myvec{1}$ is set to transition $q_0\xrightarrow{a}q_1$ to update the repetition time). Finally, we set the
-linear arithmetic $\theta$ carefully to restrict the accepted word to be
-included in $\lan(\regex)$ (e.g., $\theta = 1\leq r_1\geq 100$ is set to
-restrict the repetition times to $[1,100]$). Besides the repetition operation, other operations are non-trivial on CEFA. We individually discuss them in the following subsections.
-
-\subsection{Non-nested Repetition}\label{subsec:rep}
-Given a CEFA $\aut = (Q,\Sigma,\delta,I,F,\emptyset,true)$, the repetition operation $\{m,n\}$ on it is defined as a CEFA $\aut_{rep} = (Q, \Sigma, \delta', I, F, r_1, \theta')$ where: 
-\begin{itemize}
-  \item $r_1$ is the new register,
-  \item $\delta'$ is composed by transitions $q\xrightarrow[\myvec{v}\cdot 0]{a} q'$ for all transitions $q\xrightarrow[\myvec{v}]{a} q' \in \delta$, and transitions $q_m\xrightarrow[0_{n}\cdot 1]{\epsilon} q_0$  for all $q_m\in F$ and $q_0\in I$,
-  \item $\theta'$ is the linear arithmetic $m\leq r_1\leq n$ if all initial states are not accepting. Otherwise, $\theta'$ is the linear arithmetic $r_1\leq n$. 
-\end{itemize} 
-In the construction of $\aut_{rep}$, a new register $r_1$ is added to store the repetition times.
-The transition $q_m\xrightarrow[0_{n}\cdot 1]{\epsilon} q_0$ is added to update the repetition times.
-The linear arithmetic $\theta'$ is set to restrict the repetition times to $[m,n]$.
-Because arbitrary repetition times of empty string is still empty string, the value of $r_i$ need not be greater than $m$ when some initial states are accepting.\newline
-Note that the given CEFA $\aut$ does not contain register. So the repetition operation on $\aut$ is non-nested.
-
-\subsection{Concatenation}\label{subsec:con}
-Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2= \emptyset$ and $|R_1|=m,|R_2|=n$, the concatenation is defined as $\aut_{con}=(Q_1\cup Q_2, \Sigma, \delta', I_1, F_2, R_1\cdot R_2, \theta_1\wedge\theta_2)$ where $\delta'$ is composed by
-\begin{itemize}
-  \item $q_1\xrightarrow[\myvec{v_1}\cdot 0_n]{a} q_1'$ for each transition $q_1\xrightarrow[\myvec{v_1}]{a} q_1' \in \delta_1$,
-  \item $q_2\xrightarrow[0_m\cdot\myvec{v_2}]{a} q_2'$ for each transition $q_2\xrightarrow[\myvec{v_2}]{a} q_2' \in \delta_2$,
-  \item and $q_1\xrightarrow[0_{m+n}]{\epsilon} q_2$ for each $q_1\in F_1$ and $q_2 \in I_2$.
-\end{itemize}
-% \begin{figure}[h]
-%   \centering
-%   \begin{subfigure}{0.20\textwidth}
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state, accepting]    (q_1) [right=of q_0] {};
-%       \path[->] (q_0) edge [bend right] node [below] {$a/\myvec{v_1}$} (q_1);
-%       \node [fit=(q_0) (q_1)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The CEFA $\aut_1$}
-%   \end{subfigure}
-%   \begin{subfigure}{0.20\textwidth}
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state, accepting]    (q_1) [right=of q_0] {};
-%       \path[->] (q_0) edge [bend right] node [below] {$a/\myvec{v_2}$} (q_1);
-%       \node [fit=(q_0) (q_1)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The CEFA $\aut_2$}
-%   \end{subfigure}
-%   \begin{subfigure}{0.4\textwidth}
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state]    (q_1) [right=of q_0] {};
-%       \node[state]    (q_2) [right=of q_1] {};
-%       \node[state, accepting]    (q_3) [right=of q_2] {};
-%       \path[->]
-%       (q_0) edge [bend right] node [below] {$a/\myvec{v_1}\cdot \red{0_n}$} (q_1)
-%       (q_1) edge node [below] {$\red{0_{m+n}}$} (q_2)
-%       (q_2) edge [bend right] node [below] {$a/\red{0_m}\cdot \myvec{v_2}$} (q_3);
-%       \node [fit=(q_0) (q_1)] {$\cdots$};
-%       \node [fit=(q_2) (q_3)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The concatenation of $\aut_1$ and $\aut_2$}
-%   \end{subfigure}
-%   \caption{Concatenation}
-%   \label{fig:con}
-% \end{figure}
-The concatenation of two CEFAs is similar to the concatenation of two NFAs, except that the registers and its updates are also concatenated.
-
-% Figure \ref{fig:con} outlines the vector change on transitions when concatenating two CEFA.
-Without losing information, $\aut_{con}$ contains all registers in $\aut_1$ and $\aut_2$.
-Furthermore, $\aut_{con}$ update registers' value of $\aut_1$ and $\aut_2$ separately: $\aut_{con}$ only update registers of $R_1$ on the transitions of $\aut_1$ and update registers of $R_2$ on the transition of $\aut_2$.
-$\theta'$ is the conjunction of $\theta_1$ and $\theta_2$ to make sure all linear constraints in $\aut_1$ and $\aut_2$ are satisfiable.
-\subsection{Intersection}\label{subsec:inter}
-Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the intersection is defined as $\aut_{inter} = (Q_1\times Q_2, \Sigma, \delta', I_1\times I_2, F_1\times F_2, R_1\cdot R_2, \theta_1\wedge \theta_2)$ where $\delta'$ is composed by
-\begin{itemize}
-  \item transitions $(q_1,q_2)\xrightarrow[\myvec{v_1}\cdot\myvec{v_2}]{a} (q_1',q_2')$ for  transition $q_1\xrightarrow[\myvec{v_1}]{a}q_1'$ and transition $q_2\xrightarrow[\myvec{v_2}]{a}q_2'$ exist individually in  $\delta_1$ and $\delta_2$.
-\end{itemize}
-% \begin{figure}[h]
-%   \centering
-%   \begin{subfigure}{0.20\textwidth}
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state, accepting]    (q_1) [right=of q_0] {};
-%       \path[->]
-%       (q_0) edge [bend right] node [below] {$a$/$\myvec{v_1}$} (q_1)
-%       (q_0) edge [bend left] node [above] {$b$/$\myvec{v_1}$} (q_1);
-%       \node [fit=(q_0) (q_1)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The CEFA $\aut_1$}
-%   \end{subfigure}
-%   \begin{subfigure}{0.20\textwidth}
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state, accepting]    (q_1) [right=of q_0] {};
-%       \path[->]
-%       (q_0) edge [bend right] node [below] {$a$/$\myvec{v_2}$} (q_1)
-%       (q_0) edge [bend left] node [above] {$c$/$\myvec{v_2}$} (q_1);
-%       \node [fit=(q_0) (q_1)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The CEFA $\aut_2$}
-%   \end{subfigure}
-%   \begin{subfigure}{0.4\textwidth}
-%     \centering
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state, accepting]    (q_3) [right=of q_0] {};
-%       \path[->]
-%       (q_0) edge [bend right] node [below] {$a$/\red{$\myvec{v_1}\cdot \myvec{v_2}$}} (q_3);
-%       \node [fit=(q_0) (q_3)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The intersection of $\aut_1$ and $\aut_2$}
-%   \end{subfigure}
-%   \caption{Intersection}
-%   \label{fig:inter}
-% \end{figure}
-The intersection of two CEFAs is similar to the intersection of NFA, except that the registers updates and linear arithmetic are also intersected.
-
-\subsection{Union}\label{subsec:union}
-Given two CEFA $\aut_1 = (Q_1, \Sigma, \delta_1, I_1, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2,$ $I_2, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$ and $|R_1|=m,|R_2|=n$, the union is defined as $\aut_{union} = (Q_1\cup Q_2\cup\{q_0\}, \Sigma, \delta', \{q_0\}, F_1\cup F_2, R_1\cdot R_2\cdot (r_1, r_2), \theta')$ where $\delta'$ is composed by
-\begin{itemize}
-  \item transitions $q_0\xrightarrow[0_{m+n}\cdot(1,0)]{\epsilon}q_1$ for all $q_1\in I_1$,
-  \item transitions $q_0\xrightarrow[0_{m+n}\cdot(0,1)]{\epsilon}q_2$ for all $q_2\in I_2$,
-  \item transitions $q_1\xrightarrow[\myvec{v_1}0_{n+2}]{a} q_1'$ for all $q_1\xrightarrow[\myvec{v_1}]{a} q_1'\in \delta_1$,
-  \item transitions $q_2\xrightarrow[0_m\myvec{v_2}0_2]{a} q_2'$ for all $q_2\xrightarrow[\myvec{v_2}]{a} q_2'\in \delta_2$.
-\end{itemize}
-$r_1$ and $r_2$ are new registers.
-$q_0$ is a new state where $q_0\not\in Q_1$ and $q_0\not\in Q_2$.
-Assume that $\theta  = (r_1>0\wedge\theta_1)\vee(r_2>0\wedge\theta_2)$, $\theta'$ is constructed differently in four cases:
-\begin{itemize}
-  \item both $I_1$ and $I_2$ do not contain accepting states: $\theta'$ = $\theta $;
-  \item $I_1$ contains accepting states while $I_2$ does not: $\theta'$ = $\theta \vee (r_1==0\wedge r_2==0\wedge\theta_1)$;
-  \item $I_2$ contains accepting states while $I_1$ does not: $\theta'$ = $\theta \vee (r_1==0\wedge r_2==0\wedge\theta_2)$;
-  \item both $I_1$ and $I_2$ contain accepting states: $\theta'$ = $\theta \vee (r_1==0\wedge r_2==0\wedge(\theta_1\vee\theta_2))$;
-\end{itemize}
-
-% \begin{figure}[h]
-%   \centering
-%   \begin{subfigure}{0.20\textwidth}
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state, accepting]    (q_1) [right=of q_0] {};
-%       \path[->]
-%       (q_0) edge [bend left] node [above] {$a$/$\myvec{v_1}$} (q_1);
-%       \node [fit=(q_0) (q_1)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The CEFA $\aut_1$}
-%   \end{subfigure}
-%   \begin{subfigure}{0.20\textwidth}
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state, accepting]    (q_1) [right=of q_0] {};
-%       \path[->]
-%       (q_0) edge [bend right] node [below] {$a$/$\myvec{v_2}$} (q_1);
-%       \node [fit=(q_0) (q_1)] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The CEFA $\aut_2$}
-%   \end{subfigure}
-%   \begin{subfigure}{0.4\textwidth}
-%     \centering
-%     \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-%       every fit/.style={draw,minimum height=2cm,minimum width=3.5cm,dashed},
-%       every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-%       \node[state, initial]   (q_0) {};
-%       \node[state]   (q_1) [above right=of q_0] {};
-%       \node[state, accepting]   (q_1') [right=of q_1] {};
-%       \node[state]   (q_2) [below right=of q_0] {};
-%       \node[state, accepting]   (q_2') [right=of q_2] {};
-%       \path[->]
-%       (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(1,0)}$} (q_1)
-%       (q_0) edge node [left] {$\epsilon/\red{0_{m+n}\cdot(0,1)}$} (q_2)
-%       (q_1) edge [bend left] node [above] {$a$/\red{$\myvec{v_1}\cdot 0_{n+2}$}} (q_1')
-%       (q_2) edge [bend right] node [below] {$a$/\red{$0_m\cdot \myvec{v_2}\cdot 0_2$}} (q_2');
-%       \node [fit=(q_1) (q_1')] {$\cdots$};
-%       \node [fit=(q_2) (q_2')] {$\cdots$};
-%     \end{tikzpicture}
-%     \caption{The union of $\aut_1$ and $\aut_2$}
-%   \end{subfigure}
-%   \caption{Union}
-%   \label{fig:union}
-
-% \end{figure}
-To simulate the semantics of the union, we add transitions from $q_0$ to initial states of $\aut_1$ and $\aut_2$ to randomly choose one automaton.
-$r_1 > 0$ indicates we choose $\aut_1$ to run while $r_2 > 0$ indicates we choose $\aut_2$ to run.
-We should make sure the accepting condition is consistent.
-Therefore, the accepting condition $(r_1>0\wedge\theta_1)\vee(r_2>0\wedge\theta_2)$ is generated.
-Furthermore, the accepting run may stop at the new initial state $q_0$ with $\mathcal{V}(r_1) = 0, \mathcal{V}(r_2)=0$.
-It can only happen when some initial states of two given CEFAs are accepting.
-If some initial states of $\aut_1$ are accepting, the accepting condition $r_1=0\wedge r_2=0\wedge \theta_1$ is generated.
-Similarly, if some initial states of $\aut_2$ are accepting, the accepting condition $r_1=0\wedge r_2=0\wedge \theta_2$ is generated.
-Finally, the disjunction of all generated accepting conditions $\theta'$ is obtained to express the non-nondeterministic.
-\subsection{Complement}
-Given a CEFA $\aut = (Q, \Sigma, I, F, \delta, \emptyset, true)$, the complement $\aut^c$ is defined as the CEFA $\aut^c = (Q, \Sigma, I, F^c, \delta, R, \theta^c)$ where $F^c = Q\setminus F$ and $\theta^c = \neg \theta$.
-\subsection{Closure}
-\subsection{Complement of Repetition and Nested Repetition}\label{subsec:comp}
-As we mentioned,  CEFA
-
-\subsection{From Regex to CEFA} \label{subsec:regex2cefa}
-\highlight{Basis}: The basis has three parts with empty registers and valid linear arithmetic, shown in Fig.
-\ref{fig:basis}.
-In part \ref{fig:basis:a}, we see how to handle the expression $\epsilon$.
-The language of the automaton is easily seen to be $\{\epsilon\}$ since the only path from the start state to an accepting state
-is labeled $\epsilon$.
-Part \ref{fig:basis:b} gives the CEFA for a regular expression $\mathbf{a}$.
-The language of this CEFA consists of the single string $a$, which is also $\lan(\mathbf{a})$.
-Finally, part \ref{fig:basis:c} shows the construction for $\emptyset$.
-There are no paths from the initial state to the accepting state.
-\begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.3\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=1.2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=1.0cm,minimum width=2.2cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->] (q_0) edge node [below] {$\epsilon/\emptyset$} (q_1);
-      \node [fit=(q_0) (q_1)] {};
-    \end{tikzpicture}
-    \caption{}
-    \label{fig:basis:a}
-  \end{subfigure}
-  \begin{subfigure}{0.3\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=1.2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=1.0cm,minimum width=2.2cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \path[->] (q_0) edge node [below] {$a/\emptyset$} (q_1);
-      \node [fit=(q_0) (q_1)] {};
-    \end{tikzpicture}
-    \caption{}
-    \label{fig:basis:b}
-  \end{subfigure}
-  \begin{subfigure}{0.3\textwidth}
-    \centering
-    \begin{tikzpicture}[shorten >=1pt,node distance=1.2cm,on grid,>={Stealth[round]},
-      every fit/.style={draw,minimum height=1.0cm,minimum width=2.2cm,dashed},
-      every state/.style={draw=blue!50,minimum size = 0.1cm}, initial text=]
-      \node[state, initial]   (q_0) {};
-      \node[state, accepting]    (q_1) [right=of q_0] {};
-      \node [fit=(q_0) (q_1)] {};
-    \end{tikzpicture}
-    \caption{}
-    \label{fig:basis:c}
-  \end{subfigure}
-  \caption{The basis of the construction of a CEFA from extended regex}
-  \label{fig:basis}
-\end{figure}\\
-\highlight{Induction}: Given the CEFA of the subexpression, we construct the CEFA in five cases:
-\begin{enumerate}
-  \item The expression is $\regex\{m,n\}$ for some smaller expression $\regex$. We can repeat the CEFA of $\regex$ with lower bound $m$ and upper bound $n$ as shown in section \ref{subsec:rep}.
-  \item The expression is $\regex_1\cdot\regex_2$ for some smaller expression $\regex_1$ and $\regex_2$.
-We can concatenate the CEFA of $\regex_1$ and the CEFA of $\regex_2$ as shown in section \ref{subsec:con}.
-  \item The expression is $\regex_1\times \regex_2$ for some smaller expression $\regex_1$ and $\regex_2$.
-We can intersect the CEFA of $\regex_1$ and the CEFA of $\regex_2$ as shown in section \ref{subsec:inter}.
-  \item The expression is $\regex_1 + \regex_2$ for some smaller expression $\regex_1$ and $\regex_2$.
-We can union the CEFA of $\regex_1$ and the CEFA of $\regex_2$ as shown in section \ref{subsec:union}.
-  \item The expression is $\regex*$ for some smaller expression $\regex$. We can construct the closure Star of the CEFA of $\regex$  as shown in section \ref{subsec:klee}.
-  \item The expression is $\regex^C$ for some smaller expression $\regex$. We can construct the complement of the CEFA of $\regex$  as shown in section \ref{subsec:comp}
-\end{enumerate}
-\highlight{Special Case}: When the expression $\regex$ contains nested repetition, we firstly write $\regex$ to a new regex $\regex'$ without nested repetition.
-Then we build the CEFA of the new expression $\regex'$ by basis and induction steps.
-
-\section{Solve String Constraints with Large Repetition Bound} \label{sec:solve}
-Following the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve string constraints with help of CEFA.
-Firstly, we replace all length operations $i=\strlen{x}$ to pre-images which are represented by CEFAs, and intersect these CEFAs to $lenAut_x$.
-Then for each term $x$, we generate CEFAs of all regular expressions $\regex$ in all terms $x\in \regex$, and intersect these CEFAs with $lenAut_x$ to get the final CEFA.
-Finally, we check whether each final CEFA is empty under the linear integer arithmetic $P$.
-If one of the final CEFAs is empty, the string constraints are unsatisfiable.
-Otherwise, the string constraints are satisfiable.
-The high-level algorithm is shown in the Algorithm \ref{alg:high}.\newline
-The emptiness checking problem of CEFAs under linear integer arithmetic $P$ is theoretically pspace-complete\cite{atva2020}.
-To solve it efficiently for practical example, we add some heuristics.
-The details of the heuristics are shown in Algorithm \ref{alg:emptiness}.
-% \pagebreak
-\subsection{High-level algorithm}
-\begin{algorithm}
-  \caption{High-level algorithm}
-  \label{alg:high}
-  \begin{algorithmic}[1]
-    \Require  Conjunction $\varphi$ of the form $x\in \regex$, and conjunction of linear integer arithmetic $P$ over string lengths
-    \Ensure \emph{sat} or \emph{unsat}
-    \Statex
-    \ForAll{length operation $i = \strlen{x}$} \label{alg:high:line1}
-      \State $lenAut_{x} \leftarrow \aut_{allstring}$ \label{alg:high:line2}
-      \State Let $\aut_{i}$ be the pre-image of length operation with length $i$ \label{alg:high:line3}
-      \State $lenAut_{x} \leftarrow lenAut_{x} \times \aut_{i}$ \label{alg:high:line4}
-    \EndFor \label{alg:high:line5}
-    \State $atomAuts \leftarrow \emptyset$ \label{alg:high:line6}
-    \ForAll{string variables $x$ occurring in $\varphi$} 
-    \State Let $S$ be the set of all regexes $\regex$ in all terms $x \in \regex$ 
-    \State CEFA $\aut_x \leftarrow$ intersection of $lenAut_x$ and all CEFAs corresponding to regexes in $S$
-    \If{$nfa(\aut_x)$ is empty} \label{alg:high:line5}
-      \State \textbf{return} \emph{unsat}
-    \EndIf
-    \State $atomAuts \leftarrow atomAuts \cup \{\aut_x\}$ 
-    \EndFor
-    \If{$\algfun{isEmpty}(atomAuts, P)$ }
-      \State \textbf{return} \emph{unsat}
-    \Else 
-      \State \textbf{return} \emph{sat}
-    \EndIf
-  \end{algorithmic}
-\end{algorithm}
-The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process.
-The implemented details are eliminated for clarity.
-From line \ref{alg:high:line1} to line \ref{alg:high:line5}, we construct the CEFAs of all length operations occurring in the string constraints.
-The CEFA $lenAut_x$ is the automaton used to store length information on $x$.
-$lenAut_x$ is initiated to accept all strings at line \ref{alg:high:line2}.
-For each length operation $i = \strlen{x}$, we construct the pre-image of it at line \ref{alg:high:line3}, and intersect the pre-image to $lenAut_x$ at line \ref{alg:high:line4} to store length information.
-Note that the final $lenAut_x$ is the intersection of all pre-images so that it can store all length information on $x$.\newline
-In the following steps, we call a CEFA to be \emph{atomic} if we will not operate it anymore.
-The set $atomAuts$ is the set of all atomic CEFAs for all terms $x$ occurring in the string constraints, and is initially empty at line \ref{alg:high:line6}.
-From line 7 to line 14, each atomic automaton in the set is constructed by intersecting the length automaton $lenAut_x$ to all CEFAs corresponding to the regex expressions with regard to string term $x$.
-If the NFA form of the atomic automaton is empty (i.e., the NFA accepts no word), we return $unsat$ directly because the NFA form is an over-approximation of CEFA.
-\newline
-After obtaining the atomic CEFAs of all string terms, we check whether the atomic CEFAs are empty under the linear integer arithmetic $P$ at line 15.
-If the atomic CEFAs are empty under $P$, we return $unsat$.
-Otherwise, we return $sat$.
-The emptiness checking at line 15 is complex, and we discuss it detailly in the following subsection.\newline
-
-\subsection{Emptyness Checking}
-As mentioned, the emptiness checking problem of CEFA under linear integer arithmetic $P$ is theoretically pspace-complete \cite{atva2020}.
-In our previous research, we rewrote CEFA to an infinite system and used a model-checking tool \emph{NuSMV} to solve it.
-However, the previous method was not effictive enough.
-So we put forward a new method to solve it.\newline
-As shown in Algorithm \ref{alg:emptiness}, We simplify the CEFAs at line 1 because the input CEFAs may have many transitions and registers.
-The purpose of the simplification is removing duplicated transitions and registers in the CEFA.
-After simplifying the input CEFAs, we try to find a solution by under-approximation at line 3.
-If we find a solution, we return $false$ at line 5 because the CEFAs under linear integer arithmetic $P$ are not empty.
-Otherwise, we try to find an unsat core by over-approximation at line 8.
-If we discover an unsat core,
-we return $true$ at line 10 because we know that the CEFAs under $P$ are empty.
-Suppose that both under- and over-approximation do not make sense, we compute the Parikh images of the simplified CEFAs by algorithm in the paper \cite{parikh_2005}, and check if the Parikh images are satisfiable in conjunction with $P$ at line 12.
-The satisfiability implies non-emptiness directly.
-\newline
-Note that the under-approximation program is executed many times until $MaxBound$ is reached.
-The details of simplification is shown in Algorithm \ref{alg:simplify}.
-The details of under- and over-approximation are shown in Algorithm \ref{alg:underApprox} and Algorithm \ref{alg:overApprox} respectively.
-The details of Parikh image computation are omitted for clarity.\newline
-\begin{algorithm}
-  \caption{ $\algfun{isEmpty}(auts, P)$}
-  \label{alg:emptiness}
-  \begin{algorithmic}[1]
-    \Require CEFAs $auts$ and linear integer arithmetic $P$
-    \Ensure $true$ or $false$
-    \Statex
-    \State $simpliAuts \leftarrow \algfun{simplify}(auts)$
-    \For{$bound \gets 1, MaxBound$ }
-      \State $\varphi_{under}\gets \algfun{underApprox}(simpliAuts, bound)$
-      \If{$\varphi_{under}\wedge P$ is sat}
-        \State \textbf{return} $false$
-      \EndIf
-    \EndFor
-    \State $\varphi_{over}\gets \algfun{overApprox}(simpliAuts)$
-    \If{$\varphi_{over}\wedge P$ is unsat}
-      \State \textbf{return} $true$
-    \EndIf
-    \State $\varphi \gets \algfun{parikhImage}(simpliAuts)$
-    \If{$\varphi\wedge P$ is unsat}
-      \State \textbf{return} $true$
-    \Else
-      \State \textbf{return} $false$
-    \EndIf
-  \end{algorithmic}
-\end{algorithm}
-
-\subsection{Under-Approximation}
-To solve the satisfiable instances of the emptiness checking problem, under-approximation procedure is come up.
-The main idea is exploring the CEFA deep-firstly.
-The string length bound the deep, and linear integer arithmetic is generated from low to high string length.
-This section only discusses the situation in where the string length bound is fixed.
-The details are shown in the Algorithm \ref{alg:underApprox}.
-Firstly, the linear integer arithmetic $\varphi_{under}$ is assigned to be false at line 1.
-Then for each CEFA, we enumerate all the accepted paths with lengths less than the bound and translate the paths to linear integer arithmetic.
-The linear integer arithmetic is in conjunction with $\varphi_{under}$ at line 4.
-\begin{algorithm}
-  \caption{$\algfun{underApprox}(auts, bound)$}
-  \label{alg:underApprox}
-  \begin{algorithmic}[1]
-    \Require The CEFAs $auts$ and string length $bound$
-    \Ensure The linear integer arithmetic $\varphi_{under}$ representing under-approximation of the register values of $auts$
-    \Statex
-    \State $\varphi_{under} \gets false$
-    \For{$aut \in auts$}
-      \State Suppose $aut = (Q, \Sigma, \delta, q_0, F, (r_1, \cdots, r_m), \theta)$
-      \State $S_0 \gets \{(q_0, \myvec{0}_m)\}$
-      \ForAll{path $q_0q_1\cdots q_{n}$ whose length is $bound$ and $\myvec{R}$ is the sum of the vectors on the path}
-        \If{$q_{n}\in F$}
-          \State $\varphi_{under} \gets \varphi_{under} \bigwedge_{i\in[1,m]} r_i = \myvec{R}(i)$
-        \EndIf
-      \EndFor
-    \EndFor
-    \State \textbf{return} $\varphi_{under}$
-  \end{algorithmic}
-\end{algorithm}
-\subsection{Over-Approximation}
-Sometimes when the bound reaches the maximum, the linear integer arithmetic $\varphi_{under}$ is still unsatisfiable.
-We must use over-approximation to solve the emptiness checking problem in this case.
-The main idea of over-approximation is to split each CEFA into sub-CEFAs, translate each sub-CEFA respectively, and finally in conjunction with the LIA of all sub-CEFAs.
-The details are shown in the Algorithm \ref{alg:overApprox}.
-Firstly, each CEFA is split into $n$ sub-CEFAs, where $n$ is the number of registers in the CEFA.
-The sub-CEFA has only one register.
-After simplifying each sub-CEFA by Algorithm \ref{alg:simplify}, the vector of each transition must be $\myvec{1}$.
-So the register value of each sub-CEFA equals the length of the accepted path.
-We apply the efficient construction of semilinear representations\cite{unary_nfa_2010} to get the linear integer arithmetic $\varphi_{over}$.
-\begin{algorithm}
-  \caption{$\algfun{overApprox}(auts)$}
-  \label{alg:overApprox}
-  \begin{algorithmic}[1]
-    \Require CEFAs $auts$
-    \Ensure Linear integer arithmetic $\varphi_{over}$
-    \Statex
-    \State $\varphi_{over} \gets true$
-    \For{$aut \in auts$}
-      \State Let $subAut$ be the sub-CEFA of $aut$ with only one register
-      \State Let $subAut \gets \algfun{simplify}(subAut)$
-      \State Let $\varphi_{subAut}$ be the linear integer arithmetic generated by efficient construction of semilinear representations
-      \State $\varphi_{over} \gets \varphi_{over} \wedge \varphi_{subAut}$
-    \EndFor
-    \State \textbf{return} $\varphi_{over}$
-  \end{algorithmic}
-\end{algorithm}
-
-\subsection{Simplification of CEFA}
-The main purpose of simplification is to remove duplicated transitions and registers.
-In the emptiness checking Algorithm \ref{alg:emptiness}, the vectors on the transitions are meaningful while the letters on the transitions are not.
-So we see the alphabet of the CEFA as unary (i.e., the alphabet is $\{a\}$).
-Then the vector in the CEFA is seen as the letter in the NFA, and the vector $\myvec{0}_n$ is seen as $\epsilon$.
-Based on the homomorphism between NFA and CEFA, we determinate and minimize \cite{aut_hopcraft} the CEFA by vector firstly.
-Then we merge the registers having the same updating at all transitions.
-The main simplification framework is shown in Algorithm \ref{alg:simplify}.
-\begin{algorithm}
-  \caption{$\algfun{simplify}(auts)$}
-  \label{alg:simplify}
-  \begin{algorithmic}[1]
-    \Require CEFAs $auts$
-    \Ensure Simplified CEFAs $simpliAuts$
-    \Statex
-    \State $simpliAuts \gets \emptyset$
-    \For{$aut \in auts$}
-      \State $aut \gets \algfun{determinizeByVec}(aut)$
-      \State $aut \gets \algfun{minimizeByVec}(aut)$
-      \State $aut \gets \algfun{mergeRegisters}(aut)$
-      \State $simpliAuts \gets simpliAuts \cup \{aut\}$
-    \EndFor
-    \State \textbf{return} $simpliAuts$
-  \end{algorithmic}
-\end{algorithm}
-
-\section{Implementation and Experiment} \label{sec:imp}
-% % TODO: Implementation and experiment result
-TODO
-\subsection{Overall Evaluation of Experiment}
-tools: cvc5, z3str3, z3str3re, z3-trau, ostrich
-benchmark: total benchmark
-
-\subsection{Experimental Details}
-tools: cvc5, z3str3, z3str3re, z3-trau, ostrich
-benchmmark:
-\begin{itemize}
-  \item Small Count: the sum of upper bounds on the repetition operator is less than 50
-  \begin{itemize}
-    \item z3str3re-bench
-    \item regexlib
-    \item stackoverflow
-    \item ReDos-bench
-  \end{itemize}
-  \item Large Count: the sum of upper bounds on the repetition operator is greater than 50
-  \begin{itemize}
-    \item z3str3re-bench
-    \item regexlib
-    \item stackoverflow
-    \item ReDos-bench
-  \end{itemize}
-\end{itemize}
-
-\subsection{Analysis of All Algorithms}
-tools:
-\begin{itemize}
-  \item ostrich-baseline: the origin ostrich syntactically unwind all repetition operators.
-  \item ostrich-new: the most efficient ostrich which using CEFA and all heuristics
-  \item ostrich-without-under: without under-approxiamtion
-  \item ostrich-without-over: without over-approximation
-  \item ostrich-without-simplification: without simplification of CEFA
-  \item ostrich-without-rapidly-finding-string: without context-aware finding string
-\end{itemize}
+\section{Implementation and Experimental Results} \label{sec:implementation}
+\subimport{sections/}{implementation.tex}
 
 \section{Conclusion and Future Work} \label{sec:conclu}
-In this paper, we aim to solve the string constraints with large repetition time efficiently.
-A new automaton model CEFA is proposed to reduce the search space.
-Many basic operations on CEFA are non-trivial and we should formal them carefully.
-Moreover, we extend the algorithm in the paper \cite{atva2020} with heuristics such as under- and over-approximation.
-The implementation of the algorithm is done on string solver ostrich.
-The extensive empirical comparison against z3 over a large and diverse benchmark shows the power of our model and algorithm.
-In the future, we plan to explore the way to solve nested repetition and use CEFA to solve more string operations.
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{ref}
+\subimport{sections/}{conclusion.tex}
 

### 2023-04-11 2023-1-19/figures/cactus_plot_all.tex
atva2023 first version

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=Total,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(225,0.9749977728285077)(674,3.1805545657015593)(1123,5.703)(1572,8.438265033407571)(2021,11.531574610244988)(2470,15.075634743875279)(2919,19.097318485523385)(3368,23.513942093541203)(3817,28.284)(4266,33.33244543429844)(4715,38.708721603563475)(5164,44.401)(5613,50.33589755011136)(6062,56.600924276169266)(6511,63.173)(6960,69.98948106904231)(7409,77.14595100222718)(7858,84.631)(8307,92.40952561247217)(8756,100.53519599109131)(9205,109.03022717149221)(9654,117.91206904231626)(10103,127.1663407572383)(10552,136.837)(11001,146.92912249443208)(11450,157.46868596881959)(11899,168.51312026726058)(12348,180.07232962138085)(12797,192.1541959910913)(13246,204.78042093541202)(13695,218.04313363028953)(14144,232.00983073496658)(14593,246.74662138084634)(15042,262.27243207126946)(15491,278.68448552338526)(15940,296.06152338530063)(16389,314.4960133630289)(16838,333.9485055679287)(17287,354.4259688195991)(17736,375.96304899777283)(18185,398.6540556792873)(18634,422.5968173719376)(19083,447.8012538975501)(19532,474.371004454343)(19981,502.39159242761696)(20430,531.845280623608)(20879,562.9128819599109)(21328,595.7690712694878)(21777,630.5182316258351)(22226,667.4171893095769)(22675,706.6891113585746)(23124,748.524723830735)(23573,792.9852828507795)(24022,840.2546636971047)(24471,890.3767973273942)(24920,943.5922204899778)(25369,1000.1014365256125)(25818,1060.165797327394)(26267,1123.928570155902)(26716,1191.6269866369712)(27165,1263.5346726057908)(27614,1339.8836258351894)(28063,1421.4921870824055)(28512,1509.265877505568)(28961,1603.7898262806236)(29410,1705.7232071269486)(29859,1815.975158129176)(30308,1935.8308218262805)(30757,2066.3378129175944)(31206,2207.6831870824053)(31655,2360.5879977728287)(32104,2524.3051202672605)(32553,2699.568131403118)(33002,2887.1032249443206)(33451,3087.4128195991093)(33900,3301.4712672605788)(34349,3529.438995545657)(34798,3772.0046904231626)(35247,4029.107385300668)(35696,4301.784002227171)(36145,4592.399788418708)(36594,4903.131832962137)(37043,5237.107131403119)(37492,5598.406133630289)(37941,5992.969233853007)(38390,6426.496371937639)(38839,6909.088826280624)(39288,7452.511380846326)(39737,8072.1869844098)(40186,8790.347349665924)(40635,9647.260521158129)(41084,10728.830126948777)(41533,12233.169844097996)(41982,14371.070224944322)(42431,17689.691844097993)(42880,23713.308975501113)(43329,34464.926198218265)(43776.5,51319.2588161435)(44001,62564.102)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.001)(251,297.57713173652695)(752,919.7552734530939)(1253,1557.5426886227544)(1754,2204.4396926147706)(2255,2859.376377245509)(2756,3521.8273872255486)(3257,4190.722225548902)(3758,4865.928748502994)(4259,5547.6787385229545)(4760,6236.603149700599)(5261,6933.963383233533)(5762,7640.762471057885)(6263,8358.542546906187)(6764,9088.009331337325)(7265,9829.516295409183)(7766,10584.155027944113)(8267,11351.854083832335)(8768,12132.038473053894)(9269,12922.84225748503)(9770,13722.257604790419)(10271,14529.294508982037)(10772,15342.857842315369)(11273,16162.547750499003)(11774,16987.797055888226)(12275,17818.525373253495)(12776,18654.640872255488)(13277,19495.92945708583)(13778,20342.265848303392)(14279,21193.5768003992)(14780,22049.840229540918)(15281,22911.280876247507)(15782,23777.89823752495)(16283,24649.420652694607)(16784,25525.914844311377)(17285,26407.47073253493)(17786,27293.949608782437)(18287,28185.26401996008)(18788,29081.597538922157)(19289,29982.794083832334)(19790,30888.764532934132)(20291,31799.552532934133)(20792,32714.965686626747)(21293,33634.779389221556)(21794,34558.914994011975)(22295,35487.432938123755)(22796,36420.41224550898)(23297,37357.921341317364)(23798,38300.12236526946)(24299,39247.05026946108)(24800,40198.6993253493)(25301,41155.420005988024)(25802,42117.09206986028)(26303,43083.934487025945)(26804,44055.638161676645)(27305,45032.20359081836)(27806,46014.43762275449)(28307,47002.47610978044)(28808,47996.60786626746)(29309,48996.72237325349)(29810,50002.71481636727)(30311,51014.77076447106)(30812,52033.40894211577)(31313,53058.83036726547)(31814,54091.27846506986)(32315,55130.93350698603)(32816,56178.196696606785)(33317,57233.01951297405)(33818,58295.94183832336)(34319,59367.47835329341)(34820,60448.25150898203)(35321,61539.139007984035)(35822,62640.02783033932)(36323,63751.15949301397)(36824,64873.163516966066)(37325,66006.96277045908)(37826,67153.20774251496)(38327,68312.41110578843)(38828,69485.79568263472)(39329,70674.74570259481)(39830,71879.40951097805)(40331,73099.98904191617)(40832,74339.00549301397)(41333,75598.06305988024)(41834,76879.22272055889)(42335,78185.40860279441)(42836,79517.57918962077)(43337,80881.22110778444)(43838,82281.94577045909)(44339,83721.56675449101)(44840,85208.95984231538)(45341,86753.0387285429)(45842,88367.2720998004)(46343,90074.41964870259)(46844,91896.8463233533)(47345,93861.7311497006)(47846,96027.48211576846)(48347,98576.50299800398)(48848,102635.06975449102)(49112,108033.23818518518)(49127,108809.673)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.966)(242,253.6938115942029)(725,797.780635610766)(1208,1375.6963540372672)(1691,1971.2173726708074)(2174,2579.9891242236026)(2657,3200.1552774327124)(3140,3831.5469544513458)(3623,4473.097327122153)(4106,5124.210623188406)(4589,5784.478358178054)(5072,6452.883861283644)(5555,7128.7226770186335)(6038,7811.80366252588)(6521,8501.433523809525)(7004,9197.051412008283)(7487,9898.351950310558)(7970,10605.06412215321)(8453,11317.27030020704)(8936,12035.019962732918)(9419,12758.173621118012)(9902,13486.76760041408)(10385,14220.709316770186)(10868,14959.795536231884)(11351,15703.822519668738)(11834,16453.023033126294)(12317,17207.60976190476)(12800,17967.250432712215)(13283,18732.071757763973)(13766,19501.90405383023)(14249,20276.887979296065)(14732,21056.855813664595)(15215,21842.13654037267)(15698,22632.851068322983)(16181,23429.176252587993)(16664,24230.890689440996)(17147,25038.21724637681)(17630,25851.334213250517)(18113,26669.63826293996)(18596,27493.383886128366)(19079,28323.0271242236)(19562,29158.7289689441)(20045,30000.663378881985)(20528,30848.824979296067)(21011,31703.274051759836)(21494,32564.10966252588)(21977,33431.79361697723)(22460,34306.333964803314)(22943,35188.23764182194)(23426,36077.66052587992)(23909,36975.0900331263)(24392,37880.26252380952)(24875,38793.40235403727)(25358,39715.36438095238)(25841,40646.487689441)(26324,41586.495204968945)(26807,42535.87147412008)(27290,43494.791265010346)(27773,44463.5207184265)(28256,45442.81579710145)(28739,46433.07173706004)(29222,47434.819573498964)(29705,48449.619180124224)(30188,49478.66922360248)(30671,50522.00113043478)(31154,51581.44218426501)(31637,52657.74352795031)(32120,53751.45314699793)(32603,54863.35853830228)(33086,55994.589289855074)(33569,57145.683132505175)(34052,58318.82643478261)(34535,59515.03370600414)(35018,60737.58520703933)(35501,61988.47214492754)(35984,63269.9586563147)(36467,64585.57833333334)(36950,65939.52480745342)(37433,67336.00833747412)(37916,68780.93298964803)(38399,70278.50410351966)(38882,71836.31644513458)(39365,73463.24823602484)(39848,75170.24680331264)(40331,76972.25751759835)(40814,78886.19549068323)(41297,80940.91662111801)(41780,83159.28797722567)(42263,85568.35025051759)(42746,88213.17140786748)(43229,91128.96203933746)(43712,94354.33373498965)(44195,97990.84464389233)(44678,102163.55392546584)(45161,107056.2527805383)(45644,112920.6944989648)(46127,120179.79210559007)(46610,129819.74801035198)(47093,144581.69753830228)(47351.5,156224.77838235296)(47370,157248.051)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.011)(186,2.2441590296495955)(557,6.933)(928,11.756)(1299,16.579323450134773)(1670,21.640361185983828)(2041,27.149)(2412,32.7522641509434)(2783,38.633)(3154,44.569)(3525,50.505)(3896,56.501285714285714)(4267,62.774)(4638,69.081)(5009,75.52557412398923)(5380,82.2)(5751,88.973)(6122,96.007)(6493,103.1635552560647)(6864,110.573)(7235,117.993)(7606,125.53147978436657)(7977,133.315)(8348,141.106)(8719,148.99271698113208)(9090,157.14)(9461,165.30301886792452)(9832,173.677)(10203,182.21)(10574,190.76738005390837)(10945,199.596)(11316,208.5)(11687,217.41128032345014)(12058,226.567)(12429,235.842)(12800,245.117)(13171,254.577)(13542,264.223)(13913,273.8815498652291)(14284,283.797)(14655,293.8208894878706)(15026,304.088)(15397,314.48077088948787)(15768,325.109)(16139,335.8730970350404)(16510,346.874)(16881,358.04226415094337)(17252,369.488)(17623,381.06956603773585)(17994,392.92)(18365,404.96041239892185)(18736,417.2412641509434)(19107,429.8)(19478,442.5950269541779)(19849,455.633102425876)(20220,468.952436657682)(20591,482.541)(20962,496.35875471698114)(21333,510.47258760107815)(21704,524.8864797843665)(22075,539.608)(22446,554.6164123989217)(22817,569.9552641509433)(23188,585.6441725067385)(23559,601.7121401617251)(23930,618.1685202156334)(24301,635.0817951482479)(24672,652.4683611859839)(25043,670.3729433962263)(25414,688.8481024258759)(25785,707.9234986522912)(26156,727.6508382749325)(26527,748.0661428571428)(26898,769.1473557951483)(27269,790.9199433962264)(27640,813.4528598382749)(28011,836.8241024258759)(28382,861.080665768194)(28753,886.3027628032345)(29124,912.5774959568732)(29495,939.9839460916443)(29866,968.653962264151)(30237,998.7923530997305)(30608,1030.6136603773584)(30979,1064.2623396226415)(31350,1100.220989218329)(31721,1138.6942614555257)(32092,1179.9984878706198)(32463,1224.7958005390835)(32834,1274.0089541778977)(33205,1328.8225849056605)(33576,1391.1415417789756)(33947,1463.6065067385443)(34318,1550.8098005390837)(34689,1661.4692075471698)(35060,1824.3313234501347)(35431,2141.3325256064686)(35802,2940.3429811320757)(36151.5,6899.040887195121)(36317,12695.69)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.011)(239.5,3.003002092050209)(717.5,9.1975)(1195.5,15.473012552301256)(1673.5,22.107)(2151.5,28.998301255230125)(2629.5,36.189257322175735)(3107.5,43.723)(3585.5,51.41517364016736)(4063.5,59.4635)(4541.5,67.71654184100419)(5019.5,76.30319037656903)(5497.5,85.1595)(5975.5,94.25958786610879)(6453.5,103.694)(6931.5,113.29276150627615)(7409.5,123.2455)(7887.5,133.35723430962344)(8365.5,143.826)(8843.5,154.50561924686193)(9321.5,165.50718828451883)(9799.5,176.844)(10277.5,188.50183891213388)(10755.5,200.51678451882844)(11233.5,212.91894769874477)(11711.5,225.72532635983262)(12189.5,238.95126150627615)(12667.5,252.61902928870293)(13145.5,266.74416527196655)(13623.5,281.3792719665272)(14101.5,296.5673284518829)(14579.5,312.32517364016735)(15057.5,328.69830753138075)(15535.5,345.75547071129705)(16013.5,363.5053430962343)(16491.5,382.03205439330543)(16969.5,401.41702092050207)(17447.5,421.740859832636)(17925.5,443.13734518828454)(18403.5,465.74711715481175)(18881.5,489.6866317991632)(19359.5,515.2018326359832)(19837.5,542.4019079497908)(20315.5,571.3341841004185)(20793.5,602.0434246861925)(21271.5,634.8044414225941)(21749.5,669.9890732217573)(22227.5,707.3027949790795)(22705.5,746.5745418410041)(23183.5,787.7260481171548)(23661.5,830.9119288702929)(24139.5,876.1701464435146)(24617.5,923.622338912134)(25095.5,973.415449790795)(25573.5,1025.5190062761505)(26051.5,1080.0794079497907)(26529.5,1137.2441317991631)(27007.5,1197.1491380753137)(27485.5,1259.997587866109)(27963.5,1325.8901129707112)(28441.5,1395.2120104602511)(28919.5,1468.3164748953975)(29397.5,1545.6936443514644)(29875.5,1627.697179916318)(30353.5,1714.9648619246861)(30831.5,1808.0020460251046)(31309.5,1907.35589958159)(31787.5,2013.702589958159)(32265.5,2127.0940774058577)(32743.5,2248.581280334728)(33221.5,2378.0494142259417)(33699.5,2516.0073828451887)(34177.5,2664.039150627615)(34655.5,2823.221081589958)(35133.5,2993.5568828451883)(35611.5,3175.938089958159)(36089.5,3371.323261506276)(36567.5,3580.968144351464)(37045.5,3805.3915585774057)(37523.5,4045.9028263598325)(38001.5,4303.908370292887)(38479.5,4580.979633891214)(38957.5,4878.916422594142)(39435.5,5201.072190376569)(39913.5,5551.563246861924)(40391.5,5935.1872949790795)(40869.5,6355.800322175732)(41347.5,6819.264579497908)(41825.5,7332.79989330544)(42303.5,7913.116949790795)(42781.5,8584.49539748954)(43259.5,9376.001481171548)(43737.5,10323.55618200837)(44215.5,11494.943769874477)(44693.5,13013.801780334728)(45171.5,15102.628635983265)(45649.5,18314.33333472803)(46127.5,23806.17459414226)(46582.5,34369.86894675926)(46800,43539.844)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.003)(242.5,1.0744855371900826)(726.5,3.4655)(1210.5,5.8855)(1694.5,8.3055)(2178.5,10.889551652892562)(2662.5,13.786)(3146.5,16.69)(3630.5,19.594)(4114.5,22.498)(4598.5,25.402)(5082.5,28.306)(5566.5,31.21)(6050.5,34.114)(6534.5,37.018)(7018.5,39.922)(7502.5,42.826)(7986.5,45.73)(8470.5,48.634)(8954.5,51.538)(9438.5,54.442)(9922.5,57.45211570247933)(10406.5,60.8125)(10890.5,64.2005)(11374.5,67.5885)(11858.5,70.9765)(12342.5,74.3645)(12826.5,77.7525)(13310.5,81.1405)(13794.5,84.5285)(14278.5,88.04413636363637)(14762.5,91.898)(15246.5,95.77)(15730.5,99.642)(16214.5,103.60915702479339)(16698.5,107.9315)(17182.5,112.2875)(17666.5,116.68544421487603)(18150.5,121.443)(18634.5,126.283)(19118.5,131.25429338842974)(19602.5,136.5615)(20086.5,141.96053099173554)(20570.5,147.721)(21054.5,153.53384710743802)(21538.5,159.6475)(22022.5,165.9395)(22506.5,172.2315)(22990.5,178.64468388429754)(23474.5,185.4)(23958.5,192.176)(24442.5,199.00360330578513)(24926.5,206.1935)(25410.5,213.4535)(25894.5,220.8263409090909)(26378.5,228.546)(26862.5,236.30813636363635)(27346.5,244.4085)(27830.5,252.6365)(28314.5,261.0807252066116)(28798.5,269.8022272727273)(29282.5,278.8455)(29766.5,288.1148698347107)(30250.5,297.7528615702479)(30734.5,307.75080165289256)(31218.5,318.19113636363636)(31702.5,329.0933388429752)(32186.5,340.5123243801653)(32670.5,352.5468078512397)(33154.5,365.25928305785123)(33638.5,378.71496694214875)(34122.5,392.9674814049587)(34606.5,408.1881095041322)(35090.5,424.496923553719)(35574.5,442.0963760330579)(36058.5,461.27055165289255)(36542.5,482.10873966942154)(37026.5,504.83204132231407)(37510.5,529.7162376033058)(37994.5,557.2993388429752)(38478.5,588.2287933884298)(38962.5,623.190291322314)(39446.5,663.5498512396694)(39930.5,711.7078305785124)(40414.5,771.0276487603306)(40898.5,850.0923057851239)(41382.5,963.3128016528926)(41866.5,1101.6400867768596)(42350.5,1247.2309276859505)(42834.5,1402.3912768595042)(43318.5,1571.1703719008265)(43802.5,1754.472152892562)(44286.5,1953.5502128099172)(44770.5,2173.350842975207)(45254.5,2424.403890495868)(45738.5,2725.6362169421486)(46222.5,3127.2070268595044)(46706.5,3851.115107438017)(47176.5,6425.0990570175445)(47406,11466.323)};
\addlegendentry{Z3str3RE}

\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.013)(121.5,1.7120082644628098)(363.5,5.2225)(605.5,8.8525)(847.5,12.548330578512397)(1089.5,16.480061983471074)(1331.5,20.66350826446281)(1573.5,25.187586776859504)(1815.5,30.315636363636365)(2057.5,37.034028925619836)(2299.5,47.26819421487603)(2541.5,63.143694214876035)(2783.5,87.08737190082644)(3025.5,119.03057438016529)(3267.5,152.87779338842975)(3509.5,187.68713223140495)(3751.5,223.38856198347108)(3993.5,259.89136776859505)(4235.5,297.26910743801653)(4477.5,335.72614049586775)(4719.5,375.26788429752065)(4961.5,415.86328512396693)(5203.5,457.628826446281)(5445.5,500.5764338842975)(5687.5,545.049520661157)(5929.5,591.5783884297521)(6171.5,640.2639297520661)(6413.5,691.3767644628099)(6655.5,745.3044504132231)(6897.5,802.9776611570248)(7139.5,864.1297355371901)(7381.5,927.3781404958678)(7623.5,992.0037809917355)(7865.5,1057.7867685950412)(8107.5,1124.6315123966942)(8349.5,1192.5747231404957)(8591.5,1261.5780537190083)(8833.5,1331.6086074380164)(9075.5,1402.7028347107437)(9317.5,1474.9072066115702)(9559.5,1548.5075041322314)(9801.5,1623.6399090909092)(10043.5,1700.4721859504132)(10285.5,1779.2844545454545)(10527.5,1860.0937727272726)(10769.5,1942.9279256198347)(11011.5,2027.9387975206612)(11253.5,2115.4554380165287)(11495.5,2205.679305785124)(11737.5,2299.044983471075)(11979.5,2395.7380041322313)(12221.5,2495.453338842975)(12463.5,2597.9617561983473)(12705.5,2703.040876033058)(12947.5,2811.046743801653)(13189.5,2922.233561983471)(13431.5,3036.8190743801656)(13673.5,3155.0550041322313)(13915.5,3277.2954958677688)(14157.5,3404.018123966942)(14399.5,3535.343376033058)(14641.5,3671.3976983471075)(14883.5,3811.849888429752)(15125.5,3957.2713512396695)(15367.5,4108.5858181818185)(15609.5,4266.528115702479)(15851.5,4431.535669421488)(16093.5,4604.015574380165)(16335.5,4785.366219008264)(16577.5,4975.805739669422)(16819.5,5176.19655785124)(17061.5,5387.800747933884)(17303.5,5612.16417768595)(17545.5,5849.1159669421495)(17787.5,6099.078747933884)(18029.5,6365.81873553719)(18271.5,6652.1750991735535)(18513.5,6961.59579338843)(18755.5,7294.319004132231)(18997.5,7654.666690082645)(19239.5,8048.816743801653)(19481.5,8482.50705785124)(19723.5,8960.417227272726)(19965.5,9492.69403305785)(20207.5,10088.572396694215)(20449.5,10753.385491735537)(20691.5,11507.436082644628)(20933.5,12350.568033057853)(21175.5,13286.226838842975)(21417.5,14340.296863636364)(21659.5,15565.351520661157)(21901.5,17022.022425619834)(22143.5,18795.41270247934)(22385.5,20994.64411570248)(22627.5,23767.618681818185)(22869.5,27349.00535123967)(23111.5,32061.896181818185)(23353.5,38596.88123966942)(23595.5,48042.54463636364)(23737,55329.597317073174)(23759,56566.098)};
\addlegendentry{Z3-Trau}

\path[name path=axisCVC5] (axis cs:0,0) -- (axis cs:44001,0);
\addplot [thick,color=colourCVC5,fill=colourCVC5,fill opacity=0.1] fill between [of=pathCVC5 and axisCVC5];
\path[name path=axisOstrichCEA] (axis cs:0,0) -- (axis cs:49127,0);
\addplot [thick,color=colourOstrichCEA,fill=colourOstrichCEA,fill opacity=0.1] fill between [of=pathOstrichCEA and axisOstrichCEA];
\path[name path=axisOstrich] (axis cs:0,0) -- (axis cs:47370,0);
\addplot [thick,color=colourOstrich,fill=colourOstrich,fill opacity=0.1] fill between [of=pathOstrich and axisOstrich];
\path[name path=axisZ3str3] (axis cs:0,0) -- (axis cs:36317,0);
\addplot [thick,color=colourZ3str3,fill=colourZ3str3,fill opacity=0.1] fill between [of=pathZ3str3 and axisZ3str3];
\path[name path=axisZ3seq] (axis cs:0,0) -- (axis cs:46800,0);
\addplot [thick,color=colourZ3seq,fill=colourZ3seq,fill opacity=0.1] fill between [of=pathZ3seq and axisZ3seq];
\path[name path=axisZ3str3RE] (axis cs:0,0) -- (axis cs:47406,0);
\addplot [thick,color=colourZ3str3RE,fill=colourZ3str3RE,fill opacity=0.1] fill between [of=pathZ3str3RE and axisZ3str3RE];
\path[name path=axisZ3-Trau] (axis cs:0,0) -- (axis cs:23759,0);
\addplot [thick,color=colourZ3-Trau,fill=colourZ3-Trau,fill opacity=0.1] fill between [of=pathZ3-Trau and axisZ3-Trau];
\end{axis}\end{tikzpicture}}

\end{document}

### 2023-04-11 2023-1-19/figures/cactus_plot_automatark.tex
atva2023 first version

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=automatark,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(44,0.1929655172413793)(131,0.619)(218,1.054)(305,1.489)(392,1.9436666666666667)(479,2.461)(566,2.983)(653,3.505)(740,4.027)(827,4.583517241379311)(914,5.192)(1001,5.801)(1088,6.410114942528736)(1175,7.067)(1262,7.763)(1349,8.460206896551725)(1436,9.213)(1523,9.996)(1610,10.779)(1697,11.58373563218391)(1784,12.45)(1871,13.32)(1958,14.19)(2045,15.101034482758621)(2132,16.058)(2219,17.015)(2306,17.972)(2393,18.96351724137931)(2480,20.007)(2567,21.051)(2654,22.095)(2741,23.170045977011494)(2828,24.3)(2915,25.431)(3002,26.564655172413794)(3089,27.758)(3176,28.976)(3263,30.194632183908045)(3350,31.466)(3437,32.771)(3524,34.076)(3611,35.40875862068965)(3698,36.799)(3785,38.19365517241379)(3872,39.648)(3959,41.127)(4046,42.64232183908046)(4133,44.208)(4220,45.8121724137931)(4307,47.46741379310345)(4394,49.182)(4481,50.93724137931035)(4568,52.758758620689655)(4655,54.645)(4742,56.59175862068965)(4829,58.61818390804598)(4916,60.734206896551726)(5003,62.95365517241379)(5090,65.28090804597701)(5177,67.70108045977013)(5264,70.23856321839081)(5351,72.88997701149425)(5438,75.67103448275863)(5525,78.58893103448275)(5612,81.6562183908046)(5699,84.874)(5786,88.2651724137931)(5873,91.82601149425287)(5960,95.5585172413793)(6047,99.47231034482758)(6134,103.54482758620689)(6221,107.8031724137931)(6308,112.31964367816093)(6395,117.07937931034482)(6482,122.072091954023)(6569,127.33118390804597)(6656,132.8960804597701)(6743,138.7530804597701)(6830,144.9270459770115)(6917,151.4784712643678)(7004,158.41937931034485)(7091,165.80327586206894)(7178,173.69822988505746)(7265,182.17563218390805)(7352,191.24119540229884)(7439,201.0427931034483)(7526,211.73466666666667)(7613,223.59497701149425)(7700,236.8307471264368)(7787,252.0250344827586)(7874,270.1710804597701)(7961,293.053816091954)(8048,322.6413333333333)(8135,362.7002988505747)(8222,425.82054022988507)(8309,535.5033103448276)(8396,770.6830344827586)(8478.5,1487.735076923077)(8519,2580.115)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.001)(44.5,49.77588636363636)(132.5,153.98013636363635)(220.5,262.1894545454545)(308.5,372.31238636363634)(396.5,483.76913636363633)(484.5,596.3042386363636)(572.5,709.8801022727273)(660.5,824.4665795454546)(748.5,940.0296818181818)(836.5,1056.4871704545453)(924.5,1173.8087727272728)(1012.5,1291.9674659090908)(1100.5,1410.8886590909092)(1188.5,1530.5722159090908)(1276.5,1651.1055568181819)(1364.5,1772.5285454545453)(1452.5,1894.8319431818181)(1540.5,2018.1299886363636)(1628.5,2142.4604431818184)(1716.5,2267.7058636363636)(1804.5,2393.9053636363637)(1892.5,2521.1623863636364)(1980.5,2649.336715909091)(2068.5,2778.3925568181817)(2156.5,2908.361522727273)(2244.5,3039.2929886363636)(2332.5,3171.2455681818183)(2420.5,3304.1568181818184)(2508.5,3437.978727272727)(2596.5,3572.7547045454544)(2684.5,3708.3190795454548)(2772.5,3844.8086704545453)(2860.5,3982.276659090909)(2948.5,4120.705352272727)(3036.5,4260.052625)(3124.5,4400.310102272728)(3212.5,4541.485136363637)(3300.5,4683.616443181819)(3388.5,4826.598465909091)(3476.5,4970.501204545454)(3564.5,5115.386761363637)(3652.5,5261.080522727272)(3740.5,5407.658522727273)(3828.5,5555.073136363637)(3916.5,5703.36828409091)(4004.5,5852.564125)(4092.5,6002.664488636363)(4180.5,6153.749011363637)(4268.5,6305.792931818181)(4356.5,6458.7932045454545)(4444.5,6612.791284090909)(4532.5,6767.785272727272)(4620.5,6923.865602272727)(4708.5,7081.039670454546)(4796.5,7239.417079545454)(4884.5,7399.086931818181)(4972.5,7560.03825)(5060.5,7722.204431818182)(5148.5,7885.649727272727)(5236.5,8050.295590909091)(5324.5,8216.39771590909)(5412.5,8384.032886363637)(5500.5,8553.316522727273)(5588.5,8724.139943181819)(5676.5,8896.458170454545)(5764.5,9070.357636363637)(5852.5,9245.943272727274)(5940.5,9423.107818181817)(6028.5,9602.053295454545)(6116.5,9782.941011363637)(6204.5,9965.751875)(6292.5,10150.460022727273)(6380.5,10337.203965909091)(6468.5,10525.924090909091)(6556.5,10717.150215909092)(6644.5,10910.920056818182)(6732.5,11107.200715909092)(6820.5,11306.398920454545)(6908.5,11508.439136363637)(6996.5,11713.935943181817)(7084.5,11923.624)(7172.5,12136.768875)(7260.5,12353.715988636362)(7348.5,12574.161954545456)(7436.5,12798.799136363637)(7524.5,13029.105806818181)(7612.5,13264.319659090908)(7700.5,13505.580909090908)(7788.5,13753.832738636364)(7876.5,14009.777022727274)(7964.5,14275.649375)(8052.5,14554.259579545454)(8140.5,14849.837511363638)(8228.5,15168.880022727273)(8316.5,15522.201875)(8404.5,15935.410215909093)(8492.5,16507.840431818182)(8580.5,17813.824431818182)(8631,19480.083)(8639,19878.963)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.966)(45,51.629651685393256)(134,158.67904494382023)(223,269.89732584269666)(312,383.6197528089888)(401,499.6783033707865)(490,617.7793258426966)(579,737.6599775280899)(668,858.9771348314606)(757,981.355786516854)(846,1104.57902247191)(935,1228.659370786517)(1024,1353.5784606741574)(1113,1479.340449438202)(1202,1605.8423483146069)(1291,1732.994393258427)(1380,1860.7982471910111)(1469,1989.2398764044942)(1558,2118.2535730337077)(1647,2247.769235955056)(1736,2377.8024382022472)(1825,2508.35204494382)(1914,2639.348359550562)(2003,2770.839404494382)(2092,2902.8377078651683)(2181,3035.319370786517)(2270,3168.2678876404493)(2359,3301.7290674157307)(2448,3435.6920898876406)(2537,3570.1292921348318)(2626,3705.1524606741573)(2715,3840.691617977528)(2804,3976.759415730337)(2893,4113.360764044944)(2982,4250.445494382023)(3071,4388.062044943821)(3160,4526.229382022472)(3249,4664.950314606742)(3338,4804.172505617978)(3427,4943.860483146068)(3516,5084.05806741573)(3605,5224.723202247191)(3694,5365.906865168539)(3783,5507.576955056179)(3872,5649.704640449439)(3961,5792.306471910112)(4050,5935.380764044944)(4139,6078.9809550561795)(4228,6223.057966292135)(4317,6367.639449438202)(4406,6512.755247191011)(4495,6658.350494382023)(4584,6804.486224719101)(4673,6951.171146067415)(4762,7098.355382022472)(4851,7246.019595505618)(4940,7394.190629213483)(5029,7542.908370786517)(5118,7692.217370786517)(5207,7842.0449101123595)(5296,7992.411258426966)(5385,8143.2914269662915)(5474,8294.690213483147)(5563,8446.689786516854)(5652,8599.329584269663)(5741,8752.537707865169)(5830,8906.401494382022)(5919,9060.95129213483)(6008,9216.186011235954)(6097,9372.039516853933)(6186,9528.586505617977)(6275,9685.89011235955)(6364,9843.871674157303)(6453,10002.450629213485)(6542,10161.815808988766)(6631,10321.953292134831)(6720,10482.887561797754)(6809,10644.69070786517)(6898,10807.32670786517)(6987,10970.82293258427)(7076,11135.298629213485)(7165,11300.878033707864)(7254,11467.537505617978)(7343,11635.502033707864)(7432,11804.723314606741)(7521,11975.318898876405)(7610,12147.362651685393)(7699,12320.866617977528)(7788,12495.943325842698)(7877,12672.84586516854)(7966,12851.813775280898)(8055,13033.299011235955)(8144,13217.471460674158)(8233,13405.040426966292)(8322,13597.334921348314)(8411,13797.202966292136)(8500,14006.997168539327)(8589,14242.676)(8663.5,14719.4016)(8695,15616.104)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.011)(28,0.34405454545454545)(83,1.004)(138,1.664)(193,2.324)(248,2.984)(303,3.6490181818181817)(358,4.355)(413,5.07)(468,5.785)(523,6.5)(578,7.215)(633,7.93)(688,8.645)(743,9.36)(798,10.075)(853,10.79)(908,11.505)(963,12.22)(1018,12.935)(1073,13.65)(1128,14.365)(1183,15.08)(1238,15.795)(1293,16.51)(1348,17.234018181818183)(1403,17.999)(1458,18.769)(1513,19.541781818181818)(1568,20.355)(1623,21.217)(1678,22.11927272727273)(1733,23.054)(1788,24.01127272727273)(1843,25.001)(1898,25.992654545454545)(1953,27.022)(2008,28.067)(2063,29.112)(2118,30.1666)(2173,31.262)(2228,32.362)(2283,33.462)(2338,34.564781818181814)(2393,35.707)(2448,36.862)(2503,38.017)(2558,39.172)(2613,40.35205454545454)(2668,41.562)(2723,42.772)(2778,43.99618181818182)(2833,45.259)(2888,46.524)(2943,47.80865454545455)(2998,49.128)(3053,50.47210909090909)(3108,51.8482)(3163,53.26290909090909)(3218,54.7376)(3273,56.27590909090909)(3328,57.87347272727273)(3383,59.548418181818185)(3438,61.30281818181818)(3493,63.13972727272727)(3548,65.0678909090909)(3603,67.10025454545455)(3658,69.2492)(3713,71.49483636363637)(3768,73.84325454545454)(3823,76.31507272727272)(3878,78.93901818181818)(3933,81.7334909090909)(3988,84.68719999999999)(4043,87.8238)(4098,91.12774545454545)(4153,94.64658181818182)(4208,98.41867272727274)(4263,102.46365454545455)(4318,106.77592727272727)(4373,111.44936363636363)(4428,116.65296363636364)(4483,122.39274545454545)(4538,128.6556)(4593,135.70430909090908)(4648,143.72623636363636)(4703,152.72258181818182)(4758,162.99996363636362)(4813,175.10872727272726)(4868,189.50578181818182)(4923,208.60178181818182)(4978,241.16914545454546)(5033,301.7078909090909)(5088,407.2800363636364)(5143,527.1198909090908)(5198,654.8019272727272)(5253,840.1544181818182)(5308,1365.6359454545457)(5363,2537.6238)(5400.5,4036.3596000000002)(5412,4631.644)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.012)(44,0.5610344827586207)(131,1.688)(218,2.819)(305,3.95)(392,5.081)(479,6.212)(566,7.343)(653,8.474)(740,9.605)(827,10.736)(914,11.867)(1001,13.03806896551724)(1088,14.256)(1175,15.474)(1262,16.692)(1349,17.91)(1436,19.128)(1523,20.360655172413793)(1610,21.658)(1697,22.963)(1784,24.28096551724138)(1871,25.664)(1958,27.056)(2045,28.463241379310343)(2132,29.935)(2219,31.414)(2306,32.8931724137931)(2393,34.421)(2480,35.987)(2567,37.553)(2654,39.13308045977011)(2741,40.778)(2828,42.431)(2915,44.084)(3002,45.78)(3089,47.52)(3176,49.26)(3263,51.02618390804598)(3350,52.851)(3437,54.678)(3524,56.54132183908046)(3611,58.455)(3698,60.38365517241379)(3785,62.377)(3872,64.40044827586208)(3959,66.485)(4046,68.61403448275863)(4133,70.79366666666667)(4220,73.036)(4307,75.34001149425288)(4394,77.72368965517242)(4481,80.208)(4568,82.774)(4655,85.4200459770115)(4742,88.19042528735632)(4829,91.09298850574713)(4916,94.14202298850574)(5003,97.34010344827585)(5090,100.71949425287357)(5177,104.2736551724138)(5264,108.0643908045977)(5351,112.12058620689655)(5438,116.49328735632184)(5525,121.25075862068965)(5612,126.37032183908046)(5699,131.87488505747126)(5786,137.83209195402299)(5873,144.3935747126437)(5960,151.6332528735632)(6047,159.56349425287357)(6134,168.32394252873564)(6221,178.00933333333333)(6308,188.61080459770116)(6395,200.22363218390805)(6482,213.0765632183908)(6569,227.277816091954)(6656,243.0501379310345)(6743,260.7920344827586)(6830,280.4905517241379)(6917,302.7097586206897)(7004,327.5999540229885)(7091,355.8960229885057)(7178,388.3605862068966)(7265,425.57027586206897)(7352,467.78589655172414)(7439,515.8811034482759)(7526,572.8783908045978)(7613,640.500264367816)(7700,721.5446551724137)(7787,819.6228965517241)(7874,943.8886896551724)(7961,1102.410471264368)(8048,1306.6646551724136)(8135,1592.898448275862)(8222,2000.9801264367816)(8309,2632.139011494253)(8396,3684.789195402299)(8483,5632.933747126437)(8528.5,7474.12825)(8532,7620.921)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.004)(45,0.1892247191011236)(134,0.615)(223,1.06)(312,1.505)(401,1.95)(490,2.395)(579,2.84)(668,3.285)(757,3.73)(846,4.175)(935,4.62)(1024,5.071303370786517)(1113,5.588)(1202,6.122)(1291,6.656)(1380,7.209224719101123)(1469,7.827)(1558,8.45)(1647,9.073)(1736,9.696)(1825,10.319)(1914,10.942)(2003,11.565)(2092,12.188)(2181,12.834370786516855)(2270,13.543)(2359,14.255)(2448,14.967)(2537,15.679)(2626,16.391)(2715,17.103)(2804,17.815)(2893,18.527)(2982,19.239)(3071,19.951)(3160,20.663)(3249,21.381685393258426)(3338,22.166)(3427,22.967)(3516,23.768)(3605,24.569)(3694,25.37)(3783,26.171)(3872,26.972)(3961,27.773)(4050,28.574)(4139,29.375)(4228,30.181932584269664)(4317,31.054)(4406,31.944)(4495,32.834)(4584,33.724)(4673,34.614)(4762,35.504)(4851,36.394)(4940,37.29030337078652)(5029,38.252)(5118,39.231)(5207,40.21)(5296,41.189)(5385,42.1703595505618)(5474,43.212)(5563,44.28)(5652,45.348)(5741,46.41661797752809)(5830,47.539)(5919,48.696)(6008,49.853)(6097,51.045505617977526)(6186,52.291)(6275,53.542932584269664)(6364,54.86)(6453,56.19924719101124)(6542,57.602)(6631,59.045887640449436)(6720,60.55431460674157)(6809,62.11923595505618)(6898,63.772)(6987,65.50240449438202)(7076,67.33822471910112)(7165,69.29493258426966)(7254,71.38649438202248)(7343,73.63291011235955)(7432,76.06348314606741)(7521,78.76337078651686)(7610,81.7866179775281)(7699,85.20116853932583)(7788,89.14226966292135)(7877,93.84008988764046)(7966,99.66762921348314)(8055,106.92501123595505)(8144,116.53524719101124)(8233,130.10767415730336)(8322,150.67694382022472)(8411,185.7845842696629)(8500,252.37134831460673)(8589,453.2947752808989)(8655.5,1213.1201363636364)(8679,2048.545)};
\addlegendentry{Z3str3RE}

\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.014)(20.5,0.32530000000000003)(60.5,0.961)(100.5,1.601)(140.5,2.259525)(180.5,2.9395)(220.5,3.6195)(260.5,4.2995)(300.5,4.9795)(340.5,5.677074999999999)(380.5,6.397)(420.5,7.117)(460.5,7.837375)(500.5,8.5825)(540.5,9.3425)(580.5,10.1025)(620.5,10.86725)(660.5,11.662)(700.5,12.46365)(740.5,13.2935)(780.5,14.147525)(820.5,15.038625)(860.5,15.975775)(900.5,16.968275000000002)(940.5,18.01415)(980.5,19.11675)(1020.5,20.294700000000002)(1060.5,21.557875)(1100.5,22.9257)(1140.5,24.40535)(1180.5,26.00135)(1220.5,27.721275000000002)(1260.5,29.585775)(1300.5,31.62705)(1340.5,33.848675)(1380.5,36.232575)(1420.5,38.778974999999996)(1460.5,41.503525)(1500.5,44.394324999999995)(1540.5,47.462050000000005)(1580.5,50.750025)(1620.5,54.262875)(1660.5,58.105625)(1700.5,62.247775000000004)(1740.5,66.659425)(1780.5,71.44305)(1820.5,76.593825)(1860.5,82.178)(1900.5,88.251)(1940.5,94.871325)(1980.5,102.07889999999999)(2020.5,110.022225)(2060.5,118.74025)(2100.5,128.321775)(2140.5,138.75495)(2180.5,149.990875)(2220.5,162.040425)(2260.5,174.9545)(2300.5,188.80342499999998)(2340.5,203.825675)(2380.5,220.271825)(2420.5,238.0997)(2460.5,257.46645)(2500.5,278.476375)(2540.5,301.07705)(2580.5,325.38465)(2620.5,351.73775)(2660.5,380.3615)(2700.5,411.6698)(2740.5,446.16547499999996)(2780.5,484.531075)(2820.5,527.1384)(2860.5,574.245875)(2900.5,625.3648499999999)(2940.5,680.9376500000001)(2980.5,743.98175)(3020.5,817.6037)(3060.5,900.421375)(3100.5,991.74745)(3140.5,1092.250625)(3180.5,1203.1501)(3220.5,1326.906925)(3260.5,1463.5923500000001)(3300.5,1614.2668)(3340.5,1781.566325)(3380.5,1976.8985500000001)(3420.5,2205.8372999999997)(3460.5,2468.497475)(3500.5,2786.5406749999997)(3540.5,3160.2475)(3580.5,3582.4527749999997)(3620.5,4085.978125)(3660.5,4674.079625)(3700.5,5342.3874000000005)(3740.5,6120.993974999999)(3780.5,7068.202275000001)(3820.5,8261.846725)(3860.5,9710.5938)(3900.5,11480.593425000001)(3935,13291.69527586207)(3951,14160.091)};
\addlegendentry{Z3-Trau}

\path[name path=axisCVC5] (axis cs:0,0) -- (axis cs:8519,0);
\addplot [thick,color=colourCVC5,fill=colourCVC5,fill opacity=0.1] fill between [of=pathCVC5 and axisCVC5];
\path[name path=axisOstrichCEA] (axis cs:0,0) -- (axis cs:8639,0);
\addplot [thick,color=colourOstrichCEA,fill=colourOstrichCEA,fill opacity=0.1] fill between [of=pathOstrichCEA and axisOstrichCEA];
\path[name path=axisOstrich] (axis cs:0,0) -- (axis cs:8695,0);
\addplot [thick,color=colourOstrich,fill=colourOstrich,fill opacity=0.1] fill between [of=pathOstrich and axisOstrich];
\path[name path=axisZ3str3] (axis cs:0,0) -- (axis cs:5412,0);
\addplot [thick,color=colourZ3str3,fill=colourZ3str3,fill opacity=0.1] fill between [of=pathZ3str3 and axisZ3str3];
\path[name path=axisZ3seq] (axis cs:0,0) -- (axis cs:8532,0);
\addplot [thick,color=colourZ3seq,fill=colourZ3seq,fill opacity=0.1] fill between [of=pathZ3seq and axisZ3seq];
\path[name path=axisZ3str3RE] (axis cs:0,0) -- (axis cs:8679,0);
\addplot [thick,color=colourZ3str3RE,fill=colourZ3str3RE,fill opacity=0.1] fill between [of=pathZ3str3RE and axisZ3str3RE];
\path[name path=axisZ3-Trau] (axis cs:0,0) -- (axis cs:3951,0);
\addplot [thick,color=colourZ3-Trau,fill=colourZ3-Trau,fill opacity=0.1] fill between [of=pathZ3-Trau and axisZ3-Trau];
\end{axis}\end{tikzpicture}}

\end{document}

### 2023-04-11 2023-1-19/figures/cactus_plot_heuristic.tex
atva2023 first version

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourOstrichCEA}{HTML}{25333D}
\definecolor{colourUnder Approximation off}{HTML}{0065AB}
\definecolor{colourSimplification off}{HTML}{8939AD}
\definecolor{colourAll off}{HTML}{007E7A}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=Total,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.256)(251,375.73549500998007)(752,1183.8739021956087)(1253,2022.618491017964)(1754,2877.9200359281435)(2255,3746.0393033932137)(2756,4625.084281437126)(3257,5513.779463073853)(3758,6411.872730538922)(4259,7319.427289421158)(4760,8236.114157684631)(5261,9161.532343313374)(5762,10096.144241516966)(6263,11040.38131736527)(6764,11994.772165668663)(7265,12960.379053892215)(7766,13938.16142714571)(8267,14928.978754491018)(8768,15934.640826347304)(9269,16955.70472255489)(9770,17992.700299401196)(10271,19044.441936127743)(10772,20110.456696606787)(11273,21189.18998203593)(11774,22279.62379241517)(12275,23380.84084031936)(12776,24491.869590818365)(13277,25612.71845309381)(13778,26743.928768463076)(14279,27885.323826347307)(14780,29035.924956087823)(15281,30195.091335329344)(15782,31363.01940518962)(16283,32539.236013972055)(16784,33723.31988023953)(17285,34915.447836327345)(17786,36114.84655888224)(18287,37321.58146307385)(18788,38535.701952095806)(19289,39756.911600798405)(19790,40985.1631017964)(20291,42220.45616367266)(20792,43462.636586826346)(21293,44711.67520558883)(21794,45967.50069461078)(22295,47230.13759281437)(22796,48499.66564471058)(23297,49776.35208782435)(23798,51060.01192814371)(24299,52350.822175648704)(24800,53648.5965748503)(25301,54953.18310379241)(25802,56264.57108582834)(26303,57583.00460678643)(26804,58908.59252295409)(27305,60241.239854291416)(27806,61581.528387225546)(28307,62929.616544910175)(28808,64285.927918163674)(29309,65650.71985229541)(29810,67024.12507584831)(30311,68406.55969061877)(30812,69797.76003592815)(31313,71197.73274650698)(31814,72607.24381437126)(32315,74026.60229740519)(32816,75455.86899201597)(33317,76895.86807984032)(33818,78346.82771656686)(34319,79809.24070259482)(34820,81283.33454291416)(35321,82769.59380638723)(35822,84269.10105988024)(36323,85782.33381836327)(36824,87310.26063073853)(37325,88853.80257085829)(37826,90415.16936327345)(38327,91994.438750499)(38828,93592.4894510978)(39329,95211.69484830339)(39830,96853.58521157685)(40331,98519.82530938124)(40832,100212.75770459081)(41333,101935.10099401198)(41834,103689.06698403193)(42335,105476.94833532933)(42836,107301.12517165668)(43337,109166.71543512975)(43838,111078.39904191616)(44339,113041.1118263473)(44840,115058.31930339322)(45341,117139.44398802395)(45842,119295.3597245509)(46343,121540.35781237525)(46844,123904.0013233533)(47345,126431.7289760479)(47846,129212.59415968064)(48347,132495.7146007984)(48845.5,137664.56463508063)(49095,143594.349)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathUnder Approximation off , colourUnder Approximation off, line width=1.5pt] coordinates {(1,1.143)(247.5,345.5671659919028)(741.5,1093.1268178137652)(1235.5,1881.7518846153846)(1729.5,2688.709206477733)(2223.5,3507.6373157894736)(2717.5,4336.697226720647)(3211.5,5174.640070850202)(3705.5,6020.75543117409)(4199.5,6875.348497975709)(4693.5,7738.697793522268)(5187.5,8610.4509048583)(5681.5,9491.439477732794)(6175.5,10383.11131174089)(6669.5,11286.058060728745)(7163.5,12201.323759109313)(7657.5,13130.214445344129)(8151.5,14072.49958097166)(8645.5,15027.589060728746)(9139.5,15993.548682186234)(9633.5,16968.388783400813)(10127.5,17950.561637651823)(10621.5,18939.66844736842)(11115.5,19935.288463562752)(11609.5,20936.991455465588)(12103.5,21944.461374493927)(12597.5,22957.267400809716)(13091.5,23975.060060728745)(13585.5,24997.827248987855)(14079.5,26025.643408906883)(14573.5,27058.369396761133)(15067.5,28095.932414979758)(15561.5,29138.35586032389)(16055.5,30185.54812145749)(16549.5,31237.71652631579)(17043.5,32294.568991902837)(17537.5,33355.85782591093)(18031.5,34421.65787044534)(18525.5,35492.13017813765)(19019.5,36567.51576923077)(19513.5,37647.78307692308)(20007.5,38732.940694331985)(20501.5,39823.37698582996)(20995.5,40919.24681983805)(21489.5,42020.08232591093)(21983.5,43125.835275303645)(22477.5,44236.932014170045)(22971.5,45353.34651214575)(23465.5,46475.20208299595)(23959.5,47602.54591700405)(24453.5,48735.58559311741)(24947.5,49873.97048987854)(25441.5,51018.06316396761)(25935.5,52167.99957287449)(26429.5,53323.73327327935)(26923.5,54485.43606882591)(27417.5,55653.25192510121)(27911.5,56827.234957489876)(28405.5,58007.57878340081)(28899.5,59194.84101619433)(29393.5,60388.59112955466)(29887.5,61589.210236842104)(30381.5,62796.74455060728)(30875.5,64011.43599797571)(31369.5,65233.93253643725)(31863.5,66464.4293805668)(32357.5,67703.53380364372)(32851.5,68951.35434008097)(33345.5,70208.14511943319)(33839.5,71474.93029149798)(34333.5,72752.14231781376)(34827.5,74040.93050404859)(35321.5,75341.12895748988)(35815.5,76653.30199190283)(36309.5,77978.19206680162)(36803.5,79316.7351194332)(37297.5,80669.18660526315)(37791.5,82036.25991902834)(38285.5,83419.48054655871)(38779.5,84819.95787651822)(39273.5,86240.30562955466)(39767.5,87682.62130364371)(40261.5,89147.46975506074)(40755.5,90638.08723481782)(41249.5,92156.34871457491)(41743.5,93704.68462348178)(42237.5,95286.82339878543)(42731.5,96907.78887246964)(43225.5,98569.67491700404)(43719.5,100277.59814979757)(44213.5,102037.28515789473)(44707.5,103855.00732388663)(45201.5,105743.83414574899)(45695.5,107719.03925101215)(46189.5,109802.37090890687)(46683.5,112039.03551214574)(47177.5,114517.45951214574)(47671.5,117550.44509311742)(48165.5,123028.84814979757)(48419.5,129605.71235714285)(48428,130033.418)};
\addlegendentry{Under Approximation off}

\addplot[name path=pathSimplification off , colourSimplification off, line width=1.5pt] coordinates {(1,1.135)(246.5,363.1045792682927)(738.5,1150.2894695121952)(1230.5,1976.5712662601627)(1722.5,2827.88006097561)(2214.5,3700.4905081300813)(2706.5,4592.667786585365)(3198.5,5505.309475609756)(3690.5,6435.865410569106)(4182.5,7382.667552845528)(4674.5,8345.835542682928)(5166.5,9325.28124186992)(5658.5,10320.03525609756)(6150.5,11330.31531300813)(6642.5,12355.397339430894)(7134.5,13394.562701219513)(7626.5,14448.094024390242)(8118.5,15515.715595528456)(8610.5,16597.635471544716)(9102.5,17694.34049593496)(9594.5,18806.49131504065)(10086.5,19933.432048780487)(10578.5,21074.394237804878)(11070.5,22229.156333333332)(11562.5,23398.27930284553)(12054.5,24582.21882926829)(12546.5,25781.288851626017)(13038.5,26995.324906504065)(13530.5,28224.14231300813)(14022.5,29466.946489837395)(14514.5,30723.627083333333)(15006.5,31995.121766260163)(15498.5,33280.916351626016)(15990.5,34581.29370528455)(16482.5,35896.226640243905)(16974.5,37225.31055691057)(17466.5,38568.79462398374)(17958.5,39926.34044715447)(18450.5,41296.85248577235)(18942.5,42680.20717479674)(19434.5,44077.110611788616)(19926.5,45488.34107113821)(20418.5,46913.13556707317)(20910.5,48352.125798780486)(21402.5,49805.39538211382)(21894.5,51272.918483739835)(22386.5,52754.42153455284)(22878.5,54249.736412601625)(23370.5,55759.46517073171)(23862.5,57283.576719512195)(24354.5,58822.75940243903)(24846.5,60376.9937398374)(25338.5,61946.492164634146)(25830.5,63530.548172764225)(26322.5,65129.932030487806)(26814.5,66745.12398577236)(27306.5,68376.3347296748)(27798.5,70024.90577439025)(28290.5,71690.3053699187)(28782.5,73371.95175406504)(29274.5,75070.203699187)(29766.5,76786.4307703252)(30258.5,78521.07297357723)(30750.5,80274.46002642276)(31242.5,82047.87613211382)(31734.5,83841.58971341464)(32226.5,85655.53554268293)(32718.5,87490.54740447155)(33210.5,89347.99480691057)(33702.5,91229.68758130081)(34194.5,93135.32528455285)(34686.5,95066.21725406504)(35178.5,97024.63288211382)(35670.5,99011.55916463415)(36162.5,101029.76689634146)(36654.5,103081.27141260162)(37146.5,105168.26180081301)(37638.5,107291.90132520326)(38130.5,109453.49715853659)(38622.5,111655.81977845529)(39114.5,113904.8909186992)(39606.5,116202.81763211382)(40098.5,118552.27406707317)(40590.5,120957.2551402439)(41082.5,123425.42828861788)(41574.5,125962.37361585365)(42066.5,128575.37174593496)(42558.5,131275.79281300813)(43050.5,134077.2708373984)(43542.5,136992.64292682928)(44034.5,140037.24509959348)(44526.5,143234.2047682927)(45018.5,146613.52907520323)(45510.5,150227.2450487805)(46002.5,154142.48767479675)(46494.5,158476.08704268292)(46986.5,163481.78608130082)(47478.5,169657.74288617886)(47970.5,179379.5124085366)(48232.5,188736.69675)(48250,189680.595)};
\addlegendentry{Simplification off}

\addplot[name path=pathAll off , colourAll off, line width=1.5pt] coordinates {(1,0.875)(243,239.0925670103093)(728,789.0446762886598)(1213,1427.6660762886597)(1698,2129.867397938144)(2183,2881.0539896907217)(2668,3671.581068041237)(3153,4493.687478350515)(3638,5339.833039175258)(4123,6207.217783505154)(4608,7093.622016494845)(5093,7998.2535546391755)(5578,8919.579428865978)(6063,9857.085991752578)(6548,10809.771478350514)(7033,11776.57105154639)(7518,12756.855435051546)(8003,13750.731303092783)(8488,14758.17447628866)(8973,15778.258529896908)(9458,16810.315026804124)(9943,17854.688107216494)(10428,18910.425841237113)(10913,19977.368713402062)(11398,21055.836604123713)(11883,22146.078154639177)(12368,23247.494826804123)(12853,24359.831055670104)(13338,25483.356445360823)(13823,26618.428564948455)(14308,27765.086074226805)(14793,28923.04323298969)(15278,30092.317987628867)(15763,31272.194832989688)(16248,32463.187107216498)(16733,33665.03872577319)(17218,34878.637705154644)(17703,36103.445179381444)(18188,37338.722492783505)(18673,38585.054059793816)(19158,39842.79948659794)(19643,41112.23856082474)(20128,42392.9905072165)(20613,43685.152076288665)(21098,44988.906665979375)(21583,46304.85870309278)(22068,47632.615063917525)(22553,48972.09419381443)(23038,50323.242482474234)(23523,51686.194051546394)(24008,53061.78827835052)(24493,54449.89010927835)(24978,55849.986849484536)(25463,57262.85256494845)(25948,58688.74006185567)(26433,60128.35171546391)(26918,61580.78451546392)(27403,63046.65391546392)(27888,64526.46483505154)(28373,66020.0550185567)(28858,67528.27430103094)(29343,69051.90326185568)(29828,70591.74819381443)(30313,72149.14522061856)(30798,73724.00676701032)(31283,75316.27581237114)(31768,76926.78957319587)(32253,78555.2702701031)(32738,80202.53150515463)(33223,81871.12324948455)(33708,83561.23319381442)(34193,85273.75785979381)(34678,87009.43252783506)(35163,88769.27956701031)(35648,90556.07208453608)(36133,92373.16419587629)(36618,94221.60716907217)(37103,96102.0720371134)(37588,98018.9705113402)(38073,99975.30944329896)(38558,101974.99814432989)(39043,104021.63824536082)(39528,106116.20065360825)(40013,108263.02482474227)(40498,110468.98961237114)(40983,112746.94890721649)(41468,115107.6707484536)(41953,117562.98611546391)(42438,120126.02667628866)(42923,122802.09602061856)(43408,125607.74125979382)(43893,128581.27053608248)(44378,131755.0405072165)(44863,135193.23917113402)(45348,138956.2646639175)(45833,143194.02182268043)(46318,148200.39157938142)(46803,154703.10293814432)(47274.5,165290.41879475984)(47505,174530.666)};
\addlegendentry{All off}

\path[name path=axisOstrichCEA] (axis cs:0,0) -- (axis cs:49095,0);
\addplot [thick,color=colourOstrichCEA,fill=colourOstrichCEA,fill opacity=0.1] fill between [of=pathOstrichCEA and axisOstrichCEA];
\path[name path=axisUnder Approximation off] (axis cs:0,0) -- (axis cs:48428,0);
\addplot [thick,color=colourUnder Approximation off,fill=colourUnder Approximation off,fill opacity=0.1] fill between [of=pathUnder Approximation off and axisUnder Approximation off];
\path[name path=axisSimplification off] (axis cs:0,0) -- (axis cs:48250,0);
\addplot [thick,color=colourSimplification off,fill=colourSimplification off,fill opacity=0.1] fill between [of=pathSimplification off and axisSimplification off];
\path[name path=axisAll off] (axis cs:0,0) -- (axis cs:47505,0);
\addplot [thick,color=colourAll off,fill=colourAll off,fill opacity=0.1] fill between [of=pathAll off and axisAll off];
\end{axis}\end{tikzpicture}}

\end{document}

### 2023-04-11 2023-1-19/figures/cactus_plot_redos.tex
atva2023 first version

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourOstrichCEA}{HTML}{25333D}
\definecolor{colourOstrich}{HTML}{0065AB}
\definecolor{colourCVC5}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=redos,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.268)(8.5,12.6915625)(24.5,34.954875)(40.5,58.2241875)(56.5,82.7331875)(72.5,108.7551875)(88.5,135.7378125)(104.5,163.2775625)(120.5,191.216375)(136.5,219.530625)(152.5,248.17575)(168.5,277.0789375)(184.5,306.2231875)(200.5,335.6075)(216.5,365.1799375)(232.5,394.96425)(248.5,424.948625)(264.5,455.1505)(280.5,485.57425)(296.5,516.2539375)(312.5,547.1195625)(328.5,578.1605)(344.5,609.3965625)(360.5,640.86375)(376.5,672.526125)(392.5,704.3930625)(408.5,736.42525)(424.5,768.6708125)(440.5,801.1625625)(456.5,833.9086875)(472.5,866.889875)(488.5,900.0090625)(504.5,933.2758125)(520.5,966.7259375)(536.5,1000.365375)(552.5,1034.2524375)(568.5,1068.3616875)(584.5,1102.7155625)(600.5,1137.2868125)(616.5,1172.10175)(632.5,1207.1765)(648.5,1242.504)(664.5,1278.005125)(680.5,1313.6974375)(696.5,1349.6119375)(712.5,1385.7789375)(728.5,1422.28125)(744.5,1459.09975)(760.5,1496.2685)(776.5,1533.80525)(792.5,1571.5899375)(808.5,1609.6835)(824.5,1648.163)(840.5,1686.9795625)(856.5,1726.3140625)(872.5,1766.0058125)(888.5,1805.9916875)(904.5,1846.3615625)(920.5,1887.2036875)(936.5,1928.6034375)(952.5,1970.5518125)(968.5,2013.213875)(984.5,2056.5095625)(1000.5,2100.3145625)(1016.5,2144.6456875)(1032.5,2189.60025)(1048.5,2235.2554375)(1064.5,2281.8241875)(1080.5,2329.6734375)(1096.5,2379.1441875)(1112.5,2429.9625)(1128.5,2481.816375)(1144.5,2534.979875)(1160.5,2589.3324375)(1176.5,2645.0780625)(1192.5,2701.892125)(1208.5,2759.7080625)(1224.5,2818.4853125)(1240.5,2878.14725)(1256.5,2938.6613125)(1272.5,2999.7675)(1288.5,3061.7365)(1304.5,3124.550125)(1320.5,3188.13575)(1336.5,3252.6558125)(1352.5,3318.13175)(1368.5,3384.681875)(1384.5,3451.851)(1400.5,3519.970625)(1416.5,3589.426375)(1432.5,3660.527)(1448.5,3733.2529375)(1464.5,3807.681625)(1480.5,3883.4769375)(1496.5,3961.36525)(1512.5,4041.9930625)(1528.5,4126.6176875)(1544.5,4219.805375)(1560.5,4326.948125)(1576.5,4449.7968125)(1592.5,4610.8235625)(1601.5,4744.1385)(1604,4795.597)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,1.042)(7.5,10.421857142857142)(21.5,29.635571428571428)(35.5,50.016357142857146)(49.5,71.21285714285715)(63.5,93.25821428571429)(77.5,115.84392857142856)(91.5,138.86014285714288)(105.5,162.4882142857143)(119.5,186.6072142857143)(133.5,211.14664285714287)(147.5,236.0525714285714)(161.5,261.4626428571429)(175.5,287.39128571428574)(189.5,313.71728571428577)(203.5,340.4631428571428)(217.5,367.5703571428572)(231.5,395.1613571428572)(245.5,423.17785714285714)(259.5,451.473)(273.5,480.01521428571425)(287.5,508.8493571428572)(301.5,537.9797142857143)(315.5,567.4725)(329.5,597.379)(343.5,627.7412857142857)(357.5,658.6113571428572)(371.5,689.8423571428572)(385.5,721.4651428571428)(399.5,753.5415)(413.5,786.0342857142857)(427.5,818.8502857142856)(441.5,852.0047857142857)(455.5,885.4851428571428)(469.5,919.4435)(483.5,953.7673571428571)(497.5,988.4813571428572)(511.5,1023.6364285714285)(525.5,1059.1977857142856)(539.5,1095.152357142857)(553.5,1131.447857142857)(567.5,1168.1000714285713)(581.5,1205.2960714285714)(595.5,1243.024642857143)(609.5,1281.2957857142858)(623.5,1320.0607857142857)(637.5,1359.327357142857)(651.5,1398.982)(665.5,1439.111642857143)(679.5,1479.8170714285714)(693.5,1521.0342857142857)(707.5,1562.7634285714287)(721.5,1605.0646428571429)(735.5,1647.8864285714287)(749.5,1691.2777857142858)(763.5,1735.378642857143)(777.5,1779.983642857143)(791.5,1825.111)(805.5,1870.7785714285715)(819.5,1917.3739285714287)(833.5,1964.793142857143)(847.5,2013.078857142857)(861.5,2062.0352857142857)(875.5,2111.9066428571427)(889.5,2162.6124285714286)(903.5,2214.2143571428574)(917.5,2266.915285714286)(931.5,2320.8507142857143)(945.5,2375.982571428571)(959.5,2432.2053571428573)(973.5,2489.9445)(987.5,2549.594642857143)(1001.5,2611.896214285714)(1015.5,2677.7935714285713)(1029.5,2746.8089285714286)(1043.5,2819.2254285714284)(1057.5,2895.4688571428574)(1071.5,2976.7548571428574)(1085.5,3063.5255714285713)(1099.5,3156.2792142857143)(1113.5,3256.008714285714)(1127.5,3361.891214285714)(1141.5,3475.924785714286)(1155.5,3596.808)(1169.5,3725.2726428571427)(1183.5,3863.3013571428573)(1197.5,4012.4511428571427)(1211.5,4173.714785714286)(1225.5,4349.4121428571425)(1239.5,4536.0506428571425)(1253.5,4733.094928571428)(1267.5,4940.848285714285)(1281.5,5164.210285714285)(1295.5,5406.3664285714285)(1309.5,5666.005357142857)(1323.5,5947.754357142857)(1337.5,6272.523357142857)(1351.5,6649.797214285714)(1365.5,7108.828785714285)(1377.5,7661.63)(1384,7972.953)};
\addlegendentry{Ostrich}

\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.007)(7,0.08584615384615384)(20,0.305)(33,0.6530769230769231)(46,1.1311538461538462)(59,1.6853846153846155)(72,2.2931538461538463)(85,2.9566923076923075)(98,3.686230769230769)(111,4.479461538461538)(124,5.35023076923077)(137,6.312153846153846)(150,7.359153846153846)(163,8.470615384615385)(176,9.657692307692308)(189,10.93923076923077)(202,12.307615384615385)(215,13.752153846153846)(228,15.272)(241,16.85884615384615)(254,18.51792307692308)(267,20.254153846153848)(280,22.07076923076923)(293,24.015)(306,26.139692307692307)(319,28.53876923076923)(332,31.162307692307692)(345,34.02146153846154)(358,37.16815384615384)(371,40.49684615384616)(384,44.06376923076923)(397,47.8823076923077)(410,51.92207692307692)(423,56.27353846153846)(436,60.88161538461538)(449,65.64184615384616)(462,70.59938461538461)(475,75.76446153846153)(488,81.06407692307693)(501,86.49453846153847)(514,92.05415384615384)(527,97.75361538461539)(540,103.56776923076923)(553,109.49507692307692)(566,115.5783846153846)(579,121.86215384615384)(592,128.30061538461538)(605,134.89915384615384)(618,141.65592307692307)(631,148.56823076923078)(644,155.6096923076923)(657,162.78415384615386)(670,170.11546153846155)(683,177.60553846153846)(696,185.30261538461536)(709,193.18292307692306)(722,201.2533076923077)(735,209.55253846153846)(748,218.15223076923078)(761,227.18307692307692)(774,236.63753846153847)(787,246.61015384615385)(800,257.15207692307695)(813,268.3446923076923)(826,280.29207692307693)(839,293.0210769230769)(852,306.7554615384616)(865,321.323)(878,336.84784615384615)(891,353.35807692307696)(904,370.93038461538464)(917,389.3006923076923)(930,408.32023076923076)(943,428.23615384615385)(956,449.51346153846157)(969,472.04553846153846)(982,496.191)(995,523.0977692307692)(1008,553.4396923076922)(1021,586.0476923076923)(1034,621.8947692307693)(1047,661.3595384615385)(1060,704.5181538461538)(1073,751.4005384615385)(1086,802.835)(1099,862.5549230769232)(1112,931.1657692307692)(1125,1009.1157692307693)(1138,1101.7934615384615)(1151,1230.164076923077)(1164,1424.009923076923)(1177,1703.8506923076923)(1190,2059.8683846153845)(1203,2464.8026923076923)(1216,2921.014769230769)(1229,3424.7666153846153)(1241.5,3993.243)(1249,4346.266)};
\addlegendentry{CVC5}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.017)(5,0.13355555555555554)(14,0.37611111111111106)(23,0.639)(32,0.9286666666666666)(41,1.2483333333333333)(50,1.5871111111111111)(59,1.942777777777778)(68,2.3183333333333334)(77,2.710444444444444)(86,3.1183333333333336)(95,3.5474444444444444)(104,3.9951111111111115)(113,4.454666666666667)(122,4.926111111111111)(131,5.410111111111111)(140,5.907444444444445)(149,6.420333333333333)(158,6.947111111111111)(167,7.487666666666667)(176,8.041777777777778)(185,8.613666666666665)(194,9.2)(203,9.802666666666665)(212,10.42)(221,11.05711111111111)(230,11.704777777777778)(239,12.366333333333333)(248,13.042)(257,13.737)(266,14.446666666666665)(275,15.176222222222222)(284,15.924)(293,16.69366666666667)(302,17.484333333333332)(311,18.304)(320,19.147333333333332)(329,20.019777777777776)(338,20.91433333333333)(347,21.834222222222223)(356,22.779333333333334)(365,23.74577777777778)(374,24.738777777777777)(383,25.758666666666667)(392,26.808777777777777)(401,27.893666666666668)(410,29.01788888888889)(419,30.171666666666667)(428,31.351)(437,32.574)(446,33.85466666666667)(455,35.18366666666667)(464,36.55377777777778)(473,37.970888888888894)(482,39.43866666666666)(491,40.962111111111106)(500,42.56055555555555)(509,44.21877777777778)(518,45.95133333333334)(527,47.779111111111106)(536,49.68177777777778)(545,51.67422222222222)(554,53.775333333333336)(563,55.97422222222222)(572,58.306666666666665)(581,60.77277777777778)(590,63.406666666666666)(599,66.23022222222222)(608,69.23144444444443)(617,72.49055555555556)(626,76.05744444444444)(635,79.90144444444444)(644,84.237)(653,88.88711111111111)(662,94.08977777777778)(671,99.92533333333333)(680,106.4301111111111)(689,114.00422222222223)(698,122.53)(707,132.107)(716,143.86844444444444)(725,158.1821111111111)(734,174.91488888888887)(743,194.845)(752,218.70155555555556)(761,248.3372222222222)(770,290.79277777777776)(779,348.5783333333333)(788,417.857)(797,510.13644444444446)(806,641.939)(815,831.2733333333334)(824,1073.363111111111)(833,1364.137888888889)(842,1704.5152222222223)(851,2110.631888888889)(858,2475.6972)(862,2647.177)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.015)(7,0.13392307692307692)(20,0.4753076923076923)(33,1.0751538461538461)(46,2.187769230769231)(59,3.741076923076923)(72,5.534846153846154)(85,7.5522307692307695)(98,9.893307692307692)(111,12.54646153846154)(124,15.76876923076923)(137,19.567153846153847)(150,23.959615384615383)(163,28.68123076923077)(176,33.70907692307692)(189,39.13515384615384)(202,45.02061538461538)(215,51.28153846153846)(228,57.95976923076923)(241,64.94292307692308)(254,72.15346153846153)(267,79.66346153846153)(280,87.47692307692307)(293,95.62438461538461)(306,104.04515384615384)(319,112.723)(332,121.75030769230769)(345,131.2003076923077)(358,140.9993076923077)(371,151.17884615384617)(384,161.71284615384616)(397,172.62730769230768)(410,184.0403076923077)(423,195.81446153846153)(436,208.03846153846152)(449,220.69846153846154)(462,233.92207692307693)(475,247.7913076923077)(488,262.59430769230767)(501,278.44446153846155)(514,295.05923076923074)(527,312.72138461538464)(540,331.90353846153846)(553,352.35630769230767)(566,373.94807692307694)(579,396.50646153846156)(592,419.9123846153846)(605,444.309)(618,470.0917692307693)(631,497.68453846153847)(644,526.4123076923078)(657,557.0483846153846)(670,590.1912307692307)(683,624.9178461538461)(696,661.1273076923078)(709,699.3653076923077)(722,740.2164615384615)(735,783.0497692307692)(748,827.2873846153847)(761,873.849)(774,923.3921538461539)(787,974.9501538461539)(800,1029.0558461538462)(813,1086.2576153846155)(826,1147.4029230769231)(839,1212.1193846153844)(852,1281.6894615384615)(865,1356.7432307692306)(878,1437.5274615384615)(891,1525.3787692307692)(904,1622.077923076923)(917,1726.5867692307693)(930,1841.5621538461537)(943,1966.1236923076922)(956,2097.5923076923077)(969,2237.991846153846)(982,2388.815846153846)(995,2550.726153846154)(1008,2724.7893076923074)(1021,2912.461)(1034,3108.7013846153845)(1047,3318.6526923076926)(1060,3540.098)(1073,3780.940923076923)(1086,4046.5943846153846)(1099,4341.672692307692)(1112,4661.215)(1125,5005.762769230769)(1138,5382.683384615385)(1151,5793.749307692308)(1164,6244.779692307692)(1177,6752.641307692308)(1190,7313.696153846154)(1203,7921.302461538462)(1216,8582.782846153847)(1226,9128.86)(1231,9358.232)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.007)(8.5,0.0758125)(24.5,0.263125)(40.5,0.515125)(56.5,0.7930625)(72.5,1.0844375)(88.5,1.3903125)(104.5,1.71125)(120.5,2.04725)(136.5,2.397)(152.5,2.7555625)(168.5,3.12575)(184.5,3.508)(200.5,3.9005)(216.5,4.30275)(232.5,4.7171875)(248.5,5.1435)(264.5,5.580375)(280.5,6.032125)(296.5,6.4955)(312.5,6.9651875)(328.5,7.4506875)(344.5,7.9521875)(360.5,8.4674375)(376.5,8.9958125)(392.5,9.537)(408.5,10.0895)(424.5,10.658)(440.5,11.238875)(456.5,11.83225)(472.5,12.4380625)(488.5,13.0555)(504.5,13.6829375)(520.5,14.3269375)(536.5,14.9929375)(552.5,15.680375)(568.5,16.39425)(584.5,17.128375)(600.5,17.8755)(616.5,18.6303125)(632.5,19.3979375)(648.5,20.1785625)(664.5,20.972)(680.5,21.78225)(696.5,22.6196875)(712.5,23.4789375)(728.5,24.355875)(744.5,25.24875)(760.5,26.1598125)(776.5,27.08725)(792.5,28.0455625)(808.5,29.0368125)(824.5,30.0645625)(840.5,31.1379375)(856.5,32.2518125)(872.5,33.4005)(888.5,34.5898125)(904.5,35.821375)(920.5,37.097625)(936.5,38.4284375)(952.5,39.8054375)(968.5,41.2453125)(984.5,42.7475)(1000.5,44.3534375)(1016.5,46.0835)(1032.5,47.924875)(1048.5,49.8915625)(1064.5,52.0588125)(1080.5,54.4555625)(1096.5,57.04125)(1112.5,59.751375)(1128.5,62.618375)(1144.5,65.6106875)(1160.5,68.7401875)(1176.5,72.18275)(1192.5,75.974)(1208.5,80.25575)(1224.5,85.5225625)(1240.5,91.56425)(1256.5,98.3388125)(1272.5,106.0435)(1288.5,114.47225)(1304.5,123.289375)(1320.5,132.7138125)(1336.5,142.9955625)(1352.5,154.5948125)(1368.5,168.214)(1384.5,184.7535625)(1400.5,207.01025)(1416.5,235.7268125)(1432.5,270.52575)(1448.5,318.257)(1464.5,393.0419375)(1480.5,494.505875)(1496.5,608.450625)(1512.5,744.9885)(1528.5,957.6901875)(1544.5,1302.16275)(1560.5,1835.9473125)(1570.5,2309.625)(1574,2451.289)};
\addlegendentry{Z3str3RE}

\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.016)(2,0.053)(5,0.111)(8,0.17233333333333334)(11,0.24133333333333334)(14,0.35633333333333334)(17,0.532)(20,0.7983333333333333)(23,1.095)(26,1.5226666666666668)(29,2.1523333333333334)(32,2.9396666666666667)(35,3.9976666666666665)(38,5.294666666666667)(41,6.714)(44,8.258666666666667)(47,9.852333333333334)(50,11.533666666666665)(53,13.339333333333334)(56,15.281333333333334)(59,17.312)(62,19.477666666666668)(65,21.76233333333333)(68,24.18)(71,26.796)(74,29.68733333333333)(77,32.67433333333333)(80,35.758)(83,38.97)(86,42.28933333333334)(89,45.894333333333336)(92,49.85166666666667)(95,53.928333333333335)(98,58.059)(101,62.247)(104,66.66433333333333)(107,71.34166666666667)(110,76.268)(113,81.44766666666668)(116,86.93366666666667)(119,92.68)(122,98.49866666666667)(125,104.398)(128,110.51466666666667)(131,116.94566666666667)(134,123.67666666666668)(137,131.009)(140,138.821)(143,146.862)(146,155.07933333333335)(149,163.47833333333335)(152,172.06766666666667)(155,180.78866666666664)(158,190.297)(161,200.83833333333334)(164,211.90466666666666)(167,223.99133333333333)(170,236.898)(173,250.152)(176,263.98466666666667)(179,278.498)(182,293.6046666666667)(185,309.477)(188,326.655)(191,344.77)(194,363.702)(197,382.9943333333333)(200,402.6673333333333)(203,422.945)(206,444.157)(209,467.0073333333333)(212,491.593)(215,517.5033333333333)(218,544.213)(221,571.7546666666666)(224,601.098)(227,631.7703333333334)(230,663.7593333333334)(233,697.4513333333334)(236,732.3156666666666)(239,768.4563333333334)(242,805.529)(245,843.917)(248,883.4013333333334)(251,926.3146666666667)(254,974.039)(257,1029.1116666666667)(260,1089.092)(263,1154.1753333333334)(266,1228.3816666666667)(269,1306.6253333333332)(272,1392.2936666666667)(275,1481.7986666666668)(278,1575.6423333333332)(281,1676.5096666666668)(284,1782.0873333333332)(287,1895.8256666666668)(290,2017.9586666666667)(293,2152.2976666666664)(296,2303.433)(299,2464.662)(302,2630.6766666666667)(305,2799.423)(308,2973.517)(311,3092.419)};
\addlegendentry{Z3-Trau}

\path[name path=axisOstrichCEA] (axis cs:0,0) -- (axis cs:1604,0);
\addplot [thick,color=colourOstrichCEA,fill=colourOstrichCEA,fill opacity=0.1] fill between [of=pathOstrichCEA and axisOstrichCEA];
\path[name path=axisOstrich] (axis cs:0,0) -- (axis cs:1384,0);
\addplot [thick,color=colourOstrich,fill=colourOstrich,fill opacity=0.1] fill between [of=pathOstrich and axisOstrich];
\path[name path=axisCVC5] (axis cs:0,0) -- (axis cs:1249,0);
\addplot [thick,color=colourCVC5,fill=colourCVC5,fill opacity=0.1] fill between [of=pathCVC5 and axisCVC5];
\path[name path=axisZ3str3] (axis cs:0,0) -- (axis cs:862,0);
\addplot [thick,color=colourZ3str3,fill=colourZ3str3,fill opacity=0.1] fill between [of=pathZ3str3 and axisZ3str3];
\path[name path=axisZ3seq] (axis cs:0,0) -- (axis cs:1231,0);
\addplot [thick,color=colourZ3seq,fill=colourZ3seq,fill opacity=0.1] fill between [of=pathZ3seq and axisZ3seq];
\path[name path=axisZ3str3RE] (axis cs:0,0) -- (axis cs:1574,0);
\addplot [thick,color=colourZ3str3RE,fill=colourZ3str3RE,fill opacity=0.1] fill between [of=pathZ3str3RE and axisZ3str3RE];
\path[name path=axisZ3-Trau] (axis cs:0,0) -- (axis cs:311,0);
\addplot [thick,color=colourZ3-Trau,fill=colourZ3-Trau,fill opacity=0.1] fill between [of=pathZ3-Trau and axisZ3-Trau];
\end{axis}\end{tikzpicture}}

\end{document}

### 2023-04-11 2023-1-19/figures/cactus_plot_regexlib.tex
atva2023 first version

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourOstrichCEA}{HTML}{25333D}
\definecolor{colourCVC5}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=regexlib,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.326)(8.5,14.001375)(24.5,39.800875)(40.5,67.09)(56.5,95.3169375)(72.5,124.4550625)(88.5,154.267375)(104.5,184.69425)(120.5,215.657)(136.5,247.035125)(152.5,278.7906875)(168.5,311.0410625)(184.5,343.8286875)(200.5,377.011375)(216.5,410.68275)(232.5,444.867875)(248.5,479.5120625)(264.5,514.5951875)(280.5,550.083625)(296.5,585.994125)(312.5,622.261875)(328.5,658.8564375)(344.5,695.7899375)(360.5,733.01425)(376.5,770.5569375)(392.5,808.4133125)(408.5,846.6525625)(424.5,885.256)(440.5,924.2085625)(456.5,963.6601875)(472.5,1003.5794375)(488.5,1043.8909375)(504.5,1084.5918125)(520.5,1125.6925625)(536.5,1167.1688125)(552.5,1209.008)(568.5,1251.1431875)(584.5,1293.6194375)(600.5,1336.5265625)(616.5,1379.7884375)(632.5,1423.3959375)(648.5,1467.445375)(664.5,1512.1114375)(680.5,1557.229625)(696.5,1602.6933125)(712.5,1648.5414375)(728.5,1694.74525)(744.5,1741.259875)(760.5,1788.104625)(776.5,1835.441375)(792.5,1883.3281875)(808.5,1931.6915625)(824.5,1980.545125)(840.5,2029.794125)(856.5,2079.47)(872.5,2129.7085625)(888.5,2180.5180625)(904.5,2232.03075)(920.5,2284.4146875)(936.5,2337.7085)(952.5,2391.664625)(968.5,2446.13225)(984.5,2501.088125)(1000.5,2556.4926875)(1016.5,2612.4775)(1032.5,2669.06175)(1048.5,2726.1491875)(1064.5,2783.9013125)(1080.5,2842.3911875)(1096.5,2901.65625)(1112.5,2961.713625)(1128.5,3022.462)(1144.5,3084.2588125)(1160.5,3146.9798125)(1176.5,3210.752125)(1192.5,3275.4954375)(1208.5,3341.271875)(1224.5,3408.4449375)(1240.5,3476.9365625)(1256.5,3546.931625)(1272.5,3618.58925)(1288.5,3691.8859375)(1304.5,3767.448375)(1320.5,3845.036625)(1336.5,3924.75)(1352.5,4006.6775)(1368.5,4090.948625)(1384.5,4177.0058125)(1400.5,4266.37675)(1416.5,4358.8839375)(1432.5,4454.4639375)(1448.5,4553.3179375)(1464.5,4656.1215625)(1480.5,4765.12675)(1496.5,4880.6024375)(1512.5,5003.2408125)(1528.5,5136.673125)(1544.5,5283.0321875)(1560.5,5444.2958125)(1576.5,5642.1679375)(1592.5,5967.94825)(1602,6241.055)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(8.5,0.0501875)(24.5,0.1841875)(40.5,0.385375)(56.5,0.63275)(72.5,0.9063125)(88.5,1.2073125)(104.5,1.53075)(120.5,1.878625)(136.5,2.248)(152.5,2.6435)(168.5,3.0511875)(184.5,3.4775625)(200.5,3.919)(216.5,4.3756875)(232.5,4.8543125)(248.5,5.36475)(264.5,5.91125)(280.5,6.499375)(296.5,7.1506875)(312.5,7.8543125)(328.5,8.594375)(344.5,9.3725)(360.5,10.1935625)(376.5,11.092875)(392.5,12.035125)(408.5,13.0169375)(424.5,14.058375)(440.5,15.1575625)(456.5,16.3101875)(472.5,17.5235)(488.5,18.79075)(504.5,20.1346875)(520.5,21.5568125)(536.5,23.0485)(552.5,24.6221875)(568.5,26.2756875)(584.5,28.0125625)(600.5,29.863375)(616.5,31.8353125)(632.5,33.9231875)(648.5,36.124625)(664.5,38.4406875)(680.5,40.8851875)(696.5,43.4551875)(712.5,46.18625)(728.5,49.20325)(744.5,52.4388125)(760.5,55.897625)(776.5,59.6255)(792.5,63.556125)(808.5,67.7344375)(824.5,72.17275)(840.5,76.87375)(856.5,81.881625)(872.5,87.2705625)(888.5,92.9146875)(904.5,98.791)(920.5,104.930125)(936.5,111.3364375)(952.5,118.0683125)(968.5,125.098375)(984.5,132.4871875)(1000.5,140.3285625)(1016.5,148.5753125)(1032.5,157.201)(1048.5,166.2395)(1064.5,175.6414375)(1080.5,185.51025)(1096.5,195.957375)(1112.5,207.0698125)(1128.5,218.7384375)(1144.5,231.084125)(1160.5,244.2318125)(1176.5,257.92525)(1192.5,272.16775)(1208.5,287.037)(1224.5,302.7649375)(1240.5,319.7085625)(1256.5,337.873375)(1272.5,357.1653125)(1288.5,377.8138125)(1304.5,399.751125)(1320.5,424.0613125)(1336.5,450.661375)(1352.5,478.92)(1368.5,509.38125)(1384.5,543.107)(1400.5,581.489375)(1416.5,625.1093125)(1432.5,675.3388125)(1448.5,738.061)(1464.5,823.3106875)(1480.5,947.367625)(1496.5,1193.47425)(1512.5,1639.0449375)(1525,2121.9135555555554)(1531,2376.002)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,1.017)(8,10.258933333333333)(23,29.255599999999998)(38,50.394800000000004)(53,72.92853333333333)(68,96.32026666666667)(83,120.54106666666667)(98,145.43706666666668)(113,170.85453333333334)(128,196.90246666666667)(143,223.42426666666665)(158,250.6794)(173,278.59159999999997)(188,307.04659999999996)(203,336.0550666666667)(218,365.4665333333333)(233,395.2475333333333)(248,425.3532)(263,455.8623333333333)(278,486.82626666666664)(293,518.2761333333334)(308,550.2016666666666)(323,582.5965333333334)(338,615.5299333333334)(353,648.8835333333333)(368,682.6476)(383,716.8438000000001)(398,751.3936)(413,786.4327333333333)(428,821.8758)(443,857.6266666666667)(458,893.7378666666667)(473,930.2567333333333)(488,967.1976)(503,1004.5210666666667)(518,1042.2291333333333)(533,1080.4326)(548,1119.0616666666667)(563,1158.132)(578,1197.6022666666665)(593,1237.5477333333333)(608,1278.0738666666666)(623,1319.0354)(638,1360.3044666666665)(653,1401.9102)(668,1443.9781333333333)(683,1486.5155333333335)(698,1529.4671333333333)(713,1573.0057333333334)(728,1617.0829333333334)(743,1661.8119333333334)(758,1707.0376)(773,1752.8307333333335)(788,1799.0442666666665)(803,1845.8358666666668)(818,1893.2626)(833,1941.298)(848,1990.1431333333333)(863,2039.6957333333335)(878,2089.9846666666667)(893,2141.0992666666666)(908,2193.0147333333334)(923,2245.761466666667)(938,2299.109466666667)(953,2353.2702666666664)(968,2408.4814666666666)(983,2464.6888)(998,2521.7824)(1013,2579.9236666666666)(1028,2639.587466666667)(1043,2701.1523333333334)(1058,2764.0695333333333)(1073,2827.9558666666667)(1088,2893.3823333333335)(1103,2960.3417999999997)(1118,3029.4202666666665)(1133,3100.2347999999997)(1148,3173.076866666667)(1163,3248.1202000000003)(1178,3326.137866666667)(1193,3407.703)(1208,3491.8776666666663)(1223,3578.656933333333)(1238,3668.5506)(1253,3762.1326666666664)(1268,3859.274933333333)(1283,3961.9732666666664)(1298,4070.4924666666666)(1313,4186.787066666667)(1328,4310.513400000001)(1343,4445.3554)(1358,4594.592466666667)(1373,4759.808933333334)(1388,4944.383400000001)(1403,5149.614333333333)(1418,5387.352599999999)(1433,5664.111533333333)(1448,5990.5318)(1463,6394.039400000001)(1478,6895.506266666666)(1493,7542.774266666666)(1502,7966.798)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.014)(8,0.1492666666666667)(23,0.43839999999999996)(38,0.7554)(53,1.0912666666666666)(68,1.446)(83,1.8062)(98,2.176)(113,2.551)(128,2.929)(143,3.318)(158,3.7084)(173,4.109)(188,4.517)(203,4.936)(218,5.362066666666666)(233,5.7984)(248,6.246666666666667)(263,6.708)(278,7.1781999999999995)(293,7.658066666666667)(308,8.147)(323,8.6444)(338,9.153)(353,9.669066666666668)(368,10.1942)(383,10.729)(398,11.269666666666666)(413,11.821)(428,12.376666666666667)(443,12.943)(458,13.514)(473,14.0964)(488,14.692)(503,15.2944)(518,15.9082)(533,16.533)(548,17.166666666666668)(563,17.8124)(578,18.47)(593,19.130666666666666)(608,19.802)(623,20.48)(638,21.169)(653,21.8642)(668,22.576)(683,23.3012)(698,24.039)(713,24.7904)(728,25.5542)(743,26.329066666666666)(758,27.1184)(773,27.927)(788,28.7524)(803,29.591866666666665)(818,30.448)(833,31.318)(848,32.201)(863,33.09986666666667)(878,34.01673333333333)(893,34.955666666666666)(908,35.91266666666667)(923,36.887)(938,37.8816)(953,38.8984)(968,39.93533333333333)(983,41.0048)(998,42.1114)(1013,43.2494)(1028,44.419066666666666)(1043,45.62166666666666)(1058,46.864466666666665)(1073,48.1382)(1088,49.4416)(1103,50.77926666666667)(1118,52.1594)(1133,53.60013333333333)(1148,55.10326666666667)(1163,56.676)(1178,58.32373333333333)(1193,60.0458)(1208,61.842400000000005)(1223,63.705933333333334)(1238,65.68766666666667)(1253,67.79246666666666)(1268,70.0094)(1283,72.42713333333333)(1298,75.1118)(1313,78.03226666666666)(1328,81.21066666666667)(1343,84.72706666666667)(1358,88.56126666666667)(1373,93.02126666666666)(1388,98.26266666666668)(1403,104.86593333333333)(1418,113.51339999999999)(1433,124.53553333333333)(1448,142.9748)(1463,195.25526666666667)(1473.5,343.9191666666667)(1478,471.791)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.014)(8.5,0.1705625)(24.5,0.5270625)(40.5,0.9435)(56.5,1.411375)(72.5,1.9261875)(88.5,2.471375)(104.5,3.0486875)(120.5,3.6491875)(136.5,4.26925)(152.5,4.9183125)(168.5,5.59575)(184.5,6.2953125)(200.5,7.0183125)(216.5,7.7696875)(232.5,8.552625)(248.5,9.361625)(264.5,10.20875)(280.5,11.08875)(296.5,11.9946875)(312.5,12.9349375)(328.5,13.899875)(344.5,14.886625)(360.5,15.894625)(376.5,16.93)(392.5,18.009)(408.5,19.1270625)(424.5,20.2855625)(440.5,21.4935)(456.5,22.751125)(472.5,24.069375)(488.5,25.446875)(504.5,26.8915)(520.5,28.4119375)(536.5,30.015375)(552.5,31.7089375)(568.5,33.4641875)(584.5,35.2725)(600.5,37.1615)(616.5,39.151125)(632.5,41.2473125)(648.5,43.431625)(664.5,45.6884375)(680.5,48.03575)(696.5,50.4545)(712.5,52.9450625)(728.5,55.5413125)(744.5,58.2293125)(760.5,60.9836875)(776.5,63.813375)(792.5,66.7405)(808.5,69.76075)(824.5,72.8876875)(840.5,76.128)(856.5,79.4839375)(872.5,82.9761875)(888.5,86.62225)(904.5,90.3834375)(920.5,94.26825)(936.5,98.3461875)(952.5,102.5914375)(968.5,107.029625)(984.5,111.6445625)(1000.5,116.4698125)(1016.5,121.504625)(1032.5,126.7716875)(1048.5,132.2453125)(1064.5,137.9896875)(1080.5,144.0614375)(1096.5,150.38)(1112.5,156.9101875)(1128.5,163.803625)(1144.5,171.048375)(1160.5,178.675875)(1176.5,186.5573125)(1192.5,194.7738125)(1208.5,203.287375)(1224.5,212.0685)(1240.5,221.080125)(1256.5,230.4013125)(1272.5,240.2630625)(1288.5,250.769125)(1304.5,261.9256875)(1320.5,273.955125)(1336.5,286.6981875)(1352.5,300.027625)(1368.5,314.1886875)(1384.5,329.4320625)(1400.5,345.72025)(1416.5,363.0874375)(1432.5,381.555625)(1448.5,401.5385)(1464.5,423.8074375)(1480.5,448.4118125)(1496.5,476.286125)(1512.5,510.4356875)(1528.5,553.1431875)(1544.5,607.709625)(1560.5,678.581375)(1576.5,800.2424375)(1587,950.0282)(1591,1061.191)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.005)(8.5,0.0531875)(24.5,0.1518125)(40.5,0.2625)(56.5,0.3745)(72.5,0.4865)(88.5,0.5985)(104.5,0.7105)(120.5,0.8253125)(136.5,0.952)(152.5,1.08)(168.5,1.208)(184.5,1.336)(200.5,1.464375)(216.5,1.6035)(232.5,1.7475)(248.5,1.8915)(264.5,2.0355)(280.5,2.1795)(296.5,2.3235)(312.5,2.4675)(328.5,2.6116875)(344.5,2.766)(360.5,2.926)(376.5,3.086)(392.5,3.246)(408.5,3.406)(424.5,3.566)(440.5,3.726)(456.5,3.8873125)(472.5,4.0605)(488.5,4.2365)(504.5,4.4125)(520.5,4.5885)(536.5,4.7645)(552.5,4.9439375)(568.5,5.135)(584.5,5.327)(600.5,5.519)(616.5,5.7175625)(632.5,5.9255)(648.5,6.134125)(664.5,6.354)(680.5,6.5789375)(696.5,6.8155)(712.5,7.056125)(728.5,7.308)(744.5,7.568125)(760.5,7.840125)(776.5,8.124)(792.5,8.4185625)(808.5,8.7234375)(824.5,9.04)(840.5,9.3665625)(856.5,9.7038125)(872.5,10.053)(888.5,10.4084375)(904.5,10.7755)(920.5,11.147625)(936.5,11.5323125)(952.5,11.9296875)(968.5,12.340625)(984.5,12.7685)(1000.5,13.2081875)(1016.5,13.66875)(1032.5,14.14875)(1048.5,14.64475)(1064.5,15.15725)(1080.5,15.691375)(1096.5,16.2514375)(1112.5,16.8374375)(1128.5,17.4513125)(1144.5,18.10075)(1160.5,18.782875)(1176.5,19.5125)(1192.5,20.281875)(1208.5,21.093125)(1224.5,21.9540625)(1240.5,22.867)(1256.5,23.8339375)(1272.5,24.876125)(1288.5,26.007125)(1304.5,27.2279375)(1320.5,28.564875)(1336.5,29.9903125)(1352.5,31.529875)(1368.5,33.237)(1384.5,35.1899375)(1400.5,37.4680625)(1416.5,40.07125)(1432.5,43.1341875)(1448.5,46.8099375)(1464.5,51.341)(1480.5,57.03675)(1496.5,64.4295)(1512.5,73.6899375)(1528.5,86.0960625)(1544.5,108.3425)(1560.5,174.1435625)(1569.5,260.0555)(1572,300.23)};
\addlegendentry{Z3str3RE}

\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.014)(5.5,0.0965)(15.5,0.24659999999999999)(25.5,0.5291)(35.5,1.7757)(45.5,3.2819000000000003)(55.5,4.8925)(65.5,6.6395)(75.5,8.5756)(85.5,10.7695)(95.5,13.3338)(105.5,16.0888)(115.5,18.911099999999998)(125.5,21.776799999999998)(135.5,24.681)(145.5,27.6301)(155.5,30.6199)(165.5,33.670199999999994)(175.5,36.7772)(185.5,39.9617)(195.5,43.211400000000005)(205.5,46.5163)(215.5,49.8973)(225.5,53.3431)(235.5,56.839)(245.5,60.3826)(255.5,63.9905)(265.5,67.68169999999999)(275.5,71.49210000000001)(285.5,75.4175)(295.5,79.4315)(305.5,83.5275)(315.5,87.7416)(325.5,92.0531)(335.5,96.4757)(345.5,101.06960000000001)(355.5,105.7476)(365.5,110.49980000000001)(375.5,115.3315)(385.5,120.26480000000001)(395.5,125.32130000000001)(405.5,130.55780000000001)(415.5,135.9472)(425.5,141.4926)(435.5,147.1716)(445.5,152.968)(455.5,158.89479999999998)(465.5,164.9966)(475.5,171.2354)(485.5,177.6876)(495.5,184.32629999999997)(505.5,191.2884)(515.5,198.55870000000002)(525.5,206.118)(535.5,213.86720000000003)(545.5,221.7994)(555.5,229.9578)(565.5,238.4017)(575.5,247.17370000000003)(585.5,256.3306)(595.5,265.9233)(605.5,275.932)(615.5,286.358)(625.5,297.2522)(635.5,308.8544)(645.5,321.24490000000003)(655.5,334.15770000000003)(665.5,347.7744)(675.5,362.2491)(685.5,377.95820000000003)(695.5,394.631)(705.5,412.767)(715.5,431.72229999999996)(725.5,451.7528)(735.5,473.7269)(745.5,497.888)(755.5,523.4656)(765.5,550.4038)(775.5,579.6903000000001)(785.5,611.273)(795.5,645.323)(805.5,681.6165)(815.5,720.9826999999999)(825.5,761.813)(835.5,805.1531)(845.5,853.2948)(855.5,907.36)(865.5,969.3392)(875.5,1043.5174)(885.5,1131.0648999999999)(895.5,1238.9723999999999)(905.5,1375.8621)(915.5,1533.0866)(925.5,1712.4778000000001)(935.5,1928.2462)(945.5,2203.0395)(955.5,2557.4988)(963,2921.2174)(967,3095.75)};
\addlegendentry{Z3-Trau}

\path[name path=axisOstrichCEA] (axis cs:0,0) -- (axis cs:1602,0);
\addplot [thick,color=colourOstrichCEA,fill=colourOstrichCEA,fill opacity=0.1] fill between [of=pathOstrichCEA and axisOstrichCEA];
\path[name path=axisCVC5] (axis cs:0,0) -- (axis cs:1531,0);
\addplot [thick,color=colourCVC5,fill=colourCVC5,fill opacity=0.1] fill between [of=pathCVC5 and axisCVC5];
\path[name path=axisOstrich] (axis cs:0,0) -- (axis cs:1502,0);
\addplot [thick,color=colourOstrich,fill=colourOstrich,fill opacity=0.1] fill between [of=pathOstrich and axisOstrich];
\path[name path=axisZ3str3] (axis cs:0,0) -- (axis cs:1478,0);
\addplot [thick,color=colourZ3str3,fill=colourZ3str3,fill opacity=0.1] fill between [of=pathZ3str3 and axisZ3str3];
\path[name path=axisZ3seq] (axis cs:0,0) -- (axis cs:1591,0);
\addplot [thick,color=colourZ3seq,fill=colourZ3seq,fill opacity=0.1] fill between [of=pathZ3seq and axisZ3seq];
\path[name path=axisZ3str3RE] (axis cs:0,0) -- (axis cs:1572,0);
\addplot [thick,color=colourZ3str3RE,fill=colourZ3str3RE,fill opacity=0.1] fill between [of=pathZ3str3RE and axisZ3str3RE];
\path[name path=axisZ3-Trau] (axis cs:0,0) -- (axis cs:967,0);
\addplot [thick,color=colourZ3-Trau,fill=colourZ3-Trau,fill opacity=0.1] fill between [of=pathZ3-Trau and axisZ3-Trau];
\end{axis}\end{tikzpicture}}

\end{document}

### 2023-04-11 2023-1-19/figures/cactus_plot_stackoverflow.tex
atva2023 first version

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=stackoverflow,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(167.5,0.7233143712574851)(501.5,2.424832335329341)(835.5,4.471230538922155)(1169.5,7.107095808383233)(1503.5,10.389062874251497)(1837.5,14.099278443113771)(2171.5,18.174152694610775)(2505.5,22.56328143712575)(2839.5,27.240485029940118)(3173.5,32.199152694610774)(3507.5,37.44004491017964)(3841.5,42.9565)(4175.5,48.74484730538922)(4509.5,54.80647305389222)(4843.5,61.164)(5177.5,67.82197005988024)(5511.5,74.77786826347305)(5845.5,82.05068862275449)(6179.5,89.64715269461078)(6513.5,97.57394011976048)(6847.5,105.86460479041916)(7181.5,114.52601796407185)(7515.5,123.56620359281438)(7849.5,133.02156886227544)(8183.5,142.95500898203593)(8517.5,153.42188023952096)(8851.5,164.45122754491018)(9185.5,176.06351796407185)(9519.5,188.34054790419162)(9853.5,201.33261676646708)(10187.5,215.11561676646707)(10521.5,229.66456886227544)(10855.5,244.98857185628742)(11189.5,261.1554341317365)(11523.5,278.16943113772453)(11857.5,296.0684610778443)(12191.5,314.8944161676647)(12525.5,334.76406886227545)(12859.5,355.686380239521)(13193.5,377.6354700598802)(13527.5,400.7926766467066)(13861.5,425.26753293413174)(14195.5,451.1214670658683)(14529.5,478.60874251497006)(14863.5,507.8448353293413)(15197.5,538.9790179640718)(15531.5,572.0008802395209)(15865.5,607.0877035928144)(16199.5,644.1859670658683)(16533.5,683.3988143712575)(16867.5,724.9113922155688)(17201.5,768.7641467065869)(17535.5,815.1436047904191)(17869.5,864.0901227544911)(18203.5,915.7329730538922)(18537.5,970.133739520958)(18871.5,1027.413368263473)(19205.5,1088.0779311377246)(19539.5,1152.6376377245508)(19873.5,1221.4731976047904)(20207.5,1294.8711916167663)(20541.5,1373.1157784431136)(20875.5,1457.0711646706588)(21209.5,1547.5486616766466)(21543.5,1645.0836676646707)(21877.5,1749.5506556886228)(22211.5,1861.3744251497005)(22545.5,1980.2774341317365)(22879.5,2106.45052994012)(23213.5,2240.55351497006)(23547.5,2382.9252964071857)(23881.5,2533.9247964071856)(24215.5,2694.0401377245507)(24549.5,2863.199398203593)(24883.5,3042.0251796407188)(25217.5,3230.280344311377)(25551.5,3428.0554790419164)(25885.5,3636.7262814371256)(26219.5,3857.1243083832333)(26553.5,4090.237161676647)(26887.5,4338.172107784431)(27221.5,4602.643706586827)(27555.5,4887.577766467066)(27889.5,5196.619589820359)(28223.5,5533.495835329341)(28557.5,5904.957110778443)(28891.5,6318.40652994012)(29225.5,6784.988535928144)(29559.5,7319.875413173652)(29893.5,7949.884458083832)(30227.5,8725.226431137724)(30561.5,9789.064071856288)(30895.5,11265.184853293413)(31229.5,13413.724155688624)(31563.5,16944.67256287425)(31897.5,22938.68886227545)(32231.5,32316.48101497006)(32549.5,45359.79038741722)(32702,53261.719)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.069)(190.5,232.6589)(570.5,709.6480842105263)(950.5,1196.6337184210527)(1330.5,1690.1221210526317)(1710.5,2189.6400842105263)(2090.5,2694.497357894737)(2470.5,3204.0573736842107)(2850.5,3718.6741578947367)(3230.5,4238.482794736841)(3610.5,4764.7214894736835)(3990.5,5298.296757894736)(4370.5,5841.281960526316)(4750.5,6395.202660526315)(5130.5,6961.350839473685)(5510.5,7540.993026315789)(5890.5,8133.372015789473)(6270.5,8734.822897368422)(6650.5,9342.967752631579)(7030.5,9956.752307894736)(7410.5,10575.234568421052)(7790.5,11198.100728947367)(8170.5,11824.840531578946)(8550.5,12455.626292105264)(8930.5,13090.247586842104)(9310.5,13728.575228947368)(9690.5,14370.440260526317)(10070.5,15015.841252631579)(10450.5,15664.630397368423)(10830.5,16317.030813157895)(11210.5,16973.154363157893)(11590.5,17632.737636842106)(11970.5,18295.751634210526)(12350.5,18962.31434736842)(12730.5,19632.349584210526)(13110.5,20305.699439473687)(13490.5,20982.394255263156)(13870.5,21662.506336842103)(14250.5,22345.894881578948)(14630.5,23032.483915789475)(15010.5,23722.286118421052)(15390.5,24415.212605263157)(15770.5,25111.176465789475)(16150.5,25810.02410263158)(16530.5,26511.73647105263)(16910.5,27216.409768421054)(17290.5,27924.022686842105)(17670.5,28634.736831578946)(18050.5,29348.564321052632)(18430.5,30065.47053947368)(18810.5,30785.48525)(19190.5,31508.688036842104)(19570.5,32235.248236842108)(19950.5,32965.0526631579)(20330.5,33698.28517105264)(20710.5,34434.81481052632)(21090.5,35174.532952631576)(21470.5,35917.895857894735)(21850.5,36665.28371052632)(22230.5,37416.66357368421)(22610.5,38172.28100789474)(22990.5,38931.92542368421)(23370.5,39695.625260526314)(23750.5,40463.389355263156)(24130.5,41235.613436842104)(24510.5,42012.476486842104)(24890.5,42793.96287368421)(25270.5,43580.56005526315)(25650.5,44372.39037105263)(26030.5,45169.62203947368)(26410.5,45972.09492631579)(26790.5,46780.44576842106)(27170.5,47595.067805263156)(27550.5,48416.389299999995)(27930.5,49244.825065789475)(28310.5,50080.321313157896)(28690.5,50923.3093368421)(29070.5,51774.13953684211)(29450.5,52633.453644736845)(29830.5,53501.829744736846)(30210.5,54379.64974210526)(30590.5,55267.43845263158)(30970.5,56166.53594210526)(31350.5,57077.05190263158)(31730.5,57999.50882631579)(32110.5,58934.752134210525)(32490.5,59885.838323684206)(32870.5,60853.76433421053)(33250.5,61840.456797368424)(33630.5,62847.4605)(34010.5,63880.007623684214)(34390.5,64943.45741578947)(34770.5,66040.62170789474)(35150.5,67180.7566394737)(35530.5,68371.20348421052)(35910.5,69634.29873421052)(36290.5,71007.77509473685)(36670.5,72553.45386842104)(37050.5,74590.8398131579)(37260.5,77017.990675)(37282,77894.058)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.973)(183,190.30856164383562)(548,594.3603315068493)(913,1024.961002739726)(1278,1469.2798904109588)(1643,1923.6285232876712)(2008,2386.440526027397)(2373,2857.0123945205482)(2738,3335.2412931506847)(3103,3820.518504109589)(3468,4312.556301369863)(3833,4811.463101369864)(4198,5316.991939726027)(4563,5828.562306849315)(4928,6346.063736986301)(5293,6868.94305479452)(5658,7396.841920547946)(6023,7929.662317808219)(6388,8467.604142465754)(6753,9010.742153424659)(7118,9558.934805479452)(7483,10111.938605479452)(7848,10669.474978082191)(8213,11231.314112328768)(8578,11797.621369863013)(8943,12368.65250410959)(9308,12944.311830136987)(9673,13524.519564383561)(10038,14109.451419178082)(10403,14698.853712328768)(10768,15293.112660273973)(11133,15892.433191780823)(11498,16496.828142465754)(11863,17106.316189041096)(12228,17721.04000547945)(12593,18340.346950684932)(12958,18964.554947945202)(13323,19594.05018082192)(13688,20228.820687671232)(14053,20869.080038356162)(14418,21514.670046575342)(14783,22165.900589041095)(15148,22822.877701369864)(15513,23485.61907123288)(15878,24154.566920547943)(16243,24829.88501369863)(16608,25511.430641095892)(16973,26198.8236630137)(17338,26892.730293150686)(17703,27593.722350684933)(18068,28301.48203561644)(18433,29016.173605479453)(18798,29737.934356164384)(19163,30466.729484931508)(19528,31202.92680821918)(19893,31946.9248630137)(20258,32698.838134246576)(20623,33459.216728767125)(20988,34229.22386849315)(21353,35008.99332054795)(21718,35798.51410410959)(22083,36598.632827397254)(22448,37409.98307945205)(22813,38232.88135342466)(23178,39067.59715616438)(23543,39915.206906849315)(23908,40775.91306849315)(24273,41650.684063013694)(24638,42540.330361643835)(25003,43445.31521643835)(25368,44367.7068)(25733,45309.33676438356)(26098,46271.140583561646)(26463,47254.96390684932)(26828,48263.57510136987)(27193,49300.231649315065)(27558,50368.124427397255)(27923,51470.418468493146)(28288,52611.19690136986)(28653,53795.38869041095)(29018,55029.08482465754)(29383,56320.12154520548)(29748,57678.96482465754)(30113,59114.90866575342)(30478,60647.17013150685)(30843,62287.70946575342)(31208,64046.39155890411)(31573,65948.76017808219)(31938,68015.45561917809)(32303,70268.4742739726)(32668,72725.02970136987)(33033,75449.96638630137)(33398,78510.05700821918)(33763,81999.3380219178)(34128,86050.69222191781)(34493,90831.67789315069)(34858,96740.15275342466)(35223,104550.05547123287)(35588,116337.4376410959)(35779,125163.37964705883)(35789,125692.196)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.012)(146,1.978233676975945)(437,6.271)(728,10.63781443298969)(1019,15.179)(1310,19.835)(1601,24.491)(1892,29.147)(2183,33.827536082474225)(2474,38.724)(2765,43.671)(3056,48.636051546391755)(3347,53.813)(3638,59.053546391752576)(3929,64.473)(4220,70.01970103092785)(4511,75.778)(4802,81.598)(5093,87.44253608247422)(5384,93.503)(5675,99.614)(5966,105.74201030927836)(6257,112.081)(6548,118.483)(6839,124.9422268041237)(7130,131.615)(7421,138.308)(7712,145.08378350515463)(8003,152.059)(8294,159.043)(8585,166.03229209621992)(8876,173.212)(9167,180.487)(9458,187.762)(9749,195.08520618556702)(10040,202.625)(10331,210.191)(10622,217.77952577319587)(10913,225.583)(11204,233.44001030927836)(11495,241.445)(11786,249.593)(12077,257.8093848797251)(12368,266.234)(12659,274.69963230240546)(12950,283.382)(13241,292.1369484536083)(13532,301.108)(13823,310.1481237113402)(14114,319.401)(14405,328.73513402061855)(14696,338.284)(14987,347.95956013745706)(15278,357.8412268041237)(15569,367.892)(15860,378.1011271477663)(16151,388.526)(16442,399.09973539518904)(16733,409.8684982817869)(17024,420.836)(17315,431.97982817869416)(17606,443.3423608247423)(17897,454.9270206185567)(18188,466.716)(18479,478.7367113402062)(18770,491.00674570446733)(19061,503.5473642611684)(19352,516.3713711340206)(19643,529.517793814433)(19934,543.0013092783505)(20225,556.8603848797251)(20516,571.1063608247422)(20807,585.7789175257732)(21098,600.9315738831615)(21389,616.5986323024056)(21680,632.778206185567)(21971,649.4465979381444)(22262,666.6643917525772)(22553,684.4916597938144)(22844,702.9503024054983)(23135,722.1009312714777)(23426,742.000879725086)(23717,762.6884123711341)(24008,784.2621340206185)(24299,806.8419381443299)(24590,830.5944329896906)(24881,855.6907972508591)(25172,882.2354776632303)(25463,910.5732749140893)(25754,940.9522302405497)(26045,973.7337250859107)(26336,1009.525501718213)(26627,1049.177388316151)(26918,1094.1484364261169)(27209,1146.7408178694157)(27500,1210.8287972508592)(27791,1295.0530343642613)(28082,1428.52512371134)(28373,1936.0622164948454)(28541,3951.5852444444445)(28565,4945.078)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.011)(181.5,2.298024861878453)(543.5,7.39196132596685)(905.5,12.846621546961325)(1267.5,18.578)(1629.5,24.44856629834254)(1991.5,30.594629834254146)(2353.5,37.014)(2715.5,43.66661602209945)(3077.5,50.57362154696132)(3439.5,57.753)(3801.5,65.08817403314917)(4163.5,72.6765)(4525.5,80.4550276243094)(4887.5,88.4337955801105)(5249.5,96.6675)(5611.5,105.07338950276242)(5973.5,113.75666574585635)(6335.5,122.7165)(6697.5,131.92012154696133)(7059.5,141.41022651933702)(7421.5,151.196044198895)(7783.5,161.28051104972374)(8145.5,171.66944198895027)(8507.5,182.3868591160221)(8869.5,193.474908839779)(9231.5,204.9389502762431)(9593.5,216.7948950276243)(9955.5,229.06955801104974)(10317.5,241.797091160221)(10679.5,255.0154502762431)(11041.5,268.74189226519337)(11403.5,283.05802486187844)(11765.5,297.9990718232044)(12127.5,313.6326961325967)(12489.5,330.0478287292818)(12851.5,347.36489779005524)(13213.5,365.62986464088397)(13575.5,385.0328149171271)(13937.5,405.66013259668506)(14299.5,427.5818314917127)(14661.5,450.83144475138124)(15023.5,475.5672955801105)(15385.5,502.0523453038674)(15747.5,530.0259751381216)(16109.5,559.3107375690607)(16471.5,589.8519640883978)(16833.5,621.6678066298342)(17195.5,654.8743176795581)(17557.5,689.4013121546961)(17919.5,725.3846961325967)(18281.5,762.8980635359117)(18643.5,801.907591160221)(19005.5,842.5096629834254)(19367.5,884.8020718232044)(19729.5,928.861544198895)(20091.5,974.7612099447514)(20453.5,1022.6342651933702)(20815.5,1072.5725607734807)(21177.5,1124.8395055248618)(21539.5,1179.584991712707)(21901.5,1237.1880303867404)(22263.5,1297.957046961326)(22625.5,1362.265491712707)(22987.5,1430.3952762430938)(23349.5,1502.6981519337016)(23711.5,1579.696502762431)(24073.5,1661.6038812154698)(24435.5,1748.4525828729281)(24797.5,1840.9641022099447)(25159.5,1938.9034005524863)(25521.5,2042.6551602209943)(25883.5,2153.1485220994473)(26245.5,2271.2495)(26607.5,2396.9298314917123)(26969.5,2530.6465359116023)(27331.5,2672.95844198895)(27693.5,2824.6903425414366)(28055.5,2986.2353867403317)(28417.5,3158.2669364640883)(28779.5,3341.9625939226516)(29141.5,3538.530229281768)(29503.5,3748.9704861878454)(29865.5,3973.6326353591157)(30227.5,4215.252831491713)(30589.5,4476.184969613259)(30951.5,4760.791403314917)(31313.5,5071.179861878453)(31675.5,5412.076848066298)(32037.5,5786.981693370165)(32399.5,6205.653919889503)(32761.5,6683.778737569061)(33123.5,7242.432157458564)(33485.5,7909.979223756905)(33847.5,8733.536740331492)(34209.5,9802.194723756906)(34571.5,11351.004914364641)(34933.5,13998.519212707182)(35279.5,19650.679766666664)(35446,25499.5)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.003)(182,0.8189201101928375)(545,2.618)(908,4.4489173553719015)(1271,6.537)(1634,8.715)(1997,10.893)(2360,13.071)(2723,15.249)(3086,17.427)(3449,19.605)(3812,21.783)(4175,23.961)(4538,26.139)(4901,28.317)(5264,30.495)(5627,32.673)(5990,34.851)(6353,37.029)(6716,39.207)(7079,41.385)(7442,43.563)(7805,45.741)(8168,47.919)(8531,50.189754820936635)(8894,52.716)(9257,55.257)(9620,57.798)(9983,60.339)(10346,62.88)(10709,65.421)(11072,67.962)(11435,70.503)(11798,73.05656198347108)(12161,75.862)(12524,78.76711845730027)(12887,81.88)(13250,85.28151239669423)(13613,88.97315977961432)(13976,92.94506060606061)(14339,97.188)(14702,101.54920936639118)(15065,106.143)(15428,110.862)(15791,115.581)(16154,120.34537465564738)(16517,125.382)(16880,130.464)(17243,135.546)(17606,140.77125895316806)(17969,146.214)(18332,151.659)(18695,157.2202396694215)(19058,163.021)(19421,168.83004132231406)(19784,174.846)(20147,181.017)(20510,187.22618457300274)(20873,193.707)(21236,200.28687603305784)(21599,207.139)(21962,214.12243250688704)(22325,221.37020936639118)(22688,228.868)(23051,236.673)(23414,244.81311845730028)(23777,253.32572727272728)(24140,262.29896694214875)(24503,271.77692011019286)(24866,281.80780440771355)(25229,292.3972314049587)(25592,303.6866694214876)(25955,315.78646280991734)(26318,328.86711019283746)(26681,343.21780991735534)(27044,358.81747382920105)(27407,375.8708319559229)(27770,394.7050606060606)(28133,415.7127878787879)(28496,439.4317162534435)(28859,466.4655564738292)(29222,498.365608815427)(29585,537.2298842975206)(29948,587.2949889807162)(30311,662.5635867768594)(30674,763.2199421487603)(31037,869.8372286501378)(31400,980.2394986225895)(31763,1096.78108815427)(32126,1221.4321432506886)(32489,1354.5482093663911)(32852,1496.5741432506886)(33215,1648.5751597796143)(33578,1813.5611900826445)(33941,1997.562570247934)(34304,2211.9563140495866)(34667,2478.9477465564737)(35030,2875.3)(35393,4013.3737988980715)(35577,6494.691)(35581,6666.259)};
\addlegendentry{Z3str3RE}

\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.013)(95,1.341005291005291)(284,4.0399682539682535)(473,6.869)(662,9.70411111111111)(851,12.65937566137566)(1040,25.59284126984127)(1229,51.54501058201058)(1418,78.22667195767197)(1607,105.5319417989418)(1796,133.4236984126984)(1985,161.84444444444443)(2174,190.78955555555555)(2363,220.40304232804232)(2552,250.7406349206349)(2741,281.78158201058204)(2930,313.4990582010582)(3119,346.00148148148145)(3308,379.26011111111114)(3497,413.4176613756614)(3686,448.74649735449736)(3875,485.55874074074075)(4064,523.7897671957672)(4253,563.7060264550265)(4442,605.5690211640213)(4631,649.9228571428572)(4820,696.9802116402117)(5009,745.7844444444445)(5198,795.6489947089948)(5387,846.3269788359788)(5576,897.7440740740741)(5765,949.8416878306879)(5954,1002.637074074074)(6143,1056.1681269841272)(6332,1110.3784444444445)(6521,1165.2705343915343)(6710,1220.876931216931)(6899,1277.2039894179895)(7088,1334.4474126984128)(7277,1392.6996772486773)(7466,1452.0509206349207)(7655,1512.6050846560847)(7844,1574.619216931217)(8033,1637.9648359788362)(8222,1702.6984232804232)(8411,1768.954656084656)(8600,1836.9828518518518)(8789,1906.8673809523812)(8978,1978.6749523809524)(9167,2052.814894179894)(9356,2129.261529100529)(9545,2207.6439365079364)(9734,2287.9149523809524)(9923,2369.956126984127)(10112,2453.9330846560847)(10301,2540.037798941799)(10490,2628.356275132275)(10679,2719.279005291005)(10868,2812.8628941798943)(11057,2909.3264285714286)(11246,3009.0086507936508)(11435,3111.9666243386246)(11624,3218.299222222222)(11813,3327.769603174603)(12002,3440.6848042328043)(12191,3557.7057142857143)(12380,3679.364476190476)(12569,3806.0655767195767)(12758,3937.8237195767197)(12947,4075.3376719576722)(13136,4219.62535978836)(13325,4370.628846560847)(13514,4529.19538095238)(13703,4696.222878306879)(13892,4872.437195767196)(14081,5057.567285714285)(14270,5252.1323862433865)(14459,5458.876259259259)(14648,5679.89501058201)(14837,5918.56217989418)(15026,6175.9863597883605)(15215,6453.726322751323)(15404,6755.660825396825)(15593,7085.784804232804)(15782,7448.813486772487)(15971,7854.716571428572)(16160,8312.60244973545)(16349,8829.83808994709)(16538,9424.434878306878)(16727,10092.097708994708)(16916,10839.384137566138)(17105,11695.061899470898)(17294,12707.067682539682)(17483,13947.966777777778)(17672,15514.564391534392)(17861,17578.844534391534)(18050,20439.443920634923)(18239,24610.02486772487)(18428,31190.684534391534)(18525.5,36009.797333333336)(18530,36217.838)};
\addlegendentry{Z3-Trau}

\path[name path=axisCVC5] (axis cs:0,0) -- (axis cs:32702,0);
\addplot [thick,color=colourCVC5,fill=colourCVC5,fill opacity=0.1] fill between [of=pathCVC5 and axisCVC5];
\path[name path=axisOstrichCEA] (axis cs:0,0) -- (axis cs:37282,0);
\addplot [thick,color=colourOstrichCEA,fill=colourOstrichCEA,fill opacity=0.1] fill between [of=pathOstrichCEA and axisOstrichCEA];
\path[name path=axisOstrich] (axis cs:0,0) -- (axis cs:35789,0);
\addplot [thick,color=colourOstrich,fill=colourOstrich,fill opacity=0.1] fill between [of=pathOstrich and axisOstrich];
\path[name path=axisZ3str3] (axis cs:0,0) -- (axis cs:28565,0);
\addplot [thick,color=colourZ3str3,fill=colourZ3str3,fill opacity=0.1] fill between [of=pathZ3str3 and axisZ3str3];
\path[name path=axisZ3seq] (axis cs:0,0) -- (axis cs:35446,0);
\addplot [thick,color=colourZ3seq,fill=colourZ3seq,fill opacity=0.1] fill between [of=pathZ3seq and axisZ3seq];
\path[name path=axisZ3str3RE] (axis cs:0,0) -- (axis cs:35581,0);
\addplot [thick,color=colourZ3str3RE,fill=colourZ3str3RE,fill opacity=0.1] fill between [of=pathZ3str3RE and axisZ3str3RE];
\path[name path=axisZ3-Trau] (axis cs:0,0) -- (axis cs:18530,0);
\addplot [thick,color=colourZ3-Trau,fill=colourZ3-Trau,fill opacity=0.1] fill between [of=pathZ3-Trau and axisZ3-Trau];
\end{axis}\end{tikzpicture}}

\end{document}

### 2023-04-11 2023-1-19/sections/abstract.tex
atva2023 first version

\documentclass{standalone}
\begin{document}
Regular expression with repetition frequently appears in the real world, such as $(ab)\{1, 100\}$. However, state-of-art string
solvers can not efficiently solve string constraints with repetition bounds,
especially when the repetition bounds are large. This paper focuses on
string logic containing regular membership predicate with repetition
and linear integer constraints on string length. Repetition is captured
by cost-enriched finite automaton(CEFA), whose transitions have symbolic updates of integers limited by linear arithmetic. We propose a new systematic algorithm based on CEFA, and heuristic ways
like under-approximation and symbolic-aware simplification are used to
accelerate. We implement a powerful string solver OstrichCEA and
evaluate it on instances from the real world and other typical benchmarks.
The experiment result shows superiority.

\keywords{String Constraints, Automaton Theory, Regex Expression, Bounded Repetition, Linear Length Constraints}
\end{document}

### 2023-04-11 2023-1-19/sections/algorithms.tex
atva2023 first version

\documentclass{standalone}
\begin{document}

Based on the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve ESL formula $\varphi\wedge \psi$ where $\varphi$ is the conjunction of literals and $\psi$ is the conjunction of linear literals without length operation. For each string variable $x$, we first compute pre-images of all linear literal $i=|x|$. Then we generate CEFAs of all regular expressions $\regex$ in all regular literals $x\in \regex$ and intersect these CEFAs and pre-images to get the final automaton $\aut_x$ for $x$. At present, there is a final CEFA for each string variable $x$. The linear arithmetic constraint $\psi$ restricts the accepting word of final CEFAs. Thus the satisfiability problem is the emptiness checking problem of final CEFAs under $\psi$. If it is empty, the string constraints are unsatisfiable. Otherwise, the string constraints are satisfiable.
The emptiness checking problem of CEFAs under linear integer arithmetic is theoretically pspace-complete\cite{atva2020}. To solve it efficiently for a practical example, we develop heuristic ways such as under-approximation (Section \ref{subsec:under-approx}) and symbolic-aware simplification (Section \ref{subsec:simplify}).
\subsection{High-level algorithm}
\begin{algorithm}[h]
  \caption{High-level algorithm}
  \label{alg:high}
  \begin{algorithmic}[1]
    \Require Conjunction of literals $\varphi$ and conjunction of linear literals $\psi$
    \Ensure \emph{sat} or \emph{unsat}
    \Statex
    \State $finalAuts \leftarrow \emptyset$
    \ForAll{string variables $x$ occurring in $\varphi$}
    \State $\aut_{len} \leftarrow$ intersection of all pre-images of $i=|x|$ in $\varphi$
    \State $\aut_{regex} \leftarrow$ intersection of all CEFAs of $x \in \regex$ in $\varphi$
    \State $\aut_x \leftarrow$ intersection of $\aut_{len}$ and $\aut_{regex}$
    \State $\aut_{nfa} \leftarrow$ NFA form of $\aut_x$
    \If{$\aut_{nfa}$ is empty}
    \State \textbf{return} \emph{unsat}
    \EndIf
    \State $finalAuts \leftarrow finalAuts \cup \{\aut_x\}$
    \EndFor
    \If{$\algfun{isEmpty}(finalAuts, \psi)$ }
    \State \textbf{return} \emph{unsat}
    \Else
    \State \textbf{return} \emph{sat}
    \EndIf
  \end{algorithmic}
\end{algorithm}
The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process. We construct the automata of all length operations occurring in the ESL conjunction $\varphi$ at line 3 and the automata of all regular memberships at line 4. In the following steps, we call an automaton to be \emph{final} if we will not operate it anymore. The set $finalAuts$ contains all final automata for all string variables and is initially empty at line 1. The intersection of $\aut_{len}$ and $\aut_{regex}$ at line 5 ensures the final automaton of $x$ reserves both length and regular information. At line 6, we compute an NFA form to throw unsat rapidly. An NFA form of CEFA is obtained by removing update functions and accepting conditions while maintaining graph structure. More exactly, given a CEFA $\aut = (Q,\Sigma, \delta, q_I, F, R, \theta)$, the NFA form of $\aut$ is $(Q, \Sigma, \delta', q_I, F)$ where $\delta'$ is composed of transition $q\xrightarrow[]{a} q'$ for $q\xrightarrow[\myvec{v}]{a} q'\in \delta$. It is obvious that the NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7. Sometimes the over-approximation is useful. For example, to solve the string constraint $x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^* $ which CVC5 has failed on, the NFA form is empty because there is no path to accepting states. \newline
After obtaining all final CEFAs of all string variables and their NFA forms are not empty, we check whether the final CEFAs are empty under the linear integer arithmetic $\psi$ at line 12. If they are empty under $\psi$, we return $unsat$. Otherwise, we return $sat$.

\subsection{Emptiness Checking} \label{subsec:emptiness}
As mentioned, the emptiness checking problem of CEFAs under linear integer arithmetic $P$ is theoretically Pspace-complete. In our previous research  \cite{atva2020}, we rewrote CEFAs to an infinite system and used a model-checking tool \emph{nuXmv}\cite{nuxmv} to solve it. However, it needs to be more effective. So we put forward a new framework that brings in under-approximation and symbolic-aware simplification heuristics.\newline
As shown in Algorithm \ref{alg:emptiness}, we simplify the input CEFAs at line 1 because they may have many transitions and registers. The purpose of the simplification is to deal with duplication. After simplification, we try to find a solution by under-approximation at line 3 and line 4. An off-the-shelf SMT solver gives the result of $\varphi_{under}\wedge P$. If we find a solution, we return $false$ at line 5 because it implies that the CEFAs under linear integer arithmetic $P$ are not empty. Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $P$ at line 12. The Parikh image checking is complete so that satisfiability implies non-emptiness directly. \newline
The under-approximation program is executed many times until the $MaxBound$ is reached. $MaxBound$ is an empirical bound set to $15$ in our experiment because it brings exponential growth of searching space. The details of simplification are shown in Algorithm \ref{alg:simplify} and under-approximation are shown in Algorithm \ref{alg:underApprox}.\newline
\begin{algorithm}[h]
  \caption{ $\algfun{isEmpty}(auts, P)$}
  \label{alg:emptiness}
  \begin{algorithmic}[1]
    \Require the CEFAs $auts$ and the linear integer arithmetic $P$
    \Ensure $true$ or $false$
    \Statex
    \State $simpliAuts \leftarrow \algfun{simplify}(auts)$
    \For{$bound \gets 1, MaxBound$ }
    \State $\varphi_{under}\gets \algfun{underApprox}(simpliAuts, bound)$
    \If{$\varphi_{under}\wedge P$ is sat}
    \State \textbf{return} $false$
    \EndIf
    \EndFor
    \State $\varphi \gets \algfun{parikhImage}(simpliAuts)$
    \If{$\varphi\wedge P$ is unsat}
    \State \textbf{return} $true$
    \Else
    \State \textbf{return} $false$
    \EndIf
  \end{algorithmic}
\end{algorithm}

\subsubsection{Symbolic-Aware Simplification} \label{subsec:simplify}
The purpose of simplification is to remove duplicated transitions and registers. In the emptiness checking Algorithm \ref{alg:emptiness}, the vectors on the transitions are meritorious, while the letters are not. So we see the alphabet of the CEFA as unary (i.e., the alphabet is $\{a\}$) and see the vectors in the CEFA as letters in the NFA. The vector $\myvec{0}_n$ is seen as $\epsilon$. Precisely, given an CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$, we obtain a symbolic form  $\aut_{sym} = (Q, \Sigma', \delta', q_I, F, R, \theta)$ where
\begin{itemize}
  \item $\Sigma' = \{a\}$,
  \item the transition set $\delta'$ is composed of transition $q\xrightarrow[\myvec{v}]{a}q'$ if there is a transition $q\xrightarrow[\myvec{v}]{b} q'$ in $\delta$ for $b\in \Sigma$ .
\end{itemize}
We directly apply algorithms of epsilon-closure, determination, and simplification in \cite{aut_hopcraft}. We see $q\xrightarrow[\myvec{0}_n]{a}q'$ as epsilon transition and compute the epsilon-closure based on it. We see $q\xrightarrow[\myvec{v}]{a}q'$ as a transition with label $(a, \myvec{v})$ and determine the automaton based on the label. Two accepting states are equivalent if they have the same accepting conditions, and two states are equivalent if they reach equivalent states for each label. We simplify the automaton by merging equivalent states.
The process above comprises line 3 and line 4 of Algorithm \ref{alg:simplify}. From line 5 to line 13, we check whether some registers are duplicated. (i.e., the values of these registers are always the same). If two registers $r_i$ and $r_j$ are duplicated at line 6, we remove one at line 7 and the corresponding update of vectors at line 9 to ensure the vectors are consistent with the new registers. After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register at line 11.
\begin{algorithm}[h]
  \caption{$\algfun{simplify}(auts)$}
  \label{alg:simplify}
  \begin{algorithmic}[1]
    \Require A set of CEFAs
    \Ensure The simplified CEFAs
    \Statex
    \For{$\aut \in auts$}
    \State Suppose that $\aut = (Q, \Sigma, \delta, q_I, F,
      R, \theta)$ and $R=(r_1,\cdots, r_n)$
    \State $\algfun{determinizeByVec}(\aut)$
    \State $\algfun{minimizeByVec}(\aut)$
    \ForAll{$(i, j)$ where $1\leq i \leq j \leq n$}
    \If {$\myvec{v}[i] = \myvec{v}[j]$ for every vector $\myvec{v}\in \aut$ }
    \State $R=(\cdots r_{j-1}r_{j+1}\cdots)$ \Comment remove $r_j$ from the register vector $R$
    \ForAll{$\myvec{v'}\in \aut$}
    \State $\myvec{v'}=(\cdots\myvec{v'}[j-1]\myvec{v'}[j+1]\cdots)$ \Comment remove $\myvec{v'}[j]$ from each vector $\myvec{v'}$
    \EndFor
    \State $\theta = \theta\wedge r_i = r_j$
    \EndIf
    \EndFor
    \EndFor
    \State \textbf{return} $auts$
  \end{algorithmic}
\end{algorithm}
\begin{example}
  Considering the CEFA recognizing $(a|b)\{1,100\}$ illustrated in Fig.\ref{subfig:simp_origin_cefa}. We first obtain a symbolic CEFA by using unary alphabet (Fig.\ref{subfig:simp_symbolic_cefa}) and then minimize it based on the symbolic label "$a/(1)$"(Fig.\ref{subfig:simp_final}).
  \begin{figure}[h]
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=$1\leq r \leq 100$, accepting/.style=accepting by arrow,
        ]

        \node[state,initial]            (q_0)                      {};
        \node         (q_tmp) [right=of q_0]       {};
        \node[state, accepting]         (q_1) [above=of q_tmp]       {};
        \node[state, accepting]         (q_2) [below=of q_tmp]       {};
        \path[->] (q_0) edge   node    [right] {$a/(1)$} (q_1)
        (q_0) edge   node    [right] {$b/(1)$} (q_2)
        (q_1) edge[bend right]   node    [left] {$\epsilon/(1)$} (q_0)
        (q_2) edge[bend left]   node    [left] {$\epsilon/(1)$} (q_0);
      \end{tikzpicture}
      \caption{The CEFA recognizing $(a|b)\{1,100\}$}
      \label{subfig:simp_origin_cefa}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=$1\leq r \leq 100$, accepting/.style=accepting by arrow,
        ]

        \node[state,initial]            (q_0)                      {};
        \node         (q_tmp) [right=of q_0]       {};
        \node[state, accepting]         (q_1) [above=of q_tmp]       {};
        \node[state, accepting]         (q_2) [below=of q_tmp]       {};
        \path[->] (q_0) edge   node    [right] {$\myemph{a/(1)}$} (q_1)
        (q_0) edge   node    [right] {$\myemph{a/(1)}$} (q_2)
        (q_1) edge[bend right]   node    [left] {$\myemph{a/(1)}$} (q_0)
        (q_2) edge[bend left]   node    [left] {$\myemph{a/(1)}$} (q_0);
      \end{tikzpicture}
      \caption{The symbolic CEFA}
      \label{subfig:simp_symbolic_cefa}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=$1\leq r \leq 100$, accepting/.style=accepting by arrow,
        ]

        \node[state,initial]            (q_0)                      {};
        \node[state, accepting]         (q_1) [right=of q_0]       {};
        \path[->] (q_0) edge   node    [above] {$\myemph{a/(1)}$} (q_1)
        (q_1) edge[loop below] node {$\myemph{a/(1)}$} (q_1);
      \end{tikzpicture}
      \caption{Simplify the CEFA based on symbolic label}
      \label{subfig:simp_final}
    \end{subfigure}
    \caption{Symbolic simplification can remove duplicated transitions and states.}
    \label{fig:simplification_example}
  \end{figure}

\end{example}
\begin{example}
  Considering the string constraints $i=|x|\wedge j=|x|$. We compute the pre-images of $i=|x|$, $j=|x|$ and intersect these pre-images to get the final CEFA represented in Fig.\ref{subfig:duplicate}. However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their update functions are the same. We can simplify the CEFA by removing the duplicated register $r_2$ and corresponding update functions, as shown in Fig.\ref{subfig:remove_duplicate}. To maintain the value of $r_2$, we add a constraint $r_2=r_1$ to restrict the value of $r_2$ to be the same as $r_1$.
  \begin{figure}[h]
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=${i=r_1\wedge j=r_2 }$, accepting/.style=accepting by arrow,
        ]
        \node at (-0.5,0.5) {$R=(r_1, \myemph{r_2})$};
        \node[state,initial,accepting]            (q_0)       {};

        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1,\myemph{1})} ();
      \end{tikzpicture}
      \caption{An automaton with duplicated registers}
      \label{subfig:duplicate}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=${i=r_1\wedge j=r_2\wedge \myemph{r_1 = r_2} }$, accepting/.style=accepting by arrow,
        ]

        \node at (-0.5,0.5) {$R=(r_1)$};
        \node[state,initial,accepting]            (q_0)       {};

        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
      \end{tikzpicture}
      \caption{Remove the duplicated registers and corresponding update functions}
      \label{subfig:remove_duplicate}
    \end{subfigure}
    \caption{Symbolic simplification can remove duplicated transitions and states.}
    \label{fig:duplicate}
  \end{figure}

\end{example}

\subsubsection{Under-Approximation} \label{subsec:under-approx}
An under-approximation procedure solves the satisfiable instances of the emptiness checking problem. Inspired by Bounded Model Checking \cite{bmc_1}\cite{bmc_2}\cite{bmc_3}, we explore the states of CEFA in typological order. We use string length as the bound and probe the CEFA from low to high bound. This section discusses the situation in which the string length bound is fixed. The main idea is to enumerate all possible runs ending in accepting states with lengths less than the fixed bound. Although the number of possible runs is an exponential growth of the bound, we usually solve practical satisfiable instances within 1s. As shown in the Algorithm \ref{alg:underApprox}, for each CEFA, we enumerate all runs whose length is less than the bound and compute the value of registers by the sum of vectors on the run at line 4. If the run is ended with an accepting state, then we compute the updates of registers by the sum of vectors on the run at line 6. Together with the accepting condition of the accepting state, we add the updates of registers to the under-approximation formula at line 7.
\begin{algorithm}[h]
  \caption{$\algfun{underApprox}(auts, bound)$}
  \label{alg:underApprox}
  \begin{algorithmic}[1]
    \Require The CEFAs $auts$ and string length $bound$
    \Ensure The linear integer arithmetic $\varphi_{under}$ representing under-approximation of the register values of $auts$
    \Statex
    \State $\varphi_{under} \gets false$
    \For{$\aut \in auts$}
    \State Suppose $\aut = (Q, \Sigma, \delta, q_I, F, (r_1, \cdots, r_m), \theta)$
    \ForAll{run $q_0q_1\cdots q_{n}$ whose length is less than $bound$}
    \If{$q_{n}\in F$}
    \State Let $\myvec{V}\leftarrow$ the sum of the vectors on the run
    \State $\varphi_{under} \gets \varphi_{under} \vee(\theta(q_n)\bigwedge\limits_{i\in[1,m]} r_i = \myvec{V}[i])$
    \EndIf
    \EndFor
    \EndFor
    \State \textbf{return} $\varphi_{under}$
  \end{algorithmic}
\end{algorithm}
\begin{example}
  Consider the automaton in Fig. \ref{subfig:aut_x} again. The solution of the Parikh image of it leads to a complete but inefficient result since the quantifier-free linear integer arithmetic formulas are solved in exponential time \cite{parikh_compute}. Under-approximation can accelerate the solving process. When we set the bound to 2, the under-approximation program will enumerate all runs whose length is 2. One of them is $q_I\xrightarrow[(1,1)]{a} q_1\xrightarrow[(0,1)]{b} q_f$. The corresponding registers' values are $r_1 = 1+0 = 1, r_2 = 1+1 = 2$. Checking for $r_1= 1\wedge r_2=2\wedge r_2=i\wedge 1\leq r_1\leq100$ is a lightweight process because the values of $r_1$ and $r_2$ are fixed.
\end{example}

\end{document}

### 2023-04-11 2023-1-19/sections/automaton_model.tex
atva2023 first version

\documentclass{standalone}
\begin{document}

In this section, we recall the definition of CEFA and Parikh image.

\subsection{Cost-Enriched Finite Automaton} \label{subsec:cefa}
The definition of CEFA in this paper is lightly different from the definition in \cite{atva2020}. In \cite{atva2020}, the cost function is defined as a function $\eta: \Sigma \rightarrow \mathbb{N}$. In this paper, we define the cost function as an integer vector whose elements are the incremental value of registers. Furthermore, we add a new linear integer arithmetic constraint $\theta$ to each final state of the CEFA, which restricts the value of registers. Two types of definitions have the same expressive ability on the $SAT_{CL}$ problem.
\begin{definition}[Cost-Enriched Finite Automaton]
  A cost-enriched finite automaton $\aut$ is a 7-tuple $(Q, \Sigma, \delta, q_I, F, R, \theta)$ where
  \begin{itemize}
    \item $Q,\Sigma,q_I,F$ is defined as NFA,
    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
    \item $\delta$ is a transition set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.  $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
    \item $\theta: F\rightarrow \varphi$ is a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
  \end{itemize}
  The value of each register $r_i$ in $R$ is written as $\mathcal{V}(r_i)$ and is initiated to 0 at the initial state. A \emph{run} of $\aut$ on string $a_1\cdots a_m$ is a transition sequence $q_I\xrightarrow[\myvec{v_1}]{a_1}q_1\cdots q_{m-1}\xrightarrow[\myvec{v_m}]{a_m}q_m$  and $\mathcal{V}(r_i) = \displaystyle\sum_{j=1}^m \myvec{v_j}[i], i\in [1,n]$ is the value of $r_i$ after the run. $\theta[R/\mathcal{V}(R)](q_m)$ is obtained from $\theta(q_m)$ by replacing each register $r_i$ to its value $\mathcal{V}(r_i)$. The run is \emph{accepting} if $q_m\in F$ and $\theta[R/\mathcal{V}(R)](q_m)$ is satisfiable. $\top$ is the valid formula that is always satisfiable. A string $w$ is accepted by $\aut$ if it has an accepting run of $\aut$. The language of $\aut$ is the set of strings accepted by $\aut$, denoted by $\lan(\aut)$.

\end{definition}
\begin{example} \label{eg:1}
  Fig.\ref{fig:repetition} illustrates the CEFA recognizing $(ab)\{1,100\}$. The register vector is $(r_1)$, and the linear arithmetic constraint on $q_2$ is $1\leq r_1\leq 100$. Intuitively, the transition $q_0 \xrightarrow[(1)]{a} q_1$ accept the char $a$ and increase 1 on the value of $r_1$. The transition $q_1 \xrightarrow[(0)]{b} q_2$ accepts the char $b$ and does not change the value. The transition $q_2 \xrightarrow[(0)]{\epsilon} q_2$ is a nondeterministic choice back to initial state $q_0$. Because of the linear arithmetic constraint $1\leq r_1\leq 100$, the value of $r_1$ in the accepting run must be $[1,100]$. $\mathcal{V}(r_1)$ equal to the occurrence number of the transition $q_0 \xrightarrow[(1)]{a} q_1$, so that the accepted string is $ab\cdots ab$ in which $a$ appears at least once and at most 100 times. That is, the language of the automaton is $(ab)\{1,100\}$.
  \begin{figure}[h]
    \centering
    \begin{tikzpicture}[
      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      initial text=, every state/.style={minimum size = 0.001cm,
          accepting text=$1\leq r_1\leq 100$, accepting/.style=accepting by arrow}
      ]
      \node[state,initial]            (q_0)                      {$q_0$};
      \node[state]                    (q_1) [right=of q_0]       {$q_1$};
      \node[state,accepting]          (q_2) [right=of q_1]       {$q_2$};

      \path[->] (q_0) edge              node      [above]           {$a$/(1)} (q_1)
      (q_1) edge              node      [above]           {$b$/(0)} (q_2)
      (q_2) edge [bend left]  node      [below]           {$\epsilon$/(0)} (q_0);
    \end{tikzpicture}
    \caption{An automaton recognizing the language of $(ab)\{1,100\}$}
    \label{fig:repetition}
  \end{figure}
\end{example}
\begin{example}[The pre-image of length operation]\label{eg:pre_len} The length operation can be captured by a CEFA base on our previous work \cite{atva2020}. Fig.\ref{fig:len} shows a pre-image of linear literal $i=|x|$. It is easy to see that the pre-image accepts string words with length $i$.
  \begin{figure}[h]
    \centering
    \begin{tikzpicture}[
      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      initial text=, every state/.style={minimum size = 0.001cm},
      accepting text=${r_1=1}$, accepting/.style=accepting by arrow
      ]

      \node[state,initial,accepting]            (q_0)       {$q$};

      \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
    \end{tikzpicture}
    \caption{The pre-image of $i = |x|$}
    \label{fig:len}
  \end{figure}
\end{example}

% Parikh's theorem \cite{parikh_theorem}\cite{parikh_anthony}\cite{parikh_compute} states that the Parikh image of a context-free language is semilinear so that it can be written as Presburger formula. Following the version for context-free grammar \cite{parikh_compute} and the version for regular expression \cite{parikh_for_nfa}, we define the Parikh image of language of an CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$  as follows:
% \begin{table}[h]
%   \begin{tabular}{l l r}
%     $\psi(\aut)\equiv$& $\bigwedge\limits_{q\in Q}(\text{$f_q$ if $q\in F$ otherwise 0}) + \sum\limits_{(q,a,q',\myvec{v})\in\delta} t_{q,a,q',\myvec{v}} = $ & \\
%     & \quad \ \ (1 if $q = q_I$ otherwise 0) + $\sum\limits_{(q',a,q,\myvec{v})\in\delta} t_{q',a,q, \myvec{v}} $ & \\ 
%     & $\bigwedge\limits_{(q,a,q',\myvec{v})\in\delta} t_{q,a,q',\myvec{v}}\geq 0$ & (consistent formula)\\
%     & & \\
%     & $\bigwedge\limits_{(q,a,q',\myvec{v})\in\delta} t_{q,a,q',\myvec{v}}>0\rightarrow z_{q'} > 0$ & \\
%     & $\bigwedge\limits_{q\in F} z_q > 0\rightarrow f_q = 1$ & \\ 
%     & $\bigwedge\limits_{q\in Q} z_q > 0\rightarrow \bigvee\limits_{(q,a,q',\myvec{v})\in\delta} z_q = z_{q'} + 1\wedge t_{q,a,q',\myvec{v}}\geq 0 \wedge z_{q'} > 0$& (connected formula)\\
%     & & \\
%     &$\bigwedge\limits_{r_i\in R} r_i = \sum\limits_{(q,a,q',\myvec{v})\in \delta} t_{q,a,q',\myvec{v}}*\myvec{v}[i]$ & (register value formula)\\
%     & & \\
%     &$\bigwedge\limits_{q\in F} f_q > 0 \rightarrow \theta(q)$ & (accepting condition) 
%   \end{tabular}
% \end{table}
% $z_q$ is the distance of state $q$ from $q_f\in F$ in a spanning tree. $t_{q,a,q',\myvec{v}}$ represents the using times of transition $(q,a,q',\myvec{v})$ in the accepting run. $f_q$ stands for whether an accepting state $q\in F$ is the final state of a run. The Parikh image of $\aut$ is a Presburger formula $\psi(\aut)$, which is consistent and connected. The register value formula ensures the register values are correctly updated regarding the accepting run. 
% \begin{example} \label{exapmle:parikh}
%   Suppose that we have a CEFA $\aut$ shown in Fig. \ref{subfig:aut_x}. Using $t_1, t_2, t_3$ to record the times of transitions in the accepting run of $\aut$, the Parikh image $\psi(\aut)$ is the quantifier-free Presburger formula $\psi_{cons}\wedge \psi_{conn} \wedge \psi_{val} \wedge \psi_{aut}$ where:
%   \begin{itemize}
%     \item $\psi_{cons} \equiv 1 = t_1 \wedge t_1 + t_3 = t_2 \wedge t_2 = t_3 + 1 \bigwedge\limits_{i\in[1,3]} t_i\geq 0$ is the consistent formula.
%     \item $\psi_{conn} \equiv \top $ is the connectivity formula because all transitions in $\aut$ are connected.
%     \item $\psi_{val} \equiv r_1=t_1 + t_3\wedge r_2 = t_1+t_2+t_3$ is the formula deciding the value of $r_1$ and $r_2$ after a run.
%     \item $\psi_{aut} \equiv r_2 = i\wedge 1 \leq r_1 \leq 100$ is the accepting condition of $\aut$.
%   \end{itemize}
%   $\psi(\aut)$ can be simplified to $t_3\geq 0 \wedge t_1=1\wedge r_1 = t_3 + 1\wedge r_2 = 2*t_3+2\wedge r_2=i\wedge 1\leq r_1\leq 100$. A possible solution is $t_1 =1, t_3 = 0, r_1=1, r_2=2$ and the corresponding accepted string $ab$. It is obvious that $r_1$ is the repeat times of $ab$ and $r_2$ is the length of $ab$.
% \end{example}
\subsection{Encode Bounded Repetition to CEFA} \label{subsec:regex2cefa}
In this section, we define the construction of CEFA from the regular expression with bounded repetition. We must syntactically rewrite bounded repetition $\regex\{m,n\}$ if it is the sub-regex of complement (e.g., $(\regex\{m,n\})^C$), closure(e.g., $(\regex\{m,n\})^*$), and bounded repetition(e.g., $(\regex\{m,n\})\{m', n'\}$), we unwind it to $\regex^m\mid\cdots\mid\regex^n$. After this syntactic rewriting, we call the resulting regex $\regex'$ \emph{non-nested}.
The non-nested regex $\regex'$ possibly contains operations such as intersection, union, concatenation, complement, closure, and bounded repetition. To construct the CEFA of $\regex'$, we first create CEFA for each sub-regex and then combine them. Similar to the construction of NFA from regex\cite{aut_hopcraft}, our construction is inductive on the size of $\regex'$. The base case is for a single character, an empty string, and an empty language. The inductive step is for the concatenation, union, and intersection of two automata and one automaton's repetition, closure, and complement. We only discuss the inductive step for bounded repetition because the other operations are trivial. \newline
For a non-nested regular expression $R\{m,n\}$, suppose we have an CEFA $\aut = (Q,\Sigma,\delta,q_I,F,\emptyset,\top)$ recognizing $R$, the CEFA recognizing $R\{m,n\}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_ I, F, r, \theta')$ where:
\begin{itemize}
  \item $r$ is a new register,
  \item $\delta'$ is composed by transitions $q\xrightarrow[(0)]{a} q'$ for all transitions $q\xrightarrow[()]{a} q' \in \delta$, and transitions $q_f\xrightarrow[(1)]{\epsilon} q_I$  for each $q_f\in F$,
  \item For each accepting states $q\in F$, $\theta'(q)$ is the linear arithmetic $m\leq r\leq n$ if $q_I\not\in F$. Otherwise, $\theta'(q)$ is the linear arithmetic $r\leq n$.
\end{itemize}
In the construction illustrated in Fig.\ref{fig:construct_repetition}, a new register $r$ is added to store the repetition times. The transition $q\xrightarrow[(1)]{\epsilon} q_I$ is set to update the repetition times for each $q\in F$. The accepting condition $\theta'$ is used to restrict the repetition times of the accepting word. Because arbitrary repetition times of an empty string are still empty, the value of $r$ only needs to be less or equal to $n$ when the initial state is accepted.
\begin{figure}[h]
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \begin{tikzpicture}[
      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      initial text=, every state/.style={minimum size = 0.001cm},
      accepting text=$\varphi$, accepting/.style=accepting by arrow,
      ]

      \node[state,initial]            (q_0)                      {};
      \node[state, accepting]         (q_1) [right=of q_0]       {};
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA recognizing $\regex$}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \begin{tikzpicture}[
      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
      initial text=, every state/.style={minimum size = 0.001cm},
      accepting text=$\varphi\wedge$\myemph{$(m\leq) r\leq n$}, accepting/.style=accepting by arrow,
      ]

      \node[state,initial]            (q_0)                      {};
      \node[state, accepting]         (q_1) [right=of q_0]       {};
      \path[->] (q_1) edge[bend right]   node    [above] {\myemph{$\mathbf{\epsilon/(1)}$}} (q_0);
      \node [fit=(q_0) (q_1)] {$\cdots$};
    \end{tikzpicture}
    \caption{The CEFA recognizing $\regex\{m,n\}$}
  \end{subfigure}
  \caption{The construction of bounded repetition}
  \label{fig:construct_repetition}
\end{figure}
\begin{example}
  To construct the CEFA recognizing $(ab)\{1,100\}$, we first construct the CEFA recognizing $ab$ as shown in Fig.\ref{subfig:rep_aut_ab}. Then we add a new register $r_1$ and a transition $q_2\xrightarrow[(1)]{\epsilon} q_0$ to update the repetition times. The accepting condition $\theta'$ map accepting state to $1\leq r_1\leq 100$ because the initial state is unacceptable. The CEFA recognizing $(ab)\{1,100\}$ is shown in Fig.\ref{subfig:rep_aut_ab1_100}.
  \begin{figure}[h]
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=$\top$, accepting/.style=accepting by arrow,
        accepting where=above
        ]

        \node[state,initial]            (q_0)                      {};
        \node[state]                    (q_1) [right=of q_0]       {};
        \node[state, accepting]         (q_2) [right=of q_1]       {};

        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
        (q_1) edge              node      [above]           {$b$/()} (q_2);
      \end{tikzpicture}
      \caption{The CEFA recognizing $ab$}
      \label{subfig:rep_aut_ab}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=\myemph{1}$\leq r_1\leq$\myemph{100}, accepting/.style=accepting by arrow,
        accepting where=above
        ]

        \node[state,initial]            (q_0)                      {};
        \node[state]                    (q_1) [right=of q_0]       {};
        \node[state,accepting]          (q_2) [right=of q_1]       {};

        \path[->] (q_0) edge              node      [above]           {$a$/(\myemph{0})} (q_1)
        (q_1) edge              node      [above]           {$b$/(\myemph{0})} (q_2)
        (q_2) edge [bend left]  node      [below]           {$\epsilon$/(\myemph{1})} (q_0);
      \end{tikzpicture}
      \caption{The CEFA recognizing $(ab)\{\myemph{1},\myemph{100}\}$}
      \label{subfig:rep_aut_ab1_100}
    \end{subfigure}
    \caption{The example of bounded repetition}
  \end{figure}
\end{example}

\end{document}

### 2023-04-11 2023-1-19/sections/conclusion.tex
atva2023 first version

\documentclass{standalone}
\begin{document}

%TODO
This paper aims to efficiently solve the string constraints with bounded repetition and linear integer constraints on string length. The bounded repetition is encoded by an automaton model CEFA whose size is linear to the bound. Moreover, we extend the algorithm in the paper \cite{atva2020} with heuristics such as under-approximation and symbolic-aware simplification. The implementation of the algorithm is done on string solver OstrichCEA. The extensive empirical comparison against state-of-art string solvers over a large and diverse benchmark shows the power of our encoding for bounded repetition and heuristic ways. In the future, we plan to explore how to solve nested repetition and use CEFA to solve more string operations.

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{splncs04}
\bibliography{ref}

\end{document}

### 2023-04-11 2023-1-19/sections/implementation.tex
atva2023 first version

\documentclass{standalone}
\begin{document}
This section presents the empirical evaluation of OstrichCEA, which is our implementation of the decision procedure introduced in Section \ref{sec:algorithm}. Our objective is to validate the effectiveness of the proposed techniques by evaluating our tool's correctness and efficiency compared to other solvers. Furthermore, we assess the efficacy of our heuristics by testing different configurations of the tool. We have implemented our encoding for bounded repetition with two heuristic algorithms on Ostrich+ \cite{atva2020}. The pre-image computation for concatenation, \verb|indexOf|, \verb|substring|, \verb|replaceAll|, \verb|reverse| and finite transducer remain unchanged. OstrichCEA is written in Scala and based on the SMT solver Princess\cite{princess}.
\subsection{Benchmarks}
We conducted a comparison on four sets of benchmarks based on regex with bounded repetition, consisting of a total of 49,379 instances. We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with bounded repetition. In total, almost 18\% of the instances we evaluated were sourced from published industrial benchmarks or other solver developers. All the other instances contain regular expressions from the real world. Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large repetition upper bounds (the sum of upper bounds is greater than 50), and "small" contains the other instances. Less than 10\% of the benchmarks are in a "large" set. More details about the benchmarks are shown below.
\subsubsection{AutomatArk} is the 8,751 instances generated by Berzish et al.\cite{z3str3re}. It is based on real-world regular expression queries from Loris D'Antoni\cite{automatark}. The origin set comprises two tracks, a simple and a hard track, with 19,979 instances. The simple track contains instances with a single regular expression membership constraint, whereas the hard track can hold up to five membership constraints for a single variable per instance. We extract 8,751 instances containing bounded repetition from 19,979 instances and partition them into "large" and "small" in terms of the size of the bounds.
\subsubsection{ReDos} is the set of 1,624 instances we generated. It is based on the ReDos-attacked regular expression collected by Lenka et al. For each regular expression, we generate an instance as the template (\ref{eq:template}) where $\regex$ is the regular expression. The regular membership predicate $x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*$ sanitizes the input string $x$ to avoid the attack. The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
\subsubsection{RegexLib} is the set of 1,623 instances we generated similarly to the \textbf{ReDos} benchmark. It is based on the regular expressions collected by James C. Davis et al.\cite{regex_lingua_franca} from regex lib website\cite{regexlib}. The website is the Internet's first Regular Expression Library. Currently, it has indexed 4149 expressions from 2818 contributors around the world since 2001. We extract 1,623 instances containing bounded repetition from 4149 instances and partition them into "large" and "small" in terms of the size of the bounds.
\subsubsection{StackOverflow} is the 37381 instances we generated similarly to the \textbf{ReDos} benchmark. As the Regexlib benchmark, the real-world regex expressions are collected by James C. Davis et al.\cite{regex_lingua_franca} from StackOverflow website\cite{stackoverflow}. The website is a question-and-answer site for professional and enthusiast programmers. We extract 37,381 instances containing bounded repetition from almost 500,000 instances and partition them into "large" and "small" in terms of the size of the bounds.
\begin{equation} \label{eq:template}
  x\in \regex \wedge x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*\wedge |x| > 50(20)
\end{equation}
\subsection{Experimental Setup and Compared Solvers}
We have evaluated OstrichCEA compared to five other prominent string solvers currently available. We evaluate the solvers by directly comparing the number of cases correctly solved, the total time taken with and without timeouts, and the total count of soundness errors and program crashes. One of these solvers is CVC5\cite{cvc5}, a general SMT solver that uses algebraic reasoning to handle strings and regular expressions and is the winner of SMT-COMP 2022\cite{smt-comp}. Another solver, Z3str3\cite{z3str3}, is the most recent addition to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions. Z3str3RE\cite{z3str3re} is a variant of Z3str3 that incorporates length-aware algorithms and heuristics. Z3seq\cite{z3seq} is a sequence solver which uses a novel derivative theory for solving extended regular expressions. Z3-Trau\cite{z3trau} is the Z3 version of trau\cite{trau} that employs a flat automata-based approach, incorporating both under- and over-approximations. Finally, Ostrich\cite{ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships. We used the 1.0.5 binary version of CVC5, commit 59e9c87 of Z3str3, last version of Z3str3RE, 4.8.9 binary version of Z3Seq, commit 1628747 of Z3-Trau and commit 8297d8d of Ostrich. Z3-Trau does not support \verb|re.diff|. All other solvers support all syntax sugars listed in SMT-LIB standard\cite{smt_lib}. We omitted Z3str4\cite{z3str4} because the provided reproduction package link is wrong. All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY CPU T 3.10GHz processors and 190 GB memory. We used Zaligvinder\cite{zaligvinder_2021} framework and set the timeout to 60 seconds. 
\subsection{Overall Evaluation}
In Fig.\ref{fig:cactus_all}, the cactus plot illustrates the cumulative time each solver takes for all cases in ascending order of runtime. Solvers located towards the right and lower portion of the plot indicate better performance. OstrichCEA spent more time solving instances than other solvers. One reason was that OstrichCEA was written in Scala and ran on a Java virtual machine(JVM). The cold boot of JVM is cost. The other reason was that the implemented decision procedure was excessively cumbersome in resolving certain straightforward constraints. \newline
Table \ref{tab:results_all} summarizes the results that demonstrate OstrichCEA's superior performance, solving most instances and outperforming most competing solvers. OstrichCEA is \textbf{0.98}\mult{} faster than Z3str3RE (with timeouts), \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3 and \textbf{3.11}\mult{} faster than CVC5. Note that CVC5\cite{cvc5} yielded 5370 timeouts(11\% of all instances), and Z3str3\cite{z3str3} yielded 6139 timeouts(12\% of all instances), which is much more than other solvers. Both CVC5 and Z3str3 are DPLL(T)-based solvers. It seems that almost 10\% of the benchmarks we used seem unsuitable for them. Z3-trau\cite{z3trau} yielded 21,152 unknowns because it does not support \verb|re.diff|. Z3-trau\cite{z3trau} yielded 6673 crashes (13\% of the instances) and 1233 soundness errors (2\% of the instances), which is a large portion. Z3-based solvers Z3str3 yielded 38 soundness errors, Z3seq\cite{z3seq} yielded 51 soundness errors and Z3str3RE\cite{z3str3re} yielded 39 soundness error. Most of them are due to the mistake formalization of the backslash character. OstrichCEA resulted 5 unknowns because it reached the maximum threshold of limited memory 2GB.

\begin{figure}[h]
  \centering
  \import{figures}{cactus_plot_all.tex}
  \caption{Cactus plot summarizing performance on all benchmarks.}
  \label{fig:cactus_all}
\end{figure}
\begin{table}
  \import{tables}{table_all.tex}
  \caption{Total results of string solvers on all benchmarks. OstrichCEA solved the most benchmarks in the second shortest time.}
  \label{tab:results_all}
\end{table}

\subsection{Detailed Evaluation}
The detailed results for the \textbf{AutomatArk} benchmark are presented in Figure \ref{fig:cactus_automatrk} and Table \ref{tab:results_automatrk}. OstrichCEA solved the most \emph{unsat} instances. Z3str3RE solved the most \emph{sat} instances. Ostrich solved the greatest number of instances, while Z3str3RE used the least time with timeouts.\newline
The detailed results for the \textbf{Redos} benchmark are presented in Figure \ref{fig:cactus_redos} and Table \ref{tab:results_redos}. OstrichCEA solved the most \emph{sat} and \emph{unsat} benchmark. Z3str3RE used the least time in total. \newline 
The detailed results for the \textbf{RegexLib} benchmark are presented in Figure \ref{fig:cactus_regexlib} and Table \ref{tab:results_regexlib}. Ostrich solved the most \emph{unsat} benchmarks. OstrichCEA solved the most \emph{sat} benchmarks. OstrichCEA solved the most benchmarks in total.  Z3str3RE used the least time in total. \newline
The detailed results for the \textbf{StackOverflow} benchmark are presented in Figure \ref{fig:cactus_stackoverflow} and Table \ref{tab:results_stackoverflow}. OstrichCEA solved the most benchmarks and used the least time in total.\newline
\begin{figure}
  \centering
  \subimport{figures}{cactus_plot_automatark.tex}
  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the AutomatArk benchmark.}
  \label{fig:cactus_automatrk}
\end{figure}
\begin{table}
  \subimport{tables}{table_automatark.tex}
  \caption{Detailed results for the AutomatArk benchmark.}
  \label{tab:results_automatrk}
\end{table}

\begin{figure}
  \subimport{figures}{cactus_plot_redos.tex}
  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the ReDos benchmark.}
  \label{fig:cactus_redos}
\end{figure}
\begin{table}
  \subimport{tables}{table_redos.tex}
  \caption{Detailed results for the ReDos benchmark.}
  \label{tab:results_redos}
\end{table}

\begin{figure}
  \subimport{figures}{cactus_plot_regexlib.tex}
  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the RegexLib benchmark.}
  \label{fig:cactus_regexlib}
\end{figure}
\begin{table}
  \subimport{tables}{table_regexlib.tex}
  \caption{Detailed results for the RegexLib benchmark.}
  \label{tab:results_regexlib}
\end{table}

\begin{figure}
  \subimport{figures/}{cactus_plot_stackoverflow.tex}
  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the StackOverflow benchmark.}
  \label{fig:cactus_stackoverflow}
\end{figure}
\begin{table}
  \subimport{tables}{table_stackoverflow.tex}
  \caption{Detailed results for the StackOverflow benchmark.}
  \label{tab:results_stackoverflow}
\end{table}
\subsection{Analysis of Individual Heuristics}
In order to demonstrate the efficacy of the individual heuristics outlined in Section \ref{sec:algorithm} and incorporated into OstrichCEA, we assessed various tool configurations in which one or more heuristics were disabled. Figure \ref{fig:cactus_heuristics} and Table \ref{tab:results_heuristics} display the outcomes. The "OstrichCEA" plot line represents the tool's performance when all heuristics are enabled, while the "All heuristics off" line represents performance when all heuristics are disabled. The remaining plot lines exhibit performance with only the named heuristic disabled while all others are enabled. From the plots and table, it is evident that OstrichCEA functions most effectively when all heuristics are enabled. OstrichCEA performs 1.78 times faster when employing all of our heuristics than none. All other configurations of the tool's heuristics make sense in comparison.
\begin{figure}
  \subimport{figures/}{cactus_plot_heuristic.tex}
  \caption{A performance comparison was made on all benchmarks by disabling individual heuristics using a cactus plot.}
  \label{fig:cactus_heuristics}
\end{figure}
\begin{table}
  \subimport{tables}{table_heuristic.tex}
  \caption{A performance comparison was made on all benchmarks by disabling individual heuristics.}
  \label{tab:results_heuristics}
\end{table}

\end{document}

### 2023-04-11 2023-1-19/sections/introduction.tex
atva2023 first version

\documentclass[11pt]{standalone}
\begin{document}

String constraint solving is a subfield of computer science that deals with analyzing and manipulating strings, which are sequences of characters. String constraints solving aim to automatically infer properties of string variables, such as their length, content, and structure, to reason about the behavior of software systems that manipulate strings. It is crucial in security-critical applications, where strings represent sensitive data such as passwords, user input, and network addresses. String constraints solving combines techniques from formal methods, automata theory, and constraint solving and has many applications in areas such as software testing\cite{software_testing_1}\cite{software_testing_2}, program analysis\cite{prog_analysis_1}\cite{prog_analysis_2}\cite{prog_analysis_3}, and malware detection\cite{malware_detection_1}\cite{malware_detection_2}\cite{malware_detection_3_kudzu}. In this context, efficient algorithms and tools for solving string constraints are crucial to improve the security and reliability of modern software systems.\newline
Regular expressions are widely used in programming languages. About 30–40 \%
Java, JavaScript, and Python software use regex matching\cite{redos_fse2019}. Bounded repetition is widely used in regex matching\cite{regex_repeat} and is dangerous because Regular expression Denial of Service (ReDoS) may derive from it\cite{redos_lenka}. We have analyzed regular expressions sourced from the Internet\cite{regexlib}\cite{stackoverflow}, among which about 10\% include bounded repetition. Operations like \verb|length| that take string inputs and return an integer frequently appear in real-world JavaScript applications (78\% of string operations in 18 applications\cite{malware_detection_3_kudzu}). These statistics show that a resultful string solver reasoning about regular membership predicate with bounded repetition and \verb|length| operation is required. However, when the string constraints contain bounded repetition and lower bound on string variables, the state-of-art string solvers (\cite{z3seq}\cite{z3str3}\cite{z3str4}\cite{z3str3re}\cite{cvc5}\cite{ostrich}\cite{z3trau}\cite{trau}) lose efficiency. For example, CVC5\cite{cvc5} (which is the winner of QF\_Strings track in SMT-COMP 2022\cite{smt-comp}) failed to solve string constraints (\ref{eq:cvc5_timeout}) with timeout 60s.
\begin{equation} \label{eq:cvc5_timeout}
  x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^*
\end{equation}
$\Sigma_{/a}\{1,300\}$ repeats a letter excluding $a$ from one time to 300 times. $\Sigma^*a\Sigma^*$ accepts a string containing $a$. It is easy to see that the string constraints are unsat. Nevertheless, CVC5 is hard to find a solution for it can not answer unsat until attempting all strings with lengths less than or equal to 300. The number of the searched string is exponential. Z3str3RE\cite{z3str3re} can not solve string constraints (\ref{eq:z3str3re_timeout}) because its length abstraction is over-approximation.
\begin{equation}\label{eq:z3str3re_timeout}
  x\in \Sigma_{/a}\{13,13\}\wedge |x| > 13
\end{equation}
On account of the large automaton corresponding to the regular expression, Ostrich(+)\cite{ostrich}\cite{atva2020} crashes on string constraints (\ref{eq:ostrich_timeout}) where $\Sigma_{[0-9A-Za-z]}$ is a digital letter or an English letter.
\begin{equation}\label{eq:ostrich_timeout}
  x\in \Sigma_{[0-9A-Za-z]}\{0, 63\}\wedge |x| > 0
\end{equation}
To address these issues, we formalize bounded repetition using cost-enriched finite automaton (CEFA)\cite{atva2020} with linear arithmetical constraints. It limits the max(min) run times of some transitions on the accepting run of the automaton, which completely captures the semantics of bounded repetition. The satisfiability problem of string constraints with bounded repetition is reduced to the emptiness problem of cost-enriched finite automata under linear arithmetical constraints (abbreviated as $SAT_{CL}$ problem), which is decidable and can be solved by our previous work \cite{atva2020}. However, the previous work could perform better practically, especially when regular expressions are complex. In this paper, we propose two heuristical methods to improve performance. The first one is under-approximation, which is inspired by Bounded Model Checking \cite{bmc_1}\cite{bmc_2}\cite{bmc_3}. The second one is the symbolic-aware simplification, which is motivated by the observation that the emptiness problem is only related to the symbolic update functions. We implement a powerful string solver OstrichCEA and evaluate it on instances from the real world and other typical benchmarks. The experiment result shows superiority.

\subsubsection{Related Work}
To handle the problems in software verification reasoning about strings and integers, string theories with regular membership predicate and linear length constraints are raised. String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, Z3Str3RE\cite{z3str3re}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories. Although string theory is easily
undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_z3str3re}. There are mainly two strategies for solving string constraints: (1) DPLL(T)-based\cite{dpll_t} string solvers\cite{z3str3}\cite{cvc5} apply heuristic derivation rules to unwind the regular expression gradually and identify several classes of simplification techniques for efficiency. (2) Automata-based string solvers\cite{trau}\cite{z3trau}\cite{ostrich}\cite{atva2020}\cite{z3str3re} construct a finite automaton to model the regular expression and use the emptiness problem of the automaton (under linear integer arithmetic) to decide the satisfiability of string constraints.

\subsubsection{Our Contributions}
Our main contributions are as follows:
\begin{enumerate}
  \item  Encode regular expression with bounded repetition into CEFA with linear arithmetical constraints.
  \item  Devise heuristic methods like under-approximation and symbolic-aware simplification to solve the $SAT_{CL}$ problem.
  \item  Generate significant instances with bounded repetition from real-world regular expressions.
  \item  Implement our decision procedure on solver OstrichCEA and compare it with state-of-art string solvers. The result shows the superiority of our encoding and heuristics.
\end{enumerate}

The rest of the paper is structured as follows: Section \ref{sec:pre} introduces the preliminaries. Section \ref{sec:overview} outlines the overall algorithm. Section \ref{sec:regex2acfa} illustrates how to construct an automaton from a regular expression. Section \ref{sec:algorithm} shows how to solve a string constraint with repetition. Section \ref{sec:implementation} presents the experimental results. Section \ref{sec:conclu} concludes the paper and discusses future work.

\end{document}

### 2023-04-11 2023-1-19/sections/overview.tex
atva2023 first version

The main idea is to use CEFAs (see Subsection \ref{subsec:cefa}) to simulate the semantics of length operations and regular memberships with bounded repetitions. As mentioned, the ESL formula contains regular literals and linear literals. The regular literal $x\in \regex$ directly results in one CEFA recognizing it (see Subsection \ref{subsec:regex2cefa}). The linear literals $\alpha_1 \leq \alpha_2$ with no length operation remain unchanged. For each linear literal $\alpha_1 \leq \alpha_2$ with length operation $|x|$, we generate a fresh variable $i$ to replace all occurrences of $|x|$ and propagate new formula $i=|x|$. Then we generate the pre-image $\aut_{i}$ whose accepting words are strings with length $i$ (see Example \ref{eg:pre_len}). After the process above, the satisfiability problem of string constraints becomes a $SAT_{CL}$ problem, which has a decision procedure to check (see Subsection \ref{subsec:emptiness}). Example \ref{example:overview} illustrate it. \newline

\begin{example} \label{example:overview}
  \begin{align*}
    \varphi\equiv x\in (ab)\{1,100\}\wedge y\in ab\wedge |x| > |y|
  \end{align*}
  ESL conjunction $\varphi$ is made up of regular literals $x\in (ab)\{1,100\}$ and $y\in ab$, linear literals $|x| > |y|$. The linear literal is translated to $i = |x|\wedge j = |y| \wedge i > j$. Our algorithm solves the formula in four steps. First, we construct CEFAs for regular memberships $x\in (ab)\{1,100\}$ and $y\in ab$ (Fig.\ref{subfig:aut_ab1-100} and Fig.\ref{subfig:aut_ab}). Second, we compute the pre-images of length operations $i=|x|$ and $j=|y|$ (Fig.\ref{subfig:preimage_x} and Fig.\ref{subfig:preimage_y}). Then we intersect pre-images to automata corresponding to the regular memberships for each string variable (Fig.\ref{subfig:aut_x} and Fig.\ref{subfig:aut_y}). We translate the satisfiability problem of $\varphi$ to the emptiness checking problem of automata (Fig.\ref{subfig:preimage_x} and Fig.\ref{subfig:preimage_y}) under linear arithmetic constants $i > y$, which could be solved by the decision procedure illustrated in section \ref{sec:algorithm}.

  \begin{figure}[h]
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=$1\leq r_1\leq 100$, accepting/.style=accepting by arrow,
        accepting where=above
        ]

        \node[state,initial]            (q_0)                      {};
        \node[state]                    (q_1) [right=of q_0]       {};
        \node[state,accepting]          (q_2) [right=of q_1]       {};

        \path[->] (q_0) edge              node      [above]           {$a$/(1)} (q_1)
        (q_1) edge              node      [above]           {$b$/(0)} (q_2)
        (q_2) edge [bend left]  node      [below]           {$a$/(1)} (q_1);
      \end{tikzpicture}
      \caption{The CEFA recognizing $(ab)\{1,100\}$}
      \label{subfig:aut_ab1-100}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=$\top$, accepting/.style=accepting by arrow,
        accepting where=above
        ]

        \node[state,initial]            (q_0)                      {};
        \node[state]                    (q_1) [right=of q_0]       {};
        \node[state, accepting]         (q_2) [right=of q_1]       {};

        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
        (q_1) edge              node      [above]           {$b$/()} (q_2);
      \end{tikzpicture}
      \caption{The CEFA recognizing $ab$}
      \label{subfig:aut_ab}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=${r_2 = i}$, accepting/.style=accepting by arrow,
        ]

        \node[state,initial,accepting]            (q_0)       {};

        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
      \end{tikzpicture}
      \caption{The pre-image of $i = |x|$}
      \label{subfig:preimage_x}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=${r_3 = j}$, accepting/.style=accepting by arrow,
        ]

        \node[state,initial,accepting]            (q_0)       {};

        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} (1);
      \end{tikzpicture}
      \caption{The pre-image of $j = |y|$}
      \label{subfig:preimage_y}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=${r_2 = i\wedge 1\leq r_1 \leq 100}$, accepting/.style=accepting by arrow,
        accepting where=above
        ]

        \node[state,initial]            (q_0)                      {};
        \node[state]                    (q_1) [right=of q_0]       {};
        \node[state,accepting]          (q_2) [right=of q_1]       {};

        \path[->] (q_0) edge node [above]  {$a$/(1,1)} (q_1)
        (q_1) edge           node [above]  {$b$/(0,1)} (q_2)
        (q_2) edge [bend left]  node      [below]           {$a$/(1,1)} (q_1);
      \end{tikzpicture}
      \caption{The final automaton of $x$}
      \label{subfig:aut_x}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \begin{tikzpicture}[
        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
        initial text=, every state/.style={minimum size = 0.001cm},
        accepting text=${r_3=j}$, accepting/.style=accepting by arrow,
        accepting where=above
        ]

        \node[state,initial]            (q_0)                      {};
        \node[state]                    (q_1) [right=of q_0]       {};
        \node[state, accepting]         (q_2) [right=of q_1]       {};

        \path[->] (q_0) edge    node      [above]           {$a$/(1)} (q_1)
        (q_1) edge              node      [above]           {$b$/(1)} (q_2);
      \end{tikzpicture}
      \caption{The final automaton of $y$}
      \label{subfig:aut_y}
    \end{subfigure}
    \caption{All automata used in the example \ref{example:overview}}
  \end{figure}

\end{example}

% \pagebreak

### 2023-04-11 2023-1-19/sections/preliminaries.tex
atva2023 first version

\documentclass{standalone}
\begin{document}

% Tokens
\subsubsection{Tokens}
A finite \emph{alphabet} $\Sigma$ is the set of all \emph{letters}. A
\emph{string} (or \emph{word}) is a finite sequence of letters from $\Sigma$. $\Sigma^*$ is the set of strings over $\Sigma$. $\epsilon$ is the empty string. $L$ is grammar. A language $\lan(L)$ is a set of words generated by $L$. $\mathbb{N}$ is the set of natural numbers and $\mathbb{Z}$ is the set of integer numbers. We use $a,
  b,\cdots$ to denote the constant letters in $\Sigma$, $u, v,\cdots$ to denote constant
string, $x, y,\cdots$ to denote variable string, $m,n,\cdots$ to
denote integer constant, and $i,j\cdots$ to denote integer variable. For vector, we use $\myvec{v}$ to denote the vector of integer constant, $m_n$ to denote the vector $(m,\cdots, m)$ with length $n$, $\myvec{v}[i]$ to denote the integer value of $\myvec{v}$ at position $i$, $\myvec{v_1}\cdot\myvec{v_2}$ to denote the concatenation of $\myvec{v_1}$ and $\myvec{v_2}$, $R$ to denote the vector of registers, $R_1 \cap R_2$ to denote the same registers in $R_1$ and $R_2$, and $|\myvec{v}|$ or $|R|$ to denote the length of the vector.

\subsubsection{Syntax}
This paper proposes a quantifier-free first-order logic called \textit{Extended String Logic (ESL)}, whose syntax is presented in Table \ref{tab:syntax}. $\varphi$ is a quantifier-free formula that can be a regular membership $x\in\regex$, a quantifier-free Presburger formula $\alpha_1 \leq \alpha_2$, a negation of a formula, or a disjunction of two formulas. $\alpha$ is an integer term which can be an integer constant $m$, integer variable $i$, the length of the string term $|s|$, the minus of an integer term, and the plus of two integer terms. The regular expression $\regex$ is built on empty string $\epsilon$, constant letter $a\in \Sigma$. The supported regex operations involve concatenation $\cdot$, disjunction $+$, intersection $\times$, closure $*$, complement $C$, and bounded repetition $\{m, n\}$. We use $term(\varphi)$ to denote the set of terms and $strvar(\varphi)$ to denote the string variables occurring in $\varphi$. The \emph{literals} of $\varphi$ are $x\in \regex$ and $\alpha_1 \leq \alpha_2$. $x\in \regex$ is called \emph{regular literals} and $\alpha_1 \leq \alpha_2$ is called \emph{linear literals}.
\begin{table}[h]
  \centering
  \begin{tabular}{l r}
    $\varphi$ ::= $x\in \regex \mid \alpha_1\leq\alpha_2 \mid \neg\varphi\mid \varphi\vee\varphi$                                             & formulae            \\
    $\regex$ ::= $\epsilon\mid a\mid \regex\cdot\regex\mid \regex+\regex\mid \regex\times \regex\mid \regex^*\mid\regex^C \mid \regex\{m,n\}$ & regular expressions \\
    $\alpha$ ::= $m \mid i \mid  |s|\mid -\alpha\mid \alpha_1+\alpha_2$                                                                       & integer terms
  \end{tabular}
  \caption{Syntax}\label{tab:syntax}
\end{table}
% Semantic 
\subsubsection{Semantic}
We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables. $\eta: S\times\Sigma\rightarrow\Sigma^*$ is the interpretation on string where $\eta(c)=c$ for every letter $c\in \Sigma$. $\pi: I\rightarrow\mathbb{Z}$ is the interpretation of Presburger arithmetic. Then the semantics is given by a satisfaction relation: $\eta, \pi\models \varphi$ defined in Table \ref{tab:semantics}. We say a formula $\varphi$ is \emph{satisfiable} if a solution $(\eta, \pi)$ exists such as $\eta, \pi\models \varphi$. A formula $\varphi$ is \emph{unsatisfiable} if no solution exists.
\begin{table}[h]
  \centering
  \begin{tabular}{lcl}
    $\eta,\pi \models \varphi_1\vee \varphi_2$ & $\mathsf{iff}$ & $\eta,\pi \models \varphi_1 \text{ or } \eta,\pi \models \varphi_2$ \\
    $\eta,\pi \models \neg\varphi $            & $\mathsf{iff}$ & $\eta,\pi \not\models \varphi$                                      \\
    $\eta, \pi \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan(\regex),\eta,\pi \models x = w$                 \\
    $\eta, \pi \models \alpha_1 \leq \alpha_2$ & $\mathsf{iff}$ & $\pi(\alpha_1) \leq \pi(\alpha_2) $                                 \\
  \end{tabular}
  \caption{Semantics}
  \label{tab:semantics}
\end{table}
In addition to the classic regex operators (union, concatenation, closure), we syntactically support intersection, complement, and repetition. As we all know, the classic regular language is closed under intersection and complement \cite{aut_hopcraft}. Furthermore, the operation \emph{repetition} $\regex\{m,n\}$ means repeating regex $\regex$ at least $m$ times and at most $n$ times. It can be syntactically rewritten by concatenation and union:
$\regex\{m,n\} \equiv \regex^m\mid\cdots\mid\regex^n$ where $\regex^k$ defines concatenate $\regex$ $k$ times ($m\leq k\leq n$). So the regular language $\lan(\regex)$ defined in Table \ref{tab:syntax} is semantically equal to the classic regular language.

\end{document}

### 2023-04-23 2023-1-19/sections/implementation.tex
revise implementation

@@
 \newline
-Table \ref{tab:results_all} summarizes the results that demonstrate OstrichCEA's superior performance, solving most instances and outperforming most competing solvers.
-OstrichCEA is \textbf{0.98}\mult{} faster than Z3str3RE (with timeouts), \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3 and \textbf{3.11}\mult{} faster than CVC5.
+Table \ref{tab:results_all} summarizes the results that demonstrate OstrichCEA's superior performance, solving the most significant number of instances and outperforming most competing solvers.
+Including timeouts, OstrichCEA is \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3, \textbf{3.11}\mult{} faster than CVC5 and close to Z3str3RE with \%2 speed loss .
 Note that CVC5\cite{cvc5} yielded 5370 timeouts(11\% of all instances), and Z3str3\cite{z3str3} yielded 6139 timeouts(12\% of all instances), which is much more than other solvers.
@@
 The detailed results for the \textbf{Redos} benchmark are presented in Figure \ref{fig:cactus_redos} and Table \ref{tab:results_redos}.
-OstrichCEA solved the most \emph{sat} and \emph{unsat} benchmark.
-Z3str3RE used the least time in total.
+OstrichCEA solved the most instances on both tracks of \emph{sat} and \emph{unsat}.
+Including timeouts, OstrichCEA is \textbf{4.4}\mult{} faster than CVC5, \textbf{3.74}\mult{} faster than Ostrich, \textbf{2.09}\mult{} faster than Z3str3, \textbf{5.40}\mult{} faster than Z3seq, \textbf{2.49}\mult{} faster than Z3-Trau and close to Z3str3RE with \%20 speed loss.
 \newline
 The detailed results for the \textbf{RegexLib} benchmark are presented in Figure \ref{fig:cactus_regexlib} and Table \ref{tab:results_regexlib}.
-Ostrich solved the most \emph{unsat} benchmarks.
-OstrichCEA solved the most \emph{sat} benchmarks.
-OstrichCEA solved the most benchmarks in total.
-Z3str3RE used the least time in total.
+Ostrich solved the most \emph{unsat} instances.
+OstrichCEA solved the most \emph{sat} instances.
+In total, OstrichCEA solved the greatest number of instances and was the solver with medium speed.
 \newline
 The detailed results for the \textbf{StackOverflow} benchmark are presented in Figure \ref{fig:cactus_stackoverflow} and Table \ref{tab:results_stackoverflow}.
-OstrichCEA solved the most benchmarks and used the least time in total.\newline
+OstrichCEA solved the most instances on both tracks of \emph{sat} and \emph{unsat} and was the faster solver.\newline Including timeouts, OstrichCEA is \textbf{3.98}\mult{} faster than CVC5, \textbf{2.63}\mult{} faster than Ostrich, \textbf{2.19}\mult{} faster than Z3str3, \textbf{1.59}\mult{} faster than Z3seq, \textbf{1.28}\mult{} faster than CVC5 and \textbf{1.47}\mult{} to Z3str3RE.
+\newline
 \begin{figure}

### 2023-04-23 2023-1-19/sections/abstract.tex
title and abstract

@@
 \begin{document}
-Regular expression with repetition frequently appears in the real world, such as $(ab)\{1, 100\}$. However, state-of-art string
-solvers can not efficiently solve string constraints with repetition bounds,
-especially when the repetition bounds are large. This paper focuses on
-string logic containing regular membership predicate with repetition
-and linear integer constraints on string length. Repetition is captured
-by cost-enriched finite automaton(CEFA), whose transitions have symbolic updates of integers limited by linear arithmetic. We propose a new systematic algorithm based on CEFA, and heuristic ways
-like under-approximation and symbolic-aware simplification are used to
-accelerate. We implement a powerful string solver OstrichCEA and
-evaluate it on instances from the real world and other typical benchmarks.
-The experiment result shows superiority.
+
+Regular expressions (abbreviated as regex) and string-length function are widely used in string-manipulating programs. 
+%Solving string constraints involving regular membership and string-length function has been widely investigated. 
+Counting is a frequently used feature of regular expressions that count the number of occurrences of sub-patterns.
+The state-of-the-art string solvers e.g.
+CVC4/5, Z3str3(RE), and Z3seq are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bound is large.
+In this work, we propose an automata-theoretic approach for solving such class of string constraints efficiently.
+%
+The main idea is to model the counting operators symbolically by registers, instead of unfolding them explicitly, thus alleviating the state explosion problem resulted from the unfolding.  
+%
+Moreover, we model the string lengths by registers as well.
+As a result, solving string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, since linear integer arithmetic formulas can be computed from automata to represent their Parikh images.
+%
+%we extract linear integer arithmetic formulas from automata, which encode the constraints on the values of registers, and utilize the off-the-shelf SMT solvers to solve the linear integer arithmetic constraints.
+%
+Furthermore, to improve the performance further, on the one hand, we propose techniques to reduce automata sizes, thus reducing the sizes of linear arithmetic formulas computed from automata as well, and on the other hand, we utilize under approximations to search for solutions.
+% we propose state reduction techniques and under approximation to improve the performance further. 
+We implement the algorithms and do extensive experiments to validate this approach.
+The experimental results show better performance of this approach compared against the state-of-the-art string solvers.
+
+%Regular expression with repetition frequently appears in the real world, such as $(ab)\{1, 100\}$. However, state-of-art string
+%solvers can not efficiently solve string constraints with repetition bounds,
+%especially when the repetition bounds are large. This paper focuses on
+%string logic containing regular membership predicate with repetition
+%and linear integer constraints on string length. Repetition is captured
+%by cost-enriched finite automaton(CEFA), whose transitions have symbolic updates of integers limited by linear arithmetic. We propose a new systematic algorithm based on CEFA, and heuristic ways
+%like under-approximation and symbolic-aware simplification are used to
+%accelerate. We implement a powerful string solver OstrichCEA and
+%evaluate it on instances from the real world and other typical benchmarks.
+%The experiment result shows superiority.
 

### 2023-04-23 2023-1-19/sections/abstract.tex
title and abstract

@@
 %
-Furthermore, to improve the performance further, on the one hand, we propose techniques to reduce automata sizes, thus reducing the sizes of linear arithmetic formulas computed from automata as well, and on the other hand, we utilize under approximations to search for solutions.
+To improve the performance further, on the one hand, we propose techniques to reduce automata sizes, thus reducing the sizes of linear arithmetic formulas computed from automata as well, and on the other hand, we utilize under approximations to search for solutions.
 % we propose state reduction techniques and under approximation to improve the performance further. 

### 2023-04-23 2023-1-19/sections/introduction.tex
revise bib
partially revised introduction

@@
 These statistics show that a resultful string solver reasoning about regular membership predicate with bounded repetition and \verb|length| operation is required.
-However, when the string constraints contain bounded repetition and lower bound on string variables, the state-of-art string solvers (\cite{z3seq}\cite{z3str3}\cite{z3str4}\cite{z3str3re}\cite{cvc5}\cite{ostrich}\cite{z3trau}\cite{trau}) lose efficiency.
-For example, CVC5\cite{cvc5} (which is the winner of QF\_Strings track in SMT-COMP 2022\cite{smt-comp}) failed to solve string constraints (\ref{eq:cvc5_timeout}) with timeout 60s.
+However, such string constraints may lead to low performance.
+% the state-of-art string solvers (\cite{z3seq}\cite{z3str3}\cite{z3str4}\cite{z3str3re}\cite{cvc5}\cite{ostrich}\cite{z3trau}\cite{trau}) lose efficiency. 
+For CVC5\cite{cvc5} (which is the winner of QF\_Strings track in SMT-COMP 2022\cite{smt-comp}), the string constraints are solved based on DPLL(T) structure.
+Each string constraint is seen as a literal boolean and assigned by true or false (Boolean abstraction).
+CVC5 repeatedly applies derivation rules on these assigned string constraints until the satisfiable solution is found or unsatisfiability is detected.
+The approach is fast and sound.
+Nevertheless, it is incomplete because it may not recognize unsatisfiable literals and may not terminate when unrolling regular expression.
+For example, CVC5 unrolls regular expression $\Sigma_{/a}\{1,300\}$ and $\Sigma^*a\Sigma^*$ when solving the string constraints \ref{eq:cvc5_timeout}.
+$\Sigma_{/a}\{1,300\}$ repeats a letter excluding $a$ from one time to 300 times.
+$\Sigma^*a\Sigma^*$ accepts a string containing $a$.
+It is easy to see that the string constraints are unsat.
+However, CVC5 is hard to explore the unsatisfiability, for it can only answer once attempting all strings with lengths less than or equal to 300.
+The number of the searched string is exponential to the count.
+We test this instance on CVC5 and get a timeout result when the timeout is set to 60s.
 \begin{equation} \label{eq:cvc5_timeout}
@@
 \end{equation}
-$\Sigma_{/a}\{1,300\}$ repeats a letter excluding $a$ from one time to 300 times.
-$\Sigma^*a\Sigma^*$ accepts a string containing $a$.
-It is easy to see that the string constraints are unsat.
-Nevertheless, CVC5 is hard to find a solution for it can not answer unsat until attempting all strings with lengths less than or equal to 300.
-The number of the searched string is exponential.
-Z3str3RE\cite{z3str3re} can not solve string constraints (\ref{eq:z3str3re_timeout}) because its length abstraction is over-approximation.
+Z3Str3\cite{z3str3} is a string solver written on the famous SMT solver Z3\cite{z3}.
+It is based on the DPLL(T) structure and uses the same approach as CVC5, except that the derivation rules of Z3 differ from CVC5.
+Furthermore, Z3str3 exposes the structure of theory literals to the DPLL(T) SAT solver's branching heuristic, resulting in smarter decisions during its search.
+Z3Str3 can not solve string constraints (\ref{eq:cvc5_timeout}) as well because the optimization can not avoid the endless unwind of the regular expression.
+To handle the exponential search space of regular expression, automata-based methods were proposed.
+One of the automata-based string solver Ostrich\cite{ostrich}\cite{atva2020} encodes string constraints and regular expressions into automata and use the automata theory to solve them.
+It is sound and complete.
+But it is inefficient because it is hard to reduce the size of automata.
+When large counting is constrained on a complex sub-regex, like $ \backslash w \{1, 63\}$ where $\backslash w$ is an English character or a number character, the corresponding automaton in Ostrich becomes very large and can not be solved within 60s time limit.
+The reason is that Ostrich syntactically rewrites the counting operator to the union of finite repeatings of the sub-regex.
+For example, $\backslash w\{1, 63\}$ is rewritten to $\backslash w\mid\backslash w^2\cdots\mid\backslash w^{63}$ where $\backslash w^i$ means repeat $i\-th$ times on $\backslash w$.
+The automaton of $\backslash w$ contains $62$ states to accept each possible character, and the automaton of $\backslash w ^i$ contains $62*i$ states.
+The total number of states in the automaton is $62 + 62*2 + \cdots 62*63=124992$, causing the automaton to be unsolvable in practice.
+Trau\cite{z3trau}\cite{trau+} is another powerful automata-based solver.
+It relies on a Counter-Example Guided Abstraction Refinement (CEGAR) framework in which the under- and over-approximation of the automata are iteratively refined.
+Although it uses simple flat automata to represent regular expressions, it has to build unsolvable automata on regex $\backslash w\{1, 63\}$ as Ostrich because the solution of the flat automata should be within the solution of the original automata.
+Recently, Z3str3 has been extended to Z3str3RE\cite{z3str3re} by Berzish et al to handle string constants with regular memberships and length operation effectively.
+It uses automata to formalize the sematic of regular expression and applies several length-aware heuristics.
+Z3str3RE can avoid building unsolvable automaton because the length abstraction is directly derived from the regex, not the automaton.
+Unfortunately, the length abstraction is an over-approximation, so it can not solve string constraints (\ref{eq:z3str3re_timeout}) whose regular membership predicate contains complementary.
 \begin{equation}\label{eq:z3str3re_timeout}
   x\in \Sigma_{/a}\{13,13\}\wedge |x| > 13
-\end{equation}
-On account of the large automaton corresponding to the regular expression, Ostrich(+)\cite{ostrich}\cite{atva2020} crashes on string constraints (\ref{eq:ostrich_timeout}) where $\Sigma_{[0-9A-Za-z]}$ is a digital letter or an English letter.
-\begin{equation}\label{eq:ostrich_timeout}
-  x\in \Sigma_{[0-9A-Za-z]}\{0, 63\}\wedge |x| > 0
 \end{equation}
@@
 Section \ref{sec:overview} outlines the overall algorithm.
-Section \ref{sec:regex2acfa} illustrates how to construct an automaton from a regular expression.
+Section \ref{sec:automaton} illustrates how to construct an automaton from a regular expression.
 Section \ref{sec:algorithm} shows how to solve a string constraint with repetition.

### 2023-04-23 2023-1-19/sections/abstract.tex
fine tune abstract
abstract

@@
-\documentclass{standalone}
-\begin{document}
+%!TEX root = ../main.tex
+
+%\documentclass{standalone}
+%\begin{document}
 
@@
 %Solving string constraints involving regular membership and string-length function has been widely investigated. 
-Counting is a frequently used feature of regular expressions that count the number of occurrences of sub-patterns.
+Counting is a frequently used feature of regular expressions that count the number of matchings of sub-patterns.
 The state-of-the-art string solvers e.g.
-CVC4/5, Z3str3(RE), and Z3seq are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bound is large.
+CVC4/5, Z3str3(RE), and Z3seq are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bounds are large.
 In this work, we propose an automata-theoretic approach for solving such class of string constraints efficiently.
@@
 Moreover, we model the string lengths by registers as well. 
-As a result, solving string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, since linear integer arithmetic formulas can be computed from automata to represent their Parikh images.
+%Since Parikh images of automata can be defined by linear integer arithmetic formulas, 
+As a result, satisfiability of string constraints with regex-counting and string-length is reduced to satisfiability of linear integer arithmetic, which can then be solved by off the shelf SMT solvers.
 %
@@
 To improve the performance further, on the one hand, we propose techniques to reduce automata sizes, thus reducing the sizes of linear arithmetic formulas computed from automata as well, and on the other hand, we utilize under approximations to search for solutions.
-% we propose state reduction techniques and under approximation to improve the performance further. 
+% we propose state reduction techniques and under-approximation to improve the performance further. 
 We implement the algorithms and do extensive experiments to validate this approach.
@@
 
-\keywords{String Constraints, Automaton Theory, Regex Expression, Bounded Repetition, Linear Length Constraints}
-\end{document}
+\keywords{Regex Expressions, Counting, Length, Automata, Registers, Linear Integer Arithmetic}
+%\end{document}

### 2023-04-24 2023-1-19/sections/abstract.tex
abstract

@@
 %
-The main idea is to model the counting operators symbolically by registers, instead of unfolding them explicitly, thus alleviating the state explosion problem resulted from the unfolding.  
+The main idea is to model the counting operators symbolically by registers in automata, instead of unfolding them explicitly, thus alleviating the state explosion problem resulted from the unfolding.
 %
@@
 %Since Parikh images of automata can be defined by linear integer arithmetic formulas, 
-As a result, satisfiability of string constraints with regex-counting and string-length is reduced to satisfiability of linear integer arithmetic, which can then be solved by off the shelf SMT solvers.
+As a result, satisfiability of string constraints with regex-counting and string-length is reduced to satisfiability of linear integer arithmetic (LIA), which can then be solved by off the shelf SMT solvers.
 %
@@
 %
-To improve the performance further, on the one hand, we propose techniques to reduce automata sizes, thus reducing the sizes of linear arithmetic formulas computed from automata as well, and on the other hand, we utilize under approximations to search for solutions.
+To improve the performance further, on the one hand, we propose techniques to reduce automata sizes, 
+%thus reducing the sizes of linear arithmetic formulas computed from automata as well, 
+and on the other hand, we utilize under approximations to search for solutions.   
 % we propose state reduction techniques and under-approximation to improve the performance further. 
-We implement the algorithms and do extensive experiments to validate this approach.
-The experimental results show better performance of this approach compared against the state-of-the-art string solvers.
+We implement the algorithms and do extensive experiments to validate our approach. The experimental results show that 
+our approach can solve more problem instances than the other tools, with the same or a better performance.
+% performance of this approach compared against the state-of-the-art string solvers.
 

### 2023-04-24 2023-1-19/sections/abstract.tex
abstract

@@
 %Since Parikh images of automata can be defined by linear integer arithmetic formulas, 
-As a result, satisfiability of string constraints with regex-counting and string-length is reduced to satisfiability of linear integer arithmetic (LIA), which can then be solved by off the shelf SMT solvers.
+As a result, satisfiability of string constraints with regex-counting and string-length is reduced to satisfiability of linear integer arithmetic, which can then be solved by off the shelf SMT solvers.
 %

### 2023-04-25 2023-1-19/figures/overview_example_simplified.tex
revise overview

  \begin{tikzpicture}[
    shorten >=1pt,node distance=3cm,on grid,>={Stealth[round]},
    initial text=, every state/.style={minimum size = 0.001cm},
    accepting text=$\scriptstyle5\leq r_1\leq 40\wedge 5\leq r_2\leq 40\wedge 0\leq r_3\leq 40\wedge 80 < r_4$, accepting/.style=accepting by arrow,
    accepting where=above
    ]

    \node[state,initial]            (q_0)                      {$q_0$};
    \node[state]                    (q_1) [right=of q_0]       {$q_1$};
    \node[state, accepting]                    (q_2) [right=of q_1]       {$q_2$};

    \path[->] (q_0) edge node [above] {$\scriptstyle a:(1,0,0,1)$} (q_1)
              (q_0) edge [loop below] node  {$\scriptstyle a:(1,0,0,1)$} (q_0)
              (q_1) edge node [above] {$\scriptstyle a:(0,1,0,1)$} (q_2)
              (q_1) edge [loop below] node  {$\scriptstyle a:(0,1,0,1)$} (q_1)
              (q_2) edge [loop below] node  {$\scriptstyle a:(0,0,1,1)$} (q_2);
  \end{tikzpicture}

### 2023-04-25 2023-1-19/sections/introduction.tex
abstract

@@
-\documentclass[11pt]{standalone}
-\begin{document}
+%!TEX root = ../main.tex
+%\documentclass[11pt]{standalone}
+%\begin{document}
+
+In modern programming languages---such as JavaScript, Python, Java, and PHP---the string data type plays a crucial role. 
+It is well-known that string manipulations are error-prone and could even give rise to security vulnerabilities (e.g.\ cross-site scripting, aka XSS). 
+One powerful method for identifying such bugs in programs is \emph{symbolic execution} (possibly in combination with dynamic analysis), which analyses symbolic paths in a program by viewing them as constraints, whose feasibility is checked by constraint solvers.
+%
+Symbolic execution of string manipulating programs have motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade or so including the state-of-the-art string constraint solvers (e.g.
+Z3~\cite{Z3}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
+Z3-Trau~\cite{Z3-trau}, OSTRICH~\cite{CHL+19}, Slent~\cite{WC+18}, among many others.
+
+Regular expressions (abbreviated as regex) and string-length function are widely used in string manipulating programs.
+According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% Java, JavaScript, and Python software projects.
+Moreover, the statistics from \cite{malware_detection_3_kudzu} show that string-length function occupies 78\% of the occurrences of string operations in 18 Javascript applications. 
+%Operations like \verb|length| that take string inputs and return an integer frequently appear in real-world JavaScript applications (78\% of string operations in 18 applications)
+As a result, most of the aforementioned string constraint solvers support both regular expressions and string-length function.
+Moreover, specialized algorithms have been proposed to solve efficiently the class of string constraints with regular expressions and string-length function \cite{LTR+15,BD+23}.
+%a decision procedure based on tableaux calculus was designed  in \cite{LTR+15} for the class of string constraints with regular expressions and string-length function and the decision procedure has been implemented in CVC4/5 \cite{LRT+16}.
+
+Counting (aka repetition) is a convenient feature in regular expressions that count the number of matchings of sub-patterns.
+For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs for at least twice and at most four times and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
+Note that Kleene star and Kleene plus operator can be seen as special cases of counting operator, for instance, $a^*$ and $a^+$ are equivalent to $a^{\{0,\infty\}}$ and $a^{\{1,\infty\}}$.
+Counting is also a frequently used feature of regular expressions.
+According to the statistics from \cite{CS16}, Kleene star/plus occur in over 70\% of the Python projects, while the other forms of counting occur in over 20\% of them.
+
+Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from the string constraints with regex-counting and string-length, especially when the counting bounds are large.
+For instance, none of CVC4/5, Z3, Z3str3RE, OSTRICH is capable of solving the following constraint within 60 seconds,
+%
+\begin{equation}\label{eqn-running}
+x \in (\Sigma \setminus a)^{\{5, 40\}} (\Sigma \setminus b)^{\{5, 40\}} (\Sigma \setminus c)^{\{5, 40\}} \wedge x \in \Sigma^* c \wedge |x| > 80.
+\end{equation}
+Intuitively, the constraint in (\ref{eqn-running}) specifies that $x$ is a concatenation of three subwords $x_1, x_2, x_3$ where $a$ (resp.
+$b, c$) does not occur in $x_1$ (resp.
+$x_2, x_3$), moreover, $x$ ends with $c$, and the length of $x$ is greater than $80$.
+It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 80$ and the counting upper bound $40$ in  both $(\Sigma \setminus a)^{\{5, 40\}}$ and $(\Sigma \setminus b)^{\{5, 40\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c$ requires that $x$ has to end with $c$.
+
+%counting is used in about 6 percent of the regular expressions in Javascript programs.
+
+\paragraph*{Contribution} xxx
+
+\paragraph*{Related work} xx
+
+\paragraph*{Organization} xxx
+
+\zhilin{stopped here}
 
@@
 However, such string constraints may lead to low performance.
-% the state-of-art string solvers (\cite{z3seq}\cite{z3str3}\cite{z3str4}\cite{z3str3re}\cite{cvc5}\cite{ostrich}\cite{z3trau}\cite{trau}) lose efficiency. 
+% the state-of-art string solvers (\cite{z3seq}\cite{z3str3}\cite{z3str4}\cite{BD+23}\cite{cvc5}\cite{ostrich}\cite{z3trau}\cite{trau}) lose efficiency. 
 For CVC5\cite{cvc5} (which is the winner of QF\_Strings track in SMT-COMP 2022\cite{smt-comp}), the string constraints are solved based on DPLL(T) structure.
@@
 \end{equation}
-Z3Str3\cite{z3str3} is a string solver written on the famous SMT solver Z3\cite{z3}.
+Z3Str3\cite{z3str3} is a string solver written on the famous SMT solver Z3\cite{Z3}.
 It is based on the DPLL(T) structure and uses the same approach as CVC5, except that the derivation rules of Z3 differ from CVC5.
@@
 Although it uses simple flat automata to represent regular expressions, it has to build unsolvable automata on regex $\backslash w\{1, 63\}$ as Ostrich because the solution of the flat automata should be within the solution of the original automata.
-Recently, Z3str3 has been extended to Z3str3RE\cite{z3str3re} by Berzish et al to handle string constants with regular memberships and length operation effectively.
+Recently, Z3str3 has been extended to BD+23\cite{BD+23} by Berzish et al to handle string constants with regular memberships and length operation effectively.
 It uses automata to formalize the sematic of regular expression and applies several length-aware heuristics.
-Z3str3RE can avoid building unsolvable automaton because the length abstraction is directly derived from the regex, not the automaton.
-Unfortunately, the length abstraction is an over-approximation, so it can not solve string constraints (\ref{eq:z3str3re_timeout}) whose regular membership predicate contains complementary.
-\begin{equation}\label{eq:z3str3re_timeout}
+BD+23 can avoid building unsolvable automaton because the length abstraction is directly derived from the regex, not the automaton.
+Unfortunately, the length abstraction is an over-approximation, so it can not solve string constraints (\ref{eq:BD+23_timeout}) whose regular membership predicate contains complementary.
+\begin{equation}\label{eq:BD+23_timeout}
   x\in \Sigma_{/a}\{13,13\}\wedge |x| > 13
@@
 To handle the problems in software verification reasoning about strings and integers, string theories with regular membership predicate and linear length constraints are raised.
-String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, Z3Str3RE\cite{z3str3re}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories.
+String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, BD+23\cite{BD+23}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories.
 Although string theory is easily
-undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_z3str3re}.
+undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_BD+23}.
 There are mainly two strategies for solving string constraints: (1) DPLL(T)-based\cite{dpll_t} string solvers\cite{z3str3}\cite{cvc5} apply heuristic derivation rules to unwind the regular expression gradually and identify several classes of simplification techniques for efficiency.
-(2) Automata-based string solvers\cite{trau}\cite{z3trau}\cite{ostrich}\cite{atva2020}\cite{z3str3re} construct a finite automaton to model the regular expression and use the emptiness problem of the automaton (under linear integer arithmetic) to decide the satisfiability of string constraints.
+(2) Automata-based string solvers\cite{trau}\cite{z3trau}\cite{ostrich}\cite{atva2020}\cite{BD+23} construct a finite automaton to model the regular expression and use the emptiness problem of the automaton (under linear integer arithmetic) to decide the satisfiability of string constraints.
 
@@
 
-\end{document}
+%\end{document}

### 2023-04-25 2023-1-19/sections/preliminaries.tex
abstract

@@
-\documentclass{standalone}
-\begin{document}
+%!TEX root = ../main.tex
+%\documentclass{standalone}
+%\begin{document}
 
@@
     $\varphi$ ::= $x\in \regex \mid \alpha_1\leq\alpha_2 \mid \neg\varphi\mid \varphi\vee\varphi$                                             & formulae            \\
-    $\regex$ ::= $\epsilon\mid a\mid \regex\cdot\regex\mid \regex+\regex\mid \regex\times \regex\mid \regex^*\mid\regex^C \mid \regex\{m,n\}$ & regular expressions \\
+    $\regex$ ::= $\epsilon \mid a \mid \regex\cdot\regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \regex^C \mid \regex \setminus \regex \mid \regex^{\{m,n\}}$ & regular expressions \\
     $\alpha$ ::= $m \mid i \mid  |s|\mid -\alpha\mid \alpha_1+\alpha_2$                                                                       & integer terms

### 2023-04-25 2023-1-19/sections/introduction.tex
intro

@@
 Counting is also a frequently used feature of regular expressions.
-According to the statistics from \cite{CS16}, Kleene star/plus occur in over 70\% of the Python projects, while the other forms of counting occur in over 20\% of them.
+According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while the other forms of counting occur in more than 20\% of them.
+Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints that contain at least regular expressions with counting and string-length function.
 
 Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from the string constraints with regex-counting and string-length, especially when the counting bounds are large.
-For instance, none of CVC4/5, Z3, Z3str3RE, OSTRICH is capable of solving the following constraint within 60 seconds,
+For instance, none of string solvers e.g.
+CVC4/5, Z3, Z3str3RE, OSTRICH is capable of solving the following constraint within 300 seconds,
 %
 \begin{equation}\label{eqn-running}
-x \in (\Sigma \setminus a)^{\{5, 40\}} (\Sigma \setminus b)^{\{5, 40\}} (\Sigma \setminus c)^{\{5, 40\}} \wedge x \in \Sigma^* c \wedge |x| > 80.
+x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{5, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120.
 \end{equation}
@@
 $b, c$) does not occur in $x_1$ (resp.
-$x_2, x_3$), moreover, $x$ ends with $c$, and the length of $x$ is greater than $80$.
-It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 80$ and the counting upper bound $40$ in  both $(\Sigma \setminus a)^{\{5, 40\}}$ and $(\Sigma \setminus b)^{\{5, 40\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c$ requires that $x$ has to end with $c$.
+$x_2, x_3$), moreover, $x$ ends with $c$, and the length of $x$ is greater than $120$.
+It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 120$ and the counting upper bound $60$ in  both $(\Sigma \setminus a)^{\{5, 60\}}$ and $(\Sigma \setminus b)^{\{5, 60\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c$ requires that $x$ has to end with $c$.
+
+A typical way of string constraint solvers to deal with regex-counting is to unfold regular expressions with counting into those \emph{without} counting by utilizing the concatenation operator.
+For instance, $a^{\{0, 4\}}$ is unfolded into $\varepsilon + a + aa + aaa + aaaa$.
+Since the unfolding incurs an exponential blow-up on the constraint sizes (where the integer constants are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the bounds are large.
 
@@
 
-\paragraph*{Contribution} xxx
+\paragraph*{Contribution} In this work, we focus on the class of string constraints with regular membership and string-length function, where the counting operators may occur in regular expressions (called RECL for brevity).
+We propose an automata-theoretical approach for solving RECL constraints.
+Our main idea is to represent the counting operators by registers in automata, instead of unfolding them explicitly.
+Our approach is built upon an automata model called cost-enriched finite automata (CEFA) that was proposed in~\cite{atva2020}.
+Moreover, the string-length function can also be modeled by registers in CEFA.
+Therefore, the satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA.
 
-\paragraph*{Related work} xx
+According to the results from~ \cite{atva2020}, a linear integer arithmetic (LIA) formula can be computed to represent the potential values of registers in CEFA.
+Thus, the nonemptiness of CEFA can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers for LIA.
+%
+Because the sizes of LIA formulas depend much on the sizes of CEFA, it is beneficial to reduce the sizes of CEFA, in order to achieve a good performance.
+As a result, we propose various techniques to reduce the state space, the number of transitions, and the number of registers for CEFA.
+Furthermore, since the computation of LIA formulas from CEFA is relatively expensive, we also propose a method of searching for strings that are accepted by CEFA, based on under approximations, before constructing the LIA formulas.
 
-\paragraph*{Organization} xxx
+The representation of regex-counting and string-length as registers in CEFA, combined with the aforementioned size-reduction and under-approximation techniques, entails an efficient algorithm for solving RECL constraints.
+We implement the algorithm on top of OSTRICH, resulting into a new version of OSTRICH, called $\ostrichrecl$ for convenience.
+Furthermore, we utilize a collection of benchmark suites, which comprise 49,379 RECL constraints in total, to evaluate the performance of $\ostrichrecl$.
+The collection of benchmark suites includes a widely-used benchmark suite for string constraints, as well as benchmark suites comprising constraints generated from regular expressions in various open source regex libraries.
+%
+%Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contains sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators.
+%
+The experimental results show that $\ostrichrecl$ can solve 49,128 out of 49,379 instances, while the state-of-the-art best solver Z3str3RE solves only 47,407 instances, with a timeout of 60 seconds.
+Moreover, $\ostrichrecl$ and Z3str3RE spend almost the same amount of time in average, that is, 2.5 seconds, in solving each instance.
+In comparison, CVC5, Z3str3, and Z3seq solve only 44,001, 36,320, 46,813 instances respectively, with an average time 7.8, 7.7, 3.8 seconds per instance.
+
+\paragraph*{Related work} \zhilin{to be cleaned} To handle the problems in software verification reasoning about strings and integers, string theories with regular membership predicate and linear length constraints are raised.
+String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, BD+23\cite{BD+23}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories.
+Although string theory is easily
+undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_BD+23}.
+There are mainly two strategies for solving string constraints: (1) DPLL(T)-based\cite{dpll_t} string solvers\cite{z3str3}\cite{cvc5} apply heuristic derivation rules to unwind the regular expression gradually and identify several classes of simplification techniques for efficiency.
+(2) Automata-based string solvers\cite{trau}\cite{z3trau}\cite{ostrich}\cite{atva2020}\cite{BD+23} construct a finite automaton to model the regular expression and use the emptiness problem of the automaton (under linear integer arithmetic) to decide the satisfiability of string constraints.
+
+\paragraph*{Organization} \zhilin{to be cleaned} The rest of the paper is structured as follows: Section \ref{sec:pre} introduces the preliminaries.
+Section \ref{sec:overview} outlines the overall algorithm.
+Section \ref{sec:automaton} illustrates how to construct an automaton from a regular expression.
+Section \ref{sec:algorithm} shows how to solve a string constraint with repetition.
+Section \ref{sec:implementation} presents the experimental results.
+Section \ref{sec:conclu} concludes the paper and discusses future work.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%% original texts by Denghang %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% original texts by Denghang %%%%%%%%%%%%%%%%%
+\hide{
 String constraint solving is a subfield of computer science that deals with analyzing and manipulating strings, which are sequences of characters.
@@
 Section \ref{sec:conclu} concludes the paper and discusses future work.
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-04-25 2023-1-19/figures/overview_example.tex

--- 2023-04-25 2023-1-19/figures/overview_example_simplified.tex
@@
 
-    \path[->] (q_0) edge node [above] {$\scriptstyle a:(1,0,0,1)$} (q_1)
-              (q_0) edge [loop below] node  {$\scriptstyle a:(1,0,0,1)$} (q_0)
-              (q_1) edge node [above] {$\scriptstyle a:(0,1,0,1)$} (q_2)
-              (q_1) edge [loop below] node  {$\scriptstyle a:(0,1,0,1)$} (q_1)
-              (q_2) edge [loop below] node  {$\scriptstyle a:(0,0,1,1)$} (q_2);
+    \path[->] (q_0) edge node [above] {$\scriptstyle \Sigma \setminus a:(1,0,0,1)$} (q_1)
+              (q_0) edge [loop below] node  {$\scriptstyle\Sigma \setminus a:(1,0,0,1)$} (q_0)
+              (q_1) edge node [above] {$\scriptstyle\Sigma \setminus b:(0,1,0,1)$} (q_2)
+              (q_1) edge [loop below] node  {$\scriptstyle\Sigma \setminus b:(0,1,0,1)$} (q_1)
+              (q_2) edge [loop below] node  {$\scriptstyle\Sigma \setminus c:(0,0,1,1)$} (q_2);
   \end{tikzpicture}

### 2023-04-25 2023-1-19/sections/abstract.tex

@@
 CVC4/5, Z3str3(RE), and Z3seq are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bounds are large.
-In this work, we propose an automata-theoretic approach for solving such class of string constraints efficiently.
+In this work, we propose an automata-theoretic approach for solving such a class of string constraints efficiently.
 %
@@
 %Since Parikh images of automata can be defined by linear integer arithmetic formulas, 
-As a result, satisfiability of string constraints with regex-counting and string-length is reduced to satisfiability of linear integer arithmetic, which can then be solved by off the shelf SMT solvers.
+As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which can then be solved by off-the-shelf SMT solvers.
 %

### 2023-04-25 2023-1-19/sections/overview.tex
abstract

@@
-The main idea is to use CEFAs (see Subsection \ref{subsec:cefa}) to simulate the semantics of length operations and regular memberships with bounded repetitions.
+%!TEX root = ../main.tex
+
+Recalling the string constraint listed in Section \ref{sec:intro}, DPLL(T)- and automata- based string solvers can not solve it.
+For DPLL(T)-based string solvers, the unsatisfiability is hard to discover since it is highly related to the length and the counting, which independent derivation rules for regex and length can not conclude.
+For automata-based string solvers, the counting operators result in the big-size automaton, whose length abstraction is too complex to solve.
+To address these issues, we use automaton to encode the semantics of the counting operator, but in a smarter way by storing counting information to registers rather than unwinding it directly.
+The automaton model we used is called cost-enriched finite automaton(abbreviated as regex).
+It is carefully discussed in Section \ref{subsec:cefa}, so we briefly introduce it in this section.
+A CEFA can be seen as an extension of an NFA by appending symbolic updates of integers on each transition, linear integer arithmetic to constrain the integer values on each accepting state, and registers to store integer values.
+The main idea is based on the observation that the occurrences of exact transitions can trace the counting times, and the length can be seen as the sum of occurrences of all transitions in the accepting run.
+For example, the counting times in $(\Sigma \setminus a)^{\{5, 40\}}$ can be traced by the occurrences of transitions in sub-regex $\Sigma \setminus a$.
+To detail, we use one register to store counting, and symbolically add 1 when running one of the transitions in $\Sigma \setminus a$, tracing the counting times.
+Similarly, we use another register to store the length and symbolically add 1 to it when running any transition.
+The automaton model of string constraints \ref{eq:motivation_str_constraints} is illustrated in Figure \ref{fig:overview}.
+Register $r_1$ stores the counting times of the sub-regex $\Sigma \setminus a$, register $r_2$ stores the counting times of the sub-regex $\Sigma \setminus b$, register $r_3$ stores the counting times of the sub-regex $\Sigma \setminus c$, and register $r_4$ stores the length of the string.
+The label $\Sigma \setminus a:(1,0,0,1)$ means that when running the transition, the counting times of $\Sigma \setminus a$ (i.e., the value of $r_1$) plus 1, and the length (i.e., the value of $r_4$) plus 1.
+The accepting state $q_3$ is accepting by the linear integer arithmetic $5\leq r_1\leq 40\wedge 5\leq r_2\leq 40\wedge 0\leq r_3\leq 40\wedge 80 < r_4$.
+$5\leq r_1\leq 40$ ensure the counting times of $\Sigma \setminus a$ is in the range $[5, 40]$, $5\leq r_2\leq 40$ ensure the counting times of $\Sigma \setminus b$ is in the range $[5, 40]$, $0\leq r_3\leq 40$ ensure the counting times of $\Sigma \setminus c$ is in the range $[0, 40]$, and $80 < r_4$ ensure the length of the string is greater than 80.
+The satisfiability of the CEFA can then be reduced to the satisfiability of linear integer arithmetic, which other off-the-shelf SMT solvers solve.
+\newline
+However, even when we use CEFA to encode counting in the string constraints, the linear integer arithmetic reduced from the CEFA still needs to be simplified to solve.
+The reason is that the linear integer arithmetic is solved in exponential time of the number of variables, which is linear to the sum of transitions number and states number in the CEFA.
+To address this issue, we use symbolic-aware simplification to reduce the number of transitions and states in the CEFA.
+Simply illustrating our idea, consider a simple NFA rather than a CEFA.
+We assume the NFA consisted of three states $q_1, q_2, q_3$, where $q_1$ is the initial state, $q_2$ and $q_3$ are the accepting states.
+Assume we have three transitions from $q_1$ to $q_2$ with different characters, and three transitions from $q_1$ to $q_3$.
+Actually, we only need to attempt some of the six transitions to get the reachable result.
+We run any of the transitions, and the reachability is known.
+So this NFA can be simplified to two states $q_1', q_2'$ where $q_1'$ is the initial state, $q_2'$ is the accepting state, and one transition from $q_1'$ to $q_2'$ with abbreviated character.
+The size of NFA is sharply reduced.
+The simplification can be done by treating the character on each transition as the same character, then applying the minimization algorithm to the NFA.
+CEFA can be simplified similarly, except we need to consider the counting information, i.e., symbolic updates, on each transition.
+For example, $a:(1)$ and $b:(1)$ are treated as the same label but $a:(1)$ and $b:(0)$ are not.
+Then we can apply the minimization algorithm as NFA.
+Recalling the CEFA (Fig.
+\ref{fig:overview:orgin}) handling the string constraints \ref{eq:motivation_str_constraints}, its transitions number between $q_1$ and $q_2$ are decided by the size of alphabet $\Sigma$.
+We apply symbolic-aware simplification on it, then a much smaller CEFA (Fig.
+\ref{fig:overview:simplified}) is obtained, whose alphabet is unary so that the number of the transition between $q_1$ and $q_2$ decreases to $1$.
+The state number does not decrease because these three states are not mutually equivalent.
+\newline
+Sometimes the string constraints are satisfiable, and the strings in the solution have a short length.
+Such a solution may be quickly explored by derivation rules in DPLL(T)-based string solvers but slowly explored by our approach.
+To improve efficiency on satisfiable string constraints, we propose a light-way heuristic that tries to find a solution in the under-approximation of the string constraints.
+The main idea is to explore paths within an exact length and manually compute the registers' values, rather than reduce CEFA to heavy linear integer arithmetic.
+For example, consider the string constraints $x \in (\Sigma \setminus a)^{\{5, 40\}} (\Sigma \setminus b)^{\{5, 40\}} (\Sigma \setminus c)^{\{0, 40\}} \wedge x \in \Sigma^* c$, we can explore paths within length 10 and get a satisfiable solution $cccccccccc$.
+\begin{equation}\label{eq:motivation_str_constraints}
+  x \in (\Sigma \setminus a)^{\{5, 40\}} (\Sigma \setminus b)^{\{5, 40\}} (\Sigma \setminus c)^{\{0, 40\}} \wedge x \in \Sigma^* c \wedge |x| > 80
+\end{equation}
+\begin{figure}[ht]
+  \centering
+  \import{figures}{overview_example.tex}
+  \caption{The CEFA handling the difficult string constraints}
+  \label{fig:overview:orgin}
+\end{figure}
+\begin{figure}[ht]
+  \centering
+  \import{figures}{overview_example_simplified.tex}
+  \caption{The simplified CEFA handling the difficult string constraints}
+  \label{fig:overview:simplified}
+\end{figure}
+
+% The main idea is to use CEFAs (see Subsection \ref{subsec:cefa}) to simulate the semantics of length operations and regular memberships with bounded repetitions.
 As mentioned, the ESL formula contains regular literals and linear literals.
@@
 Then we generate the pre-image $\aut_{i}$ whose accepting words are strings with length $i$ (see Example \ref{eg:pre_len}).
-After the process above, the satisfiability problem of string constraints becomes a $SAT_{CL}$ problem, which has a decision procedure to check (see Subsection \ref{subsec:emptiness}).
+After the process above, the satisfiability problem of string constraints becomes an $SAT_{CL}$ problem, which has a decision procedure to check (see Subsection \ref{subsec:emptiness}).
 Example \ref{example:overview} illustrate it.
 \newline
-
-\begin{example} \label{example:overview}
-  \begin{align*}
-    \varphi\equiv x\in (ab)\{1,100\}\wedge y\in ab\wedge |x| > |y|
-  \end{align*}
-  ESL conjunction $\varphi$ is made up of regular literals $x\in (ab)\{1,100\}$ and $y\in ab$, linear literals $|x| > |y|$.
+% \begin{example} \label{example:overview}
+%   \begin{align*}
+%     \varphi\equiv x\in (ab)\{1,100\}\wedge y\in ab\wedge |x| > |y|
+%   \end{align*}
+%   ESL conjunction $\varphi$ is made up of regular literals $x\in (ab)\{1,100\}$ and $y\in ab$, linear literals $|x| > |y|$.
 The linear literal is translated to $i = |x|\wedge j = |y| \wedge i > j$.
@@
 
-  \begin{figure}[h]
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$1\leq r_1\leq 100$, accepting/.style=accepting by arrow,
-        accepting where=above
-        ]
+  % \begin{figure}[h]
+  %   \begin{subfigure}[b]{0.49\textwidth}
+  %     \centering
+  %     \begin{tikzpicture}[
+  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+  %       initial text=, every state/.style={minimum size = 0.001cm},
+  %       accepting text=$1\leq r_1\leq 100$, accepting/.style=accepting by arrow,
+  %       accepting where=above
+  %       ]
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state,accepting]          (q_2) [right=of q_1]       {};
+  %       \node[state,initial]            (q_0)                      {};
+  %       \node[state]                    (q_1) [right=of q_0]       {};
+  %       \node[state,accepting]          (q_2) [right=of q_1]       {};
 
-        \path[->] (q_0) edge              node      [above]           {$a$/(1)} (q_1)
-        (q_1) edge              node      [above]           {$b$/(0)} (q_2)
-        (q_2) edge [bend left]  node      [below]           {$a$/(1)} (q_1);
-      \end{tikzpicture}
-      \caption{The CEFA recognizing $(ab)\{1,100\}$}
-      \label{subfig:aut_ab1-100}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\top$, accepting/.style=accepting by arrow,
-        accepting where=above
-        ]
+  %       \path[->] (q_0) edge              node      [above]           {$a$/(1)} (q_1)
+  %       (q_1) edge              node      [above]           {$b$/(0)} (q_2)
+  %       (q_2) edge [bend left]  node      [below]           {$a$/(1)} (q_1);
+  %     \end{tikzpicture}
+  %     \caption{The CEFA recognizing $(ab)\{1,100\}$}
+  %     \label{subfig:aut_ab1-100}
+  %   \end{subfigure}
+  %   \begin{subfigure}[b]{0.49\textwidth}
+  %     \centering
+  %     \begin{tikzpicture}[
+  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+  %       initial text=, every state/.style={minimum size = 0.001cm},
+  %       accepting text=$\top$, accepting/.style=accepting by arrow,
+  %       accepting where=above
+  %       ]
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state, accepting]         (q_2) [right=of q_1]       {};
+  %       \node[state,initial]            (q_0)                      {};
+  %       \node[state]                    (q_1) [right=of q_0]       {};
+  %       \node[state, accepting]         (q_2) [right=of q_1]       {};
 
-        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
-        (q_1) edge              node      [above]           {$b$/()} (q_2);
-      \end{tikzpicture}
-      \caption{The CEFA recognizing $ab$}
-      \label{subfig:aut_ab}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${r_2 = i}$, accepting/.style=accepting by arrow,
-        ]
+  %       \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
+  %       (q_1) edge              node      [above]           {$b$/()} (q_2);
+  %     \end{tikzpicture}
+  %     \caption{The CEFA recognizing $ab$}
+  %     \label{subfig:aut_ab}
+  %   \end{subfigure}
+  %   \begin{subfigure}[b]{0.49\textwidth}
+  %     \centering
+  %     \begin{tikzpicture}[
+  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+  %       initial text=, every state/.style={minimum size = 0.001cm},
+  %       accepting text=${r_2 = i}$, accepting/.style=accepting by arrow,
+  %       ]
 
-        \node[state,initial,accepting]            (q_0)       {};
+  %       \node[state,initial,accepting]            (q_0)       {};
 
-        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
-      \end{tikzpicture}
-      \caption{The pre-image of $i = |x|$}
-      \label{subfig:preimage_x}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${r_3 = j}$, accepting/.style=accepting by arrow,
-        ]
+  %       \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
+  %     \end{tikzpicture}
+  %     \caption{The pre-image of $i = |x|$}
+  %     \label{subfig:preimage_x}
+  %   \end{subfigure}
+  %   \begin{subfigure}[b]{0.49\textwidth}
+  %     \centering
+  %     \begin{tikzpicture}[
+  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+  %       initial text=, every state/.style={minimum size = 0.001cm},
+  %       accepting text=${r_3 = j}$, accepting/.style=accepting by arrow,
+  %       ]
 
-        \node[state,initial,accepting]            (q_0)       {};
+  %       \node[state,initial,accepting]            (q_0)       {};
 
-        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} (1);
-      \end{tikzpicture}
-      \caption{The pre-image of $j = |y|$}
-      \label{subfig:preimage_y}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${r_2 = i\wedge 1\leq r_1 \leq 100}$, accepting/.style=accepting by arrow,
-        accepting where=above
-        ]
+  %       \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} (1);
+  %     \end{tikzpicture}
+  %     \caption{The pre-image of $j = |y|$}
+  %     \label{subfig:preimage_y}
+  %   \end{subfigure}
+  %   \begin{subfigure}[b]{0.49\textwidth}
+  %     \centering
+  %     \begin{tikzpicture}[
+  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+  %       initial text=, every state/.style={minimum size = 0.001cm},
+  %       accepting text=${r_2 = i\wedge 1\leq r_1 \leq 100}$, accepting/.style=accepting by arrow,
+  %       accepting where=above
+  %       ]
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state,accepting]          (q_2) [right=of q_1]       {};
+  %       \node[state,initial]            (q_0)                      {};
+  %       \node[state]                    (q_1) [right=of q_0]       {};
+  %       \node[state,accepting]          (q_2) [right=of q_1]       {};
 
-        \path[->] (q_0) edge node [above]  {$a$/(1,1)} (q_1)
-        (q_1) edge           node [above]  {$b$/(0,1)} (q_2)
-        (q_2) edge [bend left]  node      [below]           {$a$/(1,1)} (q_1);
-      \end{tikzpicture}
-      \caption{The final automaton of $x$}
-      \label{subfig:aut_x}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${r_3=j}$, accepting/.style=accepting by arrow,
-        accepting where=above
-        ]
+  %       \path[->] (q_0) edge node [above]  {$a$/(1,1)} (q_1)
+  %       (q_1) edge           node [above]  {$b$/(0,1)} (q_2)
+  %       (q_2) edge [bend left]  node      [below]           {$a$/(1,1)} (q_1);
+  %     \end{tikzpicture}
+  %     \caption{The final automaton of $x$}
+  %     \label{subfig:aut_x}
+  %   \end{subfigure}
+  %   \begin{subfigure}[b]{0.49\textwidth}
+  %     \centering
+  %     \begin{tikzpicture}[
+  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+  %       initial text=, every state/.style={minimum size = 0.001cm},
+  %       accepting text=${r_3=j}$, accepting/.style=accepting by arrow,
+  %       accepting where=above
+  %       ]
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state, accepting]         (q_2) [right=of q_1]       {};
+  %       \node[state,initial]            (q_0)                      {};
+  %       \node[state]                    (q_1) [right=of q_0]       {};
+  %       \node[state, accepting]         (q_2) [right=of q_1]       {};
 
-        \path[->] (q_0) edge    node      [above]           {$a$/(1)} (q_1)
-        (q_1) edge              node      [above]           {$b$/(1)} (q_2);
-      \end{tikzpicture}
-      \caption{The final automaton of $y$}
-      \label{subfig:aut_y}
-    \end{subfigure}
-    \caption{All automata used in the example \ref{example:overview}}
-  \end{figure}
+  %       \path[->] (q_0) edge    node      [above]           {$a$/(1)} (q_1)
+  %       (q_1) edge              node      [above]           {$b$/(1)} (q_2);
+  %     \end{tikzpicture}
+  %     \caption{The final automaton of $y$}
+  %     \label{subfig:aut_y}
+  %   \end{subfigure}
+  %   \caption{All automata used in the example \ref{example:overview}}
+  % \end{figure}
 
-\end{example}
+% \end{example}
 

### 2023-04-25 2023-1-19/sections/preliminaries.tex
restructure

@@
 % Tokens
-\subsubsection{Tokens}
+%\subsubsection{Tokens}
+
 A finite \emph{alphabet} $\Sigma$ is the set of all \emph{letters}. A
@@
 
-\subsubsection{Syntax}
-This paper proposes a quantifier-free first-order logic called \textit{Extended String Logic (ESL)}, whose syntax is presented in Table \ref{tab:syntax}.
-$\varphi$ is a quantifier-free formula that can be a regular membership $x\in\regex$, a quantifier-free Presburger formula $\alpha_1 \leq \alpha_2$, a negation of a formula, or a disjunction of two formulas.
-$\alpha$ is an integer term which can be an integer constant $m$, integer variable $i$, the length of the string term $|s|$, the minus of an integer term, and the plus of two integer terms.
-The regular expression $\regex$ is built on empty string $\epsilon$, constant letter $a\in \Sigma$.
-The supported regex operations involve concatenation $\cdot$, disjunction $+$, intersection $\times$, closure $*$, complement $C$, and bounded repetition $\{m, n\}$.
-We use $term(\varphi)$ to denote the set of terms and $strvar(\varphi)$ to denote the string variables occurring in $\varphi$.
-The \emph{literals} of $\varphi$ are $x\in \regex$ and $\alpha_1 \leq \alpha_2$.
-$x\in \regex$ is called \emph{regular literals} and $\alpha_1 \leq \alpha_2$ is called \emph{linear literals}.
-\begin{table}[h]
-  \centering
-  \begin{tabular}{l r}
-    $\varphi$ ::= $x\in \regex \mid \alpha_1\leq\alpha_2 \mid \neg\varphi\mid \varphi\vee\varphi$                                             & formulae            \\
-    $\regex$ ::= $\epsilon \mid a \mid \regex\cdot\regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \regex^C \mid \regex \setminus \regex \mid \regex^{\{m,n\}}$ & regular expressions \\
-    $\alpha$ ::= $m \mid i \mid  |s|\mid -\alpha\mid \alpha_1+\alpha_2$                                                                       & integer terms
-  \end{tabular}
-  \caption{Syntax}\label{tab:syntax}
-\end{table}
-% Semantic 
-\subsubsection{Semantic}
-We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables.
-$\eta: S\times\Sigma\rightarrow\Sigma^*$ is the interpretation on string where $\eta(c)=c$ for every letter $c\in \Sigma$.
-$\pi: I\rightarrow\mathbb{Z}$ is the interpretation of Presburger arithmetic.
-Then the semantics is given by a satisfaction relation: $\eta, \pi\models \varphi$ defined in Table \ref{tab:semantics}.
-We say a formula $\varphi$ is \emph{satisfiable} if a solution $(\eta, \pi)$ exists such as $\eta, \pi\models \varphi$.
-A formula $\varphi$ is \emph{unsatisfiable} if no solution exists.
-\begin{table}[h]
-  \centering
-  \begin{tabular}{lcl}
-    $\eta,\pi \models \varphi_1\vee \varphi_2$ & $\mathsf{iff}$ & $\eta,\pi \models \varphi_1 \text{ or } \eta,\pi \models \varphi_2$ \\
-    $\eta,\pi \models \neg\varphi $            & $\mathsf{iff}$ & $\eta,\pi \not\models \varphi$                                      \\
-    $\eta, \pi \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan(\regex),\eta,\pi \models x = w$                 \\
-    $\eta, \pi \models \alpha_1 \leq \alpha_2$ & $\mathsf{iff}$ & $\pi(\alpha_1) \leq \pi(\alpha_2) $                                 \\
-  \end{tabular}
-  \caption{Semantics}
-  \label{tab:semantics}
-\end{table}
-In addition to the classic regex operators (union, concatenation, closure), we syntactically support intersection, complement, and repetition.
-As we all know, the classic regular language is closed under intersection and complement \cite{aut_hopcraft}.
-Furthermore, the operation \emph{repetition} $\regex\{m,n\}$ means repeating regex $\regex$ at least $m$ times and at most $n$ times.
-It can be syntactically rewritten by concatenation and union:
-$\regex\{m,n\} \equiv \regex^m\mid\cdots\mid\regex^n$ where $\regex^k$ defines concatenate $\regex$ $k$ times ($m\leq k\leq n$).
-So the regular language $\lan(\regex)$ defined in Table \ref{tab:syntax} is semantically equal to the classic regular language.
-
-%\end{document}
+Finite state automata

### 2023-04-25 2023-1-19/sections/cefa.tex
restructure this paper

--- 2023-04-11 2023-1-19/sections/automaton_model.tex
@@
 
-\subsection{Cost-Enriched Finite Automaton} \label{subsec:cefa}
+%\subsection{Cost-Enriched Finite Automaton} \label{subsec:cefa}
 The definition of CEFA in this paper is lightly different from the definition in \cite{atva2020}.
@@
 % \end{example}
-\subsection{Encode Bounded Repetition to CEFA} \label{subsec:regex2cefa}
-In this section, we define the construction of CEFA from the regular expression with bounded repetition.
-We must syntactically rewrite bounded repetition $\regex\{m,n\}$ if it is the sub-regex of complement (e.g., $(\regex\{m,n\})^C$), closure(e.g., $(\regex\{m,n\})^*$), and bounded repetition(e.g., $(\regex\{m,n\})\{m', n'\}$), we unwind it to $\regex^m\mid\cdots\mid\regex^n$.
-After this syntactic rewriting, we call the resulting regex $\regex'$ \emph{non-nested}.
-The non-nested regex $\regex'$ possibly contains operations such as intersection, union, concatenation, complement, closure, and bounded repetition.
-To construct the CEFA of $\regex'$, we first create CEFA for each sub-regex and then combine them.
-Similar to the construction of NFA from regex\cite{aut_hopcraft}, our construction is inductive on the size of $\regex'$.
-The base case is for a single character, an empty string, and an empty language.
-The inductive step is for the concatenation, union, and intersection of two automata and one automaton's repetition, closure, and complement.
-We only discuss the inductive step for bounded repetition because the other operations are trivial.
-\newline
-For a non-nested regular expression $R\{m,n\}$, suppose we have an CEFA $\aut = (Q,\Sigma,\delta,q_I,F,\emptyset,\top)$ recognizing $R$, the CEFA recognizing $R\{m,n\}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_ I, F, r, \theta')$ where:
-\begin{itemize}
-  \item $r$ is a new register,
-  \item $\delta'$ is composed by transitions $q\xrightarrow[(0)]{a} q'$ for all transitions $q\xrightarrow[()]{a} q' \in \delta$, and transitions $q_f\xrightarrow[(1)]{\epsilon} q_I$  for each $q_f\in F$,
-  \item For each accepting states $q\in F$, $\theta'(q)$ is the linear arithmetic $m\leq r\leq n$ if $q_I\not\in F$. Otherwise, $\theta'(q)$ is the linear arithmetic $r\leq n$.
-\end{itemize}
-In the construction illustrated in Fig.\ref{fig:construct_repetition}, a new register $r$ is added to store the repetition times.
-The transition $q\xrightarrow[(1)]{\epsilon} q_I$ is set to update the repetition times for each $q\in F$.
-The accepting condition $\theta'$ is used to restrict the repetition times of the accepting word.
-Because arbitrary repetition times of an empty string are still empty, the value of $r$ only needs to be less or equal to $n$ when the initial state is accepted.
-\begin{figure}[h]
-  \begin{subfigure}[b]{0.49\textwidth}
-    \centering
-    \begin{tikzpicture}[
-      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=$\varphi$, accepting/.style=accepting by arrow,
-      ]
-
-      \node[state,initial]            (q_0)                      {};
-      \node[state, accepting]         (q_1) [right=of q_0]       {};
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA recognizing $\regex$}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \centering
-    \begin{tikzpicture}[
-      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=$\varphi\wedge$\myemph{$(m\leq) r\leq n$}, accepting/.style=accepting by arrow,
-      ]
-
-      \node[state,initial]            (q_0)                      {};
-      \node[state, accepting]         (q_1) [right=of q_0]       {};
-      \path[->] (q_1) edge[bend right]   node    [above] {\myemph{$\mathbf{\epsilon/(1)}$}} (q_0);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA recognizing $\regex\{m,n\}$}
-  \end{subfigure}
-  \caption{The construction of bounded repetition}
-  \label{fig:construct_repetition}
-\end{figure}
-\begin{example}
-  To construct the CEFA recognizing $(ab)\{1,100\}$, we first construct the CEFA recognizing $ab$ as shown in Fig.\ref{subfig:rep_aut_ab}.
-Then we add a new register $r_1$ and a transition $q_2\xrightarrow[(1)]{\epsilon} q_0$ to update the repetition times.
-The accepting condition $\theta'$ map accepting state to $1\leq r_1\leq 100$ because the initial state is unacceptable.
-The CEFA recognizing $(ab)\{1,100\}$ is shown in Fig.\ref{subfig:rep_aut_ab1_100}.
-  \begin{figure}[h]
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\top$, accepting/.style=accepting by arrow,
-        accepting where=above
-        ]
-
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state, accepting]         (q_2) [right=of q_1]       {};
-
-        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
-        (q_1) edge              node      [above]           {$b$/()} (q_2);
-      \end{tikzpicture}
-      \caption{The CEFA recognizing $ab$}
-      \label{subfig:rep_aut_ab}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=\myemph{1}$\leq r_1\leq$\myemph{100}, accepting/.style=accepting by arrow,
-        accepting where=above
-        ]
-
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state,accepting]          (q_2) [right=of q_1]       {};
-
-        \path[->] (q_0) edge              node      [above]           {$a$/(\myemph{0})} (q_1)
-        (q_1) edge              node      [above]           {$b$/(\myemph{0})} (q_2)
-        (q_2) edge [bend left]  node      [below]           {$\epsilon$/(\myemph{1})} (q_0);
-      \end{tikzpicture}
-      \caption{The CEFA recognizing $(ab)\{\myemph{1},\myemph{100}\}$}
-      \label{subfig:rep_aut_ab1_100}
-    \end{subfigure}
-    \caption{The example of bounded repetition}
-  \end{figure}
-\end{example}
-
-\end{document}
+%\end{document}

### 2023-04-25 2023-1-19/sections/preliminaries.tex
preliminary

@@
 
-% Tokens
-%\subsubsection{Tokens}
+We write $\Nat$ and $\Int$ for the sets of natural and integer numbers, respectively.
+For $n \in \Nat$ with $n \ge 1$, $[n]$ denotes $\{1, \ldots, n\}$; for $m,n \in \Nat$ with $m \le n$,  $[m, n]$ denotes $\{ i \in \Nat \mid m \le i \le n \}$.
+Throughout the paper, $\Sigma$ is a finite alphabet, ranged over by $a,b,\ldots$.
 
+\paragraph*{Strings and languages.}
+A string over $\Sigma$ is a (possibly empty) sequence of elements from $\Sigma$,
+denoted by $u, v, w, \ldots$. An empty string is denoted by $\varepsilon$.  We write $\Sigma^*$ (resp., $\Sigma^+$) for the set of all (resp. nonempty) strings over $\Sigma$.
+%Let 
+For a string $u$, we use $|u|$ to denote the number of letters in $u$. In particular, $|\varepsilon|=0$. Moreover, for $a \in \Sigma$, let $|u|_a$ denote the number of occurrences of $a$ in $u$. 
+Assume $u=a_0\cdots a_{n-1}$ is nonempty and $i<j \in [0,n-1]$. %Then a \emph{position} of $u$ is a number $i \in [|u|]$ (Note that the first position is $1$, instead of  0). In addition, 
+We let $u[i]$ denote $a_i$ and $u[i,j]$ for the substring %of $u$ starting from $i$ and ending with $j$ (i.e., 
+$a_i\cdots a_j$. 
+%\tl{check later for consistency}\zhilin{the indices start from 0, to be consistent with the semantics of substring and indexof}\zhilin{i do use it in section 4}
+
+Let $u, v$ be two strings. We use $u \cdot v$ to denote the \emph{concatenation} of $u$ and $v$.
+%, that is, the string $w$ such that $|w|= |u| + |v|$ and for each $i \in [0, |u|-1]$, $w[i]= u[i]$, and for each $i \in [0,|v|-1]$, $w[|u|+i]=v[i]$.
+
+\paragraph*{Finite state automata.} 
+A \emph{(nondeterministic) finite state automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, I, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $I,F \subseteq Q$ are the set of initial and final states respectively.
+For readability, we write a transition $(q, a, q') \in \delta$ as $q \xrightarrow[\delta]{a} q'$ (or simply $q \xrightarrow{a} q'$).
+%Moreover, when $\delta$ is clear from context, we omit $\delta$ in $q \xrightarrow[\delta]{a} q'$ and write $q \xrightarrow{a} q'$.
+The \emph{size} of an NFA $\NFA$, denoted by $|\NFA|$, is defined as the number of transitions of $\NFA$.
+%
+A \emph{run} of $\NFA$ on a string $w = a_1 \cdots a_n$ is a sequence of transitions $q_0 \xrightarrow{a_1} q_1 \cdots q_{n-1} \xrightarrow{a_n} q_n$ with $q_0 \in I$.
+The run is \emph{accepting} if $q_n \in F$.
+A string $w$ is accepted by an NFA $\NFA$ if there is an accepting run of $\NFA$ on $w$.
+In particular, the empty string $\varepsilon$ is accepted by $\NFA$ if $I \cap F \neq \emptyset$.
+The language of $\NFA$, denoted by $\Lang(\NFA)$, is the set of strings accepted by $\NFA$.
+%
+An NFA $\NFA$ is said to be \emph{deterministic} if $I$ is a singleton and, for every $q \in Q$ and $a \in \Sigma$, there is at most one state $q' \in Q$ such that $(q, a, q') \in \delta$.
+%
+It is well-known that finite automata capture regular languages precisely.
+
+%\tl{to put in a different place later} Note that our decision procedure is applicable to general transducers as well, however, the EXPSPACE complexity bound is not, because the distributive property $f^{-1}(L_1\cap L_2)= f^{-1}(L_1)\cap f^{-1}(L_2)$ for regular languages $L_1, L_2$ only holds for functional transducers $f$.
+
+%We remark that an FT usually defines a relation.
+
+%\smallskip
+
+%In this paper, we consider logics involving two data-types, i.e., the string data-type and the integer data-type.
+We will use $u, v, \dots$ to denote string constants,  $c, d,\dots$ to denote integer constants, $x, y, \dots$ to denote string variables, and $i, j, \dots$ to denote  integer variables.
+
+We will also use standard  quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulae, which are typically ranged over by $\phi, \varphi$, etc. %, which is essentially Presburger
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
 A finite \emph{alphabet} $\Sigma$ is the set of all \emph{letters}. A
@@
 For vector, we use $\myvec{v}$ to denote the vector of integer constant, $m_n$ to denote the vector $(m,\cdots, m)$ with length $n$, $\myvec{v}[i]$ to denote the integer value of $\myvec{v}$ at position $i$, $\myvec{v_1}\cdot\myvec{v_2}$ to denote the concatenation of $\myvec{v_1}$ and $\myvec{v_2}$, $R$ to denote the vector of registers, $R_1 \cap R_2$ to denote the same registers in $R_1$ and $R_2$, and $|\myvec{v}|$ or $|R|$ to denote the length of the vector.
-
-Finite state automata
+}

### 2023-04-25 2023-1-19/sections/algorithms.tex
abstract

@@
-\documentclass{standalone}
-\begin{document}
+%!TEX root = ../main.tex
+%\documentclass{standalone}
+%\begin{document}
+
+\subsection{Encode Bounded Repetition to CEFA} \label{subsec:regex2cefa}
+In this section, we define the construction of CEFA from the regular expression with bounded repetition.
+We must syntactically rewrite bounded repetition $\regex\{m,n\}$ if it is the sub-regex of complement (e.g., $(\regex\{m,n\})^C$), closure(e.g., $(\regex\{m,n\})^*$), and bounded repetition(e.g., $(\regex\{m,n\})\{m', n'\}$), we unwind it to $\regex^m\mid\cdots\mid\regex^n$.
+After this syntactic rewriting, we call the resulting regex $\regex'$ \emph{non-nested}.
+The non-nested regex $\regex'$ possibly contains operations such as intersection, union, concatenation, complement, closure, and bounded repetition.
+To construct the CEFA of $\regex'$, we first create CEFA for each sub-regex and then combine them.
+Similar to the construction of NFA from regex\cite{aut_hopcraft}, our construction is inductive on the size of $\regex'$.
+The base case is for a single character, an empty string, and an empty language.
+The inductive step is for the concatenation, union, and intersection of two automata and one automaton's repetition, closure, and complement.
+We only discuss the inductive step for bounded repetition because the other operations are trivial.
+\newline
+For a non-nested regular expression $R\{m,n\}$, suppose we have an CEFA $\aut = (Q,\Sigma,\delta,q_I,F,\emptyset,\top)$ recognizing $R$, the CEFA recognizing $R\{m,n\}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_ I, F, r, \theta')$ where:
+\begin{itemize}
+  \item $r$ is a new register,
+  \item $\delta'$ is composed by transitions $q\xrightarrow[(0)]{a} q'$ for all transitions $q\xrightarrow[()]{a} q' \in \delta$, and transitions $q_f\xrightarrow[(1)]{\epsilon} q_I$  for each $q_f\in F$,
+  \item For each accepting states $q\in F$, $\theta'(q)$ is the linear arithmetic $m\leq r\leq n$ if $q_I\not\in F$. Otherwise, $\theta'(q)$ is the linear arithmetic $r\leq n$.
+\end{itemize}
+In the construction illustrated in Fig.\ref{fig:construct_repetition}, a new register $r$ is added to store the repetition times.
+The transition $q\xrightarrow[(1)]{\epsilon} q_I$ is set to update the repetition times for each $q\in F$.
+The accepting condition $\theta'$ is used to restrict the repetition times of the accepting word.
+Because arbitrary repetition times of an empty string are still empty, the value of $r$ only needs to be less or equal to $n$ when the initial state is accepted.
+\begin{figure}[h]
+  \begin{subfigure}[b]{0.49\textwidth}
+    \centering
+    \begin{tikzpicture}[
+      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+      initial text=, every state/.style={minimum size = 0.001cm},
+      accepting text=$\varphi$, accepting/.style=accepting by arrow,
+      ]
+
+      \node[state,initial]            (q_0)                      {};
+      \node[state, accepting]         (q_1) [right=of q_0]       {};
+      \node [fit=(q_0) (q_1)] {$\cdots$};
+    \end{tikzpicture}
+    \caption{The CEFA recognizing $\regex$}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \centering
+    \begin{tikzpicture}[
+      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+      initial text=, every state/.style={minimum size = 0.001cm},
+      accepting text=$\varphi\wedge$\myemph{$(m\leq) r\leq n$}, accepting/.style=accepting by arrow,
+      ]
+
+      \node[state,initial]            (q_0)                      {};
+      \node[state, accepting]         (q_1) [right=of q_0]       {};
+      \path[->] (q_1) edge[bend right]   node    [above] {\myemph{$\mathbf{\epsilon/(1)}$}} (q_0);
+      \node [fit=(q_0) (q_1)] {$\cdots$};
+    \end{tikzpicture}
+    \caption{The CEFA recognizing $\regex\{m,n\}$}
+  \end{subfigure}
+  \caption{The construction of bounded repetition}
+  \label{fig:construct_repetition}
+\end{figure}
+\begin{example}
+  To construct the CEFA recognizing $(ab)\{1,100\}$, we first construct the CEFA recognizing $ab$ as shown in Fig.\ref{subfig:rep_aut_ab}.
+Then we add a new register $r_1$ and a transition $q_2\xrightarrow[(1)]{\epsilon} q_0$ to update the repetition times.
+The accepting condition $\theta'$ map accepting state to $1\leq r_1\leq 100$ because the initial state is unacceptable.
+The CEFA recognizing $(ab)\{1,100\}$ is shown in Fig.\ref{subfig:rep_aut_ab1_100}.
+  \begin{figure}[h]
+    \begin{subfigure}[b]{0.49\textwidth}
+      \centering
+      \begin{tikzpicture}[
+        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+        initial text=, every state/.style={minimum size = 0.001cm},
+        accepting text=$\top$, accepting/.style=accepting by arrow,
+        accepting where=above
+        ]
+
+        \node[state,initial]            (q_0)                      {};
+        \node[state]                    (q_1) [right=of q_0]       {};
+        \node[state, accepting]         (q_2) [right=of q_1]       {};
+
+        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
+        (q_1) edge              node      [above]           {$b$/()} (q_2);
+      \end{tikzpicture}
+      \caption{The CEFA recognizing $ab$}
+      \label{subfig:rep_aut_ab}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \centering
+      \begin{tikzpicture}[
+        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+        initial text=, every state/.style={minimum size = 0.001cm},
+        accepting text=\myemph{1}$\leq r_1\leq$\myemph{100}, accepting/.style=accepting by arrow,
+        accepting where=above
+        ]
+
+        \node[state,initial]            (q_0)                      {};
+        \node[state]                    (q_1) [right=of q_0]       {};
+        \node[state,accepting]          (q_2) [right=of q_1]       {};
+
+        \path[->] (q_0) edge              node      [above]           {$a$/(\myemph{0})} (q_1)
+        (q_1) edge              node      [above]           {$b$/(\myemph{0})} (q_2)
+        (q_2) edge [bend left]  node      [below]           {$\epsilon$/(\myemph{1})} (q_0);
+      \end{tikzpicture}
+      \caption{The CEFA recognizing $(ab)\{\myemph{1},\myemph{100}\}$}
+      \label{subfig:rep_aut_ab1_100}
+    \end{subfigure}
+    \caption{The example of bounded repetition}
+  \end{figure}
+\end{example}
 

### 2023-04-25 2023-1-19/sections/recl.tex

%!TEX root = ../main.tex
%\documentclass{standalone}
%\begin{document}

\subsubsection{Syntax}
This paper proposes a quantifier-free first-order logic called \textit{Extended String Logic (ESL)}, whose syntax is presented in Table \ref{tab:syntax}. $\varphi$ is a quantifier-free formula that can be a regular membership $x\in\regex$, a quantifier-free Presburger formula $\alpha_1 \leq \alpha_2$, a negation of a formula, or a disjunction of two formulas. $\alpha$ is an integer term which can be an integer constant $m$, integer variable $i$, the length of the string term $|s|$, the minus of an integer term, and the plus of two integer terms. The regular expression $\regex$ is built on empty string $\epsilon$, constant letter $a\in \Sigma$. The supported regex operations involve concatenation $\cdot$, disjunction $+$, intersection $\times$, closure $*$, complement $C$, and bounded repetition $\{m, n\}$. We use $term(\varphi)$ to denote the set of terms and $strvar(\varphi)$ to denote the string variables occurring in $\varphi$. The \emph{literals} of $\varphi$ are $x\in \regex$ and $\alpha_1 \leq \alpha_2$. $x\in \regex$ is called \emph{regular literals} and $\alpha_1 \leq \alpha_2$ is called \emph{linear literals}.
\begin{table}[h]
  \centering
  \begin{tabular}{l r}
    $\varphi$ ::= $x\in \regex \mid \alpha_1\leq\alpha_2 \mid \neg\varphi\mid \varphi\vee\varphi$                                             & formulae            \\
    $\regex$ ::= $\epsilon \mid a \mid \regex\cdot\regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \regex^C \mid \regex \setminus \regex \mid \regex^{\{m,n\}}$ & regular expressions \\
    $\alpha$ ::= $m \mid i \mid  |s|\mid -\alpha\mid \alpha_1+\alpha_2$                                                                       & integer terms
  \end{tabular}
  \caption{Syntax}\label{tab:syntax}
\end{table}
% Semantic 
\subsubsection{Semantic}
We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables. $\eta: S\times\Sigma\rightarrow\Sigma^*$ is the interpretation on string where $\eta(c)=c$ for every letter $c\in \Sigma$. $\pi: I\rightarrow\mathbb{Z}$ is the interpretation of Presburger arithmetic. Then the semantics is given by a satisfaction relation: $\eta, \pi\models \varphi$ defined in Table \ref{tab:semantics}. We say a formula $\varphi$ is \emph{satisfiable} if a solution $(\eta, \pi)$ exists such as $\eta, \pi\models \varphi$. A formula $\varphi$ is \emph{unsatisfiable} if no solution exists.
\begin{table}[h]
  \centering
  \begin{tabular}{lcl}
    $\eta,\pi \models \varphi_1\vee \varphi_2$ & $\mathsf{iff}$ & $\eta,\pi \models \varphi_1 \text{ or } \eta,\pi \models \varphi_2$ \\
    $\eta,\pi \models \neg\varphi $            & $\mathsf{iff}$ & $\eta,\pi \not\models \varphi$                                      \\
    $\eta, \pi \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan(\regex),\eta,\pi \models x = w$                 \\
    $\eta, \pi \models \alpha_1 \leq \alpha_2$ & $\mathsf{iff}$ & $\pi(\alpha_1) \leq \pi(\alpha_2) $                                 \\
  \end{tabular}
  \caption{Semantics}
  \label{tab:semantics}
\end{table}
In addition to the classic regex operators (union, concatenation, closure), we syntactically support intersection, complement, and repetition. As we all know, the classic regular language is closed under intersection and complement \cite{aut_hopcraft}. Furthermore, the operation \emph{repetition} $\regex\{m,n\}$ means repeating regex $\regex$ at least $m$ times and at most $n$ times. It can be syntactically rewritten by concatenation and union:
$\regex\{m,n\} \equiv \regex^m\mid\cdots\mid\regex^n$ where $\regex^k$ defines concatenate $\regex$ $k$ times ($m\leq k\leq n$). So the regular language $\lan(\regex)$ defined in Table \ref{tab:syntax} is semantically equal to the classic regular language.

%\end{document}

### 2023-04-25 2023-1-19/sections/overview.tex
encode regex with counting to CEFA

@@
 The main idea is based on the observation that the occurrences of exact transitions can trace the counting times, and the length can be seen as the sum of occurrences of all transitions in the accepting run.
-For example, the counting times in $(\Sigma \setminus a)^{\{5, 40\}}$ can be traced by the occurrences of transitions in sub-regex $\Sigma \setminus a$.
+For example, the counting times in $(\Sigma \setminus a)^{\{5, 60\}}$ can be traced by the occurrences of transitions in sub-regex $\Sigma \setminus a$.
 To detail, we use one register to store counting, and symbolically add 1 when running one of the transitions in $\Sigma \setminus a$, tracing the counting times.
 Similarly, we use another register to store the length and symbolically add 1 to it when running any transition.
-The automaton model of string constraints \ref{eq:motivation_str_constraints} is illustrated in Figure \ref{fig:overview}.
+The automaton model of string constraints \ref{eqn-running} is illustrated in Figure \ref{fig:overview}.
 Register $r_1$ stores the counting times of the sub-regex $\Sigma \setminus a$, register $r_2$ stores the counting times of the sub-regex $\Sigma \setminus b$, register $r_3$ stores the counting times of the sub-regex $\Sigma \setminus c$, and register $r_4$ stores the length of the string.
 The label $\Sigma \setminus a:(1,0,0,1)$ means that when running the transition, the counting times of $\Sigma \setminus a$ (i.e., the value of $r_1$) plus 1, and the length (i.e., the value of $r_4$) plus 1.
-The accepting state $q_3$ is accepting by the linear integer arithmetic $5\leq r_1\leq 40\wedge 5\leq r_2\leq 40\wedge 0\leq r_3\leq 40\wedge 80 < r_4$.
-$5\leq r_1\leq 40$ ensure the counting times of $\Sigma \setminus a$ is in the range $[5, 40]$, $5\leq r_2\leq 40$ ensure the counting times of $\Sigma \setminus b$ is in the range $[5, 40]$, $0\leq r_3\leq 40$ ensure the counting times of $\Sigma \setminus c$ is in the range $[0, 40]$, and $80 < r_4$ ensure the length of the string is greater than 80.
+The accepting state $q_3$ is accepting by the linear integer arithmetic $5\leq r_1\leq 60\wedge 5\leq r_2\leq 60\wedge 0\leq r_3\leq 60\wedge 120 < r_4$.
+$5\leq r_1\leq 40$ ensure the counting times of $\Sigma \setminus a$ is in the range $[5, 60]$, $5\leq r_2\leq 60$ ensure the counting times of $\Sigma \setminus b$ is in the range $[5, 60]$, $0\leq r_3\leq 60$ ensure the counting times of $\Sigma \setminus c$ is in the range $[0, 60]$, and $120 < r_4$ ensure the length of the string is greater than $120$.
 The satisfiability of the CEFA can then be reduced to the satisfiability of linear integer arithmetic, which other off-the-shelf SMT solvers solve.
@@
 Recalling the CEFA (Fig.
-\ref{fig:overview:orgin}) handling the string constraints \ref{eq:motivation_str_constraints}, its transitions number between $q_1$ and $q_2$ are decided by the size of alphabet $\Sigma$.
+\ref{fig:overview:orgin}) handling the string constraints \ref{eqn-running}, its transitions number between $q_1$ and $q_2$ are decided by the size of alphabet $\Sigma$.
 We apply symbolic-aware simplification on it, then a much smaller CEFA (Fig.
@@
 The main idea is to explore paths within an exact length and manually compute the registers' values, rather than reduce CEFA to heavy linear integer arithmetic.
-For example, consider the string constraints $x \in (\Sigma \setminus a)^{\{5, 40\}} (\Sigma \setminus b)^{\{5, 40\}} (\Sigma \setminus c)^{\{0, 40\}} \wedge x \in \Sigma^* c$, we can explore paths within length 10 and get a satisfiable solution $cccccccccc$.
-\begin{equation}\label{eq:motivation_str_constraints}
-  x \in (\Sigma \setminus a)^{\{5, 40\}} (\Sigma \setminus b)^{\{5, 40\}} (\Sigma \setminus c)^{\{0, 40\}} \wedge x \in \Sigma^* c \wedge |x| > 80
-\end{equation}
+For example, consider the string constraints $x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c$, we can explore paths within length 10 and get a satisfiable solution $x = cccccccccc$.
 \begin{figure}[ht]

### 2023-04-25 2023-1-19/sections/introduction.tex
intro

@@
 \begin{equation}\label{eqn-running}
-x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{5, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120.
+x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120.
 \end{equation}
@@
 We implement the algorithm on top of OSTRICH, resulting into a new version of OSTRICH, called $\ostrichrecl$ for convenience.
+% 
 Furthermore, we utilize a collection of benchmark suites, which comprise 49,379 RECL constraints in total, to evaluate the performance of $\ostrichrecl$.
@@
 %
-The experimental results show that $\ostrichrecl$ can solve 49,128 out of 49,379 instances, while the state-of-the-art best solver Z3str3RE solves only 47,407 instances, with a timeout of 60 seconds.
+The experimental results show that $\ostrichrecl$ can solve 49,128 out of 49,379 instances, while the state-of-the-art best solver Z3str3RE solves only 47,407 instances, with the timeout set as 60 seconds.
 Moreover, $\ostrichrecl$ and Z3str3RE spend almost the same amount of time in average, that is, 2.5 seconds, in solving each instance.
+In particular, the string constraint in~(\ref{eqn-running}) can be solved by $\ostrichrecl$ within one second. 
 In comparison, CVC5, Z3str3, and Z3seq solve only 44,001, 36,320, 46,813 instances respectively, with an average time 7.8, 7.7, 3.8 seconds per instance.

### 2023-04-25 2023-1-19/figures/overview_example.tex

@@
     initial text=, every state/.style={minimum size = 0.001cm},
-    accepting text=$\scriptstyle5\leq r_1\leq 40\wedge 5\leq r_2\leq 40\wedge 0\leq r_3\leq 40\wedge 80 < r_4$, accepting/.style=accepting by arrow,
+    accepting text=$\scriptstyle5\leq r_1\leq 60\wedge 5\leq r_2\leq 60\wedge 0\leq r_3\leq 60\wedge 120 < r_4$, accepting/.style=accepting by arrow,
     accepting where=above

### 2023-04-25 2023-1-19/sections/algorithms.tex

--- 2023-04-11 2023-1-19/sections/algorithms.tex
@@
-\documentclass{standalone}
-\begin{document}
+%!TEX root = ../main.tex
+%\documentclass{standalone}
+%\begin{document}
 
-Based on the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve ESL formula $\varphi\wedge \psi$ where $\varphi$ is the conjunction of literals and $\psi$ is the conjunction of linear literals without length operation.
+As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers in automata, instead of unfolding them explicitly.
+Additionally, we represent string lengths using registers.
+This reduces the satisfiability of string constraints that involve regex-counting and string-length to the satisfiability of linear integer arithmetic, which can be solved by off-the-shelf SMT solvers.
+We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
+\subsection{Encode Counting Operator to CEFA} \label{subsec:regex2cefa}
+One key point of our approach is the encoding of counting operator.
+In this section, we define the construction of CEFA from the regular expression with counting.
+We divide the counting operator into \emph{handled} and \emph{non-handled}.
+The counting operator is called \emph{non-handled} if it is the sub-regex of other complement operator (e.g., $(\regex^{\{m,n\}})^C$), closure operator(e.g., $(\regex^{\{m,n\}})^*$), or counting operator (e.g., $(\regex^{\{m,n\}})^{\{m', n'\}}$), otherwise it is called \emph{handled}.
+A regex is called \emph{non-handled} if it contains any non-handled counting operators, and is called \emph{handled} otherwise.
+% We must syntactically rewrite bounded repetition $\regex\{m,n\}$ if it is the sub-regex of complement (e.g., $(\regex\{m,n\})^C$), closure(e.g., $(\regex\{m,n\})^*$), and bounded repetition(e.g., $(\regex\{m,n\})\{m', n'\}$), we unwind it to $\regex^m\mid\cdots\mid\regex^n$.
+After this syntactic rewriting, we call the resulting regex $\regex'$ \emph{non-nested}.
+Given a handled regex $\regex$, operations such as intersection, union, concatenation, complement, closure, and counting may appear.
+To construct the CEFA of $\regex$, we first create CEFA for each sub-regex and then combine them.
+Similar to the construction of NFA from regex\cite{aut_hopcraft}, our construction is inductive on the size of $\regex$.
+The base case is the construction for a single character, an empty string, or an empty language.
+The inductive step is the construction for the concatenation, union, intersection of two automata of sub-regexes, counting, closure, and complement of one automaton of sub-regex.
+We only discuss the inductive step for counting because it is the most important and the other operations are trivial.
+\newline
+For a handled regular expression $\regex\{m,n\}$, suppose the CEFA recognizing $\regex$ is $\aut = (Q,\Sigma,\delta,q_I,F,\emptyset,\top)$, then the CEFA recognizing $\regex\{m,n\}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_ I, F, r, \theta)$ where:
+\begin{itemize}
+  \item $r$ is a new register,
+  \item $\delta'$ is composed by transition $q\xrightarrow[(0)]{a} q'$ for each transition $q\xrightarrow[()]{a} q' \in \delta$, and transition $q_f\xrightarrow[(1)]{\epsilon} q_I$ for each accepting state $q_f\in F$,
+  \item $\theta$ is the function mapping each accepting state to a same linear integer arithmetic $m\leq r\leq n$.
+\end{itemize}
+The construction is illustrated in Fig.\ref{fig:construct_repetition}, where a new register $r$ is added to store the counting times.
+The transition $q\xrightarrow[(1)]{\epsilon} q_I$ is used to update the counting times for each $q\in F$.
+The accepting condition $\theta'$ constrains the counting times of the accepting word to the range $[m, n]$.
+\begin{figure}[h]
+  \begin{subfigure}[b]{0.49\textwidth}
+    \centering
+    \begin{tikzpicture}[
+      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+      initial text=, every state/.style={minimum size = 0.001cm},
+      accepting text=$\top$, accepting/.style=accepting by arrow,
+      ]
+
+      \node[state,initial]            (q_0)                      {};
+      \node[state, accepting]         (q_1) [right=of q_0]       {};
+      \node [fit=(q_0) (q_1)] {$\cdots$};
+    \end{tikzpicture}
+    \caption{The CEFA recognizing $\regex$}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \centering
+    \begin{tikzpicture}[
+      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+      initial text=, every state/.style={minimum size = 0.001cm},
+      accepting text=\myemph{$m\leq r\leq n$}, accepting/.style=accepting by arrow,
+      ]
+
+      \node[state,initial]            (q_0)                      {};
+      \node[state, accepting]         (q_1) [right=of q_0]       {};
+      \path[->] (q_1) edge[bend right]   node    [above] {\myemph{$\mathbf{\epsilon/(1)}$}} (q_0);
+      \node [fit=(q_0) (q_1)] {$\cdots$};
+    \end{tikzpicture}
+    \caption{The CEFA recognizing $\regex^{\{m,n\}}$}
+  \end{subfigure}
+  \caption{The construction of counting operator}
+  \label{fig:construct_repetition}
+\end{figure}
+\begin{example}
+  To construct the CEFA recognizing $(ab)\{1,100\}$.
+As shown in Fig.\ref{subfig:rep_aut_ab1_100}, the base cases are the constructions of character $a$ (Fig.\ref{subfig:rep_aut_a}) and $b$ (Fig.\ref{subfig:rep_aut_b}).
+The first inductive step is to concatenate them to one automaton (Fig.\ref{sub@subfig:rep_aut_ab}).
+The second inductive step is to add counting information on the automaton.
+To do that we add a new register $r_1$ and a transition $q_2\xrightarrow[(1)]{\epsilon} q_0$ to update the repetition times.
+The accepting condition in accepting state is $1\leq r_1\leq 100$ so that the counting time of the accepting word is in the range $[1,100]$.
+After that we get the CEFA recognizing $(ab)\{1,100\}$ shown in Fig.\ref{subfig:rep_aut_ab1_100}.
+  \begin{figure}[h]
+    \begin{subfigure}[b]{0.49\textwidth}
+      \centering
+      \begin{tikzpicture}[
+        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+        initial text=, every state/.style={minimum size = 0.001cm},
+        accepting text=$\top$, accepting/.style=accepting by arrow,
+        accepting where=above
+        ]
+
+        \node[state,initial]            (q_0)                      {};
+        \node[state,accepting]                    (q_1) [right=of q_0]       {};
+
+        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1);
+      \end{tikzpicture}
+      \caption{The CEFA recognizing $a$}
+      \label{subfig:rep_aut_a}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \centering
+      \begin{tikzpicture}[
+        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+        initial text=, every state/.style={minimum size = 0.001cm},
+        accepting text=$\top$, accepting/.style=accepting by arrow,
+        accepting where=above
+        ]
+
+        \node[state,initial]            (q_0)                      {};
+        \node[state,accepting]                    (q_1) [right=of q_0]       {};
+
+        \path[->] (q_0) edge              node      [above]           {$b$/()} (q_1);
+      \end{tikzpicture}
+      \caption{The CEFA recognizing $b$}
+      \label{subfig:rep_aut_b}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \centering
+      \begin{tikzpicture}[
+        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+        initial text=, every state/.style={minimum size = 0.001cm},
+        accepting text=$\top$, accepting/.style=accepting by arrow,
+        accepting where=above
+        ]
+
+        \node[state,initial]            (q_0)                      {};
+        \node[state]                    (q_1) [right=of q_0]       {};
+        \node[state, accepting]         (q_2) [right=of q_1]       {};
+
+        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
+        (q_1) edge              node      [above]           {$b$/()} (q_2);
+      \end{tikzpicture}
+      \caption{The CEFA recognizing $ab$}
+      \label{subfig:rep_aut_ab}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \centering
+      \begin{tikzpicture}[
+        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+        initial text=, every state/.style={minimum size = 0.001cm},
+        accepting text=\myemph{1}$\leq r_1\leq$\myemph{100}, accepting/.style=accepting by arrow,
+        accepting where=above
+        ]
+
+        \node[state,initial]            (q_0)                      {};
+        \node[state]                    (q_1) [right=of q_0]       {};
+        \node[state,accepting]          (q_2) [right=of q_1]       {};
+
+        \path[->] (q_0) edge              node      [above]           {$a$/(\myemph{0})} (q_1)
+        (q_1) edge              node      [above]           {$b$/(\myemph{0})} (q_2)
+        (q_2) edge [bend left]  node      [below]           {$\epsilon$/(\myemph{1})} (q_0);
+      \end{tikzpicture}
+      \caption{The CEFA recognizing $(ab)\{\myemph{1},\myemph{100}\}$}
+      \label{subfig:rep_aut_ab1_100}
+    \end{subfigure}
+    \caption{The example of constructing regex with counting}
+  \end{figure}
+\end{example}
+Above discusses the construction of counting operator in a handled regex.
+The counting operator of unhandled regex can not be constructed by the same way.
+For example, for an unhandled regex $(ab^{\{1,100\}})*$, there are infinite repetitions of regex $ab^{\{1,100\}}$.
+The counting times of each repetition are irrelevant, so that we can not represent them use finite registers.
+The way we solved this problem is to syntactically rewrite the unhandled counting operator.
+More exactly, the sub-regex $\regex^{\{m,n\}}$ in the unhandled regex is rewritten into $\underbrace{\regex\cdot\regex\cdots\regex}_{m \text{ times}}\mid\cdots\mid \underbrace{\regex\cdot\regex\cdots\regex}_{n \text{ times}}$.
+% Based on the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve ESL formula $\varphi\wedge \psi$ where $\varphi$ is the conjunction of literals and $\psi$ is the conjunction of linear literals without length operation.
 For each string variable $x$, we first compute pre-images of all linear literal $i=|x|$.
@@
 Otherwise, the string constraints are satisfiable.
-The emptiness checking problem of CEFAs under linear integer arithmetic is theoretically pspace-complete\cite{atva2020}.
+% The emptiness checking problem of CEFAs under linear integer arithmetic is theoretically pspace-complete\cite{atva2020}.
 To solve it efficiently for a practical example, we develop heuristic ways such as under-approximation (Section \ref{subsec:under-approx}) and symbolic-aware simplification (Section \ref{subsec:simplify}).
+
+\subsection{Pre-iamge}
+\denghang{TODO}
+
 \subsection{High-level algorithm}

### 2023-04-25 2023-1-19/sections/recl.tex
RECL

@@
 
-\subsubsection{Syntax}
-This paper proposes a quantifier-free first-order logic called \textit{Extended String Logic (ESL)}, whose syntax is presented in Table \ref{tab:syntax}.
-$\varphi$ is a quantifier-free formula that can be a regular membership $x\in\regex$, a quantifier-free Presburger formula $\alpha_1 \leq \alpha_2$, a negation of a formula, or a disjunction of two formulas.
+%\subsubsection{Syntax}
+In the sequel, we define string constraints with regex-counting and string-length function (abbreviated as RECL). The syntax of RECL is defined by the rules in Table~\ref{tab:syntax}. 
+A RECL formula $\varphi$ is a conjunction of atomic formulas of the form $x \in \regex$, $x \not \in \regex$, or $t_1\ \op\ t_2$, where $x$ is a string variable, $\regex$ is a regular expression,  
+$t_1$ and $t_2$ are integer terms, and $\op \in \{=, \neq, \le, \ge, <, >\}$.
+Atomic formulas of the form $x \in \regex$ or $x \not \in \regex$ are called \emph{regular membership} constraints and atomic formulas of the form $t_1\ \op\ t_2$ are called \emph{length} constraints.
+%
+A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, alternation $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
+% 
+%is a quantifier-free formula that can be a regular membership $x\in\regex$, a quantifier-free Presburger formula $\alpha_1 \leq \alpha_2$, a negation of a formula, or a disjunction of two formulas.
 $\alpha$ is an integer term which can be an integer constant $m$, integer variable $i$, the length of the string term $|s|$, the minus of an integer term, and the plus of two integer terms.
@@
   \begin{tabular}{l r}
-    $\varphi$ ::= $x\in \regex \mid \alpha_1\leq\alpha_2 \mid \neg\varphi\mid \varphi\vee\varphi$                                             & formulae            \\
-    $\regex$ ::= $\epsilon \mid a \mid \regex\cdot\regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \regex^C \mid \regex \setminus \regex \mid \regex^{\{m,n\}}$ & regular expressions \\
-    $\alpha$ ::= $m \mid i \mid  |s|\mid -\alpha\mid \alpha_1+\alpha_2$                                                                       & integer terms
+    $\varphi$ ::= $x\in \regex \mid x \not \in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi $                                             & formulas            \\
+    $\regex$ ::= $\emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \overline{\regex} \mid \regex \setminus \regex \mid \regex^{\{m,n\}} \mid \regex^{\{m,\infty\}}$ & regular expressions \\
+    $t$ ::= $n \mid i \mid  |x| \mid t - t \mid t + t$                                                                       & integer terms
   \end{tabular}
-  \caption{Syntax}\label{tab:syntax}
+  \caption{Syntax of RECL }\label{tab:syntax}
 \end{table}
 % Semantic
-\subsubsection{Semantic}
+
+\zhilin{stopped here}
+
+%\subsubsection{Semantic}
 We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables.

### 2023-04-26 2023-1-19/sections/preliminaries.tex
intro
prelim

@@
 %Let 
-For a string $u$, we use $|u|$ to denote the number of letters in $u$. In particular, $|\varepsilon|=0$. Moreover, for $a \in \Sigma$, let $|u|_a$ denote the number of occurrences of $a$ in $u$. 
+For a string $u$, we use $|u|$ to denote the number of letters in $u$. In particular, $|\varepsilon|=0$. 
+%Moreover, for $a \in \Sigma$, let $|u|_a$ denote the number of occurrences of $a$ in $u$. 
 Assume $u=a_0\cdots a_{n-1}$ is nonempty and $i<j \in [0,n-1]$. %Then a \emph{position} of $u$ is a number $i \in [|u|]$ (Note that the first position is $1$, instead of  0). In addition, 
@@
 %\tl{check later for consistency}\zhilin{the indices start from 0, to be consistent with the semantics of substring and indexof}\zhilin{i do use it in section 4}
-
-Let $u, v$ be two strings. We use $u \cdot v$ to denote the \emph{concatenation} of $u$ and $v$.
+%
+Let $u, v$ be two strings. We use $u \cdot v$ to denote the \emph{concatenation} of $u$ and $v$. A language $L$ over $\Sigma$ is a subset of strings.  
+A concatenation of two languages $L_1$ and $L_2$ is defined as $\{u \cdot v \mid u \in L_1, v \in L_2\}$.
+For a language $L$ and $n \in \Nat$, we define $L^n$ inductively as follows: $L^0= \{\varepsilon\}$, $L^{n+1} = L \cdot L^n$ for every $n \in \Nat$.
 %, that is, the string $w$ such that $|w|= |u| + |v|$ and for each $i \in [0, |u|-1]$, $w[i]= u[i]$, and for each $i \in [0,|v|-1]$, $w[|u|+i]=v[i]$.

### 2023-04-26 2023-1-19/sections/recl.tex
prelim

@@
 %\subsubsection{Syntax}
-In the sequel, we define string constraints with regex-counting and string-length function (abbreviated as RECL). The syntax of RECL is defined by the rules in Table~\ref{tab:syntax}. 
-A RECL formula $\varphi$ is a conjunction of atomic formulas of the form $x \in \regex$, $x \not \in \regex$, or $t_1\ \op\ t_2$, where $x$ is a string variable, $\regex$ is a regular expression,  
+In the sequel, we define string constraints with regex-counting and string-length function (abbreviated as RECL).
+The syntax of RECL is defined by the rules in Figure~\ref{fig:syntax}, where $x$ is a string variable, $i$ is an integer variable, $a$ is a character from an alphabet $\Sigma$, and $m, n$ are integer constants.
+A RECL formula $\varphi$ is a conjunction of atomic formulas of the form $x \in \regex$, $x \not \in \regex$, or $t_1\ \op\ t_2$, where $\regex$ is a regular expression,  
 $t_1$ and $t_2$ are integer terms, and $\op \in \{=, \neq, \le, \ge, <, >\}$.
@@
 A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, alternation $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
+An integer term is is built from constants $n$, variables $i$, and string lengths $|x|$, by operators $+$ and $-$.
 % 
@@
 $x\in \regex$ is called \emph{regular literals} and $\alpha_1 \leq \alpha_2$ is called \emph{linear literals}.
-\begin{table}[h]
+\begin{figure}[h]
   \centering
-  \begin{tabular}{l r}
-    $\varphi$ ::= $x\in \regex \mid x \not \in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi $                                             & formulas            \\
-    $\regex$ ::= $\emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \overline{\regex} \mid \regex \setminus \regex \mid \regex^{\{m,n\}} \mid \regex^{\{m,\infty\}}$ & regular expressions \\
-    $t$ ::= $n \mid i \mid  |x| \mid t - t \mid t + t$                                                                       & integer terms
-  \end{tabular}
-  \caption{Syntax of RECL }\label{tab:syntax}
-\end{table}
-% Semantic
+%  \begin{tabular}{l r}
+$ \begin{array}{l l l r}
+    \varphi & ::= & x\in \regex \mid x \not \in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi                                              & \mbox{formulas}            \\
+    \regex &::= & \emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \overline{\regex} \mid \regex \setminus \regex \mid \regex^{\{m,n\}} \mid \regex^{\{m,\infty\}} \mid (e) & \mbox{regexes} \\
+    t &::= & n \mid i \mid  |x| \mid t - t \mid t + t                                                                    & \mbox{integer terms}
+    \end{array}
+  $
+%  \end{tabular}
+  \caption{Syntax of RECL }\label{fig:syntax}
+\end{figure}
+Moreover, for $S \subseteq \Sigma$ with $S = \{a_1, \cdots, a_k\}$, we use $S$ as an abbreviation of $a_1 + \cdots + a_k$.
 
@@
 %\subsubsection{Semantic}
+
 We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables.

### 2023-04-26 2023-1-19/sections/preliminaries.tex
string constraint

@@
 Let $u, v$ be two strings. We use $u \cdot v$ to denote the \emph{concatenation} of $u$ and $v$. A language $L$ over $\Sigma$ is a subset of strings.  
-A concatenation of two languages $L_1$ and $L_2$ is defined as $\{u \cdot v \mid u \in L_1, v \in L_2\}$.
+Let $L_1, L_2$ be two languages.
+Then the concatenation of $L_1$ and $L_2$, denoted by $L_1 \cdot L_2$,  is defined as $\{u \cdot v \mid u \in L_1, v \in L_2\}$.
+The union (resp.
+intersection) of $L_1$ and $L_2$, denoted by $L_1 \cup L_2$  (resp.
+$L_1 \cap L_2$), is defined as $\{u \mid u \in L_1 \mbox{ or } u \in L_2\}$ (resp.
+$\{u \mid u \in L_1 \mbox{ and } u \in L_2\}$).
+The complement of $L_1$, denoted by $\overline{L_1}$, is defined as $\{u \mid u \in \Sigma^*, u \not \in L_1\}$.
+The difference of $L_1$ and $L_2$, denoted by $L_1 \setminus L_2$, is defined as $L_1 \cap \overline{L_2}$. 
 For a language $L$ and $n \in \Nat$, we define $L^n$ inductively as follows: $L^0= \{\varepsilon\}$, $L^{n+1} = L \cdot L^n$ for every $n \in \Nat$. 
+Finally, define $L^* = \bigcup \limits_{n \in \Nat} L^n$.
 %, that is, the string $w$ such that $|w|= |u| + |v|$ and for each $i \in [0, |u|-1]$, $w[i]= u[i]$, and for each $i \in [0,|v|-1]$, $w[|u|+i]=v[i]$.
@@
 It is well-known that finite automata capture regular languages precisely.
+Moreover, the class of regular languages is closed under union, intersection, Kleene star, complement, and language difference \cite{HU79}.
 

### 2023-04-26 2023-1-19/sections/cefa.tex
cefa

@@
 
-In this section, we recall the definition of CEFA and Parikh image.
+In this section, we define the model of cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on.
 
 %\subsection{Cost-Enriched Finite Automaton} \label{subsec:cefa}
-The definition of CEFA in this paper is lightly different from the definition in \cite{atva2020}.
-In \cite{atva2020}, the cost function is defined as a function $\eta: \Sigma \rightarrow \mathbb{N}$.
+The definition of CEFA below is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions specified by LIA formulas, where the free variables are the registers, are attached to final states.
+%
+%In~\cite{atva2020}, the cost function is defined as a function $\eta: \Sigma \rightarrow \mathbb{N}$.
 In this paper, we define the cost function as an integer vector whose elements are the incremental value of registers.
@@
 \begin{definition}[Cost-Enriched Finite Automaton]
-  A cost-enriched finite automaton $\aut$ is a 7-tuple $(Q, \Sigma, \delta, q_I, F, R, \theta)$ where
+  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, q_0, F, \theta)$ where
   \begin{itemize}
-    \item $Q,\Sigma,q_I,F$ is defined as NFA,
-    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
-    \item $\delta$ is a transition set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.
+  \item $R = \{r_1, \cdots, r_n\}$ is a finite set of registers, 
+    \item $Q, \Sigma, q_0, F$ are as in the definition of NFA,
+%    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
+    \item $\delta \subseteq Q \times \Sigma_\varepsilon \times Q \times (\Int^n)^R$ is a transition set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.
 $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.

### 2023-04-26 2023-1-19/sections/introduction.tex
cefa

@@
 Our main idea is to represent the counting operators by registers in automata, instead of unfolding them explicitly.
-Our approach is built upon an automata model called cost-enriched finite automata (CEFA) that was proposed in~\cite{atva2020}.
+Our approach is built upon an automata model called cost-enriched finite automata (CEFA), which was proposed in~\cite{atva2020} to solve string constraints involving the integer data type.
 Moreover, the string-length function can also be modeled by registers in CEFA.
@@
 In comparison, CVC5, Z3str3, and Z3seq solve only 44,001, 36,320, 46,813 instances respectively, with an average time 7.8, 7.7, 3.8 seconds per instance.
+
+At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA that was introduced.
+This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, the regex-counting was unfolded explicitly.
+Moreover, in~\cite{atva2020}, the nonemptiness of CEFA was solved by utilizing the model checker nuXmv~\cite{nuxmv}, while in this work, it is solved by integrating the techniques of Parikh image computation, automata-size reduction, under approximation, and SMT solvers for LIA.
+The experimental results show that our approach achieves better performance than that in~\cite{atva2020}.
+\zhilin{this point should be supposed by experimental results.}
 

### 2023-04-26 2023-1-19/sections/preliminaries.tex
cefa

@@
 A string over $\Sigma$ is a (possibly empty) sequence of elements from $\Sigma$,
-denoted by $u, v, w, \ldots$. An empty string is denoted by $\varepsilon$.  We write $\Sigma^*$ (resp., $\Sigma^+$) for the set of all (resp. nonempty) strings over $\Sigma$.
+denoted by $u, v, w, \ldots$.
+An empty string is denoted by $\varepsilon$.
+We use $\Sigma_\varepsilon$ to denote $\Sigma \cup \{\varepsilon\}$.
+We write $\Sigma^*$ (resp., $\Sigma^+$) for the set of all (resp.
+nonempty) strings over $\Sigma$.
 %Let 
@@
 \paragraph*{Finite state automata.} 
-A \emph{(nondeterministic) finite state automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, I, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $I,F \subseteq Q$ are the set of initial and final states respectively.
+A \emph{(nondeterministic) finite state automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, q_0, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $q_0 \in Q$ is the initial state, and $F \subseteq Q$ is the set of final states.
 For readability, we write a transition $(q, a, q') \in \delta$ as $q \xrightarrow[\delta]{a} q'$ (or simply $q \xrightarrow{a} q'$).
@@
 %
-A \emph{run} of $\NFA$ on a string $w = a_1 \cdots a_n$ is a sequence of transitions $q_0 \xrightarrow{a_1} q_1 \cdots q_{n-1} \xrightarrow{a_n} q_n$ with $q_0 \in I$.
-The run is \emph{accepting} if $q_n \in F$.
+A \emph{run} of $\NFA$ on a string $w = a_1 \cdots a_n$ is a sequence of transitions $q_0 \xrightarrow{a_1} q_1 \cdots q_{n-1} \xrightarrow{a_n} q_n$. The run is \emph{accepting} if $q_n \in F$.
 A string $w$ is accepted by an NFA $\NFA$ if there is an accepting run of $\NFA$ on $w$.

### 2023-04-26 2023-1-19/sections/algorithms.tex
algorithm

@@
 We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
-\subsection{Encode Counting Operator to CEFA} \label{subsec:regex2cefa}
+\subsection{Encode Regex-Counting to CEFA} \label{subsec:regex2cefa}
 One key point of our approach is the encoding of counting operator.
@@
       initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=\myemph{$m\leq r\leq n$}, accepting/.style=accepting by arrow,
+      accepting text=\myemph{$\scriptstyle m\leq r\leq n$}, accepting/.style=accepting by arrow,
       ]
@@
       \node[state, accepting]         (q_1) [right=of q_0]       {};
-      \path[->] (q_1) edge[bend right]   node    [above] {\myemph{$\mathbf{\epsilon/(1)}$}} (q_0);
+      \path[->] (q_1) edge[bend right]   node    [above] {\myemph{$\scriptstyle \mathbf{\epsilon:(1)}$}} (q_0);
       \node [fit=(q_0) (q_1)] {$\cdots$};
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\top$, accepting/.style=accepting by arrow,
+        accepting text=$\scriptstyle \top$, accepting/.style=accepting by arrow,
         accepting where=above
@@
 
-        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1);
+        \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:()$} (q_1);
       \end{tikzpicture}
@@
 
-        \path[->] (q_0) edge              node      [above]           {$b$/()} (q_1);
+        \path[->] (q_0) edge              node      [above]           {$\scriptstyle b:()$} (q_1);
       \end{tikzpicture}
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\top$, accepting/.style=accepting by arrow,
+        accepting text=$\scriptstyle\top$, accepting/.style=accepting by arrow,
         accepting where=above
@@
 
-        \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
-        (q_1) edge              node      [above]           {$b$/()} (q_2);
+        \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:()$} (q_1)
+        (q_1) edge              node      [above]           {$\scriptstyle b:()$} (q_2);
       \end{tikzpicture}
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=\myemph{1}$\leq r_1\leq$\myemph{100}, accepting/.style=accepting by arrow,
+        accepting text=$\scriptstyle\myemph{1}\leq r_1\leq\myemph{100}$, accepting/.style=accepting by arrow,
         accepting where=above
@@
 
-        \path[->] (q_0) edge              node      [above]           {$a$/(\myemph{0})} (q_1)
-        (q_1) edge              node      [above]           {$b$/(\myemph{0})} (q_2)
-        (q_2) edge [bend left]  node      [below]           {$\epsilon$/(\myemph{1})} (q_0);
+        \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:(\myemph{0})$} (q_1)
+        (q_1) edge              node      [above]           {$\scriptstyle b:(\myemph{0})$} (q_2)
+        (q_2) edge [bend left]  node      [below]           {$\scriptstyle \epsilon:(\myemph{1})$} (q_0);
       \end{tikzpicture}
@@
 The counting times of each repetition are irrelevant, so that we can not represent them use finite registers.
-The way we solved this problem is to syntactically rewrite the unhandled counting operator.
+So we syntactically rewrite the unhandled counting operator into union operator and concatenation operator.
 More exactly, the sub-regex $\regex^{\{m,n\}}$ in the unhandled regex is rewritten into $\underbrace{\regex\cdot\regex\cdots\regex}_{m \text{ times}}\mid\cdots\mid \underbrace{\regex\cdot\regex\cdots\regex}_{n \text{ times}}$.
@@
 To solve it efficiently for a practical example, we develop heuristic ways such as under-approximation (Section \ref{subsec:under-approx}) and symbolic-aware simplification (Section \ref{subsec:simplify}).
+\subsection{Pre-iamge of String-length}
+Given a string-length constraint, we build a CEFA with a register storing the length of accepted word.
+We call such a CEFA the \emph{pre-image} of it.
+Formally, the pre-image of length constraint is a CEFA $(\{q_I\}, \Sigma, \{q_I\xrightarrow[(1)]{\Sigma} q_I\}, q_I, \{q_I\}, r, \theta)$ where accpeting condition $\theta$ is based on the length value.
+For example, example \ref{eg:pre_len} shows the pre-image of length constraints $i=|x|$, in which $\theta(q_I)$ is $r = i$.
+This automaton contains a simple loop which increase $1$ on register $r$ for all char in $\Sigma$.
+So the accepting words of it is all words with length $i$.
+\newline
+% The formal definition of pre-images of abundant string functions is listed in \cite{atva2020}, and we do not repeat it here.
+\begin{example}[The pre-image of $i = |x|$]\label{eg:pre_len} 
+  \begin{figure}[h]
+    \centering
+    \begin{tikzpicture}[
+      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+      initial text=, every state/.style={minimum size = 0.001cm},
+      accepting text=$\scriptstyle{r=i}$, accepting/.style=accepting by arrow
+      ]
 
-\subsection{Pre-iamge}
-\denghang{TODO}
+      \node[state,initial,accepting]            (q_0)       {$q_I$};
 
-\subsection{High-level algorithm}
-\begin{algorithm}[h]
-  \caption{High-level algorithm}
-  \label{alg:high}
-  \begin{algorithmic}[1]
-    \Require Conjunction of literals $\varphi$ and conjunction of linear literals $\psi$
-    \Ensure \emph{sat} or \emph{unsat}
-    \Statex
-    \State $finalAuts \leftarrow \emptyset$
-    \ForAll{string variables $x$ occurring in $\varphi$}
-    \State $\aut_{len} \leftarrow$ intersection of all pre-images of $i=|x|$ in $\varphi$
-    \State $\aut_{regex} \leftarrow$ intersection of all CEFAs of $x \in \regex$ in $\varphi$
-    \State $\aut_x \leftarrow$ intersection of $\aut_{len}$ and $\aut_{regex}$
-    \State $\aut_{nfa} \leftarrow$ NFA form of $\aut_x$
-    \If{$\aut_{nfa}$ is empty}
-    \State \textbf{return} \emph{unsat}
-    \EndIf
-    \State $finalAuts \leftarrow finalAuts \cup \{\aut_x\}$
-    \EndFor
-    \If{$\algfun{isEmpty}(finalAuts, \psi)$ }
-    \State \textbf{return} \emph{unsat}
-    \Else
-    \State \textbf{return} \emph{sat}
-    \EndIf
-  \end{algorithmic}
-\end{algorithm}
-The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process.
-We construct the automata of all length operations occurring in the ESL conjunction $\varphi$ at line 3 and the automata of all regular memberships at line 4.
-In the following steps, we call an automaton to be \emph{final} if we will not operate it anymore.
-The set $finalAuts$ contains all final automata for all string variables and is initially empty at line 1.
-The intersection of $\aut_{len}$ and $\aut_{regex}$ at line 5 ensures the final automaton of $x$ reserves both length and regular information.
-At line 6, we compute an NFA form to throw unsat rapidly.
-An NFA form of CEFA is obtained by removing update functions and accepting conditions while maintaining graph structure.
-More exactly, given a CEFA $\aut = (Q,\Sigma, \delta, q_I, F, R, \theta)$, the NFA form of $\aut$ is $(Q, \Sigma, \delta', q_I, F)$ where $\delta'$ is composed of transition $q\xrightarrow[]{a} q'$ for $q\xrightarrow[\myvec{v}]{a} q'\in \delta$.
-It is obvious that the NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7.
-Sometimes the over-approximation is useful.
-For example, to solve the string constraint $x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^* $ which CVC5 has failed on, the NFA form is empty because there is no path to accepting states.
-\newline
-After obtaining all final CEFAs of all string variables and their NFA forms are not empty, we check whether the final CEFAs are empty under the linear integer arithmetic $\psi$ at line 12.
-If they are empty under $\psi$, we return $unsat$.
-Otherwise, we return $sat$.
+      \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma:(1)$} ();
+    \end{tikzpicture}
+  \end{figure}
+\end{example} 
+\subsection{Combine Regex-counting and String-length}
+In the previous section, we have discussed the construction of regex-counting operator and the pre-image of string-length constraint.
+In this section, we show how to combine them to deal with the string constraints with regex-counting and string-length.
+\begin{definition} [The Product of Two CEFA]\newline
+  Given two CEFAs $\aut_1 = (Q_1, \Sigma, \delta_1, q_{I_1}, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2, q_{I_2}, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the product of them, denoted by $\aut_1 \times \aut_2$, is defined as $(Q_1\times Q_2, \Sigma, \delta, (q_{I_1}, q_{I_2}), F_1\times F_2, R_1\cup R_2, \theta)$ where
+  \begin{itemize}
+    \item $\delta$ comprises the tuples $((q_1, q_2), a, (q_1', q_2'), \myvec{v_1}\cdot \myvec{v_2})$ such that $(q_1, a, q_1', \myvec{v_1})\in \delta_1$ and $(q_2, a, q_2', \myvec{v_2})\in \delta_2$.
+    \item $\theta((q_1, q_2))$ is $\theta_1(q_1)\wedge \theta_2(q_2)$ for each accepting state $(q_1, q_2)\in F_1\times F_2$.
+  \end{itemize}
+\end{definition}
+With the help of product, we can combine the CEFAs of regex-counting and string-length.
+For example, the CEFA of string constraints $x\in \regex \wedge i=|x|$ is the product of the CEFA of $x\in \regex$ and the pre-image of $i=|x|$.
 
-\subsection{Emptiness Checking} \label{subsec:emptiness}
+\subsection{Emptiness Checking Problem on CEFAs} \label{subsec:emptiness}
 As mentioned, the emptiness checking problem of CEFAs under linear integer arithmetic $P$ is theoretically Pspace-complete.
@@
 \end{algorithm}
-
 \subsubsection{Symbolic-Aware Simplification} \label{subsec:simplify}
@@
     \end{subfigure}
-    \caption{Symbolic simplification can remove duplicated transitions and states.}
+    \caption{Symbolic simplification removes duplicated transitions and states.}
     \label{fig:simplification_example}
@@
     \end{subfigure}
-    \caption{Symbolic simplification can remove duplicated transitions and states.}
+    \caption{Symbolic simplification removes duplicated transitions and states.}
     \label{fig:duplicate}
@@
 
+\subsection{High-level algorithm}
+\begin{algorithm}[h]
+  \caption{High-level algorithm}
+  \label{alg:high}
+  \begin{algorithmic}[1]
+    \Require Conjunction of literals $\varphi$ and conjunction of linear literals $\psi$
+    \Ensure \emph{sat} or \emph{unsat}
+    \Statex
+    \State $finalAuts \leftarrow \emptyset$
+    \ForAll{string variables $x$ occurring in $\varphi$}
+    \State $\aut_{len} \leftarrow$ intersection of all pre-images of $i=|x|$ in $\varphi$
+    \State $\aut_{regex} \leftarrow$ intersection of all CEFAs of $x \in \regex$ in $\varphi$
+    \State $\aut_x \leftarrow$ intersection of $\aut_{len}$ and $\aut_{regex}$
+    \State $\aut_{nfa} \leftarrow$ NFA form of $\aut_x$
+    \If{$\aut_{nfa}$ is empty}
+    \State \textbf{return} \emph{unsat}
+    \EndIf
+    \State $finalAuts \leftarrow finalAuts \cup \{\aut_x\}$
+    \EndFor
+    \If{$\algfun{isEmpty}(finalAuts, \psi)$ }
+    \State \textbf{return} \emph{unsat}
+    \Else
+    \State \textbf{return} \emph{sat}
+    \EndIf
+  \end{algorithmic}
+\end{algorithm}
+The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process.
+We construct the automata of all length operations occurring in the ESL conjunction $\varphi$ at line 3 and the automata of all regular memberships at line 4.
+In the following steps, we call an automaton to be \emph{final} if we will not operate it anymore.
+The set $finalAuts$ contains all final automata for all string variables and is initially empty at line 1.
+The intersection of $\aut_{len}$ and $\aut_{regex}$ at line 5 ensures the final automaton of $x$ reserves both length and regular information.
+At line 6, we compute an NFA form to throw unsat rapidly.
+An NFA form of CEFA is obtained by removing update functions and accepting conditions while maintaining graph structure.
+More exactly, given a CEFA $\aut = (Q,\Sigma, \delta, q_I, F, R, \theta)$, the NFA form of $\aut$ is $(Q, \Sigma, \delta', q_I, F)$ where $\delta'$ is composed of transition $q\xrightarrow[]{a} q'$ for $q\xrightarrow[\myvec{v}]{a} q'\in \delta$.
+It is obvious that the NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7.
+Sometimes the over-approximation is useful.
+For example, to solve the string constraint $x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^* $ which CVC5 has failed on, the NFA form is empty because there is no path to accepting states.
+\newline
+After obtaining all final CEFAs of all string variables and their NFA forms are not empty, we check whether the final CEFAs are empty under the linear integer arithmetic $\psi$ at line 12.
+If they are empty under $\psi$, we return $unsat$.
+Otherwise, we return $sat$.
+
 %\end{document}

### 2023-04-26 2023-1-19/sections/cefa.tex
algorithm

--- 2023-04-25 2023-1-19/sections/cefa.tex
@@
 
-In this section, we recall the definition of CEFA and Parikh image.
+In this section, we introduce the definition of CEFA, Parikh image and pre-iamge.
 
@@
 Two types of definitions have the same expressive ability on the $SAT_{CL}$ problem.
-\begin{definition}[Cost-Enriched Finite Automaton]
+\begin{definition}[Cost-Enriched Finite Automaton]\newline
   A cost-enriched finite automaton $\aut$ is a 7-tuple $(Q, \Sigma, \delta, q_I, F, R, \theta)$ where
@@
       initial text=, every state/.style={minimum size = 0.001cm,
-          accepting text=$1\leq r_1\leq 100$, accepting/.style=accepting by arrow}
+          accepting text=$\scriptstyle 1\leq r_1\leq 100$, accepting/.style=accepting by arrow}
       ]
@@
 
-      \path[->] (q_0) edge              node      [above]           {$a$/(1)} (q_1)
-      (q_1) edge              node      [above]           {$b$/(0)} (q_2)
-      (q_2) edge [bend left]  node      [below]           {$\epsilon$/(0)} (q_0);
+      \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:(1)$} (q_1)
+      (q_1) edge              node      [above]           {$\scriptstyle b:(0)$} (q_2)
+      (q_2) edge [bend left]  node      [below]           {$\scriptstyle\epsilon: (0)$} (q_0);
     \end{tikzpicture}
@@
     \label{fig:repetition}
-  \end{figure}
-\end{example}
-\begin{example}[The pre-image of length operation]\label{eg:pre_len} The length operation can be captured by a CEFA base on our previous work \cite{atva2020}.
-Fig.\ref{fig:len} shows a pre-image of linear literal $i=|x|$.
-It is easy to see that the pre-image accepts string words with length $i$.
-  \begin{figure}[h]
-    \centering
-    \begin{tikzpicture}[
-      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=${r_1=1}$, accepting/.style=accepting by arrow
-      ]
-
-      \node[state,initial,accepting]            (q_0)       {$q$};
-
-      \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
-    \end{tikzpicture}
-    \caption{The pre-image of $i = |x|$}
-    \label{fig:len}
   \end{figure}

### 2023-04-26 2023-1-19/sections/recl.tex

@@
 %
-A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, alternation $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
+A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, union $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
 An integer term is is built from constants $n$, variables $i$, and string lengths $|x|$, by operators $+$ and $-$.
@@
 
-\zhilin{stopped here}
+The definition of the semantics of RECL is somehow standard. Nevertheless, for completeness, we include the definition of semantics here.
 
-%\subsubsection{Semantic}
+For each regular expression $e$, the language defined by $e$, denoted by $\Lang(e)$, is defined recursively.
+For instance, $\Lang(\emptyset) = \emptyset$, $\Lang(\varepsilon) = \{\varepsilon\}$, $\Lang(a) = \{a\}$, and $\Lang(e_1 \cdot e_2) = \Lang(e_1) \cdot \Lang(e_2)$, $\Lang(e_1 + e_2) = \Lang(e_1) \cup \Lang(e_2)$, and so on.
+It is well-known that regular expressions define the same class of languages as finite state automata, that is, the class of regular languages \cite{HU79}.
 
+Let $\varphi$ be a RECL formula and $\svars(\varphi)$ (resp. $\ivars(\varphi)$) denote the set of string (resp. integer) variables occurring in $\varphi$. 
+%
+Then the semantics of formulas are defined with respect to a mapping $\theta: \svars(\varphi) \rightarrow \Sigma^* \uplus \ivars(\varphi) \rightarrow \Int$. 
+The mapping $\theta$ can be naturally extended to the set of integer terms. For instance, $\theta(|x|) =|\theta(x)|$, $\theta(t_1 + t_2) = \theta(t_1) + \theta(t_2)$. 
+A  mapping $\theta$ is said to satisfy $\varphi$, denoted by $\theta \models \varphi$, if one of the following holds,  
+\begin{itemize}
+\item $\varphi \equiv x \in \regex$ and $\theta(x) \in \Lang(\regex)$, 
+%
+\item $\varphi \equiv x \not \in \regex$ and $\theta(x) \not \in \Lang(\regex)$, 
+%
+\item $\varphi \equiv t_1\ \op\ t_2$ and $\theta(t_1)\ \op\ \theta(t_2)$, 
+%
+\item $\varphi \equiv \varphi_1 \wedge \varphi_2$ and $\theta \models \varphi_1$ and $\theta \models \varphi_2$.
+\end{itemize}
+A RECL formula $\varphi$ is said to be satisfiable if there is a mapping $\theta$ such that $\theta \models \varphi$.
+The satisfiability problem for RECL is to decide whether a given RECL formula $\varphi$ is satisfiable.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
 We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables.
@@
 \end{table}
+%
 In addition to the classic regex operators (union, concatenation, closure), we syntactically support intersection, complement, and repetition.
@@
 So the regular language $\lan(\regex)$ defined in Table \ref{tab:syntax} is semantically equal to the classic regular language.
+}
 

### 2023-04-27 2023-1-19/sections/cefa.tex
CEFA

@@
 %\subsection{Cost-Enriched Finite Automaton} \label{subsec:cefa}
-The definition of CEFA below is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions specified by LIA formulas, where the free variables are the registers, are attached to final states.
+The definition of CEFA below is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
+%specified by LIA formulas
+%, where the free variables are the registers, 
+are attached to final states. 
 %
@@
   \begin{itemize}
-  \item $R = \{r_1, \cdots, r_n\}$ is a finite set of registers, 
+  \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers, 
     \item $Q, \Sigma, q_0, F$ are as in the definition of NFA,
 %    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
-    \item $\delta \subseteq Q \times \Sigma_\varepsilon \times Q \times (\Int^n)^R$ is a transition set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.
+    \item $\delta \subseteq Q \times \Sigma_\varepsilon \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers, 
+%  set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.
 $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
-    \item $\theta: F\rightarrow \varphi$ is a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
+    \item $\alpha: F \rightarrow \Phi(R)$ attaches to each finite state an accepting condition that is specified by an LIA formula.
+%    a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
   \end{itemize}
-  The value of each register $r_i$ in $R$ is written as $\mathcal{V}(r_i)$ and is initiated to 0 at the initial state.
+\end{definition}
+
+For readability, we assume a linear order on $R$ and write $R$ as a vector $\myvec{r} = (r_1, \cdots, r_k)$.
+Moreover, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where for each $i \in [k]$, $v_i$ is the update on the value of $r_i$.
+We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$.
+
+The semantics of CEFA is define as follows. Let $\aut = (R, Q, \Sigma, \delta, q_0, F, \alpha)$ be a CEFA. 
+A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
+The \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$, where the value of each register is zero. 
+A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{b_1} q_1 \cdots q_{m-1}\xrightarrow[\myvec{v_m}]{b_m} q_m$ such that $w = b_1 \cdots b_m$ (some of $b_i$'s may be $\varepsilon$) and $q_{i-1} \xrightarrow[\myvec{v_i}]{b_i} q_i$ for each $i \in [m]$.
+A run $q_0 \xrightarrow[\myvec{v_1}]{b_1} q_1 \cdots q_{m-1}\xrightarrow[\myvec{v_m}]{b_m} q_m$ is \emph{accepting} if $q_m \in F$ and $\alpha(q_m)[\myvec{\myvec{v'}/\myvec{r}]$ is true, where $\myvec{v'} = \sum \limits_{j \in [m]} \myvec{v_j}}$.
+Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [m]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+A string $w$ is \emph{accepted} by $\aut$ if there is an accepting run of $\aut$ on $w$.
+The language defined by $\aut$, denoted by $\Lang(\aut)$, is the set of strings that are accepted by $\aut$.
+
+%The value of each register $r_i$ in $R$ is written as $\mathcal{V}(r_i)$ and is initiated to 0 at the initial state.
 A \emph{run} of $\aut$ on string $a_1\cdots a_m$ is a transition sequence $q_I\xrightarrow[\myvec{v_1}]{a_1}q_1\cdots q_{m-1}\xrightarrow[\myvec{v_m}]{a_m}q_m$  and $\mathcal{V}(r_i) = \displaystyle\sum_{j=1}^m \myvec{v_j}[i], i\in [1,n]$ is the value of $r_i$ after the run.
@@
 
-\end{definition}
 \begin{example} \label{eg:1}

### 2023-04-27 2023-1-19/sections/cefa.tex
cefa
CEFA

@@
 In this section, we define the model of cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
+%
+Intuitively, CEFA add write-only cost registers to finite state automata.
+Here by ``write-only'', we mean that the cost registers can only be written/updated, but cannot be read, that is, cannot be used to guard the transitions.
 
-%\subsection{Cost-Enriched Finite Automaton} \label{subsec:cefa}
-The definition of CEFA below is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
-%specified by LIA formulas
-%, where the free variables are the registers, 
-are attached to final states. 
 %
@@
 \end{definition}
+The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
+are attached to final states.
 
@@
 
+\zhilin{this example should be modified to match the running example}
 \begin{example} \label{eg:1}

### 2023-04-27 2023-1-19/sections/cefa.tex
example 1

@@
     \centering
-    \begin{tikzpicture}[
-      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      initial text=, every state/.style={minimum size = 0.001cm,
-          accepting text=$\scriptstyle 1\leq r_1\leq 100$, accepting/.style=accepting by arrow}
-      ]
-      \node[state,initial]            (q_0)                      {$q_0$};
-      \node[state]                    (q_1) [right=of q_0]       {$q_1$};
-      \node[state,accepting]          (q_2) [right=of q_1]       {$q_2$};
-
-      \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:(1)$} (q_1)
-      (q_1) edge              node      [above]           {$\scriptstyle b:(0)$} (q_2)
-      (q_2) edge [bend left]  node      [below]           {$\scriptstyle\epsilon: (0)$} (q_0);
-    \end{tikzpicture}
-    \caption{An automaton recognizing the language of $(ab)\{1,100\}$}
+    \input{figures/cefa_example.tex}
+    \caption{An automaton recognizing the language of $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$}
     \label{fig:repetition}

### 2023-04-28 2023-1-19/sections/algorithms.tex
algorithm

@@
 \begin{example}
-  To construct the CEFA recognizing $(ab)\{1,100\}$.
+  To construct the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ with alphabet $\Sigma = \{a,b,c\}$.
 As shown in Fig.\ref{subfig:rep_aut_ab1_100}, the base cases are the constructions of character $a$ (Fig.\ref{subfig:rep_aut_a}) and $b$ (Fig.\ref{subfig:rep_aut_b}).
@@
 To solve it efficiently for a practical example, we develop heuristic ways such as under-approximation (Section \ref{subsec:under-approx}) and symbolic-aware simplification (Section \ref{subsec:simplify}).
-\subsection{Pre-iamge of String-length}
+\subsection{Handling of String-length}
 Given a string-length constraint, we build a CEFA with a register storing the length of accepted word.
-We call such a CEFA the \emph{pre-image} of it.
-Formally, the pre-image of length constraint is a CEFA $(\{q_I\}, \Sigma, \{q_I\xrightarrow[(1)]{\Sigma} q_I\}, q_I, \{q_I\}, r, \theta)$ where accpeting condition $\theta$ is based on the length value.
-For example, example \ref{eg:pre_len} shows the pre-image of length constraints $i=|x|$, in which $\theta(q_I)$ is $r = i$.
-This automaton contains a simple loop which increase $1$ on register $r$ for all char in $\Sigma$.
-So the accepting words of it is all words with length $i$.
+Namely, the CEFA of length constraint is $(\{q_I\}, \Sigma, \{q_I\xrightarrow[(1)]{\Sigma} q_I\}, q_I, \{q_I\}, r, \theta)$ where accpeting condition $\theta$ is based on the length value.
+For example, example \ref{eg:pre_len} shows the CEFA of length constraints $|x| > 120$, in which the corresponding $\theta(q_I)$ is $r > 120$.
+This CEFA contains a simple loop which increase $1$ on register $r$ for all char in $\Sigma$.
+The value of $r$ (i.e., the length of word) after an accepting run shoud greater than $120$, so the language of the CEFA is the set of all words whose length is greater than 120.
 \newline
 % The formal definition of pre-images of abundant string functions is listed in \cite{atva2020}, and we do not repeat it here.
-\begin{example}[The pre-image of $i = |x|$]\label{eg:pre_len} 
+\begin{example}[The CEFA of $|x| > 120$]\label{eg:pre_len} 
   \begin{figure}[h]
@@
       initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=$\scriptstyle{r=i}$, accepting/.style=accepting by arrow
+      accepting text=$\scriptstyle{r > 120}$, accepting/.style=accepting by arrow
       ]
@@
 \subsection{Combine Regex-counting and String-length}
-In the previous section, we have discussed the construction of regex-counting operator and the pre-image of string-length constraint.
+In the previous section, we have discussed the construction of regex-counting operator and string-length constraint.
 In this section, we show how to combine them to deal with the string constraints with regex-counting and string-length.
@@
 With the help of product, we can combine the CEFAs of regex-counting and string-length.
-For example, the CEFA of string constraints $x\in \regex \wedge i=|x|$ is the product of the CEFA of $x\in \regex$ and the pre-image of $i=|x|$.
+For example, the CEFA of $x$ in the string constraints $x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120$ is the product of the CEFA of regex $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, the CEFA of regex $\Sigma^*$ and the CEFA of length constraints $|x| > 120$.
 
 \subsection{Emptiness Checking Problem on CEFAs} \label{subsec:emptiness}
-As mentioned, the emptiness checking problem of CEFAs under linear integer arithmetic $P$ is theoretically Pspace-complete.
-In our previous research  \cite{atva2020}, we rewrote CEFAs to an infinite system and used a model-checking tool \emph{nuXmv}\cite{nuxmv} to solve it.
-However, it needs to be more effective.
-So we put forward a new framework that brings in under-approximation and symbolic-aware simplification heuristics.\newline
-As shown in Algorithm \ref{alg:emptiness}, we simplify the input CEFAs at line 1 because they may have many transitions and registers.
-The purpose of the simplification is to deal with duplication.
-After simplification, we try to find a solution by under-approximation at line 3 and line 4.
-An off-the-shelf SMT solver gives the result of $\varphi_{under}\wedge P$.
-If we find a solution, we return $false$ at line 5 because it implies that the CEFAs under linear integer arithmetic $P$ are not empty.
-Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $P$ at line 12.
+After encoding counting operator and length constraint to CEFAs, there are only automaton memberships $x\in \aut$ and linear integer arithmetic $t_1 \ \op \ t_2$ where $\aut$ is CEFA and $t_1, t_2$ are integer terms.
+Let $\psi$ denotes the conjunction of all LIA formulas $t_1\ \op\ t_2$ and $\Lambda_x = \{\aut_x^1, \aut_x^2,\cdots \aut_x^n\}$ denotes the set of CEFAs in the automaton membership $x\in \aut$.
+The emptiness checking problem of $\Lambda_x$ under linear integer arithmetic $\psi$ is to check whether there exists a word $w$ such that $w\in \aut_x^1, w\in \aut_x^2\cdots w\in \aut_x^n$ and $\psi[\myvec{V}/\myvec{r}]$ holds, where $\myvec{r}$ are all registers in automata of $\Lambda_x$ and $\myvec{V}$ are corresponding register values after running $w$.
+The emptiness problem is \emph{abbreviated as $SAT_{CEFA}[LIA]$ problem}.
+\newline
+As mentioned in \cite{atva2020}, the \emptinessprob{} is theoretically Pspace-complete.
+We has used a model-checking tool \emph{nuXmv}\cite{nuxmv} to solve it in previous work.
+However, it is not efficient enough for complex string constraints.
+So we put forward a new framework that brings in symbolic-aware simplification and under-approximation heuristics.\newline
+The main idea of our framework is to simplify the input CEFAs firstly and under-approximate the solution of the \emptinessprob{} by adding length bounds on string variables.
+If the under-approximation is satisfiable, the CEFAs is not empty under $\psi$.
+Otherwise, we check the Parikh image of the simplified CEFAs.
+If the Parikh image is satisfiable, the CEFAs under linear integer arithmetic $\psi$ are not empty.
+Or else, they are empty.
+The framework is \emph{sound} and \emph{complete}.\newline
+The framework is shown in Algorithm \ref{alg:emptiness}, we simplify the input CEFAs at line 1 because they may have many transitions and registers.
+The main idea of the simplification is treating alphabet as unary.
+The symbolic updates of the CEFAs are maintained, which are then treated as labels of transitions in the minimization.
+After the simplification, we try to find a solution by under-approximation at line 3 and line 4.
+An off-the-shelf SMT solver gives the result of LIA $\varphi_{under}\wedge \psi$.
+If the LIA is satisfiable, we return $true$ at line 5 because it implies that the CEFAs under the LIA $\psi$ are not empty.
+Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
 The Parikh image checking is complete so that satisfiability implies non-emptiness directly.
 \newline
-The under-approximation program is executed many times until the $MaxBound$ is reached.
+The incremental under-approximation program is executed many times until the $MaxBound$ is reached.
 $MaxBound$ is an empirical bound set to $15$ in our experiment because it brings exponential growth of searching space.
@@
 \begin{algorithm}[h]
-  \caption{ $\algfun{isEmpty}(auts, P)$}
+  \caption{ $\algfun{nonEmpty}(auts, \psi)$}
   \label{alg:emptiness}
   \begin{algorithmic}[1]
-    \Require the CEFAs $auts$ and the linear integer arithmetic $P$
+    \Require the CEFAs $auts$ and the linear integer arithmetic $\psi$
     \Ensure $true$ or $false$
@@
     \State $\varphi_{under}\gets \algfun{underApprox}(simpliAuts, bound)$
-    \If{$\varphi_{under}\wedge P$ is sat}
-    \State \textbf{return} $false$
+    \If{$\varphi_{under}\wedge \psi$ is sat}
+    \State \textbf{return} $true$
     \EndIf
@@
     \State $\varphi \gets \algfun{parikhImage}(simpliAuts)$
-    \If{$\varphi\wedge P$ is unsat}
+    \If{$\varphi\wedge \psi$ is sat}
     \State \textbf{return} $true$
@@
 The purpose of simplification is to remove duplicated transitions and registers.
-In the emptiness checking Algorithm \ref{alg:emptiness}, the vectors on the transitions are meritorious, while the letters are not.
-So we see the alphabet of the CEFA as unary (i.e., the alphabet is $\{a\}$) and see the vectors in the CEFA as letters in the NFA.
-The vector $\myvec{0}_n$ is seen as $\epsilon$.
-Precisely, given an CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$, we obtain a symbolic form  $\aut_{sym} = (Q, \Sigma', \delta', q_I, F, R, \theta)$ where
+In the emptiness checking Algorithm \ref{alg:emptiness}, the non-emptiness is equal to the reachability of CEFAs.
+Thus, the symbolic updates on transitions are meritorious because it influences registers values, while the characters are not.
+The alphabet of the CEFA can be seen as unary (i.e., the alphabet is $\{a\}$) and the vectors as labels.
+The special vector $\myvec{0}_n$ with only zero elements is seen as $\epsilon$ label.
+Namely, given a CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$, we obtain a symbolic form  $\aut_{sym} = (Q, \Sigma', \delta', q_I, F, R, \theta)$ where
 \begin{itemize}
   \item $\Sigma' = \{a\}$,
-  \item the transition set $\delta'$ is composed of transition $q\xrightarrow[\myvec{v}]{a}q'$ if there is a transition $q\xrightarrow[\myvec{v}]{b} q'$ in $\delta$ for $b\in \Sigma$ .
+  \item the transition set $\delta'$ is composed of transition $q\xrightarrow[\myvec{v}]{a}q'$ if there is a transition $q\xrightarrow[\myvec{v}]{b} q'$ in $\delta$ for $b\in \Sigma$.
 \end{itemize}
-We directly apply algorithms of epsilon-closure, determination, and simplification in \cite{aut_hopcraft}.
-We see $q\xrightarrow[\myvec{0}_n]{a}q'$ as epsilon transition and compute the epsilon-closure based on it.
-We see $q\xrightarrow[\myvec{v}]{a}q'$ as a transition with label $(a, \myvec{v})$ and determine the automaton based on the label.
-Two accepting states are equivalent if they have the same accepting conditions, and two states are equivalent if they reach equivalent states for each label.
-We simplify the automaton by merging equivalent states.
-The process above comprises line 3 and line 4 of Algorithm \ref{alg:simplify}.
-From line 5 to line 13, we check whether some registers are duplicated.
-(i.e., the values of these registers are always the same).
-If two registers $r_i$ and $r_j$ are duplicated at line 6, we remove one at line 7 and the corresponding update of vectors at line 9 to ensure the vectors are consistent with the new registers.
-After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register at line 11.
+ For the symbolic form $\aut_{sym}$, we treat $q\xrightarrow[\myvec{0}_n]{a}q'$ as epsilon transition and compute the epsilon-closure based on it.
+Likewise, we treat $q\xrightarrow[\myvec{v}]{a}q'$ as a transition with label $(a, \myvec{v})$ and determine the automaton based on the label.
+Two accepting states are equivalent if they have the same accepting condition, and two states are equivalent if they reach equivalent states for each label.
+We simplify the automaton by merging these equivalent states.
+Briefly, we directly apply algorithms of epsilon-closure, determination, and simplification in \cite{aut_hopcraft}.
+The explanation above discuss funcitons $\algfun{determinizeByVec}$ and $\algfun{minimizeByVec}$ at line 3 and line 4.
+From line 5 to line 13, we check whether two registers $r_i$ and $r_j$ are duplicated.
+(i.e., the symbolic updates of them are always the same).
+If them are duplicated at line 6, we remove one of them at line 7 and the corresponding symbolic update at line 9.
+After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register, to ensure the value of it is consistent at line 11.\newline
+We have the following proposition:
+\begin{proposition}
+  Given a set of CEFAs $\Lambda=\{\aut_1, \cdots, \aut_2\}$ and arbitrary LIA $\psi$, the emptiness of $\Lambda$ on $\psi$ is equal to the emptiness of $\algfun{simplify}(\Lambda)$ on $\psi$.
+\end{proposition}
 \begin{algorithm}[h]
@@
 \begin{example}
-  Considering the CEFA recognizing $(a|b)\{1,100\}$ illustrated in Fig.\ref{subfig:simp_origin_cefa}.
-We first obtain a symbolic CEFA by using unary alphabet (Fig.\ref{subfig:simp_symbolic_cefa}) and then minimize it based on the symbolic label "$a/(1)$"(Fig.\ref{subfig:simp_final}).
+  Considering the CEFA (Fig.\ref{subfig:simp_origin_cefa}) recognizing $(\Sigma\setminus a)\{5,60\}$ where $\Sigma = \{a,b,c\}$.
+We first obtain a symbolic form of it by using unary alphabet (Fig.\ref{subfig:simp_symbolic_cefa}) and then minimize the symbolic form based on the label "$a:(1)$"(Fig.\ref{subfig:simp_final}).
   \begin{figure}[h]
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$1\leq r \leq 100$, accepting/.style=accepting by arrow,
+        accepting text=$\scriptstyle 5\leq r \leq 60$, accepting/.style=accepting by arrow,
         ]
@@
         \node[state, accepting]         (q_2) [below=of q_tmp]       {};
-        \path[->] (q_0) edge   node    [right] {$a/(1)$} (q_1)
-        (q_0) edge   node    [right] {$b/(1)$} (q_2)
-        (q_1) edge[bend right]   node    [left] {$\epsilon/(1)$} (q_0)
-        (q_2) edge[bend left]   node    [left] {$\epsilon/(1)$} (q_0);
+        \path[->] (q_0) edge   node    [right] {$\scriptstyle c:(1)$} (q_1)
+        (q_0) edge   node    [right] {$\scriptstyle b:(1)$} (q_2)
+        (q_1) edge[bend right]   node    [left] {$\scriptstyle \epsilon:(1)$} (q_0)
+        (q_2) edge[bend left]   node    [left] {$\scriptstyle \epsilon:(1)$} (q_0);
       \end{tikzpicture}
-      \caption{The CEFA recognizing $(a|b)\{1,100\}$}
+      \caption{The CEFA recognizing $(\Sigma\setminus a)\{5,60\}$}
       \label{subfig:simp_origin_cefa}
@@
         \node[state, accepting]         (q_2) [below=of q_tmp]       {};
-        \path[->] (q_0) edge   node    [right] {$\myemph{a/(1)}$} (q_1)
-        (q_0) edge   node    [right] {$\myemph{a/(1)}$} (q_2)
-        (q_1) edge[bend right]   node    [left] {$\myemph{a/(1)}$} (q_0)
-        (q_2) edge[bend left]   node    [left] {$\myemph{a/(1)}$} (q_0);
+        \path[->] (q_0) edge   node    [right] {$\scriptstyle \myemph{a:(1)}$} (q_1)
+        (q_0) edge   node    [right] {$\scriptstyle \myemph{a:(1)}$} (q_2)
+        (q_1) edge[bend right]   node    [left] {$\scriptstyle \myemph{a:(1)}$} (q_0)
+        (q_2) edge[bend left]   node    [left] {$\scriptstyle \myemph{a:(1)}$} (q_0);
       \end{tikzpicture}
-      \caption{The symbolic CEFA}
+      \caption{The symbolic form}
       \label{subfig:simp_symbolic_cefa}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{1\textwidth}
       \centering
@@
         \node[state, accepting]         (q_1) [right=of q_0]       {};
-        \path[->] (q_0) edge   node    [above] {$\myemph{a/(1)}$} (q_1)
-        (q_1) edge[loop below] node {$\myemph{a/(1)}$} (q_1);
+        \path[->] (q_0) edge   node    [above] {$\scriptstyle\myemph{a:(1)}$} (q_1)
+        (q_1) edge[loop below] node {$\scriptstyle\myemph{a:(1)}$} (q_1);
       \end{tikzpicture}
@@
 \end{example}
+\denghang{todo}
 \begin{example}
   Considering the string constraints $i=|x|\wedge j=|x|$.
-We compute the pre-images of $i=|x|$, $j=|x|$ and intersect these pre-images to get the final CEFA represented in Fig.\ref{subfig:duplicate}.
-However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their update functions are the same.
-We can simplify the CEFA by removing the duplicated register $r_2$ and corresponding update functions, as shown in Fig.\ref{subfig:remove_duplicate}.
+We compute the CEFAs of $i=|x|$, $j=|x|$ and intersect them to get the final CEFA represented in Fig.\ref{subfig:duplicate}.
+However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their update functions are always same.
+We simplify the CEFA by removing the duplicated register $r_2$ and corresponding symbolic updates, as shown in Fig.\ref{subfig:remove_duplicate}.
 To maintain the value of $r_2$, we add a constraint $r_2=r_1$ to restrict the value of $r_2$ to be the same as $r_1$.
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${i=r_1\wedge j=r_2 }$, accepting/.style=accepting by arrow,
+        accepting text=${\scriptstyle i=r_1\wedge j=r_2 }$, accepting/.style=accepting by arrow,
         ]
@@
 
-        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1,\myemph{1})} ();
+        \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma:(1,\myemph{1})$} ();
       \end{tikzpicture}
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${i=r_1\wedge j=r_2\wedge \myemph{r_1 = r_2} }$, accepting/.style=accepting by arrow,
+        accepting text=${\scriptstyle i=r_1\wedge j=r_2\wedge \myemph{r_1 = r_2} }$, accepting/.style=accepting by arrow,
         ]
@@
 
-        \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
+        \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma$/(1)} ();
       \end{tikzpicture}

### 2023-04-28 2023-1-19/sections/introduction.tex
overview

@@
 \begin{equation}\label{eqn-running}
-x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120.
+x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c^+ \wedge |x| > 120.
 \end{equation}
@@
 $b, c$) does not occur in $x_1$ (resp.
-$x_2, x_3$), moreover, $x$ ends with $c$, and the length of $x$ is greater than $120$.
-It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 120$ and the counting upper bound $60$ in  both $(\Sigma \setminus a)^{\{5, 60\}}$ and $(\Sigma \setminus b)^{\{5, 60\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c$ requires that $x$ has to end with $c$.
+$x_2, x_3$), moreover, $x$ ends with a nonempty sequence of $c$'s, and the length of $x$ is greater than $120$.
+It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 120$ and the counting upper bound $60$ in  both $(\Sigma \setminus a)^{\{5, 60\}}$ and $(\Sigma \setminus b)^{\{5, 60\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c^+$ requires that $x$ has to end with $c$.
 

### 2023-04-28 2023-1-19/sections/overview.tex
overview

@@
 %!TEX root = ../main.tex
+
+In this section, we utilize the string constraint in Equation~(\ref{eqn-running}) to illustrate the approach in this work.
+
+%$x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c^+ \wedge |x| > 120$.
+
+\zhilin{epsilon transition should be avoided}
+
+We first construct an automaton for the regular expression $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
+We introduce three registers, say $r_1, r_2, r_3$, to represent the three counting operators.
+Moreover, we introduce another register, say $r_0$, to denote the length of strings.
+Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.
+%Moreover, $r_0$ is incremented in all the three self-loops. 
+Furthermore, the counting bounds are specified by the accepting condition $5 \le r_1 \le 60 \wedge 5 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$ that is attached to the final state $p_2$.
+Note here we represent the counting operators symbolically by registers, instead of unfolding them explicitly.
+Moreover, we also construct a CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)).
+%where the register $r_0$ is used to record the length of strings.
+
+% the register $r_1$ is incremented in the two transitions from $q_0$ to $q_0$ and $q_1$ respectively,  the register $r_2$ is incremented in the two transitions from $q_1$ to $q_1$ and $q_2$ respectively, and the register $r_3$ is incremented in the transition from $q_2$ to $q_2$ itself.
+Moreover, the register $r_4$ is incremented in each transition.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa.pdf}
+  \caption{CEFA for $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$ and $\Sigma^* c^+$}
+  \label{fig:overview}
+\end{figure}
+
+Next, we remove the $\varepsilon$-transitions of $\aut_1$, resulting into $\aut'_1$, then construct $\aut'_1 \times \aut_2$, that is, the product of $\aut'_1$ and $\aut_2$, as illustrated in Figure~\ref{fig:overview:product}.
+Furthermore, we add one special register, say $r_0$, to record the length of strings.
+Note that $r_0$ is incremented in all transitions.
+In $\aut'_1 \times \aut_2$, the accepting condition $5 \le r_1 \le 60 \wedge 5 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width = 0.5\textwidth]{sections/overview-cefa-product.pdf}
+  \caption{Product of $\aut^\prime_1$ and $\aut_2$, where the length register $r_0$ is added}
+  \label{fig:overview:product}
+\end{figure}
+
+Let $\tau_1, \cdots, \tau_m$ be an enumeration of the transitions of $\aut'_1 \times \aut_2$ and $\myvec{v_1}, \cdots, \myvec{v_m}$ be the vectors of updates on the register values in these transitions.
+For instance, in the transition from $(p_0, q_1)$ to $(p_1, q_1)$, $r_0$ is incremented, and the values of the other registers is unchanged.
+Therefore, the vector for this transition is $(1, 0, 0, 0)$.
+Then the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut'_1 \times \aut_2$. 
+From the result in \cite{}, an LIA formula $\psi(i_1, \cdots, i_m)$ can be computed to express the constraints on the number of occurrences of $\tau_1, \cdots, \tau_m$ in the accepting runs of $\aut'_1 \times \aut_2$, where $i_1, \cdots, i_m$ are the integer variables representing the number of occurrences of $\tau_1, \cdots, \tau_m$ respectively.
+Therefore, the satisfiability of the string constraint in~(\ref{eqn-running}) is reduced to the satisfiability of the following LIA formula
+\[
+\psi(i_1, \cdots, i_m) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [m]}  i_k v_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
+\]
+where for each $k \in [m]$, $v_k = (v_{k,1}, v_{k,2}, v_{k, 3}, v_{k, 4})$ is the vector of updates on the registers $r_0, r_1, r_2, r_3$ in the transition $\tau_k$, and $\alpha(r_0, r_1, r_2, r_3)$ is the accepting condition in $\aut'_1 \times \aut_2$.
+
+\zhilin{stopped here}
+
+\hide{
+\begin{figure}[ht]
+  \centering
+  \import{figures}{overview_example.tex}
+  \caption{The CEFA handling the difficult string constraints}
+  \label{fig:overview:orgin}
+\end{figure}
+}
 
@@
 The state number does not decrease because these three states are not mutually equivalent.
-\newline
+
 Sometimes the string constraints are satisfiable, and the strings in the solution have a short length.

### 2023-04-28 2023-1-19/sections/algorithms.tex

@@
 \newline
-For a handled regular expression $\regex\{m,n\}$, suppose the CEFA recognizing $\regex$ is $\aut = (Q,\Sigma,\delta,q_I,F,\emptyset,\top)$, then the CEFA recognizing $\regex\{m,n\}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_ I, F, r, \theta)$ where:
+\denghang{The encoding of counting need to be corrected}\newline
+For a handled regular expression $\regex\{m,n\}$, suppose the CEFA recognizing $\regex$ is $\aut = (Q,\Sigma,\delta,q_I,F,\emptyset,\top)$, then the CEFA recognizing $\regex\{m,n\}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_I, F\cup\{q_I\}, r, \theta)$ where:
 \begin{itemize}
+  \item $q_I$ is set to accepting state,
   \item $r$ is a new register,
@@
 The accepting condition $\theta'$ constrains the counting times of the accepting word to the range $[m, n]$.
+After the construction, we need to eliminate the transition with epsilon character.
+The elimination is done after adding transition $q\xrightarrow[(1)]{a}$  \newline
 \begin{figure}[h]
@@
       initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=$\top$, accepting/.style=accepting by arrow,
       ]
 
+      \node at (-0.5,0.5) {$\scriptstyle \top$};
       \node[state,initial]            (q_0)                      {};
@@
       initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=\myemph{$\scriptstyle m\leq r\leq n$}, accepting/.style=accepting by arrow,
+      accepting text=
       ]
 
-      \node[state,initial]            (q_0)                      {};
+      \node at (-0.5,0.5) {$\scriptstyle \myemph{m}\leq r\leq \myemph{n}$};
+      \node[state,initial,accepting]            (q_0)                      {};
       \node[state, accepting]         (q_1) [right=of q_0]       {};
@@
   To construct the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ with alphabet $\Sigma = \{a,b,c\}$.
-As shown in Fig.\ref{subfig:rep_aut_ab1_100}, the base cases are the constructions of character $a$ (Fig.\ref{subfig:rep_aut_a}) and $b$ (Fig.\ref{subfig:rep_aut_b}).
-The first inductive step is to concatenate them to one automaton (Fig.\ref{sub@subfig:rep_aut_ab}).
+As shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}, the base cases are the constructions of character $b$ (Fig.\ref{subfig:count_aut_b}) and $c$ (Fig.\ref{subfig:count_aut_c}).
+The first inductive step is construction the union of them (Fig.\ref{sub@subfig:count_aut_sigma_minus_a}).
 The second inductive step is to add counting information on the automaton.
-To do that we add a new register $r_1$ and a transition $q_2\xrightarrow[(1)]{\epsilon} q_0$ to update the repetition times.
-The accepting condition in accepting state is $1\leq r_1\leq 100$ so that the counting time of the accepting word is in the range $[1,100]$.
-After that we get the CEFA recognizing $(ab)\{1,100\}$ shown in Fig.\ref{subfig:rep_aut_ab1_100}.
+To do that we add a new register $r$ to save counting times,  transitions $q_2\xrightarrow[(1)]{\epsilon} q_0$ and $q_1\xrightarrow[(1)]{\epsilon} q_0$  to update the counting times.
+The accepting condition is $5\leq r\leq 60$ ensure the counting time of the accepting word is in the range $[5,60]$.
+After that we get the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}.
   \begin{figure}[h]
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\scriptstyle \top$, accepting/.style=accepting by arrow,
-        accepting where=above
         ]
+        \node at (-0.5, 0.5) {$\scriptstyle \top$};
+        \node[state,initial]            (q_0)                      {$\scriptstyle q_0$};
+        \node[state,accepting]                    (q_1) [right=of q_0]       {$\scriptstyle q_1$};
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state,accepting]                    (q_1) [right=of q_0]       {};
-
-        \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:()$} (q_1);
+        \path[->] (q_0) edge              node      [above]           {$\scriptstyle b:()$} (q_1);
       \end{tikzpicture}
-      \caption{The CEFA recognizing $a$}
-      \label{subfig:rep_aut_a}
+      \caption{The CEFA recognizing $b$}
+      \label{subfig:count_aut_b}
     \end{subfigure}
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\scriptstyle \top$, accepting/.style=accepting by arrow,
-        accepting where=above
         ]
+        \node at (-0.5, 0.5) {$\scriptstyle \top$};
+        \node[state,initial]            (q_0)                      {$\scriptstyle q_0$};
+        \node[state,accepting]                    (q_1) [right=of q_0]       {$\scriptstyle q_2$};
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state,accepting]                    (q_1) [right=of q_0]       {};
-
-        \path[->] (q_0) edge              node      [above]           {$\scriptstyle b:()$} (q_1);
+        \path[->] (q_0) edge              node      [above]           {$\scriptstyle c:()$} (q_1);
       \end{tikzpicture}
-      \caption{The CEFA recognizing $b$}
-      \label{subfig:rep_aut_b}
+      \caption{The CEFA recognizing $c$}
+      \label{subfig:count_aut_c}
     \end{subfigure}
@@
       \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
+        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\scriptstyle\top$, accepting/.style=accepting by arrow,
-        accepting where=above
         ]
+        \node at (-0.5, 0.5) {$\scriptstyle \top$};
+        \node[state,initial]      (q_0)                      {$\scriptstyle q_0$};
+        \node (q_tmp) [right=of q_0]       {};
+        \node[state, accepting]   (q_1) [above=of q_tmp]       {$\scriptstyle q_1$};
+        \node[state, accepting]   (q_2) [below=of q_tmp]       {$\scriptstyle q_2$};
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state, accepting]         (q_2) [right=of q_1]       {};
-
-        \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:()$} (q_1)
-        (q_1) edge              node      [above]           {$\scriptstyle b:()$} (q_2);
+        \path[->] (q_0) edge node [right] {$\scriptstyle b:()$} (q_1)
+        (q_0) edge           node [right] {$\scriptstyle c:()$} (q_2);
       \end{tikzpicture}
-      \caption{The CEFA recognizing $ab$}
-      \label{subfig:rep_aut_ab}
+      \caption{The CEFA recognizing $\Sigma \setminus a$}
+      \label{subfig:count_aut_sigma_minus_a}
     \end{subfigure}
@@
       \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\scriptstyle\myemph{1}\leq r_1\leq\myemph{100}$, accepting/.style=accepting by arrow,
-        accepting where=above
+        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
+        initial text=, every state/.style={minimum size = 0.005cm},
         ]
+        \node at (-1, 1) {$\scriptstyle \myemph{5}\leq r \leq \myemph{60}$};
+        \node[state,initial, accepting]      (q_0)                      {$\scriptstyle q_0$};
+        \node (q_tmp) [right=of q_0]       {};
+        \node[state, accepting]   (q_1) [above=of q_tmp]       {$\scriptstyle q_1$};
+        \node[state, accepting]   (q_2) [below=of q_tmp]       {$\scriptstyle q_2$};
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state]                    (q_1) [right=of q_0]       {};
-        \node[state,accepting]          (q_2) [right=of q_1]       {};
-
-        \path[->] (q_0) edge              node      [above]           {$\scriptstyle a:(\myemph{0})$} (q_1)
-        (q_1) edge              node      [above]           {$\scriptstyle b:(\myemph{0})$} (q_2)
-        (q_2) edge [bend left]  node      [below]           {$\scriptstyle \epsilon:(\myemph{1})$} (q_0);
+        \path[->] (q_0) edge node [right] {$\scriptstyle b:(0)$} (q_1)
+        (q_1) edge [bend right] node [left] {$\scriptstyle \epsilon:(\myemph{1})$} (q_0)
+        (q_0) edge           node [right] {$\scriptstyle c:(0)$} (q_2)
+        (q_2) edge [bend left] node [left] {$\scriptstyle \epsilon:(\myemph{1})$} (q_0);
       \end{tikzpicture}
-      \caption{The CEFA recognizing $(ab)\{\myemph{1},\myemph{100}\}$}
-      \label{subfig:rep_aut_ab1_100}
+      \caption{The CEFA recognizing $(\Sigma\setminus a)\{\myemph{5},\myemph{60}\}$}
+      \label{subfig:count_aut_sigma_minus_a_5_60}
     \end{subfigure}
@@
 
-      \node[state,initial,accepting]            (q_0)       {$q_I$};
+      \node[state,initial,accepting]            (q_0)       {$\scriptstyle q_I$};
 
@@
 \begin{example}
-  Considering the CEFA (Fig.\ref{subfig:simp_origin_cefa}) recognizing $(\Sigma\setminus a)\{5,60\}$ where $\Sigma = \{a,b,c\}$.
+  Considering the CEFA (Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}) recognizing $(\Sigma\setminus a)\{5,60\}$ where $\Sigma = \{a,b,c\}$.
 We first obtain a symbolic form of it by using unary alphabet (Fig.\ref{subfig:simp_symbolic_cefa}) and then minimize the symbolic form based on the label "$a:(1)$"(Fig.\ref{subfig:simp_final}).
   \begin{figure}[h]
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\scriptstyle 5\leq r \leq 60$, accepting/.style=accepting by arrow,
-        ]
-
-        \node[state,initial]            (q_0)                      {};
-        \node         (q_tmp) [right=of q_0]       {};
-        \node[state, accepting]         (q_1) [above=of q_tmp]       {};
-        \node[state, accepting]         (q_2) [below=of q_tmp]       {};
-        \path[->] (q_0) edge   node    [right] {$\scriptstyle c:(1)$} (q_1)
-        (q_0) edge   node    [right] {$\scriptstyle b:(1)$} (q_2)
-        (q_1) edge[bend right]   node    [left] {$\scriptstyle \epsilon:(1)$} (q_0)
-        (q_2) edge[bend left]   node    [left] {$\scriptstyle \epsilon:(1)$} (q_0);
-      \end{tikzpicture}
-      \caption{The CEFA recognizing $(\Sigma\setminus a)\{5,60\}$}
-      \label{subfig:simp_origin_cefa}
-    \end{subfigure}
     \begin{subfigure}[b]{0.49\textwidth}
@@
       \end{tikzpicture}
-      \caption{The symbolic form}
+      \caption{The symbolic form of the CEFA in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}}
       \label{subfig:simp_symbolic_cefa}
     \end{subfigure}
-    \begin{subfigure}[b]{1\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
       \centering
@@
 \end{example}
-\denghang{todo}
 \begin{example}
@@
 We compute the CEFAs of $i=|x|$, $j=|x|$ and intersect them to get the final CEFA represented in Fig.\ref{subfig:duplicate}.
-However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their update functions are always same.
+However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their symbolic updates are always same.
 We simplify the CEFA by removing the duplicated register $r_2$ and corresponding symbolic updates, as shown in Fig.\ref{subfig:remove_duplicate}.
-To maintain the value of $r_2$, we add a constraint $r_2=r_1$ to restrict the value of $r_2$ to be the same as $r_1$.
+To maintain the value of $r_2$, we add a constraint $r_2=r_1$ in the accepting condition.
   \begin{figure}[h]
@@
       \end{tikzpicture}
-      \caption{Remove the duplicated registers and corresponding update functions}
+      \caption{Remove the duplicated registers and corresponding symbolic updates}
       \label{subfig:remove_duplicate}
     \end{subfigure}
-    \caption{Symbolic simplification removes duplicated transitions and states.}
+    \caption{Symbolic simplification removes duplicated registers.}
     \label{fig:duplicate}
@@
 \subsubsection{Under-Approximation} \label{subsec:under-approx}
-An under-approximation procedure solves the satisfiable instances of the emptiness checking problem.
-Inspired by Bounded Model Checking \cite{bmc_1}\cite{bmc_2}\cite{bmc_3}, we explore the states of CEFA in typological order.
+\denghang{revising} \newline
+The purpose of under-approximation is to accelerate the solving process of satisfiable instances.
+With the observation that the accepted string words in practical instances are usual short, we under-approximate the \emptinessprob{} by adding length bounds on string variables.
 We use string length as the bound and probe the CEFA from low to high bound.

### 2023-04-29 2023-1-19/sections/cefa.tex
overview

@@
 %    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
-    \item $\delta \subseteq Q \times \Sigma_\varepsilon \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers, 
+    \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers, 
 %  set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.
@@
 The \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$, where the value of each register is zero. 
-A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{b_1} q_1 \cdots q_{m-1}\xrightarrow[\myvec{v_m}]{b_m} q_m$ such that $w = b_1 \cdots b_m$ (some of $b_i$'s may be $\varepsilon$) and $q_{i-1} \xrightarrow[\myvec{v_i}]{b_i} q_i$ for each $i \in [m]$.
-A run $q_0 \xrightarrow[\myvec{v_1}]{b_1} q_1 \cdots q_{m-1}\xrightarrow[\myvec{v_m}]{b_m} q_m$ is \emph{accepting} if $q_m \in F$ and $\alpha(q_m)[\myvec{\myvec{v'}/\myvec{r}]$ is true, where $\myvec{v'} = \sum \limits_{j \in [m]} \myvec{v_j}}$.
-Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [m]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$.
+A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(q_n)[\myvec{\myvec{v'}/\myvec{r}]$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}}$.
+Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
 A string $w$ is \emph{accepted} by $\aut$ if there is an accepting run of $\aut$ on $w$.
@@
 \begin{example} \label{eg:1}
-  Fig.\ref{fig:repetition} illustrates the CEFA recognizing $(ab)\{1,100\}$.
+  Fig.\ref{fig:counting} illustrates the CEFA recognizing $(ab)\{1,100\}$.
 The register vector is $(r_1)$, and the linear arithmetic constraint on $q_2$ is $1\leq r_1\leq 100$.
@@
     \caption{An automaton recognizing the language of $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$}
-    \label{fig:repetition}
+    \label{fig:counting}
   \end{figure}

### 2023-04-29 2023-1-19/sections/overview.tex
overview

--- 2023-04-25 2023-1-19/sections/overview.tex
@@
 %!TEX root = ../main.tex
+
+In this section, we utilize the string constraint in Equation~(\ref{eqn-running}) to illustrate the approach in this work.
+
+%$x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c^+ \wedge |x| > 120$.
+
+We first construct an automaton for the regular expression $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
+We introduce three registers, say $r_1, r_2, r_3$, to represent the three counting operators.
+%Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
+Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into a so-called cost-enriched finite automaton (CEFA) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
+%Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.
+%Moreover, $r_0$ is incremented in all the three self-loops. 
+Furthermore, the counting bounds are specified by the accepting condition $5 \le r_1 \le 60 \wedge 5 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$ that is attached to the final state $p_2$.
+Note here we represent the counting operators symbolically by registers, instead of unfolding them explicitly.
+Moreover, we also construct a CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators.
+%where the register $r_0$ is used to record the length of strings.
+
+% the register $r_1$ is incremented in the two transitions from $q_0$ to $q_0$ and $q_1$ respectively,  the register $r_2$ is incremented in the two transitions from $q_1$ to $q_1$ and $q_2$ respectively, and the register $r_3$ is incremented in the transition from $q_2$ to $q_2$ itself.
+Moreover, the register $r_4$ is incremented in each transition.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa.pdf}
+  \caption{CEFA for $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$ and $\Sigma^* c^+$}
+  \label{fig:overview}
+\end{figure}
+
+Next, 
+%we remove the $\varepsilon$-transitions of $\aut_1$, resulting into $\aut'_1$, 
+we construct $\aut_1 \times \aut_2$, that is, the product of $\aut_1$ and $\aut_2$, as illustrated in Figure~\ref{fig:overview:product}(a).
+Furthermore, we add one special register, say $r_0$, to record the length of strings.
+Note that $r_0$ is incremented in all transitions.
+In $\aut_1 \times \aut_2$, the accepting condition $5 \le r_1 \le 60 \wedge 5 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
+For technical convenience, we also think the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i-1}$ for each $i \in [4]$.
+For instance, the transitions corresponding to the self-loop around $(p_0, q_0)$ are thought as $(q, a', q', (1,1,0,0))$ with $a' \in \Sigma \setminus \{a\}$, since $r_0$ and $r_1$ are incremented in these transitions.
+With the updates thought as vectors, the resulting CEFA is illustrated in Figure~\ref{fig:overview:product}(b).
+%the transitions corresponding to the self-loop is $(q, a', q', (1,1,0,0))$ with $a' \in \Sigma \setminus \{a\}$.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa-product.pdf}
+  \caption{Product of $\aut_1$ and $\aut_2$, where the length register $r_0$ is added}
+  \label{fig:overview:product}
+\end{figure}
+
+Let $\tau_1, \cdots, \tau_m$ be an enumeration of the transitions of $\aut_1 \times \aut_2$ and $\myvec{v_1}, \cdots, \myvec{v_m}$ be the vectors of updates on the register values in these transitions.
+For instance, in the transition from $(p_0, q_1)$ to $(p_1, q_1)$, $r_0$ is incremented, and the values of the other registers is unchanged.
+Therefore, the vector for this transition is $(1, 0, 0, 0)$.
+Then the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \times \aut_2$. 
+From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi(i_1, \cdots, i_m)$ can be computed to express the constraints on the number of occurrences of $\tau_1, \cdots, \tau_m$ in the accepting runs of $\aut_1 \times \aut_2$, where $i_1, \cdots, i_m$ are the integer variables representing the number of occurrences of $\tau_1, \cdots, \tau_m$ respectively.
+Therefore, the satisfiability of the string constraint in~(\ref{eqn-running}) is reduced to the satisfiability of the following existential LIA formula
+\begin{equation}\label{eqn-LIA}
+\psi(i_1, \cdots, i_m) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [m]}  i_k v_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
+\end{equation}
+where for each $k \in [m]$, $v_k = (v_{k,1}, v_{k,2}, v_{k, 3}, v_{k, 4})$ is the vector of updates on the registers $r_0, r_1, r_2, r_3$ in the transition $\tau_k$, and $\alpha(r_0, r_1, r_2, r_3)$ is the accepting condition in $\aut_1 \times \aut_2$.
+Finally, the satisfiability of LIA formula can be solved by the off-the-shelf SMT solvers for LIA.
+
+Nevertheless, since it is well known that the satisfiability of existential LIA formulas is NP-complete (see e.g.
+\cite{Haase18}), the performance could be improved if the size of the formula in~(\ref{eqn-LIA}) can be reduced.
+Since the size of the formula in~(\ref{eqn-LIA}) depends on the size of $\aut_1 \times \aut_2$, that is, the number of states, transitions, and registers in $\aut_1 \times \aut_2$, we propose the techniques to reduce the size of the CEFA $\aut_1 \times \aut_2$.
+
+Our main idea to reduce the size of the CEFA $\aut_1 \times \aut_2$ is to \emph{ignore the characters in transitions}, since the updates of the values of registers in transitions are independent of the characters therein and the satisfiability of the formula in~(\ref{eqn-LIA}) only concerns about the values of registers.
+After the characters in transitions are ignored, each transition in $\aut_1 \times \aut_2$ is of the form $(q, \myvec{v}, q')$, where $\myvec{v}$ is the vector denoting the updates on the values of registers.
+Let $\cB$ denote the resulting automaton.
+We then think $\cB$ as an NFA, where the vectors $\myvec{v}$ are taken as the characters.
+Then we apply the determinization and minimization algorithm of NFAs to $\cB$, resulting into an automaton $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width = 0.5\textwidth]{sections/overview-cefa-reduced.pdf}
+  \caption{Reduced automaton $\cC$ after ignoring the characters in $\aut_1 \times \aut_2$ and applying determinization and minimization}
+  \label{fig:overview:product:reduced}
+\end{figure}
+
+\zhilin{stopped here}
+
+\hide{
+\begin{figure}[ht]
+  \centering
+  \import{figures}{overview_example.tex}
+  \caption{The CEFA handling the difficult string constraints}
+  \label{fig:overview:orgin}
+\end{figure}
+}
 

### 2023-04-29 2023-1-19/sections/preliminaries.tex
CEFA
overview

@@
 
-\paragraph*{Finite state automata.} 
-A \emph{(nondeterministic) finite state automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, q_0, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $q_0 \in Q$ is the initial state, and $F \subseteq Q$ is the set of final states.
+\paragraph*{Finite automata.} 
+A \emph{(nondeterministic) finite automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, q_0, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $q_0 \in Q$ is the initial state, and $F \subseteq Q$ is the set of final states.
 For readability, we write a transition $(q, a, q') \in \delta$ as $q \xrightarrow[\delta]{a} q'$ (or simply $q \xrightarrow{a} q'$).
@@
 
-We will also use standard  quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulae, which are typically ranged over by $\phi, \varphi$, etc. %, which is essentially Presburger
+We will also use standard  quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulae, which are typically ranged over by $\phi, \varphi$, etc. 
+For a set $X$ of variables, we use $\Phi(X)$ to denote the set of quantifier-free LIA formulas whose free variables are from $X$.
+%, which is essentially Presburger
 

### 2023-04-29 2023-1-19/sections/overview.tex
overview finished

@@
 Then we apply the determinization and minimization algorithm of NFAs to $\cB$, resulting into an automaton $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}.
+Note that $\cC$ contains only three states $q'_0, q'_1, q'_2$ and six transitions $\tau'_1, \cdots, \tau'_6$, thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
+$\{a\}, \{b\}, \{c\}, \Sigma \setminus \{a, b, c\}$, in the transitions of $\aut_1 \times \aut_2$.}.
+Then we reinterpret $\cC$ as a CEFA with the acceptance condition $\alpha(r_0, r_1, r_2, r_3)$. 
+Finally, we compute an LIA formula $\psi'(i_1, \cdots, i_6)$ from $\cC$ and reduce the satisfiability of the string constraint in~(\ref{eqn-running}) to the satisfiability of the following existential LIA formula
+\begin{equation}\label{eqn-LIA-reduced}
+\psi'(i_1, \cdots, i_6) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [6]}  i_k v'_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
+\end{equation}
+where $\myvec{v'_{k}}=(v'_{k,1}, v'_{k,2}, v'_{k,3}, v'_{k,4})$ is the vector of updates of registers of the transition $\tau'_k$ for $k \in [6]$.
 
@@
   \centering
-  \includegraphics[width = 0.5\textwidth]{sections/overview-cefa-reduced.pdf}
-  \caption{Reduced automaton $\cC$ after ignoring the characters in $\aut_1 \times \aut_2$ and applying determinization and minimization}
+  \includegraphics[width = 0.3\textwidth]{sections/overview-cefa-reduced.pdf}
+  \caption{Reduced automaton $\cC$}
   \label{fig:overview:product:reduced}
 \end{figure}
+Furthermore, we can reduce the number of registers by merging several registers into one, if they are updated with the same value in every transition of $\aut_1 \times \aut_2$.
 
-\zhilin{stopped here}
+At last, for the string constraints that are satisfied by a collection of strings whose lengths are small, computing LIA formulas from CEFA and solving them by SMT solvers are still expensive.  
+Therefore, we introduce a heuristic of searching for solutions based on \emph{under approximations}, before computing LIA formulas and solving them by SMT solvers.
+More precisely, we enforce a constant upper bound $B$ on the lengths of strings and search for a $B$-bounded satisfiable assignment, that is, a satisfiable assignment where the lengths of strings are bound by $B$.
+Initially we set $B$ to $1$.
+If there does not exist a $B$-bounded satisfiable assignment, then we let $B:=B+1$ and continue the search, until finding a satisfiable assignment or reaching a given time limit.
+For instance, if we remove $|x| > 120$ from the string constraint~(\ref{eqn-running}), then the resulting constraint is satisfiable.
+Setting the bound $B$ to $1$ is already sufficient to find a solution for $\aut_1 \times \aut_2$ (with $r_0 > 120$ ignored).
 
+%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
 \hide{
@@
 \end{figure}
-}
 
@@
 \end{figure}
+}
+%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
 

### 2023-04-29 2023-1-19/sections/cefa.tex
cefa

@@
 
+%Finally, we define the product of two CEFA. 
+Let $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1, \alpha_1)$ and  $\aut_2 = (R_2, Q_2, \Sigma, \delta_2, q_{2,0}, F_2, \alpha_2)$ be two CEFA that share the alphabet.
+Moreover, suppose $R_1 \cap R_2 = \emptyset$.
+We define the \emph{product} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \times \aut_2 = (R', Q', \Sigma, \delta', q'_0, F', \alpha')$, as follows.
+\begin{itemize}
+\item $R' = R_1 \cup R_2$, $Q' = Q_1 \times Q_2$, $q'_0 = (q_{1,0}, q_{2,0})$, $F' = F_1 \times F_2$,
+%
+\item $\alpha'((q_1, q_2)) = \alpha_1(q_1) \wedge \alpha_2(q_2)$ for each $(q_1, q_2) \in F'$, 
+%
+\item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), \myvec{v})$ such that $(q_1,a, q'_1, \prj_{R_1}(\myvec{v})) \in \delta_1$ and $(q_2,a, q'_2, \prj_{R_2}(\myvec{v})) \in \delta_2$, where $\myvec{v} \in \Int^{R'}$, $\prj_{R_1}(\myvec{v}))$ (resp.
+$\prj_{R_2}(\myvec{v}))$) is the restriction of $\myvec{v}$ to the domain $R_1$ (resp.
+$R_2$).
+\end{itemize}
+Intuitively, $\aut_1 \times \aut_2$ defines the intersection of $\Lang(\aut_1)$ and $\Lang(\aut_2)$.
+
 %The value of each register $r_i$ in $R$ is written as $\mathcal{V}(r_i)$ and is initiated to 0 at the initial state.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
 \zhilin{this example should be modified to match the running example}
@@
 \end{example}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-04-30 2023-1-19/sections/algorithms.tex
algorithm

@@
 
-As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers in automata, instead of unfolding them explicitly.
-Additionally, we represent string lengths using registers.
-This reduces the satisfiability of string constraints that involve regex-counting and string-length to the satisfiability of linear integer arithmetic, which can be solved by off-the-shelf SMT solvers.
+As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers, instead of unfolding them explicitly.
+Additionally, we use registers to represent string lengths.
+After that, the satisfiability of string constraints involve regex-counting and string-length is reduced to the satisfiability of LIA, which can be solved by off-the-shelf SMT solvers.
 We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
-\subsection{Encode Regex-Counting to CEFA} \label{subsec:regex2cefa}
-One key point of our approach is the encoding of counting operator.
-In this section, we define the construction of CEFA from the regular expression with counting.
-We divide the counting operator into \emph{handled} and \emph{non-handled}.
-The counting operator is called \emph{non-handled} if it is the sub-regex of other complement operator (e.g., $(\regex^{\{m,n\}})^C$), closure operator(e.g., $(\regex^{\{m,n\}})^*$), or counting operator (e.g., $(\regex^{\{m,n\}})^{\{m', n'\}}$), otherwise it is called \emph{handled}.
-A regex is called \emph{non-handled} if it contains any non-handled counting operators, and is called \emph{handled} otherwise.
+\subsection{Encode Regex with Counting to CEFA} \label{subsec:regex2cefa}
+The most important point of our approach is encoding counting operators by registers rather than explicitly unfolding them.
+In this section, we discuss the encoding in detail.
+A counting operator is called \emph{handled} if it is not the sub-regex of complement, closure or other counting, and called \emph{unhandled} otherwise.
+For example, $(\Sigma \setminus a)^{\{m,n\}}$ is handled, while $((\Sigma \setminus a)^{\{m,n\}})^*$ is unhandled.
+We first discuss the encoding of handled counting operators, and then discuss the encoding of unhandled counting operators.\newline
 % We must syntactically rewrite bounded repetition $\regex\{m,n\}$ if it is the sub-regex of complement (e.g., $(\regex\{m,n\})^C$), closure(e.g., $(\regex\{m,n\})^*$), and bounded repetition(e.g., $(\regex\{m,n\})\{m', n'\}$), we unwind it to $\regex^m\mid\cdots\mid\regex^n$.
 After this syntactic rewriting, we call the resulting regex $\regex'$ \emph{non-nested}.
-Given a handled regex $\regex$, operations such as intersection, union, concatenation, complement, closure, and counting may appear.
-To construct the CEFA of $\regex$, we first create CEFA for each sub-regex and then combine them.
-Similar to the construction of NFA from regex\cite{aut_hopcraft}, our construction is inductive on the size of $\regex$.
-The base case is the construction for a single character, an empty string, or an empty language.
-The inductive step is the construction for the concatenation, union, intersection of two automata of sub-regexes, counting, closure, and complement of one automaton of sub-regex.
-We only discuss the inductive step for counting because it is the most important and the other operations are trivial.
-\newline
-\denghang{The encoding of counting need to be corrected}\newline
-For a handled regular expression $\regex\{m,n\}$, suppose the CEFA recognizing $\regex$ is $\aut = (Q,\Sigma,\delta,q_I,F,\emptyset,\top)$, then the CEFA recognizing $\regex\{m,n\}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_I, F\cup\{q_I\}, r, \theta)$ where:
+Given a regex $\regex$ without unhandled counting operator, the base case is constructing CEFA of a single character, an empty string, or an empty language.
+The inductive step is constructing CEFA of the concatenation, union, intersection, closure, complement and counting of CEFA(s) of sub-regex(es).
+Operations except for counting are trivial and represented in Appendix , we only illustrate counting here.\newline
+Given a regex $\regex^{\{m,n\}}$ without unhandled counting operator, suppose the NFA recognizing $\regex$ is $\aut = (Q,\Sigma,\delta,q_I,F)$, then the CEFA recognizing $\regex^{\{m,n\}}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_I, F\cup\{q_I\}, r, \theta)$ where:
 \begin{itemize}
@@
   \item $\delta'$ is composed by transition $q\xrightarrow[(0)]{a} q'$ for each transition $q\xrightarrow[()]{a} q' \in \delta$, and transition $q_f\xrightarrow[(1)]{\epsilon} q_I$ for each accepting state $q_f\in F$,
-  \item $\theta$ is the function mapping each accepting state to a same linear integer arithmetic $m\leq r\leq n$.
+  \item $\theta$ is the function mapping each accepting state to a same linear integer arithmetic $(m\leq )r\leq n$. The lower bound $m\leq r$ is unnecessary if $q_I\in F$.
 \end{itemize}
-The construction is illustrated in Fig.\ref{fig:construct_repetition}, where a new register $r$ is added to store the counting times.
-The transition $q\xrightarrow[(1)]{\epsilon} q_I$ is used to update the counting times for each $q\in F$.
-The accepting condition $\theta'$ constrains the counting times of the accepting word to the range $[m, n]$.
-After the construction, we need to eliminate the transition with epsilon character.
-The elimination is done after adding transition $q\xrightarrow[(1)]{a}$  \newline
+The main idea is to add an epsilon transition to initial state from each accepting state like closure, to repeat the sub-regex.
+Then the counting time is incremented by 1 when the epsilon transition is invoked.
+Details are illustrated in Fig.\ref{fig:construct_repetition}.
+A new register $r$ is added to store the counting times.
+The transition $q\xrightarrow[(1)]{\epsilon} q_I$ it constructed to increment the counting times.
+The accepting condition $(m\leq) r\leq n$ is attached to each accepting state to constrain the counting times of the accepting word.
+After the construction, we need to eliminate epsilon transitions.
+It is done by adding transition $q_f\xrightarrow[(1)]{a} q$ for transition $q_I\xrightarrow[(0)]{a} q$ and then deleting the transition $q_f\xrightarrow[(1)]{\epsilon} q_I$, for each accepting state $q_f$.\newline
 \begin{figure}[h]
@@
 
-      \node at (-0.5,0.5) {$\scriptstyle \top$};
       \node[state,initial]            (q_0)                      {};
@@
     \end{tikzpicture}
-    \caption{The CEFA recognizing $\regex$}
+    \caption{The NFA recognizing $\regex$}
   \end{subfigure}
@@
 
-      \node at (-0.5,0.5) {$\scriptstyle \myemph{m}\leq r\leq \myemph{n}$};
+      \node at (-0.5,0.5) {$\scriptstyle (\myemph{m}\leq) r\leq \myemph{n}$};
       \node[state,initial,accepting]            (q_0)                      {};
@@
 To do that we add a new register $r$ to save counting times,  transitions $q_2\xrightarrow[(1)]{\epsilon} q_0$ and $q_1\xrightarrow[(1)]{\epsilon} q_0$  to update the counting times.
-The accepting condition is $5\leq r\leq 60$ ensure the counting time of the accepting word is in the range $[5,60]$.
-After that we get the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}.
+The accepting condition of each accepting state is $5\leq r\leq 60$, which ensure the counting time of the accepting word is in the range $[5,60]$.
+After epsilon elimination we get the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ (shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}).
   \begin{figure}[h]
@@
         ]
-        \node at (-0.5, 0.5) {$\scriptstyle \top$};
         \node[state,initial]            (q_0)                      {$\scriptstyle q_0$};
@@
       \end{tikzpicture}
-      \caption{The CEFA recognizing $b$}
+      \caption{The NFA recognizing $b$}
       \label{subfig:count_aut_b}
@@
       \end{tikzpicture}
-      \caption{The CEFA recognizing $c$}
+      \caption{The NFA recognizing $c$}
       \label{subfig:count_aut_c}
@@
         ]
-        \node at (-0.5, 0.5) {$\scriptstyle \top$};
         \node[state,initial]      (q_0)                      {$\scriptstyle q_0$};
@@
       \end{tikzpicture}
-      \caption{The CEFA recognizing $\Sigma \setminus a$}
+      \caption{The NFA recognizing $\Sigma \setminus a$}
       \label{subfig:count_aut_sigma_minus_a}
@@
         \path[->] (q_0) edge node [right] {$\scriptstyle b:(0)$} (q_1)
-        (q_1) edge [bend right] node [left] {$\scriptstyle \epsilon:(\myemph{1})$} (q_0)
+        (q_1) edge [loop right] node {$\scriptstyle b:(\myemph{1})$} (q_1)
         (q_0) edge           node [right] {$\scriptstyle c:(0)$} (q_2)
-        (q_2) edge [bend left] node [left] {$\scriptstyle \epsilon:(\myemph{1})$} (q_0);
+        (q_2) edge [loop right] node {$\scriptstyle c:(\myemph{1})$} (q_0);
       \end{tikzpicture}
@@
 \end{example}
-Above discusses the construction of counting operator in a handled regex.
-The counting operator of unhandled regex can not be constructed by the same way.
-For example, for an unhandled regex $(ab^{\{1,100\}})*$, there are infinite repetitions of regex $ab^{\{1,100\}}$.
-The counting times of each repetition are irrelevant, so that we can not represent them use finite registers.
-So we syntactically rewrite the unhandled counting operator into union operator and concatenation operator.
+Above discusses the construction of handled counting operators.
+The unhandled counting operator can not be constructed by the same way.
+For example, for the regex $(ab^{\{1,100\}})*$ with unhandled counting operator, there are infinite repetitions of $ab^{\{1,100\}}$.
+The counting times of each repetition are irrelevant, so that we can not represent them using finite registers.
+We have to syntactically rewrite the unhandled counting operator into union operator and concatenation operator.
 More exactly, the sub-regex $\regex^{\{m,n\}}$ in the unhandled regex is rewritten into $\underbrace{\regex\cdot\regex\cdots\regex}_{m \text{ times}}\mid\cdots\mid \underbrace{\regex\cdot\regex\cdots\regex}_{n \text{ times}}$.
@@
 \subsection{Handling of String-length}
-Given a string-length constraint, we build a CEFA with a register storing the length of accepted word.
-Namely, the CEFA of length constraint is $(\{q_I\}, \Sigma, \{q_I\xrightarrow[(1)]{\Sigma} q_I\}, q_I, \{q_I\}, r, \theta)$ where accpeting condition $\theta$ is based on the length value.
-For example, example \ref{eg:pre_len} shows the CEFA of length constraints $|x| > 120$, in which the corresponding $\theta(q_I)$ is $r > 120$.
-This CEFA contains a simple loop which increase $1$ on register $r$ for all char in $\Sigma$.
-The value of $r$ (i.e., the length of word) after an accepting run shoud greater than $120$, so the language of the CEFA is the set of all words whose length is greater than 120.
-\newline
+Given a string-length constraint, we build a CEFA with a register storing the word length.
+Namely, the CEFA is $(\{q_I\}, \Sigma, \{q_I\xrightarrow[(1)]{\Sigma} q_I\}, q_I, \{q_I\}, r, \theta)$ where accpeting condition $\theta$ is based on the length formula.
+As an illustration, example \ref{eg:pre_len} shows the CEFA of length constraints $|x| > 120$, whose language is the set of all words with length greater than $120$.
+The simple loop $q_I\xrightarrow[(1)]{\Sigma} q_I$ increase $1$ on register $r$ for all char in $\Sigma$, so that the value of $r$ is equal to the length of word.
+The accepting condition $\theta$ attachs $q_I$ to $r > 120$, ensuring the length of accepting word is greater than $120$.\newline
 % The formal definition of pre-images of abundant string functions is listed in \cite{atva2020}, and we do not repeat it here.
@@
       initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=$\scriptstyle{r > 120}$, accepting/.style=accepting by arrow
       ]
 
+      \node at (-0.5, 0.5) {$\scriptstyle r > 120$};
       \node[state,initial,accepting]            (q_0)       {$\scriptstyle q_I$};
@@
 \end{example} 
-\subsection{Combine Regex-counting and String-length}
-In the previous section, we have discussed the construction of regex-counting operator and string-length constraint.
+% \subsection{Combine Regex-counting and String-length}
+% In the previous section, we have discussed the construction of regex-counting operator and string-length constraint.
 In this section, we show how to combine them to deal with the string constraints with regex-counting and string-length.
-\begin{definition} [The Product of Two CEFA]\newline
-  Given two CEFAs $\aut_1 = (Q_1, \Sigma, \delta_1, q_{I_1}, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2, q_{I_2}, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the product of them, denoted by $\aut_1 \times \aut_2$, is defined as $(Q_1\times Q_2, \Sigma, \delta, (q_{I_1}, q_{I_2}), F_1\times F_2, R_1\cup R_2, \theta)$ where
-  \begin{itemize}
-    \item $\delta$ comprises the tuples $((q_1, q_2), a, (q_1', q_2'), \myvec{v_1}\cdot \myvec{v_2})$ such that $(q_1, a, q_1', \myvec{v_1})\in \delta_1$ and $(q_2, a, q_2', \myvec{v_2})\in \delta_2$.
-    \item $\theta((q_1, q_2))$ is $\theta_1(q_1)\wedge \theta_2(q_2)$ for each accepting state $(q_1, q_2)\in F_1\times F_2$.
-  \end{itemize}
-\end{definition}
-With the help of product, we can combine the CEFAs of regex-counting and string-length.
+% \begin{definition} [The Product of Two CEFA]\newline
+%   Given two CEFAs $\aut_1 = (Q_1, \Sigma, \delta_1, q_{I_1}, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2, q_{I_2}, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the product of them, denoted by $\aut_1 \times \aut_2$, is defined as $(Q_1\times Q_2, \Sigma, \delta, (q_{I_1}, q_{I_2}), F_1\times F_2, R_1\cup R_2, \theta)$ where
+%   \begin{itemize}
+%     \item $\delta$ comprises the tuples $((q_1, q_2), a, (q_1', q_2'), \myvec{v_1}\cdot \myvec{v_2})$ such that $(q_1, a, q_1', \myvec{v_1})\in \delta_1$ and $(q_2, a, q_2', \myvec{v_2})\in \delta_2$.
+%     \item $\theta((q_1, q_2))$ is $\theta_1(q_1)\wedge \theta_2(q_2)$ for each accepting state $(q_1, q_2)\in F_1\times F_2$.
+%   \end{itemize}
+% \end{definition}
+% With the help of product, we can combine the CEFAs of regex-counting and string-length.
 For example, the CEFA of $x$ in the string constraints $x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120$ is the product of the CEFA of regex $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, the CEFA of regex $\Sigma^*$ and the CEFA of length constraints $|x| > 120$.
@@
 Let $\psi$ denotes the conjunction of all LIA formulas $t_1\ \op\ t_2$ and $\Lambda_x = \{\aut_x^1, \aut_x^2,\cdots \aut_x^n\}$ denotes the set of CEFAs in the automaton membership $x\in \aut$.
-The emptiness checking problem of $\Lambda_x$ under linear integer arithmetic $\psi$ is to check whether there exists a word $w$ such that $w\in \aut_x^1, w\in \aut_x^2\cdots w\in \aut_x^n$ and $\psi[\myvec{V}/\myvec{r}]$ holds, where $\myvec{r}$ are all registers in automata of $\Lambda_x$ and $\myvec{V}$ are corresponding register values after running $w$.
+The emptiness checking problem of $\Lambda_x$ under linear integer arithmetic $\psi$ is to check whether there exists a word $w$ such that $w\in \aut_x^1, w\in \aut_x^2\cdots w\in \aut_x^n$ and $\psi[\myvec{V}/\myvec{r}]$ holds, where $\myvec{r}$ are all registers and $\myvec{V}$ are corresponding register values in automata of $\Lambda_x$ after running $w$.
 The emptiness problem is \emph{abbreviated as $SAT_{CEFA}[LIA]$ problem}.
@@
   Considering the CEFA (Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}) recognizing $(\Sigma\setminus a)\{5,60\}$ where $\Sigma = \{a,b,c\}$.
-We first obtain a symbolic form of it by using unary alphabet (Fig.\ref{subfig:simp_symbolic_cefa}) and then minimize the symbolic form based on the label "$a:(1)$"(Fig.\ref{subfig:simp_final}).
+We first obtain a symbolic form of it by using unary alphabet (Fig.\ref{subfig:sigma_minus_a_5_60:simplify}) and then minimize the symbolic form based on the label $"a:(1)"$(Fig.\ref{subfig:simp_final}).
   \begin{figure}[h]
@@
         shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\scriptstyle 5\leq r \leq 60$, accepting/.style=accepting by arrow,
+        initial text=, every state/.style={minimum size = 0.005cm},
         ]
+        \node at (-1, 1) {$\scriptstyle 5\leq r \leq 60$};
+        \node[state,initial, accepting]      (q_0)                      {$\scriptstyle q_0$};
+        \node (q_tmp) [right=of q_0]       {};
+        \node[state, accepting]   (q_1) [above=of q_tmp]       {$\scriptstyle q_1$};
+        \node[state, accepting]   (q_2) [below=of q_tmp]       {$\scriptstyle q_2$};
 
-        \node[state,initial]            (q_0)                      {};
-        \node         (q_tmp) [right=of q_0]       {};
-        \node[state, accepting]         (q_1) [above=of q_tmp]       {};
-        \node[state, accepting]         (q_2) [below=of q_tmp]       {};
-        \path[->] (q_0) edge   node    [right] {$\scriptstyle \myemph{a:(1)}$} (q_1)
-        (q_0) edge   node    [right] {$\scriptstyle \myemph{a:(1)}$} (q_2)
-        (q_1) edge[bend right]   node    [left] {$\scriptstyle \myemph{a:(1)}$} (q_0)
-        (q_2) edge[bend left]   node    [left] {$\scriptstyle \myemph{a:(1)}$} (q_0);
+        \path[->] (q_0) edge node [right] {$\scriptstyle a:(0)$} (q_1)
+        (q_1) edge [loop right] node {$\scriptstyle a:(1)$} (q_1)
+        (q_0) edge           node [right] {$\scriptstyle a:(0)$} (q_2)
+        (q_2) edge [loop right] node {$\scriptstyle a:(1)$} (q_0);
       \end{tikzpicture}
-      \caption{The symbolic form of the CEFA in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}}
-      \label{subfig:simp_symbolic_cefa}
+      \caption{The symbolic form of $\aut_{\Sigma\setminus a\{5,60\}}$}
+      \label{subfig:sigma_minus_a_5_60:simplify}
     \end{subfigure}
@@
         initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=$\scriptstyle 5\leq r \leq 60$, accepting/.style=accepting by arrow,
         ]
 
-        \node[state,initial]            (q_0)                      {};
-        \node[state, accepting]         (q_1) [right=of q_0]       {};
-        \path[->] (q_0) edge   node    [above] {$\scriptstyle\myemph{a:(1)}$} (q_1)
-        (q_1) edge[loop below] node {$\scriptstyle\myemph{a:(1)}$} (q_1);
+        \node at (-0.5, 0.5) {$\scriptstyle 5\leq r \leq 60$};
+        \node[state,initial,accepting]            (q_0)       {$\scriptstyle q_I$};
+
+        \path[->] (q_0) edge [loop below] node{$\scriptstyle a:(1)$} ();
       \end{tikzpicture}

### 2023-05-01 2023-1-19/sections/algorithms.tex
algorithm

@@
 \subsection{Emptiness Checking Problem on CEFAs} \label{subsec:emptiness}
-After encoding counting operator and length constraint to CEFAs, there are only automaton memberships $x\in \aut$ and linear integer arithmetic $t_1 \ \op \ t_2$ where $\aut$ is CEFA and $t_1, t_2$ are integer terms.
-Let $\psi$ denotes the conjunction of all LIA formulas $t_1\ \op\ t_2$ and $\Lambda_x = \{\aut_x^1, \aut_x^2,\cdots \aut_x^n\}$ denotes the set of CEFAs in the automaton membership $x\in \aut$.
-The emptiness checking problem of $\Lambda_x$ under linear integer arithmetic $\psi$ is to check whether there exists a word $w$ such that $w\in \aut_x^1, w\in \aut_x^2\cdots w\in \aut_x^n$ and $\psi[\myvec{V}/\myvec{r}]$ holds, where $\myvec{r}$ are all registers and $\myvec{V}$ are corresponding register values in automata of $\Lambda_x$ after running $w$.
+After encoding counting operator and length constraint to CEFAs, there are only automaton memberships $x\in \aut$ and LIA formula $t_1 \ \op \ t_2$ where $\aut$ is CEFA and $t_1, t_2$ are integer terms.
+Let $\psi$ denotes the conjunction of all LIA formulae $t_1\ \op\ t_2$ and $\Lambda_x = \{\aut_x^1, \aut_x^2,\cdots \aut_x^n\}$ denotes the set of CEFAs in the automaton membership $x\in \aut$.
+The emptiness checking problem of $\Lambda_x$ under $\psi$ is the problem that checks whether there exists a word $w$ such that $w\in \aut_x^1, w\in \aut_x^2\cdots w\in \aut_x^n$ and $\psi[\myvec{V}/\myvec{r}]$ holds, where $\myvec{r}$ are all registers and $\myvec{V}$ are corresponding register values in automata of $\Lambda_x$ after running $w$.
 The emptiness problem is \emph{abbreviated as $SAT_{CEFA}[LIA]$ problem}.
@@
 The main idea of our framework is to simplify the input CEFAs firstly and under-approximate the solution of the \emptinessprob{} by adding length bounds on string variables.
-If the under-approximation is satisfiable, the CEFAs is not empty under $\psi$.
+If the under-approximation is satisfiable, the CEFAs are not empty under $\psi$.
 Otherwise, we check the Parikh image of the simplified CEFAs.
-If the Parikh image is satisfiable, the CEFAs under linear integer arithmetic $\psi$ are not empty.
+If the Parikh image is satisfiable, the CEFAs are not empty under $\psi$.
 Or else, they are empty.
 The framework is \emph{sound} and \emph{complete}.\newline
-The framework is shown in Algorithm \ref{alg:emptiness}, we simplify the input CEFAs at line 1 because they may have many transitions and registers.
-The main idea of the simplification is treating alphabet as unary.
-The symbolic updates of the CEFAs are maintained, which are then treated as labels of transitions in the minimization.
+The framework is shown in Algorithm \ref{alg:emptiness}, we simplify the input CEFAs at line 1 because they may have too many transitions and registers to solve.
+The main idea of the simplification is treating the alphabet as unary and the symbolic updates as characters of transitions in the minimization.
 After the simplification, we try to find a solution by under-approximation at line 3 and line 4.
 An off-the-shelf SMT solver gives the result of LIA $\varphi_{under}\wedge \psi$.
-If the LIA is satisfiable, we return $true$ at line 5 because it implies that the CEFAs under the LIA $\psi$ are not empty.
+If the LIA is satisfiable, we return $true$ at line 5 because the CEFAs under the LIA $\psi$ are not empty.
 Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
@@
 $MaxBound$ is an empirical bound set to $15$ in our experiment because it brings exponential growth of searching space.
-The details of simplification are shown in Algorithm \ref{alg:simplify} and under-approximation are shown in Algorithm \ref{alg:underApprox}.\newline
+The details of simplification and under-approximation are shown in Algorithm \ref{alg:simplify} and the details of  are shown in Algorithm \ref{alg:underApprox}.\newline
 \begin{algorithm}[h]
@@
 Thus, the symbolic updates on transitions are meritorious because it influences registers values, while the characters are not.
-The alphabet of the CEFA can be seen as unary (i.e., the alphabet is $\{a\}$) and the vectors as labels.
-The special vector $\myvec{0}_n$ with only zero elements is seen as $\epsilon$ label.
+The alphabet of the CEFA can be seen as unary (i.e., the alphabet is $\{a\}$) and the vectors as characters.
+The special vector $\myvec{0}_n$ with only zero elements is seen as $\epsilon$ character.
 Namely, given a CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$, we obtain a symbolic form  $\aut_{sym} = (Q, \Sigma', \delta', q_I, F, R, \theta)$ where
@@
  For the symbolic form $\aut_{sym}$, we treat $q\xrightarrow[\myvec{0}_n]{a}q'$ as epsilon transition and compute the epsilon-closure based on it.
-Likewise, we treat $q\xrightarrow[\myvec{v}]{a}q'$ as a transition with label $(a, \myvec{v})$ and determine the automaton based on the label.
-Two accepting states are equivalent if they have the same accepting condition, and two states are equivalent if they reach equivalent states for each label.
+Likewise, we treat $q\xrightarrow[\myvec{v}]{a}q'$ as a transition with character $(a, \myvec{v})$ and determine the automaton based on it.
+Two accepting states are equivalent if they have the same accepting condition, and two states are equivalent if they reach equivalent states for each character.
 We simplify the automaton by merging these equivalent states.

### 2023-05-02 2023-1-19/sections/algorithms.tex
algorithm

@@
 The main idea of the simplification is treating the alphabet as unary and the symbolic updates as characters of transitions in the minimization.
-After the simplification, we try to find a solution by under-approximation at line 3 and line 4.
-An off-the-shelf SMT solver gives the result of LIA $\varphi_{under}\wedge \psi$.
-If the LIA is satisfiable, we return $true$ at line 5 because the CEFAs under the LIA $\psi$ are not empty.
-Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
+After the simplification, we try to find a solution by under-approximation at line 2 and line 3.
+The under-approximation algorithm explore satisfiable register values from low string-length to high string-length.
+If it finds a solution \denghang{todo} Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
 The Parikh image checking is complete so that satisfiability implies non-emptiness directly.
@@
     \State $simpliAuts \leftarrow \algfun{simplify}(auts)$
-    \For{$bound \gets 1, MaxBound$ }
-    \State $\varphi_{under}\gets \algfun{underApprox}(simpliAuts, bound)$
-    \If{$\varphi_{under}\wedge \psi$ is sat}
+    % \For{$bound \gets 1, MaxBound$ }
+    % \State $\varphi_{under}\gets \algfun{underApprox}(simpliAuts, bound)$
+    % \If{$\varphi_{under}\wedge \psi$ is sat}
+    % \State \textbf{return} $true$
+    % \EndIf
+    % \EndFor
+    \If{\algfun{underApproxSolve}($simpliAuts, \psi, MaxBound$) is true}
     \State \textbf{return} $true$
     \EndIf
-    \EndFor
     \State $\varphi \gets \algfun{parikhImage}(simpliAuts)$
@@
     \If {$\myvec{v}[i] = \myvec{v}[j]$ for every vector $\myvec{v}\in \aut$ }
-    \State $R=(\cdots r_{j-1}r_{j+1}\cdots)$ \Comment remove $r_j$ from the register vector $R$
+    \State $R\gets(\cdots r_{j-1}r_{j+1}\cdots)$ \Comment remove $r_j$ from the register vector $R$
     \ForAll{$\myvec{v'}\in \aut$}
-    \State $\myvec{v'}=(\cdots\myvec{v'}[j-1]\myvec{v'}[j+1]\cdots)$ \Comment remove $\myvec{v'}[j]$ from each vector $\myvec{v'}$
+    \State $\myvec{v'}\gets(\cdots\myvec{v'}[j-1]\myvec{v'}[j+1]\cdots)$ \Comment remove $\myvec{v'}[j]$ from each vector $\myvec{v'}$
     \EndFor
-    \State $\theta = \theta\wedge r_i = r_j$
+    \State $\theta \gets\theta\wedge r_i = r_j$
     \EndIf
@@
 \begin{algorithm}[h]
-  \caption{$\algfun{underApprox}(auts, bound)$}
+  \caption{$\algfun{underApproxSolve}(auts, bound, \psi)$}
   \label{alg:underApprox}
   \begin{algorithmic}[1]
-    \Require The CEFAs $auts$ and string length $bound$
-    \Ensure The linear integer arithmetic $\varphi_{under}$ representing under-approximation of the register values of $auts$
+    \Require The CEFAs $auts$, max string length $bound$, other LIA formula $\psi$
+    % \Ensure The linear integer arithmetic $\varphi_{under}$ representing under-approximation of the register values of $auts$
+    \Ensure \emph{true} if finding a solution, \emph{false} otherwise
     \Statex
-    \State $\varphi_{under} \gets false$
+    \State $\varphi_{under}$ is an incremental LIA formula as under approximation, initialized to $\psi$
+    \State $\varphi_\aut$ is an incremental LIA formula for each automaton $\aut$, initialized to $false$
+    \State $\theta$ is the conjunction of all accepting conditions of $auts$
+    \State $lastStates(\aut)$ is the set of (last state, vector's sum) pairs of $\aut$, initialized to $\{(q_I, 0_n)\}$ 
+    \While {$bound \geq 0$}
       \For{$\aut \in auts$}
-    \State Suppose $\aut = (Q, \Sigma, \delta, q_I, F, (r_1, \cdots, r_m), \theta)$
-    \ForAll{run $q_0q_1\cdots q_{n}$ whose length is less than $bound$}
-    \If{$q_{n}\in F$}
-    \State Let $\myvec{V}\leftarrow$ the sum of the vectors on the run
-    \State $\varphi_{under} \gets \varphi_{under} \vee(\theta(q_n)\bigwedge\limits_{i\in[1,m]} r_i = \myvec{V}[i])$
+        \For{$(q, \myvec{V}) \gets lastStates(\aut)$}
+          \If{$q\in F$}
+            \State $\varphi_{\aut} \gets \varphi_{\aut} \bigvee\limits_{i\in[1,m]} r_i = \myvec{V}[i])$
           \EndIf
+          \State Remove $(q, \myvec{V})$ from $lastStates(\aut)$
+          \State Add $(q', \myvec{V}+\myvec{v})$ to $lastStates(\aut)$ for each transition $q\xrightarrow[\myvec{v}]{a} q'\in \aut$
         \EndFor
+        \State $\varphi_{under}\gets \varphi_{under}\wedge\varphi_\aut$
       \EndFor
-    \State \textbf{return} $\varphi_{under}$
+      \If{$\varphi_{under}\wedge \theta$ is satisfiable}
+        \State \textbf{return} \emph{true}
+      \EndIf
+      \State $bound \gets bound - 1$
+    \EndWhile
+    \State \textbf{return} \emph{false}
+    % \For{$\aut \in auts$}
+    % \State $\varphi_\aut\gets false$ 
+    % \State Suppose $\aut = (Q, \Sigma, \delta, q_I, F, (r_1, \cdots, r_m), \theta)$
+    % \ForAll{run $q_0q_1\cdots q_{n}$ whose length is less than $bound$}
+    % \If{$q_{n}\in F$}
+    % \State Let $\myvec{V}$ to be the sum of the vectors on the run
+    % \State $\varphi_{\aut} \gets \varphi_{\aut} \vee(\theta(q_n)\bigwedge\limits_{i\in[1,m]} r_i = \myvec{V}[i])$
+    % \EndIf
+    % \EndFor
+    % \State $\varphi_{under} \gets \varphi_{under}\wedge \varphi_{\aut}$
+    % \EndFor
+    % \State \textbf{return} $\varphi_{under}$
   \end{algorithmic}

### 2023-05-03 2023-1-19/sections/cefa.tex
cefa

@@
 \begin{definition}[Cost-Enriched Finite Automaton]
-  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, q_0, F, \theta)$ where
+  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, q_0, F)$ where
   \begin{itemize}
@@
 %    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
-    \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers, 
+    \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers.
 %  set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.
 $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
-    \item $\alpha: F \rightarrow \Phi(R)$ attaches to each finite state an accepting condition that is specified by an LIA formula.
+%    \item $\alpha: F \rightarrow \Phi(R)$ attaches to each finite state an accepting condition that is specified by an LIA formula.
 %    a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
@@
 \end{definition}
-The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
-are attached to final states.
+%The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
+%are attached to final states.
 
-For readability, we assume a linear order on $R$ and write $R$ as a vector $\myvec{r} = (r_1, \cdots, r_k)$.
-Moreover, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where for each $i \in [k]$, $v_i$ is the update on the value of $r_i$.
+For readability, from now on, we assume a linear order on $R$ and write $R$ as a vector $\myvec{r} = (r_1, \cdots, r_k)$.
+Accordingly, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where for each $i \in [k]$, $v_i$ is the update on the value of $r_i$.
 We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$.
@@
 A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$.
-A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(q_n)[\myvec{\myvec{v'}/\myvec{r}]$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}}$.
+A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$.
+The \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is defined as $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$.Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.
+Finally, we define the semantics of a CEFA $\aut$ as $\Lang(\aut) = \{(w, \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
+
+%
+%and $\alpha(q_n)[\myvec{\myvec{v'}/\myvec{r}]$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}}$.
 Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
@@
 %
-\item $\alpha'((q_1, q_2)) = \alpha_1(q_1) \wedge \alpha_2(q_2)$ for each $(q_1, q_2) \in F'$, 
+%\item $\alpha'((q_1, q_2)) = \alpha_1(q_1) \wedge \alpha_2(q_2)$ for each $(q_1, q_2) \in F'$, 
 %
@@
 \end{itemize}
-Intuitively, $\aut_1 \times \aut_2$ defines the intersection of $\Lang(\aut_1)$ and $\Lang(\aut_2)$.
+Roughly speaking, $\aut_1 \times \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of both $\aut_1$ and $\aut_2$.  
+%the intersection of $\Lang(\aut_1)$ and $\Lang(\aut_2)$.
+
+Let $((\aut_1,\cdots, \aut_n), \varphi)$ be a tuple such that $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1)$, $\cdots$, $\aut_n = (R_n, Q_n, \Sigma, \delta_n, q_{n, 0}, F_n)$ are CEFA, and $\varphi(R_1, \cdots, R_n)$ is an LIA formula.
+Then the \emph{relation} defined by $((\aut_1, \cdots, \aut_n), \varphi)$, denoted by $\srel((\aut_1, \cdots, \aut_n), \varphi)$, is $\{(w, \myvec{v'_1}, \cdots, \myvec{v'_n}) \mid \forall i \in [n].\ (w, \myvec{v'_i}) \in \Lang(\aut_i), \varphi(\myvec{v'_1}/R_1, \cdots, \myvec{v'_n}/R_n) \mbox{ is true}\}$.
 

### 2023-05-03 2023-1-19/sections/algorithms.tex
algorithm

@@
 For example, $(\Sigma \setminus a)^{\{m,n\}}$ is handled, while $((\Sigma \setminus a)^{\{m,n\}})^*$ is unhandled.
-We first discuss the encoding of handled counting operators, and then discuss the encoding of unhandled counting operators.\newline
+We first discuss the encoding of handled counting operators, and then discuss the encoding of unhandled counting operators.
+
 % We must syntactically rewrite bounded repetition $\regex\{m,n\}$ if it is the sub-regex of complement (e.g., $(\regex\{m,n\})^C$), closure(e.g., $(\regex\{m,n\})^*$), and bounded repetition(e.g., $(\regex\{m,n\})\{m', n'\}$), we unwind it to $\regex^m\mid\cdots\mid\regex^n$.
@@
 The inductive step is constructing CEFA of the concatenation, union, intersection, closure, complement and counting of CEFA(s) of sub-regex(es).
-Operations except for counting are trivial and represented in Appendix , we only illustrate counting here.\newline
+Operations except for counting are trivial and represented in Appendix , we only illustrate counting here.
+
 Given a regex $\regex^{\{m,n\}}$ without unhandled counting operator, suppose the NFA recognizing $\regex$ is $\aut = (Q,\Sigma,\delta,q_I,F)$, then the CEFA recognizing $\regex^{\{m,n\}}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_I, F\cup\{q_I\}, r, \theta)$ where:
@@
 After the construction, we need to eliminate epsilon transitions.
-It is done by adding transition $q_f\xrightarrow[(1)]{a} q$ for transition $q_I\xrightarrow[(0)]{a} q$ and then deleting the transition $q_f\xrightarrow[(1)]{\epsilon} q_I$, for each accepting state $q_f$.\newline
+It is done by adding transition $q_f\xrightarrow[(1)]{a} q$ for transition $q_I\xrightarrow[(0)]{a} q$ and then deleting the transition $q_f\xrightarrow[(1)]{\epsilon} q_I$, for each accepting state $q_f$.
+
 \begin{figure}[h]
@@
 \end{example}
+
 Above discusses the construction of handled counting operators.
@@
 The simple loop $q_I\xrightarrow[(1)]{\Sigma} q_I$ increase $1$ on register $r$ for all char in $\Sigma$, so that the value of $r$ is equal to the length of word.
-The accepting condition $\theta$ attachs $q_I$ to $r > 120$, ensuring the length of accepting word is greater than $120$.\newline
+The accepting condition $\theta$ attachs $q_I$ to $r > 120$, ensuring the length of accepting word is greater than $120$.
+
 % The formal definition of pre-images of abundant string functions is listed in \cite{atva2020}, and we do not repeat it here.
@@
 In this section, we show how to combine them to deal with the string constraints with regex-counting and string-length.
-% \begin{definition} [The Product of Two CEFA]\newline
+% \begin{definition} [The Product of Two CEFA]
+
 %   Given two CEFAs $\aut_1 = (Q_1, \Sigma, \delta_1, q_{I_1}, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2, q_{I_2}, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the product of them, denoted by $\aut_1 \times \aut_2$, is defined as $(Q_1\times Q_2, \Sigma, \delta, (q_{I_1}, q_{I_2}), F_1\times F_2, R_1\cup R_2, \theta)$ where
@@
 The emptiness problem is \emph{abbreviated as $SAT_{CEFA}[LIA]$ problem}.
-\newline
+
 As mentioned in \cite{atva2020}, the \emptinessprob{} is theoretically Pspace-complete.
@@
 However, it is not efficient enough for complex string constraints.
-So we put forward a new framework that brings in symbolic-aware simplification and under-approximation heuristics.\newline
+So we put forward a new framework that brings in symbolic-aware simplification and under-approximation heuristics.
+
 The main idea of our framework is to simplify the input CEFAs firstly and under-approximate the solution of the \emptinessprob{} by adding length bounds on string variables.
@@
 Or else, they are empty.
-The framework is \emph{sound} and \emph{complete}.\newline
+The framework is \emph{sound} and \emph{complete}.
+
 The framework is shown in Algorithm \ref{alg:emptiness}, we simplify the input CEFAs at line 1 because they may have too many transitions and registers to solve.
@@
 After the simplification, we try to find a solution by under-approximation at line 2 and line 3.
-The under-approximation algorithm explore satisfiable register values from low string-length to high string-length.
-If it finds a solution \denghang{todo} Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
+The under-approximation algorithm explore possible satisfiable register values within a length bound $MaxBound$.
+If it finds a solution then we return true because the under-approximation is sound for sat.
+Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
 The Parikh image checking is complete so that satisfiability implies non-emptiness directly.
-\newline
-The incremental under-approximation program is executed many times until the $MaxBound$ is reached.
-$MaxBound$ is an empirical bound set to $15$ in our experiment because it brings exponential growth of searching space.
-The details of simplification and under-approximation are shown in Algorithm \ref{alg:simplify} and the details of  are shown in Algorithm \ref{alg:underApprox}.\newline
+
+The under-approximation program is incremental.
+In other words, it tries to find a solution with smaller length bound of each string variable first and increment the string length bound if the search of smaller length bound fails.
+$MaxBound$ is the max length bound we try which is empirically set to $15$ in our experiment.
+It should not be too large because of the exponential growth of searching space.
+The details of simplification and under-approximation are shown in Algorithm \ref{alg:simplify} and the details of  are shown in Algorithm \ref{alg:underApprox}.
+
 \begin{algorithm}[h]
@@
 \end{itemize}
+
  For the symbolic form $\aut_{sym}$, we treat $q\xrightarrow[\myvec{0}_n]{a}q'$ as epsilon transition and compute the epsilon-closure based on it.
@@
 If them are duplicated at line 6, we remove one of them at line 7 and the corresponding symbolic update at line 9.
-After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register, to ensure the value of it is consistent at line 11.\newline
+After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register, to ensure the value of it is consistent at line 11.
+
 We have the following proposition:
@@
 \subsubsection{Under-Approximation} \label{subsec:under-approx}
-\denghang{revising} \newline
 The purpose of under-approximation is to accelerate the solving process of satisfiable instances.
 With the observation that the accepted string words in practical instances are usual short, we under-approximate the \emptinessprob{} by adding length bounds on string variables.
-We use string length as the bound and probe the CEFA from low to high bound.
-This section discusses the situation in which the string length bound is fixed.
-The main idea is to enumerate all possible runs ending in accepting states with lengths less than the fixed bound.
-Although the number of possible runs is an exponential growth of the bound, we usually solve practical satisfiable instances within 1s.
-As shown in the Algorithm \ref{alg:underApprox}, for each CEFA, we enumerate all runs whose length is less than the bound and compute the value of registers by the sum of vectors on the run at line 4.
-If the run is ended with an accepting state, then we compute the updates of registers by the sum of vectors on the run at line 6.
-Together with the accepting condition of the accepting state, we add the updates of registers to the under-approximation formula at line 7.
+The LIA formula representing possible register value is incrementally generated based on the incremental length bounds.
+This section discusses the implementation details of it.
+The main idea is to create a LIA formula enumerating all possible values of registers in accepting run within some length bounds.
+More detailed, The enumeration is carried out from low to high length bounds, in which the end states and registers' values of last enumeration are maintained and used in the next enumeration.
+Although the number of possible runs is an exponential growth of the bound, we usually solve practical satisfiable instances within 1s because the lengths of strings in the solution is generally less than 5.
+
+As shown in the Algorithm \ref{alg:underApprox}, $\varphi_{under}$ is the under-approximated LIA formula which is initialized to the input LIA formula $\psi$ at line 2.
+$\varphi_\aut$ is the under-approximated LIA formula of each automaton $\aut$ which is initialized to $false$ at line 3.
+$lastStates$ maps each automaton $\aut$ to the set consisting of pairs of state and corresponding registers' value in the last enumeration.
+$lastStates(\aut)$ is initialized to the pair of initial state and zero values for each automaton $\aut$ at line 4.
+$length$ is the current bound of lengths of string variables which is initialized to $0$ at line 5.
+The main loop at line 6-20 iteratively tries possible solution from low to high length bound.
+For each iteration, we generate LIA formula respectively for each automaton.
+To each CEFA $\aut$, we get pairs of last state and corresponding registers' values from $lastStates$ at line 8.
+In each pair, if the last state is accepted at line 9, we add LIA formula of the possible registers' values to $\varphi_\aut$ as a conjunct at line 10.
+After that, we update the set of pairs of in $lastStates$ by removing the probed pair at line 12 and adding new pairs of next state and corresponding registers' values at line 13.
+Finally, we combine the incremental LIA formula of each automaton at line 15.
+If the LIA formula $\varphi\wedge \theta$ is satisfiable at line 17, i.e., we find a solution with all strings having length less than or equal to $length$, we return \emph{true} at line 18.
+Otherwise, the next iteration would be invoked with a larger length.
+If we can not find a solution within the max string length bound, we return \emph{false} at line 22.
 \begin{algorithm}[h]
@@
   \begin{algorithmic}[1]
-    \Require The CEFAs $auts$, max string length $bound$, other LIA formula $\psi$
+    \Require $auts$: the CEFAs, $bound$: the max string length bound, $\psi$: the LIA formula constraining the CEFAs
     % \Ensure The linear integer arithmetic $\varphi_{under}$ representing under-approximation of the register values of $auts$
@@
     \Statex
+    \State $\theta$ is the conjunction of all accepting conditions of $auts$
     \State $\varphi_{under}$ is an incremental LIA formula as under approximation, initialized to $\psi$
     \State $\varphi_\aut$ is an incremental LIA formula for each automaton $\aut$, initialized to $false$
-    \State $\theta$ is the conjunction of all accepting conditions of $auts$
     \State $lastStates(\aut)$ is the set of (last state, vector's sum) pairs of $\aut$, initialized to $\{(q_I, 0_n)\}$ 
-    \While {$bound \geq 0$}
+    \State $length$ is the current bound for string-length, initialized to $0$
+    \While {$length \leq bound$}
       \For{$\aut \in auts$}
@@
           \If{$q\in F$}
-            \State $\varphi_{\aut} \gets \varphi_{\aut} \bigvee\limits_{i\in[1,m]} r_i = \myvec{V}[i])$
+            \State $\varphi_{\aut} \gets \varphi_{\aut}\vee \bigwedge\limits_{i\in[1,m]} r_i = \myvec{V}[i]$
           \EndIf
@@
       \EndIf
-      \State $bound \gets bound - 1$
+      \State $length \gets length + 1$
     \EndWhile
@@
 \begin{example}
-  Consider the automaton in Fig.
-\ref{subfig:aut_x} again.
-The solution of the Parikh image of it leads to a complete but inefficient result since the quantifier-free linear integer arithmetic formulas are solved in exponential time \cite{parikh_compute}.
+  Consider the automaton $\aut$ in Fig.
+\ref{fig:overview:product:reduced} again without the LIA constraint $r_0 > 120$, i.e., $\theta$ changes to $1\leq r_1\leq 60\wedge 1\leq r_2 \leq 60\wedge 0\leq r_3 \leq 60 $.
+The solution of the Parikh image of it leads to a complete but inefficient result since the quantifier-free LIA formulas are solved in exponential time.
 Under-approximation can accelerate the solving process.
-When we set the bound to 2, the under-approximation program will enumerate all runs whose length is 2.
-One of them is $q_I\xrightarrow[(1,1)]{a} q_1\xrightarrow[(0,1)]{b} q_f$.
-The corresponding registers' values are $r_1 = 1+0 = 1, r_2 = 1+1 = 2$.
-Checking for $r_1= 1\wedge r_2=2\wedge r_2=i\wedge 1\leq r_1\leq100$ is a lightweight process because the values of $r_1$ and $r_2$ are fixed.
+In the first iteration of under-approximation, the pairs in the $lastStates(\aut)$ is the initial pair $(q_0', (0,0,0,0))$ and $\varphi_\aut$ maintains false at line 9 because $q_0'$ is not accepted.
+Then we update $lastStates(\aut)$ by removing the pair $(q_0', (0,0,0,0))$ and adding pairs $(q_0', (1,1,0,0)), (q_1', (1,0,1,0)), (q_2', (1,0,0,0))$.
+In the second iteration, $\varphi_\aut$ changes to $r_0=1\vee r_1=0\vee r_2=0\vee r_3 = 0$ because $q_2'$ is accepted.
+$\varphi_{under}$ is always equal to $\varphi_\aut$ since there is only one automaton.
+We solve the formula $\theta\wedge \varphi_{under}$ and find it is unsatisfiable.
+In the third iteration, the pairs in the $lastStates(\aut)$ with accepting state should be $(q_0', (2,2, 0, 0)), (q_1', (2,1,1,0))$, $(q_1', (2,0,2,0))$, $(q_2', (2,1,0,0)), (q_2', (2,0,1,0)),$ $(q_2', (2,0, 0, 0))$.
+The corresponding registers' values for the accepted state $q_2'$ is $(2,1,0,0), (2, 0, 1, 0), (2, 0, 0, 0)$, in which the value of $r_1$ and $r_2$ can not be both larger than 1 which is required by $\theta$.
+So the formula $\theta\wedge \varphi_{under}$ is still unsatisfiable.
+Finally, We obtain a pair $(q_2', (3,1,1,0))$ from the pair $(q_1', (2,1,1,0))$ and the transition $q_1'\xrightarrow[(1,0,0,0)]{} q_2'$, whose corresponding registers' values is a solution $(3,1,1,0)$, i.e., $r_0=3, r_1=1, r_2=1, r_3=0$.
 \end{example}
@@
 \subsection{High-level algorithm}
+
+The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process.
+We construct the automata of all length operations occurring in the ESL conjunction $\varphi$ at line 3 and the automata of all regular memberships at line 4.
+In the following steps, we call an automaton to be \emph{final} if we will not operate it anymore.
+The set $finalAuts$ contains all final automata for all string variables and is initially empty at line 1.
+The intersection of $\aut_{len}$ and $\aut_{regex}$ at line 5 ensures the final automaton of $x$ reserves both length and regular information.
+At line 6, we compute an NFA form to throw unsat rapidly.
+An NFA form of CEFA is obtained by removing update functions and accepting conditions while maintaining graph structure.
+More exactly, given a CEFA $\aut = (Q,\Sigma, \delta, q_I, F, R, \theta)$, the NFA form of $\aut$ is $(Q, \Sigma, \delta', q_I, F)$ where $\delta'$ is composed of transition $q\xrightarrow[]{a} q'$ for $q\xrightarrow[\myvec{v}]{a} q'\in \delta$.
+It is obvious that the NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7.
+Sometimes the over-approximation is useful.
+For example, to solve the string constraint $x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^* $ which CVC5 has failed on, the NFA form is empty because there is no path to accepting states.
+
+After obtaining all final CEFAs of all string variables and their NFA forms are not empty, we check whether the final CEFAs are empty under the linear integer arithmetic $\psi$ at line 12.
+If they are empty under $\psi$, we return $unsat$.
+Otherwise, we return $sat$.
+
 \begin{algorithm}[h]
@@
 \end{algorithm}
-The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process.
-We construct the automata of all length operations occurring in the ESL conjunction $\varphi$ at line 3 and the automata of all regular memberships at line 4.
-In the following steps, we call an automaton to be \emph{final} if we will not operate it anymore.
-The set $finalAuts$ contains all final automata for all string variables and is initially empty at line 1.
-The intersection of $\aut_{len}$ and $\aut_{regex}$ at line 5 ensures the final automaton of $x$ reserves both length and regular information.
-At line 6, we compute an NFA form to throw unsat rapidly.
-An NFA form of CEFA is obtained by removing update functions and accepting conditions while maintaining graph structure.
-More exactly, given a CEFA $\aut = (Q,\Sigma, \delta, q_I, F, R, \theta)$, the NFA form of $\aut$ is $(Q, \Sigma, \delta', q_I, F)$ where $\delta'$ is composed of transition $q\xrightarrow[]{a} q'$ for $q\xrightarrow[\myvec{v}]{a} q'\in \delta$.
-It is obvious that the NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7.
-Sometimes the over-approximation is useful.
-For example, to solve the string constraint $x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^* $ which CVC5 has failed on, the NFA form is empty because there is no path to accepting states.
-\newline
-After obtaining all final CEFAs of all string variables and their NFA forms are not empty, we check whether the final CEFAs are empty under the linear integer arithmetic $\psi$ at line 12.
-If they are empty under $\psi$, we return $unsat$.
-Otherwise, we return $sat$.
 

### 2023-05-03 2023-1-19/sections/algorithms.tex
algorithm done

@@
 
-As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers, instead of unfolding them explicitly.
+As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers instead of unfolding them explicitly.
 Additionally, we use registers to represent string lengths.
-After that, the satisfiability of string constraints involve regex-counting and string-length is reduced to the satisfiability of LIA, which can be solved by off-the-shelf SMT solvers.
+After that, the satisfiability of string constraints involves regex-counting, and string-length is reduced to the satisfiability of LIA, which off-the-shelf SMT solvers can solve.
 We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
@@
 In this section, we discuss the encoding in detail.
-A counting operator is called \emph{handled} if it is not the sub-regex of complement, closure or other counting, and called \emph{unhandled} otherwise.
+A counting operator is called \emph{handled} if it is not the sub-regex of complement, closure, or another counting, and called \emph{unhandled} otherwise.
 For example, $(\Sigma \setminus a)^{\{m,n\}}$ is handled, while $((\Sigma \setminus a)^{\{m,n\}})^*$ is unhandled.
-We first discuss the encoding of handled counting operators, and then discuss the encoding of unhandled counting operators.
+We first discuss the encoding of handled counting operators and then the encoding of unhandled counting operators.
 
@@
 After this syntactic rewriting, we call the resulting regex $\regex'$ \emph{non-nested}.
-Given a regex $\regex$ without unhandled counting operator, the base case is constructing CEFA of a single character, an empty string, or an empty language.
-The inductive step is constructing CEFA of the concatenation, union, intersection, closure, complement and counting of CEFA(s) of sub-regex(es).
+Given a regex $\regex$ without an unhandled counting operator, the base case is constructing the CEFA of a single character, an empty string, or an empty language.
+The inductive step is constructing CEFA of the concatenation, union, intersection, closure, complement, and counting of CEFA(s) of sub-regex(es).
 Operations except for counting are trivial and represented in Appendix , we only illustrate counting here.
@@
   \item $\delta'$ is composed by transition $q\xrightarrow[(0)]{a} q'$ for each transition $q\xrightarrow[()]{a} q' \in \delta$, and transition $q_f\xrightarrow[(1)]{\epsilon} q_I$ for each accepting state $q_f\in F$,
-  \item $\theta$ is the function mapping each accepting state to a same linear integer arithmetic $(m\leq )r\leq n$. The lower bound $m\leq r$ is unnecessary if $q_I\in F$.
+  \item $\theta$ is the function mapping each accepting state to the same linear integer arithmetic $(m\leq )r\leq n$. The lower bound $m\leq r$ is unnecessary if $q_I\in F$.
 \end{itemize}
-The main idea is to add an epsilon transition to initial state from each accepting state like closure, to repeat the sub-regex.
+The main idea is to add an epsilon transition to the initial state from each accepting state, like closure, to repeat the sub-regex.
 Then the counting time is incremented by 1 when the epsilon transition is invoked.
@@
 A new register $r$ is added to store the counting times.
-The transition $q\xrightarrow[(1)]{\epsilon} q_I$ it constructed to increment the counting times.
+The transition $q\xrightarrow[(1)]{\epsilon} q_I$ is constructed to increment the counting times.
 The accepting condition $(m\leq) r\leq n$ is attached to each accepting state to constrain the counting times of the accepting word.
@@
 As shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}, the base cases are the constructions of character $b$ (Fig.\ref{subfig:count_aut_b}) and $c$ (Fig.\ref{subfig:count_aut_c}).
-The first inductive step is construction the union of them (Fig.\ref{sub@subfig:count_aut_sigma_minus_a}).
+The first inductive step is building their union (Fig.\ref{sub@subfig:count_aut_sigma_minus_a}).
 The second inductive step is to add counting information on the automaton.
 To do that we add a new register $r$ to save counting times,  transitions $q_2\xrightarrow[(1)]{\epsilon} q_0$ and $q_1\xrightarrow[(1)]{\epsilon} q_0$  to update the counting times.
-The accepting condition of each accepting state is $5\leq r\leq 60$, which ensure the counting time of the accepting word is in the range $[5,60]$.
+The accepting condition of each accepting state is $5\leq r\leq 60$, which ensures the accepting word's counting time is in the range $[5,60]$.
 After epsilon elimination we get the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ (shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}).
@@
 Above discusses the construction of handled counting operators.
-The unhandled counting operator can not be constructed by the same way.
+In the same way, we can not construct the unhandled counting operator.
 For example, for the regex $(ab^{\{1,100\}})*$ with unhandled counting operator, there are infinite repetitions of $ab^{\{1,100\}}$.
-The counting times of each repetition are irrelevant, so that we can not represent them using finite registers.
-We have to syntactically rewrite the unhandled counting operator into union operator and concatenation operator.
+The counting times of each repetition are irrelevant, so we can not represent them using finite registers.
+We must syntactically rewrite the unhandled counting operator into union and concatenation operators.
 More exactly, the sub-regex $\regex^{\{m,n\}}$ in the unhandled regex is rewritten into $\underbrace{\regex\cdot\regex\cdots\regex}_{m \text{ times}}\mid\cdots\mid \underbrace{\regex\cdot\regex\cdots\regex}_{n \text{ times}}$.
@@
 Then we generate CEFAs of all regular expressions $\regex$ in all regular literals $x\in \regex$ and intersect these CEFAs and pre-images to get the final automaton $\aut_x$ for $x$.
-At present, there is a final CEFA for each string variable $x$.
+There is a final CEFA for each string variable $x$.
 The linear arithmetic constraint $\psi$ restricts the accepting word of final CEFAs.
@@
 Namely, the CEFA is $(\{q_I\}, \Sigma, \{q_I\xrightarrow[(1)]{\Sigma} q_I\}, q_I, \{q_I\}, r, \theta)$ where accpeting condition $\theta$ is based on the length formula.
-As an illustration, example \ref{eg:pre_len} shows the CEFA of length constraints $|x| > 120$, whose language is the set of all words with length greater than $120$.
-The simple loop $q_I\xrightarrow[(1)]{\Sigma} q_I$ increase $1$ on register $r$ for all char in $\Sigma$, so that the value of $r$ is equal to the length of word.
-The accepting condition $\theta$ attachs $q_I$ to $r > 120$, ensuring the length of accepting word is greater than $120$.
+As an illustration, example \ref{eg:pre_len} shows the CEFA of length constraints $|x| > 120$, whose language is the set of all words with a length greater than $120$.
+The simple loop $q_I\xrightarrow[(1)]{\Sigma} q_I$ increase $1$ on register $r$ for all char in $\Sigma$, so that the value of $r$ is equal to the length of the accepting word.
+The accepting condition $\theta$ attaches $q_I$ to $r > 120$, ensuring the length of the accepting word is greater than $120$.
 
@@
 % \subsection{Combine Regex-counting and String-length}
-% In the previous section, we have discussed the construction of regex-counting operator and string-length constraint.
+% In the previous section, we discussed the construction of the regex-counting operator and string-length constraint.
 In this section, we show how to combine them to deal with the string constraints with regex-counting and string-length.
@@
 As mentioned in \cite{atva2020}, the \emptinessprob{} is theoretically Pspace-complete.
-We has used a model-checking tool \emph{nuXmv}\cite{nuxmv} to solve it in previous work.
-However, it is not efficient enough for complex string constraints.
+In previous work, we have used a model-checking tool \emph{nuXmv}\cite{nuxmv} to solve it.
+However, it needs to be more efficient for complex string constraints.
 So we put forward a new framework that brings in symbolic-aware simplification and under-approximation heuristics.
@@
 If the Parikh image is satisfiable, the CEFAs are not empty under $\psi$.
-Or else, they are empty.
+Alternatively, they are empty.
 The framework is \emph{sound} and \emph{complete}.
 
-The framework is shown in Algorithm \ref{alg:emptiness}, we simplify the input CEFAs at line 1 because they may have too many transitions and registers to solve.
+The framework is shown in Algorithm \ref{alg:emptiness}.
+We simplify the input CEFAs at line 1 because they may have too many transitions and registers to solve.
 The main idea of the simplification is treating the alphabet as unary and the symbolic updates as characters of transitions in the minimization.
 After the simplification, we try to find a solution by under-approximation at line 2 and line 3.
-The under-approximation algorithm explore possible satisfiable register values within a length bound $MaxBound$.
-If it finds a solution then we return true because the under-approximation is sound for sat.
+The under-approximation algorithm explores possible satisfiable register values within a length bound $MaxBound$.
+We return true if it finds a solution because the under-approximation is sound for sat.
 Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
@@
 The under-approximation program is incremental.
-In other words, it tries to find a solution with smaller length bound of each string variable first and increment the string length bound if the search of smaller length bound fails.
-$MaxBound$ is the max length bound we try which is empirically set to $15$ in our experiment.
+In other words, it first tries to find a solution with a smaller length bound of each string variable and increments the string length bound if the search for a smaller length bound fails.
+$MaxBound$ is the max length bound we try, empirically set to $15$ in our experiment.
 It should not be too large because of the exponential growth of searching space.
-The details of simplification and under-approximation are shown in Algorithm \ref{alg:simplify} and the details of  are shown in Algorithm \ref{alg:underApprox}.
+The details of simplification and under-approximation are shown in Algorithm \ref{alg:simplify}, and the details are shown in Algorithm \ref{alg:underApprox}.
 
@@
 The purpose of simplification is to remove duplicated transitions and registers.
-In the emptiness checking Algorithm \ref{alg:emptiness}, the non-emptiness is equal to the reachability of CEFAs.
-Thus, the symbolic updates on transitions are meritorious because it influences registers values, while the characters are not.
-The alphabet of the CEFA can be seen as unary (i.e., the alphabet is $\{a\}$) and the vectors as characters.
-The special vector $\myvec{0}_n$ with only zero elements is seen as $\epsilon$ character.
-Namely, given a CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$, we obtain a symbolic form  $\aut_{sym} = (Q, \Sigma', \delta', q_I, F, R, \theta)$ where
+In the emptiness checking Algorithm \ref{alg:emptiness}, the non-emptiness equals the reachability of CEFAs.
+The symbolic updates on transitions are meritorious because it influences register values, while the characters are not.
+The alphabet of the CEFA can be ignored (i.e., the alphabet is $\{a\}$), and the vectors can be seen as characters.
+The special vector $\myvec{0}_n$ with only zero elements is seen as a $\epsilon$ character since it does not change the values of registers.
+Namely, given a CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$, we obtain a symbolic NFA  $\aut_{sym} = (Q, \Sigma', \delta', q_I, F)$ where
 \begin{itemize}
-  \item $\Sigma' = \{a\}$,
-  \item the transition set $\delta'$ is composed of transition $q\xrightarrow[\myvec{v}]{a}q'$ if there is a transition $q\xrightarrow[\myvec{v}]{b} q'$ in $\delta$ for $b\in \Sigma$.
+  \item $\Sigma' = \{\myvec{v} \mid \text{there exists one transition in } \aut \text{ with update } \myvec{v}\}$,
+  \item the transition set $\delta'$ is composed of transition $q\xrightarrow{\myvec{v}}q'$ if there is a transition $q\xrightarrow[\myvec{v}]{b} q'$ in $\delta$.
 \end{itemize}
 
- For the symbolic form $\aut_{sym}$, we treat $q\xrightarrow[\myvec{0}_n]{a}q'$ as epsilon transition and compute the epsilon-closure based on it.
-Likewise, we treat $q\xrightarrow[\myvec{v}]{a}q'$ as a transition with character $(a, \myvec{v})$ and determine the automaton based on it.
-Two accepting states are equivalent if they have the same accepting condition, and two states are equivalent if they reach equivalent states for each character.
-We simplify the automaton by merging these equivalent states.
-Briefly, we directly apply algorithms of epsilon-closure, determination, and simplification in \cite{aut_hopcraft}.
-The explanation above discuss funcitons $\algfun{determinizeByVec}$ and $\algfun{minimizeByVec}$ at line 3 and line 4.
-From line 5 to line 13, we check whether two registers $r_i$ and $r_j$ are duplicated.
+ For the symbolic NFA $\aut_{sym}$, we treat $q\xrightarrow{\myvec{0}_n} q'$ as an epsilon transition since it does not change the values of the registers.
+Then we apply the epsilon elimination algorithm \cite{aut_hopcraft} to delete these epsilon transitions.
+After that, we apply the determination and minimization algorithm \cite{aut_hopcraft} of NFAs to $\aut_{sym}$, resulting in a smaller automaton $\aut_{simp}$.
+Finally, we reinterpret $\aut_{simp}$ as a CEFA with the accepting condition of $\aut$ and unary alphabet $\Sigma = \{a\}$.
+Above illustrates functions $\algfun{determinizeByVec}$ and $\algfun{minimizeByVec}$ from line 3 to line 5.
+From line 6 to line 14, we check whether two registers $r_i$ and $r_j$ are duplicated.
 (i.e., the symbolic updates of them are always the same).
-If them are duplicated at line 6, we remove one of them at line 7 and the corresponding symbolic update at line 9.
-After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register, to ensure the value of it is consistent at line 11.
+If they are duplicated at line 6, we remove one of them and the corresponding symbolic update from line 8 to line 10.
+After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register at line 12, ensuring that the value of the deleted register is consistent.
 
@@
       R, \theta)$ and $R=(r_1,\cdots, r_n)$
+    \State $\algfun{epsilonElimByVec}(\aut)$
     \State $\algfun{determinizeByVec}(\aut)$
@@
 \begin{example}
-  Considering the CEFA (Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}) recognizing $(\Sigma\setminus a)\{5,60\}$ where $\Sigma = \{a,b,c\}$.
-We first obtain a symbolic form of it by using unary alphabet (Fig.\ref{subfig:sigma_minus_a_5_60:simplify}) and then minimize the symbolic form based on the label $"a:(1)"$(Fig.\ref{subfig:simp_final}).
+  Considering the CEFA (Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}) recognizing $(\Sigma\setminus a)\{1,60\}$ where $\Sigma = \{a,b,c\}$.
+We first obtain a symbolic NFA of it by ignoring the unary alphabet (Fig.\ref{subfig:sigma_minus_a_5_60:simplify}).
+Then we eliminate epsilon transitions $q_0\xrightarrow[]{(0)} q_1$ and $q_0\xrightarrow[]{(0)}q_2$, resulting in the minimized NFA directly.
+Finally, we reinterpret it as CEFA by adding accepting condition $1\leq r \leq 60$(Fig.\ref{subfig:simp_final}).
   \begin{figure}[h]
@@
         ]
-        \node at (-1, 1) {$\scriptstyle 5\leq r \leq 60$};
+        % \node at (-1, 1) {$\scriptstyle 5\leq r \leq 60$};
         \node[state,initial, accepting]      (q_0)                      {$\scriptstyle q_0$};
@@
 
-        \path[->] (q_0) edge node [right] {$\scriptstyle a:(0)$} (q_1)
-        (q_1) edge [loop right] node {$\scriptstyle a:(1)$} (q_1)
-        (q_0) edge           node [right] {$\scriptstyle a:(0)$} (q_2)
-        (q_2) edge [loop right] node {$\scriptstyle a:(1)$} (q_0);
+        \path[->] (q_0) edge node [right] {$(0)$} (q_1)
+        (q_1) edge [loop right] node {$(1)$} (q_1)
+        (q_0) edge           node [right] {$(0)$} (q_2)
+        (q_2) edge [loop right] node {$(1)$} (q_0);
       \end{tikzpicture}
-      \caption{The symbolic form of $\aut_{\Sigma\setminus a\{5,60\}}$}
+      \caption{The symbolic NFA of $\aut_{\Sigma\setminus a\{5,60\}}$}
       \label{subfig:sigma_minus_a_5_60:simplify}
@@
 
-        \node at (-0.5, 0.5) {$\scriptstyle 5\leq r \leq 60$};
+        \node at (-0.5, 0.5) {$\scriptstyle 1\leq r \leq 60$};
         \node[state,initial,accepting]            (q_0)       {$\scriptstyle q_I$};
 
-        \path[->] (q_0) edge [loop below] node{$\scriptstyle a:(1)$} ();
+        \path[->] (q_0) edge [loop below] node{$(1)$} ();
       \end{tikzpicture}
@@
 We compute the CEFAs of $i=|x|$, $j=|x|$ and intersect them to get the final CEFA represented in Fig.\ref{subfig:duplicate}.
-However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their symbolic updates are always same.
+However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their symbolic updates are always the same.
 We simplify the CEFA by removing the duplicated register $r_2$ and corresponding symbolic updates, as shown in Fig.\ref{subfig:remove_duplicate}.
@@
 
-        \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma$/(1)} ();
+        \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma:(1)$} ();
       \end{tikzpicture}
@@
 The purpose of under-approximation is to accelerate the solving process of satisfiable instances.
-With the observation that the accepted string words in practical instances are usual short, we under-approximate the \emptinessprob{} by adding length bounds on string variables.
-The LIA formula representing possible register value is incrementally generated based on the incremental length bounds.
-This section discusses the implementation details of it.
-The main idea is to create a LIA formula enumerating all possible values of registers in accepting run within some length bounds.
-More detailed, The enumeration is carried out from low to high length bounds, in which the end states and registers' values of last enumeration are maintained and used in the next enumeration.
-Although the number of possible runs is an exponential growth of the bound, we usually solve practical satisfiable instances within 1s because the lengths of strings in the solution is generally less than 5.
+With the observation that the accepted string words in practical instances are usually short, we under-approximate the \emptinessprob{} by adding length bounds on string variables.
+The LIA formula representing possible register value is incrementally generated based on the incremental length bounds, and this section discusses its implementation details.
+The main idea is to create an LIA formula enumerating all possible values of registers in accepting runs within some length bounds.
+More detailed, The enumeration is carried out from low to high length bounds, in which the end states and registers' values of the last enumeration are maintained and used in the following enumeration.
+Although the number of possible runs is an exponential growth of the bound, we usually solve practical satisfiable instances within 1s because the lengths of strings in the solution are generally less than 5.
 
@@
 $lastStates$ maps each automaton $\aut$ to the set consisting of pairs of state and corresponding registers' value in the last enumeration.
-$lastStates(\aut)$ is initialized to the pair of initial state and zero values for each automaton $\aut$ at line 4.
+$lastStates(\aut)$ is initialized to the pair of the initial state and zero values for each automaton $\aut$ at line 4.
 $length$ is the current bound of lengths of string variables which is initialized to $0$ at line 5.
-The main loop at line 6-20 iteratively tries possible solution from low to high length bound.
-For each iteration, we generate LIA formula respectively for each automaton.
+The main loop at lines 6-20 iteratively tries possible solutions from low to high length bound.
+For each iteration, we generate the LIA formula respectively for each automaton.
 To each CEFA $\aut$, we get pairs of last state and corresponding registers' values from $lastStates$ at line 8.
-In each pair, if the last state is accepted at line 9, we add LIA formula of the possible registers' values to $\varphi_\aut$ as a conjunct at line 10.
-After that, we update the set of pairs of in $lastStates$ by removing the probed pair at line 12 and adding new pairs of next state and corresponding registers' values at line 13.
+In each pair, if the last state is accepted at line 9, we add the LIA formula of the possible registers' values to $\varphi_\aut$ as a conjunct at line 10.
+After that, we update the set of pairs in $lastStates$ by removing the probed pair at line 12 and adding new pairs of the next state and corresponding registers' values at line 13.
 Finally, we combine the incremental LIA formula of each automaton at line 15.
@@
 More exactly, given a CEFA $\aut = (Q,\Sigma, \delta, q_I, F, R, \theta)$, the NFA form of $\aut$ is $(Q, \Sigma, \delta', q_I, F)$ where $\delta'$ is composed of transition $q\xrightarrow[]{a} q'$ for $q\xrightarrow[\myvec{v}]{a} q'\in \delta$.
-It is obvious that the NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7.
+The NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7.
 Sometimes the over-approximation is useful.

### 2023-05-03 2023-1-19/sections/cefa.tex
operations for NFA

@@
 A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$.
-The \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is defined as $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$.Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+The \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is defined as $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$.
+Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
 We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.
-Finally, we define the semantics of a CEFA $\aut$ as $\Lang(\aut) = \{(w, \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
+Finally, we define the semantics of a CEFA $\aut$ as $\Lang(\aut) = \{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
 
@@
 %Finally, we define the product of two CEFA.
+
+In the sequel, we define three operations on CEFA, namely, concatenation, intersection, and union. These three operations will be used for solving RECL constraints in the next section.
+
 Let $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1, \alpha_1)$ and  $\aut_2 = (R_2, Q_2, \Sigma, \delta_2, q_{2,0}, F_2, \alpha_2)$ be two CEFA that share the alphabet. 
 Moreover, suppose $R_1 \cap R_2 = \emptyset$. 
-We define the \emph{product} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \times \aut_2 = (R', Q', \Sigma, \delta', q'_0, F', \alpha')$, as follows.
+%We define two operations of CEFA, namely, the product and union, as follows.
+
+The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is
+
+The \emph{product} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \times \aut_2 = (R', Q', \Sigma, \delta', q'_0, F', \alpha')$, is defined in the sequel. 
 \begin{itemize}
@@
 \end{itemize}
-Roughly speaking, $\aut_1 \times \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of both $\aut_1$ and $\aut_2$.  
-%the intersection of $\Lang(\aut_1)$ and $\Lang(\aut_2)$.
+From the construction, $\Lang(\aut_1 \times \aut_2) = \{(w; \myvec{v'_1}, \myvec{v'_2}) \mid (w; \myvec{v'_1}) \in \Lang(\aut_1), (w; \myvec{v'_2}) \in \Lang(\aut_2)\}$. 
+Intuitively, $\aut_1 \times \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.
+
+The \emph{union} of $\aut_1$ and $\aut_2$
 
 Let $((\aut_1,\cdots, \aut_n), \varphi)$ be a tuple such that $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1)$, $\cdots$, $\aut_n = (R_n, Q_n, \Sigma, \delta_n, q_{n, 0}, F_n)$ are CEFA, and $\varphi(R_1, \cdots, R_n)$ is an LIA formula.
-Then the \emph{relation} defined by $((\aut_1, \cdots, \aut_n), \varphi)$, denoted by $\srel((\aut_1, \cdots, \aut_n), \varphi)$, is $\{(w, \myvec{v'_1}, \cdots, \myvec{v'_n}) \mid \forall i \in [n].\ (w, \myvec{v'_i}) \in \Lang(\aut_i), \varphi(\myvec{v'_1}/R_1, \cdots, \myvec{v'_n}/R_n) \mbox{ is true}\}$.
+Then the \emph{relation} defined by $((\aut_1, \cdots, \aut_n), \varphi)$, denoted by $\srel((\aut_1, \cdots, \aut_n), \varphi)$, is $\{(w, \myvec{v'_1}, \cdots, \myvec{v'_n}) \mid \varphi(\myvec{v'_1}/R_1, \cdots, \myvec{v'_n}/R_n)\equiv \ltrue, \forall i \in [n].\ (w, \myvec{v'_i}) \in \Lang(\aut_i)\}$.
+
+%the intersection of $\Lang(\aut_1)$ and $\Lang(\aut_2)$.
 

### 2023-05-03 2023-1-19/sections/preliminaries.tex
operations for NFA

@@
 An NFA $\NFA$ is said to be \emph{deterministic} if $I$ is a singleton and, for every $q \in Q$ and $a \in \Sigma$, there is at most one state $q' \in Q$ such that $(q, a, q') \in \delta$.
+We use DFA to denote deterministic finite automata.
 %
-It is well-known that finite automata capture regular languages precisely.
-Moreover, the class of regular languages is closed under union, intersection, Kleene star, complement, and language difference \cite{HU79}.
+It is well-known that finite automata capture regular languages. 
+Moreover, the class of regular languages is closed under union, intersection, concatenation, Kleene star, complement, and language difference \cite{HU79}.
+In the sequel, we recall the constructions of NFA corresponding to these language operations.
+Let $\NFA_1 = (Q_1, \Sigma, \delta_1, q_{1,0}, F_1)$ and $\NFA_2 = (Q_2, \Sigma, \delta_2, q_{2,0}, F_2)$ be two NFA such that $Q_1 \cap Q_2 = \emptyset$.
+\begin{itemize}
+\item The union of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cup \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', q'_0, F')$, where $Q'= Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $\delta' = \delta_1 \cup \delta_2 \cup \{(q'_0, a, q') \mid (q_{1,0}, a, q') \in \delta_1\} \cup \{(q'_0, a, q') \mid (q_{2,0}, a, q') \in \delta_2\}$, $F'=F_1 \cup F_2$.
+%
+\item The intersection of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cap \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', q'_0, F')$, where $Q' = Q_1 \times Q_2$, $q'_0 = (q_{1,0}, q_{2,0})$, $F' = F_1 \times F_2$, $\delta' = \{((q_1, q_2), a, (q'_1, q'_2)) \mid (q_1, a, q'_1) \in \delta_1, (q_2, a, q'_2) \in \delta_2\}$.
+%
+\item The concatenation of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \concat \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', q'_0, F')$, where $Q' = Q_1 \cup Q_2$, $q'_0 = q_{1,0}$, $\delta' = \delta_1 \cup \delta_2 \cup \{(q_1, a, q_2) \mid q_1 \in F_1, (q_{2,0}, a, q_2) \in \delta_2\}$, moreover, if $q_{2,0} \in F_2$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+%
+\item The Kleene star of $\NFA_1$, denoted by $\NFA_1^*$, is defined as $(Q_1, \Sigma, \delta'_1, q_{1,0}, F'_1)$, where $\delta'_1 = \delta_1 \cup \{(q_1, a, q'_1) \mid q_1 \in F_1, (q_{1,0}, a, q'_1) \in \delta_1\}$, $F'_1= F_1 \cup \{q_{1,0}\}$.
+%
+\item The complement of $\NFA_1$, denoted by $\overline{\NFA_1}$, is defined as $(Q'_1, \Sigma, \delta'_1, \{q_{1,0}\}, Q'_1 \setminus F'_1)$, where  $(Q'_1, \Sigma, \delta'_1, \{q_{1,0}\}, F'_1)$ is the DFA obtained from $\NFA_1$ by subset construction.
+%
+\item The language difference of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \setminus \NFA_2$, is defined as $\NFA_1 \times \overline{\NFA_2}$.
+\end{itemize}
 

### 2023-05-04 2023-1-19/sections/cefa.tex
operations of CEFA

@@
 \begin{definition}[Cost-Enriched Finite Automaton]
-  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, q_0, F)$ where
+  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F)$ where
   \begin{itemize}
   \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers, 
-    \item $Q, \Sigma, q_0, F$ are as in the definition of NFA,
+    \item $Q, \Sigma, I, F$ are as in the definition of NFA,
 %    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
@@
 $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
-%    \item $\alpha: F \rightarrow \Phi(R)$ attaches to each finite state an accepting condition that is specified by an LIA formula.
+    \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
 %    a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
@@
 
-The semantics of CEFA is define as follows. Let $\aut = (R, Q, \Sigma, \delta, q_0, F, \alpha)$ be a CEFA. 
+The semantics of CEFA is define as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
 A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
-The \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$, where the value of each register is zero. 
-A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$.
-A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$.
-The \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is defined as $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$.
+%An \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$ with $q_0 \in I$, where the value of each register is zero. 
+A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$.
+A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$.
+The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$.
 Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
@@
 Finally, we define the semantics of a CEFA $\aut$ as $\Lang(\aut) = \{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
+
+We would like to remark that the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion in the sense that the accepting condition does not distinguish final states.
+This technical choice is made so that determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.
 
@@
 
-In the sequel, we define three operations on CEFA, namely, concatenation, intersection, and union. These three operations will be used for solving RECL constraints in the next section.
+In the sequel, we define three operations on CEFA, namely, union, intersection, and concatenation. These three operations will be used for solving RECL constraints in the next section.
 
 Let $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1, \alpha_1)$ and  $\aut_2 = (R_2, Q_2, \Sigma, \delta_2, q_{2,0}, F_2, \alpha_2)$ be two CEFA that share the alphabet. 
-Moreover, suppose $R_1 \cap R_2 = \emptyset$. 
+Moreover, suppose that $R_1 \cap R_2 = \emptyset$ and $Q_1 \cap Q_2 = \emptyset$. 
 %We define two operations of CEFA, namely, the product and union, as follows.
 
-The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is
+The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$, is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.
+Two fresh auxiliary registers, say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ or from $\aut_2$.
+Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', \{q'_0\}, F', \alpha')$, where $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $\delta' = \{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, moreover,
+\begin{itemize}
+\item if $I_1 \cap F_1 \neq \emptyset$ or $I_2 \cap F_2 \neq \emptyset$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
+%
+\item otherwise, $F'=F_1 \cup F_2$ and $\alpha' = (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$.
+\end{itemize}
 
-The \emph{product} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \times \aut_2 = (R', Q', \Sigma, \delta', q'_0, F', \alpha')$, is defined in the sequel. 
+The \emph{intersection} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cap \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, is defined in the sequel. 
 \begin{itemize}
-\item $R' = R_1 \cup R_2$, $Q' = Q_1 \times Q_2$, $q'_0 = (q_{1,0}, q_{2,0})$, $F' = F_1 \times F_2$,
+\item $R' = R_1 \cup R_2$, $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, $\alpha' = \alpha_1 \wedge \alpha_2$, 
 %
@@
 %
-\item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), \myvec{v})$ such that $(q_1,a, q'_1, \prj_{R_1}(\myvec{v})) \in \delta_1$ and $(q_2,a, q'_2, \prj_{R_2}(\myvec{v})) \in \delta_2$, where $\myvec{v} \in \Int^{R'}$, $\prj_{R_1}(\myvec{v}))$ (resp.
-$\prj_{R_2}(\myvec{v}))$) is the restriction of $\myvec{v}$ to the domain $R_1$ (resp.
-$R_2$).
+\item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), (\myvec{v_1}, \myvec{v_2}))$ such that $(q_1,a, q'_1, \myvec{v_1}) \in \delta_1$ and $(q_2,a, q'_2, \myvec{v_2}) \in \delta_2$.
+%, where $\myvec{v} \in \Int^{R'}$, $\prj_{R_1}(\myvec{v}))$ (resp. $\prj_{R_2}(\myvec{v}))$) is the restriction of $\myvec{v}$ to the domain $R_1$ (resp. $R_2$). 
 \end{itemize}
-From the construction, $\Lang(\aut_1 \times \aut_2) = \{(w; \myvec{v'_1}, \myvec{v'_2}) \mid (w; \myvec{v'_1}) \in \Lang(\aut_1), (w; \myvec{v'_2}) \in \Lang(\aut_2)\}$. 
-Intuitively, $\aut_1 \times \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.
+From the construction, $\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v'_1}, \myvec{v'_2}) \mid (w; \myvec{v'_1}) \in \Lang(\aut_1), (w; \myvec{v'_2}) \in \Lang(\aut_2)\}$. 
+Intuitively, $\aut_1 \cap \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.
 
-The \emph{union} of $\aut_1$ and $\aut_2$
+The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, \vec{v_2}) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
 
-Let $((\aut_1,\cdots, \aut_n), \varphi)$ be a tuple such that $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1)$, $\cdots$, $\aut_n = (R_n, Q_n, \Sigma, \delta_n, q_{n, 0}, F_n)$ are CEFA, and $\varphi(R_1, \cdots, R_n)$ is an LIA formula.
+%Let $((\aut_1,\cdots, \aut_n), \varphi)$ be a tuple such that $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1)$, $\cdots$, $\aut_n = (R_n, Q_n, \Sigma, \delta_n, q_{n, 0}, F_n)$ are CEFA, and $\varphi(R_1, \cdots, R_n)$ is an LIA formula.
 Then the \emph{relation} defined by $((\aut_1, \cdots, \aut_n), \varphi)$, denoted by $\srel((\aut_1, \cdots, \aut_n), \varphi)$, is $\{(w, \myvec{v'_1}, \cdots, \myvec{v'_n}) \mid \varphi(\myvec{v'_1}/R_1, \cdots, \myvec{v'_n}/R_n)\equiv \ltrue, \forall i \in [n].\ (w, \myvec{v'_i}) \in \Lang(\aut_i)\}$.

### 2023-05-04 2023-1-19/sections/preliminaries.tex
operations of CEFA

--- 2023-04-29 2023-1-19/sections/preliminaries.tex
@@
 Throughout the paper, $\Sigma$ is a finite alphabet, ranged over by $a,b,\ldots$.
+
+For a function $f$ from $X$ to $Y$ and $X' \subseteq X$, we use $\prj_{X'}(f)$ to denote the restriction (aka projection) of $f$ to $X'$, that is, $\prj_{X'}(f)$ is a function from $X'$ to $Y$, and $\prj_{X'}(f)(x') = f(x')$ for each $x' \in X'$.
 
@@
 \paragraph*{Finite automata.} 
-A \emph{(nondeterministic) finite automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, q_0, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $q_0 \in Q$ is the initial state, and $F \subseteq Q$ is the set of final states.
+A \emph{(nondeterministic) finite automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, I, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $I \subseteq Q$ is the set of initial states, and $F \subseteq Q$ is the set of final states.
 For readability, we write a transition $(q, a, q') \in \delta$ as $q \xrightarrow[\delta]{a} q'$ (or simply $q \xrightarrow{a} q'$).
@@
 %
-A \emph{run} of $\NFA$ on a string $w = a_1 \cdots a_n$ is a sequence of transitions $q_0 \xrightarrow{a_1} q_1 \cdots q_{n-1} \xrightarrow{a_n} q_n$. The run is \emph{accepting} if $q_n \in F$.
+A \emph{run} of $\NFA$ on a string $w = a_1 \cdots a_n$ is a sequence of transitions $q_0 \xrightarrow{a_1} q_1 \cdots q_{n-1} \xrightarrow{a_n} q_n$ such that $q_0 \in I$.
+The run is \emph{accepting} if $q_n \in F$.
 A string $w$ is accepted by an NFA $\NFA$ if there is an accepting run of $\NFA$ on $w$.
@@
 An NFA $\NFA$ is said to be \emph{deterministic} if $I$ is a singleton and, for every $q \in Q$ and $a \in \Sigma$, there is at most one state $q' \in Q$ such that $(q, a, q') \in \delta$.
+We use DFA to denote deterministic finite automata.
 %
-It is well-known that finite automata capture regular languages precisely.
-Moreover, the class of regular languages is closed under union, intersection, Kleene star, complement, and language difference \cite{HU79}.
+
+It is well-known that finite automata capture regular languages. 
+Moreover, the class of regular languages is closed under union, intersection, concatenation, Kleene star, complement, and language difference \cite{HU79}.
+In the sequel, we recall the constructions of NFA corresponding to these language operations.
+Let $\NFA_1 = (Q_1, \Sigma, \delta_1, I_1, F_1)$ and $\NFA_2 = (Q_2, \Sigma, \delta_2, I_2, F_2)$ be two NFA such that $Q_1 \cap Q_2 = \emptyset$.
+\begin{itemize}
+\item The union of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cup \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q'= Q_1 \cup Q_2$, $\delta' = \delta_1 \cup \delta_2$, $I' = I_1 \cup I_2$, and $F'=F_1 \cup F_2$.
+%
+\item The intersection of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cap \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, and $\delta' = \{((q_1, q_2), a, (q'_1, q'_2)) \mid (q_1, a, q'_1) \in \delta_1, (q_2, a, q'_2) \in \delta_2\}$.
+%
+\item The concatenation of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \concat \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\delta' = \delta_1 \cup \delta_2 \cup \{(q_1, a, q_2) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+%
+\item The Kleene star of $\NFA_1$, denoted by $\NFA_1^*$, is defined as $(Q'_1, \Sigma, \delta'_1, I'_1, F'_1)$, where $Q'_1 = Q_1 \cup \{q_0\}$ with $q_0 \not \in Q_1$, $I'_1 = \{q_0\}$, $F'_1= F_1 \cup \{q_0\}$, $\delta'_1 = \delta_1 \cup \{(q_0, a, q'_1)  \mid \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\} \cup \{(q_1, a, q'_1) \mid q_1 \in F_1, \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\}$.
+%
+\item The complement of $\NFA_1$, denoted by $\overline{\NFA_1}$, is defined as $(Q'_1, \Sigma, \delta'_1, q'_0, Q'_1 \setminus F'_1)$, where  $(Q'_1, \Sigma, \delta'_1, q'_0, F'_1)$ is the DFA obtained from $\NFA_1$ by subset construction.
+%
+\item The language difference of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \setminus \NFA_2$, is defined as $\NFA_1 \cap \overline{\NFA_2}$.
+\end{itemize}
 

### 2023-05-04 2023-1-19/sections/cefa.tex
operations of CEFA

@@
 Two fresh auxiliary registers, say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ or from $\aut_2$.
-Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', \{q'_0\}, F', \alpha')$, where $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $\delta' = \{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, moreover,
+Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, where
+\begin{itemize}
+\item $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $I' = \{q'_0\}$, 
+\item $\delta'$ is the union of $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, and $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, where the last two components of the vectors denote the updates of $r'_1$ and $r'_2$,
+
+\item $F'$ and $\alpha'$ are defined as follows, 
 \begin{itemize}
@@
 \end{itemize}
+\end{itemize}
+From the construction, we know that 
+$$\Lang(\aut_1 \cup \aut_2) = \{(w; \myvec{v}) \mid \myvec{v} \in \Int^{R'}, (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ or } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
 
@@
 \end{itemize}
-From the construction, $\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v'_1}, \myvec{v'_2}) \mid (w; \myvec{v'_1}) \in \Lang(\aut_1), (w; \myvec{v'_2}) \in \Lang(\aut_2)\}$. 
+From the construction, 
+$$\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v}) \mid \myvec{v} \in \Int^{R'}, (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$ 
 Intuitively, $\aut_1 \cap \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.
@@
 The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, \vec{v_2}) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+From the construction,
+$$\Lang(\aut_1 \concat \aut_2) = \{(w_1w_2; \myvec{v}) \mid (w_1; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1), (w_2; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
 

### 2023-05-04 2023-1-19/figures/cactus_plot_all.tex
experiment done

@@
-\documentclass[11pt]{standalone}
+\documentclass[11.5pt]{standalone}
 \usepackage{color}
@@
 \resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=Total,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
-\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(225,0.9749977728285077)(674,3.1805545657015593)(1123,5.703)(1572,8.438265033407571)(2021,11.531574610244988)(2470,15.075634743875279)(2919,19.097318485523385)(3368,23.513942093541203)(3817,28.284)(4266,33.33244543429844)(4715,38.708721603563475)(5164,44.401)(5613,50.33589755011136)(6062,56.600924276169266)(6511,63.173)(6960,69.98948106904231)(7409,77.14595100222718)(7858,84.631)(8307,92.40952561247217)(8756,100.53519599109131)(9205,109.03022717149221)(9654,117.91206904231626)(10103,127.1663407572383)(10552,136.837)(11001,146.92912249443208)(11450,157.46868596881959)(11899,168.51312026726058)(12348,180.07232962138085)(12797,192.1541959910913)(13246,204.78042093541202)(13695,218.04313363028953)(14144,232.00983073496658)(14593,246.74662138084634)(15042,262.27243207126946)(15491,278.68448552338526)(15940,296.06152338530063)(16389,314.4960133630289)(16838,333.9485055679287)(17287,354.4259688195991)(17736,375.96304899777283)(18185,398.6540556792873)(18634,422.5968173719376)(19083,447.8012538975501)(19532,474.371004454343)(19981,502.39159242761696)(20430,531.845280623608)(20879,562.9128819599109)(21328,595.7690712694878)(21777,630.5182316258351)(22226,667.4171893095769)(22675,706.6891113585746)(23124,748.524723830735)(23573,792.9852828507795)(24022,840.2546636971047)(24471,890.3767973273942)(24920,943.5922204899778)(25369,1000.1014365256125)(25818,1060.165797327394)(26267,1123.928570155902)(26716,1191.6269866369712)(27165,1263.5346726057908)(27614,1339.8836258351894)(28063,1421.4921870824055)(28512,1509.265877505568)(28961,1603.7898262806236)(29410,1705.7232071269486)(29859,1815.975158129176)(30308,1935.8308218262805)(30757,2066.3378129175944)(31206,2207.6831870824053)(31655,2360.5879977728287)(32104,2524.3051202672605)(32553,2699.568131403118)(33002,2887.1032249443206)(33451,3087.4128195991093)(33900,3301.4712672605788)(34349,3529.438995545657)(34798,3772.0046904231626)(35247,4029.107385300668)(35696,4301.784002227171)(36145,4592.399788418708)(36594,4903.131832962137)(37043,5237.107131403119)(37492,5598.406133630289)(37941,5992.969233853007)(38390,6426.496371937639)(38839,6909.088826280624)(39288,7452.511380846326)(39737,8072.1869844098)(40186,8790.347349665924)(40635,9647.260521158129)(41084,10728.830126948777)(41533,12233.169844097996)(41982,14371.070224944322)(42431,17689.691844097993)(42880,23713.308975501113)(43329,34464.926198218265)(43776.5,51319.2588161435)(44001,62564.102)};
+\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt, dashed, dash pattern=on 2pt off 8 pt] coordinates {(1,0.004)(225,0.9749977728285077)(674,3.1805545657015593)(1123,5.703)(1572,8.438265033407571)(2021,11.531574610244988)(2470,15.075634743875279)(2919,19.097318485523385)(3368,23.513942093541203)(3817,28.284)(4266,33.33244543429844)(4715,38.708721603563475)(5164,44.401)(5613,50.33589755011136)(6062,56.600924276169266)(6511,63.173)(6960,69.98948106904231)(7409,77.14595100222718)(7858,84.631)(8307,92.40952561247217)(8756,100.53519599109131)(9205,109.03022717149221)(9654,117.91206904231626)(10103,127.1663407572383)(10552,136.837)(11001,146.92912249443208)(11450,157.46868596881959)(11899,168.51312026726058)(12348,180.07232962138085)(12797,192.1541959910913)(13246,204.78042093541202)(13695,218.04313363028953)(14144,232.00983073496658)(14593,246.74662138084634)(15042,262.27243207126946)(15491,278.68448552338526)(15940,296.06152338530063)(16389,314.4960133630289)(16838,333.9485055679287)(17287,354.4259688195991)(17736,375.96304899777283)(18185,398.6540556792873)(18634,422.5968173719376)(19083,447.8012538975501)(19532,474.371004454343)(19981,502.39159242761696)(20430,531.845280623608)(20879,562.9128819599109)(21328,595.7690712694878)(21777,630.5182316258351)(22226,667.4171893095769)(22675,706.6891113585746)(23124,748.524723830735)(23573,792.9852828507795)(24022,840.2546636971047)(24471,890.3767973273942)(24920,943.5922204899778)(25369,1000.1014365256125)(25818,1060.165797327394)(26267,1123.928570155902)(26716,1191.6269866369712)(27165,1263.5346726057908)(27614,1339.8836258351894)(28063,1421.4921870824055)(28512,1509.265877505568)(28961,1603.7898262806236)(29410,1705.7232071269486)(29859,1815.975158129176)(30308,1935.8308218262805)(30757,2066.3378129175944)(31206,2207.6831870824053)(31655,2360.5879977728287)(32104,2524.3051202672605)(32553,2699.568131403118)(33002,2887.1032249443206)(33451,3087.4128195991093)(33900,3301.4712672605788)(34349,3529.438995545657)(34798,3772.0046904231626)(35247,4029.107385300668)(35696,4301.784002227171)(36145,4592.399788418708)(36594,4903.131832962137)(37043,5237.107131403119)(37492,5598.406133630289)(37941,5992.969233853007)(38390,6426.496371937639)(38839,6909.088826280624)(39288,7452.511380846326)(39737,8072.1869844098)(40186,8790.347349665924)(40635,9647.260521158129)(41084,10728.830126948777)(41533,12233.169844097996)(41982,14371.070224944322)(42431,17689.691844097993)(42880,23713.308975501113)(43329,34464.926198218265)(43776.5,51319.2588161435)(44001,62564.102)};
 \addlegendentry{CVC5}
 
-\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.001)(251,297.57713173652695)(752,919.7552734530939)(1253,1557.5426886227544)(1754,2204.4396926147706)(2255,2859.376377245509)(2756,3521.8273872255486)(3257,4190.722225548902)(3758,4865.928748502994)(4259,5547.6787385229545)(4760,6236.603149700599)(5261,6933.963383233533)(5762,7640.762471057885)(6263,8358.542546906187)(6764,9088.009331337325)(7265,9829.516295409183)(7766,10584.155027944113)(8267,11351.854083832335)(8768,12132.038473053894)(9269,12922.84225748503)(9770,13722.257604790419)(10271,14529.294508982037)(10772,15342.857842315369)(11273,16162.547750499003)(11774,16987.797055888226)(12275,17818.525373253495)(12776,18654.640872255488)(13277,19495.92945708583)(13778,20342.265848303392)(14279,21193.5768003992)(14780,22049.840229540918)(15281,22911.280876247507)(15782,23777.89823752495)(16283,24649.420652694607)(16784,25525.914844311377)(17285,26407.47073253493)(17786,27293.949608782437)(18287,28185.26401996008)(18788,29081.597538922157)(19289,29982.794083832334)(19790,30888.764532934132)(20291,31799.552532934133)(20792,32714.965686626747)(21293,33634.779389221556)(21794,34558.914994011975)(22295,35487.432938123755)(22796,36420.41224550898)(23297,37357.921341317364)(23798,38300.12236526946)(24299,39247.05026946108)(24800,40198.6993253493)(25301,41155.420005988024)(25802,42117.09206986028)(26303,43083.934487025945)(26804,44055.638161676645)(27305,45032.20359081836)(27806,46014.43762275449)(28307,47002.47610978044)(28808,47996.60786626746)(29309,48996.72237325349)(29810,50002.71481636727)(30311,51014.77076447106)(30812,52033.40894211577)(31313,53058.83036726547)(31814,54091.27846506986)(32315,55130.93350698603)(32816,56178.196696606785)(33317,57233.01951297405)(33818,58295.94183832336)(34319,59367.47835329341)(34820,60448.25150898203)(35321,61539.139007984035)(35822,62640.02783033932)(36323,63751.15949301397)(36824,64873.163516966066)(37325,66006.96277045908)(37826,67153.20774251496)(38327,68312.41110578843)(38828,69485.79568263472)(39329,70674.74570259481)(39830,71879.40951097805)(40331,73099.98904191617)(40832,74339.00549301397)(41333,75598.06305988024)(41834,76879.22272055889)(42335,78185.40860279441)(42836,79517.57918962077)(43337,80881.22110778444)(43838,82281.94577045909)(44339,83721.56675449101)(44840,85208.95984231538)(45341,86753.0387285429)(45842,88367.2720998004)(46343,90074.41964870259)(46844,91896.8463233533)(47345,93861.7311497006)(47846,96027.48211576846)(48347,98576.50299800398)(48848,102635.06975449102)(49112,108033.23818518518)(49127,108809.673)};
+\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.001)(251,297.57713173652695)(752,919.7552734530939)(1253,1557.5426886227544)(1754,2204.4396926147706)(2255,2859.376377245509)(2756,3521.8273872255486)(3257,4190.722225548902)(3758,4865.928748502994)(4259,5547.6787385229545)(4760,6236.603149700599)(5261,6933.963383233533)(5762,7640.762471057885)(6263,8358.542546906187)(6764,9088.009331337325)(7265,9829.516295409183)(7766,10584.155027944113)(8267,11351.854083832335)(8768,12132.038473053894)(9269,12922.84225748503)(9770,13722.257604790419)(10271,14529.294508982037)(10772,15342.857842315369)(11273,16162.547750499003)(11774,16987.797055888226)(12275,17818.525373253495)(12776,18654.640872255488)(13277,19495.92945708583)(13778,20342.265848303392)(14279,21193.5768003992)(14780,22049.840229540918)(15281,22911.280876247507)(15782,23777.89823752495)(16283,24649.420652694607)(16784,25525.914844311377)(17285,26407.47073253493)(17786,27293.949608782437)(18287,28185.26401996008)(18788,29081.597538922157)(19289,29982.794083832334)(19790,30888.764532934132)(20291,31799.552532934133)(20792,32714.965686626747)(21293,33634.779389221556)(21794,34558.914994011975)(22295,35487.432938123755)(22796,36420.41224550898)(23297,37357.921341317364)(23798,38300.12236526946)(24299,39247.05026946108)(24800,40198.6993253493)(25301,41155.420005988024)(25802,42117.09206986028)(26303,43083.934487025945)(26804,44055.638161676645)(27305,45032.20359081836)(27806,46014.43762275449)(28307,47002.47610978044)(28808,47996.60786626746)(29309,48996.72237325349)(29810,50002.71481636727)(30311,51014.77076447106)(30812,52033.40894211577)(31313,53058.83036726547)(31814,54091.27846506986)(32315,55130.93350698603)(32816,56178.196696606785)(33317,57233.01951297405)(33818,58295.94183832336)(34319,59367.47835329341)(34820,60448.25150898203)(35321,61539.139007984035)(35822,62640.02783033932)(36323,63751.15949301397)(36824,64873.163516966066)(37325,66006.96277045908)(37826,67153.20774251496)(38327,68312.41110578843)(38828,69485.79568263472)(39329,70674.74570259481)(39830,71879.40951097805)(40331,73099.98904191617)(40832,74339.00549301397)(41333,75598.06305988024)(41834,76879.22272055889)(42335,78185.40860279441)(42836,79517.57918962077)(43337,80881.22110778444)(43838,82281.94577045909)(44339,83721.56675449101)(44840,85208.95984231538)(45341,86753.0387285429)(45842,88367.2720998004)(46343,90074.41964870259)(46844,91896.8463233533)(47345,93861.7311497006)(47846,96027.48211576846)(48347,98576.50299800398)(48848,102635.06975449102)(49112,108033.23818518518)(49127,108809.673)};
 \addlegendentry{OstrichCEA}
 
-\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.966)(242,253.6938115942029)(725,797.780635610766)(1208,1375.6963540372672)(1691,1971.2173726708074)(2174,2579.9891242236026)(2657,3200.1552774327124)(3140,3831.5469544513458)(3623,4473.097327122153)(4106,5124.210623188406)(4589,5784.478358178054)(5072,6452.883861283644)(5555,7128.7226770186335)(6038,7811.80366252588)(6521,8501.433523809525)(7004,9197.051412008283)(7487,9898.351950310558)(7970,10605.06412215321)(8453,11317.27030020704)(8936,12035.019962732918)(9419,12758.173621118012)(9902,13486.76760041408)(10385,14220.709316770186)(10868,14959.795536231884)(11351,15703.822519668738)(11834,16453.023033126294)(12317,17207.60976190476)(12800,17967.250432712215)(13283,18732.071757763973)(13766,19501.90405383023)(14249,20276.887979296065)(14732,21056.855813664595)(15215,21842.13654037267)(15698,22632.851068322983)(16181,23429.176252587993)(16664,24230.890689440996)(17147,25038.21724637681)(17630,25851.334213250517)(18113,26669.63826293996)(18596,27493.383886128366)(19079,28323.0271242236)(19562,29158.7289689441)(20045,30000.663378881985)(20528,30848.824979296067)(21011,31703.274051759836)(21494,32564.10966252588)(21977,33431.79361697723)(22460,34306.333964803314)(22943,35188.23764182194)(23426,36077.66052587992)(23909,36975.0900331263)(24392,37880.26252380952)(24875,38793.40235403727)(25358,39715.36438095238)(25841,40646.487689441)(26324,41586.495204968945)(26807,42535.87147412008)(27290,43494.791265010346)(27773,44463.5207184265)(28256,45442.81579710145)(28739,46433.07173706004)(29222,47434.819573498964)(29705,48449.619180124224)(30188,49478.66922360248)(30671,50522.00113043478)(31154,51581.44218426501)(31637,52657.74352795031)(32120,53751.45314699793)(32603,54863.35853830228)(33086,55994.589289855074)(33569,57145.683132505175)(34052,58318.82643478261)(34535,59515.03370600414)(35018,60737.58520703933)(35501,61988.47214492754)(35984,63269.9586563147)(36467,64585.57833333334)(36950,65939.52480745342)(37433,67336.00833747412)(37916,68780.93298964803)(38399,70278.50410351966)(38882,71836.31644513458)(39365,73463.24823602484)(39848,75170.24680331264)(40331,76972.25751759835)(40814,78886.19549068323)(41297,80940.91662111801)(41780,83159.28797722567)(42263,85568.35025051759)(42746,88213.17140786748)(43229,91128.96203933746)(43712,94354.33373498965)(44195,97990.84464389233)(44678,102163.55392546584)(45161,107056.2527805383)(45644,112920.6944989648)(46127,120179.79210559007)(46610,129819.74801035198)(47093,144581.69753830228)(47351.5,156224.77838235296)(47370,157248.051)};
+\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,0.966)(242,253.6938115942029)(725,797.780635610766)(1208,1375.6963540372672)(1691,1971.2173726708074)(2174,2579.9891242236026)(2657,3200.1552774327124)(3140,3831.5469544513458)(3623,4473.097327122153)(4106,5124.210623188406)(4589,5784.478358178054)(5072,6452.883861283644)(5555,7128.7226770186335)(6038,7811.80366252588)(6521,8501.433523809525)(7004,9197.051412008283)(7487,9898.351950310558)(7970,10605.06412215321)(8453,11317.27030020704)(8936,12035.019962732918)(9419,12758.173621118012)(9902,13486.76760041408)(10385,14220.709316770186)(10868,14959.795536231884)(11351,15703.822519668738)(11834,16453.023033126294)(12317,17207.60976190476)(12800,17967.250432712215)(13283,18732.071757763973)(13766,19501.90405383023)(14249,20276.887979296065)(14732,21056.855813664595)(15215,21842.13654037267)(15698,22632.851068322983)(16181,23429.176252587993)(16664,24230.890689440996)(17147,25038.21724637681)(17630,25851.334213250517)(18113,26669.63826293996)(18596,27493.383886128366)(19079,28323.0271242236)(19562,29158.7289689441)(20045,30000.663378881985)(20528,30848.824979296067)(21011,31703.274051759836)(21494,32564.10966252588)(21977,33431.79361697723)(22460,34306.333964803314)(22943,35188.23764182194)(23426,36077.66052587992)(23909,36975.0900331263)(24392,37880.26252380952)(24875,38793.40235403727)(25358,39715.36438095238)(25841,40646.487689441)(26324,41586.495204968945)(26807,42535.87147412008)(27290,43494.791265010346)(27773,44463.5207184265)(28256,45442.81579710145)(28739,46433.07173706004)(29222,47434.819573498964)(29705,48449.619180124224)(30188,49478.66922360248)(30671,50522.00113043478)(31154,51581.44218426501)(31637,52657.74352795031)(32120,53751.45314699793)(32603,54863.35853830228)(33086,55994.589289855074)(33569,57145.683132505175)(34052,58318.82643478261)(34535,59515.03370600414)(35018,60737.58520703933)(35501,61988.47214492754)(35984,63269.9586563147)(36467,64585.57833333334)(36950,65939.52480745342)(37433,67336.00833747412)(37916,68780.93298964803)(38399,70278.50410351966)(38882,71836.31644513458)(39365,73463.24823602484)(39848,75170.24680331264)(40331,76972.25751759835)(40814,78886.19549068323)(41297,80940.91662111801)(41780,83159.28797722567)(42263,85568.35025051759)(42746,88213.17140786748)(43229,91128.96203933746)(43712,94354.33373498965)(44195,97990.84464389233)(44678,102163.55392546584)(45161,107056.2527805383)(45644,112920.6944989648)(46127,120179.79210559007)(46610,129819.74801035198)(47093,144581.69753830228)(47351.5,156224.77838235296)(47370,157248.051)};
 \addlegendentry{Ostrich}
 
-\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.011)(186,2.2441590296495955)(557,6.933)(928,11.756)(1299,16.579323450134773)(1670,21.640361185983828)(2041,27.149)(2412,32.7522641509434)(2783,38.633)(3154,44.569)(3525,50.505)(3896,56.501285714285714)(4267,62.774)(4638,69.081)(5009,75.52557412398923)(5380,82.2)(5751,88.973)(6122,96.007)(6493,103.1635552560647)(6864,110.573)(7235,117.993)(7606,125.53147978436657)(7977,133.315)(8348,141.106)(8719,148.99271698113208)(9090,157.14)(9461,165.30301886792452)(9832,173.677)(10203,182.21)(10574,190.76738005390837)(10945,199.596)(11316,208.5)(11687,217.41128032345014)(12058,226.567)(12429,235.842)(12800,245.117)(13171,254.577)(13542,264.223)(13913,273.8815498652291)(14284,283.797)(14655,293.8208894878706)(15026,304.088)(15397,314.48077088948787)(15768,325.109)(16139,335.8730970350404)(16510,346.874)(16881,358.04226415094337)(17252,369.488)(17623,381.06956603773585)(17994,392.92)(18365,404.96041239892185)(18736,417.2412641509434)(19107,429.8)(19478,442.5950269541779)(19849,455.633102425876)(20220,468.952436657682)(20591,482.541)(20962,496.35875471698114)(21333,510.47258760107815)(21704,524.8864797843665)(22075,539.608)(22446,554.6164123989217)(22817,569.9552641509433)(23188,585.6441725067385)(23559,601.7121401617251)(23930,618.1685202156334)(24301,635.0817951482479)(24672,652.4683611859839)(25043,670.3729433962263)(25414,688.8481024258759)(25785,707.9234986522912)(26156,727.6508382749325)(26527,748.0661428571428)(26898,769.1473557951483)(27269,790.9199433962264)(27640,813.4528598382749)(28011,836.8241024258759)(28382,861.080665768194)(28753,886.3027628032345)(29124,912.5774959568732)(29495,939.9839460916443)(29866,968.653962264151)(30237,998.7923530997305)(30608,1030.6136603773584)(30979,1064.2623396226415)(31350,1100.220989218329)(31721,1138.6942614555257)(32092,1179.9984878706198)(32463,1224.7958005390835)(32834,1274.0089541778977)(33205,1328.8225849056605)(33576,1391.1415417789756)(33947,1463.6065067385443)(34318,1550.8098005390837)(34689,1661.4692075471698)(35060,1824.3313234501347)(35431,2141.3325256064686)(35802,2940.3429811320757)(36151.5,6899.040887195121)(36317,12695.69)};
+\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt,  dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.011)(186,2.2441590296495955)(557,6.933)(928,11.756)(1299,16.579323450134773)(1670,21.640361185983828)(2041,27.149)(2412,32.7522641509434)(2783,38.633)(3154,44.569)(3525,50.505)(3896,56.501285714285714)(4267,62.774)(4638,69.081)(5009,75.52557412398923)(5380,82.2)(5751,88.973)(6122,96.007)(6493,103.1635552560647)(6864,110.573)(7235,117.993)(7606,125.53147978436657)(7977,133.315)(8348,141.106)(8719,148.99271698113208)(9090,157.14)(9461,165.30301886792452)(9832,173.677)(10203,182.21)(10574,190.76738005390837)(10945,199.596)(11316,208.5)(11687,217.41128032345014)(12058,226.567)(12429,235.842)(12800,245.117)(13171,254.577)(13542,264.223)(13913,273.8815498652291)(14284,283.797)(14655,293.8208894878706)(15026,304.088)(15397,314.48077088948787)(15768,325.109)(16139,335.8730970350404)(16510,346.874)(16881,358.04226415094337)(17252,369.488)(17623,381.06956603773585)(17994,392.92)(18365,404.96041239892185)(18736,417.2412641509434)(19107,429.8)(19478,442.5950269541779)(19849,455.633102425876)(20220,468.952436657682)(20591,482.541)(20962,496.35875471698114)(21333,510.47258760107815)(21704,524.8864797843665)(22075,539.608)(22446,554.6164123989217)(22817,569.9552641509433)(23188,585.6441725067385)(23559,601.7121401617251)(23930,618.1685202156334)(24301,635.0817951482479)(24672,652.4683611859839)(25043,670.3729433962263)(25414,688.8481024258759)(25785,707.9234986522912)(26156,727.6508382749325)(26527,748.0661428571428)(26898,769.1473557951483)(27269,790.9199433962264)(27640,813.4528598382749)(28011,836.8241024258759)(28382,861.080665768194)(28753,886.3027628032345)(29124,912.5774959568732)(29495,939.9839460916443)(29866,968.653962264151)(30237,998.7923530997305)(30608,1030.6136603773584)(30979,1064.2623396226415)(31350,1100.220989218329)(31721,1138.6942614555257)(32092,1179.9984878706198)(32463,1224.7958005390835)(32834,1274.0089541778977)(33205,1328.8225849056605)(33576,1391.1415417789756)(33947,1463.6065067385443)(34318,1550.8098005390837)(34689,1661.4692075471698)(35060,1824.3313234501347)(35431,2141.3325256064686)(35802,2940.3429811320757)(36151.5,6899.040887195121)(36317,12695.69)};
 \addlegendentry{Z3str3}
 
-\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.011)(239.5,3.003002092050209)(717.5,9.1975)(1195.5,15.473012552301256)(1673.5,22.107)(2151.5,28.998301255230125)(2629.5,36.189257322175735)(3107.5,43.723)(3585.5,51.41517364016736)(4063.5,59.4635)(4541.5,67.71654184100419)(5019.5,76.30319037656903)(5497.5,85.1595)(5975.5,94.25958786610879)(6453.5,103.694)(6931.5,113.29276150627615)(7409.5,123.2455)(7887.5,133.35723430962344)(8365.5,143.826)(8843.5,154.50561924686193)(9321.5,165.50718828451883)(9799.5,176.844)(10277.5,188.50183891213388)(10755.5,200.51678451882844)(11233.5,212.91894769874477)(11711.5,225.72532635983262)(12189.5,238.95126150627615)(12667.5,252.61902928870293)(13145.5,266.74416527196655)(13623.5,281.3792719665272)(14101.5,296.5673284518829)(14579.5,312.32517364016735)(15057.5,328.69830753138075)(15535.5,345.75547071129705)(16013.5,363.5053430962343)(16491.5,382.03205439330543)(16969.5,401.41702092050207)(17447.5,421.740859832636)(17925.5,443.13734518828454)(18403.5,465.74711715481175)(18881.5,489.6866317991632)(19359.5,515.2018326359832)(19837.5,542.4019079497908)(20315.5,571.3341841004185)(20793.5,602.0434246861925)(21271.5,634.8044414225941)(21749.5,669.9890732217573)(22227.5,707.3027949790795)(22705.5,746.5745418410041)(23183.5,787.7260481171548)(23661.5,830.9119288702929)(24139.5,876.1701464435146)(24617.5,923.622338912134)(25095.5,973.415449790795)(25573.5,1025.5190062761505)(26051.5,1080.0794079497907)(26529.5,1137.2441317991631)(27007.5,1197.1491380753137)(27485.5,1259.997587866109)(27963.5,1325.8901129707112)(28441.5,1395.2120104602511)(28919.5,1468.3164748953975)(29397.5,1545.6936443514644)(29875.5,1627.697179916318)(30353.5,1714.9648619246861)(30831.5,1808.0020460251046)(31309.5,1907.35589958159)(31787.5,2013.702589958159)(32265.5,2127.0940774058577)(32743.5,2248.581280334728)(33221.5,2378.0494142259417)(33699.5,2516.0073828451887)(34177.5,2664.039150627615)(34655.5,2823.221081589958)(35133.5,2993.5568828451883)(35611.5,3175.938089958159)(36089.5,3371.323261506276)(36567.5,3580.968144351464)(37045.5,3805.3915585774057)(37523.5,4045.9028263598325)(38001.5,4303.908370292887)(38479.5,4580.979633891214)(38957.5,4878.916422594142)(39435.5,5201.072190376569)(39913.5,5551.563246861924)(40391.5,5935.1872949790795)(40869.5,6355.800322175732)(41347.5,6819.264579497908)(41825.5,7332.79989330544)(42303.5,7913.116949790795)(42781.5,8584.49539748954)(43259.5,9376.001481171548)(43737.5,10323.55618200837)(44215.5,11494.943769874477)(44693.5,13013.801780334728)(45171.5,15102.628635983265)(45649.5,18314.33333472803)(46127.5,23806.17459414226)(46582.5,34369.86894675926)(46800,43539.844)};
+\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1.5pt off 2pt] coordinates {(1,0.011)(239.5,3.003002092050209)(717.5,9.1975)(1195.5,15.473012552301256)(1673.5,22.107)(2151.5,28.998301255230125)(2629.5,36.189257322175735)(3107.5,43.723)(3585.5,51.41517364016736)(4063.5,59.4635)(4541.5,67.71654184100419)(5019.5,76.30319037656903)(5497.5,85.1595)(5975.5,94.25958786610879)(6453.5,103.694)(6931.5,113.29276150627615)(7409.5,123.2455)(7887.5,133.35723430962344)(8365.5,143.826)(8843.5,154.50561924686193)(9321.5,165.50718828451883)(9799.5,176.844)(10277.5,188.50183891213388)(10755.5,200.51678451882844)(11233.5,212.91894769874477)(11711.5,225.72532635983262)(12189.5,238.95126150627615)(12667.5,252.61902928870293)(13145.5,266.74416527196655)(13623.5,281.3792719665272)(14101.5,296.5673284518829)(14579.5,312.32517364016735)(15057.5,328.69830753138075)(15535.5,345.75547071129705)(16013.5,363.5053430962343)(16491.5,382.03205439330543)(16969.5,401.41702092050207)(17447.5,421.740859832636)(17925.5,443.13734518828454)(18403.5,465.74711715481175)(18881.5,489.6866317991632)(19359.5,515.2018326359832)(19837.5,542.4019079497908)(20315.5,571.3341841004185)(20793.5,602.0434246861925)(21271.5,634.8044414225941)(21749.5,669.9890732217573)(22227.5,707.3027949790795)(22705.5,746.5745418410041)(23183.5,787.7260481171548)(23661.5,830.9119288702929)(24139.5,876.1701464435146)(24617.5,923.622338912134)(25095.5,973.415449790795)(25573.5,1025.5190062761505)(26051.5,1080.0794079497907)(26529.5,1137.2441317991631)(27007.5,1197.1491380753137)(27485.5,1259.997587866109)(27963.5,1325.8901129707112)(28441.5,1395.2120104602511)(28919.5,1468.3164748953975)(29397.5,1545.6936443514644)(29875.5,1627.697179916318)(30353.5,1714.9648619246861)(30831.5,1808.0020460251046)(31309.5,1907.35589958159)(31787.5,2013.702589958159)(32265.5,2127.0940774058577)(32743.5,2248.581280334728)(33221.5,2378.0494142259417)(33699.5,2516.0073828451887)(34177.5,2664.039150627615)(34655.5,2823.221081589958)(35133.5,2993.5568828451883)(35611.5,3175.938089958159)(36089.5,3371.323261506276)(36567.5,3580.968144351464)(37045.5,3805.3915585774057)(37523.5,4045.9028263598325)(38001.5,4303.908370292887)(38479.5,4580.979633891214)(38957.5,4878.916422594142)(39435.5,5201.072190376569)(39913.5,5551.563246861924)(40391.5,5935.1872949790795)(40869.5,6355.800322175732)(41347.5,6819.264579497908)(41825.5,7332.79989330544)(42303.5,7913.116949790795)(42781.5,8584.49539748954)(43259.5,9376.001481171548)(43737.5,10323.55618200837)(44215.5,11494.943769874477)(44693.5,13013.801780334728)(45171.5,15102.628635983265)(45649.5,18314.33333472803)(46127.5,23806.17459414226)(46582.5,34369.86894675926)(46800,43539.844)};
 \addlegendentry{Z3seq}
 
-\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.003)(242.5,1.0744855371900826)(726.5,3.4655)(1210.5,5.8855)(1694.5,8.3055)(2178.5,10.889551652892562)(2662.5,13.786)(3146.5,16.69)(3630.5,19.594)(4114.5,22.498)(4598.5,25.402)(5082.5,28.306)(5566.5,31.21)(6050.5,34.114)(6534.5,37.018)(7018.5,39.922)(7502.5,42.826)(7986.5,45.73)(8470.5,48.634)(8954.5,51.538)(9438.5,54.442)(9922.5,57.45211570247933)(10406.5,60.8125)(10890.5,64.2005)(11374.5,67.5885)(11858.5,70.9765)(12342.5,74.3645)(12826.5,77.7525)(13310.5,81.1405)(13794.5,84.5285)(14278.5,88.04413636363637)(14762.5,91.898)(15246.5,95.77)(15730.5,99.642)(16214.5,103.60915702479339)(16698.5,107.9315)(17182.5,112.2875)(17666.5,116.68544421487603)(18150.5,121.443)(18634.5,126.283)(19118.5,131.25429338842974)(19602.5,136.5615)(20086.5,141.96053099173554)(20570.5,147.721)(21054.5,153.53384710743802)(21538.5,159.6475)(22022.5,165.9395)(22506.5,172.2315)(22990.5,178.64468388429754)(23474.5,185.4)(23958.5,192.176)(24442.5,199.00360330578513)(24926.5,206.1935)(25410.5,213.4535)(25894.5,220.8263409090909)(26378.5,228.546)(26862.5,236.30813636363635)(27346.5,244.4085)(27830.5,252.6365)(28314.5,261.0807252066116)(28798.5,269.8022272727273)(29282.5,278.8455)(29766.5,288.1148698347107)(30250.5,297.7528615702479)(30734.5,307.75080165289256)(31218.5,318.19113636363636)(31702.5,329.0933388429752)(32186.5,340.5123243801653)(32670.5,352.5468078512397)(33154.5,365.25928305785123)(33638.5,378.71496694214875)(34122.5,392.9674814049587)(34606.5,408.1881095041322)(35090.5,424.496923553719)(35574.5,442.0963760330579)(36058.5,461.27055165289255)(36542.5,482.10873966942154)(37026.5,504.83204132231407)(37510.5,529.7162376033058)(37994.5,557.2993388429752)(38478.5,588.2287933884298)(38962.5,623.190291322314)(39446.5,663.5498512396694)(39930.5,711.7078305785124)(40414.5,771.0276487603306)(40898.5,850.0923057851239)(41382.5,963.3128016528926)(41866.5,1101.6400867768596)(42350.5,1247.2309276859505)(42834.5,1402.3912768595042)(43318.5,1571.1703719008265)(43802.5,1754.472152892562)(44286.5,1953.5502128099172)(44770.5,2173.350842975207)(45254.5,2424.403890495868)(45738.5,2725.6362169421486)(46222.5,3127.2070268595044)(46706.5,3851.115107438017)(47176.5,6425.0990570175445)(47406,11466.323)};
+\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt, dashed, dash pattern=on 2pt off 4pt] coordinates {(1,0.003)(242.5,1.0744855371900826)(726.5,3.4655)(1210.5,5.8855)(1694.5,8.3055)(2178.5,10.889551652892562)(2662.5,13.786)(3146.5,16.69)(3630.5,19.594)(4114.5,22.498)(4598.5,25.402)(5082.5,28.306)(5566.5,31.21)(6050.5,34.114)(6534.5,37.018)(7018.5,39.922)(7502.5,42.826)(7986.5,45.73)(8470.5,48.634)(8954.5,51.538)(9438.5,54.442)(9922.5,57.45211570247933)(10406.5,60.8125)(10890.5,64.2005)(11374.5,67.5885)(11858.5,70.9765)(12342.5,74.3645)(12826.5,77.7525)(13310.5,81.1405)(13794.5,84.5285)(14278.5,88.04413636363637)(14762.5,91.898)(15246.5,95.77)(15730.5,99.642)(16214.5,103.60915702479339)(16698.5,107.9315)(17182.5,112.2875)(17666.5,116.68544421487603)(18150.5,121.443)(18634.5,126.283)(19118.5,131.25429338842974)(19602.5,136.5615)(20086.5,141.96053099173554)(20570.5,147.721)(21054.5,153.53384710743802)(21538.5,159.6475)(22022.5,165.9395)(22506.5,172.2315)(22990.5,178.64468388429754)(23474.5,185.4)(23958.5,192.176)(24442.5,199.00360330578513)(24926.5,206.1935)(25410.5,213.4535)(25894.5,220.8263409090909)(26378.5,228.546)(26862.5,236.30813636363635)(27346.5,244.4085)(27830.5,252.6365)(28314.5,261.0807252066116)(28798.5,269.8022272727273)(29282.5,278.8455)(29766.5,288.1148698347107)(30250.5,297.7528615702479)(30734.5,307.75080165289256)(31218.5,318.19113636363636)(31702.5,329.0933388429752)(32186.5,340.5123243801653)(32670.5,352.5468078512397)(33154.5,365.25928305785123)(33638.5,378.71496694214875)(34122.5,392.9674814049587)(34606.5,408.1881095041322)(35090.5,424.496923553719)(35574.5,442.0963760330579)(36058.5,461.27055165289255)(36542.5,482.10873966942154)(37026.5,504.83204132231407)(37510.5,529.7162376033058)(37994.5,557.2993388429752)(38478.5,588.2287933884298)(38962.5,623.190291322314)(39446.5,663.5498512396694)(39930.5,711.7078305785124)(40414.5,771.0276487603306)(40898.5,850.0923057851239)(41382.5,963.3128016528926)(41866.5,1101.6400867768596)(42350.5,1247.2309276859505)(42834.5,1402.3912768595042)(43318.5,1571.1703719008265)(43802.5,1754.472152892562)(44286.5,1953.5502128099172)(44770.5,2173.350842975207)(45254.5,2424.403890495868)(45738.5,2725.6362169421486)(46222.5,3127.2070268595044)(46706.5,3851.115107438017)(47176.5,6425.0990570175445)(47406,11466.323)};
 \addlegendentry{Z3str3RE}
 
-\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.013)(121.5,1.7120082644628098)(363.5,5.2225)(605.5,8.8525)(847.5,12.548330578512397)(1089.5,16.480061983471074)(1331.5,20.66350826446281)(1573.5,25.187586776859504)(1815.5,30.315636363636365)(2057.5,37.034028925619836)(2299.5,47.26819421487603)(2541.5,63.143694214876035)(2783.5,87.08737190082644)(3025.5,119.03057438016529)(3267.5,152.87779338842975)(3509.5,187.68713223140495)(3751.5,223.38856198347108)(3993.5,259.89136776859505)(4235.5,297.26910743801653)(4477.5,335.72614049586775)(4719.5,375.26788429752065)(4961.5,415.86328512396693)(5203.5,457.628826446281)(5445.5,500.5764338842975)(5687.5,545.049520661157)(5929.5,591.5783884297521)(6171.5,640.2639297520661)(6413.5,691.3767644628099)(6655.5,745.3044504132231)(6897.5,802.9776611570248)(7139.5,864.1297355371901)(7381.5,927.3781404958678)(7623.5,992.0037809917355)(7865.5,1057.7867685950412)(8107.5,1124.6315123966942)(8349.5,1192.5747231404957)(8591.5,1261.5780537190083)(8833.5,1331.6086074380164)(9075.5,1402.7028347107437)(9317.5,1474.9072066115702)(9559.5,1548.5075041322314)(9801.5,1623.6399090909092)(10043.5,1700.4721859504132)(10285.5,1779.2844545454545)(10527.5,1860.0937727272726)(10769.5,1942.9279256198347)(11011.5,2027.9387975206612)(11253.5,2115.4554380165287)(11495.5,2205.679305785124)(11737.5,2299.044983471075)(11979.5,2395.7380041322313)(12221.5,2495.453338842975)(12463.5,2597.9617561983473)(12705.5,2703.040876033058)(12947.5,2811.046743801653)(13189.5,2922.233561983471)(13431.5,3036.8190743801656)(13673.5,3155.0550041322313)(13915.5,3277.2954958677688)(14157.5,3404.018123966942)(14399.5,3535.343376033058)(14641.5,3671.3976983471075)(14883.5,3811.849888429752)(15125.5,3957.2713512396695)(15367.5,4108.5858181818185)(15609.5,4266.528115702479)(15851.5,4431.535669421488)(16093.5,4604.015574380165)(16335.5,4785.366219008264)(16577.5,4975.805739669422)(16819.5,5176.19655785124)(17061.5,5387.800747933884)(17303.5,5612.16417768595)(17545.5,5849.1159669421495)(17787.5,6099.078747933884)(18029.5,6365.81873553719)(18271.5,6652.1750991735535)(18513.5,6961.59579338843)(18755.5,7294.319004132231)(18997.5,7654.666690082645)(19239.5,8048.816743801653)(19481.5,8482.50705785124)(19723.5,8960.417227272726)(19965.5,9492.69403305785)(20207.5,10088.572396694215)(20449.5,10753.385491735537)(20691.5,11507.436082644628)(20933.5,12350.568033057853)(21175.5,13286.226838842975)(21417.5,14340.296863636364)(21659.5,15565.351520661157)(21901.5,17022.022425619834)(22143.5,18795.41270247934)(22385.5,20994.64411570248)(22627.5,23767.618681818185)(22869.5,27349.00535123967)(23111.5,32061.896181818185)(23353.5,38596.88123966942)(23595.5,48042.54463636364)(23737,55329.597317073174)(23759,56566.098)};
+\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt, dashed, dash pattern=on 4pt off 2pt] coordinates {(1,0.013)(121.5,1.7120082644628098)(363.5,5.2225)(605.5,8.8525)(847.5,12.548330578512397)(1089.5,16.480061983471074)(1331.5,20.66350826446281)(1573.5,25.187586776859504)(1815.5,30.315636363636365)(2057.5,37.034028925619836)(2299.5,47.26819421487603)(2541.5,63.143694214876035)(2783.5,87.08737190082644)(3025.5,119.03057438016529)(3267.5,152.87779338842975)(3509.5,187.68713223140495)(3751.5,223.38856198347108)(3993.5,259.89136776859505)(4235.5,297.26910743801653)(4477.5,335.72614049586775)(4719.5,375.26788429752065)(4961.5,415.86328512396693)(5203.5,457.628826446281)(5445.5,500.5764338842975)(5687.5,545.049520661157)(5929.5,591.5783884297521)(6171.5,640.2639297520661)(6413.5,691.3767644628099)(6655.5,745.3044504132231)(6897.5,802.9776611570248)(7139.5,864.1297355371901)(7381.5,927.3781404958678)(7623.5,992.0037809917355)(7865.5,1057.7867685950412)(8107.5,1124.6315123966942)(8349.5,1192.5747231404957)(8591.5,1261.5780537190083)(8833.5,1331.6086074380164)(9075.5,1402.7028347107437)(9317.5,1474.9072066115702)(9559.5,1548.5075041322314)(9801.5,1623.6399090909092)(10043.5,1700.4721859504132)(10285.5,1779.2844545454545)(10527.5,1860.0937727272726)(10769.5,1942.9279256198347)(11011.5,2027.9387975206612)(11253.5,2115.4554380165287)(11495.5,2205.679305785124)(11737.5,2299.044983471075)(11979.5,2395.7380041322313)(12221.5,2495.453338842975)(12463.5,2597.9617561983473)(12705.5,2703.040876033058)(12947.5,2811.046743801653)(13189.5,2922.233561983471)(13431.5,3036.8190743801656)(13673.5,3155.0550041322313)(13915.5,3277.2954958677688)(14157.5,3404.018123966942)(14399.5,3535.343376033058)(14641.5,3671.3976983471075)(14883.5,3811.849888429752)(15125.5,3957.2713512396695)(15367.5,4108.5858181818185)(15609.5,4266.528115702479)(15851.5,4431.535669421488)(16093.5,4604.015574380165)(16335.5,4785.366219008264)(16577.5,4975.805739669422)(16819.5,5176.19655785124)(17061.5,5387.800747933884)(17303.5,5612.16417768595)(17545.5,5849.1159669421495)(17787.5,6099.078747933884)(18029.5,6365.81873553719)(18271.5,6652.1750991735535)(18513.5,6961.59579338843)(18755.5,7294.319004132231)(18997.5,7654.666690082645)(19239.5,8048.816743801653)(19481.5,8482.50705785124)(19723.5,8960.417227272726)(19965.5,9492.69403305785)(20207.5,10088.572396694215)(20449.5,10753.385491735537)(20691.5,11507.436082644628)(20933.5,12350.568033057853)(21175.5,13286.226838842975)(21417.5,14340.296863636364)(21659.5,15565.351520661157)(21901.5,17022.022425619834)(22143.5,18795.41270247934)(22385.5,20994.64411570248)(22627.5,23767.618681818185)(22869.5,27349.00535123967)(23111.5,32061.896181818185)(23353.5,38596.88123966942)(23595.5,48042.54463636364)(23737,55329.597317073174)(23759,56566.098)};
 \addlegendentry{Z3-Trau}

### 2023-05-04 2023-1-19/figures/cactus_plot_automatark.tex
experiment done

@@
 \resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=automatark,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
-\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(44,0.1929655172413793)(131,0.619)(218,1.054)(305,1.489)(392,1.9436666666666667)(479,2.461)(566,2.983)(653,3.505)(740,4.027)(827,4.583517241379311)(914,5.192)(1001,5.801)(1088,6.410114942528736)(1175,7.067)(1262,7.763)(1349,8.460206896551725)(1436,9.213)(1523,9.996)(1610,10.779)(1697,11.58373563218391)(1784,12.45)(1871,13.32)(1958,14.19)(2045,15.101034482758621)(2132,16.058)(2219,17.015)(2306,17.972)(2393,18.96351724137931)(2480,20.007)(2567,21.051)(2654,22.095)(2741,23.170045977011494)(2828,24.3)(2915,25.431)(3002,26.564655172413794)(3089,27.758)(3176,28.976)(3263,30.194632183908045)(3350,31.466)(3437,32.771)(3524,34.076)(3611,35.40875862068965)(3698,36.799)(3785,38.19365517241379)(3872,39.648)(3959,41.127)(4046,42.64232183908046)(4133,44.208)(4220,45.8121724137931)(4307,47.46741379310345)(4394,49.182)(4481,50.93724137931035)(4568,52.758758620689655)(4655,54.645)(4742,56.59175862068965)(4829,58.61818390804598)(4916,60.734206896551726)(5003,62.95365517241379)(5090,65.28090804597701)(5177,67.70108045977013)(5264,70.23856321839081)(5351,72.88997701149425)(5438,75.67103448275863)(5525,78.58893103448275)(5612,81.6562183908046)(5699,84.874)(5786,88.2651724137931)(5873,91.82601149425287)(5960,95.5585172413793)(6047,99.47231034482758)(6134,103.54482758620689)(6221,107.8031724137931)(6308,112.31964367816093)(6395,117.07937931034482)(6482,122.072091954023)(6569,127.33118390804597)(6656,132.8960804597701)(6743,138.7530804597701)(6830,144.9270459770115)(6917,151.4784712643678)(7004,158.41937931034485)(7091,165.80327586206894)(7178,173.69822988505746)(7265,182.17563218390805)(7352,191.24119540229884)(7439,201.0427931034483)(7526,211.73466666666667)(7613,223.59497701149425)(7700,236.8307471264368)(7787,252.0250344827586)(7874,270.1710804597701)(7961,293.053816091954)(8048,322.6413333333333)(8135,362.7002988505747)(8222,425.82054022988507)(8309,535.5033103448276)(8396,770.6830344827586)(8478.5,1487.735076923077)(8519,2580.115)};
+\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt,dashed, dash pattern=on 2pt off 8pt] coordinates {(1,0.004)(44,0.1929655172413793)(131,0.619)(218,1.054)(305,1.489)(392,1.9436666666666667)(479,2.461)(566,2.983)(653,3.505)(740,4.027)(827,4.583517241379311)(914,5.192)(1001,5.801)(1088,6.410114942528736)(1175,7.067)(1262,7.763)(1349,8.460206896551725)(1436,9.213)(1523,9.996)(1610,10.779)(1697,11.58373563218391)(1784,12.45)(1871,13.32)(1958,14.19)(2045,15.101034482758621)(2132,16.058)(2219,17.015)(2306,17.972)(2393,18.96351724137931)(2480,20.007)(2567,21.051)(2654,22.095)(2741,23.170045977011494)(2828,24.3)(2915,25.431)(3002,26.564655172413794)(3089,27.758)(3176,28.976)(3263,30.194632183908045)(3350,31.466)(3437,32.771)(3524,34.076)(3611,35.40875862068965)(3698,36.799)(3785,38.19365517241379)(3872,39.648)(3959,41.127)(4046,42.64232183908046)(4133,44.208)(4220,45.8121724137931)(4307,47.46741379310345)(4394,49.182)(4481,50.93724137931035)(4568,52.758758620689655)(4655,54.645)(4742,56.59175862068965)(4829,58.61818390804598)(4916,60.734206896551726)(5003,62.95365517241379)(5090,65.28090804597701)(5177,67.70108045977013)(5264,70.23856321839081)(5351,72.88997701149425)(5438,75.67103448275863)(5525,78.58893103448275)(5612,81.6562183908046)(5699,84.874)(5786,88.2651724137931)(5873,91.82601149425287)(5960,95.5585172413793)(6047,99.47231034482758)(6134,103.54482758620689)(6221,107.8031724137931)(6308,112.31964367816093)(6395,117.07937931034482)(6482,122.072091954023)(6569,127.33118390804597)(6656,132.8960804597701)(6743,138.7530804597701)(6830,144.9270459770115)(6917,151.4784712643678)(7004,158.41937931034485)(7091,165.80327586206894)(7178,173.69822988505746)(7265,182.17563218390805)(7352,191.24119540229884)(7439,201.0427931034483)(7526,211.73466666666667)(7613,223.59497701149425)(7700,236.8307471264368)(7787,252.0250344827586)(7874,270.1710804597701)(7961,293.053816091954)(8048,322.6413333333333)(8135,362.7002988505747)(8222,425.82054022988507)(8309,535.5033103448276)(8396,770.6830344827586)(8478.5,1487.735076923077)(8519,2580.115)};
 \addlegendentry{CVC5}
 
-\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.001)(44.5,49.77588636363636)(132.5,153.98013636363635)(220.5,262.1894545454545)(308.5,372.31238636363634)(396.5,483.76913636363633)(484.5,596.3042386363636)(572.5,709.8801022727273)(660.5,824.4665795454546)(748.5,940.0296818181818)(836.5,1056.4871704545453)(924.5,1173.8087727272728)(1012.5,1291.9674659090908)(1100.5,1410.8886590909092)(1188.5,1530.5722159090908)(1276.5,1651.1055568181819)(1364.5,1772.5285454545453)(1452.5,1894.8319431818181)(1540.5,2018.1299886363636)(1628.5,2142.4604431818184)(1716.5,2267.7058636363636)(1804.5,2393.9053636363637)(1892.5,2521.1623863636364)(1980.5,2649.336715909091)(2068.5,2778.3925568181817)(2156.5,2908.361522727273)(2244.5,3039.2929886363636)(2332.5,3171.2455681818183)(2420.5,3304.1568181818184)(2508.5,3437.978727272727)(2596.5,3572.7547045454544)(2684.5,3708.3190795454548)(2772.5,3844.8086704545453)(2860.5,3982.276659090909)(2948.5,4120.705352272727)(3036.5,4260.052625)(3124.5,4400.310102272728)(3212.5,4541.485136363637)(3300.5,4683.616443181819)(3388.5,4826.598465909091)(3476.5,4970.501204545454)(3564.5,5115.386761363637)(3652.5,5261.080522727272)(3740.5,5407.658522727273)(3828.5,5555.073136363637)(3916.5,5703.36828409091)(4004.5,5852.564125)(4092.5,6002.664488636363)(4180.5,6153.749011363637)(4268.5,6305.792931818181)(4356.5,6458.7932045454545)(4444.5,6612.791284090909)(4532.5,6767.785272727272)(4620.5,6923.865602272727)(4708.5,7081.039670454546)(4796.5,7239.417079545454)(4884.5,7399.086931818181)(4972.5,7560.03825)(5060.5,7722.204431818182)(5148.5,7885.649727272727)(5236.5,8050.295590909091)(5324.5,8216.39771590909)(5412.5,8384.032886363637)(5500.5,8553.316522727273)(5588.5,8724.139943181819)(5676.5,8896.458170454545)(5764.5,9070.357636363637)(5852.5,9245.943272727274)(5940.5,9423.107818181817)(6028.5,9602.053295454545)(6116.5,9782.941011363637)(6204.5,9965.751875)(6292.5,10150.460022727273)(6380.5,10337.203965909091)(6468.5,10525.924090909091)(6556.5,10717.150215909092)(6644.5,10910.920056818182)(6732.5,11107.200715909092)(6820.5,11306.398920454545)(6908.5,11508.439136363637)(6996.5,11713.935943181817)(7084.5,11923.624)(7172.5,12136.768875)(7260.5,12353.715988636362)(7348.5,12574.161954545456)(7436.5,12798.799136363637)(7524.5,13029.105806818181)(7612.5,13264.319659090908)(7700.5,13505.580909090908)(7788.5,13753.832738636364)(7876.5,14009.777022727274)(7964.5,14275.649375)(8052.5,14554.259579545454)(8140.5,14849.837511363638)(8228.5,15168.880022727273)(8316.5,15522.201875)(8404.5,15935.410215909093)(8492.5,16507.840431818182)(8580.5,17813.824431818182)(8631,19480.083)(8639,19878.963)};
+\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.001)(44.5,49.77588636363636)(132.5,153.98013636363635)(220.5,262.1894545454545)(308.5,372.31238636363634)(396.5,483.76913636363633)(484.5,596.3042386363636)(572.5,709.8801022727273)(660.5,824.4665795454546)(748.5,940.0296818181818)(836.5,1056.4871704545453)(924.5,1173.8087727272728)(1012.5,1291.9674659090908)(1100.5,1410.8886590909092)(1188.5,1530.5722159090908)(1276.5,1651.1055568181819)(1364.5,1772.5285454545453)(1452.5,1894.8319431818181)(1540.5,2018.1299886363636)(1628.5,2142.4604431818184)(1716.5,2267.7058636363636)(1804.5,2393.9053636363637)(1892.5,2521.1623863636364)(1980.5,2649.336715909091)(2068.5,2778.3925568181817)(2156.5,2908.361522727273)(2244.5,3039.2929886363636)(2332.5,3171.2455681818183)(2420.5,3304.1568181818184)(2508.5,3437.978727272727)(2596.5,3572.7547045454544)(2684.5,3708.3190795454548)(2772.5,3844.8086704545453)(2860.5,3982.276659090909)(2948.5,4120.705352272727)(3036.5,4260.052625)(3124.5,4400.310102272728)(3212.5,4541.485136363637)(3300.5,4683.616443181819)(3388.5,4826.598465909091)(3476.5,4970.501204545454)(3564.5,5115.386761363637)(3652.5,5261.080522727272)(3740.5,5407.658522727273)(3828.5,5555.073136363637)(3916.5,5703.36828409091)(4004.5,5852.564125)(4092.5,6002.664488636363)(4180.5,6153.749011363637)(4268.5,6305.792931818181)(4356.5,6458.7932045454545)(4444.5,6612.791284090909)(4532.5,6767.785272727272)(4620.5,6923.865602272727)(4708.5,7081.039670454546)(4796.5,7239.417079545454)(4884.5,7399.086931818181)(4972.5,7560.03825)(5060.5,7722.204431818182)(5148.5,7885.649727272727)(5236.5,8050.295590909091)(5324.5,8216.39771590909)(5412.5,8384.032886363637)(5500.5,8553.316522727273)(5588.5,8724.139943181819)(5676.5,8896.458170454545)(5764.5,9070.357636363637)(5852.5,9245.943272727274)(5940.5,9423.107818181817)(6028.5,9602.053295454545)(6116.5,9782.941011363637)(6204.5,9965.751875)(6292.5,10150.460022727273)(6380.5,10337.203965909091)(6468.5,10525.924090909091)(6556.5,10717.150215909092)(6644.5,10910.920056818182)(6732.5,11107.200715909092)(6820.5,11306.398920454545)(6908.5,11508.439136363637)(6996.5,11713.935943181817)(7084.5,11923.624)(7172.5,12136.768875)(7260.5,12353.715988636362)(7348.5,12574.161954545456)(7436.5,12798.799136363637)(7524.5,13029.105806818181)(7612.5,13264.319659090908)(7700.5,13505.580909090908)(7788.5,13753.832738636364)(7876.5,14009.777022727274)(7964.5,14275.649375)(8052.5,14554.259579545454)(8140.5,14849.837511363638)(8228.5,15168.880022727273)(8316.5,15522.201875)(8404.5,15935.410215909093)(8492.5,16507.840431818182)(8580.5,17813.824431818182)(8631,19480.083)(8639,19878.963)};
 \addlegendentry{OstrichCEA}
 
-\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.966)(45,51.629651685393256)(134,158.67904494382023)(223,269.89732584269666)(312,383.6197528089888)(401,499.6783033707865)(490,617.7793258426966)(579,737.6599775280899)(668,858.9771348314606)(757,981.355786516854)(846,1104.57902247191)(935,1228.659370786517)(1024,1353.5784606741574)(1113,1479.340449438202)(1202,1605.8423483146069)(1291,1732.994393258427)(1380,1860.7982471910111)(1469,1989.2398764044942)(1558,2118.2535730337077)(1647,2247.769235955056)(1736,2377.8024382022472)(1825,2508.35204494382)(1914,2639.348359550562)(2003,2770.839404494382)(2092,2902.8377078651683)(2181,3035.319370786517)(2270,3168.2678876404493)(2359,3301.7290674157307)(2448,3435.6920898876406)(2537,3570.1292921348318)(2626,3705.1524606741573)(2715,3840.691617977528)(2804,3976.759415730337)(2893,4113.360764044944)(2982,4250.445494382023)(3071,4388.062044943821)(3160,4526.229382022472)(3249,4664.950314606742)(3338,4804.172505617978)(3427,4943.860483146068)(3516,5084.05806741573)(3605,5224.723202247191)(3694,5365.906865168539)(3783,5507.576955056179)(3872,5649.704640449439)(3961,5792.306471910112)(4050,5935.380764044944)(4139,6078.9809550561795)(4228,6223.057966292135)(4317,6367.639449438202)(4406,6512.755247191011)(4495,6658.350494382023)(4584,6804.486224719101)(4673,6951.171146067415)(4762,7098.355382022472)(4851,7246.019595505618)(4940,7394.190629213483)(5029,7542.908370786517)(5118,7692.217370786517)(5207,7842.0449101123595)(5296,7992.411258426966)(5385,8143.2914269662915)(5474,8294.690213483147)(5563,8446.689786516854)(5652,8599.329584269663)(5741,8752.537707865169)(5830,8906.401494382022)(5919,9060.95129213483)(6008,9216.186011235954)(6097,9372.039516853933)(6186,9528.586505617977)(6275,9685.89011235955)(6364,9843.871674157303)(6453,10002.450629213485)(6542,10161.815808988766)(6631,10321.953292134831)(6720,10482.887561797754)(6809,10644.69070786517)(6898,10807.32670786517)(6987,10970.82293258427)(7076,11135.298629213485)(7165,11300.878033707864)(7254,11467.537505617978)(7343,11635.502033707864)(7432,11804.723314606741)(7521,11975.318898876405)(7610,12147.362651685393)(7699,12320.866617977528)(7788,12495.943325842698)(7877,12672.84586516854)(7966,12851.813775280898)(8055,13033.299011235955)(8144,13217.471460674158)(8233,13405.040426966292)(8322,13597.334921348314)(8411,13797.202966292136)(8500,14006.997168539327)(8589,14242.676)(8663.5,14719.4016)(8695,15616.104)};
+\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,0.966)(45,51.629651685393256)(134,158.67904494382023)(223,269.89732584269666)(312,383.6197528089888)(401,499.6783033707865)(490,617.7793258426966)(579,737.6599775280899)(668,858.9771348314606)(757,981.355786516854)(846,1104.57902247191)(935,1228.659370786517)(1024,1353.5784606741574)(1113,1479.340449438202)(1202,1605.8423483146069)(1291,1732.994393258427)(1380,1860.7982471910111)(1469,1989.2398764044942)(1558,2118.2535730337077)(1647,2247.769235955056)(1736,2377.8024382022472)(1825,2508.35204494382)(1914,2639.348359550562)(2003,2770.839404494382)(2092,2902.8377078651683)(2181,3035.319370786517)(2270,3168.2678876404493)(2359,3301.7290674157307)(2448,3435.6920898876406)(2537,3570.1292921348318)(2626,3705.1524606741573)(2715,3840.691617977528)(2804,3976.759415730337)(2893,4113.360764044944)(2982,4250.445494382023)(3071,4388.062044943821)(3160,4526.229382022472)(3249,4664.950314606742)(3338,4804.172505617978)(3427,4943.860483146068)(3516,5084.05806741573)(3605,5224.723202247191)(3694,5365.906865168539)(3783,5507.576955056179)(3872,5649.704640449439)(3961,5792.306471910112)(4050,5935.380764044944)(4139,6078.9809550561795)(4228,6223.057966292135)(4317,6367.639449438202)(4406,6512.755247191011)(4495,6658.350494382023)(4584,6804.486224719101)(4673,6951.171146067415)(4762,7098.355382022472)(4851,7246.019595505618)(4940,7394.190629213483)(5029,7542.908370786517)(5118,7692.217370786517)(5207,7842.0449101123595)(5296,7992.411258426966)(5385,8143.2914269662915)(5474,8294.690213483147)(5563,8446.689786516854)(5652,8599.329584269663)(5741,8752.537707865169)(5830,8906.401494382022)(5919,9060.95129213483)(6008,9216.186011235954)(6097,9372.039516853933)(6186,9528.586505617977)(6275,9685.89011235955)(6364,9843.871674157303)(6453,10002.450629213485)(6542,10161.815808988766)(6631,10321.953292134831)(6720,10482.887561797754)(6809,10644.69070786517)(6898,10807.32670786517)(6987,10970.82293258427)(7076,11135.298629213485)(7165,11300.878033707864)(7254,11467.537505617978)(7343,11635.502033707864)(7432,11804.723314606741)(7521,11975.318898876405)(7610,12147.362651685393)(7699,12320.866617977528)(7788,12495.943325842698)(7877,12672.84586516854)(7966,12851.813775280898)(8055,13033.299011235955)(8144,13217.471460674158)(8233,13405.040426966292)(8322,13597.334921348314)(8411,13797.202966292136)(8500,14006.997168539327)(8589,14242.676)(8663.5,14719.4016)(8695,15616.104)};
 \addlegendentry{Ostrich}
 
-\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.011)(28,0.34405454545454545)(83,1.004)(138,1.664)(193,2.324)(248,2.984)(303,3.6490181818181817)(358,4.355)(413,5.07)(468,5.785)(523,6.5)(578,7.215)(633,7.93)(688,8.645)(743,9.36)(798,10.075)(853,10.79)(908,11.505)(963,12.22)(1018,12.935)(1073,13.65)(1128,14.365)(1183,15.08)(1238,15.795)(1293,16.51)(1348,17.234018181818183)(1403,17.999)(1458,18.769)(1513,19.541781818181818)(1568,20.355)(1623,21.217)(1678,22.11927272727273)(1733,23.054)(1788,24.01127272727273)(1843,25.001)(1898,25.992654545454545)(1953,27.022)(2008,28.067)(2063,29.112)(2118,30.1666)(2173,31.262)(2228,32.362)(2283,33.462)(2338,34.564781818181814)(2393,35.707)(2448,36.862)(2503,38.017)(2558,39.172)(2613,40.35205454545454)(2668,41.562)(2723,42.772)(2778,43.99618181818182)(2833,45.259)(2888,46.524)(2943,47.80865454545455)(2998,49.128)(3053,50.47210909090909)(3108,51.8482)(3163,53.26290909090909)(3218,54.7376)(3273,56.27590909090909)(3328,57.87347272727273)(3383,59.548418181818185)(3438,61.30281818181818)(3493,63.13972727272727)(3548,65.0678909090909)(3603,67.10025454545455)(3658,69.2492)(3713,71.49483636363637)(3768,73.84325454545454)(3823,76.31507272727272)(3878,78.93901818181818)(3933,81.7334909090909)(3988,84.68719999999999)(4043,87.8238)(4098,91.12774545454545)(4153,94.64658181818182)(4208,98.41867272727274)(4263,102.46365454545455)(4318,106.77592727272727)(4373,111.44936363636363)(4428,116.65296363636364)(4483,122.39274545454545)(4538,128.6556)(4593,135.70430909090908)(4648,143.72623636363636)(4703,152.72258181818182)(4758,162.99996363636362)(4813,175.10872727272726)(4868,189.50578181818182)(4923,208.60178181818182)(4978,241.16914545454546)(5033,301.7078909090909)(5088,407.2800363636364)(5143,527.1198909090908)(5198,654.8019272727272)(5253,840.1544181818182)(5308,1365.6359454545457)(5363,2537.6238)(5400.5,4036.3596000000002)(5412,4631.644)};
+\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.011)(28,0.34405454545454545)(83,1.004)(138,1.664)(193,2.324)(248,2.984)(303,3.6490181818181817)(358,4.355)(413,5.07)(468,5.785)(523,6.5)(578,7.215)(633,7.93)(688,8.645)(743,9.36)(798,10.075)(853,10.79)(908,11.505)(963,12.22)(1018,12.935)(1073,13.65)(1128,14.365)(1183,15.08)(1238,15.795)(1293,16.51)(1348,17.234018181818183)(1403,17.999)(1458,18.769)(1513,19.541781818181818)(1568,20.355)(1623,21.217)(1678,22.11927272727273)(1733,23.054)(1788,24.01127272727273)(1843,25.001)(1898,25.992654545454545)(1953,27.022)(2008,28.067)(2063,29.112)(2118,30.1666)(2173,31.262)(2228,32.362)(2283,33.462)(2338,34.564781818181814)(2393,35.707)(2448,36.862)(2503,38.017)(2558,39.172)(2613,40.35205454545454)(2668,41.562)(2723,42.772)(2778,43.99618181818182)(2833,45.259)(2888,46.524)(2943,47.80865454545455)(2998,49.128)(3053,50.47210909090909)(3108,51.8482)(3163,53.26290909090909)(3218,54.7376)(3273,56.27590909090909)(3328,57.87347272727273)(3383,59.548418181818185)(3438,61.30281818181818)(3493,63.13972727272727)(3548,65.0678909090909)(3603,67.10025454545455)(3658,69.2492)(3713,71.49483636363637)(3768,73.84325454545454)(3823,76.31507272727272)(3878,78.93901818181818)(3933,81.7334909090909)(3988,84.68719999999999)(4043,87.8238)(4098,91.12774545454545)(4153,94.64658181818182)(4208,98.41867272727274)(4263,102.46365454545455)(4318,106.77592727272727)(4373,111.44936363636363)(4428,116.65296363636364)(4483,122.39274545454545)(4538,128.6556)(4593,135.70430909090908)(4648,143.72623636363636)(4703,152.72258181818182)(4758,162.99996363636362)(4813,175.10872727272726)(4868,189.50578181818182)(4923,208.60178181818182)(4978,241.16914545454546)(5033,301.7078909090909)(5088,407.2800363636364)(5143,527.1198909090908)(5198,654.8019272727272)(5253,840.1544181818182)(5308,1365.6359454545457)(5363,2537.6238)(5400.5,4036.3596000000002)(5412,4631.644)};
 \addlegendentry{Z3str3}
 
-\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.012)(44,0.5610344827586207)(131,1.688)(218,2.819)(305,3.95)(392,5.081)(479,6.212)(566,7.343)(653,8.474)(740,9.605)(827,10.736)(914,11.867)(1001,13.03806896551724)(1088,14.256)(1175,15.474)(1262,16.692)(1349,17.91)(1436,19.128)(1523,20.360655172413793)(1610,21.658)(1697,22.963)(1784,24.28096551724138)(1871,25.664)(1958,27.056)(2045,28.463241379310343)(2132,29.935)(2219,31.414)(2306,32.8931724137931)(2393,34.421)(2480,35.987)(2567,37.553)(2654,39.13308045977011)(2741,40.778)(2828,42.431)(2915,44.084)(3002,45.78)(3089,47.52)(3176,49.26)(3263,51.02618390804598)(3350,52.851)(3437,54.678)(3524,56.54132183908046)(3611,58.455)(3698,60.38365517241379)(3785,62.377)(3872,64.40044827586208)(3959,66.485)(4046,68.61403448275863)(4133,70.79366666666667)(4220,73.036)(4307,75.34001149425288)(4394,77.72368965517242)(4481,80.208)(4568,82.774)(4655,85.4200459770115)(4742,88.19042528735632)(4829,91.09298850574713)(4916,94.14202298850574)(5003,97.34010344827585)(5090,100.71949425287357)(5177,104.2736551724138)(5264,108.0643908045977)(5351,112.12058620689655)(5438,116.49328735632184)(5525,121.25075862068965)(5612,126.37032183908046)(5699,131.87488505747126)(5786,137.83209195402299)(5873,144.3935747126437)(5960,151.6332528735632)(6047,159.56349425287357)(6134,168.32394252873564)(6221,178.00933333333333)(6308,188.61080459770116)(6395,200.22363218390805)(6482,213.0765632183908)(6569,227.277816091954)(6656,243.0501379310345)(6743,260.7920344827586)(6830,280.4905517241379)(6917,302.7097586206897)(7004,327.5999540229885)(7091,355.8960229885057)(7178,388.3605862068966)(7265,425.57027586206897)(7352,467.78589655172414)(7439,515.8811034482759)(7526,572.8783908045978)(7613,640.500264367816)(7700,721.5446551724137)(7787,819.6228965517241)(7874,943.8886896551724)(7961,1102.410471264368)(8048,1306.6646551724136)(8135,1592.898448275862)(8222,2000.9801264367816)(8309,2632.139011494253)(8396,3684.789195402299)(8483,5632.933747126437)(8528.5,7474.12825)(8532,7620.921)};
+\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1.5pt off 2pt] coordinates {(1,0.012)(44,0.5610344827586207)(131,1.688)(218,2.819)(305,3.95)(392,5.081)(479,6.212)(566,7.343)(653,8.474)(740,9.605)(827,10.736)(914,11.867)(1001,13.03806896551724)(1088,14.256)(1175,15.474)(1262,16.692)(1349,17.91)(1436,19.128)(1523,20.360655172413793)(1610,21.658)(1697,22.963)(1784,24.28096551724138)(1871,25.664)(1958,27.056)(2045,28.463241379310343)(2132,29.935)(2219,31.414)(2306,32.8931724137931)(2393,34.421)(2480,35.987)(2567,37.553)(2654,39.13308045977011)(2741,40.778)(2828,42.431)(2915,44.084)(3002,45.78)(3089,47.52)(3176,49.26)(3263,51.02618390804598)(3350,52.851)(3437,54.678)(3524,56.54132183908046)(3611,58.455)(3698,60.38365517241379)(3785,62.377)(3872,64.40044827586208)(3959,66.485)(4046,68.61403448275863)(4133,70.79366666666667)(4220,73.036)(4307,75.34001149425288)(4394,77.72368965517242)(4481,80.208)(4568,82.774)(4655,85.4200459770115)(4742,88.19042528735632)(4829,91.09298850574713)(4916,94.14202298850574)(5003,97.34010344827585)(5090,100.71949425287357)(5177,104.2736551724138)(5264,108.0643908045977)(5351,112.12058620689655)(5438,116.49328735632184)(5525,121.25075862068965)(5612,126.37032183908046)(5699,131.87488505747126)(5786,137.83209195402299)(5873,144.3935747126437)(5960,151.6332528735632)(6047,159.56349425287357)(6134,168.32394252873564)(6221,178.00933333333333)(6308,188.61080459770116)(6395,200.22363218390805)(6482,213.0765632183908)(6569,227.277816091954)(6656,243.0501379310345)(6743,260.7920344827586)(6830,280.4905517241379)(6917,302.7097586206897)(7004,327.5999540229885)(7091,355.8960229885057)(7178,388.3605862068966)(7265,425.57027586206897)(7352,467.78589655172414)(7439,515.8811034482759)(7526,572.8783908045978)(7613,640.500264367816)(7700,721.5446551724137)(7787,819.6228965517241)(7874,943.8886896551724)(7961,1102.410471264368)(8048,1306.6646551724136)(8135,1592.898448275862)(8222,2000.9801264367816)(8309,2632.139011494253)(8396,3684.789195402299)(8483,5632.933747126437)(8528.5,7474.12825)(8532,7620.921)};
 \addlegendentry{Z3seq}
 
-\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.004)(45,0.1892247191011236)(134,0.615)(223,1.06)(312,1.505)(401,1.95)(490,2.395)(579,2.84)(668,3.285)(757,3.73)(846,4.175)(935,4.62)(1024,5.071303370786517)(1113,5.588)(1202,6.122)(1291,6.656)(1380,7.209224719101123)(1469,7.827)(1558,8.45)(1647,9.073)(1736,9.696)(1825,10.319)(1914,10.942)(2003,11.565)(2092,12.188)(2181,12.834370786516855)(2270,13.543)(2359,14.255)(2448,14.967)(2537,15.679)(2626,16.391)(2715,17.103)(2804,17.815)(2893,18.527)(2982,19.239)(3071,19.951)(3160,20.663)(3249,21.381685393258426)(3338,22.166)(3427,22.967)(3516,23.768)(3605,24.569)(3694,25.37)(3783,26.171)(3872,26.972)(3961,27.773)(4050,28.574)(4139,29.375)(4228,30.181932584269664)(4317,31.054)(4406,31.944)(4495,32.834)(4584,33.724)(4673,34.614)(4762,35.504)(4851,36.394)(4940,37.29030337078652)(5029,38.252)(5118,39.231)(5207,40.21)(5296,41.189)(5385,42.1703595505618)(5474,43.212)(5563,44.28)(5652,45.348)(5741,46.41661797752809)(5830,47.539)(5919,48.696)(6008,49.853)(6097,51.045505617977526)(6186,52.291)(6275,53.542932584269664)(6364,54.86)(6453,56.19924719101124)(6542,57.602)(6631,59.045887640449436)(6720,60.55431460674157)(6809,62.11923595505618)(6898,63.772)(6987,65.50240449438202)(7076,67.33822471910112)(7165,69.29493258426966)(7254,71.38649438202248)(7343,73.63291011235955)(7432,76.06348314606741)(7521,78.76337078651686)(7610,81.7866179775281)(7699,85.20116853932583)(7788,89.14226966292135)(7877,93.84008988764046)(7966,99.66762921348314)(8055,106.92501123595505)(8144,116.53524719101124)(8233,130.10767415730336)(8322,150.67694382022472)(8411,185.7845842696629)(8500,252.37134831460673)(8589,453.2947752808989)(8655.5,1213.1201363636364)(8679,2048.545)};
+\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt, dashed, dash pattern=on 2pt off 4pt] coordinates {(1,0.004)(45,0.1892247191011236)(134,0.615)(223,1.06)(312,1.505)(401,1.95)(490,2.395)(579,2.84)(668,3.285)(757,3.73)(846,4.175)(935,4.62)(1024,5.071303370786517)(1113,5.588)(1202,6.122)(1291,6.656)(1380,7.209224719101123)(1469,7.827)(1558,8.45)(1647,9.073)(1736,9.696)(1825,10.319)(1914,10.942)(2003,11.565)(2092,12.188)(2181,12.834370786516855)(2270,13.543)(2359,14.255)(2448,14.967)(2537,15.679)(2626,16.391)(2715,17.103)(2804,17.815)(2893,18.527)(2982,19.239)(3071,19.951)(3160,20.663)(3249,21.381685393258426)(3338,22.166)(3427,22.967)(3516,23.768)(3605,24.569)(3694,25.37)(3783,26.171)(3872,26.972)(3961,27.773)(4050,28.574)(4139,29.375)(4228,30.181932584269664)(4317,31.054)(4406,31.944)(4495,32.834)(4584,33.724)(4673,34.614)(4762,35.504)(4851,36.394)(4940,37.29030337078652)(5029,38.252)(5118,39.231)(5207,40.21)(5296,41.189)(5385,42.1703595505618)(5474,43.212)(5563,44.28)(5652,45.348)(5741,46.41661797752809)(5830,47.539)(5919,48.696)(6008,49.853)(6097,51.045505617977526)(6186,52.291)(6275,53.542932584269664)(6364,54.86)(6453,56.19924719101124)(6542,57.602)(6631,59.045887640449436)(6720,60.55431460674157)(6809,62.11923595505618)(6898,63.772)(6987,65.50240449438202)(7076,67.33822471910112)(7165,69.29493258426966)(7254,71.38649438202248)(7343,73.63291011235955)(7432,76.06348314606741)(7521,78.76337078651686)(7610,81.7866179775281)(7699,85.20116853932583)(7788,89.14226966292135)(7877,93.84008988764046)(7966,99.66762921348314)(8055,106.92501123595505)(8144,116.53524719101124)(8233,130.10767415730336)(8322,150.67694382022472)(8411,185.7845842696629)(8500,252.37134831460673)(8589,453.2947752808989)(8655.5,1213.1201363636364)(8679,2048.545)};
 \addlegendentry{Z3str3RE}
 
-\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.014)(20.5,0.32530000000000003)(60.5,0.961)(100.5,1.601)(140.5,2.259525)(180.5,2.9395)(220.5,3.6195)(260.5,4.2995)(300.5,4.9795)(340.5,5.677074999999999)(380.5,6.397)(420.5,7.117)(460.5,7.837375)(500.5,8.5825)(540.5,9.3425)(580.5,10.1025)(620.5,10.86725)(660.5,11.662)(700.5,12.46365)(740.5,13.2935)(780.5,14.147525)(820.5,15.038625)(860.5,15.975775)(900.5,16.968275000000002)(940.5,18.01415)(980.5,19.11675)(1020.5,20.294700000000002)(1060.5,21.557875)(1100.5,22.9257)(1140.5,24.40535)(1180.5,26.00135)(1220.5,27.721275000000002)(1260.5,29.585775)(1300.5,31.62705)(1340.5,33.848675)(1380.5,36.232575)(1420.5,38.778974999999996)(1460.5,41.503525)(1500.5,44.394324999999995)(1540.5,47.462050000000005)(1580.5,50.750025)(1620.5,54.262875)(1660.5,58.105625)(1700.5,62.247775000000004)(1740.5,66.659425)(1780.5,71.44305)(1820.5,76.593825)(1860.5,82.178)(1900.5,88.251)(1940.5,94.871325)(1980.5,102.07889999999999)(2020.5,110.022225)(2060.5,118.74025)(2100.5,128.321775)(2140.5,138.75495)(2180.5,149.990875)(2220.5,162.040425)(2260.5,174.9545)(2300.5,188.80342499999998)(2340.5,203.825675)(2380.5,220.271825)(2420.5,238.0997)(2460.5,257.46645)(2500.5,278.476375)(2540.5,301.07705)(2580.5,325.38465)(2620.5,351.73775)(2660.5,380.3615)(2700.5,411.6698)(2740.5,446.16547499999996)(2780.5,484.531075)(2820.5,527.1384)(2860.5,574.245875)(2900.5,625.3648499999999)(2940.5,680.9376500000001)(2980.5,743.98175)(3020.5,817.6037)(3060.5,900.421375)(3100.5,991.74745)(3140.5,1092.250625)(3180.5,1203.1501)(3220.5,1326.906925)(3260.5,1463.5923500000001)(3300.5,1614.2668)(3340.5,1781.566325)(3380.5,1976.8985500000001)(3420.5,2205.8372999999997)(3460.5,2468.497475)(3500.5,2786.5406749999997)(3540.5,3160.2475)(3580.5,3582.4527749999997)(3620.5,4085.978125)(3660.5,4674.079625)(3700.5,5342.3874000000005)(3740.5,6120.993974999999)(3780.5,7068.202275000001)(3820.5,8261.846725)(3860.5,9710.5938)(3900.5,11480.593425000001)(3935,13291.69527586207)(3951,14160.091)};
+\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt, dashed, dash pattern=on 4pt off 2pt] coordinates {(1,0.014)(20.5,0.32530000000000003)(60.5,0.961)(100.5,1.601)(140.5,2.259525)(180.5,2.9395)(220.5,3.6195)(260.5,4.2995)(300.5,4.9795)(340.5,5.677074999999999)(380.5,6.397)(420.5,7.117)(460.5,7.837375)(500.5,8.5825)(540.5,9.3425)(580.5,10.1025)(620.5,10.86725)(660.5,11.662)(700.5,12.46365)(740.5,13.2935)(780.5,14.147525)(820.5,15.038625)(860.5,15.975775)(900.5,16.968275000000002)(940.5,18.01415)(980.5,19.11675)(1020.5,20.294700000000002)(1060.5,21.557875)(1100.5,22.9257)(1140.5,24.40535)(1180.5,26.00135)(1220.5,27.721275000000002)(1260.5,29.585775)(1300.5,31.62705)(1340.5,33.848675)(1380.5,36.232575)(1420.5,38.778974999999996)(1460.5,41.503525)(1500.5,44.394324999999995)(1540.5,47.462050000000005)(1580.5,50.750025)(1620.5,54.262875)(1660.5,58.105625)(1700.5,62.247775000000004)(1740.5,66.659425)(1780.5,71.44305)(1820.5,76.593825)(1860.5,82.178)(1900.5,88.251)(1940.5,94.871325)(1980.5,102.07889999999999)(2020.5,110.022225)(2060.5,118.74025)(2100.5,128.321775)(2140.5,138.75495)(2180.5,149.990875)(2220.5,162.040425)(2260.5,174.9545)(2300.5,188.80342499999998)(2340.5,203.825675)(2380.5,220.271825)(2420.5,238.0997)(2460.5,257.46645)(2500.5,278.476375)(2540.5,301.07705)(2580.5,325.38465)(2620.5,351.73775)(2660.5,380.3615)(2700.5,411.6698)(2740.5,446.16547499999996)(2780.5,484.531075)(2820.5,527.1384)(2860.5,574.245875)(2900.5,625.3648499999999)(2940.5,680.9376500000001)(2980.5,743.98175)(3020.5,817.6037)(3060.5,900.421375)(3100.5,991.74745)(3140.5,1092.250625)(3180.5,1203.1501)(3220.5,1326.906925)(3260.5,1463.5923500000001)(3300.5,1614.2668)(3340.5,1781.566325)(3380.5,1976.8985500000001)(3420.5,2205.8372999999997)(3460.5,2468.497475)(3500.5,2786.5406749999997)(3540.5,3160.2475)(3580.5,3582.4527749999997)(3620.5,4085.978125)(3660.5,4674.079625)(3700.5,5342.3874000000005)(3740.5,6120.993974999999)(3780.5,7068.202275000001)(3820.5,8261.846725)(3860.5,9710.5938)(3900.5,11480.593425000001)(3935,13291.69527586207)(3951,14160.091)};
 \addlegendentry{Z3-Trau}

### 2023-05-04 2023-1-19/figures/cactus_plot_heuristic.tex
experiment done

@@
 \begin{document}
-\definecolor{colourOstrichCEA}{HTML}{25333D}
-\definecolor{colourUnder Approximation off}{HTML}{0065AB}
+\definecolor{colourOstrichCEA}{HTML}{0065AB}
+\definecolor{colourUnder Approximation off}{HTML}{25333D}
 \definecolor{colourSimplification off}{HTML}{8939AD}
@@
 \resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=Total,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
-\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.256)(251,375.73549500998007)(752,1183.8739021956087)(1253,2022.618491017964)(1754,2877.9200359281435)(2255,3746.0393033932137)(2756,4625.084281437126)(3257,5513.779463073853)(3758,6411.872730538922)(4259,7319.427289421158)(4760,8236.114157684631)(5261,9161.532343313374)(5762,10096.144241516966)(6263,11040.38131736527)(6764,11994.772165668663)(7265,12960.379053892215)(7766,13938.16142714571)(8267,14928.978754491018)(8768,15934.640826347304)(9269,16955.70472255489)(9770,17992.700299401196)(10271,19044.441936127743)(10772,20110.456696606787)(11273,21189.18998203593)(11774,22279.62379241517)(12275,23380.84084031936)(12776,24491.869590818365)(13277,25612.71845309381)(13778,26743.928768463076)(14279,27885.323826347307)(14780,29035.924956087823)(15281,30195.091335329344)(15782,31363.01940518962)(16283,32539.236013972055)(16784,33723.31988023953)(17285,34915.447836327345)(17786,36114.84655888224)(18287,37321.58146307385)(18788,38535.701952095806)(19289,39756.911600798405)(19790,40985.1631017964)(20291,42220.45616367266)(20792,43462.636586826346)(21293,44711.67520558883)(21794,45967.50069461078)(22295,47230.13759281437)(22796,48499.66564471058)(23297,49776.35208782435)(23798,51060.01192814371)(24299,52350.822175648704)(24800,53648.5965748503)(25301,54953.18310379241)(25802,56264.57108582834)(26303,57583.00460678643)(26804,58908.59252295409)(27305,60241.239854291416)(27806,61581.528387225546)(28307,62929.616544910175)(28808,64285.927918163674)(29309,65650.71985229541)(29810,67024.12507584831)(30311,68406.55969061877)(30812,69797.76003592815)(31313,71197.73274650698)(31814,72607.24381437126)(32315,74026.60229740519)(32816,75455.86899201597)(33317,76895.86807984032)(33818,78346.82771656686)(34319,79809.24070259482)(34820,81283.33454291416)(35321,82769.59380638723)(35822,84269.10105988024)(36323,85782.33381836327)(36824,87310.26063073853)(37325,88853.80257085829)(37826,90415.16936327345)(38327,91994.438750499)(38828,93592.4894510978)(39329,95211.69484830339)(39830,96853.58521157685)(40331,98519.82530938124)(40832,100212.75770459081)(41333,101935.10099401198)(41834,103689.06698403193)(42335,105476.94833532933)(42836,107301.12517165668)(43337,109166.71543512975)(43838,111078.39904191616)(44339,113041.1118263473)(44840,115058.31930339322)(45341,117139.44398802395)(45842,119295.3597245509)(46343,121540.35781237525)(46844,123904.0013233533)(47345,126431.7289760479)(47846,129212.59415968064)(48347,132495.7146007984)(48845.5,137664.56463508063)(49095,143594.349)};
+\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.256)(251,375.73549500998007)(752,1183.8739021956087)(1253,2022.618491017964)(1754,2877.9200359281435)(2255,3746.0393033932137)(2756,4625.084281437126)(3257,5513.779463073853)(3758,6411.872730538922)(4259,7319.427289421158)(4760,8236.114157684631)(5261,9161.532343313374)(5762,10096.144241516966)(6263,11040.38131736527)(6764,11994.772165668663)(7265,12960.379053892215)(7766,13938.16142714571)(8267,14928.978754491018)(8768,15934.640826347304)(9269,16955.70472255489)(9770,17992.700299401196)(10271,19044.441936127743)(10772,20110.456696606787)(11273,21189.18998203593)(11774,22279.62379241517)(12275,23380.84084031936)(12776,24491.869590818365)(13277,25612.71845309381)(13778,26743.928768463076)(14279,27885.323826347307)(14780,29035.924956087823)(15281,30195.091335329344)(15782,31363.01940518962)(16283,32539.236013972055)(16784,33723.31988023953)(17285,34915.447836327345)(17786,36114.84655888224)(18287,37321.58146307385)(18788,38535.701952095806)(19289,39756.911600798405)(19790,40985.1631017964)(20291,42220.45616367266)(20792,43462.636586826346)(21293,44711.67520558883)(21794,45967.50069461078)(22295,47230.13759281437)(22796,48499.66564471058)(23297,49776.35208782435)(23798,51060.01192814371)(24299,52350.822175648704)(24800,53648.5965748503)(25301,54953.18310379241)(25802,56264.57108582834)(26303,57583.00460678643)(26804,58908.59252295409)(27305,60241.239854291416)(27806,61581.528387225546)(28307,62929.616544910175)(28808,64285.927918163674)(29309,65650.71985229541)(29810,67024.12507584831)(30311,68406.55969061877)(30812,69797.76003592815)(31313,71197.73274650698)(31814,72607.24381437126)(32315,74026.60229740519)(32816,75455.86899201597)(33317,76895.86807984032)(33818,78346.82771656686)(34319,79809.24070259482)(34820,81283.33454291416)(35321,82769.59380638723)(35822,84269.10105988024)(36323,85782.33381836327)(36824,87310.26063073853)(37325,88853.80257085829)(37826,90415.16936327345)(38327,91994.438750499)(38828,93592.4894510978)(39329,95211.69484830339)(39830,96853.58521157685)(40331,98519.82530938124)(40832,100212.75770459081)(41333,101935.10099401198)(41834,103689.06698403193)(42335,105476.94833532933)(42836,107301.12517165668)(43337,109166.71543512975)(43838,111078.39904191616)(44339,113041.1118263473)(44840,115058.31930339322)(45341,117139.44398802395)(45842,119295.3597245509)(46343,121540.35781237525)(46844,123904.0013233533)(47345,126431.7289760479)(47846,129212.59415968064)(48347,132495.7146007984)(48845.5,137664.56463508063)(49095,143594.349)};
 \addlegendentry{OstrichCEA}
 
-\addplot[name path=pathUnder Approximation off , colourUnder Approximation off, line width=1.5pt] coordinates {(1,1.143)(247.5,345.5671659919028)(741.5,1093.1268178137652)(1235.5,1881.7518846153846)(1729.5,2688.709206477733)(2223.5,3507.6373157894736)(2717.5,4336.697226720647)(3211.5,5174.640070850202)(3705.5,6020.75543117409)(4199.5,6875.348497975709)(4693.5,7738.697793522268)(5187.5,8610.4509048583)(5681.5,9491.439477732794)(6175.5,10383.11131174089)(6669.5,11286.058060728745)(7163.5,12201.323759109313)(7657.5,13130.214445344129)(8151.5,14072.49958097166)(8645.5,15027.589060728746)(9139.5,15993.548682186234)(9633.5,16968.388783400813)(10127.5,17950.561637651823)(10621.5,18939.66844736842)(11115.5,19935.288463562752)(11609.5,20936.991455465588)(12103.5,21944.461374493927)(12597.5,22957.267400809716)(13091.5,23975.060060728745)(13585.5,24997.827248987855)(14079.5,26025.643408906883)(14573.5,27058.369396761133)(15067.5,28095.932414979758)(15561.5,29138.35586032389)(16055.5,30185.54812145749)(16549.5,31237.71652631579)(17043.5,32294.568991902837)(17537.5,33355.85782591093)(18031.5,34421.65787044534)(18525.5,35492.13017813765)(19019.5,36567.51576923077)(19513.5,37647.78307692308)(20007.5,38732.940694331985)(20501.5,39823.37698582996)(20995.5,40919.24681983805)(21489.5,42020.08232591093)(21983.5,43125.835275303645)(22477.5,44236.932014170045)(22971.5,45353.34651214575)(23465.5,46475.20208299595)(23959.5,47602.54591700405)(24453.5,48735.58559311741)(24947.5,49873.97048987854)(25441.5,51018.06316396761)(25935.5,52167.99957287449)(26429.5,53323.73327327935)(26923.5,54485.43606882591)(27417.5,55653.25192510121)(27911.5,56827.234957489876)(28405.5,58007.57878340081)(28899.5,59194.84101619433)(29393.5,60388.59112955466)(29887.5,61589.210236842104)(30381.5,62796.74455060728)(30875.5,64011.43599797571)(31369.5,65233.93253643725)(31863.5,66464.4293805668)(32357.5,67703.53380364372)(32851.5,68951.35434008097)(33345.5,70208.14511943319)(33839.5,71474.93029149798)(34333.5,72752.14231781376)(34827.5,74040.93050404859)(35321.5,75341.12895748988)(35815.5,76653.30199190283)(36309.5,77978.19206680162)(36803.5,79316.7351194332)(37297.5,80669.18660526315)(37791.5,82036.25991902834)(38285.5,83419.48054655871)(38779.5,84819.95787651822)(39273.5,86240.30562955466)(39767.5,87682.62130364371)(40261.5,89147.46975506074)(40755.5,90638.08723481782)(41249.5,92156.34871457491)(41743.5,93704.68462348178)(42237.5,95286.82339878543)(42731.5,96907.78887246964)(43225.5,98569.67491700404)(43719.5,100277.59814979757)(44213.5,102037.28515789473)(44707.5,103855.00732388663)(45201.5,105743.83414574899)(45695.5,107719.03925101215)(46189.5,109802.37090890687)(46683.5,112039.03551214574)(47177.5,114517.45951214574)(47671.5,117550.44509311742)(48165.5,123028.84814979757)(48419.5,129605.71235714285)(48428,130033.418)};
+\addplot[name path=pathUnder Approximation off , colourUnder Approximation off, line width=1.5pt, dashed, dash pattern=on 2pt off 8pt] coordinates {(1,1.143)(247.5,345.5671659919028)(741.5,1093.1268178137652)(1235.5,1881.7518846153846)(1729.5,2688.709206477733)(2223.5,3507.6373157894736)(2717.5,4336.697226720647)(3211.5,5174.640070850202)(3705.5,6020.75543117409)(4199.5,6875.348497975709)(4693.5,7738.697793522268)(5187.5,8610.4509048583)(5681.5,9491.439477732794)(6175.5,10383.11131174089)(6669.5,11286.058060728745)(7163.5,12201.323759109313)(7657.5,13130.214445344129)(8151.5,14072.49958097166)(8645.5,15027.589060728746)(9139.5,15993.548682186234)(9633.5,16968.388783400813)(10127.5,17950.561637651823)(10621.5,18939.66844736842)(11115.5,19935.288463562752)(11609.5,20936.991455465588)(12103.5,21944.461374493927)(12597.5,22957.267400809716)(13091.5,23975.060060728745)(13585.5,24997.827248987855)(14079.5,26025.643408906883)(14573.5,27058.369396761133)(15067.5,28095.932414979758)(15561.5,29138.35586032389)(16055.5,30185.54812145749)(16549.5,31237.71652631579)(17043.5,32294.568991902837)(17537.5,33355.85782591093)(18031.5,34421.65787044534)(18525.5,35492.13017813765)(19019.5,36567.51576923077)(19513.5,37647.78307692308)(20007.5,38732.940694331985)(20501.5,39823.37698582996)(20995.5,40919.24681983805)(21489.5,42020.08232591093)(21983.5,43125.835275303645)(22477.5,44236.932014170045)(22971.5,45353.34651214575)(23465.5,46475.20208299595)(23959.5,47602.54591700405)(24453.5,48735.58559311741)(24947.5,49873.97048987854)(25441.5,51018.06316396761)(25935.5,52167.99957287449)(26429.5,53323.73327327935)(26923.5,54485.43606882591)(27417.5,55653.25192510121)(27911.5,56827.234957489876)(28405.5,58007.57878340081)(28899.5,59194.84101619433)(29393.5,60388.59112955466)(29887.5,61589.210236842104)(30381.5,62796.74455060728)(30875.5,64011.43599797571)(31369.5,65233.93253643725)(31863.5,66464.4293805668)(32357.5,67703.53380364372)(32851.5,68951.35434008097)(33345.5,70208.14511943319)(33839.5,71474.93029149798)(34333.5,72752.14231781376)(34827.5,74040.93050404859)(35321.5,75341.12895748988)(35815.5,76653.30199190283)(36309.5,77978.19206680162)(36803.5,79316.7351194332)(37297.5,80669.18660526315)(37791.5,82036.25991902834)(38285.5,83419.48054655871)(38779.5,84819.95787651822)(39273.5,86240.30562955466)(39767.5,87682.62130364371)(40261.5,89147.46975506074)(40755.5,90638.08723481782)(41249.5,92156.34871457491)(41743.5,93704.68462348178)(42237.5,95286.82339878543)(42731.5,96907.78887246964)(43225.5,98569.67491700404)(43719.5,100277.59814979757)(44213.5,102037.28515789473)(44707.5,103855.00732388663)(45201.5,105743.83414574899)(45695.5,107719.03925101215)(46189.5,109802.37090890687)(46683.5,112039.03551214574)(47177.5,114517.45951214574)(47671.5,117550.44509311742)(48165.5,123028.84814979757)(48419.5,129605.71235714285)(48428,130033.418)};
 \addlegendentry{Under Approximation off}
 
-\addplot[name path=pathSimplification off , colourSimplification off, line width=1.5pt] coordinates {(1,1.135)(246.5,363.1045792682927)(738.5,1150.2894695121952)(1230.5,1976.5712662601627)(1722.5,2827.88006097561)(2214.5,3700.4905081300813)(2706.5,4592.667786585365)(3198.5,5505.309475609756)(3690.5,6435.865410569106)(4182.5,7382.667552845528)(4674.5,8345.835542682928)(5166.5,9325.28124186992)(5658.5,10320.03525609756)(6150.5,11330.31531300813)(6642.5,12355.397339430894)(7134.5,13394.562701219513)(7626.5,14448.094024390242)(8118.5,15515.715595528456)(8610.5,16597.635471544716)(9102.5,17694.34049593496)(9594.5,18806.49131504065)(10086.5,19933.432048780487)(10578.5,21074.394237804878)(11070.5,22229.156333333332)(11562.5,23398.27930284553)(12054.5,24582.21882926829)(12546.5,25781.288851626017)(13038.5,26995.324906504065)(13530.5,28224.14231300813)(14022.5,29466.946489837395)(14514.5,30723.627083333333)(15006.5,31995.121766260163)(15498.5,33280.916351626016)(15990.5,34581.29370528455)(16482.5,35896.226640243905)(16974.5,37225.31055691057)(17466.5,38568.79462398374)(17958.5,39926.34044715447)(18450.5,41296.85248577235)(18942.5,42680.20717479674)(19434.5,44077.110611788616)(19926.5,45488.34107113821)(20418.5,46913.13556707317)(20910.5,48352.125798780486)(21402.5,49805.39538211382)(21894.5,51272.918483739835)(22386.5,52754.42153455284)(22878.5,54249.736412601625)(23370.5,55759.46517073171)(23862.5,57283.576719512195)(24354.5,58822.75940243903)(24846.5,60376.9937398374)(25338.5,61946.492164634146)(25830.5,63530.548172764225)(26322.5,65129.932030487806)(26814.5,66745.12398577236)(27306.5,68376.3347296748)(27798.5,70024.90577439025)(28290.5,71690.3053699187)(28782.5,73371.95175406504)(29274.5,75070.203699187)(29766.5,76786.4307703252)(30258.5,78521.07297357723)(30750.5,80274.46002642276)(31242.5,82047.87613211382)(31734.5,83841.58971341464)(32226.5,85655.53554268293)(32718.5,87490.54740447155)(33210.5,89347.99480691057)(33702.5,91229.68758130081)(34194.5,93135.32528455285)(34686.5,95066.21725406504)(35178.5,97024.63288211382)(35670.5,99011.55916463415)(36162.5,101029.76689634146)(36654.5,103081.27141260162)(37146.5,105168.26180081301)(37638.5,107291.90132520326)(38130.5,109453.49715853659)(38622.5,111655.81977845529)(39114.5,113904.8909186992)(39606.5,116202.81763211382)(40098.5,118552.27406707317)(40590.5,120957.2551402439)(41082.5,123425.42828861788)(41574.5,125962.37361585365)(42066.5,128575.37174593496)(42558.5,131275.79281300813)(43050.5,134077.2708373984)(43542.5,136992.64292682928)(44034.5,140037.24509959348)(44526.5,143234.2047682927)(45018.5,146613.52907520323)(45510.5,150227.2450487805)(46002.5,154142.48767479675)(46494.5,158476.08704268292)(46986.5,163481.78608130082)(47478.5,169657.74288617886)(47970.5,179379.5124085366)(48232.5,188736.69675)(48250,189680.595)};
+\addplot[name path=pathSimplification off , colourSimplification off, line width=1.5pt, dashdotted] coordinates {(1,1.135)(246.5,363.1045792682927)(738.5,1150.2894695121952)(1230.5,1976.5712662601627)(1722.5,2827.88006097561)(2214.5,3700.4905081300813)(2706.5,4592.667786585365)(3198.5,5505.309475609756)(3690.5,6435.865410569106)(4182.5,7382.667552845528)(4674.5,8345.835542682928)(5166.5,9325.28124186992)(5658.5,10320.03525609756)(6150.5,11330.31531300813)(6642.5,12355.397339430894)(7134.5,13394.562701219513)(7626.5,14448.094024390242)(8118.5,15515.715595528456)(8610.5,16597.635471544716)(9102.5,17694.34049593496)(9594.5,18806.49131504065)(10086.5,19933.432048780487)(10578.5,21074.394237804878)(11070.5,22229.156333333332)(11562.5,23398.27930284553)(12054.5,24582.21882926829)(12546.5,25781.288851626017)(13038.5,26995.324906504065)(13530.5,28224.14231300813)(14022.5,29466.946489837395)(14514.5,30723.627083333333)(15006.5,31995.121766260163)(15498.5,33280.916351626016)(15990.5,34581.29370528455)(16482.5,35896.226640243905)(16974.5,37225.31055691057)(17466.5,38568.79462398374)(17958.5,39926.34044715447)(18450.5,41296.85248577235)(18942.5,42680.20717479674)(19434.5,44077.110611788616)(19926.5,45488.34107113821)(20418.5,46913.13556707317)(20910.5,48352.125798780486)(21402.5,49805.39538211382)(21894.5,51272.918483739835)(22386.5,52754.42153455284)(22878.5,54249.736412601625)(23370.5,55759.46517073171)(23862.5,57283.576719512195)(24354.5,58822.75940243903)(24846.5,60376.9937398374)(25338.5,61946.492164634146)(25830.5,63530.548172764225)(26322.5,65129.932030487806)(26814.5,66745.12398577236)(27306.5,68376.3347296748)(27798.5,70024.90577439025)(28290.5,71690.3053699187)(28782.5,73371.95175406504)(29274.5,75070.203699187)(29766.5,76786.4307703252)(30258.5,78521.07297357723)(30750.5,80274.46002642276)(31242.5,82047.87613211382)(31734.5,83841.58971341464)(32226.5,85655.53554268293)(32718.5,87490.54740447155)(33210.5,89347.99480691057)(33702.5,91229.68758130081)(34194.5,93135.32528455285)(34686.5,95066.21725406504)(35178.5,97024.63288211382)(35670.5,99011.55916463415)(36162.5,101029.76689634146)(36654.5,103081.27141260162)(37146.5,105168.26180081301)(37638.5,107291.90132520326)(38130.5,109453.49715853659)(38622.5,111655.81977845529)(39114.5,113904.8909186992)(39606.5,116202.81763211382)(40098.5,118552.27406707317)(40590.5,120957.2551402439)(41082.5,123425.42828861788)(41574.5,125962.37361585365)(42066.5,128575.37174593496)(42558.5,131275.79281300813)(43050.5,134077.2708373984)(43542.5,136992.64292682928)(44034.5,140037.24509959348)(44526.5,143234.2047682927)(45018.5,146613.52907520323)(45510.5,150227.2450487805)(46002.5,154142.48767479675)(46494.5,158476.08704268292)(46986.5,163481.78608130082)(47478.5,169657.74288617886)(47970.5,179379.5124085366)(48232.5,188736.69675)(48250,189680.595)};
 \addlegendentry{Simplification off}
 
-\addplot[name path=pathAll off , colourAll off, line width=1.5pt] coordinates {(1,0.875)(243,239.0925670103093)(728,789.0446762886598)(1213,1427.6660762886597)(1698,2129.867397938144)(2183,2881.0539896907217)(2668,3671.581068041237)(3153,4493.687478350515)(3638,5339.833039175258)(4123,6207.217783505154)(4608,7093.622016494845)(5093,7998.2535546391755)(5578,8919.579428865978)(6063,9857.085991752578)(6548,10809.771478350514)(7033,11776.57105154639)(7518,12756.855435051546)(8003,13750.731303092783)(8488,14758.17447628866)(8973,15778.258529896908)(9458,16810.315026804124)(9943,17854.688107216494)(10428,18910.425841237113)(10913,19977.368713402062)(11398,21055.836604123713)(11883,22146.078154639177)(12368,23247.494826804123)(12853,24359.831055670104)(13338,25483.356445360823)(13823,26618.428564948455)(14308,27765.086074226805)(14793,28923.04323298969)(15278,30092.317987628867)(15763,31272.194832989688)(16248,32463.187107216498)(16733,33665.03872577319)(17218,34878.637705154644)(17703,36103.445179381444)(18188,37338.722492783505)(18673,38585.054059793816)(19158,39842.79948659794)(19643,41112.23856082474)(20128,42392.9905072165)(20613,43685.152076288665)(21098,44988.906665979375)(21583,46304.85870309278)(22068,47632.615063917525)(22553,48972.09419381443)(23038,50323.242482474234)(23523,51686.194051546394)(24008,53061.78827835052)(24493,54449.89010927835)(24978,55849.986849484536)(25463,57262.85256494845)(25948,58688.74006185567)(26433,60128.35171546391)(26918,61580.78451546392)(27403,63046.65391546392)(27888,64526.46483505154)(28373,66020.0550185567)(28858,67528.27430103094)(29343,69051.90326185568)(29828,70591.74819381443)(30313,72149.14522061856)(30798,73724.00676701032)(31283,75316.27581237114)(31768,76926.78957319587)(32253,78555.2702701031)(32738,80202.53150515463)(33223,81871.12324948455)(33708,83561.23319381442)(34193,85273.75785979381)(34678,87009.43252783506)(35163,88769.27956701031)(35648,90556.07208453608)(36133,92373.16419587629)(36618,94221.60716907217)(37103,96102.0720371134)(37588,98018.9705113402)(38073,99975.30944329896)(38558,101974.99814432989)(39043,104021.63824536082)(39528,106116.20065360825)(40013,108263.02482474227)(40498,110468.98961237114)(40983,112746.94890721649)(41468,115107.6707484536)(41953,117562.98611546391)(42438,120126.02667628866)(42923,122802.09602061856)(43408,125607.74125979382)(43893,128581.27053608248)(44378,131755.0405072165)(44863,135193.23917113402)(45348,138956.2646639175)(45833,143194.02182268043)(46318,148200.39157938142)(46803,154703.10293814432)(47274.5,165290.41879475984)(47505,174530.666)};
+\addplot[name path=pathAll off , colourAll off, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.875)(243,239.0925670103093)(728,789.0446762886598)(1213,1427.6660762886597)(1698,2129.867397938144)(2183,2881.0539896907217)(2668,3671.581068041237)(3153,4493.687478350515)(3638,5339.833039175258)(4123,6207.217783505154)(4608,7093.622016494845)(5093,7998.2535546391755)(5578,8919.579428865978)(6063,9857.085991752578)(6548,10809.771478350514)(7033,11776.57105154639)(7518,12756.855435051546)(8003,13750.731303092783)(8488,14758.17447628866)(8973,15778.258529896908)(9458,16810.315026804124)(9943,17854.688107216494)(10428,18910.425841237113)(10913,19977.368713402062)(11398,21055.836604123713)(11883,22146.078154639177)(12368,23247.494826804123)(12853,24359.831055670104)(13338,25483.356445360823)(13823,26618.428564948455)(14308,27765.086074226805)(14793,28923.04323298969)(15278,30092.317987628867)(15763,31272.194832989688)(16248,32463.187107216498)(16733,33665.03872577319)(17218,34878.637705154644)(17703,36103.445179381444)(18188,37338.722492783505)(18673,38585.054059793816)(19158,39842.79948659794)(19643,41112.23856082474)(20128,42392.9905072165)(20613,43685.152076288665)(21098,44988.906665979375)(21583,46304.85870309278)(22068,47632.615063917525)(22553,48972.09419381443)(23038,50323.242482474234)(23523,51686.194051546394)(24008,53061.78827835052)(24493,54449.89010927835)(24978,55849.986849484536)(25463,57262.85256494845)(25948,58688.74006185567)(26433,60128.35171546391)(26918,61580.78451546392)(27403,63046.65391546392)(27888,64526.46483505154)(28373,66020.0550185567)(28858,67528.27430103094)(29343,69051.90326185568)(29828,70591.74819381443)(30313,72149.14522061856)(30798,73724.00676701032)(31283,75316.27581237114)(31768,76926.78957319587)(32253,78555.2702701031)(32738,80202.53150515463)(33223,81871.12324948455)(33708,83561.23319381442)(34193,85273.75785979381)(34678,87009.43252783506)(35163,88769.27956701031)(35648,90556.07208453608)(36133,92373.16419587629)(36618,94221.60716907217)(37103,96102.0720371134)(37588,98018.9705113402)(38073,99975.30944329896)(38558,101974.99814432989)(39043,104021.63824536082)(39528,106116.20065360825)(40013,108263.02482474227)(40498,110468.98961237114)(40983,112746.94890721649)(41468,115107.6707484536)(41953,117562.98611546391)(42438,120126.02667628866)(42923,122802.09602061856)(43408,125607.74125979382)(43893,128581.27053608248)(44378,131755.0405072165)(44863,135193.23917113402)(45348,138956.2646639175)(45833,143194.02182268043)(46318,148200.39157938142)(46803,154703.10293814432)(47274.5,165290.41879475984)(47505,174530.666)};
 \addlegendentry{All off}

### 2023-05-04 2023-1-19/figures/cactus_plot_redos.tex
experiment done

@@
 \begin{document}
-\definecolor{colourOstrichCEA}{HTML}{25333D}
-\definecolor{colourOstrich}{HTML}{0065AB}
-\definecolor{colourCVC5}{HTML}{8939AD}
+\definecolor{colourCVC5}{HTML}{25333D}
+\definecolor{colourOstrichCEA}{HTML}{0065AB}
+\definecolor{colourOstrich}{HTML}{8939AD}
 \definecolor{colourZ3str3}{HTML}{007E7A}
@@
 \resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=redos,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
-\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.268)(8.5,12.6915625)(24.5,34.954875)(40.5,58.2241875)(56.5,82.7331875)(72.5,108.7551875)(88.5,135.7378125)(104.5,163.2775625)(120.5,191.216375)(136.5,219.530625)(152.5,248.17575)(168.5,277.0789375)(184.5,306.2231875)(200.5,335.6075)(216.5,365.1799375)(232.5,394.96425)(248.5,424.948625)(264.5,455.1505)(280.5,485.57425)(296.5,516.2539375)(312.5,547.1195625)(328.5,578.1605)(344.5,609.3965625)(360.5,640.86375)(376.5,672.526125)(392.5,704.3930625)(408.5,736.42525)(424.5,768.6708125)(440.5,801.1625625)(456.5,833.9086875)(472.5,866.889875)(488.5,900.0090625)(504.5,933.2758125)(520.5,966.7259375)(536.5,1000.365375)(552.5,1034.2524375)(568.5,1068.3616875)(584.5,1102.7155625)(600.5,1137.2868125)(616.5,1172.10175)(632.5,1207.1765)(648.5,1242.504)(664.5,1278.005125)(680.5,1313.6974375)(696.5,1349.6119375)(712.5,1385.7789375)(728.5,1422.28125)(744.5,1459.09975)(760.5,1496.2685)(776.5,1533.80525)(792.5,1571.5899375)(808.5,1609.6835)(824.5,1648.163)(840.5,1686.9795625)(856.5,1726.3140625)(872.5,1766.0058125)(888.5,1805.9916875)(904.5,1846.3615625)(920.5,1887.2036875)(936.5,1928.6034375)(952.5,1970.5518125)(968.5,2013.213875)(984.5,2056.5095625)(1000.5,2100.3145625)(1016.5,2144.6456875)(1032.5,2189.60025)(1048.5,2235.2554375)(1064.5,2281.8241875)(1080.5,2329.6734375)(1096.5,2379.1441875)(1112.5,2429.9625)(1128.5,2481.816375)(1144.5,2534.979875)(1160.5,2589.3324375)(1176.5,2645.0780625)(1192.5,2701.892125)(1208.5,2759.7080625)(1224.5,2818.4853125)(1240.5,2878.14725)(1256.5,2938.6613125)(1272.5,2999.7675)(1288.5,3061.7365)(1304.5,3124.550125)(1320.5,3188.13575)(1336.5,3252.6558125)(1352.5,3318.13175)(1368.5,3384.681875)(1384.5,3451.851)(1400.5,3519.970625)(1416.5,3589.426375)(1432.5,3660.527)(1448.5,3733.2529375)(1464.5,3807.681625)(1480.5,3883.4769375)(1496.5,3961.36525)(1512.5,4041.9930625)(1528.5,4126.6176875)(1544.5,4219.805375)(1560.5,4326.948125)(1576.5,4449.7968125)(1592.5,4610.8235625)(1601.5,4744.1385)(1604,4795.597)};
+\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.268)(8.5,12.6915625)(24.5,34.954875)(40.5,58.2241875)(56.5,82.7331875)(72.5,108.7551875)(88.5,135.7378125)(104.5,163.2775625)(120.5,191.216375)(136.5,219.530625)(152.5,248.17575)(168.5,277.0789375)(184.5,306.2231875)(200.5,335.6075)(216.5,365.1799375)(232.5,394.96425)(248.5,424.948625)(264.5,455.1505)(280.5,485.57425)(296.5,516.2539375)(312.5,547.1195625)(328.5,578.1605)(344.5,609.3965625)(360.5,640.86375)(376.5,672.526125)(392.5,704.3930625)(408.5,736.42525)(424.5,768.6708125)(440.5,801.1625625)(456.5,833.9086875)(472.5,866.889875)(488.5,900.0090625)(504.5,933.2758125)(520.5,966.7259375)(536.5,1000.365375)(552.5,1034.2524375)(568.5,1068.3616875)(584.5,1102.7155625)(600.5,1137.2868125)(616.5,1172.10175)(632.5,1207.1765)(648.5,1242.504)(664.5,1278.005125)(680.5,1313.6974375)(696.5,1349.6119375)(712.5,1385.7789375)(728.5,1422.28125)(744.5,1459.09975)(760.5,1496.2685)(776.5,1533.80525)(792.5,1571.5899375)(808.5,1609.6835)(824.5,1648.163)(840.5,1686.9795625)(856.5,1726.3140625)(872.5,1766.0058125)(888.5,1805.9916875)(904.5,1846.3615625)(920.5,1887.2036875)(936.5,1928.6034375)(952.5,1970.5518125)(968.5,2013.213875)(984.5,2056.5095625)(1000.5,2100.3145625)(1016.5,2144.6456875)(1032.5,2189.60025)(1048.5,2235.2554375)(1064.5,2281.8241875)(1080.5,2329.6734375)(1096.5,2379.1441875)(1112.5,2429.9625)(1128.5,2481.816375)(1144.5,2534.979875)(1160.5,2589.3324375)(1176.5,2645.0780625)(1192.5,2701.892125)(1208.5,2759.7080625)(1224.5,2818.4853125)(1240.5,2878.14725)(1256.5,2938.6613125)(1272.5,2999.7675)(1288.5,3061.7365)(1304.5,3124.550125)(1320.5,3188.13575)(1336.5,3252.6558125)(1352.5,3318.13175)(1368.5,3384.681875)(1384.5,3451.851)(1400.5,3519.970625)(1416.5,3589.426375)(1432.5,3660.527)(1448.5,3733.2529375)(1464.5,3807.681625)(1480.5,3883.4769375)(1496.5,3961.36525)(1512.5,4041.9930625)(1528.5,4126.6176875)(1544.5,4219.805375)(1560.5,4326.948125)(1576.5,4449.7968125)(1592.5,4610.8235625)(1601.5,4744.1385)(1604,4795.597)};
 \addlegendentry{OstrichCEA}
 
-\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,1.042)(7.5,10.421857142857142)(21.5,29.635571428571428)(35.5,50.016357142857146)(49.5,71.21285714285715)(63.5,93.25821428571429)(77.5,115.84392857142856)(91.5,138.86014285714288)(105.5,162.4882142857143)(119.5,186.6072142857143)(133.5,211.14664285714287)(147.5,236.0525714285714)(161.5,261.4626428571429)(175.5,287.39128571428574)(189.5,313.71728571428577)(203.5,340.4631428571428)(217.5,367.5703571428572)(231.5,395.1613571428572)(245.5,423.17785714285714)(259.5,451.473)(273.5,480.01521428571425)(287.5,508.8493571428572)(301.5,537.9797142857143)(315.5,567.4725)(329.5,597.379)(343.5,627.7412857142857)(357.5,658.6113571428572)(371.5,689.8423571428572)(385.5,721.4651428571428)(399.5,753.5415)(413.5,786.0342857142857)(427.5,818.8502857142856)(441.5,852.0047857142857)(455.5,885.4851428571428)(469.5,919.4435)(483.5,953.7673571428571)(497.5,988.4813571428572)(511.5,1023.6364285714285)(525.5,1059.1977857142856)(539.5,1095.152357142857)(553.5,1131.447857142857)(567.5,1168.1000714285713)(581.5,1205.2960714285714)(595.5,1243.024642857143)(609.5,1281.2957857142858)(623.5,1320.0607857142857)(637.5,1359.327357142857)(651.5,1398.982)(665.5,1439.111642857143)(679.5,1479.8170714285714)(693.5,1521.0342857142857)(707.5,1562.7634285714287)(721.5,1605.0646428571429)(735.5,1647.8864285714287)(749.5,1691.2777857142858)(763.5,1735.378642857143)(777.5,1779.983642857143)(791.5,1825.111)(805.5,1870.7785714285715)(819.5,1917.3739285714287)(833.5,1964.793142857143)(847.5,2013.078857142857)(861.5,2062.0352857142857)(875.5,2111.9066428571427)(889.5,2162.6124285714286)(903.5,2214.2143571428574)(917.5,2266.915285714286)(931.5,2320.8507142857143)(945.5,2375.982571428571)(959.5,2432.2053571428573)(973.5,2489.9445)(987.5,2549.594642857143)(1001.5,2611.896214285714)(1015.5,2677.7935714285713)(1029.5,2746.8089285714286)(1043.5,2819.2254285714284)(1057.5,2895.4688571428574)(1071.5,2976.7548571428574)(1085.5,3063.5255714285713)(1099.5,3156.2792142857143)(1113.5,3256.008714285714)(1127.5,3361.891214285714)(1141.5,3475.924785714286)(1155.5,3596.808)(1169.5,3725.2726428571427)(1183.5,3863.3013571428573)(1197.5,4012.4511428571427)(1211.5,4173.714785714286)(1225.5,4349.4121428571425)(1239.5,4536.0506428571425)(1253.5,4733.094928571428)(1267.5,4940.848285714285)(1281.5,5164.210285714285)(1295.5,5406.3664285714285)(1309.5,5666.005357142857)(1323.5,5947.754357142857)(1337.5,6272.523357142857)(1351.5,6649.797214285714)(1365.5,7108.828785714285)(1377.5,7661.63)(1384,7972.953)};
+\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,1.042)(7.5,10.421857142857142)(21.5,29.635571428571428)(35.5,50.016357142857146)(49.5,71.21285714285715)(63.5,93.25821428571429)(77.5,115.84392857142856)(91.5,138.86014285714288)(105.5,162.4882142857143)(119.5,186.6072142857143)(133.5,211.14664285714287)(147.5,236.0525714285714)(161.5,261.4626428571429)(175.5,287.39128571428574)(189.5,313.71728571428577)(203.5,340.4631428571428)(217.5,367.5703571428572)(231.5,395.1613571428572)(245.5,423.17785714285714)(259.5,451.473)(273.5,480.01521428571425)(287.5,508.8493571428572)(301.5,537.9797142857143)(315.5,567.4725)(329.5,597.379)(343.5,627.7412857142857)(357.5,658.6113571428572)(371.5,689.8423571428572)(385.5,721.4651428571428)(399.5,753.5415)(413.5,786.0342857142857)(427.5,818.8502857142856)(441.5,852.0047857142857)(455.5,885.4851428571428)(469.5,919.4435)(483.5,953.7673571428571)(497.5,988.4813571428572)(511.5,1023.6364285714285)(525.5,1059.1977857142856)(539.5,1095.152357142857)(553.5,1131.447857142857)(567.5,1168.1000714285713)(581.5,1205.2960714285714)(595.5,1243.024642857143)(609.5,1281.2957857142858)(623.5,1320.0607857142857)(637.5,1359.327357142857)(651.5,1398.982)(665.5,1439.111642857143)(679.5,1479.8170714285714)(693.5,1521.0342857142857)(707.5,1562.7634285714287)(721.5,1605.0646428571429)(735.5,1647.8864285714287)(749.5,1691.2777857142858)(763.5,1735.378642857143)(777.5,1779.983642857143)(791.5,1825.111)(805.5,1870.7785714285715)(819.5,1917.3739285714287)(833.5,1964.793142857143)(847.5,2013.078857142857)(861.5,2062.0352857142857)(875.5,2111.9066428571427)(889.5,2162.6124285714286)(903.5,2214.2143571428574)(917.5,2266.915285714286)(931.5,2320.8507142857143)(945.5,2375.982571428571)(959.5,2432.2053571428573)(973.5,2489.9445)(987.5,2549.594642857143)(1001.5,2611.896214285714)(1015.5,2677.7935714285713)(1029.5,2746.8089285714286)(1043.5,2819.2254285714284)(1057.5,2895.4688571428574)(1071.5,2976.7548571428574)(1085.5,3063.5255714285713)(1099.5,3156.2792142857143)(1113.5,3256.008714285714)(1127.5,3361.891214285714)(1141.5,3475.924785714286)(1155.5,3596.808)(1169.5,3725.2726428571427)(1183.5,3863.3013571428573)(1197.5,4012.4511428571427)(1211.5,4173.714785714286)(1225.5,4349.4121428571425)(1239.5,4536.0506428571425)(1253.5,4733.094928571428)(1267.5,4940.848285714285)(1281.5,5164.210285714285)(1295.5,5406.3664285714285)(1309.5,5666.005357142857)(1323.5,5947.754357142857)(1337.5,6272.523357142857)(1351.5,6649.797214285714)(1365.5,7108.828785714285)(1377.5,7661.63)(1384,7972.953)};
 \addlegendentry{Ostrich}
 
-\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.007)(7,0.08584615384615384)(20,0.305)(33,0.6530769230769231)(46,1.1311538461538462)(59,1.6853846153846155)(72,2.2931538461538463)(85,2.9566923076923075)(98,3.686230769230769)(111,4.479461538461538)(124,5.35023076923077)(137,6.312153846153846)(150,7.359153846153846)(163,8.470615384615385)(176,9.657692307692308)(189,10.93923076923077)(202,12.307615384615385)(215,13.752153846153846)(228,15.272)(241,16.85884615384615)(254,18.51792307692308)(267,20.254153846153848)(280,22.07076923076923)(293,24.015)(306,26.139692307692307)(319,28.53876923076923)(332,31.162307692307692)(345,34.02146153846154)(358,37.16815384615384)(371,40.49684615384616)(384,44.06376923076923)(397,47.8823076923077)(410,51.92207692307692)(423,56.27353846153846)(436,60.88161538461538)(449,65.64184615384616)(462,70.59938461538461)(475,75.76446153846153)(488,81.06407692307693)(501,86.49453846153847)(514,92.05415384615384)(527,97.75361538461539)(540,103.56776923076923)(553,109.49507692307692)(566,115.5783846153846)(579,121.86215384615384)(592,128.30061538461538)(605,134.89915384615384)(618,141.65592307692307)(631,148.56823076923078)(644,155.6096923076923)(657,162.78415384615386)(670,170.11546153846155)(683,177.60553846153846)(696,185.30261538461536)(709,193.18292307692306)(722,201.2533076923077)(735,209.55253846153846)(748,218.15223076923078)(761,227.18307692307692)(774,236.63753846153847)(787,246.61015384615385)(800,257.15207692307695)(813,268.3446923076923)(826,280.29207692307693)(839,293.0210769230769)(852,306.7554615384616)(865,321.323)(878,336.84784615384615)(891,353.35807692307696)(904,370.93038461538464)(917,389.3006923076923)(930,408.32023076923076)(943,428.23615384615385)(956,449.51346153846157)(969,472.04553846153846)(982,496.191)(995,523.0977692307692)(1008,553.4396923076922)(1021,586.0476923076923)(1034,621.8947692307693)(1047,661.3595384615385)(1060,704.5181538461538)(1073,751.4005384615385)(1086,802.835)(1099,862.5549230769232)(1112,931.1657692307692)(1125,1009.1157692307693)(1138,1101.7934615384615)(1151,1230.164076923077)(1164,1424.009923076923)(1177,1703.8506923076923)(1190,2059.8683846153845)(1203,2464.8026923076923)(1216,2921.014769230769)(1229,3424.7666153846153)(1241.5,3993.243)(1249,4346.266)};
+\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt, dashed, dash pattern=on 2pt off 8pt] coordinates {(1,0.007)(7,0.08584615384615384)(20,0.305)(33,0.6530769230769231)(46,1.1311538461538462)(59,1.6853846153846155)(72,2.2931538461538463)(85,2.9566923076923075)(98,3.686230769230769)(111,4.479461538461538)(124,5.35023076923077)(137,6.312153846153846)(150,7.359153846153846)(163,8.470615384615385)(176,9.657692307692308)(189,10.93923076923077)(202,12.307615384615385)(215,13.752153846153846)(228,15.272)(241,16.85884615384615)(254,18.51792307692308)(267,20.254153846153848)(280,22.07076923076923)(293,24.015)(306,26.139692307692307)(319,28.53876923076923)(332,31.162307692307692)(345,34.02146153846154)(358,37.16815384615384)(371,40.49684615384616)(384,44.06376923076923)(397,47.8823076923077)(410,51.92207692307692)(423,56.27353846153846)(436,60.88161538461538)(449,65.64184615384616)(462,70.59938461538461)(475,75.76446153846153)(488,81.06407692307693)(501,86.49453846153847)(514,92.05415384615384)(527,97.75361538461539)(540,103.56776923076923)(553,109.49507692307692)(566,115.5783846153846)(579,121.86215384615384)(592,128.30061538461538)(605,134.89915384615384)(618,141.65592307692307)(631,148.56823076923078)(644,155.6096923076923)(657,162.78415384615386)(670,170.11546153846155)(683,177.60553846153846)(696,185.30261538461536)(709,193.18292307692306)(722,201.2533076923077)(735,209.55253846153846)(748,218.15223076923078)(761,227.18307692307692)(774,236.63753846153847)(787,246.61015384615385)(800,257.15207692307695)(813,268.3446923076923)(826,280.29207692307693)(839,293.0210769230769)(852,306.7554615384616)(865,321.323)(878,336.84784615384615)(891,353.35807692307696)(904,370.93038461538464)(917,389.3006923076923)(930,408.32023076923076)(943,428.23615384615385)(956,449.51346153846157)(969,472.04553846153846)(982,496.191)(995,523.0977692307692)(1008,553.4396923076922)(1021,586.0476923076923)(1034,621.8947692307693)(1047,661.3595384615385)(1060,704.5181538461538)(1073,751.4005384615385)(1086,802.835)(1099,862.5549230769232)(1112,931.1657692307692)(1125,1009.1157692307693)(1138,1101.7934615384615)(1151,1230.164076923077)(1164,1424.009923076923)(1177,1703.8506923076923)(1190,2059.8683846153845)(1203,2464.8026923076923)(1216,2921.014769230769)(1229,3424.7666153846153)(1241.5,3993.243)(1249,4346.266)};
 \addlegendentry{CVC5}
 
-\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.017)(5,0.13355555555555554)(14,0.37611111111111106)(23,0.639)(32,0.9286666666666666)(41,1.2483333333333333)(50,1.5871111111111111)(59,1.942777777777778)(68,2.3183333333333334)(77,2.710444444444444)(86,3.1183333333333336)(95,3.5474444444444444)(104,3.9951111111111115)(113,4.454666666666667)(122,4.926111111111111)(131,5.410111111111111)(140,5.907444444444445)(149,6.420333333333333)(158,6.947111111111111)(167,7.487666666666667)(176,8.041777777777778)(185,8.613666666666665)(194,9.2)(203,9.802666666666665)(212,10.42)(221,11.05711111111111)(230,11.704777777777778)(239,12.366333333333333)(248,13.042)(257,13.737)(266,14.446666666666665)(275,15.176222222222222)(284,15.924)(293,16.69366666666667)(302,17.484333333333332)(311,18.304)(320,19.147333333333332)(329,20.019777777777776)(338,20.91433333333333)(347,21.834222222222223)(356,22.779333333333334)(365,23.74577777777778)(374,24.738777777777777)(383,25.758666666666667)(392,26.808777777777777)(401,27.893666666666668)(410,29.01788888888889)(419,30.171666666666667)(428,31.351)(437,32.574)(446,33.85466666666667)(455,35.18366666666667)(464,36.55377777777778)(473,37.970888888888894)(482,39.43866666666666)(491,40.962111111111106)(500,42.56055555555555)(509,44.21877777777778)(518,45.95133333333334)(527,47.779111111111106)(536,49.68177777777778)(545,51.67422222222222)(554,53.775333333333336)(563,55.97422222222222)(572,58.306666666666665)(581,60.77277777777778)(590,63.406666666666666)(599,66.23022222222222)(608,69.23144444444443)(617,72.49055555555556)(626,76.05744444444444)(635,79.90144444444444)(644,84.237)(653,88.88711111111111)(662,94.08977777777778)(671,99.92533333333333)(680,106.4301111111111)(689,114.00422222222223)(698,122.53)(707,132.107)(716,143.86844444444444)(725,158.1821111111111)(734,174.91488888888887)(743,194.845)(752,218.70155555555556)(761,248.3372222222222)(770,290.79277777777776)(779,348.5783333333333)(788,417.857)(797,510.13644444444446)(806,641.939)(815,831.2733333333334)(824,1073.363111111111)(833,1364.137888888889)(842,1704.5152222222223)(851,2110.631888888889)(858,2475.6972)(862,2647.177)};
+\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.017)(5,0.13355555555555554)(14,0.37611111111111106)(23,0.639)(32,0.9286666666666666)(41,1.2483333333333333)(50,1.5871111111111111)(59,1.942777777777778)(68,2.3183333333333334)(77,2.710444444444444)(86,3.1183333333333336)(95,3.5474444444444444)(104,3.9951111111111115)(113,4.454666666666667)(122,4.926111111111111)(131,5.410111111111111)(140,5.907444444444445)(149,6.420333333333333)(158,6.947111111111111)(167,7.487666666666667)(176,8.041777777777778)(185,8.613666666666665)(194,9.2)(203,9.802666666666665)(212,10.42)(221,11.05711111111111)(230,11.704777777777778)(239,12.366333333333333)(248,13.042)(257,13.737)(266,14.446666666666665)(275,15.176222222222222)(284,15.924)(293,16.69366666666667)(302,17.484333333333332)(311,18.304)(320,19.147333333333332)(329,20.019777777777776)(338,20.91433333333333)(347,21.834222222222223)(356,22.779333333333334)(365,23.74577777777778)(374,24.738777777777777)(383,25.758666666666667)(392,26.808777777777777)(401,27.893666666666668)(410,29.01788888888889)(419,30.171666666666667)(428,31.351)(437,32.574)(446,33.85466666666667)(455,35.18366666666667)(464,36.55377777777778)(473,37.970888888888894)(482,39.43866666666666)(491,40.962111111111106)(500,42.56055555555555)(509,44.21877777777778)(518,45.95133333333334)(527,47.779111111111106)(536,49.68177777777778)(545,51.67422222222222)(554,53.775333333333336)(563,55.97422222222222)(572,58.306666666666665)(581,60.77277777777778)(590,63.406666666666666)(599,66.23022222222222)(608,69.23144444444443)(617,72.49055555555556)(626,76.05744444444444)(635,79.90144444444444)(644,84.237)(653,88.88711111111111)(662,94.08977777777778)(671,99.92533333333333)(680,106.4301111111111)(689,114.00422222222223)(698,122.53)(707,132.107)(716,143.86844444444444)(725,158.1821111111111)(734,174.91488888888887)(743,194.845)(752,218.70155555555556)(761,248.3372222222222)(770,290.79277777777776)(779,348.5783333333333)(788,417.857)(797,510.13644444444446)(806,641.939)(815,831.2733333333334)(824,1073.363111111111)(833,1364.137888888889)(842,1704.5152222222223)(851,2110.631888888889)(858,2475.6972)(862,2647.177)};
 \addlegendentry{Z3str3}
 
-\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.015)(7,0.13392307692307692)(20,0.4753076923076923)(33,1.0751538461538461)(46,2.187769230769231)(59,3.741076923076923)(72,5.534846153846154)(85,7.5522307692307695)(98,9.893307692307692)(111,12.54646153846154)(124,15.76876923076923)(137,19.567153846153847)(150,23.959615384615383)(163,28.68123076923077)(176,33.70907692307692)(189,39.13515384615384)(202,45.02061538461538)(215,51.28153846153846)(228,57.95976923076923)(241,64.94292307692308)(254,72.15346153846153)(267,79.66346153846153)(280,87.47692307692307)(293,95.62438461538461)(306,104.04515384615384)(319,112.723)(332,121.75030769230769)(345,131.2003076923077)(358,140.9993076923077)(371,151.17884615384617)(384,161.71284615384616)(397,172.62730769230768)(410,184.0403076923077)(423,195.81446153846153)(436,208.03846153846152)(449,220.69846153846154)(462,233.92207692307693)(475,247.7913076923077)(488,262.59430769230767)(501,278.44446153846155)(514,295.05923076923074)(527,312.72138461538464)(540,331.90353846153846)(553,352.35630769230767)(566,373.94807692307694)(579,396.50646153846156)(592,419.9123846153846)(605,444.309)(618,470.0917692307693)(631,497.68453846153847)(644,526.4123076923078)(657,557.0483846153846)(670,590.1912307692307)(683,624.9178461538461)(696,661.1273076923078)(709,699.3653076923077)(722,740.2164615384615)(735,783.0497692307692)(748,827.2873846153847)(761,873.849)(774,923.3921538461539)(787,974.9501538461539)(800,1029.0558461538462)(813,1086.2576153846155)(826,1147.4029230769231)(839,1212.1193846153844)(852,1281.6894615384615)(865,1356.7432307692306)(878,1437.5274615384615)(891,1525.3787692307692)(904,1622.077923076923)(917,1726.5867692307693)(930,1841.5621538461537)(943,1966.1236923076922)(956,2097.5923076923077)(969,2237.991846153846)(982,2388.815846153846)(995,2550.726153846154)(1008,2724.7893076923074)(1021,2912.461)(1034,3108.7013846153845)(1047,3318.6526923076926)(1060,3540.098)(1073,3780.940923076923)(1086,4046.5943846153846)(1099,4341.672692307692)(1112,4661.215)(1125,5005.762769230769)(1138,5382.683384615385)(1151,5793.749307692308)(1164,6244.779692307692)(1177,6752.641307692308)(1190,7313.696153846154)(1203,7921.302461538462)(1216,8582.782846153847)(1226,9128.86)(1231,9358.232)};
+\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1pt off 2pt] coordinates {(1,0.015)(7,0.13392307692307692)(20,0.4753076923076923)(33,1.0751538461538461)(46,2.187769230769231)(59,3.741076923076923)(72,5.534846153846154)(85,7.5522307692307695)(98,9.893307692307692)(111,12.54646153846154)(124,15.76876923076923)(137,19.567153846153847)(150,23.959615384615383)(163,28.68123076923077)(176,33.70907692307692)(189,39.13515384615384)(202,45.02061538461538)(215,51.28153846153846)(228,57.95976923076923)(241,64.94292307692308)(254,72.15346153846153)(267,79.66346153846153)(280,87.47692307692307)(293,95.62438461538461)(306,104.04515384615384)(319,112.723)(332,121.75030769230769)(345,131.2003076923077)(358,140.9993076923077)(371,151.17884615384617)(384,161.71284615384616)(397,172.62730769230768)(410,184.0403076923077)(423,195.81446153846153)(436,208.03846153846152)(449,220.69846153846154)(462,233.92207692307693)(475,247.7913076923077)(488,262.59430769230767)(501,278.44446153846155)(514,295.05923076923074)(527,312.72138461538464)(540,331.90353846153846)(553,352.35630769230767)(566,373.94807692307694)(579,396.50646153846156)(592,419.9123846153846)(605,444.309)(618,470.0917692307693)(631,497.68453846153847)(644,526.4123076923078)(657,557.0483846153846)(670,590.1912307692307)(683,624.9178461538461)(696,661.1273076923078)(709,699.3653076923077)(722,740.2164615384615)(735,783.0497692307692)(748,827.2873846153847)(761,873.849)(774,923.3921538461539)(787,974.9501538461539)(800,1029.0558461538462)(813,1086.2576153846155)(826,1147.4029230769231)(839,1212.1193846153844)(852,1281.6894615384615)(865,1356.7432307692306)(878,1437.5274615384615)(891,1525.3787692307692)(904,1622.077923076923)(917,1726.5867692307693)(930,1841.5621538461537)(943,1966.1236923076922)(956,2097.5923076923077)(969,2237.991846153846)(982,2388.815846153846)(995,2550.726153846154)(1008,2724.7893076923074)(1021,2912.461)(1034,3108.7013846153845)(1047,3318.6526923076926)(1060,3540.098)(1073,3780.940923076923)(1086,4046.5943846153846)(1099,4341.672692307692)(1112,4661.215)(1125,5005.762769230769)(1138,5382.683384615385)(1151,5793.749307692308)(1164,6244.779692307692)(1177,6752.641307692308)(1190,7313.696153846154)(1203,7921.302461538462)(1216,8582.782846153847)(1226,9128.86)(1231,9358.232)};
 \addlegendentry{Z3seq}
 
-\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.007)(8.5,0.0758125)(24.5,0.263125)(40.5,0.515125)(56.5,0.7930625)(72.5,1.0844375)(88.5,1.3903125)(104.5,1.71125)(120.5,2.04725)(136.5,2.397)(152.5,2.7555625)(168.5,3.12575)(184.5,3.508)(200.5,3.9005)(216.5,4.30275)(232.5,4.7171875)(248.5,5.1435)(264.5,5.580375)(280.5,6.032125)(296.5,6.4955)(312.5,6.9651875)(328.5,7.4506875)(344.5,7.9521875)(360.5,8.4674375)(376.5,8.9958125)(392.5,9.537)(408.5,10.0895)(424.5,10.658)(440.5,11.238875)(456.5,11.83225)(472.5,12.4380625)(488.5,13.0555)(504.5,13.6829375)(520.5,14.3269375)(536.5,14.9929375)(552.5,15.680375)(568.5,16.39425)(584.5,17.128375)(600.5,17.8755)(616.5,18.6303125)(632.5,19.3979375)(648.5,20.1785625)(664.5,20.972)(680.5,21.78225)(696.5,22.6196875)(712.5,23.4789375)(728.5,24.355875)(744.5,25.24875)(760.5,26.1598125)(776.5,27.08725)(792.5,28.0455625)(808.5,29.0368125)(824.5,30.0645625)(840.5,31.1379375)(856.5,32.2518125)(872.5,33.4005)(888.5,34.5898125)(904.5,35.821375)(920.5,37.097625)(936.5,38.4284375)(952.5,39.8054375)(968.5,41.2453125)(984.5,42.7475)(1000.5,44.3534375)(1016.5,46.0835)(1032.5,47.924875)(1048.5,49.8915625)(1064.5,52.0588125)(1080.5,54.4555625)(1096.5,57.04125)(1112.5,59.751375)(1128.5,62.618375)(1144.5,65.6106875)(1160.5,68.7401875)(1176.5,72.18275)(1192.5,75.974)(1208.5,80.25575)(1224.5,85.5225625)(1240.5,91.56425)(1256.5,98.3388125)(1272.5,106.0435)(1288.5,114.47225)(1304.5,123.289375)(1320.5,132.7138125)(1336.5,142.9955625)(1352.5,154.5948125)(1368.5,168.214)(1384.5,184.7535625)(1400.5,207.01025)(1416.5,235.7268125)(1432.5,270.52575)(1448.5,318.257)(1464.5,393.0419375)(1480.5,494.505875)(1496.5,608.450625)(1512.5,744.9885)(1528.5,957.6901875)(1544.5,1302.16275)(1560.5,1835.9473125)(1570.5,2309.625)(1574,2451.289)};
+\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt, dashed, dash pattern=on 2pt off 4pt] coordinates {(1,0.007)(8.5,0.0758125)(24.5,0.263125)(40.5,0.515125)(56.5,0.7930625)(72.5,1.0844375)(88.5,1.3903125)(104.5,1.71125)(120.5,2.04725)(136.5,2.397)(152.5,2.7555625)(168.5,3.12575)(184.5,3.508)(200.5,3.9005)(216.5,4.30275)(232.5,4.7171875)(248.5,5.1435)(264.5,5.580375)(280.5,6.032125)(296.5,6.4955)(312.5,6.9651875)(328.5,7.4506875)(344.5,7.9521875)(360.5,8.4674375)(376.5,8.9958125)(392.5,9.537)(408.5,10.0895)(424.5,10.658)(440.5,11.238875)(456.5,11.83225)(472.5,12.4380625)(488.5,13.0555)(504.5,13.6829375)(520.5,14.3269375)(536.5,14.9929375)(552.5,15.680375)(568.5,16.39425)(584.5,17.128375)(600.5,17.8755)(616.5,18.6303125)(632.5,19.3979375)(648.5,20.1785625)(664.5,20.972)(680.5,21.78225)(696.5,22.6196875)(712.5,23.4789375)(728.5,24.355875)(744.5,25.24875)(760.5,26.1598125)(776.5,27.08725)(792.5,28.0455625)(808.5,29.0368125)(824.5,30.0645625)(840.5,31.1379375)(856.5,32.2518125)(872.5,33.4005)(888.5,34.5898125)(904.5,35.821375)(920.5,37.097625)(936.5,38.4284375)(952.5,39.8054375)(968.5,41.2453125)(984.5,42.7475)(1000.5,44.3534375)(1016.5,46.0835)(1032.5,47.924875)(1048.5,49.8915625)(1064.5,52.0588125)(1080.5,54.4555625)(1096.5,57.04125)(1112.5,59.751375)(1128.5,62.618375)(1144.5,65.6106875)(1160.5,68.7401875)(1176.5,72.18275)(1192.5,75.974)(1208.5,80.25575)(1224.5,85.5225625)(1240.5,91.56425)(1256.5,98.3388125)(1272.5,106.0435)(1288.5,114.47225)(1304.5,123.289375)(1320.5,132.7138125)(1336.5,142.9955625)(1352.5,154.5948125)(1368.5,168.214)(1384.5,184.7535625)(1400.5,207.01025)(1416.5,235.7268125)(1432.5,270.52575)(1448.5,318.257)(1464.5,393.0419375)(1480.5,494.505875)(1496.5,608.450625)(1512.5,744.9885)(1528.5,957.6901875)(1544.5,1302.16275)(1560.5,1835.9473125)(1570.5,2309.625)(1574,2451.289)};
 \addlegendentry{Z3str3RE}
 
-\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.016)(2,0.053)(5,0.111)(8,0.17233333333333334)(11,0.24133333333333334)(14,0.35633333333333334)(17,0.532)(20,0.7983333333333333)(23,1.095)(26,1.5226666666666668)(29,2.1523333333333334)(32,2.9396666666666667)(35,3.9976666666666665)(38,5.294666666666667)(41,6.714)(44,8.258666666666667)(47,9.852333333333334)(50,11.533666666666665)(53,13.339333333333334)(56,15.281333333333334)(59,17.312)(62,19.477666666666668)(65,21.76233333333333)(68,24.18)(71,26.796)(74,29.68733333333333)(77,32.67433333333333)(80,35.758)(83,38.97)(86,42.28933333333334)(89,45.894333333333336)(92,49.85166666666667)(95,53.928333333333335)(98,58.059)(101,62.247)(104,66.66433333333333)(107,71.34166666666667)(110,76.268)(113,81.44766666666668)(116,86.93366666666667)(119,92.68)(122,98.49866666666667)(125,104.398)(128,110.51466666666667)(131,116.94566666666667)(134,123.67666666666668)(137,131.009)(140,138.821)(143,146.862)(146,155.07933333333335)(149,163.47833333333335)(152,172.06766666666667)(155,180.78866666666664)(158,190.297)(161,200.83833333333334)(164,211.90466666666666)(167,223.99133333333333)(170,236.898)(173,250.152)(176,263.98466666666667)(179,278.498)(182,293.6046666666667)(185,309.477)(188,326.655)(191,344.77)(194,363.702)(197,382.9943333333333)(200,402.6673333333333)(203,422.945)(206,444.157)(209,467.0073333333333)(212,491.593)(215,517.5033333333333)(218,544.213)(221,571.7546666666666)(224,601.098)(227,631.7703333333334)(230,663.7593333333334)(233,697.4513333333334)(236,732.3156666666666)(239,768.4563333333334)(242,805.529)(245,843.917)(248,883.4013333333334)(251,926.3146666666667)(254,974.039)(257,1029.1116666666667)(260,1089.092)(263,1154.1753333333334)(266,1228.3816666666667)(269,1306.6253333333332)(272,1392.2936666666667)(275,1481.7986666666668)(278,1575.6423333333332)(281,1676.5096666666668)(284,1782.0873333333332)(287,1895.8256666666668)(290,2017.9586666666667)(293,2152.2976666666664)(296,2303.433)(299,2464.662)(302,2630.6766666666667)(305,2799.423)(308,2973.517)(311,3092.419)};
+\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt, dashed, dash pattern=on 4pt off 2pt] coordinates {(1,0.016)(2,0.053)(5,0.111)(8,0.17233333333333334)(11,0.24133333333333334)(14,0.35633333333333334)(17,0.532)(20,0.7983333333333333)(23,1.095)(26,1.5226666666666668)(29,2.1523333333333334)(32,2.9396666666666667)(35,3.9976666666666665)(38,5.294666666666667)(41,6.714)(44,8.258666666666667)(47,9.852333333333334)(50,11.533666666666665)(53,13.339333333333334)(56,15.281333333333334)(59,17.312)(62,19.477666666666668)(65,21.76233333333333)(68,24.18)(71,26.796)(74,29.68733333333333)(77,32.67433333333333)(80,35.758)(83,38.97)(86,42.28933333333334)(89,45.894333333333336)(92,49.85166666666667)(95,53.928333333333335)(98,58.059)(101,62.247)(104,66.66433333333333)(107,71.34166666666667)(110,76.268)(113,81.44766666666668)(116,86.93366666666667)(119,92.68)(122,98.49866666666667)(125,104.398)(128,110.51466666666667)(131,116.94566666666667)(134,123.67666666666668)(137,131.009)(140,138.821)(143,146.862)(146,155.07933333333335)(149,163.47833333333335)(152,172.06766666666667)(155,180.78866666666664)(158,190.297)(161,200.83833333333334)(164,211.90466666666666)(167,223.99133333333333)(170,236.898)(173,250.152)(176,263.98466666666667)(179,278.498)(182,293.6046666666667)(185,309.477)(188,326.655)(191,344.77)(194,363.702)(197,382.9943333333333)(200,402.6673333333333)(203,422.945)(206,444.157)(209,467.0073333333333)(212,491.593)(215,517.5033333333333)(218,544.213)(221,571.7546666666666)(224,601.098)(227,631.7703333333334)(230,663.7593333333334)(233,697.4513333333334)(236,732.3156666666666)(239,768.4563333333334)(242,805.529)(245,843.917)(248,883.4013333333334)(251,926.3146666666667)(254,974.039)(257,1029.1116666666667)(260,1089.092)(263,1154.1753333333334)(266,1228.3816666666667)(269,1306.6253333333332)(272,1392.2936666666667)(275,1481.7986666666668)(278,1575.6423333333332)(281,1676.5096666666668)(284,1782.0873333333332)(287,1895.8256666666668)(290,2017.9586666666667)(293,2152.2976666666664)(296,2303.433)(299,2464.662)(302,2630.6766666666667)(305,2799.423)(308,2973.517)(311,3092.419)};
 \addlegendentry{Z3-Trau}

### 2023-05-04 2023-1-19/figures/cactus_plot_regexlib.tex
experiment done

@@
 \begin{document}
-\definecolor{colourOstrichCEA}{HTML}{25333D}
-\definecolor{colourCVC5}{HTML}{0065AB}
+\definecolor{colourCVC5}{HTML}{25333D}
+\definecolor{colourOstrichCEA}{HTML}{0065AB}
 \definecolor{colourOstrich}{HTML}{8939AD}
@@
 \resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=regexlib,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
-\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.326)(8.5,14.001375)(24.5,39.800875)(40.5,67.09)(56.5,95.3169375)(72.5,124.4550625)(88.5,154.267375)(104.5,184.69425)(120.5,215.657)(136.5,247.035125)(152.5,278.7906875)(168.5,311.0410625)(184.5,343.8286875)(200.5,377.011375)(216.5,410.68275)(232.5,444.867875)(248.5,479.5120625)(264.5,514.5951875)(280.5,550.083625)(296.5,585.994125)(312.5,622.261875)(328.5,658.8564375)(344.5,695.7899375)(360.5,733.01425)(376.5,770.5569375)(392.5,808.4133125)(408.5,846.6525625)(424.5,885.256)(440.5,924.2085625)(456.5,963.6601875)(472.5,1003.5794375)(488.5,1043.8909375)(504.5,1084.5918125)(520.5,1125.6925625)(536.5,1167.1688125)(552.5,1209.008)(568.5,1251.1431875)(584.5,1293.6194375)(600.5,1336.5265625)(616.5,1379.7884375)(632.5,1423.3959375)(648.5,1467.445375)(664.5,1512.1114375)(680.5,1557.229625)(696.5,1602.6933125)(712.5,1648.5414375)(728.5,1694.74525)(744.5,1741.259875)(760.5,1788.104625)(776.5,1835.441375)(792.5,1883.3281875)(808.5,1931.6915625)(824.5,1980.545125)(840.5,2029.794125)(856.5,2079.47)(872.5,2129.7085625)(888.5,2180.5180625)(904.5,2232.03075)(920.5,2284.4146875)(936.5,2337.7085)(952.5,2391.664625)(968.5,2446.13225)(984.5,2501.088125)(1000.5,2556.4926875)(1016.5,2612.4775)(1032.5,2669.06175)(1048.5,2726.1491875)(1064.5,2783.9013125)(1080.5,2842.3911875)(1096.5,2901.65625)(1112.5,2961.713625)(1128.5,3022.462)(1144.5,3084.2588125)(1160.5,3146.9798125)(1176.5,3210.752125)(1192.5,3275.4954375)(1208.5,3341.271875)(1224.5,3408.4449375)(1240.5,3476.9365625)(1256.5,3546.931625)(1272.5,3618.58925)(1288.5,3691.8859375)(1304.5,3767.448375)(1320.5,3845.036625)(1336.5,3924.75)(1352.5,4006.6775)(1368.5,4090.948625)(1384.5,4177.0058125)(1400.5,4266.37675)(1416.5,4358.8839375)(1432.5,4454.4639375)(1448.5,4553.3179375)(1464.5,4656.1215625)(1480.5,4765.12675)(1496.5,4880.6024375)(1512.5,5003.2408125)(1528.5,5136.673125)(1544.5,5283.0321875)(1560.5,5444.2958125)(1576.5,5642.1679375)(1592.5,5967.94825)(1602,6241.055)};
+\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.326)(8.5,14.001375)(24.5,39.800875)(40.5,67.09)(56.5,95.3169375)(72.5,124.4550625)(88.5,154.267375)(104.5,184.69425)(120.5,215.657)(136.5,247.035125)(152.5,278.7906875)(168.5,311.0410625)(184.5,343.8286875)(200.5,377.011375)(216.5,410.68275)(232.5,444.867875)(248.5,479.5120625)(264.5,514.5951875)(280.5,550.083625)(296.5,585.994125)(312.5,622.261875)(328.5,658.8564375)(344.5,695.7899375)(360.5,733.01425)(376.5,770.5569375)(392.5,808.4133125)(408.5,846.6525625)(424.5,885.256)(440.5,924.2085625)(456.5,963.6601875)(472.5,1003.5794375)(488.5,1043.8909375)(504.5,1084.5918125)(520.5,1125.6925625)(536.5,1167.1688125)(552.5,1209.008)(568.5,1251.1431875)(584.5,1293.6194375)(600.5,1336.5265625)(616.5,1379.7884375)(632.5,1423.3959375)(648.5,1467.445375)(664.5,1512.1114375)(680.5,1557.229625)(696.5,1602.6933125)(712.5,1648.5414375)(728.5,1694.74525)(744.5,1741.259875)(760.5,1788.104625)(776.5,1835.441375)(792.5,1883.3281875)(808.5,1931.6915625)(824.5,1980.545125)(840.5,2029.794125)(856.5,2079.47)(872.5,2129.7085625)(888.5,2180.5180625)(904.5,2232.03075)(920.5,2284.4146875)(936.5,2337.7085)(952.5,2391.664625)(968.5,2446.13225)(984.5,2501.088125)(1000.5,2556.4926875)(1016.5,2612.4775)(1032.5,2669.06175)(1048.5,2726.1491875)(1064.5,2783.9013125)(1080.5,2842.3911875)(1096.5,2901.65625)(1112.5,2961.713625)(1128.5,3022.462)(1144.5,3084.2588125)(1160.5,3146.9798125)(1176.5,3210.752125)(1192.5,3275.4954375)(1208.5,3341.271875)(1224.5,3408.4449375)(1240.5,3476.9365625)(1256.5,3546.931625)(1272.5,3618.58925)(1288.5,3691.8859375)(1304.5,3767.448375)(1320.5,3845.036625)(1336.5,3924.75)(1352.5,4006.6775)(1368.5,4090.948625)(1384.5,4177.0058125)(1400.5,4266.37675)(1416.5,4358.8839375)(1432.5,4454.4639375)(1448.5,4553.3179375)(1464.5,4656.1215625)(1480.5,4765.12675)(1496.5,4880.6024375)(1512.5,5003.2408125)(1528.5,5136.673125)(1544.5,5283.0321875)(1560.5,5444.2958125)(1576.5,5642.1679375)(1592.5,5967.94825)(1602,6241.055)};
 \addlegendentry{OstrichCEA}
 
-\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(8.5,0.0501875)(24.5,0.1841875)(40.5,0.385375)(56.5,0.63275)(72.5,0.9063125)(88.5,1.2073125)(104.5,1.53075)(120.5,1.878625)(136.5,2.248)(152.5,2.6435)(168.5,3.0511875)(184.5,3.4775625)(200.5,3.919)(216.5,4.3756875)(232.5,4.8543125)(248.5,5.36475)(264.5,5.91125)(280.5,6.499375)(296.5,7.1506875)(312.5,7.8543125)(328.5,8.594375)(344.5,9.3725)(360.5,10.1935625)(376.5,11.092875)(392.5,12.035125)(408.5,13.0169375)(424.5,14.058375)(440.5,15.1575625)(456.5,16.3101875)(472.5,17.5235)(488.5,18.79075)(504.5,20.1346875)(520.5,21.5568125)(536.5,23.0485)(552.5,24.6221875)(568.5,26.2756875)(584.5,28.0125625)(600.5,29.863375)(616.5,31.8353125)(632.5,33.9231875)(648.5,36.124625)(664.5,38.4406875)(680.5,40.8851875)(696.5,43.4551875)(712.5,46.18625)(728.5,49.20325)(744.5,52.4388125)(760.5,55.897625)(776.5,59.6255)(792.5,63.556125)(808.5,67.7344375)(824.5,72.17275)(840.5,76.87375)(856.5,81.881625)(872.5,87.2705625)(888.5,92.9146875)(904.5,98.791)(920.5,104.930125)(936.5,111.3364375)(952.5,118.0683125)(968.5,125.098375)(984.5,132.4871875)(1000.5,140.3285625)(1016.5,148.5753125)(1032.5,157.201)(1048.5,166.2395)(1064.5,175.6414375)(1080.5,185.51025)(1096.5,195.957375)(1112.5,207.0698125)(1128.5,218.7384375)(1144.5,231.084125)(1160.5,244.2318125)(1176.5,257.92525)(1192.5,272.16775)(1208.5,287.037)(1224.5,302.7649375)(1240.5,319.7085625)(1256.5,337.873375)(1272.5,357.1653125)(1288.5,377.8138125)(1304.5,399.751125)(1320.5,424.0613125)(1336.5,450.661375)(1352.5,478.92)(1368.5,509.38125)(1384.5,543.107)(1400.5,581.489375)(1416.5,625.1093125)(1432.5,675.3388125)(1448.5,738.061)(1464.5,823.3106875)(1480.5,947.367625)(1496.5,1193.47425)(1512.5,1639.0449375)(1525,2121.9135555555554)(1531,2376.002)};
+\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt, dashed, dash pattern=on 2pt off 8pt] coordinates {(1,0.004)(8.5,0.0501875)(24.5,0.1841875)(40.5,0.385375)(56.5,0.63275)(72.5,0.9063125)(88.5,1.2073125)(104.5,1.53075)(120.5,1.878625)(136.5,2.248)(152.5,2.6435)(168.5,3.0511875)(184.5,3.4775625)(200.5,3.919)(216.5,4.3756875)(232.5,4.8543125)(248.5,5.36475)(264.5,5.91125)(280.5,6.499375)(296.5,7.1506875)(312.5,7.8543125)(328.5,8.594375)(344.5,9.3725)(360.5,10.1935625)(376.5,11.092875)(392.5,12.035125)(408.5,13.0169375)(424.5,14.058375)(440.5,15.1575625)(456.5,16.3101875)(472.5,17.5235)(488.5,18.79075)(504.5,20.1346875)(520.5,21.5568125)(536.5,23.0485)(552.5,24.6221875)(568.5,26.2756875)(584.5,28.0125625)(600.5,29.863375)(616.5,31.8353125)(632.5,33.9231875)(648.5,36.124625)(664.5,38.4406875)(680.5,40.8851875)(696.5,43.4551875)(712.5,46.18625)(728.5,49.20325)(744.5,52.4388125)(760.5,55.897625)(776.5,59.6255)(792.5,63.556125)(808.5,67.7344375)(824.5,72.17275)(840.5,76.87375)(856.5,81.881625)(872.5,87.2705625)(888.5,92.9146875)(904.5,98.791)(920.5,104.930125)(936.5,111.3364375)(952.5,118.0683125)(968.5,125.098375)(984.5,132.4871875)(1000.5,140.3285625)(1016.5,148.5753125)(1032.5,157.201)(1048.5,166.2395)(1064.5,175.6414375)(1080.5,185.51025)(1096.5,195.957375)(1112.5,207.0698125)(1128.5,218.7384375)(1144.5,231.084125)(1160.5,244.2318125)(1176.5,257.92525)(1192.5,272.16775)(1208.5,287.037)(1224.5,302.7649375)(1240.5,319.7085625)(1256.5,337.873375)(1272.5,357.1653125)(1288.5,377.8138125)(1304.5,399.751125)(1320.5,424.0613125)(1336.5,450.661375)(1352.5,478.92)(1368.5,509.38125)(1384.5,543.107)(1400.5,581.489375)(1416.5,625.1093125)(1432.5,675.3388125)(1448.5,738.061)(1464.5,823.3106875)(1480.5,947.367625)(1496.5,1193.47425)(1512.5,1639.0449375)(1525,2121.9135555555554)(1531,2376.002)};
 \addlegendentry{CVC5}
 
-\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,1.017)(8,10.258933333333333)(23,29.255599999999998)(38,50.394800000000004)(53,72.92853333333333)(68,96.32026666666667)(83,120.54106666666667)(98,145.43706666666668)(113,170.85453333333334)(128,196.90246666666667)(143,223.42426666666665)(158,250.6794)(173,278.59159999999997)(188,307.04659999999996)(203,336.0550666666667)(218,365.4665333333333)(233,395.2475333333333)(248,425.3532)(263,455.8623333333333)(278,486.82626666666664)(293,518.2761333333334)(308,550.2016666666666)(323,582.5965333333334)(338,615.5299333333334)(353,648.8835333333333)(368,682.6476)(383,716.8438000000001)(398,751.3936)(413,786.4327333333333)(428,821.8758)(443,857.6266666666667)(458,893.7378666666667)(473,930.2567333333333)(488,967.1976)(503,1004.5210666666667)(518,1042.2291333333333)(533,1080.4326)(548,1119.0616666666667)(563,1158.132)(578,1197.6022666666665)(593,1237.5477333333333)(608,1278.0738666666666)(623,1319.0354)(638,1360.3044666666665)(653,1401.9102)(668,1443.9781333333333)(683,1486.5155333333335)(698,1529.4671333333333)(713,1573.0057333333334)(728,1617.0829333333334)(743,1661.8119333333334)(758,1707.0376)(773,1752.8307333333335)(788,1799.0442666666665)(803,1845.8358666666668)(818,1893.2626)(833,1941.298)(848,1990.1431333333333)(863,2039.6957333333335)(878,2089.9846666666667)(893,2141.0992666666666)(908,2193.0147333333334)(923,2245.761466666667)(938,2299.109466666667)(953,2353.2702666666664)(968,2408.4814666666666)(983,2464.6888)(998,2521.7824)(1013,2579.9236666666666)(1028,2639.587466666667)(1043,2701.1523333333334)(1058,2764.0695333333333)(1073,2827.9558666666667)(1088,2893.3823333333335)(1103,2960.3417999999997)(1118,3029.4202666666665)(1133,3100.2347999999997)(1148,3173.076866666667)(1163,3248.1202000000003)(1178,3326.137866666667)(1193,3407.703)(1208,3491.8776666666663)(1223,3578.656933333333)(1238,3668.5506)(1253,3762.1326666666664)(1268,3859.274933333333)(1283,3961.9732666666664)(1298,4070.4924666666666)(1313,4186.787066666667)(1328,4310.513400000001)(1343,4445.3554)(1358,4594.592466666667)(1373,4759.808933333334)(1388,4944.383400000001)(1403,5149.614333333333)(1418,5387.352599999999)(1433,5664.111533333333)(1448,5990.5318)(1463,6394.039400000001)(1478,6895.506266666666)(1493,7542.774266666666)(1502,7966.798)};
+\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,1.017)(8,10.258933333333333)(23,29.255599999999998)(38,50.394800000000004)(53,72.92853333333333)(68,96.32026666666667)(83,120.54106666666667)(98,145.43706666666668)(113,170.85453333333334)(128,196.90246666666667)(143,223.42426666666665)(158,250.6794)(173,278.59159999999997)(188,307.04659999999996)(203,336.0550666666667)(218,365.4665333333333)(233,395.2475333333333)(248,425.3532)(263,455.8623333333333)(278,486.82626666666664)(293,518.2761333333334)(308,550.2016666666666)(323,582.5965333333334)(338,615.5299333333334)(353,648.8835333333333)(368,682.6476)(383,716.8438000000001)(398,751.3936)(413,786.4327333333333)(428,821.8758)(443,857.6266666666667)(458,893.7378666666667)(473,930.2567333333333)(488,967.1976)(503,1004.5210666666667)(518,1042.2291333333333)(533,1080.4326)(548,1119.0616666666667)(563,1158.132)(578,1197.6022666666665)(593,1237.5477333333333)(608,1278.0738666666666)(623,1319.0354)(638,1360.3044666666665)(653,1401.9102)(668,1443.9781333333333)(683,1486.5155333333335)(698,1529.4671333333333)(713,1573.0057333333334)(728,1617.0829333333334)(743,1661.8119333333334)(758,1707.0376)(773,1752.8307333333335)(788,1799.0442666666665)(803,1845.8358666666668)(818,1893.2626)(833,1941.298)(848,1990.1431333333333)(863,2039.6957333333335)(878,2089.9846666666667)(893,2141.0992666666666)(908,2193.0147333333334)(923,2245.761466666667)(938,2299.109466666667)(953,2353.2702666666664)(968,2408.4814666666666)(983,2464.6888)(998,2521.7824)(1013,2579.9236666666666)(1028,2639.587466666667)(1043,2701.1523333333334)(1058,2764.0695333333333)(1073,2827.9558666666667)(1088,2893.3823333333335)(1103,2960.3417999999997)(1118,3029.4202666666665)(1133,3100.2347999999997)(1148,3173.076866666667)(1163,3248.1202000000003)(1178,3326.137866666667)(1193,3407.703)(1208,3491.8776666666663)(1223,3578.656933333333)(1238,3668.5506)(1253,3762.1326666666664)(1268,3859.274933333333)(1283,3961.9732666666664)(1298,4070.4924666666666)(1313,4186.787066666667)(1328,4310.513400000001)(1343,4445.3554)(1358,4594.592466666667)(1373,4759.808933333334)(1388,4944.383400000001)(1403,5149.614333333333)(1418,5387.352599999999)(1433,5664.111533333333)(1448,5990.5318)(1463,6394.039400000001)(1478,6895.506266666666)(1493,7542.774266666666)(1502,7966.798)};
 \addlegendentry{Ostrich}
 
-\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.014)(8,0.1492666666666667)(23,0.43839999999999996)(38,0.7554)(53,1.0912666666666666)(68,1.446)(83,1.8062)(98,2.176)(113,2.551)(128,2.929)(143,3.318)(158,3.7084)(173,4.109)(188,4.517)(203,4.936)(218,5.362066666666666)(233,5.7984)(248,6.246666666666667)(263,6.708)(278,7.1781999999999995)(293,7.658066666666667)(308,8.147)(323,8.6444)(338,9.153)(353,9.669066666666668)(368,10.1942)(383,10.729)(398,11.269666666666666)(413,11.821)(428,12.376666666666667)(443,12.943)(458,13.514)(473,14.0964)(488,14.692)(503,15.2944)(518,15.9082)(533,16.533)(548,17.166666666666668)(563,17.8124)(578,18.47)(593,19.130666666666666)(608,19.802)(623,20.48)(638,21.169)(653,21.8642)(668,22.576)(683,23.3012)(698,24.039)(713,24.7904)(728,25.5542)(743,26.329066666666666)(758,27.1184)(773,27.927)(788,28.7524)(803,29.591866666666665)(818,30.448)(833,31.318)(848,32.201)(863,33.09986666666667)(878,34.01673333333333)(893,34.955666666666666)(908,35.91266666666667)(923,36.887)(938,37.8816)(953,38.8984)(968,39.93533333333333)(983,41.0048)(998,42.1114)(1013,43.2494)(1028,44.419066666666666)(1043,45.62166666666666)(1058,46.864466666666665)(1073,48.1382)(1088,49.4416)(1103,50.77926666666667)(1118,52.1594)(1133,53.60013333333333)(1148,55.10326666666667)(1163,56.676)(1178,58.32373333333333)(1193,60.0458)(1208,61.842400000000005)(1223,63.705933333333334)(1238,65.68766666666667)(1253,67.79246666666666)(1268,70.0094)(1283,72.42713333333333)(1298,75.1118)(1313,78.03226666666666)(1328,81.21066666666667)(1343,84.72706666666667)(1358,88.56126666666667)(1373,93.02126666666666)(1388,98.26266666666668)(1403,104.86593333333333)(1418,113.51339999999999)(1433,124.53553333333333)(1448,142.9748)(1463,195.25526666666667)(1473.5,343.9191666666667)(1478,471.791)};
+\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.014)(8,0.1492666666666667)(23,0.43839999999999996)(38,0.7554)(53,1.0912666666666666)(68,1.446)(83,1.8062)(98,2.176)(113,2.551)(128,2.929)(143,3.318)(158,3.7084)(173,4.109)(188,4.517)(203,4.936)(218,5.362066666666666)(233,5.7984)(248,6.246666666666667)(263,6.708)(278,7.1781999999999995)(293,7.658066666666667)(308,8.147)(323,8.6444)(338,9.153)(353,9.669066666666668)(368,10.1942)(383,10.729)(398,11.269666666666666)(413,11.821)(428,12.376666666666667)(443,12.943)(458,13.514)(473,14.0964)(488,14.692)(503,15.2944)(518,15.9082)(533,16.533)(548,17.166666666666668)(563,17.8124)(578,18.47)(593,19.130666666666666)(608,19.802)(623,20.48)(638,21.169)(653,21.8642)(668,22.576)(683,23.3012)(698,24.039)(713,24.7904)(728,25.5542)(743,26.329066666666666)(758,27.1184)(773,27.927)(788,28.7524)(803,29.591866666666665)(818,30.448)(833,31.318)(848,32.201)(863,33.09986666666667)(878,34.01673333333333)(893,34.955666666666666)(908,35.91266666666667)(923,36.887)(938,37.8816)(953,38.8984)(968,39.93533333333333)(983,41.0048)(998,42.1114)(1013,43.2494)(1028,44.419066666666666)(1043,45.62166666666666)(1058,46.864466666666665)(1073,48.1382)(1088,49.4416)(1103,50.77926666666667)(1118,52.1594)(1133,53.60013333333333)(1148,55.10326666666667)(1163,56.676)(1178,58.32373333333333)(1193,60.0458)(1208,61.842400000000005)(1223,63.705933333333334)(1238,65.68766666666667)(1253,67.79246666666666)(1268,70.0094)(1283,72.42713333333333)(1298,75.1118)(1313,78.03226666666666)(1328,81.21066666666667)(1343,84.72706666666667)(1358,88.56126666666667)(1373,93.02126666666666)(1388,98.26266666666668)(1403,104.86593333333333)(1418,113.51339999999999)(1433,124.53553333333333)(1448,142.9748)(1463,195.25526666666667)(1473.5,343.9191666666667)(1478,471.791)};
 \addlegendentry{Z3str3}
 
-\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.014)(8.5,0.1705625)(24.5,0.5270625)(40.5,0.9435)(56.5,1.411375)(72.5,1.9261875)(88.5,2.471375)(104.5,3.0486875)(120.5,3.6491875)(136.5,4.26925)(152.5,4.9183125)(168.5,5.59575)(184.5,6.2953125)(200.5,7.0183125)(216.5,7.7696875)(232.5,8.552625)(248.5,9.361625)(264.5,10.20875)(280.5,11.08875)(296.5,11.9946875)(312.5,12.9349375)(328.5,13.899875)(344.5,14.886625)(360.5,15.894625)(376.5,16.93)(392.5,18.009)(408.5,19.1270625)(424.5,20.2855625)(440.5,21.4935)(456.5,22.751125)(472.5,24.069375)(488.5,25.446875)(504.5,26.8915)(520.5,28.4119375)(536.5,30.015375)(552.5,31.7089375)(568.5,33.4641875)(584.5,35.2725)(600.5,37.1615)(616.5,39.151125)(632.5,41.2473125)(648.5,43.431625)(664.5,45.6884375)(680.5,48.03575)(696.5,50.4545)(712.5,52.9450625)(728.5,55.5413125)(744.5,58.2293125)(760.5,60.9836875)(776.5,63.813375)(792.5,66.7405)(808.5,69.76075)(824.5,72.8876875)(840.5,76.128)(856.5,79.4839375)(872.5,82.9761875)(888.5,86.62225)(904.5,90.3834375)(920.5,94.26825)(936.5,98.3461875)(952.5,102.5914375)(968.5,107.029625)(984.5,111.6445625)(1000.5,116.4698125)(1016.5,121.504625)(1032.5,126.7716875)(1048.5,132.2453125)(1064.5,137.9896875)(1080.5,144.0614375)(1096.5,150.38)(1112.5,156.9101875)(1128.5,163.803625)(1144.5,171.048375)(1160.5,178.675875)(1176.5,186.5573125)(1192.5,194.7738125)(1208.5,203.287375)(1224.5,212.0685)(1240.5,221.080125)(1256.5,230.4013125)(1272.5,240.2630625)(1288.5,250.769125)(1304.5,261.9256875)(1320.5,273.955125)(1336.5,286.6981875)(1352.5,300.027625)(1368.5,314.1886875)(1384.5,329.4320625)(1400.5,345.72025)(1416.5,363.0874375)(1432.5,381.555625)(1448.5,401.5385)(1464.5,423.8074375)(1480.5,448.4118125)(1496.5,476.286125)(1512.5,510.4356875)(1528.5,553.1431875)(1544.5,607.709625)(1560.5,678.581375)(1576.5,800.2424375)(1587,950.0282)(1591,1061.191)};
+\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1pt off 2pt] coordinates {(1,0.014)(8.5,0.1705625)(24.5,0.5270625)(40.5,0.9435)(56.5,1.411375)(72.5,1.9261875)(88.5,2.471375)(104.5,3.0486875)(120.5,3.6491875)(136.5,4.26925)(152.5,4.9183125)(168.5,5.59575)(184.5,6.2953125)(200.5,7.0183125)(216.5,7.7696875)(232.5,8.552625)(248.5,9.361625)(264.5,10.20875)(280.5,11.08875)(296.5,11.9946875)(312.5,12.9349375)(328.5,13.899875)(344.5,14.886625)(360.5,15.894625)(376.5,16.93)(392.5,18.009)(408.5,19.1270625)(424.5,20.2855625)(440.5,21.4935)(456.5,22.751125)(472.5,24.069375)(488.5,25.446875)(504.5,26.8915)(520.5,28.4119375)(536.5,30.015375)(552.5,31.7089375)(568.5,33.4641875)(584.5,35.2725)(600.5,37.1615)(616.5,39.151125)(632.5,41.2473125)(648.5,43.431625)(664.5,45.6884375)(680.5,48.03575)(696.5,50.4545)(712.5,52.9450625)(728.5,55.5413125)(744.5,58.2293125)(760.5,60.9836875)(776.5,63.813375)(792.5,66.7405)(808.5,69.76075)(824.5,72.8876875)(840.5,76.128)(856.5,79.4839375)(872.5,82.9761875)(888.5,86.62225)(904.5,90.3834375)(920.5,94.26825)(936.5,98.3461875)(952.5,102.5914375)(968.5,107.029625)(984.5,111.6445625)(1000.5,116.4698125)(1016.5,121.504625)(1032.5,126.7716875)(1048.5,132.2453125)(1064.5,137.9896875)(1080.5,144.0614375)(1096.5,150.38)(1112.5,156.9101875)(1128.5,163.803625)(1144.5,171.048375)(1160.5,178.675875)(1176.5,186.5573125)(1192.5,194.7738125)(1208.5,203.287375)(1224.5,212.0685)(1240.5,221.080125)(1256.5,230.4013125)(1272.5,240.2630625)(1288.5,250.769125)(1304.5,261.9256875)(1320.5,273.955125)(1336.5,286.6981875)(1352.5,300.027625)(1368.5,314.1886875)(1384.5,329.4320625)(1400.5,345.72025)(1416.5,363.0874375)(1432.5,381.555625)(1448.5,401.5385)(1464.5,423.8074375)(1480.5,448.4118125)(1496.5,476.286125)(1512.5,510.4356875)(1528.5,553.1431875)(1544.5,607.709625)(1560.5,678.581375)(1576.5,800.2424375)(1587,950.0282)(1591,1061.191)};
 \addlegendentry{Z3seq}
 
-\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.005)(8.5,0.0531875)(24.5,0.1518125)(40.5,0.2625)(56.5,0.3745)(72.5,0.4865)(88.5,0.5985)(104.5,0.7105)(120.5,0.8253125)(136.5,0.952)(152.5,1.08)(168.5,1.208)(184.5,1.336)(200.5,1.464375)(216.5,1.6035)(232.5,1.7475)(248.5,1.8915)(264.5,2.0355)(280.5,2.1795)(296.5,2.3235)(312.5,2.4675)(328.5,2.6116875)(344.5,2.766)(360.5,2.926)(376.5,3.086)(392.5,3.246)(408.5,3.406)(424.5,3.566)(440.5,3.726)(456.5,3.8873125)(472.5,4.0605)(488.5,4.2365)(504.5,4.4125)(520.5,4.5885)(536.5,4.7645)(552.5,4.9439375)(568.5,5.135)(584.5,5.327)(600.5,5.519)(616.5,5.7175625)(632.5,5.9255)(648.5,6.134125)(664.5,6.354)(680.5,6.5789375)(696.5,6.8155)(712.5,7.056125)(728.5,7.308)(744.5,7.568125)(760.5,7.840125)(776.5,8.124)(792.5,8.4185625)(808.5,8.7234375)(824.5,9.04)(840.5,9.3665625)(856.5,9.7038125)(872.5,10.053)(888.5,10.4084375)(904.5,10.7755)(920.5,11.147625)(936.5,11.5323125)(952.5,11.9296875)(968.5,12.340625)(984.5,12.7685)(1000.5,13.2081875)(1016.5,13.66875)(1032.5,14.14875)(1048.5,14.64475)(1064.5,15.15725)(1080.5,15.691375)(1096.5,16.2514375)(1112.5,16.8374375)(1128.5,17.4513125)(1144.5,18.10075)(1160.5,18.782875)(1176.5,19.5125)(1192.5,20.281875)(1208.5,21.093125)(1224.5,21.9540625)(1240.5,22.867)(1256.5,23.8339375)(1272.5,24.876125)(1288.5,26.007125)(1304.5,27.2279375)(1320.5,28.564875)(1336.5,29.9903125)(1352.5,31.529875)(1368.5,33.237)(1384.5,35.1899375)(1400.5,37.4680625)(1416.5,40.07125)(1432.5,43.1341875)(1448.5,46.8099375)(1464.5,51.341)(1480.5,57.03675)(1496.5,64.4295)(1512.5,73.6899375)(1528.5,86.0960625)(1544.5,108.3425)(1560.5,174.1435625)(1569.5,260.0555)(1572,300.23)};
+\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt, dashed, dash pattern=on 2pt off 4pt] coordinates {(1,0.005)(8.5,0.0531875)(24.5,0.1518125)(40.5,0.2625)(56.5,0.3745)(72.5,0.4865)(88.5,0.5985)(104.5,0.7105)(120.5,0.8253125)(136.5,0.952)(152.5,1.08)(168.5,1.208)(184.5,1.336)(200.5,1.464375)(216.5,1.6035)(232.5,1.7475)(248.5,1.8915)(264.5,2.0355)(280.5,2.1795)(296.5,2.3235)(312.5,2.4675)(328.5,2.6116875)(344.5,2.766)(360.5,2.926)(376.5,3.086)(392.5,3.246)(408.5,3.406)(424.5,3.566)(440.5,3.726)(456.5,3.8873125)(472.5,4.0605)(488.5,4.2365)(504.5,4.4125)(520.5,4.5885)(536.5,4.7645)(552.5,4.9439375)(568.5,5.135)(584.5,5.327)(600.5,5.519)(616.5,5.7175625)(632.5,5.9255)(648.5,6.134125)(664.5,6.354)(680.5,6.5789375)(696.5,6.8155)(712.5,7.056125)(728.5,7.308)(744.5,7.568125)(760.5,7.840125)(776.5,8.124)(792.5,8.4185625)(808.5,8.7234375)(824.5,9.04)(840.5,9.3665625)(856.5,9.7038125)(872.5,10.053)(888.5,10.4084375)(904.5,10.7755)(920.5,11.147625)(936.5,11.5323125)(952.5,11.9296875)(968.5,12.340625)(984.5,12.7685)(1000.5,13.2081875)(1016.5,13.66875)(1032.5,14.14875)(1048.5,14.64475)(1064.5,15.15725)(1080.5,15.691375)(1096.5,16.2514375)(1112.5,16.8374375)(1128.5,17.4513125)(1144.5,18.10075)(1160.5,18.782875)(1176.5,19.5125)(1192.5,20.281875)(1208.5,21.093125)(1224.5,21.9540625)(1240.5,22.867)(1256.5,23.8339375)(1272.5,24.876125)(1288.5,26.007125)(1304.5,27.2279375)(1320.5,28.564875)(1336.5,29.9903125)(1352.5,31.529875)(1368.5,33.237)(1384.5,35.1899375)(1400.5,37.4680625)(1416.5,40.07125)(1432.5,43.1341875)(1448.5,46.8099375)(1464.5,51.341)(1480.5,57.03675)(1496.5,64.4295)(1512.5,73.6899375)(1528.5,86.0960625)(1544.5,108.3425)(1560.5,174.1435625)(1569.5,260.0555)(1572,300.23)};
 \addlegendentry{Z3str3RE}
 
-\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.014)(5.5,0.0965)(15.5,0.24659999999999999)(25.5,0.5291)(35.5,1.7757)(45.5,3.2819000000000003)(55.5,4.8925)(65.5,6.6395)(75.5,8.5756)(85.5,10.7695)(95.5,13.3338)(105.5,16.0888)(115.5,18.911099999999998)(125.5,21.776799999999998)(135.5,24.681)(145.5,27.6301)(155.5,30.6199)(165.5,33.670199999999994)(175.5,36.7772)(185.5,39.9617)(195.5,43.211400000000005)(205.5,46.5163)(215.5,49.8973)(225.5,53.3431)(235.5,56.839)(245.5,60.3826)(255.5,63.9905)(265.5,67.68169999999999)(275.5,71.49210000000001)(285.5,75.4175)(295.5,79.4315)(305.5,83.5275)(315.5,87.7416)(325.5,92.0531)(335.5,96.4757)(345.5,101.06960000000001)(355.5,105.7476)(365.5,110.49980000000001)(375.5,115.3315)(385.5,120.26480000000001)(395.5,125.32130000000001)(405.5,130.55780000000001)(415.5,135.9472)(425.5,141.4926)(435.5,147.1716)(445.5,152.968)(455.5,158.89479999999998)(465.5,164.9966)(475.5,171.2354)(485.5,177.6876)(495.5,184.32629999999997)(505.5,191.2884)(515.5,198.55870000000002)(525.5,206.118)(535.5,213.86720000000003)(545.5,221.7994)(555.5,229.9578)(565.5,238.4017)(575.5,247.17370000000003)(585.5,256.3306)(595.5,265.9233)(605.5,275.932)(615.5,286.358)(625.5,297.2522)(635.5,308.8544)(645.5,321.24490000000003)(655.5,334.15770000000003)(665.5,347.7744)(675.5,362.2491)(685.5,377.95820000000003)(695.5,394.631)(705.5,412.767)(715.5,431.72229999999996)(725.5,451.7528)(735.5,473.7269)(745.5,497.888)(755.5,523.4656)(765.5,550.4038)(775.5,579.6903000000001)(785.5,611.273)(795.5,645.323)(805.5,681.6165)(815.5,720.9826999999999)(825.5,761.813)(835.5,805.1531)(845.5,853.2948)(855.5,907.36)(865.5,969.3392)(875.5,1043.5174)(885.5,1131.0648999999999)(895.5,1238.9723999999999)(905.5,1375.8621)(915.5,1533.0866)(925.5,1712.4778000000001)(935.5,1928.2462)(945.5,2203.0395)(955.5,2557.4988)(963,2921.2174)(967,3095.75)};
+\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt, dashed, dash pattern=on 4pt off 2pt] coordinates {(1,0.014)(5.5,0.0965)(15.5,0.24659999999999999)(25.5,0.5291)(35.5,1.7757)(45.5,3.2819000000000003)(55.5,4.8925)(65.5,6.6395)(75.5,8.5756)(85.5,10.7695)(95.5,13.3338)(105.5,16.0888)(115.5,18.911099999999998)(125.5,21.776799999999998)(135.5,24.681)(145.5,27.6301)(155.5,30.6199)(165.5,33.670199999999994)(175.5,36.7772)(185.5,39.9617)(195.5,43.211400000000005)(205.5,46.5163)(215.5,49.8973)(225.5,53.3431)(235.5,56.839)(245.5,60.3826)(255.5,63.9905)(265.5,67.68169999999999)(275.5,71.49210000000001)(285.5,75.4175)(295.5,79.4315)(305.5,83.5275)(315.5,87.7416)(325.5,92.0531)(335.5,96.4757)(345.5,101.06960000000001)(355.5,105.7476)(365.5,110.49980000000001)(375.5,115.3315)(385.5,120.26480000000001)(395.5,125.32130000000001)(405.5,130.55780000000001)(415.5,135.9472)(425.5,141.4926)(435.5,147.1716)(445.5,152.968)(455.5,158.89479999999998)(465.5,164.9966)(475.5,171.2354)(485.5,177.6876)(495.5,184.32629999999997)(505.5,191.2884)(515.5,198.55870000000002)(525.5,206.118)(535.5,213.86720000000003)(545.5,221.7994)(555.5,229.9578)(565.5,238.4017)(575.5,247.17370000000003)(585.5,256.3306)(595.5,265.9233)(605.5,275.932)(615.5,286.358)(625.5,297.2522)(635.5,308.8544)(645.5,321.24490000000003)(655.5,334.15770000000003)(665.5,347.7744)(675.5,362.2491)(685.5,377.95820000000003)(695.5,394.631)(705.5,412.767)(715.5,431.72229999999996)(725.5,451.7528)(735.5,473.7269)(745.5,497.888)(755.5,523.4656)(765.5,550.4038)(775.5,579.6903000000001)(785.5,611.273)(795.5,645.323)(805.5,681.6165)(815.5,720.9826999999999)(825.5,761.813)(835.5,805.1531)(845.5,853.2948)(855.5,907.36)(865.5,969.3392)(875.5,1043.5174)(885.5,1131.0648999999999)(895.5,1238.9723999999999)(905.5,1375.8621)(915.5,1533.0866)(925.5,1712.4778000000001)(935.5,1928.2462)(945.5,2203.0395)(955.5,2557.4988)(963,2921.2174)(967,3095.75)};
 \addlegendentry{Z3-Trau}

### 2023-05-04 2023-1-19/sections/algorithms.tex
experiment done
from recl to cefa

@@
 
-As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers instead of unfolding them explicitly.
+The goal of this section is to show how we solve RECL constraints by utilizing CEFA. 
+At first, we show how to reduce the satisfiability of RECL constraints into a decision problem for CEFA defined in the sequel. Then we propose algorithms to solve the decision problem.
+
+\begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula\footnote{The decision problem was called satisfiability of an LIA formula w.r.t. CEFA in \cite{atva2020}.}, abbreviated as $\cefadec$]
+Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+Then  the CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are said to be nonempty w.r.t.
+$\varphi$ if there are an assignment $\eta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors
+$\myvec{v_{1,1}}, \cdots, \myvec{v_{1, l_1}}, \cdots, \myvec{v_{n, 1}}, \cdots, \myvec{v_{n, l_n}}$ such that $(w_i; \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ for every $i \in [n], j \in [l_i]$,
+% \in \aut_{i,1}(\eta(x_1)), \cdots, \myvec{v_{i, l_i}} \in \aut_{i,l_i}(\eta(x_i))$ for every $i \in [n]$  
+%\cdots, \myvec{v_{n,1}} \in \aut_{n,1}(w_n), \cdots, \myvec{v_{n, l_n}} \in \aut_{n, l_n}(w_n)$ 
+and $\varphi[\myvec{v_{1,1}}/R_{\aut_{1,1}}, \cdots, \myvec{v_{n, l_n}}/R_{\aut_{n, l_n}}]$ is true. 
+\end{definition}
+
+\begin{proposition}[\cite{atva2020}]\label{prop-cefadec}
+$\cefadec$ is PSPACE-complete. 
+\end{proposition}
+The decision procedure for proving the upper bound in Proposition~\ref{prop-cefadec} in \cite{atva2020}  was not implemented as a matter of fact.
+Instead, the symbolic model checker nuXmv was used to solve $\cefadec$ in \cite{atva2020}.
+We do not rely on nuXmv in this work and will propose an efficient algorithm for solving $\cefadec$ in Section~\ref{subsec:cefadec}.
+
+%As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers instead of unfolding them explicitly.
 Additionally, we use registers to represent string lengths.
@@
 We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
-\subsection{Encode Regex with Counting to CEFA} \label{subsec:regex2cefa}
+
+\subsection{From $\reclsat$ to $\cefadec$} \label{subsec:regex2cefa}
+
+Let $\varphi$ be an RECL constraint. We shall reduce the satisfiability of $\varphi$ to an instance of $\cefadec$.
+
+At first, we show how to construct a CEFA from a regular expression where counting operators may occur.
+
+Let $e$ be a regular expression and $(e')^{\{m,n\}}$ be an occurrence of the counting operators in $e$.
+Then $(e')^{\{m,n\}}$ is said to be \emph{persistent} in $e$ if  $(e')^{\{m,n\}}$ is not in the scope of a complement, Kleene star, or counting operator in $e$.
+
 The most important point of our approach is encoding counting operators by registers rather than explicitly unfolding them.
@@
 To solve it efficiently for a practical example, we develop heuristic ways such as under-approximation (Section \ref{subsec:under-approx}) and symbolic-aware simplification (Section \ref{subsec:simplify}).
-\subsection{Handling of String-length}
+
+%\subsection{Handling of String-length}
 Given a string-length constraint, we build a CEFA with a register storing the word length.
@@
 
-\subsection{Emptiness Checking Problem on CEFAs} \label{subsec:emptiness}
+\subsection{Solving $\cefadec$} \label{subsec:cefadec}
 After encoding counting operator and length constraint to CEFAs, there are only automaton memberships $x\in \aut$ and LIA formula $t_1 \ \op \ t_2$ where $\aut$ is CEFA and $t_1, t_2$ are integer terms.

### 2023-05-04 2023-1-19/sections/preliminaries.tex
from recl to cefa

@@
 For a set $X$ of variables, we use $\Phi(X)$ to denote the set of quantifier-free LIA formulas whose free variables are from $X$. 
+For convenience, we use $\varphi(\vec{x})$ with $\myvec{x} = (x_1, \cdots, x_k)$ to denote an LIA formula $\varphi$ whose free variables are from $\{x_1, \cdots, x_k\}$.
+For an LIA formula $\varphi(\vec{x})$ with $\myvec{x} = (x_1, \cdots, x_k)$ and $\myvec{n} = (n_1, \cdots, n_k) \in \Int^k$, we use $\varphi[\myvec{n}/\myvec{x}]$ to denote the formula obtained by replacing $x_i$ with $n_i$ for each $i \in [k]$.
+%For convenience, we usually assume that a set $X$ of variables is a vector. 
 %, which is essentially Presburger

### 2023-05-04 2023-1-19/figures/cactus_plot_stackoverflow.tex

@@
 \resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=stackoverflow,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
-\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(167.5,0.7233143712574851)(501.5,2.424832335329341)(835.5,4.471230538922155)(1169.5,7.107095808383233)(1503.5,10.389062874251497)(1837.5,14.099278443113771)(2171.5,18.174152694610775)(2505.5,22.56328143712575)(2839.5,27.240485029940118)(3173.5,32.199152694610774)(3507.5,37.44004491017964)(3841.5,42.9565)(4175.5,48.74484730538922)(4509.5,54.80647305389222)(4843.5,61.164)(5177.5,67.82197005988024)(5511.5,74.77786826347305)(5845.5,82.05068862275449)(6179.5,89.64715269461078)(6513.5,97.57394011976048)(6847.5,105.86460479041916)(7181.5,114.52601796407185)(7515.5,123.56620359281438)(7849.5,133.02156886227544)(8183.5,142.95500898203593)(8517.5,153.42188023952096)(8851.5,164.45122754491018)(9185.5,176.06351796407185)(9519.5,188.34054790419162)(9853.5,201.33261676646708)(10187.5,215.11561676646707)(10521.5,229.66456886227544)(10855.5,244.98857185628742)(11189.5,261.1554341317365)(11523.5,278.16943113772453)(11857.5,296.0684610778443)(12191.5,314.8944161676647)(12525.5,334.76406886227545)(12859.5,355.686380239521)(13193.5,377.6354700598802)(13527.5,400.7926766467066)(13861.5,425.26753293413174)(14195.5,451.1214670658683)(14529.5,478.60874251497006)(14863.5,507.8448353293413)(15197.5,538.9790179640718)(15531.5,572.0008802395209)(15865.5,607.0877035928144)(16199.5,644.1859670658683)(16533.5,683.3988143712575)(16867.5,724.9113922155688)(17201.5,768.7641467065869)(17535.5,815.1436047904191)(17869.5,864.0901227544911)(18203.5,915.7329730538922)(18537.5,970.133739520958)(18871.5,1027.413368263473)(19205.5,1088.0779311377246)(19539.5,1152.6376377245508)(19873.5,1221.4731976047904)(20207.5,1294.8711916167663)(20541.5,1373.1157784431136)(20875.5,1457.0711646706588)(21209.5,1547.5486616766466)(21543.5,1645.0836676646707)(21877.5,1749.5506556886228)(22211.5,1861.3744251497005)(22545.5,1980.2774341317365)(22879.5,2106.45052994012)(23213.5,2240.55351497006)(23547.5,2382.9252964071857)(23881.5,2533.9247964071856)(24215.5,2694.0401377245507)(24549.5,2863.199398203593)(24883.5,3042.0251796407188)(25217.5,3230.280344311377)(25551.5,3428.0554790419164)(25885.5,3636.7262814371256)(26219.5,3857.1243083832333)(26553.5,4090.237161676647)(26887.5,4338.172107784431)(27221.5,4602.643706586827)(27555.5,4887.577766467066)(27889.5,5196.619589820359)(28223.5,5533.495835329341)(28557.5,5904.957110778443)(28891.5,6318.40652994012)(29225.5,6784.988535928144)(29559.5,7319.875413173652)(29893.5,7949.884458083832)(30227.5,8725.226431137724)(30561.5,9789.064071856288)(30895.5,11265.184853293413)(31229.5,13413.724155688624)(31563.5,16944.67256287425)(31897.5,22938.68886227545)(32231.5,32316.48101497006)(32549.5,45359.79038741722)(32702,53261.719)};
+\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt, dashed, dash pattern=on 2pt off 8pt] coordinates {(1,0.004)(167.5,0.7233143712574851)(501.5,2.424832335329341)(835.5,4.471230538922155)(1169.5,7.107095808383233)(1503.5,10.389062874251497)(1837.5,14.099278443113771)(2171.5,18.174152694610775)(2505.5,22.56328143712575)(2839.5,27.240485029940118)(3173.5,32.199152694610774)(3507.5,37.44004491017964)(3841.5,42.9565)(4175.5,48.74484730538922)(4509.5,54.80647305389222)(4843.5,61.164)(5177.5,67.82197005988024)(5511.5,74.77786826347305)(5845.5,82.05068862275449)(6179.5,89.64715269461078)(6513.5,97.57394011976048)(6847.5,105.86460479041916)(7181.5,114.52601796407185)(7515.5,123.56620359281438)(7849.5,133.02156886227544)(8183.5,142.95500898203593)(8517.5,153.42188023952096)(8851.5,164.45122754491018)(9185.5,176.06351796407185)(9519.5,188.34054790419162)(9853.5,201.33261676646708)(10187.5,215.11561676646707)(10521.5,229.66456886227544)(10855.5,244.98857185628742)(11189.5,261.1554341317365)(11523.5,278.16943113772453)(11857.5,296.0684610778443)(12191.5,314.8944161676647)(12525.5,334.76406886227545)(12859.5,355.686380239521)(13193.5,377.6354700598802)(13527.5,400.7926766467066)(13861.5,425.26753293413174)(14195.5,451.1214670658683)(14529.5,478.60874251497006)(14863.5,507.8448353293413)(15197.5,538.9790179640718)(15531.5,572.0008802395209)(15865.5,607.0877035928144)(16199.5,644.1859670658683)(16533.5,683.3988143712575)(16867.5,724.9113922155688)(17201.5,768.7641467065869)(17535.5,815.1436047904191)(17869.5,864.0901227544911)(18203.5,915.7329730538922)(18537.5,970.133739520958)(18871.5,1027.413368263473)(19205.5,1088.0779311377246)(19539.5,1152.6376377245508)(19873.5,1221.4731976047904)(20207.5,1294.8711916167663)(20541.5,1373.1157784431136)(20875.5,1457.0711646706588)(21209.5,1547.5486616766466)(21543.5,1645.0836676646707)(21877.5,1749.5506556886228)(22211.5,1861.3744251497005)(22545.5,1980.2774341317365)(22879.5,2106.45052994012)(23213.5,2240.55351497006)(23547.5,2382.9252964071857)(23881.5,2533.9247964071856)(24215.5,2694.0401377245507)(24549.5,2863.199398203593)(24883.5,3042.0251796407188)(25217.5,3230.280344311377)(25551.5,3428.0554790419164)(25885.5,3636.7262814371256)(26219.5,3857.1243083832333)(26553.5,4090.237161676647)(26887.5,4338.172107784431)(27221.5,4602.643706586827)(27555.5,4887.577766467066)(27889.5,5196.619589820359)(28223.5,5533.495835329341)(28557.5,5904.957110778443)(28891.5,6318.40652994012)(29225.5,6784.988535928144)(29559.5,7319.875413173652)(29893.5,7949.884458083832)(30227.5,8725.226431137724)(30561.5,9789.064071856288)(30895.5,11265.184853293413)(31229.5,13413.724155688624)(31563.5,16944.67256287425)(31897.5,22938.68886227545)(32231.5,32316.48101497006)(32549.5,45359.79038741722)(32702,53261.719)};
 \addlegendentry{CVC5}
 
-\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.069)(190.5,232.6589)(570.5,709.6480842105263)(950.5,1196.6337184210527)(1330.5,1690.1221210526317)(1710.5,2189.6400842105263)(2090.5,2694.497357894737)(2470.5,3204.0573736842107)(2850.5,3718.6741578947367)(3230.5,4238.482794736841)(3610.5,4764.7214894736835)(3990.5,5298.296757894736)(4370.5,5841.281960526316)(4750.5,6395.202660526315)(5130.5,6961.350839473685)(5510.5,7540.993026315789)(5890.5,8133.372015789473)(6270.5,8734.822897368422)(6650.5,9342.967752631579)(7030.5,9956.752307894736)(7410.5,10575.234568421052)(7790.5,11198.100728947367)(8170.5,11824.840531578946)(8550.5,12455.626292105264)(8930.5,13090.247586842104)(9310.5,13728.575228947368)(9690.5,14370.440260526317)(10070.5,15015.841252631579)(10450.5,15664.630397368423)(10830.5,16317.030813157895)(11210.5,16973.154363157893)(11590.5,17632.737636842106)(11970.5,18295.751634210526)(12350.5,18962.31434736842)(12730.5,19632.349584210526)(13110.5,20305.699439473687)(13490.5,20982.394255263156)(13870.5,21662.506336842103)(14250.5,22345.894881578948)(14630.5,23032.483915789475)(15010.5,23722.286118421052)(15390.5,24415.212605263157)(15770.5,25111.176465789475)(16150.5,25810.02410263158)(16530.5,26511.73647105263)(16910.5,27216.409768421054)(17290.5,27924.022686842105)(17670.5,28634.736831578946)(18050.5,29348.564321052632)(18430.5,30065.47053947368)(18810.5,30785.48525)(19190.5,31508.688036842104)(19570.5,32235.248236842108)(19950.5,32965.0526631579)(20330.5,33698.28517105264)(20710.5,34434.81481052632)(21090.5,35174.532952631576)(21470.5,35917.895857894735)(21850.5,36665.28371052632)(22230.5,37416.66357368421)(22610.5,38172.28100789474)(22990.5,38931.92542368421)(23370.5,39695.625260526314)(23750.5,40463.389355263156)(24130.5,41235.613436842104)(24510.5,42012.476486842104)(24890.5,42793.96287368421)(25270.5,43580.56005526315)(25650.5,44372.39037105263)(26030.5,45169.62203947368)(26410.5,45972.09492631579)(26790.5,46780.44576842106)(27170.5,47595.067805263156)(27550.5,48416.389299999995)(27930.5,49244.825065789475)(28310.5,50080.321313157896)(28690.5,50923.3093368421)(29070.5,51774.13953684211)(29450.5,52633.453644736845)(29830.5,53501.829744736846)(30210.5,54379.64974210526)(30590.5,55267.43845263158)(30970.5,56166.53594210526)(31350.5,57077.05190263158)(31730.5,57999.50882631579)(32110.5,58934.752134210525)(32490.5,59885.838323684206)(32870.5,60853.76433421053)(33250.5,61840.456797368424)(33630.5,62847.4605)(34010.5,63880.007623684214)(34390.5,64943.45741578947)(34770.5,66040.62170789474)(35150.5,67180.7566394737)(35530.5,68371.20348421052)(35910.5,69634.29873421052)(36290.5,71007.77509473685)(36670.5,72553.45386842104)(37050.5,74590.8398131579)(37260.5,77017.990675)(37282,77894.058)};
+\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.069)(190.5,232.6589)(570.5,709.6480842105263)(950.5,1196.6337184210527)(1330.5,1690.1221210526317)(1710.5,2189.6400842105263)(2090.5,2694.497357894737)(2470.5,3204.0573736842107)(2850.5,3718.6741578947367)(3230.5,4238.482794736841)(3610.5,4764.7214894736835)(3990.5,5298.296757894736)(4370.5,5841.281960526316)(4750.5,6395.202660526315)(5130.5,6961.350839473685)(5510.5,7540.993026315789)(5890.5,8133.372015789473)(6270.5,8734.822897368422)(6650.5,9342.967752631579)(7030.5,9956.752307894736)(7410.5,10575.234568421052)(7790.5,11198.100728947367)(8170.5,11824.840531578946)(8550.5,12455.626292105264)(8930.5,13090.247586842104)(9310.5,13728.575228947368)(9690.5,14370.440260526317)(10070.5,15015.841252631579)(10450.5,15664.630397368423)(10830.5,16317.030813157895)(11210.5,16973.154363157893)(11590.5,17632.737636842106)(11970.5,18295.751634210526)(12350.5,18962.31434736842)(12730.5,19632.349584210526)(13110.5,20305.699439473687)(13490.5,20982.394255263156)(13870.5,21662.506336842103)(14250.5,22345.894881578948)(14630.5,23032.483915789475)(15010.5,23722.286118421052)(15390.5,24415.212605263157)(15770.5,25111.176465789475)(16150.5,25810.02410263158)(16530.5,26511.73647105263)(16910.5,27216.409768421054)(17290.5,27924.022686842105)(17670.5,28634.736831578946)(18050.5,29348.564321052632)(18430.5,30065.47053947368)(18810.5,30785.48525)(19190.5,31508.688036842104)(19570.5,32235.248236842108)(19950.5,32965.0526631579)(20330.5,33698.28517105264)(20710.5,34434.81481052632)(21090.5,35174.532952631576)(21470.5,35917.895857894735)(21850.5,36665.28371052632)(22230.5,37416.66357368421)(22610.5,38172.28100789474)(22990.5,38931.92542368421)(23370.5,39695.625260526314)(23750.5,40463.389355263156)(24130.5,41235.613436842104)(24510.5,42012.476486842104)(24890.5,42793.96287368421)(25270.5,43580.56005526315)(25650.5,44372.39037105263)(26030.5,45169.62203947368)(26410.5,45972.09492631579)(26790.5,46780.44576842106)(27170.5,47595.067805263156)(27550.5,48416.389299999995)(27930.5,49244.825065789475)(28310.5,50080.321313157896)(28690.5,50923.3093368421)(29070.5,51774.13953684211)(29450.5,52633.453644736845)(29830.5,53501.829744736846)(30210.5,54379.64974210526)(30590.5,55267.43845263158)(30970.5,56166.53594210526)(31350.5,57077.05190263158)(31730.5,57999.50882631579)(32110.5,58934.752134210525)(32490.5,59885.838323684206)(32870.5,60853.76433421053)(33250.5,61840.456797368424)(33630.5,62847.4605)(34010.5,63880.007623684214)(34390.5,64943.45741578947)(34770.5,66040.62170789474)(35150.5,67180.7566394737)(35530.5,68371.20348421052)(35910.5,69634.29873421052)(36290.5,71007.77509473685)(36670.5,72553.45386842104)(37050.5,74590.8398131579)(37260.5,77017.990675)(37282,77894.058)};
 \addlegendentry{OstrichCEA}
 
-\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.973)(183,190.30856164383562)(548,594.3603315068493)(913,1024.961002739726)(1278,1469.2798904109588)(1643,1923.6285232876712)(2008,2386.440526027397)(2373,2857.0123945205482)(2738,3335.2412931506847)(3103,3820.518504109589)(3468,4312.556301369863)(3833,4811.463101369864)(4198,5316.991939726027)(4563,5828.562306849315)(4928,6346.063736986301)(5293,6868.94305479452)(5658,7396.841920547946)(6023,7929.662317808219)(6388,8467.604142465754)(6753,9010.742153424659)(7118,9558.934805479452)(7483,10111.938605479452)(7848,10669.474978082191)(8213,11231.314112328768)(8578,11797.621369863013)(8943,12368.65250410959)(9308,12944.311830136987)(9673,13524.519564383561)(10038,14109.451419178082)(10403,14698.853712328768)(10768,15293.112660273973)(11133,15892.433191780823)(11498,16496.828142465754)(11863,17106.316189041096)(12228,17721.04000547945)(12593,18340.346950684932)(12958,18964.554947945202)(13323,19594.05018082192)(13688,20228.820687671232)(14053,20869.080038356162)(14418,21514.670046575342)(14783,22165.900589041095)(15148,22822.877701369864)(15513,23485.61907123288)(15878,24154.566920547943)(16243,24829.88501369863)(16608,25511.430641095892)(16973,26198.8236630137)(17338,26892.730293150686)(17703,27593.722350684933)(18068,28301.48203561644)(18433,29016.173605479453)(18798,29737.934356164384)(19163,30466.729484931508)(19528,31202.92680821918)(19893,31946.9248630137)(20258,32698.838134246576)(20623,33459.216728767125)(20988,34229.22386849315)(21353,35008.99332054795)(21718,35798.51410410959)(22083,36598.632827397254)(22448,37409.98307945205)(22813,38232.88135342466)(23178,39067.59715616438)(23543,39915.206906849315)(23908,40775.91306849315)(24273,41650.684063013694)(24638,42540.330361643835)(25003,43445.31521643835)(25368,44367.7068)(25733,45309.33676438356)(26098,46271.140583561646)(26463,47254.96390684932)(26828,48263.57510136987)(27193,49300.231649315065)(27558,50368.124427397255)(27923,51470.418468493146)(28288,52611.19690136986)(28653,53795.38869041095)(29018,55029.08482465754)(29383,56320.12154520548)(29748,57678.96482465754)(30113,59114.90866575342)(30478,60647.17013150685)(30843,62287.70946575342)(31208,64046.39155890411)(31573,65948.76017808219)(31938,68015.45561917809)(32303,70268.4742739726)(32668,72725.02970136987)(33033,75449.96638630137)(33398,78510.05700821918)(33763,81999.3380219178)(34128,86050.69222191781)(34493,90831.67789315069)(34858,96740.15275342466)(35223,104550.05547123287)(35588,116337.4376410959)(35779,125163.37964705883)(35789,125692.196)};
+\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,0.973)(183,190.30856164383562)(548,594.3603315068493)(913,1024.961002739726)(1278,1469.2798904109588)(1643,1923.6285232876712)(2008,2386.440526027397)(2373,2857.0123945205482)(2738,3335.2412931506847)(3103,3820.518504109589)(3468,4312.556301369863)(3833,4811.463101369864)(4198,5316.991939726027)(4563,5828.562306849315)(4928,6346.063736986301)(5293,6868.94305479452)(5658,7396.841920547946)(6023,7929.662317808219)(6388,8467.604142465754)(6753,9010.742153424659)(7118,9558.934805479452)(7483,10111.938605479452)(7848,10669.474978082191)(8213,11231.314112328768)(8578,11797.621369863013)(8943,12368.65250410959)(9308,12944.311830136987)(9673,13524.519564383561)(10038,14109.451419178082)(10403,14698.853712328768)(10768,15293.112660273973)(11133,15892.433191780823)(11498,16496.828142465754)(11863,17106.316189041096)(12228,17721.04000547945)(12593,18340.346950684932)(12958,18964.554947945202)(13323,19594.05018082192)(13688,20228.820687671232)(14053,20869.080038356162)(14418,21514.670046575342)(14783,22165.900589041095)(15148,22822.877701369864)(15513,23485.61907123288)(15878,24154.566920547943)(16243,24829.88501369863)(16608,25511.430641095892)(16973,26198.8236630137)(17338,26892.730293150686)(17703,27593.722350684933)(18068,28301.48203561644)(18433,29016.173605479453)(18798,29737.934356164384)(19163,30466.729484931508)(19528,31202.92680821918)(19893,31946.9248630137)(20258,32698.838134246576)(20623,33459.216728767125)(20988,34229.22386849315)(21353,35008.99332054795)(21718,35798.51410410959)(22083,36598.632827397254)(22448,37409.98307945205)(22813,38232.88135342466)(23178,39067.59715616438)(23543,39915.206906849315)(23908,40775.91306849315)(24273,41650.684063013694)(24638,42540.330361643835)(25003,43445.31521643835)(25368,44367.7068)(25733,45309.33676438356)(26098,46271.140583561646)(26463,47254.96390684932)(26828,48263.57510136987)(27193,49300.231649315065)(27558,50368.124427397255)(27923,51470.418468493146)(28288,52611.19690136986)(28653,53795.38869041095)(29018,55029.08482465754)(29383,56320.12154520548)(29748,57678.96482465754)(30113,59114.90866575342)(30478,60647.17013150685)(30843,62287.70946575342)(31208,64046.39155890411)(31573,65948.76017808219)(31938,68015.45561917809)(32303,70268.4742739726)(32668,72725.02970136987)(33033,75449.96638630137)(33398,78510.05700821918)(33763,81999.3380219178)(34128,86050.69222191781)(34493,90831.67789315069)(34858,96740.15275342466)(35223,104550.05547123287)(35588,116337.4376410959)(35779,125163.37964705883)(35789,125692.196)};
 \addlegendentry{Ostrich}
 
-\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.012)(146,1.978233676975945)(437,6.271)(728,10.63781443298969)(1019,15.179)(1310,19.835)(1601,24.491)(1892,29.147)(2183,33.827536082474225)(2474,38.724)(2765,43.671)(3056,48.636051546391755)(3347,53.813)(3638,59.053546391752576)(3929,64.473)(4220,70.01970103092785)(4511,75.778)(4802,81.598)(5093,87.44253608247422)(5384,93.503)(5675,99.614)(5966,105.74201030927836)(6257,112.081)(6548,118.483)(6839,124.9422268041237)(7130,131.615)(7421,138.308)(7712,145.08378350515463)(8003,152.059)(8294,159.043)(8585,166.03229209621992)(8876,173.212)(9167,180.487)(9458,187.762)(9749,195.08520618556702)(10040,202.625)(10331,210.191)(10622,217.77952577319587)(10913,225.583)(11204,233.44001030927836)(11495,241.445)(11786,249.593)(12077,257.8093848797251)(12368,266.234)(12659,274.69963230240546)(12950,283.382)(13241,292.1369484536083)(13532,301.108)(13823,310.1481237113402)(14114,319.401)(14405,328.73513402061855)(14696,338.284)(14987,347.95956013745706)(15278,357.8412268041237)(15569,367.892)(15860,378.1011271477663)(16151,388.526)(16442,399.09973539518904)(16733,409.8684982817869)(17024,420.836)(17315,431.97982817869416)(17606,443.3423608247423)(17897,454.9270206185567)(18188,466.716)(18479,478.7367113402062)(18770,491.00674570446733)(19061,503.5473642611684)(19352,516.3713711340206)(19643,529.517793814433)(19934,543.0013092783505)(20225,556.8603848797251)(20516,571.1063608247422)(20807,585.7789175257732)(21098,600.9315738831615)(21389,616.5986323024056)(21680,632.778206185567)(21971,649.4465979381444)(22262,666.6643917525772)(22553,684.4916597938144)(22844,702.9503024054983)(23135,722.1009312714777)(23426,742.000879725086)(23717,762.6884123711341)(24008,784.2621340206185)(24299,806.8419381443299)(24590,830.5944329896906)(24881,855.6907972508591)(25172,882.2354776632303)(25463,910.5732749140893)(25754,940.9522302405497)(26045,973.7337250859107)(26336,1009.525501718213)(26627,1049.177388316151)(26918,1094.1484364261169)(27209,1146.7408178694157)(27500,1210.8287972508592)(27791,1295.0530343642613)(28082,1428.52512371134)(28373,1936.0622164948454)(28541,3951.5852444444445)(28565,4945.078)};
+\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.012)(146,1.978233676975945)(437,6.271)(728,10.63781443298969)(1019,15.179)(1310,19.835)(1601,24.491)(1892,29.147)(2183,33.827536082474225)(2474,38.724)(2765,43.671)(3056,48.636051546391755)(3347,53.813)(3638,59.053546391752576)(3929,64.473)(4220,70.01970103092785)(4511,75.778)(4802,81.598)(5093,87.44253608247422)(5384,93.503)(5675,99.614)(5966,105.74201030927836)(6257,112.081)(6548,118.483)(6839,124.9422268041237)(7130,131.615)(7421,138.308)(7712,145.08378350515463)(8003,152.059)(8294,159.043)(8585,166.03229209621992)(8876,173.212)(9167,180.487)(9458,187.762)(9749,195.08520618556702)(10040,202.625)(10331,210.191)(10622,217.77952577319587)(10913,225.583)(11204,233.44001030927836)(11495,241.445)(11786,249.593)(12077,257.8093848797251)(12368,266.234)(12659,274.69963230240546)(12950,283.382)(13241,292.1369484536083)(13532,301.108)(13823,310.1481237113402)(14114,319.401)(14405,328.73513402061855)(14696,338.284)(14987,347.95956013745706)(15278,357.8412268041237)(15569,367.892)(15860,378.1011271477663)(16151,388.526)(16442,399.09973539518904)(16733,409.8684982817869)(17024,420.836)(17315,431.97982817869416)(17606,443.3423608247423)(17897,454.9270206185567)(18188,466.716)(18479,478.7367113402062)(18770,491.00674570446733)(19061,503.5473642611684)(19352,516.3713711340206)(19643,529.517793814433)(19934,543.0013092783505)(20225,556.8603848797251)(20516,571.1063608247422)(20807,585.7789175257732)(21098,600.9315738831615)(21389,616.5986323024056)(21680,632.778206185567)(21971,649.4465979381444)(22262,666.6643917525772)(22553,684.4916597938144)(22844,702.9503024054983)(23135,722.1009312714777)(23426,742.000879725086)(23717,762.6884123711341)(24008,784.2621340206185)(24299,806.8419381443299)(24590,830.5944329896906)(24881,855.6907972508591)(25172,882.2354776632303)(25463,910.5732749140893)(25754,940.9522302405497)(26045,973.7337250859107)(26336,1009.525501718213)(26627,1049.177388316151)(26918,1094.1484364261169)(27209,1146.7408178694157)(27500,1210.8287972508592)(27791,1295.0530343642613)(28082,1428.52512371134)(28373,1936.0622164948454)(28541,3951.5852444444445)(28565,4945.078)};
 \addlegendentry{Z3str3}
 
-\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.011)(181.5,2.298024861878453)(543.5,7.39196132596685)(905.5,12.846621546961325)(1267.5,18.578)(1629.5,24.44856629834254)(1991.5,30.594629834254146)(2353.5,37.014)(2715.5,43.66661602209945)(3077.5,50.57362154696132)(3439.5,57.753)(3801.5,65.08817403314917)(4163.5,72.6765)(4525.5,80.4550276243094)(4887.5,88.4337955801105)(5249.5,96.6675)(5611.5,105.07338950276242)(5973.5,113.75666574585635)(6335.5,122.7165)(6697.5,131.92012154696133)(7059.5,141.41022651933702)(7421.5,151.196044198895)(7783.5,161.28051104972374)(8145.5,171.66944198895027)(8507.5,182.3868591160221)(8869.5,193.474908839779)(9231.5,204.9389502762431)(9593.5,216.7948950276243)(9955.5,229.06955801104974)(10317.5,241.797091160221)(10679.5,255.0154502762431)(11041.5,268.74189226519337)(11403.5,283.05802486187844)(11765.5,297.9990718232044)(12127.5,313.6326961325967)(12489.5,330.0478287292818)(12851.5,347.36489779005524)(13213.5,365.62986464088397)(13575.5,385.0328149171271)(13937.5,405.66013259668506)(14299.5,427.5818314917127)(14661.5,450.83144475138124)(15023.5,475.5672955801105)(15385.5,502.0523453038674)(15747.5,530.0259751381216)(16109.5,559.3107375690607)(16471.5,589.8519640883978)(16833.5,621.6678066298342)(17195.5,654.8743176795581)(17557.5,689.4013121546961)(17919.5,725.3846961325967)(18281.5,762.8980635359117)(18643.5,801.907591160221)(19005.5,842.5096629834254)(19367.5,884.8020718232044)(19729.5,928.861544198895)(20091.5,974.7612099447514)(20453.5,1022.6342651933702)(20815.5,1072.5725607734807)(21177.5,1124.8395055248618)(21539.5,1179.584991712707)(21901.5,1237.1880303867404)(22263.5,1297.957046961326)(22625.5,1362.265491712707)(22987.5,1430.3952762430938)(23349.5,1502.6981519337016)(23711.5,1579.696502762431)(24073.5,1661.6038812154698)(24435.5,1748.4525828729281)(24797.5,1840.9641022099447)(25159.5,1938.9034005524863)(25521.5,2042.6551602209943)(25883.5,2153.1485220994473)(26245.5,2271.2495)(26607.5,2396.9298314917123)(26969.5,2530.6465359116023)(27331.5,2672.95844198895)(27693.5,2824.6903425414366)(28055.5,2986.2353867403317)(28417.5,3158.2669364640883)(28779.5,3341.9625939226516)(29141.5,3538.530229281768)(29503.5,3748.9704861878454)(29865.5,3973.6326353591157)(30227.5,4215.252831491713)(30589.5,4476.184969613259)(30951.5,4760.791403314917)(31313.5,5071.179861878453)(31675.5,5412.076848066298)(32037.5,5786.981693370165)(32399.5,6205.653919889503)(32761.5,6683.778737569061)(33123.5,7242.432157458564)(33485.5,7909.979223756905)(33847.5,8733.536740331492)(34209.5,9802.194723756906)(34571.5,11351.004914364641)(34933.5,13998.519212707182)(35279.5,19650.679766666664)(35446,25499.5)};
+\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1pt off 2pt] coordinates {(1,0.011)(181.5,2.298024861878453)(543.5,7.39196132596685)(905.5,12.846621546961325)(1267.5,18.578)(1629.5,24.44856629834254)(1991.5,30.594629834254146)(2353.5,37.014)(2715.5,43.66661602209945)(3077.5,50.57362154696132)(3439.5,57.753)(3801.5,65.08817403314917)(4163.5,72.6765)(4525.5,80.4550276243094)(4887.5,88.4337955801105)(5249.5,96.6675)(5611.5,105.07338950276242)(5973.5,113.75666574585635)(6335.5,122.7165)(6697.5,131.92012154696133)(7059.5,141.41022651933702)(7421.5,151.196044198895)(7783.5,161.28051104972374)(8145.5,171.66944198895027)(8507.5,182.3868591160221)(8869.5,193.474908839779)(9231.5,204.9389502762431)(9593.5,216.7948950276243)(9955.5,229.06955801104974)(10317.5,241.797091160221)(10679.5,255.0154502762431)(11041.5,268.74189226519337)(11403.5,283.05802486187844)(11765.5,297.9990718232044)(12127.5,313.6326961325967)(12489.5,330.0478287292818)(12851.5,347.36489779005524)(13213.5,365.62986464088397)(13575.5,385.0328149171271)(13937.5,405.66013259668506)(14299.5,427.5818314917127)(14661.5,450.83144475138124)(15023.5,475.5672955801105)(15385.5,502.0523453038674)(15747.5,530.0259751381216)(16109.5,559.3107375690607)(16471.5,589.8519640883978)(16833.5,621.6678066298342)(17195.5,654.8743176795581)(17557.5,689.4013121546961)(17919.5,725.3846961325967)(18281.5,762.8980635359117)(18643.5,801.907591160221)(19005.5,842.5096629834254)(19367.5,884.8020718232044)(19729.5,928.861544198895)(20091.5,974.7612099447514)(20453.5,1022.6342651933702)(20815.5,1072.5725607734807)(21177.5,1124.8395055248618)(21539.5,1179.584991712707)(21901.5,1237.1880303867404)(22263.5,1297.957046961326)(22625.5,1362.265491712707)(22987.5,1430.3952762430938)(23349.5,1502.6981519337016)(23711.5,1579.696502762431)(24073.5,1661.6038812154698)(24435.5,1748.4525828729281)(24797.5,1840.9641022099447)(25159.5,1938.9034005524863)(25521.5,2042.6551602209943)(25883.5,2153.1485220994473)(26245.5,2271.2495)(26607.5,2396.9298314917123)(26969.5,2530.6465359116023)(27331.5,2672.95844198895)(27693.5,2824.6903425414366)(28055.5,2986.2353867403317)(28417.5,3158.2669364640883)(28779.5,3341.9625939226516)(29141.5,3538.530229281768)(29503.5,3748.9704861878454)(29865.5,3973.6326353591157)(30227.5,4215.252831491713)(30589.5,4476.184969613259)(30951.5,4760.791403314917)(31313.5,5071.179861878453)(31675.5,5412.076848066298)(32037.5,5786.981693370165)(32399.5,6205.653919889503)(32761.5,6683.778737569061)(33123.5,7242.432157458564)(33485.5,7909.979223756905)(33847.5,8733.536740331492)(34209.5,9802.194723756906)(34571.5,11351.004914364641)(34933.5,13998.519212707182)(35279.5,19650.679766666664)(35446,25499.5)};
 \addlegendentry{Z3seq}
 
-\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.003)(182,0.8189201101928375)(545,2.618)(908,4.4489173553719015)(1271,6.537)(1634,8.715)(1997,10.893)(2360,13.071)(2723,15.249)(3086,17.427)(3449,19.605)(3812,21.783)(4175,23.961)(4538,26.139)(4901,28.317)(5264,30.495)(5627,32.673)(5990,34.851)(6353,37.029)(6716,39.207)(7079,41.385)(7442,43.563)(7805,45.741)(8168,47.919)(8531,50.189754820936635)(8894,52.716)(9257,55.257)(9620,57.798)(9983,60.339)(10346,62.88)(10709,65.421)(11072,67.962)(11435,70.503)(11798,73.05656198347108)(12161,75.862)(12524,78.76711845730027)(12887,81.88)(13250,85.28151239669423)(13613,88.97315977961432)(13976,92.94506060606061)(14339,97.188)(14702,101.54920936639118)(15065,106.143)(15428,110.862)(15791,115.581)(16154,120.34537465564738)(16517,125.382)(16880,130.464)(17243,135.546)(17606,140.77125895316806)(17969,146.214)(18332,151.659)(18695,157.2202396694215)(19058,163.021)(19421,168.83004132231406)(19784,174.846)(20147,181.017)(20510,187.22618457300274)(20873,193.707)(21236,200.28687603305784)(21599,207.139)(21962,214.12243250688704)(22325,221.37020936639118)(22688,228.868)(23051,236.673)(23414,244.81311845730028)(23777,253.32572727272728)(24140,262.29896694214875)(24503,271.77692011019286)(24866,281.80780440771355)(25229,292.3972314049587)(25592,303.6866694214876)(25955,315.78646280991734)(26318,328.86711019283746)(26681,343.21780991735534)(27044,358.81747382920105)(27407,375.8708319559229)(27770,394.7050606060606)(28133,415.7127878787879)(28496,439.4317162534435)(28859,466.4655564738292)(29222,498.365608815427)(29585,537.2298842975206)(29948,587.2949889807162)(30311,662.5635867768594)(30674,763.2199421487603)(31037,869.8372286501378)(31400,980.2394986225895)(31763,1096.78108815427)(32126,1221.4321432506886)(32489,1354.5482093663911)(32852,1496.5741432506886)(33215,1648.5751597796143)(33578,1813.5611900826445)(33941,1997.562570247934)(34304,2211.9563140495866)(34667,2478.9477465564737)(35030,2875.3)(35393,4013.3737988980715)(35577,6494.691)(35581,6666.259)};
+\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt, dashed, dash pattern=on 2pt off 4pt] coordinates {(1,0.003)(182,0.8189201101928375)(545,2.618)(908,4.4489173553719015)(1271,6.537)(1634,8.715)(1997,10.893)(2360,13.071)(2723,15.249)(3086,17.427)(3449,19.605)(3812,21.783)(4175,23.961)(4538,26.139)(4901,28.317)(5264,30.495)(5627,32.673)(5990,34.851)(6353,37.029)(6716,39.207)(7079,41.385)(7442,43.563)(7805,45.741)(8168,47.919)(8531,50.189754820936635)(8894,52.716)(9257,55.257)(9620,57.798)(9983,60.339)(10346,62.88)(10709,65.421)(11072,67.962)(11435,70.503)(11798,73.05656198347108)(12161,75.862)(12524,78.76711845730027)(12887,81.88)(13250,85.28151239669423)(13613,88.97315977961432)(13976,92.94506060606061)(14339,97.188)(14702,101.54920936639118)(15065,106.143)(15428,110.862)(15791,115.581)(16154,120.34537465564738)(16517,125.382)(16880,130.464)(17243,135.546)(17606,140.77125895316806)(17969,146.214)(18332,151.659)(18695,157.2202396694215)(19058,163.021)(19421,168.83004132231406)(19784,174.846)(20147,181.017)(20510,187.22618457300274)(20873,193.707)(21236,200.28687603305784)(21599,207.139)(21962,214.12243250688704)(22325,221.37020936639118)(22688,228.868)(23051,236.673)(23414,244.81311845730028)(23777,253.32572727272728)(24140,262.29896694214875)(24503,271.77692011019286)(24866,281.80780440771355)(25229,292.3972314049587)(25592,303.6866694214876)(25955,315.78646280991734)(26318,328.86711019283746)(26681,343.21780991735534)(27044,358.81747382920105)(27407,375.8708319559229)(27770,394.7050606060606)(28133,415.7127878787879)(28496,439.4317162534435)(28859,466.4655564738292)(29222,498.365608815427)(29585,537.2298842975206)(29948,587.2949889807162)(30311,662.5635867768594)(30674,763.2199421487603)(31037,869.8372286501378)(31400,980.2394986225895)(31763,1096.78108815427)(32126,1221.4321432506886)(32489,1354.5482093663911)(32852,1496.5741432506886)(33215,1648.5751597796143)(33578,1813.5611900826445)(33941,1997.562570247934)(34304,2211.9563140495866)(34667,2478.9477465564737)(35030,2875.3)(35393,4013.3737988980715)(35577,6494.691)(35581,6666.259)};
 \addlegendentry{Z3str3RE}
 
-\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt] coordinates {(1,0.013)(95,1.341005291005291)(284,4.0399682539682535)(473,6.869)(662,9.70411111111111)(851,12.65937566137566)(1040,25.59284126984127)(1229,51.54501058201058)(1418,78.22667195767197)(1607,105.5319417989418)(1796,133.4236984126984)(1985,161.84444444444443)(2174,190.78955555555555)(2363,220.40304232804232)(2552,250.7406349206349)(2741,281.78158201058204)(2930,313.4990582010582)(3119,346.00148148148145)(3308,379.26011111111114)(3497,413.4176613756614)(3686,448.74649735449736)(3875,485.55874074074075)(4064,523.7897671957672)(4253,563.7060264550265)(4442,605.5690211640213)(4631,649.9228571428572)(4820,696.9802116402117)(5009,745.7844444444445)(5198,795.6489947089948)(5387,846.3269788359788)(5576,897.7440740740741)(5765,949.8416878306879)(5954,1002.637074074074)(6143,1056.1681269841272)(6332,1110.3784444444445)(6521,1165.2705343915343)(6710,1220.876931216931)(6899,1277.2039894179895)(7088,1334.4474126984128)(7277,1392.6996772486773)(7466,1452.0509206349207)(7655,1512.6050846560847)(7844,1574.619216931217)(8033,1637.9648359788362)(8222,1702.6984232804232)(8411,1768.954656084656)(8600,1836.9828518518518)(8789,1906.8673809523812)(8978,1978.6749523809524)(9167,2052.814894179894)(9356,2129.261529100529)(9545,2207.6439365079364)(9734,2287.9149523809524)(9923,2369.956126984127)(10112,2453.9330846560847)(10301,2540.037798941799)(10490,2628.356275132275)(10679,2719.279005291005)(10868,2812.8628941798943)(11057,2909.3264285714286)(11246,3009.0086507936508)(11435,3111.9666243386246)(11624,3218.299222222222)(11813,3327.769603174603)(12002,3440.6848042328043)(12191,3557.7057142857143)(12380,3679.364476190476)(12569,3806.0655767195767)(12758,3937.8237195767197)(12947,4075.3376719576722)(13136,4219.62535978836)(13325,4370.628846560847)(13514,4529.19538095238)(13703,4696.222878306879)(13892,4872.437195767196)(14081,5057.567285714285)(14270,5252.1323862433865)(14459,5458.876259259259)(14648,5679.89501058201)(14837,5918.56217989418)(15026,6175.9863597883605)(15215,6453.726322751323)(15404,6755.660825396825)(15593,7085.784804232804)(15782,7448.813486772487)(15971,7854.716571428572)(16160,8312.60244973545)(16349,8829.83808994709)(16538,9424.434878306878)(16727,10092.097708994708)(16916,10839.384137566138)(17105,11695.061899470898)(17294,12707.067682539682)(17483,13947.966777777778)(17672,15514.564391534392)(17861,17578.844534391534)(18050,20439.443920634923)(18239,24610.02486772487)(18428,31190.684534391534)(18525.5,36009.797333333336)(18530,36217.838)};
+\addplot[name path=pathZ3-Trau , colourZ3-Trau, line width=1.5pt, dashed, dash pattern=on 4pt off 2pt] coordinates {(1,0.013)(95,1.341005291005291)(284,4.0399682539682535)(473,6.869)(662,9.70411111111111)(851,12.65937566137566)(1040,25.59284126984127)(1229,51.54501058201058)(1418,78.22667195767197)(1607,105.5319417989418)(1796,133.4236984126984)(1985,161.84444444444443)(2174,190.78955555555555)(2363,220.40304232804232)(2552,250.7406349206349)(2741,281.78158201058204)(2930,313.4990582010582)(3119,346.00148148148145)(3308,379.26011111111114)(3497,413.4176613756614)(3686,448.74649735449736)(3875,485.55874074074075)(4064,523.7897671957672)(4253,563.7060264550265)(4442,605.5690211640213)(4631,649.9228571428572)(4820,696.9802116402117)(5009,745.7844444444445)(5198,795.6489947089948)(5387,846.3269788359788)(5576,897.7440740740741)(5765,949.8416878306879)(5954,1002.637074074074)(6143,1056.1681269841272)(6332,1110.3784444444445)(6521,1165.2705343915343)(6710,1220.876931216931)(6899,1277.2039894179895)(7088,1334.4474126984128)(7277,1392.6996772486773)(7466,1452.0509206349207)(7655,1512.6050846560847)(7844,1574.619216931217)(8033,1637.9648359788362)(8222,1702.6984232804232)(8411,1768.954656084656)(8600,1836.9828518518518)(8789,1906.8673809523812)(8978,1978.6749523809524)(9167,2052.814894179894)(9356,2129.261529100529)(9545,2207.6439365079364)(9734,2287.9149523809524)(9923,2369.956126984127)(10112,2453.9330846560847)(10301,2540.037798941799)(10490,2628.356275132275)(10679,2719.279005291005)(10868,2812.8628941798943)(11057,2909.3264285714286)(11246,3009.0086507936508)(11435,3111.9666243386246)(11624,3218.299222222222)(11813,3327.769603174603)(12002,3440.6848042328043)(12191,3557.7057142857143)(12380,3679.364476190476)(12569,3806.0655767195767)(12758,3937.8237195767197)(12947,4075.3376719576722)(13136,4219.62535978836)(13325,4370.628846560847)(13514,4529.19538095238)(13703,4696.222878306879)(13892,4872.437195767196)(14081,5057.567285714285)(14270,5252.1323862433865)(14459,5458.876259259259)(14648,5679.89501058201)(14837,5918.56217989418)(15026,6175.9863597883605)(15215,6453.726322751323)(15404,6755.660825396825)(15593,7085.784804232804)(15782,7448.813486772487)(15971,7854.716571428572)(16160,8312.60244973545)(16349,8829.83808994709)(16538,9424.434878306878)(16727,10092.097708994708)(16916,10839.384137566138)(17105,11695.061899470898)(17294,12707.067682539682)(17483,13947.966777777778)(17672,15514.564391534392)(17861,17578.844534391534)(18050,20439.443920634923)(18239,24610.02486772487)(18428,31190.684534391534)(18525.5,36009.797333333336)(18530,36217.838)};
 \addlegendentry{Z3-Trau}

### 2023-05-04 2023-1-19/sections/implementation.tex
abstract

@@
-\documentclass{standalone}
-\begin{document}
+%!TEX root = ../main.tex
+%\documentclass{standalone}
+%\begin{document}
 This section presents the empirical evaluation of OstrichCEA, which is our implementation of the decision procedure introduced in Section \ref{sec:algorithm}.
@@
 Furthermore, we assess the efficacy of our heuristics by testing different configurations of the tool.
-We have implemented our encoding for bounded repetition with two heuristic algorithms on Ostrich+ \cite{atva2020}.
+We have implemented our encoding for counting with two heuristic algorithms on Ostrich+ \cite{atva2020}.
 The pre-image computation for concatenation, \verb|indexOf|, \verb|substring|, \verb|replaceAll|, \verb|reverse| and finite transducer remain unchanged.
@@
 \subsection{Benchmarks}
-We conducted a comparison on four sets of benchmarks based on regex with bounded repetition, consisting of a total of 49,379 instances.
-We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with bounded repetition.
+We conducted a comparison on four sets of benchmarks based on regex with 
+counting operator, consisting of a total of 49,379 instances.
+We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with counting operator.
 In total, almost 18\% of the instances we evaluated were sourced from published industrial benchmarks or other solver developers.
-All the other instances contain regular expressions from the real world.
-Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large repetition upper bounds (the sum of upper bounds is greater than 50), and "small" contains the other instances.
-Less than 10\% of the benchmarks are in a "large" set.
+The other instances are generated by ourselves with regular expressions from real world.
+Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large upper bounds of counting operator (the sum of upper bounds is greater than 50), and "small" contains remained instances.
+About 10\% of the benchmarks are in a "large" set.
 More details about the benchmarks are shown below.
@@
 The simple track contains instances with a single regular expression membership constraint, whereas the hard track can hold up to five membership constraints for a single variable per instance.
-We extract 8,751 instances containing bounded repetition from 19,979 instances and partition them into "large" and "small" in terms of the size of the bounds.
+We extract 8,751 instances containing counting operator.
 \subsubsection{ReDos} is the set of 1,624 instances we generated.
@@
 Currently, it has indexed 4149 expressions from 2818 contributors around the world since 2001.
-We extract 1,623 instances containing bounded repetition from 4149 instances and partition them into "large" and "small" in terms of the size of the bounds.
+We extract 1,623 instances containing bounded repetition from 4149 instances.
+The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
 \subsubsection{StackOverflow} is the 37381 instances we generated similarly to the \textbf{ReDos} benchmark.
@@
 The website is a question-and-answer site for professional and enthusiast programmers.
-We extract 37,381 instances containing bounded repetition from almost 500,000 instances and partition them into "large" and "small" in terms of the size of the bounds.
+We extract 37,381 instances containing bounded repetition from almost 500,000 instances.
+The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
 \begin{equation} \label{eq:template}
-  x\in \regex \wedge x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*\wedge |x| > 50(20)
+  x\in \regex \wedge x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*\wedge |x| > 50(or \ 20)
 \end{equation}
@@
 We have evaluated OstrichCEA compared to five other prominent string solvers currently available.
-We evaluate the solvers by directly comparing the number of cases correctly solved, the total time taken with and without timeouts, and the total count of soundness errors and program crashes.
+We evaluate the solvers by directly comparing the number of cases correctly solved, the average time taken with and without timeouts, and the total count of soundness errors and program crashes.
 One of these solvers is CVC5\cite{cvc5}, a general SMT solver that uses algebraic reasoning to handle strings and regular expressions and is the winner of SMT-COMP 2022\cite{smt-comp}.
-Another solver, Z3str3\cite{z3str3}, is the most recent addition to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions.
+Another solver, Z3str3\cite{z3str3}, is the most recent addition we can get to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions.
 Z3str3RE\cite{z3str3re} is a variant of Z3str3 that incorporates length-aware algorithms and heuristics.
@@
 Z3-Trau\cite{z3trau} is the Z3 version of trau\cite{trau} that employs a flat automata-based approach, incorporating both under- and over-approximations.
-Finally, Ostrich\cite{ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships.
+Ostrich\cite{ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships.
 We used the 1.0.5 binary version of CVC5, commit 59e9c87 of Z3str3, last version of Z3str3RE, 4.8.9 binary version of Z3Seq, commit 1628747 of Z3-Trau and commit 8297d8d of Ostrich.
@@
 Solvers located towards the right and lower portion of the plot indicate better performance.
-OstrichCEA spent more time solving instances than other solvers.
-One reason was that OstrichCEA was written in Scala and ran on a Java virtual machine(JVM).
-The cold boot of JVM is cost.
-The other reason was that the implemented decision procedure was excessively cumbersome in resolving certain straightforward constraints.
 \newline
@@
 OstrichCEA resulted 5 unknowns because it reached the maximum threshold of limited memory 2GB.
-
+More details of the results of each benchmark are shown in \ref{appendix:experiential_results}.
 \begin{figure}[h]
@@
 \end{table}
-
-\subsection{Detailed Evaluation}
-The detailed results for the \textbf{AutomatArk} benchmark are presented in Figure \ref{fig:cactus_automatrk} and Table \ref{tab:results_automatrk}.
-OstrichCEA solved the most \emph{unsat} instances.
-Z3str3RE solved the most \emph{sat} instances.
-Ostrich solved the greatest number of instances, while Z3str3RE used the least time with timeouts.\newline
-The detailed results for the \textbf{Redos} benchmark are presented in Figure \ref{fig:cactus_redos} and Table \ref{tab:results_redos}.
-OstrichCEA solved the most instances on both tracks of \emph{sat} and \emph{unsat}.
-Including timeouts, OstrichCEA is \textbf{4.4}\mult{} faster than CVC5, \textbf{3.74}\mult{} faster than Ostrich, \textbf{2.09}\mult{} faster than Z3str3, \textbf{5.40}\mult{} faster than Z3seq, \textbf{2.49}\mult{} faster than Z3-Trau and close to Z3str3RE with \%20 speed loss.
-\newline
-The detailed results for the \textbf{RegexLib} benchmark are presented in Figure \ref{fig:cactus_regexlib} and Table \ref{tab:results_regexlib}.
-Ostrich solved the most \emph{unsat} instances.
-OstrichCEA solved the most \emph{sat} instances.
-In total, OstrichCEA solved the greatest number of instances and was the solver with medium speed.
-\newline
-The detailed results for the \textbf{StackOverflow} benchmark are presented in Figure \ref{fig:cactus_stackoverflow} and Table \ref{tab:results_stackoverflow}.
-OstrichCEA solved the most instances on both tracks of \emph{sat} and \emph{unsat} and was the faster solver.\newline Including timeouts, OstrichCEA is \textbf{3.98}\mult{} faster than CVC5, \textbf{2.63}\mult{} faster than Ostrich, \textbf{2.19}\mult{} faster than Z3str3, \textbf{1.59}\mult{} faster than Z3seq, \textbf{1.28}\mult{} faster than CVC5 and \textbf{1.47}\mult{} to Z3str3RE.
-\newline
-\begin{figure}
-  \centering
-  \subimport{figures}{cactus_plot_automatark.tex}
-  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the AutomatArk benchmark.}
-  \label{fig:cactus_automatrk}
-\end{figure}
-\begin{table}
-  \subimport{tables}{table_automatark.tex}
-  \caption{Detailed results for the AutomatArk benchmark.}
-  \label{tab:results_automatrk}
-\end{table}
-
-\begin{figure}
-  \subimport{figures}{cactus_plot_redos.tex}
-  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the ReDos benchmark.}
-  \label{fig:cactus_redos}
-\end{figure}
-\begin{table}
-  \subimport{tables}{table_redos.tex}
-  \caption{Detailed results for the ReDos benchmark.}
-  \label{tab:results_redos}
-\end{table}
-
-\begin{figure}
-  \subimport{figures}{cactus_plot_regexlib.tex}
-  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the RegexLib benchmark.}
-  \label{fig:cactus_regexlib}
-\end{figure}
-\begin{table}
-  \subimport{tables}{table_regexlib.tex}
-  \caption{Detailed results for the RegexLib benchmark.}
-  \label{tab:results_regexlib}
-\end{table}
-
-\begin{figure}
-  \subimport{figures/}{cactus_plot_stackoverflow.tex}
-  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the StackOverflow benchmark.}
-  \label{fig:cactus_stackoverflow}
-\end{figure}
-\begin{table}
-  \subimport{tables}{table_stackoverflow.tex}
-  \caption{Detailed results for the StackOverflow benchmark.}
-  \label{tab:results_stackoverflow}
-\end{table}
 \subsection{Analysis of Individual Heuristics}
@@
 From the plots and table, it is evident that OstrichCEA functions most effectively when all heuristics are enabled.
-OstrichCEA performs 1.78 times faster when employing all of our heuristics than none.
-All other configurations of the tool's heuristics make sense in comparison.
+In average time with timeout times, OstrichCEA performs \textbf{1.78}$\times$ faster than employing none of our heuristics, \textbf{1.37}$\times$ faster than turning off simplification, \textbf{1.15}$\times$ faster than truing off under-approximation.
 \begin{figure}

### 2023-05-04 2023-1-19/sections/algorithms.tex
from RECL to CEFA

@@
 At first, we show how to construct a CEFA from a regular expression where counting operators may occur. 
+Let us start with register-representable regular expressions defined in the sequel.
 
-Let $e$ be a regular expression and $(e')^{\{m,n\}}$ be an occurrence of the counting operators in $e$.
-Then $(e')^{\{m,n\}}$ is said to be \emph{persistent} in $e$ if  $(e')^{\{m,n\}}$ is not in the scope of a complement, Kleene star, or counting operator in $e$.
+Let us fix an alphabet $\Sigma$.
+
+Let $e$ be a regular expression over $\Sigma$.
+Then an occurrence of counting operators in $e$, say $(e')^{\{m,n\}}$ (or $(e')^{\{m, \infty\}}$), is said to be \emph{register-representable} if $(e')^{\{m,n\}}$ (or $(e')^{\{m, \infty\}}$) is not in the scope of a Kleene star, another counting operator, complement, or language difference in $e$.
+We say that $e$ is \emph{register-representable} if all occurrences of counting operators in $e$ are register-representable.
+For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{1,\infty\}}$ are not.
+
+Let $e$ be a register-representable regular expression over $\Sigma$. We are going to construct a CEFA out of $e$, denoted by $\aut_e$, by the following procedure. 
+\begin{enumerate}
+\item For each maximal sub-expression $e'$ of $e$ such that $e'$ contains no occurrences of counting operators, an NFA $\aut_{e'}$ can be constructed by a structural induction on the syntax of $e'$. 
+%
+\item For each sub-expression $(e')^{\{m,n\}}$ with $m \le n$ (resp.
+$(e')^{\{m, \infty\}}$) of $e$, we construct a CEFA $\aut_{(e')^{\{m,n\}}}$ (resp.
+$\aut_{(e')^{\{m, \infty\}}}$) as follows.
+Let $\aut_{e'} = (Q, \Sigma, \delta, I, F)$.
+From the construction for Kleene star in Section~\ref{sec:pre}, $(\aut_{e'})^* = (Q', \Sigma, \delta', I', F')$, where $Q' = Q \cup \{q_0\}$ with $q_0 \not \in Q$, $I' = \{q_0\}$, $F'= F \cup \{q_0\}$, $\delta' = \delta  \cup \{(q_0, a, q')  \mid \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\} \cup \{(q, a, q') \mid q \in F, \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\}$.
+Then $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a register, \\
+%
+$$
+\begin{array}{l c l}
+\delta'' & = & \{(q, a, q', (0)) \mid (q, a, q') \in \delta\}\  \cup \\
+& & \{(q_0, a, q', (1))  \mid \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\}\ \cup \\
+& & \{(q, a, q', (1)) \mid q \in F, \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\},
+\end{array}
+$$ 
+%
+moreover, $\alpha' = m \le r' \le n$ if $I \cap F = \emptyset$, and $\alpha' = r' \le n$ otherwise.
+(Intuitively, if $\varepsilon$ is accepted by $\aut_{e'}$, then the value of $r'$ can be less than $m$.) Finally, $\aut_{(e')^{\{m, \infty\}}}$ is constructed by adapting $\alpha'$ in $\aut_{(e')^{\{m,n\}}}$ as follows: $\alpha' = m \le r'$ if $I \cap F = \emptyset$ and $\alpha' = \ltrue$ otherwise.
+
+%
+\item For each sub-expression $e'$ of $e$ such that $e'$ contains occurrences of counting operators but $e'$ itself is not of the form $(e'_1)^{\{m,n\}}$ or $(e'_1)^{\{m,\infty\}}$, from the assumption that $e$ is register-representable, we know that $e'$ is of the form $e'_1 \concat e'_2$, $e'_1 + e'_2$, $e'_1 \cap e'_2$, or $(e'_1)$.
+For $e' = (e'_1)$, we have $\aut_{e'} = \aut_{e'_1}$.
+For $e' = e'_1 \concat e'_2$, $e' = e'_1 + e'_2$, or $e' = e'_1 \cap e'_2$, suppose that CEFA $\aut_{e'_1}$ and $\aut_{e'_2}$ have been constructed.
+Without loss of generality,  we assume that $R_{\aut_{e'_1}} \cap R_{\aut_{e'_2}} = \emptyset$.
+Then we have $\aut_{e'} = \aut_{e'_1} \concat \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cup \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cap \aut_{e'_2}$ respectively.
+\end{enumerate}
+
+\begin{example}
+an example here
+\end{example}
+
+\zhilin{stopped here}
 
@@
 The inductive step is constructing CEFA of the concatenation, union, intersection, closure, complement, and counting of CEFA(s) of sub-regex(es).
-Operations except for counting are trivial and represented in Appendix , we only illustrate counting here.
+Operations except for counting are trivial and represented in Appendix \ref{appendix:cefa}, we only illustrate counting here.
 

### 2023-05-04 2023-1-19/sections/algorithms.tex
from recl to cefa

@@
 
-Let $\varphi$ be an RECL constraint. We shall reduce the satisfiability of $\varphi$ to an instance of $\cefadec$.
+Let $\varphi$ be an RECL constraint and $x_1, \cdots, x_n$ be an enumeration of the string variables occurring in $\varphi$.
+Moreover, let $\varphi \equiv \varphi_1 \wedge \varphi_2$ such that $\varphi_1$ is a conjunction of regular membership constraints of $\varphi$, and $\varphi_2$ is a conjunction of length constraints of $\varphi$.
+We shall reduce the satisfiability of $\varphi$ to an instance of $\cefadec$.
 
@@
 From the construction for Kleene star in Section~\ref{sec:pre}, $(\aut_{e'})^* = (Q', \Sigma, \delta', I', F')$, where $Q' = Q \cup \{q_0\}$ with $q_0 \not \in Q$, $I' = \{q_0\}$, $F'= F \cup \{q_0\}$, $\delta' = \delta  \cup \{(q_0, a, q')  \mid \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\} \cup \{(q, a, q') \mid q \in F, \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\}$.
-Then $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a register, \\
+Then $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a register,
 %
@@
 Without loss of generality,  we assume that $R_{\aut_{e'_1}} \cap R_{\aut_{e'_2}} = \emptyset$.
-Then we have $\aut_{e'} = \aut_{e'_1} \concat \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cup \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cap \aut_{e'_2}$ respectively.
+Then we have $\aut_{e'} = \aut_{e'_1} \concat \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cup \aut_{e'_2}$, and $\aut_{e'} = \aut_{e'_1} \cap \aut_{e'_2}$ respectively.
 \end{enumerate}
@@
 
+For non-register-representable regular expressions, we first transform them into register-representable regular expressions by unfolding all the non-register-representable occurrences of  counting operators, then utilize the aforementioned procedure to construct CEFA.
+For instance, $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
+
+For each $i \in [n]$, let $x_i \in e_{i, 1}, \cdots, x_i \in e_{i, l_i}$ be an enumeration of the regular membership constraints for $x_i$ in $\varphi_1$.
+Then we can construct CEFA $\aut_{i, j}$ from $e_{i, j}$ for each $i \in [n]$ and $j \in [l_i]$.
+Moreover, we construct another CEFA $\aut_{i, 0}$ for each $i \in [n]$ to model the length of $x_i$.
+Specifically, $\aut_{i,0}$ is constructed as $((r_{i,0}), \{q_{i,0}\}, \Sigma, \delta_{i,0}, \{q_{i,0}\}, \{q_{i,0}\}, \ltrue)$, where $r_{i,0}$ is a fresh register (in particular, $r_{i,0}$ does not occur in $\aut_{i,1}, \cdots, \aut_{i, l_i}$) and $\delta_{i,0} = \{(q_{i,0}, a, q_{i,0}, (1)) \mid a \in \Sigma\}$.
+Let $\Lambda_{x_i} = \{\aut_{i,0}, \aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for each $i \in [n]$. Moreover, let $\varphi'_2 \equiv \varphi_2[r_{1,0}/|x_1|, \cdots, r_{n,0}/|x_n|]$.
+Then the satisfiability of $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi'_2$.
+
 \zhilin{stopped here}
 
+%%%%%%%%%%% original texts by denghang %%%%%
+%%%%%%%%%%% original texts by denghang %%%%%
+\hide{
 The most important point of our approach is encoding counting operators by registers rather than explicitly unfolding them.
@@
 For example, the CEFA of $x$ in the string constraints $x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120$ is the product of the CEFA of regex $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, the CEFA of regex $\Sigma^*$ and the CEFA of length constraints $|x| > 120$.
+}
+%%%%%%%%%%% original texts by denghang %%%%%
+%%%%%%%%%%% original texts by denghang %%%%%
 

### 2023-05-04 2023-1-19/sections/preliminaries.tex
from recl to cefa

@@
 For convenience, we use $\varphi(\vec{x})$ with $\myvec{x} = (x_1, \cdots, x_k)$ to denote an LIA formula $\varphi$ whose free variables are from $\{x_1, \cdots, x_k\}$.
-For an LIA formula $\varphi(\vec{x})$ with $\myvec{x} = (x_1, \cdots, x_k)$ and $\myvec{n} = (n_1, \cdots, n_k) \in \Int^k$, we use $\varphi[\myvec{n}/\myvec{x}]$ to denote the formula obtained by replacing $x_i$ with $n_i$ for each $i \in [k]$.
+For an LIA formula $\varphi(\vec{x})$ with $\myvec{x} = (x_1, \cdots, x_k)$ and $\myvec{t} = (t_1, \cdots, t_k)$ be a tuple of integer terms, we use $\varphi[\myvec{t}/\myvec{x}]$ to denote the formula obtained by replacing (simultaneously) $x_i$ with $t_i$ for every $i \in [k]$.
 %For convenience, we usually assume that a set $X$ of variables is a vector. 

### 2023-05-04 2023-1-19/sections/algorithms.tex
from recl to cefa

@@
 We say that $e$ is \emph{register-representable} if all occurrences of counting operators in $e$ are register-representable.
-For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{1,\infty\}}$ are not.
+For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ are not.
 
@@
 For non-register-representable regular expressions, we first transform them into register-representable regular expressions by unfolding all the non-register-representable occurrences of  counting operators, then utilize the aforementioned procedure to construct CEFA.
-For instance, $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
+For instance, $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa+aaaa) \concat b^*)^{\{2, \infty\}}$.
+%$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
 

### 2023-05-04 2023-1-19/sections/algorithms.tex
from recl to cefa
solving cefa

@@
 Without loss of generality,  we assume that $R_{\aut_{e'_1}} \cap R_{\aut_{e'_2}} = \emptyset$.
-Then we have $\aut_{e'} = \aut_{e'_1} \concat \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cup \aut_{e'_2}$, and $\aut_{e'} = \aut_{e'_1} \cap \aut_{e'_2}$ respectively.
+Then we have $\aut_{e'} = \aut_{e'_1} \concat \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cup \aut_{e'_2}$, or $\aut_{e'} = \aut_{e'_1} \cap \aut_{e'_2}$.
 \end{enumerate}
@@
 \subsection{Solving $\cefadec$} \label{subsec:cefadec}
+
+In the sequel, we present a procedure to solve the $\cefadec$ problem.
+
+Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+
+At first, we compute CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$ for each $i \in [n]$. For each $i \in [n]$, let $\Lambda'_{x_i} = \{\cB_i\}$. 
+Then the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
+
+Since the construction of $\cB_1, \cdots, \cB_n$ may involve exponential blow-up, it is vital to reduce the sizes of these CEFAs.
+
+It turns out that to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$, we can ignore the characters in $\cB_1,\cdots, \cB_n$.
+
+compute the product, ignore the alphabet, determinization, minimization
+
+under approximation
+
 After encoding counting operator and length constraint to CEFAs, there are only automaton memberships $x\in \aut$ and LIA formula $t_1 \ \op \ t_2$ where $\aut$ is CEFA and $t_1, t_2$ are integer terms.

### 2023-05-04 2023-1-19/sections/cefa.tex
solving cefa

@@
 Finally, we define the semantics of a CEFA $\aut$ as $\Lang(\aut) = \{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
+In particular, if $I \cap F \neq \emptyset$, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$.
 
@@
 %Finally, we define the product of two CEFA.
+
+For convenience, for a CEFA $\aut$, we use $R_\aut$ to denote the set of registers of $\aut$.
 
@@
 $$\Lang(\aut_1 \concat \aut_2) = \{(w_1w_2; \myvec{v}) \mid (w_1; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1), (w_2; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
+
+Furthermore, the union, intersection, and concatenation operations can be extended naturally to multiple CEFA, that is, $\aut_1 \cup \cdots \cup \aut_n$, $\aut_1 \cap \cdots \cap \aut_n$, $\aut_1 \concat \cdots \concat \aut_n$.
+For instance, $\aut_1 \cup \aut_2 \cup \aut_3 = (\aut_1 \cup \aut_2) \cup \aut_3$, $\aut_1 \cap \aut_2 \cap \aut_3 = (\aut_1 \cap \aut_2) \cap \aut_3$, and $\aut_1 \concat \aut_2 \concat \aut_3 = (\aut_1 \concat \aut_2) \concat \aut_3$.
 

### 2023-05-05 2023-1-19/sections/algorithms.tex
solving CEFA

@@
 
-At first, we compute CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$ for each $i \in [n]$. For each $i \in [n]$, let $\Lambda'_{x_i} = \{\cB_i\}$. 
+At first, we compute CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$ for each $i \in [n]$.
+For each $i \in [n]$, let $\Lambda'_{x_i} = \{\cB_i\}$.
+Evidently, $R_{\cB_i}= \bigcup \limits_{j \in [l_i]} R_{\aut_{i, j}}$ for each $i \in [n]$.
 Then the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
@@
 
-It turns out that to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$, we can ignore the characters in $\cB_1,\cdots, \cB_n$.
+It turns out that to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+$\varphi$, we can ignore the characters in $\cB_1,\cdots, \cB_n$.
+This is due to the fact that there is only one CEFA for each string variable and $\varphi$ only cares about the values of registers.
 
-compute the product, ignore the alphabet, determinization, minimization
+%When the characters in $\cB_1, \cdots, \cB_n$ are ignored, they can be seen as NFAs. 
+For each $i \in [n]$, let $\cC_i$ be the automaton obtained from $\cB_i$ by replacing each transition $(q, a, q', \myvec{v})$ with $(q, \myvec{v}, q')$. 
+Then for each $i \in [n]$, $\cC_i$ can be seen as an NFA over the alphabet $V_i$, where $V_i$ is the set of vectors $\myvec{v}$ occurring in the transitions $(q, a, q', \myvec{v})$ of $\cB_i$.
+
+Then the set of costs output by $\cB_i$, that is, $\{\myvec{v} \mid (w; \myvec{v}) \in \Lang(\cB_i)\}$ can be reduced to the computation of the Parikh image of $\cC_i$, namely, 
+%
+$$\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}.$$
+
+Moreover, the transitions $(q, \myvec{0}, q')$ in $\cC_i$ can be seen as $\varepsilon$-transitions, that is, we can replace each transition $(q, \myvec{0}, q')$ with $(q, \varepsilon, q')$, without affecting the set $\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}$.
+Therefore, we first do these replacements, apply the $\varepsilon$-transition removal procedure.
+Then we utilize the determinization and minimization algorithm for NFA to reduce the size of $\cC_i$.
+
+Finally, if there are two indices $1 \le i' < j' \le |R_{\cB_i}|$ such that $v_{i'} = v_{j'}$ for each vector $\myvec{v} \in V_i$, then we can remove the $j'$-th component from the characters (vectors) of $\cC_i$, and let $\varphi := \varphi \wedge r_{i, i'} = r_{i, j'}$.
+By abusing the notation, we still use $\cC_i$ to denote the resulting NFA.
+
+By doing this, we reduce the automata sizes.
+Then we compute an LIA formula $\psi_{i}$ from $\cC_i$ to specify the Parikh images of $\cC_i$.
+Then the nonemptiness of $\cB_1, \cdots, \cB_n$ w.r.t.
+$\varphi$ is reduced to the satisfiability of $\psi_1 \wedge \cdots \psi_n \wedge \varphi$.
 
 under approximation
+
+In summary, we obtain an algorithm for solving the nonemptiness of $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$, as illustrated in Figure~\ref{xxx}.
+
+\zhilin{stopped here}
 

### 2023-05-05 2023-1-19/sections/algorithms.tex
solving NE(CEFA)

@@
 Then  the CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are said to be nonempty w.r.t.
-$\varphi$ if there are an assignment $\eta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors
-$\myvec{v_{1,1}}, \cdots, \myvec{v_{1, l_1}}, \cdots, \myvec{v_{n, 1}}, \cdots, \myvec{v_{n, l_n}}$ such that $(w_i; \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ for every $i \in [n], j \in [l_i]$,
+$\varphi$ if there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors
+$\myvec{v_{1,1}}, \cdots, \myvec{v_{1, l_1}}, \cdots, \myvec{v_{n, 1}}, \cdots, \myvec{v_{n, l_n}}$ such that $(\theta(x_i); \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ for every $i \in [n], j \in [l_i]$,
 % \in \aut_{i,1}(\eta(x_1)), \cdots, \myvec{v_{i, l_i}} \in \aut_{i,l_i}(\eta(x_i))$ for every $i \in [n]$  
@@
 Then the satisfiability of $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi'_2$.
-
-\zhilin{stopped here}
 
@@
 
-In the sequel, we present a procedure to solve the $\cefadec$ problem.
+In the sequel, we present a procedure to solve the $\cefadec$ problem: Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
 
-Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+The procedure comprises four steps. 
+%
+\paragraph*{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
 
-At first, we compute CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$ for each $i \in [n]$.
+%At first, we compute CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$ for each $i \in [n]$.
 For each $i \in [n]$, let $\Lambda'_{x_i} = \{\cB_i\}$.
 Evidently, $R_{\cB_i}= \bigcup \limits_{j \in [l_i]} R_{\aut_{i, j}}$ for each $i \in [n]$.
-Then the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
+After Step 1, the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
 
-Since the construction of $\cB_1, \cdots, \cB_n$ may involve exponential blow-up, it is vital to reduce the sizes of these CEFAs.
+%CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$ 
+%
 
-It turns out that to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+%Therefore, to solve the nonemptiness of CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ w.r.t. $\varphi$, it is sufficient to compute $\cefaout(\cB_1)$
+
+%Since the construction of $\cB_1, \cdots, \cB_n$ involves the computation of the product of multiple CEFA, it incurs an exponential blow-up in the worst case.
+Therefore, it is vital to reduce the sizes of these CEFAs.
+In the sequel, we propose some techniques to reduce the automata sizes.
+
+In the sequel, we reduce the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$ to the satisfiability of an LIA formula. The reduction relies on two observations.
+
+The first observation follows from the fact that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA.
+
+\begin{observation}\label{obs-cefa-output}
+CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t.
+$\varphi$ iff there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true.
+\end{observation}
+
+%From the fact that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA, we deduce that the following two conditions are equivalent.  
+%\begin{itemize}
+%\item CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$, namely, 
+%there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{1}}, \cdots, \myvec{v_{n}}$ such that $(\theta(x_1); \myvec{v_1}) \in \Lang(\cB_1)$, $\cdots$, $(\theta(x_n); \myvec{v_n}) \in \Lang(\cB_n)$ and $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true,
+%
+%\item there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true.
+%\end{itemize}
+
+Let $\aut = (R, Q, \Sigma, \delta, I, F)$ be a CEFA and $\costset_\aut = \{\myvec{v} \mid \exists q, a, q'.\ (q, a, q', \myvec{v}) \in \delta\}$. 
+Moreover, let $\aut'$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by ignoring the characters, that is, the transitions of $\NFA'$ are the tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for some $a \in \Sigma$.
+%Then $\cefaout(\aut) = \parikh(\NFA')$.
+\begin{observation}\label{obs-cefa-nfa}
+For each CEFA $\aut$, $\cefaout(\aut) = \left\{\sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v}  \mid \eta \in \parikh(\NFA') \right\}$.
+\end{observation}
+
+From Observation~\ref{obs-cefa-nfa}, we know that the following two conditions are equivalent, 
+\begin{itemize}
+%\item CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$, namely, 
+%there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{1}}, \cdots, \myvec{v_{n}}$ such that $(\theta(x_1); \myvec{v_1}) \in \Lang(\cB_1)$, $\cdots$, $(\theta(x_n); \myvec{v_n}) \in \Lang(\cB_n)$ and $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true,
+%
+\item there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true, 
+%CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$ 
+%
+\item 
+there are $\eta_1 \in \parikh(\cB'_1), \cdots, \eta_n \in \parikh(\cB'_n)$ such that 
+%
+%\begin{equation}\label{eqn-cefa-lia}
+\[
+\varphi \left[\sum \limits_{\myvec{v} \in \costset_{\cB_1}} \eta(\myvec{v}) \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum \limits_{\myvec{v} \in \costset_{\cB_n}} \eta(\myvec{v}) \myvec{v} \big{/}R_{\cB_n} \right]
+\]
+%\end{equation} 
+%
+is true. 
+\end{itemize}
+
+Therefore, to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+$\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cB'_1}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cB'_n}(\fZ_{\costset_{\cB_n}})$, which define the Parikh images of $\cB'_1$, $\cdots$, $\cB'_n$ respectively, and solve the satisfiability of the following existential LIA formula
+\begin{equation}\label{eqn-cefa-lia}
+\bigwedge \limits_{i \in [n]} \psi_{\cB'_i}(\fZ_{\costset_{\cB_i}}) \wedge 
+\varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right],
+\end{equation}
+where $\anivarz_{\myvec{v}}$'s are integer variables to represent the number of occurrences of $\myvec{v}$.
+
+Because the sizes of the LIA formulas $\psi_{\cB'_1}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cB'_n}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cB'_1, \cdots, \cB'_n$, and it is expensive (NP-complete) to solve the satisfiability of existential LIA formulas, it is vital to reduce the sizes of these NFA.
+
+We also have the following observation: For each $i \in [n]$ and $\eta \in \parikh(\cB'_i)$, we have 
+$$\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}.$$
+In other words, the $\myvec{0}$-labeled transitions in $\cB'_i$ do not contribute to the sum $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
+
+Therefore, we can reduce the sizes of $\cB'_1, \cdots, \cB'_n$ by Step II presented in the sequel.
+
+\paragraph*{Step 2.} For each $i \in [n]$, view the transitions $(q, \myvec{0}, q')$ in $\cB'_i$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cB'_i$, determinize and minimize the resulting NFA.
+\qed
+
+For $i \in [n]$, let  $\cC_i$ denote the DFA obtained from $\cB'_i$ by executing Step 2. From the construction, we know that $\parikh(\cC_i) = \parikh(\cB'_i)$ for each $i \in [n]$.
+Therefore, we compute LIA formulas from $\cC_i$'s, instead of $\cB'_i$'s, to represent Parikh images.
+
+\paragraph*{Step 3.} For each $i \in [n]$, compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cB_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+Then solve the satisfiability of the following existential LIA formula
+%
+\[
+\bigwedge \limits_{i \in [n]} \psi_{\cC_i}(\fZ_{\costset_{\cB_i}}) \wedge 
+\varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
+\]
+
+Finally, although we propose techniques to reduce the sizes of $\cB'_i$'s, it is still relatively expensive to compute LIA formulas from NFA and solve their satisfiability, especially for those problem instances with positive answers, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
+$\varphi$.
+Therefore, in the sequel, we propose a heuristic to search for solutions for those positive problem instances by utilizing under approximations, before Step 3.
+Intuitively, we search for solutions by bounding the lengths of the strings that are accepted by $\cC_i$'s.
+The heuristic uses a constant bound $B > 0$.
+Since the heuristic is applied before Step 3, we call it Step 2.5, to denote the fact that it is applied after Step 2 and before Step 3.
+
+For $i \in [n]$, suppose $R_{\cB_i} = (r_{i,1},\cdots, r_{i, k_i})$ and $\cC_i = (Q'_i, \costset_{\cB_i}, \delta'_i, q_{i,0}, F'_i)$.
+
+\paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let $\confset_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$ and $\psi_{\cC_i}:= \lfalse$.
+Then iterate the following procedure until $len = B$.
+\begin{quote}
+For each $i \in [n]$, let $\confset'_{\cC_i}:=\confset_{\cC_i}$ and do the following:  For each $(q, \myvec{v}) \in \confset_{\cC_i}$,
+\begin{itemize}
+\item if $q \in F'_i$, then let $\psi_{\cC_i}:=\psi_{\cC_i} \vee (\bigwedge \limits_{j \in [k_i]} r_{i,j} = v_j)$, 
+%
+\item let $\confset'_{\cC_i}:=\confset'_{\cC_i} \setminus \{(q, \myvec{v})\}$, 
+%
+\item for each transition $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset'_{\cC_i}:=\confset'_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
+\end{itemize}
+Let $\varphi:=\varphi \wedge \psi_{\cC_i}$.
+
+If $\varphi$ is satisfiable, then return $\ltrue$. Let $len: = len+1$. \qed
+\end{quote}
+
+%Furthermore, for each $i \in [n]$, we can remove the redundancy of characters/vectors in $\cC_i$.
+
+\zhilin{stopped here}
+
+%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
+%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
+\hide{
+Moreover, the transitions $(q, \myvec{0}, q')$ in $\cC_i$ can be seen as $\varepsilon$-transitions, that is, we can replace each transition $(q, \myvec{0}, q')$ with $(q, \varepsilon, q')$, without affecting the set $\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}$.
+Therefore, we first do these replacements, apply the $\varepsilon$-transition removal procedure.
+Then we utilize the determinization and minimization algorithm for NFA to reduce the size of $\cC_i$.
+
+It turns out that to solve the nonemptiness of CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ w.r.t.
 $\varphi$, we can ignore the characters in $\cB_1,\cdots, \cB_n$.
@@
 \end{example}
+}
+%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
+%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
 

### 2023-05-05 2023-1-19/sections/cefa.tex
solving NE(CEFA)

@@
 We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.
-Finally, we define the semantics of a CEFA $\aut$ as $\Lang(\aut) = \{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
+We define the semantics of a CEFA $\aut$, denoted by $\Lang(\aut)$, as $\{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
 In particular, if $I \cap F \neq \emptyset$, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$.
+Moreover, we define the \emph{output} of a CEFA $\aut$, denoted by $\cefaout(\aut)$, as $\{\myvec{v'} \mid  \exists w.\ \myvec{v'} \in \aut(w)\}$.
 

### 2023-05-05 2023-1-19/sections/preliminaries.tex
solving NE(CEFA)

--- 2023-05-04 2023-1-19/sections/preliminaries.tex
@@
 For a string $u$, we use $|u|$ to denote the number of letters in $u$. In particular, $|\varepsilon|=0$. 
-%Moreover, for $a \in \Sigma$, let $|u|_a$ denote the number of occurrences of $a$ in $u$. 
+Moreover, for $a \in \Sigma$, let $|u|_a$ denote the number of occurrences of $a$ in $u$. 
 Assume $u=a_0\cdots a_{n-1}$ is nonempty and $i<j \in [0,n-1]$. %Then a \emph{position} of $u$ is a number $i \in [|u|]$ (Note that the first position is $1$, instead of  0). In addition, 
@@
 
+Let $w \in \Sigma^*$.
+The \emph{Parikh image} of $w$, denoted by $\parikh(w)$, is defined as the function $\eta: \Sigma \rightarrow \Nat$ such that $\eta(a) = |w|_a$ for each $a \in \Sigma$.
+The \emph{Parikh image} of an NFA $\NFA$, denoted by $\parikh(\NFA)$, is defined as $\{\parikh(w) \mid w \in \Lang(\NFA)\}$.
+
 %\tl{to put in a different place later} Note that our decision procedure is applicable to general transducers as well, however, the EXPSPACE complexity bound is not, because the distributive property $f^{-1}(L_1\cap L_2)= f^{-1}(L_1)\cap f^{-1}(L_2)$ for regular languages $L_1, L_2$ only holds for functional transducers $f$.
@@
 
+\paragraph*{Linear integer arithmetic and Parikh images.}
 We will also use standard quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulae, which are typically ranged over by $\phi, \varphi$, etc. 
-For a set $X$ of variables, we use $\Phi(X)$ to denote the set of quantifier-free LIA formulas whose free variables are from $X$.
+For a set $\mathfrak{X}$ of variables, we use $\Phi(\mathfrak{X})$ to denote the set of quantifier-free LIA formulas whose free variables are from $\mathfrak{X}$. 
+For convenience, we use $\varphi(\vec{\anivar})$ with $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ to denote an LIA formula $\varphi$ whose free variables are from $\{\anivar_1, \cdots, \anivar_k\}$.
+For an LIA formula $\varphi(\vec{\anivar})$ with $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ and $\myvec{t} = (t_1, \cdots, t_k)$ be a tuple of integer terms, we use $\varphi[\myvec{t}/\myvec{\anivar}]$ to denote the formula obtained by replacing (simultaneously) $\anivar_i$ with $t_i$ for every $i \in [k]$.
+%For convenience, we usually assume that a set $X$ of variables is a vector. 
 %, which is essentially Presburger
+
+At last, we recall a result about Parikh images of NFA. 
+For each $a \in \Sigma$, let $\anivarz_a$ be an integer variable. Let $\fZ_\Sigma$ denote the set of integer variables $\anivarz_a$ for $a \in \Sigma$. 
+Let $\NFA$ be an NFA over the alphabet $\Sigma$. Then 
+we say that an LIA formula $\varphi(\fZ_\Sigma)$ defines the Parikh image of $\NFA$, if $\{\eta: \Sigma \rightarrow \Nat \mid \varphi[(\eta(a) /\anivarz_a)_{a \in \Sigma}] \mbox{ is true}\} = \parikh(\NFA)$.
+
+\begin{theorem}[\cite{SSMH04}]\label{thm-nfa-parikh}
+Given an NFA $\NFA$,  an existential LIA formula $\varphi_\NFA(\fZ_\Sigma)$ can be computed in linear time that defines the Parikh image of $\NFA$.
+\end{theorem}
 

### 2023-05-05 2023-1-19/sections/recl.tex
from recl to cefa
solving NE(CEFA)

@@
 In the sequel, we define string constraints with regex-counting and string-length function (abbreviated as RECL).
-The syntax of RECL is defined by the rules in Figure~\ref{fig:syntax}, where $x$ is a string variable, $i$ is an integer variable, $a$ is a character from an alphabet $\Sigma$, and $m, n$ are integer constants.
+The syntax of RECL is defined by the rules in Figure~\ref{fig:syntax}, where $x$ is a string variable, $\anivar$ is an integer variable, $a$ is a character from an alphabet $\Sigma$, and $m, n$ are integer constants.
 A RECL formula $\varphi$ is a conjunction of atomic formulas of the form $x \in \regex$, $x \not \in \regex$, or $t_1\ \op\ t_2$, where $\regex$ is a regular expression,  
@@
 $ \begin{array}{l l l r}
-    \varphi & ::= & x\in \regex \mid x \not \in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi                                              & \mbox{formulas}            \\
+    \varphi & ::= & x\in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi                                              & \mbox{formulas}            \\
     \regex &::= & \emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \overline{\regex} \mid \regex \setminus \regex \mid \regex^{\{m,n\}} \mid \regex^{\{m,\infty\}} \mid (e) & \mbox{regexes} \\
-    t &::= & n \mid i \mid  |x| \mid t - t \mid t + t                                                                    & \mbox{integer terms}
+    t &::= & n \mid \anivar \mid  |x| \mid t - t \mid t + t                                                                    & \mbox{integer terms}
     \end{array}
@@
 %
-\item $\varphi \equiv x \not \in \regex$ and $\theta(x) \not \in \Lang(\regex)$, 
+%\item $\varphi \equiv x \not \in \regex$ and $\theta(x) \not \in \Lang(\regex)$, 
 %
@@
 A RECL formula $\varphi$ is said to be satisfiable if there is a mapping $\theta$ such that $\theta \models \varphi$.
-The satisfiability problem for RECL is to decide whether a given RECL formula $\varphi$ is satisfiable.
+The satisfiability problem for RECL (abbreviated as $\reclsat$) is to decide whether a given RECL formula $\varphi$ is satisfiable.
 

### 2023-05-05 2023-1-19/sections/algorithms.tex
solving nonemptiness of cefa

@@
 
-Let $\aut = (R, Q, \Sigma, \delta, I, F)$ be a CEFA and $\costset_\aut = \{\myvec{v} \mid \exists q, a, q'.\ (q, a, q', \myvec{v}) \in \delta\}$. 
-Moreover, let $\aut'$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by ignoring the characters, that is, the transitions of $\NFA'$ are the tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for some $a \in \Sigma$.
+Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA and $\costset_\aut = \{\myvec{v} \mid \exists q, a, q'.\ (q, a, q', \myvec{v}) \in \delta\}$. 
+Moreover, let $\aut' = (Q, \costset_\aut, \delta', I, F)$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by dropping the accepting condition and ignoring the characters, that is, $\delta'$, the transition relation of $\aut'$, comprises the tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for some $a \in \Sigma$.
 %Then $\cefaout(\aut) = \parikh(\NFA')$.
+%
 \begin{observation}\label{obs-cefa-nfa}
-For each CEFA $\aut$, $\cefaout(\aut) = \left\{\sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v}  \mid \eta \in \parikh(\NFA') \right\}$.
+For each CEFA $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$, 
+%
+$$\cefaout(\aut) = \left\{\sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \  \big{|}\ \eta \in \parikh(\NFA') \mbox{ and }  \alpha\left[ \sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \big{/} R \right] \mbox{ is true}\right\}.$$
+%
 \end{observation}
 
-From Observation~\ref{obs-cefa-nfa}, we know that the following two conditions are equivalent, 
+For $i \in [n]$, let $\alpha_i$ be the accepting condition of $\cB_i$. 
+Then from Observation~\ref{obs-cefa-nfa}, we know that the following two conditions are equivalent, 
 \begin{itemize}
@@
 \[
-\varphi \left[\sum \limits_{\myvec{v} \in \costset_{\cB_1}} \eta(\myvec{v}) \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum \limits_{\myvec{v} \in \costset_{\cB_n}} \eta(\myvec{v}) \myvec{v} \big{/}R_{\cB_n} \right]
+\bigwedge \limits_{i \in [n]} \alpha_i\left[ \sum \limits_{\myvec{v} \in \costset_{\cB_i}} \eta_i(\myvec{v}) \myvec{v} \big{/}R_{\cB_i}  \right] \wedge \varphi \left[\sum \limits_{\myvec{v} \in \costset_{\cB_1}} \eta_1(\myvec{v}) \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum \limits_{\myvec{v} \in \costset_{\cB_n}} \eta_n(\myvec{v}) \myvec{v} \big{/}R_{\cB_n} \right]
 \]
@@
 Therefore, to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
-$\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cB'_1}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cB'_n}(\fZ_{\costset_{\cB_n}})$, which define the Parikh images of $\cB'_1$, $\cdots$, $\cB'_n$ respectively, and solve the satisfiability of the following existential LIA formula
-\begin{equation}\label{eqn-cefa-lia}
-\bigwedge \limits_{i \in [n]} \psi_{\cB'_i}(\fZ_{\costset_{\cB_i}}) \wedge 
-\varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right],
-\end{equation}
-where $\anivarz_{\myvec{v}}$'s are integer variables to represent the number of occurrences of $\myvec{v}$.
+$\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cB'_1}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cB'_n}(\fZ_{\costset_{\cB_n}})$ to represent the Parikh images of $\cB'_1$, $\cdots$, $\cB'_n$ respectively, where $\fZ_{\costset_{\cB_i}} = \{\anivarz_{i,\myvec{v}} \mid \myvec{v} \in \costset_{\cB_i}\}$ for $i \in [n]$, and solve the satisfiability of the following existential LIA formula
+%
+%\begin{equation}\label{eqn-cefa-lia}
+\[
+\begin{array}{l}
+%\scriptsize
+\bigwedge \limits_{i \in [n]} \left(\psi_{\cB'_i}(\fZ_{\costset_{\cB_i}}) \wedge \alpha_i\left[\sum\limits_{\myvec{v} \in \costset_{\cB_i}} \anivarz_{i, \myvec{v}} \myvec{v} \big{/}R_{\cB_i}  \right] \right)\  \wedge \\
+\ \ \varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{1, \myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{n, \myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
+\end{array}
+\]
+%\end{equation}
+Intuitively, the integer variables $\anivarz_{i, \myvec{v}}$ represent the number of occurrences of $\myvec{v}$ in the strings accepted by $\cB'_i$.
+%where $\anivarz_{\myvec{v}}$'s are integer variables to represent the number of occurrences of $\myvec{v}$.
 
@@
 
-We also have the following observation: For each $i \in [n]$ and $\eta \in \parikh(\cB'_i)$, we have 
-$$\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}.$$
+Furthermore, we have the following observation: For each $i \in [n]$ and $\eta \in \parikh(\cB'_i)$, we have 
+$\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}.$
 In other words, the $\myvec{0}$-labeled transitions in $\cB'_i$ do not contribute to the sum $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
 
-Therefore, we can reduce the sizes of $\cB'_1, \cdots, \cB'_n$ by Step II presented in the sequel.
+Therefore, we can reduce the sizes of $\cB'_1, \cdots, \cB'_n$ by Step II in the sequel.
 
@@
 
-For $i \in [n]$, let  $\cC_i$ denote the DFA obtained from $\cB'_i$ by executing Step 2. From the construction, we know that $\parikh(\cC_i) = \parikh(\cB'_i)$ for each $i \in [n]$.
-Therefore, we compute LIA formulas from $\cC_i$'s, instead of $\cB'_i$'s, to represent Parikh images.
+For $i \in [n]$, let  $\cC_i$ denote the DFA obtained from $\cB'_i$ by executing Step 2 and $\costset_{\cC_i} := \costset_{\cB_i} \setminus \{\myvec{0}\}$.
+From the construction, we know that $\parikh(\cC_i) = \prj_{\costset_{\cC_i}}(\parikh(\cB'_i))$ for each $i \in [n]$.
+Therefore, we compute LIA formulas from $\cC_i$'s, instead of $\cB'_i$'s, to represent the Parikh images.
 
-\paragraph*{Step 3.} For each $i \in [n]$, compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cB_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+\paragraph*{Step 3.} For each $i \in [n]$, compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
 Then solve the satisfiability of the following existential LIA formula
@@
 \[
-\bigwedge \limits_{i \in [n]} \psi_{\cC_i}(\fZ_{\costset_{\cB_i}}) \wedge 
-\varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
+\begin{array}{l}
+\bigwedge \limits_{i \in [n]} \left(\psi_{\cC_i}(\fZ_{\costset_{\cC_i}}) \wedge \alpha_i\left[\sum\limits_{\myvec{v} \in \costset_{\cC_i}} \anivarz_{i, \myvec{v}} \myvec{v} \big{/}R_{\cB_i}  \right] \right) \ \wedge \\
+\ \ \varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cC_1}} \anivarz_{1, \myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cC_n}} \anivarz_{n, \myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
+\end{array}
 \]
 
-Finally, although we propose techniques to reduce the sizes of $\cB'_i$'s, it is still relatively expensive to compute LIA formulas from NFA and solve their satisfiability, especially for those problem instances with positive answers, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
+%\[
+%\bigwedge \limits_{i \in [n]} \psi_{\cC_i}(\fZ_{\costset_{\cB_i}}) \wedge 
+%\varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
+%\]
+
+Finally, although we propose techniques to reduce the sizes of $\cB'_i$'s, it is still relatively expensive to compute LIA formulas from $\cC_i$'s and solve their satisfiability, especially for those problem instances with positive answers, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
 $\varphi$.
-Therefore, in the sequel, we propose a heuristic to search for solutions for those positive problem instances by utilizing under approximations, before Step 3.
+Therefore, in the sequel, we propose a heuristic to search for solutions for those positive problem instances by utilizing under approximations, to be executed before Step 3.
 Intuitively, we search for solutions by bounding the lengths of the strings that are accepted by $\cC_i$'s.
-The heuristic uses a constant bound $B > 0$.
-Since the heuristic is applied before Step 3, we call it Step 2.5, to denote the fact that it is applied after Step 2 and before Step 3.
+The heuristic uses a constant bound $B > 0$ and searches for solutions incrementally, starting from strings of length $0$.
+Since the heuristic is executed after Step 2 and before Step 3, we call it Step 2.5.
 
-For $i \in [n]$, suppose $R_{\cB_i} = (r_{i,1},\cdots, r_{i, k_i})$ and $\cC_i = (Q'_i, \costset_{\cB_i}, \delta'_i, q_{i,0}, F'_i)$.
+For $i \in [n]$, suppose $R_{\cB_i} = (r_{i,1},\cdots, r_{i, k_i})$ and $\cC_i = (Q'_i, \costset_{\cC_i}, \delta'_i, q_{i,0}, F'_i)$.
 
-\paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let $\confset_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$ and $\psi_{\cC_i}:= \lfalse$.
-Then iterate the following procedure until $len = B$.
-\begin{quote}
-For each $i \in [n]$, let $\confset'_{\cC_i}:=\confset_{\cC_i}$ and do the following:  For each $(q, \myvec{v}) \in \confset_{\cC_i}$,
-\begin{itemize}
+\paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let $\confset_{\cC_i}:=\emptyset$, $\confset'_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$, and $\psi_{\cC_i}:= \lfalse$.
+Then iterate the following procedure, until $len = B+1$.
+\begin{enumerate}
+\item Let $\xi: = \bigwedge \limits_{i \in [n]} \alpha_i \wedge \varphi$.
+%
+\item For each $i \in [n]$, do the following.
+\begin{enumerate}
+\item Let $\confset_{\cC_i}:= \confset_{\cC_i} \cup \confset'_{\cC_i}$, $temp:=\confset'_{\cC_i}$, $\confset'_{\cC_i}:=\emptyset$.
+%
+\item For each $(q, \myvec{v}) \in temp$,
+\begin{enumerate}
 \item if $q \in F'_i$, then let $\psi_{\cC_i}:=\psi_{\cC_i} \vee (\bigwedge \limits_{j \in [k_i]} r_{i,j} = v_j)$, 
 %
-\item let $\confset'_{\cC_i}:=\confset'_{\cC_i} \setminus \{(q, \myvec{v})\}$, 
+%\item let $\confset'_{\cC_i}:=\confset'_{\cC_i} \setminus \{(q, \myvec{v})\}$, 
 %
-\item for each transition $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset'_{\cC_i}:=\confset'_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
-\end{itemize}
-Let $\varphi:=\varphi \wedge \psi_{\cC_i}$.
-
-If $\varphi$ is satisfiable, then return $\ltrue$. Let $len: = len+1$. \qed
-\end{quote}
-
+\item for each $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset'_{\cC_i}:=\confset'_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
+\end{enumerate}
+%
+%\item 
+%
+\item Let $\xi := \xi \wedge \psi_{\cC_i}$. 
+\end{enumerate}
+%
+\item If $\xi$ is satisfiable, then report $\ltrue$ and the whole algorithm terminates. 
+%
+\item Let $len: = len+1$.
+\end{enumerate}
+Intuitively, for each $i \in [n]$, $\confset'_{\cC_i}$ stores the set of ``configurations'' of $\cC_i$ that were newly discovered, and $\confset_{\cC_i}$ stores those that have been discovered before.
 %Furthermore, for each $i \in [n]$, we can remove the redundancy of characters/vectors in $\cC_i$.
@@
 \end{example}
-}
-%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
-%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
 
@@
 \end{algorithm}
+}
+%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
+%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
 

### 2023-05-05 2023-1-19/sections/algorithms.tex
solving nonemp of cefa

@@
 
-\paragraph*{Step 2.} For each $i \in [n]$, view the transitions $(q, \myvec{0}, q')$ in $\cB'_i$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cB'_i$, determinize and minimize the resulting NFA.
+\paragraph*{Step 2.} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cB'_i$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cB'_i$, determinize the resulting NFA, and minimize it.
 \qed

### 2023-05-05 2023-1-19/sections/introduction.tex
overview

@@
 \begin{equation}\label{eqn-running}
-x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c^+ \wedge |x| > 120.
+x \in (\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c^+ \wedge |x| > 120.
 \end{equation}
@@
 $x_2, x_3$), moreover, $x$ ends with a nonempty sequence of $c$'s, and the length of $x$ is greater than $120$.
-It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 120$ and the counting upper bound $60$ in  both $(\Sigma \setminus a)^{\{5, 60\}}$ and $(\Sigma \setminus b)^{\{5, 60\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c^+$ requires that $x$ has to end with $c$.
+It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 120$ and the counting upper bound $60$ in  both $(\Sigma \setminus a)^{\{1, 60\}}$ and $(\Sigma \setminus b)^{\{1, 60\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c^+$ requires that $x$ has to end with $c$.
 
 A typical way of string constraint solvers to deal with regex-counting is to unfold regular expressions with counting into those \emph{without} counting by utilizing the concatenation operator.
-For instance, $a^{\{0, 4\}}$ is unfolded into $\varepsilon + a + aa + aaa + aaaa$.
+For instance, $a^{\{1, 4\}}$ is unfolded into $a(\varepsilon + a + aa + aaa)$.
 Since the unfolding incurs an exponential blow-up on the constraint sizes (where the integer constants are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the bounds are large.

### 2023-05-05 2023-1-19/sections/overview.tex
overview

@@
 %!TEX root = ../main.tex
+
+\zhilin{to be made consistent with section 6.}
 
@@
 
-We first construct an automaton for the regular expression $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
+We first construct an automaton for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
 We introduce three registers, say $r_1, r_2, r_3$, to represent the three counting operators.
 %Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
-Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into a so-called cost-enriched finite automaton (CEFA) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
+Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
 %Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.
 %Moreover, $r_0$ is incremented in all the three self-loops. 
-Furthermore, the counting bounds are specified by the accepting condition $5 \le r_1 \le 60 \wedge 5 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$ that is attached to the final state $p_2$.
+Furthermore, the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$.
 Note here we represent the counting operators symbolically by registers, instead of unfolding them explicitly.
-Moreover, we also construct a CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators.
+Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators.
+Finally, we construct the third CEFA $\aut_3$ (see Figure~\ref{fig:overview}(c)), where a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$.
 %where the register $r_0$ is used to record the length of strings.
@@
   \centering
-  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa.pdf}
-  \caption{CEFA for $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$ and $\Sigma^* c^+$}
+  \includegraphics[width = 0.95\textwidth]{sections/overview-cefa.pdf}
+  \caption{CEFA for $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, $\Sigma^* c^+$, and $|x|$}
   \label{fig:overview}
@@
 %we remove the $\varepsilon$-transitions of $\aut_1$, resulting into $\aut'_1$, 
-we construct $\aut_1 \times \aut_2$, that is, the product of $\aut_1$ and $\aut_2$, as illustrated in Figure~\ref{fig:overview:product}(a).
-Furthermore, we add one special register, say $r_0$, to record the length of strings.
-Note that $r_0$ is incremented in all transitions.
-In $\aut_1 \times \aut_2$, the accepting condition $5 \le r_1 \le 60 \wedge 5 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
-For technical convenience, we also think the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i-1}$ for each $i \in [4]$.
-For instance, the transitions corresponding to the self-loop around $(p_0, q_0)$ are thought as $(q, a', q', (1,1,0,0))$ with $a' \in \Sigma \setminus \{a\}$, since $r_0$ and $r_1$ are incremented in these transitions.
+we construct $\aut_1 \cap \aut_2 \cap \aut_3$, that is, the intersection (aka product) of $\aut_1$, $\aut_2$, and $\aut_3$, as illustrated in Figure~\ref{fig:overview:product}(a), where the states from which no final states are reachable are removed.
+%Furthermore, we add one special register, say $r_0$, to record the length of strings. Note that $r_0$ is incremented in all transitions. 
+%In $\aut_1 \cap \aut_2 \cap \aut_3$, the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
+For technical convenience, we also think the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
+For instance, the transitions corresponding to the self-loop around $(p_0, q_0, q'_0)$ are thought as $((p_0, q_0, q'_0), a', (p_0, q_0, q'_0), (1,0,0,1))$ with $a' \in \Sigma \setminus \{a\}$, since $r_1$ and $r_4$ are incremented in these transitions.
 With the updates thought as vectors, the resulting CEFA is illustrated in Figure~\ref{fig:overview:product}(b).
@@
   \centering
-  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa-product.pdf}
-  \caption{Product of $\aut_1$ and $\aut_2$, where the length register $r_0$ is added}
+  \includegraphics[width = 0.95\textwidth]{sections/overview-cefa-product.pdf}
+  \caption{$\aut_1 \cap \aut_2 \cap \aut_3$: Intersection of $\aut_1$, $\aut_2$, and $\aut_3$}
   \label{fig:overview:product}
@@
 
-Let $\tau_1, \cdots, \tau_m$ be an enumeration of the transitions of $\aut_1 \times \aut_2$ and $\myvec{v_1}, \cdots, \myvec{v_m}$ be the vectors of updates on the register values in these transitions.
-For instance, in the transition from $(p_0, q_1)$ to $(p_1, q_1)$, $r_0$ is incremented, and the values of the other registers is unchanged.
+\zhilin{stopped here}
+
+Let $\tau_1, \cdots, \tau_m$ be an enumeration of the transitions of $\aut_1 \cap \aut_2 \cap \aut_3$ and $\myvec{v_1}, \cdots, \myvec{v_m}$ be the vectors of updates on the registers in these transitions.
+%For instance, in the transition from $(p_0, q_1)$ to $(p_1, q_1)$, $r_0$ is incremented, and the values of the other registers is unchanged.
 Therefore, the vector for this transition is $(1, 0, 0, 0)$.
-Then the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \times \aut_2$. 
-From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi(i_1, \cdots, i_m)$ can be computed to express the constraints on the number of occurrences of $\tau_1, \cdots, \tau_m$ in the accepting runs of $\aut_1 \times \aut_2$, where $i_1, \cdots, i_m$ are the integer variables representing the number of occurrences of $\tau_1, \cdots, \tau_m$ respectively.
+Then the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$. 
+From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi(i_1, \cdots, i_m)$ can be computed to express the constraints on the number of occurrences of $\tau_1, \cdots, \tau_m$ in the accepting runs of $\aut_1 \cap \aut_2 \cap \aut_3$, where $i_1, \cdots, i_m$ are the integer variables representing the number of occurrences of $\tau_1, \cdots, \tau_m$ respectively.
 Therefore, the satisfiability of the string constraint in~(\ref{eqn-running}) is reduced to the satisfiability of the following existential LIA formula

### 2023-05-06 2023-1-19/sections/overview.tex
overview

@@
 
-\zhilin{to be made consistent with section 6.}
+%\zhilin{to be made consistent with section 6.}
 
@@
 Furthermore, the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$. 
+A string $w$ is accepted by $\aut_1$ if when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition.
 Note here we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
@@
 Finally, we construct the third CEFA $\aut_3$ (see Figure~\ref{fig:overview}(c)), where a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$.
+(See Section~\ref{subsec:regex2cefa} for more details about the construction of CEFA.)
 %where the register $r_0$ is used to record the length of strings.
@@
 
-\zhilin{stopped here}
-
-Let $\tau_1, \cdots, \tau_m$ be an enumeration of the transitions of $\aut_1 \cap \aut_2 \cap \aut_3$ and $\myvec{v_1}, \cdots, \myvec{v_m}$ be the vectors of updates on the registers in these transitions.
 %For instance, in the transition from $(p_0, q_1)$ to $(p_1, q_1)$, $r_0$ is incremented, and the values of the other registers is unchanged.
 Therefore, the vector for this transition is $(1, 0, 0, 0)$.
-Then the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$. 
-From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi(i_1, \cdots, i_m)$ can be computed to express the constraints on the number of occurrences of $\tau_1, \cdots, \tau_m$ in the accepting runs of $\aut_1 \cap \aut_2 \cap \aut_3$, where $i_1, \cdots, i_m$ are the integer variables representing the number of occurrences of $\tau_1, \cdots, \tau_m$ respectively.
+The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut_1 \cap \aut_2 \cap \aut_3$, producing a cost $(v_1, v_2, v_3, v_4)$ that satisfies $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $v_4 > 120$.
+It is not hard to observe that the nonemptiness of $\aut_1 \cap \aut_2 \cap \aut_3$ w.r.t.
+$\varphi \equiv r_4 > 120$ is independent of the characters of $\aut_1 \cap \aut_2 \cap \aut_3$.
+Therefore, the characters in $\aut_1 \cap \aut_2 \cap \aut_3$ can be ignored, resulting into an NFA $\cB$ over the alphabet $\costset$ (see Figure~\ref{fig:overview:product:reduced}(a)), where $\costset$ is the set of vectors from $\Int^4$ occurring in the transitions of $\aut_1 \cap \aut_2 \cap \aut_3$.
+Then the nonemptiness of $\aut_1 \cap \aut_2 \cap \aut_3$ w.r.t.
+$\varphi \equiv r_4 > 120$ is reduced to the problem of deciding whether there exists $w' \in \costset^*$ such that it is accepted by $\cB$ and its Parikh image (i.e.
+numbers of occurrences of characters), say $\eta_{w'}: \costset \rightarrow \Nat$, satisfies that $1 \le v'_1 \le 60\wedge 1 \le v'_2 \le 60 \wedge 0 \le v'_3 \le 60$ and $v'_4 > 120$, where $\myvec{v'} = \sum \limits_{\myvec{v} \in \costset} \eta_{w'}(\myvec{v}) \myvec{v}$.
+Intuitively, $\myvec{v'}$ here is a weighted sum of vectors $\myvec{v} \in \costset$, where the weight for $\myvec{v}$ is the number of occurrences of $\myvec{v}$ in $w'$.
+(See Section~\ref{subsec:cefadec} for more detailed arguments.)
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width = 0.8\textwidth]{sections/overview-cefa-reduced.pdf}
+  \caption{Reduced automaton $\cB$ and $\cC$}
+  \label{fig:overview:product:reduced}
+\end{figure}
+
+%Let $\tau_1, \cdots, \tau_m$ be an enumeration of the transitions of $\aut_1 \cap \aut_2 \cap \aut_3$ and $\myvec{v_1}, \cdots, \myvec{v_m}$ be the vectors of updates on the registers in these transitions.
+
+%
+Let $\costset = \{\myvec{v_1}, \cdots, \myvec{v_m}\}$. 
+From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi_\cB(\anivar_1, \cdots, \anivar_m)$ can be computed to define the Parikh image of strings that are accepted by $\cB$, where $\anivar_1, \cdots, \anivar_m$ are the integer variables to denote the number of occurrences of $\myvec{v_1}, \cdots, \myvec{v_m}$.
 Therefore, the satisfiability of the string constraint in~(\ref{eqn-running}) is reduced to the satisfiability of the following existential LIA formula
 \begin{equation}\label{eqn-LIA}
-\psi(i_1, \cdots, i_m) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [m]}  i_k v_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
+\begin{array}{l}
+\psi_\cB(\anivar_1, \cdots, \anivar_m) \wedge \bigwedge \limits_{1 \le j \le 4} r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}\ \wedge \\
+1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120.
+\end{array}
 \end{equation}
-where for each $k \in [m]$, $v_k = (v_{k,1}, v_{k,2}, v_{k, 3}, v_{k, 4})$ is the vector of updates on the registers $r_0, r_1, r_2, r_3$ in the transition $\tau_k$, and $\alpha(r_0, r_1, r_2, r_3)$ is the accepting condition in $\aut_1 \times \aut_2$.
-Finally, the satisfiability of LIA formula can be solved by the off-the-shelf SMT solvers for LIA.
+%where for each $k \in [m]$, $v_k = (v_{k,1}, v_{k,2}, v_{k, 3}, v_{k, 4})$ is the vector of updates on the registers $r_0, r_1, r_2, r_3$ in the transition $\tau_k$, and $\alpha(r_0, r_1, r_2, r_3)$ is the accepting condition in $\aut_1 \times \aut_2$.
+Since the satisfiability of LIA formulas can be solved by the off-the-shelf SMT solvers for LIA, the satisfiability of the string constraint in~(\ref{eqn-running}) can thus be solved.
 
-Nevertheless, since it is well known that the satisfiability of existential LIA formulas is NP-complete (see e.g.
-\cite{Haase18}), the performance could be improved if the size of the formula in~(\ref{eqn-LIA}) can be reduced.
+Nevertheless, it turns out that the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting into the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
+\cite{Haase18}).
+To tackle this issue, we proposes techniques to reduce the sizes of NFA over the alphabet $\costset$.
+
+%the performance could be improved if the size of the formula in~(\ref{eqn-LIA}) can be reduced.
 Since the size of the formula in~(\ref{eqn-LIA}) depends on the size of $\aut_1 \times \aut_2$, that is, the number of states, transitions, and registers in $\aut_1 \times \aut_2$, we propose the techniques to reduce the size of the CEFA $\aut_1 \times \aut_2$.
 
-Our main idea to reduce the size of the CEFA $\aut_1 \times \aut_2$ is to \emph{ignore the characters in transitions}, since the updates of the values of registers in transitions are independent of the characters therein and the satisfiability of the formula in~(\ref{eqn-LIA}) only concerns about the values of registers.
+%Our main idea to reduce the size of the CEFA $\aut_1 \times \aut_2$ is to \emph{ignore the characters in transitions}, since the updates of the values of registers in transitions are independent of the characters therein and the satisfiability of the formula in~(\ref{eqn-LIA}) only concerns about the values of registers.
 After the characters in transitions are ignored, each transition in $\aut_1 \times \aut_2$ is of the form $(q, \myvec{v}, q')$, where $\myvec{v}$ is the vector denoting the updates on the values of registers.
@@
 We then think $\cB$ as an NFA, where the vectors $\myvec{v}$ are taken as the characters.
-Then we apply the determinization and minimization algorithm of NFAs to $\cB$, resulting into an automaton $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}.
-Note that $\cC$ contains only three states $q'_0, q'_1, q'_2$ and six transitions $\tau'_1, \cdots, \tau'_6$, thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
+
+We determinize $\cB$, apply the minimization algorithm to the resulting deterministic finite automaton (DFA), and obtain a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b). 
+Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
+Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experimental results in Section~\ref{sec:implementation} show us that they do reduce the sizes of NFA that are constructed from the regular expressions in practice.
+%thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
 $\{a\}, \{b\}, \{c\}, \Sigma \setminus \{a, b, c\}$, in the transitions of $\aut_1 \times \aut_2$.}.
-Then we reinterpret $\cC$ as a CEFA with the acceptance condition $\alpha(r_0, r_1, r_2, r_3)$. 
-Finally, we compute an LIA formula $\psi'(i_1, \cdots, i_6)$ from $\cC$ and reduce the satisfiability of the string constraint in~(\ref{eqn-running}) to the satisfiability of the following existential LIA formula
-\begin{equation}\label{eqn-LIA-reduced}
-\psi'(i_1, \cdots, i_6) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [6]}  i_k v'_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
-\end{equation}
-where $\myvec{v'_{k}}=(v'_{k,1}, v'_{k,2}, v'_{k,3}, v'_{k,4})$ is the vector of updates of registers of the transition $\tau'_k$ for $k \in [6]$.
+%Then we reinterpret $\cC$ as a CEFA with the acceptance condition $\alpha(r_0, r_1, r_2, r_3)$. 
+%Finally, we compute an LIA formula $\psi'(i_1, \cdots, i_6)$ from $\cC$ and reduce the satisfiability of the string constraint in~(\ref{eqn-running}) to the satisfiability of the following existential LIA formula
+%\begin{equation}\label{eqn-LIA-reduced}
+%\psi'(i_1, \cdots, i_6) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [6]}  i_k v'_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
+%\end{equation}
+%where $\myvec{v'_{k}}=(v'_{k,1}, v'_{k,2}, v'_{k,3}, v'_{k,4})$ is the vector of updates of registers of the transition $\tau'_k$ for $k \in [6]$.
 
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width = 0.3\textwidth]{sections/overview-cefa-reduced.pdf}
-  \caption{Reduced automaton $\cC$}
-  \label{fig:overview:product:reduced}
-\end{figure}
-Furthermore, we can reduce the number of registers by merging several registers into one, if they are updated with the same value in every transition of $\aut_1 \times \aut_2$.
+%Furthermore, we can reduce the number of registers by merging several registers into one, if they are updated with the same value in every transition of $\aut_1 \times \aut_2$.
 
-At last, for the string constraints that are satisfied by a collection of strings whose lengths are small, computing LIA formulas from CEFA and solving them by SMT solvers are still expensive.  
+At last, for the string constraints that are satisfied by a collection of strings whose lengths are small, computing LIA formulas from NFA and solving them by SMT solvers are still expensive.  
 Therefore, we introduce a heuristic of searching for solutions based on \emph{under approximations}, before computing LIA formulas and solving them by SMT solvers.
 More precisely, we enforce a constant upper bound $B$ on the lengths of strings and search for a $B$-bounded satisfiable assignment, that is, a satisfiable assignment where the lengths of strings are bound by $B$.
-Initially we set $B$ to $1$.
-If there does not exist a $B$-bounded satisfiable assignment, then we let $B:=B+1$ and continue the search, until finding a satisfiable assignment or reaching a given time limit.
+Initially we set $\ell$, an integer variable to denoting the lengths of strings, to $1$.
+If there does not exist a $\ell$-bounded satisfiable assignment, then we let $\ell:=\ell+1$ and continue the search, until finding a satisfiable assignment or reaching the bound $B$.
 For instance, if we remove $|x| > 120$ from the string constraint~(\ref{eqn-running}), then the resulting constraint is satisfiable.
-Setting the bound $B$ to $1$ is already sufficient to find a solution for $\aut_1 \times \aut_2$ (with $r_0 > 120$ ignored).
+Setting the bound $B$ to $3$ is sufficient to find a solution, which is witnessed by the following accepting run of $\cC$: $q^{\prime\prime}_0 \xrightarrow{(1,0,0,1)} q^{\prime\prime}_0 \xrightarrow{(0,1,0,1)} q^{\prime\prime}_1 \xrightarrow{(0,0,0,1)} q^{\prime\prime}_2$.
+Note that the accepting run produces $(1,1,0,3)$, a vector of register values,  which satisfies $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$.
 

### 2023-05-06 2023-1-19/sections/implementation.tex
benchmark

@@
 %\begin{document}
-This section presents the empirical evaluation of OstrichCEA, which is our implementation of the decision procedure introduced in Section \ref{sec:algorithm}.
+
+We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH \cite{ostrich,atva2020}.
+Then we do experiments on two benchmark suites, to evaluate the efficacy of our approach.
+In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
+
+%This section presents the empirical evaluation of OstrichCEA, which is our implementation of the decision procedure introduced in Section \ref{sec:algorithm}.
 Our objective is to validate the effectiveness of the proposed techniques by evaluating our tool's correctness and efficiency compared to other solvers.
@@
 OstrichCEA is written in Scala and based on the SMT solver Princess\cite{princess}.
-\subsection{Benchmarks}
+
+\subsection{Benchmark suites}
+
+Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoLe. In total, there are 49,379 instances in the two benchmark suites.
+
+\paragraph*{AutomatArk benchmark suite.}
+The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraints.
+There are 8,751 instances in the AutomatArk suite.
+Note that the original AutomatArk benchmark suite in \cite{z3str3re}  includes 19,979 instances, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.
+
+\paragraph*{RegCoLe benchmark suite.} There are 40,628 RECL constraints in the RegCoLe suite.
+These constraints are generated by extracting regular expressions with counting operators from \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form
+$$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$$   
+where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$.
+We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
+
+%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
+\hide{
 We conducted a comparison on four sets of benchmarks based on regex with 
@@
 More details about the benchmarks are shown below.
+
 \subsubsection{AutomatArk} is the 8,751 instances generated by Berzish et al.\cite{z3str3re}.
@@
 We extract 8,751 instances containing counting operator.
+
 \subsubsection{ReDos} is the set of 1,624 instances we generated.
@@
 The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
+
 \subsubsection{RegexLib} is the set of 1,623 instances we generated similarly to the \textbf{ReDos} benchmark.
@@
 The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
+
 \subsubsection{StackOverflow} is the 37381 instances we generated similarly to the \textbf{ReDos} benchmark.
@@
 \end{equation}
-\subsection{Experimental Setup and Compared Solvers}
+}
+%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
+
+\subsection{Experiments}
+
 We have evaluated OstrichCEA compared to five other prominent string solvers currently available.
@@
 We used Zaligvinder\cite{zaligvinder_2021} framework and set the timeout to 60 seconds.
+
 \subsection{Overall Evaluation}
@@
 \end{table}
+
 \subsection{Analysis of Individual Heuristics}

### 2023-05-06 2023-1-19/sections/implementation.tex
experiments

@@
 
-We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH \cite{ostrich,atva2020}.
-Then we do experiments on two benchmark suites, to evaluate the efficacy of our approach.
+We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting into a version of OSTRICH called OSTRICH$^{\rm RECL}$.
+Then we do experiments on two benchmark suites, to evaluate the performance of OSTRICH$^{\rm RECL}$.
 In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
@@
 
-Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoLe. In total, there are 49,379 instances in the two benchmark suites.
+Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoL. In total, there are 49,379 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
 
@@
 
-\paragraph*{RegCoLe benchmark suite.} There are 40,628 RECL constraints in the RegCoLe suite.
+\paragraph*{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite.
 These constraints are generated by extracting regular expressions with counting operators from \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form
@@
 
-\subsection{Experiments}
+\subsection{Experiment results}
 
+We evaluated the performance of OSTRICH$^{\rm RECL}$ against the main-stream string constraint solvers, including CVC5 (version 1.0.5) \cite{cvc5}, Z3seq (version 4.8.9) \cite{z3seq}, Z3-Trau (github commit 1628747) \cite{z3trau}, Z3str3 (github commit 59e9c87) \cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH (github commit 8297d8d) \cite{atva2020}.
+All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory.
+We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, with the timeout limit set as 60 seconds per instance.
+
+The experiments are designed to answer the following two research questions. 
+\begin{description}
+\item[Q1] Is OSTRICH$^{\rm RECL}$ more efficient to solve RECL constraints than the state-of-the-art string constraint solvers ?
+
+\item[Q2] Do the size-reduction and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
+\end{description}
+
+Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL.
+The experimental results can be found in Table~\ref{tab:results_all}.
+From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 49,128 instances, which is 5,127/2,315/25,369/12,808/1,721/1,756 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
+%    
+Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as Z3str3RE, the fastest solver.
+More specifically, OSTRICH$^{\rm RECL}$ spends 2.51 seconds per instance on average, while Z3str3RE spends 2.46 seconds per instance.
+Z3-Trau reports ``unknown'' on 21,152 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
+Furthermore, Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness issues, that is, their results on some instances are inconsistent with the results of the other three solvers, i.e.
+CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
+
+\zhilin{may add the results for the two benchmark suites separately.}
+
+\begin{table}[ht]
+\begin{center}
+  \import{tables}{table_all.tex}
+\end{center}
+  \caption{Experiment results for Q1}
+  \label{tab:results_all}
+\end{table}
+
+To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively.
+The experiment results can be found in Table~\ref{tab:results_heuristics}.
+From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help solve \zhilin{xxx} more instances, while adding under-approximation techniques help solve \zhilin{xxx} more instances, while adding both help solve \zhilin{xxx} more instances.
+Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.
+
+\begin{table}[ht]
+\begin{center}
+  \subimport{tables}{table_heuristic.tex}
+\end{center}
+  \caption{Experiment results for Q2}
+  \label{tab:results_heuristics}
+\end{table}
+
+\zhilin{stopped here}
+
+%%%%%%%%%% original texts by denghang %%%%%%%%%
+%%%%%%%%%% original texts by denghang %%%%%%%%%
+\hide{
+%
 We have evaluated OstrichCEA compared to five other prominent string solvers currently available.
@@
 
-\subsection{Overall Evaluation}
+%\subsection{Overall Evaluation}
 In Fig.\ref{fig:cactus_all}, the cactus plot illustrates the cumulative time each solver takes for all cases in ascending order of runtime.
@@
 \end{figure}
-\begin{table}
-  \import{tables}{table_all.tex}
-  \caption{Total results of string solvers on all benchmarks. OstrichCEA solved the most benchmarks in the second shortest time.}
-  \label{tab:results_all}
-\end{table}
 
-\subsection{Analysis of Individual Heuristics}
+%\subsection{Analysis of Individual Heuristics}
 In order to demonstrate the efficacy of the individual heuristics outlined in Section \ref{sec:algorithm} and incorporated into OstrichCEA, we assessed various tool configurations in which one or more heuristics were disabled.
@@
 \end{table}
-
+}
+%%%%%%%%%% original texts by denghang %%%%%%%%%
+%%%%%%%%%% original texts by denghang %%%%%%%%%
 %\end{document}

### 2023-05-08 2023-1-19/sections/introduction.tex
intro

@@
 
-\paragraph*{Organization} \zhilin{to be cleaned} The rest of the paper is structured as follows: Section \ref{sec:pre} introduces the preliminaries.
-Section \ref{sec:overview} outlines the overall algorithm.
-Section \ref{sec:automaton} illustrates how to construct an automaton from a regular expression.
-Section \ref{sec:algorithm} shows how to solve a string constraint with repetition.
-Section \ref{sec:implementation} presents the experimental results.
-Section \ref{sec:conclu} concludes the paper and discusses future work.
+\paragraph*{Organization} The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper.
+Section~\ref{sec:pre} introduces the preliminaries.
+Section~\ref{sec:recl} presents the syntax and semantics of RECL. 
+Section~\ref{sec:automaton} defines CEFA.
+Section~\ref{sec:algorithm} introduces the algorithm to solve RECL constraints.
+Section~\ref{sec:implementation} shows the experiment results.
+Section~\ref{sec:conclu} concludes this paper.
 

### 2023-05-08 2023-1-19/sections/introduction.tex
related work

@@
 
-\paragraph*{Related work} \zhilin{to be cleaned} To handle the problems in software verification reasoning about strings and integers, string theories with regular membership predicate and linear length constraints are raised.
+\paragraph*{Related work} 
+We discuss more related work about regular expressions with counting and real-world regular expressions in programming languages here.  
+Determinism of regular expressions with counting was investigated in~\cite{GGM12,CL15}.
+Counting-set automata was proposed in~\cite{redos_lenka,HS+23} to enable fast matching of a subclass of regular expressions with counting.
+Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regular expressions with counting.
+Nevertheless, nonemptiness problem of these automata, which is the key for automata-based string constraint solving, was not considered in ~\cite{redos_lenka,HS+23,GKM23}.
+Real-world regular expressions in programming languages include some features beyond classical regular expressions, e.g.
+the greedy/lazy Kleene star, capturing groups, and back references.
+Real-world regular expressions haven been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.
+
+%To handle the problems in software verification reasoning about strings and integers, string theories with regular membership predicate and linear length constraints are raised.
 String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, BD+23\cite{BD+23}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories.
 Although string theory is easily
-undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_BD+23}.
+%undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_BD+23}.
 There are mainly two strategies for solving string constraints: (1) DPLL(T)-based\cite{dpll_t} string solvers\cite{z3str3}\cite{cvc5} apply heuristic derivation rules to unwind the regular expression gradually and identify several classes of simplification techniques for efficiency.

### 2023-05-08 2023-1-19/sections/introduction.tex
related work

@@
 Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regular expressions with counting.
-Nevertheless, nonemptiness problem of these automata, which is the key for automata-based string constraint solving, was not considered in ~\cite{redos_lenka,HS+23,GKM23}.
+Nevertheless, nonemptiness problem of these automata was not considered in ~\cite{redos_lenka,HS+23,GKM23} and it is unclear whether these automata models can be used for solving string constraints that involve regular expressions with counting.
 Real-world regular expressions in programming languages include some features beyond classical regular expressions, e.g.

### 2023-05-08 2023-1-19/sections/introduction.tex
related work

--- 2023-05-08 2023-1-19/sections/introduction.tex
@@
 Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regular expressions with counting.
-Nevertheless, nonemptiness problem of these automata, which is the key for automata-based string constraint solving, was not considered in ~\cite{redos_lenka,HS+23,GKM23}.
+Nevertheless, nonemptiness problem of these automata was not considered in ~\cite{redos_lenka,HS+23,GKM23} and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
 Real-world regular expressions in programming languages include some features beyond classical regular expressions, e.g.

### 2023-05-09 2023-1-19/sections/introduction.tex
some syntax error in intro

--- 2023-05-08 2023-1-19/sections/introduction.tex
@@
 In modern programming languages---such as JavaScript, Python, Java, and PHP---the string data type plays a crucial role. 
-It is well-known that string manipulations are error-prone and could even give rise to security vulnerabilities (e.g.\ cross-site scripting, aka XSS). 
+It is well-known that string manipulations are error-prone and could even give rise to security vulnerabilities (e.g. \ cross-site scripting, aka XSS). 
 One powerful method for identifying such bugs in programs is \emph{symbolic execution} (possibly in combination with dynamic analysis), which analyses symbolic paths in a program by viewing them as constraints, whose feasibility is checked by constraint solvers.
 %
-Symbolic execution of string manipulating programs have motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade or so including the state-of-the-art string constraint solvers (e.g.
+Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade or so, including the state-of-the-art string constraint solvers (e.g.
 Z3~\cite{Z3}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
@@
 
-Regular expressions (abbreviated as regex) and string-length function are widely used in string manipulating programs.
+Regular expressions (abbreviated as regex) and string-length function are widely used in string-manipulating programs.
 According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% Java, JavaScript, and Python software projects.
@@
 As a result, most of the aforementioned string constraint solvers support both regular expressions and string-length function.
-Moreover, specialized algorithms have been proposed to solve efficiently the class of string constraints with regular expressions and string-length function \cite{LTR+15,BD+23}.
-%a decision procedure based on tableaux calculus was designed  in \cite{LTR+15} for the class of string constraints with regular expressions and string-length function and the decision procedure has been implemented in CVC4/5 \cite{LRT+16}.
+Moreover, specialized algorithms have been proposed to efficiently solve the class of string constraints with regular expressions and string-length function \cite{LTR+15,BD+23}.
+%a decision procedure based on tableaux calculus was designed in \cite{LTR+15} for the class of string constraints with regular expressions and string-length function.
+The decision procedure has been implemented in CVC4/5 \cite{LRT+16}.
 
 Counting (aka repetition) is a convenient feature in regular expressions that count the number of matchings of sub-patterns.
-For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs for at least twice and at most four times and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
-Note that Kleene star and Kleene plus operator can be seen as special cases of counting operator, for instance, $a^*$ and $a^+$ are equivalent to $a^{\{0,\infty\}}$ and $a^{\{1,\infty\}}$.
+For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
+Note that Kleene star and Kleene plus operator can be seen as special cases of counting operator. For instance, $a^*$ and $a^+$ are equivalent to $a^{\{0,\infty\}}$ and $a^{\{1,\infty\}}$.
 Counting is also a frequently used feature of regular expressions.
@@
 Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from the string constraints with regex-counting and string-length, especially when the counting bounds are large.
-For instance, none of string solvers e.g.
+For instance, none of the string solvers e.g.
 CVC4/5, Z3, Z3str3RE, OSTRICH is capable of solving the following constraint within 300 seconds,
@@
 
-A typical way of string constraint solvers to deal with regex-counting is to unfold regular expressions with counting into those \emph{without} counting by utilizing the concatenation operator.
+A typical way for string constraint solvers to deal with regex-counting is to unfold regular expressions with counting into those \emph{without} counting by using the concatenation operator.
 For instance, $a^{\{1, 4\}}$ is unfolded into $a(\varepsilon + a + aa + aaa)$.
@@
 The representation of regex-counting and string-length as registers in CEFA, combined with the aforementioned size-reduction and under-approximation techniques, entails an efficient algorithm for solving RECL constraints.
-We implement the algorithm on top of OSTRICH, resulting into a new version of OSTRICH, called $\ostrichrecl$ for convenience.
+We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH, called $\ostrichrecl$ for convenience.
 %
@@
 %
-%Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contains sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators.
+%Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contain sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators.
 %
 The experimental results show that $\ostrichrecl$ can solve 49,128 out of 49,379 instances, while the state-of-the-art best solver Z3str3RE solves only 47,407 instances, with the timeout set as 60 seconds.
-Moreover, $\ostrichrecl$ and Z3str3RE spend almost the same amount of time in average, that is, 2.5 seconds, in solving each instance.
+Moreover, $\ostrichrecl$ and Z3str3RE spend almost the same amount of time, on average, 2.5 seconds, to solve each instance.
 In particular, the string constraint in~(\ref{eqn-running}) can be solved by $\ostrichrecl$ within one second. 
@@
 
-At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA that was introduced.
+At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA was introduced.
 This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, the regex-counting was unfolded explicitly.
-Moreover, in~\cite{atva2020}, the nonemptiness of CEFA was solved by utilizing the model checker nuXmv~\cite{nuxmv}, while in this work, it is solved by integrating the techniques of Parikh image computation, automata-size reduction, under approximation, and SMT solvers for LIA.
+Moreover, in~\cite{atva2020}, the nonemptiness of CEFA was solved by utilizing the model checker nuXmv~\cite{nuxmv}.
+In contrast, this work solves it by integrating the techniques of Parikh image computation, automata-size reduction, under approximation, and SMT solvers for LIA.
 The experimental results show that our approach achieves better performance than that in~\cite{atva2020}.
@@
 \paragraph*{Related work} 
-We discuss more related work about regular expressions with counting and real-world regular expressions in programming languages here.  
-Determinism of regular expressions with counting was investigated in~\cite{GGM12,CL15}.
-Counting-set automata was proposed in~\cite{redos_lenka,HS+23} to enable fast matching of a subclass of regular expressions with counting.
+Here, we discuss more related work about regular expressions with counting and real-world regular expressions in programming languages.  
+The determinism of regular expressions with counting was investigated in~\cite{GGM12,CL15}.
+Counting-set automata were proposed in~\cite{redos_lenka,HS+23} to match a subclass of regular expressions with counting quickly.
 Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regular expressions with counting.
-Nevertheless, nonemptiness problem of these automata, which is the key for automata-based string constraint solving, was not considered in ~\cite{redos_lenka,HS+23,GKM23}.
-Real-world regular expressions in programming languages include some features beyond classical regular expressions, e.g.
+Nevertheless, the nonemptiness problem of these automata was not considered in ~\cite{redos_lenka,HS+23,GKM23}, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
+Real-world regular expressions in programming languages include features beyond classical regular expressions, e.g.
 the greedy/lazy Kleene star, capturing groups, and back references.
-Real-world regular expressions haven been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.
+Real-world regular expressions have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.
 
@@
 Recently, Z3str3 has been extended to BD+23\cite{BD+23} by Berzish et al to handle string constants with regular memberships and length operation effectively.
-It uses automata to formalize the sematic of regular expression and applies several length-aware heuristics.
+It uses automata to formalize the semantic of regular expression and applies several length-aware heuristics.
 BD+23 can avoid building unsolvable automaton because the length abstraction is directly derived from the regex, not the automaton.

### 2023-05-09 2023-1-19/sections/implementation.tex
experiments

@@
 All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory.
-We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, with the timeout limit set as 60 seconds per instance.
+We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, where the timeout period is set as 60 seconds per instance.
 
@@
 \begin{description}
-\item[Q1] Is OSTRICH$^{\rm RECL}$ more efficient to solve RECL constraints than the state-of-the-art string constraint solvers ?
+\item[Q1] Does OSTRICH$^{\rm RECL}$ solve RECL constraints more efficiently than the state-of-the-art string constraint solvers ?
 
@@
 The experimental results can be found in Table~\ref{tab:results_all}.
-From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 49,128 instances, which is 5,127/2,315/25,369/12,808/1,721/1,756 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
+From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 49,483 instances correctly, which is 4,253/2,561/27,184/13,787/1,407/\zhilin{xxx} more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
 %    
-Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as Z3str3RE, the fastest solver.
-More specifically, OSTRICH$^{\rm RECL}$ spends 2.51 seconds per instance on average, while Z3str3RE spends 2.46 seconds per instance.
+Note that Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth.
+If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance.
+%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
+% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
+%
+Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as the fastest solver Z3str3RE.
+More specifically, OSTRICH$^{\rm RECL}$ spends 1.77 seconds per instance on average, while Z3str3RE spends 1.61 seconds per instance, while the other solvers spend at least 3 seconds per instance.
 Z3-Trau reports ``unknown'' on 21,152 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
-Furthermore, Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness issues, that is, their results on some instances are inconsistent with the results of the other three solvers, i.e.
-CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
 
-\zhilin{may add the results for the two benchmark suites separately.}
+%\zhilin{may add the results for the two benchmark suites separately.}
 
@@
 \end{center}
-  \caption{Experiment results for Q1}
+  \caption{Experiment results for Q1, where the timeout period is 60 seconds}
   \label{tab:results_all}

### 2023-05-09 2023-1-19/sections/implementation.tex
experiments

@@
 The experiment results can be found in Table~\ref{tab:results_heuristics}.
-From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help solve \zhilin{xxx} more instances, while adding under-approximation techniques help solve \zhilin{xxx} more instances, while adding both help solve \zhilin{xxx} more instances.
-Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.
+From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%, while adding under-approximation techniques help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%, while adding both help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%.
+%Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.
 
@@
 \end{center}
-  \caption{Experiment results for Q2}
+  \caption{Experiment results for Q2, where the timeout period is 60 seconds}
   \label{tab:results_heuristics}

### 2023-05-09 2023-1-19/sections/conclusion.tex
revise bib
abstract
conclusion

@@
-\documentclass{standalone}
-\begin{document}
+%!TEX root = ../main.tex
+%\documentclass{standalone}
+%\begin{document}
 
 %TODO
-This paper aims to efficiently solve the string constraints with bounded repetition and linear integer constraints on string length.
+This work proposes an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length.
+The approach is based on the idea of encoding counting operators in regular expressions by registers symbolically, instead of unfolding them explicitly.
+Moreover, this paper proposes an automata-size reduction technique and an under-approximation based solution searching technique to improve the performance.
+Finally, we use two benchmark suites comprising almost 50,000 instances in total to evaluate the performance of our approach.
+The experimental results show that our approach can solve more instances than the other solvers, in almost the same speed as the fasted solver.
+For the future work, we plan to investigate symbolic approaches to dealing with nested counting operators.
+
+%This paper aims to efficiently solve the string constraints with bounded repetition and linear integer constraints on string length.
 The bounded repetition is encoded by an automaton model CEFA whose size is linear to the bound.
@@
 
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{splncs04}
-\bibliography{ref}
-
-\end{document}
+%\end{document}

### 2023-05-09 2023-1-19/sections/implementation.tex
experiments

@@
 \paragraph*{AutomatArk benchmark suite.}
-The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraints.
+The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable).
 There are 8,751 instances in the AutomatArk suite.
-Note that the original AutomatArk benchmark suite in \cite{z3str3re}  includes 19,979 instances, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.
+Note that the original AutomatArk benchmark suite in \cite{z3str3re} include 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.
+Only 8,751 ones out of 19,979 instances contain occurrences of counting operators.
 
@@
 
-We evaluated the performance of OSTRICH$^{\rm RECL}$ against the main-stream string constraint solvers, including CVC5 (version 1.0.5) \cite{cvc5}, Z3seq (version 4.8.9) \cite{z3seq}, Z3-Trau (github commit 1628747) \cite{z3trau}, Z3str3 (github commit 59e9c87) \cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH (github commit 8297d8d) \cite{atva2020}.
+We evaluated the performance of OSTRICH$^{\rm RECL}$ against the state-of-the-art string constraint solvers, including CVC5 
+%(version 1.0.5) 
+\cite{cvc5}, Z3seq \cite{z3seq}, Z3-Trau 
+%(github commit 1628747) 
+\cite{z3trau}, Z3str3
+%(github commit 59e9c87) 
+\cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH\footnote{The name OSTRICH+ was used in~\cite{atva2020}, where nuXmv model checker was called to solve the nonemptiness of CEFA w.r.t. LIA. } 
+%(github commit 8297d8d) 
+\cite{atva2020}.
 All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory.

### 2023-05-09 2023-1-19/sections/implementation.tex
benchmark

@@
 The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable).
-There are 8,751 instances in the AutomatArk suite.
-Note that the original AutomatArk benchmark suite in \cite{z3str3re} include 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.
-Only 8,751 ones out of 19,979 instances contain occurrences of counting operators.
+There are 8,751 instances in the AutomatArk suite here.
+Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.
+%Only 8,751 ones that contain counting operators out of 19,979 instances.
 

### 2023-05-09 2023-1-19/sections/overview.tex
overview
some syntax error in overview

@@
 Furthermore, the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$. 
-A string $w$ is accepted by $\aut_1$ if when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition.
-Note here we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
+A string $w$ is accepted by $\aut_1$ if\denghang{,} when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition.
+Note here\denghang{Note that} we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
 Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators.
@@
 %In $\aut_1 \cap \aut_2 \cap \aut_3$, the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
-For technical convenience, we also think the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
+For technical convenience, we also think \denghang{of} the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
 For instance, the transitions corresponding to the self-loop around $(p_0, q_0, q'_0)$ are thought as $((p_0, q_0, q'_0), a', (p_0, q_0, q'_0), (1,0,0,1))$ with $a' \in \Sigma \setminus \{a\}$, since $r_1$ and $r_4$ are incremented in these transitions.
-With the updates thought as vectors, the resulting CEFA is illustrated in Figure~\ref{fig:overview:product}(b).
+With the updates thought \denghang{of} as vectors, the resulting CEFA is illustrated in Figure~\ref{fig:overview:product}(b).
 %the transitions corresponding to the self-loop is $(q, a', q', (1,1,0,0))$ with $a' \in \Sigma \setminus \{a\}$.
@@
 Therefore, the vector for this transition is $(1, 0, 0, 0)$.
-The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut_1 \cap \aut_2 \cap \aut_3$, producing a cost $(v_1, v_2, v_3, v_4)$ that satisfies $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $v_4 > 120$.
+The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist\denghang{exist to exists} $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut_1 \cap \aut_2 \cap \aut_3$, producing a cost $(v_1, v_2, v_3, v_4)$ that satisfies $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $v_4 > 120$.
 It is not hard to observe that the nonemptiness of $\aut_1 \cap \aut_2 \cap \aut_3$ w.r.t.
@@
 
-Nevertheless, it turns out that the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting into the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
+Nevertheless, it turns out that the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting into\denghang{result in} the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
 \cite{Haase18}).
@@
 Let $\cB$ denote the resulting automaton.
-We then think $\cB$ as an NFA, where the vectors $\myvec{v}$ are taken as the characters.
+We then think \denghang{of} $\cB$ as an NFA, where the vectors $\myvec{v}$ are taken as the characters.
 
@@
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
-Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experimental results in Section~\ref{sec:implementation} show us that they do reduce the sizes of NFA that are constructed from the regular expressions in practice.
+Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experimental results in Section~\ref{sec:implementation} show us that they do reduce the sizes of NFA that are \denghang{too wordy, remove that are} constructed from the regular expressions in practice.
 %thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
@@
 More precisely, we enforce a constant upper bound $B$ on the lengths of strings and search for a $B$-bounded satisfiable assignment, that is, a satisfiable assignment where the lengths of strings are bound by $B$.
-Initially we set $\ell$, an integer variable to denoting the lengths of strings, to $1$.
-If there does not exist a $\ell$-bounded satisfiable assignment, then we let $\ell:=\ell+1$ and continue the search, until finding a satisfiable assignment or reaching the bound $B$.
+Initially, we set $\ell$, an integer variable to denoting\denghang{denote} the lengths of strings, to $1$.
+If there does not exist a \denghang{too wordy, there is no} $\ell$-bounded satisfiable assignment, then we let $\ell:=\ell+1$ and continue the search, until finding a satisfiable assignment or reaching the bound $B$.
 For instance, if we remove $|x| > 120$ from the string constraint~(\ref{eqn-running}), then the resulting constraint is satisfiable.
@@
 Note that the accepting run produces $(1,1,0,3)$, a vector of register values,  which satisfies $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$.
+(See Section~\ref{subsec:cefadec} for more details of the heuristic.)
 

### 2023-05-09 2023-1-19/sections/overview.tex
revise syntax in overview

@@
 A string $w$ is accepted by $\aut_1$ if\denghang{,} when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition.
-Note here\denghang{Note that} we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
+Note here\denghang{here to that} we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
 Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators.
@@
 \cite{Haase18}).
-To tackle this issue, we proposes techniques to reduce the sizes of NFA over the alphabet $\costset$.
+To tackle this issue, we proposes\denghang{propose} techniques to reduce the sizes\denghang{size} of NFA over the alphabet $\costset$.
 
@@
 % \pagebreak
+
+The wrong encoding of the backslash causes the soundness errors of z3str3re. Two backslashes are seen as two characters in the Smtlib2.6 standard, but z3str3re encodes them as one.

### 2023-05-09 2023-1-19/sections/recl.tex
revise syntax in recl

@@
 A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, union $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
-An integer term is is built from constants $n$, variables $i$, and string lengths $|x|$, by operators $+$ and $-$.
+An integer term is is \denghang{double is} built from constants $n$, variables $i$, and string lengths $|x|$, by operators $+$ and $-$.
 % 
@@
 
-The definition of the semantics of RECL is somehow standard. Nevertheless, for completeness, we include the definition of semantics here.
+The definition of the semantics of RECL is somehow\denghang{inappropriate use of somehow} standard. Nevertheless, for completeness, we include the definition of semantics here.
 

### 2023-05-09 2023-1-19/sections/cefa.tex
revise syntax in cefa

@@
 %
-Intuitively, CEFA add write-only cost registers to finite state automata.
+Intuitively, CEFA add\denghang{adds} write-only cost registers to finite state automata.
 Here by ``write-only'', we mean that the cost registers can only be written/updated, but cannot be read, that is, cannot be used to guard the transitions.
@@
 
-The semantics of CEFA is define as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
+The semantics of CEFA is define\denghang{defined} as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
 A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
@@
 The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$.
-Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+Note here \denghang{that} we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
 We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.
@@
 We would like to remark that the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion in the sense that the accepting condition does not distinguish final states.
-This technical choice is made so that determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.
+This technical choice is made so that \denghang{the} determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.
 
@@
 %and $\alpha(q_n)[\myvec{\myvec{v'}/\myvec{r}]$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}}$.
-Note here we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+Note here \denghang{that} we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
 A string $w$ is \emph{accepted} by $\aut$ if there is an accepting run of $\aut$ on $w$.
@@
 The Parikh image of $\aut$ is a Presburger formula $\psi(\aut)$, which is consistent and connected.
-The register value formula ensures the register values are correctly updated regarding the accepting run.
+The register value formula ensures \denghang{that} the register values are correctly updated regarding the accepting run.
 % \begin{example} \label{exapmle:parikh}

### 2023-05-09 2023-1-19/sections/implementation.tex
revise syntax in implementation

@@
 
-We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting into a version of OSTRICH called OSTRICH$^{\rm RECL}$.
+We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting into\denghang{in} a version of OSTRICH called OSTRICH$^{\rm RECL}$.
 Then we do experiments on two benchmark suites, to evaluate the performance of OSTRICH$^{\rm RECL}$.

### 2023-05-10 2023-1-19/sections/introduction.tex
intro
revise syntax in intro

@@
 %
-Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade or so, including the state-of-the-art string constraint solvers (e.g.
+Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade or so\denghang{or so?}, including the state-of-the-art string constraint solvers (e.g.
 Z3~\cite{Z3}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
@@
 
-\zhilin{stopped here}
-
 %%%%%%%%%%%%%%%%%%%%%%% original texts by Denghang %%%%%%%%%%%%%%%%%

### 2023-05-10 2023-1-19/sections/overview.tex
revise syntax in overview

@@
 %Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
-Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
+Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into\denghang{in} a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
 %Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.

### 2023-05-11 2023-1-19/sections/implementation.tex
experiment decripption be consistent with the result

@@
 
-Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoL. In total, there are 49,379 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
+Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoL. In total, there are 48,834 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
 
@@
 The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable).
-There are 8,751 instances in the AutomatArk suite here.
+There are 8,215 instances in the AutomatArk suite here.
 Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.
@@
 The experimental results can be found in Table~\ref{tab:results_all}.
-From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 49,483 instances correctly, which is 4,253/2,561/27,184/13,787/1,407/\zhilin{xxx} more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
+From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 48,689 instances correctly, which is 3,982/2,263/24,568/12,823/1,082/7083\zhilin{xxx} more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
 %    
@@
 Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as the fastest solver Z3str3RE.
-More specifically, OSTRICH$^{\rm RECL}$ spends 1.77 seconds per instance on average, while Z3str3RE spends 1.61 seconds per instance, while the other solvers spend at least 3 seconds per instance.
-Z3-Trau reports ``unknown'' on 21,152 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
+More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while Z3str3RE spends 1.71 seconds per instance, while the other solvers spend at least 3 seconds per instance.
+Z3-Trau reports ``unknown'' on 21,655 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
 

### 2023-05-11 2023-1-19/sections/implementation.tex
experiments

@@
 The experimental results can be found in Table~\ref{tab:results_all}.
-From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 48,689 instances correctly, which is 3,982/2,263/24,568/12,823/1,082/7083\zhilin{xxx} more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
+From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solvers almost all 48,834 instances, except 144 of them, that is, it solves 48,689 instances correctly, which is 3,982/2,263/24,568/12,823/1,082/7083 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
 %    
@@
 %
-Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as the fastest solver Z3str3RE.
-More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while Z3str3RE spends 1.71 seconds per instance, while the other solvers spend at least 3 seconds per instance.
+Moreover, OSTRICH$^{\rm RECL}$ is the second fastest solver.
+More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3 seconds per instance.
 Z3-Trau reports ``unknown'' on 21,655 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

### 2023-05-11 2023-1-19/sections/cefa.tex
experiments and resolve the comments of denghang

@@
 %
-Intuitively, CEFA add\denghang{adds} write-only cost registers to finite state automata.
+Intuitively, CEFA add write-only cost registers to finite state automata.
 Here by ``write-only'', we mean that the cost registers can only be written/updated, but cannot be read, that is, cannot be used to guard the transitions.
@@
 
-The semantics of CEFA is define\denghang{defined} as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
+The semantics of CEFA is defined as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
 A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
@@
 The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$.
-Note here \denghang{that} we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+Note that we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
 We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.
@@
 We would like to remark that the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion in the sense that the accepting condition does not distinguish final states.
-This technical choice is made so that \denghang{the} determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.
+This technical choice is made so that the determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.
 

### 2023-05-11 2023-1-19/sections/implementation.tex
experiments and resolve the comments of denghang

@@
 
-We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting into\denghang{in} a version of OSTRICH called OSTRICH$^{\rm RECL}$.
+We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting in a version of OSTRICH called OSTRICH$^{\rm RECL}$.
 Then we do experiments on two benchmark suites, to evaluate the performance of OSTRICH$^{\rm RECL}$.
@@
 The experimental results can be found in Table~\ref{tab:results_all}.
-From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solvers almost all 48,834 instances, except 144 of them, that is, it solves 48,689 instances correctly, which is 3,982/2,263/24,568/12,823/1,082/7083 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
+From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solvers almost all 48,834 instances, except 145 of them, that is, it solves 48,698 instances correctly, which is 3,994/2,272/24,577/12,832/1,091/7,092 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
 %    
@@
 Moreover, OSTRICH$^{\rm RECL}$ is the second fastest solver.
-More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3 seconds per instance.
-Z3-Trau reports ``unknown'' on 21,655 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
+More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.
+Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
 
@@
 
-To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively.
+To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the size-reduction, under-approximation, or both are removed. 
+For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both size-reduction and under-approximation techniques are removed, 
+OSTRICH$^{\rm RECL^-}_{+\rm SR}$ (resp.
+OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the size-reduction (resp.
+under-approximation) techniques to OSTRICH$^{\rm RECL^-}$.
+%OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
 The experiment results can be found in Table~\ref{tab:results_heuristics}.
-From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%, while adding under-approximation techniques help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%, while adding both help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%.
+From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column).
+Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ help to solve 19 more sat instances, while reduces the number of solved unsat instances by 3, since under approximation techniques do not help to solve unsat instances.
 %Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.
@@
 
-\zhilin{stopped here}
+%\zhilin{stopped here}
 

### 2023-05-11 2023-1-19/sections/introduction.tex
experiments and resolve the comments of denghang

@@
 %
-Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade or so\denghang{or so?}, including the state-of-the-art string constraint solvers (e.g.
+Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade, including the state-of-the-art string constraint solvers (e.g.
 Z3~\cite{Z3}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
@@
 %
-Furthermore, we utilize a collection of benchmark suites, which comprise 49,379 RECL constraints in total, to evaluate the performance of $\ostrichrecl$.
+Furthermore, we utilize a collection of benchmark suites, which comprise 48,834 RECL constraints in total, to evaluate the performance of $\ostrichrecl$.
 The collection of benchmark suites includes a widely-used benchmark suite for string constraints, as well as benchmark suites comprising constraints generated from regular expressions in various open source regex libraries.
@@
 %
-The experimental results show that $\ostrichrecl$ can solve 49,128 out of 49,379 instances, while the state-of-the-art best solver Z3str3RE solves only 47,407 instances, with the timeout set as 60 seconds.
-Moreover, $\ostrichrecl$ and Z3str3RE spend almost the same amount of time, on average, 2.5 seconds, to solve each instance.
+The experimental results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while the state-of-the-art best solver Z3str3RE on RECL constraints solves only 47,607 instances, with the timeout period set as 60 seconds.
 In particular, the string constraint in~(\ref{eqn-running}) can be solved by $\ostrichrecl$ within one second.
-In comparison, CVC5, Z3str3, and Z3seq solve only 44,001, 36,320, 46,813 instances respectively, with an average time 7.8, 7.7, 3.8 seconds per instance.
+Moreover, while $\ostrichrecl$ solves 1,091 more instances than Z3str3RE, it is only slightly slower than it (2.93 versus 1.71 seconds per instance). 
+In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively, with an average time 5.67, 3.49, 5.41, and 8.54 seconds per instance.
+(See Table~\ref{tab:results_all})
 
@@
 This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, the regex-counting was unfolded explicitly.
-Moreover, in~\cite{atva2020}, the nonemptiness of CEFA was solved by utilizing the model checker nuXmv~\cite{nuxmv}.
-In contrast, this work solves it by integrating the techniques of Parikh image computation, automata-size reduction, under approximation, and SMT solvers for LIA.
-The experimental results show that our approach achieves better performance than that in~\cite{atva2020}.
-\zhilin{this point should be supposed by experimental results.}
+Moreover, in~\cite{atva2020}, the nonemptiness of CEFA w.r.t.
+LIA formulas was solved by utilizing the model checker nuXmv~\cite{nuxmv}.
+In contrast, this work solves it by integrating the techniques of Parikh image computation, automata-size reduction, and under approximation.
+The experimental results show that our approach solves 7,092 more instances while spending less time than the solver in~\cite{atva2020}.
+(See Table~\ref{tab:results_all}, where OSTRICH denotes the solver in \cite{atva2020}.)
 

### 2023-05-11 2023-1-19/sections/overview.tex
experiments and resolve the comments of denghang

--- 2023-05-09 2023-1-19/sections/overview.tex
@@
 %Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
-Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
+Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting in a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
 %Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.
@@
 Furthermore, the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$. 
-A string $w$ is accepted by $\aut_1$ if\denghang{,} when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition.
-Note here\denghang{here to that} we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
+A string $w$ is accepted by $\aut_1$ if, when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition.
+Note that we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
 Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators.
@@
 %In $\aut_1 \cap \aut_2 \cap \aut_3$, the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
-For technical convenience, we also think \denghang{of} the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
+For technical convenience, we also think of the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
 For instance, the transitions corresponding to the self-loop around $(p_0, q_0, q'_0)$ are thought as $((p_0, q_0, q'_0), a', (p_0, q_0, q'_0), (1,0,0,1))$ with $a' \in \Sigma \setminus \{a\}$, since $r_1$ and $r_4$ are incremented in these transitions.
-With the updates thought \denghang{of} as vectors, the resulting CEFA is illustrated in Figure~\ref{fig:overview:product}(b).
+With the updates thought of as vectors, the resulting CEFA is illustrated in Figure~\ref{fig:overview:product}(b).
 %the transitions corresponding to the self-loop is $(q, a', q', (1,1,0,0))$ with $a' \in \Sigma \setminus \{a\}$.
@@
 Therefore, the vector for this transition is $(1, 0, 0, 0)$.
-The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist\denghang{exist to exists} $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut_1 \cap \aut_2 \cap \aut_3$, producing a cost $(v_1, v_2, v_3, v_4)$ that satisfies $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $v_4 > 120$.
+The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut_1 \cap \aut_2 \cap \aut_3$, producing a cost $(v_1, v_2, v_3, v_4)$ that satisfies $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $v_4 > 120$.
 It is not hard to observe that the nonemptiness of $\aut_1 \cap \aut_2 \cap \aut_3$ w.r.t.
@@
 
-Nevertheless, it turns out that the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting into\denghang{result in} the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
+Nevertheless, it turns out that the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting  in  the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
 \cite{Haase18}).
-To tackle this issue, we proposes\denghang{propose} techniques to reduce the sizes\denghang{size} of NFA over the alphabet $\costset$.
+To tackle this issue, we propose techniques to reduce the sizes of NFA over the alphabet $\costset$.
 
@@
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
-Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experimental results in Section~\ref{sec:implementation} show us that they do reduce the sizes of NFA that are \denghang{too wordy, remove that are} constructed from the regular expressions in practice.
+Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experimental results in Section~\ref{sec:implementation} show us that they do reduce the sizes of NFA constructed from the regular expressions in practice.
 %thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
@@
 More precisely, we enforce a constant upper bound $B$ on the lengths of strings and search for a $B$-bounded satisfiable assignment, that is, a satisfiable assignment where the lengths of strings are bound by $B$.
-Initially, we set $\ell$, an integer variable to denoting\denghang{denote} the lengths of strings, to $1$.
-If there does not exist a \denghang{too wordy, there is no} $\ell$-bounded satisfiable assignment, then we let $\ell:=\ell+1$ and continue the search, until finding a satisfiable assignment or reaching the bound $B$.
+Initially, we set $\ell$, an integer variable to denote the lengths of strings, to $1$.
+If there does not exist an $\ell$-bounded satisfiable assignment, then we let $\ell:=\ell+1$ and continue the search, until finding a satisfiable assignment or reaching the bound $B$.
 For instance, if we remove $|x| > 120$ from the string constraint~(\ref{eqn-running}), then the resulting constraint is satisfiable.

### 2023-05-11 2023-1-19/sections/recl.tex
experiments and resolve the comments of denghang

--- 2023-05-05 2023-1-19/sections/recl.tex
@@
 A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, union $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
-An integer term is is built from constants $n$, variables $i$, and string lengths $|x|$, by operators $+$ and $-$.
+An integer term is built from constants $n$, variables $i$, and string lengths $|x|$, by operators $+$ and $-$.
 % 
@@
 
-The definition of the semantics of RECL is somehow standard. Nevertheless, for completeness, we include the definition of semantics here.
+The definition of the semantics of RECL is standard. Nevertheless, for readibility, we include the definition of its semantics here.
 

### 2023-05-11 2023-1-19/sections/abstract.tex
intro
space adjustment

@@
 % we propose state reduction techniques and under-approximation to improve the performance further. 
-We implement the algorithms and do extensive experiments to validate our approach. The experimental results show that 
-our approach can solve more problem instances than the other tools, with the same or a better performance.
+We implement the algorithms and validate our approach on 48,834 benchmark instances. The experimental results show that 
+our approach can solve more instances than the other tools, with comparable or better performance.
 % performance of this approach compared against the state-of-the-art string solvers.
@@
 
-\keywords{Regex Expressions, Counting, Length, Automata, Registers, Linear Integer Arithmetic}
+%\keywords{Rgular Expressions, Counting, Length, Automata, Registers, Linear Integer Arithmetic}
 %\end{document}

### 2023-05-11 2023-1-19/sections/implementation.tex
space adjustment

@@
 
-\paragraph*{AutomatArk benchmark suite.}
+\medskip
+\noindent
+\emph{AutomatArk benchmark suite.}
 The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable).
@@
 
-\paragraph*{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite.
+\medskip
+\noindent
+\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite.
 These constraints are generated by extracting regular expressions with counting operators from \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form
-$$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$$   
+$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$   
 where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$.
@@
 
-\begin{table}[ht]
+\begin{table}[t]
+\vspace{-1mm}
 \begin{center}
@@
   \label{tab:results_all}
+\vspace{-5mm}
+\end{table}
+
+\begin{table}[ht]
+\vspace{-3mm}
+\begin{center}
+  \subimport{tables}{table_heuristic.tex}
+\end{center}
+  \caption{Experiment results for Q2, where the timeout period is 60 seconds}
+  \label{tab:results_heuristics}
+\vspace{-5mm}
 \end{table}
@@
 %Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.
-
-\begin{table}[ht]
-\begin{center}
-  \subimport{tables}{table_heuristic.tex}
-\end{center}
-  \caption{Experiment results for Q2, where the timeout period is 60 seconds}
-  \label{tab:results_heuristics}
-\end{table}
 

### 2023-05-11 2023-1-19/sections/introduction.tex
space adjustment

@@
 
-\paragraph*{Contribution} In this work, we focus on the class of string constraints with regular membership and string-length function, where the counting operators may occur in regular expressions (called RECL for brevity).
+\medskip
+\noindent 
+\emph{Contribution.} In this work, we focus on the class of string constraints with regular membership and string-length function, where the counting operators may occur in regular expressions (called RECL for brevity).
 We propose an automata-theoretical approach for solving RECL constraints.
@@
 Moreover, the string-length function can also be modeled by registers in CEFA.
-Therefore, the satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA.
+Then the satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA with respect to a linear integer arithmetic (LIA) formula whose free variables are registers of CEFA.
 
-According to the results from~ \cite{atva2020}, a linear integer arithmetic (LIA) formula can be computed to represent the potential values of registers in CEFA.
-Thus, the nonemptiness of CEFA can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers for LIA.
+According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
+Thus, the nonemptiness of CEFA w.r.t.
+LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers for LIA.
 %
 Because the sizes of LIA formulas depend much on the sizes of CEFA, it is beneficial to reduce the sizes of CEFA, in order to achieve a good performance.
-As a result, we propose various techniques to reduce the state space, the number of transitions, and the number of registers for CEFA.
+As a result, we propose various techniques to reduce the state space and the number of transitions for CEFA.
 Furthermore, since the computation of LIA formulas from CEFA is relatively expensive, we also propose a method of searching for strings that are accepted by CEFA, based on under approximations, before constructing the LIA formulas.
@@
 At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA was introduced.
-This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, the regex-counting was unfolded explicitly.
+This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, regex-counting was unfolded explicitly.
 Moreover, in~\cite{atva2020}, the nonemptiness of CEFA w.r.t.
 LIA formulas was solved by utilizing the model checker nuXmv~\cite{nuxmv}.
-In contrast, this work solves it by integrating the techniques of Parikh image computation, automata-size reduction, and under approximation.
+In contrast, this work solves it by integrating the techniques of Parikh-image computation, automata-size reduction, and under approximation.
 The experimental results show that our approach solves 7,092 more instances while spending less time than the solver in~\cite{atva2020}.
@@
 
-\paragraph*{Related work} 
+\medskip
+\noindent
+\emph{Related work.} 
 Here, we discuss more related work about regular expressions with counting and real-world regular expressions in programming languages.  
@@
 
-\paragraph*{Organization} The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper.
-Section~\ref{sec:pre} introduces the preliminaries.
+\medskip
+\noindent
+\emph{Organization.} 
+The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper. Section~\ref{sec:pre} introduces the preliminaries. 
 Section~\ref{sec:recl} presents the syntax and semantics of RECL. 

### 2023-05-11 2023-1-19/sections/preliminaries.tex
space adjustment

@@
 
-\paragraph*{Strings and languages.}
+\medskip
+\noindent \emph{Strings and languages.}
+%\paragraph*{Strings and languages.}
 A string over $\Sigma$ is a (possibly empty) sequence of elements from $\Sigma$,
@@
 
-\paragraph*{Finite automata.} 
+\medskip
+\noindent 
+\emph{Finite automata.} 
 A \emph{(nondeterministic) finite automaton} (NFA)  is a tuple $\NFA=(Q, \Sigma, \delta, I, F)$, where $Q$ is a finite set of states, $\Sigma$ is a finite alphabet, $\delta \subseteq Q \times \Sigma \times Q$ is the transition relation, $I \subseteq Q$ is the set of initial states, and $F \subseteq Q$ is the set of final states.
@@
 
-\paragraph*{Linear integer arithmetic and Parikh images.}
+\medskip
+\noindent 
+\emph{Linear integer arithmetic and Parikh images.}
 We will also use standard quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulae, which are typically ranged over by $\phi, \varphi$, etc. 

### 2023-05-11 2023-1-19/sections/introduction.tex
space ajustment

@@
 
-Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from the string constraints with regex-counting and string-length, especially when the counting bounds are large.
-For instance, none of the string solvers e.g.
-CVC4/5, Z3, Z3str3RE, OSTRICH is capable of solving the following constraint within 300 seconds,
+Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from string constraints with regex-counting and string-length, especially when the counting bounds are large.
+For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 300 seconds,
 %
@@
 \end{equation}
-Intuitively, the constraint in (\ref{eqn-running}) specifies that $x$ is a concatenation of three subwords $x_1, x_2, x_3$ where $a$ (resp.
+Intuitively, the constraint in (\ref{eqn-running}) specifies that $x$ is a concatenation of three strings $x_1, x_2, x_3$ where $a$ (resp.
 $b, c$) does not occur in $x_1$ (resp.
@@
 \emph{Related work.} 
-Here, we discuss more related work about regular expressions with counting and real-world regular expressions in programming languages.  
-The determinism of regular expressions with counting was investigated in~\cite{GGM12,CL15}.
-Counting-set automata were proposed in~\cite{redos_lenka,HS+23} to match a subclass of regular expressions with counting quickly.
-Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regular expressions with counting.
+We discuss more related work about regexes with counting and real-world regexes in programming languages.  
+The determinism of regexes with counting was investigated in~\cite{GGM12,CL15}.
+Counting-set automata were proposed in~\cite{redos_lenka,HS+23} to match a subclass of regexes with counting quickly.
+Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regexes with counting.
 Nevertheless, the nonemptiness problem of these automata was not considered in ~\cite{redos_lenka,HS+23,GKM23}, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
-Real-world regular expressions in programming languages include features beyond classical regular expressions, e.g.
+Real-world regexes in programming languages include features beyond classical regular expressions, e.g.
 the greedy/lazy Kleene star, capturing groups, and back references.
-Real-world regular expressions have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.
+Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.
 

### 2023-05-11 2023-1-19/sections/recl.tex
space adjustment
space ajustment

@@
 \begin{figure}[h]
+\vspace{-3mm}
   \centering
@@
   \caption{Syntax of RECL }\label{fig:syntax}
+\vspace{-3mm}
 \end{figure}
@@
 The mapping $\theta$ can be naturally extended to the set of integer terms. For instance, $\theta(|x|) =|\theta(x)|$, $\theta(t_1 + t_2) = \theta(t_1) + \theta(t_2)$. 
-A  mapping $\theta$ is said to satisfy $\varphi$, denoted by $\theta \models \varphi$, if one of the following holds,  
-\begin{itemize}
-\item $\varphi \equiv x \in \regex$ and $\theta(x) \in \Lang(\regex)$, 
+A  mapping $\theta$ is said to satisfy $\varphi$, denoted by $\theta \models \varphi$, if one of the following holds: 
+%\begin{itemize}
+%\item 
+$\varphi \equiv x \in \regex$ and $\theta(x) \in \Lang(\regex)$, 
 %
@@
 %
-\item $\varphi \equiv t_1\ \op\ t_2$ and $\theta(t_1)\ \op\ \theta(t_2)$, 
+%\item 
+$\varphi \equiv t_1\ \op\ t_2$ and $\theta(t_1)\ \op\ \theta(t_2)$, 
 %
-\item $\varphi \equiv \varphi_1 \wedge \varphi_2$ and $\theta \models \varphi_1$ and $\theta \models \varphi_2$.
-\end{itemize}
+%\item 
+$\varphi \equiv \varphi_1 \wedge \varphi_2$ and $\theta \models \varphi_1$ and $\theta \models \varphi_2$.
+%\end{itemize}
 A RECL formula $\varphi$ is said to be satisfiable if there is a mapping $\theta$ such that $\theta \models \varphi$.

### 2023-05-11 2023-1-19/sections/abstract.tex
space adjustment

@@
 
-Regular expressions (abbreviated as regex) and string-length function are widely used in string-manipulating programs. 
+Regular expressions (regex for short) and string-length function are widely used in string-manipulating programs. 
 %Solving string constraints involving regular membership and string-length function has been widely investigated. 
-Counting is a frequently used feature of regular expressions that count the number of matchings of sub-patterns.
-The state-of-the-art string solvers e.g.
-CVC4/5, Z3str3(RE), and Z3seq are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bounds are large.
-In this work, we propose an automata-theoretic approach for solving such a class of string constraints efficiently.
+Counting is a frequently used feature of regexes that count the number of matchings of sub-patterns.
+The state-of-the-art string solvers are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bounds are large.
+In this work, we propose an automata-theoretic approach for solving such class of string constraints efficiently.
 %

### 2023-05-11 2023-1-19/sections/overview.tex
space adjustment
space ajustment
overview

@@
 \begin{figure}[ht]
+\vspace{-3mm}
   \centering
-  \includegraphics[width = 0.95\textwidth]{sections/overview-cefa.pdf}
+  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa.pdf}
   \caption{CEFA for $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, $\Sigma^* c^+$, and $|x|$}
   \label{fig:overview}
+\vspace{-5mm}
 \end{figure}
@@
 \begin{figure}[ht]
+\vspace{-3mm}
   \centering
-  \includegraphics[width = 0.95\textwidth]{sections/overview-cefa-product.pdf}
+  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa-product.pdf}
   \caption{$\aut_1 \cap \aut_2 \cap \aut_3$: Intersection of $\aut_1$, $\aut_2$, and $\aut_3$}
   \label{fig:overview:product}
+\vspace{-6mm}
 \end{figure}
@@
 \begin{figure}[ht]
+\vspace{-3mm}
   \centering
@@
   \label{fig:overview:product:reduced}
+\vspace{-3mm}
 \end{figure}
@@
 
-The wrong encoding of the backslash causes the soundness errors of z3str3re. Two backslashes are seen as two characters in the Smtlib2.6 standard, but z3str3re encodes them as one.
+%The wrong encoding of the backslash causes the soundness errors of z3str3re. Two backslashes are seen as two characters in the Smtlib2.6 standard, but z3str3re encodes them as one.

### 2023-05-12 2023-1-19/sections/introduction.tex
intro

@@
 %
-Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade, including the state-of-the-art string constraint solvers (e.g.
-Z3~\cite{Z3}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
+Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade, including the state-of-the-art string constraint solvers, e.g.
+Z3seq~\cite{z3seq}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
 Z3-Trau~\cite{Z3-trau}, OSTRICH~\cite{CHL+19}, Slent~\cite{WC+18}, among many others.
@@
 According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% Java, JavaScript, and Python software projects.
-Moreover, the statistics from \cite{malware_detection_3_kudzu} show that string-length function occupies 78\% of the occurrences of string operations in 18 Javascript applications. 
+Moreover, that string-length function occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}. 
 %Operations like \verb|length| that take string inputs and return an integer frequently appear in real-world JavaScript applications (78\% of string operations in 18 applications)
@@
 Note that Kleene star and Kleene plus operator can be seen as special cases of counting operator. For instance, $a^*$ and $a^+$ are equivalent to $a^{\{0,\infty\}}$ and $a^{\{1,\infty\}}$.
-Counting is also a frequently used feature of regular expressions.
+Counting is a frequently used feature of regular expressions.
 According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while the other forms of counting occur in more than 20\% of them.
@@
 A typical way for string constraint solvers to deal with regex-counting is to unfold regular expressions with counting into those \emph{without} counting by using the concatenation operator.
-For instance, $a^{\{1, 4\}}$ is unfolded into $a(\varepsilon + a + aa + aaa)$.
-Since the unfolding incurs an exponential blow-up on the constraint sizes (where the integer constants are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the bounds are large.
+For instance, $a^{\{1, 4\}}$ is unfolded into $a(\varepsilon + a + aa + aaa)$ and $a^{\{2,\infty\}}$ is unfolded into $aaa^{*}$.
+Since the unfolding incurs an exponential blow-up on the sizes of constraints (assuming that the integer constants in string constraints are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the bounds are large.
 
@@
 We propose an automata-theoretical approach for solving RECL constraints.
-Our main idea is to represent the counting operators by registers in automata, instead of unfolding them explicitly.
+Our main idea is to represent the counting operators by registers in automata (as much as possible), instead of unfolding them explicitly.
 Our approach is built upon an automata model called cost-enriched finite automata (CEFA), which was proposed in~\cite{atva2020} to solve string constraints involving the integer data type.
@@
 Because the sizes of LIA formulas depend much on the sizes of CEFA, it is beneficial to reduce the sizes of CEFA, in order to achieve a good performance.
-As a result, we propose various techniques to reduce the state space and the number of transitions for CEFA.
+As a result, we propose various techniques to reduce the state space and the number of transitions of CEFA.
 Furthermore, since the computation of LIA formulas from CEFA is relatively expensive, we also propose a method of searching for strings that are accepted by CEFA, based on under approximations, before constructing the LIA formulas.
@@
 %
-The experimental results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while the state-of-the-art best solver Z3str3RE on RECL constraints solves only 47,607 instances, with the timeout period set as 60 seconds.
-In particular, the string constraint in~(\ref{eqn-running}) can be solved by $\ostrichrecl$ within one second.
-Moreover, while $\ostrichrecl$ solves 1,091 more instances than Z3str3RE, it is only slightly slower than it (2.93 versus 1.71 seconds per instance). 
+The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while the state-of-the-art best solver Z3str3RE on RECL constraints solves only 47,607 instances (where the timeout period is set as 60 seconds).
+Moreover, while $\ostrichrecl$ solves 1,091 more instances than Z3str3RE, its performance is comparable to Z3str3RE (2.93 versus 1.71 seconds per instance).
 In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively, with an average time 5.67, 3.49, 5.41, and 8.54 seconds per instance.
-(See Table~\ref{tab:results_all})
+(See Table~\ref{tab:results_all} for more details.)
 
@@
 Moreover, in~\cite{atva2020}, the nonemptiness of CEFA w.r.t.
-LIA formulas was solved by utilizing the model checker nuXmv~\cite{nuxmv}.
+LIA formulas was solved by utilizing the nuXmv model checker~\cite{nuxmv}.
 In contrast, this work solves it by integrating the techniques of Parikh-image computation, automata-size reduction, and under approximation.
-The experimental results show that our approach solves 7,092 more instances while spending less time than the solver in~\cite{atva2020}.
+The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time.
 (See Table~\ref{tab:results_all}, where OSTRICH denotes the solver in \cite{atva2020}.)
@@
 the greedy/lazy Kleene star, capturing groups, and back references.
-Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.
+Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
+Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22}.
 
@@
 
-\medskip
+\smallskip
 \noindent

### 2023-05-12 2023-1-19/sections/algorithms.tex
experiments
revise syntax in algorithms
space adjustment
space ajustment
section 5 and 6

@@
 The goal of this section is to show how we solve RECL constraints by utilizing CEFA. 
-At first, we show how to reduce the satisfiability of RECL constraints into a decision problem for CEFA defined in the sequel. Then we propose algorithms to solve the decision problem.
+At first, we reduce the satisfiability of RECL constraints into a decision problem for CEFA defined in the sequel. Then we propose an algorithm to solve the decision problem.
 
 \begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula\footnote{The decision problem was called satisfiability of an LIA formula w.r.t. CEFA in \cite{atva2020}.}, abbreviated as $\cefadec$]
-Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+Suppose that $x_1, \cdots, x_n$ are string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, and the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, moreover, $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
 Then  the CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are said to be nonempty w.r.t.
-$\varphi$ if there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors
-$\myvec{v_{1,1}}, \cdots, \myvec{v_{1, l_1}}, \cdots, \myvec{v_{n, 1}}, \cdots, \myvec{v_{n, l_n}}$ such that $(\theta(x_i); \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ for every $i \in [n], j \in [l_i]$,
+$\varphi$ if there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{i,j}}$ for $i \in [n], j \in [l_i]$
+%$\myvec{v_{1,1}}, \cdots, \myvec{v_{1, l_1}}, \cdots, \myvec{v_{n, 1}}, \cdots, \myvec{v_{n, l_n}}$ 
+such that $(\theta(x_i); \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ for every $i \in [n], j \in [l_i]$,
 % \in \aut_{i,1}(\eta(x_1)), \cdots, \myvec{v_{i, l_i}} \in \aut_{i,l_i}(\eta(x_i))$ for every $i \in [n]$  
 %\cdots, \myvec{v_{n,1}} \in \aut_{n,1}(w_n), \cdots, \myvec{v_{n, l_n}} \in \aut_{n, l_n}(w_n)$ 
-and $\varphi[\myvec{v_{1,1}}/R_{\aut_{1,1}}, \cdots, \myvec{v_{n, l_n}}/R_{\aut_{n, l_n}}]$ is true. 
+and 
+$\varphi[(\myvec{v_{i,j}}/R_{\aut_{i,j}})_{i \in [n], j \in [l_i]}]$ is true. 
+%$\varphi[\myvec{v_{1,1}}/R_{\aut_{1,1}}, \cdots, \myvec{v_{n, l_n}}/R_{\aut_{n, l_n}}]$ is true. 
 \end{definition}
@@
 \end{proposition}
-The decision procedure for proving the upper bound in Proposition~\ref{prop-cefadec} in \cite{atva2020}  was not implemented as a matter of fact.
+The decision procedure in \cite{atva2020} was only used to prove the upper bound in Proposition~\ref{prop-cefadec} and not implemented as a matter of fact.
 Instead, the symbolic model checker nuXmv was used to solve $\cefadec$ in \cite{atva2020}.
-We do not rely on nuXmv in this work and will propose an efficient algorithm for solving $\cefadec$ in Section~\ref{subsec:cefadec}.
+We do not rely on nuXmv in this work and shall propose an efficient algorithm for solving $\cefadec$ in Section~\ref{subsec:cefadec}.
 
@@
 
+\vspace{-2mm}
 \subsection{From $\reclsat$ to $\cefadec$} \label{subsec:regex2cefa}
 
-Let $\varphi$ be an RECL constraint and $x_1, \cdots, x_n$ be an enumeration of the string variables occurring in $\varphi$.
+Let $\varphi$ be a RECL constraint and $x_1, \cdots, x_n$ be an enumeration of the string variables occurring in $\varphi$.
 Moreover, let $\varphi \equiv \varphi_1 \wedge \varphi_2$ such that $\varphi_1$ is a conjunction of regular membership constraints of $\varphi$, and $\varphi_2$ is a conjunction of length constraints of $\varphi$.
@@
 
+\vspace{-2mm}
 \subsection{Solving $\cefadec$} \label{subsec:cefadec}
@@
 %Furthermore, for each $i \in [n]$, we can remove the redundancy of characters/vectors in $\cC_i$.
-
-\zhilin{stopped here}
 

### 2023-05-12 2023-1-19/sections/cefa.tex
space ajustment
section 5 and 6

@@
 \end{definition}
+For a CEFA $\aut$, we use $R_\aut$ to denote the set of registers of $\aut$. 
 %The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
@@
 
-For readability, from now on, we assume a linear order on $R$ and write $R$ as a vector $\myvec{r} = (r_1, \cdots, r_k)$.
+For convenience, from now on, we assume a linear order on $R$ and write $R$ as a vector $\myvec{r} = (r_1, \cdots, r_k)$.
 Accordingly, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where for each $i \in [k]$, $v_i$ is the update on the value of $r_i$.
@@
 The semantics of CEFA is defined as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
-A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
+%A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
 %An \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$ with $q_0 \in I$, where the value of each register is zero. 
@@
 
-We would like to remark that the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion in the sense that the accepting condition does not distinguish final states.
+We would like to remark that the aforementioned definition of CEFA is slightly different from that in \cite{atva2020}, where CEFA did not include accepting conditions.
+Moreover, the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion in the sense that the accepting condition does not distinguish final states.
 This technical choice is made so that the determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.
@@
 %Finally, we define the product of two CEFA.
-
-For convenience, for a CEFA $\aut$, we use $R_\aut$ to denote the set of registers of $\aut$.
 
@@
 \item $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $I' = \{q'_0\}$, 
-\item $\delta'$ is the union of $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, and $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, where the last two components of the vectors denote the updates of $r'_1$ and $r'_2$,
+\item $\delta'$ is the union of $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, and $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, where $\myvec{0}$ in $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector of updates on $R_2$ and $1,0$, the last two components of the vector, denote the updates on $r'_1$ and $r'_2$, similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.
 
@@
 
-The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, \vec{v_2}) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
 From the construction,

### 2023-05-12 2023-1-19/sections/overview.tex
intro
section 5 and 6

@@
 %Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
-Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting in a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
+Then we construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, and add the updates of registers (e.g.
+$r_1++$ for incrementing $r_1$) to transitions, resulting in a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
 %Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.
@@
 Note that we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
-Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators.
+Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no counting operators (Kleene plus is not seen as a counting operator here).
 Finally, we construct the third CEFA $\aut_3$ (see Figure~\ref{fig:overview}(c)), where a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$.
@@
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
-Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experimental results in Section~\ref{sec:implementation} show us that they do reduce the sizes of NFA constructed from the regular expressions in practice.
+Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experiment results show us that they do reduce the sizes of NFA constructed from the regular expressions in practice.
+(See Table~\ref{tab:results_heuristics}, where adding the size-reduction techniques reduces the running time for 46.4\%.)
 %thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
@@
 For instance, if we remove $|x| > 120$ from the string constraint~(\ref{eqn-running}), then the resulting constraint is satisfiable.
-Setting the bound $B$ to $3$ is sufficient to find a solution, which is witnessed by the following accepting run of $\cC$: $q^{\prime\prime}_0 \xrightarrow{(1,0,0,1)} q^{\prime\prime}_0 \xrightarrow{(0,1,0,1)} q^{\prime\prime}_1 \xrightarrow{(0,0,0,1)} q^{\prime\prime}_2$.
+Setting the bound $B$ to $3$ is sufficient to find a solution for the string constraint in~(\ref{eqn-running}), which is witnessed by the following accepting run of $\cC$: $q^{\prime\prime}_0 \xrightarrow{(1,0,0,1)} q^{\prime\prime}_0 \xrightarrow{(0,1,0,1)} q^{\prime\prime}_1 \xrightarrow{(0,0,0,1)} q^{\prime\prime}_2$.
 Note that the accepting run produces $(1,1,0,3)$, a vector of register values,  which satisfies $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$.
-(See Section~\ref{subsec:cefadec} for more details of the heuristic.)
+(See Section~\ref{subsec:cefadec} for more details.)
+
+We implement all the aforementioned techniques on top of OSTRICH, resulting into a solver $\ostrichrecl$.
+It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art strings solvers cannot solve it within 300 seconds.
 

### 2023-05-12 2023-1-19/sections/preliminaries.tex
section 5 and 6

@@
 Moreover, for $a \in \Sigma$, let $|u|_a$ denote the number of occurrences of $a$ in $u$. 
-Assume $u=a_0\cdots a_{n-1}$ is nonempty and $i<j \in [0,n-1]$. %Then a \emph{position} of $u$ is a number $i \in [|u|]$ (Note that the first position is $1$, instead of  0). In addition, 
+Assume that $u=a_1\cdots a_{n}$ is nonempty and $i<j \in [n]$. %Then a \emph{position} of $u$ is a number $i \in [|u|]$ (Note that the first position is $1$, instead of  0). In addition, 
 We let $u[i]$ denote $a_i$ and $u[i,j]$ for the substring %of $u$ starting from $i$ and ending with $j$ (i.e., 
@@
 \emph{Linear integer arithmetic and Parikh images.}
-We will also use standard quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulae, which are typically ranged over by $\phi, \varphi$, etc. 
+We will also use standard quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulas, which are typically ranged over by $\phi, \varphi$, etc. 
 For a set $\mathfrak{X}$ of variables, we use $\Phi(\mathfrak{X})$ to denote the set of quantifier-free LIA formulas whose free variables are from $\mathfrak{X}$. 

### 2023-05-12 2023-1-19/sections/recl.tex
section 5 and 6

@@
 The syntax of RECL is defined by the rules in Figure~\ref{fig:syntax}, where $x$ is a string variable, $\anivar$ is an integer variable, $a$ is a character from an alphabet $\Sigma$, and $m, n$ are integer constants.
-A RECL formula $\varphi$ is a conjunction of atomic formulas of the form $x \in \regex$, $x \not \in \regex$, or $t_1\ \op\ t_2$, where $\regex$ is a regular expression,  
+A RECL formula $\varphi$ is a conjunction of atomic formulas of the form $x \in \regex$ or $t_1\ \op\ t_2$, where $\regex$ is a regular expression,  
 $t_1$ and $t_2$ are integer terms, and $\op \in \{=, \neq, \le, \ge, <, >\}$.
-Atomic formulas of the form $x \in \regex$ or $x \not \in \regex$ are called \emph{regular membership} constraints and atomic formulas of the form $t_1\ \op\ t_2$ are called \emph{length} constraints.
+Atomic formulas of the form $x \in \regex$ are called \emph{regular membership} constraints and atomic formulas of the form $t_1\ \op\ t_2$ are called \emph{length} constraints.
 %
 A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, union $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
-An integer term is built from constants $n$, variables $i$, and string lengths $|x|$, by operators $+$ and $-$.
+An integer term is built from constants $n$, variables $\anivar$, and string lengths $|x|$, by operators $+$ and $-$.
 % 
@@
 
-The definition of the semantics of RECL is standard. Nevertheless, for readibility, we include the definition of its semantics here.
+%The definition of the semantics of RECL is standard. Nevertheless, for readibility, we include the definition of its semantics here.
 
@@
 %
-Then the semantics of formulas are defined with respect to a mapping $\theta: \svars(\varphi) \rightarrow \Sigma^* \uplus \ivars(\varphi) \rightarrow \Int$. 
-The mapping $\theta$ can be naturally extended to the set of integer terms. For instance, $\theta(|x|) =|\theta(x)|$, $\theta(t_1 + t_2) = \theta(t_1) + \theta(t_2)$. 
+Then the semantics of  $\varphi$ is defined with respect to a mapping $\theta: \svars(\varphi) \rightarrow \Sigma^* \uplus \ivars(\varphi) \rightarrow \Int$ (where $\uplus$ denotes the disjoint union).
+Note that the mapping $\theta$ can be naturally extended to the set of integer terms. For instance, $\theta(|x|) =|\theta(x)|$, $\theta(t_1 + t_2) = \theta(t_1) + \theta(t_2)$. 
 A  mapping $\theta$ is said to satisfy $\varphi$, denoted by $\theta \models \varphi$, if one of the following holds: 

### 2023-05-13 2023-1-19/sections/algorithms.tex
section 6

@@
 We say that $e$ is \emph{register-representable} if all occurrences of counting operators in $e$ are register-representable.
-For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ are not.
+For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ are not, since $a^{\{2,6\}}$ is in the scope of language difference and the counter operator $\{2, \infty\}$ respectively.
 
@@
 For $e' = e'_1 \concat e'_2$, $e' = e'_1 + e'_2$, or $e' = e'_1 \cap e'_2$, suppose that CEFA $\aut_{e'_1}$ and $\aut_{e'_2}$ have been constructed.
-Without loss of generality,  we assume that $R_{\aut_{e'_1}} \cap R_{\aut_{e'_2}} = \emptyset$.
+%Without loss of generality,  we assume that $R_{\aut_{e'_1}} \cap R_{\aut_{e'_2}} = \emptyset$. 
 Then we have $\aut_{e'} = \aut_{e'_1} \concat \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cup \aut_{e'_2}$, or $\aut_{e'} = \aut_{e'_1} \cap \aut_{e'_2}$. 
@@
 
-\begin{example}
-an example here
-\end{example}
+%\begin{example}
+%an example here
+%\end{example}
 
@@
 For instance, $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa+aaaa) \concat b^*)^{\{2, \infty\}}$.
+The unfoldings of the inner counting operators of non-register-representable regexes incur an exponential blow-up in the worst case.
+Nevertheless, those regexes occupy only 5\% of the 40,628 regexes that are collected from the practice (see Section~\ref{sec:bench}).
+Moreover, the unfoldings are partial in the sense that the outmost counting operators are not unfolded.
+It turns out that our approach can solve almost all of them, except 106.
 %$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
@@
 In the sequel, we present a procedure to solve the $\cefadec$ problem: Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+%
+The procedure comprises four steps.
 
-The procedure comprises four steps. 
-%
-\paragraph*{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
+\medskip
+\noindent
+\emph{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
 
@@
 Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA and $\costset_\aut = \{\myvec{v} \mid \exists q, a, q'.\ (q, a, q', \myvec{v}) \in \delta\}$. 
-Moreover, let $\aut' = (Q, \costset_\aut, \delta', I, F)$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by dropping the accepting condition and ignoring the characters, that is, $\delta'$, the transition relation of $\aut'$, comprises the tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for some $a \in \Sigma$.
+Moreover, let $\cU_\aut = (Q, \costset_\aut, \delta', I, F)$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by dropping the accepting condition and ignoring the characters, that is, $\delta'$ comprises the tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for some $a \in \Sigma$.
 %Then $\cefaout(\aut) = \parikh(\NFA')$.
@@
 %
-$$\cefaout(\aut) = \left\{\sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \  \big{|}\ \eta \in \parikh(\NFA') \mbox{ and }  \alpha\left[ \sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \big{/} R \right] \mbox{ is true}\right\}.$$
+$$\cefaout(\aut) = \left\{\sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \  \big{|}\ \eta \in \parikh(\cU_\aut) \mbox{ and }  \alpha\left[ \sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \big{/} R \right] \mbox{ is true}\right\}.$$
 %
@@
 \item 
-there are $\eta_1 \in \parikh(\cB'_1), \cdots, \eta_n \in \parikh(\cB'_n)$ such that 
+there are $\eta_1 \in \parikh(\cU_{\cB_1}), \cdots, \eta_n \in \parikh(\cU_{\cB_n})$ such that 
 %
@@
 Therefore, to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
-$\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cB'_1}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cB'_n}(\fZ_{\costset_{\cB_n}})$ to represent the Parikh images of $\cB'_1$, $\cdots$, $\cB'_n$ respectively, where $\fZ_{\costset_{\cB_i}} = \{\anivarz_{i,\myvec{v}} \mid \myvec{v} \in \costset_{\cB_i}\}$ for $i \in [n]$, and solve the satisfiability of the following existential LIA formula
+$\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ to represent the Parikh images of $\cU_{\cB_1}$, $\cdots$, $\cU_{\cB_n}$ respectively, where $\fZ_{\costset_{\cB_i}} = \{\anivarz_{i,\myvec{v}} \mid \myvec{v} \in \costset_{\cB_i}\}$ for $i \in [n]$, and solve the satisfiability of the following existential LIA formula
 %
@@
 %\scriptsize
-\bigwedge \limits_{i \in [n]} \left(\psi_{\cB'_i}(\fZ_{\costset_{\cB_i}}) \wedge \alpha_i\left[\sum\limits_{\myvec{v} \in \costset_{\cB_i}} \anivarz_{i, \myvec{v}} \myvec{v} \big{/}R_{\cB_i}  \right] \right)\  \wedge \\
+\bigwedge \limits_{i \in [n]} \left(\psi_{\cU_{\cB_i}}(\fZ_{\costset_{\cB_i}}) \wedge \alpha_i\left[\sum\limits_{\myvec{v} \in \costset_{\cB_i}} \anivarz_{i, \myvec{v}} \myvec{v} \big{/}R_{\cB_i}  \right] \right)\  \wedge \\
 \ \ \varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{1, \myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{n, \myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
@@
 %\end{equation}
-Intuitively, the integer variables $\anivarz_{i, \myvec{v}}$ represent the number of occurrences of $\myvec{v}$ in the strings accepted by $\cB'_i$.
+Intuitively, the integer variables $\anivarz_{i, \myvec{v}}$ represent the number of occurrences of $\myvec{v}$ in the strings accepted by $\cU_{\cB_i}$.
 %where $\anivarz_{\myvec{v}}$'s are integer variables to represent the number of occurrences of $\myvec{v}$.
 
-Because the sizes of the LIA formulas $\psi_{\cB'_1}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cB'_n}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cB'_1, \cdots, \cB'_n$, and it is expensive (NP-complete) to solve the satisfiability of existential LIA formulas, it is vital to reduce the sizes of these NFA.
+Because the sizes of the LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$, and it is expensive (NP-complete) to solve the satisfiability of existential LIA formulas, it is vital to reduce the sizes of these NFA.
 
-Furthermore, we have the following observation: For each $i \in [n]$ and $\eta \in \parikh(\cB'_i)$, we have 
+Furthermore, we have the following observation: For each $i \in [n]$ and $\eta \in \parikh(\cU_{\cB_i})$, we have 
 $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}.$
-In other words, the $\myvec{0}$-labeled transitions in $\cB'_i$ do not contribute to the sum $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
+In other words, the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the sum $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
 
-Therefore, we can reduce the sizes of $\cB'_1, \cdots, \cB'_n$ by Step II in the sequel.
+Therefore, we can reduce the sizes of $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$ by Step 2 in the sequel.
 
-\paragraph*{Step 2.} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cB'_i$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cB'_i$, determinize the resulting NFA, and minimize it.
+\paragraph*{Step 2.} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cU_{\cB_i}$, determinize and minimize the resulting NFA.
 \qed
 
-For $i \in [n]$, let  $\cC_i$ denote the DFA obtained from $\cB'_i$ by executing Step 2 and $\costset_{\cC_i} := \costset_{\cB_i} \setminus \{\myvec{0}\}$.
-From the construction, we know that $\parikh(\cC_i) = \prj_{\costset_{\cC_i}}(\parikh(\cB'_i))$ for each $i \in [n]$.
-Therefore, we compute LIA formulas from $\cC_i$'s, instead of $\cB'_i$'s, to represent the Parikh images.
+For $i \in [n]$, let  $\cC_i$ denote the DFA obtained from $\cU_{\cB_i}$ by executing Step 2 and $\costset_{\cC_i} := \costset_{\cB_i} \setminus \{\myvec{0}\}$.
+From the construction, we know that $\parikh(\cC_i) = \prj_{\costset_{\cC_i}}(\parikh(\cU_{\cB_i}))$ for each $i \in [n]$.
+Therefore, we compute LIA formulas from $\cC_i$'s, instead of $\cU_{\cB_i}$'s, to represent the Parikh images.
 
@@
 
-Finally, although we propose techniques to reduce the sizes of $\cB'_i$'s, it is still relatively expensive to compute LIA formulas from $\cC_i$'s and solve their satisfiability, especially for those problem instances with positive answers, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
+Finally, although we propose techniques to reduce the sizes of $\cU_{\cB_i}$'s, it is still relatively expensive to compute LIA formulas from $\cC_i$'s and solve their satisfiability, especially for those satisfiable problem instances, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
 $\varphi$.
-Therefore, in the sequel, we propose a heuristic to search for solutions for those positive problem instances by utilizing under approximations, to be executed before Step 3.
+Therefore, in the sequel, we propose a heuristic to search for solutions by utilizing under approximations, to be executed before Step 3.
 Intuitively, we search for solutions by bounding the lengths of the strings that are accepted by $\cC_i$'s.
@@
 
-\paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let $\confset_{\cC_i}:=\emptyset$, $\confset'_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$, and $\psi_{\cC_i}:= \lfalse$.
-Then iterate the following procedure, until $len = B+1$.
+\paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let 
+%$\confset_{\cC_i}:=\emptyset$, 
+$\confset_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$ 
+and $\psi_{\cC_i}:= \lfalse$.  Then iterate the following procedure, until $len = B+1$.
 \begin{enumerate}
@@
 \begin{enumerate}
-\item Let $\confset_{\cC_i}:= \confset_{\cC_i} \cup \confset'_{\cC_i}$, $temp:=\confset'_{\cC_i}$, $\confset'_{\cC_i}:=\emptyset$.
+\item Let 
+%$\confset_{\cC_i}:= \confset_{\cC_i} \cup \confset'_{\cC_i}$, 
+$old_i:=\confset_{\cC_i}$, $\confset_{\cC_i}:=\emptyset$.
 %
-\item For each $(q, \myvec{v}) \in temp$,
+\item For each $(q, \myvec{v}) \in old_i$,
 \begin{enumerate}
@@
 %
-\item for each $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset'_{\cC_i}:=\confset'_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
+\item for each $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset_{\cC_i}:=\confset_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
 \end{enumerate}
@@
 %
-\item Let $len: = len+1$.
+\item Let $len: = len+1$. \qed
 \end{enumerate}
-Intuitively, for each $i \in [n]$, $\confset'_{\cC_i}$ stores the set of ``configurations'' of $\cC_i$ that were newly discovered, and $\confset_{\cC_i}$ stores those that have been discovered before.
+Intuitively, for each $i \in [n]$, $\psi_{\cC_i}$ is a global variable whose value is never reset and it stores the set of ``final'' valuations of registers of $\cC_i$ (that is, the valuations obtained when reaching final states), and $\confset_{\cC_i}$ stores the set of newly discovered (not necessarily final) ``configurations'' of $\cC_i$.
+%, and $\confset_{\cC_i}$ stores those that have been discovered before. 
+Note that the solution searching algorithm in Step 2.5 is incremental in the sense that when the value of $len$ is incremented, the searching continues from $\confset_{\cC_i}$'s, not from scratch.
+%, whose values are not reset.
 %Furthermore, for each $i \in [n]$, we can remove the redundancy of characters/vectors in $\cC_i$.

### 2023-05-13 2023-1-19/sections/conclusion.tex
space adjustment
experiments

@@
 %TODO
-This work proposes an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length.
+This work proposes an efficient automata-theoretical approach for solving RECL constraints, that is, string constraints with regex-counting and string-length.
 The approach is based on the idea of encoding counting operators in regular expressions by registers symbolically, instead of unfolding them explicitly.
 Moreover, this paper proposes an automata-size reduction technique and an under-approximation based solution searching technique to improve the performance.
-Finally, we use two benchmark suites comprising almost 50,000 instances in total to evaluate the performance of our approach.
-The experimental results show that our approach can solve more instances than the other solvers, in almost the same speed as the fasted solver.
+Finally, we use two benchmark suites comprising 48,834 instances in total to evaluate the performance of our approach.
+The experimental results show that our approach can solve more instances than the state-of-the-art best solvers on RECL constraints, with a comparable performance.
 For the future work, we plan to investigate symbolic approaches to dealing with nested counting operators.

### 2023-05-13 2023-1-19/sections/implementation.tex
space ajustment
section 6
experiments

@@
 
-We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting in a version of OSTRICH called OSTRICH$^{\rm RECL}$.
-Then we do experiments on two benchmark suites, to evaluate the performance of OSTRICH$^{\rm RECL}$.
+We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
+Then we do experiments on two benchmark suites, to evaluate the performance of $\ostrichrecl$.
 In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
@@
 
-\subsection{Benchmark suites}
+\vspace{-2mm}
+\subsection{Benchmark suites}\label{sec:bench}
 
-Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoL. In total, there are 48,834 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
+Our experiments utilize two benchmark suites, namely, RegCoL and AutomatArk. In total, there are 48,834 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
+
+\medskip
+\noindent
+\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite.
+These constraints are generated by extracting regular expressions with counting operators from the open source regex library \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form
+$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$   
+where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$.
+%We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
+Moreover, among these 40,628 RECL constraints, only 5\% of them include non-register-representable regexes.
 
@@
 %Only 8,751 ones that contain counting operators out of 19,979 instances.
-
-\medskip
-\noindent
-\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite.
-These constraints are generated by extracting regular expressions with counting operators from \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form
-$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$   
-where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$.
-We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
 
@@
 
+\vspace{-3mm}
 \subsection{Experiment results}
 
-We evaluated the performance of OSTRICH$^{\rm RECL}$ against the state-of-the-art string constraint solvers, including CVC5 
+We evaluate the performance of $\ostrichrecl$ against the state-of-the-art string constraint solvers, including CVC5 
 %(version 1.0.5) 
@@
 %(github commit 8297d8d) 
-\cite{atva2020}.
+\cite{atva2020}, on RegCoL and AutomatArk.
 All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory.
@@
 
-The experiments are designed to answer the following two research questions. 
-\begin{description}
-\item[Q1] Does OSTRICH$^{\rm RECL}$ solve RECL constraints more efficiently than the state-of-the-art string constraint solvers ?
+%The experiments are designed to answer the following two research questions. 
+%\begin{description}
+%\item[Q1] Does OSTRICH$^{\rm RECL}$ solve RECL constraints more efficiently than the state-of-the-art string constraint solvers ?
+%
+%\item[Q2] Do the size-reduction and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
+%\end{description}
 
-\item[Q2] Do the size-reduction and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
-\end{description}
+\begin{table}[ht]
+\vspace{-2mm}
+\begin{center}
+  \import{tables}{table_regcol.tex}
+\end{center}
+  \caption{Experiment results on RegCol, with timeout = 60 seconds}
+  \label{tab:results_regcol}
+\vspace{-5mm}
+\end{table}
 
-Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL.
-The experimental results can be found in Table~\ref{tab:results_all}.
-From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solvers almost all 48,834 instances, except 145 of them, that is, it solves 48,698 instances correctly, which is 3,994/2,272/24,577/12,832/1,091/7,092 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively.
+The experiment results on the RegCol benchmark suite are put in Table~\ref{tab:results_regcol}. 
+From Table~\ref{tab:results_regcol}, we can see that $\ostrichrecl$ solvers almost all 40,628 instances, except 106 of them, that is, it solves 40,522 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092
+3,893/2,081/20,483/10,200/1,082/5,505 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
 %    
-Note that Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth.
+Note that the solvers  Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth\footnote{Although it seems a bit strange to use one solver as the ground truth, this is the practice for string constraint solving, since CVC5 is the most stable string solver at present.}.
 If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance.
@@
 %
-Moreover, OSTRICH$^{\rm RECL}$ is the second fastest solver.
-More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.
+Moreover, $\ostrichrecl$ is the second fastest solver.
+More specifically, $\ostrichrecl$ spends 3.02 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.56 seconds per instance.
 Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
+
+\begin{table}[ht]
+\vspace{-2mm}
+\begin{center}
+  \import{tables}{table_automatark.tex}
+\end{center}
+  \caption{Experiment results on AutomatArk, with timeout = 60 seconds}
+  \label{tab:results_automatark}
+\vspace{-5mm}
+\end{table}
+
+The experiment results on the AutomatArk benchmark suite are put in Table~\ref{tab:results_automatark}. 
+From Table~\ref{tab:results_automatark}, we can see that $\ostrichrecl$ solvers almost all 8,215 instances, except 39 of them, that is, it solves 8,176 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092
+101/191/4,094/2,632/9/1,587
+more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
+%    
+Still the soundness errors are reported by taking the results of CVC5 as the ground truth.
+%Note that Z3-Trau has soundness errors, where the result of CVC5 is taken as the ground truth.
+If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance.
+%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
+% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
+%
+Moreover, $\ostrichrecl$ spends 2.49 seconds per instance on average. 
+%while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.  
+%Note that Z3-Trau reports ``unknown'' on 2,552 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
+
+In summary, from the results in Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark}, $\ostrichrecl$ solves 48,698 out of 48,834 instances, which is 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
+Moreover, the performance (speed) of $\ostrichrecl$ is comparable to that of Z3str3RE.
+
+%Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL.
 
@@
 
-\begin{table}[t]
-\vspace{-1mm}
-\begin{center}
-  \import{tables}{table_all.tex}
-\end{center}
-  \caption{Experiment results for Q1, where the timeout period is 60 seconds}
-  \label{tab:results_all}
-\vspace{-5mm}
-\end{table}
-
+%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
+\hide{
 \begin{table}[ht]
@@
   \label{tab:results_heuristics}
-\vspace{-5mm}
+\vspace{-6mm}
 \end{table}
@@
 Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ help to solve 19 more sat instances, while reduces the number of solved unsat instances by 3, since under approximation techniques do not help to solve unsat instances.
+}
+%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
 %Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.

### 2023-05-13 2023-1-19/sections/introduction.tex
section 6
experiments

@@
 According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while the other forms of counting occur in more than 20\% of them.
-Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints that contain at least regular expressions with counting and string-length function.
+Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints that contain at least regular expressions with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function.
 
@@
 %
-The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while the state-of-the-art best solver Z3str3RE on RECL constraints solves only 47,607 instances (where the timeout period is set as 60 seconds).
-Moreover, while $\ostrichrecl$ solves 1,091 more instances than Z3str3RE, its performance is comparable to Z3str3RE (2.93 versus 1.71 seconds per instance).
-In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively, with an average time 5.67, 3.49, 5.41, and 8.54 seconds per instance.
-(See Table~\ref{tab:results_all} for more details.)
+The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while Z3str3RE, the state-of-the-art best solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
+Moreover, the speed of $\ostrichrecl$ is comparable to that of Z3str3RE.
+In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively.
+(See Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark} for more details.)
 
@@
 The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time.
-(See Table~\ref{tab:results_all}, where OSTRICH denotes the solver in \cite{atva2020}.)
+(See Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark} for more details, where OSTRICH denotes the solver in \cite{atva2020}.)
 

### 2023-05-13 2023-1-19/sections/overview.tex
experiments

@@
 Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experiment results show us that they do reduce the sizes of NFA constructed from the regular expressions in practice.
-(See Table~\ref{tab:results_heuristics}, where adding the size-reduction techniques reduces the running time for 46.4\%.)
+%(See Table~\ref{tab:results_heuristics}, where adding the size-reduction techniques reduces the running time for 46.4\%.) 
 %thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
@@
 We implement all the aforementioned techniques on top of OSTRICH, resulting into a solver $\ostrichrecl$.
-It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art strings solvers cannot solve it within 300 seconds.
+It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art string solvers are incapable of solving it within 300 seconds.
 

### 2023-05-13 2023-1-19/sections/implementation.tex
references

@@
 \begin{table}[ht]
-\vspace{-2mm}
+\vspace{-3mm}
 \begin{center}
@@
   \label{tab:results_regcol}
-\vspace{-5mm}
+\vspace{-6mm}
 \end{table}
@@
 \begin{table}[ht]
-\vspace{-2mm}
+%\vspace{-1mm}
 \begin{center}
@@
   \label{tab:results_automatark}
-\vspace{-5mm}
+\vspace{-6mm}
 \end{table}
@@
 
-In summary, from the results in Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark}, $\ostrichrecl$ solves 48,698 out of 48,834 instances, which is 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
-Moreover, the performance (speed) of $\ostrichrecl$ is comparable to that of Z3str3RE.
+In summary, $\ostrichrecl$ solves 48,698 out of 48,834 instances, which is 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
+Moreover, the speed of $\ostrichrecl$ is the second fastest and comparable to that of Z3str3RE.
+(See Table~\ref{tab:results_summary}.)
+
+\begin{table}[ht]
+\vspace{-3mm}
+\begin{center}
+  \import{tables}{table_summary.tex}
+\end{center}
+  \caption{Experiment results: A Summary}
+  \label{tab:results_summary}
+\vspace{-6mm}
+\end{table}
 

### 2023-05-13 2023-1-19/sections/introduction.tex
references

@@
 In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively.
-(See Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark} for more details.)
+(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details.)
 
@@
 The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time.
-(See Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark} for more details, where OSTRICH denotes the solver in \cite{atva2020}.)
+(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details, where OSTRICH denotes the solver in \cite{atva2020}.)
 

### 2023-05-13 2023-1-19/tables/table_summary.tex
add missing files

%\documentclass[11pt]{standalone}
%\usepackage{color}
%\usepackage{tikz}
%\usepackage{pgfplots}
%\usepgfplotslibrary{fillbetween}
%\pgfplotsset{compat=1.16}
%\begin{document}
\resizebox{.95\textwidth}{!}{\begin{tabular}{|c |c |c |c |c |c |c |c |}
    \hline
         solver                                                                  & CVC5       & Z3seq      & Z3-Trau & Z3str3     & Z3str3RE   & OSTRICH    & OSTRICH$^{\rm RECL}$ \\
    \hline\hline
    solved correctly                                                         & 44,704     & 46,426     & 24,121  & 35,866     & 47,607     & 41,606      & {\bf 48,698}         \\
    \hline
    \begin{tabular}{c}average time \\ per instance \\ (seconds)\end{tabular} & 5.67       & 3.49       & 5.41    & 8.54       & {\bf 1.71} & 3.9        & 2.93                 \\
    \hline
  \end{tabular}}

%\end{document}

### 2023-05-15 2023-1-19/sections/cefa.tex
typo
typo removement

@@
 \begin{definition}[Cost-Enriched Finite Automaton]
-  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F)$ where
+  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F, \alpha)$ where
   \begin{itemize}
@@
 \item $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $I' = \{q'_0\}$, 
-\item $\delta'$ is the union of $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, and $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, where $\myvec{0}$ in $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector of updates on $R_2$ and $1,0$, the last two components of the vector, denote the updates on $r'_1$ and $r'_2$, similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.
+%
+\item $\delta'$ is the union of $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, and $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively.
+Similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.
 
@@
 \begin{itemize}
-\item if $I_1 \cap F_1 \neq \emptyset$ or $I_2 \cap F_2 \neq \emptyset$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
+\item if either $I_1 \cap F_1 \neq \emptyset$ and $\alpha_1[\myvec{0}/R_1]$ is true, or $I_2 \cap F_2 \neq \emptyset$ and $\alpha_2[\myvec{0}/R_2]$ is true, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
+%
+%\item otherwise, if $I_2 \cap F_2 \neq \emptyset$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0 \wedge \alpha_2) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
 %
@@
 From the construction, we know that 
-$$\Lang(\aut_1 \cup \aut_2) = \{(w; \myvec{v}) \mid \myvec{v} \in \Int^{R'}, (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ or } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
+$$
+\Lang(\aut_1 \cup \aut_2) = 
+\left\{(w; \myvec{v}) \left \vert 
+\begin{array}{l}
+%\myvec{v} \in \Int^{R'}, 
+(w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } \prj_{R_2}(\myvec{v}) = \myvec{0}, \mbox{ or } \\
+(w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2) \mbox{ and } \prj_{R_1}(\myvec{v}) = \myvec{0}
+\end{array}
+\right.
+\right\}.
+$$
 

### 2023-05-15 2023-1-19/sections/overview.tex
typo removement

@@
 $\varphi \equiv r_4 > 120$ is reduced to the problem of deciding whether there exists $w' \in \costset^*$ such that it is accepted by $\cB$ and its Parikh image (i.e.
-numbers of occurrences of characters), say $\eta_{w'}: \costset \rightarrow \Nat$, satisfies that $1 \le v'_1 \le 60\wedge 1 \le v'_2 \le 60 \wedge 0 \le v'_3 \le 60$ and $v'_4 > 120$, where $\myvec{v'} = \sum \limits_{\myvec{v} \in \costset} \eta_{w'}(\myvec{v}) \myvec{v}$.
+numbers of occurrences of characters), say $\eta_{w'}: \costset \rightarrow \Nat$, satisfies that $1 \le v'_1 \le 60\wedge 1 \le v'_2 \le 60 \wedge 0 \le v'_3 \le 60$ and $v'_4 > 120$, where $\myvec{v'} = (v'_1, v'_2, v'_3, v'_4) =  \sum \limits_{\myvec{v} \in \costset} \eta_{w'}(\myvec{v}) \myvec{v}$.
 Intuitively, $\myvec{v'}$ here is a weighted sum of vectors $\myvec{v} \in \costset$, where the weight for $\myvec{v}$ is the number of occurrences of $\myvec{v}$ in $w'$.
@@
 %where for each $k \in [m]$, $v_k = (v_{k,1}, v_{k,2}, v_{k, 3}, v_{k, 4})$ is the vector of updates on the registers $r_0, r_1, r_2, r_3$ in the transition $\tau_k$, and $\alpha(r_0, r_1, r_2, r_3)$ is the accepting condition in $\aut_1 \times \aut_2$.
-Since the satisfiability of LIA formulas can be solved by the off-the-shelf SMT solvers for LIA, the satisfiability of the string constraint in~(\ref{eqn-running}) can thus be solved.
+Finally, the satisfiability of the LIA formula in~(\ref{eqn-LIA}) can be solved by the off-the-shelf SMT solvers for LIA.
+%Since the satisfiability of LIA formulas can be solved by the off-the-shelf SMT solvers for LIA, the satisfiability of the string constraint in~(\ref{eqn-running}) can thus be solved.
 
-Nevertheless, it turns out that the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting  in  the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
+Nevertheless, the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting  in  the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
 \cite{Haase18}).
@@
 
-We determinize $\cB$, apply the minimization algorithm to the resulting deterministic finite automaton (DFA), and obtain a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b). 
+Specifically, to reduce the sizes of the NFA, we determinize $\cB$, apply the minimization algorithm to the resulting deterministic finite automaton (DFA), and obtain a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 

### 2023-05-16 2023-1-19/sections/algorithms.tex
references
more revises

@@
 
+\vspace{-3mm}
 \begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula\footnote{The decision problem was called satisfiability of an LIA formula w.r.t. CEFA in \cite{atva2020}.}, abbreviated as $\cefadec$]
@@
 
+\vspace{-4mm}
 \begin{proposition}[\cite{atva2020}]\label{prop-cefadec}
@@
 
-\vspace{-2mm}
+\vspace{-3mm}
 \subsection{From $\reclsat$ to $\cefadec$} \label{subsec:regex2cefa}
@@
 The unfoldings of the inner counting operators of non-register-representable regexes incur an exponential blow-up in the worst case.
-Nevertheless, those regexes occupy only 5\% of the 40,628 regexes that are collected from the practice (see Section~\ref{sec:bench}).
+Nevertheless, those regexes occupy only 5\% of the 48,834 regexes that are collected from the practice (see Section~\ref{sec:bench}).
 Moreover, the unfoldings are partial in the sense that the outmost counting operators are not unfolded.
-It turns out that our approach can solve almost all of them, except 106.
+It turns out that our approach can solve almost all of them, except 145.
 %$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
@@
 
+\vspace{-2mm}
 \begin{observation}\label{obs-cefa-output}
@@
 %
+\vspace{-2mm}
 \begin{observation}\label{obs-cefa-nfa}

### 2023-07-13 2023-6-26开题报告/Tex/Mainmatter.tex
博士开题报告

\newcommand{\join}{\mathsf{join}}
\newcommand{\len}{\mathsf{len}}
\newcommand{\prefix}{\mathsf{prefix}}
\newcommand{\suffix}{\mathsf{suffix}}
\newcommand{\substr}{\mathsf{substr}}
\newcommand{\concat}{\mathsf{concat}}
\newcommand{\test}{\mathsf{test}}
\newcommand{\match}{\mathsf{match}}
\newcommand{\replace}{\mathsf{replace}}
\newcommand{\replaceall}{\mathsf{replaceAll}}
\newcommand{\transducer}{\mathsf{transducer}}
\newcommand{\reverse}{\mathsf{reverse}}
\newcommand{\htmlescape}{\mathsf{htmlEscape}}
\newcommand{\mysplit}{\mathsf{split}}
\newcommand{\myjoin}{\mathsf{join}}
\newcommand{\indexof}{\mathsf{indexof}}
\newcommand{\contain}{\mathsf{contain}}
%---------------------------------------------------------------------------%
%->> Main content
%---------------------------------------------------------------------------%
\section{选题的背景及意义}

\subsection{选题背景}
硬件和软件的飞速发展让通用计算机的能力得到极大提高，使得字符串约束的求解从不可能变为可能。同时，随着可满足性模理论（Satisfiability Modulo Theories）和符号执行技术的发展，字符串约束求解技术越来越被学术界和工业界重视，广泛应用到JavaScript符号执行引擎上。然而，现存的字符串求解器使用不完备的算法，不能很好的覆盖程序中的复杂字符串函数如$\mysplit$，不能处理数组类型，这极大地限制了字符串约束求解的能力及其在JavaScript符号执行中的应用。

目前有两种主流的字符串约束求解技术：基于自动机的约束求解技术\cite{sloth}\cite{abc} \cite{mult_abc}\cite{trau_2017}\cite{trau_2018}\cite{trau+}\cite{ostrich}和基于推导规则的求解技术\cite{z3}\cite{z3str2}\cite{z3str3}\cite{z3str3re}\cite{cvc4_2014}\cite{cvc4_2017}\cite{cvc4_2019}\cite{cvc4_2020}。前者的主要思想是将字符串约束转化为有限自动机，然后使用有限自动机已有的算法求解字符串约束。该技术的优点是模型比较经典，有丰富且可靠的理论基础。缺点是自动机求交会导致状态空间爆炸，求解效率比较低；后者的主要思想是根据每种字符串函数的具体含义，制定不同的推导规则，在DPLL(T) 框架\cite{dpll_t}下不断推导，直到找到一组变量的赋值或者推导出无解。该技术的优点是求解速度较快。缺点是算法可能不终止，不能高效处理正则表达式。

上诉求解器在字符串约束求解技术上取得了不错的成果，但是未考虑数组类型和一些实际程序中会出现的操作如$\mysplit$函数、$\myjoin$函数，也未考虑正则表达式的贪婪性。部分求解器不能处理整数数据类型。

字符串约束求解在程序分析和软件漏洞检测上有着广泛的应用，但是在JavaScript符号执行的应用还不够成熟。JavaScript符号执行技术分为静态\cite{safe} \cite{safe_ext}\cite{safe_str}和动态\cite{jalangi}\cite{expose_2017}\cite{expose_2019}\cite{aratha}两种方式。静态符号执行只针对源代码作分析，其过程首先用静态分析方法中的控制流分析构造控制流图，之后通过选取控制流图中某条路径并针对此路径作符号执行和路径约束求解。静态符号执行选取的路径中很大一部分是实际不可行路径，会导致误报。另一方面，程序代码中的分支语句的存在决定了程序的路径数向队友程序的规模呈指数型增长，导致路径爆炸问题。

动态符号执行是一种动静态结合的程序分析技术，在具体执行的同时对所执行到的代码施行符号执行，具体执行的特性决定了每次动态符号执行获取的路径都是可行路径，因此避免了误报。但是目前的SMT求解器不能很好的支持非线性算术理论，尤其是字符串理论。若程序某条分支产生的约束超过了求解器的求解能力范围，该分支会被丢掉，产生漏报。

JavaScript符号执行工具已经广泛应用上述技术，取得了一定的成果。对于数组的处理还不够完善。没有充分利用现有的字符串约束求解
器。

\subsection{选题意义}
目前没有研究者对同时含整数和数组类型的字符串约束进行系统研究，忽视了这两种数据类型在程序中的重要性。但是实际程序中这些数据类型和函数的使用频率很高，因此研究这些数据类型和函数的求解技术对于提高字符串约束求解技术的实用性和适用性具有重要意义。

JavaScript目前被广泛运用到Node.js引擎和Web应用中，有大量的使用者和开发者。但是，由于之前的字符串约束求解器没有很高的效率，也不能很全面的支持实际程序中的字符串函数和数据类型，已有的符号执行工具并没有很好地集成字符串约束。因此研究字符串约束在JavaScript符号执行中的高效应用具有前瞻意义。

\section{国内外本学科领域的发展现状与趋势}
由于硬件算力的提升，字符串约束求解技术发展迅速，相关的研究工作也越来越多，并且已经有一些JavaScript符号执行上的研究工作。本节将对字符串约束求解技术和JavaScript符号执行技术的发展现状和趋势进行介绍。
\subsection{字符串约束求解技术}
字符串约束求解技术在近年来引起了学术界和工业界的广泛关注，相关的研究工作也越来越多。目前，主流的字符串约束求解技术主要有两种：基于自动机的字符串约束求解技术和基于推导规则的字符串约束求解技术。

\paragraph{基于自动机的字符串约束求解技术}的主要思想是将字符串约束转化为自动机，然后使用自动机的理论求解字符串约束。该技术的优点是模型比较经典，有丰富且可靠的理论基础。缺点是效率比较低。目前，该技术的主要研究工作有：

2015年，Aydin等人\cite{abc}提出了字符串约束求解器ABC。ABC构造一个接受所有可能解的自动机，将字符串约束求解问题转化为自动机判空问题，然后使用现有的自动机判空算法求解。给定字符串的长度上界，ABC可以对所有长度小于等于该上界的解计数，直观地，解的个数等于自动机的接受路径数。

2018年被Aydin等人\cite{mult_abc}在ABC的基础上开发了MT-ABC。MT-ABC增加了对线性整数算术（Linear Integer Arithmetic）的支持。MT-ABC用上近似处理了非正则约束，不是一个完备的算法。ABC和MT-ABC都不支持数组类型。

2017年，Abdulla等人\cite{trau_2017}\cite{trau_2018}开发了字符串约束求解器Trau. Trau使用了反例引导的抽象精化（Counter-Example Guided Abstraction Refinement）框架。该框架的基本思想是用可满足的上近似来指导上下文无关文法的下近似，反过来若下近似不可满足，又可以精化上近似。不断迭代这个过程直到下近似找到解或者上近似返回无解。这个过程可能不终止，所以Trau是不完备的。

2019年，Abdulla等人\cite{trau+}对字符串约束的形式进行了一些限制，称为弱链式字符串约束（weakly chaining string constraints），并证明了该形式的字符串约束是可判定的，即可以在有限时间内求解且是完备的。基于此开发出字符串约束求解器Trau+。Trau和Trau+都不支持数组类型。

2018年，HOLÍK等人\cite{sloth}提出了第一个能够求解字符串连接函数和$\transducer$函数的字符串约束求解器SLOTH。SLOTH用轻量级选择自动机（Succinct Alternating Finite-state Automata）建模字符串约束，然后用模型检验算法如IC3求解。SLOTH的空间复杂度是指数级别的。SLOTH既不支持数组类型，也不支持整数数据类型。

2018年，Chen等人\cite{repalceall_decidable}研究了带有$\replaceall$函数的字符串约束的可判定性问题。$\replaceall$函数是一种字符串替换函数，它的作用是将字符串中的每个模式串替换为替代串。比如$\replaceall(\text{‘the cat is a cat’, ‘cat’, ‘dog’})$表示将字符串‘the cat is a cat’中的所有模式串‘cat’替换为替代串‘dog’，它返回字符串‘the dog is a dog’。 Chen等人提出了包含$\replaceall$函数的直线子集（Straight-Line Fragment），该直线子集包含了正则约束、字符串连接函数和$\replaceall$函数，规定字符串变量之间不存在循环依赖关系。基于该直线子集，Chen等人分三类情况讨论了带有$\replaceall$函数的字符串约束求解问题的可判定性。第一种情况是模式串为变量，该情况下是不可判定的；第二种情况是模式串为正则表达式，该情况下是可判定的且判定算法的复杂度为EXPSPACE，在某些特殊情况下复杂度可以降到PSPACE-Complete；第三种情况是模式串是常量，同时引入$\len$函数，该情况下是不可判定的。

2019年，Chen等人基于上述理论研究，开发了字符串约束求解器OSTRICH\cite{ostrich}。OSTRICH支持正则约束、字符串连接函数、$\replaceall$函数，$\transducer$函数和$\reverse$函数。$\transducer$函数是一种字符串转换函数，它将输入字符串转换为另一个字符串。比如Web程序中常用的输入过滤函数$\htmlescape$就可以用字符串转换器来定义。$\reverse$函数是一种字符串反转函数，比如$\reverse(\text{‘abc’})$返回字符串‘cba’。OSTRICH是第一个可以同时处理$\replaceall$函数和$\transducer$函数的字符串约束求解器，但是不能处理整数数据类型和数组数据类型。

% 2020年，Chen等人\cite{ostrich_atva}开发了OSTRICH+。它是OSTRICH的扩展，支持整数数据类型。OSTRICH+的基本思想是用线性整数算数公式表示OSTRICH中的自动机判空问题，再和整数数据类型结合起来。OSTRICH+的算法是完备的，但是它所处理的字符串约束中，$\replaceall$函数的模式串只能为常量。

% 为了正确处理实际程序中的贪婪匹配和非贪婪匹配，以及处理$\replaceall$函数中的反向引用，Chen等人2022年\cite{ostrich_greedy}提出了优先级流式字符串转换器（prioritized streaming string transducers）。优先级流式字符串转换器是带有优先级的字符串转换器，能够对正则表达式的贪婪性进行建模。OSTRICH+不支持数组类型。

\paragraph{基于推导规则的字符串约束求解} 的主要思想是根据字符串函数的具体含义，制定不同的推导规则，在DPLL(T)框架\cite{dpll_t}下不断推导，直到找到解或者推导出无解。该技术的优点是求解速度快，缺点是不完备，算法可能不终止，且不能高效处理正则表达式。目前，该技术的主要研究工作有：

2013年，Zheng等人\cite{z3str}基于Z3的DPLL(T)框架，首次提出了Z3\cite{z3}家族的字符串求解器Z3Str。Z3Str把字符串约束中的谓词看作布尔变量，得到一组一阶布尔逻辑公式，该公式可以用SAT求解器快速找到一组解或者返回无解。若SAT求解器成功找到一组解，那么将这组解中赋值为真的谓词提取出来，得到一个新的字符串约束，然后用Z3Str中的字符串约束推导规则进行推导，得到一组新的谓词，将其转化为布尔变量加入到原来的布尔公式中，再用SAT求解器求解。如此循环，直到找到所有字符串变量的赋值或者推导出无解。若字符串约束中的只含有字符串等式，则Z3Str的算法是完备的。

2015年，Zheng等人\cite{z3str2}在Z3Str的基础上开发了Z3Str2，添加了字符串约束和线性整数算术公式之间的启发式推导规则，对搜索空间进行剪枝，提高求解效率；并添加对字符串等式中重叠变量的探测，能够解决一部分不终止的问题。所谓字符串重叠变量，是指字符串变量同时在等式左值和右值出现，比如$axb=xa$中的$x$就是重叠变量。重叠变量是大部分求解器的一个瓶颈，因为它会导致求解器不断地推导，求解过程不终止。

2017年，Berzish等人\cite{z3str3}将Z3str2扩展为Z3Str3。Z3Str3的求解效率更高，它在SAT求解器对布尔逻辑进行规约时，不仅考虑布尔变量的取值，也考虑对应谓词中具体的字符串函数含义，可以更好地剪枝搜索空间。

2022年，Berzish等人\cite{z3str3re}为了解决Z3Str3不能高效处理正则表达式的问题，开发了求解器Z3Str3RE。Z3Str3RE不同于Z3Str3的地方在于，它把正则表达式看作一个特殊的谓词，不使用推导规则而是使用有限自动机来处理正则表达式，并且加入了一些启发式算法如自动机启发式求交、对线性约束启发式上近似等，提高了求解效率。Z3Str3RE在字符串约束只含有字符串长度函数、正则约束和线性整数算术时，求解速度非常快。Z3Str/2/3/RE能处理整数数据类型，但不能处理数组数据类型。

2014年，Liang等人\cite{cvc4_2014}与Z3团队几乎同时开发另一个基于推导规则的字符串约束求解器CVC4。CVC4的求解算法和Z3Str几乎一样，它们之间只有工程实现和推导规则上的略微差别，但是CVC4的求解效率更高。

迫于Z3Str不断更新的压力，CVC4在2017年\cite{cvc4_2017}添加了对整数数据类型和线性算术公式的支持，2019年\cite{cvc4_2019}添加了算术推导、多重集和基于算术的字符串约束简化，并在2020年\cite{cvc4_2020}对正则表达式的推导规则进行了优化，大大提高了求解效率。CVC4不支持数组类型。

上述工具在带有整数数据类型的字符串约束上已经取得不错的研究结果，但是它们对\textbf{整数和数组类型}的支持还\textbf{不够完善}，同时\textbf{没有支持$\mysplit$函数和$\myjoin$函数}。
\subsection{JavaScript符号执行技术}
近年来，JavaScript语言由于其易用性和杰出的异步处理，被广泛运用到Web应用中，JavaScript语言的符号执行技术也得到了飞速发展。JavaScript语言的符号执行技术主要有两种，一种是静态符号执行技术，一种是动态符号执行技术。

\paragraph{静态符号执行技术} 主要针对源代码作分析，主要的相关研究工作有：

2012年，Lee等人\cite{safe}提出了一个可扩展的ECMAScript语言分析框架SAFE。SAFE是第一个同时考虑了ECMAScript官方文档和其开源代码实现的分析框架，在工程上有很好的可扩展性和文档定义，尤其是对它的中间语言表示有规范的文档。SAFE支持插件式的扩展方式，用户可以方便地添加新特性。SAFE将整数数据类型和数组数据类型都编码到了SMT公式中，但编码时未完备考虑字符串函数的语义。

2016年，Park等人\cite{safe_ext}针对jQuery库中的正则表达式、字符串前缀、中缀和后缀操作进行抽象解释，扩展了JavaScript分析工具SAFE。jQuery是一个常用的开源库，但是当时存在的分析器不能分析它。Park等人使用了字符串抽象域对正则表达式和相关字符串函数进行抽象和分析，解决了这个问题。实验结果表明，使用字符串抽象域的SAFE比不使用字符串抽象域的SAFE能够分析更多的程序，分析精度更高。

2017年，Amadini等人\cite{safe_str}等人在静态程序分析工具SAFE上进行扩展，得到了工具SAFE$_{str}$。SAFE$_{str}$的主要优点在于同时使用多个字符串抽象域并用求交的方式把抽象域结合起来，结合后的抽象域更为精确。实验结果也表明在结合多个抽象域后，效率和准确度都得到了提升。

\paragraph{动态符号执行技术} 是一种动静态结合的程序分析技术，在具体执行的同时对所执行到的代码施行符号执行，主要的相关研究工作有：

2013年，Sen等人\cite{jalangi}提出了JavaScript符号执行框架Jalangi，它能够对JavaScript程序进行动态分析，包括对程序执行轨迹的记录、修改和重放，以及对程序中的语句进行插装。Jalangi能够对程序中的大部分语句进行插装，包括对字符串函数的插装，这使得它能够对含有字符串函数的程序进行动态分析。Jalangi有两个主要特点，一是有选择性地对程序进行记录和重放，而不是对程序的每一条语句都进行，这样可以大大减少程序分析时间；二是支持阴影值（shadow values）和阴影执行（shadow execution），这使得它能够使用符号执行技术和动态污点传播技术，以处理大型程序。相比于PinPlay\cite{pinplay}和Valgrind\cite{valgrind}等工具，Jalangi的速度在记录上有26倍的提升，在重放和分析上有30倍的提升。Jalangi未对数组数据类型进行特殊处理，需要用户自定义。

2017年，Loring等人\cite{expose_2017}借助Jalangi框架，提出了Node.js引擎的动态符号执行工具ExpoSE。ExpoSE能够自动生成测试用例，并有较高到的路径覆盖率。它主要修复了Jalangi对捕获组（capture groups）、反向引用（backreferences）和JavaScript语言正则表达式贪婪匹配的错误处理，并在开源库Minimist中找到了一个之前未被发现的漏洞。

2019年，Loring等人\cite{expose_2019}在ExpoSE的基础上，对其进行了改进，使得它能够处理更多的JavaScript语言特性，能够可靠地对ECMAScript2015标准的test和exec函数进行符号执行。Loring等人使用正则约束来模拟捕获组的语义，并用反例引导的抽象解释精化方法来处理贪婪匹配，效率得到了提高。ExpoSE能够处理整数数据类型，未对数组类型进行特殊处理。

2019年，Amadini等人\cite{aratha}借助Jalangi框架，提出了JavaScript符号执行工具Aratha。通常来说，动态符号执行工具需要使用SMT求解器来求解程序中的约束，但SMT求解器的求解效率瓶颈使得动态符号执行工具的效率受限。Aratha使用约束规划的方法来处理这种情况，该方法会将被分析程序转化为更简单的约束，能够作为动态符号执行工具的互补品，提高工具的效率。Aratha能够处理整数数据类型和数组数据类型，它将数组理论用SMT公式编码，但编码时未考虑字符串函数的语义。

上述JavaScript符号执行工具已经能够初步处理程序中的字符串和整数数据类型，但是对于\textbf{数组}的处理还\textbf{不够完善}。没有充分利用现有的字符串约束求解器，只是用简单的字符串函数去规约实际程序中复杂的字符串函数如$\mysplit$函数和$\myjoin$函数，让字符串求解器损失了一部分信息。

\section{课题主要研究内容、预期目标}
\subsection{研究内容}
本课题的主要研究含整数和数组数据类型的字符串约束求解技术，并将其应用到JavaScript符号执行上。本课题将研究以下两个子课题：
\paragraph{含整数和数组数据类型的字符串约束求解技术}
是子课题JavaScript程序符号执行研究的基础。目前国内外的字符串约束求解器对于整数和数组类型的支持不够完善。同时没有在约束求解层面上考虑会引入数组类型的函数，如$\mysplit$函数和$\myjoin$函数，也没有考虑正则表达式中的捕获组。本课题研究一种更准确的、覆盖整数和数组类型的字符串约束求解技术，在语法上支持$\mysplit$函数、$\myjoin$函数和正则表达式捕获组。探索该约束的可判定性，提取出可判定的字符串约束子集，形成判定算法，开发相应的原型工具。更细致地，本子课题将研究以下三方面内容：
\begin{itemize}
    \item 对含有整数数据类型的字符串约束的研究。
    \item 对带有正则表达式捕获组的$\replaceall$函数的研究。
    \item 对含有数组数据类型的字符串约束研究。
\end{itemize}
（1）对含有整数数据类型的字符串约束的研究：

当字符串含有整数数据类型时，字符串约束会变得更为复杂，比如带有$\replaceall$函数的字符串约束在引入整数数据类型和$\len$函数后，会变得不可判定\cite{repalceall_decidable}。本课题将研究带有整数数据类型的字符串约束的可判定性，并提出一个可判定的子集。该子集中拟支持的函数有：$\replace$函数，$\replaceall$函数， $\transducer$函数， $\reverse$函数， $\concat$函数， $\contain$函数， $\prefix$函数， $\suffix$函数， $\len$函数，$\substr$函数和$\indexof$函数；拟支持的文法约束为正则文法约束；拟支持的数据类型为字符串类型和整数类型，并支持线性整数算术公式的求解。\newline
（2）对带有正则表达式捕获组的$\replaceall$函数的研究：

正则表达式是JavaScript程序中非常常用的语言特性，支持贪婪匹配和非贪婪匹配。贪婪匹配和非贪婪匹配的区别在于，贪婪匹配会尽可能多地匹配字符串，而非贪婪匹配会尽可能少地匹配字符串。在$\replaceall$函数中，贪婪匹配和非贪婪匹配的区别会导致不同的返回结果，这会影响字符串约束的求解结果。同时，正则表达式还支持捕获组，捕获组是正则表达式中用括号括起来的部分，JavaScript程序中的$\replaceall$函数可以在替换串中使用捕获组，这也会影响字符串约束的求解结果。本课题将研究带有正则表达式捕获组的$\replaceall$函数的求解方法，并考虑正则表达式中的贪婪性。探索其可判定性，并提出一个可判定的子集。该子集中拟支持的函数有：带有捕获组的$\replace$函数，带有捕获组的$\replaceall$函数， $\transducer$函数， $\reverse$函数， $\concat$函数， $\contain$函数， $\prefix$函数， $\suffix$函数， $\len$函数，$\substr$函数和$\indexof$函数；拟支持的文法约束为正则文法约束；拟支持的数据类型为字符串类型和整数类型，并支持线性整数算术公式的求解。该部分研究是第一部分研究的扩展，增加了捕获组和正则表达式贪婪性的支持。\newline
（3）对含有数组数据类型的字符串约束研究：

JavaScript程序中的数组类型是一个非常常用的数据类型，但是现有的字符串约束求解器对数组类型的支持不够完善。本课题将研究含有数组数据类型的字符串约束的可判定性，并在已有的字符串函数集基础上，引入$\mysplit$函数和$\myjoin$函数，提出一个可判定的子集。该子集中拟支持的函数有：带有捕获组的$\replace$函数，带有捕获组的$\replaceall$函数， $\transducer$函数， $\reverse$函数， $\concat$函数， $\contain$函数， $\prefix$函数， $\suffix$函数， $\len$函数，$\substr$函数，$\indexof$函数，$\mysplit$函数和$\myjoin$函数；拟支持的文法约束为正则文法约束；拟支持的数据类型为字符串类型、数组类型和整数数据类型，并支持线性整数算术公式的求解。该部分研究是第二部分研究的扩展，增加了对数组数据类型的支持，增加了数组数据类型相关的$\mysplit$函数和$\myjoin$函数。

\paragraph{JavaScript符号执行} 字符串约束求解在程序分析和软件漏洞检测上有着广泛的应用，但是在JavaScript符号执行的应用还不够成熟，现有的分析工具不能很好地对带有整数数据类型、数组数据类型和字符串数据类型的JavaScript程序进行分析，只能部分处理数组数据类型，并未对实际程序中的$\mysplit$函数，$\myjoin$函数和捕获组进行充分考虑，对JavaScript中正则表达式的贪婪性没有很好处理。JavaScript符号执行工具Aratha\cite{aratha}具有较好的可扩展性，已经支持$\concat$、$\indexof$等基本字符串函数的插装。本子课题将对Aratha进行扩展，将带有整数数据类型、数组数据类型和字符串数据类型的路径约束规约到字符串约束上，充分考虑$\mysplit$函数，$\myjoin$函数和捕获组，正确区分正则表达式的贪婪匹配和非贪婪匹配。将含整数和数组数据类型的字符串约束求解技术子课题中开发的字符串约束求解器集成到分析框架中，更准确地刻画整数数据类型、数组类型和字符串类型及相关函数的语义，提高分析效率和正确性。

\subsection{预期目标}
本课题的预期目标为：
\begin{itemize}
    \item 开发能够处理整数和数组数据类型的字符串约束求解器，使其能够支持带有捕获组的$\replace$函数，带有捕获组的$\replaceall$函数， $\transducer$函数， $\reverse$函数， $\concat$函数， $\contain$函数， $\prefix$函数， $\suffix$函数， $\len$函数，$\substr$函数，$\indexof$函数，$\mysplit$函数和$\myjoin$函数，支持正则文法约束，并支持线性整数算术公式的求解。对该约束求解器进行优化，使其和其他主流字符串约束求解器相比，具有更好的性能，能够应用到实际的程序分析工具中。
    \item 扩展已有的JavaScript符号执行框架，使其能够处理带有整数数据类型、数组数据类型和字符串数据类型的JavaScript程序。充分考虑$\mysplit$函数，$\myjoin$函数和捕获组，能够正确区分正则表达式的贪婪匹配和非贪婪匹配。扩展后的JavaScript符号执行引擎能够将带有整数数据类型、数组数据类型和字符串数据类型的程序路径规约到字符串约束上，并将该约束交给上述开发的字符串约束求解器求解。扩展后的JavaScript符号执行引擎需要和其他主流的JavaScript符号执行引擎相比，具有更好的性能或者更好的分析效果。
\end{itemize}

\section{拟采用的研究方法、技术路线、实验方案及其可行性分析}
本节讨论本课题拟采用的研究方法、技术路线、实验方案及其可行性分析。其中研究方法、技术路线、实验方案根据课题的研究内容而定。可行性分析主要从理论上分析课题的可行性。
\subsection{拟采的研究方法、技术路线、实验方案}
根据本课题的研究内容，本课题拟采用的研究方法、技术路线、实验方案有以下两个方面：
\paragraph{含整数和数组数据类型的字符串约束求解技术} 拟采用有限状态自动机及其扩展来对字符串约束进行建模，主要分为以下三个方面：\newline
（1）对含有整数数据类型的字符串约束的求解：

Chen等人在2019年开发了字符串约束求解器OSTRICH\cite{ostrich}，OSTRICH已经能够处理大部分字符串函数，但是还不支持$\len$函数，$\substr$函数和$\indexof$函数这些和整数数据类型相关的函数，拟对OSTRICH进行自动机模型和算法层面的扩展。

首先，需要把OSTRICH的经典有限自动机模型扩展为带有寄存器的有限自动机模型。该自动机模型中每个寄存器对应一个整数变量，它的数值随着自动机中的状态变化而变化。然后，基于OSTRICH中的字符串函数反向传播算法，对$\len$函数，$\substr$函数和$\indexof$函数制定反向传播规则，仔细考虑对应的整数值的变化。每个函数反向传播的结果是一组带寄存器的有限自动机，该自动机记录了该函数中字符串的值和整数的值。当反向传播算法完成后，字符串约束被转化为一组带寄存器的有限自动机，字符串约束求解问题转化为该组自动机的判空问题。

经典自动机的判空问题是可判定的，且有高效的求解算法，但是带寄存器的有限自动机的判空问题还未被研究。它的每个寄存器的取值没有上界，所以本质上是一个无穷状态系统，它的判空问题更为复杂。受到Parikh等人\cite{parikh}将经典自动机转化为线性整数算数公式的启发，拟将带寄存器的有限自动机判空问题转化为线性整数算数公式，将寄存器的值用符号值表示，和输入字符串约束中的其他线性整数算术公式一并交给求解器求解。这个过程中涉及到自动机的求交，会带来状态空间爆炸的问题。拟采用NuXmv工具建模带寄存器的有限自动机组，转化为一个等价的无穷状态迁移系统，用经典的模型检验算法如IC3进行求解，避免求交带来的指数爆炸问题。\newline
（2）对带有正则表达式捕获组的$\replaceall$函数：

Chen等人在2019年的研究\cite{ostrich}中指出，$\replaceall$函数的语义可以用一个字符串转换器（$\transducer$函数来模拟），为了正确处理实际程序中的贪婪匹配和非贪婪匹配，以及处理$\replaceall$函数中的反向引用，需要扩展字符串转换器的表达能力。字符串转换器本质上是一个有穷状态迁移模型，拟在该迁移模型的边上添加优先级，解决贪婪匹配和非贪婪匹配的问题；同时在边上引入字符串变量，记录已经匹配到的字符串及对应的捕获组的值，解决反向引用的问题。最后，定义扩展后的字符串转换器的反向传播规则，使其能够应用OSTRICH的反向传播算法。\newline
（3）对含有数组数据类型的字符串约束：

拟将字符串数组看作一个长的字符串，该字符串用特殊的符号$\sharp$来分隔数组中的元素。如一个含三个字符串元素的数组$[‘a’,‘b’,‘c’]$，用字符串$‘a\sharp b\sharp c’$来表示它。这样，就能够用扩展后的有限状态自动机来刻画数组类型的变量，用寄存器来存储数组的下标。对于一般的数组，拟采用SMT求解器中经典的数组理论，用已有的算法求解。$\myjoin$函数输入一个字符串数组和一个连接符，返回一个连接后的字符串。拟复用OSTRICH中的反向传播算法，定义$\myjoin$的反向传播规则。需要注意到是，由于字符串数组可以用带寄存器的有限自动机来建模，$\myjoin$函数的反向传播返回一个带寄存器的有限自动机表示数组。$\mysplit$函数输入一个字符串和一个分割符，返回一个分割后的子串数组。注意不同于$\myjoin$函数，$\mysplit$函数的输出是一个数组，这个数组可能是一个变量，所以没有直接对应的带寄存器的有限自动机模型。需要分析上下文信息，探测数组中的具体字符串元素，生成对应模型，然后再定义$\mysplit$的反向传播规则。
\paragraph{JavaScript符号执行：} 本课题拟采用上述字符串约束求解器，对已有JavaScript符号执行引擎进行扩展，定义数组相关字符串函数如$\mysplit$和$\myjoin$的插装，定义带有捕获组的字符串函数如$\test$、$\match$和$\replaceall$的插装，使其能正确生成相应的字符串约束。其他字符串函数的定义则不变。引入数组类型后，求解速度可能变慢，带有寄存器的自动机组的可达性带来的路径爆炸的问题不可忽视。首先，本课题将根据已有经验，探索高效的启发式求解算法，用NuXmv工具进行启发式求解，将自动机下近似地地转化为线性整数算术公式。其次，本课题拟将Concolic执行方法应用到该分析框架中。Concolic执行遇到某些复杂的字符串函数调用时，只对被调用函数做具体执行，不进入被调用的函数，而是在函数返回后，以其输出作为新的符号变量加入到符号状态，并继续运行程序。本次执行结束后，回到调用点，根据执行的结果搜索被调用函数的路径空间，利用本次执行已获得的信息只搜集所需部分的路径约束从而避免了枚举所有路径，达到节省计算的目的。

\subsection{可行性分析}
近年来字符串约束求解技术及其应用已经被系统地进行研究，以上的理论分析已经过大量调研并产生了一定的理论成果。本人导师在自动机理论、字符串约束求解方面有着丰富的研究经验，其团队和国外团队共同开发了字符串约束求解器OSTRICH，是第一个能够支持$\replaceall$函数的字符串约束求解器。本课题的字符串约束求解工具可以在OSTRICH的基础上进行扩展；同时本人所在团队和国外团队共同扩展了JavaScript符号执行工具Aratha，使其能够支持贪婪匹配和$\replaceall$的反向引用，扩展后的Aratha效率高于ExpoSE。本课题的符号执行工具可以在Aratha的基础上进行扩展，因此本课题的研究目标是可行的。

\section{已有科研基础与所需的科研条件}
本人与导师合作发表了三篇文章:
\begin{itemize}
    \item  T. Chen, M. Hague, J. He, D. Hu, A. Lin, P. Ruemmer, Z. Wu: A Decision Procedure for Path Feasibility of String Manipulating Programs with Integer Data Type. ATVA 2020.\cite{ostrich_atva}该文章研究了带有整数类型的字符串约束求解问题，被ATVA2020录用。
    \item P. Abdulla, M. Atig, Y. Chen, B. Diep, L. Holík, D. Hu, W. Tsai, Z. Wu, D. Yen: Solving Not-Substring Constraint with Flat Abstraction. APLAS 2021.\cite{not_substr}该文章研究了带有$\mathsf{not-substring}$约束的字符串约束求解问题，被APLAS2021录用。
    \item  T. Chen, M. Hague, Z. Han, D. Hu, A. Lamas, A. Lin, S. Kan, P. Ruemmer, Z. Wu: Solving String Constraints With Regex-Dependent Functions Through Transducers With Priorities And Variables. POPL2022.\cite{ostrich_greedy}该文章研究了带有贪婪匹配正则表达式的的函数如$\test$函数，研究了带有反向引用的$\replaceall$函数的建模和求解，被POPL2022录用。
\end{itemize}

\section{研究工作计划与进度安排}
\begin{itemize}
    \item 2023年8月至2023年12月：研究带有寄存器的有限自动机的可达性问题的高效求解方法，设计并实现启发式算法。
    \item 2024年1月至2024年6月：研究带有数组类型的字符串约束的可判定性，设计求解算法并开发相应字符串约束求解器。  
    \item 2024年7月至2025年2月：扩展JavaScipt符号执行引擎，将能够处理数组类型字符串约束求解器集成到符号执行引擎中。
\end{itemize}

\nocite{*}% 使文献列表显示所有参考文献（包括未引用文献）
%---------------------------------------------------------------------------%

### 2023-08-02 2023-1-19/sections/algorithms.tex
grammerly check

@@
 
-The goal of this section is to show how we solve RECL constraints by utilizing CEFA. 
+This section aims to show how we solve RECL constraints by utilizing CEFA. 
 At first, we reduce the satisfiability of RECL constraints into a decision problem for CEFA defined in the sequel. Then we propose an algorithm to solve the decision problem.
@@
 We say that $e$ is \emph{register-representable} if all occurrences of counting operators in $e$ are register-representable.
-For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ are not, since $a^{\{2,6\}}$ is in the scope of language difference and the counter operator $\{2, \infty\}$ respectively.
+For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ are not since $a^{\{2,6\}}$ is in the scope of language difference and the counter operator $\{2, \infty\}$ respectively.
 
-Let $e$ be a register-representable regular expression over $\Sigma$. We are going to construct a CEFA out of $e$, denoted by $\aut_e$, by the following procedure. 
+Let $e$ be a register-representable regular expression over $\Sigma$. By the following procedure, we will construct a CEFA out of $e$, denoted by $\aut_e$. 
 \begin{enumerate}
-\item For each maximal sub-expression $e'$ of $e$ such that $e'$ contains no occurrences of counting operators, an NFA $\aut_{e'}$ can be constructed by a structural induction on the syntax of $e'$. 
+\item For each maximal sub-expression $e'$ of $e$ such that $e'$ contains no occurrences of counting operators, an NFA $\aut_{e'}$ can be constructed by structural induction on the syntax of $e'$. 
 %
@@
 Moreover, the unfoldings are partial in the sense that the outmost counting operators are not unfolded.
-It turns out that our approach can solve almost all of them, except 145.
+It turns out that our approach can solve almost all of them except 145.
 %$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
@@
 The inductive step is constructing CEFA of the concatenation, union, intersection, closure, complement, and counting of CEFA(s) of sub-regex(es).
-Operations except for counting are trivial and represented in Appendix \ref{appendix:cefa}, we only illustrate counting here.
+Operations except for counting are trivial and represented in Appendix \ref{appendix:cefa}; we only illustrate counting here.
 
@@
 % \subsection{Combine Regex-counting and String-length}
-% In the previous section, we discussed the construction of the regex-counting operator and string-length constraint.
-In this section, we show how to combine them to deal with the string constraints with regex-counting and string-length.
+% In the previous section, we discussed the construction of the regex-counting operator and string-length constraint. In this section, we show how to combine them. 
 % \begin{definition} [The Product of Two CEFA]
@@
 
-In the sequel, we reduce the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$ to the satisfiability of an LIA formula. The reduction relies on two observations.
+In the sequel, we reduce the non-emptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$ to the satisfiability of an LIA formula. The reduction relies on two observations.
 
-The first observation follows from the fact that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA.
+The first observation follows that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA.
 
@@
 $\confset_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$ 
-and $\psi_{\cC_i}:= \lfalse$.  Then iterate the following procedure, until $len = B+1$.
+and $\psi_{\cC_i}:= \lfalse$.  Then iterate the following procedure until $len = B+1$.
 \begin{enumerate}
@@
 \end{enumerate}
-Intuitively, for each $i \in [n]$, $\psi_{\cC_i}$ is a global variable whose value is never reset and it stores the set of ``final'' valuations of registers of $\cC_i$ (that is, the valuations obtained when reaching final states), and $\confset_{\cC_i}$ stores the set of newly discovered (not necessarily final) ``configurations'' of $\cC_i$.
+Intuitively, for each $i \in [n]$, $\psi_{\cC_i}$ is a global variable whose value is never reset, and it stores the set of ``final'' valuations of registers of $\cC_i$ (that is, the valuations obtained when reaching final states), and $\confset_{\cC_i}$ stores the set of newly discovered (not necessarily final) ``configurations'' of $\cC_i$.
 %, and $\confset_{\cC_i}$ stores those that have been discovered before. 
-Note that the solution searching algorithm in Step 2.5 is incremental in the sense that when the value of $len$ is incremented, the searching continues from $\confset_{\cC_i}$'s, not from scratch.
+Note that the solution searching algorithm in Step 2.5 is incremental because when the value of $len$ is incremented, the searching continues from $\confset_{\cC_i}$'s, not from scratch.
 %, whose values are not reset.
@@
 Moreover, the transitions $(q, \myvec{0}, q')$ in $\cC_i$ can be seen as $\varepsilon$-transitions, that is, we can replace each transition $(q, \myvec{0}, q')$ with $(q, \varepsilon, q')$, without affecting the set $\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}$.
-Therefore, we first do these replacements, apply the $\varepsilon$-transition removal procedure.
+Therefore, we first do these replacements and apply the $\varepsilon$-transition removal procedure.
 Then we utilize the determinization and minimization algorithm for NFA to reduce the size of $\cC_i$.
 
-It turns out that to solve the nonemptiness of CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ w.r.t.
-$\varphi$, we can ignore the characters in $\cB_1,\cdots, \cB_n$.
-This is due to the fact that there is only one CEFA for each string variable and $\varphi$ only cares about the values of registers.
+It turns out that to solve the non-emptiness of CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ w.r.t.
+$\varphi$.
+We can ignore the characters in $\cB_1,\cdots, \cB_n$ because there is only one CEFA for each string variable, and $\varphi$ only cares about the values of registers.
 
@@
 Moreover, the transitions $(q, \myvec{0}, q')$ in $\cC_i$ can be seen as $\varepsilon$-transitions, that is, we can replace each transition $(q, \myvec{0}, q')$ with $(q, \varepsilon, q')$, without affecting the set $\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}$.
-Therefore, we first do these replacements, apply the $\varepsilon$-transition removal procedure.
+Therefore, we first do these replacements and apply the $\varepsilon$-transition removal procedure.
 Then we utilize the determinization and minimization algorithm for NFA to reduce the size of $\cC_i$.
@@
 
-In summary, we obtain an algorithm for solving the nonemptiness of $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$, as illustrated in Figure~\ref{xxx}.
+In summary, we obtain an algorithm for solving the non-emptiness of $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$, as illustrated in Figure~\ref{xxx}.
 
@@
 To each CEFA $\aut$, we get pairs of last state and corresponding registers' values from $lastStates$ at line 8.
-In each pair, if the last state is accepted at line 9, we add the LIA formula of the possible registers' values to $\varphi_\aut$ as a conjunct at line 10.
+If the last state is accepted at line 9 in each pair, we add the LIA formula of the possible registers' values to $\varphi_\aut$ as a conjunct at line 10.
 After that, we update the set of pairs in $lastStates$ by removing the probed pair at line 12 and adding new pairs of the next state and corresponding registers' values at line 13.
@@
 In the third iteration, the pairs in the $lastStates(\aut)$ with accepting state should be $(q_0', (2,2, 0, 0)), (q_1', (2,1,1,0))$, $(q_1', (2,0,2,0))$, $(q_2', (2,1,0,0)), (q_2', (2,0,1,0)),$ $(q_2', (2,0, 0, 0))$.
-The corresponding registers' values for the accepted state $q_2'$ is $(2,1,0,0), (2, 0, 1, 0), (2, 0, 0, 0)$, in which the value of $r_1$ and $r_2$ can not be both larger than 1 which is required by $\theta$.
+The corresponding registers' values for the accepted state $q_2'$ are $(2,1,0,0), (2, 0, 1, 0), (2, 0, 0, 0)$, in which the value of $r_1$ and $r_2$ can not be both larger than 1 which is required by $\theta$.
 So the formula $\theta\wedge \varphi_{under}$ is still unsatisfiable.

### 2023-08-02 2023-1-19/sections/cefa.tex
grammerly check

@@
 
-In this section, we define the model of cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
+In this section, we define the cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
 %
-Intuitively, CEFA add write-only cost registers to finite state automata.
-Here by ``write-only'', we mean that the cost registers can only be written/updated, but cannot be read, that is, cannot be used to guard the transitions.
+Intuitively, CEFA adds write-only cost registers to finite state automata.
+Here by ``write-only'', we mean that the cost registers can only be written/updated but cannot be read; that is, they cannot be used to guard the transitions.
 
@@
 
-We would like to remark that the aforementioned definition of CEFA is slightly different from that in \cite{atva2020}, where CEFA did not include accepting conditions.
-Moreover, the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion in the sense that the accepting condition does not distinguish final states.
+We want to remark that the definition above of CEFA is slightly different from that in \cite{atva2020}, where CEFA did not include accepting conditions.
+Moreover, the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion because the accepting condition does not distinguish final states.
 This technical choice is made so that the determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.
@@
 A string $w$ is \emph{accepted} by $\aut$ if there is an accepting run of $\aut$ on $w$.
-The language defined by $\aut$, denoted by $\Lang(\aut)$, is the set of strings that are accepted by $\aut$.
+The language defined by $\aut$, denoted by $\Lang(\aut)$, is the set of strings accepted by $\aut$.
 
@@
 
-In the sequel, we define three operations on CEFA, namely, union, intersection, and concatenation. These three operations will be used for solving RECL constraints in the next section.
+In the sequel, we define three CEFA operations: union, intersection, and concatenation. The following section will use these three operations to solve RECL constraints.
 
@@
 The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$, is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.
-Two fresh auxiliary registers, say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ or from $\aut_2$.
+Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ or $\aut_2$.
 Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, where

### 2023-08-02 2023-1-19/sections/conclusion.tex
grammerly check

@@
 %TODO
-This work proposes an efficient automata-theoretical approach for solving RECL constraints, that is, string constraints with regex-counting and string-length.
-The approach is based on the idea of encoding counting operators in regular expressions by registers symbolically, instead of unfolding them explicitly.
-Moreover, this paper proposes an automata-size reduction technique and an under-approximation based solution searching technique to improve the performance.
+This work proposes an efficient automata-theoretical approach for solving RECL constraints: string constraints with regex-counting and string-length.
+The approach is based on encoding counting operators in regular expressions by registers symbolically instead of unfolding them explicitly.
+Moreover, this paper proposes an automata-size reduction technique and an under-approximation-based solution searching technique to improve performance.
 Finally, we use two benchmark suites comprising 48,834 instances in total to evaluate the performance of our approach.
-The experimental results show that our approach can solve more instances than the state-of-the-art best solvers on RECL constraints, with a comparable performance.
-For the future work, we plan to investigate symbolic approaches to dealing with nested counting operators.
+The experimental results show that our approach, with comparable performance, can solve more instances than the state-of-the-art best solvers on RECL constraints.
+We plan to investigate symbolic approaches to dealing with nested counting operators in future work.
 

### 2023-08-02 2023-1-19/sections/implementation.tex
typo removement
grammerly check

@@
 
-We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
-Then we do experiments on two benchmark suites, to evaluate the performance of $\ostrichrecl$.
+We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{Ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
+Then we do experiments on two benchmark suites to evaluate the performance of $\ostrichrecl$.
 In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
@@
 %We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
-Moreover, among these 40,628 RECL constraints, only 5\% of them include non-register-representable regexes.
 
@@
 There are 8,215 instances in the AutomatArk suite here.
-Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.
+Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, conjunctions of regular membership queries generated out of regular expressions from \cite{automatark}.
 %Only 8,751 ones that contain counting operators out of 19,979 instances.
+
+Moreover, among the 48,834 RECL constraints in the RegCoL or AutomatArk suite, only 5\% of them include non-register-representable regexes.
 
@@
 counting operator, consisting of a total of 49,379 instances.
-We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with counting operator.
+We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with the counting operator.
 In total, almost 18\% of the instances we evaluated were sourced from published industrial benchmarks or other solver developers.
-The other instances are generated by ourselves with regular expressions from real world.
-Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large upper bounds of counting operator (the sum of upper bounds is greater than 50), and "small" contains remained instances.
+The other instances are generated by ourselves with regular expressions from the real world.
+Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large upper bounds of the counting operator (the sum of upper bounds is greater than 50), and "small" contains remaining instances.
 About 10\% of the benchmarks are in a "large" set.
@@
 The simple track contains instances with a single regular expression membership constraint, whereas the hard track can hold up to five membership constraints for a single variable per instance.
-We extract 8,751 instances containing counting operator.
+We extract 8,751 instances containing counting operators.
 
@@
 Currently, it has indexed 4149 expressions from 2818 contributors around the world since 2001.
-We extract 1,623 instances containing bounded repetition from 4149 instances.
+We extracted 1,623 instances containing bounded repetition from 4149 instances.
 The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
@@
 The website is a question-and-answer site for professional and enthusiast programmers.
-We extract 37,381 instances containing bounded repetition from almost 500,000 instances.
+We extracted 37,381 instances containing bounded repetition from almost 500,000 instances.
 The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
@@
 
-The experiment results on the RegCol benchmark suite are put in Table~\ref{tab:results_regcol}. 
+The RegCol benchmark suite's experiment results are in Table~\ref{tab:results_regcol}. 
 From Table~\ref{tab:results_regcol}, we can see that $\ostrichrecl$ solvers almost all 40,628 instances, except 106 of them, that is, it solves 40,522 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092
@@
 %    
-Note that the solvers  Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth\footnote{Although it seems a bit strange to use one solver as the ground truth, this is the practice for string constraint solving, since CVC5 is the most stable string solver at present.}.
-If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance.
+Note that the solvers  Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth\footnote{Although it seems strange to use one solver as the ground truth, this is the practice for string constraint solving, since CVC5 is the most stable string solver at present.}.
+If CVC5 reports ``unknown'' or ``timeout'' in some instances, then no soundness errors will be reported in this instance.
 %A soundness error is reported if the result of a solver for an instance is different from CVC5. 
@@
 More specifically, $\ostrichrecl$ spends 3.02 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.56 seconds per instance.
-Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
+Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
 
@@
 %    
-Still the soundness errors are reported by taking the results of CVC5 as the ground truth.
+Still, the soundness errors are reported by taking the results of CVC5 as the ground truth.
 %Note that Z3-Trau has soundness errors, where the result of CVC5 is taken as the ground truth.
-If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance.
+If CVC5 reports ``unknown'' or ``timeout'' in some instances, then no soundness errors will be reported in this instance.
 %A soundness error is reported if the result of a solver for an instance is different from CVC5. 
@@
 
-In summary, $\ostrichrecl$ solves 48,698 out of 48,834 instances, which is 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
+In summary, $\ostrichrecl$ solves 48,698 out of 48,834 instances, 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
 Moreover, the speed of $\ostrichrecl$ is the second fastest and comparable to that of Z3str3RE.
@@
 From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column).
-Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ help to solve 19 more sat instances, while reduces the number of solved unsat instances by 3, since under approximation techniques do not help to solve unsat instances.
+Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ helps to solve 19 more sat instances while reducing the number of solved unsat instances by 3 since under approximation techniques do not help to solve unsat instances.
 }
@@
 One of these solvers is CVC5\cite{cvc5}, a general SMT solver that uses algebraic reasoning to handle strings and regular expressions and is the winner of SMT-COMP 2022\cite{smt-comp}.
-Another solver, Z3str3\cite{z3str3}, is the most recent addition we can get to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions.
+Another solver, Z3str3\cite{z3str3}, is the most recent edition we can get to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions.
 Z3str3RE\cite{z3str3re} is a variant of Z3str3 that incorporates length-aware algorithms and heuristics.
@@
 Z3-Trau\cite{z3trau} is the Z3 version of trau\cite{trau} that employs a flat automata-based approach, incorporating both under- and over-approximations.
-Ostrich\cite{ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships.
-We used the 1.0.5 binary version of CVC5, commit 59e9c87 of Z3str3, last version of Z3str3RE, 4.8.9 binary version of Z3Seq, commit 1628747 of Z3-Trau and commit 8297d8d of Ostrich.
+Ostrich\cite{Ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships.
+We used the 1.0.5 binary version of CVC5, commit 59e9c87 of Z3str3, the last version of Z3str3RE, 4.8.9 binary version of Z3Seq, commit 1628747 of Z3-Trau and commit 8297d8d of Ostrich.
 Z3-Trau does not support \verb|re.diff|.
@@
 \newline
-Table \ref{tab:results_all} summarizes the results that demonstrate OstrichCEA's superior performance, solving the most significant number of instances and outperforming most competing solvers.
+Table \ref{tab:results_all} summarizes the results demonstrating OstrichCEA's superior performance, solving the most significant number of instances and outperforming most competing solvers.
 Including timeouts, OstrichCEA is \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3, \textbf{3.11}\mult{} faster than CVC5 and close to Z3str3RE with \%2 speed loss .
@@
 Z3-based solvers Z3str3 yielded 38 soundness errors, Z3seq\cite{z3seq} yielded 51 soundness errors and Z3str3RE\cite{z3str3re} yielded 39 soundness error.
-Most of them are due to the mistake formalization of the backslash character.
-OstrichCEA resulted 5 unknowns because it reached the maximum threshold of limited memory 2GB.
+Most of them are due to the mistake of formalization of the backslash character.
+OstrichCEA resulted in 5 unknowns because it reached the maximum threshold of limited memory 2GB.
 More details of the results of each benchmark are shown in \ref{appendix:experiential_results}.
@@
 The remaining plot lines exhibit performance with only the named heuristic disabled while all others are enabled.
-From the plots and table, it is evident that OstrichCEA functions most effectively when all heuristics are enabled.
+The plots and table show that OstrichCEA functions most effectively when all heuristics are enabled.
 In average time with timeout times, OstrichCEA performs \textbf{1.78}$\times$ faster than employing none of our heuristics, \textbf{1.37}$\times$ faster than turning off simplification, \textbf{1.15}$\times$ faster than truing off under-approximation.
@@
   \subimport{figures/}{cactus_plot_heuristic.tex}
-  \caption{A performance comparison was made on all benchmarks by disabling individual heuristics using a cactus plot.}
+  \caption{A performance comparison was made on all benchmarks by turning off individual heuristics using a cactus plot.}
   \label{fig:cactus_heuristics}
@@
   \subimport{tables}{table_heuristic.tex}
-  \caption{A performance comparison was made on all benchmarks by disabling individual heuristics.}
+  \caption{A performance comparison was made on all benchmarks by turning off individual heuristics.}
   \label{tab:results_heuristics}

### 2023-08-02 2023-1-19/sections/preliminaries.tex
grammerly check

@@
 
-We write $\Nat$ and $\Int$ for the sets of natural and integer numbers, respectively.
+We write $\Nat$ and $\Int$ for the sets of natural and integer numbers.
 For $n \in \Nat$ with $n \ge 1$, $[n]$ denotes $\{1, \ldots, n\}$; for $m,n \in \Nat$ with $m \le n$,  $[m, n]$ denotes $\{ i \in \Nat \mid m \le i \le n \}$.
@@
 
-%\tl{to put in a different place later} Note that our decision procedure is applicable to general transducers as well, however, the EXPSPACE complexity bound is not, because the distributive property $f^{-1}(L_1\cap L_2)= f^{-1}(L_1)\cap f^{-1}(L_2)$ for regular languages $L_1, L_2$ only holds for functional transducers $f$.
+%\tl{to put in a different place later} Note that our decision procedure also applies to general transducers.
+However, the EXPSPACE complexity bound is not because the distributive property $f^{-1}(L_1\cap L_2)= f^{-1}(L_1)\cap f^{-1}(L_2)$ for regular languages $L_1, L_2$ only holds for functional transducers $f$.
 
@@
 
-%In this paper, we consider logics involving two data-types, i.e., the string data-type and the integer data-type.
+%In this paper, we consider logic involving two data types, i.e., the string and integer data types.
 We will use $u, v, \dots$ to denote string constants,  $c, d,\dots$ to denote integer constants, $x, y, \dots$ to denote string variables, and $i, j, \dots$ to denote integer variables.
@@
 \emph{Linear integer arithmetic and Parikh images.}
-We will also use standard quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulas, which are typically ranged over by $\phi, \varphi$, etc. 
+We will also use standard quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulas, which typically range over by $\phi, \varphi$. 
 For a set $\mathfrak{X}$ of variables, we use $\Phi(\mathfrak{X})$ to denote the set of quantifier-free LIA formulas whose free variables are from $\mathfrak{X}$. 
@@
 For an LIA formula $\varphi(\vec{\anivar})$ with $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ and $\myvec{t} = (t_1, \cdots, t_k)$ be a tuple of integer terms, we use $\varphi[\myvec{t}/\myvec{\anivar}]$ to denote the formula obtained by replacing (simultaneously) $\anivar_i$ with $t_i$ for every $i \in [k]$.
-%For convenience, we usually assume that a set $X$ of variables is a vector. 
+%For convenience, we assume a set $X$ of variables is a vector. 
 %, which is essentially Presburger

### 2023-08-02 2023-1-19/sections/recl.tex
grammerly check

@@
 %\subsubsection{Syntax}
-In the sequel, we define string constraints with regex-counting and string-length function (abbreviated as RECL).
+In the sequel, we define string constraints with regex-counting and string-length functions (abbreviated as RECL).
 The syntax of RECL is defined by the rules in Figure~\ref{fig:syntax}, where $x$ is a string variable, $\anivar$ is an integer variable, $a$ is a character from an alphabet $\Sigma$, and $m, n$ are integer constants.
@@
 $t_1$ and $t_2$ are integer terms, and $\op \in \{=, \neq, \le, \ge, <, >\}$.
-Atomic formulas of the form $x \in \regex$ are called \emph{regular membership} constraints and atomic formulas of the form $t_1\ \op\ t_2$ are called \emph{length} constraints.
+Atomic formulas of the form $x \in \regex$ are called \emph{regular membership} constraints, and atomic formulas of the form $t_1\ \op\ t_2$ are called \emph{length} constraints.
 %
@@
 
-%The definition of the semantics of RECL is standard. Nevertheless, for readibility, we include the definition of its semantics here.
+%The definition of the semantics of RECL is standard. Nevertheless, for readability, we include the definition of its semantics here.
 
@@
 Then the semantics of  $\varphi$ is defined with respect to a mapping $\theta: \svars(\varphi) \rightarrow \Sigma^* \uplus \ivars(\varphi) \rightarrow \Int$ (where $\uplus$ denotes the disjoint union).
-Note that the mapping $\theta$ can be naturally extended to the set of integer terms. For instance, $\theta(|x|) =|\theta(x)|$, $\theta(t_1 + t_2) = \theta(t_1) + \theta(t_2)$. 
+Note that the mapping $\theta$ can naturally extend to the set of integer terms. For instance, $\theta(|x|) =|\theta(x)|$, $\theta(t_1 + t_2) = \theta(t_1) + \theta(t_2)$. 
 A  mapping $\theta$ is said to satisfy $\varphi$, denoted by $\theta \models \varphi$, if one of the following holds: 
@@
 %\end{itemize}
-A RECL formula $\varphi$ is said to be satisfiable if there is a mapping $\theta$ such that $\theta \models \varphi$.
-The satisfiability problem for RECL (abbreviated as $\reclsat$) is to decide whether a given RECL formula $\varphi$ is satisfiable.
+A RECL formula $\varphi$ is satisfiable if there is a mapping $\theta$ such as $\theta \models \varphi$.
+The satisfiability problem for RECL (which is abbreviated as $\reclsat$) is deciding whether a given RECL formula $\varphi$ is satisfiable.
 

### 2023-08-02 2023-1-19/sections/abstract.tex
experiments
remove under approximation

@@
 %
-To improve the performance further, on the one hand, we propose techniques to reduce automata sizes, 
-%thus reducing the sizes of linear arithmetic formulas computed from automata as well, 
-and on the other hand, we utilize under approximations to search for solutions.   
+To improve the performance further, we propose techniques to reduce automata sizes.
 % we propose state reduction techniques and under-approximation to improve the performance further. 
 We implement the algorithms and validate our approach on 48,834 benchmark instances. The experimental results show that 
-our approach can solve more instances than the other tools, with comparable or better performance.
+our approach can solve more instances than the other solvers, at a comparable or faster speed.
 % performance of this approach compared against the state-of-the-art string solvers.

### 2023-08-02 2023-1-19/sections/algorithms.tex
remove under approximation

@@
 
-Finally, although we propose techniques to reduce the sizes of $\cU_{\cB_i}$'s, it is still relatively expensive to compute LIA formulas from $\cC_i$'s and solve their satisfiability, especially for those satisfiable problem instances, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
+% Finally, although we propose techniques to reduce the sizes of $\cU_{\cB_i}$'s, it is still relatively expensive to compute LIA formulas from $\cC_i$'s and solve their satisfiability, especially for those satisfiable problem instances, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
 $\varphi$.
-Therefore, in the sequel, we propose a heuristic to search for solutions by utilizing under approximations, to be executed before Step 3.
+% Therefore, in the sequel, we propose a heuristic to search for solutions by utilizing under approximations, to be executed before Step 3.
 Intuitively, we search for solutions by bounding the lengths of the strings that are accepted by $\cC_i$'s.
@@
 
-For $i \in [n]$, suppose $R_{\cB_i} = (r_{i,1},\cdots, r_{i, k_i})$ and $\cC_i = (Q'_i, \costset_{\cC_i}, \delta'_i, q_{i,0}, F'_i)$.
+% For $i \in [n]$, suppose $R_{\cB_i} = (r_{i,1},\cdots, r_{i, k_i})$ and $\cC_i = (Q'_i, \costset_{\cC_i}, \delta'_i, q_{i,0}, F'_i)$.
 
-\paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let 
-%$\confset_{\cC_i}:=\emptyset$, 
-$\confset_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$ 
-and $\psi_{\cC_i}:= \lfalse$.  Then iterate the following procedure until $len = B+1$.
-\begin{enumerate}
-\item Let $\xi: = \bigwedge \limits_{i \in [n]} \alpha_i \wedge \varphi$.
-%
-\item For each $i \in [n]$, do the following.
-\begin{enumerate}
-\item Let 
-%$\confset_{\cC_i}:= \confset_{\cC_i} \cup \confset'_{\cC_i}$, 
-$old_i:=\confset_{\cC_i}$, $\confset_{\cC_i}:=\emptyset$.
-%
-\item For each $(q, \myvec{v}) \in old_i$,
-\begin{enumerate}
-\item if $q \in F'_i$, then let $\psi_{\cC_i}:=\psi_{\cC_i} \vee (\bigwedge \limits_{j \in [k_i]} r_{i,j} = v_j)$, 
-%
-%\item let $\confset'_{\cC_i}:=\confset'_{\cC_i} \setminus \{(q, \myvec{v})\}$, 
-%
-\item for each $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset_{\cC_i}:=\confset_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
-\end{enumerate}
-%
-%\item 
-%
-\item Let $\xi := \xi \wedge \psi_{\cC_i}$. 
-\end{enumerate}
-%
-\item If $\xi$ is satisfiable, then report $\ltrue$ and the whole algorithm terminates. 
-%
-\item Let $len: = len+1$. \qed
-\end{enumerate}
-Intuitively, for each $i \in [n]$, $\psi_{\cC_i}$ is a global variable whose value is never reset, and it stores the set of ``final'' valuations of registers of $\cC_i$ (that is, the valuations obtained when reaching final states), and $\confset_{\cC_i}$ stores the set of newly discovered (not necessarily final) ``configurations'' of $\cC_i$.
-%, and $\confset_{\cC_i}$ stores those that have been discovered before. 
-Note that the solution searching algorithm in Step 2.5 is incremental because when the value of $len$ is incremented, the searching continues from $\confset_{\cC_i}$'s, not from scratch.
+% \paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let 
+% %$\confset_{\cC_i}:=\emptyset$, 
+% $\confset_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$ 
+% and $\psi_{\cC_i}:= \lfalse$.  Then iterate the following procedure until $len = B+1$.
+% \begin{enumerate}
+% \item Let $\xi: = \bigwedge \limits_{i \in [n]} \alpha_i \wedge \varphi$.
+% %
+% \item For each $i \in [n]$, do the following.
+% \begin{enumerate}
+% \item Let 
+% %$\confset_{\cC_i}:= \confset_{\cC_i} \cup \confset'_{\cC_i}$, 
+% $old_i:=\confset_{\cC_i}$, $\confset_{\cC_i}:=\emptyset$.
+% %
+% \item For each $(q, \myvec{v}) \in old_i$,
+% \begin{enumerate}
+% \item if $q \in F'_i$, then let $\psi_{\cC_i}:=\psi_{\cC_i} \vee (\bigwedge \limits_{j \in [k_i]} r_{i,j} = v_j)$, 
+% %
+% %\item let $\confset'_{\cC_i}:=\confset'_{\cC_i} \setminus \{(q, \myvec{v})\}$, 
+% %
+% \item for each $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset_{\cC_i}:=\confset_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
+% \end{enumerate}
+% %
+% %\item 
+% %
+% \item Let $\xi := \xi \wedge \psi_{\cC_i}$. 
+% \end{enumerate}
+% %
+% \item If $\xi$ is satisfiable, then report $\ltrue$ and the whole algorithm terminates. 
+% %
+% \item Let $len: = len+1$. \qed
+% \end{enumerate}
+% Intuitively, for each $i \in [n]$, $\psi_{\cC_i}$ is a global variable whose value is never reset, and it stores the set of ``final'' valuations of registers of $\cC_i$ (that is, the valuations obtained when reaching final states), and $\confset_{\cC_i}$ stores the set of newly discovered (not necessarily final) ``configurations'' of $\cC_i$.
+% %, and $\confset_{\cC_i}$ stores those that have been discovered before. 
+% Note that the solution searching algorithm in Step 2.5 is incremental because when the value of $len$ is incremented, the searching continues from $\confset_{\cC_i}$'s, not from scratch.
 %, whose values are not reset.

### 2023-08-02 2023-1-19/sections/introduction.tex
remove under approximation

@@
 As a result, we propose various techniques to reduce the state space and the number of transitions of CEFA.
-Furthermore, since the computation of LIA formulas from CEFA is relatively expensive, we also propose a method of searching for strings that are accepted by CEFA, based on under approximations, before constructing the LIA formulas.
 
-The representation of regex-counting and string-length as registers in CEFA, combined with the aforementioned size-reduction and under-approximation techniques, entails an efficient algorithm for solving RECL constraints.
+The representation of regex-counting and string-length as registers in CEFA, combined with the aforementioned size-reduction, entails an efficient algorithm for solving RECL constraints.
 We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH, called $\ostrichrecl$ for convenience.
@@
 LIA formulas was solved by utilizing the nuXmv model checker~\cite{nuxmv}.
-In contrast, this work solves it by integrating the techniques of Parikh-image computation, automata-size reduction, and under approximation.
+In contrast, this work solves it by integrating the techniques of Parikh-image computation and automata-size reduction.
 The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time.

### 2023-08-02 2023-1-19/sections/overview.tex
remove under approximation

@@
 
-At last, for the string constraints that are satisfied by a collection of strings whose lengths are small, computing LIA formulas from NFA and solving them by SMT solvers are still expensive.  
-Therefore, we introduce a heuristic of searching for solutions based on \emph{under approximations}, before computing LIA formulas and solving them by SMT solvers.
+% At last, for the string constraints that are satisfied by a collection of strings whose lengths are small, computing LIA formulas from NFA and solving them by SMT solvers are still expensive.  
+% Therefore, we introduce a heuristic of searching for solutions based on \emph{under approximations}, before computing LIA formulas and solving them by SMT solvers.
 More precisely, we enforce a constant upper bound $B$ on the lengths of strings and search for a $B$-bounded satisfiable assignment, that is, a satisfiable assignment where the lengths of strings are bound by $B$.

### 2023-08-18 2023-1-19/sections/abstract.tex
setta2023

@@
 %Solving string constraints involving regular membership and string-length function has been widely investigated. 
-Counting is a frequently used feature of regexes that count the number of matchings of sub-patterns.
+Counting is a frequently used feature in regexes that counts the number of sub-patterns matchings.
 The state-of-the-art string solvers are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bounds are large.
-In this work, we propose an automata-theoretic approach for solving such class of string constraints efficiently.
+In this work, we propose an automata-theoretic approach for solving such a class of string constraints.
 %
-The main idea is to model the counting operators symbolically by registers in automata, instead of unfolding them explicitly, thus alleviating the state explosion problem resulted from the unfolding.
+The main idea is to model the counting operators symbolically by registers in automata instead of unfolding them explicitly, thus alleviating the state explosion problem.  
 %
-Moreover, we model the string lengths by registers as well. 
+Moreover, the string-length function is modeled by register as well. 
 %Since Parikh images of automata can be defined by linear integer arithmetic formulas, 
-As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which can then be solved by off-the-shelf SMT solvers.
+As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which off-the-shelf SMT solvers can then solve.
 %
@@
 % we propose state reduction techniques and under-approximation to improve the performance further. 
-We implement the algorithms and validate our approach on 48,834 benchmark instances. The experimental results show that 
-our approach can solve more instances than the other solvers, at a comparable or faster speed.
+We implement the algorithms and validate our approach on 48,843 benchmark instances. The experimental results show that 
+our approach can solve more instances than other solvers at a comparable or faster speed.
 % performance of this approach compared against the state-of-the-art string solvers.

### 2023-08-18 2023-1-19/sections/algorithms.tex
setta2023

@@
 
-This section aims to show how we solve RECL constraints by utilizing CEFA. 
-At first, we reduce the satisfiability of RECL constraints into a decision problem for CEFA defined in the sequel. Then we propose an algorithm to solve the decision problem.
+This section aims to show how to solve RECL constraints by utilizing CEFA. 
+At first, we reduce the satisfiability of RECL constraints to a decision problem defined in the following section. Then we propose an algorithm to solve the decision problem.
 
-\vspace{-3mm}
-\begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula\footnote{The decision problem was called satisfiability of an LIA formula w.r.t. CEFA in \cite{atva2020}.}, abbreviated as $\cefadec$]
-Suppose that $x_1, \cdots, x_n$ are string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, and the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, moreover, $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+% \vspace{-3mm}
+\begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula
+% \footnote{The decision problem was called satisfiability of an LIA formula w.r.t. CEFA in \cite{atva2020}.}
+, abbreviated as $\cefadec$]
+Suppose that $x_1, \cdots, x_n$ are string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, and the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, moreover, $\varphi$ is an LIA formula whose free variables are from $ \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
 Then  the CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are said to be nonempty w.r.t.
-$\varphi$ if there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{i,j}}$ for $i \in [n], j \in [l_i]$
+$\varphi$ if there are assignments $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{i,j}}$
 %$\myvec{v_{1,1}}, \cdots, \myvec{v_{1, l_1}}, \cdots, \myvec{v_{n, 1}}, \cdots, \myvec{v_{n, l_n}}$ 
-such that $(\theta(x_i); \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ for every $i \in [n], j \in [l_i]$,
+such that $(\theta(x_i); \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ and  $\varphi[(\myvec{v_{i,j}}/R_{\aut_{i,j}})]$ is true, for every $i \in [n], j \in [l_i]$.
 % \in \aut_{i,1}(\eta(x_1)), \cdots, \myvec{v_{i, l_i}} \in \aut_{i,l_i}(\eta(x_i))$ for every $i \in [n]$  
 %\cdots, \myvec{v_{n,1}} \in \aut_{n,1}(w_n), \cdots, \myvec{v_{n, l_n}} \in \aut_{n, l_n}(w_n)$ 
-and 
-$\varphi[(\myvec{v_{i,j}}/R_{\aut_{i,j}})_{i \in [n], j \in [l_i]}]$ is true. 
+% $\varphi[(\myvec{v_{i,j}}/R_{\aut_{i,j}})_{i \in [n], j \in [l_i]}]$ is true. 
 %$\varphi[\myvec{v_{1,1}}/R_{\aut_{1,1}}, \cdots, \myvec{v_{n, l_n}}/R_{\aut_{n, l_n}}]$ is true. 
 \end{definition}
-
-\vspace{-4mm}
-\begin{proposition}[\cite{atva2020}]\label{prop-cefadec}
+% \vspace{-4mm}
+\begin{proposition}\label{prop-cefadec}
 $\cefadec$ is PSPACE-complete. 
 \end{proposition}
-The decision procedure in \cite{atva2020} was only used to prove the upper bound in Proposition~\ref{prop-cefadec} and not implemented as a matter of fact.
-Instead, the symbolic model checker nuXmv was used to solve $\cefadec$ in \cite{atva2020}.
-We do not rely on nuXmv in this work and shall propose an efficient algorithm for solving $\cefadec$ in Section~\ref{subsec:cefadec}.
+\begin{proof}
+  The lower bound follows from the fact that the nonemptiness problem of the intersection of NFAs is PSPACE-complete \cite{pspace_int}.
+For the upper bound, \cite{atva2020} showed that $\cefadec$ is in PSPACE by reducing it to monotonic counter machines.
+\end{proof}
+Note that the decision procedure in \cite{atva2020} was only used to prove the upper bound in Proposition~\ref{prop-cefadec} and not implemented as a matter of fact.
+Instead, the symbolic model checker nuXmv was used to solve $\cefadec$.
+We do not rely on nuXmv in this work and shall propose a new algorithm for solving $\cefadec$ in Section~\ref{subsec:cefadec}.
 
@@
 We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
-
 \vspace{-3mm}
@@
 Let $e$ be a register-representable regular expression over $\Sigma$. By the following procedure, we will construct a CEFA out of $e$, denoted by $\aut_e$. 
+\vspace{-1mm}
 \begin{enumerate}
-\item For each maximal sub-expression $e'$ of $e$ such that $e'$ contains no occurrences of counting operators, an NFA $\aut_{e'}$ can be constructed by structural induction on the syntax of $e'$. 
 %
@@
 Let $\aut_{e'} = (Q, \Sigma, \delta, I, F)$.
-From the construction for Kleene star in Section~\ref{sec:pre}, $(\aut_{e'})^* = (Q', \Sigma, \delta', I', F')$, where $Q' = Q \cup \{q_0\}$ with $q_0 \not \in Q$, $I' = \{q_0\}$, $F'= F \cup \{q_0\}$, $\delta' = \delta  \cup \{(q_0, a, q')  \mid \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\} \cup \{(q, a, q') \mid q \in F, \exists q'_0 \in I.\ (q'_0, a, q') \in \delta\}$.
-Then $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a register,
+Same as the construction for Kleene star except for the new register and updates on transitions, $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a new register,
 %
+\vspace{-3mm}
 $$
@@
 %
-moreover, $\alpha' = m \le r' \le n$ if $I \cap F = \emptyset$, and $\alpha' = r' \le n$ otherwise.
+moreover, $\alpha' = m \le r' \le n$ if $I \cap F = \emptyset$, otherwise $\alpha' = r' \le n$ .
 (Intuitively, if $\varepsilon$ is accepted by $\aut_{e'}$, then the value of $r'$ can be less than $m$.) Finally, $\aut_{(e')^{\{m, \infty\}}}$ is constructed by adapting $\alpha'$ in $\aut_{(e')^{\{m,n\}}}$ as follows: $\alpha' = m \le r'$ if $I \cap F = \emptyset$ and $\alpha' = \ltrue$ otherwise.
+%
 
-%
 \item For each sub-expression $e'$ of $e$ such that $e'$ contains occurrences of counting operators but $e'$ itself is not of the form $(e'_1)^{\{m,n\}}$ or $(e'_1)^{\{m,\infty\}}$, from the assumption that $e$ is register-representable, we know that $e'$ is of the form $e'_1 \concat e'_2$, $e'_1 + e'_2$, $e'_1 \cap e'_2$, or $(e'_1)$.
@@
 For $e' = e'_1 \concat e'_2$, $e' = e'_1 + e'_2$, or $e' = e'_1 \cap e'_2$, suppose that CEFA $\aut_{e'_1}$ and $\aut_{e'_2}$ have been constructed.
+
+\item For each maximal sub-expression $e'$ of $e$ such that $e'$ contains no occurrences of counting operators, an NFA $\aut_{e'}$ can be constructed by structural induction on the syntax of $e'$. 
 %Without loss of generality,  we assume that $R_{\aut_{e'_1}} \cap R_{\aut_{e'_2}} = \emptyset$. 
@@
 
-For non-register-representable regular expressions, we first transform them into register-representable regular expressions by unfolding all the non-register-representable occurrences of counting operators, then utilize the aforementioned procedure to construct CEFA.
+For non-register-representable regular expressions, we first transform them into register-representable regular expressions by unfolding all the non-register-representable occurrences of counting operators.
+After that, we utilize the aforementioned procedure to construct CEFA.
 For instance, $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa+aaaa) \concat b^*)^{\{2, \infty\}}$.
 The unfoldings of the inner counting operators of non-register-representable regexes incur an exponential blow-up in the worst case.
-Nevertheless, those regexes occupy only 5\% of the 48,834 regexes that are collected from the practice (see Section~\ref{sec:bench}).
+Nevertheless, those regexes occupy only 5\% of the 48,843 regexes that are collected from the practice (see Section~\ref{sec:bench}).
 Moreover, the unfoldings are partial in the sense that the outmost counting operators are not unfolded.
-It turns out that our approach can solve almost all of them except 145.
+It turns out that we can solve almost all of them except 181.
 %$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
@@
 Moreover, we construct another CEFA $\aut_{i, 0}$ for each $i \in [n]$ to model the length of $x_i$.
-Specifically, $\aut_{i,0}$ is constructed as $((r_{i,0}), \{q_{i,0}\}, \Sigma, \delta_{i,0}, \{q_{i,0}\}, \{q_{i,0}\}, \ltrue)$, where $r_{i,0}$ is a fresh register (in particular, $r_{i,0}$ does not occur in $\aut_{i,1}, \cdots, \aut_{i, l_i}$) and $\delta_{i,0} = \{(q_{i,0}, a, q_{i,0}, (1)) \mid a \in \Sigma\}$.
-Let $\Lambda_{x_i} = \{\aut_{i,0}, \aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for each $i \in [n]$. Moreover, let $\varphi'_2 \equiv \varphi_2[r_{1,0}/|x_1|, \cdots, r_{n,0}/|x_n|]$.
-Then the satisfiability of $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi'_2$.
+Specifically, $\aut_{i,0}$ is constructed as $((r_{i,0}), \{q_{i,0}\}, \Sigma, \delta_{i,0}, \{q_{i,0}\}, \{q_{i,0}\}, \ltrue)$ where $r_{i,0}$ is a fresh register and $\delta_{i,0} = \{(q_{i,0}, a, q_{i,0}, (1)) \mid a \in \Sigma\}$.
+Let $\Lambda_{x_i} = \{\aut_{i,0}, \aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for each $i \in [n]$, and $\varphi'_2 \equiv \varphi_2[r_{1,0}/|x_1|, \cdots, r_{n,0}/|x_n|]$.
+Then the satisfiability of $\varphi$ is reduced to the nonemptiness of CEFAs in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t.
+$\varphi'_2$.
 
@@
 
-In the sequel, we present a procedure to solve the $\cefadec$ problem: Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is an LIA formula whose free variables are from $R' = \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
-%
-The procedure comprises four steps.
+In this section, we present a procedure to solve the $\cefadec$ problem: Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ where $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$.
+Moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is a LIA formula whose free variables are from $\bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+The procedure comprises three steps.
 
@@
 \noindent
-\emph{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
+\emph{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \hfill{$\blacksquare$}
 
@@
 
-In the sequel, we reduce the non-emptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$ to the satisfiability of an LIA formula. The reduction relies on two observations.
-
-The first observation follows that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA.
+In the following steps, we reduce the non-emptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+$\varphi$ to the satisfiability of an LIA formula.
+The reduction relies on two observations: The first observation follows that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA, and the second observation follows that the non-emptiness of exactly one CEFA w.r.t LIA formulae is entirely unrelated to the alphabet.
 
@@
 \end{observation}
+\vspace{-2mm}
 
@@
 Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA and $\costset_\aut = \{\myvec{v} \mid \exists q, a, q'.\ (q, a, q', \myvec{v}) \in \delta\}$. 
-Moreover, let $\cU_\aut = (Q, \costset_\aut, \delta', I, F)$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by dropping the accepting condition and ignoring the characters, that is, $\delta'$ comprises the tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for some $a \in \Sigma$.
+Moreover, let $\cU_\aut = (Q, \costset_\aut, \delta', I, F)$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by dropping the accepting condition and ignoring the characters, that is, $\delta'$ comprises tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for $a \in \Sigma$.
 %Then $\cefaout(\aut) = \parikh(\NFA')$.
 %
+
 \vspace{-2mm}
@@
 \end{observation}
+\vspace{-1mm}
 
@@
 
-Because the sizes of the LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$, and it is expensive (NP-complete) to solve the satisfiability of existential LIA formulas, it is vital to reduce the sizes of these NFA.
+Because the sizes of the LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$, and the satisfiability of existential LIA formulas is expensive (NP-complete) to solve, we have to reduce the sizes of these NFA.
 
-Furthermore, we have the following observation: For each $i \in [n]$ and $\eta \in \parikh(\cU_{\cB_i})$, we have 
-$\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}.$
-In other words, the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the sum $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
+Actually, we find that 
+$\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}$ for each $i \in [n]$ and $\eta \in \parikh(\cU_{\cB_i})$, i.e.,
+the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the final output $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
+Therefore, we can remove these transitions in step 2.
 
-Therefore, we can reduce the sizes of $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$ by Step 2 in the sequel.
-
-\paragraph*{Step 2.} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cU_{\cB_i}$, determinize and minimize the resulting NFA.
-\qed
+\medskip
+\noindent
+\emph{Step 2.} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, and remove the $\varepsilon$-transitions from $\cU_{\cB_i}$.
+Then we determinize and minimize the resulting NFA.
+\hfill{$\blacksquare$}
 
@@
 
-\paragraph*{Step 3.} For each $i \in [n]$, compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
-Then solve the satisfiability of the following existential LIA formula
+\medskip
+\noindent
+\emph{Step 3.} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+Then we solve the satisfiability of the following formula.$\blacksquare$
 %
+\vspace{-1mm}
 \[
@@
 \]
+\vspace{-1mm}
 
@@
 % %
-% \item Let $len: = len+1$. \qed
+% \item Let $len: = len+1$. $\blacksquare$
 % \end{enumerate}

### 2023-08-18 2023-1-19/sections/cefa.tex
setta2023

@@
 Intuitively, CEFA adds write-only cost registers to finite state automata.
-Here by ``write-only'', we mean that the cost registers can only be written/updated but cannot be read; that is, they cannot be used to guard the transitions.
+``write-only'' means that the cost registers can only be written/updated but cannot be read, i.e., they cannot be used to guard the transitions.
 
@@
 Two types of definitions have the same expressive ability on the $SAT_{CL}$ problem.
+\vspace{-0.5mm}
 \begin{definition}[Cost-Enriched Finite Automaton]
@@
 \end{definition}
-For a CEFA $\aut$, we use $R_\aut$ to denote the set of registers of $\aut$. 
+\vspace{-0.5mm}
+
+For convenience, we use $R_\aut$ to denote the set of registers of $\aut$.
+We assume a linear order on $R$ and write $R$ as a vector $(r_1, \cdots, r_k)$.
+Accordingly, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where $v_i$ is the update of $r_i$ for each $i \in [k]$.
+We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$.
 %The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
 %are attached to final states.
-
-For convenience, from now on, we assume a linear order on $R$ and write $R$ as a vector $\myvec{r} = (r_1, \cdots, r_k)$.
-Accordingly, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where for each $i \in [k]$, $v_i$ is the update on the value of $r_i$.
-We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$.
 
@@
 The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$.
-Note that we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
+Note that the values of all registers are initiated to zero and updated to $\sum \limits_{j \in [n]} \myvec{v_j}$ after all the transitions in the run are executed.
 We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.
 We define the semantics of a CEFA $\aut$, denoted by $\Lang(\aut)$, as $\{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
-In particular, if $I \cap F \neq \emptyset$, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$.
+In particular, if $I \cap F \neq \emptyset$ and $\alpha(\myvec{0}/R)$ is true, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$.
 Moreover, we define the \emph{output} of a CEFA $\aut$, denoted by $\cefaout(\aut)$, as $\{\myvec{v'} \mid  \exists w.\ \myvec{v'} \in \aut(w)\}$.
 
-We want to remark that the definition above of CEFA is slightly different from that in \cite{atva2020}, where CEFA did not include accepting conditions.
+We want to remark that the definition of CEFA above is slightly different from that of \cite{atva2020}, where CEFA did not include accepting conditions.
 Moreover, the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion because the accepting condition does not distinguish final states.
@@
 The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$, is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.
-Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ or $\aut_2$.
-Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, where
+Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).
+Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where
 \begin{itemize}
@@
 %
-\item $\delta'$ is the union of $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, and $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively.
+\item $\delta'$ is the union of four transitions sets:
+\begin{itemize}
+  \item $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
+  \item $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
+  \item $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid q_1\not\in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
+  \item $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid q_2\not\in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
+\end{itemize}
+ where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively.
 Similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.
@@
 \begin{itemize}
-\item if either $I_1 \cap F_1 \neq \emptyset$ and $\alpha_1[\myvec{0}/R_1]$ is true, or $I_2 \cap F_2 \neq \emptyset$ and $\alpha_2[\myvec{0}/R_2]$ is true, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
+\item if $(\epsilon; \myvec{0})$ belongs to $\lan(\aut_1)$ or $\lan(\aut_2)$, i.e., one of the two automata accepts the empty string $\epsilon$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
 %
@@
 %\myvec{v} \in \Int^{R'}, 
-(w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } \prj_{R_2}(\myvec{v}) = \myvec{0}, \mbox{ or } \\
-(w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2) \mbox{ and } \prj_{R_1}(\myvec{v}) = \myvec{0}
+(w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } \prj_{r_1'}(\myvec{v}) = 1, \mbox{ or } \\
+(w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2) \mbox{ and } \prj_{r_2'}(\myvec{v}) = 1, \mbox{ or } \\
+(w; \myvec{v}) = (\epsilon, \myvec{0}) \mbox{ if } \aut_1 \mbox{ or } \aut_2 \mbox{ accepts } \epsilon
 \end{array}
@@
 $$ 
+Intuitively, $\aut_1 \cup \aut_2$ accepts the words that are accepted by one of the $\aut_1$ and $\aut_2$ and outputs the costs of the corresponding automaton.
 
 The \emph{intersection} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cap \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, is defined in the sequel. 
+\vspace{-0.5mm}
 \begin{itemize}
@@
 \end{itemize}
+\vspace{-0.5mm}
 From the construction, 
-$$\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v}) \mid \myvec{v} \in \Int^{R'}, (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$ 
+\vspace{-0.5mm}
+$$\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v}) \mid (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
+\vspace{-0.5mm}
 Intuitively, $\aut_1 \cap \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.
@@
 From the construction,
-$$\Lang(\aut_1 \concat \aut_2) = \{(w_1w_2; \myvec{v}) \mid (w_1; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1), (w_2; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
+$$\Lang(\aut_1 \concat \aut_2) = \{(w_1w_2; \myvec{v}) \mid (w_1; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and }(w_2; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
 

### 2023-08-18 2023-1-19/sections/conclusion.tex
remove under approximation
setta2023

@@
 The approach is based on encoding counting operators in regular expressions by registers symbolically instead of unfolding them explicitly.
-Moreover, this paper proposes an automata-size reduction technique and an under-approximation-based solution searching technique to improve performance.
-Finally, we use two benchmark suites comprising 48,834 instances in total to evaluate the performance of our approach.
+Moreover, this paper proposes an automata-size reduction technique to improve performance.
+Finally, we use two benchmark suites comprising 48,843 instances in total to evaluate the performance of our approach.
 The experimental results show that our approach, with comparable performance, can solve more instances than the state-of-the-art best solvers on RECL constraints.

### 2023-08-18 2023-1-19/sections/implementation.tex
setta2023

@@
 We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{Ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
-Then we do experiments on two benchmark suites to evaluate the performance of $\ostrichrecl$.
+Then we do experiments on two benchmark suites to evaluate the performance of $\ostrichrecl$, and carry out detailed experiments including evaluation of size-reduction techniques and the experiment of large-counting benchmark.
 In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
@@
 
+\vspace{-3mm}
+\subsection{Benchmark Suites and Experiment Setup}\label{sec:bench}
 \vspace{-2mm}
-\subsection{Benchmark suites}\label{sec:bench}
 
-Our experiments utilize two benchmark suites, namely, RegCoL and AutomatArk. In total, there are 48,834 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
+Our experiments utilize two benchmark suites, namely, RegCoL and AutomatArk. In total, there are 48,843 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
 
@@
 $x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$
-where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$.
+where $\overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is a regular expression that sanitizes all occurrence of special characters $<$, $>$, $'$, $''$, or $\&$.
+The artificial construction is meaningful because the special characters are offensive.
+For instance, they are widely used in client-side attacks like XSS\cite{malware_detection_3_kudzu}\cite{CCH+18}.
 %We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
@@
 %Only 8,751 ones that contain counting operators out of 19,979 instances. 
-
-Moreover, among the 48,834 RECL constraints in the RegCoL or AutomatArk suite, only 5\% of them include non-register-representable regexes.
-
+Moreover, only 5\% of them include non-register-representable regexes among the 48,843 instances.
 %%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
 %%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
+
+\medskip
+\noindent
+\emph{Experiment setup.}
+All experiments are conducted on CentOS Stream release 8 with 4 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory.
+We use the \textsc{zaligvinder} framework \cite{zaligvinder_2021} to execute the experiments, with a timeout of 60s for each instance.
 \hide{
@@
 \vspace{-3mm}
-\subsection{Experiment results}
+\subsection{Overall Experiment Results}
+\vspace{-2mm}
 
@@
 %(version 1.0.5) 
-\cite{cvc5}, Z3seq \cite{z3seq}, Z3-Trau 
-%(github commit 1628747) 
-\cite{z3trau}, Z3str3
+\cite{cvc5}, Z3seq \cite{z3seq}, Z3str3
 %(github commit 59e9c87) 
-\cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH\footnote{The name OSTRICH+ was used in~\cite{atva2020}, where nuXmv model checker was called to solve the nonemptiness of CEFA w.r.t. LIA. } 
+\cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH
 %(github commit 8297d8d) 
-\cite{atva2020}, on RegCoL and AutomatArk.
-All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory.
-We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, where the timeout period is set as 60 seconds per instance.
-
+\cite{ostrich2023}, on RegCoL and AutomatArk benchmark suites.
+% Z3-trau \cite{z3trau} is not evaluated because it does not support \verb|re.diff|, the language difference operator of regular expressions.  
 %The experiments are designed to answer the following two research questions. 
@@
 %\end{description}
+\vspace{-5mm}
+\begin{table}
+  \centering
+  \begin{subtable}{0.513\textwidth}
+      \centering
+      \import{tables}{table_regcol.tex}
+      \caption{Overall Experiment results,\\ with timeout = 60 seconds}
+      \label{tab:results_regcol}
+  \end{subtable}
+  \begin{subtable}{0.477\textwidth}
+      \centering
+      \import{tables}{table_simp.tex}
+      \caption{Simplification technique evaluation, with timeout = 60 seconds}
+      \label{tab:results_simp}
+  \end{subtable}
+  \caption{Experiments on RegCoL and AutomatArk benchmark suites}
+\end{table}
+\vspace{-9mm}
+% \begin{table}[ht]
+%   \vspace{-5mm}
+%   \begin{center}
+%     \import{tables}{table_regcol.tex}
+%   \end{center}
+%   \caption{Overall Experiment results, with timeout = 60 seconds}
+%   \label{tab:results_regcol}
+%   \vspace{-9mm}
+% \end{table}
 
-\begin{table}[ht]
-\vspace{-3mm}
-\begin{center}
-  \import{tables}{table_regcol.tex}
-\end{center}
-  \caption{Experiment results on RegCol, with timeout = 60 seconds}
-  \label{tab:results_regcol}
-\vspace{-6mm}
-\end{table}
-
-The RegCol benchmark suite's experiment results are in Table~\ref{tab:results_regcol}. 
-From Table~\ref{tab:results_regcol}, we can see that $\ostrichrecl$ solvers almost all 40,628 instances, except 106 of them, that is, it solves 40,522 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092
-3,893/2,081/20,483/10,200/1,082/5,505 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
+The overall experiment results are in Table~\ref{tab:results_regcol}.
+Note that we take the result of CVC5 as the ground truth\footnote{At first we used the majority vote between all results of the solvers as the ground truth, but solvers of z3 family outputed some wrong results(verified by us manually), causing the ground truth to be incorrect.} and the soundness error also be counted as unknown.
+We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
+The number is %3,994/2,272/24,577/12,832/1,091/7,092
+\textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
 %      
-Note that the solvers  Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth\footnote{Although it seems strange to use one solver as the ground truth, this is the practice for string constraint solving, since CVC5 is the most stable string solver at present.}.
-If CVC5 reports ``unknown'' or ``timeout'' in some instances, then no soundness errors will be reported in this instance.
 %A soundness error is reported if the result of a solver for an instance is different from CVC5. 
@@
 %
-Moreover, $\ostrichrecl$ is the second fastest solver.
-More specifically, $\ostrichrecl$ spends 3.02 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.56 seconds per instance.
-Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
+Moreover, our solver $\ostrichrecl$ is the second fastest solver and its average time on each instance is closed to the fastest solver Z3str3RE (\textbf{1.93}/1.62 s).
+\vspace{-3mm}
+\subsection{Evaluation of Simplification Techniques}
+\vspace{-2mm}
 
-\begin{table}[ht]
-%\vspace{-1mm}
-\begin{center}
-  \import{tables}{table_automatark.tex}
-\end{center}
-  \caption{Experiment results on AutomatArk, with timeout = 60 seconds}
-  \label{tab:results_automatark}
-\vspace{-6mm}
-\end{table}
+We evaluate the simplification techniques by comparing the performance of $\ostrichrecl$ with and without the simplification techniques.
+Moreover, we also encode the $\cefadec$ problem to infinite state transition system and solve it using \textsc{nuXmv}\cite{nuxmv}.
+% \begin{table}[ht]
+%   \vspace{-5mm}
+%   \begin{center}
+%     \import{tables}{table_simp.tex}
+%   \end{center}
+%   \caption{Simplification technique evaluation, with timeout = 60 seconds}
+%   \label{tab:results_simp}
+%   \vspace{-9mm}
+% \end{table}
 
-The experiment results on the AutomatArk benchmark suite are put in Table~\ref{tab:results_automatark}. 
-From Table~\ref{tab:results_automatark}, we can see that $\ostrichrecl$ solvers almost all 8,215 instances, except 39 of them, that is, it solves 8,176 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092
-101/191/4,094/2,632/9/1,587
-more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
-%    
-Still, the soundness errors are reported by taking the results of CVC5 as the ground truth.
+The evaluation results of simplification techniques are in Table~\ref*{tab:results_simp}.
+We can see that compared to $\ostrichrecl$ without simplification techniques, $\ostrichrecl$ with simplification techniques solves \textbf{1,503 more} instances and is \textbf{2.21$\times$} faster.
+Moreover, compared with the techniques using \textsc{nuxmv}, $\ostrichrecl$ with simplification techniques solves \textbf{1,798 more} instances and is \textbf{3.13$\times$} faster.
+
+\vspace{-3mm}
+\subsection{Large-Counting Experiment Results}
+The distribution of upper bound in RegCoL and AutomatArk suites is showed in Fig~\ref{fig:count_distri}, whose horizontal axis is the value of upper bound and vertical axis is the number of occurrences of it.
+The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$).
+Although the upper bounds of most counting operators are less than 50, there are still about two thousands of them are greater than 50.
+We extract these instances with counting upper bound greater than 50 (1,969 instances in total).
+Moreover, We change the length constraint to $|x| > 200$ (which is $|x| > 10$ in overall experiment), to make the number of $sat$ result more closed to that of $unsat$.
+\vspace{-5mm}
+\begin{figure}[ht]
+  \centering
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering\vskip 0pt
+    \includegraphics[width=1\textwidth]{counting_distribution.png}  
+    \caption{Distribution of counting operators in two benchmark suites.}  
+    \label{fig:count_distri}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering\vskip 0pt
+    \import{tables}{table_large_count.tex}
+    \vspace{4.5mm}
+    \caption{Large counting experiment, \\with timeout = 60 seconds}
+    \label{fig:table_large_count}
+  \end{subfigure}
+  \caption{Analysis of dataset and large counting experiment}
+\end{figure}
+\vspace{-7mm}
+
+% \begin{table}[ht]
+%   \vspace{-5mm}
+%   \begin{center}
+%     \import{tables}{table_large_count.tex}
+%   \end{center}
+%   \caption{Large counting experiment, with timeout = 60 seconds}
+%   \label{tab:results_simp}
+%   \vspace{-9mm}
+% \end{table}
+
+We evaluate the performance of $\ostrichrecl$ on these instances.
+The results are in Fig~\ref{fig:table_large_count}.
+We can see that $\ostrichrecl$ solves \textbf{1,873} instances correctly, which is \textbf{947/278/563/637/523 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+Moreover, \newline
+$\ostrichrecl$ is the fastest solver, who is \textbf{ 6.79/2.88/2.61/5.27/3.95$\times$ } faster than CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+\vspace{-2mm}
+
+% The results are in Table~\ref{tab:results_simplification}.
+We can see that the simplification technique improves the performance of $\ostrichrecl$ significantly.
+It solves 1,111 more instances and is 1.62 times faster than $\ostrichrecl$ without the simplification technique.
+
+% \begin{table}[ht]
+% %\vspace{-1mm}
+% \begin{center}
+%   \import{tables}{table_automatark.tex}
+% \end{center}
+%   \caption{Experiment results on AutomatArk, with timeout = 60 seconds}
+%   \label{tab:results_automatark}
+% \vspace{-6mm}
+% \end{table}
+
+% The experiment results on the AutomatArk benchmark suite are put in Table~\ref{tab:results_automatark}. 
+% From Table~\ref{tab:results_automatark}, we can see that $\ostrichrecl$ solvers almost all 8,215 instances, except 39 of them, that is, it solves 8,176 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092
+% 101/191/4,094/2,632/9/1,587
+% more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
+% %    
+% Still, the soundness errors are reported by taking the results of CVC5 as the ground truth.
 %Note that Z3-Trau has soundness errors, where the result of CVC5 is taken as the ground truth.
@@
 %
-Moreover, $\ostrichrecl$ spends 2.49 seconds per instance on average. 
+% Moreover, $\ostrichrecl$ spends 2.49 seconds per instance on average. 
 %while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.  
@@
 
-In summary, $\ostrichrecl$ solves 48,698 out of 48,834 instances, 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
+% In summary, $\ostrichrecl$ solves 48,698 out of 48,843 instances, 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
 Moreover, the speed of $\ostrichrecl$ is the second fastest and comparable to that of Z3str3RE.
@@
 
-\begin{table}[ht]
-\vspace{-3mm}
-\begin{center}
-  \import{tables}{table_summary.tex}
-\end{center}
-  \caption{Experiment results: A Summary}
-  \label{tab:results_summary}
-\vspace{-6mm}
-\end{table}
+% \begin{table}[ht]
+% \vspace{-3mm}
+% \begin{center}
+%   \import{tables}{table_summary.tex}
+% \end{center}
+%   \caption{Experiment results: A Summary}
+%   \label{tab:results_summary}
+% \vspace{-6mm}
+% \end{table}
 

### 2023-08-18 2023-1-19/sections/introduction.tex
setta2023

@@
 
-In modern programming languages---such as JavaScript, Python, Java, and PHP---the string data type plays a crucial role. 
-It is well-known that string manipulations are error-prone and could even give rise to security vulnerabilities (e.g. \ cross-site scripting, aka XSS). 
-One powerful method for identifying such bugs in programs is \emph{symbolic execution} (possibly in combination with dynamic analysis), which analyses symbolic paths in a program by viewing them as constraints, whose feasibility is checked by constraint solvers.
+In modern programming languages, such as JavaScript, Python, Java, and PHP, the string data type plays a crucial role. 
+String manipulations are error-prone and could even give rise to severe security vulnerabilities (e.g. \ cross-site scripting, aka XSS). 
+One powerful method for identifying such bugs is \emph{symbolic execution} (possibly in combination with dynamic analysis).
+It analyses symbolic paths in a program by viewing them as constraints checked by constraint solvers.
 %
-Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade, including the state-of-the-art string constraint solvers, e.g.
+Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade, e.g.,
 Z3seq~\cite{z3seq}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
@@
 Regular expressions (abbreviated as regex) and string-length function are widely used in string-manipulating programs.
-According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% Java, JavaScript, and Python software projects.
-Moreover, that string-length function occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}. 
+According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% of Java, JavaScript, and Python software projects.
+Moreover, string-length occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}. 
 %Operations like \verb|length| that take string inputs and return an integer frequently appear in real-world JavaScript applications (78\% of string operations in 18 applications)
 As a result, most of the aforementioned string constraint solvers support both regular expressions and string-length function.
-Moreover, specialized algorithms have been proposed to efficiently solve the class of string constraints with regular expressions and string-length function \cite{LTR+15,BD+23}.
+Moreover, specialized algorithms have been proposed to solve such string constraints efficiently.
+\cite{LTR+15,BD+23}.
 %a decision procedure based on tableaux calculus was designed in \cite{LTR+15} for the class of string constraints with regular expressions and string-length function.
@@
 For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
-Note that Kleene star and Kleene plus operator can be seen as special cases of counting operator. For instance, $a^*$ and $a^+$ are equivalent to $a^{\{0,\infty\}}$ and $a^{\{1,\infty\}}$.
+Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ are equivalent to $a^{\{0,\infty\}}$ and $a^+$ are equivalent to $a^{\{1,\infty\}}$.
 Counting is a frequently used feature of regular expressions.
-According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while the other forms of counting occur in more than 20\% of them.
-Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints that contain at least regular expressions with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function.
+According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while other forms of counting occur in more than 20\% of them.
+Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints containing regular expressions with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function at least.
 
-Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from string constraints with regex-counting and string-length, especially when the counting bounds are large.
-For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 300 seconds,
+Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting bounds are large.
+For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 300 seconds, and Z3 can not solve it within 120 seconds.
 %
@@
 
-A typical way for string constraint solvers to deal with regex-counting is to unfold regular expressions with counting into those \emph{without} counting by using the concatenation operator.
+A typical way for string constraint solvers to deal with regular expressions with counting is to unfold them into those \emph{without} counting using the concatenation operator.
 For instance, $a^{\{1, 4\}}$ is unfolded into $a(\varepsilon + a + aa + aaa)$ and $a^{\{2,\infty\}}$ is unfolded into $aaa^{*}$.
-Since the unfolding incurs an exponential blow-up on the sizes of constraints (assuming that the integer constants in string constraints are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the bounds are large.
+Since the unfolding incurs an exponential blow-up on the sizes of constraints (assuming that the counting in string constraints are encoded in binary), the unfolding penalizes the performance of the solvers especially when the bounds are large.
 
@@
 \noindent 
-\emph{Contribution.} In this work, we focus on the class of string constraints with regular membership and string-length function, where the counting operators may occur in regular expressions (called RECL for brevity).
-We propose an automata-theoretical approach for solving RECL constraints.
-Our main idea is to represent the counting operators by registers in automata (as much as possible), instead of unfolding them explicitly.
-Our approach is built upon an automata model called cost-enriched finite automata (CEFA), which was proposed in~\cite{atva2020} to solve string constraints involving the integer data type.
-Moreover, the string-length function can also be modeled by registers in CEFA.
+\emph{Contribution.} In this work, we focus on the class of string constraints with regular membership and string-length function, where the counting operators may occur (called RECL for brevity).
+We make the following contributions:
+\vspace{-0.5mm}
+\begin{itemize}
+  \item We propose an automata-theoretical approach for solving RECL constraints. 
+  Our main idea is to represent the counting operators by registers in cost-enriched finite automata (CEFA, see Section~\ref{sec:automaton} for the definition), instead of unfolding them explicitly.
+The satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA w.r.t.
+a linear integer arithmetic (LIA), which is then transformed to the satisfiability of existential LIA formula tackled by the off-the-shelf SMT solver.
+  % Moreover, the string-length function can also be modeled by register in CEFA.
+Then the satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA with respect to a linear integer arithmetic (LIA) formula whose free variables are registers.
+According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
+  % Thus, the nonemptiness of CEFA w.r.t. LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
+  \item We propose size-reduction techniques to reduce the state space and the number of transitions in CEFA, to achieve better performance.
+It is beneficial since the sizes of LIA formulas depend much on the sizes of CEFA.
+  \item Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
+We implement the algorithm on top of OSTRICH, resulting in a practical string solver called $\ostrichrecl$.
+  \item Finally, we utilize a collection of benchmark suites comprising 48,843 instances in total to evaluate the performance of our tool.
+The result shows that $\ostrichrecl$ solves the most number of instances among all the solvers, with comparable speed (See Table~\ref{tab:results_regcol}).
+In addition, we carry out some detailed experiments, including evaluation of size-reduction techniques  and the experiment of large-counting benchmark.
+The result shows that the size-reduction techniques are effective in practice (See Table~\ref{tab:results_simp}), and $\ostrichrecl$ performance much better than other solvers on large-counting benchmark (See Fig~\ref{fig:table_large_count}).
+  % The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,843 instances, while Z3str3RE, the state-of-the-art solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
+Moreover, the speed of $\ostrichrecl$ is comparable to that of Z3str3RE.
+In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively.
+(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details.)
+\end{itemize}
+\vspace{-0.5mm}
+% We propose an automata-theoretical approach for solving RECL constraints.
+Our main idea is to represent the counting operators by registers in automata (as much as possible) instead of unfolding them explicitly.
+Our approach is built upon cost-enriched finite automata (CEFA), proposed in~\cite{atva2020} to solve string constraints involving the integer data type.
+Moreover, the string-length function can also be modeled by register in CEFA.
 Then the satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA with respect to a linear integer arithmetic (LIA) formula whose free variables are registers of CEFA.
 
-According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
+% According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
 Thus, the nonemptiness of CEFA w.r.t.
 LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers for LIA.
-%
-Because the sizes of LIA formulas depend much on the sizes of CEFA, it is beneficial to reduce the sizes of CEFA, in order to achieve a good performance.
+Because the sizes of LIA formulas depend much on the sizes of CEFA, it is beneficial to reduce the sizes of CEFA to achieve better performance.
 As a result, we propose various techniques to reduce the state space and the number of transitions of CEFA.
 
-The representation of regex-counting and string-length as registers in CEFA, combined with the aforementioned size-reduction, entails an efficient algorithm for solving RECL constraints.
-We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH, called $\ostrichrecl$ for convenience.
-%
-Furthermore, we utilize a collection of benchmark suites, which comprise 48,834 RECL constraints in total, to evaluate the performance of $\ostrichrecl$.
-The collection of benchmark suites includes a widely-used benchmark suite for string constraints, as well as benchmark suites comprising constraints generated from regular expressions in various open source regex libraries.
-%
-%Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contain sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators.
-%
-The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while Z3str3RE, the state-of-the-art best solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
+% Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
+We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH called $\ostrichrecl$ for convenience.
+% Furthermore, we utilize a collection of benchmark suites comprising 48,843 RECL constraints in total to evaluate the performance of $\ostrichrecl$.
+It includes a widely-used benchmark suite for string constraints and benchmark suites comprising constraints generated from regular expressions in various open source regex libraries.
+% %
+% %Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contain sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators.
+% %
+% The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,843 instances, while Z3str3RE, the state-of-the-art best solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
 Moreover, the speed of $\ostrichrecl$ is comparable to that of Z3str3RE.
@@
 
-At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA was introduced.
-This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, regex-counting was unfolded explicitly.
-Moreover, in~\cite{atva2020}, the nonemptiness of CEFA w.r.t.
-LIA formulas was solved by utilizing the nuXmv model checker~\cite{nuxmv}.
+% At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA was introduced.
+This work differs from \cite{atva2020} in the following two aspects: (1) In \cite{atva2020}, regex-counting was unfolded explicitly while this work encodes it to register.
+(2) Moreover, the nonemptiness of CEFA w.r.t.
+LIA formulas was solved using the nuXmv model checker~\cite{nuxmv}.
 In contrast, this work solves it by integrating the techniques of Parikh-image computation and automata-size reduction.
 The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time.
-(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details, where OSTRICH denotes the solver in \cite{atva2020}.)
+(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details.)
 
@@
 \emph{Related work.} 
-We discuss more related work about regexes with counting and real-world regexes in programming languages.  
+We discuss more related work about regexes with counting in programming languages.  
 The determinism of regexes with counting was investigated in~\cite{GGM12,CL15}.
-Counting-set automata were proposed in~\cite{redos_lenka,HS+23} to match a subclass of regexes with counting quickly.
+Counting-set automata were proposed in~\cite{redos_lenka,HS+23} to quickly match a subclass of regexes with counting.
 Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regexes with counting.
-Nevertheless, the nonemptiness problem of these automata was not considered in ~\cite{redos_lenka,HS+23,GKM23}, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
-Real-world regexes in programming languages include features beyond classical regular expressions, e.g.
-the greedy/lazy Kleene star, capturing groups, and back references.
+Nevertheless, the nonemptiness problem of these automata was not considered, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
+Real-world regexes in programming languages include features beyond classical regular expressions, e.g., the greedy/lazy Kleene star, capturing groups, and back references.
 Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
@@
 Furthermore, Z3str3 exposes the structure of theory literals to the DPLL(T) SAT solver's branching heuristic, resulting in smarter decisions during its search.
-Z3Str3 can not solve string constraints (\ref{eq:cvc5_timeout}) as well because the optimization can not avoid the endless unwind of the regular expression.
-To handle the exponential search space of regular expression, automata-based methods were proposed.
+Z3Str3 can not solve string constraints (\ref{eq:cvc5_timeout}) because the optimization can not avoid the endless unwind of the regular expression.
+Automata-based methods were proposed to handle the exponential search space of regular expression.
 One of the automata-based string solver Ostrich\cite{ostrich}\cite{atva2020} encodes string constraints and regular expressions into automata and use the automata theory to solve them.
@@
 But it is inefficient because it is hard to reduce the size of automata.
-When large counting is constrained on a complex sub-regex, like $ \backslash w \{1, 63\}$ where $\backslash w$ is an English character or a number character, the corresponding automaton in Ostrich becomes very large and can not be solved within 60s time limit.
+When large counting is constrained on a complex sub-regex, like $ \backslash w \{1, 63\}$ where $\backslash w$ is an English character or a number character, the corresponding automaton in Ostrich becomes very large.
+It can not be solved within the 60s time limit.
 The reason is that Ostrich syntactically rewrites the counting operator to the union of finite repeatings of the sub-regex.
@@
 Recently, Z3str3 has been extended to BD+23\cite{BD+23} by Berzish et al to handle string constants with regular memberships and length operation effectively.
-It uses automata to formalize the semantic of regular expression and applies several length-aware heuristics.
+It uses automata to formalize the semantics of regular expressions and applies several length-aware heuristics.
 BD+23 can avoid building unsolvable automaton because the length abstraction is directly derived from the regex, not the automaton.
@@
 \subsubsection{Related Work}
-To handle the problems in software verification reasoning about strings and integers, string theories with regular membership predicate and linear length constraints are raised.
+String theories with regular membership predicate and linear length constraints are raised to handle the problems in software verification reasoning about strings and integers.
 String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, BD+23\cite{BD+23}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories.

### 2023-08-18 2023-1-19/sections/overview.tex
setta2023

--- 2023-05-15 2023-1-19/sections/overview.tex
@@
 
-In this section, we utilize the string constraint in Equation~(\ref{eqn-running}) to illustrate the approach in this work.
+In this section, we utilize the string constraint in Equation~(\ref{eqn-running}) to illustrate the approach in our work.
 
@@
 
-We first construct an automaton for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
-We introduce three registers, say $r_1, r_2, r_3$, to represent the three counting operators.
+First, we construct an CEFA for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
+Three registers are introduced, say $r_1, r_2, r_3$, to represent the three counting operators;
 %Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
-Then we construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, and add the updates of registers (e.g.
-$r_1++$ for incrementing $r_1$) to transitions, resulting in a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a).
+the nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$ is constructed; the updates of registers is added to the transitions of the NFA; the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$, resulting in a CEFA $\aut_1$ illustrated in Figure~\ref{fig:overview}(a).
+$r_1++$ means that we increment the value of $r_1$ by one after running the transition.
 %Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.
 %Moreover, $r_0$ is incremented in all the three self-loops. 
-Furthermore, the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$. 
-A string $w$ is accepted by $\aut_1$ if, when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition.
-Note that we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
-Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no counting operators (Kleene plus is not seen as a counting operator here).
-Finally, we construct the third CEFA $\aut_3$ (see Figure~\ref{fig:overview}(c)), where a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$.
-(See Section~\ref{subsec:regex2cefa} for more details about the construction of CEFA.)
+A string $w$ is accepted by $\aut_1$ if, when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, reaching a final state $q$ in the end, and the resulting values of the three registers, say $v_1,v_2,v_3$, satisfy the accepting condition.
+In addition, we construct other two CEFAs $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)) and $\aut_3$ for string length function (see Figure~\ref{fig:overview}(c)).
+In $\aut_3$, a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$ (See Section~\ref{subsec:regex2cefa} for more details about the construction of CEFA.) Note that we represent the counting operators symbolically by registers instead of unfolding them explicitly.
 %where the register $r_0$ is used to record the length of strings.
@@
 %we remove the $\varepsilon$-transitions of $\aut_1$, resulting into $\aut'_1$, 
-we construct $\aut_1 \cap \aut_2 \cap \aut_3$, that is, the intersection (aka product) of $\aut_1$, $\aut_2$, and $\aut_3$, as illustrated in Figure~\ref{fig:overview:product}(a), where the states from which no final states are reachable are removed.
+we construct $\aut_1 \cap \aut_2 \cap \aut_3$, that is, the intersection (aka product) of $\aut_1$, $\aut_2$, and $\aut_3$, as illustrated in Figure~\ref{fig:overview:product}(a), where the states can not reach the final states are removed.
 %Furthermore, we add one special register, say $r_0$, to record the length of strings. Note that $r_0$ is incremented in all transitions. 
 %In $\aut_1 \cap \aut_2 \cap \aut_3$, the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
-For technical convenience, we also think of the updates on the values of registers in transitions as vectors $(v_1, v_2, v_3, v_4)$, where $v_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
-For instance, the transitions corresponding to the self-loop around $(p_0, q_0, q'_0)$ are thought as $((p_0, q_0, q'_0), a', (p_0, q_0, q'_0), (1,0,0,1))$ with $a' \in \Sigma \setminus \{a\}$, since $r_1$ and $r_4$ are incremented in these transitions.
-With the updates thought of as vectors, the resulting CEFA is illustrated in Figure~\ref{fig:overview:product}(b).
+For technical convenience, we also think of the updates of registers in transitions as vectors $(u_1, u_2, u_3, u_4)$, where $u_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
+For instance, the transitions corresponding to the self-loop around $(p_0, q_0, q'_0)$ are thought as $((p_0, q_0, q'_0), a', (p_0, q_0, q'_0), (1,0,0,1))$ with $a' \in \Sigma \setminus \{a\}$, since $r_1$ and $r_4$ are incremented by one in these transitions.
+After considering the updates of registers as vectors, the CEFA is like Figure~\ref{fig:overview:product}(b).
 %the transitions corresponding to the self-loop is $(q, a', q', (1,1,0,0))$ with $a' \in \Sigma \setminus \{a\}$.
@@
   \label{fig:overview:product}
-\vspace{-6mm}
+\vspace{-3mm}
 \end{figure}
@@
 Therefore, the vector for this transition is $(1, 0, 0, 0)$.
-The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut_1 \cap \aut_2 \cap \aut_3$, producing a cost $(v_1, v_2, v_3, v_4)$ that satisfies $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $v_4 > 120$.
-It is not hard to observe that the nonemptiness of $\aut_1 \cap \aut_2 \cap \aut_3$ w.r.t.
-$\varphi \equiv r_4 > 120$ is independent of the characters of $\aut_1 \cap \aut_2 \cap \aut_3$.
-Therefore, the characters in $\aut_1 \cap \aut_2 \cap \aut_3$ can be ignored, resulting into an NFA $\cB$ over the alphabet $\costset$ (see Figure~\ref{fig:overview:product:reduced}(a)), where $\costset$ is the set of vectors from $\Int^4$ occurring in the transitions of $\aut_1 \cap \aut_2 \cap \aut_3$.
-Then the nonemptiness of $\aut_1 \cap \aut_2 \cap \aut_3$ w.r.t.
-$\varphi \equiv r_4 > 120$ is reduced to the problem of deciding whether there exists $w' \in \costset^*$ such that it is accepted by $\cB$ and its Parikh image (i.e.
-numbers of occurrences of characters), say $\eta_{w'}: \costset \rightarrow \Nat$, satisfies that $1 \le v'_1 \le 60\wedge 1 \le v'_2 \le 60 \wedge 0 \le v'_3 \le 60$ and $v'_4 > 120$, where $\myvec{v'} = (v'_1, v'_2, v'_3, v'_4) =  \sum \limits_{\myvec{v} \in \costset} \eta_{w'}(\myvec{v}) \myvec{v}$.
-Intuitively, $\myvec{v'}$ here is a weighted sum of vectors $\myvec{v} \in \costset$, where the weight for $\myvec{v}$ is the number of occurrences of $\myvec{v}$ in $w'$.
+Finally, The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut\equiv \aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, abbreviated as $\sf NE_{\varphi}(\aut)$.
+That is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut$, producing resulting registers values $(v_1, v_2, v_3, v_4)$ that satisfy $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $\varphi$.
+It is not hard to observe that $\sf NE_{\varphi}(\aut)$ is independent of the characters of $\aut$.
+Therefore, the characters in $\aut$ can be ignored, resulting into an NFA $\cB$ over the alphabet $\costset$, where $\costset$ is the set of vectors from $\Int^4$ occurring in the transitions of $\aut$ (see Figure~\ref{fig:overview:product:reduced}(a)).
+Then $\sf NE_{\varphi}(\aut)$ is reduced to the problem of deciding whether there exists $w' \in \costset^*$ such that it is accepted by $\cB$ and its Parikh image (i.e., numbers of occurrences of characters), say $\eta_{w'}: \costset \rightarrow \Nat$, satisfies that $1 \le v'_1 \le 60\wedge 1 \le v'_2 \le 60 \wedge 0 \le v'_3 \le 60$ and $v'_4 > 120$, where $(v'_1, v'_2, v'_3, v'_4) =  \sum \limits_{\myvec{v} \in \costset} \eta_{w'}(\myvec{v}) \myvec{v}$ for each $\myvec{v}\in \costset$.
+Intuitively, $(v'_1, v'_2, v'_3, v'_4)$ is a weighted sum of vectors $\myvec{v} \in \costset$, where the weight is the number of occurrences of $\myvec{v}$ in $w'$.
 (See Section~\ref{subsec:cefadec} for more detailed arguments.)
@@
 From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi_\cB(\anivar_1, \cdots, \anivar_m)$ can be computed to define the Parikh image of strings that are accepted by $\cB$, where $\anivar_1, \cdots, \anivar_m$ are the integer variables to denote the number of occurrences of $\myvec{v_1}, \cdots, \myvec{v_m}$.
-Therefore, the satisfiability of the string constraint in~(\ref{eqn-running}) is reduced to the satisfiability of the following existential LIA formula
+Therefore, the satisfiability of the string constraint in~(\ref{eqn-running}) is reduced to the satisfiability of the following existential LIA formula,
 \begin{equation}\label{eqn-LIA}
@@
 %where for each $k \in [m]$, $v_k = (v_{k,1}, v_{k,2}, v_{k, 3}, v_{k, 4})$ is the vector of updates on the registers $r_0, r_1, r_2, r_3$ in the transition $\tau_k$, and $\alpha(r_0, r_1, r_2, r_3)$ is the accepting condition in $\aut_1 \times \aut_2$.
-Finally, the satisfiability of the LIA formula in~(\ref{eqn-LIA}) can be solved by the off-the-shelf SMT solvers for LIA.
+which can be solved by the off-the-shelf SMT solvers.
 %Since the satisfiability of LIA formulas can be solved by the off-the-shelf SMT solvers for LIA, the satisfiability of the string constraint in~(\ref{eqn-running}) can thus be solved.
 
-Nevertheless, the algorithm illustrated above is insufficient to solve the string constraints with regex-counting and string-length efficiently, since the sizes of NFA obtained from CEFA can still be big, resulting  in  the LIA formulas of big sizes, while the satisfiability of existential LIA formulas is NP-complete (see e.g.
-\cite{Haase18}).
-To tackle this issue, we propose techniques to reduce the sizes of NFA over the alphabet $\costset$.
+Nevertheless, the algorithm illustrated above is insufficient when regexes are complicated.
+The size of $\cB$ can still be big, causing the resulted existential LIA formulas are of big sizes and hard to be solved (NP-complete \cite{Haase18}).
+To tackle this issue, we propose techniques to reduce the sizes of $\cB$ over the alphabet $\costset$.
 
@@
 
-Specifically, to reduce the sizes of the NFA, we determinize $\cB$, apply the minimization algorithm to the resulting deterministic finite automaton (DFA), and obtain a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
+Specifically, to reduce the sizes of the $\cB$, we determinize $\cB$ and apply the minimization algorithm to the resulting deterministic finite automaton (DFA), obtaining a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
-Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experiment results show us that they do reduce the sizes of NFA constructed from the regular expressions in practice.
-%(See Table~\ref{tab:results_heuristics}, where adding the size-reduction techniques reduces the running time for 46.4\%.) 
-%thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g.
-$\{a\}, \{b\}, \{c\}, \Sigma \setminus \{a, b, c\}$, in the transitions of $\aut_1 \times \aut_2$.}.
-%Then we reinterpret $\cC$ as a CEFA with the acceptance condition $\alpha(r_0, r_1, r_2, r_3)$. 
-%Finally, we compute an LIA formula $\psi'(i_1, \cdots, i_6)$ from $\cC$ and reduce the satisfiability of the string constraint in~(\ref{eqn-running}) to the satisfiability of the following existential LIA formula
-%\begin{equation}\label{eqn-LIA-reduced}
-%\psi'(i_1, \cdots, i_6) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [6]}  i_k v'_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
-%\end{equation}
-%where $\myvec{v'_{k}}=(v'_{k,1}, v'_{k,2}, v'_{k,3}, v'_{k,4})$ is the vector of updates of registers of the transition $\tau'_k$ for $k \in [6]$.
+The evaluation in section \cite{sec} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.
 
-%Furthermore, we can reduce the number of registers by merging several registers into one, if they are updated with the same value in every transition of $\aut_1 \times \aut_2$.
-
-At last, for the string constraints that are satisfied by a collection of strings whose lengths are small, computing LIA formulas from NFA and solving them by SMT solvers are still expensive.  
-Therefore, we introduce a heuristic of searching for solutions based on \emph{under approximations}, before computing LIA formulas and solving them by SMT solvers.
-More precisely, we enforce a constant upper bound $B$ on the lengths of strings and search for a $B$-bounded satisfiable assignment, that is, a satisfiable assignment where the lengths of strings are bound by $B$.
-Initially, we set $\ell$, an integer variable to denote the lengths of strings, to $1$.
-If there does not exist an $\ell$-bounded satisfiable assignment, then we let $\ell:=\ell+1$ and continue the search, until finding a satisfiable assignment or reaching the bound $B$.
-For instance, if we remove $|x| > 120$ from the string constraint~(\ref{eqn-running}), then the resulting constraint is satisfiable.
-Setting the bound $B$ to $3$ is sufficient to find a solution for the string constraint in~(\ref{eqn-running}), which is witnessed by the following accepting run of $\cC$: $q^{\prime\prime}_0 \xrightarrow{(1,0,0,1)} q^{\prime\prime}_0 \xrightarrow{(0,1,0,1)} q^{\prime\prime}_1 \xrightarrow{(0,0,0,1)} q^{\prime\prime}_2$.
-Note that the accepting run produces $(1,1,0,3)$, a vector of register values,  which satisfies $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$.
-(See Section~\ref{subsec:cefadec} for more details.)
-
-We implement all the aforementioned techniques on top of OSTRICH, resulting into a solver $\ostrichrecl$.
+We implement all the aforementioned techniques on the top of OSTRICH, resulting in a solver $\ostrichrecl$.
 It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art string solvers are incapable of solving it within 300 seconds.

### 2023-08-18 2023-1-19/sections/preliminaries.tex
setta2023

@@
 For $n \in \Nat$ with $n \ge 1$, $[n]$ denotes $\{1, \ldots, n\}$; for $m,n \in \Nat$ with $m \le n$,  $[m, n]$ denotes $\{ i \in \Nat \mid m \le i \le n \}$.
-Throughout the paper, $\Sigma$ is a finite alphabet, ranged over by $a,b,\ldots$.
+Throughout the paper, $\Sigma$ is a finite alphabet, ranged over $a,b,\ldots$.
 
-For a function $f$ from $X$ to $Y$ and $X' \subseteq X$, we use $\prj_{X'}(f)$ to denote the restriction (aka projection) of $f$ to $X'$, that is, $\prj_{X'}(f)$ is a function from $X'$ to $Y$, and $\prj_{X'}(f)(x') = f(x')$ for each $x' \in X'$.
+For a function $f$ from $X$ to $Y$ and $X' \subseteq X$, we use $\prj_{X'}(f)$ to denote the restriction (aka projection) of $f$ to $X'$, that is, $\prj_{X'}(f)$ is the function from $X'$ to $Y$, and $\prj_{X'}(f)(x') = f(x')$ for each $x' \in X'$.
 
 \medskip
-\noindent \emph{Strings and languages.}
+\noindent 
+\emph{Strings and languages.}
 %\paragraph*{Strings and languages.}
@@
 Moreover, the class of regular languages is closed under union, intersection, concatenation, Kleene star, complement, and language difference \cite{HU79}.
-In the sequel, we recall the constructions of NFA corresponding to these language operations.
-Let $\NFA_1 = (Q_1, \Sigma, \delta_1, I_1, F_1)$ and $\NFA_2 = (Q_2, \Sigma, \delta_2, I_2, F_2)$ be two NFA such that $Q_1 \cap Q_2 = \emptyset$.
-\begin{itemize}
-\item The union of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cup \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q'= Q_1 \cup Q_2$, $\delta' = \delta_1 \cup \delta_2$, $I' = I_1 \cup I_2$, and $F'=F_1 \cup F_2$.
-%
-\item The intersection of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cap \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, and $\delta' = \{((q_1, q_2), a, (q'_1, q'_2)) \mid (q_1, a, q'_1) \in \delta_1, (q_2, a, q'_2) \in \delta_2\}$.
-%
-\item The concatenation of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \concat \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\delta' = \delta_1 \cup \delta_2 \cup \{(q_1, a, q_2) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
-%
-\item The Kleene star of $\NFA_1$, denoted by $\NFA_1^*$, is defined as $(Q'_1, \Sigma, \delta'_1, I'_1, F'_1)$, where $Q'_1 = Q_1 \cup \{q_0\}$ with $q_0 \not \in Q_1$, $I'_1 = \{q_0\}$, $F'_1= F_1 \cup \{q_0\}$, $\delta'_1 = \delta_1 \cup \{(q_0, a, q'_1)  \mid \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\} \cup \{(q_1, a, q'_1) \mid q_1 \in F_1, \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\}$.
-%
-\item The complement of $\NFA_1$, denoted by $\overline{\NFA_1}$, is defined as $(Q'_1, \Sigma, \delta'_1, q'_0, Q'_1 \setminus F'_1)$, where  $(Q'_1, \Sigma, \delta'_1, q'_0, F'_1)$ is the DFA obtained from $\NFA_1$ by subset construction.
-%
-\item The language difference of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \setminus \NFA_2$, is defined as $\NFA_1 \cap \overline{\NFA_2}$.
-\end{itemize}
+The constructions of NFA corresponding to these language operations are list in \ref{appendix:cefa}
+% In the sequel, we recall the constructions of NFA corresponding to these language operations. 
+% Let $\NFA_1 = (Q_1, \Sigma, \delta_1, I_1, F_1)$ and $\NFA_2 = (Q_2, \Sigma, \delta_2, I_2, F_2)$ be two NFA such that $Q_1 \cap Q_2 = \emptyset$. 
+% \begin{itemize}
+% \item The union of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cup \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q'= Q_1 \cup Q_2$, $\delta' = \delta_1 \cup \delta_2$, $I' = I_1 \cup I_2$, and $F'=F_1 \cup F_2$.
+% %
+% \item The intersection of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cap \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, and $\delta' = \{((q_1, q_2), a, (q'_1, q'_2)) \mid (q_1, a, q'_1) \in \delta_1, (q_2, a, q'_2) \in \delta_2\}$.
+% %
+% \item The concatenation of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \concat \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\delta' = \delta_1 \cup \delta_2 \cup \{(q_1, a, q_2) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+% %
+% \item The Kleene star of $\NFA_1$, denoted by $\NFA_1^*$, is defined as $(Q'_1, \Sigma, \delta'_1, I'_1, F'_1)$, where $Q'_1 = Q_1 \cup \{q_0\}$ with $q_0 \not \in Q_1$, $I'_1 = \{q_0\}$, $F'_1= F_1 \cup \{q_0\}$, $\delta'_1 = \delta_1 \cup \{(q_0, a, q'_1)  \mid \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\} \cup \{(q_1, a, q'_1) \mid q_1 \in F_1, \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\}$.
+% %
+% \item The complement of $\NFA_1$, denoted by $\overline{\NFA_1}$, is defined as $(Q'_1, \Sigma, \delta'_1, q'_0, Q'_1 \setminus F'_1)$, where  $(Q'_1, \Sigma, \delta'_1, q'_0, F'_1)$ is the DFA obtained from $\NFA_1$ by subset construction.
+% %
+% \item The language difference of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \setminus \NFA_2$, is defined as $\NFA_1 \cap \overline{\NFA_2}$.
+% \end{itemize}
 
@@
 \emph{Linear integer arithmetic and Parikh images.}
-We will also use standard quantifier-free/existential \emph{linear integer arithmetic} (LIA) formulas, which typically range over by $\phi, \varphi$. 
-For a set $\mathfrak{X}$ of variables, we use $\Phi(\mathfrak{X})$ to denote the set of quantifier-free LIA formulas whose free variables are from $\mathfrak{X}$. 
-For convenience, we use $\varphi(\vec{\anivar})$ with $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ to denote an LIA formula $\varphi$ whose free variables are from $\{\anivar_1, \cdots, \anivar_k\}$.
-For an LIA formula $\varphi(\vec{\anivar})$ with $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ and $\myvec{t} = (t_1, \cdots, t_k)$ be a tuple of integer terms, we use $\varphi[\myvec{t}/\myvec{\anivar}]$ to denote the formula obtained by replacing (simultaneously) $\anivar_i$ with $t_i$ for every $i \in [k]$.
+We use standard existential \emph{linear integer arithmetic} (LIA) formulas, which
+ typically range over $\psi, \varphi, \Phi, \alpha$. 
+For a set $\mathfrak{X}$ of variables, we use $\psi/\varphi/\Phi/\alpha(\mathfrak{X})$ to denote the set of existential LIA formulas whose free variables are from $\mathfrak{X}$. 
+For example, we use $\varphi(\vec{\anivar})$ with $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ to denote an LIA formula $\varphi$ whose free variables are from $\{\anivar_1, \cdots, \anivar_k\}$.
+For an LIA formula $\varphi(\vec{\anivar})$, we use $\varphi[\myvec{t}/\myvec{\anivar}]$ to denote the formula obtained by replacing (simultaneously) $\anivar_i$ with $t_i$ for every $i \in [k]$ where $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ and $\myvec{t} = (t_1, \cdots, t_k)$ are tuples of integer terms.
 %For convenience, we assume a set $X$ of variables is a vector. 
@@
 
-At last, we recall a result about Parikh images of NFA. 
+At last, we recall the result about Parikh images of NFA. 
 For each $a \in \Sigma$, let $\anivarz_a$ be an integer variable. Let $\fZ_\Sigma$ denote the set of integer variables $\anivarz_a$ for $a \in \Sigma$. 
 Let $\NFA$ be an NFA over the alphabet $\Sigma$. Then 
-we say that an LIA formula $\varphi(\fZ_\Sigma)$ defines the Parikh image of $\NFA$, if $\{\eta: \Sigma \rightarrow \Nat \mid \varphi[(\eta(a) /\anivarz_a)_{a \in \Sigma}] \mbox{ is true}\} = \parikh(\NFA)$.
+we say that an LIA formula $\psi(\fZ_\Sigma)$ defines the Parikh image of $\NFA$, if $\{\eta: \Sigma \rightarrow \Nat \mid \psi[(\eta(a) /\anivarz_a)_{a \in \Sigma}] \mbox{ is true}\} = \parikh(\NFA)$.
 
 \begin{theorem}[\cite{SSMH04}]\label{thm-nfa-parikh}
-Given an NFA $\NFA$,  an existential LIA formula $\varphi_\NFA(\fZ_\Sigma)$ can be computed in linear time that defines the Parikh image of $\NFA$.
+Given an NFA $\NFA$,  an existential LIA formula $\psi_\NFA(\fZ_\Sigma)$ can be computed in linear time that defines the Parikh image of $\NFA$.
 \end{theorem}
-
+\vspace{-3mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-18 2023-1-19/sections/recl.tex
setta2023

@@
 %\subsubsection{Syntax}
-In the sequel, we define string constraints with regex-counting and string-length functions (abbreviated as RECL).
+In the sequel, we define the string constraints with regex-counting and string-length functions, i.e., \textbf{RE}gex-\textbf{C}ounting \textbf{L}ogic (abbreviated as RECL).
 The syntax of RECL is defined by the rules in Figure~\ref{fig:syntax}, where $x$ is a string variable, $\anivar$ is an integer variable, $a$ is a character from an alphabet $\Sigma$, and $m, n$ are integer constants.
@@
 %
-A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and characters $a$ by using concatenation  $\cdot$, union $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
-An integer term is built from constants $n$, variables $\anivar$, and string lengths $|x|$, by operators $+$ and $-$.
+A regular expression $\regex$ is built from $\emptyset$, the empty string $\epsilon$, and the character $a$ by using concatenation  $\cdot$, union $+$, Kleene star $^*$, intersection $\cap$, complement $\bar{\mbox{ }}$, difference $\setminus$, counting $^{\{m,n\}}$ or $^{\{m,\infty\}}$.
+An integer term is built from constants $n$, variables $\anivar$, and string lengths $|x|$ by operators $+$ and $-$.
 % 
@@
 \begin{figure}[h]
-\vspace{-3mm}
   \centering
@@
   \caption{Syntax of RECL }\label{fig:syntax}
-\vspace{-3mm}
+\vspace{-4mm}
 \end{figure}

### 2023-08-18 2023-1-19/sections/abstract.tex
some little errors

@@
 
-%\documentclass{standalone}
-%\begin{document}
-
 Regular expressions (regex for short) and string-length function are widely used in string-manipulating programs.
-%Solving string constraints involving regular membership and string-length function has been widely investigated. 
-Counting is a frequently used feature in regexes that counts the number of sub-patterns matchings.
-The state-of-the-art string solvers are incapable of solving string constraints with regex-counting and string-length efficiently, especially when the counting bounds are large.
+Counting is a frequently used feature in regexes that counts the number of matchings of sub-patterns.
+The state-of-the-art string solvers are incapable of solving string constraints with regex-counting and string-length eﬀiciently, especially when the counting and length bounds are large. 
 In this work, we propose an automata-theoretic approach for solving such a class of string constraints. 
-%
 The main idea is to model the counting operators symbolically by registers in automata instead of unfolding them explicitly, thus alleviating the state explosion problem.
-%
-Moreover, the string-length function is modeled by register as well. 
-%Since Parikh images of automata can be defined by linear integer arithmetic formulas, 
-As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which off-the-shelf SMT solvers can then solve.
-%
-%we extract linear integer arithmetic formulas from automata, which encode the constraints on the values of registers, and utilize the off-the-shelf SMT solvers to solve the linear integer arithmetic constraints.
-%
-To improve the performance further, we propose techniques to reduce automata sizes.
-% we propose state reduction techniques and under-approximation to improve the performance further. 
-We implement the algorithms and validate our approach on 48,843 benchmark instances. The experimental results show that 
-our approach can solve more instances than other solvers at a comparable or faster speed.
-% performance of this approach compared against the state-of-the-art string solvers.
-
-%Regular expression with repetition frequently appears in the real world, such as $(ab)\{1, 100\}$. However, state-of-art string
-%solvers can not efficiently solve string constraints with repetition bounds,
-%especially when the repetition bounds are large. This paper focuses on
-%string logic containing regular membership predicate with repetition
-%and linear integer constraints on string length. Repetition is captured
-%by cost-enriched finite automaton(CEFA), whose transitions have symbolic updates of integers limited by linear arithmetic. We propose a new systematic algorithm based on CEFA, and heuristic ways
-%like under-approximation and symbolic-aware simplification are used to
-%accelerate. We implement a powerful string solver OstrichCEA and
-%evaluate it on instances from the real world and other typical benchmarks.
-%The experiment result shows superiority.
-
-%\keywords{Rgular Expressions, Counting, Length, Automata, Registers, Linear Integer Arithmetic}
-%\end{document}
+Moreover, the string-length function is modeled by a register as well.
+As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which the off-the-shelf SMT solvers can then solve.
+To improve the performance further, we propose techniques to reduce automata sizes. We implement the algorithms and validate our approach on 48,843 benchmark instances. 
+The experimental results show that our approach can solve more instances than the other solvers, at a comparable or faster speed, especially when the counting and length bounds are large.

### 2023-08-18 2023-1-19/sections/introduction.tex
some little errors

@@
 
-Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting bounds are large.
+Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting bounds and length bounds are large.
 For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 300 seconds, and Z3 can not solve it within 120 seconds.

### 2023-08-18 2023-1-19/sections/overview.tex
some little errors

@@
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
-The evaluation in section \cite{sec} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.
+The evaluation in Table~\ref{tab:results_simp} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.
 

### 2023-08-21 2023-1-19/sections/implementation.tex
some little errors
some updates

@@
 We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{Ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
-Then we do experiments on two benchmark suites to evaluate the performance of $\ostrichrecl$, and carry out detailed experiments including evaluation of size-reduction techniques and the experiment of large-counting benchmark.
+Then we do experiments on two benchmark suites to evaluate the performance of $\ostrichrecl$, and carry out detailed experiments, including the evaluation of size-reduction techniques and the experiment of large-counting benchmark.
 In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
@@
 There are 8,215 instances in the AutomatArk suite here.
-Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, conjunctions of regular membership queries generated out of regular expressions from \cite{automatark}.
-%Only 8,751 ones that contain counting operators out of 19,979 instances. 
+Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances, conjunctions of regular membership queries generated out of regular expressions from \cite{automatark}.
+%Only 8,751 contain counting operators out of 19,979 instances. 
 Moreover, only 5\% of them include non-register-representable regexes among the 48,843 instances.
@@
       \import{tables}{table_regcol.tex}
-      \caption{Overall Experiment results,\\ with timeout = 60 seconds}
+      \caption{Overall experiment results,\\ with timeout = 60 seconds.}
       \label{tab:results_regcol}
@@
       \import{tables}{table_simp.tex}
-      \caption{Simplification technique evaluation, with timeout = 60 seconds}
+      \caption{Simplification technique evaluation, with timeout = 60 seconds.}
       \label{tab:results_simp}
   \end{subtable}
+  \vspace{-6mm}
   \caption{Experiments on RegCoL and AutomatArk benchmark suites}
@@
 The overall experiment results are in Table~\ref{tab:results_regcol}.
-Note that we take the result of CVC5 as the ground truth\footnote{At first we used the majority vote between all results of the solvers as the ground truth, but solvers of z3 family outputed some wrong results(verified by us manually), causing the ground truth to be incorrect.} and the soundness error also be counted as unknown.
+Note that we take the result of CVC5 as the ground truth\footnote{At first we used the majority vote between all results of the solvers as the ground truth, but solvers of z3 family output some wrong results(verified by us manually), causing the ground truth to be incorrect.}.
 We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
@@
 %
-Moreover, our solver $\ostrichrecl$ is the second fastest solver and its average time on each instance is closed to the fastest solver Z3str3RE (\textbf{1.93}/1.62 s).
+Moreover, our solver $\ostrichrecl$ is the second fastest solver, and its average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93}/1.62 s).
 \vspace{-3mm}
@@
 We evaluate the simplification techniques by comparing the performance of $\ostrichrecl$ with and without the simplification techniques.
-Moreover, we also encode the $\cefadec$ problem to infinite state transition system and solve it using \textsc{nuXmv}\cite{nuxmv}.
+Moreover, we also encode the $\cefadec$ problem to an infinite state transition system and solve it using \textsc{nuXmv}\cite{nuxmv}.
 % \begin{table}[ht]
@@
 The evaluation results of simplification techniques are in Table~\ref*{tab:results_simp}.
-We can see that compared to $\ostrichrecl$ without simplification techniques, $\ostrichrecl$ with simplification techniques solves \textbf{1,503 more} instances and is \textbf{2.21$\times$} faster.
+Compared to $\ostrichrecl$ without simplification techniques, $\ostrichrecl$ with simplification techniques solves \textbf{1,503 more} instances and is \textbf{2.21$\times$} faster.
 Moreover, compared with the techniques using \textsc{nuxmv}, $\ostrichrecl$ with simplification techniques solves \textbf{1,798 more} instances and is \textbf{3.13$\times$} faster.
@@
 \subsection{Large-Counting Experiment Results}
-The distribution of upper bound in RegCoL and AutomatArk suites is showed in Fig~\ref{fig:count_distri}, whose horizontal axis is the value of upper bound and vertical axis is the number of occurrences of it.
+The distribution of upper bounds of counting in RegCoL and AutomatArk suites is shown in Fig~\ref{fig:count_distri}, whose horizontal axis is the value of the upper bound and vertical axis is the number of occurrences.
 The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$).
-Although the upper bounds of most counting operators are less than 50, there are still about two thousands of them are greater than 50.
-We extract these instances with counting upper bound greater than 50 (1,969 instances in total).
-Moreover, We change the length constraint to $|x| > 200$ (which is $|x| > 10$ in overall experiment), to make the number of $sat$ result more closed to that of $unsat$.
+Although most upper bounds of counting operators are less than 50, about two thousand are still greater than 50.
+We extract instances with upper bounds greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total).
+Moreover, We change the length constraint of each instance to $|x| > 200$ (which is $|x| > 10$ in the overall experiment), to make the suite more balanced.
 \vspace{-5mm}
@@
     \vspace{4.5mm}
-    \caption{Large counting experiment, \\with timeout = 60 seconds}
+    \caption{Large-counting experiment, \\with timeout = 60 seconds.}
     \label{fig:table_large_count}
   \end{subfigure}
-  \caption{Analysis of dataset and large counting experiment}
+  \vspace{-2mm}
+  \caption{Analysis of dataset and large-counting experiment.}
 \end{figure}
-\vspace{-7mm}
+\vspace{-5mm}
 
@@
 %   \end{center}
-%   \caption{Large counting experiment, with timeout = 60 seconds}
+%   \caption{Large-counting experiment, with timeout = 60 seconds}
 %   \label{tab:results_simp}

### 2023-08-21 2023-1-19/sections/introduction.tex
some updates

--- 2023-08-18 2023-1-19/sections/introduction.tex
@@
 
-In modern programming languages, such as JavaScript, Python, Java, and PHP, the string data type plays a crucial role. 
+The string data type plays a crucial role in modern programming languages, such as JavaScript, Python, Java, and PHP. 
 String manipulations are error-prone and could even give rise to severe security vulnerabilities (e.g. \ cross-site scripting, aka XSS). 
@@
 
-Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting bounds are large.
+Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting and length bounds are large.
 For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 300 seconds, and Z3 can not solve it within 120 seconds.
@@
 For instance, $a^{\{1, 4\}}$ is unfolded into $a(\varepsilon + a + aa + aaa)$ and $a^{\{2,\infty\}}$ is unfolded into $aaa^{*}$.
-Since the unfolding incurs an exponential blow-up on the sizes of constraints (assuming that the counting in string constraints are encoded in binary), the unfolding penalizes the performance of the solvers especially when the bounds are large.
+Since the unfolding incurs an exponential blow-up on the sizes of constraints (assuming that the counting in string constraints are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the bounds are large.
 
@@
   \item Finally, we utilize a collection of benchmark suites comprising 48,843 instances in total to evaluate the performance of our tool.
-The result shows that $\ostrichrecl$ solves the most number of instances among all the solvers, with comparable speed (See Table~\ref{tab:results_regcol}).
-In addition, we carry out some detailed experiments, including evaluation of size-reduction techniques  and the experiment of large-counting benchmark.
-The result shows that the size-reduction techniques are effective in practice (See Table~\ref{tab:results_simp}), and $\ostrichrecl$ performance much better than other solvers on large-counting benchmark (See Fig~\ref{fig:table_large_count}).
+The result shows that $\ostrichrecl$ solves the most instances among all the solvers, with comparable speed (See Table~\ref{tab:results_regcol}).
+In addition, we carry out some detailed experiments, including the evaluation of size-reduction techniques and the experiment of large-counting benchmarks.
+The result shows that the size-reduction techniques are effective in practice (See Table~\ref{tab:results_simp}), and $\ostrichrecl$ performs much better than other solvers on the large-counting benchmark (See Fig~\ref{fig:table_large_count}).
   % The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,843 instances, while Z3str3RE, the state-of-the-art solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).

### 2023-08-30 2023-1-19/sections/abstract.tex
some updates
add files

@@
-%!TEX root = ../main.tex
-
 Regular expressions (regex for short) and string-length function are widely used in string-manipulating programs.
@@
 The state-of-the-art string solvers are incapable of solving string constraints with regex-counting and string-length eﬀiciently, especially when the counting and length bounds are large. 
-In this work, we propose an automata-theoretic approach for solving such a class of string constraints. 
-The main idea is to model the counting operators symbolically by registers in automata instead of unfolding them explicitly, thus alleviating the state explosion problem.
+In this work, we propose an automata-theoretic approach for solving such class of string constraints. 
+The main idea is to symbolically model the counting operators by registers in automata instead of unfolding them explicitly, thus alleviating the state explosion problem.
 Moreover, the string-length function is modeled by a register as well.
 As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which the off-the-shelf SMT solvers can then solve.
-To improve the performance further, we propose techniques to reduce automata sizes. We implement the algorithms and validate our approach on 48,843 benchmark instances. 
-The experimental results show that our approach can solve more instances than the other solvers, at a comparable or faster speed, especially when the counting and length bounds are large.
+To improve the performance further, we propose simplification techniques to reduce automata sizes. We implement the algorithms and validate our approach on 48,843 benchmark instances. 
+The experimental results show that our approach can solve more instances than the state-of-the-art solvers, at a comparable or faster speed, especially when the counting and length bounds are large.
+
+%\keywords{Rgular Expressions, Counting, Length, Automata, Registers, Linear Integer Arithmetic}
+%\end{document}

### 2023-08-30 2023-1-19/sections/implementation.tex
some updates
add files

@@
 %\begin{document}
-
-We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{Ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
-Then we do experiments on two benchmark suites to evaluate the performance of $\ostrichrecl$, and carry out detailed experiments, including the evaluation of size-reduction techniques and the experiment of large-counting benchmark.
-In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
+In this section, we list our experimental results.
+We first present the overall experiment results on RegCoL and AutomatArk benchmark suites.
+Then we evaluate the simplification techniques and large-counting experiment results.
 
@@
 
-\vspace{-3mm}
+\vspace{-2mm}
 \subsection{Benchmark Suites and Experiment Setup}\label{sec:bench}
-\vspace{-2mm}
+\vspace{-1mm}
 
-Our experiments utilize two benchmark suites, namely, RegCoL and AutomatArk. In total, there are 48,843 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.
+Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}. There are 48,843 instances in total, and all benchmark instances are in SMTLIB2 format.
 
@@
 \noindent
-\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite.
-These constraints are generated by extracting regular expressions with counting operators from the open source regex library \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form
-$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$
-where $\overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is a regular expression that sanitizes all occurrence of special characters $<$, $>$, $'$, $''$, or $\&$.
+\emph{RegCoL benchmark suite.} There are 40,628 RECL instances in the RegCoL suite.
+These instances are generated by extracting regexes with counting operators from the open source regex library \cite{regex_lingua_franca,redos_lenka} and manually constructing a RECL constraint $x \in e \wedge x \in e_{sani} \wedge |x| > 10$ for each regex $e$,
+where $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is a regular expression that sanitizes all occurrence of special characters $<$, $>$, $'$, $''$, or $\&$.
 The artificial construction is meaningful because the special characters are offensive.
-For instance, they are widely used in client-side attacks like XSS\cite{malware_detection_3_kudzu}\cite{CCH+18}.
+For instance, they are widely used in client-side attacks like XSS\cite{malware_detection_3_kudzu,CCH_18}.
 %We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
+\vspace{-0.1mm}
 
@@
 \emph{AutomatArk benchmark suite.}
-The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable).
-There are 8,215 instances in the AutomatArk suite here.
-Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances, conjunctions of regular membership queries generated out of regular expressions from \cite{automatark}.
+The AutomatArk benchmark suite is adapted from the AutomatArk suite \cite{z3str3re} by picking out the string constraints containing counting operators.
+We add length constraint $|x| > 10$ for each string variable $x$ because there is no original length constraints.
+There are 8,215 instances in the AutomatArk suite.
+Note that the original AutomatArk benchmark suite \cite{z3str3re} includes 19,979 instances, conjunctions of regular membership queries generated out of regular expressions from \cite{automatark}.
 %Only 8,751 contain counting operators out of 19,979 instances. 
-Moreover, only 5\% of them include non-register-representable regexes among the 48,843 instances.
+Moreover, only 5\% of regexes among the 48,843 instances are non-register-representable.
 %%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
@@
 
-\vspace{-3mm}
+\vspace{-2mm}
 \subsection{Overall Experiment Results}
-\vspace{-2mm}
+\vspace{-1mm}
 
@@
 %
-%\item[Q2] Do the size-reduction and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
+%\item[Q2] Do the simplification and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
 %\end{description}
@@
       \import{tables}{table_simp.tex}
-      \caption{Simplification technique evaluation, with timeout = 60 seconds.}
+      \caption{Simplification techniques evaluation, with timeout = 60 seconds.}
       \label{tab:results_simp}
@@
 %
-Moreover, our solver $\ostrichrecl$ is the second fastest solver, and its average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93}/1.62 s).
-\vspace{-3mm}
+Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93 s}/1.62 s).
+\vspace{-2mm}
 \subsection{Evaluation of Simplification Techniques}
-\vspace{-2mm}
+\vspace{-1mm}
 
 We evaluate the simplification techniques by comparing the performance of $\ostrichrecl$ with and without the simplification techniques.
-Moreover, we also encode the $\cefadec$ problem to an infinite state transition system and solve it using \textsc{nuXmv}\cite{nuxmv}.
+Moreover, we encode the $\cefadec$ problem to an infinite state transition system and use \textsc{nuXmv}\cite{nuxmv} to solve it.
+We also compare the simplification techniques to the \textsc{nuXmv}-based techniques.
 % \begin{table}[ht]
@@
 
-The evaluation results of simplification techniques are in Table~\ref*{tab:results_simp}.
-Compared to $\ostrichrecl$ without simplification techniques, $\ostrichrecl$ with simplification techniques solves \textbf{1,503 more} instances and is \textbf{2.21$\times$} faster.
-Moreover, compared with the techniques using \textsc{nuxmv}, $\ostrichrecl$ with simplification techniques solves \textbf{1,798 more} instances and is \textbf{3.13$\times$} faster.
+The evaluation results of simplification techniques are shown in Table~\ref*{tab:results_simp}.
+$\ostrichrecl_{\rm -SIMP}$ is the tool without simplification techniques.
+$\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques.
+We can see that our solver solves \textbf{1,503 more} instances and is \textbf{2.21$\times$} faster than it without simplification techniques.
+Moreover, compared to the \textsc{nuXmv}-based techniques tool, our solver solves \textbf{1,798 more} instances and is \textbf{3.13$\times$} faster.
 
-\vspace{-3mm}
+\vspace{-2mm}
 \subsection{Large-Counting Experiment Results}
+\vspace{-1mm}
 The distribution of upper bounds of counting in RegCoL and AutomatArk suites is shown in Fig~\ref{fig:count_distri}, whose horizontal axis is the value of the upper bound and vertical axis is the number of occurrences.
 The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$).
-Although most upper bounds of counting operators are less than 50, about two thousand are still greater than 50.
-We extract instances with upper bounds greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total).
-Moreover, We change the length constraint of each instance to $|x| > 200$ (which is $|x| > 10$ in the overall experiment), to make the suite more balanced.
+Although most upper bounds are small, about two thousand of them are still greater than 50.
+We extract these instances containing regex with upper bound greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total).
+Moreover, We change the length constraint of each instance to $|x| > 200$ (which is $|x| > 10$ in the overall experiment), to make the suite harder to solve.
 \vspace{-5mm}
@@
 
-  To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the size-reduction, under-approximation, or both are removed.
-  For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both size-reduction and under-approximation techniques are removed,
+  To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the simplification, under-approximation, or both are removed.
+  For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both simplification and under-approximation techniques are removed,
   OSTRICH$^{\rm RECL^-}_{+\rm SR}$ (resp.
-OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the size-reduction (resp.
+OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the simplification (resp.
 under-approximation) techniques to OSTRICH$^{\rm RECL^-}$.
-  %OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
+  %OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove simplification, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
   The experiment results can be found in Table~\ref{tab:results_heuristics}.
-  From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column).
+  From Table~\ref{tab:results_heuristics}, we can see that adding simplification techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column).
 Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ helps to solve 19 more sat instances while reducing the number of solved unsat instances by 3 since under approximation techniques do not help to solve unsat instances.

### 2023-08-30 2023-1-19/sections/introduction.tex
add files

@@
 
-The string data type plays a crucial role in modern programming languages, such as JavaScript, Python, Java, and PHP. 
-String manipulations are error-prone and could even give rise to severe security vulnerabilities (e.g. \ cross-site scripting, aka XSS). 
-One powerful method for identifying such bugs is \emph{symbolic execution} (possibly in combination with dynamic analysis).
+The string data type plays a crucial role in modern programming languages such as JavaScript, Python, Java, and PHP. 
+String manipulations are error-prone and could even give rise to severe security vulnerabilities (e.g., cross-site scripting, aka XSS). 
+One powerful method for identifying such bugs is \emph{symbolic execution}, which is possibly in combination with dynamic analysis.
 It analyses symbolic paths in a program by viewing them as constraints checked by constraint solvers.
@@
   % Thus, the nonemptiness of CEFA w.r.t. LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
-  \item We propose size-reduction techniques to reduce the state space and the number of transitions in CEFA, to achieve better performance.
+  \item We propose simplification techniques to reduce the state space and the number of transitions in CEFA, to achieve better performance.
 It is beneficial since the sizes of LIA formulas depend much on the sizes of CEFA.
-  \item Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
+  \item Combined with the simplification techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
 We implement the algorithm on top of OSTRICH, resulting in a practical string solver called $\ostrichrecl$.
@@
 The result shows that $\ostrichrecl$ solves the most instances among all the solvers, with comparable speed (See Table~\ref{tab:results_regcol}).
-In addition, we carry out some detailed experiments, including the evaluation of size-reduction techniques and the experiment of large-counting benchmarks.
-The result shows that the size-reduction techniques are effective in practice (See Table~\ref{tab:results_simp}), and $\ostrichrecl$ performs much better than other solvers on the large-counting benchmark (See Fig~\ref{fig:table_large_count}).
+In addition, we carry out some detailed experiments, including the evaluation of simplification techniques and the experiment of large-counting benchmarks.
+The result shows that the simplification techniques are effective in practice (See Table~\ref{tab:results_simp}), and $\ostrichrecl$ performs much better than other solvers on the large-counting benchmark (See Fig~\ref{fig:table_large_count}).
   % The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,843 instances, while Z3str3RE, the state-of-the-art solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
@@
 
-% Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
+% Combined with the simplification techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
 We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH called $\ostrichrecl$ for convenience.

### 2023-08-30 2023-1-19/sections/introduction.tex
intro

@@
 Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting and length bounds are large.
-For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 300 seconds, and Z3 can not solve it within 120 seconds.
+For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 120 seconds.
+%, and Z3 can not solve it within 120 seconds.
 %
@@
 For instance, $a^{\{1, 4\}}$ is unfolded into $a(\varepsilon + a + aa + aaa)$ and $a^{\{2,\infty\}}$ is unfolded into $aaa^{*}$.
-Since the unfolding incurs an exponential blow-up on the sizes of constraints (assuming that the counting in string constraints are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the bounds are large.
+Since the unfolding incurs an exponential blow-up on the sizes of constraints (assuming that the counting in string constraints are encoded in binary), the unfolding penalizes the performance of the solvers, especially when the length bounds are also available.
 
@@
 \emph{Contribution.} In this work, we focus on the class of string constraints with regular membership and string-length function, where the counting operators may occur (called RECL for brevity).
-We make the following contributions:
+We make the following contributions.
 \vspace{-0.5mm}
@@
   \item We propose an automata-theoretical approach for solving RECL constraints. 
-  Our main idea is to represent the counting operators by registers in cost-enriched finite automata (CEFA, see Section~\ref{sec:automaton} for the definition), instead of unfolding them explicitly.
+  Our main idea is to represent the counting operators by cost registers in cost-enriched finite automata (CEFA, see Section~\ref{sec:automaton} for the definition), instead of unfolding them explicitly.
+The string-length function is modeled by cost registers as well.
 The satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA w.r.t.
-a linear integer arithmetic (LIA), which is then transformed to the satisfiability of existential LIA formula tackled by the off-the-shelf SMT solver.
+a linear integer arithmetic (LIA) formula.
+According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
+Thus, the nonemptiness of CEFA w.r.t. LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
+%
   % Moreover, the string-length function can also be modeled by register in CEFA.
@@
   \item We propose simplification techniques to reduce the state space and the number of transitions in CEFA, to achieve better performance.
-It is beneficial since the sizes of LIA formulas depend much on the sizes of CEFA.
+%  , since the sizes of LIA formulas depend much on the sizes of CEFA.
   \item Combined with the simplification techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
-We implement the algorithm on top of OSTRICH, resulting in a practical string solver called $\ostrichrecl$.
-  \item Finally, we utilize a collection of benchmark suites comprising 48,843 instances in total to evaluate the performance of our tool.
-The result shows that $\ostrichrecl$ solves the most instances among all the solvers, with comparable speed (See Table~\ref{tab:results_regcol}).
-In addition, we carry out some detailed experiments, including the evaluation of simplification techniques and the experiment of large-counting benchmarks.
+We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$.
+ %
+  \item Finally, we utilize a collection of benchmark suites comprising 48,843 instances in total to evaluate the performance of $\ostrichrecl$.
+The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers, especially when the counting and length bounds are large (see Table~\ref{tab:results_regcol} and Figure~\ref{fig:table_large_count}).
+For instance, on 1,873 benchmark instances where the counting bounds are greater than or equal to $50$ and the string lengths are required to be beyond $200$, $\ostrichrecl$ solves at least $278$ more instances than the other solvers, while spending only half or less time per instance on average.
+%  For instance,  the most number of instances than the other solvers, with comparable or faster speed (See Table~\ref{tab:results_regcol}).
+Moreover, when the counting and length bounds are large, $\ostrichrecl$ solves much more instances than the other solvers, while using much less time.
+
+%In addition, we carry out some detailed experiments, including the evaluation of simplification techniques and the experiment of large-counting benchmarks.
 The result shows that the simplification techniques are effective in practice (See Table~\ref{tab:results_simp}), and $\ostrichrecl$ performs much better than other solvers on the large-counting benchmark (See Fig~\ref{fig:table_large_count}).
+
 % The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,843 instances, while Z3str3RE, the state-of-the-art solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
@@
 Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22}.
+Solving string constraints involving lengths has also been investigated by various researchers, see e.g.
+\cite{WC+18,atva2020,z3str3re}.
 

### 2023-08-30 2023-1-19/sections/algorithms.tex
add files
experiments

@@
 
-% \vspace{-3mm}
+% \vspace{-2mm}
 \begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula
@@
 We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
-\vspace{-3mm}
+\vspace{-2mm}
 \subsection{From $\reclsat$ to $\cefadec$} \label{subsec:regex2cefa}
+\vspace{-1mm}
 
@@
 Moreover, the unfoldings are partial in the sense that the outmost counting operators are not unfolded.
-It turns out that we can solve almost all of them except 181.
+It turns out that our approach can solve almost all the RECL constraints involving these 48,843 regexes, except 181 of them (See Table~\ref{tab:results_regcol}). 
 %$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.
@@
 \subsection{Solving $\cefadec$} \label{subsec:cefadec}
+\vspace{-1mm}
 
@@
 \noindent
-\emph{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \hfill{$\blacksquare$}
+\emph{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
 
@@
 \end{observation}
-\vspace{-2mm}
+\vspace{-1mm}
 
@@
 
-Because the sizes of the LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$, and the satisfiability of existential LIA formulas is expensive (NP-complete) to solve, we have to reduce the sizes of these NFA.
+Because the sizes of the LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$, and the satisfiability of existential LIA formulas is NP-complete, it is vital to reduce the sizes of these NFA to improve the performance.
 
-Actually, we find that 
-$\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}$ for each $i \in [n]$ and $\eta \in \parikh(\cU_{\cB_i})$, i.e.,
+Since
+$\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v} = \sum \limits_{\myvec{v} \in \costset(\cB_i) \setminus \{\myvec{0}\}} \eta(\myvec{v}) \myvec{v}$ for each $i \in [n]$ and $\eta \in \parikh(\cU_{\cB_i})$, it turns out that
 the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the final output $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
-Therefore, we can remove these transitions in step 2.
+Therefore, we propose the following simplification technique for the NFA $\cU_{\cB_i}$'s.
 
@@
 Then we determinize and minimize the resulting NFA.
-\hfill{$\blacksquare$}
+\qed
 
@@
 \emph{Step 3.} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
-Then we solve the satisfiability of the following formula.$\blacksquare$
+Then we solve the satisfiability of the following formula,
 %
@@
 \vspace{-1mm}
-
+\qed
 %\[

### 2023-08-30 2023-1-19/sections/implementation.tex
intro
experiments

@@
 
-Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}. There are 48,843 instances in total, and all benchmark instances are in SMTLIB2 format.
+Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}. There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
+Moreover, it turns out that only 5\% of regexes among the 48,843 instances are non-register-representable (see Section~\ref{subsec:regex2cefa}).
 
@@
 where $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is a regular expression that sanitizes all occurrence of special characters $<$, $>$, $'$, $''$, or $\&$. 
-The artificial construction is meaningful because the special characters are offensive.
-For instance, they are widely used in client-side attacks like XSS\cite{malware_detection_3_kudzu,CCH_18}.
+%The artificial construction is meaningful because the special characters are offensive. 
+The expression $e_{sani}$ is introduced in view of the fact that these characters are usually sanitized in Web browsers to alleviate the XSS attacks \cite{malware_detection_3_kudzu,CCH_18}.
 %We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
@@
 The AutomatArk benchmark suite is adapted from the AutomatArk suite \cite{z3str3re} by picking out the string constraints containing counting operators.
-We add length constraint $|x| > 10$ for each string variable $x$ because there is no original length constraints.
+We also add the length constraint $|x| > 10$ for each string variable $x$.
 There are 8,215 instances in the AutomatArk suite.
-Note that the original AutomatArk benchmark suite \cite{z3str3re} includes 19,979 instances, conjunctions of regular membership queries generated out of regular expressions from \cite{automatark}.
+Note that the original AutomatArk benchmark suite \cite{z3str3re} includes 19,979 instances, which are conjunctions of regular membership queries generated out of regular expressions in \cite{automatark}.
 %Only 8,751 contain counting operators out of 19,979 instances.
-Moreover, only 5\% of regexes among the 48,843 instances are non-register-representable.
+
 %%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
 %%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
+
+\medskip
+\noindent
+\emph{Distribution of problem instances w.r.t. counting bounds. }
+The distribution of problem instances w.r.t.
+the counting bounds in RegCoL and AutomatArk suites is shown in Fig~\ref{fig:count_distri}, where the $x$-axis represents the counting bound and the $y$-axis represents the number of problem instances whose maximum counting bound is equal to the value of the $x$-axis.
+%The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
+From Fig~\ref{fig:count_distri}, we can see that while most problem instances contain only small bounds, there are still around 2,000  (about 4\%) of them using large counting bounds (i.e.
+greater than or equal to $50$).
+%Although most upper bounds are small, about two thousand of them are still greater than 50.
 
@@
 We use the \textsc{zaligvinder} framework \cite{zaligvinder_2021} to execute the experiments, with a timeout of 60s for each instance.
+
+%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
 \hide{
@@
 \vspace{-2mm}
-\subsection{Overall Experiment Results}
+\subsection{Experiment Results}
 \vspace{-1mm}
@@
 %\end{description}
-\vspace{-5mm}
+
+\paragraph*{Overall evaluation.}
+%
+\vspace{-7mm}
 \begin{table}
@@
       \import{tables}{table_regcol.tex}
-      \caption{Overall experiment results,\\ with timeout = 60 seconds.}
+      \caption{Overall evaluation, with timeout = 60 seconds.}
       \label{tab:results_regcol}
@@
       \import{tables}{table_simp.tex}
-      \caption{Simplification techniques evaluation, with timeout = 60 seconds.}
+      \caption{Evaluation of the simplification techniques, with timeout = 60 seconds.}
       \label{tab:results_simp}
   \end{subtable}
-  \vspace{-6mm}
-  \caption{Experiments on RegCoL and AutomatArk benchmark suites}
+  \vspace{-2mm}
+  \caption{Experiment results}
 \end{table}
-\vspace{-9mm}
+\vspace{-7mm}
 % \begin{table}[ht]
@@
 
-The overall experiment results are in Table~\ref{tab:results_regcol}.
-Note that we take the result of CVC5 as the ground truth\footnote{At first we used the majority vote between all results of the solvers as the ground truth, but solvers of z3 family output some wrong results(verified by us manually), causing the ground truth to be incorrect.}.
+The experiment results can be found in Table~\ref{tab:results_regcol}.
+Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results as the ground truth, but the results of all the three solvers in the Z3 family on some problem instances are wrong (verified by us manually), thus failing this approach.}.
 We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
@@
 %
-Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93 s}/1.62 s).
-\vspace{-2mm}
-\subsection{Evaluation of Simplification Techniques}
-\vspace{-1mm}
+Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93s}/1.62s).
 
-We evaluate the simplification techniques by comparing the performance of $\ostrichrecl$ with and without the simplification techniques.
-Moreover, we encode the $\cefadec$ problem to an infinite state transition system and use \textsc{nuXmv}\cite{nuxmv} to solve it.
-We also compare the simplification techniques to the \textsc{nuXmv}-based techniques.
-% \begin{table}[ht]
-%   \vspace{-5mm}
-%   \begin{center}
-%     \import{tables}{table_simp.tex}
-%   \end{center}
-%   \caption{Simplification technique evaluation, with timeout = 60 seconds}
-%   \label{tab:results_simp}
-%   \vspace{-9mm}
-% \end{table}
-
-The evaluation results of simplification techniques are shown in Table~\ref*{tab:results_simp}.
-$\ostrichrecl_{\rm -SIMP}$ is the tool without simplification techniques.
-$\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques.
-We can see that our solver solves \textbf{1,503 more} instances and is \textbf{2.21$\times$} faster than it without simplification techniques.
-Moreover, compared to the \textsc{nuXmv}-based techniques tool, our solver solves \textbf{1,798 more} instances and is \textbf{3.13$\times$} faster.
-
-\vspace{-2mm}
-\subsection{Large-Counting Experiment Results}
-\vspace{-1mm}
-The distribution of upper bounds of counting in RegCoL and AutomatArk suites is shown in Fig~\ref{fig:count_distri}, whose horizontal axis is the value of the upper bound and vertical axis is the number of occurrences.
-The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$).
-Although most upper bounds are small, about two thousand of them are still greater than 50.
-We extract these instances containing regex with upper bound greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total).
-Moreover, We change the length constraint of each instance to $|x| > 200$ (which is $|x| > 10$ in the overall experiment), to make the suite harder to solve.
+\paragraph*{Evaluation on problem instances with large bounds.}
+%
+We extract the 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
+%regex with upper bound greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total). 
+Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
 \vspace{-5mm}
@@
     \includegraphics[width=1\textwidth]{counting_distribution.png}  
-    \caption{Distribution of counting operators in two benchmark suites.}  
+    \caption{Distribution of problem instances w.r.t. counting bounds}  
     \label{fig:count_distri}
@@
     \vspace{4.5mm}
-    \caption{Large-counting experiment, \\with timeout = 60 seconds.}
+    \caption{Experiment results for large bounds, \\with timeout = 60 seconds.}
     \label{fig:table_large_count}
@@
   \vspace{-2mm}
-  \caption{Analysis of dataset and large-counting experiment.}
+  \caption{Distribution of counting bounds and experiment results for large bounds}
 \end{figure}
@@
 
-We evaluate the performance of $\ostrichrecl$ on these instances.
-The results are in Fig~\ref{fig:table_large_count}.
-We can see that $\ostrichrecl$ solves \textbf{1,873} instances correctly, which is \textbf{947/278/563/637/523 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-Moreover, \newline
-$\ostrichrecl$ is the fastest solver, who is \textbf{ 6.79/2.88/2.61/5.27/3.95$\times$ } faster than CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+We then evaluate the performance of $\ostrichrecl$ on these 1,969 instances. 
+The experiment results are put in Fig~\ref{fig:table_large_count}.
+From the results, $\ostrichrecl$ solves \textbf{1,873} instances correctly, which is \textbf{947/278/563/637/523 more} than that solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+Moreover, $\ostrichrecl$ is \textbf{ 6.79/2.88/2.61/5.27/3.95} times faster than CVC5/ Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
 \vspace{-2mm}
+
+\paragraph*{Evaluation of the simplification techniques.}
+We also do experiments to evaluate the effectiveness of the simplification techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
+Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the simplification techniques removed. 
+Meanwhile, we compare $\ostrichrecl$ and $\ostrichrecl_{\rm -SIMP}$ against $\ostrichrecl_{\rm NUXMV}$, where the $\cefadec$ problem is solved by the \textsc{nuXmv} model checker \cite{nuxmv}, instead of the procedure in Section~\ref{subsec:cefadec}.
+The experiment results are put in Table~\ref{tab:results_simp}. 
+%$\ostrichrecl_{\rm -SIMP}$ is the tool without simplification techniques. $\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques. 
+From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$, which shows that the simplification techniques indeed play a vital role in the performance improvement.
+Moreover, $\ostrichrecl$ solves \textbf{1,798 more} instances and is \textbf{3.13} times faster than $\ostrichrecl_{\rm NUXMV}$.
+
+%Moreover, we encode the $\cefadec$ problem to an infinite state transition system and use \textsc{nuXmv}\cite{nuxmv} to solve it.
+We also compare the simplification techniques to the \textsc{nuXmv}-based techniques.
+%$\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques.
+%We evaluate the simplification techniques by comparing the performance of $\ostrichrecl$ with and without the simplification techniques.
+
+% \begin{table}[ht]
+%   \vspace{-5mm}
+%   \begin{center}
+%     \import{tables}{table_simp.tex}
+%   \end{center}
+%   \caption{Simplification technique evaluation, with timeout = 60 seconds}
+%   \label{tab:results_simp}
+%   \vspace{-9mm}
+% \end{table}
 

### 2023-08-30 2023-1-19/sections/overview.tex
overview

--- 2023-08-18 2023-1-19/sections/overview.tex
@@
 Therefore, the vector for this transition is $(1, 0, 0, 0)$.
-Finally, The satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut\equiv \aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, abbreviated as $\sf NE_{\varphi}(\aut)$.
-That is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut$, producing resulting registers values $(v_1, v_2, v_3, v_4)$ that satisfy $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $\varphi$.
-It is not hard to observe that $\sf NE_{\varphi}(\aut)$ is independent of the characters of $\aut$.
+Finally, the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut\equiv \aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut$, so that the resulting registers values $(v_1, v_2, v_3, v_4)$ satisfy both $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $\varphi$.
+It is not hard to observe that the nonemptiness of $\aut$ with respect to $\varphi$ is independent of the characters of $\aut$.
 Therefore, the characters in $\aut$ can be ignored, resulting into an NFA $\cB$ over the alphabet $\costset$, where $\costset$ is the set of vectors from $\Int^4$ occurring in the transitions of $\aut$ (see Figure~\ref{fig:overview:product:reduced}(a)).
-Then $\sf NE_{\varphi}(\aut)$ is reduced to the problem of deciding whether there exists $w' \in \costset^*$ such that it is accepted by $\cB$ and its Parikh image (i.e., numbers of occurrences of characters), say $\eta_{w'}: \costset \rightarrow \Nat$, satisfies that $1 \le v'_1 \le 60\wedge 1 \le v'_2 \le 60 \wedge 0 \le v'_3 \le 60$ and $v'_4 > 120$, where $(v'_1, v'_2, v'_3, v'_4) =  \sum \limits_{\myvec{v} \in \costset} \eta_{w'}(\myvec{v}) \myvec{v}$ for each $\myvec{v}\in \costset$.
+Then the original problem is reduced to the problem of deciding whether there exists a string $w' \in \costset^*$ that is accepted by $\cB$ and its Parikh image (i.e., numbers of occurrences of characters), say $\eta_{w'}: \costset \rightarrow \Nat$, satisfies $1 \le v'_1 \le 60\wedge 1 \le v'_2 \le 60 \wedge 0 \le v'_3 \le 60 \wedge v'_4 > 120$, where $(v'_1, v'_2, v'_3, v'_4) =  \sum \limits_{\myvec{v} \in \costset} \eta_{w'}(\myvec{v}) \myvec{v}$ for each $\myvec{v}\in \costset$.
 Intuitively, $(v'_1, v'_2, v'_3, v'_4)$ is a weighted sum of vectors $\myvec{v} \in \costset$, where the weight is the number of occurrences of $\myvec{v}$ in $w'$.
@@
 
-Nevertheless, the algorithm illustrated above is insufficient when regexes are complicated.
-The size of $\cB$ can still be big, causing the resulted existential LIA formulas are of big sizes and hard to be solved (NP-complete \cite{Haase18}).
-To tackle this issue, we propose techniques to reduce the sizes of $\cB$ over the alphabet $\costset$.
+Nevertheless, when the original regexes are complicated (e.g.
+contains the occurrences of negation or intersection operators), the sizes of the NFA $\cB$ can still be big and the sizes of the LIA formulas defining the Parikh image of $\cB$ are also big.
+Since the satisfiability of LIA formulas is an NP-complete problem \cite{Haase18}, big sizes of LIA formulas would be a bottleneck of the efficiency.
+To tackle this issue, we propose techniques to reduce the sizes of the NFA $\cB$.
+%over the alphabet $\costset$.
 
@@
 
-Specifically, to reduce the sizes of the $\cB$, we determinize $\cB$ and apply the minimization algorithm to the resulting deterministic finite automaton (DFA), obtaining a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
+Specifically, to reduce the sizes of $\cB$, we take $\vec{0}$-labeled transitions as $\epsilon$-transitions, determinize $\cB$, and apply the minimization algorithm to the resulting deterministic finite automaton (DFA), resulting in a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
-The evaluation in section \cite{sec} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.
+%The evaluation in Table~\ref{tab:results_simp} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.
 
 We implement all the aforementioned techniques on the top of OSTRICH, resulting in a solver $\ostrichrecl$.
-It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art string solvers are incapable of solving it within 300 seconds.
+It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art string solvers are incapable of solving it within 120 seconds.
 

### 2023-08-30 2023-1-19/sections/overview.tex
overview

@@
 
-Specifically, to reduce the sizes of $\cB$, we take $\vec{0}$-labeled transitions as $\epsilon$-transitions, determinize $\cB$, and apply the minimization algorithm to the resulting deterministic finite automaton (DFA), resulting in a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
+Specifically, to reduce the sizes of $\cB$, we determinize $\cB$, and apply the minimization algorithm to the resulting deterministic finite automaton (DFA), resulting in a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
 Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions.
+Furthermore, if $\cB$ contains $\vec{0}$-labeled transitions, then we can take these transitions as $\epsilon$-transitions and potentially reduce the sizes of automata further.
 %The evaluation in Table~\ref{tab:results_simp} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.

### 2023-08-30 2023-1-19/sections/conclusion.tex
conclusion

@@
 
-%TODO
-This work proposes an efficient automata-theoretical approach for solving RECL constraints: string constraints with regex-counting and string-length.
-The approach is based on encoding counting operators in regular expressions by registers symbolically instead of unfolding them explicitly.
-Moreover, this paper proposes an automata-size reduction technique to improve performance.
-Finally, we use two benchmark suites comprising 48,843 instances in total to evaluate the performance of our approach.
-The experimental results show that our approach, with comparable performance, can solve more instances than the state-of-the-art best solvers on RECL constraints.
-We plan to investigate symbolic approaches to dealing with nested counting operators in future work.
+This work proposes an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length.
+The approach is based on encoding counting operators in regular expressions by cost registers symbolically instead of unfolding them explicitly.
+Moreover, this paper proposes automata-size reduction techniques to improve performance further.
+Finally, we use two benchmark suites comprising 48,843 instances to evaluate the performance of our approach.
+The experimental results show that our approach can solve more instances than the state-of-the-art best solvers, at a comparable or faster speed, especially when the counting and length bounds are large.
+For the future work, we plan to investigate how the symbolic approach can be extended to reason about nested counting operators.
 

### 2023-08-30 2023-1-19/sections/implementation.tex
conclusion

@@
 \emph{AutomatArk benchmark suite.}
-The AutomatArk benchmark suite is adapted from the AutomatArk suite \cite{z3str3re} by picking out the string constraints containing counting operators.
+This benchmark suite is adapted from the AutomatArk suite \cite{z3str3re} by picking out the string constraints containing counting operators.
 We also add the length constraint $|x| > 10$ for each string variable $x$.
@@
 
-\paragraph*{Overall evaluation.}
+\medskip
+\noindent
+\emph{Overall evaluation.} 
+The experiment results can be found in Table~\ref{tab:results_regcol}.
+Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}.
+We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
+The number is %3,994/2,272/24,577/12,832/1,091/7,092
+\textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
 %      
-\vspace{-7mm}
+%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
+% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
+%
+Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93s}/1.62s).
+
+%
 \begin{table}
+  \vspace{-3mm}
   \centering
@@
   \caption{Experiment results}
+  \vspace{-6mm}
 \end{table}
-\vspace{-7mm}
 % \begin{table}[ht]
@@
 
-The experiment results can be found in Table~\ref{tab:results_regcol}.
-Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results as the ground truth, but the results of all the three solvers in the Z3 family on some problem instances are wrong (verified by us manually), thus failing this approach.}.
-We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
-The number is %3,994/2,272/24,577/12,832/1,091/7,092
-\textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-%      
-%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
-% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
-%
-Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93s}/1.62s).
-
-\paragraph*{Evaluation on problem instances with large bounds.}
+\smallskip
+\noindent
+\emph{Evaluation on problem instances with large bounds.}
 %
@@
 Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
-\vspace{-5mm}
+%
 \begin{figure}[ht]
@@
   \caption{Distribution of counting bounds and experiment results for large bounds}
+\vspace{-5mm}
 \end{figure}
-\vspace{-5mm}
 
@@
 Moreover, $\ostrichrecl$ is \textbf{ 6.79/2.88/2.61/5.27/3.95} times faster than CVC5/ Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-\vspace{-2mm}
 
-\paragraph*{Evaluation of the simplification techniques.}
+\medskip
+\noindent 
+\emph{Evaluation of the effectiveness of the simplification techniques.}
 We also do experiments to evaluate the effectiveness of the simplification techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 

### 2023-08-30 2023-1-19/sections/implementation.tex
abstract

@@
 \begin{table}
-  \vspace{-3mm}
+  \vspace{-4mm}
   \centering
@@
       \import{tables}{table_simp.tex}
-      \caption{Evaluation of the simplification techniques, with timeout = 60 seconds.}
+      \caption{Evaluation of the automata size-reduction techniques, with timeout = 60 seconds.}
       \label{tab:results_simp}
@@
   \caption{Experiment results}
-  \vspace{-6mm}
+  \vspace{-8mm}
 \end{table}
@@
 \noindent 
-\emph{Evaluation of the effectiveness of the simplification techniques.}
-We also do experiments to evaluate the effectiveness of the simplification techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
-Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the simplification techniques removed. 
+\emph{Evaluation of the effectiveness of the automata size-reduction techniques.}
+We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
+Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
 Meanwhile, we compare $\ostrichrecl$ and $\ostrichrecl_{\rm -SIMP}$ against $\ostrichrecl_{\rm NUXMV}$, where the $\cefadec$ problem is solved by the \textsc{nuXmv} model checker \cite{nuxmv}, instead of the procedure in Section~\ref{subsec:cefadec}.
@@
 %$\ostrichrecl_{\rm -SIMP}$ is the tool without simplification techniques. $\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques. 
-From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$, which shows that the simplification techniques indeed play a vital role in the performance improvement.
+From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$, which shows that the size-reduction techniques indeed play a vital role in the performance improvement.
 Moreover, $\ostrichrecl$ solves \textbf{1,798 more} instances and is \textbf{3.13} times faster than $\ostrichrecl_{\rm NUXMV}$.

### 2023-08-30 2023-1-19/sections/introduction.tex
conclusion
abstract

@@
 
-Regular expressions (abbreviated as regex) and string-length function are widely used in string-manipulating programs.
+Regular expressions (regex for short) and string-length function are widely used in string-manipulating programs.
 According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% of Java, JavaScript, and Python software projects.
@@
   % Thus, the nonemptiness of CEFA w.r.t. LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
-  \item We propose simplification techniques to reduce the state space and the number of transitions in CEFA, to achieve better performance.
+  \item We propose techniques to reduce the sizes (i.e. the number of states and transitions) of CEFA, in order to achieve better performance.
 %  , since the sizes of LIA formulas depend much on the sizes of CEFA.
-  \item Combined with the simplification techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
+  \item Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
 We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$.

### 2023-09-04 2023-9-4/extend_split/note.tex
add note of handling string array

\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage[fleqn]{amsmath}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{amsthm}
\usepackage{graphicx}

\theoremstyle{remark}
\newtheorem{definition}{Defination}[section]

\title{A Note for Solving String Constraints with Split Function}
\author{Denghang Hu}
\begin{document}
\maketitle

\section{Preliminary}
\subsection{Incremental Nondeterministic Cost Register Automaton (INCRA)}
A \textit{incremental nondeterministic cost register automaton} (INCRA) $\mathcal{A} $ is a tuple $(Q, \Sigma, \delta,q_0,F, R)$ where:
\begin{itemize}
    \item $Q$ is a finite set of \textit{states}.
    \item $\Sigma$ is the alphabet.
    \item $\delta\in Q\times\Sigma\times Q\times M$ is the \textit{transition relation}. $M$ is the set of the update function $\eta$ satisfying that for each $r\in R$, $\eta(r) = r+c$ for some integer constant $c$.
    \item $q_0\in Q$ is the $initial$ state.
    \item $F\subseteq Q$ is the set of $final$ states.
    \item $R = r_1\cdots r_m$ is vector of counters.
\end{itemize}
For a string $w=a_1\cdots a_n $, a run of $\mathcal{A}$ on $w$ is a state sequence $q_0\cdots q_n$ such that for each $i\in[n]$, $(q_{i-1},a_i,q_i,\eta)\in \delta$. A run $q_0\cdots q_n$ on formula $\phi$ is $accepting$ if $q_n \in F$ and $R\models \phi$. INCRA equal to NFA when $R=\emptyset$.
\subsection{Special INCRA for Array}
We define a special INCRA $\mathcal{A}^s$ for \textbf{array} sort. $\mathcal{A}^s$ use a preserved character '$\#$' as $array$ elements separator (note that $\#\not\in\Sigma_{\mathcal{A}^s}$). The speciality of $\mathcal{A}^s$ rely on  its construction.\\
Consider $array$ $A$ with $|A|=m+1$ and assume that for each $i\in\{0,\cdots, m\}$, $A[i]\in \mathcal{A}_i$, then we can construct $A^s=(\bigcup\limits_{0\leq i \leq m} Q_i,\bigcup\limits_{0\leq i \leq m} \Sigma_i, \delta', q_0^{\mathcal{A}_1}, F^{\mathcal{A}_m}, \bigcup\limits_{0\leq i \leq m} R_i), $ as fig \ref{fig:special_nfa}.Note that the language of $A^s$ is $\mathcal{L}(A_1)\cdot\{\#\}\cdot\mathcal{L}(A_2)\ ... \ \cdot\{\#\}\cdot \mathcal{L}(A_{m}) $.
\begin{figure}[H]
    \includegraphics[width=\linewidth]{special_nfa.png}
    \caption{NFA of array $A$}
    \label{fig:special_nfa}
\end{figure}

\section{Straight-Line String Theory with Integer and Array $SL_{I,A,S} $}
We defined a theory $SL_{I,A,S}$ with three sorts: \textbf{string}, \textbf{integer} and \textbf{array}. The \textit{elements} of \textbf{array} can only be \textbf{string} sort. As a convention, the $index$ of \textbf{array} is \textbf{Integer} sort.
\subsection{Syntax}
The syntax of $SL_{I,A,S}$ is defined as fig \ref{fig:syntax}, where $\mathcal{A}$ is an NFA, $\mathcal{A}^s $ is a special NFA for \textbf{array} sort and $\circ \in \{=,\not=, <, \leq, >, \geq \}$. For technical convenience, we assume that all assignments in F are \textit{Static Singly Assignment (SSA)} form.
\begin{figure}[H]
    % denote
    $u,v,\cdots$  \hfill{String constants}\\
    $x,y,\cdots$  \hfill{String varibles}\\
    $m,n,\cdots$  \hfill{Integer constants}\\
    $i,j,\cdots$  \hfill{Integer varibles}\\
    $M,N,\cdots$  \hfill{Array constants}\\
    $X,Y,\cdots$  \hfill{Array varibles}\\

    % term and expression
    $s \ ::= \ u \ |\ x$ \hfill{String term}\\
    $t \ ::= \  m \ |\ i \ |\ ct \ |\ t+t \ |\ t-t \ |\ |A| $ \hfill{Integer term}\\
    $A \ ::= \  M \ |\ X  $ \hfill{Array term}\\
    $\beta \ ::= \  m \ |\ |A| \ |\ |A|+m  $  \hfill{Bound expression}\\

    % formula
    $LA \ ::= \ t\circ t \ |\ LA\wedge LA \ |\ \neg LA $  \hfill{Linear arithmatic}\\
    $SC \ ::= \ x=s \ |\ x=A[t] \ |\ x=s\cdot s \ |\ x=\mathrm{join}(A,u) \ |\ s\in\mathcal{A} \ |\ SC\wedge SC $   \flushright{String constraints}\\
    $AC \ ::= \ A = \mathrm{split}(s,e) \ |\ A = A[\beta_1:\beta_2] \ |\ A = A[t\rightarrow s] \ |\ A\in \mathcal{A}^s \ |\ A = \mathcal{T}(A) $ \flushright{Array constraints}\\ 
    $F \ ::= \  LA \ |\ SC \ |\ AC \ |\ F\wedge F $ \hfill{Formula of $SL_{I,A,S} $}
    \caption{Syntax of $SL_{I,A,S}$}
    \label{fig:syntax}
\end{figure}

\subsection{Semantic}
The semantic of $SL_{I,A,S} $ is:
\begin{itemize}
    \item $A[t]$ : Return the $element$ of $A$ at index $t$.
    \item $A[t\rightarrow s]$ : Return a new array the same as $A$ except  that the $element$ of $A$ at index $t$ changes to string $s$.
    \item $s\cdot s$ : String concatenation.
    \item $\mathrm{join}(A,u) $ : Return a new string by concatenating all of $elements$ in array $A$, separated by a specified separator string $u$.
    \item $\mathrm{split}(s,e) $ : Return a new array by dividing string $s$ into ordered substring array. The separator string is regular expression $e$.
    \item $\mathcal{T}(A) $: Return a new array by applying transducer $\mathcal{T}$ on each $element$ of array $A$. 
    \item $A[\beta_1:\beta_2] $ Return a new array which is the subarray of $A$.
\end{itemize}
\subsection{Defination of Straight-Line Restriction }
We consider two sorts: \textbf{string} and \textbf{array}.
\begin{definition}[Relational constraints ]
    Relational constraints $\phi$ are defined by the following rules:
    \begin{align*}
        \phi \ ::= \ x=s\cdot s \ |\ x=\mathrm{join}(A,u) \ |\ A = \mathrm{split}(s,e) \ |\ A = A[\beta_1:\beta_2] \ |\ A = A[t\rightarrow s] \ |\ \phi \wedge \phi
    \end{align*}
\end{definition}
\begin{definition}[Straight-line relational constraints] 
    A relational constraint $\phi$ is straight-line if $\phi = \bigwedge\limits_{1\leq i \leq m} x_i = P_i$ such that
    \begin{itemize}
        \item $x_1,\cdots,x_m $ are mutally distinct.
        \item For each $i\in [m] $, all the varibles in $P_i$ are either source varibles or varibles in set $\{x_1,\cdots,x_{m-1} \}$.
    \end{itemize} 
\end{definition}
\begin{definition}[Straight-line formula]
    A formula $F$ of $SL_{I,A,S}$ is straight-line iff all relational constraints in $F$ are straight-line.
\end{definition}

\section{Pre-image of Assignment}
\subsection{Array Assignment}
Assume $A\in A^s$ and $A^s=(Q, \Sigma, \delta,q_0,F,R)$ construct like fig \ref{fig:special_nfa}.
\begin{itemize}
    \item $A = \mathrm{split}(s,e)$: assume $e\in \mathcal{A}_e$, then we can construct $\mathcal{B}=(Q', \Sigma', \delta',q_0,F,R)$ like fig \ref{fig:pre_image_split} s.t $s\in B$.
    \item $B = A[\beta_1:\beta_2]$:  
\end{itemize}
\begin{figure}
    \includegraphics[width=\linewidth]{pre_image_split.png}
    \caption{pre-image of split operation}
    \label{fig:pre_image_split}
\end{figure}
\bibliographystyle{abbrv} % 指定格式，
% \bibliographystyle{apa} % 这是姓名年份应用格式
\bibliography{ref} %  ../.bib表示bib的具体位置
\end{document}

### 2023-10-13 2023-1-19/sections/implementation.tex
review 1 question 2

@@
 Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
-Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}.
-We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, \denghang{and the results distinct to the ground truth are called soundness errors.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
 The number is %3,994/2,272/24,577/12,832/1,091/7,092

### 2023-10-13 2023-1-19/sections/introduction.tex
review 2

@@
 
-Regular expressions (regex for short) and string-length function are widely used in string-manipulating programs.
+Regular expressions (regex for short) and the string-length function are widely used in string-manipulating programs.
 According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% of Java, JavaScript, and Python software projects.
@@
 For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
-Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ are equivalent to $a^{\{0,\infty\}}$ and $a^+$ are equivalent to $a^{\{1,\infty\}}$.
+Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ is equivalent to $a^{\{0,\infty\}}$ and $a^+$ are equivalent to $a^{\{1,\infty\}}$.
 Counting is a frequently used feature of regular expressions.

### 2023-10-13 2023-1-19/sections/overview.tex
latest version
review 2

@@
 %Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
-the nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$ is constructed; the updates of registers is added to the transitions of the NFA; the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$, resulting in a CEFA $\aut_1$ illustrated in Figure~\ref{fig:overview}(a).
+the nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$ is constructed; the updates of registers are added to the transitions of the NFA; the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$, resulting in a CEFA $\aut_1$ illustrated in Figure~\ref{fig:overview}(a).
 $r_1++$ means that we increment the value of $r_1$ by one after running the transition.
@@
 Nevertheless, when the original regexes are complicated (e.g.
-contains the occurrences of negation or intersection operators), the sizes of the NFA $\cB$ can still be big and the sizes of the LIA formulas defining the Parikh image of $\cB$ are also big.
-Since the satisfiability of LIA formulas is an NP-complete problem \cite{Haase18}, big sizes of LIA formulas would be a bottleneck of the efficiency.
+contain occurrences of negation or intersection operators), the sizes of the NFA $\cB$ can still be big and the sizes of the LIA formulas defining the Parikh image of $\cB$ are also big.
+Since the satisfiability of LIA formulas is an NP-complete problem \cite{Haase18}, big sizes of LIA formulas would be a bottleneck of the performance.
 To tackle this issue, we propose techniques to reduce the sizes of the NFA $\cB$.

### 2023-10-17 2023-1-19/sections/cefa.tex
review 3 partially

@@
 
-In the sequel, we define three CEFA operations: union, intersection, and concatenation. The following section will use these three operations to solve RECL constraints.
+In the sequel, we define three CEFA operations: union, intersection, and concatenation.
+The following section will use these three operations to solve RECL constraints.
+\denghang{Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than symbolic register automata~\cite{sra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.}
 

### 2023-10-17 2023-1-19/sections/implementation.tex
review 3 partially

--- 2023-08-30 2023-1-19/sections/implementation.tex
@@
 We first present the overall experiment results on RegCoL and AutomatArk benchmark suites.
-Then we evaluate the simplification techniques and large-counting experiment results.
+Then we present experiment results of the large-counting part and evaluate the simplification techniques.
+\denghang{The goal of our experiments is to answer the following questions:
+\begin{itemize}
+  \item [Q1:] Are our decision procedure more efficient than the state-of-the-art string constraint solvers on RECL constraints?
+  \item [Q2:] Why our decision procedure is more efficient?
+  \item [Q3:] Are the size-reduction techniques helpful to improve the performance?
+\end{itemize}
+}
 
@@
 Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
-Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}.
-We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, \denghang{and the results distinct to the ground truth are called \emph{soundness errors} in the result table.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
 The number is %3,994/2,272/24,577/12,832/1,091/7,092

### 2023-10-17 2023-1-19/sections/introduction.tex
review 3 partially

@@
 Z3seq~\cite{z3seq}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
-Z3-Trau~\cite{Z3-trau}, OSTRICH~\cite{CHL+19}, Slent~\cite{WC+18}, among many others.
+Z3-Trau~\cite{Z3-trau}\cite{z3trau}, OSTRICH~\cite{CHL+19}, Slent~\cite{WC+18}, among many others.
 
@@
 Real-world regexes in programming languages include features beyond classical regular expressions, e.g., the greedy/lazy Kleene star, capturing groups, and back references.
-Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
-Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22}.
+\denghang{Symbolic register automata\cite{sra} are raised to handle back references.} Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
+Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22} \denghang{and \cite{sra}}.
 Solving string constraints involving lengths has also been investigated by various researchers, see e.g.
 \cite{WC+18,atva2020,z3str3re}.
+\denghang{Rule-based string solvers like Z3str/2/3/4 and CVC4/5 are incapable of handling regexes with counting and complementary, even for the simple constraint $x\in [0-8]^{\{1,200\}}\wedge x\not\in [0-9]^+$.
+Automata-based string solvers like Z3Str3RE and Ostrich can solve it, but they are inefficient because they have to build automata by unwinding counting operator, resulting in an automaton with more than $1800$ states for regex $[0-8]^{\{1,200\}}$.
+Moreover, the counting operator is not supported by string solvers Z3-Trau and Slent.}
 

### 2023-10-17 2023-1-19/sections/preliminaries.tex
review 3 partially

@@
 For readability, we write a transition $(q, a, q') \in \delta$ as $q \xrightarrow[\delta]{a} q'$ (or simply $q \xrightarrow{a} q'$).
-%Moreover, when $\delta$ is clear from context, we omit $\delta$ in $q \xrightarrow[\delta]{a} q'$ and write $q \xrightarrow{a} q'$.
+\denghang{Note that one initial state is sufficient.
+A set of initial states is a technical choice to simplify the defination of union operation in Sec \ref{sec:automaton}.}%Moreover, when $\delta$ is clear from context, we omit $\delta$ in $q \xrightarrow[\delta]{a} q'$ and write $q \xrightarrow{a} q'$.
 The \emph{size} of an NFA $\NFA$, denoted by $|\NFA|$, is defined as the number of transitions of $\NFA$.

### 2023-10-18 2023-1-19/sections/algorithms.tex
abstract
review 3 partially
all review finished

@@
 This section aims to show how to solve RECL constraints by utilizing CEFA. 
-At first, we reduce the satisfiability of RECL constraints to a decision problem defined in the following section. Then we propose an algorithm to solve the decision problem.
+At first, we reduce the satisfiability of RECL constraints to a decision problem defined in the following section. Then we propose an decision procedure to solve the problem.
 
@@
 We say that $e$ is \emph{register-representable} if all occurrences of counting operators in $e$ are register-representable.
-For instance, $(a^{\{2, 6\}} \concat b^*) \cap (a + b)^{\{4, \infty\}}$ is register-representable, while $(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ and $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ are not since $a^{\{2,6\}}$ is in the scope of language difference and the counter operator $\{2, \infty\}$ respectively.
+For instance, $a^{\{2, 6\}} \cap a^{\{4, \infty\}}$ is register-representable, while $\overline{a^{\{2, 6\}}}$ and $(a^{\{2, 6\}})^{\{4,\infty\}}$ are not since $a^{\{2,6\}}$ is in the scope of complement and the counter operator $\{2, \infty\}$ respectively.
 
@@
 For instance, $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa+aaaa) \concat b^*)^{\{2, \infty\}}$.
-The unfoldings of the inner counting operators of non-register-representable regexes incur an exponential blow-up in the worst case.
+The unfoldings of the inner counting operators of non-register-representable regexes incur an exponential blowup in the worst case.
 Nevertheless, those regexes occupy only 5\% of the 48,843 regexes that are collected from the practice (see Section~\ref{sec:bench}).
@@
 the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the final output $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
-Therefore, we propose the following simplification technique for the NFA $\cU_{\cB_i}$'s.
+Therefore, we propose the following size-reduction technique for the NFA $\cU_{\cB_i}$'s.
 

### 2023-10-18 2023-1-19/sections/cefa.tex
all review finished

@@
 We define the semantics of a CEFA $\aut$, denoted by $\Lang(\aut)$, as $\{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.
-In particular, if $I \cap F \neq \emptyset$ and $\alpha(\myvec{0}/R)$ is true, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$.
+In particular, if $I \cap F \neq \emptyset$ and $\alpha[\myvec{0}/R]$ is true, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$.
 Moreover, we define the \emph{output} of a CEFA $\aut$, denoted by $\cefaout(\aut)$, as $\{\myvec{v'} \mid  \exists w.\ \myvec{v'} \in \aut(w)\}$.
@@
 
-The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$, is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.
+The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$ \sout{is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states}.
 Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).

### 2023-10-18 2023-1-19/sections/implementation.tex
all review finished

@@
 \begin{itemize}
-  \item [Q1:] Are our decision procedure more efficient than the state-of-the-art string constraint solvers on RECL constraints?
-  \item [Q2:] Why our decision procedure is more efficient?
-  \item [Q3:] Are the size-reduction techniques helpful to improve the performance?
+  \item [Q1:] Are our decision procedure more efficient than the state-of-the-art string constraint solvers on RECL constraints? (Sec \ref{subsec:overall_eval})
+  \item [Q2:] Why our decision procedure is more efficient?(Sec \ref{subsec:large_bounds_eval})
+  \item [Q3:] Are the size-reduction techniques practical?(Sec \ref{subsec:size_reduction_eval})
+  \item [Q4:] How effective is the algorithm for solving the nonemptiness problem compared to the case that uses the nuXmv model checker? (Sec \ref{subsec:size_reduction_eval})
 \end{itemize}
@@
 
-Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}. There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
+Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}.
+\denghang{Other industrial benchmarks suites are not utilized because they contains no counting operator.} There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
 Moreover, it turns out that only 5\% of regexes among the 48,843 instances are non-register-representable (see Section~\ref{subsec:regex2cefa}).
@@
 Note that the original AutomatArk benchmark suite \cite{z3str3re} includes 19,979 instances, which are conjunctions of regular membership queries generated out of regular expressions in \cite{automatark}.
-%Only 8,751 contain counting operators out of 19,979 instances.
 
+\medskip
+\noindent
+\denghang{
+\emph{Large-Bounds part.} This benchmark suite is composed of 1,969 problem instances with large counting bounds (greater than or equal to $50$) from RegCoL and AutomatArk benchmark suites.  
+%regex with upper bound greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total). 
+Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
+}
 %%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
@@
 \vspace{-2mm}
-\subsection{Experiment Results}
+\subsection{Overall Evaluation}\label{subsec:overall_eval}
 \vspace{-1mm}
@@
 
-\medskip
-\noindent
-\emph{Overall evaluation.} 
+% \medskip
+% \noindent
+% \emph{Overall evaluation.} 
 The experiment results can be found in Table~\ref{tab:results_regcol}.
@@
 Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93s}/1.62s).
+\denghang{To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.}
 
@@
       \import{tables}{table_simp.tex}
-      \caption{Evaluation of the automata size-reduction techniques, with timeout = 60 seconds.}
+      \caption{Evaluation of the size-reduction techniques, with timeout = 60 seconds.}
       \label{tab:results_simp}
@@
   \vspace{-2mm}
-  \caption{Experiment results}
+  \caption{Overall evaluation and the evaluation of the size-reduction techniques}
   \vspace{-8mm}
@@
 
-\smallskip
-\noindent
-\emph{Evaluation on problem instances with large bounds.}
+\subsection{Evaluation on problem instances with large bounds}\label{subsec:large_bounds_eval}
+% \smallskip
+% \noindent
+% \emph{Evaluation on problem instances with large bounds.}
 %
-We extract the 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
+\sout{We extract the 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
 %regex with upper bound greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total). 
-Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
+Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.}
 %
@@
     \vspace{4.5mm}
-    \caption{Experiment results for large bounds, \\with timeout = 60 seconds.}
+    \caption{Experiment results on Large-Bounds part, with timeout = 60 seconds.}
     \label{fig:table_large_count}
@@
 
-We then evaluate the performance of $\ostrichrecl$ on these 1,969 instances. 
+We evaluate the performance of $\ostrichrecl$ on 1,969 instances of the Large-Bounds part. 
 The experiment results are put in Fig~\ref{fig:table_large_count}.
@@
 Moreover, $\ostrichrecl$ is \textbf{ 6.79/2.88/2.61/5.27/3.95} times faster than CVC5/ Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+\denghang{To answer \textbf{Q2}, we can see that $\ostrichrecl$ is far more efficient than the other solvers on problem instances with large bounds.
+\textbf{It is because the complexity in our decision procedure is irrelevant to counting bounds}, while the complexity of other solvers is linear or even exponential to counting bounds.}
 
-\medskip
-\noindent 
-\emph{Evaluation of the effectiveness of the automata size-reduction techniques.}
+\subsection{Evaluation of the effectiveness of size-reduction techniques}\label{subsec:size_reduction_eval}
+% \medskip
+% \noindent 
+% \emph{Evaluation of the effectiveness of the automata size-reduction techniques.}
 We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
@@
 %$\ostrichrecl_{\rm -SIMP}$ is the tool without simplification techniques. $\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques. 
-From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$, which shows that the size-reduction techniques indeed play a vital role in the performance improvement.
+From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$.
+\denghang{To answer \textbf{Q3}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}}.
 Moreover, $\ostrichrecl$ solves \textbf{1,798 more} instances and is \textbf{3.13} times faster than $\ostrichrecl_{\rm NUXMV}$.
+\denghang{To answer \textbf{Q4}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}}.
 

### 2023-10-18 2023-1-19/sections/introduction.tex
all review finished

@@
 Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade, e.g.,
-Z3seq~\cite{z3seq}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
+Z3seq~\cite{Z3-seq}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
 Z3-Trau~\cite{Z3-trau}\cite{z3trau}, OSTRICH~\cite{CHL+19}, Slent~\cite{WC+18}, among many others.
@@
 \cite{WC+18,atva2020,z3str3re}.
-\denghang{Rule-based string solvers like Z3str/2/3/4 and CVC4/5 are incapable of handling regexes with counting and complementary, even for the simple constraint $x\in [0-8]^{\{1,200\}}\wedge x\not\in [0-9]^+$.
+\denghang{Rule-based string solvers like Z3str/2/3/4/sequences and CVC4/5 are incapable of handling regexes with counting and complementary, even for the simple constraint $x\in [0-8]^{\{1,200\}}\wedge x\not\in [0-9]^+$.
 Automata-based string solvers like Z3Str3RE and Ostrich can solve it, but they are inefficient because they have to build automata by unwinding counting operator, resulting in an automaton with more than $1800$ states for regex $[0-8]^{\{1,200\}}$.

### 2023-10-18 2023-1-19/sections/cefa.tex
all review finished

@@
 The following section will use these three operations to solve RECL constraints.
-\denghang{Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than symbolic register automata~\cite{sra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.}
+\denghang{Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than symbolic register automata~\cite{sra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting condition is attached to each automaton, not each final state.}
 

### 2023-10-18 2023-1-19/sections/implementation.tex
all review finished

@@
   \item [Q1:] Are our decision procedure more efficient than the state-of-the-art string constraint solvers on RECL constraints? (Sec \ref{subsec:overall_eval})
-  \item [Q2:] Why our decision procedure is more efficient?(Sec \ref{subsec:large_bounds_eval})
-  \item [Q3:] Are the size-reduction techniques practical?(Sec \ref{subsec:size_reduction_eval})
-  \item [Q4:] How effective is the algorithm for solving the nonemptiness problem compared to the case that uses the nuXmv model checker? (Sec \ref{subsec:size_reduction_eval})
+  \item [Q2:] Why is our decision procedure more efficient? (Sec \ref{subsec:large_bounds_eval})
+  \item [Q3:] Are the size-reduction techniques practical? (Sec \ref{subsec:size_reduction_eval})
+  \item [Q4:] How effective is the algorithm for solving the nonemptiness problem compared to the case that uses the nuXmv model checker~\cite{atva2020}? (Sec \ref{subsec:size_reduction_eval})
 \end{itemize}
@@
 Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}.
-\denghang{Other industrial benchmarks suites are not utilized because they contains no counting operator.} There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
+\denghang{Other industrial benchmarks suites are not utilized because they contains no counting operators.} There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
 Moreover, it turns out that only 5\% of regexes among the 48,843 instances are non-register-representable (see Section~\ref{subsec:regex2cefa}).
@@
 Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
-Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, \denghang{and the results distinct to the ground truth are called \emph{soundness errors} in the result table.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, \denghang{and the results distinct to the ground truth are called \emph{soundness errors}.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
 The number is %3,994/2,272/24,577/12,832/1,091/7,092

### 2023-10-18 2023-1-19/sections/introduction.tex
all review finished

@@
 \denghang{Rule-based string solvers like Z3str/2/3/4/sequences and CVC4/5 are incapable of handling regexes with counting and complementary, even for the simple constraint $x\in [0-8]^{\{1,200\}}\wedge x\not\in [0-9]^+$.
-Automata-based string solvers like Z3Str3RE and Ostrich can solve it, but they are inefficient because they have to build automata by unwinding counting operator, resulting in an automaton with more than $1800$ states for regex $[0-8]^{\{1,200\}}$.
+Automata-based string solvers like Z3Str3RE and Ostrich can solve it, but they are inefficient because they have to build automata by unwinding counting operator, resulting in state explosion problem.
 Moreover, the counting operator is not supported by string solvers Z3-Trau and Slent.}

### 2023-10-19 2023-1-19/sections/algorithms.tex
some updates

@@
 \noindent
-\emph{Step 1.} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
+\emph{Step 1.\denghang{(Intersection)}} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
 
@@
 the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the final output $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
-Therefore, we propose the following size-reduction technique for the NFA $\cU_{\cB_i}$'s.
+\sout{Therefore, we propose the following size-reduction technique for the NFA $\cU_{\cB_i}$'s.} \denghang{Regardless of alphabet, we take register updates as new alphabet symbols and $\myvec{0}$ as $\epsilon$ symbol.
+Then we are capable of using standard minimization to reduce the automata size.}
 
@@
 \noindent
-\emph{Step 2.} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, and remove the $\varepsilon$-transitions from $\cU_{\cB_i}$.
+\emph{Step 2.\denghang{(Automata size reduction)}} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, and remove the $\varepsilon$-transitions from $\cU_{\cB_i}$.
 Then we determinize and minimize the resulting NFA.
@@
 \noindent
-\emph{Step 3.} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+\emph{Step 3.\denghang{(Parikh image)}} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
 Then we solve the satisfiability of the following formula,

### 2023-10-19 2023-1-19/sections/cefa.tex
some updates

--- 2023-10-18 2023-1-19/sections/cefa.tex
@@
 The following section will use these three operations to solve RECL constraints.
-\denghang{Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than symbolic register automata~\cite{sra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.}
+\denghang{Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than register automata~\cite{ra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting condition is attached to each automaton, not each final state.}
 

### 2023-10-19 2023-1-19/sections/implementation.tex
some updates

@@
 \begin{itemize}
-  \item [Q1:] Are our decision procedure more efficient than the state-of-the-art string constraint solvers on RECL constraints? (Sec \ref{subsec:overall_eval})
-  \item [Q2:] Why is our decision procedure more efficient? (Sec \ref{subsec:large_bounds_eval})
-  \item [Q3:] Are the size-reduction techniques practical? (Sec \ref{subsec:size_reduction_eval})
-  \item [Q4:] How effective is the algorithm for solving the nonemptiness problem compared to the case that uses the nuXmv model checker~\cite{atva2020}? (Sec \ref{subsec:size_reduction_eval})
+  \item [Q1:] Does the decision procedure perform well~(Sec \ref{subsec:overall_eval}), especially when the counting bounds are large?~(Sec \ref{subsec:large_bounds_eval})
+  \item [Q2:] Are the size-reduction techniques practical?~(Sec \ref{subsec:size_reduction_eval})
+  \item [Q3:] How effective is the algorithm for solving the nonemptiness problem compared to the case that uses the nuXmv model checker~\cite{atva2020}?~(Sec \ref{subsec:size_reduction_eval})
 \end{itemize}
@@
 Moreover, $\ostrichrecl$ is \textbf{ 6.79/2.88/2.61/5.27/3.95} times faster than CVC5/ Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-\denghang{To answer \textbf{Q2}, we can see that $\ostrichrecl$ is far more efficient than the other solvers on problem instances with large bounds.
-\textbf{It is because the complexity in our decision procedure is irrelevant to counting bounds}, while the complexity of other solvers is linear or even exponential to counting bounds.}
+\denghang{To answer \textbf{Q1}, we can see that $\ostrichrecl$ \textbf{is far more efficient than the other solvers on problem instances with large bounds.}}
 
@@
 From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$.
-\denghang{To answer \textbf{Q3}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}}.
+\denghang{To answer \textbf{Q2}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}}.
 Moreover, $\ostrichrecl$ solves \textbf{1,798 more} instances and is \textbf{3.13} times faster than $\ostrichrecl_{\rm NUXMV}$.
-\denghang{To answer \textbf{Q4}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}}.
+\denghang{To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}}.
 

### 2023-10-19 2023-1-19/sections/introduction.tex
some updates

--- 2023-10-17 2023-1-19/sections/introduction.tex
@@
 Nevertheless, the nonemptiness problem of these automata was not considered, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
+\denghang{For the automata model, the definition of registers of CEFAs resembles the counters of the counter automata class~\cite{GGM12,redos_lenka,HS+23,GKM23}, but CEFAs contain no guards in each transition.
+Register automata~\cite{ra} and symbolic register automata~\cite{sra} utilize registers to store input variables (i.e., the letters of the alphabet), on which only equality and inequality are permitted.
+In contrast, CEFAs utilize registers to store integers constrained by linear arithmetic formulae.}
 Real-world regexes in programming languages include features beyond classical regular expressions, e.g., the greedy/lazy Kleene star, capturing groups, and back references.
-\denghang{Symbolic register automata\cite{sra} are raised to handle back references.} Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
-Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22} \denghang{and \cite{sra}}.
-Solving string constraints involving lengths has also been investigated by various researchers, see e.g.
-\cite{WC+18,atva2020,z3str3re}.
-\denghang{Rule-based string solvers like Z3str/2/3/4 and CVC4/5 are incapable of handling regexes with counting and complementary, even for the simple constraint $x\in [0-8]^{\{1,200\}}\wedge x\not\in [0-9]^+$.
-Automata-based string solvers like Z3Str3RE and Ostrich can solve it, but they are inefficient because they have to build automata by unwinding counting operator, resulting in an automaton with more than $1800$ states for regex $[0-8]^{\{1,200\}}$.
-Moreover, the counting operator is not supported by string solvers Z3-Trau and Slent.}
+Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
+Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22}.
+\sout{Solving string constraints involving lengths has also been investigated by various researchers, see e.g.
+\cite{WC+18,atva2020,z3str3re}.} \denghang{Except for the string solvers mentioned before, some related works about string constraints with the length function exist.
+Trau~\cite{z3trau} relies on a Counter-Example Guided Abstraction Refinement (CEGAR) framework in which the under- and over-approximation of the automata are iteratively refined to solve length and regex constraints.
+Slent~\cite{WC+18} transfers the string and length constraints to length-encoded automata, and leverages a symbolic model checker as an engine for the emptiness checking of automata.
+However, both Trau and Slent do not support counting operators.}
 

### 2023-10-19 2023-1-19/sections/algorithms.tex
remove comments

@@
 %!TEX root = ../main.tex
-%\documentclass{standalone}
-%\begin{document}
 
@@
 
-% \vspace{-2mm}
 \begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula
-% \footnote{The decision problem was called satisfiability of an LIA formula w.r.t. CEFA in \cite{atva2020}.}
 , abbreviated as $\cefadec$]
@@
 $\varphi$ if there are assignments $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{i,j}}$
-%$\myvec{v_{1,1}}, \cdots, \myvec{v_{1, l_1}}, \cdots, \myvec{v_{n, 1}}, \cdots, \myvec{v_{n, l_n}}$ 
 such that $(\theta(x_i); \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ and  $\varphi[(\myvec{v_{i,j}}/R_{\aut_{i,j}})]$ is true, for every $i \in [n], j \in [l_i]$.
-% \in \aut_{i,1}(\eta(x_1)), \cdots, \myvec{v_{i, l_i}} \in \aut_{i,l_i}(\eta(x_i))$ for every $i \in [n]$  
-%\cdots, \myvec{v_{n,1}} \in \aut_{n,1}(w_n), \cdots, \myvec{v_{n, l_n}} \in \aut_{n, l_n}(w_n)$ 
-% $\varphi[(\myvec{v_{i,j}}/R_{\aut_{i,j}})_{i \in [n], j \in [l_i]}]$ is true. 
-%$\varphi[\myvec{v_{1,1}}/R_{\aut_{1,1}}, \cdots, \myvec{v_{n, l_n}}/R_{\aut_{n, l_n}}]$ is true. 
 \end{definition}
-% \vspace{-4mm}
 \begin{proposition}\label{prop-cefadec}
@@
 
-%As mentioned in Section \ref{sec:overview}, the main idea of our approach is to model the counting operators symbolically by registers instead of unfolding them explicitly.
-Additionally, we use registers to represent string lengths.
-After that, the satisfiability of string constraints involves regex-counting, and string-length is reduced to the satisfiability of LIA, which off-the-shelf SMT solvers can solve.
-We also propose techniques to reduce automata sizes and utilize under approximations to enhance performance.
-\vspace{-2mm}
 \subsection{From $\reclsat$ to $\cefadec$} \label{subsec:regex2cefa}
-\vspace{-1mm}
 
@@
 Let $e$ be a register-representable regular expression over $\Sigma$. By the following procedure, we will construct a CEFA out of $e$, denoted by $\aut_e$. 
-\vspace{-1mm}
 \begin{enumerate}
@@
 %
-\vspace{-3mm}
 $$
@@
 \item For each maximal sub-expression $e'$ of $e$ such that $e'$ contains no occurrences of counting operators, an NFA $\aut_{e'}$ can be constructed by structural induction on the syntax of $e'$. 
-%Without loss of generality,  we assume that $R_{\aut_{e'_1}} \cap R_{\aut_{e'_2}} = \emptyset$. 
 Then we have $\aut_{e'} = \aut_{e'_1} \concat \aut_{e'_2}$, $\aut_{e'} = \aut_{e'_1} \cup \aut_{e'_2}$, or $\aut_{e'} = \aut_{e'_1} \cap \aut_{e'_2}$. 
 \end{enumerate}
-
-%\begin{example}
-%an example here
-%\end{example}
 
@@
 
-%%%%%%%%%%% original texts by denghang %%%%%
-%%%%%%%%%%% original texts by denghang %%%%%
-\hide{
-The most important point of our approach is encoding counting operators by registers rather than explicitly unfolding them.
-In this section, we discuss the encoding in detail.
-A counting operator is called \emph{handled} if it is not the sub-regex of complement, closure, or another counting, and called \emph{unhandled} otherwise.
-For example, $(\Sigma \setminus a)^{\{m,n\}}$ is handled, while $((\Sigma \setminus a)^{\{m,n\}})^*$ is unhandled.
-We first discuss the encoding of handled counting operators and then the encoding of unhandled counting operators.
-
-% We must syntactically rewrite bounded repetition $\regex\{m,n\}$ if it is the sub-regex of complement (e.g., $(\regex\{m,n\})^C$), closure(e.g., $(\regex\{m,n\})^*$), and bounded repetition(e.g., $(\regex\{m,n\})\{m', n'\}$), we unwind it to $\regex^m\mid\cdots\mid\regex^n$.
-After this syntactic rewriting, we call the resulting regex $\regex'$ \emph{non-nested}.
-Given a regex $\regex$ without an unhandled counting operator, the base case is constructing the CEFA of a single character, an empty string, or an empty language.
-The inductive step is constructing CEFA of the concatenation, union, intersection, closure, complement, and counting of CEFA(s) of sub-regex(es).
-Operations except for counting are trivial and represented in Appendix \ref{appendix:cefa}; we only illustrate counting here.
-
-Given a regex $\regex^{\{m,n\}}$ without unhandled counting operator, suppose the NFA recognizing $\regex$ is $\aut = (Q,\Sigma,\delta,q_I,F)$, then the CEFA recognizing $\regex^{\{m,n\}}$ is defined as $\aut_{m,n} = (Q, \Sigma, \delta',q_I, F\cup\{q_I\}, r, \theta)$ where:
-\begin{itemize}
-  \item $q_I$ is set to accepting state,
-  \item $r$ is a new register,
-  \item $\delta'$ is composed by transition $q\xrightarrow[(0)]{a} q'$ for each transition $q\xrightarrow[()]{a} q' \in \delta$, and transition $q_f\xrightarrow[(1)]{\epsilon} q_I$ for each accepting state $q_f\in F$,
-  \item $\theta$ is the function mapping each accepting state to the same linear integer arithmetic $(m\leq )r\leq n$. The lower bound $m\leq r$ is unnecessary if $q_I\in F$.
-\end{itemize}
-The main idea is to add an epsilon transition to the initial state from each accepting state, like closure, to repeat the sub-regex.
-Then the counting time is incremented by 1 when the epsilon transition is invoked.
-Details are illustrated in Fig.\ref{fig:construct_repetition}.
-A new register $r$ is added to store the counting times.
-The transition $q\xrightarrow[(1)]{\epsilon} q_I$ is constructed to increment the counting times.
-The accepting condition $(m\leq) r\leq n$ is attached to each accepting state to constrain the counting times of the accepting word.
-After the construction, we need to eliminate epsilon transitions.
-It is done by adding transition $q_f\xrightarrow[(1)]{a} q$ for transition $q_I\xrightarrow[(0)]{a} q$ and then deleting the transition $q_f\xrightarrow[(1)]{\epsilon} q_I$, for each accepting state $q_f$.
-
-\begin{figure}[h]
-  \begin{subfigure}[b]{0.49\textwidth}
-    \centering
-    \begin{tikzpicture}[
-      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      initial text=, every state/.style={minimum size = 0.001cm},
-      ]
-
-      \node[state,initial]            (q_0)                      {};
-      \node[state, accepting]         (q_1) [right=of q_0]       {};
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The NFA recognizing $\regex$}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \centering
-    \begin{tikzpicture}[
-      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      initial text=, every state/.style={minimum size = 0.001cm},
-      accepting text=
-      ]
-
-      \node at (-0.5,0.5) {$\scriptstyle (\myemph{m}\leq) r\leq \myemph{n}$};
-      \node[state,initial,accepting]            (q_0)                      {};
-      \node[state, accepting]         (q_1) [right=of q_0]       {};
-      \path[->] (q_1) edge[bend right]   node    [above] {\myemph{$\scriptstyle \mathbf{\epsilon:(1)}$}} (q_0);
-      \node [fit=(q_0) (q_1)] {$\cdots$};
-    \end{tikzpicture}
-    \caption{The CEFA recognizing $\regex^{\{m,n\}}$}
-  \end{subfigure}
-  \caption{The construction of counting operator}
-  \label{fig:construct_repetition}
-\end{figure}
-\begin{example}
-  To construct the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ with alphabet $\Sigma = \{a,b,c\}$.
-As shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}, the base cases are the constructions of character $b$ (Fig.\ref{subfig:count_aut_b}) and $c$ (Fig.\ref{subfig:count_aut_c}).
-The first inductive step is building their union (Fig.\ref{sub@subfig:count_aut_sigma_minus_a}).
-The second inductive step is to add counting information on the automaton.
-To do that we add a new register $r$ to save counting times,  transitions $q_2\xrightarrow[(1)]{\epsilon} q_0$ and $q_1\xrightarrow[(1)]{\epsilon} q_0$  to update the counting times.
-The accepting condition of each accepting state is $5\leq r\leq 60$, which ensures the accepting word's counting time is in the range $[5,60]$.
-After epsilon elimination we get the CEFA recognizing $(\Sigma\setminus a)\{5,60\}$ (shown in Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}).
-  \begin{figure}[h]
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        ]
-        \node[state,initial]            (q_0)                      {$\scriptstyle q_0$};
-        \node[state,accepting]                    (q_1) [right=of q_0]       {$\scriptstyle q_1$};
-
-        \path[->] (q_0) edge              node      [above]           {$\scriptstyle b:()$} (q_1);
-      \end{tikzpicture}
-      \caption{The NFA recognizing $b$}
-      \label{subfig:count_aut_b}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        ]
-        \node[state,initial]            (q_0)                      {$\scriptstyle q_0$};
-        \node[state,accepting]                    (q_1) [right=of q_0]       {$\scriptstyle q_2$};
-
-        \path[->] (q_0) edge              node      [above]           {$\scriptstyle c:()$} (q_1);
-      \end{tikzpicture}
-      \caption{The NFA recognizing $c$}
-      \label{subfig:count_aut_c}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        ]
-        \node[state,initial]      (q_0)                      {$\scriptstyle q_0$};
-        \node (q_tmp) [right=of q_0]       {};
-        \node[state, accepting]   (q_1) [above=of q_tmp]       {$\scriptstyle q_1$};
-        \node[state, accepting]   (q_2) [below=of q_tmp]       {$\scriptstyle q_2$};
-
-        \path[->] (q_0) edge node [right] {$\scriptstyle b:()$} (q_1)
-        (q_0) edge           node [right] {$\scriptstyle c:()$} (q_2);
-      \end{tikzpicture}
-      \caption{The NFA recognizing $\Sigma \setminus a$}
-      \label{subfig:count_aut_sigma_minus_a}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.005cm},
-        ]
-        \node at (-1, 1) {$\scriptstyle \myemph{5}\leq r \leq \myemph{60}$};
-        \node[state,initial, accepting]      (q_0)                      {$\scriptstyle q_0$};
-        \node (q_tmp) [right=of q_0]       {};
-        \node[state, accepting]   (q_1) [above=of q_tmp]       {$\scriptstyle q_1$};
-        \node[state, accepting]   (q_2) [below=of q_tmp]       {$\scriptstyle q_2$};
-
-        \path[->] (q_0) edge node [right] {$\scriptstyle b:(0)$} (q_1)
-        (q_1) edge [loop right] node {$\scriptstyle b:(\myemph{1})$} (q_1)
-        (q_0) edge           node [right] {$\scriptstyle c:(0)$} (q_2)
-        (q_2) edge [loop right] node {$\scriptstyle c:(\myemph{1})$} (q_0);
-      \end{tikzpicture}
-      \caption{The CEFA recognizing $(\Sigma\setminus a)\{\myemph{5},\myemph{60}\}$}
-      \label{subfig:count_aut_sigma_minus_a_5_60}
-    \end{subfigure}
-    \caption{The example of constructing regex with counting}
-  \end{figure}
-\end{example}
-
-Above discusses the construction of handled counting operators.
-In the same way, we can not construct the unhandled counting operator.
-For example, for the regex $(ab^{\{1,100\}})*$ with unhandled counting operator, there are infinite repetitions of $ab^{\{1,100\}}$.
-The counting times of each repetition are irrelevant, so we can not represent them using finite registers.
-We must syntactically rewrite the unhandled counting operator into union and concatenation operators.
-More exactly, the sub-regex $\regex^{\{m,n\}}$ in the unhandled regex is rewritten into $\underbrace{\regex\cdot\regex\cdots\regex}_{m \text{ times}}\mid\cdots\mid \underbrace{\regex\cdot\regex\cdots\regex}_{n \text{ times}}$.
-% Based on the decision procedure defined in the paper \cite{atva2020}, we propose an efficient algorithm to solve ESL formula $\varphi\wedge \psi$ where $\varphi$ is the conjunction of literals and $\psi$ is the conjunction of linear literals without length operation.
-For each string variable $x$, we first compute pre-images of all linear literal $i=|x|$.
-Then we generate CEFAs of all regular expressions $\regex$ in all regular literals $x\in \regex$ and intersect these CEFAs and pre-images to get the final automaton $\aut_x$ for $x$.
-There is a final CEFA for each string variable $x$.
-The linear arithmetic constraint $\psi$ restricts the accepting word of final CEFAs.
-Thus the satisfiability problem is the emptiness checking problem of final CEFAs under $\psi$.
-If it is empty, the string constraints are unsatisfiable.
-Otherwise, the string constraints are satisfiable.
-% The emptiness checking problem of CEFAs under linear integer arithmetic is theoretically pspace-complete\cite{atva2020}.
-To solve it efficiently for a practical example, we develop heuristic ways such as under-approximation (Section \ref{subsec:under-approx}) and symbolic-aware simplification (Section \ref{subsec:simplify}).
-
-%\subsection{Handling of String-length}
-Given a string-length constraint, we build a CEFA with a register storing the word length.
-Namely, the CEFA is $(\{q_I\}, \Sigma, \{q_I\xrightarrow[(1)]{\Sigma} q_I\}, q_I, \{q_I\}, r, \theta)$ where accpeting condition $\theta$ is based on the length formula.
-As an illustration, example \ref{eg:pre_len} shows the CEFA of length constraints $|x| > 120$, whose language is the set of all words with a length greater than $120$.
-The simple loop $q_I\xrightarrow[(1)]{\Sigma} q_I$ increase $1$ on register $r$ for all char in $\Sigma$, so that the value of $r$ is equal to the length of the accepting word.
-The accepting condition $\theta$ attaches $q_I$ to $r > 120$, ensuring the length of the accepting word is greater than $120$.
-
-% The formal definition of pre-images of abundant string functions is listed in \cite{atva2020}, and we do not repeat it here.
-\begin{example}[The CEFA of $|x| > 120$]\label{eg:pre_len} 
-  \begin{figure}[h]
-    \centering
-    \begin{tikzpicture}[
-      shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-      initial text=, every state/.style={minimum size = 0.001cm},
-      ]
-
-      \node at (-0.5, 0.5) {$\scriptstyle r > 120$};
-      \node[state,initial,accepting]            (q_0)       {$\scriptstyle q_I$};
-
-      \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma:(1)$} ();
-    \end{tikzpicture}
-  \end{figure}
-\end{example} 
-% \subsection{Combine Regex-counting and String-length}
-% In the previous section, we discussed the construction of the regex-counting operator and string-length constraint. In this section, we show how to combine them. 
-% \begin{definition} [The Product of Two CEFA]
-
-%   Given two CEFAs $\aut_1 = (Q_1, \Sigma, \delta_1, q_{I_1}, F_1, R_1, \theta_1)$ and $\aut_2 = (Q_2, \Sigma, \delta_2, q_{I_2}, F_2, R_2, \theta_2)$ with $R_1\cap R_2 = \emptyset$, the product of them, denoted by $\aut_1 \times \aut_2$, is defined as $(Q_1\times Q_2, \Sigma, \delta, (q_{I_1}, q_{I_2}), F_1\times F_2, R_1\cup R_2, \theta)$ where
-%   \begin{itemize}
-%     \item $\delta$ comprises the tuples $((q_1, q_2), a, (q_1', q_2'), \myvec{v_1}\cdot \myvec{v_2})$ such that $(q_1, a, q_1', \myvec{v_1})\in \delta_1$ and $(q_2, a, q_2', \myvec{v_2})\in \delta_2$.
-%     \item $\theta((q_1, q_2))$ is $\theta_1(q_1)\wedge \theta_2(q_2)$ for each accepting state $(q_1, q_2)\in F_1\times F_2$.
-%   \end{itemize}
-% \end{definition}
-% With the help of product, we can combine the CEFAs of regex-counting and string-length.
-For example, the CEFA of $x$ in the string constraints $x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c \wedge |x| > 120$ is the product of the CEFA of regex $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, the CEFA of regex $\Sigma^*$ and the CEFA of length constraints $|x| > 120$.
-}
-%%%%%%%%%%% original texts by denghang %%%%%
-%%%%%%%%%%% original texts by denghang %%%%%
-
-\vspace{-2mm}
 \subsection{Solving $\cefadec$} \label{subsec:cefadec}
-\vspace{-1mm}
 
@@
 
-%At first, we compute CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$ for each $i \in [n]$.
-For each $i \in [n]$, let $\Lambda'_{x_i} = \{\cB_i\}$.
-Evidently, $R_{\cB_i}= \bigcup \limits_{j \in [l_i]} R_{\aut_{i, j}}$ for each $i \in [n]$.
 After Step 1, the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
-
-%CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$ 
-%
-
-%Therefore, to solve the nonemptiness of CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ w.r.t. $\varphi$, it is sufficient to compute $\cefaout(\cB_1)$
-
-%Since the construction of $\cB_1, \cdots, \cB_n$ involves the computation of the product of multiple CEFA, it incurs an exponential blow-up in the worst case.
-Therefore, it is vital to reduce the sizes of these CEFAs.
-In the sequel, we propose some techniques to reduce the automata sizes.
 
@@
 
-\vspace{-2mm}
 \begin{observation}\label{obs-cefa-output}
@@
 \end{observation}
-\vspace{-1mm}
-
-%From the fact that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA, we deduce that the following two conditions are equivalent.  
-%\begin{itemize}
-%\item CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$, namely, 
-%there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{1}}, \cdots, \myvec{v_{n}}$ such that $(\theta(x_1); \myvec{v_1}) \in \Lang(\cB_1)$, $\cdots$, $(\theta(x_n); \myvec{v_n}) \in \Lang(\cB_n)$ and $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true,
-%
-%\item there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true.
-%\end{itemize}
 
@@
 
-\vspace{-2mm}
 \begin{observation}\label{obs-cefa-nfa}
@@
 \end{observation}
-\vspace{-1mm}
 
@@
 \begin{itemize}
-%\item CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$, namely, 
-%there are an assignment $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{1}}, \cdots, \myvec{v_{n}}$ such that $(\theta(x_1); \myvec{v_1}) \in \Lang(\cB_1)$, $\cdots$, $(\theta(x_n); \myvec{v_n}) \in \Lang(\cB_n)$ and $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true,
-%
+
 \item there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true, 
-%CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t. $\varphi$ 
-%
 \item 
 there are $\eta_1 \in \parikh(\cU_{\cB_1}), \cdots, \eta_n \in \parikh(\cU_{\cB_n})$ such that 
-%
-%\begin{equation}\label{eqn-cefa-lia}
 \[
@@
 \]
-%\end{equation} 
-%
 is true. 
@@
 $\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ to represent the Parikh images of $\cU_{\cB_1}$, $\cdots$, $\cU_{\cB_n}$ respectively, where $\fZ_{\costset_{\cB_i}} = \{\anivarz_{i,\myvec{v}} \mid \myvec{v} \in \costset_{\cB_i}\}$ for $i \in [n]$, and solve the satisfiability of the following existential LIA formula
-%
-%\begin{equation}\label{eqn-cefa-lia}
 \[
 \begin{array}{l}
-%\scriptsize
 \bigwedge \limits_{i \in [n]} \left(\psi_{\cU_{\cB_i}}(\fZ_{\costset_{\cB_i}}) \wedge \alpha_i\left[\sum\limits_{\myvec{v} \in \costset_{\cB_i}} \anivarz_{i, \myvec{v}} \myvec{v} \big{/}R_{\cB_i}  \right] \right)\  \wedge \\
@@
 \]
-%\end{equation}
 Intuitively, the integer variables $\anivarz_{i, \myvec{v}}$ represent the number of occurrences of $\myvec{v}$ in the strings accepted by $\cU_{\cB_i}$.
-%where $\anivarz_{\myvec{v}}$'s are integer variables to represent the number of occurrences of $\myvec{v}$.
 
@@
 %
-\vspace{-1mm}
 \[
@@
 \]
-\vspace{-1mm}
 \qed
-%\[
-%\bigwedge \limits_{i \in [n]} \psi_{\cC_i}(\fZ_{\costset_{\cB_i}}) \wedge 
-%\varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cB_1}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cB_n}} \anivarz_{\myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
-%\]
-
-% Finally, although we propose techniques to reduce the sizes of $\cU_{\cB_i}$'s, it is still relatively expensive to compute LIA formulas from $\cC_i$'s and solve their satisfiability, especially for those satisfiable problem instances, namely, those instances where CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty w.r.t.
-$\varphi$.
-% Therefore, in the sequel, we propose a heuristic to search for solutions by utilizing under approximations, to be executed before Step 3.
-Intuitively, we search for solutions by bounding the lengths of the strings that are accepted by $\cC_i$'s.
-The heuristic uses a constant bound $B > 0$ and searches for solutions incrementally, starting from strings of length $0$.
-Since the heuristic is executed after Step 2 and before Step 3, we call it Step 2.5.
-
-% For $i \in [n]$, suppose $R_{\cB_i} = (r_{i,1},\cdots, r_{i, k_i})$ and $\cC_i = (Q'_i, \costset_{\cC_i}, \delta'_i, q_{i,0}, F'_i)$.
-
-% \paragraph*{Step 2.5.} Initially, let $len := 0$, and for each $i \in [n]$, let 
-% %$\confset_{\cC_i}:=\emptyset$, 
-% $\confset_{\cC_i}:=\{(q_{i,0}, \myvec{0})\}$ 
-% and $\psi_{\cC_i}:= \lfalse$.  Then iterate the following procedure until $len = B+1$.
-% \begin{enumerate}
-% \item Let $\xi: = \bigwedge \limits_{i \in [n]} \alpha_i \wedge \varphi$.
-% %
-% \item For each $i \in [n]$, do the following.
-% \begin{enumerate}
-% \item Let 
-% %$\confset_{\cC_i}:= \confset_{\cC_i} \cup \confset'_{\cC_i}$, 
-% $old_i:=\confset_{\cC_i}$, $\confset_{\cC_i}:=\emptyset$.
-% %
-% \item For each $(q, \myvec{v}) \in old_i$,
-% \begin{enumerate}
-% \item if $q \in F'_i$, then let $\psi_{\cC_i}:=\psi_{\cC_i} \vee (\bigwedge \limits_{j \in [k_i]} r_{i,j} = v_j)$, 
-% %
-% %\item let $\confset'_{\cC_i}:=\confset'_{\cC_i} \setminus \{(q, \myvec{v})\}$, 
-% %
-% \item for each $(q, \myvec{v'}, q') \in \delta'_i$, let $\confset_{\cC_i}:=\confset_{\cC_i} \cup \{(q', \myvec{v}+ \myvec{v'})\}$. 
-% \end{enumerate}
-% %
-% %\item 
-% %
-% \item Let $\xi := \xi \wedge \psi_{\cC_i}$. 
-% \end{enumerate}
-% %
-% \item If $\xi$ is satisfiable, then report $\ltrue$ and the whole algorithm terminates. 
-% %
-% \item Let $len: = len+1$. $\blacksquare$
-% \end{enumerate}
-% Intuitively, for each $i \in [n]$, $\psi_{\cC_i}$ is a global variable whose value is never reset, and it stores the set of ``final'' valuations of registers of $\cC_i$ (that is, the valuations obtained when reaching final states), and $\confset_{\cC_i}$ stores the set of newly discovered (not necessarily final) ``configurations'' of $\cC_i$.
-% %, and $\confset_{\cC_i}$ stores those that have been discovered before. 
-% Note that the solution searching algorithm in Step 2.5 is incremental because when the value of $len$ is incremented, the searching continues from $\confset_{\cC_i}$'s, not from scratch.
-%, whose values are not reset.
-%Furthermore, for each $i \in [n]$, we can remove the redundancy of characters/vectors in $\cC_i$.
-
-%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
-%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
-\hide{
-Moreover, the transitions $(q, \myvec{0}, q')$ in $\cC_i$ can be seen as $\varepsilon$-transitions, that is, we can replace each transition $(q, \myvec{0}, q')$ with $(q, \varepsilon, q')$, without affecting the set $\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}$.
-Therefore, we first do these replacements and apply the $\varepsilon$-transition removal procedure.
-Then we utilize the determinization and minimization algorithm for NFA to reduce the size of $\cC_i$.
-
-It turns out that to solve the non-emptiness of CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ w.r.t.
-$\varphi$.
-We can ignore the characters in $\cB_1,\cdots, \cB_n$ because there is only one CEFA for each string variable, and $\varphi$ only cares about the values of registers.
-
-%When the characters in $\cB_1, \cdots, \cB_n$ are ignored, they can be seen as NFAs. 
-For each $i \in [n]$, let $\cC_i$ be the automaton obtained from $\cB_i$ by replacing each transition $(q, a, q', \myvec{v})$ with $(q, \myvec{v}, q')$. 
-Then for each $i \in [n]$, $\cC_i$ can be seen as an NFA over the alphabet $V_i$, where $V_i$ is the set of vectors $\myvec{v}$ occurring in the transitions $(q, a, q', \myvec{v})$ of $\cB_i$.
-
-Then the set of costs output by $\cB_i$, that is, $\{\myvec{v} \mid (w; \myvec{v}) \in \Lang(\cB_i)\}$ can be reduced to the computation of the Parikh image of $\cC_i$, namely, 
-%
-$$\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}.$$
-
-Moreover, the transitions $(q, \myvec{0}, q')$ in $\cC_i$ can be seen as $\varepsilon$-transitions, that is, we can replace each transition $(q, \myvec{0}, q')$ with $(q, \varepsilon, q')$, without affecting the set $\{ \sum\limits_{\myvec{v} \in V_i} m_{\myvec{v}} \myvec{v} \mid \myvec{m} \in parikh(\cC_i)\}$.
-Therefore, we first do these replacements and apply the $\varepsilon$-transition removal procedure.
-Then we utilize the determinization and minimization algorithm for NFA to reduce the size of $\cC_i$.
-
-Finally, if there are two indices $1 \le i' < j' \le |R_{\cB_i}|$ such that $v_{i'} = v_{j'}$ for each vector $\myvec{v} \in V_i$, then we can remove the $j'$-th component from the characters (vectors) of $\cC_i$, and let $\varphi := \varphi \wedge r_{i, i'} = r_{i, j'}$.
-By abusing the notation, we still use $\cC_i$ to denote the resulting NFA.
-
-By doing this, we reduce the automata sizes.
-Then we compute an LIA formula $\psi_{i}$ from $\cC_i$ to specify the Parikh images of $\cC_i$.
-Then the nonemptiness of $\cB_1, \cdots, \cB_n$ w.r.t.
-$\varphi$ is reduced to the satisfiability of $\psi_1 \wedge \cdots \psi_n \wedge \varphi$.
-
-under approximation
-
-In summary, we obtain an algorithm for solving the non-emptiness of $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$, as illustrated in Figure~\ref{xxx}.
-
-\zhilin{stopped here}
-
-After encoding counting operator and length constraint to CEFAs, there are only automaton memberships $x\in \aut$ and LIA formula $t_1 \ \op \ t_2$ where $\aut$ is CEFA and $t_1, t_2$ are integer terms.
-Let $\psi$ denotes the conjunction of all LIA formulae $t_1\ \op\ t_2$ and $\Lambda_x = \{\aut_x^1, \aut_x^2,\cdots \aut_x^n\}$ denotes the set of CEFAs in the automaton membership $x\in \aut$.
-The emptiness checking problem of $\Lambda_x$ under $\psi$ is the problem that checks whether there exists a word $w$ such that $w\in \aut_x^1, w\in \aut_x^2\cdots w\in \aut_x^n$ and $\psi[\myvec{V}/\myvec{r}]$ holds, where $\myvec{r}$ are all registers and $\myvec{V}$ are corresponding register values in automata of $\Lambda_x$ after running $w$.
-The emptiness problem is \emph{abbreviated as $SAT_{CEFA}[LIA]$ problem}.
-
-As mentioned in \cite{atva2020}, the \emptinessprob{} is theoretically Pspace-complete.
-In previous work, we have used a model-checking tool \emph{nuXmv}\cite{nuxmv} to solve it.
-However, it needs to be more efficient for complex string constraints.
-So we put forward a new framework that brings in symbolic-aware simplification and under-approximation heuristics.
-
-The main idea of our framework is to simplify the input CEFAs firstly and under-approximate the solution of the \emptinessprob{} by adding length bounds on string variables.
-If the under-approximation is satisfiable, the CEFAs are not empty under $\psi$.
-Otherwise, we check the Parikh image of the simplified CEFAs.
-If the Parikh image is satisfiable, the CEFAs are not empty under $\psi$.
-Alternatively, they are empty.
-The framework is \emph{sound} and \emph{complete}.
-
-The framework is shown in Algorithm \ref{alg:emptiness}.
-We simplify the input CEFAs at line 1 because they may have too many transitions and registers to solve.
-The main idea of the simplification is treating the alphabet as unary and the symbolic updates as characters of transitions in the minimization.
-After the simplification, we try to find a solution by under-approximation at line 2 and line 3.
-The under-approximation algorithm explores possible satisfiable register values within a length bound $MaxBound$.
-We return true if it finds a solution because the under-approximation is sound for sat.
-Otherwise, we compute the Parikh images of the simplified CEFAs and check if the Parikh images are satisfiable in conjunction with $\psi$ at line 12.
-The Parikh image checking is complete so that satisfiability implies non-emptiness directly.
-
-The under-approximation program is incremental.
-In other words, it first tries to find a solution with a smaller length bound of each string variable and increments the string length bound if the search for a smaller length bound fails.
-$MaxBound$ is the max length bound we try, empirically set to $15$ in our experiment.
-It should not be too large because of the exponential growth of searching space.
-The details of simplification and under-approximation are shown in Algorithm \ref{alg:simplify}, and the details are shown in Algorithm \ref{alg:underApprox}.
-
-\begin{algorithm}[h]
-  \caption{ $\algfun{nonEmpty}(auts, \psi)$}
-  \label{alg:emptiness}
-  \begin{algorithmic}[1]
-    \Require the CEFAs $auts$ and the linear integer arithmetic $\psi$
-    \Ensure $true$ or $false$
-    \Statex
-    \State $simpliAuts \leftarrow \algfun{simplify}(auts)$
-    % \For{$bound \gets 1, MaxBound$ }
-    % \State $\varphi_{under}\gets \algfun{underApprox}(simpliAuts, bound)$
-    % \If{$\varphi_{under}\wedge \psi$ is sat}
-    % \State \textbf{return} $true$
-    % \EndIf
-    % \EndFor
-    \If{\algfun{underApproxSolve}($simpliAuts, \psi, MaxBound$) is true}
-    \State \textbf{return} $true$
-    \EndIf
-    \State $\varphi \gets \algfun{parikhImage}(simpliAuts)$
-    \If{$\varphi\wedge \psi$ is sat}
-    \State \textbf{return} $true$
-    \Else
-    \State \textbf{return} $false$
-    \EndIf
-  \end{algorithmic}
-\end{algorithm}
-\subsubsection{Symbolic-Aware Simplification} \label{subsec:simplify}
-The purpose of simplification is to remove duplicated transitions and registers.
-In the emptiness checking Algorithm \ref{alg:emptiness}, the non-emptiness equals the reachability of CEFAs.
-The symbolic updates on transitions are meritorious because it influences register values, while the characters are not.
-The alphabet of the CEFA can be ignored (i.e., the alphabet is $\{a\}$), and the vectors can be seen as characters.
-The special vector $\myvec{0}_n$ with only zero elements is seen as a $\epsilon$ character since it does not change the values of registers.
-Namely, given a CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$, we obtain a symbolic NFA  $\aut_{sym} = (Q, \Sigma', \delta', q_I, F)$ where
-\begin{itemize}
-  \item $\Sigma' = \{\myvec{v} \mid \text{there exists one transition in } \aut \text{ with update } \myvec{v}\}$,
-  \item the transition set $\delta'$ is composed of transition $q\xrightarrow{\myvec{v}}q'$ if there is a transition $q\xrightarrow[\myvec{v}]{b} q'$ in $\delta$.
-\end{itemize}
-
- For the symbolic NFA $\aut_{sym}$, we treat $q\xrightarrow{\myvec{0}_n} q'$ as an epsilon transition since it does not change the values of the registers.
-Then we apply the epsilon elimination algorithm \cite{aut_hopcraft} to delete these epsilon transitions.
-After that, we apply the determination and minimization algorithm \cite{aut_hopcraft} of NFAs to $\aut_{sym}$, resulting in a smaller automaton $\aut_{simp}$.
-Finally, we reinterpret $\aut_{simp}$ as a CEFA with the accepting condition of $\aut$ and unary alphabet $\Sigma = \{a\}$.
-Above illustrates functions $\algfun{determinizeByVec}$ and $\algfun{minimizeByVec}$ from line 3 to line 5.
-From line 6 to line 14, we check whether two registers $r_i$ and $r_j$ are duplicated.
-(i.e., the symbolic updates of them are always the same).
-If they are duplicated at line 6, we remove one of them and the corresponding symbolic update from line 8 to line 10.
-After deleting the duplicated registers, we add constraint $r_i = r_j$ to store the value of the deleted register at line 12, ensuring that the value of the deleted register is consistent.
-
-We have the following proposition:
-\begin{proposition}
-  Given a set of CEFAs $\Lambda=\{\aut_1, \cdots, \aut_2\}$ and arbitrary LIA $\psi$, the emptiness of $\Lambda$ on $\psi$ is equal to the emptiness of $\algfun{simplify}(\Lambda)$ on $\psi$.
-\end{proposition}
-\begin{algorithm}[h]
-  \caption{$\algfun{simplify}(auts)$}
-  \label{alg:simplify}
-  \begin{algorithmic}[1]
-    \Require A set of CEFAs
-    \Ensure The simplified CEFAs
-    \Statex
-    \For{$\aut \in auts$}
-    \State Suppose that $\aut = (Q, \Sigma, \delta, q_I, F,
-      R, \theta)$ and $R=(r_1,\cdots, r_n)$
-    \State $\algfun{epsilonElimByVec}(\aut)$
-    \State $\algfun{determinizeByVec}(\aut)$
-    \State $\algfun{minimizeByVec}(\aut)$
-    \ForAll{$(i, j)$ where $1\leq i \leq j \leq n$}
-    \If {$\myvec{v}[i] = \myvec{v}[j]$ for every vector $\myvec{v}\in \aut$ }
-    \State $R\gets(\cdots r_{j-1}r_{j+1}\cdots)$ \Comment remove $r_j$ from the register vector $R$
-    \ForAll{$\myvec{v'}\in \aut$}
-    \State $\myvec{v'}\gets(\cdots\myvec{v'}[j-1]\myvec{v'}[j+1]\cdots)$ \Comment remove $\myvec{v'}[j]$ from each vector $\myvec{v'}$
-    \EndFor
-    \State $\theta \gets\theta\wedge r_i = r_j$
-    \EndIf
-    \EndFor
-    \EndFor
-    \State \textbf{return} $auts$
-  \end{algorithmic}
-\end{algorithm}
-\begin{example}
-  Considering the CEFA (Fig.\ref{subfig:count_aut_sigma_minus_a_5_60}) recognizing $(\Sigma\setminus a)\{1,60\}$ where $\Sigma = \{a,b,c\}$.
-We first obtain a symbolic NFA of it by ignoring the unary alphabet (Fig.\ref{subfig:sigma_minus_a_5_60:simplify}).
-Then we eliminate epsilon transitions $q_0\xrightarrow[]{(0)} q_1$ and $q_0\xrightarrow[]{(0)}q_2$, resulting in the minimized NFA directly.
-Finally, we reinterpret it as CEFA by adding accepting condition $1\leq r \leq 60$(Fig.\ref{subfig:simp_final}).
-  \begin{figure}[h]
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.005cm},
-        ]
-        % \node at (-1, 1) {$\scriptstyle 5\leq r \leq 60$};
-        \node[state,initial, accepting]      (q_0)                      {$\scriptstyle q_0$};
-        \node (q_tmp) [right=of q_0]       {};
-        \node[state, accepting]   (q_1) [above=of q_tmp]       {$\scriptstyle q_1$};
-        \node[state, accepting]   (q_2) [below=of q_tmp]       {$\scriptstyle q_2$};
-
-        \path[->] (q_0) edge node [right] {$(0)$} (q_1)
-        (q_1) edge [loop right] node {$(1)$} (q_1)
-        (q_0) edge           node [right] {$(0)$} (q_2)
-        (q_2) edge [loop right] node {$(1)$} (q_0);
-      \end{tikzpicture}
-      \caption{The symbolic NFA of $\aut_{\Sigma\setminus a\{5,60\}}$}
-      \label{subfig:sigma_minus_a_5_60:simplify}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        ]
-
-        \node at (-0.5, 0.5) {$\scriptstyle 1\leq r \leq 60$};
-        \node[state,initial,accepting]            (q_0)       {$\scriptstyle q_I$};
-
-        \path[->] (q_0) edge [loop below] node{$(1)$} ();
-      \end{tikzpicture}
-      \caption{Simplify the CEFA based on symbolic label}
-      \label{subfig:simp_final}
-    \end{subfigure}
-    \caption{Symbolic simplification removes duplicated transitions and states.}
-    \label{fig:simplification_example}
-  \end{figure}
-
-\end{example}
-\begin{example}
-  Considering the string constraints $i=|x|\wedge j=|x|$.
-We compute the CEFAs of $i=|x|$, $j=|x|$ and intersect them to get the final CEFA represented in Fig.\ref{subfig:duplicate}.
-However, the register $r_1$ and $r_2$ in the final CEFA are duplicated since their symbolic updates are always the same.
-We simplify the CEFA by removing the duplicated register $r_2$ and corresponding symbolic updates, as shown in Fig.\ref{subfig:remove_duplicate}.
-To maintain the value of $r_2$, we add a constraint $r_2=r_1$ in the accepting condition.
-  \begin{figure}[h]
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${\scriptstyle i=r_1\wedge j=r_2 }$, accepting/.style=accepting by arrow,
-        ]
-        \node at (-0.5,0.5) {$R=(r_1, \myemph{r_2})$};
-        \node[state,initial,accepting]            (q_0)       {};
-
-        \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma:(1,\myemph{1})$} ();
-      \end{tikzpicture}
-      \caption{An automaton with duplicated registers}
-      \label{subfig:duplicate}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \centering
-      \begin{tikzpicture}[
-        shorten >=1pt,node distance=1cm,on grid,>={Stealth[round]},
-        initial text=, every state/.style={minimum size = 0.001cm},
-        accepting text=${\scriptstyle i=r_1\wedge j=r_2\wedge \myemph{r_1 = r_2} }$, accepting/.style=accepting by arrow,
-        ]
-
-        \node at (-0.5,0.5) {$R=(r_1)$};
-        \node[state,initial,accepting]            (q_0)       {};
-
-        \path[->] (q_0) edge [loop below] node{$\scriptstyle\Sigma:(1)$} ();
-      \end{tikzpicture}
-      \caption{Remove the duplicated registers and corresponding symbolic updates}
-      \label{subfig:remove_duplicate}
-    \end{subfigure}
-    \caption{Symbolic simplification removes duplicated registers.}
-    \label{fig:duplicate}
-  \end{figure}
-
-\end{example}
-
-\subsubsection{Under-Approximation} \label{subsec:under-approx}
-The purpose of under-approximation is to accelerate the solving process of satisfiable instances.
-With the observation that the accepted string words in practical instances are usually short, we under-approximate the \emptinessprob{} by adding length bounds on string variables.
-The LIA formula representing possible register value is incrementally generated based on the incremental length bounds, and this section discusses its implementation details.
-The main idea is to create an LIA formula enumerating all possible values of registers in accepting runs within some length bounds.
-More detailed, The enumeration is carried out from low to high length bounds, in which the end states and registers' values of the last enumeration are maintained and used in the following enumeration.
-Although the number of possible runs is an exponential growth of the bound, we usually solve practical satisfiable instances within 1s because the lengths of strings in the solution are generally less than 5.
-
-As shown in the Algorithm \ref{alg:underApprox}, $\varphi_{under}$ is the under-approximated LIA formula which is initialized to the input LIA formula $\psi$ at line 2.
-$\varphi_\aut$ is the under-approximated LIA formula of each automaton $\aut$ which is initialized to $false$ at line 3.
-$lastStates$ maps each automaton $\aut$ to the set consisting of pairs of state and corresponding registers' value in the last enumeration.
-$lastStates(\aut)$ is initialized to the pair of the initial state and zero values for each automaton $\aut$ at line 4.
-$length$ is the current bound of lengths of string variables which is initialized to $0$ at line 5.
-The main loop at lines 6-20 iteratively tries possible solutions from low to high length bound.
-For each iteration, we generate the LIA formula respectively for each automaton.
-To each CEFA $\aut$, we get pairs of last state and corresponding registers' values from $lastStates$ at line 8.
-If the last state is accepted at line 9 in each pair, we add the LIA formula of the possible registers' values to $\varphi_\aut$ as a conjunct at line 10.
-After that, we update the set of pairs in $lastStates$ by removing the probed pair at line 12 and adding new pairs of the next state and corresponding registers' values at line 13.
-Finally, we combine the incremental LIA formula of each automaton at line 15.
-If the LIA formula $\varphi\wedge \theta$ is satisfiable at line 17, i.e., we find a solution with all strings having length less than or equal to $length$, we return \emph{true} at line 18.
-Otherwise, the next iteration would be invoked with a larger length.
-If we can not find a solution within the max string length bound, we return \emph{false} at line 22.
-\begin{algorithm}[h]
-  \caption{$\algfun{underApproxSolve}(auts, bound, \psi)$}
-  \label{alg:underApprox}
-  \begin{algorithmic}[1]
-    \Require $auts$: the CEFAs, $bound$: the max string length bound, $\psi$: the LIA formula constraining the CEFAs
-    % \Ensure The linear integer arithmetic $\varphi_{under}$ representing under-approximation of the register values of $auts$
-    \Ensure \emph{true} if finding a solution, \emph{false} otherwise
-    \Statex
-    \State $\theta$ is the conjunction of all accepting conditions of $auts$
-    \State $\varphi_{under}$ is an incremental LIA formula as under approximation, initialized to $\psi$
-    \State $\varphi_\aut$ is an incremental LIA formula for each automaton $\aut$, initialized to $false$
-    \State $lastStates(\aut)$ is the set of (last state, vector's sum) pairs of $\aut$, initialized to $\{(q_I, 0_n)\}$ 
-    \State $length$ is the current bound for string-length, initialized to $0$
-    \While {$length \leq bound$}
-      \For{$\aut \in auts$}
-        \For{$(q, \myvec{V}) \gets lastStates(\aut)$}
-          \If{$q\in F$}
-            \State $\varphi_{\aut} \gets \varphi_{\aut}\vee \bigwedge\limits_{i\in[1,m]} r_i = \myvec{V}[i]$
-          \EndIf
-          \State Remove $(q, \myvec{V})$ from $lastStates(\aut)$
-          \State Add $(q', \myvec{V}+\myvec{v})$ to $lastStates(\aut)$ for each transition $q\xrightarrow[\myvec{v}]{a} q'\in \aut$
-        \EndFor
-        \State $\varphi_{under}\gets \varphi_{under}\wedge\varphi_\aut$
-      \EndFor
-      \If{$\varphi_{under}\wedge \theta$ is satisfiable}
-        \State \textbf{return} \emph{true}
-      \EndIf
-      \State $length \gets length + 1$
-    \EndWhile
-    \State \textbf{return} \emph{false}
-    % \For{$\aut \in auts$}
-    % \State $\varphi_\aut\gets false$ 
-    % \State Suppose $\aut = (Q, \Sigma, \delta, q_I, F, (r_1, \cdots, r_m), \theta)$
-    % \ForAll{run $q_0q_1\cdots q_{n}$ whose length is less than $bound$}
-    % \If{$q_{n}\in F$}
-    % \State Let $\myvec{V}$ to be the sum of the vectors on the run
-    % \State $\varphi_{\aut} \gets \varphi_{\aut} \vee(\theta(q_n)\bigwedge\limits_{i\in[1,m]} r_i = \myvec{V}[i])$
-    % \EndIf
-    % \EndFor
-    % \State $\varphi_{under} \gets \varphi_{under}\wedge \varphi_{\aut}$
-    % \EndFor
-    % \State \textbf{return} $\varphi_{under}$
-  \end{algorithmic}
-\end{algorithm}
-\begin{example}
-  Consider the automaton $\aut$ in Fig.
-\ref{fig:overview:product:reduced} again without the LIA constraint $r_0 > 120$, i.e., $\theta$ changes to $1\leq r_1\leq 60\wedge 1\leq r_2 \leq 60\wedge 0\leq r_3 \leq 60 $.
-The solution of the Parikh image of it leads to a complete but inefficient result since the quantifier-free LIA formulas are solved in exponential time.
-Under-approximation can accelerate the solving process.
-In the first iteration of under-approximation, the pairs in the $lastStates(\aut)$ is the initial pair $(q_0', (0,0,0,0))$ and $\varphi_\aut$ maintains false at line 9 because $q_0'$ is not accepted.
-Then we update $lastStates(\aut)$ by removing the pair $(q_0', (0,0,0,0))$ and adding pairs $(q_0', (1,1,0,0)), (q_1', (1,0,1,0)), (q_2', (1,0,0,0))$.
-In the second iteration, $\varphi_\aut$ changes to $r_0=1\vee r_1=0\vee r_2=0\vee r_3 = 0$ because $q_2'$ is accepted.
-$\varphi_{under}$ is always equal to $\varphi_\aut$ since there is only one automaton.
-We solve the formula $\theta\wedge \varphi_{under}$ and find it is unsatisfiable.
-In the third iteration, the pairs in the $lastStates(\aut)$ with accepting state should be $(q_0', (2,2, 0, 0)), (q_1', (2,1,1,0))$, $(q_1', (2,0,2,0))$, $(q_2', (2,1,0,0)), (q_2', (2,0,1,0)),$ $(q_2', (2,0, 0, 0))$.
-The corresponding registers' values for the accepted state $q_2'$ are $(2,1,0,0), (2, 0, 1, 0), (2, 0, 0, 0)$, in which the value of $r_1$ and $r_2$ can not be both larger than 1 which is required by $\theta$.
-So the formula $\theta\wedge \varphi_{under}$ is still unsatisfiable.
-Finally, We obtain a pair $(q_2', (3,1,1,0))$ from the pair $(q_1', (2,1,1,0))$ and the transition $q_1'\xrightarrow[(1,0,0,0)]{} q_2'$, whose corresponding registers' values is a solution $(3,1,1,0)$, i.e., $r_0=3, r_1=1, r_2=1, r_3=0$.
-\end{example}
-
-\subsection{High-level algorithm}
-
-The pseudocode presented in Algorithm \ref{alg:high} outlines the framework of our solving process.
-We construct the automata of all length operations occurring in the ESL conjunction $\varphi$ at line 3 and the automata of all regular memberships at line 4.
-In the following steps, we call an automaton to be \emph{final} if we will not operate it anymore.
-The set $finalAuts$ contains all final automata for all string variables and is initially empty at line 1.
-The intersection of $\aut_{len}$ and $\aut_{regex}$ at line 5 ensures the final automaton of $x$ reserves both length and regular information.
-At line 6, we compute an NFA form to throw unsat rapidly.
-An NFA form of CEFA is obtained by removing update functions and accepting conditions while maintaining graph structure.
-More exactly, given a CEFA $\aut = (Q,\Sigma, \delta, q_I, F, R, \theta)$, the NFA form of $\aut$ is $(Q, \Sigma, \delta', q_I, F)$ where $\delta'$ is composed of transition $q\xrightarrow[]{a} q'$ for $q\xrightarrow[\myvec{v}]{a} q'\in \delta$.
-The NFA form is an over-approximation of the CEFA, so that unsat is directly thrown if we find the NFA form is already empty at line 7.
-Sometimes the over-approximation is useful.
-For example, to solve the string constraint $x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^* $ which CVC5 has failed on, the NFA form is empty because there is no path to accepting states.
-
-After obtaining all final CEFAs of all string variables and their NFA forms are not empty, we check whether the final CEFAs are empty under the linear integer arithmetic $\psi$ at line 12.
-If they are empty under $\psi$, we return $unsat$.
-Otherwise, we return $sat$.
-
-\begin{algorithm}[h]
-  \caption{High-level algorithm}
-  \label{alg:high}
-  \begin{algorithmic}[1]
-    \Require Conjunction of literals $\varphi$ and conjunction of linear literals $\psi$
-    \Ensure \emph{sat} or \emph{unsat}
-    \Statex
-    \State $finalAuts \leftarrow \emptyset$
-    \ForAll{string variables $x$ occurring in $\varphi$}
-    \State $\aut_{len} \leftarrow$ intersection of all pre-images of $i=|x|$ in $\varphi$
-    \State $\aut_{regex} \leftarrow$ intersection of all CEFAs of $x \in \regex$ in $\varphi$
-    \State $\aut_x \leftarrow$ intersection of $\aut_{len}$ and $\aut_{regex}$
-    \State $\aut_{nfa} \leftarrow$ NFA form of $\aut_x$
-    \If{$\aut_{nfa}$ is empty}
-    \State \textbf{return} \emph{unsat}
-    \EndIf
-    \State $finalAuts \leftarrow finalAuts \cup \{\aut_x\}$
-    \EndFor
-    \If{$\algfun{isEmpty}(finalAuts, \psi)$ }
-    \State \textbf{return} \emph{unsat}
-    \Else
-    \State \textbf{return} \emph{sat}
-    \EndIf
-  \end{algorithmic}
-\end{algorithm}
-}
-%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
-%%%%%%%%%%%% the original texts by Denghang %%%%%%%%%
-
-%\end{document}

### 2023-10-19 2023-1-19/sections/cefa.tex
remove comments

@@
 %!TEX root = ../main.tex
-%\documentclass{standalone}
-%\begin{document}
-
 In this section, we define the cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
@@
 ``write-only'' means that the cost registers can only be written/updated but cannot be read, i.e., they cannot be used to guard the transitions.
-
 %
-%In~\cite{atva2020}, the cost function is defined as a function $\eta: \Sigma \rightarrow \mathbb{N}$.
-In this paper, we define the cost function as an integer vector whose elements are the incremental value of registers.
-Furthermore, we add a new linear integer arithmetic constraint $\theta$ to each final state of the CEFA, which restricts the value of registers.
-Two types of definitions have the same expressive ability on the $SAT_{CL}$ problem.
 \vspace{-0.5mm}
@@
     \item $Q, \Sigma, I, F$ are as in the definition of NFA,
-%    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
     \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers.
-%  set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.
-$(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
     \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
-%    a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
   \end{itemize}
@@
 We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$.
-%The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
-%are attached to final states.
 
 The semantics of CEFA is defined as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
-%A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
-%An \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$ with $q_0 \in I$, where the value of each register is zero. 
 A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$.
@@
 
-%
-%and $\alpha(q_n)[\myvec{\myvec{v'}/\myvec{r}]$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}}$.
-Note here \denghang{that} we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed.
-A string $w$ is \emph{accepted} by $\aut$ if there is an accepting run of $\aut$ on $w$.
-The language defined by $\aut$, denoted by $\Lang(\aut)$, is the set of strings accepted by $\aut$.
-
-%Finally, we define the product of two CEFA.
-
 In the sequel, we define three CEFA operations: union, intersection, and concatenation.
@@
 Moreover, suppose that $R_1 \cap R_2 = \emptyset$ and $Q_1 \cap Q_2 = \emptyset$.
-%We define two operations of CEFA, namely, the product and union, as follows.
 
@@
 \item if $(\epsilon; \myvec{0})$ belongs to $\lan(\aut_1)$ or $\lan(\aut_2)$, i.e., one of the two automata accepts the empty string $\epsilon$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
-%
-%\item otherwise, if $I_2 \cap F_2 \neq \emptyset$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0 \wedge \alpha_2) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$,
-%
 \item otherwise, $F'=F_1 \cup F_2$ and $\alpha' = (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$.
@@
 \item $R' = R_1 \cup R_2$, $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, $\alpha' = \alpha_1 \wedge \alpha_2$, 
-%
-%\item $\alpha'((q_1, q_2)) = \alpha_1(q_1) \wedge \alpha_2(q_2)$ for each $(q_1, q_2) \in F'$, 
-%
 \item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), (\myvec{v_1}, \myvec{v_2}))$ such that $(q_1,a, q'_1, \myvec{v_1}) \in \delta_1$ and $(q_2,a, q'_2, \myvec{v_2}) \in \delta_2$.
-%, where $\myvec{v} \in \Int^{R'}$, $\prj_{R_1}(\myvec{v}))$ (resp. $\prj_{R_2}(\myvec{v}))$) is the restriction of $\myvec{v}$ to the domain $R_1$ (resp. $R_2$). 
 \end{itemize}
@@
 For instance, $\aut_1 \cup \aut_2 \cup \aut_3 = (\aut_1 \cup \aut_2) \cup \aut_3$, $\aut_1 \cap \aut_2 \cap \aut_3 = (\aut_1 \cap \aut_2) \cap \aut_3$, and $\aut_1 \concat \aut_2 \concat \aut_3 = (\aut_1 \concat \aut_2) \concat \aut_3$.
-
-%Let $((\aut_1,\cdots, \aut_n), \varphi)$ be a tuple such that $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1)$, $\cdots$, $\aut_n = (R_n, Q_n, \Sigma, \delta_n, q_{n, 0}, F_n)$ are CEFA, and $\varphi(R_1, \cdots, R_n)$ is an LIA formula.
-Then the \emph{relation} defined by $((\aut_1, \cdots, \aut_n), \varphi)$, denoted by $\srel((\aut_1, \cdots, \aut_n), \varphi)$, is $\{(w, \myvec{v'_1}, \cdots, \myvec{v'_n}) \mid \varphi(\myvec{v'_1}/R_1, \cdots, \myvec{v'_n}/R_n)\equiv \ltrue, \forall i \in [n].\ (w, \myvec{v'_i}) \in \Lang(\aut_i)\}$.
-
-%the intersection of $\Lang(\aut_1)$ and $\Lang(\aut_2)$.
-
-%The value of each register $r_i$ in $R$ is written as $\mathcal{V}(r_i)$ and is initiated to 0 at the initial state.
-A \emph{run} of $\aut$ on string $a_1\cdots a_m$ is a transition sequence $q_I\xrightarrow[\myvec{v_1}]{a_1}q_1\cdots q_{m-1}\xrightarrow[\myvec{v_m}]{a_m}q_m$  and $\mathcal{V}(r_i) = \displaystyle\sum_{j=1}^m \myvec{v_j}[i], i\in [1,n]$ is the value of $r_i$ after the run.
-$\theta[R/\mathcal{V}(R)](q_m)$ is obtained from $\theta(q_m)$ by replacing each register $r_i$ to its value $\mathcal{V}(r_i)$.
-The run is \emph{accepting} if $q_m\in F$ and $\theta[R/\mathcal{V}(R)](q_m)$ is satisfiable.
-$\top$ is the valid formula that is always satisfiable.
-A string $w$ is accepted by $\aut$ if it has an accepting run of $\aut$.
-The language of $\aut$ is the set of strings accepted by $\aut$, denoted by $\lan(\aut)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\hide{
-\zhilin{this example should be modified to match the running example}
-\begin{example} \label{eg:1}
-  Fig.\ref{fig:counting} illustrates the CEFA recognizing $(ab)\{1,100\}$.
-The register vector is $(r_1)$, and the linear arithmetic constraint on $q_2$ is $1\leq r_1\leq 100$.
-Intuitively, the transition $q_0 \xrightarrow[(1)]{a} q_1$ accept the char $a$ and increase 1 on the value of $r_1$.
-The transition $q_1 \xrightarrow[(0)]{b} q_2$ accepts the char $b$ and does not change the value.
-The transition $q_2 \xrightarrow[(0)]{\epsilon} q_2$ is a nondeterministic choice back to initial state $q_0$.
-Because of the linear arithmetic constraint $1\leq r_1\leq 100$, the value of $r_1$ in the accepting run must be $[1,100]$.
-$\mathcal{V}(r_1)$ equal to the occurrence number of the transition $q_0 \xrightarrow[(1)]{a} q_1$, so that the accepted string is $ab\cdots ab$ in which $a$ appears at least once and at most 100 times.
-That is, the language of the automaton is $(ab)\{1,100\}$.
-  \begin{figure}[h]
-    \centering
-    \input{figures/cefa_example.tex}
-    \caption{An automaton recognizing the language of $(\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$}
-    \label{fig:counting}
-  \end{figure}
-\end{example}
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Parikh's theorem \cite{parikh_theorem}\cite{parikh_anthony}\cite{parikh_compute} states that the Parikh image of a context-free language is semilinear so that it can be written as Presburger formula.
-Following the version for context-free grammar \cite{parikh_compute} and the version for regular expression \cite{parikh_for_nfa}, we define the Parikh image of language of an CEFA $\aut = (Q, \Sigma, \delta, q_I, F, R, \theta)$  as follows:
-% \begin{table}[h]
-%   \begin{tabular}{l l r}
-%     $\psi(\aut)\equiv$& $\bigwedge\limits_{q\in Q}(\text{$f_q$ if $q\in F$ otherwise 0}) + \sum\limits_{(q,a,q',\myvec{v})\in\delta} t_{q,a,q',\myvec{v}} = $ & \\
-%     & \quad \ \ (1 if $q = q_I$ otherwise 0) + $\sum\limits_{(q',a,q,\myvec{v})\in\delta} t_{q',a,q, \myvec{v}} $ & \\ 
-%     & $\bigwedge\limits_{(q,a,q',\myvec{v})\in\delta} t_{q,a,q',\myvec{v}}\geq 0$ & (consistent formula)\\
-%     & & \\
-%     & $\bigwedge\limits_{(q,a,q',\myvec{v})\in\delta} t_{q,a,q',\myvec{v}}>0\rightarrow z_{q'} > 0$ & \\
-%     & $\bigwedge\limits_{q\in F} z_q > 0\rightarrow f_q = 1$ & \\ 
-%     & $\bigwedge\limits_{q\in Q} z_q > 0\rightarrow \bigvee\limits_{(q,a,q',\myvec{v})\in\delta} z_q = z_{q'} + 1\wedge t_{q,a,q',\myvec{v}}\geq 0 \wedge z_{q'} > 0$& (connected formula)\\
-%     & & \\
-%     &$\bigwedge\limits_{r_i\in R} r_i = \sum\limits_{(q,a,q',\myvec{v})\in \delta} t_{q,a,q',\myvec{v}}*\myvec{v}[i]$ & (register value formula)\\
-%     & & \\
-%     &$\bigwedge\limits_{q\in F} f_q > 0 \rightarrow \theta(q)$ & (accepting condition) 
-%   \end{tabular}
-% \end{table}
-% $z_q$ is the distance of state $q$ from $q_f\in F$ in a spanning tree.
-$t_{q,a,q',\myvec{v}}$ represents the using times of transition $(q,a,q',\myvec{v})$ in the accepting run.
-$f_q$ stands for whether an accepting state $q\in F$ is the final state of a run.
-The Parikh image of $\aut$ is a Presburger formula $\psi(\aut)$, which is consistent and connected.
-The register value formula ensures \denghang{that} the register values are correctly updated regarding the accepting run.
-% \begin{example} \label{exapmle:parikh}
-%   Suppose that we have a CEFA $\aut$ shown in Fig.
-\ref{subfig:aut_x}.
-Using $t_1, t_2, t_3$ to record the times of transitions in the accepting run of $\aut$, the Parikh image $\psi(\aut)$ is the quantifier-free Presburger formula $\psi_{cons}\wedge \psi_{conn} \wedge \psi_{val} \wedge \psi_{aut}$ where:
-%   \begin{itemize}
-%     \item $\psi_{cons} \equiv 1 = t_1 \wedge t_1 + t_3 = t_2 \wedge t_2 = t_3 + 1 \bigwedge\limits_{i\in[1,3]} t_i\geq 0$ is the consistent formula.
-%     \item $\psi_{conn} \equiv \top $ is the connectivity formula because all transitions in $\aut$ are connected.
-%     \item $\psi_{val} \equiv r_1=t_1 + t_3\wedge r_2 = t_1+t_2+t_3$ is the formula deciding the value of $r_1$ and $r_2$ after a run.
-%     \item $\psi_{aut} \equiv r_2 = i\wedge 1 \leq r_1 \leq 100$ is the accepting condition of $\aut$.
-%   \end{itemize}
-%   $\psi(\aut)$ can be simplified to $t_3\geq 0 \wedge t_1=1\wedge r_1 = t_3 + 1\wedge r_2 = 2*t_3+2\wedge r_2=i\wedge 1\leq r_1\leq 100$.
-A possible solution is $t_1 =1, t_3 = 0, r_1=1, r_2=2$ and the corresponding accepted string $ab$.
-It is obvious that $r_1$ is the repeat times of $ab$ and $r_2$ is the length of $ab$.
-% \end{example}
-%\end{document}

### 2023-10-19 2023-1-19/sections/implementation.tex
remove comments

@@
 %!TEX root = ../main.tex
-%\documentclass{standalone}
-%\begin{document}
 In this section, we list our experimental results.
@@
 }
-
-%This section presents the empirical evaluation of OstrichCEA, which is our implementation of the decision procedure introduced in Section \ref{sec:algorithm}.
-Our objective is to validate the effectiveness of the proposed techniques by evaluating our tool's correctness and efficiency compared to other solvers.
-Furthermore, we assess the efficacy of our heuristics by testing different configurations of the tool.
-We have implemented our encoding for counting with two heuristic algorithms on Ostrich+ \cite{atva2020}.
-The pre-image computation for concatenation, \verb|indexOf|, \verb|substring|, \verb|replaceAll|, \verb|reverse| and finite transducer remain unchanged.
-OstrichCEA is written in Scala and based on the SMT solver Princess\cite{princess}.
 
@@
 where $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is a regular expression that sanitizes all occurrence of special characters $<$, $>$, $'$, $''$, or $\&$. 
-%The artificial construction is meaningful because the special characters are offensive. 
 The expression $e_{sani}$ is introduced in view of the fact that these characters are usually sanitized in Web browsers to alleviate the XSS attacks \cite{malware_detection_3_kudzu,CCH_18}.
-%We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.
 \vspace{-0.1mm}
@@
 \emph{Large-Bounds part.} This benchmark suite is composed of 1,969 problem instances with large counting bounds (greater than or equal to $50$) from RegCoL and AutomatArk benchmark suites.  
-%regex with upper bound greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total). 
 Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
 }
-%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
-%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
-%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
-\hide{
-  We conducted a comparison on four sets of benchmarks based on regex with
-  counting operator, consisting of a total of 49,379 instances.
-We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with the counting operator.
-In total, almost 18\% of the instances we evaluated were sourced from published industrial benchmarks or other solver developers.
-The other instances are generated by ourselves with regular expressions from the real world.
-Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large upper bounds of the counting operator (the sum of upper bounds is greater than 50), and "small" contains remaining instances.
-About 10\% of the benchmarks are in a "large" set.
-More details about the benchmarks are shown below.
-
-  \subsubsection{AutomatArk} is the 8,751 instances generated by Berzish et al.\cite{z3str3re}.
-It is based on real-world regular expression queries from Loris D'Antoni\cite{automatark}.
-The origin set comprises two tracks, a simple and a hard track, with 19,979 instances.
-The simple track contains instances with a single regular expression membership constraint, whereas the hard track can hold up to five membership constraints for a single variable per instance.
-We extract 8,751 instances containing counting operators.
-
-  \subsubsection{ReDos} is the set of 1,624 instances we generated.
-It is based on the ReDos-attacked regular expression collected by Lenka et al.
-For each regular expression, we generate an instance as the template (\ref{eq:template}) where $\regex$ is the regular expression.
-The regular membership predicate $x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*$ sanitizes the input string $x$ to avoid the attack.
-The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
-
-  \subsubsection{RegexLib} is the set of 1,623 instances we generated similarly to the \textbf{ReDos} benchmark.
-It is based on the regular expressions collected by James C.
-Davis et al.\cite{regex_lingua_franca} from regex lib website\cite{regexlib}.
-The website is the Internet's first Regular Expression Library.
-Currently, it has indexed 4149 expressions from 2818 contributors around the world since 2001.
-We extracted 1,623 instances containing bounded repetition from 4149 instances.
-The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
-
-  \subsubsection{StackOverflow} is the 37381 instances we generated similarly to the \textbf{ReDos} benchmark.
-As the Regexlib benchmark, the real-world regex expressions are collected by James C.
-Davis et al.\cite{regex_lingua_franca} from StackOverflow website\cite{stackoverflow}.
-The website is a question-and-answer site for professional and enthusiast programmers.
-We extracted 37,381 instances containing bounded repetition from almost 500,000 instances.
-The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
-  \begin{equation} \label{eq:template}
-    x\in \regex \wedge x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*\wedge |x| > 50(or \ 20)
-  \end{equation}
-}
-%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
-%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
-
 \vspace{-2mm}
@@
 We evaluate the performance of $\ostrichrecl$ against the state-of-the-art string constraint solvers, including CVC5
-%(version 1.0.5) 
 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3
-%(github commit 59e9c87) 
 \cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH
-%(github commit 8297d8d) 
 \cite{ostrich2023}, on RegCoL and AutomatArk benchmark suites.
-% Z3-trau \cite{z3trau} is not evaluated because it does not support \verb|re.diff|, the language difference operator of regular expressions.  
-%The experiments are designed to answer the following two research questions. 
-%\begin{description}
-%\item[Q1] Does OSTRICH$^{\rm RECL}$ solve RECL constraints more efficiently than the state-of-the-art string constraint solvers ?
-%
-%\item[Q2] Do the simplification and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
-%\end{description}
-
-% \medskip
-% \noindent
-% \emph{Overall evaluation.} 
 The experiment results can be found in Table~\ref{tab:results_regcol}.
@@
 Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, \denghang{and the results distinct to the ground truth are called \emph{soundness errors}.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
-The number is %3,994/2,272/24,577/12,832/1,091/7,092
-\textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-%      
-%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
-% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
+The number is \textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
 %
@@
 \end{table}
-% \begin{table}[ht]
-%   \vspace{-5mm}
-%   \begin{center}
-%     \import{tables}{table_regcol.tex}
-%   \end{center}
-%   \caption{Overall Experiment results, with timeout = 60 seconds}
-%   \label{tab:results_regcol}
-%   \vspace{-9mm}
-% \end{table}
 
 \subsection{Evaluation on problem instances with large bounds}\label{subsec:large_bounds_eval}
-% \smallskip
-% \noindent
-% \emph{Evaluation on problem instances with large bounds.}
 %
 \sout{We extract the 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
-%regex with upper bound greater than 50 and generate a \emph{`large-counting'} benchmark suite (1,969 instances in total). 
 Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.}
@@
 
-% \begin{table}[ht]
-%   \vspace{-5mm}
-%   \begin{center}
-%     \import{tables}{table_large_count.tex}
-%   \end{center}
-%   \caption{Large-counting experiment, with timeout = 60 seconds}
-%   \label{tab:results_simp}
-%   \vspace{-9mm}
-% \end{table}
-
 We evaluate the performance of $\ostrichrecl$ on 1,969 instances of the Large-Bounds part. 
@@
 \subsection{Evaluation of the effectiveness of size-reduction techniques}\label{subsec:size_reduction_eval}
-% \medskip
-% \noindent 
-% \emph{Evaluation of the effectiveness of the automata size-reduction techniques.}
 We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
@@
 The experiment results are put in Table~\ref{tab:results_simp}. 
-%$\ostrichrecl_{\rm -SIMP}$ is the tool without simplification techniques. $\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques. 
 From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$.
@@
 \denghang{To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}}.
-
-%Moreover, we encode the $\cefadec$ problem to an infinite state transition system and use \textsc{nuXmv}\cite{nuxmv} to solve it.
-We also compare the simplification techniques to the \textsc{nuXmv}-based techniques.
-%$\ostrichrecl_{\rm NUXMV}$ is the tool using \textsc{nuXmv}-based techniques.
-%We evaluate the simplification techniques by comparing the performance of $\ostrichrecl$ with and without the simplification techniques.
-
-% \begin{table}[ht]
-%   \vspace{-5mm}
-%   \begin{center}
-%     \import{tables}{table_simp.tex}
-%   \end{center}
-%   \caption{Simplification technique evaluation, with timeout = 60 seconds}
-%   \label{tab:results_simp}
-%   \vspace{-9mm}
-% \end{table}
-
-% The results are in Table~\ref{tab:results_simplification}.
-We can see that the simplification technique improves the performance of $\ostrichrecl$ significantly.
-It solves 1,111 more instances and is 1.62 times faster than $\ostrichrecl$ without the simplification technique.
-
-% \begin{table}[ht]
-% %\vspace{-1mm}
-% \begin{center}
-%   \import{tables}{table_automatark.tex}
-% \end{center}
-%   \caption{Experiment results on AutomatArk, with timeout = 60 seconds}
-%   \label{tab:results_automatark}
-% \vspace{-6mm}
-% \end{table}
-
-% The experiment results on the AutomatArk benchmark suite are put in Table~\ref{tab:results_automatark}. 
-% From Table~\ref{tab:results_automatark}, we can see that $\ostrichrecl$ solvers almost all 8,215 instances, except 39 of them, that is, it solves 8,176 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092
-% 101/191/4,094/2,632/9/1,587
-% more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
-% %    
-% Still, the soundness errors are reported by taking the results of CVC5 as the ground truth.
-%Note that Z3-Trau has soundness errors, where the result of CVC5 is taken as the ground truth.
-If CVC5 reports ``unknown'' or ``timeout'' in some instances, then no soundness errors will be reported in this instance.
-%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
-% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
-%
-% Moreover, $\ostrichrecl$ spends 2.49 seconds per instance on average. 
-%while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.  
-%Note that Z3-Trau reports ``unknown'' on 2,552 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
-
-% In summary, $\ostrichrecl$ solves 48,698 out of 48,843 instances, 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints.
-Moreover, the speed of $\ostrichrecl$ is the second fastest and comparable to that of Z3str3RE.
-(See Table~\ref{tab:results_summary}.)
-
-% \begin{table}[ht]
-% \vspace{-3mm}
-% \begin{center}
-%   \import{tables}{table_summary.tex}
-% \end{center}
-%   \caption{Experiment results: A Summary}
-%   \label{tab:results_summary}
-% \vspace{-6mm}
-% \end{table}
-
-%Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL.
-
-%\zhilin{may add the results for the two benchmark suites separately.}
-
-%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
-\hide{
-  \begin{table}[ht]
-    \vspace{-3mm}
-    \begin{center}
-      \subimport{tables}{table_heuristic.tex}
-    \end{center}
-    \caption{Experiment results for Q2, where the timeout period is 60 seconds}
-    \label{tab:results_heuristics}
-    \vspace{-6mm}
-  \end{table}
-
-  To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the simplification, under-approximation, or both are removed.
-  For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both simplification and under-approximation techniques are removed,
-  OSTRICH$^{\rm RECL^-}_{+\rm SR}$ (resp.
-OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the simplification (resp.
-under-approximation) techniques to OSTRICH$^{\rm RECL^-}$.
-  %OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove simplification, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
-  The experiment results can be found in Table~\ref{tab:results_heuristics}.
-  From Table~\ref{tab:results_heuristics}, we can see that adding simplification techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column).
-Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ helps to solve 19 more sat instances while reducing the number of solved unsat instances by 3 since under approximation techniques do not help to solve unsat instances.
-}
-%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
-%Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.
-
-%\zhilin{stopped here}
-
-%%%%%%%%%% original texts by denghang %%%%%%%%%
-%%%%%%%%%% original texts by denghang %%%%%%%%%
-\hide{
-  %
-  We have evaluated OstrichCEA compared to five other prominent string solvers currently available.
-We evaluate the solvers by directly comparing the number of cases correctly solved, the average time taken with and without timeouts, and the total count of soundness errors and program crashes.
-One of these solvers is CVC5\cite{cvc5}, a general SMT solver that uses algebraic reasoning to handle strings and regular expressions and is the winner of SMT-COMP 2022\cite{smt-comp}.
-Another solver, Z3str3\cite{z3str3}, is the most recent edition we can get to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions.
-Z3str3RE\cite{z3str3re} is a variant of Z3str3 that incorporates length-aware algorithms and heuristics.
-Z3seq\cite{z3seq} is a sequence solver which uses a novel derivative theory for solving extended regular expressions.
-Z3-Trau\cite{z3trau} is the Z3 version of trau\cite{trau} that employs a flat automata-based approach, incorporating both under- and over-approximations.
-Ostrich\cite{Ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships.
-We used the 1.0.5 binary version of CVC5, commit 59e9c87 of Z3str3, the last version of Z3str3RE, 4.8.9 binary version of Z3Seq, commit 1628747 of Z3-Trau and commit 8297d8d of Ostrich.
-Z3-Trau does not support \verb|re.diff|.
-All other solvers support all syntax sugars listed in SMT-LIB standard\cite{smt_lib}.
-We omitted Z3str4\cite{z3str4} because the provided reproduction package link is wrong.
-All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY CPU T 3.10GHz processors and 190 GB memory.
-We used Zaligvinder\cite{zaligvinder_2021} framework and set the timeout to 60 seconds.
-
-  %\subsection{Overall Evaluation}
-  In Fig.\ref{fig:cactus_all}, the cactus plot illustrates the cumulative time each solver takes for all cases in ascending order of runtime.
-Solvers located towards the right and lower portion of the plot indicate better performance.
-\newline
-  Table \ref{tab:results_all} summarizes the results demonstrating OstrichCEA's superior performance, solving the most significant number of instances and outperforming most competing solvers.
-Including timeouts, OstrichCEA is \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3, \textbf{3.11}\mult{} faster than CVC5 and close to Z3str3RE with \%2 speed loss .
-Note that CVC5\cite{cvc5} yielded 5370 timeouts(11\% of all instances), and Z3str3\cite{z3str3} yielded 6139 timeouts(12\% of all instances), which is much more than other solvers.
-Both CVC5 and Z3str3 are DPLL(T)-based solvers.
-It seems that almost 10\% of the benchmarks we used seem unsuitable for them.
-Z3-trau\cite{z3trau} yielded 21,152 unknowns because it does not support \verb|re.diff|.
-Z3-trau\cite{z3trau} yielded 6673 crashes (13\% of the instances) and 1233 soundness errors (2\% of the instances), which is a large portion.
-Z3-based solvers Z3str3 yielded 38 soundness errors, Z3seq\cite{z3seq} yielded 51 soundness errors and Z3str3RE\cite{z3str3re} yielded 39 soundness error.
-Most of them are due to the mistake of formalization of the backslash character.
-OstrichCEA resulted in 5 unknowns because it reached the maximum threshold of limited memory 2GB.
-More details of the results of each benchmark are shown in \ref{appendix:experiential_results}.
-  \begin{figure}[h]
-    \centering
-    \import{figures}{cactus_plot_all.tex}
-    \caption{Cactus plot summarizing performance on all benchmarks.}
-    \label{fig:cactus_all}
-  \end{figure}
-
-  %\subsection{Analysis of Individual Heuristics}
-  In order to demonstrate the efficacy of the individual heuristics outlined in Section \ref{sec:algorithm} and incorporated into OstrichCEA, we assessed various tool configurations in which one or more heuristics were disabled.
-Figure \ref{fig:cactus_heuristics} and Table \ref{tab:results_heuristics} display the outcomes.
-The "OstrichCEA" plot line represents the tool's performance when all heuristics are enabled, while the "All heuristics off" line represents performance when all heuristics are disabled.
-The remaining plot lines exhibit performance with only the named heuristic disabled while all others are enabled.
-The plots and table show that OstrichCEA functions most effectively when all heuristics are enabled.
-In average time with timeout times, OstrichCEA performs \textbf{1.78}$\times$ faster than employing none of our heuristics, \textbf{1.37}$\times$ faster than turning off simplification, \textbf{1.15}$\times$ faster than truing off under-approximation.
-  \begin{figure}
-    \subimport{figures/}{cactus_plot_heuristic.tex}
-    \caption{A performance comparison was made on all benchmarks by turning off individual heuristics using a cactus plot.}
-    \label{fig:cactus_heuristics}
-  \end{figure}
-  \begin{table}
-    \subimport{tables}{table_heuristic.tex}
-    \caption{A performance comparison was made on all benchmarks by turning off individual heuristics.}
-    \label{tab:results_heuristics}
-  \end{table}
-}
-%%%%%%%%%% original texts by denghang %%%%%%%%%
-%%%%%%%%%% original texts by denghang %%%%%%%%%
-%\end{document}

### 2023-10-19 2023-1-19/sections/introduction.tex
remove comments

@@
 %!TEX root = ../main.tex
-%\documentclass[11pt]{standalone}
-%\begin{document}
-
 The string data type plays a crucial role in modern programming languages such as JavaScript, Python, Java, and PHP. 
@@
 Moreover, string-length occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}. 
-%Operations like \verb|length| that take string inputs and return an integer frequently appear in real-world JavaScript applications (78\% of string operations in 18 applications)
 As a result, most of the aforementioned string constraint solvers support both regular expressions and string-length function.
@@
 \cite{LTR+15,BD+23}.
-%a decision procedure based on tableaux calculus was designed in \cite{LTR+15} for the class of string constraints with regular expressions and string-length function.
-The decision procedure has been implemented in CVC4/5 \cite{LRT+16}.
 
@@
 
-%counting is used in about 6 percent of the regular expressions in Javascript programs.
-
 \medskip
@@
 Thus, the nonemptiness of CEFA w.r.t. LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
-%
-  % Moreover, the string-length function can also be modeled by register in CEFA.
-Then the satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA with respect to a linear integer arithmetic (LIA) formula whose free variables are registers.
-According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
-  % Thus, the nonemptiness of CEFA w.r.t. LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
   \item We propose techniques to reduce the sizes (i.e. the number of states and transitions) of CEFA, in order to achieve better performance.
-%  , since the sizes of LIA formulas depend much on the sizes of CEFA.
   \item Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
@@
 For instance, on 1,873 benchmark instances where the counting bounds are greater than or equal to $50$ and the string lengths are required to be beyond $200$, $\ostrichrecl$ solves at least $278$ more instances than the other solvers, while spending only half or less time per instance on average.
-%  For instance,  the most number of instances than the other solvers, with comparable or faster speed (See Table~\ref{tab:results_regcol}).
-Moreover, when the counting and length bounds are large, $\ostrichrecl$ solves much more instances than the other solvers, while using much less time.
-
-%In addition, we carry out some detailed experiments, including the evaluation of simplification techniques and the experiment of large-counting benchmarks.
-The result shows that the simplification techniques are effective in practice (See Table~\ref{tab:results_simp}), and $\ostrichrecl$ performs much better than other solvers on the large-counting benchmark (See Fig~\ref{fig:table_large_count}).
-
-% The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,843 instances, while Z3str3RE, the state-of-the-art solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
-Moreover, the speed of $\ostrichrecl$ is comparable to that of Z3str3RE.
-In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively.
-(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details.)
 \end{itemize}
 \vspace{-0.5mm}
-% We propose an automata-theoretical approach for solving RECL constraints.
-Our main idea is to represent the counting operators by registers in automata (as much as possible) instead of unfolding them explicitly.
-Our approach is built upon cost-enriched finite automata (CEFA), proposed in~\cite{atva2020} to solve string constraints involving the integer data type.
-Moreover, the string-length function can also be modeled by register in CEFA.
-Then the satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA with respect to a linear integer arithmetic (LIA) formula whose free variables are registers of CEFA.
-
-% According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
-Thus, the nonemptiness of CEFA w.r.t.
-LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers for LIA.
-Because the sizes of LIA formulas depend much on the sizes of CEFA, it is beneficial to reduce the sizes of CEFA to achieve better performance.
-As a result, we propose various techniques to reduce the state space and the number of transitions of CEFA.
-
-% Combined with the simplification techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
-We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH called $\ostrichrecl$ for convenience.
-% Furthermore, we utilize a collection of benchmark suites comprising 48,843 RECL constraints in total to evaluate the performance of $\ostrichrecl$.
-It includes a widely-used benchmark suite for string constraints and benchmark suites comprising constraints generated from regular expressions in various open source regex libraries.
-% %
-% %Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contain sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators.
-% %
-% The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,843 instances, while Z3str3RE, the state-of-the-art best solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds).
-Moreover, the speed of $\ostrichrecl$ is comparable to that of Z3str3RE.
-In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively.
-(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details.)
-
-% At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA was introduced.
-This work differs from \cite{atva2020} in the following two aspects: (1) In \cite{atva2020}, regex-counting was unfolded explicitly while this work encodes it to register.
-(2) Moreover, the nonemptiness of CEFA w.r.t.
-LIA formulas was solved using the nuXmv model checker~\cite{nuxmv}.
-In contrast, this work solves it by integrating the techniques of Parikh-image computation and automata-size reduction.
-The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time.
-(See Table~\ref{tab:results_regcol}-\ref{tab:results_summary} for more details.)
 
@@
 
-%To handle the problems in software verification reasoning about strings and integers, string theories with regular membership predicate and linear length constraints are raised.
-String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, BD+23\cite{BD+23}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories.
-Although string theory is easily
-%undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_BD+23}.
-There are mainly two strategies for solving string constraints: (1) DPLL(T)-based\cite{dpll_t} string solvers\cite{z3str3}\cite{cvc5} apply heuristic derivation rules to unwind the regular expression gradually and identify several classes of simplification techniques for efficiency.
-(2) Automata-based string solvers\cite{trau}\cite{z3trau}\cite{ostrich}\cite{atva2020}\cite{BD+23} construct a finite automaton to model the regular expression and use the emptiness problem of the automaton (under linear integer arithmetic) to decide the satisfiability of string constraints.
-
 \smallskip
@@
 Section~\ref{sec:conclu} concludes this paper.
-
-%%%%%%%%%%%%%%%%%%%%%%% original texts by Denghang %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%% original texts by Denghang %%%%%%%%%%%%%%%%%
-\hide{
-String constraint solving is a subfield of computer science that deals with analyzing and manipulating strings, which are sequences of characters.
-String constraints solving aim to automatically infer properties of string variables, such as their length, content, and structure, to reason about the behavior of software systems that manipulate strings.
-It is crucial in security-critical applications, where strings represent sensitive data such as passwords, user input, and network addresses.
-String constraints solving combines techniques from formal methods, automata theory, and constraint solving and has many applications in areas such as software testing\cite{software_testing_1}\cite{software_testing_2}, program analysis\cite{prog_analysis_1}\cite{prog_analysis_2}\cite{prog_analysis_3}, and malware detection\cite{malware_detection_1}\cite{malware_detection_2}\cite{malware_detection_3_kudzu}.
-In this context, efficient algorithms and tools for solving string constraints are crucial to improve the security and reliability of modern software systems.\newline
-Regular expressions are widely used in programming languages. About 30–40 \%
-Java, JavaScript, and Python software use regex matching\cite{redos_fse2019}.
-Bounded repetition is widely used in regex matching\cite{regex_repeat} and is dangerous because Regular expression Denial of Service (ReDoS) may derive from it\cite{redos_lenka}.
-We have analyzed regular expressions sourced from the Internet\cite{regexlib}\cite{stackoverflow}, among which about 10\% include bounded repetition.
-Operations like \verb|length| that take string inputs and return an integer frequently appear in real-world JavaScript applications (78\% of string operations in 18 applications\cite{malware_detection_3_kudzu}).
-These statistics show that a resultful string solver reasoning about regular membership predicate with bounded repetition and \verb|length| operation is required.
-However, such string constraints may lead to low performance.
-% the state-of-art string solvers (\cite{z3seq}\cite{z3str3}\cite{z3str4}\cite{BD+23}\cite{cvc5}\cite{ostrich}\cite{z3trau}\cite{trau}) lose efficiency. 
-For CVC5\cite{cvc5} (which is the winner of QF\_Strings track in SMT-COMP 2022\cite{smt-comp}), the string constraints are solved based on DPLL(T) structure.
-Each string constraint is seen as a literal boolean and assigned by true or false (Boolean abstraction).
-CVC5 repeatedly applies derivation rules on these assigned string constraints until the satisfiable solution is found or unsatisfiability is detected.
-The approach is fast and sound.
-Nevertheless, it is incomplete because it may not recognize unsatisfiable literals and may not terminate when unrolling regular expression.
-For example, CVC5 unrolls regular expression $\Sigma_{/a}\{1,300\}$ and $\Sigma^*a\Sigma^*$ when solving the string constraints \ref{eq:cvc5_timeout}.
-$\Sigma_{/a}\{1,300\}$ repeats a letter excluding $a$ from one time to 300 times.
-$\Sigma^*a\Sigma^*$ accepts a string containing $a$.
-It is easy to see that the string constraints are unsat.
-However, CVC5 is hard to explore the unsatisfiability, for it can only answer once attempting all strings with lengths less than or equal to 300.
-The number of the searched string is exponential to the count.
-We test this instance on CVC5 and get a timeout result when the timeout is set to 60s.
-\begin{equation} \label{eq:cvc5_timeout}
-  x\in \Sigma_{/a}\{1,300\}\wedge x\in \Sigma^*a\Sigma^*
-\end{equation}
-Z3Str3\cite{z3str3} is a string solver written on the famous SMT solver Z3\cite{Z3}.
-It is based on the DPLL(T) structure and uses the same approach as CVC5, except that the derivation rules of Z3 differ from CVC5.
-Furthermore, Z3str3 exposes the structure of theory literals to the DPLL(T) SAT solver's branching heuristic, resulting in smarter decisions during its search.
-Z3Str3 can not solve string constraints (\ref{eq:cvc5_timeout}) because the optimization can not avoid the endless unwind of the regular expression.
-Automata-based methods were proposed to handle the exponential search space of regular expression.
-One of the automata-based string solver Ostrich\cite{ostrich}\cite{atva2020} encodes string constraints and regular expressions into automata and use the automata theory to solve them.
-It is sound and complete.
-But it is inefficient because it is hard to reduce the size of automata.
-When large counting is constrained on a complex sub-regex, like $ \backslash w \{1, 63\}$ where $\backslash w$ is an English character or a number character, the corresponding automaton in Ostrich becomes very large.
-It can not be solved within the 60s time limit.
-The reason is that Ostrich syntactically rewrites the counting operator to the union of finite repeatings of the sub-regex.
-For example, $\backslash w\{1, 63\}$ is rewritten to $\backslash w\mid\backslash w^2\cdots\mid\backslash w^{63}$ where $\backslash w^i$ means repeat $i\-th$ times on $\backslash w$.
-The automaton of $\backslash w$ contains $62$ states to accept each possible character, and the automaton of $\backslash w ^i$ contains $62*i$ states.
-The total number of states in the automaton is $62 + 62*2 + \cdots 62*63=124992$, causing the automaton to be unsolvable in practice.
-Trau\cite{z3trau}\cite{trau+} is another powerful automata-based solver.
-It relies on a Counter-Example Guided Abstraction Refinement (CEGAR) framework in which the under- and over-approximation of the automata are iteratively refined.
-Although it uses simple flat automata to represent regular expressions, it has to build unsolvable automata on regex $\backslash w\{1, 63\}$ as Ostrich because the solution of the flat automata should be within the solution of the original automata.
-Recently, Z3str3 has been extended to BD+23\cite{BD+23} by Berzish et al to handle string constants with regular memberships and length operation effectively.
-It uses automata to formalize the semantics of regular expressions and applies several length-aware heuristics.
-BD+23 can avoid building unsolvable automaton because the length abstraction is directly derived from the regex, not the automaton.
-Unfortunately, the length abstraction is an over-approximation, so it can not solve string constraints (\ref{eq:BD+23_timeout}) whose regular membership predicate contains complementary.
-\begin{equation}\label{eq:BD+23_timeout}
-  x\in \Sigma_{/a}\{13,13\}\wedge |x| > 13
-\end{equation}
-To address these issues, we formalize bounded repetition using cost-enriched finite automaton (CEFA)\cite{atva2020} with linear arithmetical constraints.
-It limits the max(min) run times of some transitions on the accepting run of the automaton, which completely captures the semantics of bounded repetition.
-The satisfiability problem of string constraints with bounded repetition is reduced to the emptiness problem of cost-enriched finite automata under linear arithmetical constraints (abbreviated as $SAT_{CL}$ problem), which is decidable and can be solved by our previous work \cite{atva2020}.
-However, the previous work could perform better practically, especially when regular expressions are complex.
-In this paper, we propose two heuristical methods to improve performance.
-The first one is under-approximation, which is inspired by Bounded Model Checking \cite{bmc_1}\cite{bmc_2}\cite{bmc_3}.
-The second one is the symbolic-aware simplification, which is motivated by the observation that the emptiness problem is only related to the symbolic update functions.
-We implement a powerful string solver OstrichCEA and evaluate it on instances from the real world and other typical benchmarks.
-The experiment result shows superiority.
-
-\subsubsection{Related Work}
-String theories with regular membership predicate and linear length constraints are raised to handle the problems in software verification reasoning about strings and integers.
-String solvers such as Z3Str3\cite{z3str3}, Z3Seq\cite{z3seq}, BD+23\cite{BD+23}, CVC4\cite{cvc4}, CVC5\cite{cvc5}, (Z3-)Trau\cite{trau}\cite{z3trau}, Ostrich(+)\cite{ostrich}\cite{atva2020}, Sloth\cite{sloth}, S3\cite{s3}, and ABC\cite{abc} are developed on these theories.
-Although string theory is easily
-undecidable\cite{undecidable_1}\cite{undecidable_2}, the satisfiability problems for string constraints of regular expressions, linear integer arithmetic, and the string length is decidable\cite{theory_BD+23}.
-There are mainly two strategies for solving string constraints: (1) DPLL(T)-based\cite{dpll_t} string solvers\cite{z3str3}\cite{cvc5} apply heuristic derivation rules to unwind the regular expression gradually and identify several classes of simplification techniques for efficiency.
-(2) Automata-based string solvers\cite{trau}\cite{z3trau}\cite{ostrich}\cite{atva2020}\cite{BD+23} construct a finite automaton to model the regular expression and use the emptiness problem of the automaton (under linear integer arithmetic) to decide the satisfiability of string constraints.
-
-\subsubsection{Our Contributions}
-Our main contributions are as follows:
-\begin{enumerate}
-  \item  Encode regular expression with bounded repetition into CEFA with linear arithmetical constraints.
-  \item  Devise heuristic methods like under-approximation and symbolic-aware simplification to solve the $SAT_{CL}$ problem.
-  \item  Generate significant instances with bounded repetition from real-world regular expressions.
-  \item  Implement our decision procedure on solver OstrichCEA and compare it with state-of-art string solvers. The result shows the superiority of our encoding and heuristics.
-\end{enumerate}
-
-The rest of the paper is structured as follows: Section \ref{sec:pre} introduces the preliminaries.
-Section \ref{sec:overview} outlines the overall algorithm.
-Section \ref{sec:automaton} illustrates how to construct an automaton from a regular expression.
-Section \ref{sec:algorithm} shows how to solve a string constraint with repetition.
-Section \ref{sec:implementation} presents the experimental results.
-Section \ref{sec:conclu} concludes the paper and discusses future work.
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\end{document}

### 2023-10-19 2023-1-19/sections/overview.tex
remove comments

@@
 %!TEX root = ../main.tex
-
-%\zhilin{to be made consistent with section 6.}
 
@@
 
-%$x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c^+ \wedge |x| > 120$.
-
 First, we construct an CEFA for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
 Three registers are introduced, say $r_1, r_2, r_3$, to represent the three counting operators;
-%Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
 the nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$ is constructed; the updates of registers are added to the transitions of the NFA; the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$, resulting in a CEFA $\aut_1$ illustrated in Figure~\ref{fig:overview}(a).
 $r_1++$ means that we increment the value of $r_1$ by one after running the transition.
-%Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented.
-%Moreover, $r_0$ is incremented in all the three self-loops. 
 A string $w$ is accepted by $\aut_1$ if, when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, reaching a final state $q$ in the end, and the resulting values of the three registers, say $v_1,v_2,v_3$, satisfy the accepting condition.
@@
 In $\aut_3$, a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$ (See Section~\ref{subsec:regex2cefa} for more details about the construction of CEFA.) Note that we represent the counting operators symbolically by registers instead of unfolding them explicitly.
-%where the register $r_0$ is used to record the length of strings.
-
-% the register $r_1$ is incremented in the two transitions from $q_0$ to $q_0$ and $q_1$ respectively,  the register $r_2$ is incremented in the two transitions from $q_1$ to $q_1$ and $q_2$ respectively, and the register $r_3$ is incremented in the transition from $q_2$ to $q_2$ itself.
-Moreover, the register $r_4$ is incremented in each transition.
 
@@
 Next, 
-%we remove the $\varepsilon$-transitions of $\aut_1$, resulting into $\aut'_1$, 
 we construct $\aut_1 \cap \aut_2 \cap \aut_3$, that is, the intersection (aka product) of $\aut_1$, $\aut_2$, and $\aut_3$, as illustrated in Figure~\ref{fig:overview:product}(a), where the states can not reach the final states are removed.
-%Furthermore, we add one special register, say $r_0$, to record the length of strings. Note that $r_0$ is incremented in all transitions. 
-%In $\aut_1 \cap \aut_2 \cap \aut_3$, the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_0 > 120$ is attached to both $(p_0,q_1)$ and $(p_1,q_1)$, where $r_0 > 120$ is added as a conjunct to express $|x| > 120$.
 For technical convenience, we also think of the updates of registers in transitions as vectors $(u_1, u_2, u_3, u_4)$, where $u_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
@@
 After considering the updates of registers as vectors, the CEFA is like Figure~\ref{fig:overview:product}(b).
-%the transitions corresponding to the self-loop is $(q, a', q', (1,1,0,0))$ with $a' \in \Sigma \setminus \{a\}$.
 
@@
 
-%For instance, in the transition from $(p_0, q_1)$ to $(p_1, q_1)$, $r_0$ is incremented, and the values of the other registers is unchanged.
-Therefore, the vector for this transition is $(1, 0, 0, 0)$.
 Finally, the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut\equiv \aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut$, so that the resulting registers values $(v_1, v_2, v_3, v_4)$ satisfy both $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $\varphi$.
@@
 \end{figure}
-
-%Let $\tau_1, \cdots, \tau_m$ be an enumeration of the transitions of $\aut_1 \cap \aut_2 \cap \aut_3$ and $\myvec{v_1}, \cdots, \myvec{v_m}$ be the vectors of updates on the registers in these transitions.
-
 %
@@
 \end{equation}
-%where for each $k \in [m]$, $v_k = (v_{k,1}, v_{k,2}, v_{k, 3}, v_{k, 4})$ is the vector of updates on the registers $r_0, r_1, r_2, r_3$ in the transition $\tau_k$, and $\alpha(r_0, r_1, r_2, r_3)$ is the accepting condition in $\aut_1 \times \aut_2$.
 which can be solved by the off-the-shelf SMT solvers.
-%Since the satisfiability of LIA formulas can be solved by the off-the-shelf SMT solvers for LIA, the satisfiability of the string constraint in~(\ref{eqn-running}) can thus be solved.
 
@@
 To tackle this issue, we propose techniques to reduce the sizes of the NFA $\cB$.
-%over the alphabet $\costset$.
-
-%the performance could be improved if the size of the formula in~(\ref{eqn-LIA}) can be reduced.
-Since the size of the formula in~(\ref{eqn-LIA}) depends on the size of $\aut_1 \times \aut_2$, that is, the number of states, transitions, and registers in $\aut_1 \times \aut_2$, we propose the techniques to reduce the size of the CEFA $\aut_1 \times \aut_2$.
-
-%Our main idea to reduce the size of the CEFA $\aut_1 \times \aut_2$ is to \emph{ignore the characters in transitions}, since the updates of the values of registers in transitions are independent of the characters therein and the satisfiability of the formula in~(\ref{eqn-LIA}) only concerns about the values of registers.
-After the characters in transitions are ignored, each transition in $\aut_1 \times \aut_2$ is of the form $(q, \myvec{v}, q')$, where $\myvec{v}$ is the vector denoting the updates on the values of registers.
-Let $\cB$ denote the resulting automaton.
-We then think \denghang{of} $\cB$ as an NFA, where the vectors $\myvec{v}$ are taken as the characters.
 
@@
 Furthermore, if $\cB$ contains $\vec{0}$-labeled transitions, then we can take these transitions as $\epsilon$-transitions and potentially reduce the sizes of automata further.
-%The evaluation in Table~\ref{tab:results_simp} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.
 
@@
 It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art string solvers are incapable of solving it within 120 seconds.
-
-%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
-\hide{
-\begin{figure}[ht]
-  \centering
-  \import{figures}{overview_example.tex}
-  \caption{The CEFA handling the difficult string constraints}
-  \label{fig:overview:orgin}
-\end{figure}
-
-Recalling the string constraint listed in Section \ref{sec:intro}, DPLL(T)- and automata- based string solvers can not solve it.
-For DPLL(T)-based string solvers, the unsatisfiability is hard to discover since it is highly related to the length and the counting, which independent derivation rules for regex and length can not conclude.
-For automata-based string solvers, the counting operators result in the big-size automaton, whose length abstraction is too complex to solve.
-To address these issues, we use automaton to encode the semantics of the counting operator, but in a smarter way by storing counting information to registers rather than unwinding it directly.
-The automaton model we used is called cost-enriched finite automaton(abbreviated as regex).
-It is carefully discussed in Section \ref{subsec:cefa}, so we briefly introduce it in this section.
-A CEFA can be seen as an extension of an NFA by appending symbolic updates of integers on each transition, linear integer arithmetic to constrain the integer values on each accepting state, and registers to store integer values.
-The main idea is based on the observation that the occurrences of exact transitions can trace the counting times, and the length can be seen as the sum of occurrences of all transitions in the accepting run.
-For example, the counting times in $(\Sigma \setminus a)^{\{5, 60\}}$ can be traced by the occurrences of transitions in sub-regex $\Sigma \setminus a$.
-To detail, we use one register to store counting, and symbolically add 1 when running one of the transitions in $\Sigma \setminus a$, tracing the counting times.
-Similarly, we use another register to store the length and symbolically add 1 to it when running any transition.
-The automaton model of string constraints \ref{eqn-running} is illustrated in Figure \ref{fig:overview}.
-Register $r_1$ stores the counting times of the sub-regex $\Sigma \setminus a$, register $r_2$ stores the counting times of the sub-regex $\Sigma \setminus b$, register $r_3$ stores the counting times of the sub-regex $\Sigma \setminus c$, and register $r_4$ stores the length of the string.
-The label $\Sigma \setminus a:(1,0,0,1)$ means that when running the transition, the counting times of $\Sigma \setminus a$ (i.e., the value of $r_1$) plus 1, and the length (i.e., the value of $r_4$) plus 1.
-The accepting state $q_3$ is accepting by the linear integer arithmetic $5\leq r_1\leq 60\wedge 5\leq r_2\leq 60\wedge 0\leq r_3\leq 60\wedge 120 < r_4$.
-$5\leq r_1\leq 40$ ensure the counting times of $\Sigma \setminus a$ is in the range $[5, 60]$, $5\leq r_2\leq 60$ ensure the counting times of $\Sigma \setminus b$ is in the range $[5, 60]$, $0\leq r_3\leq 60$ ensure the counting times of $\Sigma \setminus c$ is in the range $[0, 60]$, and $120 < r_4$ ensure the length of the string is greater than $120$.
-The satisfiability of the CEFA can then be reduced to the satisfiability of linear integer arithmetic, which other off-the-shelf SMT solvers solve.
-\newline
-However, even when we use CEFA to encode counting in the string constraints, the linear integer arithmetic reduced from the CEFA still needs to be simplified to solve.
-The reason is that the linear integer arithmetic is solved in exponential time of the number of variables, which is linear to the sum of transitions number and states number in the CEFA.
-To address this issue, we use symbolic-aware simplification to reduce the number of transitions and states in the CEFA.
-Simply illustrating our idea, consider a simple NFA rather than a CEFA.
-We assume the NFA consisted of three states $q_1, q_2, q_3$, where $q_1$ is the initial state, $q_2$ and $q_3$ are the accepting states.
-Assume we have three transitions from $q_1$ to $q_2$ with different characters, and three transitions from $q_1$ to $q_3$.
-Actually, we only need to attempt some of the six transitions to get the reachable result.
-We run any of the transitions, and the reachability is known.
-So this NFA can be simplified to two states $q_1', q_2'$ where $q_1'$ is the initial state, $q_2'$ is the accepting state, and one transition from $q_1'$ to $q_2'$ with abbreviated character.
-The size of NFA is sharply reduced.
-The simplification can be done by treating the character on each transition as the same character, then applying the minimization algorithm to the NFA.
-CEFA can be simplified similarly, except we need to consider the counting information, i.e., symbolic updates, on each transition.
-For example, $a:(1)$ and $b:(1)$ are treated as the same label but $a:(1)$ and $b:(0)$ are not.
-Then we can apply the minimization algorithm as NFA.
-Recalling the CEFA (Fig.
-\ref{fig:overview:orgin}) handling the string constraints \ref{eqn-running}, its transitions number between $q_1$ and $q_2$ are decided by the size of alphabet $\Sigma$.
-We apply symbolic-aware simplification on it, then a much smaller CEFA (Fig.
-\ref{fig:overview:simplified}) is obtained, whose alphabet is unary so that the number of the transition between $q_1$ and $q_2$ decreases to $1$.
-The state number does not decrease because these three states are not mutually equivalent.
-
-Sometimes the string constraints are satisfiable, and the strings in the solution have a short length.
-Such a solution may be quickly explored by derivation rules in DPLL(T)-based string solvers but slowly explored by our approach.
-To improve efficiency on satisfiable string constraints, we propose a light-way heuristic that tries to find a solution in the under-approximation of the string constraints.
-The main idea is to explore paths within an exact length and manually compute the registers' values, rather than reduce CEFA to heavy linear integer arithmetic.
-For example, consider the string constraints $x \in (\Sigma \setminus a)^{\{5, 60\}} (\Sigma \setminus b)^{\{5, 60\}} (\Sigma \setminus c)^{\{0, 60\}} \wedge x \in \Sigma^* c$, we can explore paths within length 10 and get a satisfiable solution $x = cccccccccc$.
-\begin{figure}[ht]
-  \centering
-  \import{figures}{overview_example.tex}
-  \caption{The CEFA handling the difficult string constraints}
-  \label{fig:overview:orgin}
-\end{figure}
-\begin{figure}[ht]
-  \centering
-  \import{figures}{overview_example_simplified.tex}
-  \caption{The simplified CEFA handling the difficult string constraints}
-  \label{fig:overview:simplified}
-\end{figure}
-}
-%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%original texts by Denghang%%%%%%%%%%%%%%%
-
-% The main idea is to use CEFAs (see Subsection \ref{subsec:cefa}) to simulate the semantics of length operations and regular memberships with bounded repetitions.
-As mentioned, the ESL formula contains regular literals and linear literals.
-The regular literal $x\in \regex$ directly results in one CEFA recognizing it (see Subsection \ref{subsec:regex2cefa}).
-The linear literals $\alpha_1 \leq \alpha_2$ with no length operation remain unchanged.
-For each linear literal $\alpha_1 \leq \alpha_2$ with length operation $|x|$, we generate a fresh variable $i$ to replace all occurrences of $|x|$ and propagate new formula $i=|x|$.
-Then we generate the pre-image $\aut_{i}$ whose accepting words are strings with length $i$ (see Example \ref{eg:pre_len}).
-After the process above, the satisfiability problem of string constraints becomes an $SAT_{CL}$ problem, which has a decision procedure to check (see Subsection \ref{subsec:emptiness}).
-Example \ref{example:overview} illustrate it.
-\newline
-% \begin{example} \label{example:overview}
-%   \begin{align*}
-%     \varphi\equiv x\in (ab)\{1,100\}\wedge y\in ab\wedge |x| > |y|
-%   \end{align*}
-%   ESL conjunction $\varphi$ is made up of regular literals $x\in (ab)\{1,100\}$ and $y\in ab$, linear literals $|x| > |y|$.
-The linear literal is translated to $i = |x|\wedge j = |y| \wedge i > j$.
-Our algorithm solves the formula in four steps.
-First, we construct CEFAs for regular memberships $x\in (ab)\{1,100\}$ and $y\in ab$ (Fig.\ref{subfig:aut_ab1-100} and Fig.\ref{subfig:aut_ab}).
-Second, we compute the pre-images of length operations $i=|x|$ and $j=|y|$ (Fig.\ref{subfig:preimage_x} and Fig.\ref{subfig:preimage_y}).
-Then we intersect pre-images to automata corresponding to the regular memberships for each string variable (Fig.\ref{subfig:aut_x} and Fig.\ref{subfig:aut_y}).
-We translate the satisfiability problem of $\varphi$ to the emptiness checking problem of automata (Fig.\ref{subfig:preimage_x} and Fig.\ref{subfig:preimage_y}) under linear arithmetic constants $i > y$, which could be solved by the decision procedure illustrated in section \ref{sec:algorithm}.
-
-  % \begin{figure}[h]
-  %   \begin{subfigure}[b]{0.49\textwidth}
-  %     \centering
-  %     \begin{tikzpicture}[
-  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-  %       initial text=, every state/.style={minimum size = 0.001cm},
-  %       accepting text=$1\leq r_1\leq 100$, accepting/.style=accepting by arrow,
-  %       accepting where=above
-  %       ]
-
-  %       \node[state,initial]            (q_0)                      {};
-  %       \node[state]                    (q_1) [right=of q_0]       {};
-  %       \node[state,accepting]          (q_2) [right=of q_1]       {};
-
-  %       \path[->] (q_0) edge              node      [above]           {$a$/(1)} (q_1)
-  %       (q_1) edge              node      [above]           {$b$/(0)} (q_2)
-  %       (q_2) edge [bend left]  node      [below]           {$a$/(1)} (q_1);
-  %     \end{tikzpicture}
-  %     \caption{The CEFA recognizing $(ab)\{1,100\}$}
-  %     \label{subfig:aut_ab1-100}
-  %   \end{subfigure}
-  %   \begin{subfigure}[b]{0.49\textwidth}
-  %     \centering
-  %     \begin{tikzpicture}[
-  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-  %       initial text=, every state/.style={minimum size = 0.001cm},
-  %       accepting text=$\top$, accepting/.style=accepting by arrow,
-  %       accepting where=above
-  %       ]
-
-  %       \node[state,initial]            (q_0)                      {};
-  %       \node[state]                    (q_1) [right=of q_0]       {};
-  %       \node[state, accepting]         (q_2) [right=of q_1]       {};
-
-  %       \path[->] (q_0) edge              node      [above]           {$a$/()} (q_1)
-  %       (q_1) edge              node      [above]           {$b$/()} (q_2);
-  %     \end{tikzpicture}
-  %     \caption{The CEFA recognizing $ab$}
-  %     \label{subfig:aut_ab}
-  %   \end{subfigure}
-  %   \begin{subfigure}[b]{0.49\textwidth}
-  %     \centering
-  %     \begin{tikzpicture}[
-  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-  %       initial text=, every state/.style={minimum size = 0.001cm},
-  %       accepting text=${r_2 = i}$, accepting/.style=accepting by arrow,
-  %       ]
-
-  %       \node[state,initial,accepting]            (q_0)       {};
-
-  %       \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} ();
-  %     \end{tikzpicture}
-  %     \caption{The pre-image of $i = |x|$}
-  %     \label{subfig:preimage_x}
-  %   \end{subfigure}
-  %   \begin{subfigure}[b]{0.49\textwidth}
-  %     \centering
-  %     \begin{tikzpicture}[
-  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-  %       initial text=, every state/.style={minimum size = 0.001cm},
-  %       accepting text=${r_3 = j}$, accepting/.style=accepting by arrow,
-  %       ]
-
-  %       \node[state,initial,accepting]            (q_0)       {};
-
-  %       \path[->] (q_0) edge [loop below] node{$\Sigma$/(1)} (1);
-  %     \end{tikzpicture}
-  %     \caption{The pre-image of $j = |y|$}
-  %     \label{subfig:preimage_y}
-  %   \end{subfigure}
-  %   \begin{subfigure}[b]{0.49\textwidth}
-  %     \centering
-  %     \begin{tikzpicture}[
-  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-  %       initial text=, every state/.style={minimum size = 0.001cm},
-  %       accepting text=${r_2 = i\wedge 1\leq r_1 \leq 100}$, accepting/.style=accepting by arrow,
-  %       accepting where=above
-  %       ]
-
-  %       \node[state,initial]            (q_0)                      {};
-  %       \node[state]                    (q_1) [right=of q_0]       {};
-  %       \node[state,accepting]          (q_2) [right=of q_1]       {};
-
-  %       \path[->] (q_0) edge node [above]  {$a$/(1,1)} (q_1)
-  %       (q_1) edge           node [above]  {$b$/(0,1)} (q_2)
-  %       (q_2) edge [bend left]  node      [below]           {$a$/(1,1)} (q_1);
-  %     \end{tikzpicture}
-  %     \caption{The final automaton of $x$}
-  %     \label{subfig:aut_x}
-  %   \end{subfigure}
-  %   \begin{subfigure}[b]{0.49\textwidth}
-  %     \centering
-  %     \begin{tikzpicture}[
-  %       shorten >=1pt,node distance=2cm,on grid,>={Stealth[round]},
-  %       initial text=, every state/.style={minimum size = 0.001cm},
-  %       accepting text=${r_3=j}$, accepting/.style=accepting by arrow,
-  %       accepting where=above
-  %       ]
-
-  %       \node[state,initial]            (q_0)                      {};
-  %       \node[state]                    (q_1) [right=of q_0]       {};
-  %       \node[state, accepting]         (q_2) [right=of q_1]       {};
-
-  %       \path[->] (q_0) edge    node      [above]           {$a$/(1)} (q_1)
-  %       (q_1) edge              node      [above]           {$b$/(1)} (q_2);
-  %     \end{tikzpicture}
-  %     \caption{The final automaton of $y$}
-  %     \label{subfig:aut_y}
-  %   \end{subfigure}
-  %   \caption{All automata used in the example \ref{example:overview}}
-  % \end{figure}
-
-% \end{example}
-
-% \pagebreak
-
-%The wrong encoding of the backslash causes the soundness errors of z3str3re. Two backslashes are seen as two characters in the Smtlib2.6 standard, but z3str3re encodes them as one.

### 2023-10-19 2023-1-19/sections/preliminaries.tex
all review finished
some updates
remove comments

--- 2023-08-18 2023-1-19/sections/preliminaries.tex
@@
 \emph{Strings and languages.}
-%\paragraph*{Strings and languages.}
 A string over $\Sigma$ is a (possibly empty) sequence of elements from $\Sigma$,
@@
 Moreover, for $a \in \Sigma$, let $|u|_a$ denote the number of occurrences of $a$ in $u$. 
-Assume that $u=a_1\cdots a_{n}$ is nonempty and $i<j \in [n]$. %Then a \emph{position} of $u$ is a number $i \in [|u|]$ (Note that the first position is $1$, instead of  0). In addition, 
-We let $u[i]$ denote $a_i$ and $u[i,j]$ for the substring %of $u$ starting from $i$ and ending with $j$ (i.e., 
+Assume that $u=a_1\cdots a_{n}$ is nonempty and $1\leq i<j \leq n$. 
+We let $u[i]$ denote $a_i$ and $u[i,j]$ for the substring 
 $a_i\cdots a_j$. 
-%\tl{check later for consistency}\zhilin{the indices start from 0, to be consistent with the semantics of substring and indexof}\zhilin{i do use it in section 4}
 %
@@
 Finally, define $L^* = \bigcup \limits_{n \in \Nat} L^n$.
-%, that is, the string $w$ such that $|w|= |u| + |v|$ and for each $i \in [0, |u|-1]$, $w[i]= u[i]$, and for each $i \in [0,|v|-1]$, $w[|u|+i]=v[i]$.
 
@@
 For readability, we write a transition $(q, a, q') \in \delta$ as $q \xrightarrow[\delta]{a} q'$ (or simply $q \xrightarrow{a} q'$).
-%Moreover, when $\delta$ is clear from context, we omit $\delta$ in $q \xrightarrow[\delta]{a} q'$ and write $q \xrightarrow{a} q'$.
+\denghang{Note that one initial state is sufficient.
+A set of initial states is a technical choice to simplify the defination of union operation in Sec \ref{sec:automaton}.}
 The \emph{size} of an NFA $\NFA$, denoted by $|\NFA|$, is defined as the number of transitions of $\NFA$.
@@
 Moreover, the class of regular languages is closed under union, intersection, concatenation, Kleene star, complement, and language difference \cite{HU79}.
-The constructions of NFA corresponding to these language operations are list in \ref{appendix:cefa}
-% In the sequel, we recall the constructions of NFA corresponding to these language operations. 
-% Let $\NFA_1 = (Q_1, \Sigma, \delta_1, I_1, F_1)$ and $\NFA_2 = (Q_2, \Sigma, \delta_2, I_2, F_2)$ be two NFA such that $Q_1 \cap Q_2 = \emptyset$. 
-% \begin{itemize}
-% \item The union of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cup \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q'= Q_1 \cup Q_2$, $\delta' = \delta_1 \cup \delta_2$, $I' = I_1 \cup I_2$, and $F'=F_1 \cup F_2$.
-% %
-% \item The intersection of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \cap \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, and $\delta' = \{((q_1, q_2), a, (q'_1, q'_2)) \mid (q_1, a, q'_1) \in \delta_1, (q_2, a, q'_2) \in \delta_2\}$.
-% %
-% \item The concatenation of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \concat \NFA_2$, is defined as the tuple $(Q', \Sigma, \delta', I', F')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\delta' = \delta_1 \cup \delta_2 \cup \{(q_1, a, q_2) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
-% %
-% \item The Kleene star of $\NFA_1$, denoted by $\NFA_1^*$, is defined as $(Q'_1, \Sigma, \delta'_1, I'_1, F'_1)$, where $Q'_1 = Q_1 \cup \{q_0\}$ with $q_0 \not \in Q_1$, $I'_1 = \{q_0\}$, $F'_1= F_1 \cup \{q_0\}$, $\delta'_1 = \delta_1 \cup \{(q_0, a, q'_1)  \mid \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\} \cup \{(q_1, a, q'_1) \mid q_1 \in F_1, \exists q'_0 \in I_1.\ (q'_0, a, q'_1) \in \delta_1\}$.
-% %
-% \item The complement of $\NFA_1$, denoted by $\overline{\NFA_1}$, is defined as $(Q'_1, \Sigma, \delta'_1, q'_0, Q'_1 \setminus F'_1)$, where  $(Q'_1, \Sigma, \delta'_1, q'_0, F'_1)$ is the DFA obtained from $\NFA_1$ by subset construction.
-% %
-% \item The language difference of $\NFA_1$ and $\NFA_2$, denoted by $\NFA_1 \setminus \NFA_2$, is defined as $\NFA_1 \cap \overline{\NFA_2}$.
-% \end{itemize}
+\sout{The constructions of NFA corresponding to these language operations are list in \ref{appendix:cefa}}
 
@@
 The \emph{Parikh image} of an NFA $\NFA$, denoted by $\parikh(\NFA)$, is defined as $\{\parikh(w) \mid w \in \Lang(\NFA)\}$.
-
-%\tl{to put in a different place later} Note that our decision procedure also applies to general transducers.
-However, the EXPSPACE complexity bound is not because the distributive property $f^{-1}(L_1\cap L_2)= f^{-1}(L_1)\cap f^{-1}(L_2)$ for regular languages $L_1, L_2$ only holds for functional transducers $f$.
-
-%We remark that an FT usually defines a relation.
-
-%\smallskip
-
-%In this paper, we consider logic involving two data types, i.e., the string and integer data types.
-We will use $u, v, \dots$ to denote string constants,  $c, d,\dots$ to denote integer constants, $x, y, \dots$ to denote string variables, and $i, j, \dots$ to denote integer variables.
 
@@
 For an LIA formula $\varphi(\vec{\anivar})$, we use $\varphi[\myvec{t}/\myvec{\anivar}]$ to denote the formula obtained by replacing (simultaneously) $\anivar_i$ with $t_i$ for every $i \in [k]$ where $\myvec{\anivar} = (\anivar_1, \cdots, \anivar_k)$ and $\myvec{t} = (t_1, \cdots, t_k)$ are tuples of integer terms.
-%For convenience, we assume a set $X$ of variables is a vector. 
-%, which is essentially Presburger
 
@@
 \vspace{-3mm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\hide{
-A finite \emph{alphabet} $\Sigma$ is the set of all \emph{letters}. A
-\emph{string} (or \emph{word}) is a finite sequence of letters from $\Sigma$.
-$\Sigma^*$ is the set of strings over $\Sigma$.
-$\epsilon$ is the empty string.
-$L$ is grammar.
-A language $\lan(L)$ is a set of words generated by $L$.
-$\mathbb{N}$ is the set of natural numbers and $\mathbb{Z}$ is the set of integer numbers.
-We use $a,
-  b,\cdots$ to denote the constant letters in $\Sigma$, $u, v,\cdots$ to denote constant
-string, $x, y,\cdots$ to denote variable string, $m,n,\cdots$ to
-denote integer constant, and $i,j\cdots$ to denote integer variable.
-For vector, we use $\myvec{v}$ to denote the vector of integer constant, $m_n$ to denote the vector $(m,\cdots, m)$ with length $n$, $\myvec{v}[i]$ to denote the integer value of $\myvec{v}$ at position $i$, $\myvec{v_1}\cdot\myvec{v_2}$ to denote the concatenation of $\myvec{v_1}$ and $\myvec{v_2}$, $R$ to denote the vector of registers, $R_1 \cap R_2$ to denote the same registers in $R_1$ and $R_2$, and $|\myvec{v}|$ or $|R|$ to denote the length of the vector.
-}

### 2023-10-19 2023-1-19/sections/recl.tex
remove comments

@@
 %!TEX root = ../main.tex
-%\documentclass{standalone}
-%\begin{document}
-
-%\subsubsection{Syntax}
 In the sequel, we define the string constraints with regex-counting and string-length functions, i.e., \textbf{RE}gex-\textbf{C}ounting \textbf{L}ogic (abbreviated as RECL).
@@
 % 
-%is a quantifier-free formula that can be a regular membership $x\in\regex$, a quantifier-free Presburger formula $\alpha_1 \leq \alpha_2$, a negation of a formula, or a disjunction of two formulas.
-$\alpha$ is an integer term which can be an integer constant $m$, integer variable $i$, the length of the string term $|s|$, the minus of an integer term, and the plus of two integer terms.
-The regular expression $\regex$ is built on empty string $\epsilon$, constant letter $a\in \Sigma$.
-The supported regex operations involve concatenation $\cdot$, disjunction $+$, intersection $\times$, closure $*$, complement $C$, and bounded repetition $\{m, n\}$.
-We use $term(\varphi)$ to denote the set of terms and $strvar(\varphi)$ to denote the string variables occurring in $\varphi$.
-The \emph{literals} of $\varphi$ are $x\in \regex$ and $\alpha_1 \leq \alpha_2$.
-$x\in \regex$ is called \emph{regular literals} and $\alpha_1 \leq \alpha_2$ is called \emph{linear literals}.
 \begin{figure}[h]
   \centering
-%  \begin{tabular}{l r}
 $ \begin{array}{l l l r}
@@
   $
-%  \end{tabular}
   \caption{Syntax of RECL }\label{fig:syntax}
@@
 Moreover, for $S \subseteq \Sigma$ with $S = \{a_1, \cdots, a_k\}$, we use $S$ as an abbreviation of $a_1 + \cdots + a_k$.
-
-%The definition of the semantics of RECL is standard. Nevertheless, for readability, we include the definition of its semantics here.
 
@@
 A  mapping $\theta$ is said to satisfy $\varphi$, denoted by $\theta \models \varphi$, if one of the following holds: 
-%\begin{itemize}
-%\item 
 $\varphi \equiv x \in \regex$ and $\theta(x) \in \Lang(\regex)$, 
 %
-%\item $\varphi \equiv x \not \in \regex$ and $\theta(x) \not \in \Lang(\regex)$, 
-%
-%\item 
 $\varphi \equiv t_1\ \op\ t_2$ and $\theta(t_1)\ \op\ \theta(t_2)$, 
 %
-%\item 
 $\varphi \equiv \varphi_1 \wedge \varphi_2$ and $\theta \models \varphi_1$ and $\theta \models \varphi_2$.
-%\end{itemize}
 A RECL formula $\varphi$ is satisfiable if there is a mapping $\theta$ such as $\theta \models \varphi$.
 The satisfiability problem for RECL (which is abbreviated as $\reclsat$) is deciding whether a given RECL formula $\varphi$ is satisfiable.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\hide{
-We assume that $S$ is the set of string variables over $\Sigma^*$, and $I$ is the set of integer variables.
-$\eta: S\times\Sigma\rightarrow\Sigma^*$ is the interpretation on string where $\eta(c)=c$ for every letter $c\in \Sigma$.
-$\pi: I\rightarrow\mathbb{Z}$ is the interpretation of Presburger arithmetic.
-Then the semantics is given by a satisfaction relation: $\eta, \pi\models \varphi$ defined in Table \ref{tab:semantics}.
-We say a formula $\varphi$ is \emph{satisfiable} if a solution $(\eta, \pi)$ exists such as $\eta, \pi\models \varphi$.
-A formula $\varphi$ is \emph{unsatisfiable} if no solution exists.
-\begin{table}[h]
-  \centering
-  \begin{tabular}{lcl}
-    $\eta,\pi \models \varphi_1\vee \varphi_2$ & $\mathsf{iff}$ & $\eta,\pi \models \varphi_1 \text{ or } \eta,\pi \models \varphi_2$ \\
-    $\eta,\pi \models \neg\varphi $            & $\mathsf{iff}$ & $\eta,\pi \not\models \varphi$                                      \\
-    $\eta, \pi \models x\in \regex$            & $\mathsf{iff}$ & $\exists w \in \lan(\regex),\eta,\pi \models x = w$                 \\
-    $\eta, \pi \models \alpha_1 \leq \alpha_2$ & $\mathsf{iff}$ & $\pi(\alpha_1) \leq \pi(\alpha_2) $                                 \\
-  \end{tabular}
-  \caption{Semantics}
-  \label{tab:semantics}
-\end{table}
-%
-In addition to the classic regex operators (union, concatenation, closure), we syntactically support intersection, complement, and repetition.
-As we all know, the classic regular language is closed under intersection and complement \cite{aut_hopcraft}.
-Furthermore, the operation \emph{repetition} $\regex\{m,n\}$ means repeating regex $\regex$ at least $m$ times and at most $n$ times.
-It can be syntactically rewritten by concatenation and union:
-$\regex\{m,n\} \equiv \regex^m\mid\cdots\mid\regex^n$ where $\regex^k$ defines concatenate $\regex$ $k$ times ($m\leq k\leq n$).
-So the regular language $\lan(\regex)$ defined in Table \ref{tab:syntax} is semantically equal to the classic regular language.
-}
-
-%\end{document}

### 2023-10-19 2023-1-19/sections/cefa.tex
remove vspace

@@
 %
-\vspace{-0.5mm}
 \begin{definition}[Cost-Enriched Finite Automaton]
@@
 \end{definition}
-\vspace{-0.5mm}
 
@@
 The \emph{intersection} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cap \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, is defined in the sequel. 
-\vspace{-0.5mm}
 \begin{itemize}
@@
 \end{itemize}
-\vspace{-0.5mm}
 From the construction, 
-\vspace{-0.5mm}
 $$\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v}) \mid (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
-\vspace{-0.5mm}
 Intuitively, $\aut_1 \cap \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.

### 2023-10-19 2023-1-19/sections/algorithms.tex
remove denghang comments

@@
 \noindent
-\emph{Step 1.\denghang{(Intersection)}} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
+\emph{Step 1.(Intersection)} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
 
@@
 the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the final output $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
-\sout{Therefore, we propose the following size-reduction technique for the NFA $\cU_{\cB_i}$'s.} \denghang{Regardless of alphabet, we take register updates as new alphabet symbols and $\myvec{0}$ as $\epsilon$ symbol.
-Then we are capable of using standard minimization to reduce the automata size.}
+Therefore, we propose the following size-reduction technique for the NFA $\cU_{\cB_i}$'s.
+Regardless of alphabet, we take register updates as new alphabet symbols and $\myvec{0}$ as $\epsilon$ symbol.
+Then we are capable of using standard minimization to reduce the automata size.
 
@@
 \noindent
-\emph{Step 2.\denghang{(Automata size reduction)}} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, and remove the $\varepsilon$-transitions from $\cU_{\cB_i}$.
+\emph{Step 2.(Automata size reduction)} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, and remove the $\varepsilon$-transitions from $\cU_{\cB_i}$.
 Then we determinize and minimize the resulting NFA.
@@
 \noindent
-\emph{Step 3.\denghang{(Parikh image)}} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+\emph{Step 3.(Parikh image)} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
 Then we solve the satisfiability of the following formula,

### 2023-10-19 2023-1-19/sections/cefa.tex
remove denghang comments

@@
 The following section will use these three operations to solve RECL constraints.
-\denghang{Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than register automata~\cite{ra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting condition is attached to each automaton, not each final state.}
+Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than register automata~\cite{ra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting condition is attached to each automaton, not each final state.
 
@@
 
-The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$ \sout{is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states}.
+The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$ is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.
 Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).

### 2023-10-19 2023-1-19/sections/implementation.tex
remove vspace
remove denghang comments

@@
 Then we present experiment results of the large-counting part and evaluate the simplification techniques.
-\denghang{The goal of our experiments is to answer the following questions:
+The goal of our experiments is to answer the following questions:
 \begin{itemize}
@@
 \end{itemize}
-}
 
-\vspace{-2mm}
 \subsection{Benchmark Suites and Experiment Setup}\label{sec:bench}
-\vspace{-1mm}
 
 Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}.
-\denghang{Other industrial benchmarks suites are not utilized because they contains no counting operators.} There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
+Other industrial benchmarks suites are not utilized because they contains no counting operators.
+There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
 Moreover, it turns out that only 5\% of regexes among the 48,843 instances are non-register-representable (see Section~\ref{subsec:regex2cefa}).
@@
 The expression $e_{sani}$ is introduced in view of the fact that these characters are usually sanitized in Web browsers to alleviate the XSS attacks \cite{malware_detection_3_kudzu,CCH_18}.
-\vspace{-0.1mm}
 
@@
 \noindent
-\denghang{
+
 \emph{Large-Bounds part.} This benchmark suite is composed of 1,969 problem instances with large counting bounds (greater than or equal to $50$) from RegCoL and AutomatArk benchmark suites.  
 Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
-}
 
@@
 
-\vspace{-2mm}
 \subsection{Overall Evaluation}\label{subsec:overall_eval}
-\vspace{-1mm}
 
@@
 Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
-Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, \denghang{and the results distinct to the ground truth are called \emph{soundness errors}.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results distinct to the ground truth are called \emph{soundness errors}.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
 The number is \textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
@@
 Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93s}/1.62s).
-\denghang{To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.}
+To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.
 
@@
 \begin{table}
-  \vspace{-4mm}
   \centering
@@
   \end{subtable}
-  \vspace{-2mm}
   \caption{Overall evaluation and the evaluation of the size-reduction techniques}
-  \vspace{-8mm}
 \end{table}
@@
 %
-\sout{We extract the 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
-Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.}
+We extract the 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
+Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
 %
@@
     \import{tables}{table_large_count.tex}
-    \vspace{4.5mm}
     \caption{Experiment results on Large-Bounds part, with timeout = 60 seconds.}
@@
   \end{subfigure}
-  \vspace{-2mm}
   \caption{Distribution of counting bounds and experiment results for large bounds}
-\vspace{-5mm}
 \end{figure}
@@
 Moreover, $\ostrichrecl$ is \textbf{ 6.79/2.88/2.61/5.27/3.95} times faster than CVC5/ Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-\denghang{To answer \textbf{Q1}, we can see that $\ostrichrecl$ \textbf{is far more efficient than the other solvers on problem instances with large bounds.}}
+To answer \textbf{Q1}, we can see that $\ostrichrecl$ \textbf{is far more efficient than the other solvers on problem instances with large bounds.}
 
@@
 From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$.
-\denghang{To answer \textbf{Q2}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}}.
+To answer \textbf{Q2}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}.
 Moreover, $\ostrichrecl$ solves \textbf{1,798 more} instances and is \textbf{3.13} times faster than $\ostrichrecl_{\rm NUXMV}$.
-\denghang{To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}}.
+To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}.

### 2023-10-19 2023-1-19/sections/introduction.tex
remove vspace
remove denghang comments

@@
 We make the following contributions.
-\vspace{-0.5mm}
 \begin{itemize}
@@
 \end{itemize}
-\vspace{-0.5mm}
 
@@
 Nevertheless, the nonemptiness problem of these automata was not considered, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
-\denghang{For the automata model, the definition of registers of CEFAs resembles the counters of the counter automata class~\cite{GGM12,redos_lenka,HS+23,GKM23}, but CEFAs contain no guards in each transition.
+For the automata model, the definition of registers of CEFAs resembles the counters of the counter automata class~\cite{GGM12,redos_lenka,HS+23,GKM23}, but CEFAs contain no guards in each transition.
 Register automata~\cite{ra} and symbolic register automata~\cite{sra} utilize registers to store input variables (i.e., the letters of the alphabet), on which only equality and inequality are permitted.
-In contrast, CEFAs utilize registers to store integers constrained by linear arithmetic formulae.}
+In contrast, CEFAs utilize registers to store integers constrained by linear arithmetic formulae.
 Real-world regexes in programming languages include features beyond classical regular expressions, e.g., the greedy/lazy Kleene star, capturing groups, and back references.
@@
 Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22}.
-\sout{Solving string constraints involving lengths has also been investigated by various researchers, see e.g.
-\cite{WC+18,atva2020,z3str3re}.} \denghang{Except for the string solvers mentioned before, some related works about string constraints with the length function exist.
+Solving string constraints involving lengths has also been investigated by various researchers, see e.g.
+\cite{WC+18,atva2020,z3str3re}.
+Except for the string solvers mentioned before, some related works about string constraints with the length function exist.
 Trau~\cite{z3trau} relies on a Counter-Example Guided Abstraction Refinement (CEGAR) framework in which the under- and over-approximation of the automata are iteratively refined to solve length and regex constraints.
 Slent~\cite{WC+18} transfers the string and length constraints to length-encoded automata, and leverages a symbolic model checker as an engine for the emptiness checking of automata.
-However, both Trau and Slent do not support counting operators.}
+However, both Trau and Slent do not support counting operators.
 

### 2023-10-19 2023-1-19/sections/preliminaries.tex
remove vspace
remove denghang comments

@@
 For readability, we write a transition $(q, a, q') \in \delta$ as $q \xrightarrow[\delta]{a} q'$ (or simply $q \xrightarrow{a} q'$).
-\denghang{Note that one initial state is sufficient.
-A set of initial states is a technical choice to simplify the defination of union operation in Sec \ref{sec:automaton}.}
+Note that one initial state is sufficient.
+A set of initial states is a technical choice to simplify the defination of union operation in Sec \ref{sec:automaton}.
 The \emph{size} of an NFA $\NFA$, denoted by $|\NFA|$, is defined as the number of transitions of $\NFA$.
@@
 Moreover, the class of regular languages is closed under union, intersection, concatenation, Kleene star, complement, and language difference \cite{HU79}.
-\sout{The constructions of NFA corresponding to these language operations are list in \ref{appendix:cefa}}
+The constructions of NFA corresponding to these language operations are list in \ref{appendix:cefa}
 
@@
 \end{theorem}
-\vspace{-3mm}

### 2023-10-19 2023-1-19/sections/implementation.tex
remove denghang comments

@@
 Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
-Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results distinct to the ground truth are called \emph{soundness errors}.} We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results distinct to the ground truth are called \emph{soundness errors}.
+We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
 The number is \textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.

### 2023-10-19 2023-1-19/sections/cefa.tex
remove some contents

@@
 
-The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$ is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states.
+The \emph{union} of $\aut_1$ and $\aut_2$ is denoted by $\aut_1 \cup \aut_2$.
 Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).

### 2023-10-19 2023-1-19/sections/introduction.tex
remove some contents
related work

@@
 Regular expressions (regex for short) and the string-length function are widely used in string-manipulating programs.
-According to the statistics from \cite{CS16,DCSL18,WS18}, regular expressions are used in about 30–40\% of Java, JavaScript, and Python software projects.
+According to the statistics from \cite{CS16,DCSL18,WS18}, regexes are used in about 30–40\% of Java, JavaScript, and Python software projects.
 Moreover, string-length occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}. 
-As a result, most of the aforementioned string constraint solvers support both regular expressions and string-length function.
-Moreover, specialized algorithms have been proposed to solve such string constraints efficiently.
-\cite{LTR+15,BD+23}.
+As a result, most of the aforementioned string constraint solvers support both regexes and string-length function.
+Moreover, specialized algorithms have been proposed to solve such string constraints efficiently (see e.g.
+\cite{LTR+15,BD+23}).
 
-Counting (aka repetition) is a convenient feature in regular expressions that count the number of matchings of sub-patterns.
+Counting (aka repetition) is a convenient feature in regexes that count the number of matchings of sub-patterns.
 For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
 Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ is equivalent to $a^{\{0,\infty\}}$ and $a^+$ are equivalent to $a^{\{1,\infty\}}$.
-Counting is a frequently used feature of regular expressions.
+Counting is a frequently used feature of regexes.
 According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while other forms of counting occur in more than 20\% of them.
-Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints containing regular expressions with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function at least.
+Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints containing regexes with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function at least.
 
 Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting and length bounds are large.
-For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 120 seconds.
+For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 120 seconds,
 %, and Z3 can not solve it within 120 seconds.
@@
 \emph{Related work.} 
-We discuss more related work about regexes with counting in programming languages.  
+We discuss more related work about regexes with counting, string-length function, and automata with registers/counters.  
+%
 The determinism of regexes with counting was investigated in~\cite{GGM12,CL15}. 
+%
+Real-world regexes in programming languages include features beyond classical regexes, e.g., the greedy/lazy Kleene star, capturing groups, and back references.
+Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
+Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22}. 
+%
+Trau focuses on string constraints involving flat regular languages and string-length function and solves them by computing LIA formulas that define the Parikh images of flat regular languages~\cite{z3trau}.
+Slent solves string constraints involving string-length function by encoding the string constraints into so called length-encoded automata, and solving their nonemptiness problem by symbolic model checkers~\cite{WC+18}.
+However, neither Trau nor Slent supports counting operators.
+In other words, counting operators in regexes should be unfolded before solved by them.
+%
+The cost registers in CEFAs are different from registers in (symbolic) register automata~\cite{ra,sra}, where registers are used to store input values and they can only be compared for equality/inequality.
+In contrast, registers in CEFAs are used to store integer-valued costs and they can be updated by adding/subtracting integer constants and constrained by the accepting conditions which are LIA formulas.
+%
+\zhilin{stopped here}
+Intuitively speaking, CEFAs can be adapted from classical counter automata \cite{xxx},  by removing the transition guards and adding the accepting conditions. 
+%
+For the automata model, the definition of registers of CEFAs resembles the counters of the counter automata class~\cite{GGM12,redos_lenka,HS+23,GKM23}, but CEFAs contain no guards in each transition. 
+%
 Counting-set automata were proposed in~\cite{redos_lenka,HS+23} to quickly match a subclass of regexes with counting.
@@
 Nevertheless, the nonemptiness problem of these automata was not considered, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
-For the automata model, the definition of registers of CEFAs resembles the counters of the counter automata class~\cite{GGM12,redos_lenka,HS+23,GKM23}, but CEFAs contain no guards in each transition.
-Register automata~\cite{ra} and symbolic register automata~\cite{sra} utilize registers to store input variables (i.e., the letters of the alphabet), on which only equality and inequality are permitted.
-In contrast, CEFAs utilize registers to store integers constrained by linear arithmetic formulae.
-Real-world regexes in programming languages include features beyond classical regular expressions, e.g., the greedy/lazy Kleene star, capturing groups, and back references.
-Real-world regexes have been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving~\cite{CF+22}.
-Nevertheless, the counting operators are still unfolded explicitly in~\cite{CF+22}.
-Solving string constraints involving lengths has also been investigated by various researchers, see e.g.
-\cite{WC+18,atva2020,z3str3re}.
-Except for the string solvers mentioned before, some related works about string constraints with the length function exist.
-Trau~\cite{z3trau} relies on a Counter-Example Guided Abstraction Refinement (CEGAR) framework in which the under- and over-approximation of the automata are iteratively refined to solve length and regex constraints.
-Slent~\cite{WC+18} transfers the string and length constraints to length-encoded automata, and leverages a symbolic model checker as an engine for the emptiness checking of automata.
-However, both Trau and Slent do not support counting operators.
+
+%Except for the string solvers mentioned before, some related works about string constraints with the length function exist.
 

### 2023-10-19 2023-1-19/sections/introduction.tex
related work

@@
 %
-Trau focuses on string constraints involving flat regular languages and string-length function and solves them by computing LIA formulas that define the Parikh images of flat regular languages~\cite{z3trau}.
-Slent solves string constraints involving string-length function by encoding the string constraints into so called length-encoded automata, and solving their nonemptiness problem by symbolic model checkers~\cite{WC+18}.
-However, neither Trau nor Slent supports counting operators.
-In other words, counting operators in regexes should be unfolded before solved by them.
+The Trau tool focuses on string constraints involving flat regular languages and string-length function and solves them by computing LIA formulas that define the Parikh images of flat regular languages~\cite{z3trau}.
+The Slent tool solves the string constraints involving string-length function by encoding them into so-called length-encoded automata, then utilizing symbolic model checkers to solve their nonemptiness problem~\cite{WC+18}.
+However, neither Trau nor Slent supports counting operators explictly, in other words, counting operators in regexes should be unfolded before solved by them.
 %
-The cost registers in CEFAs are different from registers in (symbolic) register automata~\cite{ra,sra}, where registers are used to store input values and they can only be compared for equality/inequality.
-In contrast, registers in CEFAs are used to store integer-valued costs and they can be updated by adding/subtracting integer constants and constrained by the accepting conditions which are LIA formulas.
+Cost registers in CEFAs are different from registers in (symbolic) register automata~\cite{ra,sra}:  In register automata, registers are used to store input values and  can only be compared for equality/inequality, while in CEFAs, cost registers are used to store integer-valued costs and can be updated by adding/subtracting integer constants and constrained by the accepting conditions which are LIA formulas.
 %
-\zhilin{stopped here}
-Intuitively speaking, CEFAs can be adapted from classical counter automata \cite{xxx},  by removing the transition guards and adding the accepting conditions. 
+Therefore, cost registers in CEFAs are more like counters in counter automata/machines~\cite{Minsky67}, that is, CEFAs can be obtained from counter machines by removing  transition guards and adding accepting conditions.
 %
-For the automata model, the definition of registers of CEFAs resembles the counters of the counter automata class~\cite{GGM12,redos_lenka,HS+23,GKM23}, but CEFAs contain no guards in each transition. 
+%For the automata model, the definition of registers of CEFAs resembles the counters of the counter automata class~\cite{Minsky67}, but CEFAs contain no guards in each transition. 
 %

### 2023-10-19 2023-1-19/sections/algorithms.tex
remove some contents
section 6

@@
 
-This section aims to show how to solve RECL constraints by utilizing CEFA. 
-At first, we reduce the satisfiability of RECL constraints to a decision problem defined in the following section. Then we propose an decision procedure to solve the problem.
+The goal of this section is to show how to solve RECL constraints by utilizing CEFA. 
+At first, we reduce the satisfiability of RECL constraints to a decision problem defined in the sequel. Then we propose a decision procedure for this problem.
 
@@
 \end{definition}
-\begin{proposition}\label{prop-cefadec}
+\begin{proposition}[\cite{atva2020}]\label{prop-cefadec}
 $\cefadec$ is PSPACE-complete. 
 \end{proposition}
-\begin{proof}
-  The lower bound follows from the fact that the nonemptiness problem of the intersection of NFAs is PSPACE-complete \cite{pspace_int}.
+%\begin{proof}
+%  The lower bound follows from the fact that the nonemptiness problem of the intersection of NFAs is PSPACE-complete \cite{pspace_int}.
 For the upper bound, \cite{atva2020} showed that $\cefadec$ is in PSPACE by reducing it to monotonic counter machines.
-\end{proof}
+%\end{proof}
 Note that the decision procedure in \cite{atva2020} was only used to prove the upper bound in Proposition~\ref{prop-cefadec} and not implemented as a matter of fact.
-Instead, the symbolic model checker nuXmv was used to solve $\cefadec$.
+Instead, the symbolic model checker nuXmv~\cite{nuxmv} was used to solve $\cefadec$.
 We do not rely on nuXmv in this work and shall propose a new algorithm for solving $\cefadec$ in Section~\ref{subsec:cefadec}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Solving $\cefadec$} \label{subsec:cefadec}
@@
 \noindent
-\emph{Step 1.(Intersection)} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
+\emph{Step 1 (Computing intersection automata).} For each $i \in [n]$, compute a CEFA $\cB_{i} = \aut_{i,1} \cap \cdots \cap \aut_{i, l_i}$, and let $\Lambda'_{x_i} := \{\cB_i\}$. \qed
 
-After Step 1, the nonemptiness of CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
+After Step 1, the nonemptiness of CEFAs in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFAs in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
 
-In the following steps, we reduce the non-emptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+In the following steps, we reduce the non-emptiness of CEFAs in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
 $\varphi$ to the satisfiability of an LIA formula.
-The reduction relies on two observations: The first observation follows that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA, and the second observation follows that the non-emptiness of exactly one CEFA w.r.t LIA formulae is entirely unrelated to the alphabet.
+The reduction relies on the following two observations.
+%The first observation follows from the fact that $\Lambda'_{x_i}$ for each $i \in [n]$ contains exactly one CEFA, and the second observation follows from the fact that the non-emptiness of exactly one CEFA w.r.t an LIA formula is entirely unrelated to the alphabet.
 
@@
 %
-$$\cefaout(\aut) = \left\{\sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \  \big{|}\ \eta \in \parikh(\cU_\aut) \mbox{ and }  \alpha\left[ \sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \big{/} R \right] \mbox{ is true}\right\}.$$
+$$\cefaout(\aut) = \left\{\sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \left \vert\ \eta \in \parikh(\cU_\aut) \mbox{ and }  \alpha\left[  \sum \limits_{\myvec{v} \in \costset_\aut} \eta(\myvec{v}) \myvec{v} \big{/}  R \right] \mbox{ is true}\right.\right\}.$$
 %
@@
 
-Because the sizes of the LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$, and the satisfiability of existential LIA formulas is NP-complete, it is vital to reduce the sizes of these NFA to improve the performance.
+Because the sizes of the LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ are proportional to the sizes (more precisely, the alphabet size, the number of states and transitions) of NFA $\cU_{\cB_1}, \cdots, \cU_{\cB_n}$, and the satisfiability of existential LIA formulas is NP-complete, it is vital to reduce the sizes of these NFAs to improve the performance.
 
@@
 the $\myvec{0}$-labeled transitions in $\cU_{\cB_i}$ do not contribute to the final output $\sum \limits_{\myvec{v} \in \costset(\cB_i)} \eta(\myvec{v}) \myvec{v}$.
-Therefore, we propose the following size-reduction technique for the NFA $\cU_{\cB_i}$'s.
-Regardless of alphabet, we take register updates as new alphabet symbols and $\myvec{0}$ as $\epsilon$ symbol.
-Then we are capable of using standard minimization to reduce the automata size.
+Therefore, we can apply the following size-reduction technique for $\cU_{\cB_i}$'s.
+%Regardless of alphabet, we take register updates as new alphabet symbols and $\myvec{0}$ as $\epsilon$ symbol. Then we are capable of using standard minimization to reduce the automata size.
 
@@
 \noindent
-\emph{Step 2.(Automata size reduction)} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, and remove the $\varepsilon$-transitions from $\cU_{\cB_i}$.
+\emph{Step 2 (Reducing automata sizes).} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cU_{\cB_i}$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, and remove the $\varepsilon$-transitions from $\cU_{\cB_i}$.
 Then we determinize and minimize the resulting NFA.
@@
 \noindent
-\emph{Step 3.(Parikh image)} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+\emph{Step 3 (Computing Parikh images).} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
 Then we solve the satisfiability of the following formula,
@@
 \]
-\qed
+%\qed

### 2023-10-20 2023-1-19/sections/implementation.tex
remove some contents
crv version finished

@@
 %!TEX root = ../main.tex
-In this section, we list our experimental results.
-We first present the overall experiment results on RegCoL and AutomatArk benchmark suites.
-Then we present experiment results of the large-counting part and evaluate the simplification techniques.
-The goal of our experiments is to answer the following questions:
-\begin{itemize}
-  \item [Q1:] Does the decision procedure perform well~(Sec \ref{subsec:overall_eval}), especially when the counting bounds are large?~(Sec \ref{subsec:large_bounds_eval})
-  \item [Q2:] Are the size-reduction techniques practical?~(Sec \ref{subsec:size_reduction_eval})
-  \item [Q3:] How effective is the algorithm for solving the nonemptiness problem compared to the case that uses the nuXmv model checker~\cite{atva2020}?~(Sec \ref{subsec:size_reduction_eval})
-\end{itemize}
 
-\subsection{Benchmark Suites and Experiment Setup}\label{sec:bench}
+We implemented the algorithm in Section~\ref{sec:algorithm} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
+%
+In this section, we evaluate the performance of $\ostrichrecl$ on two benchmark suites, that is, RegCoL and AutomatArk.
+In the sequel, we first describe the two benchmark suites as well as the experiment setup.
+Then we present the experiment results.
+We do experiments to compare the performance of $\ostrichrecl$ with the state-of-the-art string solvers.
+Moreover, in order to know whether $\ostrichrecl$ is good at solving string constraints with large counting and length bounds, we extract 1,969 instances with large bounds out of the two benchmark suites, and compare the performance of $\ostrichrecl$ with the other solvers on these instances.
+Finally, we empirically justify the technical choices made in the decision procedure of Section~\ref{subsec:cefadec} by comparing $\ostrichrecl$ with the following two variants of $\ostrichrecl$: $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$, where $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$ are obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
+Step 2 in Section~\ref{subsec:cefadec}) and using the nuXmv model checker to solve the nonemptiness of $\cefadec$ respectively.
+
+%including the results for an overall evaluation as well as the results on the benchmark instances with large bounds.
+Moreover, we do experiments to show the effectiveness of the automata size-reduction technique (i.e.
+Step 2 in Section~\ref{sec:algorithm}) as well as compare $\ostrichrecl$ with the  nuXmv-based approach in \cite{atva2020}.
+
+%Then we present experiment results of the large-counting part and evaluate the simplification techniques. The goal of our experiments is to answer the following questions:
+%\begin{itemize}
+%  \item [Q1:] Does the decision procedure perform well~(Sec \ref{subsec:overall_eval}), especially when the counting bounds are large?~(Sec \ref{subsec:large_bounds_eval})
+%  \item [Q2:] Are the size-reduction techniques practical?~(Sec \ref{subsec:size_reduction_eval})
+%  \item [Q3:] How effective is the algorithm for solving the nonemptiness problem compared to the case that uses the nuXmv model checker~\cite{atva2020}?~(Sec \ref{subsec:size_reduction_eval})
+%\end{itemize}
+
+\subsection{Benchmark suites and experiment setup}\label{sec:bench}
 
@@
 \noindent
-
-\emph{Large-Bounds part.} This benchmark suite is composed of 1,969 problem instances with large counting bounds (greater than or equal to $50$) from RegCoL and AutomatArk benchmark suites.  
-Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
-
-\medskip
-\noindent
 \emph{Distribution of problem instances w.r.t. counting bounds. }
@@
 
-\subsection{Overall Evaluation}\label{subsec:overall_eval}
-
-We evaluate the performance of $\ostrichrecl$ against the state-of-the-art string constraint solvers, including CVC5
-\cite{cvc5}, Z3seq \cite{z3seq}, Z3str3
-\cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH
-\cite{ostrich2023}, on RegCoL and AutomatArk benchmark suites.
-The experiment results can be found in Table~\ref{tab:results_regcol}.
-Note that we take the result of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
-Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results distinct to the ground truth are called \emph{soundness errors}.
-We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves \textbf{48,662} instances correctly.
-The number is \textbf{3,908/1,111/12,838/2,306/2,396 more} than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-%
-Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (\textbf{1.93s}/1.62s).
-To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.
-
-%
-\begin{table}
-  \centering
-  \begin{subtable}{0.513\textwidth}
-      \centering
-      \import{tables}{table_regcol.tex}
-      \caption{Overall evaluation, with timeout = 60 seconds.}
-      \label{tab:results_regcol}
-  \end{subtable}
-  \begin{subtable}{0.477\textwidth}
-      \centering
-      \import{tables}{table_simp.tex}
-      \caption{Evaluation of the size-reduction techniques, with timeout = 60 seconds.}
-      \label{tab:results_simp}
-  \end{subtable}
-  \caption{Overall evaluation and the evaluation of the size-reduction techniques}
-\end{table}
-
-\subsection{Evaluation on problem instances with large bounds}\label{subsec:large_bounds_eval}
-%
-We extract the 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
-Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
 %
@@
     \centering\vskip 0pt
-    \includegraphics[width=1\textwidth]{counting_distribution.png}  
+    \includegraphics[width=0.9\textwidth]{counting_distribution.png}  
     \caption{Distribution of problem instances w.r.t. counting bounds}  
@@
     \centering\vskip 0pt
-    \import{tables}{table_large_count.tex}
-    \caption{Experiment results on Large-Bounds part, with timeout = 60 seconds.}
-    \label{fig:table_large_count}
+      \import{tables}{table_regcol.tex}
+      \caption{Overall performance evaluation}
+    \label{fig:table_overall_eval}
   \end{subfigure}
-  \caption{Distribution of counting bounds and experiment results for large bounds}
+  \caption{Distribution of counting bounds and performance evaluation}
 \end{figure}
 
-We evaluate the performance of $\ostrichrecl$ on 1,969 instances of the Large-Bounds part. 
-The experiment results are put in Fig~\ref{fig:table_large_count}.
-From the results, $\ostrichrecl$ solves \textbf{1,873} instances correctly, which is \textbf{947/278/563/637/523 more} than that solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-Moreover, $\ostrichrecl$ is \textbf{ 6.79/2.88/2.61/5.27/3.95} times faster than CVC5/ Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
-To answer \textbf{Q1}, we can see that $\ostrichrecl$ \textbf{is far more efficient than the other solvers on problem instances with large bounds.}
+\subsection{Performance evaluation}\label{subsec:overall_eval}
 
-\subsection{Evaluation of the effectiveness of size-reduction techniques}\label{subsec:size_reduction_eval}
-We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
-Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
-Meanwhile, we compare $\ostrichrecl$ and $\ostrichrecl_{\rm -SIMP}$ against $\ostrichrecl_{\rm NUXMV}$, where the $\cefadec$ problem is solved by the \textsc{nuXmv} model checker \cite{nuxmv}, instead of the procedure in Section~\ref{subsec:cefadec}.
-The experiment results are put in Table~\ref{tab:results_simp}. 
-From the results, $\ostrichrecl$ solves \textbf{1,503 more} instances and is \textbf{2.21} times faster than $\ostrichrecl_{\rm -SIMP}$.
-To answer \textbf{Q2}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}.
-Moreover, $\ostrichrecl$ solves \textbf{1,798 more} instances and is \textbf{3.13} times faster than $\ostrichrecl_{\rm NUXMV}$.
-To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}.
+We evaluate the performance of $\ostrichrecl$ against the state-of-the-art string constraint solvers, including CVC5
+\cite{cvc5}, Z3seq \cite{z3seq}, Z3str3
+\cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH
+\cite{CHL+19}, on RegCoL and AutomatArk benchmark suites.
+The experiment results can be found in Figure~\ref{fig:table_overall_eval}.
+Note that we take the results of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results different from the ground truth are classified as \emph{soundness error}.
+We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves 48,662 instances correctly.
+The number is 3,908/1,111/12,838/2,306/2,396 more than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+%
+Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (1.93s versus 1.62s).
+
+%To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.
+
+%
+
+\subsection{Evaluation on problem instances with large bounds}\label{subsec:large_bounds_eval}
+
+We extract 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
+Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
+
+We evaluate the performance of $\ostrichrecl$ on the 1,969 instances. 
+The experiment results can be found in Table~\ref{tab:large-bound}.
+We can see that $\ostrichrecl$ solves 1,873 instances correctly, which is 947/278/563/637/523 more than those solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+Furthermore, $\ostrichrecl$ is 6.79/2.88/2.61/5.27/3.95 times faster than CVC5/Z3str3RE/ Z3str3/Z3seq/OSTRICH respectively.
+From the results, we can conclude that $\ostrichrecl$ is much more effective and efficient to solve the problem instances with large bounds than the other solvers.
+%To answer \textbf{Q1}, we can see that $\ostrichrecl$ \textbf{is far more efficient than the other solvers on problem instances with large bounds.}
+
+\begin{table}
+  \centering
+  \begin{subtable}{0.53\textwidth}
+      \centering
+    \import{tables}{table_large_count.tex}
+      \caption{Large bounds}
+      \label{tab:large-bound}
+  \end{subtable}
+  \begin{subtable}{0.45\textwidth}
+      \centering
+      \import{tables}{table_simp.tex}
+      \caption{Empirical justification of the technical choices in the decision procedure}
+      \label{tab:results_simp}
+  \end{subtable}
+  \caption{More experiment results, where the time limit is set as 60 seconds}
+\end{table}
+
+\subsection{Empirical justification of the technical choices made in the decision procedure}\label{subsec:size_reduction_eval}
+%
+%We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
+%Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
+We compare $\ostrichrecl$ with $\ostrichrecl_{\rm -ASR}$ and $\ostrichrecl_{\rm NUXMV}$, to justify the technical choices made in Section~\ref{subsec:cefadec}. 
+The experiment results can be found in Table~\ref{tab:results_simp}. 
+We can see that $\ostrichrecl$ solves 1,503 more instances and is 2.21 times faster than $\ostrichrecl_{\rm -ASR}$.
+Therefore, the automata size-reduction technique indeed plays an essential role in the performance improvement.
+%To answer \textbf{Q2}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}. 
+Moreover, $\ostrichrecl$ solves 1,798 more instances and is 3.13 times faster than $\ostrichrecl_{\rm NUXMV}$.
+Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv.
+
+%To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}.

### 2023-10-20 2023-1-19/sections/introduction.tex
crv version finished

@@
 Symbolic execution of string manipulating programs has motivated the highly active research area of \emph{string constraint solving}, resulting in the development of numerous string solvers in the last decade, e.g.,
-Z3seq~\cite{z3seq}, CVC4/5~\cite{cvc4}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
+Z3seq~\cite{z3seq}, CVC4/5~\cite{cvc4,cvc5}, Z3str/2/3/4~\cite{Z3-str,Z3-str2,Z3-str3,BerzishMurphy2021}, Z3str3RE~\cite{BD+23}, 
 Z3-Trau~\cite{Z3-trau}\cite{z3trau}, OSTRICH~\cite{CHL+19}, Slent~\cite{WC+18}, among many others.

### 2023-10-20 2023-1-19/sections/introduction.tex
crv version finished

@@
   \item Finally, we utilize a collection of benchmark suites comprising 48,843 instances in total to evaluate the performance of $\ostrichrecl$.
-The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers, especially when the counting and length bounds are large (see Table~\ref{tab:results_regcol} and Figure~\ref{fig:table_large_count}).
-For instance, on 1,873 benchmark instances where the counting bounds are greater than or equal to $50$ and the string lengths are required to be beyond $200$, $\ostrichrecl$ solves at least $278$ more instances than the other solvers, while spending only half or less time per instance on average.
+The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers, especially when the counting and length bounds are large (see Figure~\ref{fig:table_overall_eval} and Table~\ref{tab:large-bound}).
+For instance, on 1,969 benchmark instances where the counting bounds are greater than or equal to $50$ and the string lengths are required to be beyond $200$, $\ostrichrecl$ solves at least $278$ more instances than the other solvers, while spending only half or less time per instance on average.
 \end{itemize}

### 2023-10-20 2023-1-19/sections/algorithms.tex
crv version

@@
 
-\begin{definition}[Nonemptiness of CEFA w.r.t. an LIA formula
-, abbreviated as $\cefadec$]
-Suppose that $x_1, \cdots, x_n$ are string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$, and the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, moreover, $\varphi$ is an LIA formula whose free variables are from $ \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
+\begin{definition}[$\cefadec$]
+Let $x_1, \cdots, x_n$ be string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ be nonempty sets of CEFA over the alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$ where the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, moreover, let $\varphi$ be an LIA formula whose free variables are from $ \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
 Then  the CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are said to be nonempty w.r.t.
@@
 \end{definition}
+
 \begin{proposition}[\cite{atva2020}]\label{prop-cefadec}
@@
 
-At first, we show how to construct a CEFA from a regular expression where counting operators may occur. 
-Let us start with register-representable regular expressions defined in the sequel.
+At first, we show how to construct a CEFA from a regex where counting operators may occur. 
+Let us start with register-representable regexes defined in the sequel.
 
@@
 
-Let $e$ be a regular expression over $\Sigma$.
+Let $e$ be a regex over $\Sigma$.
 Then an occurrence of counting operators in $e$, say $(e')^{\{m,n\}}$ (or $(e')^{\{m, \infty\}}$), is said to be \emph{register-representable} if $(e')^{\{m,n\}}$ (or $(e')^{\{m, \infty\}}$) is not in the scope of a Kleene star, another counting operator, complement, or language difference in $e$.
@@
 
-Let $e$ be a register-representable regular expression over $\Sigma$. By the following procedure, we will construct a CEFA out of $e$, denoted by $\aut_e$. 
+Let $e$ be a register-representable regex over $\Sigma$. By the following procedure, we will construct a CEFA out of $e$, denoted by $\aut_e$. 
 \begin{enumerate}
@@
 $(e')^{\{m, \infty\}}$) of $e$, we construct a CEFA $\aut_{(e')^{\{m,n\}}}$ (resp.
-$\aut_{(e')^{\{m, \infty\}}}$) as follows.
+$\aut_{(e')^{\{m, \infty\}}}$).
 Let $\aut_{e'} = (Q, \Sigma, \delta, I, F)$.
-Same as the construction for Kleene star except for the new register and updates on transitions, $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a new register,
+%
+At first, $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a new register, $Q' = Q \cup \{q_0\}$ with $q_0 \not \in Q$, $I' = \{q_0\}$, $F'= F \cup \{q_0\}$, and 
 %
@@
 
-For non-register-representable regular expressions, we first transform them into register-representable regular expressions by unfolding all the non-register-representable occurrences of counting operators.
+For non-register-representable regexes, we first transform them into register-representable regexes by unfolding all the non-register-representable occurrences of counting operators.
 After that, we utilize the aforementioned procedure to construct CEFA.
@@
 Moreover, the unfoldings are partial in the sense that the outmost counting operators are not unfolded.
-It turns out that our approach can solve almost all the RECL constraints involving these 48,843 regexes, except 181 of them (See Table~\ref{tab:results_regcol}). 
+It turns out that our approach can solve almost all the RECL constraints involving these 48,843 regexes, except 181 of them (See Figure~\ref{fig:table_overall_eval}). 
 %$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.

### 2023-10-20 2023-1-19/sections/introduction.tex
crv version

@@
 \emph{Related work.} 
-We discuss more related work about regexes with counting, string-length function, and automata with registers/counters.  
+We discuss more related work on regexes with counting, string-length function, and automata with registers/counters.  
 %
-The determinism of regexes with counting was investigated in~\cite{GGM12,CL15}. 
+Determinism of regexes with counting was investigated in~\cite{GGM12,CL15}. 
 %

### 2023-10-20 2023-1-19/sections/algorithms.tex
crv version

@@
 %
-At first, $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a new register, $Q' = Q \cup \{q_0\}$ with $q_0 \not \in Q$, $I' = \{q_0\}$, $F'= F \cup \{q_0\}$, and 
+Then $\aut_{(e')^{\{m,n\}}} = ((r'), Q', \Sigma, \delta'', I', F', \alpha')$, where $r'$ is a new register, $Q' = Q \cup \{q_0\}$ with $q_0 \not \in Q$, $I' = \{q_0\}$, $F'= F \cup \{q_0\}$, and 
 %
@@
 moreover, $\alpha' = m \le r' \le n$ if $I \cap F = \emptyset$, otherwise $\alpha' = r' \le n$ .
-(Intuitively, if $\varepsilon$ is accepted by $\aut_{e'}$, then the value of $r'$ can be less than $m$.) Finally, $\aut_{(e')^{\{m, \infty\}}}$ is constructed by adapting $\alpha'$ in $\aut_{(e')^{\{m,n\}}}$ as follows: $\alpha' = m \le r'$ if $I \cap F = \emptyset$ and $\alpha' = \ltrue$ otherwise.
+(Intuitively, if $\varepsilon$ is accepted by $\aut_{e'}$, then the value of $r'$ can be less than $m$.) Moreover, $\aut_{(e')^{\{m, \infty\}}}$ is constructed by adapting $\alpha'$ in $\aut_{(e')^{\{m,n\}}}$ as follows: $\alpha' = m \le r'$ if $I \cap F = \emptyset$ and $\alpha' = \ltrue$ otherwise.
 %

### 2023-10-20 2023-1-19/crv/sections/cefa.tex
add crv folder

--- 2023-10-19 2023-1-19/sections/cefa.tex
@@
 %!TEX root = ../main.tex
-In this section, we define the cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
+In this section, we define cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
 %
@@
 The following section will use these three operations to solve RECL constraints.
-Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than register automata~\cite{ra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting condition is attached to each automaton, not each final state.
+Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than register automata~\cite{ra} and counter automata~\cite{GGM12}, as a result of the (additional) accepting conditions.
+%the technical choice that the accepting condition is attached to each automaton, not to each final state.
 

### 2023-10-20 2023-9-4_note/extend_split/note.tex
add the note of string array

\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage[fleqn]{amsmath}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{amsthm}
\usepackage{graphicx}

\usepackage{tikz}

\newcommand*{\aut}{\mathcal{A}}
\newcommand*{\Int}{\mathbb{Z}}
\newcommand*{\myvec}[1]{\vec{#1}}
\newcommand{\cefaout}{\mathcal{O}}
\newcommand{\Lang}{\mathcal{L}}
\newcommand{\arrconcat}{\sharp}
\newcommand{\denghang}[1]{{\color{teal}\textbf{DH:} #1 \textbf{:HD}\color{black}}}
\newcommand{\comment}[1]{{\color{blue}\textbf{MARK:} #1 \textbf{:KRAM}\color{black}}}
\newcommand{\todo}[1]{{\color{orange}\textbf{TODO:} #1 \textbf{:ODOT}\color{black}}}
\newcommand{\mysplit}{\mathsf{split}}
\newcommand{\myjoin}{\mathsf{join}}
\newcommand{\mylen}{\mathsf{len}}
\newcommand{\myread}{\mathsf{read}}
\newcommand{\mywrite}{\mathsf{write}}
\newcommand{\myset}[1]{\{#1\}}

\theoremstyle{remark}
\newtheorem{definition}{Defination}[section]

\title{A Note for Solving String Constraints with Split Function}
\author{Denghang Hu}
\begin{document}
\maketitle

\section{Preliminary}
\subsection{Cost-enriched Finite State Automata (CEFA)}
In this section, we define the cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
%
Intuitively, CEFA adds write-only cost registers to finite state automata. ``write-only'' means that the cost registers can only be written/updated but cannot be read, i.e., they cannot be used to guard the transitions.

%
%In~\cite{atva2020}, the cost function is defined as a function $\eta: \Sigma \rightarrow \mathbb{N}$. In this paper, we define the cost function as an integer vector whose elements are the incremental value of registers. Furthermore, we add a new linear integer arithmetic constraint $\theta$ to each final state of the CEFA, which restricts the value of registers. Two types of definitions have the same expressive ability on the $SAT_{CL}$ problem.
\vspace{-0.5mm}
\begin{definition}[Cost-Enriched Finite Automaton]
    A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F, \alpha)$ where
    \begin{itemize}
        \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers,
        \item $Q, \Sigma, I, F$ are as in the definition of NFA,
              %    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
        \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers.
              %  set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.  $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
        \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
              %    a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
    \end{itemize}
\end{definition}
\vspace{-0.5mm}

For convenience, we use $R_\aut$ to denote the set of registers of $\aut$. We assume a linear order on $R$ and write $R$ as a vector $(r_1, \cdots, r_k)$. Accordingly, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where $v_i$ is the update of $r_i$ for each $i \in [k]$. We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$. The transition $(q,a,q',())$ with empty updates is abbreviated as $(q,a,q')$.
%The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
%are attached to final states.

The semantics of CEFA is defined as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
%A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
%An \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$ with $q_0 \in I$, where the value of each register is zero. 
A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$. A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$. The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$. Note that the values of all registers are initiated to zero and updated to $\sum \limits_{j \in [n]} \myvec{v_j}$ after all the transitions in the run are executed. We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.  
We define the semantics of a CEFA $\aut$, denoted by $\Lang(\aut)$, as $\{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.  In particular, if $I \cap F \neq \emptyset$ and $\alpha(\myvec{0}/R)$ is true, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$. Moreover, we define the \emph{output} of a CEFA $\aut$, denoted by $\cefaout(\aut)$, as $\{\myvec{v'} \mid  \exists w.\ \myvec{v'} \in \aut(w)\}$.

\subsection{Special CEFA for String Array}
%%
We define a special CEFA for string array. The CEFA uses a preserved character $``\arrconcat"$ as $array$ elements separator (note that $\arrconcat\not\in\Sigma$). The speciality of $\aut_s$ rely on  its construction.
%%
\paragraph{Array of fixed length and constant index} Considering an $array$ $A$ with fixed length $m$, we assume that each array element $A[i]$ $(i\in[1,m])$ is constrained by a CEFA $\aut_i\equiv (R_i, Q_i, \Sigma, \delta_i, I_i, F_i, \alpha_i)$. Note that the index of the array starts from 1.  Then we can construct the CEFA of the array $A$ as $\aut_s\equiv (R_s, Q_s, \Sigma\cup\{\arrconcat\}, \delta_s, I_s, F_s, \alpha_s)$, where:
\begin{itemize}
    % \item $R_s = \bigcup\limits_{1\leq i \leq m} R_i$,
    \item $R_s = \bigcup\limits_{1\leq i \leq m} R_i\cup \myset{r}$ for a fresh register r,
    \item $Q_s = \bigcup\limits_{1\leq i \leq m} Q_i\cup \myset{q_0, q_f}$ for fresh states $q_0$ and $q_f$,
    \item $\delta_s$ is composed of four transitions set
          \begin{itemize}
              \item  $\{(q_0, \arrconcat, q_1, (\myvec{0}, 1))\mid q_1\in I_1\}$,
              \item  $\myset{(q_m, \sharp, q_f, (\myvec{0}, 0))\mid q_m\in F_m}$,
              \item  $\{(q, \arrconcat, q', (\myvec{0}, 1)) \mid q\in F_i, q'\in I_{i+1}, i\in[1,m]\}$ where $ I_{m+1}=\emptyset$,
              \item  and $\{(q, a, q', (\myvec{0},\myvec{v_i},\myvec{0}))\mid (q, a, q', \myvec{v_i})\in \aut_i, i\in[1,m]\}$,
          \end{itemize}
          where $(\myvec{0}, 1)$ is a vector that increases the value of $r$ by 1 and remains other registers unchanged, and $(\myvec{0},\myvec{v_i},\myvec{0})$ is a vector that updates the value of $R_i$ by $\myvec{v_i}$ and remains other registers unchanged. Similarly for $(\myvec{0}, 0)$ and so on.
    \item $I_s = \myset{q_0}$, $F_s = \myset{q_f},$ and $\alpha_s = \bigwedge\limits_{1\leq i \leq m} \alpha_i$.
          % and $\alpha_s = \bigwedge\limits_{1\leq i \leq m} \alpha_i$.
\end{itemize}
The resulting CEFA is shown in fig \ref{fig:fixed_len_cons_idx}, where $q_i\in I_i$ and $q_i'\in F_i$ for each $i\in [1,m]$. The main idea of the construction above is using $\arrconcat$ to separate each element of the array and one register to record the index of each element. We introduce two fresh states $q_0$ and $q_f$ to ensure each element is started and ended with at least one $\arrconcat $, which is beneficial to the construction of pre-images of string constraints (see \ref*{sec:pre_image} for more details). The accepting condition $\alpha_s$ is the conjunction of accepting conditions of each element.
% It is obviously that the accepting word $w$ of $\aut_s$ is in language $\mathcal{L}(\aut_1)\arrconcat\mathcal{L}(\aut_2)\ ... \ \arrconcat \mathcal{L}(\aut_{m}) $.
\begin{figure}[H]
    \centering
    \usetikzlibrary {automata, positioning, fit}
    \begin{tikzpicture}[initial text =, initial distance=3ex,
            node distance=1.2cm, auto,
            state/.style={circle, draw, inner sep=0pt, minimum size=5mm},
            accepting by double]

        \node[state,initial]            (q_0)                {$q_0$};
        \node[state]                    (q_1) [right=of q_0] {$q_1$};
        \node[state]                    (q_1') [right=of q_1] {$q_1'$};
        \node                           (omit)[right=of q_1'] {$\cdots$};
        \node[state]                    (q_m) [right=of omit] {$q_m$};
        \node[state]                    (q_m') [right=of q_m] {$q_m'$};
        \node[state, accepting]         (q_f)  [right=of q_m'] {$q_f$};

        \node[draw, fit=(q_1) (q_1'), inner sep=0.5em, label=above:$\aut_1$] [dashed] {};
        \node[draw, fit=(q_m) (q_m'), inner sep=0.5em, label=above:$\aut_m$] [dashed] {};

        \path[->]
        (q_0) edge [above] node {$\scriptstyle \arrconcat$} (q_1)
        (q_0) edge [below] node {${\scriptstyle r++}$} (q_1)
        (q_1') edge [above] node {$\scriptstyle \arrconcat$} (omit)
        (q_1') edge [below] node {${\scriptstyle r++}$} (omit)
        (omit) edge [above] node {$\scriptstyle \arrconcat$} (q_m)
        (omit) edge [below] node {${\scriptstyle r++}$} (q_m)
        (q_m') edge [above] node {$\scriptstyle \arrconcat$} (q_f)
        (q_m') edge [below] node {${\scriptstyle r}$} (q_f);

    \end{tikzpicture}
    \caption{The CEFA of $A$ with accepting condition $\alpha_s = \bigwedge\limits_{1\leq i \leq m} \alpha_i$}
    \label{fig:fixed_len_cons_idx}
\end{figure}
The construction of $\aut_s$ can be used to formalize the array containing constant string. For example, for a 2-length array $A$ constrained by $``a" = \myread(A, 1)\wedge ``b" = \myread(A, 2) \wedge \mylen(A) = 2$ , where $\myread(A, m)$ read the  element of $A$ at constant index $m$ and $\mylen(A)$ is the length of $A$, we can construct the automaton of $A$ as following: \\
$(\emptyset, \{q_0,q_1,q_1',q_2,q_2'\}, \{a,b,\arrconcat\}, \{q_0\xrightarrow[(1)]{\arrconcat}q_1, q_1\xrightarrow[(0)]{a}q_1', q_1'\xrightarrow[(1)]{\arrconcat}q_2, q_2\xrightarrow[(0)]{b}q_2'\}, \{q_0\}, \{q_2'\}, \top)$. 
%%
\paragraph{Array of varible length and index} \todo{TODO}

\section{Straight-Line String Theory with Integer and Array $SL_{I,A,S} $}\label{sec:SL}
We defined a theory $SL_{I,A,S}$ with three sorts: \textbf{string}, \textbf{integer} and \textbf{array}. The \textit{elements} of \textbf{array} can only be \textbf{string} sort, and the $index$ of \textbf{array} is \textbf{Integer} sort.
\subsection{Syntax}
The syntax of $SL_{I,A,S}$ is defined in table \ref{tab:syntax} where: $e$ is a regular expression; $\mylen(A)$ is the length of array $A$, $\mylen(x)$ is the length of string $x$; $\myread(A, m)$ read the  element of $A$ at index $m$, $\mywrite(B, x ,m)$ write string $x$ to array $B$ at index $m$;  $\myjoin(A,u)$ connect all of elements in array $A$ by connector $u$; $\mysplit(s,e)$ split string $x$ into ordered string array by separator $e$; $y\cdot z$ connects string $y$ and $z$; $\circ \in \{=,\not=, <, \leq, >, \geq \}$ is the set of arithmatic binary predicates.
%  For technical convenience, we assume that all assignments in F are \textit{Static Singly Assignment (SSA)} form.
\begin{table}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{l l l r}
        $x,y$ & $\cdots$ &                                                                       & String varibles          \\
        $m,n$ & $\cdots$ &                                                                       & Integer constants        \\
        $i,j$ & $\cdots$ &                                                                       & Integer varibles         \\
        $A,B$ & $\cdots$ &                                                                       & Array varibles           \\
        $t$   & $::=$    & $m \mid i \mid t+t \mid t-t \mid \mylen(A)\mid \mylen(x) $            & Integer term             \\
        $SC$  & $::=$    & $x=\myread(A, m) \mid A = \mywrite(B, x ,m) \mid x=\myjoin(A,u) \mid$ &                          \\
              &          & $A = \mysplit(x, e) \mid x= y\cdot z\mid x\in e$                      & String constraints       \\
        $F$   & $::=$    & $t\circ t \mid SC \mid F\wedge F $                                    & Formula of $SL_{I,A,S} $

    \end{tabular}
    \caption{Syntax of $SL_{I,A,S}$}
    \label{tab:syntax}
\end{table}
\subsection{Defination of Straight-Line Restriction }
We consider two sorts: \textbf{string} and \textbf{array}.
\begin{definition}[Relational constraints ]
    Relational constraints $\phi$ are defined by the following rules:
    \begin{align*}
        \phi \ ::= \  & x=y\cdot z \mid x=\myjoin(A,u) \mid A = \mysplit(x,e) \mid        \\
                      & x=\myread(A, m) \mid A = \mywrite(B, x ,m) \mid \phi \wedge \phi 
    \end{align*}
\end{definition}
\begin{definition}[Straight-line relational constraints]
    A relational constraint $\phi$ is straight-line if $\phi = \bigwedge\limits_{1\leq i \leq m} \chi_i = P_i$ such that
    \begin{itemize}
        \item $\chi_1,\cdots,\chi_m $ are mutally distinct string varibles and array varibles.
        \item For each $i\in [m] $, all the varibles in $P_i$ are in the set $\{\chi_1,\cdots,\chi_{m-1} \}$.
    \end{itemize}
\end{definition}
\begin{definition}[Straight-line formula]
    A formula $F$ of $SL_{I,A,S}$ is straight-line iff all relational constraints in $F$ are straight-line.
\end{definition}
% \begin{figure}[H]
%     % denote
%     % $u,v,\cdots$  \hfill{String constants}\\
%     $x,y,\cdots$  \hfill{String varibles}\\
%     $m,n,\cdots$  \hfill{Integer constants}\\
%     $i,j,\cdots$  \hfill{Integer varibles}\\
%     % $M,N,\cdots$  \hfill{Array constants}\\
%     $A,B,\cdots$  \hfill{Array varibles}\\

%     % term and expression
%     % $s \ ::= \ u \mid x$ \hfill{String term}\\
%     $t \ ::= \  m \mid i \mid t+t \mid t-t \mid |A|\mid |x| $ \hfill{Integer term}\\
%     % $A \ ::= \  M \mid X  $ \hfill{Array term}\\
%     % $\beta \ ::= \  m \mid |A| \mid |A|+m  $  \hfill{Bound expression}\\

%     % formula
%     % $LA \ ::= \ t\circ t \mid LA\wedge LA \mid \neg LA $  \hfill{Linear arithmatic}\\
%     $SC \ ::= \ x=read(A, m) \mid A = write(A, x ,m) \mid x=\myjoin(A,u)\mid A = \mysplit(x, e) \mid x\in e$   \flushright{String constraints}\\
%     % $AC \ ::= \ A = \mysplit(s,e) \mid A = A[\beta_1:\beta_2] \mid A = A[t\rightarrow s] \mid A\in \aut_s \mid A = \mathcal{T}(A) $ \flushright{Array constraints}\\ 
%     $F \ ::= \ t\circ t \mid SC \mid F\wedge F $ \hfill{Formula of $SL_{I,A,S} $}
%     \caption{Syntax of $SL_{I,A,S}$}
%     \label{fig:syntax}
% \end{figure}

% \section{Pre-image of String Constraints}
% \subsection{Array Assignment}
% Assume $A\in \aut_s$ and $\aut_s=(Q, \Sigma, \delta,q_0,F,R)$ construct like fig \ref{fig:special_nfa}.
% \begin{itemize}
%     \item $A = \mysplit(s,e)$: assume $e\in \mathcal{A}_e$, then we can construct $\mathcal{B}=(Q', \Sigma', \delta',q_0,F,R)$ like fig \ref{fig:pre_image_split} s.t $s\in B$.
%     \item $B = A[\beta_1:\beta_2]$:
% \end{itemize}

% % \begin{itemize}
% %     \item $e$ : A regular expression.
% %     \item $A[m]$ : Return the $element$ of $A$ at index $m$.
% %     % \item $A[t\rightarrow s]$ : Return a new array the same as $A$ except  that the $element$ of $A$ at index $t$ changes to string $s$.
% %     % \item $s\cdot s$ : String concatenation.
% %     \item $\myjoin(A,u) $ : Return a new string by concatenating all of $elements$ in array $A$, separated by a specified separator string $u$.
% %     \item $\mysplit(s,e) $ : Return a new array by dividing string $s$ into ordered substring array. The separator string is regular expression $e$.
% %     % \item $\mathcal{T}(A) $: Return a new array by applying transducer $\mathcal{T}$ on each $element$ of array $A$.
% %     % \item $A[\beta_1:\beta_2] $ Return a new array which is the subarray of $A$.
% % \end{itemize}
% % \subsection{Defination of Straight-Line Restriction }
% We consider two sorts: \textbf{string} and \textbf{array}.
% \begin{definition}[Relational constraints ]
%     Relational constraints $\phi$ are defined by the following rules:
%     \begin{align*}
%         \phi \ ::= \ x=s\cdot s \mid x=\myjoin(A,u) \mid A = \mysplit(s,e) \mid A = A[\beta_1:\beta_2] \mid A = A[t\rightarrow s] \mid \phi \wedge \phi
%     \end{align*}
% \end{definition}
% \begin{definition}[Straight-line relational constraints]
%     A relational constraint $\phi$ is straight-line if $\phi = \bigwedge\limits_{1\leq i \leq m} x_i = P_i$ such that
%     \begin{itemize}
%         \item $x_1,\cdots,x_m $ are mutally distinct.
%         \item For each $i\in [m] $, all the varibles in $P_i$ are either source varibles or varibles in set $\{x_1,\cdots,x_{m-1} \}$.
%     \end{itemize}
% \end{definition}
% \begin{definition}[Straight-line formula]
%     A formula $F$ of $SL_{I,A,S}$ is straight-line iff all relational constraints in $F$ are straight-line.
% \end{definition}

% \begin{figure}
%     \includegraphics[width=\linewidth]{pre_image_split.png}
%     \caption{pre-image of split operation}
%     \label{fig:pre_image_split}
% \end{figure}
% \bibliographystyle{abbrv} % 指定格式，
% % \bibliographystyle{apa} % 这是姓名年份应用格式
% \bibliography{ref} %  ../.bib表示bib的具体位置

\section{Pre-images of String Constraints}\label{sec:pre_image}
In this section, we define the pre-image of each string constraint formula.
\paragraph{- $i = \mylen(A)$:} The pre-image for this formula is a CEFA $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrconcat\}, \delta_A, I_A, F_A, \alpha_A)$, where
\begin{itemize}
    \item $R_A = \{r\}$ for a fresh register $r$, $Q_A = \{q_0, q_f\}$, $\delta_A = \myset{q_0\xrightarrow[(0)]{\Sigma}q_0, q_0\xrightarrow[(1)]{\sharp}q_0, q_0\xrightarrow[(0)]{\arrconcat}q_f }$, $I_A = \myset{q_0}$, $F_A = \myset{q_f}$, and $\alpha_A \equiv r = i$.
\end{itemize}

\paragraph{- $i = \mylen(x)$:} As the pre-image of length function in \cite{atva2020}.

\paragraph{- $x = \myread(A, m)$:} Suppose that $x$ is constrained by $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$, then the pre-image for $A$ is a CEFA $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrconcat\}, \delta_A, I_A, F_A, \alpha_A)$, where
\begin{itemize}
    \item $R_A = R_x$,
    \item $Q_A = Q_x\cup\myset{q_0, q_1, \cdots, q_{m}}$,
    \item $\delta_A$ is the union of six transitions set:
          \begin{itemize}
              \item $\myset{q_i\xrightarrow[(\myvec{0})]{\Sigma}q_i\mid i\in [1,m-1]}$,
              \item $\myset{q_i\xrightarrow[(\myvec{0})]{\arrconcat}q_{i+1}\mid i\in[0,m-2]}$,
              \item $\myset{q_{m-1}\xrightarrow[(\myvec{0})]{\arrconcat}q_0^x \mid q_0^x\in I_x}$,
              \item $\myset{q_f^x\xrightarrow[(\myvec{0})]{\arrconcat}q_m \mid q_f^x\in F_x}$,
              \item $\myset{q_m\xrightarrow[(\myvec{0})]{\arrconcat}q_m}$,
              \item $\myset{q\xrightarrow[(\myvec{v})]{a}q'\mid q\xrightarrow[\myvec{v}]{a}q'\in \delta_x}$.
          \end{itemize}
    \item $I_A = \myset{q_0}$, $F_A = \myset{q_m}$, and $\alpha_A = \alpha_x$.
\end{itemize}

\paragraph{- $A = \mywrite(B, x, m)$:} Suppose that $A$ is constrained by $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrconcat\}, \delta_A, I_A, F_A, \alpha_A)$, we firstly consider $A$ as a \emph{string varible} in the formula $A = x_1\arrconcat x_2\arrconcat x_3$. The pre-image of the formula is a set of tuple $(\aut_1, \aut_2, \aut_3)$ in which $x_1\in \aut_1, x_2\in \aut_2, x_3\in \aut_3$. There is at least one tuple with both $\aut_1$ and $\aut_3$ to be non-empty, as we ensure that each element of array is started and ended with at least one $\arrconcat$. Then the pre-image of $A = \mywrite(B, x, m)$ is a set of tuple $(\aut_B, \aut_x)$ where
\begin{itemize}
    \item $\aut_B = \aut_1'\arrconcat\Sigma^*\arrconcat\aut_3$, $\aut_1'$ add a new register $r$ to $\aut_1$ to record the occurence times of $\arrconcat$ in $\aut_1$ and add the constraint $r = m$ for the occurence times,
    \item $\aut_x = \aut_2$.
\end{itemize}

\paragraph{- $x = \myjoin(A,u)$:} Suppose that $x$ is constrained by $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$, then the pre-image is a CEFA

\end{document}

### 2023-10-20 2023-1-19/crv/sections/conclusion.tex

--- 2023-08-30 2023-1-19/sections/conclusion.tex
@@
 %!TEX root = ../main.tex
-%\documentclass{standalone}
-%\begin{document}
 
-This work proposes an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length.
+This work proposed an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length.
 The approach is based on encoding counting operators in regular expressions by cost registers symbolically instead of unfolding them explicitly.
-Moreover, this paper proposes automata-size reduction techniques to improve performance further.
-Finally, we use two benchmark suites comprising 48,843 instances to evaluate the performance of our approach.
+Moreover, this work proposed automata-size reduction techniques to improve performance further.
+Finally, we used two benchmark suites comprising 48,843 instances in total to evaluate the performance of our approach.
 The experimental results show that our approach can solve more instances than the state-of-the-art best solvers, at a comparable or faster speed, especially when the counting and length bounds are large.
 For the future work, we plan to investigate how the symbolic approach can be extended to reason about nested counting operators.
-
-%This paper aims to efficiently solve the string constraints with bounded repetition and linear integer constraints on string length.
-The bounded repetition is encoded by an automaton model CEFA whose size is linear to the bound.
-Moreover, we extend the algorithm in the paper \cite{atva2020} with heuristics such as under-approximation and symbolic-aware simplification.
-The implementation of the algorithm is done on string solver OstrichCEA.
-The extensive empirical comparison against state-of-art string solvers over a large and diverse benchmark shows the power of our encoding for bounded repetition and heuristic ways.
-In the future, we plan to explore how to solve nested repetition and use CEFA to solve more string operations.
-
-%\end{document}

### 2023-10-20 2023-1-19/crv/sections/overview.tex

--- 2023-10-19 2023-1-19/sections/overview.tex
@@
 
-First, we construct an CEFA for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
+At first, we construct a CEFA for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$.
 Three registers are introduced, say $r_1, r_2, r_3$, to represent the three counting operators;
@@
   \label{fig:overview}
-\vspace{-5mm}
+\vspace{-3mm}
 \end{figure}
@@
 \begin{figure}[ht]
-\vspace{-3mm}
+\vspace{-4mm}
   \centering
@@
   \label{fig:overview:product}
-\vspace{-3mm}
+\vspace{-4mm}
 \end{figure}
@@
 \begin{figure}[ht]
-\vspace{-3mm}
+\vspace{-2mm}
   \centering
@@
   \label{fig:overview:product:reduced}
-\vspace{-3mm}
+\vspace{-4mm}
 \end{figure}

### 2023-10-23 2023-9-4_note/extend_split/note.tex
daily update the note of string array

@@
 \newcommand{\myset}[1]{\{#1\}}
+\newcommand{\hide}[1]{ }
+\newcommand{\arraylogic}{SL_{I,A,S}}
 
 \theoremstyle{remark}
-\newtheorem{definition}{Defination}[section]
+\newtheorem{definition}{Definition}[section]
 
@@
 
+%% write by denghang ==================================================================
+%% write by denghang ==================================================================
+\hide{
     \subsection{Special CEFA for String Array}
@@
     \paragraph{Array of varible length and index} \todo{TODO}
+}%% write by denghang ==================================================================
+%% write by denghang ==================================================================
 
-\section{Straight-Line String Theory with Integer and Array $SL_{I,A,S} $}\label{sec:SL}
-We defined a theory $SL_{I,A,S}$ with three sorts: \textbf{string}, \textbf{integer} and \textbf{array}.
-The \textit{elements} of \textbf{array} can only be \textbf{string} sort, and the $index$ of \textbf{array} is \textbf{Integer} sort.
-\subsection{Syntax}
-The syntax of $SL_{I,A,S}$ is defined in table \ref{tab:syntax} where: $e$ is a regular expression; $\mylen(A)$ is the length of array $A$, $\mylen(x)$ is the length of string $x$; $\myread(A, m)$ read the  element of $A$ at index $m$, $\mywrite(B, x ,m)$ write string $x$ to array $B$ at index $m$;  $\myjoin(A,u)$ connect all of elements in array $A$ by connector $u$; $\mysplit(s,e)$ split string $x$ into ordered string array by separator $e$; $y\cdot z$ connects string $y$ and $z$; $\circ \in \{=,\not=, <, \leq, >, \geq \}$ is the set of arithmatic binary predicates.
+\section{String Theory with Integer and Array $\arraylogic $}\label{sec:SL}
+We defined a theory $\arraylogic$ with three sorts: \textbf{string}, \textbf{integer} and \textbf{array}.
+The \textit{elements} of \textbf{array} are in \textbf{string} sort, and the $index$ of \textbf{array} is in \textbf{Integer} sort.
+The syntax of $\arraylogic$ is defined in table \ref{tab:syntax}.
+A $\arraylogic$ formula $\varphi$ is a conjunction of the integer atomic formulas $t_1\circ t_2$, or the string atomic formulas $x = \myread(A,m)$, $A = \mywrite(B, x, m)$, $x=\myjoin(A,u)$, $A=\mysplit(x,e)$, $x=y\cdot z$ and $x\in e$.
+Moreover, $t$ is a integer term built from the constant $m$, the varible $i$, the size of array $\mylen(A)$ and the length of string $\mylen(x)$ by operators $+$ and $-$; $\circ \in \{=,\not=, <, \leq, >, \geq \}$ is the set of arithmatic binary predicates on integer terms $t_1$ and $t_2$; $e$ is a regular expression; $\myread(A, m)$ returns the $m$-th element of $A$; $\mywrite(B, x ,m)$ returns the array $B$ after $x$ is written to $m$-th position of $B$; $\myjoin(A,u)$ joins all of the elements in $A$ by string $u$; $\mysplit(x,e)$ splits $x$ into an ordered string array by regex $e$; $y\cdot z$ is the concatenation of $y$ and $z$.
 %  For technical convenience, we assume that all assignments in F are \textit{Static Singly Assignment (SSA)} form.
@@
               &          & $A = \mysplit(x, e) \mid x= y\cdot z\mid x\in e$                      & String constraints       \\
-        $F$   & $::=$    & $t\circ t \mid SC \mid F\wedge F $                                    & Formula of $SL_{I,A,S} $
+        $\varphi$   & $::=$    & $t\circ t \mid SC \mid \varphi\wedge \varphi $                                    & Formula of $\arraylogic $
 
     \end{tabular}
-    \caption{Syntax of $SL_{I,A,S}$}
+    \caption{Syntax of $\arraylogic$}
     \label{tab:syntax}
 \end{table}
-\subsection{Defination of Straight-Line Restriction }
-We consider two sorts: \textbf{string} and \textbf{array}.
+\subsection{Definition of Straight-Line Formula }
 \begin{definition}[Relational constraints ]
@@
 \begin{definition}[Straight-line formula]
-    A formula $F$ of $SL_{I,A,S}$ is straight-line iff all relational constraints in $F$ are straight-line.
+    A formula $F$ of $\arraylogic$ is straight-line iff all relational constraints in $F$ are straight-line.
 \end{definition}
-% \begin{figure}[H]
-%     % denote
-%     % $u,v,\cdots$  \hfill{String constants}\\
-%     $x,y,\cdots$  \hfill{String varibles}\\
-%     $m,n,\cdots$  \hfill{Integer constants}\\
-%     $i,j,\cdots$  \hfill{Integer varibles}\\
-%     % $M,N,\cdots$  \hfill{Array constants}\\
-%     $A,B,\cdots$  \hfill{Array varibles}\\
-
-%     % term and expression
-%     % $s \ ::= \ u \mid x$ \hfill{String term}\\
-%     $t \ ::= \  m \mid i \mid t+t \mid t-t \mid |A|\mid |x| $ \hfill{Integer term}\\
-%     % $A \ ::= \  M \mid X  $ \hfill{Array term}\\
-%     % $\beta \ ::= \  m \mid |A| \mid |A|+m  $  \hfill{Bound expression}\\
-
-%     % formula
-%     % $LA \ ::= \ t\circ t \mid LA\wedge LA \mid \neg LA $  \hfill{Linear arithmatic}\\
-%     $SC \ ::= \ x=read(A, m) \mid A = write(A, x ,m) \mid x=\myjoin(A,u)\mid A = \mysplit(x, e) \mid x\in e$   \flushright{String constraints}\\
-%     % $AC \ ::= \ A = \mysplit(s,e) \mid A = A[\beta_1:\beta_2] \mid A = A[t\rightarrow s] \mid A\in \aut_s \mid A = \mathcal{T}(A) $ \flushright{Array constraints}\\ 
-%     $F \ ::= \ t\circ t \mid SC \mid F\wedge F $ \hfill{Formula of $SL_{I,A,S} $}
-%     \caption{Syntax of $SL_{I,A,S}$}
-%     \label{fig:syntax}
-% \end{figure}
-
-% \section{Pre-image of String Constraints}
-% \subsection{Array Assignment}
-% Assume $A\in \aut_s$ and $\aut_s=(Q, \Sigma, \delta,q_0,F,R)$ construct like fig \ref{fig:special_nfa}.
-% \begin{itemize}
-%     \item $A = \mysplit(s,e)$: assume $e\in \mathcal{A}_e$, then we can construct $\mathcal{B}=(Q', \Sigma', \delta',q_0,F,R)$ like fig \ref{fig:pre_image_split} s.t $s\in B$.
-%     \item $B = A[\beta_1:\beta_2]$:
-% \end{itemize}
-
-% % \begin{itemize}
-% %     \item $e$ : A regular expression.
-% %     \item $A[m]$ : Return the $element$ of $A$ at index $m$.
-% %     % \item $A[t\rightarrow s]$ : Return a new array the same as $A$ except  that the $element$ of $A$ at index $t$ changes to string $s$.
-% %     % \item $s\cdot s$ : String concatenation.
-% %     \item $\myjoin(A,u) $ : Return a new string by concatenating all of $elements$ in array $A$, separated by a specified separator string $u$.
-% %     \item $\mysplit(s,e) $ : Return a new array by dividing string $s$ into ordered substring array. The separator string is regular expression $e$.
-% %     % \item $\mathcal{T}(A) $: Return a new array by applying transducer $\mathcal{T}$ on each $element$ of array $A$.
-% %     % \item $A[\beta_1:\beta_2] $ Return a new array which is the subarray of $A$.
-% % \end{itemize}
-% % \subsection{Defination of Straight-Line Restriction }
-% We consider two sorts: \textbf{string} and \textbf{array}.
-% \begin{definition}[Relational constraints ]
-%     Relational constraints $\phi$ are defined by the following rules:
-%     \begin{align*}
-%         \phi \ ::= \ x=s\cdot s \mid x=\myjoin(A,u) \mid A = \mysplit(s,e) \mid A = A[\beta_1:\beta_2] \mid A = A[t\rightarrow s] \mid \phi \wedge \phi
-%     \end{align*}
-% \end{definition}
-% \begin{definition}[Straight-line relational constraints]
-%     A relational constraint $\phi$ is straight-line if $\phi = \bigwedge\limits_{1\leq i \leq m} x_i = P_i$ such that
-%     \begin{itemize}
-%         \item $x_1,\cdots,x_m $ are mutally distinct.
-%         \item For each $i\in [m] $, all the varibles in $P_i$ are either source varibles or varibles in set $\{x_1,\cdots,x_{m-1} \}$.
-%     \end{itemize}
-% \end{definition}
-% \begin{definition}[Straight-line formula]
-%     A formula $F$ of $SL_{I,A,S}$ is straight-line iff all relational constraints in $F$ are straight-line.
-% \end{definition}
-
-% \begin{figure}
-%     \includegraphics[width=\linewidth]{pre_image_split.png}
-%     \caption{pre-image of split operation}
-%     \label{fig:pre_image_split}
-% \end{figure}
-% \bibliographystyle{abbrv} % 指定格式，
-% % \bibliographystyle{apa} % 这是姓名年份应用格式
-% \bibliography{ref} %  ../.bib表示bib的具体位置
 
 \section{Pre-images of String Constraints}\label{sec:pre_image}
-In this section, we define the pre-image of each string constraint formula.
-\paragraph{- $i = \mylen(A)$:} The pre-image for this formula is a CEFA $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrconcat\}, \delta_A, I_A, F_A, \alpha_A)$, where
+In this section, we define the pre-images of string constraint formulae.
+\paragraph{- $i = \mylen(A)$:} The pre-image for the array length function is a CEFA $\aut_{arrlen}=(R, Q, \Sigma\cup\{\arrconcat\}, \delta, I, F, \alpha)$, where
 \begin{itemize}
-    \item $R_A = \{r\}$ for a fresh register $r$, $Q_A = \{q_0, q_f\}$, $\delta_A = \myset{q_0\xrightarrow[(0)]{\Sigma}q_0, q_0\xrightarrow[(1)]{\sharp}q_0, q_0\xrightarrow[(0)]{\arrconcat}q_f }$, $I_A = \myset{q_0}$, $F_A = \myset{q_f}$, and $\alpha_A \equiv r = i$.
+    \item $R = \{r\}$ for a fresh register $r$, $Q = \{q_0, q_f\}$, $\delta = \myset{q_0\xrightarrow[(0)]{\Sigma}q_0, q_0\xrightarrow[(1)]{\sharp}q_0, q_0\xrightarrow[(0)]{\arrconcat}q_f }$, $I = \myset{q_0}$, $F = \myset{q_f}$, and $\alpha \equiv r = i$.
 \end{itemize}
@@
 
-\paragraph{- $x = \myread(A, m)$:} Suppose that $x$ is constrained by $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$, then the pre-image for $A$ is a CEFA $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrconcat\}, \delta_A, I_A, F_A, \alpha_A)$, where
+\todo{Rewrite the pre-images of array read and write function.}
+\paragraph{- $x = \myread(A, m)$:} Suppose that $x$ is constrained by the CEFA $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$, then the pre-image for the array read function is a CEFA $\aut_{read}=(R, Q, \Sigma\cup\{\arrconcat\}, \delta, I, F, \alpha)$, where
 \begin{itemize}
-    \item $R_A = R_x$,
-    \item $Q_A = Q_x\cup\myset{q_0, q_1, \cdots, q_{m}}$,
-    \item $\delta_A$ is the union of six transitions set:
+    \item $R = R_x$,
+    \item $Q = Q_x\cup\myset{q_0, q_1, \cdots, q_{m}}$,
+    \item $\delta$ is the union of six transitions set:
           \begin{itemize}
@@
           \end{itemize}
-    \item $I_A = \myset{q_0}$, $F_A = \myset{q_m}$, and $\alpha_A = \alpha_x$.
+    \item $I = \myset{q_0}$, $F = \myset{q_m}$, and $\alpha = \alpha_x$.
 \end{itemize}
@@
 
+\bibliographystyle{abbrv}
+\bibliography{ref}
+
 \end{document}

### 2023-10-27 2023-9-4_note/extend_split/note.tex
string array note update

@@
 \newcommand*{\aut}{\mathcal{A}}
+\newcommand*{\transducer}{\mathcal{T}}
 \newcommand*{\Int}{\mathbb{Z}}
@@
 \newcommand{\Lang}{\mathcal{L}}
-\newcommand{\arrconcat}{\sharp}
+\newcommand{\arrseparator}{\sharp}
 \newcommand{\denghang}[1]{{\color{teal}\textbf{DH:} #1 \textbf{:HD}\color{black}}}
@@
 
-\title{A Note for Solving String Constraints with Split Function}
+\title{A Note for Solving String Constraints with Array Type}
 \author{Denghang Hu}
@@
     We define a special CEFA for string array.
-The CEFA uses a preserved character $``\arrconcat"$ as $array$ elements separator (note that $\arrconcat\not\in\Sigma$).
+The CEFA uses a preserved character $``\arrseparator"$ as $array$ elements separator (note that $\arrseparator\not\in\Sigma$).
 The speciality of $\aut_s$ rely on  its construction.
@@
 Note that the index of the array starts from 1.
-Then we can construct the CEFA of the array $A$ as $\aut_s\equiv (R_s, Q_s, \Sigma\cup\{\arrconcat\}, \delta_s, I_s, F_s, \alpha_s)$, where:
+Then we can construct the CEFA of the array $A$ as $\aut_s\equiv (R_s, Q_s, \Sigma\cup\{\arrseparator\}, \delta_s, I_s, F_s, \alpha_s)$, where:
     \begin{itemize}
@@
               \begin{itemize}
-                  \item  $\{(q_0, \arrconcat, q_1, (\myvec{0}, 1))\mid q_1\in I_1\}$,
+                  \item  $\{(q_0, \arrseparator, q_1, (\myvec{0}, 1))\mid q_1\in I_1\}$,
                   \item  $\myset{(q_m, \sharp, q_f, (\myvec{0}, 0))\mid q_m\in F_m}$,
-                  \item  $\{(q, \arrconcat, q', (\myvec{0}, 1)) \mid q\in F_i, q'\in I_{i+1}, i\in[1,m]\}$ where $ I_{m+1}=\emptyset$,
+                  \item  $\{(q, \arrseparator, q', (\myvec{0}, 1)) \mid q\in F_i, q'\in I_{i+1}, i\in[1,m]\}$ where $ I_{m+1}=\emptyset$,
                   \item  and $\{(q, a, q', (\myvec{0},\myvec{v_i},\myvec{0}))\mid (q, a, q', \myvec{v_i})\in \aut_i, i\in[1,m]\}$,
@@
     The resulting CEFA is shown in fig \ref{fig:fixed_len_cons_idx}, where $q_i\in I_i$ and $q_i'\in F_i$ for each $i\in [1,m]$.
-The main idea of the construction above is using $\arrconcat$ to separate each element of the array and one register to record the index of each element.
-We introduce two fresh states $q_0$ and $q_f$ to ensure each element is started and ended with at least one $\arrconcat $, which is beneficial to the construction of pre-images of string constraints (see \ref*{sec:pre_image} for more details).
+The main idea of the construction above is using $\arrseparator$ to separate each element of the array and one register to record the index of each element.
+We introduce two fresh states $q_0$ and $q_f$ to ensure each element is started and ended with at least one $\arrseparator $, which is beneficial to the construction of pre-images of string constraints (see \ref*{sec:pre_image} for more details).
 The accepting condition $\alpha_s$ is the conjunction of accepting conditions of each element.
-    % It is obviously that the accepting word $w$ of $\aut_s$ is in language $\mathcal{L}(\aut_1)\arrconcat\mathcal{L}(\aut_2)\ ... \ \arrconcat \mathcal{L}(\aut_{m}) $.
+    % It is obviously that the accepting word $w$ of $\aut_s$ is in language $\mathcal{L}(\aut_1)\arrseparator\mathcal{L}(\aut_2)\ ... \ \arrseparator \mathcal{L}(\aut_{m}) $.
     \begin{figure}[H]
@@
             \path[->]
-            (q_0) edge [above] node {$\scriptstyle \arrconcat$} (q_1)
+            (q_0) edge [above] node {$\scriptstyle \arrseparator$} (q_1)
             (q_0) edge [below] node {${\scriptstyle r++}$} (q_1)
-            (q_1') edge [above] node {$\scriptstyle \arrconcat$} (omit)
+            (q_1') edge [above] node {$\scriptstyle \arrseparator$} (omit)
             (q_1') edge [below] node {${\scriptstyle r++}$} (omit)
-            (omit) edge [above] node {$\scriptstyle \arrconcat$} (q_m)
+            (omit) edge [above] node {$\scriptstyle \arrseparator$} (q_m)
             (omit) edge [below] node {${\scriptstyle r++}$} (q_m)
-            (q_m') edge [above] node {$\scriptstyle \arrconcat$} (q_f)
+            (q_m') edge [above] node {$\scriptstyle \arrseparator$} (q_f)
             (q_m') edge [below] node {${\scriptstyle r}$} (q_f);
@@
 For example, for a 2-length array $A$ constrained by $``a" = \myread(A, 1)\wedge ``b" = \myread(A, 2) \wedge \mylen(A) = 2$ , where $\myread(A, m)$ read the  element of $A$ at constant index $m$ and $\mylen(A)$ is the length of $A$, we can construct the automaton of $A$ as following: \\
-    $(\emptyset, \{q_0,q_1,q_1',q_2,q_2'\}, \{a,b,\arrconcat\}, \{q_0\xrightarrow[(1)]{\arrconcat}q_1, q_1\xrightarrow[(0)]{a}q_1', q_1'\xrightarrow[(1)]{\arrconcat}q_2, q_2\xrightarrow[(0)]{b}q_2'\}, \{q_0\}, \{q_2'\}, \top)$.
+    $(\emptyset, \{q_0,q_1,q_1',q_2,q_2'\}, \{a,b,\arrseparator\}, \{q_0\xrightarrow[(1)]{\arrseparator}q_1, q_1\xrightarrow[(0)]{a}q_1', q_1'\xrightarrow[(1)]{\arrseparator}q_2, q_2\xrightarrow[(0)]{b}q_2'\}, \{q_0\}, \{q_2'\}, \top)$.
     %%
@@
 \section{String Theory with Integer and Array $\arraylogic $}\label{sec:SL}
-We defined a theory $\arraylogic$ with three sorts: \textbf{string}, \textbf{integer} and \textbf{array}.
+We define a theory $\arraylogic$ with three sorts: \textbf{string}, \textbf{integer} and \textbf{array}.
 The \textit{elements} of \textbf{array} are in \textbf{string} sort, and the $index$ of \textbf{array} is in \textbf{Integer} sort.
 The syntax of $\arraylogic$ is defined in table \ref{tab:syntax}.
-A $\arraylogic$ formula $\varphi$ is a conjunction of the integer atomic formulas $t_1\circ t_2$, or the string atomic formulas $x = \myread(A,m)$, $A = \mywrite(B, x, m)$, $x=\myjoin(A,u)$, $A=\mysplit(x,e)$, $x=y\cdot z$ and $x\in e$.
-Moreover, $t$ is a integer term built from the constant $m$, the varible $i$, the size of array $\mylen(A)$ and the length of string $\mylen(x)$ by operators $+$ and $-$; $\circ \in \{=,\not=, <, \leq, >, \geq \}$ is the set of arithmatic binary predicates on integer terms $t_1$ and $t_2$; $e$ is a regular expression; $\myread(A, m)$ returns the $m$-th element of $A$; $\mywrite(B, x ,m)$ returns the array $B$ after $x$ is written to $m$-th position of $B$; $\myjoin(A,u)$ joins all of the elements in $A$ by string $u$; $\mysplit(x,e)$ splits $x$ into an ordered string array by regex $e$; $y\cdot z$ is the concatenation of $y$ and $z$.
+A $\arraylogic$ formula $\varphi$ is a conjunction of formulas of the form $t_1\circ t_2$, $A = B[m:n]$, $A = \transducer(B)$, $x = \myread(A,m)$, $A = \mywrite(B, x, m)$, $x=\myjoin(A,u)$, $A=\mysplit(x,e)$, $x = \transducer(y)$, $x=y\cdot z$ or $x\in e$.
+Definitely, $t$ is a integer term built from the constant $m$, the varible $i$, the size of array $\mylen(A)$ and the length of string $\mylen(x)$ by operators $+$ and $-$; $\circ \in \{=,\not=, <, \leq, >, \geq \}$ is the set of arithmatic binary predicates on integer terms $t_1$ and $t_2$; $e$ is a regular expression; $B[m:n]$ is the sub-array of $B$ containing elements between $m$ and $n$; $\transducer(B)$ modifies the elements of $B$ by transducer $\transducer$ and returns the result; $\myread(A, m)$ returns the $m$-th element of $A$; $\mywrite(B, x ,m)$ returns the array $B$ after $x$ is written to $m$-th position of $B$; $\myjoin(A,u)$ joins all of the elements in $A$ by string $u$; $\mysplit(x,e)$ splits $x$ into an ordered string array by regex $e$; $\transducer(y)$ returns the output of the transducer $\transducer$ running on $y$; $y\cdot z$ is the concatenation of $y$ and $z$.
 %  For technical convenience, we assume that all assignments in F are \textit{Static Singly Assignment (SSA)} form.
@@
         $t$       & $::=$    & $m \mid i \mid t+t \mid t-t \mid \mylen(A)\mid \mylen(x) $               & Integer term              \\
-        $SC$  & $::=$    & $x=\myread(A, m) \mid A = \mywrite(B, x ,m) \mid x=\myjoin(A,u) \mid$ &                          \\
-              &          & $A = \mysplit(x, e) \mid x= y\cdot z\mid x\in e$                      & String constraints       \\
+        $SC$      & $::=$    & $A = B[m: n] \mid A = \transducer(B) \mid x=\myread(A, m) \mid$          &                           \\
+                  &          & $A = \mywrite(B, x ,m) \mid x=\myjoin(A,u) \mid A = \mysplit(x, e) \mid$ &                           \\
+                  &          & $x= y\cdot z \mid x = \transducer(y)\mid x\in e$                         & String constraints        \\
         $\varphi$ & $::=$    & $t\circ t \mid SC \mid \varphi\wedge \varphi $                           & Formula of $\arraylogic $
@@
     \begin{align*}
-        \phi \ ::= \  & x=y\cdot z \mid x=\myjoin(A,u) \mid A = \mysplit(x,e) \mid         \\
-                      & x=\myread(A, m) \mid A = \mywrite(B, x ,m) \mid \phi \wedge \phi 
+        \phi \ ::= \  & A = B[m:n] \mid A = \transducer(B) \mid x=\myjoin(A,u) \mid A = \mysplit(x,e) \mid         \\
+                      & x=\myread(A, m) \mid A = \mywrite(B, x ,m) \mid x = \transducer(y) \mid x=y\cdot z \mid \phi \wedge \phi 
     \end{align*}
@@
 \section{Pre-images of String Constraints}\label{sec:pre_image}
+
 In this section, we define the pre-images of string constraint formulae. 
-\paragraph{- $i = \mylen(A)$:} The pre-image for the array length function is a CEFA $\aut_{arrlen}=(R, Q, \Sigma\cup\{\arrconcat\}, \delta, I, F, \alpha)$, where
+\pagebreak
+
+We let $\aut_{n}$ be the automaton accepting all arrays with length $n$, that is, $\aut_{n} = q_0\xrightarrow{\arrseparator}q_1\cdots\xrightarrow{\arrseparator}q_{n}$ with $q_i\xrightarrow{\Sigma}q_i$ for $0\leq i \leq n-1$.
+$\aut_*$ is the automaton accepting all arrays with arbitrary length.
+Then the pre-images of operations are defined as follow.
+
+\paragraph{- $i = \mylen(x)$:} As \cite{atva2020}.
+
+\paragraph{- $x = y\cdot z$:} As \cite{ostrich}.
+
+\paragraph{- $x = \transducer(y)$:} As \cite{ostrich}.
+
+\paragraph{- $i = \mylen(A)$:} The pre-image for the array length function is the CEFA $\aut_{arrlen}=(R, Q, \Sigma\cup\{\arrseparator\}, \delta, I, F, \alpha)$, where
 \begin{itemize}
-    \item $R = \{r\}$ for a fresh register $r$, $Q = \{q_0, q_f\}$, $\delta = \myset{q_0\xrightarrow[(0)]{\Sigma}q_0, q_0\xrightarrow[(1)]{\sharp}q_0, q_0\xrightarrow[(0)]{\arrconcat}q_f }$, $I = \myset{q_0}$, $F = \myset{q_f}$, and $\alpha \equiv r = i$.
+    \item $R = \{r\}$ for a fresh register $r$, $Q = \{q_0, q_f\}$, $\delta = \myset{q_0\xrightarrow[(0)]{\Sigma}q_0, q_0\xrightarrow[(1)]{\sharp}q_0,  q_0\xrightarrow{\sharp}q_1} $, $I = \myset{q_0}$, $F = \myset{q_1}$, and $\alpha \equiv r = i$.
 \end{itemize}
 
-\paragraph{- $i = \mylen(x)$:} As the pre-image of length function in \cite{atva2020}.
+\paragraph{- $A = B[m:n]$:} Suppose that $A$ is constrained by $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrseparator\}, \delta_A, I_A, F_A, \alpha_A)$, the pre-image of sub-array operation is defined as $\aut_m\cdot (\aut_A\cap \aut_{m-n})\cdot \aut_{*}$.
 
-\todo{Rewrite the pre-images of array read and write function.}
-\paragraph{- $x = \myread(A, m)$:} Suppose that $x$ is constrained by the CEFA $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$, then the pre-image for the array read function is a CEFA $\aut_{read}=(R, Q, \Sigma\cup\{\arrconcat\}, \delta, I, F, \alpha)$, where
+\paragraph{- $A = \transducer(B)$:} We consider $A$ and $B$ as string varibles and apply the pre-image computation in \cite{ostrich} directly.
+
+\paragraph{- $x = \myread(A, m)$:} Suppose that $x$ is constrained by the CEFA $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$, the pre-image for the array read function is the CEFA $\aut_{read}=(R, Q, \Sigma\cup\{\arrseparator\}, \delta, I, F, \alpha)$ where
 \begin{itemize}
@@
     \item $Q = Q_x\cup\myset{q_0, q_1, \cdots, q_{m}}$,
-    \item $\delta$ is the union of six transitions set:
+    \item $\delta$ is the union of the following transitions set:
           \begin{itemize}
-              \item $\myset{q_i\xrightarrow[(\myvec{0})]{\Sigma}q_i\mid i\in [1,m-1]}$,
-              \item $\myset{q_i\xrightarrow[(\myvec{0})]{\arrconcat}q_{i+1}\mid i\in[0,m-2]}$,
-              \item $\myset{q_{m-1}\xrightarrow[(\myvec{0})]{\arrconcat}q_0^x \mid q_0^x\in I_x}$,
-              \item $\myset{q_f^x\xrightarrow[(\myvec{0})]{\arrconcat}q_m \mid q_f^x\in F_x}$,
-              \item $\myset{q_m\xrightarrow[(\myvec{0})]{\arrconcat}q_m}$,
-              \item $\myset{q\xrightarrow[(\myvec{v})]{a}q'\mid q\xrightarrow[\myvec{v}]{a}q'\in \delta_x}$.
+              \item $\myset{q_i\xrightarrow[\myvec{0}]{\Sigma}q_i\mid i\in [0, m-1]}$,
+              \item $\myset{q_i\xrightarrow[\myvec{0}]{\arrseparator}q_{i+1}\mid i\in[0,m-2]}$,
+              \item $\myset{q_{m-1}\xrightarrow[\myvec{0}]{\arrseparator}q_0^x \mid q_0^x\in I_x}$,
+              \item $\myset{q\xrightarrow[\myvec{v}]{a}q'\mid q\xrightarrow[\myvec{v}]{a}q'\in \delta_x}$,
+              \item $\myset{q_f^x\xrightarrow[\myvec{0}]{\arrseparator}q_m \mid q_f^x\in F_x}$,
+              \item $\myset{q_m\xrightarrow[\myvec{0}]{\Sigma\cup\arrseparator} q_m}$,
           \end{itemize}
@@
 
-\paragraph{- $A = \mywrite(B, x, m)$:} Suppose that $A$ is constrained by $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrconcat\}, \delta_A, I_A, F_A, \alpha_A)$, we firstly consider $A$ as a \emph{string varible} in the formula $A = x_1\arrconcat x_2\arrconcat x_3$.
-The pre-image of the formula is a set of tuple $(\aut_1, \aut_2, \aut_3)$ in which $x_1\in \aut_1, x_2\in \aut_2, x_3\in \aut_3$.
-There is at least one tuple with both $\aut_1$ and $\aut_3$ to be non-empty, as we ensure that each element of array is started and ended with at least one $\arrconcat$.
-Then the pre-image of $A = \mywrite(B, x, m)$ is a set of tuple $(\aut_B, \aut_x)$ where
-\begin{itemize}
-    \item $\aut_B = \aut_1'\arrconcat\Sigma^*\arrconcat\aut_3$, $\aut_1'$ add a new register $r$ to $\aut_1$ to record the occurence times of $\arrconcat$ in $\aut_1$ and add the constraint $r = m$ for the occurence times,
-    \item $\aut_x = \aut_2$.
-\end{itemize}
+\paragraph{- $A = \mywrite(B, x, m)$:} Suppose that $A$ is constrained by $\aut_A=(R_A, Q_A, \Sigma\cup\{\arrseparator\}, \delta_A, I_A, F_A, \alpha_A)$ and $\aut_A = \aut_{pre}\cdot\aut_{ele}\cdot\aut_{post}$.
+Then there are $O(|\aut_A|)$ possible concatenation portfolios $(\aut_{pre},\aut_{ele}$, $\aut_{post})$, and for each portfolio satisfying $\aut_{pre}\cap\aut_{m-1}\not=\emptyset$ and $\aut_{ele}\cap\aut_1\not=\emptyset$, we obtain a tuple $((\aut_{pre}\cap\aut_{m-1})\cdot\aut_1\cdot\aut_{post}, \aut_{ele}\cap\aut_1)$ which is one of the pre-image for array write function.
+The final pre-image is a list of these tuples.
 
-\paragraph{- $x = \myjoin(A,u)$:} Suppose that $x$ is constrained by $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$, then the pre-image is a CEFA
+\paragraph{- $x = \myjoin(A,u)$:} Suppose that $x$ is constrained by $\aut_x=(R_x, Q_x, \Sigma, \delta_x, I_x, F_x, \alpha_x)$ and $u=a_1a_2\cdots a_n$, the pre-image for array join function, $\aut_{join}=(R_x, Q_x\cup\myset{q_f}, \Sigma, \delta, I_x, \myset{q_f}, \alpha_x)$, is generated from $\aut_x$ by adding the transition $q\xrightarrow{\arrseparator}q'$ for each $q\xrightarrow{u}q'\in\aut_x$ and $q_f^x\xrightarrow{\arrseparator}q_f$ for each $q_f^x\in F_x$.
+For $q\xrightarrow{u}q'\in \aut_x$, we mean the state of $\aut_x$ transfer from $q$ to $q'$ after reading the word $u$, that is, there is a path $q\xrightarrow{a_1}q_1\cdots q_{n-1}\xrightarrow{a_n}q'$ in $\aut_x$.
+
+\paragraph{- $A = \mysplit(x, e)$:} Consider $A$ as string, the semantic of this operation is equal to $A = replaceAll(x, e, \arrseparator)$.
+We can apply the computation of pre-image of replaceAll function in \cite{ostrich} directly.
 

### 2023-11-27 2023-1-19/setta2023_report/setta2023_report.tex
setta_report

\documentclass[landscape]{beamer}
\usepackage{xcolor}
\usepackage{amsmath, amsthm}
\newtheorem{benchmark}{Benchmark}
\newtheorem{environment}{Environment}
\newtheorem{distribution}{The Distribution of Counting Operators in Our Benchmark}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{tikz}
\usetikzlibrary {decorations.pathmorphing, curvilinear, shadows,shapes.symbols, automata, positioning, shapes,arrows, matrix}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{array}
\usepackage{colortbl}
\definecolor{grayshade}{gray}{0.9}
\usepackage{listings}
\lstdefinestyle{myjs}{
  language=C,
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  stringstyle=\color{red},
  commentstyle=\color{green},
  backgroundcolor=\color{gray!10},
  breaklines=true,
  frame=single,
  captionpos=b
}
\usepackage{booktabs}
\usepackage{siunitx}

\linespread{1.5}
\newcommand{\aut}{\mathcal{A}}
\newcommand{\myvec}[1]{\overrightarrow{#1}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\anivar}{\mathfrak{x}}
\newcommand*{\ostrichrecl}{\rm OSTRICH^{RECL}}

\colorlet{noteColor}{green!10!orange}

\mode<presentation> {

\usetheme{Singapore}

\useinnertheme{rounded}

\useoutertheme{split}

\usefonttheme{professionalfonts}
}

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\graphicspath{{pics/}}

\title{String Constraints with Regex-Counting and
String-Length Solved More Efficiently}
\author{\textbf{Denghang Hu}, Zhilin Wu}
\institute{Institute of Software, University of Chinese Academy of Sciences}

% Add the image inside titlegraphics macro
\titlegraphic{
  \includegraphics[width=0.2\textwidth]{pics/ISCAS-logo.jpeg} \quad\quad\quad\quad
  \includegraphics[width=0.3\textwidth]{pics/ucas_logo.pdf}
}

%End of title page configuration block
%------------------------------------------------------------

%------------------------------------------------------------
%The next block of commands puts the table of contents at the 
%beginning of each section and highlights the current section:

\AtBeginSection[]
{
  \begin{frame}
    \tableofcontents[currentsection]
  \end{frame}
}
%------------------------------------------------------------

\begin{document}

\pdfbookmark{Title}{Title}
%The next statement creates the title page.
\frame{\titlepage}

% no more than 15 mins 
% Introduction : (3min)
% 1 Motivation
% 3 contribution of our work (overview)
\section{Introduction}

\begin{frame}{String is Important}
  \textbf{String is a primitive data type in program languages:}
  \begin{itemize}
    \item C/++/\#
    \item Java
    \item JavaScript/TypeScript
    \item Python
    \item Go
    \item ...
  \end{itemize}
\end{frame}

\begin{frame}{String is Widely Used in Security-Critical Situations}
  \begin{itemize}
    \item Input sanitisation, validation
    \item Quary generation for databases
    \item Data handling: XML, JSON, HTML
    \item Dynamic code generation
    \item ...
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{String is Error-Prone}
  \begin{tikzpicture}
    \node[starburst,drop shadow,fill=white,draw] at (0,0) {XSS Attack};
    \node[starburst,drop shadow,fill=white,draw] at (5,0) {ReDos Attack};
    \node[starburst,drop shadow,fill=white,draw] at (0,-3) {Broken Access Control};
    \node[starburst,drop shadow,fill=white,draw] at (5,-3) {...};
  \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{Detect Attacks by String Constraints}
  \textbf{Malicious User Input:}
  \begin{lstlisting}[style=myjs]
      <script> XSSAtack </script>
    \end{lstlisting}
  \textbf{Security String Constraints:}
  \begin{lstlisting}[style=myjs]
    (assert (not (str.contains x '<script>')))
  \end{lstlisting}
\end{frame}

\begin{frame}
  \frametitle{String Solvers}
  \begin{multicols}{2}
    \begin{itemize}
      \item ABC
      \item CVC3/4/5
      \item Gecode+S
      \item OSTRICH
      \item Stranger
      \item S3/p/\#
      \item Sloth
      \item SLENT
      \item TRAU/+
      \item Woorpje
      \item Z3str2/3/4/RE/Seq
      \item ...
    \end{itemize}
  \end{multicols}
\end{frame}

\begin{frame}{But...}
  \textbf{Existing Solvers Cannot Solve:}
  \begin{tikzpicture}
    \node (formula) at (0,0) {
      $
        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
      $
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}
\begin{frame}{But...}
  \textbf{Existing Solvers Cannot Solve:}
  \begin{tikzpicture}
    \node (formula) at (0,0) {
      $
        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
      $
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]
  \frametitle{However ...}
  \textbf{Regex-Countings are Widely Used}
  \begin{table}
    \centering
    \begin{tabular}{l l l S[table-format=1.2]}
      \toprule
      \textbf{Rank} & \textbf{Type}  & \textbf{Example} & \textbf{\% Projects} \\
      \midrule
      1             & $\cdot\{1,\}$  & $z^+$            & 0.1                  \\
      3             & $\cdot\{0,\}$  & $z^*$            & 0.2                  \\
      18            & $\cdot\{n\}$   & $z\{8\}$         & 0.05                 \\
      20            & $\cdot\{n,m\}$ & $z\{8,9\}$       & 0.3                  \\
      \bottomrule
    \end{tabular}
    \caption{The Rank and Percentage of Regex-Countings in Python \footnote{Chapman,C. et al: Exploring regular expression usage and context in python}}
  \end{table}

\end{frame}

\begin{frame}[fragile]
  \frametitle{However ...}
  \textbf{String-Length is Widely Used}
  \begin{figure}
    \includegraphics[width=.5\linewidth]{length_percentage.jpg}
    \caption{The Percentages of String Operations in Web Applications \footnote{Saxena, P. et al: A symbolic execution framework for JavaScript.}}
  \end{figure}
\end{frame}

% Technical details : (8min)
% 1 What is Regex-Counting
% 2 normal ways (z3, cvc5, trau)
% 3 our ways
%   1 An example (5-7 pages)
%   2 Decisino procedure 1 pages
\section{Our Approach}
\begin{frame}{Example}
  \begin{tikzpicture}
    \node (placeholder) at (0,0) {
      $
        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
      $
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Rule-based (CVC5, Z3): \textbf{Repeatly unroll} counting operators by derivation rules. For example,
      $x\in \Sigma\cdot z \wedge z\in \Sigma^*c^+$ is derived from $x\in \Sigma^*c^+$ in CVC5.
    };
    \node (cvc5) at (0,-3) {
      \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
    };
    \node (z3) at (5,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node [align=left,rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror},opacity=0] at (5,-3) {Exponentially Search ?};
  \end{tikzpicture}
\end{frame}
\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Rule-based (CVC5, Z3): \textbf{Repeatly unroll} counting operators by derivation rules. For example,
      $x\in \Sigma\cdot z \wedge z\in \Sigma^*c^+$ is derived from $x\in \Sigma^*c^+$ in CVC5.
    };
    \node (cvc5) at (0,-3) {
      \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
    };
    \node (z3) at (5,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node [align=left,rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (5,-3) {\uppercase{Exponential ?}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Automaton-based (Z3Str3RE, OSTRICH):\textbf{ Syntactically unwind} counting operators and then construct automata. E.g., $(\Sigma/a)^{\{1,60\}}$ is unwound to $\Sigma/a\mid \Sigma/a \Sigma/a \mid \cdots$
    };
    \node (z3) at (0,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node (ostrich) at (5,-3) {
      \includegraphics[width=0.3\linewidth]{ostrich_logo.jpeg}
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror},opacity=0] at (5,-3) {STATE EXPLOSION ?};
  \end{tikzpicture}
\end{frame}
\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Automaton-based (Z3Str3RE, OSTRICH):\textbf{ Syntactically unwind} counting operators and then construct automata. E.g., $(\Sigma/a)^{\{1,60\}}$ is unwound to $\Sigma/a\mid \Sigma/a \Sigma/a \mid \cdots$
    };
    \node (z3) at (0,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node (ostrich) at (5,-3) {
      \includegraphics[width=0.3\linewidth]{ostrich_logo.jpeg}
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (5,-3) {STATE EXPLOSION ?};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Our Techniques to Such Constraints}
  \begin{itemize}
    \item Automata with integer registers
    \item Encode counting operators by registers (no explicitly unwind)
    \item Size reduction techniques for automata
  \end{itemize}
\end{frame}

\begin{frame}{Intuition}
  \begin{tikzpicture}[anchor=west]
    \node (a_1_3) at (0, 0) {
      \begin{tikzpicture}[node distance=0.5cm, auto,semithick, font =\small, initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial] (q0) {$q_0$};
        \node[state, accepting] (q1) [right=of q0] {$q_1$};
        \node[state, accepting] (q2) [right=of q1] {$q_2$};
        \node[state, accepting] (q3) [right=of q2] {$q_3$};
        \path[->]
        (q0) edge [above] node {$a$} (q1)
        (q1) edge [above] node {$a$} (q2)
        (q2) edge [above] node {$a$} (q3);
      \end{tikzpicture}
    };
    \node (text1) at (6,0) {\textbf{Finite Automata}};
    \node [opacity = 0] (a_star) at (0,-2) {
      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial,accepting] (q0) {$q_0$};
        \node (accepting_condition) [right=of q0] {$1\leq r\leq3$};
        \path[->]
        (q0) edge [loop above] node [align=center] {$r++$ \\ $a$} (q0);
      \end{tikzpicture}
    };
    \node [opacity = 0] (text2) at (6,-2) {\textbf{Extended with Registers}};
  \end{tikzpicture}
\end{frame}
\begin{frame}[fragile]{Intuition}
  \begin{tikzpicture}[anchor=west]
    \node (a_1_3) at (0, 0) {
      \begin{tikzpicture}[node distance=0.5cm, auto,semithick, initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial] (q0) {$q_0$};
        \node[state, accepting] (q1) [right=of q0] {$q_1$};
        \node[state, accepting] (q2) [right=of q1] {$q_2$};
        \node[state, accepting] (q3) [right=of q2] {$q_3$};
        \path[->]
        (q0) edge [above] node {$a$} (q1)
        (q1) edge [above] node {$a$} (q2)
        (q2) edge [above] node {$a$} (q3);
      \end{tikzpicture}
    };
    \node (text1) at (6,0) {\textbf{Finite Automata}};
    \node (a_star) at (0,-2) {
      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial,accepting] (q0) {$q_0$};
        \node (accepting_condition) [right=of q0] {$1\leq r\leq3$};
        \path[->]
        (q0) edge [loop above] node [align=center] {$r++$ \\ $a$} (q0);
      \end{tikzpicture}
    };
    \node [align=center] (text2) at (6,-2.5) {\textbf{Extended with Registers}\\\textbf{(CEFA)}};

  \end{tikzpicture}
\end{frame}

\begin{frame}{$ x\in \textcolor{red}{(\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{1. Encode Counting Operators : }
  \begin{figure}
    \includegraphics[width=\linewidth]{overview_regex1.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \textcolor{red}{\Sigma^*c^+} \wedge |x| > 120$}
  \textbf{1. Basic Regex Operations : }
  \begin{figure}
    \includegraphics[width=.5\linewidth]{overview_regex2.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120$}
  \textbf{1. The Pre-Image of String-Length :}
  \begin{figure}
    \includegraphics[width=.25\linewidth]{overview_length_pre.jpg}
  \end{figure}
\end{frame}

\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{2. Production : }
  \begin{figure}
    \includegraphics[width=.65\linewidth]{overview_product.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{2. Abstract the Updates of Registers as Vectors : }
  \begin{figure}
    \includegraphics[width=.65\linewidth]{overview_product_vector.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{2. Size-Reduction of the Automaton : }
  \begin{figure}
    \includegraphics[width=.45\linewidth]{overview_product_vector_simplify.jpg}
  \end{figure}
\end{frame}

\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{3. Reduce the Automaton to Parikh Images : }
  \begin{equation}\label{eqn-LIA}
    \begin{array}{l}
      \textcolor{red}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}\ \wedge \\
      1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120.
    \end{array}
  \end{equation}
  \begin{tikzpicture}
    \node [opacity = 0] (placeholder) at (0,0) { \textbf{4. Solve the Parikh Images by the SMT Solver (Princess)} };
    \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,0) {1s SOLVED!!!};
  \end{tikzpicture}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{3. Reduce the Automaton to Parikh Images : }
  \begin{equation}\label{eqn-LIA}
    \begin{array}{l}
      \textcolor{red}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}\ \wedge \\
      1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120.
    \end{array}
  \end{equation}
  \begin{tikzpicture}
    \node (placeholder) at (0,0) { \textbf{4. Solve the Parikh Images by the SMT Solver (Princess)} };
    \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,0) {1s SOLVED!!!};
  \end{tikzpicture}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{3. Reduce the Automaton to Parikh Images : }
  \begin{equation}\label{eqn-LIA}
    \begin{array}{l}
      \textcolor{red}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}\ \wedge \\
      1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120.
    \end{array}
  \end{equation}
  \begin{tikzpicture}
    \node (placeholder) at (0,0) { \textbf{4. Solve the Parikh Images by the SMT Solver (Princess)} };
    \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (0,0) {1s SOLVED!!!};
  \end{tikzpicture}
\end{frame}

% \begin{frame}{Automaton-based}
%   \begin{definition}[Cost-Enriched Finite Automaton]
%     A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F, \alpha)$ where
%     \begin{itemize}
%       \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers,
%       \item $Q, \Sigma, I, F$ are as in the definition of NFA,
%       \item $\delta \subseteq Q \times \Sigma \times Q \times \mathbb{Z}^R$ is a transition relation, where $\mathbb{Z}^R$ denotes the updates on the values of registers.
%       \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
%     \end{itemize}
%   \end{definition}
% \end{frame}

% \begin{frame}{Automaton-based}
%   Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA.
%   \begin{run}
%     A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$.
%   \end{run}

%   \begin{accepting}
%     A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$
%   \end{accepting}

% \end{frame}

% \begin{frame}{Symbolically encoding}
%   illustrate the CEFA of regexes in the example. explain why it is symbolic and what the difference is compared to unwinding
% \end{frame}

% \begin{frame}{Size reduction techniques}
%   trival minimization: (a, v) together as one symbol
%   but not enough
% \end{frame}

% \begin{frame}{Size reduction techniques}
%   only consider vectors, i.e., the alphabet is unary. and let 0 vector be epsilon label. do the minimization techniques.

%   significantly improve the preformance. (show the data)
% \end{frame}

\begin{frame}{The Brief of Decision Procedure}
  \begin{enumerate}
    \item Encode counting operators by the automata with registers.
    \item Product the automata and simplify them.
    \item Convert them to parikh images.
    \item Solve the parikh images by the SMT solver (Princess).
  \end{enumerate}
\end{frame}

% Experiment Results (3min)
% 1 Introduction of benchmark suites
% 2 Explanation for results
\section{Evaluation}

\begin{frame}{System Overview}
  \begin{figure}[!htb]
    \centering
    \resizebox{\textwidth}{!}{ % Resize the TikZ picture to fit the frame width
      \begin{tikzpicture}[>=latex]

        % Define block styles
        \tikzstyle{input} = [rectangle, draw, fill=white!20, text width=2cm, text centered, rounded corners, minimum height=1.5cm]
        \tikzstyle{output} = [rectangle, draw, fill=white!20, text width=2cm, text centered, rounded corners, minimum height=1.5cm]
        \tikzstyle{component} = [rectangle, draw, fill=blue!20, text width=3.5cm, text centered, rounded corners, minimum height=1.5cm]
        \tikzstyle{core} = [rectangle, draw, fill=yellow!20, text width=2.5cm, text centered, minimum height=2cm]
        \tikzstyle{logic} = [ellipse, draw, fill=red!20, text width=2.5cm, text centered, minimum height=1.5cm]
        \tikzstyle{file} = [rectangle, draw, fill=green!20, text width=1.5cm, text centered, rounded corners, minimum height=1cm]
        \tikzstyle{arrow} = [thick,->,>=stealth]

        % Components
        \node (input) [input] {Smtlib2 File};
        \node (integer) [logic, right=3.5cm of input] {Integer Logic};
        \node (core) [core, below=1.5cm of integer] {Core Solver};
        \node (string) [logic, below=1.6cm of input] {String Logic};
        \node (smtsolver) [component, right=1.5cm of integer] {SMT Solver};
        \node (output) [output, below=1.5cm of smtsolver] {Sat/Unsat};

        % Arrows
        \draw [arrow] (input) -- (integer);
        \draw [arrow] (integer) -- (core);
        \draw [arrow] (core) to[out=60,in=-60] node[midway, right] {\textbf{Parikh Images}} (integer);
        \draw [arrow] (input) -- (string);
        \draw [arrow] (string) to node[midway, above] {\textbf{Encode Countings}} (core);
        \draw [arrow] (core) to[out=-150,in=-30] node[midway, below] {Pre-Images} (string);
        \draw [arrow] (integer) -- (smtsolver);
        \draw [arrow] (smtsolver) -- (output);

        % Labels
        \node [above=0.2cm of input] {Input};
        \node [below=0.2cm of output] {Output};

      \end{tikzpicture}
    }
  \end{figure}

\end{frame}

\begin{frame}{Benchmark Suites and Environment}
  \begin{benchmark}
    \begin{itemize}
      \item \textbf{RegCoL:} 40,628 instances that contains regexes from real-world website and is manually constructed.
      \item \textbf{AutomatArk:}  8,215 instances that is adapted from the AutomatArk suite.
    \end{itemize}
  \end{benchmark}
\end{frame}

\begin{frame}{Benchmark Suites and Environment}
  \begin{distribution}
    \includegraphics[width=\linewidth]{counting_distribution.png}
  \end{distribution}
\end{frame}

\begin{frame}{Benchmark Suites and Environment}
  \begin{environment}
    \begin{itemize}
      \item \textbf{Operating System: } CentOS Stream release 8
      \item \textbf{CPU: } Intel(R) Xeon(R) Platinum 8269CY 3.10GHz
      \item \textbf{Memory: } 190 GB
      \item \textbf{Timeout Limit: } 60s
    \end{itemize}
  \end{environment}
\end{frame}

\begin{frame}{Our Solver Solve the Most Instances}
  \centering
  \include{tables/table_regcol}
\end{frame}

\begin{frame}{Our Technical Choises Are the Most Efficient}
  \centering
  \include{tables/table_simp}
\end{frame}

% Summary and Future work (1min)
% 1 contribution again and main points
% 2 how to handle non-register-representable counting
% 3 potential application 
\section{Conclusion and Future Work}
\begin{frame}
  \frametitle{Our Contributions}
  \begin{enumerate}
    \item Divise an algorithm that efficiently solve string constraints with regex-counting and string-length
    \item Propose particular size-reduction techniques for automata with registers
    \item Carry out abundant experiments
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Future Work}
  \begin{enumerate}
    \item Symbolically encode non-register-representable counting operators, such as $(a^{\{1,3\}})^*$ and $\overline{a^{\{1,3\}}}$.
    \item Apply this method in the analysis of real-world programs.
  \end{enumerate}
\end{frame}

\end{document}

### 2024-05-15 2024-5-13/sections/cefa.tex
commit the paper extended by setta2023

--- 2023-10-20 2023-1-19/crv/sections/cefa.tex
@@
 A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$.
-The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$.
-Note that the values of all registers are initiated to zero and updated to $\sum \limits_{j \in [n]} \myvec{v_j}$ after all the transitions in the run are executed.
+The string $w$ is $accepted$ by the CEFA if and only if there is an accepting run of $w$.
+The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$.Note that the values of all registers are initiated to zero and updated to $\sum \limits_{j \in [n]} \myvec{v_j}$ after all the transitions in the run are executed.
 We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.

### 2024-05-15 2024-5-13/sections/heuristic.tex
commit the paper extended by setta2023

In the previous paper \cite{Denghang2023}, we naively unwind the counting operators when they are in other counting or complement operator. However, this approach is not efficient when the counting bounds are large. In this section, we present some heuristics to solve the RECL constraints more efficiently.

\subsection{Heuristic for RECL Constraints with Nested Counting}\label{heuristic:nested}
 The naive unwinding approach in the paper \cite{Denghang2023} is to unwind all inner counting operators. This approach may generate a large number of states, which is linear to the product of the counting bounds in regex and exponential to the length of the regex. For example, naive unwinding regex $(a^{\{1,1000\}})^{\{1,2\}}$ generate a CEFA containing 1000 states. But if we only unwind the outer counting operator of the regex, not inner, we obtain a CEFA containing only 2 states. The side effect is that we need more registers to store the information of conuting in the inner regex. Recall that unwinding of outer counting operator repeat the inner regex, which also repeat the registers of the inner regex.We present a heuristic to reduce the number of states generated by the unwinding process. The idea is to unwind the counting operator with less bound and less side effect firstly. We present the heuristic in the following algorithm.

\medskip
\noindent
\emph{Step 1. (Compute the number of states generated by each counting operator if we unwind it).}

For a regex $\regex$, we can approximate the number of states $size(\regex)$ generated by the following formula: 
\begin{itemize}
  \item If $\regex = \emptyset$ or $\regex = \epsilon$, then $size(\regex) = 0$. 
  \item If $\regex = \regex_1 \cdot \regex_2$ or $\regex = \regex_1 + \regex_2$, then $size(\regex) = size(\regex_1) + size(\regex_2)$.
  \item If $\regex = \regex_1^*$, then $size(\regex) = size(\regex_1)$.
  \item If $\regex = \regex_1 \cap \regex_2$, then $size(\regex) = min(size(\regex_1), size(\regex_2))$.
  \item If $\regex = \overline{\regex_1}$, then $size(\regex) = 2^{size(\regex_1)} + 1$.
  \item $\regex = \regex_1 \backslash \regex_2$ can be transfered to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the size can be computed by the formula of $\cap$ and $\bar{}$.
  \item For $\regex = \regex_1^{\{n,m\}}$ or $\regex = \regex_1^{\{m,\infty\}}$, $size(\regex)$ is equal to $m*size(\regex_1)$ if it is unwinded, and $size(\regex_1)$ otherwise.
\end{itemize}

For each counting operator $^{\{n,m\}}$ or $^{\{m,\infty\}}$ with $\regex$ as its subregex, the number of states generated by it is $m*size(\regex)$ if we unwind it.

The formula above is an approximation of the states of CEFA generated by Thompson's construction. Note that the number of states is linear to the bound for the counting operator.

\medskip
\noindent
\emph{Step 2. (Compute the number of registers generated by each counting operator if we unwind it).}

We unwind the counting operator with less bound first. The reason is that the number of states generated by the counting operator is linear to its bound. If we unwind the counting operator with less bound first, the number of states generated by the unwinding process is less. However, the hardness of solving the $\cefadec$ problem is not only relevant to the number of states, but also the number of registers. For a regex $\regex$, we can approximate the number of registers $reg(\regex)$ generated by the following formula:
\begin{itemize}
  \item If $\regex = \emptyset$, $\regex = \epsilon$, $\regex = \regex_1^*$ or $\regex = \overline{\regex_1}$, then $reg(\regex) = 0$.
  \item If $\regex = \regex_1\cdot \regex_2$ or $\regex = \regex_1 \cap \regex_2$, then $reg(\regex) = reg(\regex_1) + reg(\regex_2)$.
  \item If $\regex = \regex_1 + \regex_2$, then $reg(\regex) = reg(\regex_1) + reg(\regex_2) + 1$.
  \item $\regex = \regex_1 \backslash \regex_2$ can be transfered to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the number of registers can be computed by the formula of $\cap$ and $\bar{}$.
  \item For $\regex = \regex_1^{\{n,m\}}$ or $\regex = \regex^{\{m, \infty\}}$, $reg(\regex)$ is equal to $m*reg(\regex_1)$ if it is unwinded, and $1$ otherwise.
\end{itemize}

For each counting operator $^{\{n,m\}}$ or $^{\{m,\infty\}}$ with $\regex$ as its subregex, the number of registers generated by it is $m*reg(\regex)$ if we unwind it.

\medskip
\noindent
\emph{Step 3. (Unwind the counting operator with less bound and less registers first).}

In the above two steps, we compute the number of states and registers generated by each counting operator. In some cases, we can unwind the counting operator with less bound and less registers directly. But in most cases, there are multiple counting operators where one counting operator has less bound and another counting operator has less registers. To consider the number of states and registers at the same time, we can compute the score of each counting operator by the following formula:
\begin{itemize}
  \item $score(\regex) = size(\regex) * (reg(\regex)+1)$.
\end{itemize} 
The reason why we use product to combine the two factors is that the hardness of the $\cefadec$ problem is highly relevant to the number of variables in the final existential LIA formula, which is linear to the product of the number of states and the number of registers. Use $reg(\regex) + 1$ not $reg(\regex)$ is because the registers number may be $0$.We unwind the counting operator with the smallest score first.

\begin{example}
  Consider the regex $(a^{\{1,1000\}})^{\{1,2\}}$. The score of $^{\{1,1000\}}$ is $1000*(0+1) = 1000$ and the score of $^{\{1,2\}}$ is $2*(2+1) = 6$. We unwind the outer counting operator first and obtain a CEFA containing only 2 states.  
\end{example}

\subsection{Heuristic for RECL Constraints with Complement on Counting}
As we mentioned in the above section \ref{heuristic:nested}, the unwinding process of the complement operator is exponential to the counting bounds in the worst case. We present a heuristic to reduce the number of states generated by the unwinding process. The idea is to under-approximate and over-approximate the language of the regex first, so that we can avoid unwinding counting operators in complement. We present the heuristic in the following algorithm.

\medskip
\noindent
\emph{Step 1. (Under-approximate the language of the regex with complement operators).}

The under-approximation is replacing each counting operator in the subregex of complement with a Kleene star operator. The language of the subregex is a superset of the language of it after under-approximation. In sequential, the complement of the subregex is a subset of origin. Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement. For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.

\medskip
\noindent
\emph{Step 2. (Over-approximate the language of the regex with complement operators).}

The over-approximation is to complement the CEFA of the subregex directly, without unwinding the counting operators in the subregex. The over-approximated complementary algorithm for CEFA is as follows:

Given a CEFA $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$, the over-approximated complement of it is a tuple $(R\cup\{r\}, Q\cup\{s,f\}, \Sigma, \delta', I, (Q\cup\{s,f\})\backslash F, \alpha')$, where :
\begin{itemize}
  \item $r$ is a new regesiter not in $R$.
  \item $s$ and $f$ are two new states not in $Q$.
  \item $\delta'$ is a transitions set containing all transitions in $\delta$ and transitions from each state $q$ in $Q$ to $s$ with label $a$ if there is no transitions from $q$ to any state with label $a$ in $\aut$. To be more detailed, $\delta'$ is the union of four sets:
  \begin{itemize}
    \item $\{(q, a, q',(\vec{v}, \vec{0})) \mid (q, a, q', \vec{v})\in \delta\}$
    \item $\{(q, a, s,(\vec{0}, \vec{0})) \mid \forall q'\in Q,\vec{v}. (q, a, q', \vec{v})\not\in \delta\}$
    \item $\{(q, a, f,(\vec{v}, \vec{1})) \mid \exists q'\in F, (q, a, q', \vec{v})\in \delta\}$
    \item $\{(s, \Sigma, s, (\vec{0}, \vec{0}))\}$
  \end{itemize}
  \item $\alpha'$ is $r \not= 1\vee \neg \alpha$
\end{itemize}

$r$ is the register used to check whether the accepted state is also accepted in the original CEFA. $s$ is the self loop state accepting all string that is not accepted by the original CEFA. $f$ is the merged accepted state of original CEFA. If there is a transition $(q, a, q', \vec{v})$ teminates at the accepted state $q'$ in the original CEFA, we add a corresponding transition $(q, a, f, (\vec{v}, \vec{1}))$ in the over-approximated complement. From the definition of $\delta'$, we can see that only the transitions goto $f$ increase the value of regesiter $r$. The value of $r$ is $1$ if and only if the accepted state is also accepted in the original CEFA. With above construction, the meaning of the accepting condition $\alpha'$ is obvious: If the string teminates at the accepting state in the original CEFA, then the accepting condition $\alpha$ is false.

\begin{theorem}
  The language of over-approximated complement of CEFA is a superset of the language of exact complement.
\end{theorem}
\begin{proof}
   Suppose that the original CEFA is $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$, the over-approximated complement of it is $\overline{\aut}_{over} = (R\cup\{r\}, Q\cup\{s,f\}, \Sigma, \delta', I, (Q\cup\{s,f\})\backslash F, \alpha')$, and the exact complement of it is $\overline{\aut}$. To prove the theorem, we only need to show that if a string is accepted by $\overline{\aut}$, then it is accepted by $\overline{\aut}_{over}$. In other words, we need to show that if a string is not accepted by $\overline{\aut}_{over}$, then it is not accepted by $\overline{\aut}$, which means it is accepted by $\aut$. We prove it by construction.

   In the definition of CEFA in section \ref{sec:automaton}, a run $q_0 \xrightarrow[\myvec{\overline{v}_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{\overline{v}_n}]{a_n} q_n$ is \emph{accepting} by $\overline{\aut}_{over}$ if $q_n \in (Q\cup\{s,f\})\backslash F$ and $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is true, where $\myvec{\overline{v}'} = \sum \limits_{j \in [n]} \myvec{\overline{v}_j}$. If a string is not accepted by $\overline{\aut}_{over}$, then each run of the string is not accepting run, which means the run teminates at state $q\in F$ or the accepting condition $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is $false$.

   If each run teminates at state $q_f\in F$, suppose that each is of form $q_0\xrightarrow[(\myvec{v_1},\myvec{0})]{a_1}q_1\cdots q_{n-1}\xrightarrow[(\myvec{v_n},\myvec{0})]{a_n}q_f$, where $\myvec{\overline{v}_i}$ is $(\myvec{v_i}, \myvec{0})$ or $(\myvec{v_i}, \myvec{1})$ for $1\leq i\leq n$. Then there is a transition $(q_{n-1}, a_n, q_f, \myvec{v_n})$ in $\delta$ because there is a transition $(q_{n-1}, a_n, q_f, (\myvec{v_n}, \myvec{0}))$ in $\delta'$. So there is a transition $(q_{n-1}, a_n, f, (\myvec{v_n}, \myvec{1}))$ in $\delta'$ based on our construction for $\delta'$. The run $q_0\xrightarrow[(\myvec{v_1},\myvec{0})]{a_1}q_1\cdots q_{n-1}\xrightarrow[(\myvec{v_n},\myvec{1})]{a_n}f$ teminates at the accepting state $f$, contridicting the assumption.

   If each run makes the accepting condition $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ false, then the negation of the accepting condition $\neg\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is true. The negation can be rewriten to $(r=1\wedge \alpha)(\myvec{\overline{v}'}/(R\cup\{r\})) = (r=1)(\myvec{\overline{v}'}/(R\cup\{r\}))\wedge \alpha(\myvec{\overline{v}'}/(R\cup\{r\}))$. In our construction, only the transitions teminate at $f$ increase one to the value of $r$, so that the run must end at $f$ to make $r=1$ be true. $\alpha(\myvec{\overline{v}'}/(R\cup\{r\})) = \alpha(\myvec{v'}/R)$ is also need to be true, implying that the run is an accepting run of $\aut$.
\end{proof}

\subsection{Heuristic for Finding a Accepted Word in a Cost-enriched Automaton}
In the section \ref{sec:algorithm}, we present an algorithm to solve the $\cefadec$ problem. The algorithm computes existential LIA formulas and then uses SMT solver to solve it. However, this procedure only anwser the question whether the language of the regex is empty or not. If the language is not empty, we need to find a word in the language in practice. In our preivous paper \cite{Denghang2023}, we do not explicitly present the algorithm to find a word in the language because of the space limitation. We have used a naive approach which randomly searching the CEFAs by the depth-first search, based on the regesiters values obtained from solving the existential LIA formula. However, this approach is not efficient. Suppose that there are $n$ registers whose values are $r_1,\cdots, r_n$ respectively in the CEFA, we may visit each transition $O(r_1*r_2\cdots *r_n)$ times during the search. To relieve this problem, we present a heuristic to find a word in the language as following algorithm.

\medskip
\noindent
\emph{Step 1. (Compute the transitions times visited by the accepted strings of CEFAs).}

For each CEFA $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$, we already know the values of its registers after solving the existential LIA formula. The values can be seen as a constant vector of length $|R|$. We use $\myvec{R}$ to denote the vector and use $\eta((q, a, q', \myvec{v}))$ to denote the parikh image of $\aut$. Then the number of times that the transition $(q, a, q', \myvec{v})$ visited by the accepted stirng is obtained from the following formula:
$$ \sum \limits_{(q, a, q', \myvec{v})\in \delta} \eta((q, a, q', \myvec{v}))\myvec{v} = \myvec{R}$$

\medskip
\noindent
\emph{Step 2. (Cut off the search tree early by the transitions times visited during the search process).}

After computing the transitions times visited by the accepted strings, we can cut off the search tree of the CEFA. The idea is that we only visit the transition $(q, a, q', \myvec{v})$ if the number of times that the transition visited by the accepted string is greater than $0$. Other transitions are deleted from the CEFA so that we can reduce the search space. Note that the transitions times is updated during the search process so the search space is reduced dynamically. The presudo code of the algorithm is as follows:

### 2024-05-15 2024-5-13/sections/introduction.tex
commit the paper extended by setta2023

--- 2023-10-20 2023-1-19/sections/introduction.tex
@@
 
-Counting (aka repetition) is a convenient feature in regexes that count the number of matchings of sub-patterns.
+Counting (aka repetition) is a convenient feature in regexes that counts the number of matchings of sub-patterns.
 For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
-Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ is equivalent to $a^{\{0,\infty\}}$ and $a^+$ are equivalent to $a^{\{1,\infty\}}$.
+Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ is equivalent to $a^{\{0,\infty\}}$ and $a^+$ is equivalent to $a^{\{1,\infty\}}$.
 Counting is a frequently used feature of regexes.
@@
 The Slent tool solves the string constraints involving string-length function by encoding them into so-called length-encoded automata, then utilizing symbolic model checkers to solve their nonemptiness problem~\cite{WC+18}.
-However, neither Trau nor Slent supports counting operators explictly, in other words, counting operators in regexes should be unfolded before solved by them.
+However, neither Trau nor Slent supports counting operators explicitly, in other words, counting operators in regexes should be unfolded before solved by them.
 %

### 2024-05-15 2024-5-13/setta2023_report/setta2023_report.tex
commit the paper extended by setta2023

--- 2023-11-27 2023-1-19/setta2023_report/setta2023_report.tex
@@
 \usepackage{siunitx}
+\usepackage{graphicx}
 
@@
 \newcommand*{\ostrichrecl}{\rm OSTRICH^{RECL}}
+\newcommand*{\op}{o}
+\newcommand*{\regex}{e}
 
@@
 \author{\textbf{Denghang Hu}, Zhilin Wu}
-\institute{Institute of Software, University of Chinese Academy of Sciences}
+% \institute{}
 
@@
 
-\begin{frame}{String is Important}
-  \textbf{String is a primitive data type in program languages:}
+\begin{frame}{Strings are Important}
+  \textbf{Strings are primitive in program languages:}
   \begin{itemize}
-    \item C/++/\#
+    \item C/C++/C\#
     \item Java
@@
     \item Go
-    \item ...
   \end{itemize}
@@
 
-\begin{frame}{String is Widely Used in Security-Critical Situations}
+\begin{frame}{Strings are Widely Used in Security-Critical Situations\footnote{Tevfik Bultan, et al.: String Analysis for Software Verification and Security.}}
   \begin{itemize}
@@
     \item Dynamic code generation
-    \item ...
   \end{itemize}
@@
 \begin{frame}
-  \frametitle{String is Error-Prone}
+  \frametitle{Strings Are Error-Prone}
   \begin{tikzpicture}
@@
     \end{lstlisting}
-  \textbf{Security String Constraints:}
+  \textbf{Detect the Attack by String Constraints:}
   \begin{lstlisting}[style=myjs]
-    (assert (not (str.contains x '<script>')))
+    (assert (str.contains x '<script>'))
   \end{lstlisting}
@@
       \item ABC
-      \item CVC3/4/5
+      \item \textbf{CVC3/4/5}
       \item Gecode+S
-      \item OSTRICH
+      \item \textbf{OSTRICH}
       \item Stranger
@@
       \item Woorpje
-      \item Z3str2/3/4/RE/Seq
+      \item \textbf{Z3str2/3/4/RE/Seq}
       \item ...
@@
 
-\begin{frame}{But...}
-  \textbf{Existing Solvers Cannot Solve:}
+\begin{frame}{Motivation Example}
+  \textbf{CVC5 and Z3 Cannot Solve:}
   \begin{tikzpicture}
@@
     $
-        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
+      x\in (\Sigma \backslash a)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash b)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash c)^{\textcolor{red}{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120
     $
     };
-    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
+    \node [rotate=45, scale=2, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
   \end{tikzpicture}
 \end{frame}
-\begin{frame}{But...}
-  \textbf{Existing Solvers Cannot Solve:}
+\begin{frame}{Motivation Example}
+  \textbf{CVC5 and Z3 Cannot Solve:}
   \begin{tikzpicture}
@@
     $
-        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
+      x\in (\Sigma \backslash a)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash b)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash c)^{\textcolor{red}{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120
     $
     };
-    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (1,0) {300s TIMEOUT};
+    \node [rotate=45, scale=2, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (1,0) {300s TIMEOUT};
   \end{tikzpicture}
@@
       \midrule
-      1             & $\cdot\{1,\}$  & $z^+$            & 0.1                  \\
-      3             & $\cdot\{0,\}$  & $z^*$            & 0.2                  \\
-      18            & $\cdot\{n\}$   & $z\{8\}$         & 0.05                 \\
-      20            & $\cdot\{n,m\}$ & $z\{8,9\}$       & 0.3                  \\
+      1             & $\cdot\{1,\}$  & $z^+$            & 73.2                 \\
+      3             & $\cdot\{0,\}$  & $z^*$            & 66.8                 \\
+      18            & $\cdot\{n\}$   & $z\{8\}$         & 20.7                 \\
+      20            & $\cdot\{n,m\}$ & $z\{8,9\}$       & 14.5                 \\
       \bottomrule
@@
 \section{Our Approach}
-\begin{frame}{Example}
+\begin{frame}{The Problem}
+  Syntax of \textbf{RE}gex-\textbf{C}ounting \textbf{L}ogic (\textbf{RECL}):
+  \begin{figure}[h]
+    \centering
+    \resizebox{1\linewidth}{!}{
+      $
+        \begin{array}{l l l l}
+          \varphi & ::= & x\in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi                                                                                         & \mbox{formulas}      \\
+          \regex  & ::= & \emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid                                 &                      \\
+                  &     & \overline{\regex} \mid \regex \setminus \regex \mid {\textcolor{red!90}{\regex^{\{m,n\}}}} \mid {\textcolor{red!90}{\regex^{\{m,\infty\}}}} \mid (e) & \mbox{regexes}       \\
+          t       & ::= & n \mid \anivar \mid  {\textcolor{red!90}{|x|}} \mid t - t \mid t + t                                                                                 & \mbox{integer terms}
+        \end{array}
+      $
+    }
+  \end{figure}
+\end{frame}
+\begin{frame}{Motivation Example}
   \begin{tikzpicture}
@@
     $
-        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
+      x\in (\Sigma \backslash a)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash b)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash c)^{\textcolor{red}{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120
     $
     };
-    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
+    \node [rotate=45, scale=2, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
   \end{tikzpicture}
@@
 
-\begin{frame}{Exsiting Techniques to Such Constraints}
+\begin{frame}[fragile]{Exsiting Techniques to Solve Such Constraints}
+  \begin{minipage}{0.48\linewidth}
     \begin{tikzpicture}
-    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
-      Rule-based (CVC5, Z3): \textbf{Repeatly unroll} counting operators by derivation rules. For example,
-      $x\in \Sigma\cdot z \wedge z\in \Sigma^*c^+$ is derived from $x\in \Sigma^*c^+$ in CVC5.
+      \node [anchor=west, align=left, text width = .9\linewidth] (text) at (0,-2) {
+        Rule-based (CVC5, Z3): \\ \textbf{Repeatly unwind} counting operators by derivation rules.
       };
-    \node (cvc5) at (0,-3) {
+      \node [anchor=west, align=left] (cvc5) at (0,-4) {
         \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
       };
-    \node (z3) at (5,-3) {
+      \node [anchor=west, align=left] (z3) at (3,-4) {
         \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
       };
-    \node [align=left,rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror},opacity=0] at (5,-3) {Exponentially Search ?};
+      \node [anchor=west, align=left] (example) at (0,-5.5) {$a^{\{1,3\}}: a, aa, aaa$};
+      \node [anchor=west, align=left,rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,-5.5) {Exponential Search Space};
     \end{tikzpicture}
-\end{frame}
-\begin{frame}{Exsiting Techniques to Such Constraints}
+  \end{minipage}
+  \begin{minipage}{0.48\linewidth}
     \begin{tikzpicture}
-    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
-      Rule-based (CVC5, Z3): \textbf{Repeatly unroll} counting operators by derivation rules. For example,
-      $x\in \Sigma\cdot z \wedge z\in \Sigma^*c^+$ is derived from $x\in \Sigma^*c^+$ in CVC5.
+      \node [anchor=west, align=left, text width = \linewidth] (text) at (0,-2) {
+        Automaton-based (Z3Str3RE, OSTRICH):\textbf{Unwind} counting operators before constructing automata.
       };
-    \node (cvc5) at (0,-3) {
-      \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
+      \node [anchor = west, align=center] (z3) at (3,-4) {
+        \includegraphics[width=0.25\linewidth]{ostrich_logo.jpeg}
       };
-    \node (z3) at (5,-3) {
-      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
-    };
-    \node [align=left,rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (5,-3) {\uppercase{Exponential ?}};
-  \end{tikzpicture}
-\end{frame}
-
-\begin{frame}{Exsiting Techniques to Such Constraints}
-  \begin{tikzpicture}
-    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
-      Automaton-based (Z3Str3RE, OSTRICH):\textbf{ Syntactically unwind} counting operators and then construct automata.
-E.g., $(\Sigma/a)^{\{1,60\}}$ is unwound to $\Sigma/a\mid \Sigma/a \Sigma/a \mid \cdots$
-    };
-    \node (z3) at (0,-3) {
-      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
-    };
-    \node (ostrich) at (5,-3) {
-      \includegraphics[width=0.3\linewidth]{ostrich_logo.jpeg}
-    };
-    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror},opacity=0] at (5,-3) {STATE EXPLOSION ?};
-  \end{tikzpicture}
-\end{frame}
-\begin{frame}{Exsiting Techniques to Such Constraints}
-  \begin{tikzpicture}
-    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
-      Automaton-based (Z3Str3RE, OSTRICH):\textbf{ Syntactically unwind} counting operators and then construct automata.
-E.g., $(\Sigma/a)^{\{1,60\}}$ is unwound to $\Sigma/a\mid \Sigma/a \Sigma/a \mid \cdots$
-    };
-    \node (z3) at (0,-3) {
-      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
-    };
-    \node (ostrich) at (5,-3) {
-      \includegraphics[width=0.3\linewidth]{ostrich_logo.jpeg}
-    };
-    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (5,-3) {STATE EXPLOSION ?};
-  \end{tikzpicture}
-\end{frame}
-
-\begin{frame}{Our Techniques to Such Constraints}
-  \begin{itemize}
-    \item Automata with integer registers
-    \item Encode counting operators by registers (no explicitly unwind)
-    \item Size reduction techniques for automata
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Intuition}
-  \begin{tikzpicture}[anchor=west]
-    \node (a_1_3) at (0, 0) {
-      \begin{tikzpicture}[node distance=0.5cm, auto,semithick, font =\small, initial text=$a^{\{1,3\}}:$,
+      \node [anchor = west, align=left, rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,-4) {State Explosion};
+      \node [anchor=west, align=left] (example) at (0,-5.5) {
+        \begin{tikzpicture}[node distance=0.5cm, auto,semithick, initial text=$a^{\{1,3\}}:$,
             every state/.style={inner sep=1pt, minimum size=5pt}]
@@
       };
-    \node (text1) at (6,0) {\textbf{Finite Automata}};
-    \node [opacity = 0] (a_star) at (0,-2) {
-      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$a^{\{1,3\}}:$,
+    \end{tikzpicture}
+  \end{minipage}
+\end{frame}
+\begin{frame}[fragile]{Exsiting Techniques to Solve Such Constraints}
+  \begin{minipage}{0.48\linewidth}
+    \begin{tikzpicture}
+      \node [anchor=west, align=left, text width = .9\linewidth] (text) at (0,-2) {
+        Rule-based (CVC5, Z3): \\ \textbf{Repeatly unwind} counting operators by derivation rules.
+      };
+      \node [anchor=west, align=left] (cvc5) at (0,-4) {
+        \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
+      };
+      \node [anchor=west, align=left] (z3) at (3,-4) {
+        \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
+      };
+      \node [anchor=west, align=left] (example) at (0,-5.5) {$a^{\{1,3\}}: a, aa, aaa$};
+      \node [anchor=west, align=left,rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (0,-5.5) {Exponential Search Space};
+    \end{tikzpicture}
+  \end{minipage}
+  \begin{minipage}{0.48\linewidth}
+    \begin{tikzpicture}
+      \node [anchor=west, align=left, text width = \linewidth] (text) at (0,-2) {
+        Automaton-based (Z3Str3RE, OSTRICH):\textbf{Unwind} counting operators before constructing automata.
+      };
+      \node [anchor = west, align=center] (z3) at (3,-4) {
+        \includegraphics[width=0.25\linewidth]{ostrich_logo.jpeg}
+      };
+      \node [anchor = west, align=left, rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (0,-4) {State Explosion};
+      \node [anchor=west, align=left] (example) at (0,-5.5) {
+        \begin{tikzpicture}[node distance=0.5cm, auto,semithick, initial text=$a^{\{1,3\}}:$,
             every state/.style={inner sep=1pt, minimum size=5pt}]
-        \node[state,initial,accepting] (q0) {$q_0$};
-        \node (accepting_condition) [right=of q0] {$1\leq r\leq3$};
+          \node[state,initial] (q0) {$q_0$};
+          \node[state, accepting] (q1) [right=of q0] {$q_1$};
+          \node[state, accepting] (q2) [right=of q1] {$q_2$};
+          \node[state, accepting] (q3) [right=of q2] {$q_3$};
           \path[->]
-        (q0) edge [loop above] node [align=center] {$r++$ \\ $a$} (q0);
+          (q0) edge [above] node {$a$} (q1)
+          (q1) edge [above] node {$a$} (q2)
+          (q2) edge [above] node {$a$} (q3);
         \end{tikzpicture}
       };
-    \node [opacity = 0] (text2) at (6,-2) {\textbf{Extended with Registers}};
     \end{tikzpicture}
+  \end{minipage}
 \end{frame}
-\begin{frame}[fragile]{Intuition}
+
+% \begin{frame}{Our Techniques to Such Constraints}
+%   \begin{itemize}
+%     \item Automata with integer registers
+%     \item Encode counting operators by registers (no explicitly unwind)
+%     \item Size reduction techniques for automata
+%   \end{itemize}
+% \end{frame}
+
+\begin{frame}[fragile]{The Main Idea of Our Approach}
+  \linespread{0.9}
   \begin{tikzpicture}[anchor=west]
@@
     \node (text1) at (6,0) {\textbf{Finite Automata}};
-    \node (a_star) at (0,-2) {
+    \node (a_1_3_cefa) at (0,-1.5) {
       \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$a^{\{1,3\}}:$,
@@
         \node[state,initial,accepting] (q0) {$q_0$};
-        \node (accepting_condition) [right=of q0] {$1\leq r\leq3$};
+        \node (accepting_condition) [right=of q0] {$\textcolor{red!90}{1\leq r\leq3}$};
         \path[->]
-        (q0) edge [loop above] node [align=center] {$r++$ \\ $a$} (q0);
+        (q0) edge [loop above] node [align=center] {$\textcolor{red!90}{r++}$ \\ $a$} (q0);
       \end{tikzpicture}
     };
-    \node [align=center] (text2) at (6,-2.5) {\textbf{Extended with Registers}\\\textbf{(CEFA)}};
+    \node [align=center] (text2) at (5,-3.25) {\textbf{Cost-Enriched Finite Automata}\\\textbf{(CEFA)}};
+    \node (a_len) at (0, -4) {
+      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$|x|:$,
+          every state/.style={inner sep=1pt, minimum size=5pt}]
+        \node[state,initial,accepting] (q0) {$q_0$};
+        \node (accepting_condition) [right=of q0] {$\textcolor{red!90}{true}$};
+        \path[->]
+        (q0) edge [loop above] node [align=center] {$\textcolor{red!90}{r++}$ \\ $\Sigma$} (q0);
+      \end{tikzpicture}
+    };
 
@@
 
-\begin{frame}{$ x\in \textcolor{red}{(\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
-  \textbf{1. Encode Counting Operators : }
+\begin{frame}{$ x\in \textcolor{red!90}{(\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
+  \textbf{1. Encode Counting Operators and Lengths by CEFAs }
   \begin{figure}
@@
 \end{frame}
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \textcolor{red}{\Sigma^*c^+} \wedge |x| > 120$}
-  \textbf{1. Basic Regex Operations : }
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \textcolor{red!90}{\Sigma^*c^+} \wedge |x| > 120$}
+  \textbf{1. Encode Counting Operators and Lengths by CEFAs }
   \begin{figure}
@@
 \end{frame}
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120$}
-  \textbf{1. The Pre-Image of String-Length :}
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red!90}{|x|} > 120$}
+  \textbf{1. Encode Counting Operators and Lengths by CEFAs}
   \begin{figure}
@@
 
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
-  \textbf{2. Production : }
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
+  \textbf{2. Compute the Product of CEFAs }
   \begin{figure}
@@
 \end{frame}
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
-  \textbf{2. Abstract the Updates of Registers as Vectors : }
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x| > 120}$}
+  \textbf{2. Compute the Product of CEFAs }
+  \begin{tikzpicture}
+    \node (product) at (0,0) {
+      \includegraphics[width=.65\linewidth]{overview_product.jpg}
+    };
+    \node (lia) at (6,0) {
+      $\textcolor{red}{r_4 > 120}$
+    };
+  \end{tikzpicture}
+\end{frame}
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x| > 120}$}
+  \textbf{2. Compute the Product of CEFAs }
+  \begin{tikzpicture}
+    \node (product) at (0,0) {
+      \includegraphics[width=.65\linewidth]{overview_product.jpg}
+    };
+    \node (lia) at (6,0) {
+      $\textcolor{red}{r_4 > 120}$
+    };
+    \node (nonempty) [scale=1.3, text=blue!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (2, 0) {The Nonemptiness of CEFA w.r.t LIA Formulas};
+  \end{tikzpicture}
+\end{frame}
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x| > 120}$}
+  \textbf{2. Compute the Product of CEFAs }
+  \begin{tikzpicture}
+    \node (product) at (0,0) {
+      \includegraphics[width=.65\linewidth]{overview_product.jpg}
+    };
+    \node (lia) at (6,0) {
+      $\textcolor{red}{r_4 > 120}$
+    };
+    \node (nonempty) [scale=1.3, text=blue!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (2, 0) {The Nonemptiness of CEFA w.r.t LIA Formulas};
+    \node (satisfy) [scale=1.3, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (2, -2) {The Satisfiability of LIA Formulas};
+    \draw [->, line width=4pt, orange!100, -triangle 90] (nonempty) -- (satisfy);
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
+  3. Reduce the Nonemptiness of CEFA w.r.t. LIA formulas to the Satisfiability of LIA Formulas: \textbf{Size-Reduction Techniques}
   \begin{figure}
-    \includegraphics[width=.65\linewidth]{overview_product_vector.jpg}
-  \end{figure}
-\end{frame}
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
-  \textbf{2. Size-Reduction of the Automaton : }
-  \begin{figure}
-    \includegraphics[width=.45\linewidth]{overview_product_vector_simplify.jpg}
+    \includegraphics[width=.55\linewidth]{overview_product_vector.jpg}
   \end{figure}
@@
 
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
-  \textbf{3. Reduce the Automaton to Parikh Images : }
-  \begin{equation}\label{eqn-LIA}
+\begin{frame}[fragile]{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
+  3. Reduce the Nonemptiness of CEFA w.r.t. LIA formulas to the Satisfiability of LIA Formulas: \textbf{Size-Reduction Techniques}
+  \begin{tikzpicture}
+    \node (B) at (0,0) {$\cB$};
+    \node (simplify) [right=of B] {\includegraphics[width=.4\linewidth]{overview_product_vector_simplify.jpg}};
+    \node [align=left, text width = .9\linewidth] (size-reduct)  [right=of simplify] {\textcolor{red!60}{\textbf{Determination \\ Minimization}}};
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
+  \textbf{3. Reduce the Nonemptiness of CEFA w.r.t. LIA formulas to the Satisfiability of LIA Formulas}
+  \begin{equation*}\label{eqn-LIA}
     \begin{array}{l}
-      \textcolor{red}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}\ \wedge \\
-      1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120.
+      \textcolor{red!90}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} \textcolor{blue!90}{ r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}}\ \wedge \\
+      \textcolor{orange!90}{1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120}.
     \end{array}
-  \end{equation}
+  \end{equation*}
   \begin{tikzpicture}
-    \node [opacity = 0] (placeholder) at (0,0) { \textbf{4. Solve the Parikh Images by the SMT Solver (Princess)} };
+    \node [opacity = 0] (placeholder) at (0,0) { \textbf{4. Solve the Parikh Images by the Off-the-Shelf SMT Solver } };
     \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,0) {1s SOLVED!!!};
@@
 \end{frame}
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
-  \textbf{3. Reduce the Automaton to Parikh Images : }
-  \begin{equation}\label{eqn-LIA}
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
+  \textbf{3. Reduce the Nonemptiness of CEFA w.r.t. LIA formulas to the Satisfiability of LIA Formulas}
+  \begin{equation*}\label{eqn-LIA}
     \begin{array}{l}
-      \textcolor{red}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}\ \wedge \\
-      1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120.
+      \textcolor{red!90}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} \textcolor{blue!90}{ r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}}\ \wedge \\
+      \textcolor{orange!90}{1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120}.
     \end{array}
-  \end{equation}
+  \end{equation*}
   \begin{tikzpicture}
-    \node (placeholder) at (0,0) { \textbf{4. Solve the Parikh Images by the SMT Solver (Princess)} };
-    \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,0) {1s SOLVED!!!};
+    \node (placeholder) at (0,0) { \textbf{4. Solve the LIA Formulas by the Off-the-Shelf SMT Solver } };
+    \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,0) {1s SOLVED!};
   \end{tikzpicture}
 \end{frame}
-\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
-  \textbf{3. Reduce the Automaton to Parikh Images : }
-  \begin{equation}\label{eqn-LIA}
+\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
+  \textbf{3. Reduce the Nonemptiness of CEFA w.r.t. LIA formulas to the Satisfiability of LIA Formulas}
+  \begin{equation*}\label{eqn-LIA}
     \begin{array}{l}
-      \textcolor{red}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}\ \wedge \\
-      1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120.
+      \textcolor{red!90}{\psi_\cB(\anivar_1, \cdots, \anivar_m)} \wedge \bigwedge \limits_{1 \le j \le 4} \textcolor{blue!90}{ r_j = \sum \limits_{1\le k \le m}  \anivar_k v_{k, j}}\ \wedge \\
+      \textcolor{orange!90}{1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60 \wedge r_4 > 120}.
     \end{array}
-  \end{equation}
+  \end{equation*}
   \begin{tikzpicture}
-    \node (placeholder) at (0,0) { \textbf{4. Solve the Parikh Images by the SMT Solver (Princess)} };
-    \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (0,0) {1s SOLVED!!!};
+    \node (placeholder) at (0,0) { \textbf{4. Solve the LIA Formulas by the Off-the-Shelf SMT Solver }  };
+    \node [rotate=45, scale=1.8, text=green!90!black, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (0,0) {1s SOLVED!};
   \end{tikzpicture}
@@
 
-\begin{frame}{The Brief of Decision Procedure}
+\begin{frame}{Decision Procedure}
   \begin{enumerate}
-    \item Encode counting operators by the automata with registers.
-    \item Product the automata and simplify them.
-    \item Convert them to parikh images.
-    \item Solve the parikh images by the SMT solver (Princess).
+    \item \textbf{Encode} Counting Operators and Length \textbf{by CEFAs}
+    \item Compute the \textbf{Product} of CEFAs
+    \item \textbf{Reduce} the Nonemptiness of CEFA w.r.t. LIA formulas \textbf{to} the \textbf{Satisfiability of LIA Formulas}
+          \begin{itemize}
+            \item \textbf{Size-Reduction Techniques}
+          \end{itemize}
+    \item \textbf{Solve the LIA Formulas} by the Off-the-Shelf SMT Solver
   \end{enumerate}
@@
     \centering
-    \resizebox{\textwidth}{!}{ % Resize the TikZ picture to fit the frame width
+    \resizebox{1\textwidth}{!}{ % Resize the TikZ picture to fit the frame width
       \begin{tikzpicture}[>=latex]
@@
         % Components
-        \node (input) [input] {Smtlib2 File};
-        \node (integer) [logic, right=3.5cm of input] {Integer Logic};
-        \node (core) [core, below=1.5cm of integer] {Core Solver};
-        \node (string) [logic, below=1.6cm of input] {String Logic};
-        \node (smtsolver) [component, right=1.5cm of integer] {SMT Solver};
-        \node (output) [output, below=1.5cm of smtsolver] {Sat/Unsat};
+        \node (input) [input] {String Constraints};
+        \node (integer) [logic, right=3.5cm of input] {LIA Formulas};
+        \node (string) [logic, below=1.6cm of input] {Regular Membership};
+        \node (core) [core, below=1.4cm of integer] {RECL Solver};
+        \node (output) [output, right=1.5cm of integer] {Sat/Unsat};
+        \node (automata) [component, below=.5cm of core] {Automata Lib \\ (Size-Reduction)};
+        \node (integer2) [logic, below=1.6cm of output] {LIA Formulas};
 
@@
         \draw [arrow] (input) -- (integer);
-        \draw [arrow] (integer) -- (core);
-        \draw [arrow] (core) to[out=60,in=-60] node[midway, right] {\textbf{Parikh Images}} (integer);
+        \draw [arrow] (integer) to node [midway] {\textbf{\ \ String Lengths}} (core);
         \draw [arrow] (input) -- (string);
-        \draw [arrow] (string) to node[midway, above] {\textbf{Encode Countings}} (core);
-        \draw [arrow] (core) to[out=-150,in=-30] node[midway, below] {Pre-Images} (string);
-        \draw [arrow] (integer) -- (smtsolver);
-        \draw [arrow] (smtsolver) -- (output);
+        \draw [arrow] (string) to node[midway, above] {\textbf{Regexes with}} (core);
+        \draw [arrow] (string) to node[midway, below] {\textbf{Countings}} (core);
+        \draw [arrow] (integer) -- (output);
+        \draw [arrow] (automata) -- (core);
+        \draw [arrow] (core) -- (automata);
+        \draw [arrow] (core) -- (integer2);
+        \draw [arrow] (integer2) -- (output);
 
@@
         \node [above=0.2cm of input] {Input};
-        \node [below=0.2cm of output] {Output};
+        \node [above=0.2cm of output] {Output};
 
@@
     \begin{itemize}
-      \item \textbf{RegCoL:} 40,628 instances that contains regexes from real-world website and is manually constructed.
-      \item \textbf{AutomatArk:}  8,215 instances that is adapted from the AutomatArk suite.
+      \item \textbf{RegCoL:} 40,628 instances that contain regexes from real-world websites and are manually constructed.
+      \item \textbf{AutomatArk:}  8,215 instances that are adapted from the AutomatArk suite.
     \end{itemize}
@@
 
-\begin{frame}{Our Technical Choises Are the Most Efficient}
+\begin{frame}{When the Counting Bounds are Large ($\geq 50$)}
+  \centering
+  \include{tables/table_large_count}
+\end{frame}
+
+\begin{frame}{Justification of Our Technical Choices}
   \centering
@@
   \begin{enumerate}
-    \item Divise an algorithm that efficiently solve string constraints with regex-counting and string-length
-    \item Propose particular size-reduction techniques for automata with registers
-    \item Carry out abundant experiments
+    \item Divise an algorithm that efficiently solves string constraints with regex-counting and string-length
+    \item Propose particular size-reduction techniquesniques for automata
+    \item Carry out extensive experiments
   \end{enumerate}
@@
     \item Symbolically encode non-register-representable counting operators, such as $(a^{\{1,3\}})^*$ and $\overline{a^{\{1,3\}}}$.
-    \item Apply this method in the analysis of real-world programs.
+    \item Apply this method in generating attack strings of ReDos attack.
   \end{enumerate}

### 2024-05-17 2024-5-13/sections/heuristic.tex
add findmodel algorithm

@@
 \subsection{Heuristic for RECL Constraints with Nested Counting}\label{heuristic:nested}
- The naive unwinding approach in the paper \cite{Denghang2023} is to unwind all inner counting operators.
+ The naive approach for nested counting in the paper \cite{Denghang2023} is to unwind all inner counting operators.
 This approach may generate a large number of states, which is linear to the product of the counting bounds in regex and exponential to the length of the regex.
@@
 But if we only unwind the outer counting operator of the regex, not inner, we obtain a CEFA containing only 2 states.
-The side effect is that we need more registers to store the information of conuting in the inner regex.
-Recall that unwinding of outer counting operator repeat the inner regex, which also repeat the registers of the inner regex.We present a heuristic to reduce the number of states generated by the unwinding process.
+The side effect is that we need two registers to store the information of conuting in the inner regex (unwinding of outer counting operator repeat the inner regex, which also repeat the registers of the inner regex).We present a heuristic to reduce the number of states generated by the unwinding process.
 The idea is to unwind the counting operator with less bound and less side effect firstly.
@@
 
-The over-approximation is to complement the CEFA of the subregex directly, without unwinding the counting operators in the subregex.
+The over-approximation is to "complement" the CEFA of the subregex directly, without unwinding the counting operators in the subregex.
 The over-approximated complementary algorithm for CEFA is as follows:
@@
 \noindent
-\emph{Step 1. (Compute the transitions times visited by the accepted strings of CEFAs).}
+\emph{Step 1. (Compute the transitions times visited by the accepted string of CEFAs).}
 
@@
 We use $\myvec{R}$ to denote the vector and use $\eta((q, a, q', \myvec{v}))$ to denote the parikh image of $\aut$.
-Then the number of times that the transition $(q, a, q', \myvec{v})$ visited by the accepted stirng is obtained from the following formula:
+Then the transitions times visited by the accepted stirng is obtained from the following formula:
 $$ \sum \limits_{(q, a, q', \myvec{v})\in \delta} \eta((q, a, q', \myvec{v}))\myvec{v} = \myvec{R}$$
@@
 \noindent
-\emph{Step 2. (Cut off the search tree early by the transitions times visited during the search process).}
+\emph{Step 2. (Prune the search tree early by the transitions times during the search process).}
 
-After computing the transitions times visited by the accepted strings, we can cut off the search tree of the CEFA.
-The idea is that we only visit the transition $(q, a, q', \myvec{v})$ if the number of times that the transition visited by the accepted string is greater than $0$.
+After computing the transitions times visited by the accepted string, we prune the search tree of the CEFA based on the transitions times.
+The idea is that we only visit transitions whose visited times are greater than $0$.
 Other transitions are deleted from the CEFA so that we can reduce the search space.
 Note that the transitions times is updated during the search process so the search space is reduced dynamically.
-The presudo code of the algorithm is as follows:
+The presudo code is presented in Algorithm \ref{alg:findword}.
+
+\begin{algorithm}
+  \caption{Find a word in the language of a CEFA}\label{alg:findword}
+  \begin{algorithmic}[1]
+  \Procedure{findmodel}{$\aut,tmap$}\Comment{$tmap$ maps transition to its visited times}
+      \State $todo \gets Stack(\aut_{init}, tmap, '''')$\Comment{todo is a stack of 3-tuple (state, tmap, word)}
+      \State $visited \gets \emptyset$\Comment{visited is a set of 2-tuple (state, tmap)}
+      \While{$todo$ is not empty}
+        \State $(q, tmap, w) \gets todo.pop()$
+        \If{$q\in \aut_{final}$ and all times of transitions in $tmap$ are $0$}
+          \State \Return $w$
+        \EndIf
+        \For{$(q, a, q', \myvec{v})\in \delta$}
+          \State $tmap'[(q, a, q', \myvec{v})] \gets tmap[(q, a, q', \myvec{v})] - 1$
+          \If{$tmap'[(q, a, q', \myvec{v})] < 0$}
+            \State \textbf{continue}\Comment{Prune}
+          \EndIf
+          \If{$(q', tmap')\in visited$}
+            \State \textbf{continue}\Comment{Prune}
+          \EndIf
+          \If{there exisits $t$ with $tmap[t]>0$ not reachable from $q'$}
+            \State \textbf{continue}\Comment{Prune}
+          \EndIf
+          \State $todo.push((q', tmap', w+a))$
+          \State $visited.add((q', tmap'))$
+        \EndFor
+      \EndWhile
+      \State \Return $\emptyset$ 
+  \EndProcedure
+  \end{algorithmic}
+  \end{algorithm}
+
+  The procedure \textsc{findmodel} takes a CEFA $\aut$ and a map $tmap$ as input.
+The map $tmap$ maps each transition to its visited times.
+Stack $todo$ is used to store the state need to be visited and its corresponding map and word.
+The procedure uses a set $visited$ to store the state and its corresponding map that have been visited.
+In the while loop from line 4 to line 23, the procedure depth-first search the CEFA.
+If the state is an accepting state and all transitions are visited with correct times, the procedure returns the word (line 7).
+During the search process, the procedure prunes the search space by the transitions times.
+If the visited times of a transition is less than $0$, the procedure does not visit it (line 11).
+If the state and its corresponding map have been visited, the procedure does not visit it (line 14).
+If there is a transition with visited times greater than $0$ not reachable from the current state, the procedure does not visit it(line 18).
+In practice, the pruning in line 18 make a great contribution to the efficiency of the search process.

### 2024-05-20 2024-5-13/sections/heuristic.tex
add some experiment results

@@
 
-\subsection{Heuristic for Finding a Accepted Word in a Cost-enriched Automaton}
+\subsection{Heuristic for Finding an Accepted Word}
 In the section \ref{sec:algorithm}, we present an algorithm to solve the $\cefadec$ problem.
@@
 Suppose that there are $n$ registers whose values are $r_1,\cdots, r_n$ respectively in the CEFA, we may visit each transition $O(r_1*r_2\cdots *r_n)$ times during the search.
-To relieve this problem, we present a heuristic to find a word in the language as following algorithm.
+To relieve this problem, we present a heuristic to find a word in the language as follows.
 
@@
 Note that the transitions times is updated during the search process so the search space is reduced dynamically.
-The presudo code is presented in Algorithm \ref{alg:findword}.
+The presudo code is presented in Algorithm~\ref{alg:findword}.
 
-\begin{algorithm}
+\begin{algorithm}[t]
   \caption{Find a word in the language of a CEFA}\label{alg:findword}

### 2024-05-20 2024-5-13/sections/implementation.tex
add some experiment results

--- 2023-10-20 2023-1-19/sections/implementation.tex
@@
 
-We implemented the algorithm in Section~\ref{sec:algorithm} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
+We implemented the algorithm in Section~\ref{sec:algorithm} and Section~\ref{sec:heuristic} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
 %
-In this section, we evaluate the performance of $\ostrichrecl$ on two benchmark suites, that is, RegCoL and AutomatArk.
-In the sequel, we first describe the two benchmark suites as well as the experiment setup.
+In this section, we evaluate the performance of $\ostrichrecl$ on three benchmark suites, that is, RegCoL, AutomatArk, and ComplexCounting.
+In the sequel, we first describe the three benchmark suites as well as the experiment setup.
 Then we present the experiment results.
-We do experiments to compare the performance of $\ostrichrecl$ with the state-of-the-art string solvers.
-Moreover, in order to know whether $\ostrichrecl$ is good at solving string constraints with large counting and length bounds, we extract 1,969 instances with large bounds out of the two benchmark suites, and compare the performance of $\ostrichrecl$ with the other solvers on these instances.
+We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}.
+We also compare $\ostrichrecl$ with two variants of it, that is, $\ostrichrecl_{\rm -ASR}$ and $\ostrichrecl_{\rm NUXMV}$, to justify the technical choices made in the decision procedure of Section~\ref{subsec:cefadec}.
+
+% We do experiments to compare the performance of $\ostrichrecl$ with the state-of-the-art string solvers.
+Moreover, in order to know whether $\ostrichrecl$ is good at solving string constraints with large counting and length, we extract \denghang{todo} instances with large bounds out of , and compare the performance of $\ostrichrecl$ with the other solvers on these instances.
 Finally, we empirically justify the technical choices made in the decision procedure of Section~\ref{subsec:cefadec} by comparing $\ostrichrecl$ with the following two variants of $\ostrichrecl$: $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$, where $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$ are obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
@@
 Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}.
-Other industrial benchmarks suites are not utilized because they contains no counting operators.
-There are 48,843 instances in total, and all benchmark instances are in the SMTLIB2 format.
-Moreover, it turns out that only 5\% of regexes among the 48,843 instances are non-register-representable (see Section~\ref{subsec:regex2cefa}).
+Other industrial benchmark suites are not utilized because they contain no counting operators.
+There are \denghang{todo} instances in total, and all benchmark instances are in the SMTLIB2 format.
 
@@
 \noindent
+\emph{ComplexCounting benchmark suite.} This benchmark suite is generated by the extension of \textsc{stringfuzz} \cite{stringfuzz}.
+We extend the \textsc{stringfuzz} tool with counting operators and generate 1,000 instances in which half of them contain complement on the counting operators and the other half contain nested counting.
+The length bound is set to $|x| > 50$ for each string variable $x$.
+
+\medskip
+\noindent
 \emph{Distribution of problem instances w.r.t. counting bounds. }
@@
 %The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
-From Fig~\ref{fig:count_distri}, we can see that while most problem instances contain only small bounds, there are still around 2,000  (about 4\%) of them using large counting bounds (i.e.
+From Fig~\ref{fig:count_distri}, we can see that while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e.
 greater than or equal to $50$).
@@
 %
-\begin{figure}[ht]
-  \centering
-  \begin{subfigure}[t]{0.49\textwidth}
+\begin{figure}
   \centering\vskip 0pt
@@
   \label{fig:count_distri}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{0.49\textwidth}
-    \centering\vskip 0pt
-      \import{tables}{table_regcol.tex}
-      \caption{Overall performance evaluation}
-    \label{fig:table_overall_eval}
-  \end{subfigure}
-  \caption{Distribution of counting bounds and performance evaluation}
 \end{figure}
@@
 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH
-\cite{CHL+19}, on RegCoL and AutomatArk benchmark suites.
+\cite{CHL+19}, on RegCoL, AutomatArk and ComplexCounting benchmark suites.
 The experiment results can be found in Figure~\ref{fig:table_overall_eval}.
@@
 Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results different from the ground truth are classified as \emph{soundness error}.
-We can see that $\ostrichrecl$ solves almost all 48,843 instances, except 182 of them, that is, it solves 48,662 instances correctly.
+We can see that $\ostrichrecl$ solves almost all \denghang{todo} instances, except 182 of them, that is, it solves 48,662 instances correctly.
 The number is 3,908/1,111/12,838/2,306/2,396 more than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
@@
 
+\begin{table}
+  \centering\vskip 0pt
+    \import{tables}{table_regcol.tex}
+    \caption{Overall performance evaluation}
+  \label{fig:table_overall_eval}
+\end{table}
 %To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.
 
-%
+% \subsection{Evaluation on problem instances with large bounds}\label{subsec:large_bounds_eval}
+% We extract \denghang{todo} problem instances with large sum of counting upper bounds (greater than or equal to $50$) from the three benchmark suites.  
+% Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $50$, that is, $|x| > 50$.
 
-\subsection{Evaluation on problem instances with large bounds}\label{subsec:large_bounds_eval}
-
-We extract 1,969 problem instances with large counting bounds (greater than or equal to $50$) from the RegCoL and AutomatArk benchmark suites.  
-Moreover, in order to test the performance of the solvers on string constraints with large length bounds as well, we increase the length bound to $200$, that is, $|x| > 200$.
-
-We evaluate the performance of $\ostrichrecl$ on the 1,969 instances. 
-The experiment results can be found in Table~\ref{tab:large-bound}.
+% We evaluate the performance of $\ostrichrecl$ on the \denghang{todo} instances. 
+% The experiment results can be found in Table~\ref{tab:large-bound}.
 We can see that $\ostrichrecl$ solves 1,873 instances correctly, which is 947/278/563/637/523 more than those solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
@@
 
-\begin{table}
-  \centering
-  \begin{subtable}{0.53\textwidth}
-      \centering
-    \import{tables}{table_large_count.tex}
-      \caption{Large bounds}
-      \label{tab:large-bound}
-  \end{subtable}
-  \begin{subtable}{0.45\textwidth}
-      \centering
-      \import{tables}{table_simp.tex}
-      \caption{Empirical justification of the technical choices in the decision procedure}
-      \label{tab:results_simp}
-  \end{subtable}
-  \caption{More experiment results, where the time limit is set as 60 seconds}
-\end{table}
+% \begin{table}[H]
+%   \import{tables}{table_large_count.tex}
+%   \caption{The performance of solvers on instances with large bounds}\label{tab:large-bound}
+% \end{table}
 
-\subsection{Empirical justification of the technical choices made in the decision procedure}\label{subsec:size_reduction_eval}
-%
+\subsection{Empirical justification of the technical choices and heuristics}\label{subsec:size_reduction_eval}
+We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}.
+Then we compare the performance of several heuristics in Section~\ref{sec:heuristic}.
+\subsubsection{Empirical justification of the technical choices}
 %We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
 %Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
-We compare $\ostrichrecl$ with $\ostrichrecl_{\rm -ASR}$ and $\ostrichrecl_{\rm NUXMV}$, to justify the technical choices made in Section~\ref{subsec:cefadec}. 
+We compare $\ostrichrecl$ with $\ostrichrecl_{\rm -ASR}$ and $\ostrichrecl_{\rm NUXMV}$, where $\ostrichrecl_{\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
+Step 2 in Section~\ref{subsec:cefadec}), and $\ostrichrecl_{\rm NUXMV}$ is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.
+
 The experiment results can be found in Table~\ref{tab:results_simp}. 
@@
 Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv.
+\begin{table}[H]
+  \import{tables}{table_simp.tex}
+  \caption{Empirical justification of the technical choices in the decision procedure}\label{tab:results_simp}
+\end{table}
+
+\subsubsection{Empirical justification of the heuristics} We compare the performance of $\ostrichrecl$ with $\ostrichrecl_{\rm -NEST}$, $\ostrichrecl_{\rm -COMP}$, $\ostrichrecl_{\rm -FIND}$, and $\ostrichrecl_{\rm -ALL}$ where $\ostrichrecl_{\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting, $\ostrichrecl_{\rm -COMP}$ is obtained from $\ostrichrecl$ by removing the heuristic for complement on counting operators, $\ostrichrecl_{\rm -FIND}$ is obtained from $\ostrichrecl$ by removing the heuristic for finding the accepted word of the automaton, and $\ostrichrecl_{\rm -ALL}$ is obtained from $\ostrichrecl$ by removing all the heuristics.
+The experiment results can be found in Table~\ref{tab:results_heuristic}.
+
+\begin{table}
+  \import{tables}{table_heuristics.tex}
+  \caption{Empirical justification of the heuristics}\label{tab:results_heuristic}
+\end{table}
 

### 2024-05-26 2024-5-13/sections/implementation.tex
add data

@@
 
-\subsubsection{Empirical justification of the heuristics} We compare the performance of $\ostrichrecl$ with $\ostrichrecl_{\rm -NEST}$, $\ostrichrecl_{\rm -COMP}$, $\ostrichrecl_{\rm -FIND}$, and $\ostrichrecl_{\rm -ALL}$ where $\ostrichrecl_{\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting, $\ostrichrecl_{\rm -COMP}$ is obtained from $\ostrichrecl$ by removing the heuristic for complement on counting operators, $\ostrichrecl_{\rm -FIND}$ is obtained from $\ostrichrecl$ by removing the heuristic for finding the accepted word of the automaton, and $\ostrichrecl_{\rm -ALL}$ is obtained from $\ostrichrecl$ by removing all the heuristics.
+\subsubsection{Empirical justification of the heuristics} We compare the performance of $\ostrichrecl$ with ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$, and ${\rm -ALL}$ where ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting, ${\rm -COMP}$ is obtained from $\ostrichrecl$ by removing the heuristic for complement on counting operators, ${\rm -FIND}$ is obtained from $\ostrichrecl$ by removing the heuristic for finding the accepted word of the automaton, and ${\rm -ALL}$ is obtained from $\ostrichrecl$ by removing all the heuristics.
 The experiment results can be found in Table~\ref{tab:results_heuristic}.

### 2024-05-28 2024-5-13/sections/heuristic.tex
add data
change the score of intersection from min to multiply
rewrite the algorithm of findmodel heuristic

@@
   \item If $\regex = \regex_1^*$, then $size(\regex) = size(\regex_1)$.
-  \item If $\regex = \regex_1 \cap \regex_2$, then $size(\regex) = min(size(\regex_1), size(\regex_2))$.
+  \item If $\regex = \regex_1 \cap \regex_2$, then $size(\regex) = size(\regex_1)*size(\regex_2)$.
   \item If $\regex = \overline{\regex_1}$, then $size(\regex) = 2^{size(\regex_1)} + 1$.
@@
 After computing the transitions times visited by the accepted string, we prune the search tree of the CEFA based on the transitions times.
-The idea is that we only visit transitions whose visited times are greater than $0$.
-Other transitions are deleted from the CEFA so that we can reduce the search space.
-Note that the transitions times is updated during the search process so the search space is reduced dynamically.
-The presudo code is presented in Algorithm~\ref{alg:findword}.
+The idea is that we only visit the state which is able to reach all transitions need to be visited.
+Other states are deleted from the CEFA so that we can reduce the search space.
+Note that the transitions times is updated during the search process so the search space is reduced dynamically. The presudo code is presented in Algorithm~\ref{alg:findword}.
 
-\begin{algorithm}[t]
+\begin{algorithm}[H]
   \caption{Find a word in the language of a CEFA}\label{alg:findword}
   \begin{algorithmic}[1]
-  \Procedure{findmodel}{$\aut,tmap$}\Comment{$tmap$ maps transition to its visited times}
-      \State $todo \gets Stack(\aut_{init}, tmap, '''')$\Comment{todo is a stack of 3-tuple (state, tmap, word)}
-      \State $visited \gets \emptyset$\Comment{visited is a set of 2-tuple (state, tmap)}
+  \Procedure{findmodel}{$\aut,tmap$}
+  % \State \Comment{$tmap$ maps transition to its remaining visited times}
+      \State $todo \gets Stack(\aut_{init}, tmap, '''')$
+      \State $visited \gets \emptyset$
+      % \State \Comment{a stack of state, remaining visited times and word}
       \While{$todo$ is not empty}
         \State $(q, tmap, w) \gets todo.pop()$
-        \If{$q\in \aut_{final}$ and all times of transitions in $tmap$ are $0$}
+        \If{$q\in \aut_{final}$ and $tmap.values = \myvec{0}$}
           \State \Return $w$
         \EndIf
-        \For{$(q, a, q', \myvec{v})\in \delta$}
+
+        \For{each transition $(q, a, q', \myvec{v})$ where $tmap[(q, a, q', \myvec{v})]>0$}
           \State $tmap'[(q, a, q', \myvec{v})] \gets tmap[(q, a, q', \myvec{v})] - 1$
-          \If{$tmap'[(q, a, q', \myvec{v})] < 0$}
-            \State \textbf{continue}\Comment{Prune}
+          \If{$(q', tmap')\not\in visited$ \textbf{and} \textsc{isReachable}($\aut, q', tmap'$)}
+            \State $todo.push((q', tmap', w\cdot a))$
+            \State $visited.add((q', tmap'))$
           \EndIf
-          \If{$(q', tmap')\in visited$}
-            \State \textbf{continue}\Comment{Prune}
-          \EndIf
-          \If{there exisits $t$ with $tmap[t]>0$ not reachable from $q'$}
-            \State \textbf{continue}\Comment{Prune}
-          \EndIf
-          \State $todo.push((q', tmap', w+a))$
-          \State $visited.add((q', tmap'))$
         \EndFor
@@
 
-  The procedure \textsc{findmodel} takes a CEFA $\aut$ and a map $tmap$ as input.
-The map $tmap$ maps each transition to its visited times.
-Stack $todo$ is used to store the state need to be visited and its corresponding map and word.
-The procedure uses a set $visited$ to store the state and its corresponding map that have been visited.
-In the while loop from line 4 to line 23, the procedure depth-first search the CEFA.
-If the state is an accepting state and all transitions are visited with correct times, the procedure returns the word (line 7).
-During the search process, the procedure prunes the search space by the transitions times.
-If the visited times of a transition is less than $0$, the procedure does not visit it (line 11).
-If the state and its corresponding map have been visited, the procedure does not visit it (line 14).
-If there is a transition with visited times greater than $0$ not reachable from the current state, the procedure does not visit it(line 18).
-In practice, the pruning in line 18 make a great contribution to the efficiency of the search process.
+  The procedure \textsc{findmodel} takes a CEFA $\aut$ and a transitions-times map $tmap$ as input.
+$tmap$ maps each transition to its remaining visited times.
+Stack $todo$ contains states need to be visited, their corresponding transitions-times maps and current word.
+Set $visited$ is used to store the visited state with corresponding map.
+$todo$ is initialized with the initial state of the CEFA, the input map $tmap$ and an empty word (line 2).
+$visited$ is initialized as an empty set (line 3).
+  In the while loop from line 4 to line 16, the state combined with its transitions-times map is searched by the depth-first search algorithm.
+During the search process, the procedure returns the word if the state is an accepting state and all remaining times of transitions are $0$ (line 7).
+For each transition $(q, a, q', \myvec{v})$ whose remaining times are greater than $0$, the procedure decreases the remaining times by $1$ (line 10) and checks whether $(q', tmap')$ is not visited and $tmap'$ is reachable from $q'$ (line 11).
+We say that \textit{$tmap'$ is reachable from $q'$} if each transition $t$ with $tmap'(t)> 0$ are reachable from the state $q'$.
+The reachability check (Algorithm~\ref{alg:isReachable}) is vital to prune the search space and reduce the search time .
+If the state $q'$ is not visited and $tmap'$ is reachable from $q'$, then we push $(q', tmap', w\cdot a)$ to $todo$ and add $(q', tmap')$ to $visited$ to continue the search(line 12-13).
+If the while loop terminates without finding an accepting word, the procedure returns $\emptyset$ (line 17).
+
+  \begin{algorithm}[H]
+    \caption{Check whether the map is reachable from the state}\label{alg:isReachable}
+    \begin{algorithmic}[1]
+      \Procedure{isReachable}{$\aut, q, tmap$}
+      \State $todo \gets Stack(q)$
+      \State $visited \gets \emptyset$
+      \State $qreach \gets \emptyset$
+      \While{$todo$ is not empty}
+        \State $q \gets todo.pop()$
+        \State $visited.add(q)$
+        \For{each transition $t=(q,a,q',\myvec{v})$ where $tmap(t)>0$}
+          \State $qreach.add(t)$
+          \If{$q'\not\in visited$}
+            \State $todo.push(q')$
+          \EndIf
+        \EndFor
+      \EndWhile
+      \State Select all transitions $t$ where $tmap(t)>0$ to set $T$
+      \If{$T\subseteq qreach$}
+        \State \Return \textit{true}  
+      \Else 
+        \State \Return \textit{false}
+      \EndIf
+      \EndProcedure
+    \end{algorithmic}
+  \end{algorithm}
+
+  In Algorithm~\ref{alg:isReachable}, all transitions reachable from the state $q'$ is computed and saved to $qreach$.
+If $qreach$ covers all transitions with positive times in the input map $tmap$, then we say that $tmap$ is reachable from $q'$ and the procedure \textsc{isReachable} returns true, otherwise it returns false.

### 2024-05-28 2024-5-13/sections/heuristic.tex
change vector to constant in overapprox heuristic

@@
   \begin{itemize}
-    \item $\{(q, a, q',(\vec{v}, \vec{0})) \mid (q, a, q', \vec{v})\in \delta\}$
-    \item $\{(q, a, s,(\vec{0}, \vec{0})) \mid \forall q'\in Q,\vec{v}. (q, a, q', \vec{v})\not\in \delta\}$
-    \item $\{(q, a, f,(\vec{v}, \vec{1})) \mid \exists q'\in F, (q, a, q', \vec{v})\in \delta\}$
-    \item $\{(s, \Sigma, s, (\vec{0}, \vec{0}))\}$
+    \item $\{(q, a, q',(\vec{v}, 0)) \mid (q, a, q', \vec{v})\in \delta\}$
+    \item $\{(q, a, s,(\vec{0}, 0)) \mid \forall q'\in Q,\vec{v}. (q, a, q', \vec{v})\not\in \delta\}$
+    \item $\{(q, a, f,(\vec{v}, 1)) \mid \exists q'\in F, (q, a, q', \vec{v})\in \delta\}$
+    \item $\{(s, \Sigma, s, (\vec{0}, 0))\}$
   \end{itemize}
@@
 $f$ is the merged accepted state of original CEFA.
-If there is a transition $(q, a, q', \vec{v})$ teminates at the accepted state $q'$ in the original CEFA, we add a corresponding transition $(q, a, f, (\vec{v}, \vec{1}))$ in the over-approximated complement.
+If there is a transition $(q, a, q', \vec{v})$ teminates at the accepted state $q'$ in the original CEFA, we add a corresponding transition $(q, a, f, (\vec{v}, 1))$ in the over-approximated complement.
 From the definition of $\delta'$, we can see that only the transitions goto $f$ increase the value of regesiter $r$.

### 2024-05-29 2024-5-13/crv/sections/abstract.tex
add experiment results and explanation

--- 2023-08-30 2023-1-19/sections/abstract.tex
@@
 As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which the off-the-shelf SMT solvers can then solve.
-To improve the performance further, we propose simplification techniques to reduce automata sizes. We implement the algorithms and validate our approach on 48,843 benchmark instances. 
+To improve the performance further, we also propose techniques to reduce the sizes of automata. We implement the algorithms and validate our approach on 49,843 benchmark instances. 
 The experimental results show that our approach can solve more instances than the state-of-the-art solvers, at a comparable or faster speed, especially when the counting and length bounds are large.
-
-%\keywords{Rgular Expressions, Counting, Length, Automata, Registers, Linear Integer Arithmetic}
-%\end{document}

### 2024-05-29 2024-5-13/sections/implementation.tex
add experiment results and explanation

@@
 We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}.
-We also compare $\ostrichrecl$ with two variants of it, that is, $\ostrichrecl_{\rm -ASR}$ and $\ostrichrecl_{\rm NUXMV}$, to justify the technical choices made in the decision procedure of Section~\ref{subsec:cefadec}.
+We also compare $\ostrichrecl$ with several variants of it, to justify the technical choices and heuristics we take in the Section~\ref{subsec:cefadec} and Section~\ref{sec:heuristic}.
 
@@
 Other industrial benchmark suites are not utilized because they contain no counting operators.
-There are \denghang{todo} instances in total, and all benchmark instances are in the SMTLIB2 format.
+There are 49,843 instances in total, where 48,843 of them are collected from the real world and 1,000 of them are generated by fuzzing tool.
+All benchmark instances are in the SMTLIB2 format.
 
@@
 The distribution of problem instances w.r.t.
-the counting bounds in RegCoL and AutomatArk suites is shown in Fig~\ref{fig:count_distri}, where the $x$-axis represents the counting bound and the $y$-axis represents the number of problem instances whose maximum counting bound is equal to the value of the $x$-axis.
+the counting bounds in the three suites is shown in Fig~\ref{fig:count_distri}, where the $x$-axis represents the counting bound and the $y$-axis represents the number of problem instances containing the counting bound.
 %The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
@@
 Note that we take the results of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
-Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results different from the ground truth are classified as \emph{soundness error}.
-We can see that $\ostrichrecl$ solves almost all \denghang{todo} instances, except 182 of them, that is, it solves 48,662 instances correctly.
-The number is 3,908/1,111/12,838/2,306/2,396 more than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
+Nevertheless, on some problem instances, all the results of the three solvers in the Z3 family are wrong (after manual inspection), thus failing this approach on these instances.}, and the results different from the ground truth are classified as \emph{error}.
+We can see that $\ostrichrecl$ solves almost all instances, except 182 of them, that is, it solves 49,638 instances correctly.
+The number is 4,547/1,917/13,618/2,764/3,134 more than the number of instances solved by CVC5/Z3str3RE/Z3str3/Z3seq/OSTRICH respectively.
 %
-Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (1.93s versus 1.62s).
+Moreover, $\ostrichrecl$ is the second fastest solver, whose average time on each instance is close to the fastest solver Z3str3RE (2.88s versus 1.99s).
 
@@
 \subsection{Empirical justification of the technical choices and heuristics}\label{subsec:size_reduction_eval}
-We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}.
-Then we compare the performance of several heuristics in Section~\ref{sec:heuristic}.
+We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 of Section~\ref{subsec:cefadec}.
+We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}.
+Finally, we carry out experiment on the ComplexCounting benchmarks to justify the heuristics of Section~\ref{sec:heuristic}.
 \subsubsection{Empirical justification of the technical choices}
@@
 %Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
-We compare $\ostrichrecl$ with $\ostrichrecl_{\rm -ASR}$ and $\ostrichrecl_{\rm NUXMV}$, where $\ostrichrecl_{\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
-Step 2 in Section~\ref{subsec:cefadec}), and $\ostrichrecl_{\rm NUXMV}$ is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.
+We compare $\ostrichrecl$ with its variants ${\rm -ASR}$ and ${\rm +NUXMV}$.
+${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
+Step 2 of Section~\ref{subsec:cefadec}).
+${\rm +NUXMV}$ uses the nuXmv model checker to solve the nonemptiness of $\cefadec$.
 
-The experiment results can be found in Table~\ref{tab:results_simp}. 
-We can see that $\ostrichrecl$ solves 1,503 more instances and is 2.21 times faster than $\ostrichrecl_{\rm -ASR}$.
+The experiment results can be found in Table~\ref{tab:results_heuristic}.
+We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$.
 Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.
-%To answer \textbf{Q2}, \textbf{the size-reduction techniques indeed play a vital role in the performance improvement}. 
-Moreover, $\ostrichrecl$ solves 1,798 more instances and is 3.13 times faster than $\ostrichrecl_{\rm NUXMV}$.
+We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$.
 Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv.
-\begin{table}[H]
-  \import{tables}{table_simp.tex}
-  \caption{Empirical justification of the technical choices in the decision procedure}\label{tab:results_simp}
+\begin{table}
+  \import{tables}{table_heuristics.tex}
+  \caption{Empirical justification of the technical choices and heuristics}\label{tab:results_heuristic}
 \end{table}
 
-\subsubsection{Empirical justification of the heuristics} We compare the performance of $\ostrichrecl$ with ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$, and ${\rm -ALL}$ where ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting, ${\rm -COMP}$ is obtained from $\ostrichrecl$ by removing the heuristic for complement on counting operators, ${\rm -FIND}$ is obtained from $\ostrichrecl$ by removing the heuristic for finding the accepted word of the automaton, and ${\rm -ALL}$ is obtained from $\ostrichrecl$ by removing all the heuristics.
-The experiment results can be found in Table~\ref{tab:results_heuristic}.
+\subsubsection{Empirical justification of the heuristics} 
+We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$.
+${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting.
+${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators.
+${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.
+
+The overall experiment results can be found in Table~\ref{tab:results_heuristic}.
+We can see that $\ostrichrecl$ solves 77/388/349 more instances and is 1.13/1.18/1.24 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
+
+The ComplexCounting benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}.
+We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
+
+From the results, the heuristic for complement on counting operators and the heuristic for finding the accepted word of the automaton are more effective than the heuristic for nested counting.
+Futhermore, the heuristic for complement on counting operators contributes both to satisfiable and unsatisfiable instances, while the heuristic for finding the accepted word and the heuristic for nested counting contribute only to satisfiable instances.
+All the heuristics improve the performance of $\ostrichrecl$.
 
 \begin{table}
-  \import{tables}{table_heuristics.tex}
-  \caption{Empirical justification of the heuristics}\label{tab:results_heuristic}
+  \import{tables}{table_heuristics_complex.tex}
+  \caption{Empirical justification of the heuristics on ComplexCounting benchmarks}\label{tab:results_heuristic_complex}
 \end{table}

### 2024-05-30 2024-5-13/sections/introduction.tex
add some comments

@@
 \begin{itemize}
-  \item We propose an automata-theoretical approach for solving RECL constraints. 
+  \item We propose an automata-theoretical approach for solving RECL constraints. \zhilin{update this paragraph later}
   Our main idea is to represent the counting operators by cost registers in cost-enriched finite automata (CEFA, see Section~\ref{sec:automaton} for the definition), instead of unfolding them explicitly.

### 2024-05-30 2024-5-13/sections/implementation.tex
change experiments

@@
 \subsection{Empirical justification of the technical choices and heuristics}\label{subsec:size_reduction_eval}
-We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 of Section~\ref{subsec:cefadec}.
+We also do experiments to evaluate the effectiveness of the automata size-reduction techniques for register-representable regexes, that is, Step 2 of Section~\ref{subsec:cefadec}.
 We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}.
-Finally, we carry out experiment on the ComplexCounting benchmarks to justify the heuristics of Section~\ref{sec:heuristic}.
+Finally, we carry out experiment on the ComplexCounting benchmarks to justify the heuristics of Section~\ref{sec:heuristic} for non-register-representable regexes.
 \subsubsection{Empirical justification of the technical choices}
@@
 %Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
-We compare $\ostrichrecl$ with its variants ${\rm -ASR}$ and ${\rm +NUXMV}$.
-${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
-Step 2 of Section~\ref{subsec:cefadec}).
-${\rm +NUXMV}$ uses the nuXmv model checker to solve the nonemptiness of $\cefadec$.
+We compare $\ostrichrecl$ with its variant  ${\rm +NUXMV}$. ${\rm +NUXMV}$  is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.
 
 The experiment results can be found in Table~\ref{tab:results_heuristic}.
-We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$.
-Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.
 We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$.
@@
 
-\subsubsection{Empirical justification of the heuristics} 
+\subsubsection{Empirical justification of the size-reduction technique for register-representable regexes}
+We compare $\ostrichrecl$ with its variant ${\rm -ASR}$.  ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). 
+The experiment results can be found in Table~\ref{tab:results_heuristic}.
+We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$.
+Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.
+
+\subsubsection{Empirical justification of the heuristics for non-regesiter-representable regexes} 
 We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$.

### 2024-05-30 2024-5-13/sections/heuristic.tex
change experiments
optimization for nested counting

@@
-In the previous paper \cite{Denghang2023}, we naively unwind the counting operators when they are in other counting or complement operator.
-However, this approach is not efficient when the counting bounds are large.
-In this section, we present some heuristics to solve the RECL constraints more efficiently.
+%!TEX root = ../main.tex
 
-\subsection{Heuristic for RECL Constraints with Nested Counting}\label{heuristic:nested}
+In Section~\ref{sec:algorithm}, to deal with the non-register-representable RECL constraints, we unfold all the non-register-representable occurrences of counting operators. Nevertheless, 
+the naive unfolding incurs an exponential blow-up over the formula sizes, especially when the counting bounds are large. 
+Recall that an occurrence of counting operators is said to be non-register-representable if it is in the scope of some Kleene star, another counting operator, complement, or language difference.
+Since Kleene star can be seen as a special case of the counting operators, and language difference $e_1 \setminus e_2$ can be rewritten as $e_1 \cap \overline{e_2}$, without loss of generality, we can assume that a non-register representable occurrence of a  counting operator is in the scope of another counting operator or some complement operator.
+In the sequel, to alleviate the formula-size blow-up problem resulted from the naive unfolding, we present various optimizations, for the nesting of counting operators and the nesting of a counting operator and a complement operator respectively.
+% two situations that a counting operator is in the scope of another counting operator and in the scope of a complement operator respectively.
+
+\subsection{Optimizations for the nesting of counting operators}\label{heuristic:nested}
+
+In the sequel, we propose an optimization for the nesting of counting operators. 
+The optimization is designed for the special case that the nesting depth of counting operators is one.
+For a RECL constraint whose nesting depth of counting operators is greater than two, we can apply the optimization for the inner-most nesting of counting operators and decrement the nesting depth, then apply the optimization again to the resulting constraint, and continue this process, until obtaining a register-representable RECL constraint.
+
+The main idea of the optimization is illustrated by the constraint $x \in (a^{\{1,1000\}})^{\{1,2\}}$.
+If we apply the naive unfolding in Section~\ref{sec:algorithm}, we will unfold  $a^{\{1,1000\}}$ and obtain the constraint $x \in (a(\varepsilon + a + aa + \cdots + \underbrace{a\cdots a}_{999}))^{\{1,2\}}$.
+It is easy to observe that a smarter way is to unfold  $^{\{1,2\}}$, instead of $^{\{1, 1000\}}$.
+If we do this, then we get a constraint $x \in (a^{\{1,1000\}})(\varepsilon + a^{\{1,1000\}})$, whose size is much smaller, compared to $x \in (a(\varepsilon + a + aa + \cdots + \underbrace{a\cdots a}_{999}))^{\{1,2\}}$.
+(Recall that we assume a binary encoding of the integer constants in counting operators.)
+
+Let us describe the optimization more precisely.
+For a regular expression $x \in (e_1)^{\{m,n\}}$ where $e_1$ contains counting operators (but does not contain the nesting of counting operators), we can unfold the counting operators in the following ways to obtain a register-representable RECL constraint, (i) unfold the counting operators in $e_1$, (ii) unfold the counting operator $^{\{m,n\}}$.
+Let $e', e''$ denote the resulting constraints.
+We estimate the sizes of the two CEFAs constructed from $e', e''$ respectively, say $N'$ and $N''$.
+If $N' \le N''$, then we choose to unfold the counting operators in $e_1$.
+Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$.
+Note that when we estimate the sizes of the CEFAs, we do not really need unfold the counting operators.
+We can simply compute the estimations of the CEFA sizes, without any unfolding.
+
+\zhilin{stopped here}
+
+In the sequel, we show how we estimate the sizes of CEFAs of the register-representable
+
 The naive approach for nested counting in the paper \cite{Denghang2023} is to unwind all inner counting operators.
@@
 
-\subsection{Heuristic for RECL Constraints with Complement on Counting}
+\subsection{Optimizations for the nesting of a counting operator and a complement operator}
 As we mentioned in the above section \ref{heuristic:nested}, the unwinding process of the complement operator is exponential to the counting bounds in the worst case.

### 2024-05-30 2024-5-13/sections/introduction.tex
optimization for nested counting

@@
 \noindent
-\emph{Organization.} 
+\emph{Structure.} 
 The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper. Section~\ref{sec:pre} introduces the preliminaries. 
 Section~\ref{sec:recl} presents the syntax and semantics of RECL. 
-Section~\ref{sec:automaton} defines CEFA.
-Section~\ref{sec:algorithm} introduces the algorithm to solve RECL constraints.
-Section~\ref{sec:implementation} shows the experiment results.
-Section~\ref{sec:conclu} concludes this paper.
+Section~\ref{sec:automaton} defines CEFA. Section~\ref{sec:algorithm} introduces the algorithm to solve RECL constraints. 
+Section~\ref{sec:heuristic} presents some heuristics for improving the performance of solving RECL constraints where the counting operators are inside the scope of some other counting operators or complement operators.
+\zhilin{double check later}
+Section~\ref{sec:implementation} shows the experiment results. Section~\ref{sec:conclu} concludes this paper.
+
+A preliminary version of this paper has appeared in the proceedings of SETTA 2023~\cite{Denghang2023}.
+This paper extends the SETTA paper in the following two aspects: (i) To improve the performance of complex RECL constraints where the counting operators are nested with some other counting operators or nested with the complement operators, various heuristics are proposed, (ii) moreover, to evaluate the performance of these heuristics, the benchmarks as well as the experiments are extended.
+\zhilin{double check later}

### 2024-05-31 2024-5-13/sections/heuristic.tex
optimizations

@@
 Let us describe the optimization more precisely. 
-For a regular expression $x \in (e_1)^{\{m,n\}}$ where $e_1$ contains counting operators (but does not contain the nesting of counting operators), we can unfold the counting operators in the following ways to obtain a register-representable RECL constraint, (i) unfold the counting operators in $e_1$, (ii) unfold the counting operator $^{\{m,n\}}$.
+\begin{itemize}
+\item For a regular expression $x \in (e_1)^{\{m,n\}}$ where $e_1$ contains counting operators (but does not contain the nesting of counting operators), we can unfold the counting operators in the following ways to obtain a register-representable RECL constraint: (i) unfold the counting operators in $e_1$, (ii) unfold the counting operator $^{\{m,n\}}$.
+%
 Let $e', e''$ denote the resulting constraints.
-We estimate the sizes of the two CEFAs constructed from $e', e''$ respectively, say $N'$ and $N''$.
-If $N' \le N''$, then we choose to unfold the counting operators in $e_1$.
-Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$.
-Note that when we estimate the sizes of the CEFAs, we do not really need unfold the counting operators.
-We can simply compute the estimations of the CEFA sizes, without any unfolding.
+
+\item We estimate the sizes of the two CEFAs $\aut', \aut''$ constructed from $e', e''$ respectively as pairs $(s', r')$ and $(s'', r'')$, where $s'$ and $r'$ are the estimates of the number of states and registers in $\aut'$, similarly for $s''$ and $r''$.
+%
+\item From the construction in Section~\ref{sec:algorithm}, 
+two NFAs $\cU_{\aut'}, \cU_{\aut''}$ are constructed from $\aut', \aut''$ by dropping the accepting conditions and ignoring the characters.
+As a result, the alphabets of $\cU_{\aut'}, \cU_{\aut''}$ are the set of integer vectors  $\myvec{v}$ occurring in the transitions of $\aut', \aut''$ respectively.
+The integer vectors of  $\aut'$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.
+Consequently, the size of the alphabet of $\cU_{\aut'}$ is bounded by $r'$.
+Similarly for $\cU_{\aut''}$.
+Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut'}, \cU_{\aut''}$ as $sz' = (s')^2 r'$ and $sz''= (s'')^2 r''$ respectively.
+%
+\item If $sz' \le sz''$, then we choose to unfold the counting operators in $e_1$. Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$. 
+\end{itemize}
+
+In the sequel, we show how we estimate the sizes of CEFAs constructed from register-representable regular expressions.
+
+Let $\regex$ be a register-representable regular expression.
+Then we compute $(s_\regex, r_\regex) \in \Nat \times \Nat$, i.e.
+the pair (estimate of the number of states, estimate of the number of registers), as follows.
+\begin{itemize}
+  \item If $\regex = \emptyset$ or $\regex = \epsilon$, then $s_{\regex} = 0$ and $r_\regex = 0$. 
+  \item If $\regex = \regex_1 \concat \regex_2$, then $s_{\regex} = s_{\regex_1} + s_{\regex_2}$ and $r_{\regex} = r_{\regex_1} + r_{\regex_2}$.
+  \item If $\regex = \regex_1 + \regex_2$, then $s_{\regex} = s_{\regex_1} + s_{\regex_2}$ and $r_{\regex} = r_{\regex_1} + r_{\regex_2}+1$. 
+  \item If $\regex = \regex_1 \cap \regex_2$, then $size(\regex) = size(\regex_1)*size(\regex_2)$ and $r_{\regex} = r_{\regex_1} + r_{\regex_2}$.
+  \item If $\regex = \overline{\regex_1}$, then $s_\regex = 2^{s_{\regex_1}}$ (since the determinization is needed for the complement) and $r_\regex = 0$.
+  \item If $\regex = \regex_1^*$, then $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 0$.
+%  \item $\regex = \regex_1 \backslash \regex_2$ can be transferred to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the size can be computed by the formula of $\cap$ and $\bar{}$.
+  \item For $\regex = \regex_1^{\{m, n\}}$ or $\regex = \regex_1^{\{n,\infty\}}$, $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 1$.
+\end{itemize}
 
@@
 
-In the sequel, we show how we estimate the sizes of CEFAs of the register-representable
-
-The naive approach for nested counting in the paper \cite{Denghang2023} is to unwind all inner counting operators.
+%The naive approach for nested counting in the paper \cite{Denghang2023} is to unwind all inner counting operators.
 This approach may generate a large number of states, which is linear to the product of the counting bounds in regex and exponential to the length of the regex.
@@
 We have used a naive approach which randomly searching the CEFAs by the depth-first search, based on the regesiters values obtained from solving the existential LIA formula.
-However, this approach is not efficient.
+However, this approach is not efficient when the regexes is non-regesiter-representable.
 Suppose that there are $n$ registers whose values are $r_1,\cdots, r_n$ respectively in the CEFA, we may visit each transition $O(r_1*r_2\cdots *r_n)$ times during the search.

### 2024-05-31 2024-5-13/sections/heuristic.tex
section 7.1

@@
 \begin{itemize}
-\item For a regular expression $x \in (e_1)^{\{m,n\}}$ where $e_1$ contains counting operators (but does not contain the nesting of counting operators), we can unfold the counting operators in the following ways to obtain a register-representable RECL constraint: (i) unfold the counting operators in $e_1$, (ii) unfold the counting operator $^{\{m,n\}}$.
+\item For a regular expression $e = (e_1)^{\{m,n\}}$ where $e_1$ is a register-representable regular expression, we can unfold the counting operators in the following ways to obtain a register-representable RECL constraint: (i) unfold the counting operators in $e_1$, (ii) unfold the counting operator $^{\{m,n\}}$.
 %
-Let $e', e''$ denote the resulting constraints.
+Let $\ufld_1(e)$ and $\ufld_2(e)$ denote the resulting regular expressions.
 
-\item We estimate the sizes of the two CEFAs $\aut', \aut''$ constructed from $e', e''$ respectively as pairs $(s', r')$ and $(s'', r'')$, where $s'$ and $r'$ are the estimates of the number of states and registers in $\aut'$, similarly for $s''$ and $r''$.
+\item We estimate the sizes of the two CEFAs $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ constructed from $\ufld_1(e), \ufld_2(e)$ respectively as pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$, where $\snum_1(e)$ and $\rnum_1(e)$ are the estimates of the number of states and registers in $\aut_{\ufld_1(e)}$, similarly for $(\snum_2(e)$ and $\rnum_2(e))$.
 %
 \item From the construction in Section~\ref{sec:algorithm}, 
-two NFAs $\cU_{\aut'}, \cU_{\aut''}$ are constructed from $\aut', \aut''$ by dropping the accepting conditions and ignoring the characters.
-As a result, the alphabets of $\cU_{\aut'}, \cU_{\aut''}$ are the set of integer vectors  $\myvec{v}$ occurring in the transitions of $\aut', \aut''$ respectively.
-The integer vectors of  $\aut'$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.
-Consequently, the size of the alphabet of $\cU_{\aut'}$ is bounded by $r'$.
-Similarly for $\cU_{\aut''}$.
-Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut'}, \cU_{\aut''}$ as $sz' = (s')^2 r'$ and $sz''= (s'')^2 r''$ respectively.
+two NFAs $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignoring the characters.
+As a result, the alphabets of $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors  $\myvec{v}$ occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively.
+The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.
+Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
+Similarly for $\cU_{\aut_{\ufld_1(e)}}$.
+Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut_{\ufld_1(e)}}, \cU_{\aut_{\ufld_2(e)}}$ as $sz_1 = (\snum_1(e))^2 \cdot \rnum_1(e)$ and $sz_2 = (\snum_2(e))^2 \cdot \rnum_2(e)$ respectively.
 %
-\item If $sz' \le sz''$, then we choose to unfold the counting operators in $e_1$. Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$. 
+\item If $sz_1 \le sz_2$, then we choose to unfold the counting operators in $e_1$. Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$. 
 \end{itemize}
 
-In the sequel, we show how we estimate the sizes of CEFAs constructed from register-representable regular expressions.
+%In the sequel, we show how we estimate the sizes of CEFAs constructed from register-representable regular expressions.
 
-Let $\regex$ be a register-representable regular expression.
-Then we compute $(s_\regex, r_\regex) \in \Nat \times \Nat$, i.e.
-the pair (estimate of the number of states, estimate of the number of registers), as follows.
+It remains to show how to compute the pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$ from $e=(e_1)^{\{m,n\}}$.
+Let $e=(e_1)^{\{m,n\}}$ be a regular expression where $e_1$ is a register-representable regular expression.
+Then we compute $\snum'_1(e_1)$ and $(\snum'_2(e_1), \rnum'_2(e_1))$ by a structural induction on $e_1$.
+Finally, let $(\snum_1(e), \rnum_1(e)) = (\snum'_1(e_1), 1)$ and $(\snum_2(e), \rnum_2(e)) = (\snum'_2(e_1), \rnum'_2(e_1))$.
 \begin{itemize}
-  \item If $\regex = \emptyset$ or $\regex = \epsilon$, then $s_{\regex} = 0$ and $r_\regex = 0$. 
-  \item If $\regex = \regex_1 \concat \regex_2$, then $s_{\regex} = s_{\regex_1} + s_{\regex_2}$ and $r_{\regex} = r_{\regex_1} + r_{\regex_2}$.
-  \item If $\regex = \regex_1 + \regex_2$, then $s_{\regex} = s_{\regex_1} + s_{\regex_2}$ and $r_{\regex} = r_{\regex_1} + r_{\regex_2}+1$. 
-  \item If $\regex = \regex_1 \cap \regex_2$, then $size(\regex) = size(\regex_1)*size(\regex_2)$ and $r_{\regex} = r_{\regex_1} + r_{\regex_2}$.
-  \item If $\regex = \overline{\regex_1}$, then $s_\regex = 2^{s_{\regex_1}}$ (since the determinization is needed for the complement) and $r_\regex = 0$.
-  \item If $\regex = \regex_1^*$, then $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 0$.
+  \item If $e_1 = \emptyset$ or $e_1 = \epsilon$, then $\snum'_1(e_1)  = 0$ and $(\snum'_2(e_1), \rnum'_2(e_1))  = (0, 0)$. 
+%
+ %
+  \item If $e_1 = e_2 \concat e_3$, then $\snum'_1(e_1) = \snum'_1(e_2) + \snum'_1(e_3)$ and 
+%
+  $$
+  \begin{array}{l }
+  (\snum'_2(e_1), \rnum'_2(e_1)) =  \\
+  \ \ \ \ (n(\snum'_2(e_2) + \snum'_2(e_3)), n(\rnum'_2(e_2) + \rnum'_2(e_3))).
+ \end{array}
+  $$
+%
+ \item If $e_1 = e_2 + e_3$, then $\snum'_1(e_1) = \snum'_1(e_2) + \snum'_1(e_3)$ and 
+%
+  $$
+  \begin{array}{l }
+  (\snum'_2(e_1), \rnum'_2(e_1)) =  \\
+  \ \ \ \ (n(\snum'_2(e_2) + \snum'_2(e_3)), n(\rnum'_2(e_2) + \rnum'_2(e_3)+1)).
+ \end{array}
+  $$
+  (Recall that the construction of $\aut_1 \cup \aut_2$ introduces one additional register.)
+%
+ \item If $e_1 = e_2 \cap e_3$, then $\snum'_1(e_1) = \snum'_1(e_2) \times \snum'_1(e_3)$ and 
+%
+  $$
+  \begin{array}{l }
+  (\snum'_2(e_1), \rnum'_2(e_1)) =  \\
+  \ \ \ \ (n(\snum'_2(e_2) \times \snum'_2(e_3)), n(\rnum'_2(e_2) + \rnum'_2(e_3))).
+ \end{array}
+  $$
+%
+ \item If $e_1 = \overline{e_2}$, then $\snum'_1(e_1) = 2^{\snum'_1(e_2)}$ and 
+%
+  $
+%  \begin{array}{l }
+  (\snum'_2(e_1), \rnum'_2(e_1)) =  (n \cdot 2^{\snum'_2(e_2)}, 0).
+% \end{array}
+  $
+ (The exponential blow-up is explained by the fact that the determinization is needed for the complementation.) 
+%
+%  \item If $\regex = \overline{\regex_1}$, then $s_\regex = 2^{s_{\regex_1}}$ (since the determinization is needed for the complement) and $r_\regex = 0$.
+%
+ \item If $e_1 = (e_2)^*$, then $\snum'_1(e_1) = \snum'_1(e_2)$ and 
+%
+  $
+%  \begin{array}{l }
+  (\snum'_2(e_1), \rnum'_2(e_1)) =  (n \snum'_2(e_2), 0).
+% \end{array}
+  $
+%  \item If $\regex = \regex_1^*$, then $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 0$.
 %  \item $\regex = \regex_1 \backslash \regex_2$ can be transferred to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the size can be computed by the formula of $\cap$ and $\bar{}$.
-  \item For $\regex = \regex_1^{\{m, n\}}$ or $\regex = \regex_1^{\{n,\infty\}}$, $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 1$.
+ \item If $e_1 = (e_2)^{\{m', n'\}}$ or $e_1 = (e_2)^{\{n', \infty\}}$, then $\snum'_1(e_1) = n' \snum'_1(e_2)$ and 
+%
+  $
+%  \begin{array}{l }
+  (\snum'_2(e_1), \rnum'_2(e_1)) =  (n \snum'_2(e_2), n).
+% \end{array}
+  $
+%  \item For $\regex = \regex_1^{\{m, n\}}$ or $\regex = \regex_1^{\{n,\infty\}}$, $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 1$.
 \end{itemize}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
 \medskip
@@
 \end{example}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2024-05-31 2024-5-13/sections/heuristic.tex
section 7.2

@@
 Since Kleene star can be seen as a special case of the counting operators, and language difference $e_1 \setminus e_2$ can be rewritten as $e_1 \cap \overline{e_2}$, without loss of generality, we can assume that a non-register representable occurrence of a  counting operator is in the scope of another counting operator or some complement operator.
-In the sequel, to alleviate the formula-size blow-up problem resulted from the naive unfolding, we present various optimizations, for the nesting of counting operators and the nesting of a counting operator and a complement operator respectively.
+In the sequel, to alleviate the formula-size blow-up problem resulted from the naive unfolding, we present various optimizations, for the nesting of counting operators and the nesting of  counting operators and a complement operator respectively.
 % two situations that a counting operator is in the scope of another counting operator and in the scope of a complement operator respectively.
@@
 
-\zhilin{stopped here}
-
 %The naive approach for nested counting in the paper \cite{Denghang2023} is to unwind all inner counting operators.
@@
 
-\subsection{Optimizations for the nesting of a counting operator and a complement operator}
-As we mentioned in the above section \ref{heuristic:nested}, the unwinding process of the complement operator is exponential to the counting bounds in the worst case.
+\subsection{Optimizations for the nesting of counting operators and a complement operator}
+
+As mentioned in Section~\ref{sec:algorithm}, if some counting operators are in the scope of a complement operator, it is necessary to unfold these counting operators before the complement operation.
+The exponential blow-up in the unfolding combined with the blow-up in the complement operation will produce huge number of states.
+To alleviate this problem, we propose two approximations of the complement operation, i.e.
+an under-approximation and an over-approximation, and combine them into a procedure that achieves a nice balance between efficiency and precision.
+
+Let $e = \overline{e_1}$ be a regular expression, where $e_1$ is a register-representable regular expression.
+
+\paragraph*{Under approximation}
+%
+One way of doing the complement operation is to transform $e_1$ into a regular expression that does not contain counting operators.
+We compute an under-approximation of $e$ by replacing each occurrence of the counting operators in $e_1$, say $(e_2)^{\{m,n\}}$ or $(e_2^{\{n, \infty\}})$, by $e_2^*$.
+Let us use $e'_1$ denote the resulting regular expression.
+Note that $e'_1$ does not contain counting operators.
+Moreover, it is easy to observe that $\Lang(e_1) \subseteq \Lang(e'_1)$.
+As a result, we have $\Lang(\overline{e'_1}) \subseteq \Lang(\overline{e_1})$.
+That is, $\overline{e'_1}$ is an under-approximation of $\overline{e_1}$.
+
+%The under-approximation is replacing each counting operator in the subregex of complement with a Kleene star operator.
+The language of the subregex is a superset of the language of it after under-approximation.
+In sequential, the complement of the subregex is a subset of origin.
+Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement.
+For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.
+
+\zhilin{stopped here}
+
+%As we mentioned in the above section \ref{heuristic:nested}, the unwinding process of the complement operator is exponential to the counting bounds in the worst case.
 We present a heuristic to reduce the number of states generated by the unwinding process.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
 \medskip
@@
 For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2024-05-31 2024-5-13/sections/heuristic.tex
section 7.2

@@
 
-\paragraph*{Under approximation}
+\paragraph*{Under-approximation}
 %
@@
 
-\zhilin{stopped here}
+\paragraph*{Over-approximation}
+For $e = \overline{e_1}$, we utilize the CEFA constructed from $e_1$, say $\aut_{e_1}$, to construct a CEFA $\cB$ of $e$ so that $\Lang(\cB)$ is an over-approximation of $\Lang(e)$. 
+Let $\aut_{e_1} = (R, Q, \Sigma, \delta, I, F, \alpha)$.
+The main idea of the construction is explained as follows: If a string $w$ is not accepted by $\aut_{e_1}$, then either there are no runs of $\aut_{e_1}$ on $w$, or every run of $\aut_{e_1}$ on $w$ stop at a non-final state or enter a final state but do not satisfy the accepting condition $\alpha$.
+We shall construct a CEFA $\cB$ that accepts when one of these situations occurs.
+Then $\overline{\Lang(\aut_{e_1})} \subseteq \Lang(\cB)$, that is, $\cB$ is an over-approximation of $e$.
+
+Without loss of generality, we can assume that there are no transitions out of $F$ in $\aut_{e_1}$.
+If this is not the case, then a new state $q_f$ can be introduced to transform $\aut_{e_1}$ into a CEFA satisfying this constraint, where $q_f$ is the unique accepting state.
+Then we define $\cB= (R \cup \{r'\}, Q \cup \{q_s\}, \Sigma, \delta', I, Q \cup \{q_s\}, \alpha')$, where
+\begin{itemize}
+  \item $r'$ is a new register not in $R$, 
+  \item $q_s$ is a new state not in $Q$,
+  \item $\delta'$ comprises the following transitions, 
+  \begin{itemize}
+    \item $(q, a, q', (\vec{v}, 0))$ such that $(q, a, q', \vec{v}) \in \delta$ and $q' \not \in F$,
+%
+    \item $(q, a, q_s,(\vec{0}, 0))$ such that there do \emph{not} exist $a$-labeled transitions out of $q$, that is, for every $q'$ and $\vec{v}$, we have $(q, a, q', \vec{v}) \not\in \delta$,
+%
+    \item $(q, a, q', (\vec{v}, 1))$ such that $(q, a, q', \vec{v}) \in \delta$ and $q' \in F$,
+%
+    \item $(q_s, a, q_s, (\vec{0}, 0))$ such that $a \in \Sigma$, 
+  \end{itemize}
+  \item $\alpha'$ is defined as $r' = 1 \rightarrow \neg \alpha$.
+\end{itemize}
+Intuitively, $q_s$ is a sink state that deals with the situations that there are no runs and $r'$ is a register newly introduced so that the different cases of the non-accepting runs of $\aut_{e_1}$ can be captured by a single accepting condition $\alpha'$.
+
+Note that $\cB$ is a strict over-approximation of $e = \overline{e_1}$ since $\aut_{e_1}$ may be nondeterministic.
+For instance, if there are two runs of $\aut_{e_1}$ on a string $w$, say one run that ends at a non-final state and another run that ends at a final state and satisfies accepting condition $\alpha$.
+Then $w \in \Lang(\aut_{e_1})$, thus $w \not \in \Lang(\overline{\aut_{e_1}})$.
+Nevertheless, according to the construction, $w$ is accepted by $\cB$, witnessed by the run of $\aut_{e_1}$ that ends at a non-final state.
 
@@
 For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{proof}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\zhilin{stopped here}
 

### 2024-06-01 2024-5-13/sections/heuristic.tex
model generation

@@
 
+\section{Optimizations for model generation}\label{sec-opt-sol-gen}
+
+Recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
+\[
+\begin{array}{l}
+\bigwedge \limits_{i \in [n]} \left(\psi_{\cC_i}(\fZ_{\costset_{\cC_i}}) \wedge \alpha_i\left[\sum\limits_{\myvec{v} \in \costset_{\cC_i}} \anivarz_{i, \myvec{v}} \myvec{v} \big{/}R_{\cB_i}  \right] \right) \ \wedge \\
+\ \ \varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cC_1}} \anivarz_{1, \myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cC_n}} \anivarz_{n, \myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right].
+\end{array}
+\]
+Let us use $\theta$ to denote this formula. 
+Then we utilize some SMT solver, say Z3, to solve the satisfiability of $\theta$.
+If Z3 reports ``sat'', then it also returns a model, namely, an assignment $\amodel$ of natural numbers to the free integer variables in $\theta$.
+Then we utilize $\amodel$ to generate a model $\amodel'$ of the original RECL constraint $\varphi$, i.e.
+an assignment of strings to the string variables so that $\varphi$ is evaluated to true under $\amodel'$.
+
+Note that for each $i \in [n]$, the free variables $\fZ_{\costset_{\cC_i}}$ in $\theta$ correspond to the number of occurrences of characters in $\costset_{\cC_i}$, i.e.
+the alphabet of the NFA $\cC_i$.
+Moreover, recall that in $\cC_i$, the characters are just the integer vectors and the characters in the original CEFAs $\cB_i$ used to construct $\cC_i$ are ignored.
+When we utilize $\amodel$ and the CEFAs $\cB_i$ to generate $\amodel'$, for each $i \in [n]$, we record the remaining occurrences of vectors $\myvec{v}$ in the transitions of the CEFAs $\cB_i$ as a number $\nvec_{i, \myvec{v}}$ and
+each time when a transition $(q, a, q', \myvec{v})$ in $\cB_i$ is traversed, $\nvec_{i, \myvec{v}}$ is decremented.
+Note that initially $\nvec_{i, \myvec{v}}$ is set to $\amodel(\anivarz_{i, \myvec{v}})$.
+The searching process terminates when $\nvec_{i, \myvec{v}}$ becomes $0$ for every $\myvec{v}$.
+We record the characters in the traversed transitions and obtain a string for the string variable $x_i$ when the searching process terminates.
+As a result, we obtain a model of $\varphi$ in the end.
+
+It turns out that this model generation process is inefficient, mainly due to the fact that the information about the occurrences of vectors $\myvec{v}$ in $\cB_i$ in the searching process is too coarse.
+In the sequel, we would like to refine this process by using the LIA formulas to obtain the information about the number of occurrences of transitions, instead of just the integer vectors, and utilize this information to guide the searching process.
+Moreover, some additional tricks are introduced to prune the searching space further.
+
 \zhilin{stopped here}
 
-\subsection{Heuristic for Finding an Accepted Word}
 In the section \ref{sec:algorithm}, we present an algorithm to solve the $\cefadec$ problem.

### 2024-06-01 2024-5-13/sections/heuristic.tex
fix some mistakes in heuristic

@@
 
-\item We estimate the sizes of the two CEFAs $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ constructed from $\ufld_1(e), \ufld_2(e)$ respectively as pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$, where $\snum_1(e)$ and $\rnum_1(e)$ are the estimates of the number of states and registers in $\aut_{\ufld_1(e)}$, similarly for $(\snum_2(e)$ and $\rnum_2(e))$.
+\item We estimate the sizes of the two CEFAs $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ constructed from $\ufld_1(e), \ufld_2(e)$ respectively as pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$, where $\snum_1(e)$ and $\rnum_1(e)$ are the estimates of the number of states and registers in $\aut_{\ufld_1(e)}$, similarly for $\snum_2(e)$ and $\rnum_2(e)$.
 %

### 2024-06-01 2024-5-13/sections/implementation.tex
change heuristics to optimizations in the experiment chapter

@@
 
-\subsection{Empirical justification of the technical choices and heuristics}\label{subsec:size_reduction_eval}
+\subsection{Empirical justification of the technical choices and optimizations}\label{subsec:size_reduction_eval}
 We also do experiments to evaluate the effectiveness of the automata size-reduction techniques for register-representable regexes, that is, Step 2 of Section~\ref{subsec:cefadec}.
 We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}.
-Finally, we carry out experiment on the ComplexCounting benchmarks to justify the heuristics of Section~\ref{sec:heuristic} for non-register-representable regexes.
+Finally, we carry out experiment on the ComplexCounting benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
 \subsubsection{Empirical justification of the technical choices}
@@
   \import{tables}{table_heuristics.tex}
-  \caption{Empirical justification of the technical choices and heuristics}\label{tab:results_heuristic}
+  \caption{Empirical justification of the technical choices and optimizations}\label{tab:results_heuristic}
 \end{table}
@@
 
-\subsubsection{Empirical justification of the heuristics for non-regesiter-representable regexes} 
+\subsubsection{Empirical justification of the optimizations for non-regesiter-representable regexes} 
 We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$.
@@
 Futhermore, the heuristic for complement on counting operators contributes both to satisfiable and unsatisfiable instances, while the heuristic for finding the accepted word and the heuristic for nested counting contribute only to satisfiable instances.
-All the heuristics improve the performance of $\ostrichrecl$.
+All the optimizations improve the performance of $\ostrichrecl$.
 
@@
   \import{tables}{table_heuristics_complex.tex}
-  \caption{Empirical justification of the heuristics on ComplexCounting benchmarks}\label{tab:results_heuristic_complex}
+  \caption{Empirical justification of the optimizations on ComplexCounting benchmarks}\label{tab:results_heuristic_complex}
 \end{table}

### 2024-06-01 2024-5-13/sections/implementation.tex
update description for ComplexCounting benchmark suite and explanation for experiment results

@@
 \noindent
-\emph{ComplexCounting benchmark suite.} This benchmark suite is generated by the extension of \textsc{stringfuzz} \cite{stringfuzz}.
-We extend the \textsc{stringfuzz} tool with counting operators and generate 1,000 instances in which half of them contain complement on the counting operators and the other half contain nested counting.
-The length bound is set to $|x| > 50$ for each string variable $x$.
+\emph{ComplexCounting benchmark suite.} This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator.
+We generate 500 instances of the nesting of counting operators containing the RECL constraint $x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50$ in each of them, where $e_{nest}\equiv (e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}})^{\{m_4,n_4\}}$ is a regex of the nesting of counting operators and $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is as RegCoL benchmark suite.
+Note that $0\leq m_i\leq n_i\leq 20$ for $i\in [4]$ and $e_i$ containing no counting operators for $i\in [3]$ is randomly generated.
+We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{nest}\wedge x\in e_{comp} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{nest}$ and $e_{sani}$ are as above.
+Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.
 
@@
 %The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
-From Fig~\ref{fig:count_distri}, we can see that while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e.
-greater than or equal to $50$).
+In our statistics, while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e. greater than or equal to $50$).
 %Although most upper bounds are small, about two thousand of them are still greater than 50.
@@
 
-\subsubsection{Empirical justification of the size-reduction technique for register-representable regexes}
+\subsubsection{Empirical justification of the optimizations for register-representable regexes}
 We compare $\ostrichrecl$ with its variant ${\rm -ASR}$.  ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). 
@@
 
+Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results.
+Therefore, we consider the ComplexCounting benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes.
 The ComplexCounting benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}.
 We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
-
-From the results, the heuristic for complement on counting operators and the heuristic for finding the accepted word of the automaton are more effective than the heuristic for nested counting.
-Futhermore, the heuristic for complement on counting operators contributes both to satisfiable and unsatisfiable instances, while the heuristic for finding the accepted word and the heuristic for nested counting contribute only to satisfiable instances.
-All the optimizations improve the performance of $\ostrichrecl$.
+From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the complex non-register-representable regexes.
 

### 2024-06-01 2024-5-13/sections/implementation.tex
update description for ComplexCounting benchmark suite and explanation for experiment results

@@
 We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
-From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the complex non-register-representable regexes.
+From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the non-register-representable regexes.
 

### 2024-06-02 2024-5-13/sections/heuristic.tex
section 7.3

@@
 It turns out that this model generation process is inefficient, mainly due to the fact that the information about the occurrences of vectors $\myvec{v}$ in $\cB_i$ in the searching process is too coarse.
-In the sequel, we would like to refine this process by using the LIA formulas to obtain the information about the number of occurrences of transitions, instead of just the integer vectors, and utilize this information to guide the searching process.
-Moreover, some additional tricks are introduced to prune the searching space further.
+In the sequel, we would like to refine this process by using the LIA formulas to obtain the information about the number of occurrences of transitions, instead of just the occurrences of integer vectors, and utilize this information to guide the search process.
+Specifically, for each $i \in [n]$ and each transition $(q, a, q', \myvec{v})$ in $\cB_i$, we introduce an integer variable $\anivarz_{i, (q, a, q', \myvec{v})}$ to denote the number of occurrences of the transition, and solve the satisfiability of the following formula,
+\[
+\begin{array}{l}
+\bigwedge \limits_{i \in [n]} \left(\psi_{\cC_i}(\fZ_{\costset_{\cC_i}}) \wedge \alpha_i\left[\sum\limits_{\myvec{v} \in \costset_{\cC_i}} \anivarz_{i, \myvec{v}} \myvec{v} \big{/}R_{\cB_i}  \right] \right) \ \wedge \\
+\ \ \varphi \left[ \sum\limits_{\myvec{v} \in \costset_{\cC_1}} \anivarz_{1, \myvec{v}} \myvec{v} \big{/}R_{\cB_1}, \cdots, \sum\limits_{\myvec{v} \in \costset_{\cC_n}} \anivarz_{n, \myvec{v}} \myvec{v} \big{/}R_{\cB_n} \right]\ \wedge \\
+\ \ \bigwedge \limits_{i \in [n]} \bigwedge \limits_{\myvec{v} \in \costset_{\cC_i}} \anivarz_{i, \myvec{v}} = \sum \limits_{(q, a, q', \myvec{v}) \mbox{ occurs in } \cB_i} \anivarz_{i, (q, a, q', \myvec{v})}.
+\end{array}
+\]
+If an SMT solver reports that the aforementioned formula is satisfiable, then the solver can also returns a model, which assigns to each variable $\anivarz_{i, (q, a, q', \myvec{v})}$ a natural number.
+%For each $i \in [n]$ and each transition $(q, a, q', \myvec{v})$ in $\cB_i$, let us use $nt_{i, (q, a, q', \myvec{v})}$ to denote the value of $\anivarz_{i, (q, a, q', \myvec{v})}$ in the model.
+Then we utilize these values to generate a model (an assignment of strings to string variables) of $\varphi$. 
+Let $i \in [n]$.
+We use a function $\lambda_i$ to record the number of occurrences of the transitions in $\cB_i$.
+During the search process for $\cB_i$, each time when a transition $(q, a, q', \myvec{v})$ is traversed, $\lambda_i$ is updated by decrementing $\lambda_i((q, a, q', \myvec{v}))$, moreover, $a$ is also recorded.
+Initially, for each $i \in [n]$ and each transition $(q, a, q', \myvec{v})$ in $\cB_i$, $\lambda_i((q, a, q', \myvec{v}))$ is set to be the value of $\anivarz_{i, (q, a, q', \myvec{v})}$ in the model.
+When a final state of $\cB_i$ is reached and $\lambda_i((q, a, q', \myvec{v}))$ becomes zero for each transition $(q, a, q', \myvec{v})$ in $\cB_i$, then a desired string is generated for the string variable $x_i$.
 
-\zhilin{stopped here}
+Moreover, propose a method to prune the search space further.
+Let $i \in [n]$.
+Suppose that during the search process for $\cB_i$, let $q$ be the current state of $\cB_i$ and $\lambda_i$ record the remaining occurrences of transitions of $\cB_i$.
+We compute the set of transitions of $\cB_i$ that are reachable from the state $q$.
+Let $\cT_q$ denote this set.
+If $\{(q, a, q', \myvec{c}) \mid \lambda_i((q, a, q', \myvec{c})) > 0\} \not \subseteq \cT_q$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_i$ will be found and meanwhile the constraint on the number of transitions enforced by $\lambda_i$ is satisfied.
+Therefore, in this case, the search process for $\cB_i$ in this direction halts and the search process is backtracked.
 
+%\zhilin{stopped here}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
 In the section \ref{sec:algorithm}, we present an algorithm to solve the $\cefadec$ problem.
@@
 If $qreach$ covers all transitions with positive times in the input map $tmap$, then we say that $tmap$ is reachable from $q'$ and the procedure \textsc{isReachable} returns true, otherwise it returns false.
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-06-02 2024-5-13/sections/implementation.tex
section 7.3

@@
 
-We implemented the algorithm in Section~\ref{sec:algorithm} and Section~\ref{sec:heuristic} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
+We implemented the procedures and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
 %
-In this section, we evaluate the performance of $\ostrichrecl$ on three benchmark suites, that is, RegCoL, AutomatArk, and ComplexCounting.
+In this section, we evaluate the performance of $\ostrichrecl$ on three benchmark suites, that is, RegCoL, AutomatArk, and NestC.
 In the sequel, we first describe the three benchmark suites as well as the experiment setup.
@@
 We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}.
-We also compare $\ostrichrecl$ with several variants of it, to justify the technical choices and heuristics we take in the Section~\ref{subsec:cefadec} and Section~\ref{sec:heuristic}.
+We also compare $\ostrichrecl$ with several variants of it, to justify the technical choices made in Section~\ref{sec:algorithm} and evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}-\ref{sec-opt-sol-gen}.
 
@@
 
-\subsection{Benchmark suites and experiment setup}\label{sec:bench}
+\subsection{Benchmark suites and the experiment setup}\label{sec:bench}
 
-Our experiments utilize two benchmark suites, namely, \emph{RegCoL} and \emph{AutomatArk}.
-Other industrial benchmark suites are not utilized because they contain no counting operators.
-There are 49,843 instances in total, where 48,843 of them are collected from the real world and 1,000 of them are generated by fuzzing tool.
-All benchmark instances are in the SMTLIB2 format.
+Our experiments utilize three benchmark suites, namely, \emph{RegCoL}, \emph{AutomatArk}, and \emph{NestC}. 
+%Other benchmark suites are not utilized because they contain no counting operators. 
+There are 49,843 instances in total.
+%, where 48,843 of them are collected from the real world and 1,000 of them are generated by the string fuzzing tool. 
+All benchmark instances are in the SMTLIB2 format. In the sequel, we give more details of these three benchmark suites.
 
@@
 \noindent
-\emph{ComplexCounting benchmark suite.} This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator.
+\emph{NestC benchmark suite.} 
+\zhilin{To be cleaned}
+This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator.
 We generate 500 instances of the nesting of counting operators containing the RECL constraint $x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50$ in each of them, where $e_{nest}\equiv (e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}})^{\{m_4,n_4\}}$ is a regex of the nesting of counting operators and $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is as RegCoL benchmark suite.
@@
 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH
-\cite{CHL+19}, on RegCoL, AutomatArk and ComplexCounting benchmark suites.
-The experiment results can be found in Figure~\ref{fig:table_overall_eval}.
+\cite{CHL+19}, on RegCoL, AutomatArk and NestC benchmark suites.
+The experiment results can be found in Table~\ref{tab:table_overall_eval}.
 Note that we take the results of CVC5 as the ground truth\footnote{Initially,  we used the majority vote of the results of the solvers as the ground truth.
@@
     \caption{Overall performance evaluation}
-  \label{fig:table_overall_eval}
+  \label{tab:table_overall_eval}
 \end{table}
@@
 We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}.
-Finally, we carry out experiment on the ComplexCounting benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
+Finally, we carry out experiment on the NestC benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
 \subsubsection{Empirical justification of the technical choices}
@@
 Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results.
-Therefore, we consider the ComplexCounting benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes.
-The ComplexCounting benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}.
+Therefore, we consider the NestC benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes.
+The NestC benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}.
 We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
@@
   \import{tables}{table_heuristics_complex.tex}
-  \caption{Empirical justification of the optimizations on ComplexCounting benchmarks}\label{tab:results_heuristic_complex}
+  \caption{Empirical justification of the optimizations on NestC benchmarks}\label{tab:results_heuristic_complex}
 \end{table}

### 2024-06-02 2024-5-13/sections/implementation.tex
experiments

@@
 We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}.
-We also compare $\ostrichrecl$ with several variants of it, to justify the technical choices made in Section~\ref{sec:algorithm} and evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}-\ref{sec-opt-sol-gen}.
+We also compare $\ostrichrecl$ with several variants of itself, to evaluate the effectiveness of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}.
 
@@
 All experiments are conducted on CentOS Stream release 8 with 4 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory.
-We use the \textsc{zaligvinder} framework \cite{zaligvinder_2021} to execute the experiments, with a timeout of 60s for each instance.
+We use the \textsc{zaligvinder} framework \cite{zaligvinder_2021} to execute the experiments, with a timeout of 60 seconds per instance.
 
@@
 
-\subsection{Performance evaluation}\label{subsec:overall_eval}
+\subsection{Performance evaluation against the other solvers}\label{subsec:overall_eval}
 
@@
 
-\subsection{Empirical justification of the technical choices and optimizations}\label{subsec:size_reduction_eval}
-We also do experiments to evaluate the effectiveness of the automata size-reduction techniques for register-representable regexes, that is, Step 2 of Section~\ref{subsec:cefadec}.
-We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}.
-Finally, we carry out experiment on the NestC benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
-\subsubsection{Empirical justification of the technical choices}
+\subsection{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}}\label{subsec:size_reduction_eval}
+
+At first, we do experiments to evaluate the effectiveness of the automata size-reduction techniques (i.e.
+Step 2) in Section~\ref{sec:algorithm}.
+Then we justify our technical choices of reducing the satisfiability problem to that of LIA formulas and resort to the SMT solvers to solve them.
+Specifically, we compare $\ostrichrecl$ with a variant where the nuXmv model checker like \cite{atva2020} is used to solve the $\cefadec$ problem.
+%
+%We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. 
+We also evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}, i.e.
+the optimizations for the nesting of counting operators as well as the nesting of counting operators and a complement operator.
+Finally, we evaluate the effectiveness of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}.
+
+%Finally, we carry out experiment on the NestC benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
+%\subsubsection{Empirical justification of the technical choices}
 %We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
 %Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed.
-We compare $\ostrichrecl$ with its variant  ${\rm +NUXMV}$. ${\rm +NUXMV}$  is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.
 
-The experiment results can be found in Table~\ref{tab:results_heuristic}.
-We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$.
-Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv.
+\paragraph*{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}
+We compare $\ostrichrecl$ with its variant  $\ostrichrecl_{\rm +NUXMV}$, which is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the $\cefadec$ problem.
+Moreover, we also compare $\ostrichrecl$ with its variant $\ostrichrecl_{\rm -ASR}$, which is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
+Step 2 in Section~\ref{subsec:cefadec}).
+
+The experiment results can be found in Table~\ref{tab:results_algorithm}.
+From the results, we can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than $\ostrichrecl_{\rm +NUXMV}$.
+Therefore, the technical choice in Section~\ref{sec:algorithm} where LIA formulas are computed and then solved by the SMT solvers is reasonable, since $\ostrichrecl$ with this technical choice is more efficient than $\ostrichrecl_{\rm +NUXMV}$, where nuXmv is used to solve the $\cefadec$ problem.
+%
+Moreover, $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than $\ostrichrecl_{\rm -ASR}$. 
+From the results, we can see that the automata-size reduction technique indeed plays an important role for the performance improvement. 
+%
 \begin{table}
-  \import{tables}{table_heuristics.tex}
-  \caption{Empirical justification of the technical choices and optimizations}\label{tab:results_heuristic}
+  \import{tables}{table_algorithm.tex}
+  \caption{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}\label{tab:results_algorithm}
 \end{table}
 
-\subsubsection{Empirical justification of the optimizations for register-representable regexes}
-We compare $\ostrichrecl$ with its variant ${\rm -ASR}$.  ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). 
-The experiment results can be found in Table~\ref{tab:results_heuristic}.
-We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$.
-Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.
+%\subsubsection{Empirical justification of the optimizations for register-representable regexes}
 
-\subsubsection{Empirical justification of the optimizations for non-regesiter-representable regexes} 
+\zhilin{stopped here}
+
+\paragraph*{Evaluation of the optimizations in Section~\ref{sec:heuristic}}
+%
+%\subsubsection{Empirical evaluation of the optimizations for non-regesiter-representable regexes} 
 We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$.
@@
 ${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.
+
+\begin{table}
+  \import{tables}{table_heuristics.tex}
+  \caption{Evaluation of the optimizations in Section~\ref{sec:heuristic}}\label{tab:results_heuristic}
+\end{table}
 
@@
 
+\paragraph*{Evaluation of the optimizations in Section~\ref{sec-opt-sol-gen}}
+
 %To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}.

### 2024-06-02 2024-5-13/sections/implementation.tex
correct the description of complement instances in NestC benchmark suite

@@
 Note that $0\leq m_i\leq n_i\leq 20$ for $i\in [4]$ and $e_i$ containing no counting operators for $i\in [3]$ is randomly generated.
-We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{nest}\wedge x\in e_{comp} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{nest}$ and $e_{sani}$ are as above.
+We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{comp1}\wedge x\in e_{comp2} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp\{1,2\}}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{sani}$ are as above.
 Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.
@@
 From the results, we can see that the automata-size reduction technique indeed plays an important role for the performance improvement.
-%
+
 \begin{table}

### 2024-06-02 2024-5-13/sections/implementation.tex
experiments

--- 2024-06-02 2024-5-13/sections/implementation.tex
@@
 
-\subsection{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}}\label{subsec:size_reduction_eval}
+\subsection{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}}\label{subsec:size_reduction_eval}
 
@@
 
-\paragraph*{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}
+\paragraph*{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}
+%
 We compare $\ostrichrecl$ with its variant  $\ostrichrecl_{\rm +NUXMV}$, which is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the $\cefadec$ problem.
@@
 \begin{table}
-  \import{tables}{table_heuristics.tex}
-  \caption{Evaluation of the optimizations in Section~\ref{sec:heuristic}}\label{tab:results_heuristic}
+  \import{tables}{table_heuristics_complex.tex}
+  \caption{Evaluation of the optimizations in Section~\ref{sec:heuristic}}\label{tab:results_heuristic_complex}
 \end{table}
@@
 
+\paragraph*{Evaluation of the optimizations in Section~\ref{sec-opt-sol-gen}}
+
+Table~\ref{tab:results_model-gen}.
+
 \begin{table}
-  \import{tables}{table_heuristics_complex.tex}
-  \caption{Empirical justification of the optimizations on NestC benchmarks}\label{tab:results_heuristic_complex}
+  \import{tables}{table_heuristics_model_gen.tex}
+  \caption{Evaluation of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}}\label{tab:results_model-gen}
 \end{table}
 
-\paragraph*{Evaluation of the optimizations in Section~\ref{sec-opt-sol-gen}}
-
 %To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}.

### 2024-06-02 2024-5-13/sections/implementation.tex
the expriments finished

@@
 
-\begin{table}
+\begin{table}[htbp]
   \centering\vskip 0pt
@@
 %
-We compare $\ostrichrecl$ with its variant  $\ostrichrecl_{\rm +NUXMV}$, which is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the $\cefadec$ problem.
-Moreover, we also compare $\ostrichrecl$ with its variant $\ostrichrecl_{\rm -ASR}$, which is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
+We compare $\ostrichrecl$ with $\ostrichrecl_{\rm NUXMV}$, which is a variant of $\ostrichrecl$ where the nuXmv model checker is used to solve the $\cefadec$ problem.
+Moreover, we also compare $\ostrichrecl$ with $\ostrichrecl_{\rm -ASR}$, which is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
 Step 2 in Section~\ref{subsec:cefadec}).
@@
 The experiment results can be found in Table~\ref{tab:results_algorithm}.
-From the results, we can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than $\ostrichrecl_{\rm +NUXMV}$.
-Therefore, the technical choice in Section~\ref{sec:algorithm} where LIA formulas are computed and then solved by the SMT solvers is reasonable, since $\ostrichrecl$ with this technical choice is more efficient than $\ostrichrecl_{\rm +NUXMV}$, where nuXmv is used to solve the $\cefadec$ problem.
+From the results, we can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than $\ostrichrecl_{\rm NUXMV}$.
+Therefore, the technical choice in Section~\ref{sec:algorithm} where LIA formulas are computed and then solved by the SMT solvers is reasonable, since $\ostrichrecl$ with this technical choice is more efficient than $\ostrichrecl_{\rm NUXMV}$, where nuXmv is used to solve the $\cefadec$ problem.
 %
@@
 
-\begin{table}
+\begin{table}[htbp]
   \import{tables}{table_algorithm.tex}
@@
 
-\zhilin{stopped here}
-
 \paragraph*{Evaluation of the optimizations in Section~\ref{sec:heuristic}}
@@
 %\subsubsection{Empirical evaluation of the optimizations for non-regesiter-representable regexes} 
-We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$.
-${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting.
-${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators.
-${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.
+We also compare the performance of $\ostrichrecl$ with its variants $\ostrichrecl_{\rm -NEST}$ and $\ostrichrecl_{\rm -COMP}$, where $\ostrichrecl_{\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the optimization for the nesting of counting operators, and $\ostrichrecl_{\rm -COMP}$ is obtained by removing the optimization for the nesting of counting operators and a complement operator.
+Since these optimizations are not targeted for register-representable RECL constraints and there are very few non-register-representable RECL constraints in the RegCoL and AutomatArk benchmark suites, we restrict our attention to the NestC benchmark suite here.
 
-\begin{table}
+\begin{table}[htbp]
   \import{tables}{table_heuristics_complex.tex}
@@
 
-The overall experiment results can be found in Table~\ref{tab:results_heuristic}.
-We can see that $\ostrichrecl$ solves 77/388/349 more instances and is 1.13/1.18/1.24 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
+The experiment results can be found in Table~\ref{tab:results_heuristic_complex}.
+From the results, we can see that on 1,000 problem instances, $\ostrichrecl$ solves 82/339 more instances and is 1.02/1.92 times faster than $\ostrichrecl_{\rm -NEST}$/$\ostrichrecl_{\rm -COMP}$ respectively.
+As a result, while both optimizations do play a role in the performance improvement in solving these complex RECL constraints, the optimization for the nesting of counting operators and a complement operator plays a greater role since it allows solving around 1/3 more instances.
 
-Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results.
+%The experiment results can be found in Table~\ref{tab:results_heuristic}. 
+%We can see that $\ostrichrecl$ solves 77/388/349 more instances and is 1.13/1.18/1.24 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
+
+%Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results.
 Therefore, we consider the NestC benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes.
@@
 
-\paragraph*{Evaluation of the optimizations in Section~\ref{sec-opt-sol-gen}}
+\paragraph*{Evaluation of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}}
 
-Table~\ref{tab:results_model-gen}.
+We compare the performance of $\ostrichrecl$ with $\ostrichrecl_{\rm -MODEL}$, where $\ostrichrecl_{\rm -MODEL}$ is obtained from $\ostrichrecl$ by removing the optimizations for the model generation.
 
-\begin{table}
+\begin{table}[htbp]
   \import{tables}{table_heuristics_model_gen.tex}
@@
 
+The experiment results can be found in Table~\ref{tab:results_model-gen}.
+From the results, we can see that compared to $\ostrichrecl$, $\ostrichrecl_{\rm -MODEL}$ solves 349 less instances and is 23\% slower on average (3.57s versus 2.88s).
+As a result, the optimization for the model generation does improve the performance, especially when the sizes of the CEFAs are huge.
+Note that the optimization for model generation only affects the satisfiable instances, that is, those instances where the generated LIA formulas can be solved, but the generation of models for these RECL constraints is unsuccessful.
+
 %To answer \textbf{Q3}, \textbf{our algorithm for solving the nonemptiness problem is much better than the \textsc{nuXmv}-based techniques}.

### 2024-06-02 2024-5-13/sections/implementation.tex
NestC benchmark suite

@@
 \emph{NestC benchmark suite.} 
-\zhilin{To be cleaned}
-This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator.
-We generate 500 instances of the nesting of counting operators containing the RECL constraint $x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50$ in each of them, where $e_{nest}\equiv (e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}})^{\{m_4,n_4\}}$ is a regex of the nesting of counting operators and $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is as RegCoL benchmark suite.
-Note that $0\leq m_i\leq n_i\leq 20$ for $i\in [4]$ and $e_i$ containing no counting operators for $i\in [3]$ is randomly generated.
-We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{comp1}\wedge x\in e_{comp2} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp\{1,2\}}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{sani}$ are as above.
+We generate this benchmark suite by utilizing the string fuzzing tool \textsc{stringfuzz}~\cite{stringfuzz}. Note that \textsc{stringfuzz} is slightly extended by adding the counting operators.
+%This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator. 
+For the benchmarks that contain the nestings of counting operators, we use the following template
+\[x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50\]
+where $e_{nest}$  is of the form 
+\[(e_1^{\{m_1, n_1\}}e_2^{\{m_2, n_2\}}e_3^{\{m_3, n_3\}}e_4^{\{m_4, n_4\}})^{\{m_5, n_5\}},\]
+such that $0 \leq m_i\leq n_i\leq 20$ for each $i \in [5]$ and $e_i$ contains no counting operators for each $i  \in [4]$,
+moreover, 
+\[e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}.\]
+Based on this template, we generate 500 instances.
+
+For the benchmarks that contain the nestings of counting operators and a complement operator, we utilize the following template
+\[x \in e_{comp1} \wedge x \in e_{comp2} \wedge x \in e_{sani} \wedge |x| > 50, \]
+where both $e_{comp1}$ and $e_{comp2}$ are of the form $\overline{e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}} e_4^{\{m_4, n_4\}}}$, such that for each $i \in [4]$, $20 \leq m_i\leq n_i\leq 1000$  and $e_i$ contains no counting operators.
+Note that two regular expressions $e_{comp1} $ and $e_{comp2}$ are introduced to have a better balance between the numbers of satisfiable and unsatisfiable instances.
+
+%We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{comp1}\wedge x\in e_{comp2} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp\{1,2\}}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{sani}$ are as above.
 Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.

### 2024-06-02 2024-5-13/sections/abstract.tex
commit the paper extended by setta2023
update description for ComplexCounting benchmark suite and explanation for experiment results
abstract and intro

--- 2023-08-30 2023-1-19/sections/abstract.tex
@@
+%!TEX root = ../main.tex
+
 Regular expressions (regex for short) and string-length function are widely used in string-manipulating programs.
@@
 As a result, the satisfiability of string constraints with regex-counting and string-length is reduced to the satisfiability of linear integer arithmetic, which the off-the-shelf SMT solvers can then solve.
-To improve the performance further, we propose simplification techniques to reduce automata sizes. We implement the algorithms and validate our approach on 48,843 benchmark instances. 
-The experimental results show that our approach can solve more instances than the state-of-the-art solvers, at a comparable or faster speed, especially when the counting and length bounds are large.
-
-%\keywords{Rgular Expressions, Counting, Length, Automata, Registers, Linear Integer Arithmetic}
-%\end{document}
+To improve the performance further, we also propose various optimization techniques.
+We implement the algorithms and validate our approach on 49,843 benchmark instances. 
+The experimental results show that our approach can solve more instances than the state-of-the-art solvers, at a comparable or faster speed, especially when the counting and length bounds are large or when the counting operators are nested with some other counting operators or complement operators.
+%\denghang{need to be changed before submitting}

### 2024-06-02 2024-5-13/sections/introduction.tex
abstract and intro

--- 2024-05-15 2024-5-13/sections/introduction.tex
@@
 According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
-Thus, the nonemptiness of CEFA w.r.t. LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
-  \item We propose techniques to reduce the sizes (i.e. the number of states and transitions) of CEFA, in order to achieve better performance.
-  \item Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints.
-We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$.
+Thus, the nonemptiness of CEFA w.r.t.
+LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
+Moreover, we propose techniques to reduce the sizes (i.e.
+the number of states and transitions) of CEFA, in order to achieve better performance.
 %
-  \item Finally, we utilize a collection of benchmark suites comprising 48,843 instances in total to evaluate the performance of $\ostrichrecl$.
-The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers, especially when the counting and length bounds are large (see Figure~\ref{fig:table_overall_eval} and Table~\ref{tab:large-bound}).
-For instance, on 1,969 benchmark instances where the counting bounds are greater than or equal to $50$ and the string lengths are required to be beyond $200$, $\ostrichrecl$ solves at least $278$ more instances than the other solvers, while spending only half or less time per instance on average.
+  \item For complex RECL constraints where the counting operators may be nested with the other counting operators or complement operators, we propose optimization techniques to improve the performance.
+Furthermore, for the satisfiable RECL constraints where the solutions of the LIA formulas can be obtained, but the models of the original RECL constraint cannot be generated,  we propose optimization techniques to accelerate the model generation process.
+%
+%  \item 
+%  Combined with the size-reduction techniques mentioned above, the register representation of regex-counting and string-length in CEFA entails an efficient algorithm for solving RECL constraints. 
+ %
+\item We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$.
+Finally, we utilize a collection of benchmark suites comprising 49,843 problem instances in total to evaluate the performance of $\ostrichrecl$.
+The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers (see Table~\ref{tab:table_overall_eval}-\ref{tab:results_model-gen}).
+For instance, $\ostrichrecl$ solves 49,638 out of 49,843 instances, while the best state-of-the-art solvers solve only 47,721 instances.
+We also do experiments to justify some of our technical choices and evaluate the performance of the optimizations.
+%
+% 1,000 benchmark instances where the counting and length bounds are large or the counting operators are nested with some other counting operators or complement operators, $\ostrichrecl$ solves at least $278$ more instances than the other solvers, while spending only half or less time per instance on average.
 \end{itemize}
@@
 \noindent
-\emph{Organization.} 
+\emph{Structure.} 
 The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper. Section~\ref{sec:pre} introduces the preliminaries. 
 Section~\ref{sec:recl} presents the syntax and semantics of RECL. 
-Section~\ref{sec:automaton} defines CEFA.
-Section~\ref{sec:algorithm} introduces the algorithm to solve RECL constraints.
+Section~\ref{sec:automaton} defines CEFA. Section~\ref{sec:algorithm} introduces the algorithm to solve RECL constraints. 
+Section~\ref{sec:heuristic} presents some heuristics for improving the performance of solving RECL constraints where the counting operators are nested with some other counting operators or complement operators.
 Section~\ref{sec:implementation} shows the experiment results.
 Section~\ref{sec:conclu} concludes this paper.
+
+\smallskip
+
+A preliminary version of this paper has appeared in the proceedings of SETTA 2023~\cite{Denghang2023}. This paper extends the SETTA paper in the following three aspects.
+\begin{itemize}
+\item To improve the performance of complex RECL constraints where the counting operators are nested with some other counting operators or complement operators, various optimizations are proposed. 
+\item To deal with the issue that the satisfiability of LIA formulas can be solved, but models of the original RECL constraints cannot be generated, we propose techniques to optimize the model generation process.
+\item The benchmarks are extended to cove the situations that the counting operators are nested with some other counting operators or complement operators, and the experiments are extended accordingly.
+\end{itemize}

### 2024-06-02 2024-5-13/sections/conclusion.tex
the expriments finished
experiments on NestC benchmark suite

--- 2023-10-20 2023-1-19/crv/sections/conclusion.tex
@@
 The approach is based on encoding counting operators in regular expressions by cost registers symbolically instead of unfolding them explicitly.
-Moreover, this work proposed automata-size reduction techniques to improve performance further.
-Finally, we used two benchmark suites comprising 48,843 instances in total to evaluate the performance of our approach.
-The experimental results show that our approach can solve more instances than the state-of-the-art best solvers, at a comparable or faster speed, especially when the counting and length bounds are large.
-For the future work, we plan to investigate how the symbolic approach can be extended to reason about nested counting operators.
+Moreover, this work proposed various optimization techniques to improve the performance further.
+Finally, we used three benchmark suites comprising 49,843 instances in total to evaluate the performance of our approach.
+The experimental results show that our approach can solve more instances than the state-of-the-art best solvers, at a comparable or faster speed, especially when the counting and length bounds are large or when counting operators are nested with some other counting operators or complement operators.
+%For the future work, we plan to investigate how the symbolic approach can be extended to reason about nested counting operators.

### 2024-06-02 2024-5-13/sections/implementation.tex
NestC benchmark suite
add results of the NestC benchmark suite
experiments on NestC benchmark suite

@@
 Note that two regular expressions $e_{comp1} $ and $e_{comp2}$ are introduced to have a better balance between the numbers of satisfiable and unsatisfiable instances.
+Based on this template, we also generate 500 instances.
+
+In total, the NestC benchmark suite contains 1000 instances.
 
@@
   \label{tab:table_overall_eval}
+\end{table}
+
+Furthermore, in order to see how $\ostrichrecl$ performs on the RECL constraints where the counting and length bounds are large or when the counting operators are nested with some other counting operators or with complement operators, we also compare $\ostrichrecl$ with the other solvers solely on the NestC benchmark suite.
+The experiment results can be found in Table~\ref{tab:table_nestc_eval}.
+From the results, we can see that $\ostrichrecl$ outperforms the other solvers in both the number of solved instances and the average time.
+Specifically, $\ostrichrecl$ solves 873 out of 1000 instances, while the best state-of-the-art solver (Z3seq) solves only 518 instances.
+Moreover, while the average time of $\ostrichrecl$  is only slightly better than Z3str3RE (19.49s versus 20.09s), $\ostrichrecl$ solves much more instances than it (873 versus 170).
+The results show the great advantage of $\ostrichrecl$ against the other solvers on the NestC benchmark suite.
+
+\begin{table}[htbp]
+  \centering\vskip 0pt
+    \import{tables}{table_nestc.tex}
+    \caption{Performance evaluation on the NestC benchmark suite}
+  \label{tab:table_nestc_eval}
 \end{table}

### 2024-06-02 2024-5-13/sections/conclusion.tex
fix the syntax error in conclusion

@@
 Finally, we used three benchmark suites comprising 49,843 instances in total to evaluate the performance of our approach.
-The experimental results show that our approach can solve more instances than the state-of-the-art best solvers, at a comparable or faster speed, especially when the counting and length bounds are large or when counting operators are nested with some other counting operators or complement operators.
+The experimental results show that our approach can solve more instances than the best state-of-the-art solver, at a comparable or faster speed, especially when the counting and length bounds are large or when counting operators are nested with some other counting operators or complement operators.
 %For the future work, we plan to investigate how the symbolic approach can be extended to reason about nested counting operators.

### 2024-06-02 2024-5-13/sections/heuristic.tex
fix the syntax error in heuristics

@@
 For example, naive unwinding regex $(a^{\{1,1000\}})^{\{1,2\}}$ generate a CEFA containing 1000 states.
-But if we only unwind the outer counting operator of the regex, not inner, we obtain a CEFA containing only 2 states.
-The side effect is that we need two registers to store the information of conuting in the inner regex (unwinding of outer counting operator repeat the inner regex, which also repeat the registers of the inner regex).We present a heuristic to reduce the number of states generated by the unwinding process.
-The idea is to unwind the counting operator with less bound and less side effect firstly.
+But if we only unwind the outer counting operator of the regex, not the inner, we obtain a CEFA containing only 2 states.
+The side effect is that we need two registers to store the information of counting in the inner regex (unwinding of the outer counting operator repeats the inner regex, which also repeats the registers of the inner regex).
+We present a heuristic to reduce the number of states generated by the unwinding process.
+The idea is to unwind the counting operator with less bound and fewer side effects firstly.
 We present the heuristic in the following algorithm.
@@
   \item If $\regex = \overline{\regex_1}$, then $size(\regex) = 2^{size(\regex_1)} + 1$.
-  \item $\regex = \regex_1 \backslash \regex_2$ can be transfered to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the size can be computed by the formula of $\cap$ and $\bar{}$.
+  \item $\regex = \regex_1 \backslash \regex_2$ can be transferred to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the size can be computed by the formula of $\cap$ and $\bar{}$.
   \item For $\regex = \regex_1^{\{n,m\}}$ or $\regex = \regex_1^{\{m,\infty\}}$, $size(\regex)$ is equal to $m*size(\regex_1)$ if it is unwinded, and $size(\regex_1)$ otherwise.
@@
   \item If $\regex = \regex_1 + \regex_2$, then $reg(\regex) = reg(\regex_1) + reg(\regex_2) + 1$.
-  \item $\regex = \regex_1 \backslash \regex_2$ can be transfered to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the number of registers can be computed by the formula of $\cap$ and $\bar{}$.
+  \item $\regex = \regex_1 \backslash \regex_2$ can be transferred to $\regex = \regex_1 \cap \overline{\regex_2}$ and then the number of registers can be computed by the formula of $\cap$ and $\bar{}$.
   \item For $\regex = \regex_1^{\{n,m\}}$ or $\regex = \regex^{\{m, \infty\}}$, $reg(\regex)$ is equal to $m*reg(\regex_1)$ if it is unwinded, and $1$ otherwise.
@@
 \noindent
-\emph{Step 3. (Unwind the counting operator with less bound and less registers first).}
+\emph{Step 3. (Unwind the counting operator with less bound and fewer registers first).}
 
 In the above two steps, we compute the number of states and registers generated by each counting operator.
-In some cases, we can unwind the counting operator with less bound and less registers directly.
-But in most cases, there are multiple counting operators where one counting operator has less bound and another counting operator has less registers.
+In some cases, we can unwind the counting operator with less bound and fewer registers directly.
+But in most cases, there are multiple counting operators where one counting operator has less bound and another counting operator has fewer registers.
 To consider the number of states and registers at the same time, we can compute the score of each counting operator by the following formula:
@@
 \end{itemize} 
-The reason why we use product to combine the two factors is that the hardness of the $\cefadec$ problem is highly relevant to the number of variables in the final existential LIA formula, which is linear to the product of the number of states and the number of registers.
-Use $reg(\regex) + 1$ not $reg(\regex)$ is because the registers number may be $0$.We unwind the counting operator with the smallest score first.
+The reason why we use the product to combine the two factors is that the hardness of the $\cefadec$ problem is highly relevant to the number of variables in the final existential LIA formula, which is linear to the product of the number of states and the number of registers.
+Using $reg(\regex) + 1$ not $reg(\regex)$ is because the number of registers may be $0$.We unwind the counting operator with the smallest score first.
 
@@
 The score of $^{\{1,1000\}}$ is $1000*(0+1) = 1000$ and the score of $^{\{1,2\}}$ is $2*(2+1) = 6$.
-We unwind the outer counting operator first and obtain a CEFA containing only 2 states.
+We unwind the outer counting operator first and obtain a CEFA containing only two states.
 \end{example}
@@
 As mentioned in Section~\ref{sec:algorithm}, if some counting operators are in the scope of a complement operator, it is necessary to unfold these counting operators before the complement operation.
-The exponential blow-up in the unfolding combined with the blow-up in the complement operation will produce huge number of states.
-To alleviate this problem, we propose two approximations of the complement operation, i.e.
-an under-approximation and an over-approximation, and combine them into a procedure that achieves a nice balance between efficiency and precision.
+The exponential blow-up in the unfolding combined with the blow-up in the complement operation will produce a huge number of states.
+To alleviate this problem, we propose two approximations of the complement operation, i.e., an under-approximation and an over-approximation, and combine them into a procedure that achieves a nice balance between efficiency and precision.
 
@@
 We compute an under-approximation of $e$ by replacing each occurrence of the counting operators in $e_1$, say $(e_2)^{\{m,n\}}$ or $(e_2^{\{n, \infty\}})$, by $e_2^*$.
-Let us use $e'_1$ denote the resulting regular expression.
+Let us use $e'_1$ to denote the resulting regular expression.
 Note that $e'_1$ does not contain counting operators.
@@
 The language of the subregex is a superset of the language of it after under-approximation.
-In sequential, the complement of the subregex is a subset of origin.
+In sequential, the complement of the subregex is a subset of the origin.
 Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement.
@@
 \end{itemize}
-Intuitively, $q_s$ is a sink state that deals with the situations that there are no runs and $r'$ is a register newly introduced so that the different cases of the non-accepting runs of $\aut_{e_1}$ can be captured by a single accepting condition $\alpha'$.
+Intuitively, $q_s$ is a sink state that deals with the situations where there are no runs, and $r'$ is a register newly introduced so that the different cases of the non-accepting runs of $\aut_{e_1}$ can be captured by a single accepting condition $\alpha'$.
 
@@
 $r$ is the register used to check whether the accepted state is also accepted in the original CEFA.
-$s$ is the self loop state accepting all string that is not accepted by the original CEFA.
-$f$ is the merged accepted state of original CEFA.
-If there is a transition $(q, a, q', \vec{v})$ teminates at the accepted state $q'$ in the original CEFA, we add a corresponding transition $(q, a, f, (\vec{v}, 1))$ in the over-approximated complement.
-From the definition of $\delta'$, we can see that only the transitions goto $f$ increase the value of regesiter $r$.
+$s$ is the self-loop state accepting all strings that are not accepted by the original CEFA.
+$f$ is the merged accepted state of the original CEFA.
+If there is a transition $(q, a, q', \vec{v})$ terminating at the accepted state $q'$ in the original CEFA, we add a corresponding transition $(q, a, f, (\vec{v}, 1))$ in the over-approximated complement.
+From the definition of $\delta'$, we can see that only the transitions goto $f$ increase the value of register $r$.
 The value of $r$ is $1$ if and only if the accepted state is also accepted in the original CEFA.
-With above construction, the meaning of the accepting condition $\alpha'$ is obvious: If the string teminates at the accepting state in the original CEFA, then the accepting condition $\alpha$ is false.
+With the above construction, the meaning of the accepting condition $\alpha'$ is obvious: If the string terminates at the accepting state in the original CEFA, then the accepting condition $\alpha$ is false.
 
@@
  In the definition of CEFA in section \ref{sec:automaton}, a run $q_0 \xrightarrow[\myvec{\overline{v}_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{\overline{v}_n}]{a_n} q_n$ is \emph{accepting} by $\overline{\aut}_{over}$ if $q_n \in (Q\cup\{s,f\})\backslash F$ and $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is true, where $\myvec{\overline{v}'} = \sum \limits_{j \in [n]} \myvec{\overline{v}_j}$.
-If a string is not accepted by $\overline{\aut}_{over}$, then each run of the string is not accepting run, which means the run teminates at state $q\in F$ or the accepting condition $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is $false$.
+If a string is not accepted by $\overline{\aut}_{over}$, then each run of the string is not accepting run, which means the run terminates at state $q\in F$ or the accepting condition $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is $false$.
 
@@
 The negation can be rewriten to $(r=1\wedge \alpha)(\myvec{\overline{v}'}/(R\cup\{r\})) = (r=1)(\myvec{\overline{v}'}/(R\cup\{r\}))\wedge \alpha(\myvec{\overline{v}'}/(R\cup\{r\}))$.
-In our construction, only the transitions teminate at $f$ increase one to the value of $r$, so that the run must end at $f$ to make $r=1$ be true.
+In our construction, only the transitions terminate at $f$ increase one to the value of $r$, so that the run must end at $f$ to make $r=1$ be true.
 $\alpha(\myvec{\overline{v}'}/(R\cup\{r\})) = \alpha(\myvec{v'}/R)$ is also need to be true, implying that the run is an accepting run of $\aut$.
@@
 If Z3 reports ``sat'', then it also returns a model, namely, an assignment $\amodel$ of natural numbers to the free integer variables in $\theta$.
-Then we utilize $\amodel$ to generate a model $\amodel'$ of the original RECL constraint $\varphi$, i.e.
-an assignment of strings to the string variables so that $\varphi$ is evaluated to true under $\amodel'$.
+Then we utilize $\amodel$ to generate a model $\amodel'$ of the original RECL constraint $\varphi$, i.e., an assignment of strings to the string variables so that $\varphi$ is evaluated to true under $\amodel'$.
 
@@
 \]
-If an SMT solver reports that the aforementioned formula is satisfiable, then the solver can also returns a model, which assigns to each variable $\anivarz_{i, (q, a, q', \myvec{v})}$ a natural number.
+If an SMT solver reports that the aforementioned formula is satisfiable, then the solver can also return a model, which assigns to each variable $\anivarz_{i, (q, a, q', \myvec{v})}$ a natural number.
 %For each $i \in [n]$ and each transition $(q, a, q', \myvec{v})$ in $\cB_i$, let us use $nt_{i, (q, a, q', \myvec{v})}$ to denote the value of $\anivarz_{i, (q, a, q', \myvec{v})}$ in the model.
@@
 If $\{(q, a, q', \myvec{c}) \mid \lambda_i((q, a, q', \myvec{c})) > 0\} \not \subseteq \cT_q$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_i$ will be found and meanwhile the constraint on the number of transitions enforced by $\lambda_i$ is satisfied.
-Therefore, in this case, the search process for $\cB_i$ in this direction halts and the search process is backtracked.
+Therefore, in this case, the search process for $\cB_i$ in this direction halts, and the search process is backtracked.
 
@@
 In the section \ref{sec:algorithm}, we present an algorithm to solve the $\cefadec$ problem.
-The algorithm computes existential LIA formulas and then uses SMT solver to solve it.
-However, this procedure only anwser the question whether the language of the regex is empty or not.
+The algorithm computes existential LIA formulas and then uses an SMT solver to solve them.
+However, this procedure only answers the question of whether the language of the regex is empty or not.
 If the language is not empty, we need to find a word in the language in practice.
-In our preivous paper \cite{Denghang2023}, we do not explicitly present the algorithm to find a word in the language because of the space limitation.
-We have used a naive approach which randomly searching the CEFAs by the depth-first search, based on the regesiters values obtained from solving the existential LIA formula.
-However, this approach is not efficient when the regexes is non-regesiter-representable.
-Suppose that there are $n$ registers whose values are $r_1,\cdots, r_n$ respectively in the CEFA, we may visit each transition $O(r_1*r_2\cdots *r_n)$ times during the search.
+In our previous paper \cite{Denghang2023}, we do not explicitly present the algorithm to find a word in the language because of space limitation.
+We used a naive approach, which randomly searched the CEFAs by the depth-first search based on the register values obtained from solving the existential LIA formula.
+However, this approach is not efficient when the regexes are non-register-representable.
+Suppose that there are $n$ registers whose values are $r_1,\cdots, r_n$ respectively in the CEFA.
+We may visit each transition $O(r_1*r_2\cdots *r_n)$ times during the search.
 To relieve this problem, we present a heuristic to find a word in the language as follows.
@@
 We use $\myvec{R}$ to denote the vector and use $\eta((q, a, q', \myvec{v}))$ to denote the parikh image of $\aut$.
-Then the transitions times visited by the accepted stirng is obtained from the following formula:
+Then the transition times visited by the accepted string are obtained from the following formula:
 $$ \sum \limits_{(q, a, q', \myvec{v})\in \delta} \eta((q, a, q', \myvec{v}))\myvec{v} = \myvec{R}$$
@@
 \noindent
-\emph{Step 2. (Prune the search tree early by the transitions times during the search process).}
+\emph{Step 2. (Prune the search tree early by the transition times during the search process).}
 
-After computing the transitions times visited by the accepted string, we prune the search tree of the CEFA based on the transitions times.
+After computing the transition times visited by the accepted string, we prune the search tree of the CEFA based on the transition times.
 The idea is that we only visit the state which is able to reach all transitions need to be visited.
 Other states are deleted from the CEFA so that we can reduce the search space.
-Note that the transitions times is updated during the search process so the search space is reduced dynamically. The presudo code is presented in Algorithm~\ref{alg:findword}.
+Note that the transition times are updated during the search process, so the search space is reduced dynamically. The pseudo-code is presented in Algorithm~\ref{alg:findword}.
 
@@
 $tmap$ maps each transition to its remaining visited times.
-Stack $todo$ contains states need to be visited, their corresponding transitions-times maps and current word.
-Set $visited$ is used to store the visited state with corresponding map.
+Stack $todo$ contains states need to be visited, their corresponding transitions-times maps and the current word.
+Set $visited$ is used to store the visited state with the corresponding map.
 $todo$ is initialized with the initial state of the CEFA, the input map $tmap$ and an empty word (line 2).
@@
 For each transition $(q, a, q', \myvec{v})$ whose remaining times are greater than $0$, the procedure decreases the remaining times by $1$ (line 10) and checks whether $(q', tmap')$ is not visited and $tmap'$ is reachable from $q'$ (line 11).
-We say that \textit{$tmap'$ is reachable from $q'$} if each transition $t$ with $tmap'(t)> 0$ are reachable from the state $q'$.
-The reachability check (Algorithm~\ref{alg:isReachable}) is vital to prune the search space and reduce the search time .
+We say that \textit{$tmap'$ is reachable from $q'$} if each transition $t$ with $tmap'(t)> 0$ is reachable from the state $q'$.
+The reachability check (Algorithm~\ref{alg:isReachable}) is vital to prune the search space and reduce the search time.
 If the state $q'$ is not visited and $tmap'$ is reachable from $q'$, then we push $(q', tmap', w\cdot a)$ to $todo$ and add $(q', tmap')$ to $visited$ to continue the search(line 12-13).
@@
 
-  In Algorithm~\ref{alg:isReachable}, all transitions reachable from the state $q'$ is computed and saved to $qreach$.
+ In Algorithm~\ref{alg:isReachable}, all transitions reachable from the state $q'$ are computed and saved to $qreach$.
 If $qreach$ covers all transitions with positive times in the input map $tmap$, then we say that $tmap$ is reachable from $q'$ and the procedure \textsc{isReachable} returns true, otherwise it returns false.

### 2024-06-02 2024-5-13/sections/implementation.tex
fix the syntax error in implementation

@@
 
-We implemented the procedures and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
+We implemented the procedures and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen} on top of OSTRICH, resulting in a string solver called $\ostrichrecl$. 
 %
@@
 % We do experiments to compare the performance of $\ostrichrecl$ with the state-of-the-art string solvers.
-Moreover, in order to know whether $\ostrichrecl$ is good at solving string constraints with large counting and length, we extract \denghang{todo} instances with large bounds out of , and compare the performance of $\ostrichrecl$ with the other solvers on these instances.
+Moreover, in order to know whether $\ostrichrecl$ is good at solving string constraints with large counting and length, we extract \denghang{todo} instances with large bounds out of, and compare the performance of $\ostrichrecl$ with the other solvers on these instances.
 Finally, we empirically justify the technical choices made in the decision procedure of Section~\ref{subsec:cefadec} by comparing $\ostrichrecl$ with the following two variants of $\ostrichrecl$: $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$, where $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$ are obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e.
@@
 %The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
-In our statistics, while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e. greater than or equal to $50$).
+In our statistics, while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e., greater than or equal to $50$).
 %Although most upper bounds are small, about two thousand of them are still greater than 50.
@@
 
-At first, we do experiments to evaluate the effectiveness of the automata size-reduction techniques (i.e.
-Step 2) in Section~\ref{sec:algorithm}.
+At first, we do experiments to evaluate the effectiveness of the automata size-reduction techniques (i.e., Step 2) in Section~\ref{sec:algorithm}.
 Then we justify our technical choices of reducing the satisfiability problem to that of LIA formulas and resort to the SMT solvers to solve them.
@@
 %We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. 
-We also evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}, i.e.
-the optimizations for the nesting of counting operators as well as the nesting of counting operators and a complement operator.
+We also evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}, i.e., the optimizations for the nesting of counting operators as well as the nesting of counting operators and a complement operator.
 Finally, we evaluate the effectiveness of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}.
@@
 Therefore, we consider the NestC benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes.
-The NestC benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}.
+The NestC benchmark experiment results are shown in Table~\ref{tab:results_heuristic_complex}.
 We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.
@@
 The experiment results can be found in Table~\ref{tab:results_model-gen}.
-From the results, we can see that compared to $\ostrichrecl$, $\ostrichrecl_{\rm -MODEL}$ solves 349 less instances and is 23\% slower on average (3.57s versus 2.88s).
+From the results, we can see that compared to $\ostrichrecl$, $\ostrichrecl_{\rm -MODEL}$ solves 349 fewer instances and is 23\% slower on average (3.57s versus 2.88s).
 As a result, the optimization for the model generation does improve the performance, especially when the sizes of the CEFAs are huge.

### 2024-06-02 2024-5-13/sections/introduction.tex
fix the syntax error in introduction

@@
 The string-length function is modeled by cost registers as well.
-The satisfiability of RECL constraints is reduced to the nonemptiness problem of CEFA w.r.t.
+The satisfiability of RECL constraints is reduced to the non-emptiness problem of CEFA w.r.t.
 a linear integer arithmetic (LIA) formula.
 According to the results from~\cite{atva2020}, an LIA formula can be computed to represent the potential values of registers in CEFA.
-Thus, the nonemptiness of CEFA w.r.t.
+Thus, the non-emptiness of CEFA w.r.t.
 LIA formulas can be reduced to the satisfiability of LIA formulas, which is then tackled by off-the-shelf SMT solvers.
-Moreover, we propose techniques to reduce the sizes (i.e.
-the number of states and transitions) of CEFA, in order to achieve better performance.
+Moreover, we propose techniques to reduce the sizes (i.e., the number of states and transitions) of CEFA in order to achieve better performance.
 %
@@
 The Trau tool focuses on string constraints involving flat regular languages and string-length function and solves them by computing LIA formulas that define the Parikh images of flat regular languages~\cite{z3trau}.
-The Slent tool solves the string constraints involving string-length function by encoding them into so-called length-encoded automata, then utilizing symbolic model checkers to solve their nonemptiness problem~\cite{WC+18}.
+The Slent tool solves the string constraints involving string-length function by encoding them into so-called length-encoded automata, then utilizing symbolic model checkers to solve their non-emptiness problem~\cite{WC+18}.
 However, neither Trau nor Slent supports counting operators explicitly, in other words, counting operators in regexes should be unfolded before solved by them.
@@
 Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regexes with counting.
-Nevertheless, the nonemptiness problem of these automata was not considered, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
+Nevertheless, the non-emptiness problem of these automata was not considered, and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
 
@@
 \item To deal with the issue that the satisfiability of LIA formulas can be solved, but models of the original RECL constraints cannot be generated, we propose techniques to optimize the model generation process.
-\item The benchmarks are extended to cove the situations that the counting operators are nested with some other counting operators or complement operators, and the experiments are extended accordingly.
+\item The benchmarks are extended to cover the situations where the counting operators are nested with some other counting operators or complement operators, and the experiments are extended accordingly.
 \end{itemize}

### 2024-06-02 2024-5-13/sections/algorithms.tex
commit the paper extended by setta2023
change nonemptiness to non-emptiness

--- 2023-10-20 2023-1-19/sections/algorithms.tex
@@
 %\begin{proof}
-%  The lower bound follows from the fact that the nonemptiness problem of the intersection of NFAs is PSPACE-complete \cite{pspace_int}.
+%  The lower bound follows from the fact that the non-emptiness problem of the intersection of NFAs is PSPACE-complete \cite{pspace_int}.
 For the upper bound, \cite{atva2020} showed that $\cefadec$ is in PSPACE by reducing it to monotonic counter machines.
@@
 At first, we show how to construct a CEFA from a regex where counting operators may occur.
+Our approach is based on Thompson's construction~\cite{Thompson1968} for regexes without counting operators.
 Let us start with register-representable regexes defined in the sequel.
@@
 Let $\Lambda_{x_i} = \{\aut_{i,0}, \aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for each $i \in [n]$, and $\varphi'_2 \equiv \varphi_2[r_{1,0}/|x_1|, \cdots, r_{n,0}/|x_n|]$.
-Then the satisfiability of $\varphi$ is reduced to the nonemptiness of CEFAs in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t.
+Then the satisfiability of $\varphi$ is reduced to the non-emptiness of CEFAs in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t.
 $\varphi'_2$.
@@
 
-After Step 1, the nonemptiness of CEFAs in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t. $\varphi$ is reduced to the nonemptiness of CEFAs in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t. $\varphi$.
+After Step 1, the non-emptiness of CEFAs in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ w.r.t.
+$\varphi$ is reduced to the non-emptiness of CEFAs in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+$\varphi$.
 
@@
 
-Therefore, to solve the nonemptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+Therefore, to solve the non-emptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
 $\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ to represent the Parikh images of $\cU_{\cB_1}$, $\cdots$, $\cU_{\cB_n}$ respectively, where $\fZ_{\costset_{\cB_i}} = \{\anivarz_{i,\myvec{v}} \mid \myvec{v} \in \costset_{\cB_i}\}$ for $i \in [n]$, and solve the satisfiability of the following existential LIA formula

### 2024-06-02 2024-5-13/sections/overview.tex
change nonemptiness to non-emptiness

--- 2023-10-20 2023-1-19/crv/sections/overview.tex
@@
 
-Finally, the satisfiability of the original string constraint is reduced to the nonemptiness of the CEFA $\aut\equiv \aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut$, so that the resulting registers values $(v_1, v_2, v_3, v_4)$ satisfy both $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $\varphi$.
-It is not hard to observe that the nonemptiness of $\aut$ with respect to $\varphi$ is independent of the characters of $\aut$.
+Finally, the satisfiability of the original string constraint is reduced to the non-emptiness of the CEFA $\aut\equiv \aut_1 \cap \aut_2 \cap \aut_3$ with respect to the LIA formula $\varphi \equiv r_4 > 120$, that is, whether there exist $w \in \Sigma^*$ and $(v_1, v_2, v_3, v_4) \in \Int^4$ such that $w$ is accepted by $\aut$, so that the resulting registers values $(v_1, v_2, v_3, v_4)$ satisfy both $1 \le v_1 \le 60\wedge 1 \le v_2 \le 60 \wedge 0 \le v_3 \le 60$ and $\varphi$.
+It is not hard to observe that the non-emptiness of $\aut$ with respect to $\varphi$ is independent of the characters of $\aut$.
 Therefore, the characters in $\aut$ can be ignored, resulting into an NFA $\cB$ over the alphabet $\costset$, where $\costset$ is the set of vectors from $\Int^4$ occurring in the transitions of $\aut$ (see Figure~\ref{fig:overview:product:reduced}(a)).

### 2024-06-02 2024-5-13/sections/heuristic.tex
fix the syntax error in heuristics

@@
 
-Moreover, propose a method to prune the search space further.
+Moreover, we propose a method to prune the search space further.
 Let $i \in [n]$.
@@
 If $\{(q, a, q', \myvec{c}) \mid \lambda_i((q, a, q', \myvec{c})) > 0\} \not \subseteq \cT_q$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_i$ will be found and meanwhile the constraint on the number of transitions enforced by $\lambda_i$ is satisfied.
-Therefore, in this case, the search process for $\cB_i$ in this direction halts, and the search process is backtracked.
+Therefore, in this case, the search process for $\cB_i$ halts and is backtracked.
 

### 2024-06-02 2024-5-13/sections/algorithms.tex
fix the out-of-date data in section Soliving RECL constraints

@@
 For instance, $(a^{\{2, 6\}} \concat b^*)^{\{2,\infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa+aaaa) \concat b^*)^{\{2, \infty\}}$.
-The unfoldings of the inner counting operators of non-register-representable regexes incur an exponential blowup in the worst case.
-Nevertheless, those regexes occupy only 5\% of the 48,843 regexes that are collected from the practice (see Section~\ref{sec:bench}).
-Moreover, the unfoldings are partial in the sense that the outmost counting operators are not unfolded.
-It turns out that our approach can solve almost all the RECL constraints involving these 48,843 regexes, except 181 of them (See Figure~\ref{fig:table_overall_eval}). 
 %$(a^{\{2, 6\}} \concat b^*) \setminus (a + b)^{\{4, \infty\}}$ is transformed into $(aa(\varepsilon + a + aa + aaa + aaaa) \concat b^*) \setminus (a+b)(a+b)(a+b)(a+b)(a+b)^*$.

### 2024-11-26 jsa2024_rebuttal.md
push the comments of jsa2024

# An Efficient String Solver for String Constraints with Regex-Counting and String-Length

## Reviewer #1 
### Summary
The paper extends the string solver OSTRICH and the underlying decision procedure with a capability of efficient handling regular expressions with counting (such "something{1000}"), which can e asily become a performance bottleneck for string solvers.

The idea is to encode counting in automata using simple counters (the idea has been extensively studied in regular pattern matching, but the application in string solving is new).

This neatly fits into the framework for handling string length constraints using so called cost enriched automata, introduced earlier by some of the authors (when the counting is not nested and not under a complement). The counters are never expanded and are ultimately discharged and solved in the form of LIA formulae. The state space blow up that would otherwise occur because of counting is hence avoided. The paper confirms this experimentally, by showing that a version of OSTRICH extended with this techniques is far superior on benchmarks with counting than the original, and often better than most of the state of the art solvers.

The technique is relevant also for other methods than that of OSTRICH.

Overall, I think this is a nice paper. It also has sufficient amount of new content respective to the conference version (optimizations and extended experiment).

### Comments
I have only some mild criticism and suggestions:

I think that the fact that Kleene star occurs in about 70% of Python projects is cited in a misleading way (page 2, bottom). It sounds as an argument for relevance of this work, however, the presented techniques do not improve handling of Kleene star (or plus).
They do improve handling of "the other forms of counting", but that is only the 20%.

On the other hand, please, provide a link to the benchmark if at all possible. Unlike the previous point, I consider this relatively important (reproducibility, extensibility of the experiment, the benchmark could be used by others).

I think that CEFA are a variation on the Parikh automata. It would be good to mention the relation in Related work.

Reduction of CEFA - would something as simulation reduction work too? It might be better than determinization and minimization. Does determinization sometimes blow up?

The Overapproximation on page 22. I am wandering about the transition from an original final state to qs that increments the new counter, and the subsequent self loop on qs. Does this also cause overapproximation? All extensions of the originally accepted words are accepted? If yes, it would deserve a comment.

I had troubles to understand the section about optimized model generation. Maybe stating what the technical problem that it is solving is in a more dumb proof way would help.

The experimental counting constraints and length constraints you introduce, e.g. those on top of page 26. Could you comment a bit more on what is the ratio of introducing exactly these? Is it motivated by something practical?

I would be very much interested in how Z3-Noodler works on the benchmark. The p aper is fine as is, I do not insist on this at all, the conference version appeared before Noodler and the current experimental results show the merit of the proposed techniques clearly enough. But in case the authors have nothing better to do and seek ways of fighting boredom, it would be interesting to see the comparison.

Typos and little things:
page 2, third line - "...which is possibly ..." is not a sentence
page 2, second paragraph "3040%"
page 12, bottom: the automata A1 and A2 have a single initial state, but the definition works with a set of initial states. This may occur on more places.
The font in table 5 is strangely huge.
page 15, the modified Thompson construction. Maybe one should mention that similar constructions, and also alternatives, were proposed elsewhere (the papers on pattern matching and automata with counters might have references).

## Reviewer #2 
### Summary
Counting is a frequently utilized feature in regular expressions (regex) that quantifies the number of matches for sub-patterns. This paper presents an automata-based approach to addressing string constraints that involve regex counting and string length. The main idea is to symbolically represent the counting operators using registers within automata, rather than explicitly unfolding them, thereby mitigating the state explosion problem. Experimental results demonstrate that this approach achieves superior performance compared to state-of-the-art solvers.

### Comments
Line 2, Para 2, Page 2: "3040%" should be "30-40%"

Better to place Section 3 (Preliminaries) before Section 2 (Overview), as some notation introduced in Section 2 is explained in Section 3.

Line 7, Para 3, Page 11: "one of the following holds …" . Better to rephrase the conditions, as they are likely to lead to misund erstandings.

Para 2, Page 14: the register component is absent for the concatenation.

Para -1, Page 18: better to explain how to solve the satisfiability of the formula and derive a solution, (even though I found that it is discussed in Section 8).

Para 3, Page 20: Firstly, some U_{A_{ufld_{*1*}(e)}} should be U_{A_{ufld_{*2*}(e)}}, while some U_{A_{ufld_{*2*}(e)}} should be U_{A_{ufld_{*1*}(e)}}. Please check this carefully.
Secondly, what is r'?
Thirdly, I did not follow why the form (0,…,0,1,0,…,0), as for the union of two CEFAs, two registers as well as two kinds of transitions (\overrightarrow{v1},\overrightarrow{0},1,0) and (\overrightarrow{0},\overrightarrow{v2},0,1) are introduced.

Sec 7.2, Page 21: better to explain how to combine these two approximation. By the way, utilizing an under-approximation may result in a false negative, whereas employing an over-approximation could lead to a fal se positive. Please engage in a discussion regarding this matter.

Sec 9, Page 26: It is advisable to conduct a comprehensive analysis regarding the complexity of problem instances for further clarification, with respect to Figure 4. For example, one should consider the depth of counting nesting, the number of regex variables (is it sufficient in practice to utilize just a single variable x?), as well as constraints associated with string length—not limited to a singular condition such as |x| > 10/50.

### 2024-12-12 jsa2024_rebuttal.md
first finished edition

@@
-# An Efficient String Solver for String Constraints with Regex-Counting and String-Length
+## Reduction of CEFA - would something as simulation reduction work too? It might be better than determinization and minimization. Does determinization sometimes blow up?
 
-## Reviewer #1 
-### Summary
-The paper extends the string solver OSTRICH and the underlying decision procedure with a capability of efficient handling regular expressions with counting (such "something{1000}"), which can e asily become a performance bottleneck for string solvers.
+We have not tried something like simulation minimization, but it is interesting advice.
+Determinization in reducing automata sizes rarely blows up because most vectors are the same, except for those with counting, since we do determinization only at the vector level.
 
-The idea is to encode counting in automata using simple counters (the idea has been extensively studied in regular pattern matching, but the application in string solving is new).
+## Thirdly, I did not follow why the form (0,…,0,1,0,…,0), as for the union of two CEFAs, two registers as well as two kinds of transitions (\overrightarrow{v1},\overrightarrow{0},1,0) and (\overrightarrow{0},\overrightarrow{v2},0,1) are introduced.
 
-This neatly fits into the framework for handling string length constraints using so called cost enriched automata, introduced earlier by some of the authors (when the counting is not nested and not under a complement).
-The counters are never expanded and are ultimately discharged and solved in the form of LIA formulae.
-The state space blow up that would otherwise occur because of counting is hence avoided.
-The paper confirms this experimentally, by showing that a version of OSTRICH extended with this techniques is far superior on benchmarks with counting than the original, and often better than most of the state of the art solvers.
-
-The technique is relevant also for other methods than that of OSTRICH.
-
-Overall, I think this is a nice paper. It also has sufficient amount of new content respective to the conference version (optimizations and extended experiment).
-
-### Comments
-I have only some mild criticism and suggestions:
-
-I think that the fact that Kleene star occurs in about 70% of Python projects is cited in a misleading way (page 2, bottom).
-It sounds as an argument for relevance of this work, however, the presented techniques do not improve handling of Kleene star (or plus).
-They do improve handling of "the other forms of counting", but that is only the 20%.
-
-On the other hand, please, provide a link to the benchmark if at all possible.
-Unlike the previous point, I consider this relatively important (reproducibility, extensibility of the experiment, the benchmark could be used by others).
-
-I think that CEFA are a variation on the Parikh automata. It would be good to mention the relation in Related work.
-
-Reduction of CEFA - would something as simulation reduction work too? It might be better than determinization and minimization. Does determinization sometimes blow up?
-
-The Overapproximation on page 22.
-I am wandering about the transition from an original final state to qs that increments the new counter, and the subsequent self loop on qs.
-Does this also cause overapproximation?
-All extensions of the originally accepted words are accepted?
-If yes, it would deserve a comment.
-
-I had troubles to understand the section about optimized model generation. Maybe stating what the technical problem that it is solving is in a more dumb proof way would help.
-
-The experimental counting constraints and length constraints you introduce, e.g.
-those on top of page 26.
-Could you comment a bit more on what is the ratio of introducing exactly these?
-Is it motivated by something practical?
-
-I would be very much interested in how Z3-Noodler works on the benchmark.
-The p aper is fine as is, I do not insist on this at all, the conference version appeared before Noodler and the current experimental results show the merit of the proposed techniques clearly enough.
-But in case the authors have nothing better to do and seek ways of fighting boredom, it would be interesting to see the comparison.
-
-Typos and little things:
-page 2, third line - "...which is possibly ..." is not a sentence
-page 2, second paragraph "3040%"
-page 12, bottom: the automata A1 and A2 have a single initial state, but the definition works with a set of initial states. This may occur on more places.
-The font in table 5 is strangely huge.
-page 15, the modified Thompson construction.
-Maybe one should mention that similar constructions, and also alternatives, were proposed elsewhere (the papers on pattern matching and automata with counters might have references).
-
-## Reviewer #2 
-### Summary
-Counting is a frequently utilized feature in regular expressions (regex) that quantifies the number of matches for sub-patterns.
-This paper presents an automata-based approach to addressing string constraints that involve regex counting and string length.
-The main idea is to symbolically represent the counting operators using registers within automata, rather than explicitly unfolding them, thereby mitigating the state explosion problem.
-Experimental results demonstrate that this approach achieves superior performance compared to state-of-the-art solvers.
-
-### Comments
-Line 2, Para 2, Page 2: "3040%" should be "30-40%"
-
-Better to place Section 3 (Preliminaries) before Section 2 (Overview), as some notation introduced in Section 2 is explained in Section 3.
-
-Line 7, Para 3, Page 11: "one of the following holds …" . Better to rephrase the conditions, as they are likely to lead to misund erstandings.
-
-Para 2, Page 14: the register component is absent for the concatenation.
-
-Para -1, Page 18: better to explain how to solve the satisfiability of the formula and derive a solution, (even though I found that it is discussed in Section 8).
-
-Para 3, Page 20: Firstly, some U_{A_{ufld_{*1*}(e)}} should be U_{A_{ufld_{*2*}(e)}}, while some U_{A_{ufld_{*2*}(e)}} should be U_{A_{ufld_{*1*}(e)}}. Please check this carefully.
-Secondly, what is r'?
-Thirdly, I did not follow why the form (0,…,0,1,0,…,0), as for the union of two CEFAs, two registers as well as two kinds of transitions (\overrightarrow{v1},\overrightarrow{0},1,0) and (\overrightarrow{0},\overrightarrow{v2},0,1) are introduced.
-
-Sec 7.2, Page 21: better to explain how to combine these two approximation.
-By the way, utilizing an under-approximation may result in a false negative, whereas employing an over-approximation could lead to a fal se positive.
-Please engage in a discussion regarding this matter.
-
-Sec 9, Page 26: It is advisable to conduct a comprehensive analysis regarding the complexity of problem instances for further clarification, with respect to Figure 4.
-For example, one should consider the depth of counting nesting, the number of regex variables (is it sufficient in practice to utilize just a single variable x?), as well as constraints associated with string length—not limited to a singular condition such as |x| > 10/50.
+This is mainly because the accepting condition is global.
+Assuming that we do not introduce new registers and transitions, we can not decide which accepting condition to use when arriving at a final state.

### 2024-12-12 2024-5-13/sections/algorithms.tex
first finished edition

@@
 CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t.
-$\varphi$ iff there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true.
+$\varphi$ iff there are \hdh{outputs} $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true.
 \end{observation}
@@
 
-\item there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true, 
+\item there are \hdh{outputs} $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true, 
 \item 
@@
 \emph{Step 3 (Computing Parikh images).} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
-Then we solve the satisfiability of the following formula,
+Then we \hdh{can utilize existing SMT solver like Z3 \cite{Z3}} to solve the satisfiability of the following formula,
 %

### 2024-12-12 2024-5-13/sections/cefa.tex
first finished edition

@@
 
-Let $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1, \alpha_1)$ and  $\aut_2 = (R_2, Q_2, \Sigma, \delta_2, q_{2,0}, F_2, \alpha_2)$ be two CEFA that share the alphabet. 
+Let $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1, \alpha_1)$ and  $\aut_2 = (R_2, Q_2, \Sigma, \delta_2, q_{2,0}, F_2, \alpha_2)$\footnote{\hdh{We use a single initial state for simplicity.
+A set of initial states can be transferred to a single one by introducing a new state $q_I$ and adding $\epsilon-$transition from $q_I$ to each initial state.}} be two CEFA that share the alphabet.
 Moreover, suppose that $R_1 \cap R_2 = \emptyset$ and $Q_1 \cap Q_2 = \emptyset$.
@@
 The \emph{union} of $\aut_1$ and $\aut_2$ is denoted by $\aut_1 \cup \aut_2$.
-Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).
-Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where
+Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).\hdh{This is mainly because the accepting condition is "global", i.e., the accepting condition is attached to the CEFA, not specific final state.} Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where
 \begin{itemize}
@@
 
-The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(\hdh{R'}, Q', \Sigma, \delta', I', F', \alpha')$, where $\hdh{R' = R_1\cup R_2,} Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
 From the construction,

### 2024-12-12 2024-5-13/sections/heuristic.tex
first finished edition

@@
 \item From the construction in Section~\ref{sec:algorithm}, 
-two NFAs $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignoring the characters.
-As a result, the alphabets of $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors  $\myvec{v}$ occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively.
-The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.
-Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
-Similarly for $\cU_{\aut_{\ufld_1(e)}}$.
+two NFAs $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignoring the characters.
+As a result, the alphabets of $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors \sout{$\myvec{v}$} occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively.
+\sout{The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.} \hdh{These integer vectors are of form $(0,\cdots,0,1,0,\cdots, 0)$ whose length is the number of registers.} Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
+Similarly for $\cU_{\aut_{\ufld_\hdh{2}(e)}}$.
 Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut_{\ufld_1(e)}}, \cU_{\aut_{\ufld_2(e)}}$ as $sz_1 = (\snum_1(e))^2 \cdot \rnum_1(e)$ and $sz_2 = (\snum_2(e))^2 \cdot \rnum_2(e)$ respectively.
@@
 Let $e=(e_1)^{\{m,n\}}$ be a regular expression where $e_1$ is a register-representable regular expression.
-Then we compute $\snum'_1(e_1)$ and $(\snum'_2(e_1), \rnum'_2(e_1))$ by a structural induction on $e_1$.
-Finally, let $(\snum_1(e), \rnum_1(e)) = (\snum'_1(e_1), 1)$ and $(\snum_2(e), \rnum_2(e)) = (\snum'_2(e_1), \rnum'_2(e_1))$.
+Then we compute $\snum'_1(e_1)$ and $(\snum'_2(e_1), \rnum'_2(e_1))$\hdh{(TODO:Change all the $num'$ to $num$, to avoid ambiguity)} by a structural induction on $e_1$, \hdh{in condition, $\rnum_1(e_1)$ is set to $1$.} \sout{Finally, let $(\snum_1(e), \rnum_1(e)) = (\snum'_1(e_1), 1)$ and $(\snum_2(e), \rnum_2(e)) = (\snum'_2(e_1), \rnum'_2(e_1))$.}
 \begin{itemize}
@@
 %
+  \item \hdh{If $e_1 = a$, then $\snum'_1(e_1) = 1$ and ($\snum'_2(e_1), \rnum'_2(e_1)) = (n, 0)$.}
  %
@@
 Without loss of generality, we can assume that there are no transitions out of $F$ in $\aut_{e_1}$.
-If this is not the case, then a new state $q_f$ can be introduced to transform $\aut_{e_1}$ into a CEFA satisfying this constraint, where $q_f$ is the unique accepting state.
+If this is not the case, then a new state $q_f$ can be introduced to transform $\aut_{e_1}$ into a CEFA satisfying this constraint, where $q_f$ is the unique accepting state.\footnote{\hdh{Note that if any initial states are in $F$, a new state $q_I$ without transitions out can be introduced and add to $F$, to accept empty string.
+Then we can remove all original initial states out of $F$.}}
 Then we define $\cB= (R \cup \{r'\}, Q \cup \{q_s\}, \Sigma, \delta', I, Q \cup \{q_s\}, \alpha')$, where
@@
 Nevertheless, according to the construction, $w$ is accepted by $\cB$, witnessed by the run of $\aut_{e_1}$ that ends at a non-final state.
+
+\hdh{\paragraph*{Combination of under- and over-approximation}
+Since these two types of approximation influence each other, we separate them apart and run them parallelly.
+}
 
@@
 
-Recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
+\hdh{The naive approach of finding satisfied string models is to search the accepted words on CEFAs based on the integer models of vectors, which causes an exponential blow-up of searching space.
+Specifically, } recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
 \[
@@
 As a result, we obtain a model of $\varphi$ in the end.
+\hdh{In the worst case, we need search O($\prod_{i=0}^{n} \amodel(\anivarz_{i, \myvec{v}})$) times to find an accepted word.}
 
 It turns out that this model generation process is inefficient, mainly due to the fact that the information about the occurrences of vectors $\myvec{v}$ in $\cB_i$ in the searching process is too coarse.
-In the sequel, we would like to refine this process by using the LIA formulas to obtain the information about the number of occurrences of transitions, instead of just the occurrences of integer vectors, and utilize this information to guide the search process.
+In the sequel, we would like to refine this process by using \sout{the LIA formulas to obtain the information about} the number of occurrences of transitions, instead of just the occurrences of integer vectors, \sout{and utilize this information} to guide the search process.
 Specifically, for each $i \in [n]$ and each transition $(q, a, q', \myvec{v})$ in $\cB_i$, we introduce an integer variable $\anivarz_{i, (q, a, q', \myvec{v})}$ to denote the number of occurrences of the transition, and solve the satisfiability of the following formula,

### 2024-12-12 2024-5-13/sections/implementation.tex
first finished edition

@@
 \[(e_1^{\{m_1, n_1\}}e_2^{\{m_2, n_2\}}e_3^{\{m_3, n_3\}}e_4^{\{m_4, n_4\}})^{\{m_5, n_5\}},\]
-such that $0 \leq m_i\leq n_i\leq 20$ for each $i \in [5]$ and $e_i$ contains no counting operators for each $i  \in [4]$,
+such that $0 \leq m_i\leq n_i\leq 20$ \hdh{is chosen randomly} for each $i \in [5]$ and $e_i$ contains no counting operators for each $i  \in [4]$,
 moreover, 
@@
 \[x \in e_{comp1} \wedge x \in e_{comp2} \wedge x \in e_{sani} \wedge |x| > 50, \]
-where both $e_{comp1}$ and $e_{comp2}$ are of the form $\overline{e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}} e_4^{\{m_4, n_4\}}}$, such that for each $i \in [4]$, $20 \leq m_i\leq n_i\leq 1000$ and $e_i$ contains no counting operators.
+where both $e_{comp1}$ and $e_{comp2}$ are of the form $\overline{e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}} e_4^{\{m_4, n_4\}}}$, such that for each $i \in [4]$, $20 \leq m_i\leq n_i\leq 1000$ \hdh{is chosen randomly} and $e_i$ contains no counting operators.
 Note that two regular expressions $e_{comp1} $ and $e_{comp2}$ are introduced to have a better balance between the numbers of satisfiable and unsatisfiable instances.
@@
 
-In total, the NestC benchmark suite contains 1000 instances.
+In total, the NestC benchmark suite contains 1000 \hdh{tough} instances \hdh{which may not be practical in real-world programs}.
 
@@
 \begin{table}[htbp]
+  \centering
   \import{tables}{table_heuristics_model_gen.tex}

### 2024-12-12 2024-5-13/sections/introduction.tex
fix the syntax error in introduction
first finished edition

@@
 Regular expressions (regex for short) and the string-length function are widely used in string-manipulating programs.
-According to the statistics from \cite{CS16,DCSL18,WS18}, regexes are used in about 30–40\% of Java, JavaScript, and Python software projects.
-Moreover, string-length occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}. 
-As a result, most of the aforementioned string constraint solvers support both regexes and string-length function.
-Moreover, specialized algorithms have been proposed to solve such string constraints efficiently (see e.g.
-\cite{LTR+15,BD+23}).
+\sout{According to the statistics from \cite{CS16,DCSL18,WS18}, regexes are used in about 30–40\% of Java, JavaScript, and Python software projects.
+Moreover, string-length occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}.} \hdh{Specifically, regexes are used in about 30–40\% of Java, JavaScript, and Python software projects, while string-length occupies 78\% of the occurrences of string operations in 18 Javascript applications\footnote{According to the statistics from \cite{CS16,DCSL18,WS18,malware_detection_3_kudzu}.}.
+As a result, most of the aforementioned string constraint solvers support both regexes and string-length function, and specialized algorithms have been proposed to solve such string constraints efficiently (see e.g.
+\cite{LTR+15,BD+23}).}
 
@@
 For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
-Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ is equivalent to $a^{\{0,\infty\}}$ and $a^+$ is equivalent to $a^{\{1,\infty\}}$.
-Counting is a frequently used feature of regexes.
-According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while other forms of counting occur in more than 20\% of them.
+Note that the Kleene star and the Kleene plus operator are special cases of counting, i.e., $a^*$ is equivalent to $a^{\{0,\infty\}}$ and $a^+$ is equivalent to $a^{\{1,\infty\}}$.
+Counting is a frequently used feature of regexes \hdh{:}\sout{According to the statistics from \cite{CS16},} kleene star/plus occur in more than 70\% of 1,204 Python projects, while other forms of counting occur in more than 20\% of them\hdh{\footnote{According to the statistics from \cite{CS16}.}}.
 Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints containing regexes with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function at least.
+\hdh{To the best of our knowledge, there is no such solver optimized for both counting and string-length.}
 
-Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting and length bounds are large.
+\sout{Nevertheless, }The aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting and length bounds are large.
 For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 120 seconds,
@@
  %
-\item We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$.
-Finally, we utilize a collection of benchmark suites comprising 49,843 problem instances in total to evaluate the performance of $\ostrichrecl$.
+\item We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$\footnote{The tool is available as open source at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024}.}.
+Finally, we utilize a collection of benchmark suites comprising 49,843 problem instances\footnote{The benchmark suites are available at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024/zaligvinder/models/jsa2024}.} in total to evaluate the performance of $\ostrichrecl$.
 The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers (see Table~\ref{tab:table_overall_eval}-\ref{tab:results_model-gen}).
-For instance, $\ostrichrecl$ solves 49,638 out of 49,843 instances, while the best state-of-the-art solvers solve only 47,721 instances.
+For instance, $\ostrichrecl$ solves 49,638 out of 49,843 instances, while the best state-of-the-art solver solve only 47,721 instances.
 We also do experiments to justify some of our technical choices and evaluate the performance of the optimizations.
@@
 Therefore, cost registers in CEFAs are more like counters in counter automata/machines~\cite{Minsky67}, that is, CEFAs can be obtained from counter machines by removing transition guards and adding accepting conditions.
+\hdh{CEFAs can also be considered as Parikh automata \cite{parikh_automaton_2003} equipped with the ability to decrease counters.}
 %
@@
 \emph{Structure.} 
-The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper. Section~\ref{sec:pre} introduces the preliminaries. 
+The rest of this paper is structured as follows: \sout{Section~\ref{sec:overview} gives an overview of the approach in this paper.
+Section~\ref{sec:pre} introduces the preliminaries.} \hdh{Section~\ref{sec:pre} introduces the preliminaries.
+Section~\ref{sec:overview} gives an overview of the approach in this paper.}
 Section~\ref{sec:recl} presents the syntax and semantics of RECL. 

### 2024-12-12 2024-5-13/sections/recl.tex
commit the paper extended by setta2023
add some comments
first finished edition

--- 2023-10-19 2023-1-19/sections/recl.tex
@@
 \begin{figure}[h]
+\vspace{-2mm}
   \centering
@@
     \varphi & ::= & x\in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi                                              & \mbox{formulas}            \\
-    \regex &::= & \emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \overline{\regex} \mid \regex \setminus \regex \mid \regex^{\{m,n\}} \mid \regex^{\{m,\infty\}} \mid (e) & \mbox{regexes} \\
+    \regex &::= & \emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid  \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid \\
+    & & \ \ \overline{\regex} \mid \regex \setminus \regex \mid \regex^{\{m,n\}} \mid \regex^{\{m,\infty\}} \mid (e) & \mbox{regexes} \\
     t &::= & n \mid \anivar \mid  |x| \mid t - t \mid t + t                                                                    & \mbox{integer terms}
@@
   \caption{Syntax of RECL }\label{fig:syntax}
-\vspace{-4mm}
+\vspace{-2mm}
 \end{figure}
+
 Moreover, for $S \subseteq \Sigma$ with $S = \{a_1, \cdots, a_k\}$, we use $S$ as an abbreviation of $a_1 + \cdots + a_k$.
@@
 A  mapping $\theta$ is said to satisfy $\varphi$, denoted by $\theta \models \varphi$, if one of the following holds: 
-$\varphi \equiv x \in \regex$ and $\theta(x) \in \Lang(\regex)$, 
+\hdh{(1) }$\varphi \equiv x \in \regex$ and $\theta(x) \in \Lang(\regex)$, 
 %
-$\varphi \equiv t_1\ \op\ t_2$ and $\theta(t_1)\ \op\ \theta(t_2)$, 
+\hdh{(2) }$\varphi \equiv t_1\ \op\ t_2$ and $\theta(t_1)\ \op\ \theta(t_2)$, 
 %
-$\varphi \equiv \varphi_1 \wedge \varphi_2$ and $\theta \models \varphi_1$ and $\theta \models \varphi_2$.
+\hdh{(3) }$\varphi \equiv \varphi_1 \wedge \varphi_2$ and $\theta \models \varphi_1$ and $\theta \models \varphi_2$.
 A RECL formula $\varphi$ is satisfiable if there is a mapping $\theta$ such as $\theta \models \varphi$.

### 2024-12-24 jsa2024_rebuttal.md
complete complexity analysis

@@
-## Reduction of CEFA - would something as simulation reduction work too? It might be better than determinization and minimization. Does determinization sometimes blow up?
+## Reviewer #1
+### Reduction of CEFA - would something as simulation reduction work too? It might be better than determinization and minimization. Does determinization sometimes blow up?
 
 We have not tried something like simulation minimization, but it is interesting advice.
-Determinization in reducing automata sizes rarely blows up because most vectors are the same, except for those with counting, since we do determinization only at the vector level.
 
-## Thirdly, I did not follow why the form (0,…,0,1,0,…,0), as for the union of two CEFAs, two registers as well as two kinds of transitions (\overrightarrow{v1},\overrightarrow{0},1,0) and (\overrightarrow{0},\overrightarrow{v2},0,1) are introduced.
+Yes, the determinization sometimes blow up because the size of the  result CEFA is exponential at worst case.
+
+### Thirdly, I did not follow why the form (0,…,0,1,0,…,0), as for the union of two CEFAs, two registers as well as two kinds of transitions (\overrightarrow{v1},\overrightarrow{0},1,0) and (\overrightarrow{0},\overrightarrow{v2},0,1) are introduced.
 
@@
 Assuming that we do not introduce new registers and transitions, we can not decide which accepting condition to use when arriving at a final state.
+We have added some notes at page 13.
+
+### The Overapproximation on page 22.
+I am wandering about the transition from an original final state to qs that increments the new counter, and the subsequent self loop on qs.
+Does this also cause overapproximation?
+All extensions of the originally accepted words are accepted?
+If yes, it would deserve a comment.
+
+No, this causes the autmoton reject some word supposing to be accepted. For example, the word

### 2024-12-24 2024-5-13/sections/algorithms.tex
complete complexity analysis

--- 2024-06-02 2024-5-13/sections/algorithms.tex
@@
 Then  the CEFA in $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are said to be nonempty w.r.t.
-$\varphi$ if there are assignments $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v_{i,j}}$
-such that $(\theta(x_i); \myvec{v_{i,j}}) \in \Lang(\aut_{i, j})$ and  $\varphi[(\myvec{v_{i,j}}/R_{\aut_{i,j}})]$ is true, for every $i \in [n], j \in [l_i]$.
+$\varphi$ if there are assignments $\theta: \{x_1, \cdots, x_n\} \rightarrow \Sigma^*$ and vectors $\myvec{v}_{i,j}$
+such that $(\theta(x_i); \myvec{v}_{i,j}) \in \Lang(\aut_{i, j})$ and  $\varphi[(\myvec{v}_{i,j}/R_{\aut_{i,j}})]$ is true, for every $i \in [n], j \in [l_i]$.
 \end{definition}
@@
 At first, we show how to construct a CEFA from a regex where counting operators may occur.
-Our approach is based on Thompson's construction~\cite{Thompson1968} for regexes without counting operators.
+\hdh{Glushkov’s construction~\cite{Gluskov61} and its variants~\cite{redos_lenka,HS+23,GKM23} convert a regex to a $\epsilon$-free automaton.
+In contrast, Thompson's construction~\cite{Thompson1968} results in an automaton with $\epsilon$-transitions but the algorithm is simpler and straightforward.
+}Our approach is based on Thompson's construction~\cite{Thompson1968} \hdh{and we remove $\epsilon$-transitions on the fly (See union at Section \ref{sec:automaton} and construction of counting operators below)}.
 Let us start with register-representable regexes defined in the sequel.
@@
 Then an occurrence of counting operators in $e$, say $(e')^{\{m,n\}}$ (or $(e')^{\{m, \infty\}}$), is said to be \emph{register-representable} if $(e')^{\{m,n\}}$ (or $(e')^{\{m, \infty\}}$) is not in the scope of a Kleene star, another counting operator, complement, or language difference in $e$.
-We say that $e$ is \emph{register-representable} if all occurrences of counting operators in $e$ are register-representable.
+We say that $e$ is \emph{register-representable} if and only if all occurrences of counting operators in $e$ are register-representable.
 For instance, $a^{\{2, 6\}} \cap a^{\{4, \infty\}}$ is register-representable, while $\overline{a^{\{2, 6\}}}$ and $(a^{\{2, 6\}})^{\{4,\infty\}}$ are not since $a^{\{2,6\}}$ is in the scope of complement and the counter operator $\{2, \infty\}$ respectively.
@@
 
-For non-register-representable regexes, we first transform them into register-representable regexes by unfolding all the non-register-representable occurrences of counting operators.
+For non-register-representable regexes, we first convert them into register-representable regexes by unfolding all the non-register-representable occurrences of counting operators.
 After that, we utilize the aforementioned procedure to construct CEFA.
@@
 
-In this section, we present a procedure to solve the $\cefadec$ problem: Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ where $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$.
+In this section, we present a procedure to solve the $\cefadec$ problem: Suppose that $x_1, \cdots, x_n$ are mutually distinct string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ are nonempty sets of CEFA over the same alphabet $\Sigma$ where $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots,$ $ \aut_{i, l_i}\}$ for every $i \in [n]$.
 Moreover, the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, and $\varphi$ is a LIA formula whose free variables are from $\bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
@@
 
-In the following steps, we reduce the non-emptiness of CEFAs in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
+In the following steps, we reduce the non-emptiness of CEFAs in $\Lambda'_{x_1}, \cdots, $ $\Lambda'_{x_n}$ w.r.t.
 $\varphi$ to the satisfiability of an LIA formula.
@@
 CEFA in $\Lambda'_{x_1} = \{\cB_1\}, \cdots, \Lambda'_{x_n} = \{\cB_n\}$ are nonempty w.r.t.
-$\varphi$ iff there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true.
+$\varphi$ iff there are \hdh{outputs} $\myvec{v}_1 \in \cefaout(\cB_1), \cdots, \myvec{v}_n \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v}_1/R_{\cB_{1}}, \cdots, $ $\myvec{v}_n/R_{\cB_{n}}]$ is true.
 \end{observation}
 
-Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA and $\costset_\aut = \{\myvec{v} \mid \exists q, a, q'.\ (q, a, q', \myvec{v}) \in \delta\}$. 
+Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA and $\costset_\aut = \{\myvec{v} \mid \exists q, a, q'.\ (q, a, q', \myvec{v}) $ $\in \delta\}$. 
 Moreover, let $\cU_\aut = (Q, \costset_\aut, \delta', I, F)$ be an NFA over the alphabet $\costset_\aut$ that is obtained from $\aut$ by dropping the accepting condition and ignoring the characters, that is, $\delta'$ comprises tuples $(q, \myvec{v}, q')$ such that $(q, a, q', \myvec{v}) \in \delta$ for $a \in \Sigma$.
@@
 
-\item there are $\myvec{v_{1}} \in \cefaout(\cB_1), \cdots, \myvec{v_{n}} \in \cefaout(\cB_n)$ such that $\varphi[\myvec{v_{1}}/R_{\cB_{1}}, \cdots, \myvec{v_{n}}/R_{\cB_{n}}]$ is true, 
+\item there are \hdh{outputs} $\myvec{v}_1 \in \cefaout(\cB_1), \cdots, \myvec{v}_n \in \cefaout(\cB_n)$ such that \\$\varphi[\myvec{v}_1/R_{\cB_{1}}, \cdots, \myvec{v}_n/R_{\cB_{n}}]$ is true, 
 \item 
@@
 Therefore, to solve the non-emptiness of CEFA in $\Lambda'_{x_1}, \cdots, \Lambda'_{x_n}$ w.r.t.
-$\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, \psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ to represent the Parikh images of $\cU_{\cB_1}$, $\cdots$, $\cU_{\cB_n}$ respectively, where $\fZ_{\costset_{\cB_i}} = \{\anivarz_{i,\myvec{v}} \mid \myvec{v} \in \costset_{\cB_i}\}$ for $i \in [n]$, and solve the satisfiability of the following existential LIA formula
+$\varphi$, it is sufficient to compute the existential LIA formulas $\psi_{\cU_{\cB_1}}(\fZ_{\costset_{\cB_1}}), \cdots, $ $\psi_{\cU_{\cB_n}}(\fZ_{\costset_{\cB_n}})$ to represent the Parikh images of $\cU_{\cB_1}$, $\cdots$, $\cU_{\cB_n}$ respectively, where $\fZ_{\costset_{\cB_i}} = \{\anivarz_{i,\myvec{v}} \mid \myvec{v} \in \costset_{\cB_i}\}$ for $i \in [n]$, and solve the satisfiability of the following existential LIA formula
 \[
@@
 \noindent
-\emph{Step 3 (Computing Parikh images).} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
-Then we solve the satisfiability of the following formula,
+\emph{Step 3 (Computing Parikh images \hdh{and derive a solution}).} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+\hdh{Subsequently, we can employ established SMT solvers to determine the satisfiability of the formula and derive a solution if it is satisfiable.
+The integer variable solutions are directly extracted from the partial model of the formula.
+The string variable solutions are obtained through indirect means, whose detailed methodology is discussed in Section \ref{sec-opt-sol-gen}.
+The final Parikh images are as follow :}
 %
@@
 %\qed
+
+\hdh{
+\subsection{Complexity Analysis of the $\reclsat$ Problem}
+The time complexity of regular expression equivalence with complement has been established as nonelementary~\cite{complementary_complexity_1974}.
+This directly implies that the $\reclsat$ problem exhibits a nonelementary lower bound.
+We now turn our attention to analyzing the complexity of the $\reclsat$ problem in the absence of complement operations.
+
+\begin{lemma}\label{lemma:regex2cefa}
+    Register-representable regex without complement operation can be converted to CEFA in PSPACE.
+\end{lemma}
+
+\begin{proof}
+    We prove this lemma through structural induction on regular expression $e$.
+For the base case—where the regular expression consists of a single character, $\epsilon$, or $\emptyset$—the lemma holds trivially.
+    For the inductive cases, assuming the lemma holds for regular expressions $e_1$ and $e_2$:
+    When $e = e_1\concat e_2$ or $e = e_1+e_2$, the concatenation or union operations described in Section \ref{sec:automaton} produce a CEFA of size $O(|e_1|^{k_1} + |e_2|^{k_2})=O(|e|^{\max(k_1, k_2)})$.
+    For $e = e_1\cap e_2$, the intersection operation detailed in Section \ref{sec:automaton} yields a CEFA of size $O(|e_1|^{k_1}\cdot|e_2|^{k_2})=O(|e|^{k_1+k_2})$.
+    In the case of $e=e_1^{\{m,n\}}$, our construction in Section \ref{subsec:regex2cefa} avoids direct unfolding of counting operators, resulting in a CEFA of size $O(|e_1|^{k_1})=O(|e|^{k_1})$.
+    Finally, for $e=(e_1)$ and $e=e^*$, our application of Thompson's construction~\cite{Thompson1968} produces a CEFA of size $O(|e_1|^{k_1})=O(|e|^{k_1})$.
+\end{proof}
+
+\begin{theorem}\label{theorem_pspace}
+    If all regexes are register-representable and complement operations are excluded, $\reclsat$ can be solved in PSPACE-complete.
+\end{theorem}
+\begin{proof}
+    Based on Lemma \ref{lemma:regex2cefa}, our construction yields a CEFA of polynomial size for each register-representable regex without complement operation.
+Furthermore, for each string variable's length function, a CEFA of constant size is constructed in Section \ref{subsec:regex2cefa}.
+    Consequently,  the construction outlined in Section \ref{subsec:regex2cefa} requires nondeterministic polynomial size.
+By Proposition \ref{prop-cefadec}, we can demonstrate that the procedure described in Section \ref{subsec:cefadec} likewise requires nondeterministic polynomial size.
+Therefore, the complexity of the complete decision procedure for solving the restricted $\reclsat$ problem is NPSPACE-complete, which yields PSPACE-complete by Savitch's theorem~\cite{complexity-book}.
+\end{proof}
+
+\begin{theorem}
+    $\reclsat$ can be solved in EXPSPACE when complement operations are excluded.
+\end{theorem}
+
+\begin{proof}
+    In Section \ref{subsec:regex2cefa}, unfolding non-register-representable occurrences of counting operators leads to an exponential growth in expression length.
+For each non-register-representable regular expression of length $l$, the unfolding process generates a register-representable regular expression of length $O(m^n\cdot l)=O((2^{|l|})^{|l|}\cdot l) = O(2^{|l|})$, where $m$ represents the maximum counting bound and $n$ denotes the maximum depth of nested counting operators.
+By Theorem \ref{theorem_pspace}, the complexity of the complete decision procedure for solving the $\reclsat$ problem without complement operations is EXPSPACE.
+\end{proof}
+}

### 2024-12-24 2024-5-13/sections/cefa.tex
complete complexity analysis

--- 2024-05-15 2024-5-13/sections/cefa.tex
@@
 The semantics of CEFA is defined as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
-A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$.
-A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$.
+A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v}_1]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v}_n]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v}_i]{a_i} q_i$ for each $i \in [n]$.
+A run $q_0 \xrightarrow[\myvec{v}_1]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v}_n]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v}_j$.
 The string $w$ is $accepted$ by the CEFA if and only if there is an accepting run of $w$.
-The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$.Note that the values of all registers are initiated to zero and updated to $\sum \limits_{j \in [n]} \myvec{v_j}$ after all the transitions in the run are executed.
+The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v}_j$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v}_1]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v}_n]{a_n} q_n$.Note that the values of all registers are initiated to zero and updated to $\sum \limits_{j \in [n]} \myvec{v}_j$ after all the transitions in the run are executed.
 We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.
@@
 
-Let $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, q_{1,0}, F_1, \alpha_1)$ and  $\aut_2 = (R_2, Q_2, \Sigma, \delta_2, q_{2,0}, F_2, \alpha_2)$ be two CEFA that share the alphabet. 
+Let $\aut_1 = (R_1, Q_1, \Sigma, \delta_1, \hdh{I_1}, F_1, \alpha_1)$ and  $\aut_2 = (R_2, Q_2, \Sigma, \delta_2, \hdh{I_2}, F_2, \alpha_2)$ be two CEFA that share the alphabet. 
 Moreover, suppose that $R_1 \cap R_2 = \emptyset$ and $Q_1 \cap Q_2 = \emptyset$.
@@
 The \emph{union} of $\aut_1$ and $\aut_2$ is denoted by $\aut_1 \cup \aut_2$.
-Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).
-Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where
+Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).\hdh{This is mainly because the same accepting condition is applied to all final states, in other words, the accepting condition does not distinguish between final states.} Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where
 \begin{itemize}
@@
 \begin{itemize}
-  \item $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
-  \item $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
-  \item $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid q_1\not\in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
-  \item $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid q_2\not\in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
+  \item $\{(q'_0, a, q'_1, (\myvec{v}_1, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v}_1) \in \delta_1\}$
+  \item $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v}_2, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v}_2) \in \delta_2\}$
+  \item $\{(q_1, a, q'_1, (\myvec{v}_1, \myvec{0}, 0, 0)) \mid q_1\not\in I_1.\ (q_1, a, q'_1, \myvec{v}_1) \in \delta_1\}$
+  \item $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v}_2, 0, 0)) \mid q_2\not\in I_2.\ (q_2, a, q'_2, \myvec{v}_2) \in \delta_2\}$
 \end{itemize}
- where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively.
-Similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.
+ where $(\myvec{v}_1, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v}_1$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively.
+Similarly for $(\myvec{0}, \myvec{v}_2, 0, 1)$, and so on.
 
@@
 
-The \emph{intersection} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cap \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, is defined in the sequel. 
+The \emph{intersection} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cap \aut_2 = (R', Q', \Sigma, \delta', I', F',$ $ \alpha')$, is defined in the sequel. 
 \begin{itemize}
 \item $R' = R_1 \cup R_2$, $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, $\alpha' = \alpha_1 \wedge \alpha_2$, 
-\item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), (\myvec{v_1}, \myvec{v_2}))$ such that $(q_1,a, q'_1, \myvec{v_1}) \in \delta_1$ and $(q_2,a, q'_2, \myvec{v_2}) \in \delta_2$.
+\item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), (\myvec{v}_1, \myvec{v}_2))$ such that $(q_1,a, q'_1, $ $\myvec{v}_1)\in \delta_1$ and $(q_2,a, q'_2, \myvec{v}_2) \in \delta_2$.
 \end{itemize}
@@
 
-The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(\hdh{R'}, Q', \Sigma, \delta', I', F', \alpha')$, where \hdh{$R' = R_1\cup R_2$}, $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v}_1, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v}_1) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v}_2)) \mid (q_2, a, q'_2, \myvec{v}_2) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
 From the construction,

### 2024-12-24 2024-5-13/sections/heuristic.tex
complete complexity analysis

@@
 As a result, the alphabets of $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors \sout{$\myvec{v}$} occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively.
-\sout{The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.} \hdh{These integer vectors are of form $(0,\cdots,0,1,0,\cdots, 0)$ whose length is the number of registers.} Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
+\sout{The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.} \hdh{The integer vectors of  $\aut_{\ufld_1(e)}$ are of the form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{\rnum_1(e)-i-1})$, where $i \in [\rnum_1(e)]$.} Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
 Similarly for $\cU_{\aut_{\ufld_\hdh{2}(e)}}$.
@@
 Let $e=(e_1)^{\{m,n\}}$ be a regular expression where $e_1$ is a register-representable regular expression.
-Then we compute $\snum'_1(e_1)$ and $(\snum'_2(e_1), \rnum'_2(e_1))$\hdh{(TODO:Change all the $num'$ to $num$, to avoid ambiguity)} by a structural induction on $e_1$, \hdh{in condition, $\rnum_1(e_1)$ is set to $1$.} \sout{Finally, let $(\snum_1(e), \rnum_1(e)) = (\snum'_1(e_1), 1)$ and $(\snum_2(e), \rnum_2(e)) = (\snum'_2(e_1), \rnum'_2(e_1))$.}
+Then we compute $\snum'_1(e_1)$ and $(\snum'_2(e_1), \rnum'_2(e_1))$.
+Finally, let $(\snum_1(e), \rnum_1(e)) = (\snum'_1(e_1), 1)$ and $(\snum_2(e), \rnum_2(e)) = (\snum'_2(e_1), \rnum'_2(e_1))$.
 \begin{itemize}
@@
 Without loss of generality, we can assume that there are no transitions out of $F$ in $\aut_{e_1}$.
-If this is not the case, then a new state $q_f$ can be introduced to transform $\aut_{e_1}$ into a CEFA satisfying this constraint, where $q_f$ is the unique accepting state.\footnote{\hdh{Note that if any initial states are in $F$, a new state $q_I$ without transitions out can be introduced and add to $F$, to accept empty string.
-Then we can remove all original initial states out of $F$.}}
+If this is not the case, then a new state $q_f$ can be introduced to transform $\aut_{e_1}$ into a CEFA satisfying this constraint, where $q_f$ is the unique accepting state.
 Then we define $\cB= (R \cup \{r'\}, Q \cup \{q_s\}, \Sigma, \delta', I, Q \cup \{q_s\}, \alpha')$, where
@@
 \hdh{\paragraph*{Combination of under- and over-approximation}
-Since these two types of approximation influence each other, we separate them apart and run them parallelly.
+ In our configuration, under-approximation is performed first due to its superior computational efficiency, and we proceed with over-approximation if it yields an unsatisfiable result.
+In cases where over-approximation produces a satisfiable result, we execute the decision procedure wherein all non-register-representable regular expressions are naively unfold.
+To minimize computational overhead, we apply approximation techniques only in cases involving non-register-representable regular expressions with significant counting bounds—specifically, those exceeding 20 in our experimental configuration.
 }
@@
 
-\hdh{The naive approach of finding satisfied string models is to search the accepted words on CEFAs based on the integer models of vectors, which causes an exponential blow-up of searching space.
-Specifically, } recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
+\zhilin{TODO: I had troubles to understand the section about optimized model generation.
+Maybe stating what the technical problem that it is solving is in a more dumb proof way would help., } recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
 \[

### 2024-12-24 2024-5-13/sections/implementation.tex
complete complexity analysis

--- 2024-06-02 2024-5-13/sections/implementation.tex
@@
 
-In total, the NestC benchmark suite contains 1000 instances.
+In total, the NestC benchmark suite contains 1000 \hdh{tough} instances, \hdh{where the regexes and their associated counting bounds are generated randomly.}
 
@@
 
-We evaluate the performance of $\ostrichrecl$ against the state-of-the-art string constraint solvers, including CVC5
-\cite{cvc5}, Z3seq \cite{z3seq}, Z3str3
-\cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH
-\cite{CHL+19}, on RegCoL, AutomatArk and NestC benchmark suites. 
+We evaluate the performance of $\ostrichrecl$ against the state-of-the-art string constraint solvers, including CVC5~\cite{cvc5}, Z3seq~\cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE~\cite{BD+23}, and OSTRICH \cite{CHL+19}, on RegCoL, AutomatArk and NestC benchmark suites.
 The experiment results can be found in Table~\ref{tab:table_overall_eval}.

### 2024-12-24 2024-5-13/sections/introduction.tex
complete complexity analysis

@@
 Intuitively, the constraint in (\ref{eqn-running}) specifies that $x$ is a concatenation of three strings $x_1, x_2, x_3$ where $a$ (resp.
-$b, c$) does not occur in $x_1$ (resp.
-$x_2, x_3$), moreover, $x$ ends with a nonempty sequence of $c$'s, and the length of $x$ is greater than $120$.
+$b$, $c$) does not occur in $x_1$ (resp.
+$x_2$, $x_3$), moreover, $x$ ends with a nonempty sequence of $c$'s, and the length of $x$ is greater than $120$.
 It is easy to observe that this constraint is unsatisfiable since on the one hand, $|x| > 120$ and the counting upper bound $60$ in both $(\Sigma \setminus a)^{\{1, 60\}}$ and $(\Sigma \setminus b)^{\{1, 60\}}$ imply that $x$ must end with some character from $\Sigma \setminus c$, that is, a character different from $c$, and on the other hand, $x \in \Sigma^*c^+$ requires that $x$ has to end with $c$.
@@
  %
-\item We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$\footnote{The tool is available as open source at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024}.}.
-Finally, we utilize a collection of benchmark suites comprising 49,843 problem instances\footnote{The benchmark suites are available at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024/zaligvinder/models/jsa2024}.} in total to evaluate the performance of $\ostrichrecl$.
+\item We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$.
+Finally, we utilize a collection of benchmark suites comprising 49,843 problem instances in total to evaluate the performance of $\ostrichrecl$.
 The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers (see Table~\ref{tab:table_overall_eval}-\ref{tab:results_model-gen}).
 For instance, $\ostrichrecl$ solves 49,638 out of 49,843 instances, while the best state-of-the-art solver solve only 47,721 instances.
-We also do experiments to justify some of our technical choices and evaluate the performance of the optimizations.
+We also do experiments to justify some of our technical choices and evaluate the performance of the optimizations\footnote{\hdh{The tool is available as open source at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024}.
+
+The benchmark suites are available at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024/zaligvinder/models/jsa2024}.}}. 
 %
@@
 Therefore, cost registers in CEFAs are more like counters in counter automata/machines~\cite{Minsky67}, that is, CEFAs can be obtained from counter machines by removing transition guards and adding accepting conditions.
-\hdh{CEFAs can also be considered as Parikh automata \cite{parikh_automaton_2003} equipped with the ability to decrease counters.}
+\hdh{CEFAs can also be considered as a variation of Parikh automata \cite{parikh_automaton_2003} in which the numbers in the alphabet can be integers, instead of natural numbers.}
 %

### 2024-12-24 2024-5-13/sections/overview.tex
complete complexity analysis

@@
 %
-Let $\costset = \{\myvec{v_1}, \cdots, \myvec{v_m}\}$. 
-From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi_\cB(\anivar_1, \cdots, \anivar_m)$ can be computed to define the Parikh image of strings that are accepted by $\cB$, where $\anivar_1, \cdots, \anivar_m$ are the integer variables to denote the number of occurrences of $\myvec{v_1}, \cdots, \myvec{v_m}$.
+Let $\costset = \{\myvec{v}_1, \cdots, \myvec{v}_m\}$. 
+From the results in \cite{SSMH04,VSS05}, an existential LIA formula $\psi_\cB(\anivar_1, \cdots, \anivar_m)$ can be computed to define the Parikh image of strings that are accepted by $\cB$, where $\anivar_1, \cdots, \anivar_m$ are the integer variables to denote the number of occurrences of $\myvec{v}_1, \cdots, \myvec{v}_m$.
 Therefore, the satisfiability of the string constraint in~(\ref{eqn-running}) is reduced to the satisfiability of the following existential LIA formula,

### 2024-12-31 2024-5-13/sections/algorithms.tex
Some revision from prof. wu and change about complexity analysis

@@
 
-\begin{definition}[$\cefadec$]
+\begin{definition}[$\cefadec$]\label{def-cefadec}
 Let $x_1, \cdots, x_n$ be string variables, $\Lambda_{x_1}, \cdots, \Lambda_{x_n}$ be nonempty sets of CEFA over the alphabet $\Sigma$ with $\Lambda_{x_i} = \{\aut_{i, 1}, \cdots, \aut_{i, l_i}\}$ for every $i \in [n]$ where the sets of registers $R_{\aut_{1, 1}}, \cdots, R_{\aut_{1, l_1}}, \cdots, R_{\aut_{n, 1}}, \cdots, R_{\aut_{n, l_n}}$ are mutually disjoint, moreover, let $\varphi$ be an LIA formula whose free variables are from $ \bigcup \limits_{i \in [n], j \in [l_i]} R_{\aut_{i, j}}$.
@@
 At first, we show how to construct a CEFA from a regex where counting operators may occur.
-\hdh{Glushkov’s construction~\cite{Gluskov61} and its variants~\cite{redos_lenka,HS+23,GKM23} convert a regex to a $\epsilon$-free automaton.
-In contrast, Thompson's construction~\cite{Thompson1968} results in an automaton with $\epsilon$-transitions but the algorithm is simpler and straightforward.
-}Our approach is based on Thompson's construction~\cite{Thompson1968} \hdh{and we remove $\epsilon$-transitions on the fly (See union at Section \ref{sec:automaton} and construction of counting operators below)}.
+\hdh{Our approach largely follows Thompson's construction~\cite{Thompson1968} but we avoid using the $\epsilon$-transitions.
+Similar ideas of representing counting operators as counters in automata have been used in e.g.
+\cite{redos_lenka}.
+}
+%\hdh{and we remove $\epsilon$-transitions on the fly (See union at Section \ref{sec:automaton} and construction of counting operators below)}. 
+%\hdh{Some other algorithms to construct NFA from regular expressions are also available, for instance, Glushkov’s construction~\cite{Gluskov61} and its variants~\cite{redos_lenka,HS+23,GKM23}.}
+
 Let us start with register-representable regexes defined in the sequel.
@@
 We say that $e$ is \emph{register-representable} if and only if all occurrences of counting operators in $e$ are register-representable.
-For instance, $a^{\{2, 6\}} \cap a^{\{4, \infty\}}$ is register-representable, while $\overline{a^{\{2, 6\}}}$ and $(a^{\{2, 6\}})^{\{4,\infty\}}$ are not since $a^{\{2,6\}}$ is in the scope of complement and the counter operator $\{2, \infty\}$ respectively.
+For instance, $a^{\{2, 6\}} \cap a^{\{4, \infty\}}$ is register-representable, while $\overline{a^{\{2, 6\}}}$ and $(a^{\{2, 6\}})^{\{4,\infty\}}$ are not since $a^{\{2,6\}}$ is in the scope of complement and the counter operator $\{4, \infty\}$ respectively.
 
@@
 \noindent
-\emph{Step 3 (Computing Parikh images \hdh{and derive a solution}).} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
-\hdh{Subsequently, we can employ established SMT solvers to determine the satisfiability of the formula and derive a solution if it is satisfiable.
-The integer variable solutions are directly extracted from the partial model of the formula.
-The string variable solutions are obtained through indirect means, whose detailed methodology is discussed in Section \ref{sec-opt-sol-gen}.
-The final Parikh images are as follow :}
+\emph{Step 3 (Computing an LIA formula).} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
+Then the $\cefadec$ problem is reduced to the satisfiability of the following LIA formula,
 %
-\[
+\begin{equation}\label{eq:parikh_image}
 \begin{array}{l}
@@
 \end{array}
-\]
+\end{equation}
+
+%\hdh{The final Parikh images are as LIA formula (\ref{eq:parikh_image}).
+Subsequently, we can employ established SMT solvers to determine the satisfiability of the formula and derive a solution if it is satisfiable.
+The integer variable solutions are directly extracted from the partial model of the formula.
+The string variable solutions are obtained through indirect means, whose detailed methodology is discussed in Section \ref{sec-opt-sol-gen}.}
+
+\medskip
+\noindent
+\emph{Step 4 (Solving the LIA formula).}
+We utilize some off-the-shelf SMT solver (e.g.
+Z3) to solve the satisfiability of the LIA formula in Equation~(\ref{eq:parikh_image}).
+If the solver reports ``sat'' and returns a solution $\amodel$, then we go to Step 5.
+Otherwise, the $\cefadec$ problem has no solution.
+
+\hdh{
+\medskip
+\noindent
+\emph{Step 5 (Constructing a solution).}
+%For each $i \in [n]$, 
+Let $\amodel$ be a solution of the LIA formula in Equation~(\ref{eq:parikh_image}).
+We want to construct from $\amodel$ and the CEFAs $\cB_i$ for $i \in [n]$, a solution $\amodel'$ of the $\cefadec$ problem.
+The construction of $\amodel'$ is obtained by constructing $\amodel'(x_i)$ for each $i \in [n]$.
+Let $i \in [n]$. We describe how to construct $\amodel'(x_i)$. 
+The free variables $\fZ_{\costset_{\cC_i}}$ correspond to the number of occurrences of characters in $\costset_{\cC_i}$, i.e.
+the alphabet of the NFA $\cC_i$.
+Moreover, in $\cC_i$, the characters are just the integer vectors and the characters in the original CEFAs $\cB_i$ used to construct $\cC_i$ are ignored.
+The construction of $\amodel'(x_i)$ is actually to solve the reachability problems in a finite transition system where 
+\begin{itemize}
+\item the nodes are of the form $(q, (\nvec_{i, \myvec{v}})_{\myvec{v} \in \costset_{\cC_i}})$, where $\nvec_{i, \myvec{v}}$ denotes the number of the remaining occurrences of the integer vector $\myvec{v}$ in $\cB_i$,
+%
+\item the transitions are of the form 
+$$((q, (\nvec_{i, \myvec{v}})_{\myvec{v} \in \costset_{\cC_i}}), (q, a, q', \myvec{u}), (q', (\nvec'_{i, \myvec{v}})_{\myvec{v} \in \costset_{\cC_i}}))$$
+such that $(q, a, q', \myvec{u})$ is a transition in $\cB_i$, $\nvec'_{i, \myvec{u}} = \nvec_{i, \myvec{u}}-1$, moreover, $\nvec'_{i, \myvec{v}} = \nvec_{i, \myvec{v}}$ for every $\myvec{v} \neq \myvec{u}$.
+\end{itemize}
+Moreover, the initial and final state of the reachability problem are set to be $(q_0, (\amodel(\anivarz_{i, \myvec{v}}))_{\myvec{v} \in \costset_{\cC_i}})$ and $(q_f, (0,\cdots, 0))$ for some initial state $q_0$ and final state $q_f$ in $\cB_i$.
+If a path from the initial state to the final state is found, then the path gives us a desired string $\amodel'(x_i)$.
+}
+%Note that the transition system contains exponentially many nodes.
+As a result, the searching process takes \emph{doubly exponential time} in the worst case, since there are at most doubly exponentially many simple paths.
+To alleviate the path-explosion problem, in the sequel, we propose two techniques to reduce the number of transitions of the transition system.
+
 %\qed
@@
 This directly implies that the $\reclsat$ problem exhibits a nonelementary lower bound.
-We now turn our attention to analyzing the complexity of the $\reclsat$ problem in the absence of complement operations.
+We now turn our attention to analyzing the complexity of the $\reclsat$ problem in the absence of complement operations (no occurrence of $\Bar{e}$ and $e_1 \backslash e_2$).
 
 \begin{lemma}\label{lemma:regex2cefa}
-    Register-representable regex without complement operation can be converted to CEFA in PSPACE.
+    Register-representable regex without complement operation can be converted to CEFA in EXPSPACE.
 \end{lemma}
@@
     For the inductive cases, assuming the lemma holds for regular expressions $e_1$ and $e_2$:
-    When $e = e_1\concat e_2$ or $e = e_1+e_2$, the concatenation or union operations described in Section \ref{sec:automaton} produce a CEFA of size $O(|e_1|^{k_1} + |e_2|^{k_2})=O(|e|^{\max(k_1, k_2)})$.
-    For $e = e_1\cap e_2$, the intersection operation detailed in Section \ref{sec:automaton} yields a CEFA of size $O(|e_1|^{k_1}\cdot|e_2|^{k_2})=O(|e|^{k_1+k_2})$.
-    In the case of $e=e_1^{\{m,n\}}$, our construction in Section \ref{subsec:regex2cefa} avoids direct unfolding of counting operators, resulting in a CEFA of size $O(|e_1|^{k_1})=O(|e|^{k_1})$.
-    Finally, for $e=(e_1)$ and $e=e^*$, our application of Thompson's construction~\cite{Thompson1968} produces a CEFA of size $O(|e_1|^{k_1})=O(|e|^{k_1})$.
+    When $e = e_1\concat e_2$ or $e = e_1+e_2$, the concatenation or union operations described in Section \ref{sec:automaton} produce a CEFA of size $O(2^{|e_1|} + 2^{|e_2|}) = O(2^{\max(|e_1|, |e_2|)}) = O(2^{|e|})$.
+    For $e = e_1\cap e_2$, the intersection operation detailed in Section \ref{sec:automaton} yields a CEFA of size $O(2^{|e_1|}\cdot 2^{|e_2|})=O(2^{|e_1| + |e_2|})=O(2^{|e|})$.
+    In the case of $e=e_1^{\{m,n\}}$, our construction in Section \ref{subsec:regex2cefa} avoids direct unfolding of counting operators, resulting in a CEFA of size $O(2^{|e_1|}) = O(2^{|e|})$.
+    Finally, for $e=(e_1)$ and $e=e^*$, our application of Thompson's construction~\cite{Thompson1968} produces a CEFA of size $O(2^{|e_1|}) = O(2^{|e|})$.
 \end{proof}
@@
 \begin{theorem}\label{theorem_pspace}
-    If all regexes are register-representable and complement operations are excluded, $\reclsat$ can be solved in PSPACE-complete.
+    If all regexes are register-representable and complement operations are excluded, $\reclsat$ can be solved in EXPSPACE.
 \end{theorem}
 \begin{proof}
-    Based on Lemma \ref{lemma:regex2cefa}, our construction yields a CEFA of polynomial size for each register-representable regex without complement operation.
+    Our decision procedure for $\reclsat$ with only register-representable regexes can be decomposed into two steps: (1) constructing CEFAs from regular membership and length function, (2) solving $\cefadec$.
+    Based on Lemma \ref{lemma:regex2cefa}, our construction yields a CEFA of exponential size for each register-representable regex without complement operation.
 Furthermore, for each string variable's length function, a CEFA of constant size is constructed in Section \ref{subsec:regex2cefa}.
-    Consequently,  the construction outlined in Section \ref{subsec:regex2cefa} requires nondeterministic polynomial size.
-By Proposition \ref{prop-cefadec}, we can demonstrate that the procedure described in Section \ref{subsec:cefadec} likewise requires nondeterministic polynomial size.
-Therefore, the complexity of the complete decision procedure for solving the restricted $\reclsat$ problem is NPSPACE-complete, which yields PSPACE-complete by Savitch's theorem~\cite{complexity-book}.
+    Consequently, constructing CEFAs in the decision procedure outlined in Section \ref{subsec:regex2cefa} requires nondeterministic exponential size.
+After constructing CEFAs, the $\reclsat$ problem is transferred to the $\cefadec$ problem.
+By Proposition \ref{prop-cefadec}, we can demonstrate that the decision procedure likewise requires nondeterministic exponential size.
+Therefore, the complexity of the decision procedure for solving the restricted $\reclsat$ problem is NEXPSPACE, which yields EXPSPACE by Savitch's theorem~\cite{complexity-book}.
 \end{proof}
@@
 \begin{theorem}
-    $\reclsat$ can be solved in EXPSPACE when complement operations are excluded.
+    $\reclsat$ can be solved in 3-EXPTIME when complement operations are excluded.
 \end{theorem}
@@
 \begin{proof}
-    In Section \ref{subsec:regex2cefa}, unfolding non-register-representable occurrences of counting operators leads to an exponential growth in expression length.
+    Our decision procedure for $\reclsat$ with non-register-representable regexes can be decomposed into three steps: (1) unfolding non-register-representable occurrences of counting operators, (2) constructing CEFAs from regular membership and length function, (3) solving $\cefadec$.
+    From the decision procedure in Section \ref{subsec:regex2cefa}, unfolding non-register-representable occurrences of counting operators leads to an exponential growth in expression length.
 For each non-register-representable regular expression of length $l$, the unfolding process generates a register-representable regular expression of length $O(m^n\cdot l)=O((2^{|l|})^{|l|}\cdot l) = O(2^{|l|})$, where $m$ represents the maximum counting bound and $n$ denotes the maximum depth of nested counting operators.
-By Theorem \ref{theorem_pspace}, the complexity of the complete decision procedure for solving the $\reclsat$ problem without complement operations is EXPSPACE.
+By Theorem \ref{theorem_pspace} and the fact that EXPSPACE $\subseteq$ 2-EXPTIME \cite{complexity-book}, the complexity of the decision procedure for solving the $\reclsat$ problem without complement operations is 3-EXPTIME.
 \end{proof}

### 2024-12-31 2024-5-13/sections/cefa.tex
Some revision from prof. wu and change about complexity analysis

@@
 
-The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(\hdh{R'}, Q', \Sigma, \delta', I', F', \alpha')$, where \hdh{$R' = R_1\cup R_2$}, $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v}_1, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v}_1) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v}_2)) \mid (q_2, a, q'_2, \myvec{v}_2) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
+The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(\hdh{R'}, Q', \Sigma, \delta', I', F', \alpha')$, where \hdh{$R' = R_1\cup R_2$}, $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v}_1, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v}_1) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v}_2)) \mid (q_2, a, q'_2, \myvec{v}_2) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \myvec{v}_2)) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \myvec{v}_2) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$.
 From the construction,

### 2024-12-31 2024-5-13/sections/heuristic.tex
Some revision from prof. wu and change about complexity analysis

@@
 two NFAs $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignoring the characters.
-As a result, the alphabets of $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors \sout{$\myvec{v}$} occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively.
-\sout{The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$.} \hdh{The integer vectors of  $\aut_{\ufld_1(e)}$ are of the form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{\rnum_1(e)-i-1})$, where $i \in [\rnum_1(e)]$.} Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
+As a result, the alphabets of $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively.
+\hdh{Note that there is only one register in $\aut_{\ufld_1(e)}$.
+Because each occurrence of the counting operators in $\ufld_2(e)$ originates from the register-representable $e_1$, thus not in the scope of any Kleene star, counting, complement, or language difference, it follows that
+in $\aut_{\ufld_2(e)}$, the registers corresponding to these counting operators are updated independently, that is, the integer vectors of  $\aut_{\ufld_2(e)}$ are of the form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{\rnum_1(e)-i-1})$, where $i \in [\rnum_2(e)]$.} Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
 Similarly for $\cU_{\aut_{\ufld_\hdh{2}(e)}}$.
 Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut_{\ufld_1(e)}}, \cU_{\aut_{\ufld_2(e)}}$ as $sz_1 = (\snum_1(e))^2 \cdot \rnum_1(e)$ and $sz_2 = (\snum_2(e))^2 \cdot \rnum_2(e)$ respectively.
+\zhilin{to be checked}
 %
@@
  In our configuration, under-approximation is performed first due to its superior computational efficiency, and we proceed with over-approximation if it yields an unsatisfiable result.
-In cases where over-approximation produces a satisfiable result, we execute the decision procedure wherein all non-register-representable regular expressions are naively unfold.
+When the under-approximation yields an unsatisfiable result and the over-approximation yields a satisfiable result, we employ the decision procedure to obtain an answer, which implies that our approach is sound and complete.
 To minimize computational overhead, we apply approximation techniques only in cases involving non-register-representable regular expressions with significant counting bounds—specifically, those exceeding 20 in our experimental configuration.
@@
 
-\section{Optimizations for model generation}\label{sec-opt-sol-gen}
+\section{\hdh{Optimizations for model generation}}\label{sec-opt-sol-gen}
 
-\zhilin{TODO: I had troubles to understand the section about optimized model generation.
-Maybe stating what the technical problem that it is solving is in a more dumb proof way would help., } recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
+\zhilin{Double check}
+
+%\zhilin{TODO: I had troubles to understand the section about optimized model generation. Maybe stating what the technical problem that it is solving is in a more dumb proof way would help., } 
+Recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
 \[
@@
 If Z3 reports ``sat'', then it also returns a model, namely, an assignment $\amodel$ of natural numbers to the free integer variables in $\theta$.
-Then we utilize $\amodel$ to generate a model $\amodel'$ of the original RECL constraint $\varphi$, i.e., an assignment of strings to the string variables so that $\varphi$ is evaluated to true under $\amodel'$.
+Then we utilize $\amodel$ to generate a model $\amodel'$ of the $\cefadec$ problem, i.e., an assignment $\amodel'$ of strings to the string variables so that the conditions in Definition~\ref{def-cefadec} are satisfied.
+In the sequel, let us assume $n=1$ for simplicity.
+%and use an example to illustrate
+We first describe the naive algorithm of generating $\amodel'$ from $\amodel$. Then we show how we optimize this model generation process.
 
-Note that for each $i \in [n]$, the free variables $\fZ_{\costset_{\cC_i}}$ in $\theta$ correspond to the number of occurrences of characters in $\costset_{\cC_i}$, i.e.
-the alphabet of the NFA $\cC_i$.
-Moreover, recall that in $\cC_i$, the characters are just the integer vectors and the characters in the original CEFAs $\cB_i$ used to construct $\cC_i$ are ignored.
-When we utilize $\amodel$ and the CEFAs $\cB_i$ to generate $\amodel'$, for each $i \in [n]$, we record the remaining occurrences of vectors $\myvec{v}$ in the transitions of the CEFAs $\cB_i$ as a number $\nvec_{i, \myvec{v}}$ and
-each time when a transition $(q, a, q', \myvec{v})$ in $\cB_i$ is traversed, $\nvec_{i, \myvec{v}}$ is decremented.
-Note that initially $\nvec_{i, \myvec{v}}$ is set to $\amodel(\anivarz_{i, \myvec{v}})$.
-The searching process terminates when $\nvec_{i, \myvec{v}}$ becomes $0$ for every $\myvec{v}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
+\begin{example}\label{exmp-model-gen-naive}
+The CEFA $\cB_1$ and the corresponding NFA $\cC_1$ are illustrated in Figure~\ref{fig-model-gen-opt}.
+Moreover, let $\varphi \equiv r_1 = 12$.
+Since the structure of $\cC_1$ is relatively simple, it is not hard to see that
+$$\psi_{\cC_1}(\anivarz_{1,(1,0)}, \anivarz_{1,(0,1)}) = \anivarz_{1,(1,0)} \ge 2 \wedge \anivarz_{1,(1,0)} \equiv 0 \bmod 2 \wedge  0 \le \anivarz_{1,(0,1)} \le 2.$$ 
+Moreover, $\alpha_1[(\anivarz_{1,(1,0)}(1,0) + \anivarz_{1,(0,1)}(0,1)) /(r_1, r_2)] \equiv \anivarz_{1,(1,0)} \ge 10 \wedge \anivarz_{1,(0,1)} = 2$.
+Then 
+$$
+\begin{array}{l c l}
+\theta & \equiv & 
+\anivarz_{1,(1,0)} \ge 2 \wedge \anivarz_{1,(1,0)} \equiv 0 \bmod 2 \wedge  0 \le \anivarz_{1,(0,1)} \le 2\ \wedge \\
+& & \anivarz_{1,(1,0)} \ge 10 \wedge \anivarz_{1,(0,1)} = 2 \wedge 
+\anivarz_{1,(1,0)} = 12.
+\end{array}
+$$
+Then $\amodel$ defined by $\amodel(\anivarz_{1,(1,0)}) = 12$ and  $\amodel(\anivarz_{1,(0,1)})= 2$ is a model of $\theta$.
+
+To generate a model $\amodel'$ for $\cefadec$ problem, it is necessary to generate a string $w$ such that $(w, (12, 2))$ is accepted by $\cB_1$.
+
+\begin{figure}[htbp]
+\includegraphics[scale = 0.65]{2024-5-13/sections/model-gen-exmp.pdf}
+\caption{The CEFA $\cB_1$ and the NFA $\cC_1$}
+\label{fig-model-gen-opt}
+\end{figure}
+\end{example}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\paragraph*{A naive algorithm for model generation}
+%For each $i \in [n]$, 
+The free variables $\fZ_{\costset_{\cC_1}}$ in $\theta$ correspond to the number of occurrences of characters in $\costset_{\cC_1}$, i.e.
+the alphabet of the NFA $\cC_1$.
+Moreover, in $\cC_1$, the characters are just the integer vectors and the characters in the original CEFAs $\cB_1$ used to construct $\cC_1$ are ignored.
+We then utilize $\amodel$ and the CEFA $\cB_1$ to generate $\amodel'$. Essentially, we are solving the reachability problems in a finite transition system where 
+\begin{itemize}
+\item the nodes are of the form $(q, (\nvec_{1, \myvec{v}})_{v \in \costset_{\cC_1}})$,
+%
+\item the transitions are of the form 
+$$((q, (\nvec_{1, \myvec{v}})_{\myvec{v} \in \costset_{\cC_1}}), (q, a, q', \myvec{u}), (q', (\nvec'_{1, \myvec{v}})_{\myvec{v} \in \costset_{\cC_1}}))$$
+such that $(q, a, q', \myvec{u})$ is a transition in $\cB_1$, $\nvec'_{1, \myvec{u}} = \nvec_{1, \myvec{u}}-1$, moreover, $\nvec'_{1, \myvec{v}} = \nvec_{1, \myvec{v}}$ for every $\myvec{v} \neq \myvec{u}$.
+\end{itemize}
+Moreover, the initial and final state of the reachability problem are set to be $(q_0, (\amodel(\anivarz_{1, \myvec{v}}))_{\myvec{v} \in \costset_{\cC_1}})$ and $(q_f, (0,\cdots, 0))$ for some initial state $q_0$ and final state $q_f$.
+Note that the transition system contains exponentially many nodes.
+As a result, the searching process takes \emph{doubly exponential time} in the worst case, since there are at most doubly exponentially many paths.
+To alleviate the path-explosion problem, in the sequel, we propose two techniques to reduce the number of transitions of the transition system.
+
+\hide{
+we record the remaining occurrences of vectors $\myvec{v}$ in the transitions of the CEFAs $\cB_1$ as a number $\nvec_{1, \myvec{v}}$ and
+each time when a transition $(q, a, q', \myvec{v})$ in $\cB_1$ is traversed, $\nvec_{1, \myvec{v}}$ is decremented.
+Initially $\nvec_{1, \myvec{v}}$ is set to $\amodel(\anivarz_{1, \myvec{v}})$.
+The searching process terminates when $\nvec_{1, \myvec{v}}$ becomes $0$ for every $\myvec{v}$.
 We record the characters in the traversed transitions and obtain a string for the string variable $x_i$ when the searching process terminates.
-As a result, we obtain a model of $\varphi$ in the end.
-\hdh{In the worst case, we need search O($\prod_{i=0}^{n} \amodel(\anivarz_{i, \myvec{v}})$) times to find an accepted word.}
+As a result, we obtain a model of $\cefadec$ in the end.
+Note that the searching process can be seen as solving the reachability problem in a finite-state transition system where the nodes are of the form $(q, (\nvec_{1, \myvec{v}}))$ and the transitions are
+is nondeterministic since there may be multiple transitions 
+}
+%\hdh{In the worst case, we need search O($\prod_{i=0}^{n} \amodel(\anivarz_{i, \myvec{v}})$) times to find an accepted word.}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
+\begin{example}\label{exmp-model-gen-naive-2}
+There are two distinct vectors $(1,0)$ and $(0,1)$ in $\cC_1$. 
+The searching process starts from the state $(q_0, (12, 2))$, where $\nvec_{1, (1,0)} = 12$ and $\nvec_{1, (0,1)} = 2$.
+There are three transitions out of $q_0$, $(q_0, a, (1,0), q_1)$, $(q_0, b, (1,0), q_2)$, $(q_0, c, (1,0), q_3)$.
+\begin{itemize}
+\item If the searching process chooses the transition $(q_0, a, (1,0), q_1)$, then the state $(q_1, (11,2))$ is reached and a letter $a$ is added to the end of the string (to be generated). 
+%
+\item If the searching process chooses the transition $(q_0, c, (1,0), q_2)$, then the state $(q_2, (11,2))$ is reached and a letter $c$ is added to the end of the string  (to be generated).
+%
+\item If the searching process chooses the transition $(q_0, c, (1,0), q_3)$, then the state $(q_3, (11,2))$ is reached and a letter $c$ is added to the end of the string  (to be generated).
+\end{itemize}
+The searching process continues from the state $q_1$, $q_2$, and $q_3$ respectively.
+If a state $(q_5, (n_1,n_2))$ such that $n_1 > 0$ or $n_2 > 0$ is reached, then some wrong choices have been made before and the searching process should be backtracked.
+If a state $(q_5, (0,0))$ is reached, then a desired model is found.
+\end{example}
+Note that since we do not have the information about the number of occurrences of the transitions out of $q_0$, starting from the state $(q_0, (12, 2))$, we have to search all the three transitions out of $q_0$.
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+At first, we refine the states of the transition system by recording the number of transitions, instead of just the number of occurrences of the integer vectors.
+
+\paragraph*{Refining the states of the transition system by recording the number of transitions}
+We shall construct the formula $\theta'$ so that a model of $\theta'$ includes the information about the number of occurrences of the transitions of $\cB_1$.
+\[
+\begin{array}{l c l}
+\theta'  & \equiv &  \psi_{\cB_1}(\fZ_{\cB_1}) \wedge \bigwedge \limits_{\myvec{v} \in \costset_{\cC_1}} \anivarz_{1, \myvec{v}} = \amodel(\anivarz_{1, \myvec{v}}) \ \wedge \\
+& & \ \ \bigwedge \limits_{\myvec{v} \in \costset_{\cC_1}} \anivarz_{1, \myvec{v}} = \sum \limits_{(q, a, q') \mbox{ s.t.
+} (q, a, q', \myvec{v}) \mbox{ is a transition in } \cB_1} \anivarz_{1, (q, a, q', \myvec{v})},
+\end{array}
+\]
+where $\fZ_{\cB_1} = \{\anivarz_{1, (q, a, q', \myvec{v})} \mid (q, a, q', \myvec{v}) \mbox{ is a transition in } \cB_1\}$ is the set of variables $\anivarz_{1, (q, a, q', \myvec{v})}$ denoting the number of occurrences of $(q, a, q', \myvec{v})$.
+Note that compared to $\theta$, $\theta'$ uses the LIA formula $\psi_{\cB_1}$, which is constructed from $\cB_1$ by ignoring its accepting condition and taking it as an NFA where the alphabet is seen as the set of transitions.
+Moreover, $\theta'$ relates the values of the variables $\anivarz_{1, \myvec{v}}$ and $\anivarz_{1, (q, a, q', \myvec{v})}$, as well as restricts that the values of $\anivarz_{1, \myvec{v}}$ should be $\amodel(\anivarz_{1, \myvec{v}})$.
+We then submit $\theta'$ to some SMT solver, which returns a model for $\theta'$, in particular, the values of the variables $\anivarz_{1, (q, a, q', \myvec{v})}$.
+Equipped with the model, we refine the transition system by considering the nodes $(q, (\nvec_{1, (q, a, q', \myvec{v})})_{(q, a, q', \myvec{v})\mbox{ is a transition in } \cB_1})$, where $\nvec_{1, (q, a, q', \myvec{v})}$ denotes the number of remaining occurrences of $(q, a, q', \myvec{v})$.
+Note that this refinement can reduce the number of transitions.
+For instance, if $\nvec_{1, (q, a, q', \myvec{v})} = 0$ for some $(q, a, q', \myvec{v})$, then we can avoid searching the transition $(q, a, q', \myvec{v})$ out of $q$.
+On the other hand, if in the original transition system where $\nvec_{1, \myvec{v}}$ is used, then it may be the case that we have $\nvec_{1, \myvec{v}} > 0$ (since there may be multiple transitions associated with $\myvec{v}$) and the transition $(q, a, q', \myvec{v})$ should still be searched.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hide{
+\begin{example}\label{exmp-model-gen-naive-3}
+Let us continue Example~\ref{exmp-model-gen-naive-2}.
+$$
+\begin{array}{l c l}
+\theta' & \equiv & 
+\anivarz_{1,(1,0)} \ge 2 \wedge \anivarz_{1,(1,0)} \equiv 0 \bmod 2 \wedge  0 \le \anivarz_{1,(0,1)} \le 2\ \wedge \\
+& & \anivarz_{1,(1,0)} \ge 10 \wedge \anivarz_{1,(0,1)} = 2 \wedge 
+\anivarz_{1,(1,0)} = 12\ \wedge \\
+& & \anivarz_{1,(1,0)} = \anivarz_{1, (q_0, a, q_1, (1,0))} + \anivarz_{1, (q_1, b, q_0, (1,0))} + \anivarz_{1, (q_0, c, q_2, (1,0))} +\\
+& & \ \ \ \ \ \ \ \ \ \ \  \anivarz_{1, (q_0, c, q_3, (1,0))} + \anivarz_{1, (q_3, c, q_4, (1,0))} + \anivarz_{1, (q_3, c, q_5, (1,0))}\ \wedge\\
+& & \anivarz_{1,(0,1)} = \anivarz_{1, (q_2, d, q_3, (0,1))} + \anivarz_{1, (q_4, d, q_5, (0,1))}.
+\end{array}
+$$
+A model of 
+\end{example}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\hide{
 It turns out that this model generation process is inefficient, mainly due to the fact that the information about the occurrences of vectors $\myvec{v}$ in $\cB_i$ in the searching process is too coarse.
-In the sequel, we would like to refine this process by using \sout{the LIA formulas to obtain the information about} the number of occurrences of transitions, instead of just the occurrences of integer vectors, \sout{and utilize this information} to guide the search process.
+In the sequel, we would like to refine this process by using the number of occurrences of transitions, instead of just the occurrences of integer vectors, to guide the search process.
 Specifically, for each $i \in [n]$ and each transition $(q, a, q', \myvec{v})$ in $\cB_i$, we introduce an integer variable $\anivarz_{i, (q, a, q', \myvec{v})}$ to denote the number of occurrences of the transition, and solve the satisfiability of the following formula,
@@
 When a final state of $\cB_i$ is reached and $\lambda_i((q, a, q', \myvec{v}))$ becomes zero for each transition $(q, a, q', \myvec{v})$ in $\cB_i$, then a desired string is generated for the string variable $x_i$.
+}
 
-Moreover, we propose a method to prune the search space further.
-Let $i \in [n]$.
-Suppose that during the search process for $\cB_i$, let $q$ be the current state of $\cB_i$ and $\lambda_i$ record the remaining occurrences of transitions of $\cB_i$.
-We compute the set of transitions of $\cB_i$ that are reachable from the state $q$.
-Let $\cT_q$ denote this set.
-If $\{(q, a, q', \myvec{c}) \mid \lambda_i((q, a, q', \myvec{c})) > 0\} \not \subseteq \cT_q$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_i$ will be found and meanwhile the constraint on the number of transitions enforced by $\lambda_i$ is satisfied.
-Therefore, in this case, the search process for $\cB_i$ halts and is backtracked.
+Moreover, we propose a method to reduce the number of transitions in the transition system further.
+
+\paragraph*{Pruning the transitions in the transition system}
+%Let $i \in [n]$. 
+Let the current state of the transition system be $(p, (\nvec_{1, (q, a, q', \myvec{v})})_{(q, a, q', \myvec{v})\mbox{ is a transition in } \cB_1})$. 
+Let us compute the set of transitions of $\cB_1$ that are reachable from the state $p$.
+Let $\cT_p$ denote this set.
+If $\{(q, a, q', \myvec{v}) \mid \nvec_{1, ((q, a, q', \myvec{v}))} > 0\} \not \subseteq \cT_p$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_1$ will be found and meanwhile the constraint on the number of transitions enforced by $\nvec_{1, (q, a, q', \myvec{v})}$ is satisfied.
+Therefore, in this case, we can remove all the transitions out of $(p, (\nvec_{1, (q, a, q', \myvec{v})})_{(q, a, q', \myvec{v})\mbox{ is a transition in } \cB_1})$ and the search halts in this state and is backtracked.
 

### 2024-12-31 2024-5-13/sections/introduction.tex
Some revision from prof. wu and change about complexity analysis

--- 2024-06-02 2024-5-13/sections/introduction.tex
@@
 String manipulations are error-prone and could even give rise to severe security vulnerabilities (e.g., cross-site scripting, aka XSS). 
-One powerful method for identifying such bugs is \emph{symbolic execution}, which is possibly in combination with dynamic analysis.
-It analyses symbolic paths in a program by viewing them as constraints checked by constraint solvers.
+\hdh{One powerful method for identifying such bugs is \emph{symbolic execution}}.
+%, which \hdh{can be combined with } dynamic analysis. 
+It analyses the feasibility of execution paths in a program by encoding the paths as logical formulas and utilizing the constraint solvers (e.g.
+Z3~\cite{Z3}) to solve the satisfiability of the formulas.
 %
@@
 
-Regular expressions (regex for short) and the string-length function are widely used in string-manipulating programs.
-According to the statistics from \cite{CS16,DCSL18,WS18}, regexes are used in about 30–40\% of Java, JavaScript, and Python software projects.
+Regular expressions (regex for short) and the string-length function are widely used in string-manipulating programs. According to the statistics
+from \cite{CS16,DCSL18,WS18}, regexes are used in about \hdh{30–40\%} of Java, JavaScript, and Python software projects.
 Moreover, string-length occupies 78\% of the occurrences of string operations in 18 Javascript applications, according to the statistics from \cite{malware_detection_3_kudzu}.
@@
 For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice.
-Note that the Kleene star and the Kleene plus operator are special cases of counting. For instance, $a^*$ is equivalent to $a^{\{0,\infty\}}$ and $a^+$ is equivalent to $a^{\{1,\infty\}}$.
+\hdh{Note that although the Kleene star and the Kleene plus operator are special cases of counting, i.e., $e^*$ is equivalent to $e^{\{0,\infty\}}$ and $e^+$ is equivalent to $e^{\{1,\infty\}}$, 
+in the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.}
 Counting is a frequently used feature of regexes.
-According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while other forms of counting occur in more than 20\% of them.
-Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints containing regexes with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function at least.
+According to the statistics from \cite{CS16}, \hdh{counting occurs in more than 20\% of 1,204 Python projects}.
+Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints containing regexes with counting and string-length function at least.
 
-Nevertheless, the aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting and length bounds are large.
+The aforementioned state-of-the-art string constraint solvers still suffer from such string constraints, especially when the counting and length bounds are large.
 For instance, none of the string solvers CVC5, Z3seq, Z3-Trau, Z3str3, Z3str3RE, and OSTRICH is capable of solving the following constraint within 120 seconds,
@@
  %
-\item We implement the algorithm on top of OSTRICH, resulting in a string solver called $\ostrichrecl$.
-Finally, we utilize a collection of benchmark suites comprising 49,843 problem instances in total to evaluate the performance of $\ostrichrecl$.
-The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers (see Table~\ref{tab:table_overall_eval}-\ref{tab:results_model-gen}).
-For instance, $\ostrichrecl$ solves 49,638 out of 49,843 instances, while the best state-of-the-art solvers solve only 47,721 instances.
-We also do experiments to justify some of our technical choices and evaluate the performance of the optimizations.
+\item We implement the algorithm on top of OSTRICH, resulting in a string solver\footnote{\hdh{The solver is open source and available at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024}}} called $\ostrichrecl$.
+Finally, we utilize a collection of benchmark suites\footnote{\hdh{The benchmarks are available at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024/zaligvinder/models/jsa2024}}.} comprising 49,843 problem instances in total to evaluate the performance of $\ostrichrecl$.
+The experiment results show that $\ostrichrecl$ solves the RECL constraints more efficiently than the state-of-the-art string solvers (see Table~\ref{tab:table_overall_eval}-\ref{tab:results_model-gen} for details).
+For instance, $\ostrichrecl$ solves 49,638 out of 49,843 instances, while the best state-of-the-art solver solve only 47,721 instances.
+We also do experiments to justify some of our technical choices and evaluate the performance of the optimizations
+
+%\footnote{\hdh{The tool is available as open source at \url{https://github.com/SimpleXiaohu/ostrich/tree/jsa2024}.
 %
@@
 Therefore, cost registers in CEFAs are more like counters in counter automata/machines~\cite{Minsky67}, that is, CEFAs can be obtained from counter machines by removing transition guards and adding accepting conditions.
+\hdh{CEFAs can also be considered as a variation of Parikh automata \cite{parikh_automaton_2003} in which the numbers in the alphabet can be integers, instead of natural numbers.}
 %
@@
 \emph{Structure.} 
-The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper. Section~\ref{sec:pre} introduces the preliminaries. 
+The rest of this paper is structured as follows:  \hdh{Section~\ref{sec:pre} introduces the preliminaries. Section~\ref{sec:overview} gives an overview of the approach in this paper.}
 Section~\ref{sec:recl} presents the syntax and semantics of RECL. 

### 2025-01-05 2024-5-13/sections/algorithms.tex
Final version of revision

@@
 \hdh{Our approach largely follows Thompson's construction~\cite{Thompson1968} but we avoid using the $\epsilon$-transitions.
-Similar ideas of representing counting operators as counters in automata have been used in e.g.
+Similar ideas of representing counting operators as counters in automata have appeared in e.g.
 \cite{redos_lenka}.
@@
 \emph{Step 3 (Computing an LIA formula).} For each $i \in [n]$, we compute an existential LIA formula $\psi_{\cC_i}(\fZ_{\costset_{\cC_i}})$ from $\cC_i$ to represent $\parikh(\cC_i)$.
-Then the $\cefadec$ problem is reduced to the satisfiability of the following LIA formula,
+Then the $\cefadec$ problem is reduced to the satisfiability of the following LIA formula,  \qed
 %
@@
 Otherwise, the $\cefadec$ problem has no solution.
+\qed
 
@@
 Moreover, in $\cC_i$, the characters are just the integer vectors and the characters in the original CEFAs $\cB_i$ used to construct $\cC_i$ are ignored.
-The construction of $\amodel'(x_i)$ is actually to solve the reachability problems in a finite transition system where 
+The construction of $\amodel'(x_i)$ is actually to solve the reachability problem in a finite transition system where 
 \begin{itemize}
@@
 Moreover, the initial and final state of the reachability problem are set to be $(q_0, (\amodel(\anivarz_{i, \myvec{v}}))_{\myvec{v} \in \costset_{\cC_i}})$ and $(q_f, (0,\cdots, 0))$ for some initial state $q_0$ and final state $q_f$ in $\cB_i$.
-If a path from the initial state to the final state is found, then the path gives us a desired string $\amodel'(x_i)$.
+If a path from the initial state to the final state is found, then the path gives us a desired string $\amodel'(x_i)$. \qed
 }
@@
 %\qed
-
-\hdh{
-\subsection{Complexity Analysis of the $\reclsat$ Problem}
-The time complexity of regular expression equivalence with complement has been established as nonelementary~\cite{complementary_complexity_1974}.
-This directly implies that the $\reclsat$ problem exhibits a nonelementary lower bound.
-We now turn our attention to analyzing the complexity of the $\reclsat$ problem in the absence of complement operations (no occurrence of $\Bar{e}$ and $e_1 \backslash e_2$).
-
-\begin{lemma}\label{lemma:regex2cefa}
-    Register-representable regex without complement operation can be converted to CEFA in EXPSPACE.
-\end{lemma}
-
-\begin{proof}
-    We prove this lemma through structural induction on regular expression $e$.
-For the base case—where the regular expression consists of a single character, $\epsilon$, or $\emptyset$—the lemma holds trivially.
-    For the inductive cases, assuming the lemma holds for regular expressions $e_1$ and $e_2$:
-    When $e = e_1\concat e_2$ or $e = e_1+e_2$, the concatenation or union operations described in Section \ref{sec:automaton} produce a CEFA of size $O(2^{|e_1|} + 2^{|e_2|}) = O(2^{\max(|e_1|, |e_2|)}) = O(2^{|e|})$.
-    For $e = e_1\cap e_2$, the intersection operation detailed in Section \ref{sec:automaton} yields a CEFA of size $O(2^{|e_1|}\cdot 2^{|e_2|})=O(2^{|e_1| + |e_2|})=O(2^{|e|})$.
-    In the case of $e=e_1^{\{m,n\}}$, our construction in Section \ref{subsec:regex2cefa} avoids direct unfolding of counting operators, resulting in a CEFA of size $O(2^{|e_1|}) = O(2^{|e|})$.
-    Finally, for $e=(e_1)$ and $e=e^*$, our application of Thompson's construction~\cite{Thompson1968} produces a CEFA of size $O(2^{|e_1|}) = O(2^{|e|})$.
-\end{proof}
-
-\begin{theorem}\label{theorem_pspace}
-    If all regexes are register-representable and complement operations are excluded, $\reclsat$ can be solved in EXPSPACE.
-\end{theorem}
-\begin{proof}
-    Our decision procedure for $\reclsat$ with only register-representable regexes can be decomposed into two steps: (1) constructing CEFAs from regular membership and length function, (2) solving $\cefadec$.
-    Based on Lemma \ref{lemma:regex2cefa}, our construction yields a CEFA of exponential size for each register-representable regex without complement operation.
-Furthermore, for each string variable's length function, a CEFA of constant size is constructed in Section \ref{subsec:regex2cefa}.
-    Consequently, constructing CEFAs in the decision procedure outlined in Section \ref{subsec:regex2cefa} requires nondeterministic exponential size.
-After constructing CEFAs, the $\reclsat$ problem is transferred to the $\cefadec$ problem.
-By Proposition \ref{prop-cefadec}, we can demonstrate that the decision procedure likewise requires nondeterministic exponential size.
-Therefore, the complexity of the decision procedure for solving the restricted $\reclsat$ problem is NEXPSPACE, which yields EXPSPACE by Savitch's theorem~\cite{complexity-book}.
-\end{proof}
-
-\begin{theorem}
-    $\reclsat$ can be solved in 3-EXPTIME when complement operations are excluded.
-\end{theorem}
-
-\begin{proof}
-    Our decision procedure for $\reclsat$ with non-register-representable regexes can be decomposed into three steps: (1) unfolding non-register-representable occurrences of counting operators, (2) constructing CEFAs from regular membership and length function, (3) solving $\cefadec$.
-    From the decision procedure in Section \ref{subsec:regex2cefa}, unfolding non-register-representable occurrences of counting operators leads to an exponential growth in expression length.
-For each non-register-representable regular expression of length $l$, the unfolding process generates a register-representable regular expression of length $O(m^n\cdot l)=O((2^{|l|})^{|l|}\cdot l) = O(2^{|l|})$, where $m$ represents the maximum counting bound and $n$ denotes the maximum depth of nested counting operators.
-By Theorem \ref{theorem_pspace} and the fact that EXPSPACE $\subseteq$ 2-EXPTIME \cite{complexity-book}, the complexity of the decision procedure for solving the $\reclsat$ problem without complement operations is 3-EXPTIME.
-\end{proof}
-}

### 2025-01-05 2024-5-13/sections/cefa.tex
Final version of revision

@@
 The \emph{union} of $\aut_1$ and $\aut_2$ is denoted by $\aut_1 \cup \aut_2$.
-Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).\hdh{This is mainly because the same accepting condition is applied to all final states, in other words, the accepting condition does not distinguish between final states.} Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where
+Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$).
+\hdh{Note that the fresh auxiliary registers are introduced to distinguish whether $\aut_1$ or $\aut_2$ accepts and weave the two accepting conditions of $\aut_1$ and $\aut_2$ into one accepting condition.}
+%is mainly because the same accepting condition is applied to all final states, in other words, the accepting condition does not distinguish between final states.} 
+Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where 
 \begin{itemize}
@@
 Intuitively, $\aut_1 \cup \aut_2$ accepts the words that are accepted by one of the $\aut_1$ and $\aut_2$ and outputs the costs of the corresponding automaton.
+Note that an integer vector $\myvec{v}_1$ in $\aut_1$, is copied at most twice in $\aut_1 \cup \aut_2$, namely, $(\myvec{v}_1, \myvec{0}, 0,0)$ and $(\myvec{v}_1, \myvec{0}, 1,0)$.
+Simiarly for the integer vectors in $\aut_2$.
 

### 2025-01-05 2024-5-13/sections/heuristic.tex
Final version of revision

@@
 Let $\ufld_1(e)$ and $\ufld_2(e)$ denote the resulting regular expressions.
+\hdh{Note that in $\ufld_1(e)$, all the counting operators in $e_1$ (if there is any) disappear, while in $\ufld_2(e)$, all the counting operators in $e_1$ are preserved and copied for $n$ times.
+}
 
-\item We estimate the sizes of the two CEFAs $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ constructed from $\ufld_1(e), \ufld_2(e)$ respectively as pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$, where $\snum_1(e)$ and $\rnum_1(e)$ are the estimates of the number of states and registers in $\aut_{\ufld_1(e)}$, similarly for $\snum_2(e)$ and $\rnum_2(e)$.
+\item In the sequel, we estimate the sizes (the number of transitions) of
+the NFAs $\cU_{\aut_{\ufld_1(e)}}$ and $\cU_{\aut_{\ufld_2(e)}}$, denoted by $sz_1$ and $sz_2$.
+If $sz_1 \leq sz_2$, then we choose to unfold the counting operators in $e_1$.
+Otherwise, we choose to unfold the counting operator $^{\{m, n\}}$.
+%to make a decision whether to choose $ufld_1(e)$ or $ufld_2(e)$.
+
+\item To estimate the sizes of $\cU_{\aut_{\ufld_1(e)}}$ and $\cU_{\aut_{\ufld_2(e)}}$, we first estimate the sizes of the  CEFAs $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$   
+as \hdh{two pairs $(\snum_1(e), \anum_1(e))$ and $(\snum_2(e),\anum_2(e))$, where $\snum_1(e)$ and $\anum_1(e)$ are the estimates of the number of states and integer vectors in $\aut_{\ufld_1(e)}$ separately, similarly for $(\snum_2(e)$, $\anum_2(e))$.
+Since the NFAs $\cU_{\aut_{\ufld_1(e)}}$ and $\cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignore characters, $\snum_1(e)$ and $\anum_1(e)$ are the estimates of the number of states and characters of $\cU_{\aut_{\ufld_1(e)}}$, similarly for $\cU_{\aut_{\ufld_2(e)}}$.
+Then we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut_{\ufld_1(e)}}$ and $\cU_{\aut_{\ufld_2(e)}}$ as $sz_1 = (\snum_1(e))^2 \cdot \anum_1(e)$ and $sz_2 = (\snum_2(e))^2 \cdot \anum_2(e)$ respectively.}
 %
-\item From the construction in Section~\ref{sec:algorithm}, 
+\mycomment {\item From the construction in Section~\ref{sec:algorithm}, 
 two NFAs $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignoring the characters.
 As a result, the alphabets of $\cU_{\aut_{\ufld_\hdh{1}(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively.
-\hdh{Note that there is only one register in $\aut_{\ufld_1(e)}$.
-Because each occurrence of the counting operators in $\ufld_2(e)$ originates from the register-representable $e_1$, thus not in the scope of any Kleene star, counting, complement, or language difference, it follows that
-in $\aut_{\ufld_2(e)}$, the registers corresponding to these counting operators are updated independently, that is, the integer vectors of  $\aut_{\ufld_2(e)}$ are of the form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{\rnum_1(e)-i-1})$, where $i \in [\rnum_2(e)]$.} Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$.
-Similarly for $\cU_{\aut_{\ufld_\hdh{2}(e)}}$.
+\hdh{Note that there is only one register and two integer vectors in $\aut_{\ufld_1(e)}$, in other words, the number of registers and the alphabet size are fixed.
+}
 Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut_{\ufld_1(e)}}, \cU_{\aut_{\ufld_2(e)}}$ as $sz_1 = (\snum_1(e))^2 \cdot \rnum_1(e)$ and $sz_2 = (\snum_2(e))^2 \cdot \rnum_2(e)$ respectively.
-\zhilin{to be checked}
+\zhilin{to be checked}}
 %
-\item If $sz_1 \le sz_2$, then we choose to unfold the counting operators in $e_1$. Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$. 
+%\item If $sz_1 \le sz_2$, then we choose to unfold the counting operators in $e_1$. Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$. 
 \end{itemize}
@@
 
-It remains to show how to compute the pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$ from $e=(e_1)^{\{m,n\}}$.
+\hdh{It remains to show how to compute $(\snum_1(e), \anum_1(e))$ and $(\snum_2(e),$ $ \anum_2(e))$ from $e=(e_1)^{\{m,n\}}$.
 Let $e=(e_1)^{\{m,n\}}$ be a regular expression where $e_1$ is a register-representable regular expression.
-Then we compute $\snum'_1(e_1)$ and $(\snum'_2(e_1), \rnum'_2(e_1))$.
-Finally, let $(\snum_1(e), \rnum_1(e)) = (\snum'_1(e_1), 1)$ and $(\snum_2(e), \rnum_2(e)) = (\snum'_2(e_1), \rnum'_2(e_1))$.
+Note that there is only one register in $\aut_{\ufld_1(e)}$.
+As a result, we set $\anum_1(e) = 2$.
+Moreover, in the sequel, we inductively compute $\snum'_1(e_1)$ and $(\snum'_2(e_1), \anum'_2(e_1))$ from $e_1$, then let $\snum_1(e)  = \snum'_1(e_1)$ and $(\snum_2(e), \anum_2(e)) = (\snum'_2(e_1),$ $ \anum'_2(e_1))$.
 \begin{itemize}
-  \item If $e_1 = \emptyset$ or $e_1 = \epsilon$, then $\snum'_1(e_1)  = 0$ and $(\snum'_2(e_1), \rnum'_2(e_1))  = (0, 0)$. 
+  \item If $e_1 = \emptyset$ or $e_1 = \epsilon$, then $\snum'_1(e_1)  = 0$ and 
+  $$
+  \begin{array}{l}
+    (\snum'_2(e_1), \anum'_2(e_1))  = (0, 0).
+  \end{array}
+  $$
+  (Note that here the constant $0$, instead of $1$, is chosen, so that later on, when we consider $e_1 = e_2 \cap e_3$, $\snum'_2(e_2) \times \snum'_2(e_3)$ and $\vnum'_2(e_2) \times \vnum'_2(e_3)$ will become 0 since $\epsilon\cap e_3 = \epsilon$ and $\emptyset\cap e_3 = \emptyset$)
 %
-  \item \hdh{If $e_1 = a$, then $\snum'_1(e_1) = 1$ and ($\snum'_2(e_1), \rnum'_2(e_1)) = (n, 0)$.}
+  \item If $e_1 = a$, then $\snum'_1(e_1) = 2$ and 
+  $$
+  \begin{array}{l}
+    (\snum'_2(e_1), \anum'_2(e_1)) = (2n, 1).
+  \end{array}
+  $$
  %
@@
   \begin{array}{l }
- (\snum'_2(e_1), \rnum'_2(e_1)) =  \\
-  \ \ \ \ (n(\snum'_2(e_2) + \snum'_2(e_3)), n(\rnum'_2(e_2) + \rnum'_2(e_3))).
+ (\snum'_2(e_1), \anum'_2(e_1)) = \\
+ \ \ \ \ (  n(\snum'_2(e_2) + \snum'_2(e_3)), n(\anum'_2(e_2) + \anum'_2(e_3))).
  \end{array}
   $$
+  Note that because $e_1$ is concatenated for $n$ times in $\ufld_2(e)$, we define $\snum'_2(e_1)$ as  $n(\snum'_2(e_2) + \snum'_2(e_3))$.
+Moreover, since the integer vectors in $\aut_1 \cdot \aut_2$ are of the form $(\myvec{v}_1,\myvec{0})$ and $(\myvec{0}, \myvec{v}_2)$ where $\myvec{v}_1$ and $\myvec{v}_2$ are integer vectors in $\aut_1$ and $\aut_2$ respectively, we define $\anum'_2(e_1)$ as $n(\anum'_2(e_2) + \anum'_2(e_3)))$.
 %
@@
   \begin{array}{l }
- (\snum'_2(e_1), \rnum'_2(e_1)) =  \\
-  \ \ \ \ (n(\snum'_2(e_2) + \snum'_2(e_3)), n(\rnum'_2(e_2) + \rnum'_2(e_3)+1)).
+ (\snum'_2(e_1), \anum'_2(e_1)) =  \\
+  \ \ \ \ (n(\snum'_2(e_2) + \snum'_2(e_3)+1),   n(2\anum'_2(e_2) + 2\anum'_2(e_3))).
  \end{array}
   $$
- (Recall that the construction of $\aut_1 \cup \aut_2$ introduces one additional register.)
+ (Recall that each integer vector in $\aut_1$ resp. $\aut_2$ is copied at most twice in the construction of $\aut_1 \cup \aut_2$.)
 %
@@
   \begin{array}{l }
- (\snum'_2(e_1), \rnum'_2(e_1)) =  \\
-  \ \ \ \ (n(\snum'_2(e_2) \times \snum'_2(e_3)), n(\rnum'_2(e_2) + \rnum'_2(e_3))).
+ (\snum'_2(e_1), \anum'_2(e_1)) =  \\
+  \ \ \ \ (n(\snum'_2(e_2) \times \snum'_2(e_3)),  n(\anum'_2(e_2) \times \anum'_2(e_3)) 
+  ).
  \end{array}
   $$
+  (Recall that the integer vectors in $\aut_1 \cap \aut_2$ are of the form $(\myvec{v}_1, \myvec{v}_2)$, where $\myvec{v}_1$ and $\myvec{v}_2$ are the integer vectors in $\aut_1$ and $\aut_2$ repsectively.)
 %
@@
 %
-  $
-%  \begin{array}{l }
- (\snum'_2(e_1), \rnum'_2(e_1)) =  (n \cdot 2^{\snum'_2(e_2)}, 0).
-% \end{array}
-  $
- (The exponential blow-up is explained by the fact that the determinization is needed for the complementation.) 
+  $$
+ \begin{array}{l }
+ (\snum'_2(e_1), \anum'_2(e_1)) = (n \cdot 2^{\snum'_2(e_2)}, 1).
+ \end{array}
+  $$
+ (In this case, since $e_1$ is register-representable, we know that $e_2$ contains no counting operators.
+As a result, we first construct the NFA for $e_2$, then determinize and complement it to construct the automaton for $e_1$.)
 %
@@
 %
-  $
-%  \begin{array}{l }
- (\snum'_2(e_1), \rnum'_2(e_1)) =  (n \snum'_2(e_2), 0).
-% \end{array}
-  $
+  $$
+ \begin{array}{l }
+ (\snum'_2(e_1), \anum'_2(e_1) =  (n \snum'_2(e_2), 1).
+ \end{array}
+  $$
+  (In this case, since $e_1$ is register-representable, we know that $e_2$ contains no counting operators.)
 %  \item If $\regex = \regex_1^*$, then $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 0$.
@@
 %
-  $
-%  \begin{array}{l }
- (\snum'_2(e_1), \rnum'_2(e_1)) =  (n \snum'_2(e_2), n).
-% \end{array}
-  $
+  $$
+ \begin{array}{l }
+ (\snum'_2(e_1), \anum'_2(e_1)) =  (n \snum'_2(e_2), n).
+\end{array}
+  $$
+  (In this case, since $e_1$ is register-representable, we know that $e_2$ contains no counting operators.)
 %  \item For $\regex = \regex_1^{\{m, n\}}$ or $\regex = \regex_1^{\{n,\infty\}}$, $s_{\regex} = s_{\regex_1}$ and $r_{\regex} = 1$.
 \end{itemize}
-
+}
 %The naive approach for nested counting in the paper \cite{Denghang2023} is to unwind all inner counting operators.
@@
 \hdh{\paragraph*{Combination of under- and over-approximation}
- In our configuration, under-approximation is performed first due to its superior computational efficiency, and we proceed with over-approximation if it yields an unsatisfiable result.
-When the under-approximation yields an unsatisfiable result and the over-approximation yields a satisfiable result, we employ the decision procedure to obtain an answer, which implies that our approach is sound and complete.
+ We combine the under- and over-approximation as well as the decision procedure into the following procedure.  
+ \begin{enumerate}
+ \item We first apply the under-approximation.
+ \item If the under-approximation returns ``sat'', then we know that the original constraint is satisfiable. Otherwise, the under-approximation returns ``unsat'' and we apply the over-approximation.
+ \item If the over-approximation returns ``unsat'', then we know that the original constraint is unsatisfiable.
+Otherwise, the over-approximation returns ``sat'' and we resort to the decision procedure (without approximations) in Section~\ref{sec:algorithm} to solve the RECL constraint.
+ \end{enumerate}
+% In our configuration, under-approximation is performed first due to its superior computational efficiency, and we proceed with over-approximation if under-approximation yields an "unsat" result.
+If the over-approximation yields a "sat" result, we employ the decision procedure to obtain an answer, which implies that our approach is sound and complete.
 To minimize computational overhead, we apply approximation techniques only in cases involving non-register-representable regular expressions with significant counting bounds—specifically, those exceeding 20 in our experimental configuration.
@@
 
-\zhilin{Double check}
+%\zhilin{Double check}
 
 %\zhilin{TODO: I had troubles to understand the section about optimized model generation. Maybe stating what the technical problem that it is solving is in a more dumb proof way would help., }
+
+Recall that in Step 5 of Section~\ref{sec:algorithm}, we construct a solution $\amodel'$ from the model $\amodel$ of the LIA formula in Equation~(\ref{eq:parikh_image}) by solving the reachability problems in a finite transition system.
+It is easy to see that the transition system contains exponentially many nodes in general and a naive search over the transition system is not efficient.
+In the sequel, we describe two optimizations so that the reachability problem can be solved more efficiently.
+
+\hide{
 Recall that in Section~\ref{sec:algorithm}, the satisfiability of the original RECL constraint is reduced to the satisfiability of the existential LIA formula
@@
 We first describe the naive algorithm of generating $\amodel'$ from $\amodel$. Then we show how we optimize this model generation process. 
+}
 
@@
 
+\hide{
 \paragraph*{A naive algorithm for model generation}
@@
 To alleviate the path-explosion problem, in the sequel, we propose two techniques to reduce the number of transitions of the transition system.
+}
 
@@
 
+To ease the presentation, let us assume that $n$, i.e. the number of string variables, to be $1$.
+
 At first, we refine the states of the transition system by recording the number of transitions, instead of just the number of occurrences of the integer vectors.
@@
 \paragraph*{Refining the states of the transition system by recording the number of transitions}
-We shall construct the formula $\theta'$ so that a model of $\theta'$ includes the information about the number of occurrences of the transitions of $\cB_1$.
+Let $\theta$ denote the formula in Equation~(\ref{eq:parikh_image}).
+We shall construct the formula $\theta'$ so that any model of $\theta'$ necessarily encodes the number of occurrences of transitions within $\cB_1$.
 \[
@@
 Note that compared to $\theta$, $\theta'$ uses the LIA formula $\psi_{\cB_1}$, which is constructed from $\cB_1$ by ignoring its accepting condition and taking it as an NFA where the alphabet is seen as the set of transitions.
-Moreover, $\theta'$ relates the values of the variables $\anivarz_{1, \myvec{v}}$ and $\anivarz_{1, (q, a, q', \myvec{v})}$, as well as restricts that the values of $\anivarz_{1, \myvec{v}}$ should be $\amodel(\anivarz_{1, \myvec{v}})$.
-We then submit $\theta'$ to some SMT solver, which returns a model for $\theta'$, in particular, the values of the variables $\anivarz_{1, (q, a, q', \myvec{v})}$.
+Furthermore, $\theta'$ relates the values of the variables $\anivarz_{1, \myvec{v}}$ and $\anivarz_{1, (q, a, q', \myvec{v})}$, while simultaneously constraining the values of $\anivarz_{1, \myvec{v}}$ to be $\amodel(\anivarz_{1, \myvec{v}})$.
+We then submit $\theta'$ to SMT solver, which returns a model of $\theta'$, in particular, the values of the variables $\anivarz_{1, (q, a, q', \myvec{v})}$.
 Equipped with the model, we refine the transition system by considering the nodes $(q, (\nvec_{1, (q, a, q', \myvec{v})})_{(q, a, q', \myvec{v})\mbox{ is a transition in } \cB_1})$, where $\nvec_{1, (q, a, q', \myvec{v})}$ denotes the number of remaining occurrences of $(q, a, q', \myvec{v})$.
-Note that this refinement can reduce the number of transitions.
+Note that this refinement can avoid searching useless transitions.
 For instance, if $\nvec_{1, (q, a, q', \myvec{v})} = 0$ for some $(q, a, q', \myvec{v})$, then we can avoid searching the transition $(q, a, q', \myvec{v})$ out of $q$.
-On the other hand, if in the original transition system where $\nvec_{1, \myvec{v}}$ is used, then it may be the case that we have $\nvec_{1, \myvec{v}} > 0$ (since there may be multiple transitions associated with $\myvec{v}$) and the transition $(q, a, q', \myvec{v})$ should still be searched.
+This stands in contrast to the original transition system where $\nvec_{1, \myvec{v}}$ is used, it may be the case that we have $\nvec_{1, \myvec{v}} > 0$ (since there may be multiple transitions associated with $\myvec{v}$) and the transition $(q, a, q', \myvec{v})$ should still be searched.
 
@@
 Let the current state of the transition system be $(p, (\nvec_{1, (q, a, q', \myvec{v})})_{(q, a, q', \myvec{v})\mbox{ is a transition in } \cB_1})$. 
-Let us compute the set of transitions of $\cB_1$ that are reachable from the state $p$.
-Let $\cT_p$ denote this set.
-If $\{(q, a, q', \myvec{v}) \mid \nvec_{1, ((q, a, q', \myvec{v}))} > 0\} \not \subseteq \cT_p$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_1$ will be found and meanwhile the constraint on the number of transitions enforced by $\nvec_{1, (q, a, q', \myvec{v})}$ is satisfied.
-Therefore, in this case, we can remove all the transitions out of $(p, (\nvec_{1, (q, a, q', \myvec{v})})_{(q, a, q', \myvec{v})\mbox{ is a transition in } \cB_1})$ and the search halts in this state and is backtracked.
+Let $\cT_p$ denote the set of transitions that are reachable from the state $p$ in $\cB_1$.
+If $\{(q, a, q', \myvec{v}) \mid \nvec_{1, (q, a, q', \myvec{v})} > 0\} \not \subseteq \cT_p$, in other words, there exists some transitions $(q, a, q', \myvec{v})$ not reachable from the state $p$ in $\cB_1$ while $\nvec_{1, (q, a, q', \myvec{v})} > 0$ is established in the current state $(p, (\nvec_{1, (q, a, q', \myvec{v})})_{(q, a, q', \myvec{v})\mbox{ is a transition in } \cB_1})$, then we know that it is impossible to reach the final state $(q_f, (0,\cdots, 0))$ from the current state so that we can remove all the transitions out of the current state in the transition system.
 

### 2025-01-05 2024-5-13/sections/implementation.tex
Final version of revision

@@
 
-In total, the NestC benchmark suite contains 1000 \hdh{tough} instances, \hdh{where the regexes and their associated counting bounds are generated randomly.}
+In total, the NestC benchmark suite contains 1000 instances.
+
+\hdh{Note that the two templates are chosen so that on the one hand, the nestings of counting operators or nestings of counting operators and complement operators are available, and on the other hand, some additional regular and length constraints are introduced, so that the constraints are not trivially satisfied, in particular, the constraints are not satisfied by very short strings.
+}
+
+\hide{
+\hdh{where the regexes and their associated counting bounds are generated randomly.
+
+It is sufficient to utilize only one string variable in the template, as there is no interaction between different string variables.
+Moreover, the depth of nested counting is set to 2 in the template since it is the most common case in real-world programs.
+Concerning string variable length constraints, there exists a positive correlation between bound value and instance complexity.
+Therefore, we employ two fixed length bounds—a smaller one $10$ and a larger one $50$—to encompass both simple and complex instances.
+Finally, all the features in Fig.\ref{fig:syntax} except counting and complement are randomly generated on the regexes of the template.
+}
+}
 

### 2025-01-05 2024-5-13/sections/overview.tex
Final version of revision

@@
 Next, 
-we construct $\aut_1 \cap \aut_2 \cap \aut_3$, that is, the intersection (aka product) of $\aut_1$, $\aut_2$, and $\aut_3$, as illustrated in Figure~\ref{fig:overview:product}(a), where the states can not reach the final states are removed.
+we construct $\aut_1 \cap \aut_2 \cap \aut_3$, that is, the intersection (aka product) of $\aut_1$, $\aut_2$, and $\aut_3$, as illustrated in Figure~\ref{fig:overview:product}(a), where the states that cannot reach the final states are removed.
 For technical convenience, we also think of the updates of registers in transitions as vectors $(u_1, u_2, u_3, u_4)$, where $u_i \in \Int$ is the update on the register $r_{i}$ for each $i \in [4]$.
